### 2013-05-21 tex/bytecode.tex
Added stuff

\section{Bytecodes}

PUTFIELD needs to remove path constraints from PC that enforcing equality between references.

\noindent \textbf{Assume}: all symbolic locations are concertized lazily. Although the algorithm is not specific to any particular initialization strategy, the presentation assumes a lazy initialization. Extending to lazier initialization may be non-trivial even though this reduction is orthogonal to the lazier reduction (i.e., this reduction should further improve the performance of the lazier algorithm).

\noindent \textbf{Assume}: all variables, symbolic or otherwise, are non-primitive (i.e. objects). \textit{Must relax this assumption because you need to do some interesting things with primitives as they relate to getfield}.

This papers uses subsumption, which is expressed as a subtyping relation $\leq$ over types $T$. For classes $C$ and $D$, $C \leq D$ iff either $C = D$ or the class declaration for $C$ is \texttt{class C extends B $\{\ldots\}$} for some $B \leq D$. For example, in $A \leq B \leq C \leq D$, $D$ is the supertype, and if you have something that is an instance of $A$ but currently viewed as $B$, then you can move it toward $D$ in a typecast (up the hierarchy).

Heap locations range over positive natural numbers $H \subseteq \mathbb{N}_{\geq 0}$. Every heap location has a special variable $T_h$ used in constraints over the type of the object stored in the heap location. The varable $\mathit{SH}$ is the set of heap locations created when concretizing symbolic variables. The set of constraints over the type stored in the heap location is given by the function $\mathtt{C}(h)$. Constraints are of the form $T_h \sim T$ or $T \sim T$ where $\sim\ \in \{\leq, =, \not =\}$. The initial type hierarchy for the program is expressed as a set of constraints $C_\mathrm{init}$. The set contains all relationships needed to describe the entire hierarchy.

For a set of constraints $C$, the function $\mathtt{SAT}(C) \mapsto \{0,1\}$ returns 1 if the constraints are satisfiable and 0 otherwise. The usual Boolean connectives are used as expected. The function $\mathtt{Type}(h)$ returns the actual type of the object in the heap location and the function $\mathtt{Obj}(h)$ returns the object at the location.

Each variable $v$ is associated with a set of heap locations $H(v) = \{h_0, h_1, \ldots, h_n\}$ that represents an equivalence class (i.e., each heap location yields the same execution path and behavior up to the current point of execution).  The representative object for a given variable (i.e., the one that is currently being used by the variable) is given by the function $I(v) \mapsto H(v)$. The set of heap locations and the representative location are part of the meta-deta for the variable. This meta-data follows the variable through the program execution and is appropriately copied on assignment to other variables such that each variable has its own copy of the meta-data that is separate from other copies.

Finally, there is a global variable $\mathit{PC}$ that represents the path constraint along the current path of exploration. This path constraint is used to track relationships between symbolic variables such as equality. Properties of symbolic variables are represented in the path constraint by creating special variables for the representative and the set of represented objects. For a variable $v$, the special variable $I_v$ is the representative heap opbject and the special variable $H_v$ is the set of associated heap locations. It is assumed the $v$ is alpha-renamed to be unique in the path constraint. Finally, we use the special value \texttt{SYM} to denote a symbolic variable that is yet to be initialized.

\subsection{Reference}
\noindent \textbf{\texttt{GETFIELD}}: the bytecode behavior depends on the field operand: concrete, concrete though initialized from symbolic, and symbolic. Each case is enumerated:
\begin{compactenum}
\item Referencing a concrete field: the bytecode has default behavior returning the field.
\item Referencing an initialized field from a symbolic variable (i.e., the base type for the field is initialized from a symbolic object): the bytecode may have multiple outcomes; it partitions the equiavalence class to group heap locations with objects that have common values for the field.
\item Referencing a symbolic variable that has yet to be initialized: the bytecode has two outcomes: one that returns \texttt{null} and another that builds the potential equivalence class, chooses a representative location, and returns that location.
\end{compactenum}
Consider the code
\begin{lstlisting}
// The declared type of f is F
T t = b.f;
\end{lstlisting}
For the case where \texttt{b.f} is an already initialized symbolic variable, $h = \mathtt{I}(\mathtt{b})$, $\mathtt{H}(\mathtt{b})$ is partitioned into disjoint sets, $S_0, P_1, \ldots, P_n$, with $n+1$ partitions, or choices. The first set $S_0$ is a special set that includes $h$, the representative object for \texttt{b}, and any members of the equivalence class that either have the same field value for \texttt{b.f} or the field value is a symbolic variable that has yet to be initialized:
\begin{eqnarray*}
S_0 &=& \{h_i \mid h_i \in \mathtt{H}(\mathtt{b})\ \wedge \\
    & & (\mathtt{Obj}(h).\mathtt{f} = \mathtt{Obj}(h_i).\mathtt{f}\ \vee\ \mathtt{Obj}(h_i).\mathtt{f} = \mathtt{SYM})\}
\end{eqnarray*}
For this special case of $S_0$,  $\mathtt{H}_0(\mathtt{b}) = S_0$, and $I_0(\mathtt{b}) = h$ where the subscript indicates the choice number in the choice generator (i.e., the partition size may change but not the representative heap location). The other partitions group common values of the field such that
\begin{compactitem}
\item $\forall h_i, h_j \in P_i,\ \mathtt{Obj}(h_i).f = \mathtt{Obj}(h_j).f$ 
\item $\mathtt{H}_i(\mathtt{b}) = P_i$ 
\item $\exists h \in P_i,\ \mathtt{I}_i(\mathtt{b}) = h$
\end{compactitem}
The partitions are maximal and represent a unique value that has been created thus far in the program execution. The non-initialized symbolic members of the partition all belong to $S_0$ as the original representative heap location $h$ captures that these other aliases were intended to have the same field value for field \texttt{f} before the split (i.e., the value is assigned programatically but the change was only reflected in the representative heap location). Once the choice generator is created over the different partitions, the bytecode returns the requested field value of the representative as expected.

Returning to the third behavior of the bytecode, the case in which the accessed field has yet to be initialized, then the bytecode follows lazy initialization creating a \texttt{null} instance, a new instance that is the representative, and the alias set. When creating the alias set, the new instance should be included in the set, as well as any prior object created in concretization of symbolic variables that is type compatible with the new instance. Recall that $\mathit{SH}$ is set of locations in the symbolic heap and $C_\mathrm{init}$ is the set of constraints describing the type hierarchy, assuming $h$ is the heap location of the new instance of the type, then 
\begin{compactitem}
\item $\mathtt{I}(\mathtt{b.f}) = h$
\item $\forall h_i \in \mathit{SH}, \mathtt{SAT}(C_\mathrm{init} \cup \{T_h \leq \mathtt{Type}(h_i)\}) \rightarrow h_i \in \mathtt{H}(\mathtt{b.f})$  
\item $\mathtt{C}(\mathtt{b.f}) = C_\mathrm{init} \cup \{T_h \leq \mathtt{Type}(h)\}$  
\end{compactitem}
The $C_\mathrm{init}$ set constains relationships in the class hierarchy with the correct sub-types and super-types as they relate to the delcared type of the object.

\noindent \textbf{\texttt{GETSTATIC}}: the bytecode is handled similarly to \texttt{GETFIELD}.

\noindent \textbf{\texttt{ALOAD}}: the bytecode is handled similarly to \texttt{GETFIELD}.

\subsection{Comparison}

\noindent \textbf{\texttt{IF\_ACMPEQ}}: the bytecode may return both the \texttt{true} and \texttt{false} values, and it must possibly refine the set of represented concretizations and mutate the heap location of the object involved in the bytecode according to the returned outcome. Consider the code
\begin{lstlisting}
if (a == b) {
   // code...
}
\end{lstlisting}
There are two cases that need to be considered to determine the outcome of the bytecode:
\begin{compactenum}
\item $\mathtt{H}(a) \cap \mathtt{H}(b) = \emptyset$: the bytecode returns \texttt{false} and nothing further is requred.
\item $\mathtt{H}(a) \cap \mathtt{H}(b) \not = \emptyset$ $\wedge$ $\mathtt{SAT}(PC \cup \{I_a = I_b, H_a = H_b\})$: the bytecode may return either \texttt{true} or \texttt{false} and a choice generator needs to be created.
\end{compactenum}
The choice generator for the compare bytecode is more complex than for other bytecodes because it must create representative sets without enumerating all possible outcomes using the path constraint. For the case \texttt{true} outcome
\begin{compactitem}
\item $\mathit{PC} = \mathit{PC} \cup \{\mathtt{I}(a) = \mathtt{I}(b),\mathtt{H}(a) = \mathtt{H}(b)\}$
\item $\mathtt{H}(a) = \mathtt{H}(b) = \mathtt{H}(a) \cap \mathtt{H}(b)$
\item $\mathtt{I}(a) \in \mathtt{H}(a) \cap \mathtt{H}(b) \rightarrow \mathtt{I}(b) = \mathtt{I}(a)$ $\vee$ $\exists h \in \mathtt{H}(a) \cap \mathtt{H}(b)\ .\ \mathtt{I}(b) = \mathtt{I}(a) = h$
\end{compactitem}
In essence, in the case where two variable reference the same object, the path constraint and sets are modified to represent the new restriction. The \texttt{false} outcome is handled similarly with a few notable exceptions on the path constraint and the represented set.
\begin{compactitem}
\item $\mathit{PC} = \mathit{PC} \cup \{\mathtt{I}(a) \not = \mathtt{I}(b)\}$
\item $\mathtt{I}(a) = \mathtt{I}(b) \rightarrow \exists h \in \mathtt{H}(b)\ .\ h \not = \mathtt{I}(a) \wedge \mathtt{I}(b) = h$
\end{compactitem}

\noindent \textbf{\texttt{IF\_ACMPNE}}: the bytecode is handled similarly to \texttt{IF\_ACMPEQ}.

\subsection{Invocation}
\textbf{\texttt{INVOKEVIRTUAL}}

When we come to an invoke virtual you have to look for all the specialized implementations
of the method, creating choices with symbolic locations of various "actual types". The number
of choices will be equal to the number of specialized implementations of the method. When you create a choice on a specialization, you need to update the "actual type" field in the symbolic location. The "current cast" does not need to change. The number of types that the symbolic location cannot be will also be updated according to the "actual type" field. The number of types that the symbolic location cannot be will be updated with the types of the other specializations since invoking a specialization associated with a type implies that the object cannot be the types containing the other specializations.

\subsection{Checking Types and Casting}
\noindent\textbf{\texttt{INSTANCEOF}}: the bytecode may return both the \texttt{true} and \texttt{false} values when dealing with initialized symbolic variables, and it must possibly refine the equivalence class for the represented object referenced by the variable and mutate the contents of the heap location of the object involved in the bytecode according to the returned outcome. The bytecode implements the default bahvior when the operand is concrete and not an initialized symbolic variable. For the rest of the discussion, assume the operand is an initialized symbolic variable.
Consider the code
\begin{lstlisting}
if (a instanceof C) {
   // code...
}
\end{lstlisting}
There are two cases that need to be considered to determine the outcome of the bytecode where $h = \mathtt{I}(a)$ is the representative object of the equivalence class:
\begin{compactenum}
\item $\mathtt{Type}(h) = C$: the bytecode returns \texttt{true} and nothing further is required as the type stored in the heap location is $C$.
\item $\neg \mathtt{SAT}(\mathtt{C}(h) \cup \{T_h \leq C\})$: the bytecode returns \texttt{false} and nothing further is requred as the current constraints on what is in the heap location restrict it from being of type $C$.
\item $\mathtt{SAT}(\mathtt{C}(h) \cup \{T_h \leq C\})$: the bytecode can return either \texttt{true} or \texttt{false} requiring a choice generator.
\end{compactenum}
% // C <= B <= A
% A a; // C(a) = {(T_a <= A)}
%
%if (a instance of C) {
%    ** TRUE **
%    (T_h \leq C)
%    ...
%}
% ** FALSE **
% (C \leq T_h) \wedge (T_h \not = C)
% ** TRUE **
% (T_h \leq C)
\noindent The \texttt{true} outcome for the choice generator in clause (3) is
\begin{compactitem}
    \item $\mathtt{C}(h) = \mathtt{C}(h) \cup \{T_h \leq C\}$
    \item $\mathtt{Type}(h) = C$
    \item $\mathtt{H}(a) = H^\prime$ where $H^\prime = \{h_i \mid h_i \in \mathtt{H}(a) \wedge \mathtt{SAT}(\mathtt{C}(h_i) \cup \{T_{h_i} \leq C\})\}$ 
\end{compactitem}
The second statement indicates that the actual type in the heap location $h$ needs to change. As such, the object is mutated to be an instance of $C$. This mutation retains all fields and values from the previous object and only adds new fields for type $C$. The last statement refines the equivalence class to exclude any heap locations that cannot be considered something of type $C$.

For the \texttt{false} outcome of the generator, $\mathtt{C}(h) = \mathtt{C}(h) \cup \{C \leq T_h, T_h \not = C\}$. Unlike the \texttt{true} outcome, the \texttt{false} outcome retains the entire equivalence class and does not need to mutate any heap entries.

\noindent\textbf{\texttt{CHECKCAST}}: the bytecode is syntactic sugar for 
\begin{lstlisting}
if (! (obj == null  ||  obj instanceof <class>)) {
    throw new ClassCastException();
}
// if this point is reached, then object 
// is either null, or an instance of <class> 
// or one of its superclasses.
\end{lstlisting}
Please see the \texttt{IFNULL} and \texttt{INSTANCEOF} bytecodes for details. If the exception is thrown, then JPF will catch the unhandled exception as per its normal behavior.

\subsection{Programs to consider}
\begin{compactitem}
\item \texttt{TestGetfieldSplit.java}: checks alias equivalence classes when assigning to initialized values.
\end{compactitem}

### 2013-06-14 tex/execution.tex
Adde intro,results,state, and execution sections

\section{Semantic Model}
Program execution proceeds an in standard symbolic execution, with additional rules to handle heap constructs. The Java Virtual Macine (JVM) implements five classes of semantic rules, a categorization which we find relevant to symbolic execution: 1) load/store instructions, 2) arithmetic instructions, 3) object creation / manipulation instructions, 4) control transfer instructions, and 5) assume/assert instructions. We will deal with each class of instruction in sequence.
\subsection{Reference Target Resolution}
Load and store instructions take symbolic references as arguments. Since an uninitialized symbolic reference may point to any one of a number of symbolic locations, we need to be able to resolve which locations are feasible targets of a particular references.
Location resolution begins with an empty list of heap locations, and then adds locations by comparing locations on the symbolic heap to the constraints on the symbolic reference obtained from the abstract store. Locations are checked in the following order:
\begin{compactenum}
\item If the null location is feasible, return a null pointer exception and terminate execution.
\item If the non-null location is feasible, create a new symbolic location of the proper type and add it to the symbolic heap. Search the heap for type-compatible objects and add those to the symbolic value set for the reference, and remove the non-null location from the symbolic value set.
\item Check the symbolic heap for type-compatible objects, comparing those against the constraints in the symbolic value set. Add any feasible objects to the feasible location set.
\end{compactenum}

\subsection{Read}
The load instruction has two arguments: a reference $r$ and a field index $f$. If $r$ is a symbolic location, then load simply accesses the field and returns the value contained there. If $r$ is a symbolic reference, then the following steps are taken, in order.
\begin{compactenum}
\item Resolve a list of feasible targets as described above.
\item Access the fields of the feasible targets, gathering a set of the symbolic values contained therein. 
\item Form a new symbolic value, and create a new entry in the symbolic store mapping the value to the symbolic value set. Return the new symbolic value.
\end{compactenum}

\subsection{Write}
The write instruction takes three arguments: a reference $r$, a field $f$, and a value $v$. If $r$ is a symbolic location, then the target field is written with the value directly. If $r$ is a symbolic reference, write proceeds as follows:
\begin{compactenum}
\item Resolve a list of feasible targets.
\item Access the fields of the feasible targets, performing a conditional write. The conditional write works by modifying the constraint equation as follows:
\newline  ((A==h_n) => F==V) and (~(A==h_n) => Eqn_o_l_d)
\end{compactenum}

\subsection{Arithmetic Instructions}
\subsection{Object Creation/Manipulation Instructions}
\subsection{Control Transfer Instructions}
\subsection{Assume / Assert Instructions}

### 2013-06-14 tex/intro.tex
Adde intro,results,state, and execution sections

\section{Introduction}

\newcommand{\Indstate}[1][1]{\State\hspace{#1\algorithmicindent}}

\begin{figure}
\begin{center}
\begin{algorithmic}[1]
\Procedure{load}{$r,f$}
\If{$r$ is initialized and $f$ is uninitialized}
\If{ $f$ has a reference type}
\State nondeterministically assign to $f$:
\State  \ \ null  %hacky way to indent.
\State \ \ non-null
\EndIf
\If{$f$ has a primitive type}
\State assign $f$ a new symbol
\EndIf
\EndIf
\If{$r$ is uninitialized}
\State nondeterministically assign to $f$:
\State  \ \ a new symbolic location  %hacky way to indent.
\State \ \ an existing symbolic location
\EndIf
\State\Return $r.f$
\EndProcedure
\end{algorithmic}
\end{center}
\caption{Lazier\# Initialization}
\end{figure}

Lazy initialization is a symbolic execution technique where memory structures are created on-demand, as they are required.

### 2013-06-14 tex/state.tex
Adde intro,results,state, and execution sections

\section{System State}
The program state is represented using a path condition, a program location, a stack, a symbolic heap, and a symbolic store. The path condition is a collection of predicates over the program inputs that indicates constraints on the values of those inputs at the present location. The program location indicates the instruction to be executed presently. The symbolic heap is a mapping from heap locations symbolic objects. 
\paragraph{Heap Symbols}
Heap symbols are symbols which are created and destroyed in the process of performing heap operations. The dynamic nature of heap symbols distinguishes them from statically-created symbols like tbose found in the path condition. Heap symbols may be symbolic primitives, symbolic references, symbolic locations, or symbolic types.
\paragraph{Symbolic References}
Symbolic references are symbolic points-to relations. The symbolic reference has a state parameter that indicates whether the reference is uninitialized, non-null, or initialized. The uninitialized and non-null states indicate that the location pointed to by the reference has yet to be resolved. The non-null state reflects the additional constraint that the reference does not point to the null location. References in the initialized state are assosciated with constraints reflecting which location the reference points to and under what condition it points to that location. References point to one and only one location at a time, so the conditions must be mutually exclusive, yet collectively exhaustive.
\paragraph{Symbolic Locations}
Symbolic locations represent the locations of slots in the heap structure that may hold symbolic objects. Each symbolic location represents a unique slot on the symbolic heap. The constraints assosciated with symbolic locations reflect the uniqueness of each location. Each slot on the heap may contain a symbolic object. 
\paragraph{Symbolic Objects}
A symbolic object represents the contents of a heap slot. A symbolic object contains a symbolic type paired with a mapping from fields to heap symbols.
\paragraph{Symbolic Store}
The symbolic store is a mapping from heap symbols to symbolic value sets. The symbolic value set represents the values that may be assigned to the symbol, along with the constraints assosciated with each value. Taken together, the constraints in the abstract store represent a set of unique heaps common to the current program execution path. Compare this to the path condition, which contains constraints common to all the heaps in the abstract store.
\paragraph{Heap}
The symbolic heap is a mapping from symbolic locations to symbolic objects. Like the path condition, the symbolic heap contains heap state which is common to all heaps on the current execution path. Unlike the path condition, the symbolic heap does not contain any logical constraints.
\paragraph{Stack}
The Java Virtual Machine uses a system stack.

### 2013-06-14 tex/execution.tex
Refined the definitions, added more math symbols

@@
 \item Access the fields of the feasible targets, performing a conditional write. The conditional write works by modifying the constraint equation as follows:
-\newline  ((A==h_n) => F==V) and (~(A==h_n) => Eqn_o_l_d)
+\begin{equation}
+  ((r\rightarrow h_n) \Rightarrow f\rightarrow v)  \wedge (\lnot (r\rightarrow h_n) \Rightarrow Eqn_o_l_d)
+\end{equation}
 \end{compactenum}
@@
 \subsection{Control Transfer Instructions}
+Control transfer instructions are those instructions that have a "branching" nature.
+They are instructions that have more than one possible program location successor.
+Control transfer instructions are executed by comparing the compare condition to the constraints contained in the symbolic store.
+Those values in the store for which the constraints are now infeasible are eliminated.
 \subsection{Assume / Assert Instructions}

### 2013-06-14 tex/state.tex
Refined the definitions, added more math symbols

@@
 \paragraph{Heap Symbols}
-Heap symbols are symbols which are created and destroyed in the process of performing heap operations.
-The dynamic nature of heap symbols distinguishes them from statically-created symbols like tbose found in the path condition.
+A heap symbol $\pi$ is a symbol which is created in the process of performing heap operations.
+The dynamic nature of heap symbols distinguishes them from statically-created symbols like those found in the path condition.
 Heap symbols may be symbolic primitives, symbolic references, symbolic locations, or symbolic types.
@@
 The non-null state reflects the additional constraint that the reference does not point to the null location.
-References in the initialized state are assosciated with constraints reflecting which location the reference points to and under what condition it points to that location.
+References in the initialized state are associated with constraints reflecting which location the reference points to and under what condition it points to that location.
 References point to one and only one location at a time, so the conditions must be mutually exclusive, yet collectively exhaustive.
 \paragraph{Symbolic Locations}
-Symbolic locations represent the locations of slots in the heap structure that may hold symbolic objects.
+A symbolic location $h$ represents the index of a slot in the heap structure that holds a symbolic object.
 Each symbolic location represents a unique slot on the symbolic heap.
-The constraints assosciated with symbolic locations reflect the uniqueness of each location.
-Each slot on the heap may contain a symbolic object.
+There are two special symbolic locations null and non-null, which are never in the symbolic heap.
 \paragraph{Symbolic Objects}
-A symbolic object represents the contents of a heap slot. A symbolic object contains a symbolic type paired with a mapping from fields to heap symbols.
+A symbolic object represents the contents of a heap slot. A symbolic object is characterized by a symbolic type, and contains a mapping from fields to heap symbols.
+\paragraph{Constrained Symbol}
+A constrained symbol $\psi$ is a symbol that assumes a value $\pi$ contingent upon the satisfiability of a constraint condition $\phi$.
+\begin{equation}
+\psi\models \phi\uparrow \Rightarrow\pi
+\end{equation}
+\paragraph{Symbolic Value Set}
+A symbolic value set $\theta$ is a set of constrained symbols $\theta\colon \{\psi _1,\psi _2,...,\psi _n\}$, for which the constraints are mutually exclusive and collectively exhaustive.
 \paragraph{Symbolic Store}
-The symbolic store is a mapping from heap symbols to symbolic value sets.
-The symbolic value set represents the values that may be assigned to the symbol, along with the constraints assosciated with each value.
-Taken together, the constraints in the abstract store represent a set of unique heaps common to the current program execution path.
-Compare this to the path condition, which contains constraints common to all the heaps in the abstract store.
+The symbolic store is a mapping from heap symbols to symbolic value sets $\mathbb{S}\colon \pi \mapsto \theta$.
+The abstract store represents a set of heaps common to the current program execution path.
 \paragraph{Heap}
-The symbolic heap is a mapping from symbolic locations to symbolic objects.
-Like the path condition, the symbolic heap contains heap state which is common to all heaps on the current execution path.
-Unlike the path condition, the symbolic heap does not contain any logical constraints.
+The symbolic heap $\mathbb{H}$ is an indexed set of symbolic objects. Like the path condition, the symbolic heap contains heap state which is common to all heaps on the current execution path. 
 \paragraph{Stack}

### 2014-02-03 tex/pseudo-code.tex
Added

\section{Pseudo-code}
The presentation assumes a purely syntactic semantics for a CEKS
machine for a Java-like language \cite{saints-MS}. The machine state
for the semantics consists of a (C)ontrol string representing the
expression being evaluated, an (E)nvironment for local variables, a
(K)ontinuation for what is to be executed next, and a (S)tore for the
heap. This paper only defines salient features of the machine relevant
to understanding JPF's partial order reduction. 
\begin{itemize}
\item $n$ is a number, and the set of all positive natural numbers is $\mathbb{N}^+$.
\item $x$ is a variable, and the set of all variables is $\mathbb{X}$.
\item $f$ is a named field in an object.
\item $v$ is a value, and the set of all values is $\mathbb{V}$. A value can be a primitive, and object with named fields, or a reference to an object. 
\item $\eta : \mathbb{X} \rightarrow \mathbb{V}$ is an environment
\item $h : \mathbb{N}^+ \rightarrow \mathbb{V}$ is a heap
\item $k$ is a continuation to resolve evaluation order and return points from calls. Are particular interest are the continuations for thread completion (\texttt{ret}), thread creation 
\item $e$ is an expression. Expressions can be values $v$, sequencing ($(begin\ e\ \ldots)$),
  thread start ($(\mathtt{thread}\ e.m(e\ \ldots))$), field access ($(x.f)$ or $(x.f := e)$), and other constructs
  indicative of the Java language.
\item $t = (\eta\ e\ k)$ is a thread state.
\item $s = (\mu\ h\ (t\ \ldots))$ is a machine state.
\item $(h^\prime\ (\eta^\prime \ e^\prime\ k^\prime)) = \mathrm{execute}(\mu, h, \eta, e, k)$ is a function that returns a new heap and thread by evaluating the expression in the thread until the thread is either done, creates a new thread, or accesses a field in the heap that is shared:
  \begin{itemize}
    \item $(\eta^\prime\ v (* \$ f \rightarrow k))$
  \end{itemize}
\end{itemize}

% Algorithm2e environment
% http://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package

\begin{algorithm}
 \SetAlgoLined
 \KwData{this text}
 \KwResult{how to write algorithm with \LaTeX2e }
 initialization\;
 \While{not at end of this document $\wedge x < 2$}{
  read current\;
  \eIf{understand}{
   go to next section\;
   current section becomes this one\;
   }{
   go back to the beginning of current section\;
  }
 }
 \caption{How to write algorithms}
\end{algorithm}

### 2014-02-11 tex/pseudo-code.tex
Added stuff

@@
 \section{Pseudo-code}
+
 The presentation assumes a purely syntactic semantics for a CEKS
@@
 (K)ontinuation for what is to be executed next, and a (S)tore for the
-heap. This paper only defines salient features of the machine relevant
-to understanding JPF's partial order reduction. 
+heap. This paper only defines salient features of the machine relevant to understanding the new algorithm.
 \begin{itemize}
-\item $n$ is a number, and the set of all positive natural numbers is $\mathbb{N}^+$.
-\item $x$ is a variable, and the set of all variables is $\mathbb{X}$.
-\item $f$ is a named field in an object.
-\item $v$ is a value, and the set of all values is $\mathbb{V}$. A value can be a primitive, and object with named fields, or a reference to an object. 
-\item $\eta : \mathbb{X} \rightarrow \mathbb{V}$ is an environment
-\item $h : \mathbb{N}^+ \rightarrow \mathbb{V}$ is a heap
-\item $k$ is a continuation to resolve evaluation order and return points from calls. Are particular interest are the continuations for thread completion (\texttt{ret}), thread creation 
-\item $e$ is an expression. Expressions can be values $v$, sequencing ($(begin\ e\ \ldots)$),
-  thread start ($(\mathtt{thread}\ e.m(e\ \ldots))$), field access ($(x.f)$ or $(x.f := e)$), and other constructs
-  indicative of the Java language.
-\item $t = (\eta\ e\ k)$ is a thread state.
-\item $s = (\mu\ h\ (t\ \ldots))$ is a machine state.
-\item $(h^\prime\ (\eta^\prime \ e^\prime\ k^\prime)) = \mathrm{execute}(\mu, h, \eta, e, k)$ is a function that returns a new heap and thread by evaluating the expression in the thread until the thread is either done, creates a new thread, or accesses a field in the heap that is shared:
+\item $n$ are numbers, and the set of all positive natural numbers is $\mathbb{N}^+$.
+\item $x$ is a variable, and the set of all variables is $X$.
+\item $f$ is a field name in an object, and the set of all field names is $F$.
+\item $v$ is a value, and the set of all values is $V$. A value can only be a reference. 
+\item $\eta : X \rightarrow V$ is an environment
+\item $h$ is a heap represented as a bipartite graph (see below).
+\item $k$ is a continuation to resolve evaluation order and return points from calls. Of particular interest are the continuations for completion (\texttt{ret}), ...
+\item $e$ is an expression. Expressions can be values $v$, sequencing
+  ($(begin\ e\ \ldots)$), field access ($(x.f)$ or $(x.f := e)$), and
+  other constructs to be defined soon,...
+\item $\mu$ is the text that defines classes and methods.
+\item $P$ is a program $(\mu, (C m))$ where $C$ is a class defined in
+  $\mu$ and $m$ is a method in that class.
+\item $s = (\mu\ h\ \eta\ e\ k)$ is a machine state.
+\item $(\mu\ h^\prime\ \eta^\prime\ e^\prime\ k^\prime) =
+  \mathrm{execute}(\mu, h, \eta, e, k)$ is a function that returns a
+  state by evaluating the expression.
+\end{itemize}
+
+The heap is a bipartite graph defined on locations $L$ and references
+$R$. $R$ and $L$ include the special symbol $\bot$ to indicate an
+uninitialized reference and location respectively. Additionally, $L$
+includes a special location $\mathtt{NULL}$ for null references.
+
+Locations are boxes in the graphical representation and indicated with
+the letter $l$ in the math. References are circles in the graphical
+representation and indicated with the letter $r$ in the math. Edges
+from locations are labeled with field names $f \in F$. Edges from the
+references are labeled with constraints $\phi \in \Phi$ (we assume
+$\Phi$ is a power set over individual constraints and $phi$ is a set
+of constraints for the edge).
+
+The heap is now defined
+as $h = (L\ R\ \mathit{ref}\ \mathit{loc})$ where
 \begin{itemize}
-    \item $(\eta^\prime\ v (* \$ f \rightarrow k))$
+\item $\mathit{ref} : L \times F \mapsto R$ is the
+  connection between locations and references on a named field. The
+  function can also be viewed as a set $\mathit{ref} \subseteq L
+  \times F \times R$ in a set if that is preferred to a function.
+\item $\mathit{loc} : R \mapsto 2^{L \times \Phi}$ is the connection
+  between a reference and a location on a constraint. The function
+  $\mathit{loc}$ can also be viewed as a set $\mathit{loc} \subseteq R
+  \times \Phi \times L$.
 \end{itemize}
-\end{itemize}
+
+\input{machine-rules}
 
@@
 % http://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
-
+\begin{comment}
 \begin{algorithm}
@@
 \end{algorithm}
+\end{comment}

### 2014-02-12 tex/pseudo-code.tex
Added

@@
 \section{Pseudo-code}
-
-The presentation assumes a purely syntactic semantics for a CEKS
-machine for a Java-like language \cite{saints-MS}. The machine state
-for the semantics consists of a (C)ontrol string representing the
+The presentation assumes a CEKS machine for a Java-like language
+(mostly a syntactic machine) \cite{saints-MS}. The machine state for
+the semantics consists of a (C)ontrol string representing the
 expression being evaluated, an (E)nvironment for local variables, a
 (K)ontinuation for what is to be executed next, and a (S)tore for the
-heap. This paper only defines salient features of the machine relevant to understanding the new algorithm.
+heap. This paper only defines salient features of the machine relevant
+to understanding the new algorithm.
+
+The language is defined as in the following figure.
+\input{grammar}
+
+%\item $n$ are numbers, and the set of all positive natural numbers is $\mathbb{N}^+$.
 \begin{itemize}
-\item $n$ are numbers, and the set of all positive natural numbers is $\mathbb{N}^+$.
-\item $x$ is a variable, and the set of all variables is $X$.
-\item $f$ is a field name in an object, and the set of all field names is $F$.
-\item $v$ is a value, and the set of all values is $V$. A value can only be a reference. 
-\item $\eta : X \rightarrow V$ is an environment
-\item $h$ is a heap represented as a bipartite graph (see below).
-\item $k$ is a continuation to resolve evaluation order and return points from calls. Of particular interest are the continuations for completion (\texttt{ret}), ...
-\item $e$ is an expression. Expressions can be values $v$, sequencing
+\item $x \in X$ is a variable
+\item $f\in F$ is a field name in an object
+\item $r\in V$ is a reference
+\item $e$ is an expression.
+  \begin{itemize}
+  \item $v$
+  \item $x$
+  \item $(e\ \$\ f)$
+  \item $(x\ := e)$
+  \item
+  \end{itemize} Expressions can be values $v$, sequencing
   ($(begin\ e\ \ldots)$), field access ($(x.f)$ or $(x.f := e)$), and
@@
   $\mu$ and $m$ is a method in that class.
+\item $(L,R)$ represent the heap and form a bipartite graph (see below).
+\item $\eta : X \rightarrow V$ is an environment
+\item $k$ is a continuation to resolve evaluation order and return points from calls
+\begin{itemize}
+\item $\mathtt{end}$: nothing comes next
+\item $(*\ \$\ f \rightarrow k)$: access field $f$ once expression is reduced to a reference.
+\end{itemize}
 \item $s = (\mu\ h\ \eta\ e\ k)$ is a machine state.

### 2014-02-13 tex/pseudo-code.tex
Added some stuff

@@
 \section{Pseudo-code}
-The presentation assumes a CEKS machine for a Java-like language
-(mostly a syntactic machine) \cite{saints-MS}. The machine state for
-the semantics consists of a (C)ontrol string representing the
-expression being evaluated, an (E)nvironment for local variables, a
-(K)ontinuation for what is to be executed next, and a (S)tore for the
-heap. This paper only defines salient features of the machine relevant
-to understanding the new algorithm.
+\figref{fig:surface-syntax} defines the surface syntax for the
+Javalite language \cite{saints-MS}. The \figref{fig:machine-syntax} is
+the machine syntax. The semantics of Javalite is syntax based and
+defined as rewrites on a string. The semantics use a CEKS machine
+model with a (C)ontrol string representing the expression being
+evaluated, an (E)nvironment for local variables, a (K)ontinuation for
+what is to be executed next, and a (S)tore for the heap. This paper
+only defines salient features of the language and machine relevant to
+understanding the new algorithm.
 
-The language is defined as in the following figure.
-\input{grammar}
+\input{surface-syntax}
+\input{machine-syntax}
 

### 2014-02-13 tex/pseudo-code.tex
Added

@@
 %\item $n$ are numbers, and the set of all positive natural numbers is $\mathbb{N}^+$.
+This paper uses a standard definition of constraints $\phi \in \Phi$
+assuming all the usual relational operators and connectives. The heap
+is a labeled bipartite graph consisting of references $R$ and
+locations $L$ in the store. The functions $R$ and $L$ are defined for convenience
+in manipulating the labeled bipartite graph.
 \begin{itemize}
-\item $x \in X$ is a variable
-\item $f\in F$ is a field name in an object
-\item $r\in V$ is a reference
-\item $e$ is an expression.
-  \begin{itemize}
-  \item $v$
-  \item $x$
-  \item $(e\ \$\ f)$
-  \item $(x\ := e)$
-  \item
-  \end{itemize} Expressions can be values $v$, sequencing
-  ($(begin\ e\ \ldots)$), field access ($(x.f)$ or $(x.f := e)$), and
-  other constructs to be defined soon,...
-\item $\mu$ is the text that defines classes and methods.
-\item $P$ is a program $(\mu, (C m))$ where $C$ is a class defined in
-  $\mu$ and $m$ is a method in that class.
-\item $(L,R)$ represent the heap and form a bipartite graph (see below).
-\item $\eta : X \rightarrow V$ is an environment
-\item $k$ is a continuation to resolve evaluation order and return points from calls
-\begin{itemize}
-\item $\mathtt{end}$: nothing comes next
-\item $(*\ \$\ f \rightarrow k)$: access field $f$ once expression is reduced to a reference.
+\item $R(l,f)$ maps location-field pairs from the store to a reference in $R$; and
+\item $L(r)$ maps references to a set of location-constraint pairs in the store.
 \end{itemize}
-\item $s = (\mu\ h\ \eta\ e\ k)$ is a machine state.
-\item $(\mu\ h^\prime\ \eta^\prime\ e^\prime\ k^\prime) =
-  \mathrm{execute}(\mu, h, \eta, e, k)$ is a function that returns a
-  state by evaluating the expression.
-\end{itemize}
+A reference is a node that gathers the possible store locations for an
+object during symbolic execution. Each store location is guarded by a
+constraint derived from the path constraint in the symbolic execution.
+Intuitively, the reference is a level of indirection between a
+variable and the store, and the reference is used to group a set of
+possible store locations each predicated on the associated constraint.
+For an variable (or field) to access any particular store location associated with its reference, the corresponding constraint must be satisfied.
 
-The heap is a bipartite graph defined on locations $L$ and references
+\begin{comment}
+ defined on value sets $L$ and references
 $R$. $R$ and $L$ include the special symbol $\bot$ to indicate an
@@
 includes a special location $\mathtt{NULL}$ for null references.
+\end{comment}
 
@@
 of constraints for the edge).
-
-The heap is now defined
-as $h = (L\ R\ \mathit{ref}\ \mathit{loc})$ where
-\begin{itemize}
-\item $\mathit{ref} : L \times F \mapsto R$ is the
-  connection between locations and references on a named field. The
-  function can also be viewed as a set $\mathit{ref} \subseteq L
-  \times F \times R$ in a set if that is preferred to a function.
-\item $\mathit{loc} : R \mapsto 2^{L \times \Phi}$ is the connection
-  between a reference and a location on a constraint. The function
-  $\mathit{loc}$ can also be viewed as a set $\mathit{loc} \subseteq R
-  \times \Phi \times L$.
-\end{itemize}
 

### 2014-02-14 tex/pseudo-code.tex
Minor typo fix.

@@
 object during symbolic execution. Each store location is guarded by a
-constraint derived from the path constraint in the symbolic execution.
-Intuitively, the reference is a level of indirection between a
-variable and the store, and the reference is used to group a set of
-possible store locations each predicated on the associated constraint.
-For an variable (or field) to access any particular store location associated with its reference, the corresponding constraint must be satisfied.
+constraint that determines the aliasing in the heap. Intuitively, the
+reference is a level of indirection between a variable and the store,
+and the reference is used to group a set of possible store locations
+each predicated on the possible aliasing in the associated constraint.
+For a variable (or field) to access any particular store location
+associated with its reference, the corresponding constraint must be
+satisfied.
 
@@
 references are labeled with constraints $\phi \in \Phi$ (we assume
-$\Phi$ is a power set over individual constraints and $phi$ is a set
+$\Phi$ is a power set over individual constraints and $\phi$ is a set
 of constraints for the edge).

### 2014-02-21 tex/pseudo-code.tex
Added
Made function
Added refined formating on function
Added new
added more detail to the equals (references true) rule

@@
 
+The function $\mathbb{VS}(L,R,r,f)$ constructs the value-set given a
+heap, reference, and desired field such that
+$(l^\prime\ \phi^\prime\wedge\phi) \in \mathbb{VS}(L,R,r,f)$ if and
+only if
+\[
+\begin{array}{l}
+  \exists (l\ \phi) \in L(r) ( \\
+  \ \ \ \ \ \ \ \ \ \exists r^\prime \in R(l,f) ( \\
+  \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \exists (l^\prime\ \phi^\prime) \in L(r^\prime) (\mathbb{S}(\phi\wedge\phi^\prime))))
+\end{array}
+\]
+where $\mathbb{S}(\phi)$ returns true if $\phi$ is satisfiable.
+
+The function $\mathbb{CP}(L,r,\phi^\prime)$ constructs the location, constraint
+pair $(l\ \phi\wedge\phi^\prime)$ such that $(l\ \phi\wedge\phi^\prime)\in\mathbb{CP}(L,r,\phi^\prime)$ if and only if $\exists (l\ \phi)\in L(r)\wedge\mathbb{S}(\phi\wedge\phi^\prime)$
+
 \input{machine-rules}

### 2014-02-21 figs/dot2pdf.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+for FILE in ./*.dot; 
+do ID=`echo ${FILE} | sed 's/dot/pdf/'`; 
+dot -Tpdf ${FILE} -o ${ID};
+done
+

### 2014-03-06 tex/pseudo-code.tex
added auxilliary functions for the field access rules

@@
 
+The function $\mathbb{B}(l,\phi^\prime)$ returns the set of references: $\{r | \exists(l,\phi) \in L(r)(\neg \mathbb{S}(\phi \vee \phi^\prime))\}}$
+
+The function $\mathbb{C}(L,R,X,\eta,k)$ checks the heap to see if any references in set $X$ are connected to any references in $k$.
+If there are, then it returns $0$.
+Otherwise, it returns $1$: $$\mathbb{C}(L,R,X,\eta,k) =  \left\{ \begin{array}{rcl}0 & \exists r \in X ( \exists r^\prime \in \cfgt{ref}(k) \cup \cfgt{ref}(\eta)(\cfgt{reach}(r,r^\prime))) \\ 1 & \mbox{otherwise}\end{array}\right$$
+
 \input{machine-rules}

### 2014-03-06 tex/pseudo-code.tex
Added stuff

--- 2014-02-21 tex/pseudo-code.tex
@@
 
-The function $\mathbb{CP}(L,r,\phi^\prime)$ constructs the location, constraint
-pair $(l\ \phi\wedge\phi^\prime)$ such that $(l\ \phi\wedge\phi^\prime)\in\mathbb{CP}(L,r,\phi^\prime)$ if and only if $\exists (l\ \phi)\in L(r)\wedge\mathbb{S}(\phi\wedge\phi^\prime)$
+The strengthen function $\mathbb{ST}(L,r,\phi^\prime)$ strengthens every
+constraint from the reference $r$ and keeps only location-constraint
+pairs that are satisfiable after strengthening. Formally,
+$(l\ \phi\wedge\phi^\prime)\in\mathbb{ST}(L,r,\phi^\prime)$ if and
+only if $\exists (l\ \phi)\in
+L(r)\wedge\mathbb{S}(\phi\wedge\phi^\prime)$
+
+The empty-reference function $\mathbb{ER}(L,\phi^\prime) = \{r\ |\ L(r) \neq
+\emptyset \wedge \forall(l,\phi) \in L(r)(\neg \mathbb{S}(\phi \wedge
+\phi^\prime))\}$ searches the heap for references that become
+disconnected from all their locations after strengthening. These
+references, if reachable, imply the heap is no longer valid on the
+current search path. As such, the symbolic execution algorithm should
+backtrack. This check is similar to a feasibility check in classic
+symbolic execution with only primitive data types.
+
+The consistency function is critical to the soundness of the algorithm
+as it detects when a symbolic heap becomes invalid along a path,
+similar to a feasibility check when doing classical symbolic execution
+with just primitives. As the constraints in the heap are strengthened
+with different aliasing requirements, it is possible to reach a point
+where the heap is no longer connected. Meaning, a valid reference is
+live, either in the local environment or the continuation, the reaches
+another reference that is no longer connected to any locations due to
+strengthening. The function relies on the empty-reference function to
+identify disconnected references. The function in essence checks every
+reference in the local environment and every reference found in the
+continuation, as these are all considered live. This operation similar
+to garbage collection where the local environment and stack are
+inspected to find the roots of the heap for the scan.
+
+The consistency function relies on two auxiliary functions which are
+informally defined. The function $\mathrm{ref}(\eta,\cfgnt{k})$
+inspects the local environment and continuation for all live
+references, and it returns those references in a set. The function
+$\mathrm{reach}(L, R, r, r^\prime)$ returns true if $r^\prime$ is
+reachable from $r$ in the heap and false otherwise. The consistency function $\mathbb{C}(L,R,X,\eta,k)$ is now defined as
+\[
+ \left\{ \begin{array}{rl} 
+        0 & \exists r \in \mathrm{ref}(\eta, \cfgnt{k})\ (\exists r^\prime \in X\ (\mathrm{reach}(L, R, r,r^\prime))) \\ 
+        1 & \mbox{otherwise}\end{array}\right .
+\]
 

### 2014-06-24 tex/motivation.tex
took a stab at some text - mainly the abstract and intro

\section{Background and Motivation}
\label{motivations}

Example

### 2014-06-24 tex/stateDescriptions.tex
took a stab at some text - mainly the abstract and intro

--- 2014-03-06 tex/pseudo-code.tex
@@
-\section{Pseudo-code}
-\figref{fig:surface-syntax} defines the surface syntax for the
-Javalite language \cite{saints-MS}. The \figref{fig:machine-syntax} is
-the machine syntax. The semantics of Javalite is syntax based and
-defined as rewrites on a string. The semantics use a CEKS machine
-model with a (C)ontrol string representing the expression being
-evaluated, an (E)nvironment for local variables, a (K)ontinuation for
-what is to be executed next, and a (S)tore for the heap. This paper
-only defines salient features of the language and machine relevant to
-understanding the new algorithm.
+\section{Uber-lazy Operational Semantics}
+\label{semantics}
+
+The operational semantics for Uber-lazy
+symbolic execution are specified using the Javalite 
+language~\cite{saints-MS}. Javalite is an imperative model of Java
+that includes many features of the Java language. In this work, we 
+present only the salient features of the Javalite
+language relevant to understanding the Uber-lazy symbolic execution
+algorithm. A detailed explanation of Javalite is available in~\cite{saints-MS}.
+
+Javalite is an imperative model of the Java language
+developed to facilitate rapid prototyping 
+of model checking algorithms and proofs about the
+algorithms. It is specified with a Java-like syntax and a set
+of reduction rules for syntacticly executing Javalite programs.
+Javalite is based on a variant of the CEKS syntactic 
+machine~\cite{Felleisen:1987}. The operational semantics are 
+defined using the structure (syntax)
+of the language and a set of reduction rules for syntactically
+executing Javalite programs. In a CEKS machine, the
+(C)ontrol string represents a program, command, or instruction to be
+evaluated; it is initialized to a string representing the entire progam. 
+An (E)nvironment  maps (local) variables to their values. The (K)ontinuation 
+specifies what is to be executed next, and the (S)tore is used to store 
+dynamically allocated data, i.e., the heap.
+
+\subsection{Symbolic Store}
+
+At the core of the Uber-lazy symbolic execution algorithm
+is a fully symbolic heap, i.e., a heap in which objects
+are never materialized as concrete objects during symbolic
+execution, but instead are represented using constraints
+charactering feasible heap shapes. To represent the heap
+store ($S$), our algorithm defines a labeled bi-partite 
+graph where $S = (R, L, E)$.  $R$ contains the set of nodes 
+representing program \emph{references}.
+$L$ contains the set of nodes representing \emph{locations} in the store. 
+The store is initialized with two special locations: $null$ and $\bot$ representing a null object
+and an uninitialized location respectively. Each edge in the set of labeled
+edges, $E$, is uni-directional. An edge from a reference $r \in R$ to a location $l \in L$ is
+labeled with a constraint $\phi$ indicating the conditions under which $r$ references
+i.e., points to, that location in the store. This paper uses a standard definition
+of constraints $\phi \in \Phi$ assuming all of the usual relation operators and connectives.
+Reference nodes collect the the
+feasible points-to relations for a given program execution path during symbolic execution.
+Each edge from a location $l \in L$ to a reference $r \in R$ is labeled with the 
+name of a field $f \in F$.
+
+More details here including we assume the input program is typesafe
+or if there is a type and a mismatch occurs, then the machine halts.
+
+The machine also halts if an exception is thrown.
+
+\subsection{Syntax}
 
@@
 
-%\item $n$ are numbers, and the set of all positive natural numbers is $\mathbb{N}^+$.
-This paper uses a standard definition of constraints $\phi \in \Phi$
-assuming all the usual relational operators and connectives. The heap
-is a labeled bipartite graph consisting of references $R$ and
-locations $L$ in the store. The functions $R$ and $L$ are defined for convenience
-in manipulating the labeled bipartite graph.
-\begin{itemize}
-\item $R(l,f)$ maps location-field pairs from the store to a reference in $R$; and
-\item $L(r)$ maps references to a set of location-constraint pairs in the store.
-\end{itemize}
-A reference is a node that gathers the possible store locations for an
-object during symbolic execution. Each store location is guarded by a
-constraint that determines the aliasing in the heap. Intuitively, the
-reference is a level of indirection between a variable and the store,
-and the reference is used to group a set of possible store locations
-each predicated on the possible aliasing in the associated constraint.
-For a variable (or field) to access any particular store location
-associated with its reference, the corresponding constraint must be
-satisfied.
+Javalite programs and expressions are written in a syntax specified by the 
+grammar in~\figref{fig:machine-syntax}. The production rules correspond
+to the various features supported by Javalite such as classes, fields,
+methods, and expressions.
 
-\begin{comment}
- defined on value sets $L$ and references
-$R$. $R$ and $L$ include the special symbol $\bot$ to indicate an
-uninitialized reference and location respectively. Additionally, $L$
-includes a special location $\mathtt{NULL}$ for null references.
-\end{comment}
+\figref{fig:machine-syntax} specifies
+the machine syntax for Javalite. The expression $e$ is equivalent to
+a CEKS machine's control string. The
 
-Locations are boxes in the graphical representation and indicated with
-the letter $l$ in the math. References are circles in the graphical
-representation and indicated with the letter $r$ in the math. Edges
-from locations are labeled with field names $f \in F$. Edges from the
-references are labeled with constraints $\phi \in \Phi$ (we assume
-$\Phi$ is a power set over individual constraints and $\phi$ is a set
-of constraints for the edge).
+\subsection{Reduction Rules}
+
+We first present the reduction rules
+
+\subsubsection{Basic Reduction Rules}
+
+Most rules presented here - short discussion
+
+\subsubsection{Store Update Rules}
+
+Interesting rules presented here; more elaborate discussion
+
+Start off with helper functions for rules that manipulate the store...
 
@@
 \input{machine-rules}
-
-% Algorithm2e environment
-% http://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
-\begin{comment}
-\begin{algorithm}
- \SetAlgoLined
- \KwData{this text}
- \KwResult{how to write algorithm with \LaTeX2e }
- initialization\;
- \While{not at end of this document $\wedge x < 2$}{
-  read current\;
-  \eIf{understand}{
-   go to next section\;
-   current section becomes this one\;
-   }{
-   go back to the beginning of current section\;
-  }
- }
- \caption{How to write algorithms}
-\end{algorithm}
-\end{comment}

### 2014-06-24 tex/intro.tex
Added

@@
 
+In recent years symbolic execution --
+a program analysis technique for systematic exploration of
+program execution paths using symbolic input values -- has provided
+the basis for many software testing and analysis techniques.
+For each execution path explored during symbolic execution, constraints
+on the symbolic inputs are collected to create a \emph{path
+condition}. The set of path conditions computed by symbolic execution
+characterize the observed program execution behaviours and can
+be used to perform various analyses of program behavior, e.g.,
+regression testing~\cite{} and differential program 
+analysis~\cite{}.
+
+Initial work on symbolic execution largely focused on checking 
+properties of programs with primitive types, such as integers and 
+booleans~\cite{clarke76TSE,King:76}. With the advent of object-oriented
+languages, such as Java and C$++$, one of the fundamental challenges 
+of using symbolic execution for program analysis
+has been how to analyze programs containing
+complex data structures with unbounded domains, i.e., data stored
+on the heap. State-of-the-art symbolic execution techniques have 
+addressed this challenge by constructing the heap in a lazy manner, 
+deferring materialization of objects on the concrete heap until
+they are needed, i.e., until execution of a statement with a 
+dereference expression ($x = r.f$)~\cite{Kiasan06,Kiasan07,GSE03}.
+
+Although the lazy symbolic execution techniques have been instrumental 
+in enabling analysis of heap manipulating software, treatment of
+heap data follows concrete program semantics once a heap location is
+materialized. The effect is to exacerbate 
+the state space explosion problem by creating additional points of 
+non-determinism during symbolic execution to account for the 
+different possible concrete heap configurations.
+
+Need a transition here to talk about a symbolic heap
+
+In this paper we present a novel approach to lazy symbolic
+execution....
+
+Our technique is 1) scalable -- it constructs the symbolic
+heap on-the-fly during symbolic execution but avoids introducing 
+additional points of non-determinism
+by maintaining only a (fully) symbolic heap,
+2) precise -- at any given point during symbolic execution, 
+the symbolic heap represents the exact set of feasible
+concrete heap structures for the program under analysis, and
+3) expressive -- the symbolic heap can represent recursive data structures 
+and heaps resulting from loops and recursive control structures in the code. 
+We report on a case-study of an implementation of our technique in the
+Symbolic PathFinder tool to illustrate
+ its scalability and we discuss how test case generation -- a common
+ use for the results of symbolic execution -- can benefit from symbolic
+ execution using a fully symbolic heap.
+
+This paper makes the following contributions:
+
+\begin{itemize}
+\item{We present a novel technique for analyzing heap manipulating
+programs that constructs a fully symbolic representatino of
+the heap on-the-fly durig symbolic execution.}
+\item{We prove the soundness and completeness of our algorithm...}
+\item{We implement our approach in the Symbolic PathFinder tool}
+\item{We demonstrate experimentally that our technique improves
+the scalability of symbolic execution of heap maninpulating software
+over state-of-the-art techniques.}
+
+ \end{itemize}
+
+\begin{comment}
 \newcommand{\Indstate}[1][1]{\State\hspace{#1\algorithmicindent}}
@@
 Lazy initialization is a symbolic execution technique where memory structures are created on-demand, as they are required.
+\end{comment}

### 2014-06-24 tex/related.tex

\section{Related Work}
\label{related}

The related work goes here.

### 2014-06-25 tex/intro.tex

--- 2013-06-14 tex/intro.tex
@@
 
+In recent years symbolic execution --
+a program analysis technique for systematic exploration of
+program execution paths using symbolic input values -- has provided
+the basis for various software testing and analysis techniques.
+For each execution path explored during symbolic execution, constraints
+on the symbolic inputs are collected to create a \emph{path
+condition}. The set of path conditions computed by symbolic execution
+characterize the observed program execution behaviours and can
+be used as an enabling technology for various applications, e.g., 
+regression 
+analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12}, 
+data structure repair~\cite{KhurshidETAL05RepairingStructurally}, dynamic
+discovery of invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, 
+and debugging\cite{Ma:2011}.
+
+Initial work on symbolic execution largely focused on checking 
+properties of programs with primitive types, such as integers and 
+booleans~\cite{clarke76TSE,King:76}. Despite recent advances
+in constraint solving technologies, improvements in
+raw computing power, and advances in reduction
+and abstraction techniques~\cite{AnandETAL2009AbsSymExe,Godefroid:POPL07}
+symbolic execution of programs of modest size containing only
+primitive types, remains challenging
+because of the large number of execution paths generated
+during symbolic analysis.
+
+With the advent of object-oriented
+languages that manipulate dynamically allocated data,
+ .g., Java and C$++$, recent work has generalized the core ideas of 
+symbolic execution to enable analysis of programs containing
+complex data structures with unbounded domains, i.e., data stored
+on the heap~\cite{Kiasan06,Kiasan07,GSE03}.
+These techniques onstruct the heap in a lazy manner, 
+deferring materialization of objects on the concrete heap until
+they are needed for the analysis to proceed.
+%, i.e., until execution of a statement with a  dereference expression 
+%($x = r.f$).
+Treatment of
+heap allocated data then follows concrete program semantics 
+once a heap location is materialized, resulting in a large number
+of feasible concrete heap configurations, and as a result, a large
+number of points of 
+non-determinism to be analyzed, further exacerbating 
+the state space explosion problem.
+
+THIS PARA IS NOT QUITE RIGHT BUT THE IDEA IS STARTING TO COME OUT.
+Although lazy symbolic execution techniques have been instrumental 
+in enabling analysis of heap manipulating programs, they miss an
+important opportunity to control the state space explosion problem
+by treating only inputs with primitive types symbolically and
+materializing a concrete heap. As we show in this work, the use of
+a fully \emph{symbolic heap} during lazy symbolic execution, 
+can improve the scalability of the analysis while maintaining
+precision and efficiency. Moreover, the number of path conditions
+computed by lazy symbolic execution when a symbolic heap
+is used
+produces considerably fewer path conditions -- a valuable benefit
+for client analyses that use the results of symbolic execution,
+e.g., regression analyses.
+
+The key advantages of our approach to lazy symbolic execution
+using a fully symbolic heap include:
+\begin{itemize}
+\item{\emph{Scalability.} Our approach constructs the symbolic
+heap on-the-fly during symbolic execution and avoids creating
+the additional points of non-determinism
+introduced by existing lazy initialization techniques. Moreover, it explores
+each execution path only once for any given set of isomorphic heaps.}
+\item{\emph{Precision.} At any given point during symbolic execution, 
+the symbolic heap represents the exact set of feasible
+concrete heap structures for the program under analysis}
+\item{\emph{Expressiveness.} The symbolic heap can represent recursive 
+data structures  and heap structures resulting from loops and recursive control 
+structures in the analyzed code. }
+ \end{itemize}
+
+This paper makes the following contributions:
+
+\begin{itemize}
+\item{We present a novel lazy symbolic execution technique
+ for analyzing heap manipulating
+programs that constructs a fully symbolic representatino of
+the heap on-the-fly durig symbolic execution.}
+\item{We prove the soundness and completeness of our algorithm...}
+\item{We implement our approach in the Symbolic PathFinder tool}
+\item{We demonstrate experimentally that our technique improves
+the scalability of symbolic execution of heap maninpulating software
+over state-of-the-art techniques, while maintaining efficiency and precision.}
+  \item{We discuss the benefits of using a symbolic heap that
+  can be realized by the client analysis that uses the results of symbolic execution.}
+ \end{itemize}
+
+\begin{comment}
 \newcommand{\Indstate}[1][1]{\State\hspace{#1\algorithmicindent}}

### 2014-06-28 tex/pseudo-code.tex
Added global invariant to machine state, and changed the References-Equals rules to reflect it's use
Fixed a typo that was causing an error in psuedo-code.tex
Almost done with lazy initialization

--- 2014-02-21 tex/pseudo-code.tex
@@
 
-\begin{comment}
- defined on value sets $L$ and references
-$R$. $R$ and $L$ include the special symbol $\bot$ to indicate an
-uninitialized reference and location respectively. Additionally, $L$
-includes a special location $\mathtt{NULL}$ for null references.
-\end{comment}
-
 Locations are boxes in the graphical representation and indicated with
@@
 
-The function $\mathbb{VS}(L,R,r,f)$ constructs the value-set given a
-heap, reference, and desired field such that
-$(l^\prime\ \phi^\prime\wedge\phi) \in \mathbb{VS}(L,R,r,f)$ if and
-only if
+The function $\mathbb{VS}(L,R,\phi_g,r,f)$ constructs the value-set given a
+heap, reference, and desired field:
 \[
-\begin{array}{l}
-  \exists (l\ \phi) \in L(r) ( \\
-  \ \ \ \ \ \ \ \ \ \exists r^\prime \in R(l,f) ( \\
-  \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \exists (l^\prime\ \phi^\prime) \in L(r^\prime) (\mathbb{S}(\phi\wedge\phi^\prime))))
+\begin{array}{rcl}
+  \mathbb{VS}(L,R,\phi_g,r,f) & = & \{(l^\prime\ \phi^\prime\wedge\phi) \mid \\
+  & & \ \ \ \ \exists l\ ((l\ \phi) \in L(r)\ \wedge \\
+  & & \ \ \ \ \ \ \ \ \exists r^\prime \in R(l,f) ( \\
+  & & \ \ \ \ \ \ \ \ \ \ \ \ (l^\prime\ \phi^\prime) \in L(r^\prime)\ \wedge\\
+  & & \ \ \ \ \ \ \ \ \ \ \ \ \mathbb{S}(\phi\wedge\phi^\prime\wedge \phi_g)))\}
 \end{array}
@@
 
-The function $\mathbb{CP}(L,r,\phi^\prime)$ constructs the location, constraint
-pair $(l\ \phi\wedge\phi^\prime)$ such that $(l\ \phi\wedge\phi^\prime)\in\mathbb{CP}(L,r,\phi^\prime)$ if and only if $\exists (l\ \phi)\in L(r)\wedge\mathbb{S}(\phi\wedge\phi^\prime)$
+The strengthen function $\mathbb{ST}(L,r,\phi^\prime)$ strengthens every
+constraint from the reference $r$ with $\phi^\prime$ and keeps only location-constraint
+pairs that are satisfiable after this strengthening:
+\[
+\begin{array}{rcl} 
+\mathbb{ST}(L,r,\phi^\prime) & = & \{ (l\ \phi\wedge\phi^\prime) \mid 
+(l\ \phi)\in L(r)\wedge\mathbb{S}(\phi\wedge\phi^\prime) \}
+\end{array}
+\]
 
 \input{machine-rules}
-
-% Algorithm2e environment
-% http://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
-\begin{comment}
-\begin{algorithm}
- \SetAlgoLined
- \KwData{this text}
- \KwResult{how to write algorithm with \LaTeX2e }
- initialization\;
- \While{not at end of this document $\wedge x < 2$}{
-  read current\;
-  \eIf{understand}{
-   go to next section\;
-   current section becomes this one\;
-   }{
-   go back to the beginning of current section\;
-  }
- }
- \caption{How to write algorithms}
-\end{algorithm}
-\end{comment}

### 2014-06-28 tex/motivation.tex

@@
 
-Example
+In this section we present the background on state of the art
+techniques that have been developed to handle data non-determinism
+arising from complex data structures. We present an overview of lazy
+initialization and lazier\# initialization. We also present a brief
+description of the two bounding strategies used in symbolic execution
+in heap manipulating programs. Next we present a motivating examples
+where current concrete initialization of the heap structures struggle
+to scale to medium sized program due to non-determinism introduced in
+the symbolic execution tree. We use this example to motivate the need
+for a more truly symbolic and compact representation of the heap in a
+manner similar to that of primitive types.
+
+Generalized symbolic execution technique generates a concrete
+representation of connected memory structures using only the implicit
+information from the program itself.  In the original lazy
+initialization algorithm, symbolic execution explores different heap
+shapes by concretizing the heap at the first memory access (read) to
+an un-initialized symbolic object. At this point, a non-deterministic
+choice point of concreate heap locations is created that includes: (a)
+null, (b) an access to a new instance of the object, and (c) aliases
+to other type-compatible symbolic objects that have been concretized
+along the same execution path~\cite{GSE:TACAS2003}.  The number of
+choices explored in lazy initialization greatly increases the
+non-determinism and often makes the exploration of the program state
+space intractable.
+
+%Various improvements have been proposed to reduce the amount of
+%nondeterminism from lazy initialization. One such optimization,
+%introduced in \cite{Kiasan06} , is called lazier\#
+%initialization.
+The Lazier\# algorithm is an improvement of the lazy initialization
+and it pushes the non-deterministic choices further into the execution
+tree. In the case of a memory access to an uninitialized reference
+location, by default, no choice point is created. Instead, the read
+returns a unique symbolic reference representing the contents of the
+location. The reference may assume any one of three states:
+uninitialized, non-null, or initialized. The reference is returned in
+an uninitialized state, and only in a subsequent memory access is the
+reference concretely initialized.

### 2014-06-30 tex/pseudo-code.tex
Fixed last of lazy initialization rules

@@
 the letter $l$ in the math. References are circles in the graphical
-representation and indicated with the letter $r$ in the math. Edges
-from locations are labeled with field names $f \in F$. Edges from the
-references are labeled with constraints $\phi \in \Phi$ (we assume
-$\Phi$ is a power set over individual constraints and $\phi$ is a set
-of constraints for the edge).
+representation and indicated with the letter $\cfgnt{r}$ in the
+math. The special symbol $\bot$ is an uninitialized reference. Edges
+from locations are labeled with field names $\cfgnt{f}$. Edges from
+the references are labeled with constraints $\phi \in \Phi$ (it is
+assumed that $\Phi$ is a power set over individual constraints and
+$\phi$ is a set of constraints for the edge).
 

### 2014-06-30 tex/proofs.tex

\section{Proofs}

\subsection{Definitions}

\subsubsection{State Representation Relation}
A symbolic system state represents a set of lazy system states. To denote the representation relationship, we use the expression $\mathcal{L}\sqsubset \mathcal{S} $ to say that lazy system state $\mathcal{L}:\lp \mu\ \cfgnt{L}_{\mathcal{L}}\ \cfgnt{R}_{\mathcal{L}}\ \phi_{\mathcal{L}}\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp$ is represented by symbolic state $\mathcal{S}:\lp \mu\ \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_{\mathcal{S}}\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp$ . The representation relationship is defined as follows: $\mathcal{L}\sqsubseteq \mathcal{S} $ if and only if there exists functions $g:\cfgnt{r} \mapsto \cfgnt{r}$ and $h:\cfgnt{l} \mapsto \cfgnt{l}$ such that for any reference $r \in \mathcal{L}$, location $l \in \mathcal{L}$, and field $f$, $$ l = L_{\mathcal{L}}(r) \leftrightarrow h(l)\in L_{\mathcal{S}}(g(r))$$ and $$ r = R_{\mathcal{L}}(\cfgnt{l},f) \leftrightarrow g(r) = R_{\mathcal{S}}(h(l),f)$$

\subsection{Theorems}

### 2014-06-30 tex/abstract.tex
moving the abstract to another file

One of the fundamental challenges of using symbolic execution
to analyze software has been the treatment of dynamically
allocated data.
%, i.e., programs with complex data structures with
%unbounded domains.
State-of-the-art symbolic execution techniques 
have addressed this challenge by constructing the heap \emph{lazily},
materializing objects on the concrete heap ``as needed'' and
using non-deterministic choice points to explore each feasible
concrete heap configuration. Because analysis of the materialized
heap locations relies on concrete program semantics, the lazy
initialization approach exacerbates the state space explosion
problem that limits the scalability of symbolic execution.
In this work we present a novel approach for lazy symbolic execution
of heap manipulating software which utilizes 
a fully symbolic heap constructed on-the-fly during symbolic execution.
Our approach is 1) \emph{scalable} -- it does not
create the additional points of non-determinism
introduced by existing lazy initialization techniques and it explores
each execution path only once for any given set of isomorphic heaps,
2) \emph{precise} -- at any given point during symbolic execution, 
the symbolic heap represents the exact set of feasible
concrete heap structures for the program under analysis, and
3) \emph{expressive} -- the symbolic heap can represent recursive data structures 
and heaps resulting from loops and recursive control structures in the code. 
We report on a case-study of an implementation of our technique in the
Symbolic PathFinder tool to illustrate its scalability, precision
and expressiveness. We also discuss how test case generation -- a common
 use for symbolic execution results -- can benefit from symbolic
 execution which uses a fully symbolic heap.

### 2014-06-30 tex/motivation.tex
updating the figures in the motivation

@@
 reference concretely initialized.
+
+\begin{figure}
+\begin{tabular}[c]{l}
+\begin{lstlisting}
+public class LinkedList {
+
+/** assume the linked list is valid with no cycles **/
+LLNode head;
+Data data0, data1, data2, data3, data4;
+
+private class Data { Integer val; }
+
+private class LLNode {
+  protected Data elem;
+  protected LLNode next; }
+
+public static boolean contains(LLNode root, Data val) {
+  LLNode node = root;
+  while (true) {
+    if(node.val == val)  return true;
+    if(node.next == null) return false;
+    node = node.next;
+}}
+
+public void run() {
+if(LinkedList.contains(head, data0) && LinkedList.contains(head,data1) &&
+   LinkedList.contains(head, data2) && LinkedList.contains(head, data3) &&
+   LinkedList.contains(head, data4)) return;
+\end{lstlisting}
+\end{tabular} 
+\caption{Linked list}
+\label{fig:example}
+\end{figure}
+
+\begin{figure}[htb]
+\scalebox{0.45}
+{\includegraphics[width=563px]{../figs/time_vs_complexity.pdf}}
+\caption{Time versus complexity for the linked list example}
+\label{fig:tvc}
+\end{figure}

### 2014-07-02 tex/proofs.tex
Added theorem environment to paper.tex, updated proofs.tex with examples

@@
 
-\subsubsection{State Representation Relation}
+\begin{definition}
 A symbolic system state represents a set of lazy system states.
@@
 The representation relationship is defined as follows: $\mathcal{L}\sqsubseteq \mathcal{S} $ if and only if there exists functions $g:\cfgnt{r} \mapsto \cfgnt{r}$ and $h:\cfgnt{l} \mapsto \cfgnt{l}$ such that for any reference $r \in \mathcal{L}$, location $l \in \mathcal{L}$, and field $f$, $$ l = L_{\mathcal{L}}(r) \leftrightarrow h(l)\in L_{\mathcal{S}}(g(r))$$ and $$ r = R_{\mathcal{L}}(\cfgnt{l},f) \leftrightarrow g(r) = R_{\mathcal{S}}(h(l),f)$$
+\end{definition}
 
 \subsection{Theorems}
+The following theorem demonstrates the use of the theorem environment.
+\begin{theorem}
+Let $f$ be continuous on $[a,b]$.  If $G$ is
+an antiderivative for $f$ on $[a,b]$, then
+\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
+\end{theorem}

### 2014-07-02 tex/lazy.tex
Regrouped rules and divided into separate files (one per figure)

\begin{figure*}[t]
\begin{center}
\mprset{flushleft}
\begin{mathpar}
	\inferrule[Field Access]{
      \{\lp\phi\ l\rp\} = \cfgnt{L}\lp\cfgnt{r}\rp\\
      l \neq \cfgnt{l}_\mathit{null}\\\\
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \cfgnt{r}\ \cfgnt{f}\rp \rightarrow^*_I 
      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi_g^\prime\ \cfgnt{r}\ \cfgnt{f} \rp \\\\ 
      \{\lp\phi^\prime\ l^\prime\rp\} = \cfgnt{L}^\prime\lp\cfgnt{R}^\prime\lp l,\cfgnt{f}\rp\rp \\
      \mathrm{fresh}_r\lp\rp  = \cfgnt{r}^\prime \\
    }{
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp  \rightarrow \\\\
      \lp \cfgnt{L}^\prime[\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}^\prime\ \phi_g^\prime\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp 
	}
\and
	\inferrule[Field Write]{
      \cfgnt{r}_x = \eta\lp \cfgnt{x}\rp\\ 
      \{\lp\phi\ l\rp\} = \cfgnt{L}\lp\cfgnt{r}_x\rp \\
      l \neq \cfgnt{l}_\mathit{null}\\\\
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \cfgnt{r}_x\ \cfgnt{f}\rp \rightarrow^*_I 
      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi_g^\prime\ \cfgnt{r}_x\ \cfgnt{f} \rp \\\\ 
      \mathrm{fresh}_r\lp\rp = \cfgnt{r}^\prime\\
      \theta =  \cfgnt{L}^\prime\lp\cfgnt{r}\rp 
    }{
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp  \rightarrow \\\\
      \lp \cfgnt{L}^\prime[\cfgnt{r}^{\prime} \mapsto \theta]\ \cfgnt{R}^\prime[\lp l\ \cfgnt{f}\rp  \mapsto \cfgnt{r}^\prime]\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp 
	}	
\and
    \inferrule[Equals (reference-true)]{
    \cfgnt{L}\lp \cfgnt{r}_0\rp = \cfgnt{L}\lp \cfgnt{r}_1\rp\\
    \phi_g^\prime = \lp\phi_g \wedge r_0 = r_1\rp
    }{
    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\ \cfgt{=}\ \cfgt{*} \rightarrow \cfgnt{k}\rp \rp  \rightarrow \\\\
    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp 
    }
\and
    \inferrule[Equals (reference-false)]{
    \cfgnt{L}\lp \cfgnt{r}_0\rp \neq \cfgnt{L}\lp \cfgnt{r}_1\rp\\
    \phi_g^\prime = \lp\phi_g \wedge r_0 \neq r_1\rp
   }{
    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\ \cfgt{=}\ \cfgt{*} \rightarrow \cfgnt{k}\rp \rp  \rightarrow \\\\
    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp 
    }
\end{mathpar}
\end{center}
\caption{Generalized symbolic execution with lazy initialization.}
\label{fig:lazy}
\end{figure*}

### 2014-07-02 tex/precise.tex
Regrouped rules and divided into separate files (one per figure)

\begin{figure*}[t]
\begin{center}
\mprset{flushleft}
\begin{mathpar}
	\inferrule[Field Access]{
      \forall \lp \phi\ l\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp \ \lp l = l_{\mathit{null}} \rightarrow \neg \mathbb{S}\lp \phi \wedge \phi_g\rp \rp  \\\\
      \lp \cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\rp \rightarrow^*_S \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \cfgnt{r}\ \cfgnt{f}\rp \\
      \cfgnt{r}^\prime = \mathrm{fresh}_r\lp \rp
    }{
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp  \rightarrow 
      \lp \cfgnt{L}^\prime[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}^\prime,\cfgnt{R}^\prime,\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}^\prime\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp 
	}
\and
	\inferrule[Field Write]{
	\cfgnt{r}_x = \eta\lp \cfgnt{x}\rp \\
\forall \lp \phi\ l\rp  \in \cfgnt{L}\lp \cfgnt{r}_x\rp \ \lp l = l_{\mathit{null}} \rightarrow \neg \mathbb{S}\lp \phi \wedge \phi_g\rp \rp  \\\\
      \lp \cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}_x\ \cfgnt{f}\rp \rightarrow^*_S \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \cfgnt{r}_x\ \cfgnt{f}\rp \\\\
      \Psi_x =\{\lp \cfgnt{r}_\mathit{old}\ \phi\ l\rp  \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}^\prime\lp \cfgnt{r}_x\rp  \wedge \cfgnt{r}_\mathit{old} \in \cfgnt{R}\lp l,\cfgnt{f}\rp  \}\\\\
      X = \{ \lp \cfgnt{r}_\mathit{old}\ \theta\ l\rp  \mid \exists \phi\ \lp \lp \cfgnt{r}_\mathit{old}\ \phi\ l\rp \in \Psi_x \wedge \theta = \mathbb{ST}\lp \cfgnt{L}^\prime,\cfgnt{r},\phi\rp  \cup \mathbb{ST}\lp \cfgnt{L}^\prime,\cfgnt{r}_\mathit{old},\neg\phi\rp \rp  \}\\\\
      \cfgnt{R}^{\prime\prime} = \cfgnt{R}^\prime[\forall \lp \cfgnt{r}_\mathit{old}\ \theta\ l\rp  \in X\ \lp \lp l\ \cfgnt{f}\rp  \mapsto \mathrm{fresh}_r\lp \rp \rp ]\\\\
      \cfgnt{L}^{\prime\prime} = \cfgnt{L}^\prime[\forall \lp \cfgnt{r}_\mathit{old}\ \theta\ l\rp  \in X\ \lp \exists \cfgnt{r}^{\prime}\ \lp \cfgnt{r}^\prime = \cfgnt{R}^\prime\lp l,\cfgnt{f}\rp \wedge \lp\cfgnt{r}^{\prime} \mapsto \theta\rp  \rp \rp ]
    }{
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp  \rightarrow 
      \lp \cfgnt{L}^{\prime\prime} \cfgnt{R}^{\prime\prime}\ \phi_g\ \eta\ \cfgnt{k}\rp 
	}	
\and
    \inferrule[Equals (references-true)]{
    \theta_\alpha = \{\phi_0 \wedge \phi_1 \mid \exists l\ \lp \lp \phi_0\ l\rp  \in \cfgnt{L}\lp \cfgnt{r}_0\rp  \wedge \lp \phi_1\ l\rp  \in \cfgnt{L}\lp \cfgnt{r}_1\rp \rp \} \\\\
    \theta_0 = \{\phi_0 \mid \exists l_0\ \lp \lp \phi_0\ l_0\rp  \in \cfgnt{L}\lp \cfgnt{r}_0\rp  \wedge \forall \lp \phi_1\ l_1\rp  \in \cfgnt{L}\lp \cfgnt{r}_1\rp \ \lp l_0 \neq l_1\rp \rp \} \\\\
    \theta_1 = \{\phi_1 \mid \exists l_1\ \lp \lp \phi_1\ l_1\rp  \in \cfgnt{L}\lp \cfgnt{r}_1\rp  \wedge \forall \lp \phi_0\ l_0\rp  \in \cfgnt{L}\lp \cfgnt{r}_0\rp \ \lp l_0 \neq l_1\rp \rp \} \\\\
    \phi_g^\prime =  \phi_g \wedge \lp \vee_{\phi_\alpha\in\theta_\alpha}\phi_\alpha\rp \wedge\lp \wedge_{\phi_0 \in \theta_0} \neg \phi_0\rp \wedge\lp \wedge_{\phi_1
    \in \theta_1} \neg \phi_1\rp \\\\ \mathbb{S}(\phi_g^\prime)}{
    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp  \rightarrow
    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp 
    }
\and
    \inferrule[Equals (references-false)]{
    \theta_\alpha = \{\phi_0 \rightarrow \neg \phi_1 \mid \exists l\ \lp \lp \phi_0\ l\rp  \in \cfgnt{L}\lp \cfgnt{r}_0\rp  \wedge \lp \phi_1\ l\rp  \in \cfgnt{L}\lp \cfgnt{r}_1\rp \rp \} \\\\
    \theta_0 = \{\phi_0 \mid \exists l_0\ \lp \lp \phi_0\ l_0\rp  \in \cfgnt{L}\lp \cfgnt{r}_0\rp  \wedge \forall \lp \phi_1\ l_1\rp  \in \cfgnt{L}\lp \cfgnt{r}_1\rp \ \lp l_0 \neq l_1\rp \rp \} \\\\
    \theta_1 = \{\phi_1 \mid \exists l_1\ \lp \lp \phi_1\ l_1\rp  \in \cfgnt{L}\lp \cfgnt{r}_1\rp  \wedge \forall \lp \phi_0\ l_0\rp  \in \cfgnt{L}\lp \cfgnt{r}_0\rp \ \lp l_0 \neq l_1\rp \rp \} \\\\
    \phi_g^\prime = \phi_g \wedge \lp \wedge_{\phi_\alpha\in\theta_\alpha}\phi_\alpha\rp \vee\lp \lp \vee_{\phi_0 \in \theta_0} \phi_0\rp   \vee\lp \vee_{\phi_1
    \in \theta_1} \phi_1\rp \rp  \\\\ \mathbb{S}(\phi_g^\prime)}{
    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp  \rightarrow
    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp 
    }
\end{mathpar}
\end{center}
\caption{Precise symbolic heap summaries from symbolic execution.}
\label{fig:sym}
\end{figure*}

### 2014-07-03 tex/proofs.tex
Added amsthm package to preamble

--- 2014-06-30 tex/proofs.tex
@@
 
-\subsubsection{State Representation Relation}
+\begin{definition}{State Representation}
 A symbolic system state represents a set of lazy system states.
@@
 The representation relationship is defined as follows: $\mathcal{L}\sqsubseteq \mathcal{S} $ if and only if there exists functions $g:\cfgnt{r} \mapsto \cfgnt{r}$ and $h:\cfgnt{l} \mapsto \cfgnt{l}$ such that for any reference $r \in \mathcal{L}$, location $l \in \mathcal{L}$, and field $f$, $$ l = L_{\mathcal{L}}(r) \leftrightarrow h(l)\in L_{\mathcal{S}}(g(r))$$ and $$ r = R_{\mathcal{L}}(\cfgnt{l},f) \leftrightarrow g(r) = R_{\mathcal{S}}(h(l),f)$$
+\end{definition}
+
+\begin{definition}{Exact Symbolic State}
+A symbolic state $\mathcal{S}$ is \textbf{exact} if and only if it represents the set of all feasible lazy states on the current execution path, and represents no infeasible state.
+\end{definition}
 
 \subsection{Theorems}
+
+\begin{lemma}
+If symbolic state $\mathcal{S}$ is exact prior to executing the Field Access rule, then the state $\mathcal{S}^\prime$ is also exact.
+\end{lemma}
+
+\begin{proof}
+Suppose that all relevant fields are initialized.
+Take an arbitrary lazy state $\mathcal{L} \sqsubset \mathcal{S}$ and execute the lazy field access rule to achieve state $\mathcal{L}^\prime$.
+Note that by rule, $\mathcal{L} = The only differences between  $\mathcal{L}$ and  $\mathcal{L}^\prime$ are the
+\end{proof}

### 2014-07-03 tex/proofs.tex
Started proof for field access rule. Updated definition for the representation relation

--- 2014-06-30 tex/proofs.tex
@@
 
-\subsubsection{State Representation Relation}
+\begin{definition}
+A feasible symbolic heap is defined as...
+\end{definition}
+
+\begin{definition}
+A subheap is defined as...
+\end{definition}
+
+\begin{definition}
 A symbolic system state represents a set of lazy system states.
-To denote the representation relationship, we use the expression $\mathcal{L}\sqsubset \mathcal{S} $ to say that lazy system state $\mathcal{L}:\lp \mu\ \cfgnt{L}_{\mathcal{L}}\ \cfgnt{R}_{\mathcal{L}}\ \phi_{\mathcal{L}}\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp$ is represented by symbolic state $\mathcal{S}:\lp \mu\ \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_{\mathcal{S}}\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp$ .
-The representation relationship is defined as follows: $\mathcal{L}\sqsubseteq \mathcal{S} $ if and only if there exists functions $g:\cfgnt{r} \mapsto \cfgnt{r}$ and $h:\cfgnt{l} \mapsto \cfgnt{l}$ such that for any reference $r \in \mathcal{L}$, location $l \in \mathcal{L}$, and field $f$, $$ l = L_{\mathcal{L}}(r) \leftrightarrow h(l)\in L_{\mathcal{S}}(g(r))$$ and $$ r = R_{\mathcal{L}}(\cfgnt{l},f) \leftrightarrow g(r) = R_{\mathcal{S}}(h(l),f)$$
+To denote the representation relationship, we use the expression $\mathcal{L}\sqsubset \mathcal{S} $ to say that lazy system state $\mathcal{L}:\lp \mu_{\mathcal{L}}\ \cfgnt{L}_{\mathcal{L}}\ \cfgnt{R}_{\mathcal{L}}\ \phi_{\mathcal{L}}\ \eta_{\mathcal{L}}\ \cfgnt{e}_{\mathcal{L}}\ \cfgnt{k}_{\mathcal{L}}\rp$ is represented by symbolic state $\mathcal{S}:\lp \mu_{\mathcal{S}}\ \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_{\mathcal{S}}\ \eta_{\mathcal{S}}\ \cfgnt{e}_{\mathcal{S}}\ \cfgnt{k}_{\mathcal{S}}\rp$ .
+The \textbf{representation relation} is defined as follows: $\mathcal{L}\sqsubset \mathcal{S} $ if and only if
+$$\eta_{\mathcal{L}} = \eta_{\mathcal{S}} ,\ \cfgnt{e}_{\mathcal{L}} = \cfgnt{e}_{\mathcal{S}} ,\ \cfgnt{k}_{\mathcal{L}} = \cfgnt{k}_{\mathcal{S}}$$
+and there exists functions $g:\cfgnt{r} \mapsto \cfgnt{r}$ and $h:\cfgnt{l} \mapsto \cfgnt{l}$ such that for any reference $r \in \mathcal{L}$, location $l \in \mathcal{L}$, and field $f$, $$ l = L_{\mathcal{L}}(r) \leftrightarrow h(l)\in L_{\mathcal{S}}(g(r))$$ and $$ r = R_{\mathcal{L}}(\cfgnt{l},f) \leftrightarrow g(r) = R_{\mathcal{S}}(h(l),f)$$ and the subheap of state $\mathcal{S}$ formed by selecting the image of $g$ and $h$ is feasible.
+
+\end{definition}
+
+\begin{definition}
+A symbolic state $\mathcal{S}$ is \textbf{exact} if and only if it represents the set of all feasible lazy states on the current execution path, and represents no infeasible state.
+\end{definition}
 
 \subsection{Theorems}
+
+\begin{lemma}
+If symbolic state $\mathcal{S}$ is exact prior to executing the Field Access rule, then the state $\mathcal{S}^\prime $ is also exact.
+\end{lemma}
+
+\begin{proof}
+Suppose we have some symbolic state  $\mathcal{S} =  \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp $ , and that all relevant fields are initialized.
+Take an arbitrary lazy state $\mathcal{L} \sqsubset \mathcal{S}$.
+Since $\mathcal{S}$ is exact,  $\mathcal{L} = \lp \cfgnt{L}_{\mathcal{L}}\ \cfgnt{R}_{\mathcal{L}}\ \phi_L\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k} \rp \rp$.
+If we apply the lazy field access rule to $\mathcal{L}$, we achieve state $\mathcal{L}^\prime = \lp \cfgnt{L}_{\mathcal{L}} [\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}_{\mathcal{L}}\ \phi_L\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $.
+Likewise, by applying the symbolic field access rule to $\mathcal{S}$, we obtain state $\mathcal{S}^\prime = \lp \cfgnt{L}_{\mathcal{S}}[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}_{\mathcal{S}},\cfgnt{R}_{\mathcal{S}},\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $.
+
+We now show that state $\mathcal{S}^\prime$ represents state $\mathcal{L}^\prime $.
+Since $\eta$, $e$, and $k$ are identical between $\mathcal{S}^\prime$ and $\mathcal{L}^\prime $, the first condition is met by default.
+Constructing the reference and location mappings is only slightly less trivial: $$g^\prime = g$$ $$h^\prime = h[ r^\prime \mapsto r^\prime]$$
+
+It only remains to show that the heap in $\mathcal{L}^\prime$ is feasible, WHICH WILL BE EASY ONCE WE DEFINE WHAT THAT MEANS.
+
+Now, we show that no infeasible lazy states are allowed by $\mathcal{S}^\prime$. NEED TO FILL IN THIS BIT, TOO

### 2014-07-03 tex/pseudo-code.tex
Finished preciese heap summaries
Regrouped rules and divided into separate files (one per figure)
Added end on proof environment

@@
 \figref{fig:surface-syntax} defines the surface syntax for the
-Javalite language \cite{saints-MS}. The \figref{fig:machine-syntax} is
-the machine syntax. The semantics of Javalite is syntax based and
-defined as rewrites on a string. The semantics use a CEKS machine
-model with a (C)ontrol string representing the expression being
+Javalite language \cite{saints-MS}. \figref{fig:machine-syntax} is
+the machine syntax. Javalite is syntactic machine
+defined as rewrites on a string. The semantics use a CEKS model with a (C)ontrol string representing the expression being
 evaluated, an (E)nvironment for local variables, a (K)ontinuation for
-what is to be executed next, and a (S)tore for the heap. This paper
-only defines salient features of the language and machine relevant to
-understanding the new algorithm.
+what is to be executed next, and a (S)tore for the heap.
 
@@
 %\item $n$ are numbers, and the set of all positive natural numbers is $\mathbb{N}^+$.
-This paper uses a standard definition of constraints $\phi \in \Phi$
-assuming all the usual relational operators and connectives. The heap
-is a labeled bipartite graph consisting of references $R$ and
+The heap is a labeled bipartite graph consisting of references $R$ and
 locations $L$ in the store. The functions $R$ and $L$ are defined for convenience
@@
 \begin{array}{rcl}
-  \mathbb{VS}(L,R,\phi_g,r,f) & = & \{(l^\prime\ \phi^\prime\wedge\phi) \mid \\
+  \mathbb{VS}(L,R,\phi_g,r,f) & = & \{(l^\prime\ \phi\wedge\phi^\prime) \mid \\
   & & \ \ \ \ \exists l\ ((l\ \phi) \in L(r)\ \wedge \\
@@
 
-\input{machine-rules}
+\input{javalite-common}
+\input{initialize-lazy}
+\input{lazy}
+\input{summarize-precise}
+\input{precise}

### 2014-07-03 tex/proofs.tex
Minor change to the field access proof
Added end on proof environment
added definitions for state sequences

@@
 \begin{definition}
-A feasible symbolic heap is defined as...
+A \textbf{state transition function} $\Phi$ is a mapping $\Phi : s \mapsto s$ , which takes one machine state and transforms it into another machine state.
 \end{definition}
@@
 \begin{definition}
-A subheap is defined as...
+Given a sequence of states $$\Sigma_n = s_0,s_1,...,s_n$$ where $$s_i = \lp \mu_i\ \cfgnt{L}_i\ \cfgnt{R}_i\ \phi_i\ \eta_i\ \cfgnt{e}_i\ \cfgnt{k}_i\rp$$ the \textbf{control flow sequence} of $\Sigma_n$ is the defined as the sequence of tuples $$ \sigma_n = \mathbb{CF}(\Sigma_n) = (\eta_0,\cfgnt{e}_0,\cfgnt{k}_0),(\eta_1,\cfgnt{e}_1,\cfgnt{k}_1),...,(\eta_n,\cfgnt{e}_n,\cfgnt{k}_n)$$
+\end{definition}
+
+\begin{definition}
+A \textbf{feasible state sequence} is defined as a sequence of states resulting from repeated application of the state transition relation: $$ \Sigma_n = s_0, \Phi (s_0) ,..., \Phi_{n-1} (s_0) $$
+\end{definition}
+
+\begin{definition}
+Given a state transition function $\Phi$, an initial state $s_0$ and a control flow sequence $\sigma_n$, the \textbf{feasible state set} $\zeta = \mathbb{FS}(\Phi,s_0,sigma)$ is defined as
+ $$\zeta = \{ \forall s | \sigma_n = \mathbb{CF}(\Sigma_n) \wedge s = max_s(\Sigma) \wedge s = \Phi_{n-1}(s_o)\} $$
 \end{definition}
@@
 A symbolic state $\mathcal{S}$ is \textbf{exact} if and only if it represents the set of all feasible lazy states on the current execution path, and represents no infeasible state.
+
+ \forall (R_S^i\ L_S^i) \in \mathit{Heaps}(S_s)\ (\exists (R_L\ S_L)\ ((R_L\ S_L) = (R_S^i\ L_S^i))) \\ \\
+
 \end{definition}
@@
 
-It only remains to show that the heap in $\mathcal{L}^\prime$ is feasible, WHICH WILL BE EASY ONCE WE DEFINE WHAT THAT MEANS.
+It only remains to show that the image of $\mathcal{L}^\prime$ in $\mathcal{S}^\prime$ is feasible, WHICH WILL BE EASY ONCE WE DEFINE WHAT THAT MEANS.
 
 Now, we show that no infeasible lazy states are allowed by $\mathcal{S}^\prime$. NEED TO FILL IN THIS BIT, TOO
+
+$\mathbb{S}(\bigwedge_{(\phi l) \in L_s^i} \phi)) \wedge \forall l \in L_L (\exists l \in L_s^i)$
+\end{proof}

### 2014-07-03 tex/pseudo-code.tex
Added

@@
-\section{Pseudo-code}
+\section{Generalized Symbolic Execution with Lazy Initialization}
+Generalized symbolic execution with lazy initialization is a technique
+to apply symbolic execution to non-primitive data types (i.e.,
+objects) \cite{GSE03}. The approach initializes each symbolic object
+to be either null, a new instance of the object, or an alias to an
+object previously created as part of lazy initialization. Each of
+these outcomes is a possible choice, and a model checker is able to
+exhaustively enumerates these choices effectively creating all
+possible concrete heaps under the choice sets. The approach is first formalized in this section and then extended to describe the precise heap summaries.
+
+Many of these concrete
+heaps explore redundant control flow paths in the program under test,
+but since symbolic model checking is stateless, subject to a bound to
+terminate the search, the model checker needlessly explores many
+redundant state leading to severe state explosion.
+
 \figref{fig:surface-syntax} defines the surface syntax for the

### 2014-07-04 tex/proofs.tex
Added
Changed the title. Miscellaneous corrections and additions to the proofs section

--- 2014-07-03 tex/proofs.tex
@@
 \begin{definition}
-A feasible symbolic heap is defined as...
+A \textbf{state transition function} $\rightarrow_{\Phi}$ is a mapping $\rightarrow_{\Phi} : s \mapsto s$ , which takes one machine state and transforms it into another machine state.
+The state transition function with superscript represents composition of the state transition function: $$ s_a \rightarrow_{\Phi} s_b \rightarrow_{\Phi} s_c \implies s_a \rightarrow_{\Phi}^2 s_c $$
 \end{definition}
@@
 \begin{definition}
-A subheap is defined as...
+A \textbf{feasible state sequence} is defined as a sequence of states resulting from repeated application of the state transition relation to some initial state $s_0$: $$\Pi_n = s_0,s_1,...,s_n$$ where the relation $s_i \rightarrow_{\Phi} s_{i+1}$ holds for all $i \in \{ i | 0 \leq i < n \}$
 \end{definition}
@@
 \begin{definition}
+Given a sequence of states $$\Pi_n = s_0,s_1,...,s_n$$ where $$s_i = \lp \mu_i\ \cfgnt{L}_i\ \cfgnt{R}_i\ \phi_i\ \eta_i\ \cfgnt{e}_i\ \cfgnt{k}_i\rp$$ the \textbf{control flow sequence} of $\Pi_n$ is the defined as the sequence of tuples $$ \pi_n = \mathbb{CF}(\Pi_n) = (\eta_0\ \cfgnt{e}_0\ \cfgnt{k}_0),(\eta_1\ \cfgnt{e}_1\ \cfgnt{k}_1),...,(\eta_n\ \cfgnt{e}_n\ \cfgnt{k}_n)$$
+\end{definition}
+
+\begin{definition}
+Given a state transition function $\rightarrow_{\Phi}$, an initial state $s_0$ and a control flow sequence $\pi_n$, the \textbf{feasible state set} $\zeta = \mathbb{FS}(\rightarrow_{\Phi},s_0,sigma)$ is defined as
+ $$\zeta = \{ \forall s | \pi_n = \mathbb{CF}(\Pi_n) \wedge s = max_s(\Pi) \wedge s_0 \rightarrow_{\Phi}^{n-1} s\} $$
+\end{definition}
+
+\begin{definition}
+A \textbf{heap homomorphism} between two states $s_x$ and $s_y$ is defined as a pair of functions $g:\cfgnt{r} \mapsto \cfgnt{r}$ and $h:\cfgnt{l} \mapsto \cfgnt{l}$ such that for any reference $r \in \s_x$, location $l \in s_x$, and field $f$, $$ l = L_x(r) \leftrightarrow h(l)\in L_y(g(r))$$ and $$ r = R_x(\cfgnt{l},f) \leftrightarrow g(r) = R_y(h(l),f)$$ If a such a pair of functions exists from one state $s_x$ to another state $s_y$ we say that state $s_x$ is \textbf{heap homomorphic} to state $s_y$, indicated by the notation $(g\ f):\ s_x \rightarrow s_y$.
+
+\begin{definition}
 A symbolic system state represents a set of lazy system states.
-To denote the representation relationship, we use the expression $\mathcal{L}\sqsubset \mathcal{S} $ to say that lazy system state $\mathcal{L}:\lp \mu_{\mathcal{L}}\ \cfgnt{L}_{\mathcal{L}}\ \cfgnt{R}_{\mathcal{L}}\ \phi_{\mathcal{L}}\ \eta_{\mathcal{L}}\ \cfgnt{e}_{\mathcal{L}}\ \cfgnt{k}_{\mathcal{L}}\rp$ is represented by symbolic state $\mathcal{S}:\lp \mu_{\mathcal{S}}\ \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_{\mathcal{S}}\ \eta_{\mathcal{S}}\ \cfgnt{e}_{\mathcal{S}}\ \cfgnt{k}_{\mathcal{S}}\rp$ .
+To denote the representation relationship, we use the expression $\mathcal{L} \sqsubset \mathcal{S} $ to say that lazy system state $\mathcal{L}:\lp \mu_{\mathcal{L}}\ \cfgnt{L}_{\mathcal{L}}\ \cfgnt{R}_{\mathcal{L}}\ \phi_{\mathcal{L}}\ \eta_{\mathcal{L}}\ \cfgnt{e}_{\mathcal{L}}\ \cfgnt{k}_{\mathcal{L}}\rp$ is represented by symbolic state $\mathcal{S}:\lp \mu_{\mathcal{S}}\ \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_{\mathcal{S}}\ \eta_{\mathcal{S}}\ \cfgnt{e}_{\mathcal{S}}\ \cfgnt{k}_{\mathcal{S}}\rp$ .
 The \textbf{representation relation} is defined as follows: $\mathcal{L}\sqsubset \mathcal{S} $ if and only if
@@
 A symbolic state $\mathcal{S}$ is \textbf{exact} if and only if it represents the set of all feasible lazy states on the current execution path, and represents no infeasible state.
+\[
+ \forall (R_S^i\ L_S^i) \in \mathit{Heaps}(S_s)\ (\exists (R_L\ S_L)\ ((R_L\ S_L) = (R_S^i\ L_S^i))) \\ \\
+\]
+
 \end{definition}

### 2014-07-05 tex/proofs.tex
Added more definitions.

--- 2014-07-03 tex/proofs.tex
@@
 \begin{definition}
-A symbolic system state represents a set of lazy system states.
-To denote the representation relationship, we use the expression $\mathcal{L}\sqsubset \mathcal{S} $ to say that lazy system state $\mathcal{L}:\lp \mu_{\mathcal{L}}\ \cfgnt{L}_{\mathcal{L}}\ \cfgnt{R}_{\mathcal{L}}\ \phi_{\mathcal{L}}\ \eta_{\mathcal{L}}\ \cfgnt{e}_{\mathcal{L}}\ \cfgnt{k}_{\mathcal{L}}\rp$ is represented by symbolic state $\mathcal{S}:\lp \mu_{\mathcal{S}}\ \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_{\mathcal{S}}\ \eta_{\mathcal{S}}\ \cfgnt{e}_{\mathcal{S}}\ \cfgnt{k}_{\mathcal{S}}\rp$ .
-The \textbf{representation relation} is defined as follows: $\mathcal{L}\sqsubset \mathcal{S} $ if and only if
-$$\eta_{\mathcal{L}} = \eta_{\mathcal{S}} ,\ \cfgnt{e}_{\mathcal{L}} = \cfgnt{e}_{\mathcal{S}} ,\ \cfgnt{k}_{\mathcal{L}} = \cfgnt{k}_{\mathcal{S}}$$
-and there exists functions $g:\cfgnt{r} \mapsto \cfgnt{r}$ and $h:\cfgnt{l} \mapsto \cfgnt{l}$ such that for any reference $r \in \mathcal{L}$, location $l \in \mathcal{L}$, and field $f$, $$ l = L_{\mathcal{L}}(r) \leftrightarrow h(l)\in L_{\mathcal{S}}(g(r))$$ and $$ r = R_{\mathcal{L}}(\cfgnt{l},f) \leftrightarrow g(r) = R_{\mathcal{S}}(h(l),f)$$ and the subheap of state $\mathcal{S}$ formed by selecting the image of $g$ and $h$ is feasible.
-
+Given a sequence of states $$\Pi_n = s_0,s_1,...,s_n$$ where $$s_i = ( \mu_i\ \cfgnt{L}_i\ \cfgnt{R}_i\ \phi_i\ \eta_i\ \cfgnt{e}_i\ \cfgnt{k}_i )$$ the \textbf{control flow sequence} of $\Pi_n$ is the defined as the sequence of tuples $$ \pi_n = \mathbb{CF}(\Pi_n) = (\eta_0\ \cfgnt{e}_0\ \cfgnt{k}_0),(\eta_1\ \cfgnt{e}_1\ \cfgnt{k}_1),...,(\eta_n\ \cfgnt{e}_n\ \cfgnt{k}_n)$$
 \end{definition}
@@
 \begin{definition}
-A symbolic state $\mathcal{S}$ is \textbf{exact} if and only if it represents the set of all feasible lazy states on the current execution path, and represents no infeasible state.
+Given a state transition function $\rightarrow_{\Phi}$, an initial state $s_0$ and a control flow sequence $\pi_n$, the \textbf{feasible state set} $\zeta = \mathbb{FS}(\rightarrow_{\Phi},s_0,\pi_n)$ is defined as
+ $$\zeta = \{ \forall s | \pi_n = \mathbb{CF}(\Pi_n) \wedge s = max_s(\Pi) \wedge s_0 \rightarrow_{\Phi}^{n-1} s\} $$
+\end{definition}
+
+\begin{definition}
+A \textbf{heap homomorphism} $(g\ h)$ between two states $s_x$ and $s_y$ is defined as a pair of functions $g:\cfgnt{r} \mapsto \cfgnt{r}$ and $h:\cfgnt{l} \mapsto \cfgnt{l}$ such that for any reference $r \in s_x$, location $l \in s_x$, and field $f$, $$ l \in \cfgnt{L}_x(r) \Leftrightarrow h(l)\in \cfgnt{L}_y(g(r))$$ and $$ r = \cfgnt{R}_x(l,f) \Leftrightarrow g(r) = \cfgnt{R}_y(h(l),f)$$ If a such a pair of functions exists from one state $s_x$ to another state $s_y$ we say that state $s_x$ is \textbf{heap homomorphic} to state $s_y$, indicated by the notation $(g\ f):\ s_x \rightarrow s_y$.
+
+Suppose we take the set of constraints from the image of $s_x$ in $s_y$ under $(g\ h)$ :
+$$\chi = \{ \phi\ | \exists (r \in \cfgnt{R}_x,\  l \in \cfgnt{L}_x) ( (\phi\ h(l)) \in \cfgnt{L}_y (g(r))  \}$$ and we conjoin those constraints with the global invariant from $s_y$ :
+$$\phi_G = \phi_y \bigwedge_{\phi_i \in \chi} \phi_i $$
+ If the expression $\phi_G$ is satisfiable, we say that the heap homomorphism $(g\ h):\ s_x \rightarrow s_y $ is \textbf{valid}.
+\end{definition}
+\begin{definition}
+A symbolic system state represents a set of lazy system states.
+To denote the representation relationship, we use the expression $s_\ell \sqsubset s_s $ to say that lazy system state $s_\ell$ is represented by symbolic state $s_s$ .
+The \textbf{representation relation} is defined as follows: $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a valid heap homomorphism $(g\ h):\ s_\ell \rightarrow s_s $.
+\end{definition}
+
+\begin{definition}
+A symbolic state $s_s$ is \textbf{exact} with respect to an initial state $s_0$ and control flow path $\pi$ if and only if it represents every state in the set feasible lazy states and represents no infeasible state:
+
+$$ s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi) \Leftrightarrow s_\ell \sqsubset s_s $$
+
 \end{definition}

### 2014-07-06 tex/proofs.tex
More work on the proofs section.

@@
 \begin{definition}
-A symbolic system state represents a set of lazy system states.
-To denote the representation relationship, we use the expression $s_\ell \sqsubset s_s $ to say that lazy system state $s_\ell$ is represented by symbolic state $s_s$ .
-The \textbf{representation relation} is defined as follows: $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a valid heap homomorphism $(g\ h):\ s_\ell \rightarrow s_s $.
+The \textbf{representation relation} is defined as follows: given two states $s_\ell$ and $s_s$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a valid heap homomorphism $(g\ h):\ s_\ell \rightarrow s_s $.
+The expression $s_\ell \sqsubset s_s $ can be read as "state $s_\ell$ is represented by state $s_s$ .
 \end{definition}
@@
 \begin{definition}
-A symbolic state $s_s$ is \textbf{exact} with respect to an initial state $s_0$ and control flow path $\pi$ if and only if it represents every state in the set feasible lazy states and represents no infeasible state:
+A state $s_s$ is \textbf{congruent} to a set of states $\mathcal{S}$ if and only if $s$ represents every state in $\mathcal{S}$ and represents no other state: 
+$$ s_s \equiv \mathcal{S} : s_i \in \mathcal{S} \Leftrightarrow s_i \sqsubset s_s $$
+\end{definition}
 
-$$ s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi) \Leftrightarrow s_\ell \sqsubset s_s $$
-
+\begin{definition}
+A symbolic state $s_s$ is \textbf{exact} with respect to an initial state $s_0$ and control flow sequence $\pi$ if and only if it is congruent the set of feasible lazy states on the same control flow path:
+$$ s_s \equiv \mathbb{FS}(\rightarrow_{\ell},s_0,\pi)$$
 \end{definition}
@@
 \begin{lemma}
-If symbolic state $\mathcal{S}$ is exact prior to executing the Field Access rule, then the state $\mathcal{S}^\prime $ is also exact.
+If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the state $s_s^\prime : s_s \rightarrow_s s_s^\prime$ is exact with respect to $s_0$ and $\pi_{n+1}.
 \end{lemma}
@@
 \begin{proof}
-Suppose we have some symbolic state  $\mathcal{S} =  \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp $ , and that all relevant fields are initialized.
-Take an arbitrary lazy state $\mathcal{L} \sqsubset \mathcal{S}$.
-Since $\mathcal{S}$ is exact,  $\mathcal{L} = \lp \cfgnt{L}_{\mathcal{L}}\ \cfgnt{R}_{\mathcal{L}}\ \phi_L\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k} \rp \rp$.
-If we apply the lazy field access rule to $\mathcal{L}$, we achieve state $\mathcal{L}^\prime = \lp \cfgnt{L}_{\mathcal{L}} [\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}_{\mathcal{L}}\ \phi_L\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $.
-Likewise, by applying the symbolic field access rule to $\mathcal{S}$, we obtain state $\mathcal{S}^\prime = \lp \cfgnt{L}_{\mathcal{S}}[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}_{\mathcal{S}},\cfgnt{R}_{\mathcal{S}},\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $.
+We will consider two cases for this proof. In the first case, we assume that all of the fields involved in the read are initialized. In the second case we consider the case of uninitialized fields.
 
-We now show that state $\mathcal{S}^\prime$ represents state $\mathcal{L}^\prime $.
-Since $\eta$, $e$, and $k$ are identical between $\mathcal{S}^\prime$ and $\mathcal{L}^\prime $, the first condition is met by default.
-Constructing the reference and location mappings is only slightly less trivial: $$g^\prime = g$$ $$h^\prime = h[ r^\prime \mapsto r^\prime]$$
+Case 1: suppose all of the pertinent fields in $s_s$ are initialized.
+Take an arbitrary lazy state $s_\ell \sqsubset s_s$.
+Since $s_s$ is exact,  $s_\ell = \lp \cfgnt{L}_{\ell}\ \cfgnt{R}_{\ell}\ \phi_L\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k} \rp \rp$.
+If we apply the state transition functions to achieve states $s_\ell^\prime : s_\ell \rightarrow_\ell s_\ell^\prime$ and $s_s^\prime : s_s \rightarrow_s s_s^\prime$, we find that:
+$$s_\ell^\prime = \lp \cfgnt{L}_{\ell} [\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}_{\ell}\ \phi_L\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
+ and 
+ $$ s_s^\prime = \lp \cfgnt{L}_{s}[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}_{\mathcal{S}},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
 
-It only remains to show that the image of $\mathcal{L}^\prime$ in $\mathcal{S}^\prime$ is feasible, WHICH WILL BE EASY ONCE WE DEFINE WHAT THAT MEANS.
+We now show that $s_\ell^\prime \sqsubset s_s^\prime$.
+Since $\eta$, $e$, and $k$ are identical between $s_s^\prime$ and $s_\ell^\prime $, the first condition is met by default.
+To find a valid heap homomorphism, first construct functions $g^\prime : g^\prime = g[ r^\prime \mapsto r^\prime]$ and $h^\prime : h^\prime = h$.
+
+%we now need to show that we have a heap homomorphism here, and that the homomorphism is valid. once we've done that , we've proved the soundness case
 
@@
 $\mathbb{S}(\bigwedge_{(\phi l) \in L_s^i} \phi)) \wedge \forall l \in L_L (\exists l \in L_s^i)$
+
+Since $s_\ell \subseteq s_s$
 \end{proof}

### 2014-07-06 tex/proofs.tex
Case 1 for the first proof is complete.

@@
 \begin{definition}
-A \textbf{heap homomorphism} $(g\ h)$ between two states $s_x$ and $s_y$ is defined as a pair of functions $g:\cfgnt{r} \mapsto \cfgnt{r}$ and $h:\cfgnt{l} \mapsto \cfgnt{l}$ such that for any reference $r \in s_x$, location $l \in s_x$, and field $f$, $$ l \in \cfgnt{L}_x(r) \Leftrightarrow h(l)\in \cfgnt{L}_y(g(r))$$ and $$ r = \cfgnt{R}_x(l,f) \Leftrightarrow g(r) = \cfgnt{R}_y(h(l),f)$$ If a such a pair of functions exists from one state $s_x$ to another state $s_y$ we say that state $s_x$ is \textbf{heap homomorphic} to state $s_y$, indicated by the notation $(g\ f):\ s_x \rightarrow s_y$.
+A \textbf{heap homomorphism} $(g\ h)$ between two states $s_x$ and $s_y$ is defined as a pair of functions $g:\cfgnt{r} \mapsto \cfgnt{r}$ and $h:\cfgnt{l} \mapsto \cfgnt{l}$ such that for any reference $r \in s_x$, location $l \in s_x$, and field $f$, $$ (\phi_x\ l) \in \cfgnt{L}_x(r) \Rightarrow (\phi_y\ h(l))\in \cfgnt{L}_y(g(r))$$ and $$ r = \cfgnt{R}_x(l,f) \Rightarrow g(r) = \cfgnt{R}_y(h(l),f)$$ If a such a pair of functions exists from one state $s_x$ to another state $s_y$ we say that state $s_x$ is \textbf{heap homomorphic} to state $s_y$, indicated by the notation $(g\ f):\ s_x \rightarrow s_y$.
 
@@
 \begin{definition}
+\label{representation}
 The \textbf{representation relation} is defined as follows: given two states $s_\ell$ and $s_s$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a valid heap homomorphism $(g\ h):\ s_\ell \rightarrow s_s $.
@@
 \begin{definition}
+\label{congruent}
 A state $s_s$ is \textbf{congruent} to a set of states $\mathcal{S}$ if and only if $s$ represents every state in $\mathcal{S}$ and represents no other state: 
@@
 \begin{definition}
+\label{exact}
 A symbolic state $s_s$ is \textbf{exact} with respect to an initial state $s_0$ and control flow sequence $\pi$ if and only if it is congruent the set of feasible lazy states on the same control flow path:
@@
 Take an arbitrary lazy state $s_\ell \sqsubset s_s$.
-Since $s_s$ is exact,  $s_\ell = \lp \cfgnt{L}_{\ell}\ \cfgnt{R}_{\ell}\ \phi_L\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k} \rp \rp$.
+Since $s_s$ is exact,  $s_\ell = \lp \cfgnt{L}_{\ell}\ \cfgnt{R}_{\ell}\ \phi_L\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k} \rp \rp$, and that $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$.
 If we apply the state transition functions to achieve states $s_\ell^\prime : s_\ell \rightarrow_\ell s_\ell^\prime$ and $s_s^\prime : s_s \rightarrow_s s_s^\prime$, we find that:
@@
 Since $\eta$, $e$, and $k$ are identical between $s_s^\prime$ and $s_\ell^\prime $, the first condition is met by default.
-To find a valid heap homomorphism, first construct functions $g^\prime : g^\prime = g[ r^\prime \mapsto r^\prime]$ and $h^\prime : h^\prime = h$.
+Now we construct functions $g^\prime : g^\prime = g[ r^\prime \mapsto r^\prime]$ and $h^\prime : h^\prime = h$.
+Observe that since $s_\ell \rightarrow s_s$, and since $\cfgnt{R}_\ell$ and $\cfgnt{R}_s$ are unchanged from states $s_\ell$ to $s_\ell^\prime$ and $s_s$ to $s_s^\prime$ respectively, we are guaranteed that $ r = \cfgnt{R}_\ell(l,f) \Rightarrow g^\prime(r) = \cfgnt{R}_s(h^\prime(l),f)$.
+Since $(\phi_\ell^\prime\ l^\prime) =  \cfgnt{L}_\ell(\cfgnt{R}_\ell(l,f))$, and since $(g\ h)$ is valid, we know that:
+ $$(\phi_s \wedge \phi_s^\prime\ l^\prime) \in \mathbb{VS}\lp \cfgnt{L}_{\mathcal{S}},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp$$ 
+From this, we may deduce that:
+$$ (\phi_\ell\ l) \in \cfgnt{L}_\ell^\prime(r^\prime) \Rightarrow (\phi_s \wedge \phi_s^\prime\ h^\prime(l))\in \cfgnt{L}_s^\prime(g^\prime(r^\prime))$$
+Since $r^\prime$ the only new addition to $L_\ell^\prime$ and $L_s^\prime$, we now know that the assertion above holds for all $l \in s_\ell^\prime$.
+Thus, we have shown that $(g^\prime\ h^\prime)$ is a heap homomorphism from $s_\ell^\prime$ to $s_s^\prime$.
+Furthermore, since $\mathbb{S}(\phi_s\wedge\phi_s^\prime\wedge \phi_g)$ holds true, we know that $(g^\prime\ h^\prime):\ s_\ell^\prime \rightarrow s_s^\prime$ is valid.
+Since there is a valid heap homomorphism, and since $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, we  by definition \ref{representation} know $s_\ell^\prime \sqsubset s_s^\prime$.
+We have now shown that for any lazy state $s_\ell$: $$s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime}$$
+%Since since only the lazy field access rule accepts states with the same form as $s_\ell$, and since only the lazy field access rule produces a state with the same form as $s_\ell^\prime$, we know that $$s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$$
+%by combining the previous two equations, we can finally conclude that 
+%$$s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1}) \Rightarrow  s_\ell^\prime \sqsubset s_s^\prime}$$
 
-%we now need to show that we have a heap homomorphism here, and that the homomorphism is valid. once we've done that , we've proved the soundness case
+Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$, but $s_i^\prime \notin \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
+Since $s_i^\prime \sqsubset s_s^\prime$, there must exist a valid homomorphism (g_i^\prime h_i^\prime): s_i^\prime \rightarrow s_s^\prime$.
+If $(g_i^\prime\ h_i^\prime)$ is valid, then there must also exist a valid homomorphism $(g_i\ h_i) : s_i \rightarrow s_s$, and by extension, state $s_i \sqsubset s_s$.
+However, since $s_s$ is exact, $s_i \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n})$, and by our previous result, $s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
+We have a contradiction.
+Therefore, $$s_i^\prime \sqsubset s_s^\prime \Rightarrow s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$$ Combining the two previous equations, we find that
+$$s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime}$$
+By definition \ref{congruent}, $s_s^\prime \equiv \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, and so by definition \ref{exact}, $s_s^\prime$ is exact.
 
-Now, we show that no infeasible lazy states are allowed by $\mathcal{S}^\prime$. NEED TO FILL IN THIS BIT, TOO
-
-$\mathbb{S}(\bigwedge_{(\phi l) \in L_s^i} \phi)) \wedge \forall l \in L_L (\exists l \in L_s^i)$
-
-Since $s_\ell \subseteq s_s$
 \end{proof}

### 2014-07-06 tex/proofs.tex
fixed some bugs in proofs.tex

@@
 \begin{lemma}
-If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the state $s_s^\prime : s_s \rightarrow_s s_s^\prime$ is exact with respect to $s_0$ and $\pi_{n+1}.
+If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the state $s_s^\prime : s_s \rightarrow_s s_s^\prime$ is exact with respect to $s_0$ and $\pi_{n+1}$.
 \end{lemma}
@@
 Since there is a valid heap homomorphism, and since $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, we  by definition \ref{representation} know $s_\ell^\prime \sqsubset s_s^\prime$.
-We have now shown that for any lazy state $s_\ell$: $$s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime}$$
+We have now shown that for any lazy state $s_\ell$:
+$$s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime)$$
 %Since since only the lazy field access rule accepts states with the same form as $s_\ell$, and since only the lazy field access rule produces a state with the same form as $s_\ell^\prime$, we know that $$s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$$
@@
 Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$, but $s_i^\prime \notin \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
-Since $s_i^\prime \sqsubset s_s^\prime$, there must exist a valid homomorphism (g_i^\prime h_i^\prime): s_i^\prime \rightarrow s_s^\prime$.
+Since $s_i^\prime \sqsubset s_s^\prime$, there must exist a valid homomorphism $(g_i^\prime h_i^\prime): s_i^\prime \rightarrow s_s^\prime$.
 If $(g_i^\prime\ h_i^\prime)$ is valid, then there must also exist a valid homomorphism $(g_i\ h_i) : s_i \rightarrow s_s$, and by extension, state $s_i \sqsubset s_s$.
@@
 Therefore, $$s_i^\prime \sqsubset s_s^\prime \Rightarrow s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$$ Combining the two previous equations, we find that
-$$s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime}$$
+$$s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime)$$
 By definition \ref{congruent}, $s_s^\prime \equiv \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, and so by definition \ref{exact}, $s_s^\prime$ is exact.

### 2014-07-07 tex/proofs.tex
Added proof for reference compares.

@@
 
+\begin{theorem}
+\label{thm:mutex}
+In any symbolic state $s_s$, the constraints in the value set of any reference are mutually exclusive.
+\end{theorem}
+\begin{proof}
+\end{proof}
+
 \begin{lemma}
-If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the state $s_s^\prime : s_s \rightarrow_s s_s^\prime$ is exact with respect to $s_0$ and $\pi_{n+1}$.
+\label{lem:init}
+If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the intermediate state state $s_f : s_s \rightarrow w_s s_f$ is congruent to $\{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$.
+\end{lemma}
+
+\begin{proof}%going through this one quickly, could be more formal...
+Given a lazy state $s_\ell \sqsubset s_s$, there are four distinct possibilities for $s_\ell^\prime$: either the field is already initialized, or the field is initialized to a new reference, the null reference, or an alias.
+
+Case 1: Suppose the field is initialized. In this case, the rule does nothing and the theorem is trivially true.
+
+%for the next case, we need to show that the constraints in the symbolic heap don't allow any infeasible heaps.
+The key to this will be in showing that the constraints are mutually exclusive and collectively exhaustive.
+Mutually exclusive constraints are required because lazy heaps only point to one place at at time.
+Collectively exhaustive constraints are required to eliminate any other possible heaps.
+We could start by explicitly enumerating the members of the product feasible set, and working from there to show that the symbolic heap is congruent to that set.
+Or, we might do this on a case-by-case basis to show that for an arbitrary lazy state, any of it's three possible target states is in the feasible set.
+
+Case 2: The "new" rule gets executed.
+
+Case 3: The "null" rule gets executed.
+
+Case 4: The "alias" rule gets executed.
+\end{proof}
+
+\begin{lemma}
+If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the state $s_s^\prime : s_s \rightarrow_s s_f$ is exact with respect to $s_0$ and $\pi_{n+1}$.
 \end{lemma}
@@
 We have now shown that for any lazy state $s_\ell$:
-$$s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime)$$
-%Since since only the lazy field access rule accepts states with the same form as $s_\ell$, and since only the lazy field access rule produces a state with the same form as $s_\ell^\prime$, we know that $$s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$$
-%by combining the previous two equations, we can finally conclude that 
-%$$s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1}) \Rightarrow  s_\ell^\prime \sqsubset s_s^\prime}$$
+$$s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$$
+
+%there is a little hand-waving here.
+We claim that that a valid (g' h') implies a valid (g h), but the reason for this is actually pretty subtle and should probably be detailed better.
+Basically, it depends on the fact that the value set for the returned reference is contingent on the entire access path from the root of the heap.
+Another hand-wavy part is showing that the lazy machine will turn si into si'.
+Finally, we still need to show that if we run the lazy machine on every feasible state in si that we get every feasible state in si' .
 
@@
 
+Case 2: If there are uninitialized fields, then the lazy initialization machine will make an intermediate state $s_t$.
+By lemma \ref{lem:init}, the symbolic state is congruent to the set of lazy initialized states.
+From the intermediate state, the proof is the same as for case 1.
 \end{proof}
+
+%proof for field write
+\begin{lemma}
+The field write rule is correct.
+\end{lemma}
+\begin{proof}
+\end{proof}
+
+%proof for reference compares. Here we will rely on the fact that since the L and R functions don't change, and since the phi function
+\begin{lemma}
+If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the state $s_s^\prime : s_s \rightarrow_s s_f$ is exact with respect to $s_0$ and $\pi_{n+1}$.
+\end{lemma}
+There are two rules that apply to state $s_s$, one for the $\cfgt{true}$ branch and one for the $\cfgt{false}$ branch.
+Since the proofs for both rules are nearly identical, for clarity we will only prove the case for the $\cfgt{true}$ branch here.
+\begin{proof}
+Choose any $s_\ell \sqsubset s_s$, and let $\zeta_T = \mathbb{FS}(\rightarrow_{\ell},s_0,(\pi_n,(\eta\ \cfgt{true}\ \cfgnt{k})))$.
+Since $s_s$ is exact, we know that $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, $s_l = \lp \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$, and that there exists $(g\ h) : s_\ell \rightarrow s_s$.
+Depending on the values of $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, there are two different rules that might apply to $s_\ell$.
+In either case, $\cfgnt{L}_\ell$ and $\cfgnt{R}_\ell$ are unchanged, and $\phi_\ell$ is strengthened, so we already know that
+$$ \zeta_T \subseteq \{s_\ell^\prime | \exists s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n}) (s_\ell \rightarrow_\ell s_\ell^\prime )\}$$
+
+Case 1: Assume $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp = \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$.
+In this case, the equals - references true rule applies, and we know state $s_\ell^\prime : s_\ell \rightarrow_\ell s_\ell^\prime$ is in $\zeta_T$.
+Since $(g\ h)$ is valid, we know that $\exists \lp \phi_0\ l \rp \in \cfgnt{L}_\ell\lp g \lp \cfgnt{r}_0\rp \rp$, $\exists \lp \phi_1\ l \rp \in \cfgnt{L}_\ell\lp g \lp \cfgnt{r}_1\rp \rp$, and that $\mathbb{S}\lp\phi_s\wedge\phi_0\wedge \phi_1\rp$ holds true.
+Observe that by applying theorem \ref{thm:mutex}, $\phi_s^\prime \wedge \phi_0 \wedge \phi_1$ reduces to $\phi_s$.
+Therefore, $\lp g\ h \rp: s_\ell^\prime \rightarrow s_s^\prime$ is a valid heap homomorphism, and by extension, $s_\ell^\prime \sqsubset s_s^\prime$.
+Since this relation holds for arbitrary $s_\ell^\prime \in \zeta_t$, we now know that $s_\ell^\prime \in \zeta_T \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$.
+% Furthermore, since  and since we may conclude that $s_s^\prime \equiv \zeta_T$.
+
+\end{proof}
+
+\begin{theorem}
+Every symbolic state on every execution path is exact.
+\end{theorem}
+\begin{proof}
+Combine all of the production-rule lemmas to inductively prove the theorem.
+\end{proof}

### 2014-07-07 tex/proofs.tex
Fixed a typo in the field initialization lemma
The reference compares proof is now nearly complete

@@
 \label{lem:init}
-If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the intermediate state state $s_f : s_s \rightarrow w_s s_f$ is congruent to $\{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$.
+If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the intermediate state state $s_f : s_s \rightarrow_S s_f$ is congruent to $\{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$.
 \end{lemma}
@@
 \begin{lemma}
-If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the state $s_s^\prime : s_s \rightarrow_s s_f$ is exact with respect to $s_0$ and $\pi_{n+1}$.
+If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the state $s_s^\prime : s_s \rightarrow_s s_s^\prime$ is exact with respect to $s_0$ and $\pi_{n+1}$.
 \end{lemma}
@@
 Depending on the values of $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, there are two different rules that might apply to $s_\ell$.
-In either case, $\cfgnt{L}_\ell$ and $\cfgnt{R}_\ell$ are unchanged, and $\phi_\ell$ is strengthened, so we already know that
-$$ \zeta_T \subseteq \{s_\ell^\prime | \exists s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n}) (s_\ell \rightarrow_\ell s_\ell^\prime )\}$$
+%I'm not sure we actually use this fact anywhere
+ %In either case, $\cfgnt{L}_\ell$ and $\cfgnt{R}_\ell$ are unchanged, and $\phi_\ell$ is strengthened, so we already know that 
+%$$ \zeta_T \subseteq \{s_\ell^\prime | \exists s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n}) (s_\ell \rightarrow_\ell s_\ell^\prime )\}$$
 
-Case 1: Assume $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp = \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$.
-In this case, the equals - references true rule applies, and we know state $s_\ell^\prime : s_\ell \rightarrow_\ell s_\ell^\prime$ is in $\zeta_T$.
+Case 1: Assume $s_\ell : \cfgnt{L}_\ell \lp \cfgnt{r}_0\rp = \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, and let 
+$$\zeta_t = \zeta_T \setminus \{ s_f | \cfgnt{L}_f \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_f \lp \cfgnt{r}_1 \rp \}$$ In this case, the lazy ``equals - references true" rule applies, and we know state $s_\ell^\prime : s_\ell \rightarrow_\ell s_\ell^\prime$ is in $\zeta_t$.
 Since $(g\ h)$ is valid, we know that $\exists \lp \phi_0\ l \rp \in \cfgnt{L}_\ell\lp g \lp \cfgnt{r}_0\rp \rp$, $\exists \lp \phi_1\ l \rp \in \cfgnt{L}_\ell\lp g \lp \cfgnt{r}_1\rp \rp$, and that $\mathbb{S}\lp\phi_s\wedge\phi_0\wedge \phi_1\rp$ holds true.
@@
 Therefore, $\lp g\ h \rp: s_\ell^\prime \rightarrow s_s^\prime$ is a valid heap homomorphism, and by extension, $s_\ell^\prime \sqsubset s_s^\prime$.
-Since this relation holds for arbitrary $s_\ell^\prime \in \zeta_t$, we now know that $s_\ell^\prime \in \zeta_T \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$.
-% Furthermore, since  and since we may conclude that $s_s^\prime \equiv \zeta_T$.
+Since this relation holds for arbitrary $s_\ell^\prime \in \zeta_t$, we now know that $$s_\ell^\prime \in \zeta_t \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$$
+Now we prove the case for the other direction.
+Consider the state $s_s^\prime : s_s \rightarrow_s s_s^\prime$.
+Define $\theta_\alpha$, $\theta_0$ and $\theta_1$ as in the ``equals (references-true) rule''.
+Since $\cfgnt{L}_s$ and $\cfgnt{R}_s$ are unchanged from $s_s$, and $\phi_g$ is only strengthened,  we know that:
+$$\{s_\ell^\prime | s_\ell^\prime \sqsubset s_s^\prime \} \subseteq \{s_\ell^\prime | \exists s_\ell \lp s_\ell \sqsubset s_s \rp \wedge s_\ell \rightarrow_s s_\ell^\prime\} $$
+Suppose that there exists state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$ and $s_i^\prime \notin \zeta_t$.
+Because of the above conclusion, we know that $$s_i^\prime \in \{s_\ell^\prime | \exists s_\ell \lp s_\ell \sqsubset s_s\rp \wedge s_\ell \rightarrow_s s_\ell^\prime\}$$ Combining this with the assumption that $s_i^\prime \notin \zeta_t$, we must conclude that $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp \neq  \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$.
+Because of this, and because of theorem \ref{thm:mutex}, we know that either all constraints $$\phi_i : \exists \phi_\alpha (\phi_\alpha \in \theta_\alpha)\wedge \phi_i = \lp\phi_\alpha \wedge \phi_0 \wedge \phi_1\rp$$ are unsatisfiable, or that at least one constraint $$\phi_i : \exists \phi_\alpha (\phi_\alpha \in \lp \theta_0 \cup \theta_1 \rp)\wedge \lp \phi_i = \phi_\alpha \wedge \phi_0 \wedge \phi_1 \rp$$ is valid.
+Either way, $\mathbb{S}\lp\phi_i^\prime \wedge\phi_0\wedge \phi_1\rp$ is false, $\lp g\ h\rp$ is not a valid homomorphism, and $s_s^\prime$ does not represent $s_i^\prime$.
+We have a contradiction.
+Therefore: $$s_\ell^\prime \sqsubset s_s^\prime \Rightarrow s_\ell^\prime \in \zeta_t$$
+Combining this with our previous result, we conclude that $$s_\ell^\prime \in \zeta_t \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$
 
+Case 2: Assume $s_\ell : \cfgnt{L}_\ell \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, and let 
+$$\zeta_f = \zeta_T \setminus \{ s_t | \cfgnt{L}_t \lp \cfgnt{r}_0\rp = \cfgnt{L}_t \lp \cfgnt{r}_1 \rp \}$$ 
+This means that the lazy ``equals - references false" rule applies.
+The proof for the ``equals - references false" rule is highly similar to the proof for ``equals - references true", so we omit it for the sake of brevity.
+The result for this case is:
+$$s_\ell^\prime \in \zeta_f \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$
+
+Since $\zeta_T = \zeta_t \cup \zeta_f$, we can combine the results of the two cases to find that $$s_\ell^\prime \in \zeta_T \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$.
+By definition \ref{congruent}, $s_s^\prime \equiv \zeta_T$, and by definition \ref{exact}, $s_s^\prime$ is exact.
 \end{proof}

### 2014-07-08 tex/proofs.tex
Minor changes

@@
 \begin{definition}
-A \textbf{state transition function} $\rightarrow_{\Phi}$ is a mapping $\rightarrow_{\Phi} : s \mapsto s$ , which takes one machine state and transforms it into another machine state.
-The state transition function with superscript represents composition of the state transition function: $$ s_a \rightarrow_{\Phi} s_b \rightarrow_{\Phi} s_c \implies s_a \rightarrow_{\Phi}^2 s_c $$
+A \textbf{state transition function} $\rightarrow_{\Phi}$ is a mapping $\rightarrow_{\Phi} : s \mapsto s$, which takes one machine state and transforms it into another machine state. 
 \end{definition}
@@
 \begin{definition}
+A \textbf{state sequence} is as a sequence of states denoted as $\Pi_n = s_0,s_1,...,s_n$.
+A \textbf{feasible state sequence}, $\Pi_n^\phi = s_0,s_1,...,s_n$ is consistent with the transition: $\forall i\ (0 \leq i < n \Rightarrow s_i \rightarrow_{\Phi} s_{i+1})$.
+\end{definition}
+
+\begin{comment}
+\begin{definition}
 A \textbf{feasible state sequence} is defined as a sequence of states resulting from repeated application of the state transition relation to some initial state $s_0$: $$\Pi_n = s_0,s_1,...,s_n$$ where the relation $s_i \rightarrow_{\Phi} s_{i+1}$ holds for all $i \in \{ i | 0 \leq i < n \}$
 \end{definition}
+\end{comment}
 
@@
 \begin{definition}
-Given a state transition function $\rightarrow_{\Phi}$, an initial state $s_0$ and a control flow sequence $\pi_n$, the \textbf{feasible state set} $\zeta = \mathbb{FS}(\rightarrow_{\Phi},s_0,\pi_n)$ is defined as
- $$\zeta = \{ \forall s | \pi_n = \mathbb{CF}(\Pi_n) \wedge s = max_s(\Pi) \wedge s_0 \rightarrow_{\Phi}^{n-1} s\} $$
+Given a state transition function $\rightarrow_{\Phi}$, an initial state $s_0$ and a control flow sequence $\pi_n$, the \textbf{feasible state set}, $\mathbb{FS}(\rightarrow_{\Phi},s_0,\pi_n)$, is defined as
+ $$
+\begin{array}{l}
+\mathbb{FS}(\rightarrow_{\Phi},s_0,\pi_n) = \\
+\ \ \ \ \ \ \{s \mid \exists \Pi_n^\phi\ (\pi_n = \mathbb{CF}(\Pi_n^\Phi) \wedge s = \mathit{last}(\Pi_n))\} 
+\end{array}
+$$
+where $\mathit{last}(\Pi_n)$ returns the last state on the feasible sequence.
 \end{definition}
@@
 \begin{definition}
-A \textbf{heap homomorphism} $(g\ h)$ between two states $s_x$ and $s_y$ is defined as a pair of functions $g:\cfgnt{r} \mapsto \cfgnt{r}$ and $h:\cfgnt{l} \mapsto \cfgnt{l}$ such that for any reference $r \in s_x$, location $l \in s_x$, and field $f$, $$ (\phi_x\ l) \in \cfgnt{L}_x(r) \Rightarrow (\phi_y\ h(l))\in \cfgnt{L}_y(g(r))$$ and $$ r = \cfgnt{R}_x(l,f) \Rightarrow g(r) = \cfgnt{R}_y(h(l),f)$$ If a such a pair of functions exists from one state $s_x$ to another state $s_y$ we say that state $s_x$ is \textbf{heap homomorphic} to state $s_y$, indicated by the notation $(g\ f):\ s_x \rightarrow s_y$.
+A \textbf{heap homomorphism} $(g\ h)$ between two states $s_x$ and $s_y$ is defined as a pair of functions $g:\cfgnt{r} \mapsto \cfgnt{r}$ and $h:\cfgnt{l} \mapsto \cfgnt{l}$ such that for any reference $r \in \mathit{refs}(s_x)$, location $l \in \mathit{locs}(s_x)$, and field $f$, $$ (\phi_x\ l) \in \cfgnt{L}_x(r) \Rightarrow (\phi_y\ h(l))\in \cfgnt{L}_y(g(r))$$ and $$ r = \cfgnt{R}_x(l,f) \Rightarrow g(r) = \cfgnt{R}_y(h(l),f)$$ If a such a pair of functions exists from one state $s_x$ to another state $s_y$ we say that state $s_x$ is \textbf{heap homomorphic} to state $s_y$, indicated by the notation $s_x \rightharpoonup_{(g\ h)} s_y$.
 
 Suppose we take the set of constraints from the image of $s_x$ in $s_y$ under $(g\ h)$ :
-$$\chi = \{ \phi\ | \exists (r \in \cfgnt{R}_x,\  l \in \cfgnt{L}_x) ( (\phi\ h(l)) \in \cfgnt{L}_y (g(r))  \}$$ and we conjoin those constraints with the global invariant from $s_y$ :
-$$\phi_G = \phi_y \bigwedge_{\phi_i \in \chi} \phi_i $$
- If the expression $\phi_G$ is satisfiable, we say that the heap homomorphism $(g\ h):\ s_x \rightarrow s_y $ is \textbf{valid}.
+$$\chi = \{ \phi\ | \exists (r \in \cfgnt{R}_x,\  l \in \cfgnt{L}_x) ( (\phi\ h(l)) \in \cfgnt{L}_y (g(r))  \}$$ and we conjoin those constraints with the global invariant $\phi_y$ from $s_y$ :
+$$\phi_G = \phi_y \wedge (\bigwedge_{\phi_i \in \chi} \phi_i) $$
+ If the expression $\phi_G$ is satisfiable, we say that the heap homomorphism $s_x \rightharpoonup_{(g\ h)} s_y$ is \textbf{valid}.
 \end{definition}
@@
 \label{representation}
-The \textbf{representation relation} is defined as follows: given two states $s_\ell$ and $s_s$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a valid heap homomorphism $(g\ h):\ s_\ell \rightarrow s_s $.
+The \textbf{representation relation} is defined as follows: given two states $s_\ell$ and $s_s$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a valid heap homomorphism $\ s_\ell \rightharpoonup_{(g\ h)} s_s $.
 The expression $s_\ell \sqsubset s_s $ can be read as "state $s_\ell$ is represented by state $s_s$ .
@@
 \label{congruent}
-A state $s_s$ is \textbf{congruent} to a set of states $\mathcal{S}$ if and only if $s$ represents every state in $\mathcal{S}$ and represents no other state: 
-$$ s_s \equiv \mathcal{S} : s_i \in \mathcal{S} \Leftrightarrow s_i \sqsubset s_s $$
+A state $s$ is \textbf{congruent} to a set of states $\mathcal{S}$ if and only if $s$ represents every state in $\mathcal{S}$ and represents no other state: 
+$$s \cong \mathcal{S} : s_i \in \mathcal{S} \Leftrightarrow s_i \sqsubset s $$
 \end{definition}
+
+Need to define a \emph{lazy state} and a \emph{summary state} (or whatever name we are using).
 
@@
 \label{exact}
-A symbolic state $s_s$ is \textbf{exact} with respect to an initial state $s_0$ and control flow sequence $\pi$ if and only if it is congruent the set of feasible lazy states on the same control flow path:
-$$ s_s \equiv \mathbb{FS}(\rightarrow_{\ell},s_0,\pi)$$
+A state $s$ is \textbf{exact} with respect to a transition relation, $\rightarrow_\phi$, an initial state, $s_0$, and specific control flow path, $\pi_n$, if and only if it is congruent to the set of feasible state set:
+$$ s \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi)$$
 \end{definition}

### 2014-07-08 tex/proofs.tex
Clarified the verbage for the Field Access Lemma

@@
 
+%we need to define how r' is arrived at for this one to work...
 \begin{lemma}
-If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the state $s_s^\prime : s_s \rightarrow_s s_f$ is exact with respect to $s_0$ and $\pi_{n+1}$.
+If there are symbolic states $s_s$ and $s_s^\prime$, and control sequences $\pi_n$ and $\pi_{n+1}$ such that 
+$$s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$$ 
+$$s_s \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp$$ 
+$$\pi_{n+1} =\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp$$ then 
+$$s_s^\prime \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_{n+1} \rp$$
 \end{lemma}

### 2014-07-09 tex/proofs.tex
Clarified definitions for homomorphism and representation, and the field access lemma statement

--- 2014-07-08 tex/proofs.tex
@@
 \begin{definition}
-A \textbf{heap homomorphism} $(g\ h)$ between two states $s_x$ and $s_y$ is defined as a pair of functions $g:\cfgnt{r} \mapsto \cfgnt{r}$ and $h:\cfgnt{l} \mapsto \cfgnt{l}$ such that for any reference $r \in \mathit{refs}(s_x)$, location $l \in \mathit{locs}(s_x)$, and field $f$, $$ (\phi_x\ l) \in \cfgnt{L}_x(r) \Rightarrow (\phi_y\ h(l))\in \cfgnt{L}_y(g(r))$$ and $$ r = \cfgnt{R}_x(l,f) \Rightarrow g(r) = \cfgnt{R}_y(h(l),f)$$ If a such a pair of functions exists from one state $s_x$ to another state $s_y$ we say that state $s_x$ is \textbf{heap homomorphic} to state $s_y$, indicated by the notation $s_x \rightharpoonup_{(g\ h)} s_y$.
+A \textbf{homomorphism} $s_x \rightharpoonup_{(g\ h)} s_y$, from state $s_x = ( \cfgnt{L}_x\ \cfgnt{R}_x\ \phi_x\ \eta_x\ \cfgnt{e}_x\ \cfgnt{k}_x )$ to state $s_y = ( \cfgnt{L}_y\ \cfgnt{R}_y\ \phi_y\ \eta_y\ \cfgnt{e}_y\ \cfgnt{k}_y )$, is defined as follows:
+%a pair of functions $g:\mathcal{R} \mapsto \mathcal{R}$ and $h: \mathcal{L} \mapsto \mathcal{L}$ such that the following conditions are met:
 
-Suppose we take the set of constraints from the image of $s_x$ in $s_y$ under $(g\ h)$ :
-$$\chi = \{ \phi\ | \exists (r \in \cfgnt{R}_x,\  l \in \cfgnt{L}_x) ( (\phi\ h(l)) \in \cfgnt{L}_y (g(r))  \}$$ and we conjoin those constraints with the global invariant $\phi_y$ from $s_y$ :
-$$\phi_G = \phi_y \wedge (\bigwedge_{\phi_i \in \chi} \phi_i) $$
- If the expression $\phi_G$ is satisfiable, we say that the heap homomorphism $s_x \rightharpoonup_{(g\ h)} s_y$ is \textbf{valid}.
-\end{definition}
+\begin{array}{l}
+ s_x \rightharpoonup_{(g\ h)} s_y \Leftrightarrow \\
+\ \ \ \ \ \ \ \ \exists g:\mathcal{R} \mapsto \mathcal{R}\ ( \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{r} \in \mathcal{R}\ (\forall \cfgnt{l} \in \mathcal{L}\ ( \\ 
+\ \ \ \ \ \ \ \ \ \ \ \ (\phi_x\ \cfgnt{l}) \in \cfgnt{L}_x(\cfgnt{r}) \Rightarrow (\phi_y\ h(\cfgnt{l}))\in \cfgnt{L}_y(g(\cfgnt{r}))\ \wedge \\
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \cfgnt{r} = \cfgnt{R}_x(\cfgnt{l},f) \Rightarrow g(\cfgnt{r}) = \cfgnt{R}_y(h(\cfgnt{l}),f) )) )) 
+\end{array}
+
 \begin{definition}
 \label{representation}
-The \textbf{representation relation} is defined as follows: given two states $s_\ell$ and $s_s$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a valid heap homomorphism $\ s_\ell \rightharpoonup_{(g\ h)} s_s $.
-The expression $s_\ell \sqsubset s_s $ can be read as "state $s_\ell$ is represented by state $s_s$ .
+The \textbf{representation relation} is defined as follows: given lazy state $s_\ell$ and summary state $s_s$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a homomorphism $\ s_\ell \rightharpoonup_{(g\ h)} s_s $ such that if $$\chi = \{ \phi\ | \exists (r \in \cfgnt{R}_x,\  l \in \cfgnt{L}_x) ( (\phi\ h(l)) \in \cfgnt{L}_y (g(r))  \}$$ then
+\begin{equation}
+\label{eqn:valid}
+ \mathbb{S}( \phi_y \wedge (\bigwedge_{\phi_i \in \chi} \phi_i)) 
+\end{equation}
 \end{definition}
@@
 \label{congruent}
-A state $s$ is \textbf{congruent} to a set of states $\mathcal{S}$ if and only if $s$ represents every state in $\mathcal{S}$ and represents no other state: 
-$$s \cong \mathcal{S} : s_i \in \mathcal{S} \Leftrightarrow s_i \sqsubset s $$
+A summary state $s$ is \textbf{congruent} to a set of lazy states $P$ if and only if $s$ represents every state in $P$ and represents no other state: 
+$$s \cong P \Leftrightarrow \forall s_i \in \mathcal{S}\ (s_i \in P \Leftrightarrow s_i \sqsubset s) $$
 \end{definition}
-
-Need to define a \emph{lazy state} and a \emph{summary state} (or whatever name we are using).
 
@@
 
+%we need to define how r' is arrived at for this one to work...
 \begin{lemma}
-If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the state $s_s^\prime : s_s \rightarrow_s s_f$ is exact with respect to $s_0$ and $\pi_{n+1}$.
+If there are symbolic states $s_s$ and $s_s^\prime$, control sequences $\pi_n$ and $\pi_{n+1}$, initial state $s_0$, and reference $\cfgnt{r}^\prime$ such that the following conditions hold:
+\begin{align}
+s_s &= \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp \\
+s_s &\cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp \\
+\cfgnt{r}^\prime &= \mathrm{fresh}_r\lp \rp \\
+\pi_{n+1} &=\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp \\
+s_s &\rightarrow_s s_s^\prime
+\end{align}
+%$$s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$$ 
+%$$s_s \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp$$ 
+%$$\pi_{n+1} =\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp$$
+
+then 
+$$s_s^\prime \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_{n+1} \rp$$
 \end{lemma}
@@
 Case 1: suppose all of the pertinent fields in $s_s$ are initialized.
-Take an arbitrary lazy state $s_\ell \sqsubset s_s$.
-Since $s_s$ is exact,  $s_\ell = \lp \cfgnt{L}_{\ell}\ \cfgnt{R}_{\ell}\ \phi_L\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k} \rp \rp$, and that $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$.
-If we apply the state transition functions to achieve states $s_\ell^\prime : s_\ell \rightarrow_\ell s_\ell^\prime$ and $s_s^\prime : s_s \rightarrow_s s_s^\prime$, we find that:
+Take an arbitrary lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$.
+Since $s_s$ is exact,  $s_\ell = \lp \cfgnt{L}_{\ell}\ \cfgnt{R}_{\ell}\ \phi_\ell\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k} \rp \rp$, and $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$.
+If we apply the state transition functions to achieve states $s_\ell^\prime$ and $s_s^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$ and  $s_s \rightarrow_s s_s^\prime$, we find that:
 $$s_\ell^\prime = \lp \cfgnt{L}_{\ell} [\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}_{\ell}\ \phi_L\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
@@
 Since $\eta$, $e$, and $k$ are identical between $s_s^\prime$ and $s_\ell^\prime $, the first condition is met by default.
-Now we construct functions $g^\prime : g^\prime = g[ r^\prime \mapsto r^\prime]$ and $h^\prime : h^\prime = h$.
-Observe that since $s_\ell \rightarrow s_s$, and since $\cfgnt{R}_\ell$ and $\cfgnt{R}_s$ are unchanged from states $s_\ell$ to $s_\ell^\prime$ and $s_s$ to $s_s^\prime$ respectively, we are guaranteed that $ r = \cfgnt{R}_\ell(l,f) \Rightarrow g^\prime(r) = \cfgnt{R}_s(h^\prime(l),f)$.
+Now we construct functions $g^\prime$ and $h^\prime$ such that $g^\prime = g[ r^\prime \mapsto r^\prime]$ and $h^\prime = h$.
+Observe that since $s_\ell \rightharpoonup_{(g\ h)} s_s$, and since $\cfgnt{R}_\ell$ and $\cfgnt{R}_s$ are unchanged from states $s_\ell$ to $s_\ell^\prime$ and $s_s$ to $s_s^\prime$ respectively, we are guaranteed that $ r = \cfgnt{R}_\ell(l,f) \Rightarrow g^\prime(r) = \cfgnt{R}_s(h^\prime(l),f)$.
 Since $(\phi_\ell^\prime\ l^\prime) =  \cfgnt{L}_\ell(\cfgnt{R}_\ell(l,f))$, and since $(g\ h)$ is valid, we know that:
@@
 $$ (\phi_\ell\ l) \in \cfgnt{L}_\ell^\prime(r^\prime) \Rightarrow (\phi_s \wedge \phi_s^\prime\ h^\prime(l))\in \cfgnt{L}_s^\prime(g^\prime(r^\prime))$$
-Since $r^\prime$ the only new addition to $L_\ell^\prime$ and $L_s^\prime$, we now know that the assertion above holds for all $l \in s_\ell^\prime$.
-Thus, we have shown that $(g^\prime\ h^\prime)$ is a heap homomorphism from $s_\ell^\prime$ to $s_s^\prime$.
-Furthermore, since $\mathbb{S}(\phi_s\wedge\phi_s^\prime\wedge \phi_g)$ holds true, we know that $(g^\prime\ h^\prime):\ s_\ell^\prime \rightarrow s_s^\prime$ is valid.
+Since $r^\prime$ the only new addition to $L_\ell^\prime$ and $L_s^\prime$, we now know that the assertion above holds for all $l \in \mathcal{L}$.
+Thus, we have shown that $s_\ell^\prime \rightharpoonup_{(g\ h)} s_s^\prime$.
+Furthermore, since $\mathbb{S}(\phi_s\wedge\phi_s^\prime\wedge \phi_g)$ evaluates to $\cfgt{true}$, we know that equation \ref{eqn:valid} also evaluates to $\cfgt{true}$.
 Since there is a valid heap homomorphism, and since $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, we  by definition \ref{representation} know $s_\ell^\prime \sqsubset s_s^\prime$.
@@
 Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$, but $s_i^\prime \notin \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
-Since $s_i^\prime \sqsubset s_s^\prime$, there must exist a valid homomorphism $(g_i^\prime h_i^\prime): s_i^\prime \rightarrow s_s^\prime$.
+Since $s_i^\prime \sqsubset s_s^\prime$, there must exist a valid homomorphism $s_i^\prime \rightharpoonup_{(g^\prime\ h^\prime)} s_s^\prime$.
 If $(g_i^\prime\ h_i^\prime)$ is valid, then there must also exist a valid homomorphism $(g_i\ h_i) : s_i \rightarrow s_s$, and by extension, state $s_i \sqsubset s_s$.

### 2014-07-10 tex/proofs.tex
Added definitions for access paths.

@@
 A \textbf{state transition function} $\rightarrow_{\Phi}$ is a mapping $\rightarrow_{\Phi} : s \mapsto s$, which takes one machine state and transforms it into another machine state.
+Two important state transition functions are the \textbf{lazy state transition function} $\rightarrow_\ell$ and the \textbf{summary state transition function} $\rightarrow_s$.
 \end{definition}
@@
 \end{comment}
+
+\begin{definition}
+A \textbf{lazy state} $s_\ell$ is any state such that there exists an integer $i$, initial state $s_0$, and feasible state sequence $\Pi_n^\ell$ satisfying the following requirements:
+\begin{align}
+\Pi_n^\ell &= s_0,s_1,...,s_n\\
+s_\ell &= s_i
+\end{align}
+\end{definition}
+
+\begin{definition}
+A \textbf{summary state} $s_s$ is any state such that there exists an integer $i$, initial state $s_0$, and feasible state sequence $\Pi_n^s$ satisfying the following requirements:
+\begin{align}
+\Pi_n^s &= s_0,s_1,...,s_n\\
+s_\ell &= s_i
+\end{align}
+\end{definition}
 
@@
 \begin{definition}
+A \textbf{field access descriptor} $\gamma_i$ is a tuple 
+$$ \gamma_i = (\cfgnt{r}_i\ \phi_i\ \cfgnt{l}_i\ \cfgnt{f}_i)$$
+\end{definition}
+
+\begin{definition}
+An \textbf{access path} $\Gamma_n$ is a sequence of field access descriptors
+$ \Gamma_n = \gamma_0,\gamma_1,...,\gamma_n $.
+\end{definition}
+
+\begin{definition}
+For a given access path $\Gamma_n$ the \textbf{access path constraint} $\mathbb{PC}(\Gamma_n)$ is defined as
+$$\mathbb{PC}(\Gamma_n) =  \bigwedge \{\phi \mid \exists \gamma \in \Gamma_n \ (\gamma = (\cfgnt{r}\ \phi\ \cfgnt{e}\ \cfgnt{f}))\}$$  
+\end{definition}
+
+\begin{definition}
+For a given state $s= ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, a \textbf{valid access path} $\Gamma_n^s = \gamma_0,\gamma_1,...,\gamma_n$ satisfies the properties
+\begin{align*}
+\cfgnt{r}_0 &\in \mathit{refs}(\eta_s) \\
+\mathbb{S}(&\phi_s \wedge \mathbb{PC}(\Gamma_n^s)) \\
+\forall i & \in \mathbb{N}\ ( 0 \leq i < n \Leftrightarrow \gamma_i \in \Gamma_n^s\  \wedge\\
+&\ \ \ \  \gamma_{i+1} \in \Gamma_n^s\  \wedge\\
+&\ \ \ \  (\phi_i\ \cfgnt{l}_i)\in \cfgnt{L}_s(\cfgnt{r}_i)\ \wedge \\
+&\ \ \ \  \cfgnt{r}_{i+1} = \cfgnt{R}_s(\cfgnt{l}_i,\cfgnt{f}_i)\ \wedge\\
+&\ \ \ \ (\phi_{i+1}\ \cfgnt{l}_{i+1}) = \cfgnt{L}_s(\cfgnt{r}_{i+1}) )
+\end{align*}
+where $\gamma_i = (\cfgnt{r}_i\ \phi_i\ \cfgnt{l}_i\ \cfgnt{f}_i)$
+\end{definition}
+
+\begin{definition}
 A \textbf{homomorphism} $s_x \rightharpoonup_{(g\ h)} s_y$, from state $s_x = ( \cfgnt{L}_x\ \cfgnt{R}_x\ \phi_x\ \eta_x\ \cfgnt{e}_x\ \cfgnt{k}_x )$ to state $s_y = ( \cfgnt{L}_y\ \cfgnt{R}_y\ \phi_y\ \eta_y\ \cfgnt{e}_y\ \cfgnt{k}_y )$, is defined as follows:
-%a pair of functions $g:\mathcal{R} \mapsto \mathcal{R}$ and $h: \mathcal{L} \mapsto \mathcal{L}$ such that the following conditions are met:
-
+$$
 \begin{array}{l}
@@
 \end{array}
+$$
+\end{definition}
 
@@
 \label{representation}
-The \textbf{representation relation} is defined as follows: given lazy state $s_\ell$ and summary state $s_s$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a homomorphism $\ s_\ell \rightharpoonup_{(g\ h)} s_s $ such that if $$\chi = \{ \phi\ | \exists (r \in \cfgnt{R}_x,\  l \in \cfgnt{L}_x) ( (\phi\ h(l)) \in \cfgnt{L}_y (g(r))  \}$$ then
+The \textbf{representation relation} is defined as follows: given lazy state $s_\ell$ and summary state $s_s$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a homomorphism $\ s_\ell \rightharpoonup_{(g\ h)} s_s $ such that if $$\theta = \{ \phi\ | \exists (r \in \cfgnt{R}_x,\  l \in \cfgnt{L}_x) ( (\phi\ h(l)) \in \cfgnt{L}_y (g(r))  \}$$ then
 \begin{equation}
 \label{eqn:valid}
- \mathbb{S}( \phi_y \wedge (\bigwedge_{\phi_i \in \chi} \phi_i)) 
+ \mathbb{S}( \phi_y \wedge (\bigwedge_{\phi_i \in \theta} \phi_i)) 
 \end{equation}
@@
 \label{congruent}
-A summary state $s$ is \textbf{congruent} to a set of lazy states $P$ if and only if $s$ represents every state in $P$ and represents no other state: 
-$$s \cong P \Leftrightarrow \forall s_i \in \mathcal{S}\ (s_i \in P \Leftrightarrow s_i \sqsubset s) $$
+A summary state $s_s$ is \textbf{congruent} to a set of lazy states $P$ if and only if $s_s$ represents every state in $P$ and represents no other state: 
+$$s \cong P \Leftrightarrow \forall s_i \in \mathcal{S}\ (s_i \in P \Leftrightarrow s_i \sqsubset s_s) $$
 \end{definition}
@@
 \end{theorem}
+\begin{proof}
+\end{proof}
+
+\begin{lemma}
+For any symbolic state $s_s$, constraint $\phi$, and stack reference $\cfgnt{r}$ such that $(\phi\ \ell) \in \cfgnt{L}_s (r)$, $\phi$ is the conjunction of constraints for the access path to $l$.
+\end{lemma}
+\begin{proof}
+\end{proof}
+
+\begin{lemma}
+If there is some access path $\sigma$ in state $s_s$ such that $\mathbb{s}(\phi_\sigma \wedge \phi_s)$, then $\sigma \sqsubset$  
+\end{lemma}
 \begin{proof}

### 2014-07-10 tex/proofs.tex
fixed some minor typos

@@
 A state $s$ is \textbf{exact} with respect to a transition relation, $\rightarrow_\phi$, an initial state, $s_0$, and specific control flow path, $\pi_n$, if and only if it is congruent to the set of feasible state set:
-$$ s \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi)$$
+$$ s \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$$
 \end{definition}
@@
 \begin{lemma}
-If there is some access path $\sigma$ in state $s_s$ such that $\mathbb{s}(\phi_\sigma \wedge \phi_s)$, then $\sigma \sqsubset$  
+If there is some access path $\Gamma$ in state $s_s$ such that $\mathbb{S}(\phi_\sigma \wedge \phi_s)$, then $\sigma \sqsubset$  
 \end{lemma}

### 2014-07-11 tex/proofs.tex
Added more definitions

@@
 \subsection{Definitions}
+
+\begin{definition}
+The set of \textbf{states} $\mathcal{S}$ is defined as
+\end{definition}
+
+\begin{definition}
+The set of \textbf{initial states} $\mathcal{S}_0$ is defined as
+\end{definition}
 
@@
 A \textbf{state sequence} is as a sequence of states denoted as $\Pi_n = s_0,s_1,...,s_n$.
-A \textbf{feasible state sequence}, $\Pi_n^\phi = s_0,s_1,...,s_n$ is consistent with the transition: $\forall i\ (0 \leq i < n \Rightarrow s_i \rightarrow_{\Phi} s_{i+1})$.
+A \textbf{feasible state sequence}, $\Pi_n^\phi = s_0,s_1,...,s_n$ is consistent with the transition: $\forall i\ (0 \leq i < n \Rightarrow s_i \rightarrow_{\Phi} s_{i+1})$, where $s_0\in \mathcal{S}_0$.
 \end{definition}
@@
 \begin{definition}
-A \textbf{feasible state sequence} is defined as a sequence of states resulting from repeated application of the state transition relation to some initial state $s_0$: $$\Pi_n = s_0,s_1,...,s_n$$ where the relation $s_i \rightarrow_{\Phi} s_{i+1}$ holds for all $i \in \{ i | 0 \leq i < n \}$
+A \textbf{feasible state sequence} is defined as a sequence of states resulting from repeated application of the state transition relation to some initial state $s_0\in \mathcal{S}_0$: $$\Pi_n = s_0,s_1,...,s_n$$ where the relation $s_i \rightarrow_{\Phi} s_{i+1}$ holds for all $i \in \{ i | 0 \leq i < n \}$
 \end{definition}
@@
 \begin{definition}
-A \textbf{lazy state} $s_\ell$ is any state such that there exists an integer $i$, initial state $s_0$, and feasible state sequence $\Pi_n^\ell$ satisfying the following requirements:
+The set of \textbf{lazy states} $\mathcal{S}_\ell$ is defined as
 \begin{align}
-\Pi_n^\ell &= s_0,s_1,...,s_n\\
-s_\ell &= s_i
+\mathcal{S}_\ell = \{s_\ell \mid \exists \Pi_n^\ell\ (\Pi_n^\ell = s_0, \ldots, s_\ell)\}
 \end{align}
@@
 \begin{definition}
-A \textbf{summary state} $s_s$ is any state such that there exists an integer $i$, initial state $s_0$, and feasible state sequence $\Pi_n^s$ satisfying the following requirements:
+The set of \textbf{summary states} $\mathcal{S}_s$ is defined as
 \begin{align}
-\Pi_n^s &= s_0,s_1,...,s_n\\
-s_\ell &= s_i
+\mathcal{S}_s = \{s_s \mid \exists \Pi_n^s\ (\Pi_n^s = s_0, \ldots, s_s)\}
 \end{align}
@@
 \ \ \ \ \ \ \ \ \exists g:\mathcal{R} \mapsto \mathcal{R}\ ( \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{r} \in \mathcal{R}\ (\forall \cfgnt{l} \in \mathcal{L}\ ( \\ 
-\ \ \ \ \ \ \ \ \ \ \ \ (\phi_x\ \cfgnt{l}) \in \cfgnt{L}_x(\cfgnt{r}) \Rightarrow (\phi_y\ h(\cfgnt{l}))\in \cfgnt{L}_y(g(\cfgnt{r}))\ \wedge \\
+\ \ \ \ \ \ \ \ \ \ \ \ (\phi_a\ \cfgnt{l}) \in \cfgnt{L}_x(\cfgnt{r}) \Rightarrow (\phi_b\ h(\cfgnt{l}))\in \cfgnt{L}_y(g(\cfgnt{r}))\ \wedge \\
 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \cfgnt{r} = \cfgnt{R}_x(\cfgnt{l},f) \Rightarrow g(\cfgnt{r}) = \cfgnt{R}_y(h(\cfgnt{l}),f) )) )) 
@@
 \label{representation}
-The \textbf{representation relation} is defined as follows: given lazy state $s_\ell$ and summary state $s_s$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a homomorphism $\ s_\ell \rightharpoonup_{(g\ h)} s_s $ such that if $$\theta = \{ \phi\ | \exists (r \in \cfgnt{R}_x,\  l \in \cfgnt{L}_x) ( (\phi\ h(l)) \in \cfgnt{L}_y (g(r))  \}$$ then
+The \textbf{representation relation} is defined as follows: given lazy state $s_\ell = ( \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta_\ell\ \cfgnt{e}_\ell\ \cfgnt{k}_\ell )$ and summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a homomorphism $\ s_\ell \rightharpoonup_{(g\ h)} s_s $ such that if
+$$\theta = \{ \phi_b\ | \exists r \in \cfgnt{L}_\ell^\leftarrow\ (\exists (\phi_a\ l) \in \cfgnt{L}_\ell^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_y (g(r))))  \}$$ then 
 \begin{equation}
 \label{eqn:valid}
- \mathbb{S}( \phi_y \wedge (\bigwedge_{\phi_i \in \theta} \phi_i)) 
+ \mathbb{S}( \phi_s \wedge (\bigwedge_{\phi_i \in \theta} \phi_i)) 
 \end{equation}
@@
 A summary state $s_s$ is \textbf{congruent} to a set of lazy states $P$ if and only if $s_s$ represents every state in $P$ and represents no other state: 
-$$s \cong P \Leftrightarrow \forall s_i \in \mathcal{S}\ (s_i \in P \Leftrightarrow s_i \sqsubset s_s) $$
+$$s_s \cong P \Leftrightarrow \forall s_i \in \mathcal{S}\ (s_i \in P \Leftrightarrow s_i \sqsubset s_s) $$
+\end{definition}
+
+\begin{definition}
+\label{sound}
+A state $s$ is \textbf{sound} with respect to a transition relation, $\rightarrow_\phi$, initial state, $s_0$, and control flow path, $\pi_n$, if and only if 
+$$ \forall s_\ell \in \mathcal{S}_\ell\ (s_\ell \sqsubset s_s \Rightarrow s_\ell \in \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n) ) $$
+\end{definition}
+
+\begin{definition}
+\label{complete}
+A state $s$ is \textbf{complete} with respect to a transition relation, $\rightarrow_\phi$, initial state, $s_0$, and control flow path, $\pi_n$, if and only if 
+$$ \forall s_\ell \in \mathcal{S}_\ell\ ( s_\ell \in \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)\Rightarrow s_\ell \sqsubset s_s ) $$
 \end{definition}
@@
 \label{exact}
-A state $s$ is \textbf{exact} with respect to a transition relation, $\rightarrow_\phi$, an initial state, $s_0$, and specific control flow path, $\pi_n$, if and only if it is congruent to the set of feasible state set:
+A state $s$ is \textbf{exact} with respect to a transition relation, $\rightarrow_\phi$, initial state, $s_0$, and control flow path, $\pi_n$, if and only if it is both sound and complete:
 $$ s \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$$

### 2014-07-17 tex/definitions.tex
Cleaned up field access proof. Added definition for Heap Constraint.

--- 2014-07-11 tex/proofs.tex
@@
-\section{Proofs}
-
 \subsection{Definitions}
@@
 \begin{definition}
+\label{def:hc}
+Given homomorphism $s_x \rightharpoonup_{(g\ h)} s_y$, the \textbf{homomorphism constraint} $\mathbb{HC}(s_x \rightharpoonup_{(g\ h)} s_y)$ is defined as:
+\begin{align*}
+\mathbb{HC}(s_x \rightharpoonup_{(g\ h)} s_y) = \\
+ \bigwedge \{ \phi_b\ | \exists r \in \cfgnt{L}_x^\leftarrow\ (\exists (\phi_a\ l) \in \cfgnt{L}_x^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_y (g(r)))) 
+\end{align*}
+\end{definition}
+
+\begin{definition}
 \label{representation}
-The \textbf{representation relation} is defined as follows: given lazy state $s_\ell = ( \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta_\ell\ \cfgnt{e}_\ell\ \cfgnt{k}_\ell )$ and summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a homomorphism $\ s_\ell \rightharpoonup_{(g\ h)} s_s $ such that if
-$$\theta = \{ \phi_b\ | \exists r \in \cfgnt{L}_\ell^\leftarrow\ (\exists (\phi_a\ l) \in \cfgnt{L}_\ell^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_y (g(r))))  \}$$ then 
+The \textbf{representation relation} is defined as follows: given lazy state $s_\ell = ( \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta_\ell\ \cfgnt{e}_\ell\ \cfgnt{k}_\ell )$ and summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a homomorphism $\ s_\ell \rightharpoonup_{(g\ h)} s_s $ such that
 \begin{equation}
 \label{eqn:valid}
- \mathbb{S}( \phi_s \wedge (\bigwedge_{\phi_i \in \theta} \phi_i)) 
+ \mathbb{S}( \phi_s \wedge \mathbb{HC}(s_\ell \rightharpoonup_{(g\ h)} s_s) ) 
 \end{equation}
@@
 \begin{definition}
-\label{congruent}
-A summary state $s_s$ is \textbf{congruent} to a set of lazy states $P$ if and only if $s_s$ represents every state in $P$ and represents no other state: 
+\label{equivalent}
+A summary state $s_s$ is \textbf{equivalent} to a set of lazy states $P$ if and only if $s_s$ represents every state in $P$ and represents no other state: 
 $$s_s \cong P \Leftrightarrow \forall s_i \in \mathcal{S}\ (s_i \in P \Leftrightarrow s_i \sqsubset s_s) $$
@@
 \end{definition}
-
-\subsection{Theorems}
-
-\begin{theorem}
-\label{thm:mutex}
-In any symbolic state $s_s$, the constraints in the value set of any reference are mutually exclusive.
-\end{theorem}
-\begin{proof}
-\end{proof}
-
-\begin{lemma}
-For any symbolic state $s_s$, constraint $\phi$, and stack reference $\cfgnt{r}$ such that $(\phi\ \ell) \in \cfgnt{L}_s (r)$, $\phi$ is the conjunction of constraints for the access path to $l$.
-\end{lemma}
-\begin{proof}
-\end{proof}
-
-\begin{lemma}
-If there is some access path $\Gamma$ in state $s_s$ such that $\mathbb{S}(\phi_\sigma \wedge \phi_s)$, then $\sigma \sqsubset$  
-\end{lemma}
-\begin{proof}
-\end{proof}
-
-\begin{lemma}
-\label{lem:init}
-If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the intermediate state state $s_f : s_s \rightarrow_S s_f$ is congruent to $\{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$.
-\end{lemma}
-
-\begin{proof}%going through this one quickly, could be more formal...
-Given a lazy state $s_\ell \sqsubset s_s$, there are four distinct possibilities for $s_\ell^\prime$: either the field is already initialized, or the field is initialized to a new reference, the null reference, or an alias.
-
-Case 1: Suppose the field is initialized. In this case, the rule does nothing and the theorem is trivially true.
-
-%for the next case, we need to show that the constraints in the symbolic heap don't allow any infeasible heaps.
-The key to this will be in showing that the constraints are mutually exclusive and collectively exhaustive.
-Mutually exclusive constraints are required because lazy heaps only point to one place at at time.
-Collectively exhaustive constraints are required to eliminate any other possible heaps.
-We could start by explicitly enumerating the members of the product feasible set, and working from there to show that the symbolic heap is congruent to that set.
-Or, we might do this on a case-by-case basis to show that for an arbitrary lazy state, any of it's three possible target states is in the feasible set.
-
-Case 2: The "new" rule gets executed.
-
-Case 3: The "null" rule gets executed.
-
-Case 4: The "alias" rule gets executed.
-\end{proof}
-
-%we need to define how r' is arrived at for this one to work...
-\begin{lemma}
-If there are symbolic states $s_s$ and $s_s^\prime$, control sequences $\pi_n$ and $\pi_{n+1}$, initial state $s_0$, and reference $\cfgnt{r}^\prime$ such that the following conditions hold:
-\begin{align}
-s_s &= \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp \\
-s_s &\cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp \\
-\cfgnt{r}^\prime &= \mathrm{fresh}_r\lp \rp \\
-\pi_{n+1} &=\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp \\
-s_s &\rightarrow_s s_s^\prime
-\end{align}
-%$$s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$$ 
-%$$s_s \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp$$ 
-%$$\pi_{n+1} =\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp$$
-
-then 
-$$s_s^\prime \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_{n+1} \rp$$
-\end{lemma}
-
-\begin{proof}
-We will consider two cases for this proof. In the first case, we assume that all of the fields involved in the read are initialized. In the second case we consider the case of uninitialized fields.
-
-Case 1: suppose all of the pertinent fields in $s_s$ are initialized.
-Take an arbitrary lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$.
-Since $s_s$ is exact,  $s_\ell = \lp \cfgnt{L}_{\ell}\ \cfgnt{R}_{\ell}\ \phi_\ell\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k} \rp \rp$, and $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$.
-If we apply the state transition functions to achieve states $s_\ell^\prime$ and $s_s^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$ and  $s_s \rightarrow_s s_s^\prime$, we find that:
-$$s_\ell^\prime = \lp \cfgnt{L}_{\ell} [\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}_{\ell}\ \phi_L\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
- and 
- $$ s_s^\prime = \lp \cfgnt{L}_{s}[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}_{\mathcal{S}},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
-
-We now show that $s_\ell^\prime \sqsubset s_s^\prime$.
-Since $\eta$, $e$, and $k$ are identical between $s_s^\prime$ and $s_\ell^\prime $, the first condition is met by default.
-Now we construct functions $g^\prime$ and $h^\prime$ such that $g^\prime = g[ r^\prime \mapsto r^\prime]$ and $h^\prime = h$.
-Observe that since $s_\ell \rightharpoonup_{(g\ h)} s_s$, and since $\cfgnt{R}_\ell$ and $\cfgnt{R}_s$ are unchanged from states $s_\ell$ to $s_\ell^\prime$ and $s_s$ to $s_s^\prime$ respectively, we are guaranteed that $ r = \cfgnt{R}_\ell(l,f) \Rightarrow g^\prime(r) = \cfgnt{R}_s(h^\prime(l),f)$.
-Since $(\phi_\ell^\prime\ l^\prime) =  \cfgnt{L}_\ell(\cfgnt{R}_\ell(l,f))$, and since $(g\ h)$ is valid, we know that:
- $$(\phi_s \wedge \phi_s^\prime\ l^\prime) \in \mathbb{VS}\lp \cfgnt{L}_{\mathcal{S}},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp$$ 
-From this, we may deduce that:
-$$ (\phi_\ell\ l) \in \cfgnt{L}_\ell^\prime(r^\prime) \Rightarrow (\phi_s \wedge \phi_s^\prime\ h^\prime(l))\in \cfgnt{L}_s^\prime(g^\prime(r^\prime))$$
-Since $r^\prime$ the only new addition to $L_\ell^\prime$ and $L_s^\prime$, we now know that the assertion above holds for all $l \in \mathcal{L}$.
-Thus, we have shown that $s_\ell^\prime \rightharpoonup_{(g\ h)} s_s^\prime$.
-Furthermore, since $\mathbb{S}(\phi_s\wedge\phi_s^\prime\wedge \phi_g)$ evaluates to $\cfgt{true}$, we know that equation \ref{eqn:valid} also evaluates to $\cfgt{true}$.
-Since there is a valid heap homomorphism, and since $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, we  by definition \ref{representation} know $s_\ell^\prime \sqsubset s_s^\prime$.
-We have now shown that for any lazy state $s_\ell$:
-$$s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$$
-
-%there is a little hand-waving here.
-We claim that that a valid (g' h') implies a valid (g h), but the reason for this is actually pretty subtle and should probably be detailed better.
-Basically, it depends on the fact that the value set for the returned reference is contingent on the entire access path from the root of the heap.
-Another hand-wavy part is showing that the lazy machine will turn si into si'.
-Finally, we still need to show that if we run the lazy machine on every feasible state in si that we get every feasible state in si' .
-
-Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$, but $s_i^\prime \notin \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
-Since $s_i^\prime \sqsubset s_s^\prime$, there must exist a valid homomorphism $s_i^\prime \rightharpoonup_{(g^\prime\ h^\prime)} s_s^\prime$.
-If $(g_i^\prime\ h_i^\prime)$ is valid, then there must also exist a valid homomorphism $(g_i\ h_i) : s_i \rightarrow s_s$, and by extension, state $s_i \sqsubset s_s$.
-However, since $s_s$ is exact, $s_i \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n})$, and by our previous result, $s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
-We have a contradiction.
-Therefore, $$s_i^\prime \sqsubset s_s^\prime \Rightarrow s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$$ Combining the two previous equations, we find that
-$$s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime)$$
-By definition \ref{congruent}, $s_s^\prime \equiv \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, and so by definition \ref{exact}, $s_s^\prime$ is exact.
-
-Case 2: If there are uninitialized fields, then the lazy initialization machine will make an intermediate state $s_t$.
-By lemma \ref{lem:init}, the symbolic state is congruent to the set of lazy initialized states.
-From the intermediate state, the proof is the same as for case 1.
-\end{proof}
-
-%proof for field write
-\begin{lemma}
-The field write rule is correct.
-\end{lemma}
-\begin{proof}
-\end{proof}
-
-%proof for reference compares. Here we will rely on the fact that since the L and R functions don't change, and since the phi function
-\begin{lemma}
-If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the state $s_s^\prime : s_s \rightarrow_s s_s^\prime$ is exact with respect to $s_0$ and $\pi_{n+1}$.
-\end{lemma}
-There are two rules that apply to state $s_s$, one for the $\cfgt{true}$ branch and one for the $\cfgt{false}$ branch.
-Since the proofs for both rules are nearly identical, for clarity we will only prove the case for the $\cfgt{true}$ branch here.
-\begin{proof}
-Choose any $s_\ell \sqsubset s_s$, and let $\zeta_T = \mathbb{FS}(\rightarrow_{\ell},s_0,(\pi_n,(\eta\ \cfgt{true}\ \cfgnt{k})))$.
-Since $s_s$ is exact, we know that $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, $s_l = \lp \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$, and that there exists $(g\ h) : s_\ell \rightarrow s_s$.
-Depending on the values of $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, there are two different rules that might apply to $s_\ell$.
-%I'm not sure we actually use this fact anywhere
- %In either case, $\cfgnt{L}_\ell$ and $\cfgnt{R}_\ell$ are unchanged, and $\phi_\ell$ is strengthened, so we already know that 
-%$$ \zeta_T \subseteq \{s_\ell^\prime | \exists s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n}) (s_\ell \rightarrow_\ell s_\ell^\prime )\}$$
-
-Case 1: Assume $s_\ell : \cfgnt{L}_\ell \lp \cfgnt{r}_0\rp = \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, and let 
-$$\zeta_t = \zeta_T \setminus \{ s_f | \cfgnt{L}_f \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_f \lp \cfgnt{r}_1 \rp \}$$ In this case, the lazy ``equals - references true" rule applies, and we know state $s_\ell^\prime : s_\ell \rightarrow_\ell s_\ell^\prime$ is in $\zeta_t$.
-Since $(g\ h)$ is valid, we know that $\exists \lp \phi_0\ l \rp \in \cfgnt{L}_\ell\lp g \lp \cfgnt{r}_0\rp \rp$, $\exists \lp \phi_1\ l \rp \in \cfgnt{L}_\ell\lp g \lp \cfgnt{r}_1\rp \rp$, and that $\mathbb{S}\lp\phi_s\wedge\phi_0\wedge \phi_1\rp$ holds true.
-Observe that by applying theorem \ref{thm:mutex}, $\phi_s^\prime \wedge \phi_0 \wedge \phi_1$ reduces to $\phi_s$.
-Therefore, $\lp g\ h \rp: s_\ell^\prime \rightarrow s_s^\prime$ is a valid heap homomorphism, and by extension, $s_\ell^\prime \sqsubset s_s^\prime$.
-Since this relation holds for arbitrary $s_\ell^\prime \in \zeta_t$, we now know that $$s_\ell^\prime \in \zeta_t \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$$
-Now we prove the case for the other direction.
-Consider the state $s_s^\prime : s_s \rightarrow_s s_s^\prime$.
-Define $\theta_\alpha$, $\theta_0$ and $\theta_1$ as in the ``equals (references-true) rule''.
-Since $\cfgnt{L}_s$ and $\cfgnt{R}_s$ are unchanged from $s_s$, and $\phi_g$ is only strengthened,  we know that:
-$$\{s_\ell^\prime | s_\ell^\prime \sqsubset s_s^\prime \} \subseteq \{s_\ell^\prime | \exists s_\ell \lp s_\ell \sqsubset s_s \rp \wedge s_\ell \rightarrow_s s_\ell^\prime\} $$
-Suppose that there exists state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$ and $s_i^\prime \notin \zeta_t$.
-Because of the above conclusion, we know that $$s_i^\prime \in \{s_\ell^\prime | \exists s_\ell \lp s_\ell \sqsubset s_s\rp \wedge s_\ell \rightarrow_s s_\ell^\prime\}$$ Combining this with the assumption that $s_i^\prime \notin \zeta_t$, we must conclude that $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp \neq  \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$.
-Because of this, and because of theorem \ref{thm:mutex}, we know that either all constraints $$\phi_i : \exists \phi_\alpha (\phi_\alpha \in \theta_\alpha)\wedge \phi_i = \lp\phi_\alpha \wedge \phi_0 \wedge \phi_1\rp$$ are unsatisfiable, or that at least one constraint $$\phi_i : \exists \phi_\alpha (\phi_\alpha \in \lp \theta_0 \cup \theta_1 \rp)\wedge \lp \phi_i = \phi_\alpha \wedge \phi_0 \wedge \phi_1 \rp$$ is valid.
-Either way, $\mathbb{S}\lp\phi_i^\prime \wedge\phi_0\wedge \phi_1\rp$ is false, $\lp g\ h\rp$ is not a valid homomorphism, and $s_s^\prime$ does not represent $s_i^\prime$.
-We have a contradiction.
-Therefore: $$s_\ell^\prime \sqsubset s_s^\prime \Rightarrow s_\ell^\prime \in \zeta_t$$
-Combining this with our previous result, we conclude that $$s_\ell^\prime \in \zeta_t \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$
-
-Case 2: Assume $s_\ell : \cfgnt{L}_\ell \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, and let 
-$$\zeta_f = \zeta_T \setminus \{ s_t | \cfgnt{L}_t \lp \cfgnt{r}_0\rp = \cfgnt{L}_t \lp \cfgnt{r}_1 \rp \}$$ 
-This means that the lazy ``equals - references false" rule applies.
-The proof for the ``equals - references false" rule is highly similar to the proof for ``equals - references true", so we omit it for the sake of brevity.
-The result for this case is:
-$$s_\ell^\prime \in \zeta_f \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$
-
-Since $\zeta_T = \zeta_t \cup \zeta_f$, we can combine the results of the two cases to find that $$s_\ell^\prime \in \zeta_T \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$.
-By definition \ref{congruent}, $s_s^\prime \equiv \zeta_T$, and by definition \ref{exact}, $s_s^\prime$ is exact.
-\end{proof}
-
-\begin{theorem}
-Every symbolic state on every execution path is exact.
-\end{theorem}
-\begin{proof}
-Combine all of the production-rule lemmas to inductively prove the theorem.
-\end{proof}

### 2014-07-17 tex/proofs.tex
Cleaned up field access proof. Added definition for Heap Constraint.

--- 2014-07-10 tex/proofs.tex
@@
 
-\subsection{Definitions}
-
-\begin{definition}
-A \textbf{state transition function} $\rightarrow_{\Phi}$ is a mapping $\rightarrow_{\Phi} : s \mapsto s$, which takes one machine state and transforms it into another machine state.
-Two important state transition functions are the \textbf{lazy state transition function} $\rightarrow_\ell$ and the \textbf{summary state transition function} $\rightarrow_s$.
-\end{definition}
-
-\begin{definition}
-A \textbf{state sequence} is as a sequence of states denoted as $\Pi_n = s_0,s_1,...,s_n$.
-A \textbf{feasible state sequence}, $\Pi_n^\phi = s_0,s_1,...,s_n$ is consistent with the transition: $\forall i\ (0 \leq i < n \Rightarrow s_i \rightarrow_{\Phi} s_{i+1})$.
-\end{definition}
-
-\begin{comment}
-\begin{definition}
-A \textbf{feasible state sequence} is defined as a sequence of states resulting from repeated application of the state transition relation to some initial state $s_0$: $$\Pi_n = s_0,s_1,...,s_n$$ where the relation $s_i \rightarrow_{\Phi} s_{i+1}$ holds for all $i \in \{ i | 0 \leq i < n \}$
-\end{definition}
-\end{comment}
-
-\begin{definition}
-A \textbf{lazy state} $s_\ell$ is any state such that there exists an integer $i$, initial state $s_0$, and feasible state sequence $\Pi_n^\ell$ satisfying the following requirements:
-\begin{align}
-\Pi_n^\ell &= s_0,s_1,...,s_n\\
-s_\ell &= s_i
-\end{align}
-\end{definition}
-
-\begin{definition}
-A \textbf{summary state} $s_s$ is any state such that there exists an integer $i$, initial state $s_0$, and feasible state sequence $\Pi_n^s$ satisfying the following requirements:
-\begin{align}
-\Pi_n^s &= s_0,s_1,...,s_n\\
-s_\ell &= s_i
-\end{align}
-\end{definition}
-
-\begin{definition}
-Given a sequence of states $$\Pi_n = s_0,s_1,...,s_n$$ where $$s_i = ( \mu_i\ \cfgnt{L}_i\ \cfgnt{R}_i\ \phi_i\ \eta_i\ \cfgnt{e}_i\ \cfgnt{k}_i )$$ the \textbf{control flow sequence} of $\Pi_n$ is the defined as the sequence of tuples $$ \pi_n = \mathbb{CF}(\Pi_n) = (\eta_0\ \cfgnt{e}_0\ \cfgnt{k}_0),(\eta_1\ \cfgnt{e}_1\ \cfgnt{k}_1),...,(\eta_n\ \cfgnt{e}_n\ \cfgnt{k}_n)$$
-\end{definition}
-
-\begin{definition}
-Given a state transition function $\rightarrow_{\Phi}$, an initial state $s_0$ and a control flow sequence $\pi_n$, the \textbf{feasible state set}, $\mathbb{FS}(\rightarrow_{\Phi},s_0,\pi_n)$, is defined as
- $$
-\begin{array}{l}
-\mathbb{FS}(\rightarrow_{\Phi},s_0,\pi_n) = \\
-\ \ \ \ \ \ \{s \mid \exists \Pi_n^\phi\ (\pi_n = \mathbb{CF}(\Pi_n^\Phi) \wedge s = \mathit{last}(\Pi_n))\} 
-\end{array}
-$$
-where $\mathit{last}(\Pi_n)$ returns the last state on the feasible sequence.
-\end{definition}
-
-\begin{definition}
-A \textbf{field access descriptor} $\gamma_i$ is a tuple 
-$$ \gamma_i = (\cfgnt{r}_i\ \phi_i\ \cfgnt{l}_i\ \cfgnt{f}_i)$$
-\end{definition}
-
-\begin{definition}
-An \textbf{access path} $\Gamma_n$ is a sequence of field access descriptors
-$ \Gamma_n = \gamma_0,\gamma_1,...,\gamma_n $.
-\end{definition}
-
-\begin{definition}
-For a given access path $\Gamma_n$ the \textbf{access path constraint} $\mathbb{PC}(\Gamma_n)$ is defined as
-$$\mathbb{PC}(\Gamma_n) =  \bigwedge \{\phi \mid \exists \gamma \in \Gamma_n \ (\gamma = (\cfgnt{r}\ \phi\ \cfgnt{e}\ \cfgnt{f}))\}$$  
-\end{definition}
-
-\begin{definition}
-For a given state $s= ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, a \textbf{valid access path} $\Gamma_n^s = \gamma_0,\gamma_1,...,\gamma_n$ satisfies the properties
-\begin{align*}
-\cfgnt{r}_0 &\in \mathit{refs}(\eta_s) \\
-\mathbb{S}(&\phi_s \wedge \mathbb{PC}(\Gamma_n^s)) \\
-\forall i & \in \mathbb{N}\ ( 0 \leq i < n \Leftrightarrow \gamma_i \in \Gamma_n^s\  \wedge\\
-&\ \ \ \  \gamma_{i+1} \in \Gamma_n^s\  \wedge\\
-&\ \ \ \  (\phi_i\ \cfgnt{l}_i)\in \cfgnt{L}_s(\cfgnt{r}_i)\ \wedge \\
-&\ \ \ \  \cfgnt{r}_{i+1} = \cfgnt{R}_s(\cfgnt{l}_i,\cfgnt{f}_i)\ \wedge\\
-&\ \ \ \ (\phi_{i+1}\ \cfgnt{l}_{i+1}) = \cfgnt{L}_s(\cfgnt{r}_{i+1}) )
-\end{align*}
-where $\gamma_i = (\cfgnt{r}_i\ \phi_i\ \cfgnt{l}_i\ \cfgnt{f}_i)$
-\end{definition}
-
-\begin{definition}
-A \textbf{homomorphism} $s_x \rightharpoonup_{(g\ h)} s_y$, from state $s_x = ( \cfgnt{L}_x\ \cfgnt{R}_x\ \phi_x\ \eta_x\ \cfgnt{e}_x\ \cfgnt{k}_x )$ to state $s_y = ( \cfgnt{L}_y\ \cfgnt{R}_y\ \phi_y\ \eta_y\ \cfgnt{e}_y\ \cfgnt{k}_y )$, is defined as follows:
-$$
-\begin{array}{l}
- s_x \rightharpoonup_{(g\ h)} s_y \Leftrightarrow \\
-\ \ \ \ \ \ \ \ \exists g:\mathcal{R} \mapsto \mathcal{R}\ ( \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{r} \in \mathcal{R}\ (\forall \cfgnt{l} \in \mathcal{L}\ ( \\ 
-\ \ \ \ \ \ \ \ \ \ \ \ (\phi_x\ \cfgnt{l}) \in \cfgnt{L}_x(\cfgnt{r}) \Rightarrow (\phi_y\ h(\cfgnt{l}))\in \cfgnt{L}_y(g(\cfgnt{r}))\ \wedge \\
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \cfgnt{r} = \cfgnt{R}_x(\cfgnt{l},f) \Rightarrow g(\cfgnt{r}) = \cfgnt{R}_y(h(\cfgnt{l}),f) )) )) 
-\end{array}
-$$
-\end{definition}
-
-\begin{definition}
-\label{representation}
-The \textbf{representation relation} is defined as follows: given lazy state $s_\ell$ and summary state $s_s$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a homomorphism $\ s_\ell \rightharpoonup_{(g\ h)} s_s $ such that if $$\theta = \{ \phi\ | \exists (r \in \cfgnt{R}_x,\  l \in \cfgnt{L}_x) ( (\phi\ h(l)) \in \cfgnt{L}_y (g(r))  \}$$ then
-\begin{equation}
-\label{eqn:valid}
- \mathbb{S}( \phi_y \wedge (\bigwedge_{\phi_i \in \theta} \phi_i)) 
-\end{equation}
-\end{definition}
-
-\begin{definition}
-\label{congruent}
-A summary state $s_s$ is \textbf{congruent} to a set of lazy states $P$ if and only if $s_s$ represents every state in $P$ and represents no other state: 
-$$s \cong P \Leftrightarrow \forall s_i \in \mathcal{S}\ (s_i \in P \Leftrightarrow s_i \sqsubset s_s) $$
-\end{definition}
-
-\begin{definition}
-\label{exact}
-A state $s$ is \textbf{exact} with respect to a transition relation, $\rightarrow_\phi$, an initial state, $s_0$, and specific control flow path, $\pi_n$, if and only if it is congruent to the set of feasible state set:
-$$ s \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi)$$
-\end{definition}
+\input{definitions}
 
 \subsection{Theorems}
+\begin{lemma}
+\label{lem:lazyrefprops}
+For any lazy state $s_\ell = ( \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta_\ell\ \cfgnt{e}_\ell\ \cfgnt{k}_\ell )$, for any reference $r \in \cfgnt{L}_\ell^\leftarrow$, 
+$$ | \cfgnt{L}_\ell ( r) | = 1 $$
+\end{lemma}
+
+\begin{proof}
+In every rule in the Lazy machine that establishes a reference mapping, the value set contains exactly one location, constraint pair. 
+\end{proof}
 
@@
 \label{thm:mutex}
-In any symbolic state $s_s$, the constraints in the value set of any reference are mutually exclusive.
+If we have a summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$ that is equivalent to some set of lazy states $\zeta$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, and any two pairs $(\phi_\alpha\ l_\alpha) &\in \cfgnt{L}_s(r)$ and $(\phi_\beta\ l_\beta) &\in \cfgnt{L}_s(r)$ such that $l_\alpha &\ne l_\beta$,
+%\begin{align*}
+%(\phi_\alpha\ l_\alpha) &\in \cfgnt{L}_s(r)\\
+%(\phi_\beta\ l_\beta) &\in \cfgnt{L}_s(r)\\
+%l_\alpha &\ne l_\beta
+%\end{align*}
+the following predicate is valid
+$$\neg (\phi_s \wedge \phi_\alpha \wedge \phi_\beta)$$
 \end{theorem}
@@
 \begin{lemma}
-For any symbolic state $s_s$, constraint $\phi$, and stack reference $\cfgnt{r}$ such that $(\phi\ \ell) \in \cfgnt{L}_s (r)$, $\phi$ is the conjunction of constraints for the access path to $l$.
+\label{lem:ref}
+For any symbolic state $s_s$, constraint $\phi$, and stack reference $\cfgnt{r}$ such that $(\phi\ \ell) \in \cfgnt{L}_s (\cfgnt{r})$, then 
+\begin{equation}
+\exists \Gamma_n^s\ ( \phi = \mathbb{PC} (\Gamma_n^s) )
+\end{equation}
 \end{lemma}
@@
 \begin{lemma}
-If there is some access path $\sigma$ in state $s_s$ such that $\mathbb{s}(\phi_\sigma \wedge \phi_s)$, then $\sigma \sqsubset$  
+\label{lem:path}
+If there is some access path $\Gamma_n^s$ in state $s_s$ such that $\mathbb{S}(\phi_s \wedge \mathbb{PC}(\Gamma_n^s))$, then $\Gamma_n^\ell$ is an access path in some lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$
 \end{lemma}
@@
 \label{lem:init}
-If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the intermediate state state $s_f : s_s \rightarrow_S s_f$ is congruent to $\{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$.
+If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the intermediate state state $s_f : s_s \rightarrow_S s_f$ is equivalent to $\{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$.
 \end{lemma}
@@
 Collectively exhaustive constraints are required to eliminate any other possible heaps.
-We could start by explicitly enumerating the members of the product feasible set, and working from there to show that the symbolic heap is congruent to that set.
+We could start by explicitly enumerating the members of the product feasible set, and working from there to show that the symbolic heap is equivalent to that set.
 Or, we might do this on a case-by-case basis to show that for an arbitrary lazy state, any of it's three possible target states is in the feasible set.
@@
 \begin{lemma}
+\label{lem:access}
 If there are symbolic states $s_s$ and $s_s^\prime$, control sequences $\pi_n$ and $\pi_{n+1}$, initial state $s_0$, and reference $\cfgnt{r}^\prime$ such that the following conditions hold:
@@
 $$ (\phi_\ell\ l) \in \cfgnt{L}_\ell^\prime(r^\prime) \Rightarrow (\phi_s \wedge \phi_s^\prime\ h^\prime(l))\in \cfgnt{L}_s^\prime(g^\prime(r^\prime))$$
-Since $r^\prime$ the only new addition to $L_\ell^\prime$ and $L_s^\prime$, we now know that the assertion above holds for all $l \in \mathcal{L}$.
+Since $r^\prime$ is the only new addition to $L_\ell^\prime$ and $L_s^\prime$, we now know that the assertion above holds for all $l \in \mathcal{L}$.
 Thus, we have shown that $s_\ell^\prime \rightharpoonup_{(g\ h)} s_s^\prime$.
 Furthermore, since $\mathbb{S}(\phi_s\wedge\phi_s^\prime\wedge \phi_g)$ evaluates to $\cfgt{true}$, we know that equation \ref{eqn:valid} also evaluates to $\cfgt{true}$.
-Since there is a valid heap homomorphism, and since $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, we  by definition \ref{representation} know $s_\ell^\prime \sqsubset s_s^\prime$.
+Since there is a valid heap homomorphism, and since $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, by Definition \ref{representation} we know $s_\ell^\prime \sqsubset s_s^\prime$.
 We have now shown that for any lazy state $s_\ell$:
 $$s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$$
+Since there is only one possible control flow sequence $\pi_{n+1}$, this means that if $s_\ell \rightarrow_\ell s_\ell^\prime$, then $$s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime\ \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$$
+Combining the two previous equations, we may finally conclude that $s_s^\prime$ is complete with respect to $\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$
+\begin{equation}
+\label{eqn:readforwards}
+s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1}) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime
+\end{equation}
 
@@
 
+%Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$, but $s_i^\prime \notin \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
+Since $s_i^\prime \sqsubset s_s^\prime$, then by Lemma \ref{lem:ref}, $\cfgnt{r}^\prime$ represents a valid path $\Gamma_{n+1}^{s\prime}$, in states $s_i^\prime$ and $s_s^\prime$.
+Furthermore, by Lemma \ref{lem:path} we can surmise that $\mathbb{S}(\phi_s^\prime \wedge \mathbb{PC}(\Gamma_{n+1}^{s\prime}))$.
+By construction, $\Gamma_{n+1}^{s\prime}$ is an extension of the valid access path $\Gamma_{n}^{s}$ represented by reference $\cfgnt{r}$ in state $s_s$.
+Since $s_s$ is exact, there exists state $s_i$ such that $s_i \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n})$.
+and by our previous result, $s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
+We have a contradiction.
+
 Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$, but $s_i^\prime \notin \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
-Since $s_i^\prime \sqsubset s_s^\prime$, there must exist a valid homomorphism $s_i^\prime \rightharpoonup_{(g^\prime\ h^\prime)} s_s^\prime$.
-If $(g_i^\prime\ h_i^\prime)$ is valid, then there must also exist a valid homomorphism $(g_i\ h_i) : s_i \rightarrow s_s$, and by extension, state $s_i \sqsubset s_s$.
-However, since $s_s$ is exact, $s_i \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n})$, and by our previous result, $s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
+Since $s_i^\prime \sqsubset s_s^\prime$, then by Definition \ref{representation}, we know there exists a homomorphism $s_i^\prime \rightharpoonup_{(g^\prime\ h^\prime)} s_s^\prime$, and that $\mathbb{S}( \phi_s^\prime \wedge \mathbb{HC}(s_i^\prime \rightharpoonup_{(g^\prime\ h^\prime)} s_s^\prime) )$.
+From state $s_i^\prime$, construct state $s_i$ such that
+\begin{align*}
+s_i &= \lp \cfgnt{L}_{i}\ \cfgnt{R}_{i}\ \phi_i\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp\\
+L_i &= L_i^\prime \setminus \cfgnt{r}^\prime \\
+R_i &= R_{i^\prime}\\
+\phi_i &= \phi_i^\prime
+\end{align*}
+Observe that $s_i \rightarrow_\ell s_i^\prime$.
+Now, construct functions $g_i$ and $h_i$ so that $g_i = g^\prime \setminus \cfgnt{r}^\prime$ and $h_i = h^\prime$.
+Observe that $s_i \rightharpoonup_{(g_i\ h_i)} s_s$, and that $\mathbb{S}( \phi_i \wedge \mathbb{HC}(s_i \rightharpoonup_{(g_i\ h_i)} s_s) )$, so $s_i \sqsubset s_s$.
+By the hypothesis that $s_s$ is exact, $s_i \in\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$.
+Combining this with the fact that $s_i \rightarrow_\ell s_i^\prime$, we conclude that $s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
 We have a contradiction.
-Therefore, $$s_i^\prime \sqsubset s_s^\prime \Rightarrow s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$$ Combining the two previous equations, we find that
-$$s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime)$$
-By definition \ref{congruent}, $s_s^\prime \equiv \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, and so by definition \ref{exact}, $s_s^\prime$ is exact.
+
+ Therefore, $s_s^\prime$ is sound with respect to $\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$
+ \begin{equation}
+ \label{eqn:readbackwards}
+ s_i^\prime \sqsubset s_s^\prime \Rightarrow s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})
+ \end{equation}
+Since $s_s$ is both sound and complete, we may combine Equations \ref{eqn:readforwards} and \ref{eqn:readbackwards} to find that 
+$$s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1}) \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$
+By Definition \ref{equivalent}, $s_s^\prime \cong \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, and so by Definition \ref{exact}, $s_s^\prime$ is exact.
 
 Case 2: If there are uninitialized fields, then the lazy initialization machine will make an intermediate state $s_t$.
-By lemma \ref{lem:init}, the symbolic state is congruent to the set of lazy initialized states.
+By lemma \ref{lem:init}, the symbolic state is equivalent to the set of lazy initialized states.
 From the intermediate state, the proof is the same as for case 1.
@@
 Since $\zeta_T = \zeta_t \cup \zeta_f$, we can combine the results of the two cases to find that $$s_\ell^\prime \in \zeta_T \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$.
-By definition \ref{congruent}, $s_s^\prime \equiv \zeta_T$, and by definition \ref{exact}, $s_s^\prime$ is exact.
+By definition \ref{equivalent}, $s_s^\prime \equiv \zeta_T$, and by definition \ref{exact}, $s_s^\prime$ is exact.
 \end{proof}

### 2014-07-18 tex/proofs.tex
Added proof for constraint mutual exclusion.

@@
 \label{thm:mutex}
-If we have a summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$ that is equivalent to some set of lazy states $\zeta$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, and any two pairs $(\phi_\alpha\ l_\alpha) &\in \cfgnt{L}_s(r)$ and $(\phi_\beta\ l_\beta) &\in \cfgnt{L}_s(r)$ such that $l_\alpha &\ne l_\beta$,
+If we have a summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, and any two pairs $(\phi_\alpha\ l_\alpha) &\in \cfgnt{L}_s(r)$ and $(\phi_\beta\ l_\beta) &\in \cfgnt{L}_s(r)$ such that $l_\alpha &\ne l_\beta$, then
 %\begin{align*}
@@
 %\end{align*}
-the following predicate is valid
-$$\neg (\phi_s \wedge \phi_\alpha \wedge \phi_\beta)$$
+$$(\phi_\alpha \wedge \phi_\beta) = \cfgt{false}$$
 \end{theorem}
 \begin{proof}
+The proof will proceed inductively. For the base case, consider any initial state $s_0$. The property holds by construction. (Hands waving around in the air for emphasis)
+
+Now we will show that if the exclusivity property holds for some state $s_s$, then it holds for any state $s_s^\prime$ where $s_s \rightarrow_s s_s^\prime$.
+
+First, suppose we have state $s_s$ and intermediate state $s_s^\prime$ where $s_s \rightarrow_S s_s^\prime$.
+If all fields are initialized, then $s_s$ and $s_s^\prime$ are identical, so the property holds for $s_s^\prime$.
+If any field is uninitialized, then the fields are initialized to new references, for which the exclusivity property holds by construction.
+(Hands waving around in the air for emphasis)
+
+Since the exclusivity property holds for every intermediate state, for any instruction that relies on the summary machine we can assume without loss of generality that all pertinent fields are initialized.
+
+Now, suppose we have a field read instruction.
+When we read the field, a new value set is created based on the $\mathbb{VS}$ function.
+The members of the value set have the form $(\phi\wedge \phi^\prime\ \ l)$.
+Choose any two distinct members of the value set, $(\phi_\alpha \wedge \phi_\alpha^\prime\ \ l_\alpha)$ and $(\phi_\beta \wedge \phi_\beta^\prime\ \ l_\beta)$.
+If $\phi_\alpha \ne \phi_\beta$, we know that exclusivity holds because $\phi_\alpha$ and $\phi_\beta$ came from the same value set in $s_s$, and are therefore exclusive.
+If $\phi_\alpha = \phi_\beta$, we know that exclusivity holds because $\phi_\alpha^\prime$ and $\phi_\beta^\prime$ came from the same value set in $s_s$ and are therefore exclusive.
+Thus, the exclusivity property holds for any pair of constraints in the value set.
+Since the only new value set in $L_{s^\prime}^\rightarrow$ is generated by the $\mathbb{VS}$ function, we are guaranteed that if exclusivity holds for $s_s$, then exclusivity holds for $s_s^\prime$.
+
+Suppose we have a field write instruction.
+This case is nearly identical as the field read.
+In this instruction, a new value set is created.
+The members of the value set have the form $(\phi\wedge \phi^\prime\ \ l)$.
+Choose any two distinct members of the value set, $(\phi_\alpha \wedge \phi_\alpha^\prime\ \ l_\alpha)$ and $(\phi_\beta \wedge \phi_\beta^\prime\ \ l_\beta)$.
+If $\phi_\alpha \ne \phi_\beta$, we know that exclusivity holds because $\phi_\alpha$ and $\phi_\beta$ came from the same value set in $s_s$, and are therefore exclusive.
+If $\phi_\alpha = \phi_\beta$, we know that exclusivity holds because $\phi_\alpha^\prime$ and $\phi_\beta^\prime$ came from the same value set in $s_s$ and are therefore exclusive.
+Thus, the exclusivity property holds for any pair of constraints in the value set.
+Since exclusivity holds for the only new value set in $L_{s^\prime}^\rightarrow$, we are guaranteed that if exclusivity holds for $s_s$, then exclusivity holds for $s_s^\prime$.
+
+Suppose we have a "new" instruction. In this case, only one value set is added to $L_{s^\prime}^\rightarrow$, and that value set contains only one member, so exclusivity holds by default.
+
+Suppose we have any instruction other that a read, write, or new.
+No machine rule other than those three listed instructions modifies the $L$ function.
+Therefore, the exclusivity property must hold for $s_s^\prime$ in these cases.
+
+Since the exclusivity property holds for any initial state, and since it holds for any "next" state if the property holds for the previous state, we have proven the property for every symbolic state.
 \end{proof}

### 2014-07-28 tex/proofs.tex
Minor changes to mutual exclusion proof.
fixed alignment character bug in mutex theorem

@@
 \subsection{Theorems}
-\begin{lemma}
-\label{lem:lazyrefprops}
-For any lazy state $s_\ell = ( \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta_\ell\ \cfgnt{e}_\ell\ \cfgnt{k}_\ell )$, for any reference $r \in \cfgnt{L}_\ell^\leftarrow$, 
-$$ | \cfgnt{L}_\ell ( r) | = 1 $$
-\end{lemma}
-
-\begin{proof}
-In every rule in the Lazy machine that establishes a reference mapping, the value set contains exactly one location, constraint pair. 
-\end{proof}
+%\begin{lemma}
+%\label{lem:lazyrefprops}
+%For any lazy state $s_\ell = ( \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta_\ell\ \cfgnt{e}_\ell\ \cfgnt{k}_\ell )$, for any reference $r \in \cfgnt{L}_\ell^\leftarrow$, 
+%$$ | \cfgnt{L}_\ell ( r) | = 1 $$
+%\end{lemma}
+%
+%\begin{proof}
+%In every rule in the Lazy machine that establishes a reference mapping, the value set contains exactly one location, constraint pair. 
+%\end{proof}
 
@@
 \label{thm:mutex}
-If we have a summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, and any two pairs $(\phi_\alpha\ l_\alpha) &\in \cfgnt{L}_s(r)$ and $(\phi_\beta\ l_\beta) &\in \cfgnt{L}_s(r)$ such that $l_\alpha &\ne l_\beta$, then
-%\begin{align*}
-%(\phi_\alpha\ l_\alpha) &\in \cfgnt{L}_s(r)\\
-%(\phi_\beta\ l_\beta) &\in \cfgnt{L}_s(r)\\
-%l_\alpha &\ne l_\beta
-%\end{align*}
+If we have a summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, and any two pairs $(\phi_\alpha\ l_\alpha) \in \cfgnt{L}_s(r)$ and $(\phi_\beta\ l_\beta) \in \cfgnt{L}_s(r)$ such that $l_\alpha \ne l_\beta$, then
 $$(\phi_\alpha \wedge \phi_\beta) = \cfgt{false}$$
@@
 If any field is uninitialized, then the fields are initialized to new references, for which the exclusivity property holds by construction.
-(Hands waving around in the air for emphasis)
+(More hands waving)
 
@@
 Choose any two distinct members of the value set, $(\phi_\alpha \wedge \phi_\alpha^\prime\ \ l_\alpha)$ and $(\phi_\beta \wedge \phi_\beta^\prime\ \ l_\beta)$.
-If $\phi_\alpha \ne \phi_\beta$, we know that exclusivity holds because $\phi_\alpha$ and $\phi_\beta$ came from the same value set in $s_s$, and are therefore exclusive.
+If $\phi_\alpha \ne \phi_\beta$, we know that exclusivity holds because $\phi_\alpha = \neg \phi_\beta$, so $\phi_\alpha$ and $\phi_\beta$ are therefore exclusive.
 If $\phi_\alpha = \phi_\beta$, we know that exclusivity holds because $\phi_\alpha^\prime$ and $\phi_\beta^\prime$ came from the same value set in $s_s$ and are therefore exclusive.
@@
 
-\begin{lemma}
-\label{lem:ref}
-For any symbolic state $s_s$, constraint $\phi$, and stack reference $\cfgnt{r}$ such that $(\phi\ \ell) \in \cfgnt{L}_s (\cfgnt{r})$, then 
-\begin{equation}
-\exists \Gamma_n^s\ ( \phi = \mathbb{PC} (\Gamma_n^s) )
-\end{equation}
-\end{lemma}
-\begin{proof}
-\end{proof}
-
-\begin{lemma}
-\label{lem:path}
-If there is some access path $\Gamma_n^s$ in state $s_s$ such that $\mathbb{S}(\phi_s \wedge \mathbb{PC}(\Gamma_n^s))$, then $\Gamma_n^\ell$ is an access path in some lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$
-\end{lemma}
-\begin{proof}
-\end{proof}
+%\begin{lemma}
+%\label{lem:ref}
+%For any symbolic state $s_s$, constraint $\phi$, and stack reference $\cfgnt{r}$ such that $(\phi\ \ell) \in \cfgnt{L}_s (\cfgnt{r})$, then 
+%\begin{equation}
+%\exists \Gamma_n^s\ ( \phi = \mathbb{PC} (\Gamma_n^s) )
+%\end{equation}
+%\end{lemma}
+%\begin{proof}
+%\end{proof}
+%
+%\begin{lemma}
+%\label{lem:path}
+%If there is some access path $\Gamma_n^s$ in state $s_s$ such that $\mathbb{S}(\phi_s \wedge \mathbb{PC}(\Gamma_n^s))$, then $\Gamma_n^\ell$ is an access path in some lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$
+%\end{lemma}
+%\begin{proof}
+%\end{proof}
 
@@
 \label{lem:init}
-If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the intermediate state state $s_f : s_s \rightarrow_S s_f$ is equivalent to $\{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$.
+If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the intermediate state state $s_f$ such that $s_s \rightarrow_S s_f$ is equivalent to $\{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$.
 \end{lemma}
@@
 We claim that that a valid (g' h') implies a valid (g h), but the reason for this is actually pretty subtle and should probably be detailed better.
-Basically, it depends on the fact that the value set for the returned reference is contingent on the entire access path from the root of the heap.
 Another hand-wavy part is showing that the lazy machine will turn si into si'.
@@
 \begin{lemma}
-If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the state $s_s^\prime : s_s \rightarrow_s s_s^\prime$ is exact with respect to $s_0$ and $\pi_{n+1}$.
+If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then any state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$ is equal to $ \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_{s^\prime}\ \eta\ \cfgnt{v}_{s^\prime}\ \cfgnt{k}\rp$ and is exact with respect to $s_0$ and $\pi_n \ (\eta\ \cfgnt{v}_{s^\prime}\ \cfgnt{k})$.
 \end{lemma}
 There are two rules that apply to state $s_s$, one for the $\cfgt{true}$ branch and one for the $\cfgt{false}$ branch.
-Since the proofs for both rules are nearly identical, for clarity we will only prove the case for the $\cfgt{true}$ branch here.
+Since the proofs for both rules are nearly identical, for clarity we will only show the proof for the case for the $\cfgt{true}$ branch here.
 \begin{proof}
 Choose any $s_\ell \sqsubset s_s$, and let $\zeta_T = \mathbb{FS}(\rightarrow_{\ell},s_0,(\pi_n,(\eta\ \cfgt{true}\ \cfgnt{k})))$.
-Since $s_s$ is exact, we know that $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, $s_l = \lp \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$, and that there exists $(g\ h) : s_\ell \rightarrow s_s$.
+Since $s_s$ is exact, we know that $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, $s_l = \lp \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$, and that there exists a homomorphism $s_\ell \rightarrow_{(g\ h) } s_s$ such that $\mathbb{S}( \phi_s \wedge \mathbb{HC}(s_\ell \rightharpoonup_{(g\ h)} s_s) ) $.
 Depending on the values of $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, there are two different rules that might apply to $s_\ell$.

### 2014-07-28 tex/proofs.tex
Cleaned up the reference-compare proof

@@
 Choose any $s_\ell \sqsubset s_s$, and let $\zeta_T = \mathbb{FS}(\rightarrow_{\ell},s_0,(\pi_n,(\eta\ \cfgt{true}\ \cfgnt{k})))$.
-Since $s_s$ is exact, we know that $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, $s_l = \lp \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$, and that there exists a homomorphism $s_\ell \rightarrow_{(g\ h) } s_s$ such that $\mathbb{S}( \phi_s \wedge \mathbb{HC}(s_\ell \rightharpoonup_{(g\ h)} s_s) ) $.
+Since $s_s$ is exact, we know that $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, $s_l = \lp \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$, and that there exists a homomorphism $s_\ell \rightharpoonup_{(g\ h) } s_s$ such that $\mathbb{S}( \phi_s \wedge \mathbb{HC}(s_\ell \rightharpoonup_{(g\ h)} s_s) ) $.
 Depending on the values of $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, there are two different rules that might apply to $s_\ell$.
@@
 $$\zeta_t = \zeta_T \setminus \{ s_f | \cfgnt{L}_f \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_f \lp \cfgnt{r}_1 \rp \}$$ In this case, the lazy ``equals - references true" rule applies, and we know state $s_\ell^\prime : s_\ell \rightarrow_\ell s_\ell^\prime$ is in $\zeta_t$.
-Since $(g\ h)$ is valid, we know that $\exists \lp \phi_0\ l \rp \in \cfgnt{L}_\ell\lp g \lp \cfgnt{r}_0\rp \rp$, $\exists \lp \phi_1\ l \rp \in \cfgnt{L}_\ell\lp g \lp \cfgnt{r}_1\rp \rp$, and that $\mathbb{S}\lp\phi_s\wedge\phi_0\wedge \phi_1\rp$ holds true.
 Observe that by applying theorem \ref{thm:mutex}, $\phi_s^\prime \wedge \phi_0 \wedge \phi_1$ reduces to $\phi_s$.
-Therefore, $\lp g\ h \rp: s_\ell^\prime \rightarrow s_s^\prime$ is a valid heap homomorphism, and by extension, $s_\ell^\prime \sqsubset s_s^\prime$.
+Therefore, $\mathbb{S}( \phi_s^\prime \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{(g\ h)} s_s^\prime) ) $ is true, and by extension, $s_\ell^\prime \sqsubset s_s^\prime$.
 Since this relation holds for arbitrary $s_\ell^\prime \in \zeta_t$, we now know that $$s_\ell^\prime \in \zeta_t \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$$
 Now we prove the case for the other direction.
-Consider the state $s_s^\prime : s_s \rightarrow_s s_s^\prime$.
+Consider a state $s_s^\prime$ where  $s_s \rightarrow_s s_s^\prime$.
 Define $\theta_\alpha$, $\theta_0$ and $\theta_1$ as in the ``equals (references-true) rule''.
-Since $\cfgnt{L}_s$ and $\cfgnt{R}_s$ are unchanged from $s_s$, and $\phi_g$ is only strengthened,  we know that:
+Since $\cfgnt{L}_s$ and $\cfgnt{R}_s$ are unchanged from $s_s$, and $\phi_s^\prime$ is only a strengthened version of $\phi_s$,  we know that
 $$\{s_\ell^\prime | s_\ell^\prime \sqsubset s_s^\prime \} \subseteq \{s_\ell^\prime | \exists s_\ell \lp s_\ell \sqsubset s_s \rp \wedge s_\ell \rightarrow_s s_\ell^\prime\} $$
 Suppose that there exists state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$ and $s_i^\prime \notin \zeta_t$.
-Because of the above conclusion, we know that $$s_i^\prime \in \{s_\ell^\prime | \exists s_\ell \lp s_\ell \sqsubset s_s\rp \wedge s_\ell \rightarrow_s s_\ell^\prime\}$$ Combining this with the assumption that $s_i^\prime \notin \zeta_t$, we must conclude that $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp \neq  \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$.
-Because of this, and because of theorem \ref{thm:mutex}, we know that either all constraints $$\phi_i : \exists \phi_\alpha (\phi_\alpha \in \theta_\alpha)\wedge \phi_i = \lp\phi_\alpha \wedge \phi_0 \wedge \phi_1\rp$$ are unsatisfiable, or that at least one constraint $$\phi_i : \exists \phi_\alpha (\phi_\alpha \in \lp \theta_0 \cup \theta_1 \rp)\wedge \lp \phi_i = \phi_\alpha \wedge \phi_0 \wedge \phi_1 \rp$$ is valid.
-Either way, $\mathbb{S}\lp\phi_i^\prime \wedge\phi_0\wedge \phi_1\rp$ is false, $\lp g\ h\rp$ is not a valid homomorphism, and $s_s^\prime$ does not represent $s_i^\prime$.
+Because of the above conclusion, we know that $$s_i^\prime \in \{s_\ell^\prime | \exists s_\ell \lp s_\ell \sqsubset s_s\rp \wedge s_\ell \rightarrow_s s_\ell^\prime\}$$
+Combining this with the assumption that $s_i^\prime \notin \zeta_t$, we must conclude that $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp \neq  \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$.
+Because of this, and because of Theorem \ref{thm:mutex}, we know that either all constraints in the set
+$$\{\phi_i \mid \exists \phi_\alpha (\phi_\alpha \in \theta_\alpha)\wedge \phi_i = \lp\phi_\alpha \wedge \phi_0 \wedge \phi_1\rp\}$$ are unsatisfiable, or that at least one constraint in the set
+$$\{\phi_i \mid \exists \phi_\alpha (\phi_\alpha \in \lp \theta_0 \cup \theta_1 \rp)\wedge \lp \phi_i = \phi_\alpha \wedge \phi_0 \wedge \phi_1 \rp\}$$ 
+is valid.
+Either way, $\mathbb{S}\lp\phi_i^\prime \wedge\phi_0\wedge \phi_1\rp$ is false and $s_s^\prime$ does not represent $s_i^\prime$.
 We have a contradiction.
@@
 
-Since $\zeta_T = \zeta_t \cup \zeta_f$, we can combine the results of the two cases to find that $$s_\ell^\prime \in \zeta_T \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$.
-By definition \ref{equivalent}, $s_s^\prime \equiv \zeta_T$, and by definition \ref{exact}, $s_s^\prime$ is exact.
+Since $\zeta_T = \zeta_t \cup \zeta_f$, we can combine the results of the two cases to find that 
+$$s_\ell^\prime \in \zeta_T \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$
+ By Definition \ref{equivalent}, $s_s^\prime \equiv \zeta_T$, and by definition \ref{exact}, $s_s^\prime$ is exact.
 \end{proof}

### 2014-07-31 tex/proofs.tex
Added theorem for colletive exhaustion property. Sketched in more details for the summary initialization lemma.

@@
 
+\begin{theorem}
+\label{thm:colex}
+If we have a summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, 
+$$\bigvee \{ \phi \mid (\phi\ \cfgnt{l})\in \cfgnt{L}_s (\cfgnt{r})\} = \cfgt{true}$$
+\end{theorem}
+\begin{proof}
+For now, the proof is left as an exercise to the reader.
+\end{proof}
 %\begin{lemma}
@@
 \label{lem:init}
-If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the intermediate state state $s_f$ such that $s_s \rightarrow_S s_f$ is equivalent to $\{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$.
+If symbolic state $s_s = \lp \cfgnt{L}_s\ \cfgnt{R}_{s}\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the intermediate state state $s_s^*$ such that $s_s \rightarrow_S^* s_s^*$ is equivalent to $\{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$.
 \end{lemma}
@@
 \begin{proof}%going through this one quickly, could be more formal...
-Given a lazy state $s_\ell \sqsubset s_s$, there are four distinct possibilities for $s_\ell^\prime$: either the field is already initialized, or the field is initialized to a new reference, the null reference, or an alias.
+Take any lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$.
+By Definition \ref{representation}, we know $s_\ell = \lp \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.
+The state $s_\ell^\prime$ where $s_\ell \rightarrow_I^* s_\ell^\prime$ may take one of four forms: either the field is already initialized, or the uninitialized field is initialized to a new reference, the null reference, or an alias.
 
-Case 1: Suppose the field is initialized. In this case, the rule does nothing and the theorem is trivially true.
+We now show that the following four cases for $s_\ell^*$ are represented in $s_s^*$.
+
+Case 1: Suppose the field in question is initialized. In this case, we don't change the field so there is no way to mess anything up.
 
@@
 
-Case 2: The "new" rule gets executed.
+Case 2: The "new" rule gets executed. We add a new location, so this case is represented.
 
-Case 3: The "null" rule gets executed.
+Case 3: The "null" rule gets executed. We add a link to the null location, so this case is represented.
 
 Case 4: The "alias" rule gets executed.
+We add links to all possible aliases, so this case is also represented.
+In fact, we add more links than we really need, but the extra ones are infeasible for the case in question so it's not a problem.
+
+Having demonstrated each of these four cases, we now know that 
+$$s_\ell^* \in \{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \} \Rightarrow  s_\ell^* \sqsubset s_s^*$$
+
+We now prove the reverse case, that $s_s^*$ represents no infeasible states.
+We modified no references from the previous heap, and did not alter the global invariant.
+This means that every old reference points to the right place at the right time, and that no old reference points to the wrong place at the wrong time.
+Thus, if there is a problem with a reference, it must be with one of the new references we created.
+Since we have already proved that every reference points to the right place at the write time, there must be some field that points to the wrong place at the wrong time.
+Since we know that every field points to the right place at the right time, and since we know that the constraints are mutually exclusive, we know that the "wrong time" can never be at the same time as the "right time".
+Since the right time is every time due to Theorem \ref{thm:colex}, this implies that the wrong time is no time.
+We have now proven that
+$$ s_\ell^* \sqsubset s_s^*  \Rightarrow  s_\ell^* \in \{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$$
+This fact, combined with our previous result, proves that
+$$s_s^*  \cong \{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$$
+
 \end{proof}
@@
 
-%there is a little hand-waving here.
-We claim that that a valid (g' h') implies a valid (g h), but the reason for this is actually pretty subtle and should probably be detailed better.
-Another hand-wavy part is showing that the lazy machine will turn si into si'.
-Finally, we still need to show that if we run the lazy machine on every feasible state in si that we get every feasible state in si' .
-
 %Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$, but $s_i^\prime \notin \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
@@
 s_i &= \lp \cfgnt{L}_{i}\ \cfgnt{R}_{i}\ \phi_i\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp\\
-L_i &= L_i^\prime \setminus \cfgnt{r}^\prime \\
+L_i &= L_{i^\prime} \setminus \{\cfgnt{r}^\prime \}\\
 R_i &= R_{i^\prime}\\

### 2014-08-05 tex/definitions.tex
Added definitions for image and preimage
Simplified definition for homomorphism. Still need to update proofs to reflect the change.

@@
 The set of \textbf{initial states} $\mathcal{S}_0$ is defined as
+\end{definition}
+
+\begin{definition}
+For a given function $f:A \mapsto B$, the \textbf{image} $f^\rightarrow$ and \textbf{preimage} $f^\leftarrow$ are defined as
+\begin{align}
+ f^\rightarrow &= \{ f(a) \mid a \in A\}\\
+ f^\leftarrow &= \{ a \mid f(a) \in B \}§
+ \end{align}
 \end{definition}
@@
 \begin{definition}
-A \textbf{homomorphism} $s_x \rightharpoonup_{(g\ h)} s_y$, from state $s_x = ( \cfgnt{L}_x\ \cfgnt{R}_x\ \phi_x\ \eta_x\ \cfgnt{e}_x\ \cfgnt{k}_x )$ to state $s_y = ( \cfgnt{L}_y\ \cfgnt{R}_y\ \phi_y\ \eta_y\ \cfgnt{e}_y\ \cfgnt{k}_y )$, is defined as follows:
+A \textbf{homomorphism} $s_x \rightharpoonup_{h} s_y$, from state $s_x = ( \cfgnt{L}_x\ \cfgnt{R}_x\ \phi_x\ \eta_x\ \cfgnt{e}_x\ \cfgnt{k}_x )$ to state $s_y = ( \cfgnt{L}_y\ \cfgnt{R}_y\ \phi_y\ \eta_y\ \cfgnt{e}_y\ \cfgnt{k}_y )$, is defined as follows:
 $$
 \begin{array}{l}
- s_x \rightharpoonup_{(g\ h)} s_y \Leftrightarrow \\
-\ \ \ \ \ \ \ \ \exists g:\mathcal{R} \mapsto \mathcal{R}\ ( \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{r} \in \mathcal{R}\ (\forall \cfgnt{l} \in \mathcal{L}\ ( \\ 
-\ \ \ \ \ \ \ \ \ \ \ \ (\phi_a\ \cfgnt{l}) \in \cfgnt{L}_x(\cfgnt{r}) \Rightarrow (\phi_b\ h(\cfgnt{l}))\in \cfgnt{L}_y(g(\cfgnt{r}))\ \wedge \\
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \cfgnt{r} = \cfgnt{R}_x(\cfgnt{l},f) \Rightarrow g(\cfgnt{r}) = \cfgnt{R}_y(h(\cfgnt{l}),f) )) )) 
+ s_x \rightharpoonup_{h} s_y \Leftrightarrow \\
+\ \ \ \ \ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha \in \mathcal{L}\ (\forall \cfgnt{l}_\beta \in \mathcal{L}\ ( \\ 
+\ \ \ \ \ \ \ \ \ \ \ \ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_x(\cfgnt{R}_x (\cfgnt{l}_\beta,f )) \Rightarrow (\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_y(\cfgnt{R}_y (h(\cfgnt{l}_\beta),f ))\ \\
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  )) ) 
 \end{array}
@@
 \label{def:hc}
-Given homomorphism $s_x \rightharpoonup_{(g\ h)} s_y$, the \textbf{homomorphism constraint} $\mathbb{HC}(s_x \rightharpoonup_{(g\ h)} s_y)$ is defined as:
+Given homomorphism $s_x \rightharpoonup_{h} s_y$, the \textbf{homomorphism constraint} $\mathbb{HC}(s_x \rightharpoonup_{h} s_y)$ is defined as:
 \begin{align*}
-\mathbb{HC}(s_x \rightharpoonup_{(g\ h)} s_y) = \\
- \bigwedge \{ \phi_b\ | \exists r \in \cfgnt{L}_x^\leftarrow\ (\exists (\phi_a\ l) \in \cfgnt{L}_x^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_y (g(r)))) 
+\mathbb{HC}(s_x \rightharpoonup_{h} s_y) &= \\
+ \bigwedge \{ \phi_b\ | \exists r \in \cfgnt{L}_x^\leftarrow\ &(\exists (\phi_a\ l) \in \cfgnt{L}_x^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_y (g(r)))) 
 \end{align*}
@@
 \label{representation}
-The \textbf{representation relation} is defined as follows: given lazy state $s_\ell = ( \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta_\ell\ \cfgnt{e}_\ell\ \cfgnt{k}_\ell )$ and summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a homomorphism $\ s_\ell \rightharpoonup_{(g\ h)} s_s $ such that
+The \textbf{representation relation} is defined as follows: given lazy state $s_\ell = ( \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta_\ell\ \cfgnt{e}_\ell\ \cfgnt{k}_\ell )$ and summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a homomorphism $\ s_\ell \rightharpoonup_{h} s_s $ such that
 \begin{equation}
 \label{eqn:valid}
- \mathbb{S}( \phi_s \wedge \mathbb{HC}(s_\ell \rightharpoonup_{(g\ h)} s_s) ) 
+ \mathbb{S}( \phi_s \wedge \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s) ) 
 \end{equation}

### 2014-08-05 tex/proofs.tex
Updated field access proof to reflect changes to homomorphism definition.

@@
 We now show that the following four cases for $s_\ell^*$ are represented in $s_s^*$.
+For the following cases, let $\rightharpoonup_{(g\ h)}$ be the homomorphism such that $s_\ell \rightharpoonup_{(g\ h)} s_s$, let $\cfgnt{l}_\ell = \cfgnt{L}_\ell(\cfgnt{r})$, and let $\cfgnt{l}_s = h(\cfgnt{l}_\ell) $
 
-Case 1: Suppose the field in question is initialized. In this case, we don't change the field so there is no way to mess anything up.
+Case 1: Suppose $\cfgnt{R}_\ell(\cfgnt{l}_\ell) \neq \bot$.
+In this case, because $s_\ell \rightharpoonup_{(g\ h)} s_s$, we know that $\cfgnt{L}_s(h(\cfgnt{l})) \neq \bot$.
+This means that in the Summarize rule, $\cfgnt{l} \notin \Lambda$, and therefore, $\cfgnt{R}_s = \cfgnt{R}_{s^*} $.
+By extension,
+
+Case 2: Suppose the field is uninitialized, and the "new" rule gets executed. We add a new location, so this case is represented.
+
+Case 3: Suppose the field is uninitialized, and the "null" rule gets executed. We add a link to the null location, so this case is represented.
+
+Case 4: Suppose the field is uninitialized, and the "alias" rule gets executed.
+We add links to all possible aliases, so this case is also represented.
+In fact, we add more links than we really need, but the extra ones are infeasible for the case in question so it's not a problem.
 
@@
 
-Case 2: The "new" rule gets executed. We add a new location, so this case is represented.
-
-Case 3: The "null" rule gets executed. We add a link to the null location, so this case is represented.
-
-Case 4: The "alias" rule gets executed.
-We add links to all possible aliases, so this case is also represented.
-In fact, we add more links than we really need, but the extra ones are infeasible for the case in question so it's not a problem.
-
 Having demonstrated each of these four cases, we now know that 
@@
 Thus, if there is a problem with a reference, it must be with one of the new references we created.
-Since we have already proved that every reference points to the right place at the write time, there must be some field that points to the wrong place at the wrong time.
+Since we have already proved that every reference points to the right place at the right time, there must be some field that points to the wrong place at the wrong time.
 Since we know that every field points to the right place at the right time, and since we know that the constraints are mutually exclusive, we know that the "wrong time" can never be at the same time as the "right time".
@@
  and 
- $$ s_s^\prime = \lp \cfgnt{L}_{s}[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}_{\mathcal{S}},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
+ $$ s_s^\prime = \lp \cfgnt{L}_{s}[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}_{s},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}_{s}\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
 
@@
 Since $\eta$, $e$, and $k$ are identical between $s_s^\prime$ and $s_\ell^\prime $, the first condition is met by default.
-Now we construct functions $g^\prime$ and $h^\prime$ such that $g^\prime = g[ r^\prime \mapsto r^\prime]$ and $h^\prime = h$.
-Observe that since $s_\ell \rightharpoonup_{(g\ h)} s_s$, and since $\cfgnt{R}_\ell$ and $\cfgnt{R}_s$ are unchanged from states $s_\ell$ to $s_\ell^\prime$ and $s_s$ to $s_s^\prime$ respectively, we are guaranteed that $ r = \cfgnt{R}_\ell(l,f) \Rightarrow g^\prime(r) = \cfgnt{R}_s(h^\prime(l),f)$.
-Since $(\phi_\ell^\prime\ l^\prime) =  \cfgnt{L}_\ell(\cfgnt{R}_\ell(l,f))$, and since $(g\ h)$ is valid, we know that:
- $$(\phi_s \wedge \phi_s^\prime\ l^\prime) \in \mathbb{VS}\lp \cfgnt{L}_{\mathcal{S}},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp$$ 
+Now we construct the function $h^\prime$ such that $h^\prime = h$.
+Observe that since $s_\ell \rightharpoonup_{h} s_s$, and since $\cfgnt{R}_\ell$ and $\cfgnt{R}_s$ are unchanged from states $s_\ell$ to $s_\ell^\prime$ and $s_s$ to $s_s^\prime$ respectively, we are guaranteed that $ \cfgnt{r} = \cfgnt{R}_\ell(l,f) \Rightarrow \cfgnt{r} = \cfgnt{R}_s(h^\prime(l),f)$.
+Let $\{(\phi_\ell^\prime\ l^\prime)\} =  \cfgnt{L}_\ell(\cfgnt{R}_\ell(l,f))$.
+Since $\mathbb{S}(\phi_g \wedge \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s))$ is valid, we know that:
+ $$(\phi_s \wedge \phi_s^\prime\ h(l^\prime)) \in \mathbb{VS}\lp \cfgnt{L}_{s},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp$$ 
 From this, we may deduce that:
-$$ (\phi_\ell\ l) \in \cfgnt{L}_\ell^\prime(r^\prime) \Rightarrow (\phi_s \wedge \phi_s^\prime\ h^\prime(l))\in \cfgnt{L}_s^\prime(g^\prime(r^\prime))$$
-Since $r^\prime$ is the only new addition to $L_\ell^\prime$ and $L_s^\prime$, we now know that the assertion above holds for all $l \in \mathcal{L}$.
+$$ (\phi_\ell\ l) \in \cfgnt{L}_\ell^\prime(\cfgnt{r}^\prime) \Rightarrow (\phi_s \wedge \phi_s^\prime\ h^\prime(l))\in \cfgnt{L}_s^\prime(\cfgnt{r}^\prime)$$
+Since $\cfgnt{r}^\prime$ is the only new addition to $L_\ell^\prime$ and $L_s^\prime$, we now know that the assertion above holds for all $l \in \mathcal{L}$.
 Thus, we have shown that $s_\ell^\prime \rightharpoonup_{(g\ h)} s_s^\prime$.
-Furthermore, since $\mathbb{S}(\phi_s\wedge\phi_s^\prime\wedge \phi_g)$ evaluates to $\cfgt{true}$, we know that equation \ref{eqn:valid} also evaluates to $\cfgt{true}$.
-Since there is a valid heap homomorphism, and since $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, by Definition \ref{representation} we know $s_\ell^\prime \sqsubset s_s^\prime$.
+Furthermore, since $\mathbb{S}(\phi_g \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime))$, and since $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, by Definition \ref{representation} we know $s_\ell^\prime \sqsubset s_s^\prime$.
 We have now shown that for any lazy state $s_\ell$:
-$$s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$$
-Since there is only one possible control flow sequence $\pi_{n+1}$, this means that if $s_\ell \rightarrow_\ell s_\ell^\prime$, then $$s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime\ \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$$
-Combining the two previous equations, we may finally conclude that $s_s^\prime$ is complete with respect to $\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$
+\begin{equation}
+\label{eqn:slimpliesslprime}
+s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime
+\end{equation}
+
+Since there is only one possible control flow sequence $\pi_{n+1}$, this means that if $s_\ell \rightarrow_\ell s_\ell^\prime$, then 
+\begin{equation}
+\label{eqn:slimpliesslprime2}
+s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime\ \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})
+\end{equation}
+
+Combining Equations \ref{eqn:slimpliesslprime} and \ref{eqn:slimpliesslprime2}, we may finally conclude that $s_s^\prime$ is complete with respect to $\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$
 \begin{equation}
@@
 Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$, but $s_i^\prime \notin \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
-Since $s_i^\prime \sqsubset s_s^\prime$, then by Definition \ref{representation}, we know there exists a homomorphism $s_i^\prime \rightharpoonup_{(g^\prime\ h^\prime)} s_s^\prime$, and that $\mathbb{S}( \phi_s^\prime \wedge \mathbb{HC}(s_i^\prime \rightharpoonup_{(g^\prime\ h^\prime)} s_s^\prime) )$.
+Since $s_i^\prime \sqsubset s_s^\prime$, then by Definition \ref{representation}, we know there exists a homomorphism $s_i^\prime \rightharpoonup_{h^\prime} s_s^\prime$, and that $\mathbb{S}( \phi_i^\prime \wedge \mathbb{HC}(s_i^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$.
 From state $s_i^\prime$, construct state $s_i$ such that
@@
 Observe that $s_i \rightarrow_\ell s_i^\prime$.
-Now, construct functions $g_i$ and $h_i$ so that $g_i = g^\prime \setminus \cfgnt{r}^\prime$ and $h_i = h^\prime$.
-Observe that $s_i \rightharpoonup_{(g_i\ h_i)} s_s$, and that $\mathbb{S}( \phi_i \wedge \mathbb{HC}(s_i \rightharpoonup_{(g_i\ h_i)} s_s) )$, so $s_i \sqsubset s_s$.
+Now, construct function $h_i$ so that $h_i = h^\prime$.
+Observe that $s_i \rightharpoonup_{h_i} s_s$, and that $\mathbb{S}( \phi_i \wedge \mathbb{HC}(s_i \rightharpoonup_{h_i} s_s) )$, so $s_i \sqsubset s_s$.
 By the hypothesis that $s_s$ is exact, $s_i \in\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$.

### 2014-08-20 tex/proofs.tex
Added more to the summary machine proof

@@
 By Definition \ref{representation}, we know $s_\ell = \lp \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.
-The state $s_\ell^\prime$ where $s_\ell \rightarrow_I^* s_\ell^\prime$ may take one of four forms: either the field is already initialized, or the uninitialized field is initialized to a new reference, the null reference, or an alias.
+Take any state $s_\ell^\prime$ where $s_\ell \rightarrow_I^* s_\ell^\prime$, and state $s_s^\prime$ where $s_s \rightarrow_S^* s_s^\prime$.
+Note that  state $s_\ell^\prime$ has the form: $s_\ell^\prime = \lp \cfgnt{L}_{\ell^\prime}\ \cfgnt{R}_{\ell^\prime}\ \phi_\ell\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.Take any location, field pair $\lp l_\ell\  \cfgnt{f}\rp$ such that $\lp l_\ell\  \cfgnt{f}\rp \in \cfgnt{R}_{\ell}^\leftarrow$, and let $l_s = h(l_\ell)$.
+We may classify $l_\ell$ into one of three categories, based on the values of the $\cfgnt{R}$ function in each of the states $s_\ell$, $s_\ell^\prime$, $s_s$, and $s_s^\prime$, and we may define a function $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ based on that classification.
 
-We now show that the following four cases for $s_\ell^*$ are represented in $s_s^*$.
-For the following cases, let $\rightharpoonup_{(g\ h)}$ be the homomorphism such that $s_\ell \rightharpoonup_{(g\ h)} s_s$, let $\cfgnt{l}_\ell = \cfgnt{L}_\ell(\cfgnt{r})$, and let $\cfgnt{l}_s = h(\cfgnt{l}_\ell) $
+Class 1: $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f}) = \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_s,  \cfgnt{f}) = \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$.
+In this case, let $h^\prime(l_\ell) = h(l_\ell)$.
+Since $s_\ell \rightharpoonup_h s_s$, obviously:
+$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$$.
+Furthermore, since $\mathbb{HC}()$
 
-Case 1: Suppose $\cfgnt{R}_\ell(\cfgnt{l}_\ell) \neq \bot$.
-In this case, because $s_\ell \rightharpoonup_{(g\ h)} s_s$, we know that $\cfgnt{L}_s(h(\cfgnt{l})) \neq \bot$.
-This means that in the Summarize rule, $\cfgnt{l} \notin \Lambda$, and therefore, $\cfgnt{R}_s = \cfgnt{R}_{s^*} $.
+Class 2: $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f}) = \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_s,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$.
+Notice that since $\cfgnt{R}_{s} ( l_s,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$, we may deduce that $ (\phi_b\ \bot)\in \cfgnt{L}_{s}(\cfgnt{R}_{s} (\cfgnt{l}_s,f ))$, and by extension, ${(\phi_a\ \bot)} = \cfgnt{L}_{\ell}(\cfgnt{R}_{\ell} (\cfgnt{l}_\ell,f )) $.
+In this case, we let $h^\prime(l_\ell) = h(l_\ell)$.
+Since $(\phi_a\ \bot) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f ))$, and since by rule $ (\phi_b\ \bot)\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$, we can see that in this case:
+$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$$.
+STILL NEED TO SHOW WHAT HAPPENS WITH THE CONSTRAINTS.
+
+Class 3: $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f}) \neq \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_s,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$.
+
+Since for all possible $l_\ell$ there exists an $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ such that 
+$$ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f )) $$ we know that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$.
+Furthermore, since the heap constraint is satisfiable, we know that $s_\ell^\prime \sqsubset s_s^\prime $.
+We have therefore shown that for some summary state $s_s$ and an arbitrary lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$ :
+\begin{equation} 
+(s_\ell \rightarrow_I^* s_\ell^\prime \wedge s_s \rightarrow_S^* s_s^\prime) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime 
+\end{equation}
+
+%may take one of four forms: either the field is already initialized, or the uninitialized field is initialized to a new reference, the null reference, or an alias.
+%
+%We now show that the following four cases for $s_\ell^*$ are represented in $s_s^*$.
+For the following cases, let $\rightharpoonup_{h}$ be the homomorphism such that $s_\ell \rightharpoonup_{h} s_s$, let $\cfgnt{l}_\ell = \cfgnt{L}_\ell(\cfgnt{r})$, and let $\cfgnt{l}_s = h(\cfgnt{l}_\ell) $
+%
+%Case 1: Suppose $\cfgnt{R}_\ell(\cfgnt{l}_\ell) \neq \bot$.
+In this case, because $s_\ell \rightharpoonup_{h} s_s$, we know that $\cfgnt{R}_s(\cfgnt{l}_s) \neq \bot$.
+This means that in the Summarize rule, $\cfgnt{l}_s \notin \Lambda$, and therefore, $\cfgnt{R}_s(\cfgnt{l}_s) = \cfgnt{R}_{s^*}(\cfgnt{l}_s) $.
 By extension,
-
-Case 2: Suppose the field is uninitialized, and the "new" rule gets executed. We add a new location, so this case is represented.
-
-Case 3: Suppose the field is uninitialized, and the "null" rule gets executed. We add a link to the null location, so this case is represented.
-
-Case 4: Suppose the field is uninitialized, and the "alias" rule gets executed.
+%
+%Case 2: Suppose the field is uninitialized, and the "new" rule gets executed. We add a new location, so this case is represented.
+%
+%Case 3: Suppose the field is uninitialized, and the "null" rule gets executed. We add a link to the null location, so this case is represented.
+%
+%Case 4: Suppose the field is uninitialized, and the "alias" rule gets executed.
 We add links to all possible aliases, so this case is also represented.
 In fact, we add more links than we really need, but the extra ones are infeasible for the case in question so it's not a problem.
-
-%for the next case, we need to show that the constraints in the symbolic heap don't allow any infeasible heaps.
+%
+%%for the next case, we need to show that the constraints in the symbolic heap don't allow any infeasible heaps.
 The key to this will be in showing that the constraints are mutually exclusive and collectively exhaustive.
@@
 Or, we might do this on a case-by-case basis to show that for an arbitrary lazy state, any of it's three possible target states is in the feasible set.
-
-Having demonstrated each of these four cases, we now know that 
-$$s_\ell^* \in \{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \} \Rightarrow  s_\ell^* \sqsubset s_s^*$$
+%
+%Having demonstrated each of these four cases, we now know that 
+%$$s_\ell^* \in \{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \} \Rightarrow  s_\ell^* \sqsubset s_s^*$$
 

### 2014-08-20 tex/proofs.tex
Finished a rough version of the summary machine proof.

@@
 
-Class 1: $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f}) = \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_s,  \cfgnt{f}) = \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$.
+Class 1: $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f} ) = \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f} )$ and $\cfgnt{R}_{s} ( l_s,  \cfgnt{f} ) = \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$.
 In this case, let $h^\prime(l_\ell) = h(l_\ell)$.
 Since $s_\ell \rightharpoonup_h s_s$, obviously:
-$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$$.
-Furthermore, since $\mathbb{HC}()$
+$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$$
 
@@
 Since $(\phi_a\ \bot) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f ))$, and since by rule $ (\phi_b\ \bot)\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$, we can see that in this case:
-$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$$.
-STILL NEED TO SHOW WHAT HAPPENS WITH THE CONSTRAINTS.
+$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$$
 
 Class 3: $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f}) \neq \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_s,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$.
+In this case, let $l_\alpha$ be any location such that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) $.
+If $\lp *\ l_\alpha \rp \in \cfgnt{L}_{\ell}^\rightarrow $, let $h^\prime(l_\alpha) = h(l_\alpha)$.
+Otherwise, let $l_\beta$ be the location such that $(\phi_b\ \cfgnt{l}_\beta) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f )) $ and $(\phi_b\ \cfgnt{l}_\beta) \notin \cfgnt{L}_{s}(\cfgnt{R}_{s} (\cfgnt{l}_s,f )) $.
+Now, let $h^\prime(l_\alpha) = l_\beta$.
+Observe that either way,
+$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$$
 
-Since for all possible $l_\ell$ there exists an $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ such that 
-$$ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f )) $$ we know that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$.
-Furthermore, since the heap constraint is satisfiable, we know that $s_\ell^\prime \sqsubset s_s^\prime $.
+Furthemore, since $l_\alpha$ and $l_\beta$ are new locations with uninitialized fields, we know that for any field $f^\prime$, $\{(\phi_p\ \bot)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\alpha,f^\prime ))$ and $ \{(\phi_p\ \bot)\} = \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\beta,f^\prime ))$ therefore, we know that:
+$$(\phi_p\ \cfgnt{l}_x) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\alpha,f^\prime )) \Rightarrow (\phi_q\ h^\prime (\cfgnt{l}_x))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} ( h^\prime(\cfgnt{l}_\alpha),f ))$$
+
+We have now shown that there exists a mapping $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ for all $\cfgnt{l}_{\ell^\prime} \in \cfgnt{L}_{\ell^\prime}^\rightarrow$ such that:
+$$ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_{\ell^\prime},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_{\ell^\prime},f )) $$.
+By Definition \ref{def:homomorphism} we know that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$.
+Furthermore, since the heap constraint is satisfiable (hands waving here), we know that $s_\ell^\prime \sqsubset s_s^\prime $.
 We have therefore shown that for some summary state $s_s$ and an arbitrary lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$ :

### 2014-08-21 tex/definitions.tex
Added more to the summary machine proof
Fixed some typos.

@@
 \begin{definition}
+\label{def:homomorphism}
 A \textbf{homomorphism} $s_x \rightharpoonup_{h} s_y$, from state $s_x = ( \cfgnt{L}_x\ \cfgnt{R}_x\ \phi_x\ \eta_x\ \cfgnt{e}_x\ \cfgnt{k}_x )$ to state $s_y = ( \cfgnt{L}_y\ \cfgnt{R}_y\ \phi_y\ \eta_y\ \cfgnt{e}_y\ \cfgnt{k}_y )$, is defined as follows:
@@
  s_x \rightharpoonup_{h} s_y \Leftrightarrow \\
-\ \ \ \ \ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha \in \mathcal{L}\ (\forall \cfgnt{l}_\beta \in \mathcal{L}\ ( \\ 
+\ \ \ \ \ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha \in \mathcal{L}\ (\forall \cfgnt{l}_\beta \in \mathcal{L}\ ( \forall f \in \mathcal{F}( \\ 
 \ \ \ \ \ \ \ \ \ \ \ \ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_x(\cfgnt{R}_x (\cfgnt{l}_\beta,f )) \Rightarrow (\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_y(\cfgnt{R}_y (h(\cfgnt{l}_\beta),f ))\ \\
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  )) ) 
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  )) ) )
 \end{array}
@@
 \mathbb{HC}(s_x \rightharpoonup_{h} s_y) &= \\
- \bigwedge \{ \phi_b\ | \exists r \in \cfgnt{L}_x^\leftarrow\ &(\exists (\phi_a\ l) \in \cfgnt{L}_x^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_y (g(r)))) 
+ \bigwedge \{ \phi_b\ | \exists r \in \cfgnt{L}_y^\leftarrow\ &(\exists (\phi_a\ l) \in \cfgnt{L}_x^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_y (r))) 
 \end{align*}

### 2014-08-21 tex/proofs.tex
Fixed some typos.

@@
 
+%there is a flaw in the following argument: we claim that "every reference points to the right place at the right time" However, this statement is misleading.
+The truth is that the way we've defined representation, we can only guarantee that every reference points to the right place at some right time, not every right time like we imply here.
+The rest of the argument falls apart unless we can first prove that every reference points to the right place at every right time.
+So, instead of saying A points to B some time when condition X is true, we need to say that A points to B every time condition X is true.
+In other words, that condition X implies A points to B.
+This is easy to prove if we don't introduce new variables into the Heap Condition.
+However, in this case we certainly do introduce a new variable: it's the new reference that we put into the empty field.
 We now prove the reverse case, that $s_s^*$ represents no infeasible states.
@@
 Thus, if there is a problem with a reference, it must be with one of the new references we created.
-Since we have already proved that every reference points to the right place at the right time, there must be some field that points to the wrong place at the wrong time.
+Since we have already proved that every reference points to the right place at the right time (WARNING: though the preceding statement may be true, we haven't actually proved it yet.
+See the above comment), there must be some field that points to the wrong place at the wrong time.
 Since we know that every field points to the right place at the right time, and since we know that the constraints are mutually exclusive, we know that the "wrong time" can never be at the same time as the "right time".
@@
 $$s_s^*  \cong \{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$$
+
+%okay, here is another crack at proving soundness
+So, suppose that $s_s^\prime$ represents some infeasible state. Since the path condition is unaltered,
 

### 2014-08-22 tex/lazy.tex
Renamed and Organized

@@
-\begin{figure*}[t]
-\begin{center}
-\mprset{flushleft}
-\begin{mathpar}
-	\inferrule[Field Access]{
-      \{\lp\phi\ l\rp\} = \cfgnt{L}\lp\cfgnt{r}\rp\\
-      l \neq \cfgnt{l}_\mathit{null}\\\\
-      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \cfgnt{r}\ \cfgnt{f}\rp \rightarrow^*_I 
-      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi_g^\prime\ \cfgnt{r}\ \cfgnt{f} \rp \\\\ 
-      \{\lp\phi^\prime\ l^\prime\rp\} = \cfgnt{L}^\prime\lp\cfgnt{R}^\prime\lp l,\cfgnt{f}\rp\rp \\
-      \mathrm{fresh}_r\lp\rp  = \cfgnt{r}^\prime \\
-    }{
-      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp  \rightarrow \\\\
-      \lp \cfgnt{L}^\prime[\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}^\prime\ \phi_g^\prime\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp 
-	}
-\and
-	\inferrule[Field Write]{
-      \cfgnt{r}_x = \eta\lp \cfgnt{x}\rp\\ 
-      \{\lp\phi\ l\rp\} = \cfgnt{L}\lp\cfgnt{r}_x\rp \\
-      l \neq \cfgnt{l}_\mathit{null}\\\\
-      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \cfgnt{r}_x\ \cfgnt{f}\rp \rightarrow^*_I 
-      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi_g^\prime\ \cfgnt{r}_x\ \cfgnt{f} \rp \\\\ 
-      \mathrm{fresh}_r\lp\rp = \cfgnt{r}^\prime\\
-      \theta =  \cfgnt{L}^\prime\lp\cfgnt{r}\rp 
-    }{
-      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp  \rightarrow \\\\
-      \lp \cfgnt{L}^\prime[\cfgnt{r}^{\prime} \mapsto \theta]\ \cfgnt{R}^\prime[\lp l\ \cfgnt{f}\rp  \mapsto \cfgnt{r}^\prime]\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp 
-	}	
-\and
-    \inferrule[Equals (reference-true)]{
-    \cfgnt{L}\lp \cfgnt{r}_0\rp = \cfgnt{L}\lp \cfgnt{r}_1\rp\\
-    \phi_g^\prime = \lp\phi_g \wedge r_0 = r_1\rp
-    }{
-    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\ \cfgt{=}\ \cfgt{*} \rightarrow \cfgnt{k}\rp \rp  \rightarrow \\\\
-    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp 
-    }
-\and
-    \inferrule[Equals (reference-false)]{
-    \cfgnt{L}\lp \cfgnt{r}_0\rp \neq \cfgnt{L}\lp \cfgnt{r}_1\rp\\
-    \phi_g^\prime = \lp\phi_g \wedge r_0 \neq r_1\rp
-   }{
-    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\ \cfgt{=}\ \cfgt{*} \rightarrow \cfgnt{k}\rp \rp  \rightarrow \\\\
-    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp 
-    }
-\end{mathpar}
-\end{center}
-\caption{Generalized symbolic execution with lazy initialization.}
-\label{fig:lazy}
-\end{figure*}
+\section{Generalized Symbolic Execution with Lazy Initialization}
+
+The function $\mathbb{VS}(L,R,\phi_g,r,f)$ constructs the value-set given a
+heap, reference, and desired field:
+\[
+\begin{array}{rcl}
+  \mathbb{VS}(L,R,\phi_g,r,f) & = & \{(\phi\wedge\phi^\prime\ l^\prime) \mid \\
+  & & \ \ \ \ \exists l\ ((l\ \phi) \in L(r)\ \wedge \\
+  & & \ \ \ \ \ \ \ \ \exists r^\prime \in R(l,f) ( \\
+  & & \ \ \ \ \ \ \ \ \ \ \ \ (l^\prime\ \phi^\prime) \in L(r^\prime)\ \wedge\\
+  & & \ \ \ \ \ \ \ \ \ \ \ \ \mathbb{S}(\phi\wedge\phi^\prime\wedge \phi_g)))\}
+\end{array}
+\]
+where $\mathbb{S}(\phi)$ returns true if $\phi$ is satisfiable.
+
+The strengthen function $\mathbb{ST}(L,r,\phi^\prime)$ strengthens every
+constraint from the reference $r$ with $\phi^\prime$ and keeps only location-constraint
+pairs that are satisfiable after this strengthening:
+\[
+\begin{array}{rcl} 
+\mathbb{ST}(L,r,\phi) & = & \{ (\phi\wedge\phi^\prime\ l) \mid 
+(\phi^\prime\ l)\in L(r)\wedge\mathbb{S}(\phi\wedge\phi^\prime\wedge\phi_g) \}
+\end{array}
+\]
+
+\input{initialize-lazy}
+\input{lazy-fig}
+
+\begin{comment}
+NOT SURE THIS NEEDS TO BE HERE ANYMORE
+Generalized symbolic execution with lazy initialization is a technique
+to apply symbolic execution to non-primitive data types (i.e.,
+objects) \cite{GSE03}. The approach initializes each symbolic object
+to be either null, a new instance of the object, or an alias to an
+object previously created as part of lazy initialization. Each of
+these outcomes is a possible choice, and a model checker is able to
+exhaustively enumerates these choices effectively creating all
+possible concrete heaps under the choice sets. The approach is first
+formalized in this section and then extended to describe the precise
+heap summaries.
+
+Many of these concrete
+heaps explore redundant control flow paths in the program under test,
+but since symbolic model checking is stateless, subject to a bound to
+terminate the search, the model checker needlessly explores many
+redundant state leading to severe state explosion.
+
+A reference is a node that gathers the possible store locations for an
+object during symbolic execution. Each store location is guarded by a
+constraint that sets the conditions under which the edge is valid. Intuitively, the
+reference is a level of indirection between a variable and the store,
+and the reference is used to group a set of possible store locations
+each predicated on the possible aliasing in the associated constraint.
+For a variable (or field) to access any particular store location
+associated with its reference, the corresponding constraint must be
+satisfied.
+
+Locations are boxes in the graphical representation and indicated with
+the letter $l$ in the math. References are circles in the graphical
+representation and indicated with the letter $\cfgnt{r}$ in the
+math. The special symbol $\bot$ is an uninitialized reference. Edges
+from locations are labeled with field names $\cfgnt{f}$. Edges from
+the references are labeled with constraints $\phi \in \Phi$ (it is
+assumed that $\Phi$ is a power set over individual constraints and
+$\phi$ is a set of constraints for the edge).
+\end{comment}

### 2014-08-22 tex/javalite.tex
Added new files

\section{Javalite}
\figref{fig:surface-syntax} defines the surface syntax for the
Javalite language \cite{saints-MS}. \figref{fig:machine-syntax} is the
machine syntax. Javalite is syntactic machine defined as rewrites on a
string. The semantics use a CEKS model with a (C)ontrol string
representing the expression being evaluated, an (E)nvironment for
local variables, a (K)ontinuation for what is to be executed next, and
a (S)tore for the heap.

\input{surface-syntax}
\input{machine-syntax}

The environment, $\eta$, associates a variable $\cfgnt{x}$ with a
value $\cfgnt{v}$. The value can be a reference, $\cfgnt{r}$ or one of
the special values $\cfgt{null}$, $\cfgt{true}$, or
$\cfgt{false}$. Although the Javalite machine is purely syntactic, for
clarity and brevity in the presentation, the more complex structures
such as the environment are treated as partial functions. As such,
$\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference mapped to the variable
in the environment. The notation $\eta^\prime = \eta[\cfgnt{x} \mapsto
  \cfgnt{v}]$ defines a new partial function $\eta^\prime$ that is
just like $\eta$ only the variable $\cfgnt{x}$ now maps to
$\cfgnt{v}$.

The heap is a labeled bipartite graph consisting of references,
$\cfgnt{r}$, and locations, $\cfgnt{l}$. The machine syntax in
\figref{fig:machine-syntax} defines that graph in $\cfgnt{L}$, the
location map, and $\cfgnt{R}$, the reference map. As done with the
environment, $\cfgnt{L}$ and $\cfgnt{R}$ are treated as partial
functions where $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the set
of location-constraint pairs in the heap associated with the given
reference, and$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the
reference associated with the given location-field pair in the
heap.

As the updates to $\cfgnt{L}$ and $\cfgnt{R}$ are complex in the
machine semantics, predicate calculus is used to describe updates to
the functions. Consider the following example where $\cfgnt{l}$ is
some location and$\rho$ is a set of references.
\[
\cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}][\forall \cfgnt{r}^\prime \in \rho\ \lp \cfgnt{r}^\prime \mapsto \lp \cfgt{true}\ l_\mathit{null}\rp \rp ]
\]
The new function $\cfgnt{L}^\prime$ is just like $\cfgnt{L}$ only it
remaps $\cfgnt{r}$, and it remaps all the references in $\rho$.

The location $\cfgnt{l}_\mathit{null}$ is a special location in the
heap to represent null. It has a companion reference
$\cfgnt{r}_\mathit{null}$. The initial heap for the machine is defined such that $\cfgnt{L}(\cfgnt{r}_\mathit{null}) = \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})}$

$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the
reference associated with the given location-field pair in the heap,
and $\cfgnt{L}(r) = \{(\cfgnt{l}\ \phi)\ ...\}$

\input{javalite-common}

The rewrite rules defining the semantics update those functions with the following notation:

The rewrite rules that define the Javalite semantics are in
\figref{fig:general}.

### 2014-08-22 tex/javalite.tex
Defined the UN function

@@
 \]
-The new function $\cfgnt{L}^\prime$ is just like $\cfgnt{L}$ only it
+The new partial function $\cfgnt{L}^\prime$ is just like $\cfgnt{L}$ only it
 remaps $\cfgnt{r}$, and it remaps all the references in $\rho$.
 
-The location $\cfgnt{l}_\mathit{null}$ is a special location in the
-heap to represent null. It has a companion reference
-$\cfgnt{r}_\mathit{null}$. The initial heap for the machine is defined such that $\cfgnt{L}(\cfgnt{r}_\mathit{null}) = \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})}$
+The location $\cfgnt{l}_\mathit{null}$ is a special location in the heap
+to represent null. It has a companion reference
+$\cfgnt{r}_\mathit{null}$. The initial heap for the machine is defined
+such that $\cfgnt{L}(\cfgnt{r}_\mathit{null}) = \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$
 
-$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the
-reference associated with the given location-field pair in the heap,
-and $\cfgnt{L}(r) = \{(\cfgnt{l}\ \phi)\ ...\}$
+The initial state of the machine needs to be defined.
 
@@
 
-The rewrite rules defining the semantics update those functions with the following notation:
-
 The rewrite rules that define the Javalite semantics are in
-\figref{fig:general}.
+\figref{fig:javalite-common}.

### 2014-08-22 tex/lazy.tex
Defined the UN function

@@
-\section{Generalized Symbolic Execution with Lazy Initialization}
+\section{GSE with Lazy Initialization}
 
-The function $\mathbb{VS}(L,R,\phi_g,r,f)$ constructs the value-set given a
-heap, reference, and desired field:
+A special reference, $\cfgnt{r}_\mathit{un}$, and location,
+$\cfgnt{l}_\mathit{un}$, is introduced to support lazy initialization
+in GSE. The '$\mathit{un}$' is to indicate the reference or location
+is uninitialized at the point of execution. The initial state of the
+machine maps $\cfgnt{r}_\mathit{null}$ as before and adds
+$\cfgnt{L}(\cfgnt{r}_\mathit{un}) = \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$
+
+A field in an object is symbolic, meaning it is uninitialized, if the
+location for the field is $\cfgnt{l}_\mathit{un}$ on some constraint. The function
+$\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) =
+\{\cfgnt{l}\ ...\}$ returns locations in which the field $\cfgnt{f}$
+is uninitialized:
 \[
 \begin{array}{rcl}
-  \mathbb{VS}(L,R,\phi_g,r,f) & = & \{(\phi\wedge\phi^\prime\ l^\prime) \mid \\
-  & & \ \ \ \ \exists l\ ((l\ \phi) \in L(r)\ \wedge \\
-  & & \ \ \ \ \ \ \ \ \exists r^\prime \in R(l,f) ( \\
-  & & \ \ \ \ \ \ \ \ \ \ \ \ (l^\prime\ \phi^\prime) \in L(r^\prime)\ \wedge\\
-  & & \ \ \ \ \ \ \ \ \ \ \ \ \mathbb{S}(\phi\wedge\phi^\prime\wedge \phi_g)))\}
+\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ l \mid \exists \phi\ \lp \lp \phi\ l\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \\
+& & \ \ \ \ \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \\
+& & \ \ \ \ \ \ \ \ \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\rp\}\\
 \end{array}
 \]
-where $\mathbb{S}(\phi)$ returns true if $\phi$ is satisfiable.
-
-The strengthen function $\mathbb{ST}(L,r,\phi^\prime)$ strengthens every
-constraint from the reference $r$ with $\phi^\prime$ and keeps only location-constraint
-pairs that are satisfiable after this strengthening:
-\[
-\begin{array}{rcl} 
-\mathbb{ST}(L,r,\phi) & = & \{ (\phi\wedge\phi^\prime\ l) \mid 
-(\phi^\prime\ l)\in L(r)\wedge\mathbb{S}(\phi\wedge\phi^\prime\wedge\phi_g) \}
-\end{array}
-\]
+where $\mathbb{S}(\phi)$ returns true if $\phi$ is satisfiable. The
+cardinality of the set is never greater than one in GSE and the
+constraint is always satisfiable because all constraints are
+constant. This property is relaxed in GSE with heap summaries.
 

### 2014-08-22 tex/precise.tex
Minor changes
Defined syntax for constraints
Added new files
Defined the UN function

@@
-\begin{figure*}[t]
-\begin{center}
-\mprset{flushleft}
-\begin{mathpar}
-	\inferrule[Field Access]{
-      \forall \lp \phi\ l\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp \ \lp l = l_{\mathit{null}} \rightarrow \neg \mathbb{S}\lp \phi \wedge \phi_g\rp \rp  \\\\
-      \lp \cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\rp \rightarrow^*_S \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \cfgnt{r}\ \cfgnt{f}\rp \\
-      \cfgnt{r}^\prime = \mathrm{fresh}_r\lp \rp
-    }{
-      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp  \rightarrow 
-      \lp \cfgnt{L}^\prime[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}^\prime,\cfgnt{R}^\prime,\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}^\prime\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp 
-	}
-\and
-	\inferrule[Field Write]{
-	\cfgnt{r}_x = \eta\lp \cfgnt{x}\rp \\
-\forall \lp \phi\ l\rp  \in \cfgnt{L}\lp \cfgnt{r}_x\rp \ \lp l = l_{\mathit{null}} \rightarrow \neg \mathbb{S}\lp \phi \wedge \phi_g\rp \rp  \\\\
-      \lp \cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}_x\ \cfgnt{f}\rp \rightarrow^*_S \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \cfgnt{r}_x\ \cfgnt{f}\rp \\\\
-      \Psi_x =\{\lp \cfgnt{r}_\mathit{old}\ \phi\ l\rp  \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}^\prime\lp \cfgnt{r}_x\rp  \wedge \cfgnt{r}_\mathit{old} \in \cfgnt{R}\lp l,\cfgnt{f}\rp  \}\\\\
-      X = \{ \lp \cfgnt{r}_\mathit{old}\ \theta\ l\rp  \mid \exists \phi\ \lp \lp \cfgnt{r}_\mathit{old}\ \phi\ l\rp \in \Psi_x \wedge \theta = \mathbb{ST}\lp \cfgnt{L}^\prime,\cfgnt{r},\phi\rp  \cup \mathbb{ST}\lp \cfgnt{L}^\prime,\cfgnt{r}_\mathit{old},\neg\phi\rp \rp  \}\\\\
-      \cfgnt{R}^{\prime\prime} = \cfgnt{R}^\prime[\forall \lp \cfgnt{r}_\mathit{old}\ \theta\ l\rp  \in X\ \lp \lp l\ \cfgnt{f}\rp  \mapsto \mathrm{fresh}_r\lp \rp \rp ]\\\\
-      \cfgnt{L}^{\prime\prime} = \cfgnt{L}^\prime[\forall \lp \cfgnt{r}_\mathit{old}\ \theta\ l\rp  \in X\ \lp \exists \cfgnt{r}^{\prime}\ \lp \cfgnt{r}^\prime = \cfgnt{R}^\prime\lp l,\cfgnt{f}\rp \wedge \lp\cfgnt{r}^{\prime} \mapsto \theta\rp  \rp \rp ]
-    }{
-      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp  \rightarrow 
-      \lp \cfgnt{L}^{\prime\prime} \cfgnt{R}^{\prime\prime}\ \phi_g\ \eta\ \cfgnt{k}\rp 
-	}	
-\and
-    \inferrule[Equals (references-true)]{
-    \theta_\alpha = \{\phi_0 \wedge \phi_1 \mid \exists l\ \lp \lp \phi_0\ l\rp  \in \cfgnt{L}\lp \cfgnt{r}_0\rp  \wedge \lp \phi_1\ l\rp  \in \cfgnt{L}\lp \cfgnt{r}_1\rp \rp \} \\\\
-    \theta_0 = \{\phi_0 \mid \exists l_0\ \lp \lp \phi_0\ l_0\rp  \in \cfgnt{L}\lp \cfgnt{r}_0\rp  \wedge \forall \lp \phi_1\ l_1\rp  \in \cfgnt{L}\lp \cfgnt{r}_1\rp \ \lp l_0 \neq l_1\rp \rp \} \\\\
-    \theta_1 = \{\phi_1 \mid \exists l_1\ \lp \lp \phi_1\ l_1\rp  \in \cfgnt{L}\lp \cfgnt{r}_1\rp  \wedge \forall \lp \phi_0\ l_0\rp  \in \cfgnt{L}\lp \cfgnt{r}_0\rp \ \lp l_0 \neq l_1\rp \rp \} \\\\
-    \phi_g^\prime =  \phi_g \wedge \lp \vee_{\phi_\alpha\in\theta_\alpha}\phi_\alpha\rp \wedge\lp \wedge_{\phi_0 \in \theta_0} \neg \phi_0\rp \wedge\lp \wedge_{\phi_1
-    \in \theta_1} \neg \phi_1\rp \\\\ \mathbb{S}(\phi_g^\prime)}{
-    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp  \rightarrow
-    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp 
-    }
-\and
-    \inferrule[Equals (references-false)]{
-    \theta_\alpha = \{\phi_0 \rightarrow \neg \phi_1 \mid \exists l\ \lp \lp \phi_0\ l\rp  \in \cfgnt{L}\lp \cfgnt{r}_0\rp  \wedge \lp \phi_1\ l\rp  \in \cfgnt{L}\lp \cfgnt{r}_1\rp \rp \} \\\\
-    \theta_0 = \{\phi_0 \mid \exists l_0\ \lp \lp \phi_0\ l_0\rp  \in \cfgnt{L}\lp \cfgnt{r}_0\rp  \wedge \forall \lp \phi_1\ l_1\rp  \in \cfgnt{L}\lp \cfgnt{r}_1\rp \ \lp l_0 \neq l_1\rp \rp \} \\\\
-    \theta_1 = \{\phi_1 \mid \exists l_1\ \lp \lp \phi_1\ l_1\rp  \in \cfgnt{L}\lp \cfgnt{r}_1\rp  \wedge \forall \lp \phi_0\ l_0\rp  \in \cfgnt{L}\lp \cfgnt{r}_0\rp \ \lp l_0 \neq l_1\rp \rp \} \\\\
-    \phi_g^\prime = \phi_g \wedge \lp \wedge_{\phi_\alpha\in\theta_\alpha}\phi_\alpha\rp \vee\lp \lp \vee_{\phi_0 \in \theta_0} \phi_0\rp   \vee\lp \vee_{\phi_1
-    \in \theta_1} \phi_1\rp \rp  \\\\ \mathbb{S}(\phi_g^\prime)}{
-    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp  \rightarrow
-    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp 
-    }
-\end{mathpar}
-\end{center}
-\caption{Precise symbolic heap summaries from symbolic execution.}
-\label{fig:sym}
-\end{figure*}
+\section{GSE with Heap Summaries}
+
+The function $\mathbb{VS}(L,R,\phi_g,r,f)$ constructs the value-set given a
+heap, reference, and desired field:
+\[
+\begin{array}{rcl}
+  \mathbb{VS}(L,R,\phi_g,r,f) & = & \{(\phi\wedge\phi^\prime\ l^\prime) \mid \\
+  & & \ \ \ \ \exists l\ ((l\ \phi) \in L(r)\ \wedge \\
+  & & \ \ \ \ \ \ \ \ \exists r^\prime \in R(l,f) ( \\
+  & & \ \ \ \ \ \ \ \ \ \ \ \ (l^\prime\ \phi^\prime) \in L(r^\prime)\ \wedge\\
+  & & \ \ \ \ \ \ \ \ \ \ \ \ \mathbb{S}(\phi\wedge\phi^\prime\wedge \phi_g)))\}
+\end{array}
+\]
+where $\mathbb{S}(\phi)$ returns true if $\phi$ is satisfiable.
+
+The strengthen function $\mathbb{ST}(L,r,\phi^\prime)$ strengthens every
+constraint from the reference $r$ with $\phi^\prime$ and keeps only location-constraint
+pairs that are satisfiable after this strengthening:
+\[
+\begin{array}{rcl} 
+\mathbb{ST}(L,r,\phi) & = & \{ (\phi\wedge\phi^\prime\ l) \mid 
+(\phi^\prime\ l)\in L(r)\wedge\mathbb{S}(\phi\wedge\phi^\prime\wedge\phi_g) \}
+\end{array}
+\]
+
+\input{summarize-precise}
+\input{precise-fig}

### 2014-08-25 tex/definitions.tex
Added definitons for different reference classes. Started field write and exactness proofs.

@@
 The set of \textbf{initial states} $\mathcal{S}_0$ is defined as
+\end{definition}
+
+\begin{definition}
+The set of \textbf{references} $\mathcal{R}$ is defined as the set of natural numbers
+ $$\mathcal{R} = \mathbb{N}$$
+\end{definition}
+
+The total number of references in a summary state and a lazy state that it represents are generally not the same.
+However, the number of references on the stack in either state is always the same.
+In order to make the distinction between different types of references, we partition the set of natural numbers using modular arithmetic.
+
+\begin{definition}
+The set of \textbf{stack references} $\mathcal{R}_t$ is defined as
+ $$\mathcal{R}_t =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 0\}$$. 
+\end{definition}
+
+\begin{definition}
+The set of \textbf{input heap references} $\mathcal{R}_h$ is defined as
+ $$\mathcal{R}_h =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 1\}$$. 
+\end{definition}
+
+\begin{definition}
+The set of \textbf{new heap references} $\mathcal{R}_f$ is defined as
+ $$\mathcal{R}_n =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$. 
 \end{definition}
@@
 \begin{definition}
-A \textbf{state sequence} is as a sequence of states denoted as $\Pi_n = s_0,s_1,...,s_n$.
+A \textbf{state sequence} is a sequence of states denoted as $\Pi_n = s_0,s_1,...,s_n$.
 A \textbf{feasible state sequence}, $\Pi_n^\phi = s_0,s_1,...,s_n$ is consistent with the transition: $\forall i\ (0 \leq i < n \Rightarrow s_i \rightarrow_{\Phi} s_{i+1})$, where $s_0\in \mathcal{S}_0$.

### 2014-08-25 tex/proofs.tex
Added definitons for different reference classes. Started field write and exactness proofs.

--- 2014-08-20 tex/proofs.tex
@@
 
+%I'm wondering... do we use this theorem anywhere? I think the place we needed it got re-structured, am I right?
 \begin{theorem}
@@
 \begin{proof}
-For now, the proof is left as an exercise to the reader.
+The proof will proceed inductively.
+
+Base Case: In the initial state $s_0$ there is only one location, and all of it's fields are initialized to contain the uninitiated reference $\cfgnt{r}_{un}$.
+Since the only reference is the uninitialized reference, for which the desired property holds by construction, the property is true for all references on the heap.
+
+Inductive Step: 
+Suppose we have a summary state $s_s$ for which the property holds, and some state $s_s^\prime$ such that $s_s \rightarrow_S s_s^\prime$.
+If all relevant fields are initialized, then $s_s = s_s^\prime$, and the property holds trivially.
+If there is some uninitialized fields, then on of those fields will have a new reference $\cfgnt{r}_{new}$ added to it.
+The disjunction
+$$ \bigvee \{ \phi \mid (\phi\ \cfgnt{l})\in \cfgnt{L}_s (\cfgnt{r}_{new})\}$$
+Takes the form
+\begin{align*}
+ (\phi_0) \vee (\neg \phi_0 \wedge \phi_1) \vee (\neg \phi_0 \wedge \neg \phi_1 \wedge \phi_2) \vee ...\\
+ ... \vee (\neg \phi_0 \wedge \neg \phi_1 \wedge ... \wedge \phi_n) \vee (\neg \phi_0 \wedge \neg \phi_1 \wedge ... \wedge \neg \phi_n)
+ \end{align*}
+ Which reduces to $\cfgt{true}$.
+Thus, the collective exhaustion property holds for intermediate states.
+Because the property holds for intermediate states, for summary machine rules we will assume without loss of generality that all relevant fields are initialized.
+ Suppose that the rule executed in the transition from $s_s$ to $s_s^\prime$ is the field read rule. 
+Suppose we have a state $s_s$ for which the property holds, and some state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$.
+
 \end{proof}
@@
 \label{lem:init}
-If symbolic state $s_s = \lp \cfgnt{L}_s\ \cfgnt{R}_{s}\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the intermediate state state $s_s^*$ such that $s_s \rightarrow_S^* s_s^*$ is equivalent to $\{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$.
+If symbolic state $s_s = \lp \cfgnt{L}_s\ \cfgnt{R}_{s}\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the intermediate state state $s_s^\prime$ such that $s_s \rightarrow_S^* s_s^\prime$ is equivalent to $\{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$.
 \end{lemma}
@@
 
-We now prove the reverse case, that $s_s^*$ represents no infeasible states.
+%Comment:
+% there is a flaw in the following argument: we claim that "every reference points to the right place at the right time" However, this statement is misleading.
+The truth is that the way we've defined representation, we can only guarantee that every reference points to the right place at some right time, not every right time like we imply here.
+The rest of the argument falls apart unless we can first prove that every reference points to the right place at every right time.
+So, instead of saying A points to B some time when condition X is true, we need to say that A points to B every time condition X is true.
+In other words, that condition X implies A points to B.
+This is easy to prove if we don't introduce new variables into the Heap Condition.
+However, in this case we certainly do introduce a new variable: it's the new reference that we put into the empty field.
+%Flawed argument:
+%We now prove the reverse case, that $s_s^*$ represents no infeasible states.
 We modified no references from the previous heap, and did not alter the global invariant.
@@
 Thus, if there is a problem with a reference, it must be with one of the new references we created.
-Since we have already proved that every reference points to the right place at the right time, there must be some field that points to the wrong place at the wrong time.
+Since we have already proved that every reference points to the right place at the right time (WARNING: though the preceding statement may be true, we haven't actually proved it yet.
+See the above comment), there must be some field that points to the wrong place at the wrong time.
 Since we know that every field points to the right place at the right time, and since we know that the constraints are mutually exclusive, we know that the "wrong time" can never be at the same time as the "right time".
 Since the right time is every time due to Theorem \ref{thm:colex}, this implies that the wrong time is no time.
+
+%okay, here is another crack at proving soundness
+We now prove the reverse case, that $s_s^*$ represents no infeasible states.
+Suppose that $s_s^\prime$ represents some infeasible state.
+This means that we represent some lazy state that has some reference r which points somewhere that no place in the feasible set points to.
+Since we don't change the path condition, all the old references still point exactly to the same places they used to.
+So, the problem must be with one of the new references.
+All of the new references point to either a new location, the null location, the uninitialized location, or some alias.
+The new, null, and uninitialized locations are pretty straightforward and easy to show that they are all pointing to the correct places at the correct times.
+This means that there must be a feasible path to a target location that does not exist for any lazy heap.
+So, pick an arbitrary lazy heap containing the location and field in question.
+If said target location does not exist, then there is no reference in the lazy heap pointing to that location.
+In the summary heap, the path constraint on the path leading to the undesired target contains an aliasing condition that states that the source reference only points to this target location on condition that the parent reference points there.
+However, since we already know that no other reference in the lazy heap points there, this condition must be infeasible.
+Therefore, it is not part of the represented state.
+We have a contradiction.
+Therefore, there is no alias that points somewhere it's not supposed to.
+
 We have now proven that 
@@
 \begin{lemma}
-The field write rule is correct.
+\label{lem:write}
+If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then $s_s^\prime$ is equal to $ \lp \cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \eta\ \cfgnt{k}\rp$ and is exact with respect to $s_0$ and $\pi_n \ (\eta\ \cfgnt{k}\ \emptyset)$.
+
 \end{lemma}
 \begin{proof}
+By Lemma \ref{lem:init} we know that if $s_s$ is exact, then the intermediate state $s_x$ such that $s_s \rightarrow_S^* s_x$ is also exact.
+Thus, for $s_s$ and any state  $s_i$ such that $s_i \sqsubset s_s$ we will assume, without loss of generality, that all relevant fields have been initialized.
+
+First, we show that every state in the feasible set is represented by the $s_s^\prime$.
+Take some lazy state $s_i$ such that $s_i \sqsubset s_s$.
+It is easy to see that $s_i^\prime$ is represented by $s_s^\prime$.
+
+Next, we show that every state represented by $s_s^\prime$ is in the feasible set.
+We use the same argument as in the field read proof, that because $s_s^\prime$ represents every state in the feasible set, and since the cardinality of the set of states represented by $s_s^\prime$ is less than or equal to the cardinality of the feasible set, that $s_s^\prime$ can only represent feasible states.
+
 \end{proof}
@@
 \begin{lemma}
-If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then any state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$ is equal to $ \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_{s^\prime}\ \eta\ \cfgnt{v}_{s^\prime}\ \cfgnt{k}\rp$ and is exact with respect to $s_0$ and $\pi_n \ (\eta\ \cfgnt{v}_{s^\prime}\ \cfgnt{k})$.
+\label{lem:compare}
+If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then $s_s^\prime$ is equal to $ \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_{s^\prime}\ \eta\ \cfgnt{v}_{s^\prime}\ \cfgnt{k}\rp$ and is exact with respect to $s_0$ and $\pi_n \ (\eta\ \cfgnt{v}_{s^\prime}\ \cfgnt{k})$.
 \end{lemma}
@@
 \begin{theorem}
-Every symbolic state on every execution path is exact.
+If we have some initial state $s_0$, and we apply the summary state transition function n times in order to get a sequence of summary states $\Pi_n^s$, then the following statement is true:
+\begin{equation}
+\mathit{last}(\Pi_n^s) \cong \mathbb{FS}(\rightarrow_\ell, s_0, \mathbb{CF}(\Pi_n^s) )
+\end{equation}
 \end{theorem}
 \begin{proof}
-Combine all of the production-rule lemmas to inductively prove the theorem.
+The proof will proceed inductively.
+
+Base case: The initial state is exact. (hands waving)
+
+Inductive step: If summary state $s_s$ is exact, then any state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$ is also exact.
+Suppose $s_s$ has the form for a field read, field write, or reference compare rule.
+By Lemmas \ref{lem:access}, \ref{lem:write}, and \ref{lem:compare}, $s_s^\prime$ will also be exact.
+
 \end{proof}

### 2014-08-25 tex/proofs.tex
Fixed some typos in the rules, added additional condition summarization semantics to the summarize rule

@@
 
+\begin{comment}
 %I'm wondering... do we use this theorem anywhere? I think the place we needed it got re-structured, am I right?
@@
 \end{proof}
+\end{comment}
 %\begin{lemma}
@@
 \begin{theorem}
-If we have some initial state $s_0$, and we apply the summary state transition function n times in order to get a sequence of summary states $\Pi_n^s$, then the following statement is true:
+If $\Pi_n^s$ is a feasible summary state sequence, then the final state in $\Pi_n^s$ is equivalent to the feasible set of lazy states sharing the same control flow sequence:
 \begin{equation}
-\mathit{last}(\Pi_n^s) \cong \mathbb{FS}(\rightarrow_\ell, s_0, \mathbb{CF}(\Pi_n^s) )
+\mathit{last}(\Pi_n^s) \cong \mathbb{FS}(\rightarrow_\ell, \mathit{first}(\Pi_n^s), \mathbb{CF}(\Pi_n^s) )
 \end{equation}
@@
 
-Base case: The initial state is exact. (hands waving)
+Base case: For any initial state $s_0$, the feasible state set reduces to $\{s_0\}$:
+$$\mathbb{FS}(\rightarrow_\ell, s_0, \mathbb{CF}(s_0)) = \{s_0\}$$
+It's obvious that a homomorphism from $s_0$ to $s_0$ exists, and that the Heap Constraint is always satisfiable by construction. Thus, $s_0 \in  s_0 \sqsubset s_0$.
 
 Inductive step: If summary state $s_s$ is exact, then any state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$ is also exact.
-Suppose $s_s$ has the form for a field read, field write, or reference compare rule.
+Suppose $s_s $ has the form for a field read, field write, or reference compare rule.
 By Lemmas \ref{lem:access}, \ref{lem:write}, and \ref{lem:compare}, $s_s^\prime$ will also be exact.
+Suppose $s_s$ is accepted by the "new" rule.
+In this case, the new reference points to the new location on condition true, so it's obvious that $s_s$ represents all of the proper lazy states, and the existence of any infeasible lazy states represented by $s_s^prime$ would imply that $s_s$ is not exact.
+For all the other rules, the L and R functions are unchanged, and the rules for the $\eta$, $e$, and $k$ are exactly the same between the lazy and summary machines, so there is a bijective mapping between the represented states in $s_s$ and $s_s^\prime$.
+Thus, in all cases, if $s_s$ is exact, then $s_s^\prime$ is also exact.
+
+Having proved both the base case and the inductive step, the it follows that for any $n$, $s_n$ will be exact.
 

### 2014-09-02 tex/definitions.tex
Fixed some typos in the rules, added additional condition summarization semantics to the summarize rule
Constraint mutual exclusion proof updated with details for summary machine

@@
 \begin{definition}
+\label{def:state}
 The set of \textbf{states} $\mathcal{S}$ is defined as
@@
 \begin{definition}
-The set of \textbf{initial states} $\mathcal{S}_0$ is defined as
+\label{def:initate}
+The set of \textbf{initial states} $\mathcal{S}_0$ is defined as (TBD)
 \end{definition}
@@
 
+%For these definitions, we should bring in the notion of 
 \begin{definition}
@@
 \end{align}
+\end{definition}
+
+\begin{definition}
+\label{def:interstate}
+\textbf{Intermediate states} are imaginary placeholder states used when reasoning about complex transition rules in terms of simpler sub-rules.
+For example, the transition $s_x \rightarrow_\phi s_y$ may be equivalent to a sequence of simpler transitions $s_x \rightarrow_\alpha s_a \rightarrow_\beta s_b \rightarrow_\gamma s_y$.
+When reasoning about this equivalent transition sequence, it can be useful to discuss the notional intermediate states $s_a$ and $s_b$.
+However, it is important to remember that $s_a$ and $s_b$ are not technically involved in the transition $s_x \rightarrow_\phi s_y$, and indeed may not be part of any feasible state sequence under transition relation $\rightarrow_\phi$.
 \end{definition}
@@
 
-\begin{definition}
-A \textbf{field access descriptor} $\gamma_i$ is a tuple 
-$$ \gamma_i = (\cfgnt{r}_i\ \phi_i\ \cfgnt{l}_i\ \cfgnt{f}_i)$$
-\end{definition}
-
-\begin{definition}
-An \textbf{access path} $\Gamma_n$ is a sequence of field access descriptors
-$ \Gamma_n = \gamma_0,\gamma_1,...,\gamma_n $.
-\end{definition}
-
-\begin{definition}
-For a given access path $\Gamma_n$ the \textbf{access path constraint} $\mathbb{PC}(\Gamma_n)$ is defined as
-$$\mathbb{PC}(\Gamma_n) =  \bigwedge \{\phi \mid \exists \gamma \in \Gamma_n \ (\gamma = (\cfgnt{r}\ \phi\ \cfgnt{e}\ \cfgnt{f}))\}$$  
-\end{definition}
-
-\begin{definition}
-For a given state $s= ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, a \textbf{valid access path} $\Gamma_n^s = \gamma_0,\gamma_1,...,\gamma_n$ satisfies the properties
-\begin{align*}
-\cfgnt{r}_0 &\in \mathit{refs}(\eta_s) \\
-\mathbb{S}(&\phi_s \wedge \mathbb{PC}(\Gamma_n^s)) \\
-\forall i & \in \mathbb{N}\ ( 0 \leq i < n \Leftrightarrow \gamma_i \in \Gamma_n^s\  \wedge\\
-&\ \ \ \  \gamma_{i+1} \in \Gamma_n^s\  \wedge\\
-&\ \ \ \  (\phi_i\ \cfgnt{l}_i)\in \cfgnt{L}_s(\cfgnt{r}_i)\ \wedge \\
-&\ \ \ \  \cfgnt{r}_{i+1} = \cfgnt{R}_s(\cfgnt{l}_i,\cfgnt{f}_i)\ \wedge\\
-&\ \ \ \ (\phi_{i+1}\ \cfgnt{l}_{i+1}) = \cfgnt{L}_s(\cfgnt{r}_{i+1}) )
-\end{align*}
-where $\gamma_i = (\cfgnt{r}_i\ \phi_i\ \cfgnt{l}_i\ \cfgnt{f}_i)$
-\end{definition}
+%\begin{definition}
+%A \textbf{field access descriptor} $\gamma_i$ is a tuple 
+%$$ \gamma_i = (\cfgnt{r}_i\ \phi_i\ \cfgnt{l}_i\ \cfgnt{f}_i)$$
+%\end{definition}
+%
+%\begin{definition}
+%An \textbf{access path} $\Gamma_n$ is a sequence of field access descriptors
+%$ \Gamma_n = \gamma_0,\gamma_1,...,\gamma_n $.
+%\end{definition}
+%
+%\begin{definition}
+%For a given access path $\Gamma_n$ the \textbf{access path constraint} $\mathbb{PC}(\Gamma_n)$ is defined as
+%$$\mathbb{PC}(\Gamma_n) =  \bigwedge \{\phi \mid \exists \gamma \in \Gamma_n \ (\gamma = (\cfgnt{r}\ \phi\ \cfgnt{e}\ \cfgnt{f}))\}$$  
+%\end{definition}
+%
+%\begin{definition}
+%For a given state $s= ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, a \textbf{valid access path} $\Gamma_n^s = \gamma_0,\gamma_1,...,\gamma_n$ satisfies the properties
+%\begin{align*}
+%\cfgnt{r}_0 &\in \mathit{refs}(\eta_s) \\
+%\mathbb{S}(&\phi_s \wedge \mathbb{PC}(\Gamma_n^s)) \\
+%\forall i & \in \mathbb{N}\ ( 0 \leq i < n \Leftrightarrow \gamma_i \in \Gamma_n^s\  \wedge\\
+%&\ \ \ \  \gamma_{i+1} \in \Gamma_n^s\  \wedge\\
+%&\ \ \ \  (\phi_i\ \cfgnt{l}_i)\in \cfgnt{L}_s(\cfgnt{r}_i)\ \wedge \\
+%&\ \ \ \  \cfgnt{r}_{i+1} = \cfgnt{R}_s(\cfgnt{l}_i,\cfgnt{f}_i)\ \wedge\\
+%&\ \ \ \ (\phi_{i+1}\ \cfgnt{l}_{i+1}) = \cfgnt{L}_s(\cfgnt{r}_{i+1}) )
+%\end{align*}
+%where $\gamma_i = (\cfgnt{r}_i\ \phi_i\ \cfgnt{l}_i\ \cfgnt{f}_i)$
+%\end{definition}
 
@@
  s_x \rightharpoonup_{h} s_y \Leftrightarrow \\
-\ \ \ \ \ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha \in \mathcal{L}\ (\forall \cfgnt{l}_\beta \in \mathcal{L}\ ( \forall f \in \mathcal{F}( \\ 
+\ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha \in \mathcal{L}\ (\forall \cfgnt{l}_\beta \in \mathcal{L}\ ( \forall f \in \mathcal{F}( \exists \phi_\alpha \in \Phi(\exists \phi_\beta \in \Phi( \\
 \ \ \ \ \ \ \ \ \ \ \ \ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_x(\cfgnt{R}_x (\cfgnt{l}_\beta,f )) \Rightarrow (\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_y(\cfgnt{R}_y (h(\cfgnt{l}_\beta),f ))\ \\
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  )) ) )
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  )) ) ) ) )
 \end{array}
@@
 \mathbb{HC}(s_x \rightharpoonup_{h} s_y) &= \\
- \bigwedge \{ \phi_b\ | \exists r \in \cfgnt{L}_y^\leftarrow\ &(\exists (\phi_a\ l) \in \cfgnt{L}_x^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_y (r))) 
+ \bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_x^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}^\rightarrow)\} 
 \end{align*}
@@
 A summary state $s_s$ is \textbf{equivalent} to a set of lazy states $P$ if and only if $s_s$ represents every state in $P$ and represents no other state: 
-$$s_s \cong P \Leftrightarrow \forall s_i \in \mathcal{S}\ (s_i \in P \Leftrightarrow s_i \sqsubset s_s) $$
+$$s_s \cong P \Leftrightarrow (\forall s_i \in \mathcal{S}\ (s_i \in P \Leftrightarrow s_i \sqsubset s_s) )$$
 \end{definition}
@@
 \label{sound}
-A state $s$ is \textbf{sound} with respect to a transition relation, $\rightarrow_\phi$, initial state, $s_0$, and control flow path, $\pi_n$, if and only if 
+A state $s_s$ is \textbf{sound} with respect to a transition relation, $\rightarrow_\phi$, initial state, $s_0$, and control flow path, $\pi_n$, if and only if 
 $$ \forall s_\ell \in \mathcal{S}_\ell\ (s_\ell \sqsubset s_s \Rightarrow s_\ell \in \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n) ) $$
@@
 \label{complete}
-A state $s$ is \textbf{complete} with respect to a transition relation, $\rightarrow_\phi$, initial state, $s_0$, and control flow path, $\pi_n$, if and only if 
+A state $s_s$ is \textbf{complete} with respect to a transition relation, $\rightarrow_\phi$, initial state, $s_0$, and control flow path, $\pi_n$, if and only if 
 $$ \forall s_\ell \in \mathcal{S}_\ell\ ( s_\ell \in \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)\Rightarrow s_\ell \sqsubset s_s ) $$

### 2014-09-02 tex/proofs.tex
Constraint mutual exclusion proof updated with details for summary machine

--- 2014-08-25 tex/proofs.tex
@@
 \label{thm:mutex}
-If we have a summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, and any two pairs $(\phi_\alpha\ l_\alpha) \in \cfgnt{L}_s(r)$ and $(\phi_\beta\ l_\beta) \in \cfgnt{L}_s(r)$ such that $l_\alpha \ne l_\beta$, then
+If we have a reachable summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, and any two pairs $(\phi_\alpha\ l_\alpha) \in \cfgnt{L}_s(r)$ and $(\phi_\beta\ l_\beta) \in \cfgnt{L}_s(r)$ such that $l_\alpha \ne l_\beta$, then
 $$(\phi_\alpha \wedge \phi_\beta) = \cfgt{false}$$
@@
 \begin{proof}
-The proof will proceed inductively. For the base case, consider any initial state $s_0$. The property holds by construction. (Hands waving around in the air for emphasis)
+The proof will proceed inductively.
 
-Now we will show that if the exclusivity property holds for some state $s_s$, then it holds for any state $s_s^\prime$ where $s_s \rightarrow_s s_s^\prime$.
+Base Case: Let $s_s$ be an initial state.
+By Definition \ref{def:initstate}, for every reference $r_i \in \cfgnt{L}_s^\leftarrow$, the set $\cfgnt{L}_s(r_i)$ contains at most one element.
+Thus, the requirement that $l_\alpha \ne l_\beta$ is never met, and the Theorem is vacuously true.
 
-First, suppose we have state $s_s$ and intermediate state $s_s^\prime$ where $s_s \rightarrow_S s_s^\prime$.
-If all fields are initialized, then $s_s$ and $s_s^\prime$ are identical, so the property holds for $s_s^\prime$.
-If any field is uninitialized, then the fields are initialized to new references, for which the exclusivity property holds by construction.
-(More hands waving)
+Inductive Step: Now we will show that if the exclusivity property holds for some state $s_s$, then it holds for any state $s_s^\prime$ where $s_s \rightarrow_s s_s^\prime$.
+In order to evaluate whether Theorem \ref{thm:mutex} holds for state any $s_s\prime$, we must consider the rule that applied during the transition from $s_s$ to $s_s\prime$.
+There are two broad classes of rules: rules where $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$, and rules where $ \cfgnt{L}_s =  \cfgnt{L}_{s^\prime}$.
+Rules in the $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$ class modify the structure of the heap, and must be considered carefully to to consider the impact of those modifications.
+Only three rules belong to the class $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$: Field Access, Field Read, and New.
 
-Since the exclusivity property holds for every intermediate state, for any instruction that relies on the summary machine we can assume without loss of generality that all pertinent fields are initialized.
+We begin by considering the Field Access rule.
+Suppose $s_s$ has the form $\lp \cfgnt{L}_s\ \cfgnt{R}_{s}\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.
+In this case, the relationship between $s_s$ and $s_s^\prime$ is described by the Field Access rule.
+The Field Access rule uses the Summarize rule to describe the relation between $\cfgnt{L}_{s}$ and $\cfgnt{L}_{s^\prime}$.
+Because the summarize rule is essentially a fixed-point computation, we can reason about it as a machine that produces a sequence of intermediate states $s_1, s_2, ...
+, s_n$.
+We will use an inductive argument to show that the mutual exclusion property holds for any of those intermediate states.
+First, let state $s_\alpha$ be any state for which the property in Theorem \ref{thm:mutex} holds, and let $s_\beta$ be the intermediate state where $s_\alpha \rightarrow_S s_\beta$.
+If all fields are initialized, then $s_\alpha$ and $s_\beta$ are identical, so the mutually exclusive property holds for $s_\beta$.
+Otherwise, there must be some location $\cfgnt{l}_{un} \in \cfgnt{L}_\alpha(r)$ for which field f contains a reference $r_a$ that could feasibly point to the uninitialized location.
+In this case, a new reference is created and a single entry is added to $\cfgnt{L}_\beta$.
+The elements of the set $\theta_{all} = \cfgnt{L}_\beta(\cfgnt{R}_\beta(\cfgnf{l}_{un},\cfgnt{f}))$ can be divided into four distinct subsets, $\theta_{cur}$, $\theta_{null}$, $\theta_{new}$, and $\theta_{alias}$.
+The set $\theta_{cur}$ contains the pairs containing locations from the reference $r_a$, $\theta_{null}$ contains the pair with the null location, $\theta_{new}$ contains a pair with a new location, and $\theta_{alias}$ contains pairs representing alias locations.
+Any two constraints in $\theta_{cur}$ are guaranteed to be pairwise mutually exclusive because of the inductive hypothesis, and any single constraint is guaranteed to be pairwise mutually exclusive with any constraint in $\theta_{null}$, $\theta_{new}$, or $\theta_{alias}$ because constraints in $\theta_{cur}$ contain the conjunct $\neg \phi$, while constraints in the other three sets are conjoined with $\phi$.
+The set $\theta_{null}$ contains only one element, which in turn contains the constraint $r_f = r_{null}$, which is guaranteed to be mutually exclusive with any constraint in $\theta_{new}$, or $\theta_{alias}$ because constraints in those sets contain the conjunct $r_f \neq r_{null}$.
+The set $\theta_{new}$ contains one element, which in turn contains the constraint containing the conjunct $ \wedge_{\lp \cfgnt{r}^\prime_a,\ \phi^\prime_a,\ l^\prime_a\rp  \in \rho} \cfgnt{r}_f \ne \cfgnt{r}^\prime_a$, which is guaranteed to be mutually exclusive with any constraint in $\theta_{alias}$, because each constraint in that set contains the conjunct $r_f = r_a$ for some $(r_a\ \phi_a\ l_a)\in \rho$.
+Any two elements of the set $\theta_{alias}$ are guaranteed to pairwise mutually exclusive because for each constraint that contains the conjunct $r_f = r_a$, every other constraint contains the conjunct $r_f \ne r_a$.
+Thus, all constraints from all pairs in $\theta{all}$ are guaranteed to be mutually exclusive, and the property from Theorem \ref{thm:mutex} holds for intermediate state $s_\beta$.
 
-Now, suppose we have a field read instruction.
-When we read the field, a new value set is created based on the $\mathbb{VS}$ function.
+We have now shown that whether there are any uninitialized fields or not, the mutual exclusivity property holds for any intermediate state $s_\beta$, so long as $s_\alpha \rightarrow_S s_\beta$ and the property holds for $s_\alpha$.
+So, since the mutual exclusivity property holds for $s_s$, $s_s \rightarrow_S s_1$, and $s_{i} \rightarrow_S s_{i+1} $ for all $i$ such that $0 < i < n$, we are guaranteed that the mutually exclusive property holds for the final intermediate state $s_n$.
+This concludes the inductive argument about intermediate state.
+
+We now use this result to show that the mutual exclusion property holds for state $s_s^\prime$.
+The relation between the L-functions from the final intermediate state and $s_s^\prime$ is $ $  SOMETHING MISSING HERE , a new value set is created based on the $\mathbb{VS}$ function.
 The members of the value set have the form $(\phi\wedge \phi^\prime\ \ l)$.
@@
 
-%I'm wondering... do we use this theorem anywhere? I think the place we needed it got re-structured, am I right?
-\begin{theorem}
-\label{thm:colex}
-If we have a summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, 
-$$\bigvee \{ \phi \mid (\phi\ \cfgnt{l})\in \cfgnt{L}_s (\cfgnt{r})\} = \cfgt{true}$$
-\end{theorem}
-\begin{proof}
-The proof will proceed inductively.
-
-Base Case: In the initial state $s_0$ there is only one location, and all of it's fields are initialized to contain the uninitiated reference $\cfgnt{r}_{un}$.
+%\begin{comment}
+%%I'm wondering... do we use this theorem anywhere? I think the place we needed it got re-structured, am I right?
+%\begin{theorem}
+%\label{thm:colex}
+%If we have a summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, 
+%$$\bigvee \{ \phi \mid (\phi\ \cfgnt{l})\in \cfgnt{L}_s (\cfgnt{r})\} = \cfgt{true}$$
+%\end{theorem}
+%\begin{proof}
+%The proof will proceed inductively.
+%
+%Base Case: In the initial state $s_0$ there is only one location, and all of it's fields are initialized to contain the uninitiated reference $\cfgnt{r}_{un}$.
 Since the only reference is the uninitialized reference, for which the desired property holds by construction, the property is true for all references on the heap.
-
-Inductive Step: 
-Suppose we have a summary state $s_s$ for which the property holds, and some state $s_s^\prime$ such that $s_s \rightarrow_S s_s^\prime$.
+%
+%Inductive Step: 
+%Suppose we have a summary state $s_s$ for which the property holds, and some state $s_s^\prime$ such that $s_s \rightarrow_S s_s^\prime$.
 If all relevant fields are initialized, then $s_s = s_s^\prime$, and the property holds trivially.
@@
 The disjunction
-$$ \bigvee \{ \phi \mid (\phi\ \cfgnt{l})\in \cfgnt{L}_s (\cfgnt{r}_{new})\}$$
-Takes the form
-\begin{align*}
- (\phi_0) \vee (\neg \phi_0 \wedge \phi_1) \vee (\neg \phi_0 \wedge \neg \phi_1 \wedge \phi_2) \vee ...\\
- ... \vee (\neg \phi_0 \wedge \neg \phi_1 \wedge ... \wedge \phi_n) \vee (\neg \phi_0 \wedge \neg \phi_1 \wedge ... \wedge \neg \phi_n)
- \end{align*}
- Which reduces to $\cfgt{true}$.
+%$$ \bigvee \{ \phi \mid (\phi\ \cfgnt{l})\in \cfgnt{L}_s (\cfgnt{r}_{new})\}$$
+%Takes the form
+%\begin{align*}
+% (\phi_0) \vee (\neg \phi_0 \wedge \phi_1) \vee (\neg \phi_0 \wedge \neg \phi_1 \wedge \phi_2) \vee ...\\
+% ... \vee (\neg \phi_0 \wedge \neg \phi_1 \wedge ... \wedge \phi_n) \vee (\neg \phi_0 \wedge \neg \phi_1 \wedge ... \wedge \neg \phi_n)
+% \end{align*}
+% Which reduces to $\cfgt{true}$.
 Thus, the collective exhaustion property holds for intermediate states.
 Because the property holds for intermediate states, for summary machine rules we will assume without loss of generality that all relevant fields are initialized.
- Suppose that the rule executed in the transition from $s_s$ to $s_s^\prime$ is the field read rule. 
-Suppose we have a state $s_s$ for which the property holds, and some state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$.
-
-\end{proof}
+% Suppose that the rule executed in the transition from $s_s$ to $s_s^\prime$ is the field read rule. 
+%Suppose we have a state $s_s$ for which the property holds, and some state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$. 
+% 
+%\end{proof}
+%\end{comment}
 %\begin{lemma}
@@
 Note that  state $s_\ell^\prime$ has the form: $s_\ell^\prime = \lp \cfgnt{L}_{\ell^\prime}\ \cfgnt{R}_{\ell^\prime}\ \phi_\ell\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.Take any location, field pair $\lp l_\ell\  \cfgnt{f}\rp$ such that $\lp l_\ell\  \cfgnt{f}\rp \in \cfgnt{R}_{\ell}^\leftarrow$, and let $l_s = h(l_\ell)$.
-We may classify $l_\ell$ into one of three categories, based on the values of the $\cfgnt{R}$ function in each of the states $s_\ell$, $s_\ell^\prime$, $s_s$, and $s_s^\prime$, and we may define a function $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ based on that classification.
+We may classify $l_\ell$ into one of three ways, based on the values of the $\cfgnt{R}$ function in each of the states $s_\ell$, $s_\ell^\prime$, $s_s$, and $s_s^\prime$, and we may define a function $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ based on that classification.
 
@@
 In this case, let $h^\prime(l_\ell) = h(l_\ell)$.
-Since $s_\ell \rightharpoonup_h s_s$, obviously:
+Since $s_\ell \rightharpoonup_h s_s$, we may surmise that:
 $$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$$
@@
 \begin{proof}
+THIS PROOF IS A WORK IN PROGRESS.
+
 By Lemma \ref{lem:init} we know that if $s_s$ is exact, then the intermediate state $s_x$ such that $s_s \rightarrow_S^* s_x$ is also exact.
@@
 
-First, we show that every state in the feasible set is represented by the $s_s^\prime$.
+First, we show that every state in the feasible set is represented by $s_s^\prime$.
 Take some lazy state $s_i$ such that $s_i \sqsubset s_s$.
@@
 
-Base case: The initial state is exact. (hands waving)
+Base case: For any initial state $s_0$, the feasible state set contains a single element, $\{s_0\}$:
+$$\mathbb{FS}(\rightarrow_\ell, (s_0), \mathbb{CF}(s_0)) = \{s_0\}$$
+It's obvious that a homomorphism from $s_0$ to $s_0$ exists, and that the Heap Constraint is always satisfiable by construction. Thus, $s_0 \in {s_0} \Rightarrow s_0 \sqsubset s_0$. 
+Furthermore, since every reference points to a single place, there is only one possible represented heap.
+Thus, $s_0 \sqsubset s_0 \Rightarrow s_0 \in {s_0}$.
+We have now shown that $s_0 \cong \mathbb{FS}(\rightarrow_\ell, (s_0), \mathbb{CF}(s_0))$ for an arbitrary initial state $s_0$.
+Since every feasible state sequence starts with an initial state, we now know that:
+ $$\mathit{last}(\Pi_1^s) \cong \mathbb{FS}(\rightarrow_\ell, \mathit{first}(\Pi_1^s), \mathbb{CF}(\Pi_1^s) ) $$
 
 Inductive step: If summary state $s_s$ is exact, then any state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$ is also exact.
-Suppose $s_s$ has the form for a field read, field write, or reference compare rule.
+Suppose $s_s $ has the form for a field read, field write, or reference compare rule.
 By Lemmas \ref{lem:access}, \ref{lem:write}, and \ref{lem:compare}, $s_s^\prime$ will also be exact.
+Suppose $s_s$ is accepted by the "new" rule.
+In this case, the new reference points to the new location on condition true, so it's obvious that $s_s$ represents all of the proper lazy states, and the existence of any infeasible lazy states represented by $s_s^\prime$ would imply that $s_s$ is not exact.
+For all the other rules, the L and R functions and $\phi$ are unchanged, and the rules for  $\eta$, $e$, and $k$ are exactly the same between the lazy and summary machines, so there is a bijective mapping between the represented states in $s_s$ and $s_s^\prime$.
+Thus, in all cases, if $s_s$ is exact, then $s_s^\prime$ is also exact.
+
+We have now shown that any feasible state sequence $\Pi_n^s$ is exact if the sub-sequence $\Pi_{n-1}^s$ is exact.
+
+Combining the result from the inductive step with the result from the base case, we can now say with certainty that for all $n$,
+
+$$\mathit{last}(\Pi_n^s) \cong \mathbb{FS}(\rightarrow_\ell, \mathit{first}(\Pi_n^s), \mathbb{CF}(\Pi_n^s) ) $$
 
 \end{proof}
+
+\begin{corollary}
+For any given initial state, the set of possible control flow sequences under the lazy transition relation is exactly the set of possible control flow sequences under the summary transition relation.
+\end{corollary}
+
+\begin{corollary}
+For any given initial state, the number of final summary states is exactly the number of possible control flow sequences.
+\end{corollary}
+
+%\begin{corollary}
+%For any given initial state, the set of solutions to the constraints in the final summary states provides an optimal set of concrete test inputs.
+There is no smaller set that will exercise every possible control flow sequence.
+%\end{corollary}
+
+%proof: the global invariant is a constraint equation over the initial heap.
+That is to say, when you solve it, it assigns an integer to every variable.
+Those variables are references.
+Thus, solving the constraint equation gives you the location that each reference in the initial heap pointed to.
+%problem: Where the references pointed is only half of the problem.
+We also need to know which references were stored in which fields of which locations at the beginning of the program.
+This would not be hard to do - if we kept track of the initial heap as we created it, separate from the active heap, it should work - however, this is unimplemented

### 2014-09-03 tex/proofs.tex
Miscellaneous fixes and improvements to all proofs

@@
 
-\begin{theorem}
+\begin{theorem}[Mutual Exclusion]
 \label{thm:mutex}
@@
 Base Case: Let $s_s$ be an initial state.
-By Definition \ref{def:initstate}, for every reference $r_i \in \cfgnt{L}_s^\leftarrow$, the set $\cfgnt{L}_s(r_i)$ contains at most one element.
+By Definition~\ref{def:initstate}, for every reference $r_i \in \cfgnt{L}_s^\leftarrow$, the set $\cfgnt{L}_s(r_i)$ contains at most one element.
 Thus, the requirement that $l_\alpha \ne l_\beta$ is never met, and the Theorem is vacuously true.
@@
 Inductive Step: Now we will show that if the exclusivity property holds for some state $s_s$, then it holds for any state $s_s^\prime$ where $s_s \rightarrow_s s_s^\prime$.
-In order to evaluate whether Theorem \ref{thm:mutex} holds for state any $s_s\prime$, we must consider the rule that applied during the transition from $s_s$ to $s_s\prime$.
+In order to evaluate whether Theorem~\ref{thm:mutex} holds for state any $s_s\prime$, we must consider the rule that applied during the transition from $s_s$ to $s_s\prime$.
 There are two broad classes of rules: rules where $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$, and rules where $ \cfgnt{L}_s =  \cfgnt{L}_{s^\prime}$.
@@
 We will use an inductive argument to show that the mutual exclusion property holds for any of those intermediate states.
-First, let state $s_\alpha$ be any state for which the property in Theorem \ref{thm:mutex} holds, and let $s_\beta$ be the intermediate state where $s_\alpha \rightarrow_S s_\beta$.
+First, let state $s_\alpha$ be any state for which the property in Theorem~\ref{thm:mutex} holds, and let $s_\beta$ be the intermediate state where $s_\alpha \rightarrow_S s_\beta$.
 If all fields are initialized, then $s_\alpha$ and $s_\beta$ are identical, so the mutually exclusive property holds for $s_\beta$.
@@
 Any two elements of the set $\theta_{alias}$ are guaranteed to pairwise mutually exclusive because for each constraint that contains the conjunct $r_f = r_a$, every other constraint contains the conjunct $r_f \ne r_a$.
-Thus, all constraints from all pairs in $\theta{all}$ are guaranteed to be mutually exclusive, and the property from Theorem \ref{thm:mutex} holds for intermediate state $s_\beta$.
+Thus, all constraints from all pairs in $\theta{all}$ are guaranteed to be mutually exclusive, and the property from Theorem~\ref{thm:mutex} holds for intermediate state $s_\beta$.
 
@@
 We now use this result to show that the mutual exclusion property holds for state $s_s^\prime$.
-The relation between the L-functions from the final intermediate state and $s_s^\prime$ is $ $  SOMETHING MISSING HERE , a new value set is created based on the $\mathbb{VS}$ function.
+The relation between the L-function from the final intermediate state $\cfgnt{L}^\prime$ and the L-function in $s_s^\prime$ is $ \cfgnt{L}_{s^\prime} = \cfgnt{L}^\prime[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}^\prime,\cfgnt{R}^\prime,\cfgnt{r},\cfgnt{f},\phi_g\rp ]$, where a new value set is created based on the $\mathbb{VS}$ function.
 The members of the value set have the form $(\phi\wedge \phi^\prime\ \ l)$.
@@
 
-\begin{lemma}
+\begin{lemma}[Exactness of Summarize Rule]
 \label{lem:init}
-If symbolic state $s_s = \lp \cfgnt{L}_s\ \cfgnt{R}_{s}\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the intermediate state state $s_s^\prime$ such that $s_s \rightarrow_S^* s_s^\prime$ is equivalent to $\{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$.
+If $s_s \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$ for symbolic state $s_s = \lp \cfgnt{L}_s\ \cfgnt{R}_{s}\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$, initial state $s_0$, and control flow path $\pi_n$, and if there exists some intermediate state state $s_s^\prime$ such that $(\cfgnt{L}_s\ \cfgnt{R}_{s}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C}) \rightarrow_S^* (\cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C})$, then:
+ $$s_s^\prime \cong \{\forall s_\ell^\prime | \exists s_\ell (s_\ell \sqsubset s_s \wedge (s_\ell \rightarrow_I^* s_\ell^\prime) ) \}$$
 \end{lemma}
 
-\begin{proof}%going through this one quickly, could be more formal...
-Take any lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$.
-By Definition \ref{representation}, we know $s_\ell = \lp \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.
+\begin{proof}
+In order for a state to be equivalent to a set of lazy states, it must be both sound and complete with respect to the set.
+We will begin the proof by showing completeness, and then finish by demonstrating soundness.
+
+To show completeness, we must show that any state in the set is represented by $s_s$.
+The definition of representation requires the both the existence of a homomorphism, and proof that the homomorphism constraint is satisfiable.
+To show that a homomorphism exits, take any lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$.
+By Definition~\ref{representation}, we know $s_\ell = \lp \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.
 Take any state $s_\ell^\prime$ where $s_\ell \rightarrow_I^* s_\ell^\prime$, and state $s_s^\prime$ where $s_s \rightarrow_S^* s_s^\prime$.
-Note that  state $s_\ell^\prime$ has the form: $s_\ell^\prime = \lp \cfgnt{L}_{\ell^\prime}\ \cfgnt{R}_{\ell^\prime}\ \phi_\ell\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.Take any location, field pair $\lp l_\ell\  \cfgnt{f}\rp$ such that $\lp l_\ell\  \cfgnt{f}\rp \in \cfgnt{R}_{\ell}^\leftarrow$, and let $l_s = h(l_\ell)$.
+Note that  state $s_\ell^\prime$ has the form: $s_\ell^\prime = \lp \cfgnt{L}_{\ell^\prime}\ \cfgnt{R}_{\ell^\prime}\ \phi_{\ell^\prime}\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.Take any location, field pair $\lp l_\ell\  \cfgnt{f}\rp$ such that $\lp l_\ell\  \cfgnt{f}\rp \in \cfgnt{R}_{\ell}^\leftarrow$, and let $l_s = h(l_\ell)$.
 We may classify $l_\ell$ into one of three ways, based on the values of the $\cfgnt{R}$ function in each of the states $s_\ell$, $s_\ell^\prime$, $s_s$, and $s_s^\prime$, and we may define a function $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ based on that classification.
@@
 Class 1: $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f} ) = \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f} )$ and $\cfgnt{R}_{s} ( l_s,  \cfgnt{f} ) = \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$.
-In this case, let $h^\prime(l_\ell) = h(l_\ell)$.
+Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{\ell}(\cfgnt{R}_{\ell} (\cfgnt{l}_\ell,f )) $.
+In this case, let $h^\prime(l_\alpha) = h(l_\alpha)$.
 Since $s_\ell \rightharpoonup_h s_s$, we may surmise that:
@@
 Class 2: $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f}) = \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_s,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$.
-Notice that since $\cfgnt{R}_{s} ( l_s,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$, we may deduce that $ (\phi_b\ \bot)\in \cfgnt{L}_{s}(\cfgnt{R}_{s} (\cfgnt{l}_s,f ))$, and by extension, ${(\phi_a\ \bot)} = \cfgnt{L}_{\ell}(\cfgnt{R}_{\ell} (\cfgnt{l}_\ell,f )) $.
-In this case, we let $h^\prime(l_\ell) = h(l_\ell)$.
-Since $(\phi_a\ \bot) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f ))$, and since by rule $ (\phi_b\ \bot)\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$, we can see that in this case:
+Since $\cfgnt{R}_{s} ( l_s,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$, the Summarize rule must have altered this reference.
+A reference created by the Summarize rule has a value set $\theta_{all}$ with four subsets: $\theta_{null}$, $\theta_{new}$, $\theta_{alias}$, and $\theta_{orig}$.
+Because $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f}) = \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f})$, we know that the location we want to map to lies in $\theta_{orig}$.
+Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{\ell}(\cfgnt{R}_{\ell} (\cfgnt{l}_\ell,f )) $, and let $l_{orig} = h(l_\alpha)$.
+In this case, we let $h^\prime(l_\alpha) = h(l_\alpha)$.
+Since $(\phi_a\ l_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f ))$.
+Let $l_{orig} = h(l_\alpha)$.
+We can see that by the Summarize rule $ (\phi_b\ l_{orig})\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$, so therefore:
 $$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$$
@@
 Class 3: $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f}) \neq \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_s,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$.
-In this case, let $l_\alpha$ be any location such that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) $.
-If $\lp *\ l_\alpha \rp \in \cfgnt{L}_{\ell}^\rightarrow $, let $h^\prime(l_\alpha) = h(l_\alpha)$.
+In this case, there are two possibilities: either the new reference $\cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f})$ points to some location we've seen before $l_\alpha$, or it points to a previously unobserved location $l_\beta$.
+By establishing which of these possibilities has happened, we can build $h^\prime$.
+To construct $h^\prime$, let $l_\alpha$ be any location such that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) $.
+If there exists $\phi_\alpha$ such that $\lp \phi_\alpha\ l_\alpha \rp \in \cfgnt{L}_{\ell}^\rightarrow $, let $h^\prime(l_\alpha) = h(l_\alpha)$.
 Otherwise, let $l_\beta$ be the location such that $(\phi_b\ \cfgnt{l}_\beta) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f )) $ and $(\phi_b\ \cfgnt{l}_\beta) \notin \cfgnt{L}_{s}(\cfgnt{R}_{s} (\cfgnt{l}_s,f )) $.
@@
 We have now shown that there exists a mapping $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ for all $\cfgnt{l}_{\ell^\prime} \in \cfgnt{L}_{\ell^\prime}^\rightarrow$ such that:
-$$ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_{\ell^\prime},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_{\ell^\prime},f )) $$.
-By Definition \ref{def:homomorphism} we know that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$.
-Furthermore, since the heap constraint is satisfiable (hands waving here), we know that $s_\ell^\prime \sqsubset s_s^\prime $.
+$$ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_{\ell^\prime},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_{\ell^\prime},f )) $$
+By Definition~\ref{def:homomorphism} we know that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$.
+
+It remains to show that $\mathbb{S}( \phi_s^\prime \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h} s_s^\prime) )$.
+For locations in Class 1, no new conjuncts are added to $\mathbb{HC}(s_\ell^prime \rightharpoonup_{h} s_s^\prime)$, and therefore the satisfiability cannot be changed.
+For locations in Class 2 or Class 3, the new constraints take either the form $\phi_x \wedge \phi_{orig}$, or $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$.
+Constraints of the form  $\phi_x \wedge \phi_{orig}$ contain terms $\phi_x$ and $\phi_{orig}$ which were already conjoined to prior heap constraint, so satisfiability is not affected.
+In constraints of the form $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$, the term $\phi_x$ is conjoined to the prior heap constraint, and all the other terms involve the new variable $r_f$, so satisfiability is not affected.
+Since the previous heap constrain is satisfiable, and none of the new terms can impact the satisfiability, we know that the new heap constraint must also be satisfiable.
+
+Since the heap constraint is satisfiable, we know that $s_\ell^\prime \sqsubset s_s^\prime $.
 We have therefore shown that for some summary state $s_s$ and an arbitrary lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$ :
@@
 Since we know that every field points to the right place at the right time, and since we know that the constraints are mutually exclusive, we know that the "wrong time" can never be at the same time as the "right time".
-Since the right time is every time due to Theorem \ref{thm:colex}, this implies that the wrong time is no time.
+Since the right time is every time due to Theorem~\ref{thm:colex}, this implies that the wrong time is no time.
 
@@
 We have now proven that 
-$$ s_\ell^* \sqsubset s_s^*  \Rightarrow  s_\ell^* \in \{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$$
+$$ s_\ell^* \sqsubset s_s^*  \Rightarrow  s_\ell^* \in \{\forall s_\ell^\prime | \exists s_\ell (s_\ell \sqsubset s_s \wedge (s_\ell \rightarrow_I^* s_\ell^\prime) ) \}$$
 This fact, combined with our previous result, proves that
-$$s_s^*  \cong \{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \}$$
+$$s_s^*  \cong \{\forall s_\ell^\prime | \exists s_\ell (s_\ell \sqsubset s_s \wedge (s_\ell \rightarrow_I^* s_\ell^\prime) ) \}$$
 
@@
 %we need to define how r' is arrived at for this one to work...
-\begin{lemma}
+\begin{lemma}[Exactness of Field Access Rule]
 \label{lem:access}
@@
 \begin{proof}
-We will consider two cases for this proof. In the first case, we assume that all of the fields involved in the read are initialized. In the second case we consider the case of uninitialized fields.
+Begin by assuming the conditions stated in Lemma~\ref{lem:access}.
+We will consider two cases for this proof.
+In the first case, we assume that all of the fields involved in the read are initialized.
+In the second case we consider uninitialized fields.
 
-Case 1: suppose all of the pertinent fields in $s_s$ are initialized.
+Case 1: Suppose all of the pertinent fields in $s_s$ are initialized.
 Take an arbitrary lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$.
 Since $s_s$ is exact,  $s_\ell = \lp \cfgnt{L}_{\ell}\ \cfgnt{R}_{\ell}\ \phi_\ell\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k} \rp \rp$, and $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$.
-If we apply the state transition functions to achieve states $s_\ell^\prime$ and $s_s^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$ and  $s_s \rightarrow_s s_s^\prime$, we find that:
+If we apply the state transition functions to achieve states $s_\ell^\prime$ and $s_s^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$ and  $s_s \rightarrow_s s_s^\prime$, we find that according to the Field Access rule:
 $$s_\ell^\prime = \lp \cfgnt{L}_{\ell} [\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}_{\ell}\ \phi_L\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
@@
 Since $\cfgnt{r}^\prime$ is the only new addition to $L_\ell^\prime$ and $L_s^\prime$, we now know that the assertion above holds for all $l \in \mathcal{L}$.
-Thus, we have shown that $s_\ell^\prime \rightharpoonup_{(g\ h)} s_s^\prime$.
-Furthermore, since $\mathbb{S}(\phi_g \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime))$, and since $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, by Definition \ref{representation} we know $s_\ell^\prime \sqsubset s_s^\prime$.
+Thus, we have shown that $s_\ell^\prime \rightharpoonup_{h} s_s^\prime$.
+Furthermore, since the constraints in $\mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime)$ are constructed using conjuncts already present in $ \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s)$, we are guaranteed that $\mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) \Leftrightarrow \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s)$, and therefore $\mathbb{S}(\phi_g \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime))$.
+This fact, and the fact that $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, means that by Definition~\ref{representation} we know $s_\ell^\prime \sqsubset s_s^\prime$.
 We have now shown that for any lazy state $s_\ell$:
@@
 %Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$, but $s_i^\prime \notin \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
-Since $s_i^\prime \sqsubset s_s^\prime$, then by Lemma \ref{lem:ref}, $\cfgnt{r}^\prime$ represents a valid path $\Gamma_{n+1}^{s\prime}$, in states $s_i^\prime$ and $s_s^\prime$.
-Furthermore, by Lemma \ref{lem:path} we can surmise that $\mathbb{S}(\phi_s^\prime \wedge \mathbb{PC}(\Gamma_{n+1}^{s\prime}))$.
+Since $s_i^\prime \sqsubset s_s^\prime$, then by Lemma~\ref{lem:ref}, $\cfgnt{r}^\prime$ represents a valid path $\Gamma_{n+1}^{s\prime}$, in states $s_i^\prime$ and $s_s^\prime$.
+Furthermore, by Lemma~\ref{lem:path} we can surmise that $\mathbb{S}(\phi_s^\prime \wedge \mathbb{PC}(\Gamma_{n+1}^{s\prime}))$.
 By construction, $\Gamma_{n+1}^{s\prime}$ is an extension of the valid access path $\Gamma_{n}^{s}$ represented by reference $\cfgnt{r}$ in state $s_s$.
@@
 Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$, but $s_i^\prime \notin \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
-Since $s_i^\prime \sqsubset s_s^\prime$, then by Definition \ref{representation}, we know there exists a homomorphism $s_i^\prime \rightharpoonup_{h^\prime} s_s^\prime$, and that $\mathbb{S}( \phi_i^\prime \wedge \mathbb{HC}(s_i^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$.
+Since $s_i^\prime \sqsubset s_s^\prime$, then by Definition~\ref{representation}, we know there exists a homomorphism $s_i^\prime \rightharpoonup_{h^\prime} s_s^\prime$, and that $\mathbb{S}( \phi_i^\prime \wedge \mathbb{HC}(s_i^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$.
 From state $s_i^\prime$, construct state $s_i$ such that
@@
 \end{align*}
-Observe that $s_i \rightarrow_\ell s_i^\prime$.
+Observe that by virtue of the lazy Field Access rule, $s_i \rightarrow_\ell s_i^\prime$.
 Now, construct function $h_i$ so that $h_i = h^\prime$.
-Observe that $s_i \rightharpoonup_{h_i} s_s$, and that $\mathbb{S}( \phi_i \wedge \mathbb{HC}(s_i \rightharpoonup_{h_i} s_s) )$, so $s_i \sqsubset s_s$.
-By the hypothesis that $s_s$ is exact, $s_i \in\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$.
+Observe that by Definition~\ref{def:homomorphism} $s_i \rightharpoonup_{h_i} s_s$,  and that $\mathbb{S}( \phi_i \wedge \mathbb{HC}(s_i \rightharpoonup_{h_i} s_s) )$, so $s_i \sqsubset s_s$.
+Since $s_s$ is exact, $s_i \in\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$.
 Combining this with the fact that $s_i \rightarrow_\ell s_i^\prime$, we conclude that $s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
@@
 
- Therefore, $s_s^\prime$ is sound with respect to $\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$
+ Therefore, $s_s^\prime$ is sound with respect to $\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$:
  \begin{equation}
@@
 $$s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1}) \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$
-By Definition \ref{equivalent}, $s_s^\prime \cong \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, and so by Definition \ref{exact}, $s_s^\prime$ is exact.
+By Definition~\ref{equivalent}, $s_s^\prime \cong \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, and so by Definition~\ref{exact}, $s_s^\prime$ is exact.
 
 Case 2: If there are uninitialized fields, then the lazy initialization machine will make an intermediate state $s_t$.
-By lemma \ref{lem:init}, the symbolic state is equivalent to the set of lazy initialized states.
-From the intermediate state, the proof is the same as for case 1.
+By Lemma~\ref{lem:init}, the summary intermediate state is equivalent to the set of lazy intermediate states.
+Since the summary intermediate state From the intermediate state, the proof is the same as for case 1.
 \end{proof}
@@
 %proof for field write
-\begin{lemma}
+\begin{lemma}[Exactness of Field Write Rule]
 \label{lem:write}
@@
 \begin{proof}
-THIS PROOF IS A WORK IN PROGRESS.
-
-By Lemma \ref{lem:init} we know that if $s_s$ is exact, then the intermediate state $s_x$ such that $s_s \rightarrow_S^* s_x$ is also exact.
+By Lemma~\ref{lem:init} we know that if $s_s$ is exact, then the intermediate state $s_x$ such that $s_s \rightarrow_S^* s_x$ is also exact.
 Thus, for $s_s$ and any state  $s_i$ such that $s_i \sqsubset s_s$ we will assume, without loss of generality, that all relevant fields have been initialized.
@@
 Take some lazy state $s_i$ such that $s_i \sqsubset s_s$.
-It is easy to see that $s_i^\prime$ is represented by $s_s^\prime$.
+Observe that the field write rule places every possible target value into the reference stored at the target location.
+Thus, whatever the write value was for $s_i^\prime$ was, it was written to the target field, meaning $s_i^\prime$ is represented by $s_s^\prime$.
 
@@
 %proof for reference compares. Here we will rely on the fact that since the L and R functions don't change, and since the phi function
-\begin{lemma}
+\begin{lemma}[Exactness of Reference Compare Rule]
 \label{lem:compare}
@@
 There are two rules that apply to state $s_s$, one for the $\cfgt{true}$ branch and one for the $\cfgt{false}$ branch.
-Since the proofs for both rules are nearly identical, for clarity we will only show the proof for the case for the $\cfgt{true}$ branch here.
+Since the proofs for both rules are nearly identical, for brevity we will only show the proof for the case for the $\cfgt{true}$ branch.
 \begin{proof}
 Choose any $s_\ell \sqsubset s_s$, and let $\zeta_T = \mathbb{FS}(\rightarrow_{\ell},s_0,(\pi_n,(\eta\ \cfgt{true}\ \cfgnt{k})))$.
-Since $s_s$ is exact, we know that $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, $s_l = \lp \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$, and that there exists a homomorphism $s_\ell \rightharpoonup_{(g\ h) } s_s$ such that $\mathbb{S}( \phi_s \wedge \mathbb{HC}(s_\ell \rightharpoonup_{(g\ h)} s_s) ) $.
+Since $s_s$ is exact, we know that $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, $s_l = \lp \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$, and that there exists a homomorphism $s_\ell \rightharpoonup_{h} s_s$ such that $\mathbb{S}( \phi_s \wedge \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s) ) $.
 Depending on the values of $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, there are two different rules that might apply to $s_\ell$.
@@
 
-Case 1: Assume $s_\ell : \cfgnt{L}_\ell \lp \cfgnt{r}_0\rp = \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, and let 
-$$\zeta_t = \zeta_T \setminus \{ s_f | \cfgnt{L}_f \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_f \lp \cfgnt{r}_1 \rp \}$$ In this case, the lazy ``equals - references true" rule applies, and we know state $s_\ell^\prime : s_\ell \rightarrow_\ell s_\ell^\prime$ is in $\zeta_t$.
-Observe that by applying theorem \ref{thm:mutex}, $\phi_s^\prime \wedge \phi_0 \wedge \phi_1$ reduces to $\phi_s$.
-Therefore, $\mathbb{S}( \phi_s^\prime \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{(g\ h)} s_s^\prime) ) $ is true, and by extension, $s_\ell^\prime \sqsubset s_s^\prime$.
+Case 1: Assume $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp = \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, and let 
+$$\zeta_t = \zeta_T \setminus \{ s_f | (s_f= \lp \cfgnt{L}_f\ \cfgnt{R}_f\ \phi_\ell\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp) \wedge (\cfgnt{L}_f \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_f \lp \cfgnt{r}_1 \rp ) \}$$
+In this case, the lazy ``equals - references true" rule applies, and we know state $s_\ell^\prime : s_\ell \rightarrow_\ell s_\ell^\prime$ is in $\zeta_t$.
+Observe that by applying Theorem~\ref{thm:mutex}, $\phi_s^\prime \wedge \phi_0 \wedge \phi_1$ reduces to $\phi_s$.
+Therefore, $\mathbb{S}( \phi_s^\prime \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h} s_s^\prime) ) $ is true, and by extension, $s_\ell^\prime \sqsubset s_s^\prime$.
 Since this relation holds for arbitrary $s_\ell^\prime \in \zeta_t$, we now know that $$s_\ell^\prime \in \zeta_t \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$$
@@
 Combining this with the assumption that $s_i^\prime \notin \zeta_t$, we must conclude that $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp \neq  \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$.
-Because of this, and because of Theorem \ref{thm:mutex}, we know that either all constraints in the set
+Because of this, and because of Theorem~\ref{thm:mutex}, we know that either all constraints in the set
 $$\{\phi_i \mid \exists \phi_\alpha (\phi_\alpha \in \theta_\alpha)\wedge \phi_i = \lp\phi_\alpha \wedge \phi_0 \wedge \phi_1\rp\}$$ are unsatisfiable, or that at least one constraint in the set
@@
 $$s_\ell^\prime \in \zeta_T \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$
- By Definition \ref{equivalent}, $s_s^\prime \equiv \zeta_T$, and by definition \ref{exact}, $s_s^\prime$ is exact.
+ By Definition~\ref{equivalent}, $s_s^\prime \equiv \zeta_T$, and by Definition~\ref{exact}, $s_s^\prime$ is exact.
 \end{proof}
 
-\begin{theorem}
+\begin{theorem}[Exactness of Summary Machine States]
 If $\Pi_n^s$ is a feasible summary state sequence, then the final state in $\Pi_n^s$ is equivalent to the feasible set of lazy states sharing the same control flow sequence:
@@
 $$\mathbb{FS}(\rightarrow_\ell, (s_0), \mathbb{CF}(s_0)) = \{s_0\}$$
-It's obvious that a homomorphism from $s_0$ to $s_0$ exists, and that the Heap Constraint is always satisfiable by construction. Thus, $s_0 \in {s_0} \Rightarrow s_0 \sqsubset s_0$. 
-Furthermore, since every reference points to a single place, there is only one possible represented heap.
-Thus, $s_0 \sqsubset s_0 \Rightarrow s_0 \in {s_0}$.
+We can define a homomorphism from $s_0$ to $s_0$ using the identity function: 
+$$\forall a \in \cfgnt{L}_0^\rightarrow ( h(a) = a )$$ 
+Because the only constraints in the heap are $\mathit{true}$, the heap constraint evaluates to $\mathit{true}$.
+Since $phi_0$ also evaluates to $\mathit{true}$, the expression $\mathbb{S}(\phi_0 \wedge \mathbb{HC}(s_0 \rigtharrow_h s_0 ) ) $ must evaluate to true.
+Thus, any state in the feasible set must be represented by $s_0$: :
+$$s_0 \in \mathbb{FS}(\rightarrow_\ell,s_0, (\eta_0\ e_0\ k_0) ) \Rightarrow s_0 \sqsubset s_0$$
+Furthermore, since every reference points to a single place, there is only one possible represented heap. Thus:
+$$ \{s_0\} = \mathbb{FS}(\rightarrow_\ell,s_0, (\eta_0\ e_0\ k_0) )$$
+Since $s_0$ is the only represented heap, and since we know $s_0$ is in the feasible set, 
+$$s_0 \sqsubset s_0 \Leftrightarrow s_0 \in \{s_0\}$$
 We have now shown that $s_0 \cong \mathbb{FS}(\rightarrow_\ell, (s_0), \mathbb{CF}(s_0))$ for an arbitrary initial state $s_0$.
@@
 Inductive step: If summary state $s_s$ is exact, then any state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$ is also exact.
-Suppose $s_s $ has the form for a field read, field write, or reference compare rule.
+Suppose $s_s$ has the form for a field read, field write, or reference compare rule.
 By Lemmas \ref{lem:access}, \ref{lem:write}, and \ref{lem:compare}, $s_s^\prime$ will also be exact.

### 2014-09-03 tex/definitions.tex
Miscellaneous fixes and improvements to all proofs
Added preliminary definition for initial states

@@
 \begin{definition}
-\label{def:initate}
-The set of \textbf{initial states} $\mathcal{S}_0$ is defined as (TBD)
+\label{def:initstate}
+$\mathcal{S}_0$ is defined as the set of \textbf{initial states}.
+An initial state is a state meeting the following conditions:  The range of L has exactly three locations: $l_{null}$, $l_{un}$, and $l_0$, the function R is defined only for location $l_0$, and for any field $f$, $R(l_0,f)$ returns $r_{un}$.
 \end{definition}
@@
  f^\rightarrow &= \{ f(a) \mid a \in A\}\\
- f^\leftarrow &= \{ a \mid f(a) \in B \}§
+ f^\leftarrow &= \{ a \mid f(a) \in B \}
  \end{align}
+ The bracket notation $ f^\rightarrow [C] $ is used to denote that the image is drawn from a specific subset:
+ \begin{align}
+ f^\rightarrow [C] &= \{ f(a) \mid a \in C\}\\
+ f^\leftarrow [D] &= \{ a \mid f(a) \in D \}
+ \end{align}
+ Where $C \subset A$ and $D \subset B$
 \end{definition}

### 2014-09-03 tex/javalite.tex
Fixed some typos in the javalite and precise rules figures.

@@
 of location-constraint pairs in the heap associated with the given
-reference, and$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the
+reference, and $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the
 reference associated with the given location-field pair in the

### 2014-09-03 tex/proofs.tex
Fixed some typos in the math the kept the paper from building.

@@
 In this case, a new reference is created and a single entry is added to $\cfgnt{L}_\beta$.
-The elements of the set $\theta_{all} = \cfgnt{L}_\beta(\cfgnt{R}_\beta(\cfgnf{l}_{un},\cfgnt{f}))$ can be divided into four distinct subsets, $\theta_{cur}$, $\theta_{null}$, $\theta_{new}$, and $\theta_{alias}$.
+The elements of the set $\theta_{all} = \cfgnt{L}_\beta(\cfgnt{R}_\beta(\cfgnt{l}_{un},\cfgnt{f}))$ can be divided into four distinct subsets, $\theta_{cur}$, $\theta_{null}$, $\theta_{new}$, and $\theta_{alias}$.
 The set $\theta_{cur}$ contains the pairs containing locations from the reference $r_a$, $\theta_{null}$ contains the pair with the null location, $\theta_{new}$ contains a pair with a new location, and $\theta_{alias}$ contains pairs representing alias locations.
@@
 Because the only constraints in the heap are $\mathit{true}$, the heap constraint evaluates to $\mathit{true}$.
-Since $phi_0$ also evaluates to $\mathit{true}$, the expression $\mathbb{S}(\phi_0 \wedge \mathbb{HC}(s_0 \rigtharrow_h s_0 ) ) $ must evaluate to true.
+Since $phi_0$ also evaluates to $\mathit{true}$, the expression $\mathbb{S}(\phi_0 \wedge \mathbb{HC}(s_0 \rightarrow_h s_0 ) ) $ must evaluate to true.
 Thus, any state in the feasible set must be represented by $s_0$: :

### 2014-09-03 tex/proofs.tex
Committing changes before merge.

--- 2014-09-03 tex/proofs.tex
@@
 \label{lem:write}
-If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then $s_s^\prime$ is equal to $ \lp \cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \eta\ \cfgnt{k}\rp$ and is exact with respect to $s_0$ and $\pi_n \ (\eta\ \cfgnt{k}\ \emptyset)$.
+If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then $s_s^\prime$ is equal to $ \lp \cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \eta\ \cfgnt{k}\rp$ and is exact with respect to $s_0$ and $\pi_n \ (\eta\ \cfgnt{k}\ \emptyset)$:
+$$s_\ell^\prime \sqsubset s_s^\prime \Leftrightarrow s_\ell^\prime \in \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) ) $$
 
@@
 \begin{proof}
-By Lemma~\ref{lem:init} we know that if $s_s$ is exact, then the intermediate state $s_x$ such that $s_s \rightarrow_S^* s_x$ is also exact.
-Thus, for $s_s$ and any state  $s_i$ such that $s_i \sqsubset s_s$ we will assume, without loss of generality, that all relevant fields have been initialized.
+Begin by assuming the conditions from Lemma~\ref{lem:write}.
 
-First, we show that every state in the feasible set is represented by $s_s^\prime$.
-Take some lazy state $s_i$ such that $s_i \sqsubset s_s$.
+The first step is to show that $s_s^\prime$ is complete with respect to the feasible set.
+Take any lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$, and find state $s_\ell^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$.
+Let $l_\ell$ be the location such that $\{(\phi\ l_\ell )\} = \cfgnt{L}_\ell(\cfgnt{r}_x) $ for some $\phi$.
+To show that $s_\ell^\prime \sqsubset s_s^\prime$, we need to demonstrate that there exists a function $h^\prime$ such that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$, and that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$.
+Since $s_h \sqsubset s_s$, we know that there exists a function $h$ such that $s_\ell \rightharpoonup_{h} s_s$.
+Let $h^\prime = h$.
+
+To see that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$, we must consider how $s_s^\prime$ is constructed.
+Let $l_\alpha$ and $l_\beta$ be arbitrary locations in $\cfgnt{L}_{\ell^\prime}^\rightarrow$ such that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\beta,f ))$, let $\theta = \cfgnt{L}_s(\cfgnt{R}_s(h(l_\ell),f))$, and let $\theta^\prime =   \cfgnt{L}_s^\prime(\cfgnt{R}_s^\prime(h(l_\ell),f))$.
+If $l_\beta \neq l_\ell$, then either $\theta = \theta^\prime$ or $\theta \neq \theta^\prime$ .
+In the first case, we are guaranteed that the homomorphism works by default.
+Otherwise, if $\theta \neq \theta^\prime$.
+We can see from the construction of the set $X$ in the summary Field Write rule that any feasible location in the set $\theta$ must also be in the set $\theta^\prime$.
+Since $s_\ell \sqsubset s_s$, we know that $h(l_\alpha)$ is in $\theta$, and is likewise in $\theta^\prime$.
+We have now established that in either case:
+ $$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\beta,f )) \Rightarrow (\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (h(\cfgnt{l}_\beta),f ))$$
+On the other hand, if $l_\beta = l_\ell$, then we know that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\ell,f ))$.
+From the lazy field rule, we can use the fact that $ $ surmise that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell}( )$, and since $s_\ell \sqsubset s_s$, we know $(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s}(\cfgnt{r}_x)$ for some constraint $phi_b$.
+Using this fact, we can apply the summary Field Write rule to infer that $l_\alpha$ must be one of the locations in $\theta^\prime$, and therefore $(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s^\prime}(adfa)$
+
+Thus, for arbitrary $l_\alpha$ and $l_\beta$:
+$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\beta,f )) \Rightarrow (\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (h(\cfgnt{l}_\beta),f ))$$
+Therefore, we have shown that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$.
+
 Observe that the field write rule places every possible target value into the reference stored at the target location.

### 2014-09-03 tex/proofs.tex
Added more detail to the Field Write proof, and fixed some typos in the lazy Field Access rule.

@@
 Let $l_\alpha$ and $l_\beta$ be arbitrary locations in $\cfgnt{L}_{\ell^\prime}^\rightarrow$ such that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\beta,f ))$, let $\theta = \cfgnt{L}_s(\cfgnt{R}_s(h(l_\ell),f))$, and let $\theta^\prime =   \cfgnt{L}_s^\prime(\cfgnt{R}_s^\prime(h(l_\ell),f))$.
-If $l_\beta \neq l_\ell$, then either $\theta = \theta^\prime$ or $\theta \neq \theta^\prime$ .
+
+Suppose $l_\beta \neq l_\ell$.
+In this case either $\theta = \theta^\prime$ or $\theta \neq \theta^\prime$ .
 In the first case, we are guaranteed that the homomorphism works by default.
@@
 Since $s_\ell \sqsubset s_s$, we know that $h(l_\alpha)$ is in $\theta$, and is likewise in $\theta^\prime$.
-We have now established that in either case:
- $$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\beta,f )) \Rightarrow (\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (h(\cfgnt{l}_\beta),f ))$$
-On the other hand, if $l_\beta = l_\ell$, then we know that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\ell,f ))$.
-From the lazy field rule, we can use the fact that $ $ surmise that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell}( )$, and since $s_\ell \sqsubset s_s$, we know $(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s}(\cfgnt{r}_x)$ for some constraint $phi_b$.
-Using this fact, we can apply the summary Field Write rule to infer that $l_\alpha$ must be one of the locations in $\theta^\prime$, and therefore $(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s^\prime}(adfa)$
+We have now established that in either case where $l_\beta \neq l_\ell$, $(\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (h(\cfgnt{l}_\beta),f ))$.
+
+On the other hand, suppose $l_\beta = l_\ell$.
+In this case we know that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\ell,f ))$.
+From the lazy field rule, we can surmise that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell}(\cfgnt{r} )$, and since $s_\ell \sqsubset s_s$, we know that$(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s}(\cfgnt{r})$ for some constraint $\phi_b$.
+Using this fact, we can apply the summary Field Write rule to infer that $l_\alpha$ must be one of the locations in $\theta^\prime$, and therefore $(\phi_c\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}^\prime(l_\ell,f))$
 
@@
 
+Establishing the fact that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$ is left as an exercise to the reader.
+
 Observe that the field write rule places every possible target value into the reference stored at the target location.
@@
 
-Next, we show that every state represented by $s_s^\prime$ is in the feasible set.
-We use the same argument as in the field read proof, that because $s_s^\prime$ represents every state in the feasible set, and since the cardinality of the set of states represented by $s_s^\prime$ is less than or equal to the cardinality of the feasible set, that $s_s^\prime$ can only represent feasible states.
+To show that $s_s^\prime$ is exact with respect to the feasible set, we use the same argument as in the field read proof: that because $s_s^\prime$ represents every state in the feasible set, and since the cardinality of the set of states represented by $s_s^\prime$ is less than or equal to the cardinality of the feasible set, that $s_s^\prime$ can only represent feasible states.
 

### 2014-09-05 tex/proofs.tex
Updated soundness portion of the field write proof.

@@
 It remains to show that $\mathbb{S}( \phi_s^\prime \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h} s_s^\prime) )$.
-For locations in Class 1, no new conjuncts are added to $\mathbb{HC}(s_\ell^prime \rightharpoonup_{h} s_s^\prime)$, and therefore the satisfiability cannot be changed.
+For locations in Class 1, no new conjuncts are added to $\mathbb{HC}(s_\ell^\prime \rightharpoonup_{h} s_s^\prime)$, and therefore the satisfiability cannot be changed.
 For locations in Class 2 or Class 3, the new constraints take either the form $\phi_x \wedge \phi_{orig}$, or $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$.
@@
 \label{lem:write}
-If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then $s_s^\prime$ is equal to $ \lp \cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \eta\ \cfgnt{k}\rp$ and is exact with respect to $s_0$ and $\pi_n \ (\eta\ \cfgnt{k}\ \emptyset)$:
+If $s_s \cong \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n )$ for some symbolic state $s_s$, initial state $s_0$, and control flow path $\pi_n$, and if $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then:
 $$s_\ell^\prime \sqsubset s_s^\prime \Leftrightarrow s_\ell^\prime \in \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) ) $$
@@
 Take any lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$, and find state $s_\ell^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$.
-Let $l_\ell$ be the location such that $\{(\phi\ l_\ell )\} = \cfgnt{L}_\ell(\cfgnt{r}_x) $ for some $\phi$.
+Let $l_\ell$ be the location such that $\{(\phi_a\ l_\ell )\} = \cfgnt{L}_\ell(\cfgnt{r}_x) $ for some $\phi_a$.
 To show that $s_\ell^\prime \sqsubset s_s^\prime$, we need to demonstrate that there exists a function $h^\prime$ such that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$, and that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$.
@@
 
-To see that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$, we must consider how $s_s^\prime$ is constructed.
+First, we consider how $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$.
 Let $l_\alpha$ and $l_\beta$ be arbitrary locations in $\cfgnt{L}_{\ell^\prime}^\rightarrow$ such that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\beta,f ))$, let $\theta = \cfgnt{L}_s(\cfgnt{R}_s(h(l_\ell),f))$, and let $\theta^\prime =   \cfgnt{L}_s^\prime(\cfgnt{R}_s^\prime(h(l_\ell),f))$.
@@
 In this case we know that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\ell,f ))$.
-From the lazy field rule, we can surmise that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell}(\cfgnt{r} )$, and since $s_\ell \sqsubset s_s$, we know that$(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s}(\cfgnt{r})$ for some constraint $\phi_b$.
+From the lazy field rule, we can surmise that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell}(\cfgnt{r} )$, and since $s_\ell \sqsubset s_s$, we know that $(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s}(\cfgnt{r})$ for some constraint $\phi_b$.
 Using this fact, we can apply the summary Field Write rule to infer that $l_\alpha$ must be one of the locations in $\theta^\prime$, and therefore $(\phi_c\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}^\prime(l_\ell,f))$
@@
 
-Observe that the field write rule places every possible target value into the reference stored at the target location.
-Thus, whatever the write value was for $s_i^\prime$ was, it was written to the target field, meaning $s_i^\prime$ is represented by $s_s^\prime$.
+By proving the existence of a valid homomorphism, we have shown that if $s_\ell \sqsubset s_s$, $s_\ell \rightarrow_\ell s_\ell^\prime$, and $s_s \rightarrow_s s_s^\prime$, then $s_\ell^\prime \sqsubset s_s^\prime$.
+Since $s_s \cong \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n )$, and since $\pi_n (\eta\ \cfgnt{k}\ \emptyset)$  is the only possible control flow sequence from state $s_s$ or any state $s_\ell$ where $s_\ell \sqsubset s_s$, we may deduce that $\{ s_\ell^\prime | \exists s_\ell (s_\ell \sqsubset s_s \wedge s_\ell \rightarrow_\ell s_\ell^\prime ) \} = \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) )$.
+Therefore, $s_\ell^\prime \in \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$.
+This concludes the proof of completeness.
 
-To show that $s_s^\prime$ is exact with respect to the feasible set, we use the same argument as in the field read proof: that because $s_s^\prime$ represents every state in the feasible set, and since the cardinality of the set of states represented by $s_s^\prime$ is less than or equal to the cardinality of the feasible set, that $s_s^\prime$ can only represent feasible states.
+To show that $s_s^\prime$ is sound with respect to the feasible set, we use the same argument as in the field read proof: that any state $s_\ell^\prime$ represented by $s_s^\prime$ must have a counterpart state $s_\ell$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$ and $s_\ell \sqsubset s_s$.
+Because $s_s$ is exact, $s_\ell^\prime$ must be a part of the feasible set.
 

### 2014-09-12 tex/definitions.tex
Added definition for bisimulation. Re-wrote the main theorem to be a bisimulation proof instead of a trace-based proof. Restructured the supporting lemmas to support the main coinductive bisimulation proof.

@@
 
+%For 
 \begin{comment}
@@
 \begin{align}
-\mathcal{S}_\ell = \{s_\ell \mid \exists \Pi_n^\ell\ (\Pi_n^\ell = s_0, \ldots, s_\ell)\}
+\mathcal{S}_\ell = \{s_n \mid \exists \Pi_n^\ell\ (\Pi_n^\ell = s_0, \ldots, s_n)\}
 \end{align}
@@
 \begin{align}
-\mathcal{S}_s = \{s_s \mid \exists \Pi_n^s\ (\Pi_n^s = s_0, \ldots, s_s)\}
+\mathcal{S}_s = \{s_n \mid \exists \Pi_n^s\ (\Pi_n^s = s_0, \ldots, s_n)\}
 \end{align}
+\end{definition}
+
+\begin{definition}
+The sets $\mathcal{FA}$, $\mathcal{FW}$, $\mathcal{RC}$, and  $\mathcal{NW}$ are defined as the sets of states having the forms $ \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$,  $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$, $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$, and $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \lp \cfgt{new}\ \cfgnt{C}\rp \ \cfgnt{k}\rp$ respectively.
 \end{definition}
@@
 Given a sequence of states $$\Pi_n = s_0,s_1,...,s_n$$ where $$s_i = ( \mu_i\ \cfgnt{L}_i\ \cfgnt{R}_i\ \phi_i\ \eta_i\ \cfgnt{e}_i\ \cfgnt{k}_i )$$ the \textbf{control flow sequence} of $\Pi_n$ is the defined as the sequence of tuples $$ \pi_n = \mathbb{CF}(\Pi_n) = (\eta_0\ \cfgnt{e}_0\ \cfgnt{k}_0),(\eta_1\ \cfgnt{e}_1\ \cfgnt{k}_1),...,(\eta_n\ \cfgnt{e}_n\ \cfgnt{k}_n)$$
-\end{definition}
-
-\begin{definition}
-Given a state transition function $\rightarrow_{\Phi}$, an initial state $s_0$ and a control flow sequence $\pi_n$, the \textbf{feasible state set}, $\mathbb{FS}(\rightarrow_{\Phi},s_0,\pi_n)$, is defined as
- $$
-\begin{array}{l}
-\mathbb{FS}(\rightarrow_{\Phi},s_0,\pi_n) = \\
-\ \ \ \ \ \ \{s \mid \exists \Pi_n^\phi\ (\pi_n = \mathbb{CF}(\Pi_n^\Phi) \wedge s = \mathit{last}(\Pi_n))\} 
-\end{array}
-$$
-where $\mathit{last}(\Pi_n)$ returns the last state on the feasible sequence.
 \end{definition}
@@
 \label{representation}
-The \textbf{representation relation} is defined as follows: given lazy state $s_\ell = ( \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta_\ell\ \cfgnt{e}_\ell\ \cfgnt{k}_\ell )$ and summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a homomorphism $\ s_\ell \rightharpoonup_{h} s_s $ such that
+The \textbf{representation relation} is defined as follows: given state $s_y = ( \cfgnt{L}_y\ \cfgnt{R}_y\ \phi_y\ \eta_y\ \cfgnt{e}_y\ \cfgnt{k}_y )$ and state $s_x = ( \cfgnt{L}_x\ \cfgnt{R}_x\ \phi_x\ \eta_x\ \cfgnt{e}_x\ \cfgnt{k}_x )$, $s_y \sqsubset s_x $ if and only if $\eta_y = \eta_x ,\ \cfgnt{e}_y = \cfgnt{e}_x ,\ \cfgnt{k}_y = \cfgnt{k}_x$, and there exists a homomorphism $\ s_y \rightharpoonup_{h} s_x $ such that
 \begin{equation}
 \label{eqn:valid}
- \mathbb{S}( \phi_s \wedge \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s) ) 
+ \mathbb{S}( \phi_x \wedge \mathbb{HC}(s_y \rightharpoonup_{h} s_x) ) 
 \end{equation}
+\end{definition}
+
+\begin{definition}
+\label{bisimulation}
+A state relation $\mathcal{R}$ is a \textbf{bisimulation} if and only if for every state $s_x$ and $s_y$ such that $s_x\ \mathcal{R}\ s_y$, the following two properties hold: 
+\begin{equation}
+\label{eqn:BisimulationForwards}
+\forall s_x^\prime ( s_x \rightarrow_x s_x^\prime \Rightarrow \exists s_y^\prime( (s_y \rightarrow_y s_y^\prime )\wedge (s_x^\prime\ \mathcal{R}\ s_y^\prime ))  )
+\end{equation}
+\begin{equation}
+\label{eqn:BisimulationBackwards}
+\forall s_y^\prime ( s_y \rightarrow_y s_y^\prime\Rightarrow \exists s_x^\prime( (s_x \rightarrow_x s_x^\prime )\wedge (s_x^\prime\ \mathcal{R}\ s_y^\prime ))  )
+\end{equation}
+\end{definition}
+
+Note that in the literature it is customary to define bisimulation in terms of a single labeled transition system, whereas for the purposes of this paper the definition of bisimulation refers to a pair of transition relations $\rightarrow_x$ and $\rightarrow_y$ defined by reduction rules.
+Since it is possible to create a union of the two rule systems $\rightarrow_x \cup \rightarrow_y$, and since none of the transitions in the reduction rules in this paper are labeled, this definition is sufficient for all of the customary properties of bisimulation to apply.
+For a more detailed treatment on the application of bisimulation to reduction rule systems see \cite{GSE:barbedbisimulation}.
+
+\begin{definition}
+Given a state transition function $\rightarrow_{\Phi}$, an initial state $s_0$ and a control flow sequence $\pi_n$, the \textbf{feasible state set}, $\mathbb{FS}(\rightarrow_{\Phi},s_0,\pi_n)$, is defined as
+ $$
+\begin{array}{l}
+\mathbb{FS}(\rightarrow_{\Phi},s_0,\pi_n) = \\
+\ \ \ \ \ \ \{s \mid \exists \Pi_n^\Phi\ (\pi_n = \mathbb{CF}(\Pi_n^\Phi) \wedge s \sqsubset \mathit{last}(\Pi_n^\Phi))\} 
+\end{array}
+$$
+where $\mathit{last}(\Pi_n^\Phi)$ returns the last state on the feasible sequence.
 \end{definition}

### 2014-09-12 tex/proofs.tex
Added definition for bisimulation. Re-wrote the main theorem to be a bisimulation proof instead of a trace-based proof. Restructured the supporting lemmas to support the main coinductive bisimulation proof.

@@
 Since the exclusivity property holds for any initial state, and since it holds for any "next" state if the property holds for the previous state, we have proven the property for every symbolic state.
+\end{proof}
+
+\begin{corollary}
+Any state represented by any reachable summary state is a lazy state.
+\end{corollary}
+
+\begin{proof}
+By Theorem \ref{thm:mutex} since the constraints on every reference are mutually exclusive, the heap constraint for any heap with a reference pointing to more than one location will be unsatisfiable, and by Definition \ref{representation} will not be represented by the summary state.
 \end{proof}
@@
 In constraints of the form $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$, the term $\phi_x$ is conjoined to the prior heap constraint, and all the other terms involve the new variable $r_f$, so satisfiability is not affected.
-Since the previous heap constrain is satisfiable, and none of the new terms can impact the satisfiability, we know that the new heap constraint must also be satisfiable.
+Since the previous heap constraint is satisfiable, and none of the new terms can impact the satisfiability, we know that the new heap constraint must also be satisfiable.
 
@@
 Since we don't change the path condition, all the old references still point exactly to the same places they used to.
+
 So, the problem must be with one of the new references.
 All of the new references point to either a new location, the null location, the uninitialized location, or some alias.
-The new, null, and uninitialized locations are pretty straightforward and easy to show that they are all pointing to the correct places at the correct times.
+In the Summarize rule, the values and constraints for the new, null, uninitialized, and alias locations are contained in the sets $\theta_{new}$, $\theta_{null}$, $\theta{orig}$, and $\theta_{alias}$.
+Since the null, and uninitialized locations are already accounted for by the homomorphism $s_\ell \rightharpoonup_h s_s$, and since a new location was created symmetrically for both $s_\ell^\prime$ and $s_s^\prime$, the problem must be with some alias location that is part of $s_s$ but not $s_\ell$.
 This means that there must be a feasible path to a target location that does not exist for any lazy heap.
@@
 \label{lem:access}
-If there are symbolic states $s_s$ and $s_s^\prime$, control sequences $\pi_n$ and $\pi_{n+1}$, initial state $s_0$, and reference $\cfgnt{r}^\prime$ such that the following conditions hold:
-\begin{align}
-s_s &= \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp \\
-s_s &\cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp \\
-\cfgnt{r}^\prime &= \mathrm{fresh}_r\lp \rp \\
-\pi_{n+1} &=\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp \\
-s_s &\rightarrow_s s_s^\prime
-\end{align}
-%$$s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$$ 
-%$$s_s \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp$$ 
-%$$\pi_{n+1} =\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp$$
-
-then 
-$$s_s^\prime \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_{n+1} \rp$$
+%If there are symbolic states $s_s$ and $s_s^\prime$, control sequences $\pi_n$ and $\pi_{n+1}$, initial state $s_0$, and reference $\cfgnt{r}^\prime$ such that the following conditions hold:
+%\begin{align}
+%s_s &= \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp \\
+%s_s &\cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp \\
+%\cfgnt{r}^\prime &= \mathrm{fresh}_r\lp \rp \\
+%\pi_{n+1} &=\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp \\
+%s_s &\rightarrow_s s_s^\prime
+%\end{align}
+%%$$s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$$ 
+%%$$s_s \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp$$ 
+%%$$\pi_{n+1} =\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp$$ 
+%
+%then 
+%$$s_s^\prime \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_{n+1} \rp$$
+If there exists states $s_\ell$ and $s_s$ such that $s_s \in \mathcal{FA}$ and $s_\ell \sqsubset s_s$, then:
+\begin{equation}
+\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\end{equation}
+and
+\begin{equation}
+\forall s_s^\prime ( s_s \rightarrow_s s_s^\prime\Rightarrow \exists s_\ell^\prime( (s_\ell \rightarrow_\ell s_\ell^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\end{equation}
 \end{lemma}
@@
 Begin by assuming the conditions stated in Lemma~\ref{lem:access}.
-We will consider two cases for this proof.
-In the first case, we assume that all of the fields involved in the read are initialized.
-In the second case we consider uninitialized fields.
-
-Case 1: Suppose all of the pertinent fields in $s_s$ are initialized.
+By Lemma~\ref{lem:init}, the summary intermediate state is equivalent to the set of lazy intermediate states, so we may assume without loss of generality that all of the pertinent fields in $s_s$ are initialized.
 Take an arbitrary lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$.
@@
 This fact, and the fact that $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, means that by Definition~\ref{representation} we know $s_\ell^\prime \sqsubset s_s^\prime$.
-We have now shown that for any lazy state $s_\ell$:
+We have now shown that:
 \begin{equation}
-\label{eqn:slimpliesslprime}
-s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime
+\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
 \end{equation}
 
-Since there is only one possible control flow sequence $\pi_{n+1}$, this means that if $s_\ell \rightarrow_\ell s_\ell^\prime$, then 
-\begin{equation}
-\label{eqn:slimpliesslprime2}
-s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime\ \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})
-\end{equation}
+%for any lazy state $s_\ell$: 
+%\begin{equation}
+%\label{eqn:slimpliesslprime}
+%s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime
+%\end{equation}
 
-Combining Equations \ref{eqn:slimpliesslprime} and \ref{eqn:slimpliesslprime2}, we may finally conclude that $s_s^\prime$ is complete with respect to $\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$
-\begin{equation}
-\label{eqn:readforwards}
-s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1}) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime
-\end{equation}
+%Since there is only one possible control flow sequence $\pi_{n+1}$, this means that if $s_\ell \rightarrow_\ell s_\ell^\prime$, then 
+%\begin{equation}
+%\label{eqn:slimpliesslprime2}
+%s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime\ \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})
+%\end{equation}
+%
+%Combining Equations \ref{eqn:slimpliesslprime} and \ref{eqn:slimpliesslprime2}, we may finally conclude that $s_s^\prime$ is complete with respect to $\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$
+%\begin{equation}
+%\label{eqn:readforwards}
+%s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1}) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime
+%\end{equation}
 
@@
 
-Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$, but $s_i^\prime \notin \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
+Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$.
 Since $s_i^\prime \sqsubset s_s^\prime$, then by Definition~\ref{representation}, we know there exists a homomorphism $s_i^\prime \rightharpoonup_{h^\prime} s_s^\prime$, and that $\mathbb{S}( \phi_i^\prime \wedge \mathbb{HC}(s_i^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$.
@@
 Observe that by Definition~\ref{def:homomorphism} $s_i \rightharpoonup_{h_i} s_s$,  and that $\mathbb{S}( \phi_i \wedge \mathbb{HC}(s_i \rightharpoonup_{h_i} s_s) )$, so $s_i \sqsubset s_s$.
-Since $s_s$ is exact, $s_i \in\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$.
+Therefore:
+\begin{equation}
+\forall s_s^\prime ( s_s \rightarrow_s s_s^\prime\Rightarrow \exists s_\ell^\prime( (s_\ell \rightarrow_\ell s_\ell^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\end{equation}
+ This concludes the proof.
+
+%Since $s_s$ is exact, $s_i \in\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$.
 Combining this with the fact that $s_i \rightarrow_\ell s_i^\prime$, we conclude that $s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
 We have a contradiction.
+%
+% Therefore, $s_s^\prime$ is sound with respect to $\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$:
+% \begin{equation}
+% \label{eqn:readbackwards}
+% s_i^\prime \sqsubset s_s^\prime \Rightarrow s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})
+% \end{equation}
+%Since $s_s$ is both sound and complete, we may combine Equations \ref{eqn:readforwards} and \ref{eqn:readbackwards} to find that 
+%$$s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1}) \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$
+%By Definition~\ref{equivalent}, $s_s^\prime \cong \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, and so by Definition~\ref{exact}, $s_s^\prime$ is exact.
 
- Therefore, $s_s^\prime$ is sound with respect to $\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$:
- \begin{equation}
- \label{eqn:readbackwards}
- s_i^\prime \sqsubset s_s^\prime \Rightarrow s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})
- \end{equation}
-Since $s_s$ is both sound and complete, we may combine Equations \ref{eqn:readforwards} and \ref{eqn:readbackwards} to find that 
-$$s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1}) \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$
-By Definition~\ref{equivalent}, $s_s^\prime \cong \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, and so by Definition~\ref{exact}, $s_s^\prime$ is exact.
-
-Case 2: If there are uninitialized fields, then the lazy initialization machine will make an intermediate state $s_t$.
+%Case 2: If there are uninitialized fields, then the lazy initialization machine will make an intermediate state $s_t$.
 By Lemma~\ref{lem:init}, the summary intermediate state is equivalent to the set of lazy intermediate states.
@@
 \label{lem:write}
-If $s_s \cong \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n )$ for some symbolic state $s_s$, initial state $s_0$, and control flow path $\pi_n$, and if $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then:
-$$s_\ell^\prime \sqsubset s_s^\prime \Leftrightarrow s_\ell^\prime \in \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) ) $$
-
+%If $s_s \cong \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n )$ for some symbolic state $s_s$, initial state $s_0$, and control flow path $\pi_n$, and if $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then:
+%$$s_\ell^\prime \sqsubset s_s^\prime \Leftrightarrow s_\ell^\prime \in \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) ) $$
+If there exists states $s_\ell$ and $s_s$ such that $s_s \in \mathcal{FW}$ and $s_\ell \sqsubset s_s$, then:
+\begin{equation}
+\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\end{equation}
+and
+\begin{equation}
+\forall s_s^\prime ( s_s \rightarrow_s s_s^\prime\Rightarrow \exists s_\ell^\prime( (s_\ell \rightarrow_\ell s_\ell^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\end{equation}
 \end{lemma}
@@
 
-The first step is to show that $s_s^\prime$ is complete with respect to the feasible set.
+The first step is to show that there exists a state $s_s^\prime$ that is complete with respect to the feasible set.
+Take state $s_s$ and compute state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$.
 Take any lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$, and find state $s_\ell^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$.
@@
 
-Establishing the fact that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$ is left as an exercise to the reader.
+Establishing the fact that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$ is left as an exercise to the reader (waving hands in the air).
 
-By proving the existence of a valid homomorphism, we have shown that if $s_\ell \sqsubset s_s$, $s_\ell \rightarrow_\ell s_\ell^\prime$, and $s_s \rightarrow_s s_s^\prime$, then $s_\ell^\prime \sqsubset s_s^\prime$.
-Since $s_s \cong \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n )$, and since $\pi_n (\eta\ \cfgnt{k}\ \emptyset)$  is the only possible control flow sequence from state $s_s$ or any state $s_\ell$ where $s_\ell \sqsubset s_s$, we may deduce that $\{ s_\ell^\prime | \exists s_\ell (s_\ell \sqsubset s_s \wedge s_\ell \rightarrow_\ell s_\ell^\prime ) \} = \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) )$.
-Therefore, $s_\ell^\prime \in \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$.
+By proving the existence of a valid homomorphism, we have shown that for any state $s_\ell^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$, then the state $s_s^\prime$ such that $s_s \rightarrow_s s_\ell^\prime$ represents $s_\ell^\prime$.
+Therefore, $\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )$.
 This concludes the proof of completeness.
@@
 Because $s_s$ is exact, $s_\ell^\prime$ must be a part of the feasible set.
+Therefore, $\forall s_s^\prime ( s_s \rightarrow_s s_s^\prime\Rightarrow \exists s_\ell^\prime( (s_\ell \rightarrow_\ell s_\ell^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )$.
 
@@
 \label{lem:compare}
-If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then $s_s^\prime$ is equal to $ \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_{s^\prime}\ \eta\ \cfgnt{v}_{s^\prime}\ \cfgnt{k}\rp$ and is exact with respect to $s_0$ and $\pi_n \ (\eta\ \cfgnt{v}_{s^\prime}\ \cfgnt{k})$.
+%If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then $s_s^\prime$ is equal to $ \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_{s^\prime}\ \eta\ \cfgnt{v}_{s^\prime}\ \cfgnt{k}\rp$ and is exact with respect to $s_0$ and $\pi_n \ (\eta\ \cfgnt{v}_{s^\prime}\ \cfgnt{k})$.
+If there exists states $s_\ell$ and $s_s$ such that $s_s \in \mathcal{RC}$ and $s_\ell \sqsubset s_s$, then:
+\begin{equation}
+\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\end{equation}
+and
+\begin{equation}
+\forall s_s^\prime ( s_s \rightarrow_s s_s^\prime\Rightarrow \exists s_\ell^\prime( (s_\ell \rightarrow_\ell s_\ell^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\end{equation}
 \end{lemma}
 There are two rules that apply to state $s_s$, one for the $\cfgt{true}$ branch and one for the $\cfgt{false}$ branch.
-Since the proofs for both rules are nearly identical, for brevity we will only show the proof for the case for the $\cfgt{true}$ branch.
+Since the proofs for both rules are nearly identical, for brevity we will only show the proofs for the case for the $\cfgt{true}$ branch.
 \begin{proof}
-Choose any $s_\ell \sqsubset s_s$, and let $\zeta_T = \mathbb{FS}(\rightarrow_{\ell},s_0,(\pi_n,(\eta\ \cfgt{true}\ \cfgnt{k})))$.
-Since $s_s$ is exact, we know that $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, $s_l = \lp \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$, and that there exists a homomorphism $s_\ell \rightharpoonup_{h} s_s$ such that $\mathbb{S}( \phi_s \wedge \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s) ) $.
-Depending on the values of $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, there are two different rules that might apply to $s_\ell$.
-%I'm not sure we actually use this fact anywhere
- %In either case, $\cfgnt{L}_\ell$ and $\cfgnt{R}_\ell$ are unchanged, and $\phi_\ell$ is strengthened, so we already know that 
-%$$ \zeta_T \subseteq \{s_\ell^\prime | \exists s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n}) (s_\ell \rightarrow_\ell s_\ell^\prime )\}$$
+Assume there exists states $s_\ell$ and $s_s$ such that $s_s \in \mathcal{RC}$ and $s_\ell \sqsubset s_s$.
+Let $s_s^\prime$ be any state such that $s_s \rightarrow_s s_s$ and let $\zeta_T = \forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime )$.
+Since $s_\ell \sqsubset s_s$, we know that $s_\ell \in \mathcal{RC}$, and that there exists a homomorphism $s_\ell \rightharpoonup_{h} s_s$ such that $\mathbb{S}( \phi_s \wedge \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s) ) $.
+We partition $\zeta_T$ based on the values of $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$ as follows: Let
+$$\zeta_t = \zeta_T \setminus \{ s_f | (s_f= \lp \cfgnt{L}_f\ \cfgnt{R}_f\ \phi_\ell\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp) \wedge (\cfgnt{L}_f \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_f \lp \cfgnt{r}_1 \rp ) \}$$
+and let
+$$\zeta_f = \zeta_T \setminus \zeta_t$$
 
-Case 1: Assume $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp = \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, and let 
-$$\zeta_t = \zeta_T \setminus \{ s_f | (s_f= \lp \cfgnt{L}_f\ \cfgnt{R}_f\ \phi_\ell\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp) \wedge (\cfgnt{L}_f \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_f \lp \cfgnt{r}_1 \rp ) \}$$
-In this case, the lazy ``equals - references true" rule applies, and we know state $s_\ell^\prime : s_\ell \rightarrow_\ell s_\ell^\prime$ is in $\zeta_t$.
+Furthermore, there are two possible configurations for $s_s^\prime$: $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp $ and $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp $.
+We now consider the partitions of $\zeta_T$ and configurations of $s_s^\prime$ in separate cases.
+
+Case 1: Assume that $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp = \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$. 
+Compute state $s_\ell^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$.
+In this case, the lazy ``equals - references true" rule applied, therefore $s_\ell^\prime$ is in $\zeta_t$.
 Observe that by applying Theorem~\ref{thm:mutex}, $\phi_s^\prime \wedge \phi_0 \wedge \phi_1$ reduces to $\phi_s$.
 Therefore, $\mathbb{S}( \phi_s^\prime \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h} s_s^\prime) ) $ is true, and by extension, $s_\ell^\prime \sqsubset s_s^\prime$.
-Since this relation holds for arbitrary $s_\ell^\prime \in \zeta_t$, we now know that $$s_\ell^\prime \in \zeta_t \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$$
-Now we prove the case for the other direction.
-Consider a state $s_s^\prime$ where  $s_s \rightarrow_s s_s^\prime$.
-Define $\theta_\alpha$, $\theta_0$ and $\theta_1$ as in the ``equals (references-true) rule''.
+Since this relation holds for arbitrary $s_\ell^\prime \in \zeta_t$, we now know that
+\begin{equation}
+\label{eqn:RCForwardsTrue}
+((\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp = \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp) \wedge (s_\ell^\prime \in \zeta_t)) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime
+\end{equation}
+
+Case 2:  Assume that $s_s^\prime$ has the form $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp $, and define $\theta_\alpha$, $\theta_0$ and $\theta_1$ as in the ``equals (references-true) rule''.
 Since $\cfgnt{L}_s$ and $\cfgnt{R}_s$ are unchanged from $s_s$, and $\phi_s^\prime$ is only a strengthened version of $\phi_s$,  we know that
-$$\{s_\ell^\prime | s_\ell^\prime \sqsubset s_s^\prime \} \subseteq \{s_\ell^\prime | \exists s_\ell \lp s_\ell \sqsubset s_s \rp \wedge s_\ell \rightarrow_s s_\ell^\prime\} $$
-Suppose that there exists state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$ and $s_i^\prime \notin \zeta_t$.
-Because of the above conclusion, we know that $$s_i^\prime \in \{s_\ell^\prime | \exists s_\ell \lp s_\ell \sqsubset s_s\rp \wedge s_\ell \rightarrow_s s_\ell^\prime\}$$
+\begin{equation}
+\label{eqn:RCSubset}
+\{s_\ell^\prime | s_\ell^\prime \sqsubset s_s^\prime \} \subseteq \{s_\ell^\prime | \exists s_\ell \lp s_\ell \sqsubset s_s \rp \wedge s_\ell \rightarrow_s s_\ell^\prime\}
+\end{equation}
+Suppose that there exists state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$ and $s_i^\prime \notin \zeta_t$. Because of Equation \ref{eqn:RCSubset}, we know that 
+$$s_i^\prime \in \{s_\ell^\prime | \exists s_\ell \lp s_\ell \sqsubset s_s\rp \wedge s_\ell \rightarrow_s s_\ell^\prime\}$$ 
 Combining this with the assumption that $s_i^\prime \notin \zeta_t$, we must conclude that $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp \neq  \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$.
@@
 $$\{\phi_i \mid \exists \phi_\alpha (\phi_\alpha \in \lp \theta_0 \cup \theta_1 \rp)\wedge \lp \phi_i = \phi_\alpha \wedge \phi_0 \wedge \phi_1 \rp\}$$ 
-is valid.
-Either way, $\mathbb{S}\lp\phi_i^\prime \wedge\phi_0\wedge \phi_1\rp$ is false and $s_s^\prime$ does not represent $s_i^\prime$.
-We have a contradiction.
-Therefore: $$s_\ell^\prime \sqsubset s_s^\prime \Rightarrow s_\ell^\prime \in \zeta_t$$
-Combining this with our previous result, we conclude that $$s_\ell^\prime \in \zeta_t \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$
+is valid. Either way, $\mathbb{S}\lp\phi_i^\prime \wedge\phi_0\wedge \phi_1\rp$ is false and $s_s^\prime$ does not represent $s_i^\prime$. We have a contradiction. Therefore: 
+\begin{equation}
+\label{eqn:RCBackwardsTrue}
+((s_s^\prime=\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp) \wedge (s_\ell^\prime \sqsubset s_s^\prime)) \Rightarrow s_\ell^\prime \in \zeta_t
+\end{equation}
 
-Case 2: Assume $s_\ell : \cfgnt{L}_\ell \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$, and let 
-$$\zeta_f = \zeta_T \setminus \{ s_t | \cfgnt{L}_t \lp \cfgnt{r}_0\rp = \cfgnt{L}_t \lp \cfgnt{r}_1 \rp \}$$ 
+Case 3: Assume that $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$.
 This means that the lazy ``equals - references false" rule applies.
-The proof for the ``equals - references false" rule is highly similar to the proof for ``equals - references true", so we omit it for the sake of brevity.
+The proof for the ``equals - references false" rule is highly similar to the proof for Case 1, so we omit it for the sake of brevity.
 The result for this case is:
-$$s_\ell^\prime \in \zeta_f \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$
+\begin{equation}
+\label{eqn:RCForwardsFalse}
+((\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp = \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp) \wedge (s_\ell^\prime \in \zeta_t)) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime
+\end{equation}
 
-Since $\zeta_T = \zeta_t \cup \zeta_f$, we can combine the results of the two cases to find that 
-$$s_\ell^\prime \in \zeta_T \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$
- By Definition~\ref{equivalent}, $s_s^\prime \equiv \zeta_T$, and by Definition~\ref{exact}, $s_s^\prime$ is exact.
+Case 4: Assume that $s_s^\prime$ has the form $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp $.
+The proof for this case is highly similar to the proof for Case 2, so we omit it for the sake of brevity. The result for this case is:
+\begin{equation}
+\label{eqn:RCBackwardsFalse}
+s_s^\prime=\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp \wedge s_\ell^\prime \sqsubset s_s^\prime \Rightarrow s_\ell^\prime \in \zeta_f
+\end{equation}
+
+Since $\zeta_T = \zeta_t \cup \zeta_f$, we can combine Equation \ref{eqn:RCForwardsTrue} with \ref{eqn:RCForwardsFalse} to find that 
+\begin{equation}
+\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\end{equation}
+Likewise, we can combine Equation \ref{eqn:RCBackwardsTrue} with Equation \ref{eqn:RCBackwardsFalse} to find that
+\begin{equation}
+\forall s_s^\prime ( s_s \rightarrow_s s_s^\prime\Rightarrow \exists s_\ell^\prime( (s_\ell \rightarrow_\ell s_\ell^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\end{equation}
 \end{proof}
 
-\begin{theorem}[Exactness of Summary Machine States]
-If $\Pi_n^s$ is a feasible summary state sequence, then the final state in $\Pi_n^s$ is equivalent to the feasible set of lazy states sharing the same control flow sequence:
+\begin{lemma}[Exactness of New Rule]
+\label{lem:new}
+If there exists states $s_\ell$ and $s_s$ such that $s_s \in \mathcal{NW}$ and $s_\ell \sqsubset s_s$, then:
 \begin{equation}
-\mathit{last}(\Pi_n^s) \cong \mathbb{FS}(\rightarrow_\ell, \mathit{first}(\Pi_n^s), \mathbb{CF}(\Pi_n^s) )
+\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
 \end{equation}
-\end{theorem}
+and
+\begin{equation}
+\forall s_s^\prime ( s_s \rightarrow_s s_s^\prime\Rightarrow \exists s_\ell^\prime( (s_\ell \rightarrow_\ell s_\ell^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\end{equation}
+
 \begin{proof}
-The proof will proceed inductively.
+The proof is left as an exercise to the reader.
+\end{proof}
 
-Base case: For any initial state $s_0$, the feasible state set contains a single element, $\{s_0\}$:
-$$\mathbb{FS}(\rightarrow_\ell, (s_0), \mathbb{CF}(s_0)) = \{s_0\}$$
-We can define a homomorphism from $s_0$ to $s_0$ using the identity function: 
-$$\forall a \in \cfgnt{L}_0^\rightarrow ( h(a) = a )$$ 
-Because the only constraints in the heap are $\mathit{true}$, the heap constraint evaluates to $\mathit{true}$.
+\end{lemma}
+
+%\begin{theorem}[Exactness of Summary Machine States]
+%If $\Pi_n^s$ is a feasible summary state sequence, then the final state in $\Pi_n^s$ is equivalent to the feasible set of lazy states sharing the same control flow sequence:
+%\begin{equation}
+%\mathit{last}(\Pi_n^s) \cong \mathbb{FS}(\rightarrow_\ell, \mathit{first}(\Pi_n^s), \mathbb{CF}(\Pi_n^s) )
+%\end{equation}
+%\end{theorem}
+%\begin{proof}
+%The proof will proceed inductively.
+%
+%Base case: For any initial state $s_0$, the feasible state set contains a single element, $\{s_0\}$:
+%$$\mathbb{FS}(\rightarrow_\ell, (s_0), \mathbb{CF}(s_0)) = \{s_0\}$$
+%We can define a homomorphism from $s_0$ to $s_0$ using the identity function: 
+%$$\forall a \in \cfgnt{L}_0^\rightarrow ( h(a) = a )$$ 
+%Because the only constraints in the heap are $\mathit{true}$, the heap constraint evaluates to $\mathit{true}$.
 Since $phi_0$ also evaluates to $\mathit{true}$, the expression $\mathbb{S}(\phi_0 \wedge \mathbb{HC}(s_0 \rightarrow_h s_0 ) ) $ must evaluate to true.
 Thus, any state in the feasible set must be represented by $s_0$: :
-$$s_0 \in \mathbb{FS}(\rightarrow_\ell,s_0, (\eta_0\ e_0\ k_0) ) \Rightarrow s_0 \sqsubset s_0$$
-Furthermore, since every reference points to a single place, there is only one possible represented heap. Thus:
-$$ \{s_0\} = \mathbb{FS}(\rightarrow_\ell,s_0, (\eta_0\ e_0\ k_0) )$$
-Since $s_0$ is the only represented heap, and since we know $s_0$ is in the feasible set, 
-$$s_0 \sqsubset s_0 \Leftrightarrow s_0 \in \{s_0\}$$
-We have now shown that $s_0 \cong \mathbb{FS}(\rightarrow_\ell, (s_0), \mathbb{CF}(s_0))$ for an arbitrary initial state $s_0$.
+%$$s_0 \in \mathbb{FS}(\rightarrow_\ell,s_0, (\eta_0\ e_0\ k_0) ) \Rightarrow s_0 \sqsubset s_0$$
+%Furthermore, since every reference points to a single place, there is only one possible represented heap. Thus:
+%$$ \{s_0\} = \mathbb{FS}(\rightarrow_\ell,s_0, (\eta_0\ e_0\ k_0) )$$
+%Since $s_0$ is the only represented heap, and since we know $s_0$ is in the feasible set, 
+%$$s_0 \sqsubset s_0 \Leftrightarrow s_0 \in \{s_0\}$$
+%We have now shown that $s_0 \cong \mathbb{FS}(\rightarrow_\ell, (s_0), \mathbb{CF}(s_0))$ for an arbitrary initial state $s_0$.
 Since every feasible state sequence starts with an initial state, we now know that:
- $$\mathit{last}(\Pi_1^s) \cong \mathbb{FS}(\rightarrow_\ell, \mathit{first}(\Pi_1^s), \mathbb{CF}(\Pi_1^s) ) $$
-
-Inductive step: If summary state $s_s$ is exact, then any state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$ is also exact.
+% $$\mathit{last}(\Pi_1^s) \cong \mathbb{FS}(\rightarrow_\ell, \mathit{first}(\Pi_1^s), \mathbb{CF}(\Pi_1^s) ) $$
+%
+%Inductive step: If summary state $s_s$ is exact, then any state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$ is also exact.
 Suppose $s_s$ has the form for a field read, field write, or reference compare rule.
 By Lemmas \ref{lem:access}, \ref{lem:write}, and \ref{lem:compare}, $s_s^\prime$ will also be exact.
-Suppose $s_s$ is accepted by the "new" rule.
+%Suppose $s_s$ is accepted by the "new" rule.
 In this case, the new reference points to the new location on condition true, so it's obvious that $s_s$ represents all of the proper lazy states, and the existence of any infeasible lazy states represented by $s_s^\prime$ would imply that $s_s$ is not exact.
-For all the other rules, the L and R functions and $\phi$ are unchanged, and the rules for  $\eta$, $e$, and $k$ are exactly the same between the lazy and summary machines, so there is a bijective mapping between the represented states in $s_s$ and $s_s^\prime$.
-Thus, in all cases, if $s_s$ is exact, then $s_s^\prime$ is also exact.
+%For all the other rules, the L and R functions and $\phi$ are unchanged, and the rules for  $\eta$, $e$, and $k$ are exactly the same between the lazy and summary machines, so there is a bijective mapping between the represented states in $s_s$ and $s_s^\prime$.
+%Thus, in all cases, if $s_s$ is exact, then $s_s^\prime$ is also exact.
+%
+%We have now shown that any feasible state sequence $\Pi_n^s$ is exact if the sub-sequence $\Pi_{n-1}^s$ is exact.
+%
+%Combining the result from the inductive step with the result from the base case, we can now say with certainty that for all $n$,
+%
+%$$\mathit{last}(\Pi_n^s) \cong \mathbb{FS}(\rightarrow_\ell, \mathit{first}(\Pi_n^s), \mathbb{CF}(\Pi_n^s) ) $$
+%
+%\end{proof}
 
-We have now shown that any feasible state sequence $\Pi_n^s$ is exact if the sub-sequence $\Pi_{n-1}^s$ is exact.
+\begin{theorem}
+The representation relation $\sqsubset$ is a bisimulation.
+\end{theorem}
 
-Combining the result from the inductive step with the result from the base case, we can now say with certainty that for all $n$,
-
-$$\mathit{last}(\Pi_n^s) \cong \mathbb{FS}(\rightarrow_\ell, \mathit{first}(\Pi_n^s), \mathbb{CF}(\Pi_n^s) ) $$
+\begin{proof}
+Take any two states $s_\ell$ and $s_s$ such that $s_\ell \sqsubset s_s$.
+If $s_s \in \mathcal{FA} \cup \mathcal{FW} \cup \mathcal{RC} \cup \mathcal{NW}$, then by Lemmas \ref{lem:access}, \ref{lem:write}, \ref{lem:compare}, and \ref{lem:new} we know Equations \ref{eqn:BisimulationForwards} and \ref{eqn:BisimulationBackwards} hold.
+If $s_s$ has any other form, the heap is not modified for $s_\ell^\prime$ or $s_s^\prime$, so then Equations \ref{eqn:BisimulationForwards} and \ref{eqn:BisimulationBackwards} hold by default.
+Thus, Equations \ref{eqn:BisimulationForwards} and \ref{eqn:BisimulationBackwards} hold for all  $s_\ell$ and $s_s$ such that $s_\ell \sqsubset s_s$.
+By Definition \ref{bisimulation}, $\sqsubset$ is a bisimulation.
 

### 2014-09-15 tex/definitions.tex
Fixed some typos in the definitions.

@@
 \begin{definition}
-A \textbf{state transition function} $\rightarrow_{\Phi}$ is a mapping $\rightarrow_{\Phi} : s \mapsto s$, which takes one machine state and transforms it into another machine state.
-Two important state transition functions are the \textbf{lazy state transition function} $\rightarrow_\ell$ and the \textbf{summary state transition function} $\rightarrow_s$.
+A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times \mathcal{S} $, which relates machine states with successor states.
+Two important state transition relations are the \textbf{lazy state transition relation} $\rightarrow_\ell$ and the \textbf{summary state transition relation} $\rightarrow_s$.
 \end{definition}
 
-\begin{definition}
-A \textbf{state sequence} is a sequence of states denoted as $\Pi_n = s_0,s_1,...,s_n$.
+%\begin{definition}
+%A \textbf{state sequence} is a sequence of states denoted as $\Pi_n = s_0,s_1,...,s_n$.
 A \textbf{feasible state sequence}, $\Pi_n^\phi = s_0,s_1,...,s_n$ is consistent with the transition: $\forall i\ (0 \leq i < n \Rightarrow s_i \rightarrow_{\Phi} s_{i+1})$, where $s_0\in \mathcal{S}_0$.
-\end{definition}
-
-%For 
-\begin{comment}
-\begin{definition}
-A \textbf{feasible state sequence} is defined as a sequence of states resulting from repeated application of the state transition relation to some initial state $s_0\in \mathcal{S}_0$: $$\Pi_n = s_0,s_1,...,s_n$$ where the relation $s_i \rightarrow_{\Phi} s_{i+1}$ holds for all $i \in \{ i | 0 \leq i < n \}$
-\end{definition}
-\end{comment}
+%\end{definition}
+%
+%%For 
+%\begin{comment}
+%\begin{definition}
+%A \textbf{feasible state sequence} is defined as a sequence of states resulting from repeated application of the state transition relation to some initial state $s_0\in \mathcal{S}_0$: $$\Pi_n = s_0,s_1,...,s_n$$ where the relation $s_i \rightarrow_{\Phi} s_{i+1}$ holds for all $i \in \{ i | 0 \leq i < n \}$
+%\end{definition}
+%\end{comment}
 
 %For these definitions, we should bring in the notion of 
-\begin{definition}
-The set of \textbf{lazy states} $\mathcal{S}_\ell$ is defined as
-\begin{align}
-\mathcal{S}_\ell = \{s_n \mid \exists \Pi_n^\ell\ (\Pi_n^\ell = s_0, \ldots, s_n)\}
-\end{align}
-\end{definition}
-
-\begin{definition}
-The set of \textbf{summary states} $\mathcal{S}_s$ is defined as
-\begin{align}
-\mathcal{S}_s = \{s_n \mid \exists \Pi_n^s\ (\Pi_n^s = s_0, \ldots, s_n)\}
-\end{align}
-\end{definition}
+%\begin{definition}
+%The set of \textbf{lazy states} $\mathcal{S}_\ell$ is defined as
+%\begin{align}
+%\mathcal{S}_\ell = \{s_n \mid \exists \Pi_n^\ell\ (\Pi_n^\ell = s_0, \ldots, s_n)\}
+%\end{align}
+%\end{definition}
+%
+%\begin{definition}
+%The set of \textbf{summary states} $\mathcal{S}_s$ is defined as
+%\begin{align}
+%\mathcal{S}_s = \{s_n \mid \exists \Pi_n^s\ (\Pi_n^s = s_0, \ldots, s_n)\}
+%\end{align}
+%\end{definition}
 
@@
 \ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha \in \mathcal{L}\ (\forall \cfgnt{l}_\beta \in \mathcal{L}\ ( \forall f \in \mathcal{F}( \exists \phi_\alpha \in \Phi(\exists \phi_\beta \in \Phi( \\
-\ \ \ \ \ \ \ \ \ \ \ \ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_x(\cfgnt{R}_x (\cfgnt{l}_\beta,f )) \Rightarrow (\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_y(\cfgnt{R}_y (h(\cfgnt{l}_\beta),f ))\ \\
+\ \ \ \ \ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_x(\cfgnt{R}_x (\cfgnt{l}_\beta,f )) \Rightarrow (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_y(\cfgnt{R}_y (h(\cfgnt{l}_\beta),f ))\ \\
 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  )) ) ) ) )
@@
 \mathbb{HC}(s_x \rightharpoonup_{h} s_y) &= \\
- \bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_x^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}^\rightarrow)\} 
+ \bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_x^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_y^\rightarrow)\} 
 \end{align*}
@@
 \label{representation}
-The \textbf{representation relation} is defined as follows: given state $s_y = ( \cfgnt{L}_y\ \cfgnt{R}_y\ \phi_y\ \eta_y\ \cfgnt{e}_y\ \cfgnt{k}_y )$ and state $s_x = ( \cfgnt{L}_x\ \cfgnt{R}_x\ \phi_x\ \eta_x\ \cfgnt{e}_x\ \cfgnt{k}_x )$, $s_y \sqsubset s_x $ if and only if $\eta_y = \eta_x ,\ \cfgnt{e}_y = \cfgnt{e}_x ,\ \cfgnt{k}_y = \cfgnt{k}_x$, and there exists a homomorphism $\ s_y \rightharpoonup_{h} s_x $ such that
+The \textbf{representation relation} $\sqsubset$ is defined as follows: given state $s_y = ( \cfgnt{L}_y\ \cfgnt{R}_y\ \phi_y\ \eta_y\ \cfgnt{e}_y\ \cfgnt{k}_y )$ and state $s_x = ( \cfgnt{L}_x\ \cfgnt{R}_x\ \phi_x\ \eta_x\ \cfgnt{e}_x\ \cfgnt{k}_x )$, $s_y \sqsubset s_x $ if and only if $\eta_y = \eta_x ,\ \cfgnt{e}_y = \cfgnt{e}_x ,\ \cfgnt{k}_y = \cfgnt{k}_x$, and there exists a homomorphism $\ s_y \rightharpoonup_{h} s_x $ such that
 \begin{equation}
@@
 
-\begin{definition}
-Given a state transition function $\rightarrow_{\Phi}$, an initial state $s_0$ and a control flow sequence $\pi_n$, the \textbf{feasible state set}, $\mathbb{FS}(\rightarrow_{\Phi},s_0,\pi_n)$, is defined as
- $$
-\begin{array}{l}
-\mathbb{FS}(\rightarrow_{\Phi},s_0,\pi_n) = \\
-\ \ \ \ \ \ \{s \mid \exists \Pi_n^\Phi\ (\pi_n = \mathbb{CF}(\Pi_n^\Phi) \wedge s \sqsubset \mathit{last}(\Pi_n^\Phi))\} 
-\end{array}
-$$
-where $\mathit{last}(\Pi_n^\Phi)$ returns the last state on the feasible sequence.
-\end{definition}
-
-\begin{definition}
-\label{equivalent}
-A summary state $s_s$ is \textbf{equivalent} to a set of lazy states $P$ if and only if $s_s$ represents every state in $P$ and represents no other state: 
-$$s_s \cong P \Leftrightarrow (\forall s_i \in \mathcal{S}\ (s_i \in P \Leftrightarrow s_i \sqsubset s_s) )$$
-\end{definition}
-
-\begin{definition}
-\label{sound}
-A state $s_s$ is \textbf{sound} with respect to a transition relation, $\rightarrow_\phi$, initial state, $s_0$, and control flow path, $\pi_n$, if and only if 
-$$ \forall s_\ell \in \mathcal{S}_\ell\ (s_\ell \sqsubset s_s \Rightarrow s_\ell \in \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n) ) $$
-\end{definition}
-
-\begin{definition}
-\label{complete}
-A state $s_s$ is \textbf{complete} with respect to a transition relation, $\rightarrow_\phi$, initial state, $s_0$, and control flow path, $\pi_n$, if and only if 
-$$ \forall s_\ell \in \mathcal{S}_\ell\ ( s_\ell \in \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)\Rightarrow s_\ell \sqsubset s_s ) $$
-\end{definition}
-
-\begin{definition}
-\label{exact}
-A state $s$ is \textbf{exact} with respect to a transition relation, $\rightarrow_\phi$, initial state, $s_0$, and control flow path, $\pi_n$, if and only if it is both sound and complete:
-$$ s \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$$
-\end{definition}
+%\begin{definition}
+%Given a state transition function $\rightarrow_{\Phi}$, an initial state $s_0$ and a control flow sequence $\pi_n$, the \textbf{feasible state set}, $\mathbb{FS}(\rightarrow_{\Phi},s_0,\pi_n)$, is defined as
+% $$
+%\begin{array}{l}
+%\mathbb{FS}(\rightarrow_{\Phi},s_0,\pi_n) = \\
+%\ \ \ \ \ \ \{s \mid \exists \Pi_n^\Phi\ (\pi_n = \mathbb{CF}(\Pi_n^\Phi) \wedge s \sqsubset \mathit{last}(\Pi_n^\Phi))\} 
+%\end{array}
+%$$
+%where $\mathit{last}(\Pi_n^\Phi)$ returns the last state on the feasible sequence.
+%\end{definition}
+%
+%\begin{definition}
+%\label{equivalent}
+%A summary state $s_s$ is \textbf{equivalent} to a set of lazy states $P$ if and only if $s_s$ represents every state in $P$ and represents no other state: 
+%$$s_s \cong P \Leftrightarrow (\forall s_i \in \mathcal{S}\ (s_i \in P \Leftrightarrow s_i \sqsubset s_s) )$$
+%\end{definition}
+%
+%\begin{definition}
+%\label{sound}
+%A state $s_s$ is \textbf{sound} with respect to a transition relation, $\rightarrow_\phi$, initial state, $s_0$, and control flow path, $\pi_n$, if and only if 
+%$$ \forall s_\ell \in \mathcal{S}_\ell\ (s_\ell \sqsubset s_s \Rightarrow s_\ell \in \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n) ) $$
+%\end{definition}
+%
+%\begin{definition}
+%\label{complete}
+%A state $s_s$ is \textbf{complete} with respect to a transition relation, $\rightarrow_\phi$, initial state, $s_0$, and control flow path, $\pi_n$, if and only if 
+%$$ \forall s_\ell \in \mathcal{S}_\ell\ ( s_\ell \in \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)\Rightarrow s_\ell \sqsubset s_s ) $$
+%\end{definition}
+%
+%\begin{definition}
+%\label{exact}
+%A state $s$ is \textbf{exact} with respect to a transition relation, $\rightarrow_\phi$, initial state, $s_0$, and control flow path, $\pi_n$, if and only if it is both sound and complete:
+%$$ s \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$$
+%\end{definition}

### 2014-09-29 tex/definitions.tex
Rewrite some of mutual exclusion

@@
 \begin{definition}
-A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times \mathcal{S} $, which relates machine states with successor states.
-Two important state transition relations are the \textbf{lazy state transition relation} $\rightarrow_\ell$ and the \textbf{summary state transition relation} $\rightarrow_s$.
+A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times \mathcal{S} $, which relat
+es machine states with successor states.
+Two important state transition relations are the \textbf{lazy state transition relation} $\rightarrow_\ell$ and the \textbf{summary state transition relation} $\rightarrow_\varsigma$.
+Each of these use a separate relation for initialization: $\rightarrow_I$ for initialization the lazy transition relation and $\rightarrow_S$ for initialization the summary transition relation.
+All of these transition relations are defined in \figref{fig:lazy}, \figref{fig:lazyInit}, \figref{fig:sym}, and \figref{fig:symInit}.
 \end{definition}
 
+\begin{definition}
+A state $s = (\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k})$ is a \textbf{lazy state} if and only if $\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (|\cfgnt{L}(\cfgnt{r})| = 1)$]
+\end{definition}
+
+\begin{definition}
+A state $s = (\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k})$ is a \textbf{summary state} if and only if 
+$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (|\cfgnt{L}(\cfgnt{r})| \ge 1)$.
+A lazy state is also a summary state by definition.
+\end{definition}
+
+\begin{definition}
+A heap, $(\cfgnt{L}\ \cfgnt{R})$, is \textbf{location mutual exclusive} if and only if 
+\[
+\begin{array}{l}
+\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi_\alpha\ \cfgnt{l}_\alpha),(\phi_\beta\ \cfgnt{l}_\beta) \in \cfgnt{L}{r}\ (\\
+\ \ \ \ \cfgnt{l}_\alpha \neq \cfgnt{l}_\beta \Rightarrow \phi_\alpha \wedge \phi_\beta = \cfgt{false}))
+\end{array}
+\]
+\end{definition}
 %\begin{definition}
@@
 \begin{definition}
-Given a sequence of states $$\Pi_n = s_0,s_1,...,s_n$$ where $$s_i = ( \mu_i\ \cfgnt{L}_i\ \cfgnt{R}_i\ \phi_i\ \eta_i\ \cfgnt{e}_i\ \cfgnt{k}_i )$$ the \textbf{control flow sequence} of $\Pi_n$ is the defined as the sequence of tuples $$ \pi_n = \mathbb{CF}(\Pi_n) = (\eta_0\ \cfgnt{e}_0\ \cfgnt{k}_0),(\eta_1\ \cfgnt{e}_1\ \cfgnt{k}_1),...,(\eta_n\ \cfgnt{e}_n\ \cfgnt{k}_n)$$
+Given a sequence of states $$\Pi_n = s_0,s_1,...,s_n$$ where $$s_i = (\cfgnt{L}_i\ \cfgnt{R}_i\ \phi_i\ \eta_i\ \cfgnt{e}_i\ \cfgnt{k}_i )$$ the \textbf{control flow sequence} of $\Pi_n$ is the defined as the sequence of tuples $$ \pi_n = \mathbb{CF}(\Pi_n) = (\eta_0\ \cfgnt{e}_0\ \cfgnt{k}_0),(\eta_1\ \cfgnt{e}_1\ \cfgnt{k}_1),...,(\eta_n\ \cfgnt{e}_n\ \cfgnt{k}_n)$$
 \end{definition}
@@
  s_x \rightharpoonup_{h} s_y \Leftrightarrow \\
-\ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha \in \mathcal{L}\ (\forall \cfgnt{l}_\beta \in \mathcal{L}\ ( \forall f \in \mathcal{F}( \exists \phi_\alpha \in \Phi(\exists \phi_\beta \in \Phi( \\
+\ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}( \exists \phi_\alpha\ (\exists \phi_\beta\ ( \\ 
 \ \ \ \ \ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_x(\cfgnt{R}_x (\cfgnt{l}_\beta,f )) \Rightarrow (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_y(\cfgnt{R}_y (h(\cfgnt{l}_\beta),f ))\ \\
@@
 $$
+\begin{comment}
+$$
+\begin{array}{l}
+s_x \rightharpoonup_{h} s_y \Leftrightarrow \\
+\ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathit{fields}(\mathrm{type}(\cfgnt{l}_\beta))\ ( \\
+\ \ \ \ \ \ \ \ \ \ \ \ \forall (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_x(\cfgnt{R}_x (\cfgnt{l}_\beta,f ))\ ( \\
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \exists \phi_\beta\ ((\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_y(\cfgnt{R}_y (h(\cfgnt{l}_\beta),f )))))))\\
+\end{array}
+$$
+\end{comment}
 \end{definition}

### 2014-09-29 tex/proofs.tex
Rewrite some of mutual exclusion

@@
 \subsection{Theorems}
-%\begin{lemma}
-%\label{lem:lazyrefprops}
-%For any lazy state $s_\ell = ( \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta_\ell\ \cfgnt{e}_\ell\ \cfgnt{k}_\ell )$, for any reference $r \in \cfgnt{L}_\ell^\leftarrow$, 
-%$$ | \cfgnt{L}_\ell ( r) | = 1 $$
-%\end{lemma}
-%
-%\begin{proof}
-%In every rule in the Lazy machine that establishes a reference mapping, the value set contains exactly one location, constraint pair. 
-%\end{proof}
+\begin{lemma}[Location Mutual Exclusion in $\rightarrow^*_S$]
+Given a location mutual exclusive heap, $(\cfgnt{L}_0\ \cfgnt{R}_0)$, from a
+summary state with a reference $\cfgnt{r}$ and field $\cfgnt{f}$, the
+new heap, $(\cfgnt{L}^\prime\ \cfgnt{R}^\prime)$, from the summary
+initialization machine, $(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f})
+\rightarrow^*_S
+(\cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \cfgnt{r}\ \cfgnt{f})$, after any number of machine steps, is also
+location mutual exclusive.
+\end{lemma}
+\begin{proof}
+Induction over the number of machine steps on the summary initialization machine in \figref{fig:symInit}.
 
-\begin{theorem}[Mutual Exclusion]
-\label{thm:mutex}
-If we have a reachable summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, and any two pairs $(\phi_\alpha\ l_\alpha) \in \cfgnt{L}_s(r)$ and $(\phi_\beta\ l_\beta) \in \cfgnt{L}_s(r)$ such that $l_\alpha \ne l_\beta$, then
-$$(\phi_\alpha \wedge \phi_\beta) = \cfgt{false}$$
-\end{theorem}
-\begin{proof}
-The proof will proceed inductively.
+\noindent\textbf{Base Case}. The machine takes one step: $(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f})
+\rightarrow_S
+(\cfgnt{L}_1 \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f})$. Let $\Lambda = \mathbb{UN}(\cfgnt{L}_0, \cfgnt{R}_0, \cfgnt{r},
+\cfgnt{f})$ be the set of uninitialized locations. If $\Lambda = \emptyset$, then the \texttt{Summarize (end)}
+rule is active and $(\cfgnt{L}_1\ \cfgnt{R}_1) = (\cfgnt{L}_0\ \cfgnt{R}_0)$, which is location mutual exclusive by definition.
 
-Base Case: Let $s_s$ be an initial state.
-By Definition~\ref{def:initstate}, for every reference $r_i \in \cfgnt{L}_s^\leftarrow$, the set $\cfgnt{L}_s(r_i)$ contains at most one element.
-Thus, the requirement that $l_\alpha \ne l_\beta$ is never met, and the Theorem is vacuously true.
+If $\Lambda \neq \emptyset$, then the \texttt{Summarize} rule is
+active, and each new constraint location pair must be considered
+individually. These pairs are partitioned into the sets
+$\theta_\mathit{null}$, $\theta_\mathit{new}$,
+$\theta_\mathit{alias}$, and $\theta_\mathit{orig}$ by the rule. 
+\begin{itemize}
+\item Any member of $\theta_\mathit{null}$, $\theta_\mathit{new}$, and
+  $\theta_\mathit{alias}$ has a constraint of the form $\phi_x \wedge
+  \ldots$ while any member of $\theta_\mathrm{orig}$ has a constraint
+  of the form $\neg \phi_x \wedge \ldots$. As every
+  $(\phi_\mathit{orig}\ \cfgnt{l}_\mathit{orig}) \in
+  \cfgnt{L}_n(\cfgnt{R}_n(\cfgnt{l}_x,\cfgnt{f}))$ is location mutual exclusive
+  by definition, members of $\theta_\mathit{orig}$ are location
+  mutual exclusive with each other and with members in $\theta_\mathit{null}$,
+  $\theta_\mathit{new}$, and $\theta_\mathit{alias}$.
+\item Any member of $\theta_\mathit{null}$ has the form $\ldots \wedge
+  \cfgnt{r}_f = \cfgnt{r}_\mathit{null}$ while any member of
+  $\theta_\mathit{new}$ and $\theta_\mathit{alias}$ has the form
+  $\ldots \wedge \cfgnt{r}_f \neq \cfgnt{r}_\mathit{null} \wedge
+  \ldots$. As $\theta_\mathit{null}$ is a singleton set, its location is
+  location mutual exclusive from those in $\theta_\mathit{new}$ and
+  $\theta_\mathit{alias}$.
+\item Any member of $\theta_\mathit{new}$ has a constraint of the form
+  $\ldots \wedge ( \wedge_{(
+  \cfgnt{r}_a,\ \phi_a,\ l_a) \in \rho}
+  \cfgnt{r}_f \ne \cfgnt{r}_a) )$ to assert it does not
+  alias anything while any member of $\theta_\mathit{alias}$ has
+  the form $\ldots \wedge \cfgnt{r}_f = \cfgnt{r}_a \wedge \ldots$ for
+  some alias $\cfgnt{r}_a$ with both partitions reasoning over the same set of aliases $\rho$.  As $\theta_\mathit{new}$ is a singleton set, its
+  location is location mutual exclusive from any member of
+  $\theta_\mathit{alias}$.
+\item Any member of $\theta_\mathit{alias}$ has the form
+\[\ldots \wedge \cfgnt{r}_f = \cfgnt{r}_a \wedge ( \wedge_{( \cfgnt{r}^{\prime}_a\ \phi^{\prime}_a\ l^{\prime}_a)  \in \rho\ ( \cfgnt{r}^\prime_a \neq \cfgnt{r}_a) } \cfgnt{r}_f \neq \cfgnt{r}^{\prime}_a)\]
+Each is mutually exclusive over the particular alias it asserts.
+\end{itemize}
+Every member in $\theta = \theta_\mathit{null} \cup
+\theta_\mathit{new} \cup \theta_\mathit{alias} \cup
+\theta_\mathit{orig}$ is thus location mutual exclusive making $(\cfgnt{L}_1 \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f})$ location mutual exclusive as well.
 
-Inductive Step: Now we will show that if the exclusivity property holds for some state $s_s$, then it holds for any state $s_s^\prime$ where $s_s \rightarrow_s s_s^\prime$.
-In order to evaluate whether Theorem~\ref{thm:mutex} holds for state any $s_s\prime$, we must consider the rule that applied during the transition from $s_s$ to $s_s\prime$.
-There are two broad classes of rules: rules where $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$, and rules where $ \cfgnt{L}_s =  \cfgnt{L}_{s^\prime}$.
-Rules in the $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$ class modify the structure of the heap, and must be considered carefully to to consider the impact of those modifications.
-Only three rules belong to the class $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$: Field Access, Field Read, and New.
-
-We begin by considering the Field Access rule.
-Suppose $s_s$ has the form $\lp \cfgnt{L}_s\ \cfgnt{R}_{s}\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.
-In this case, the relationship between $s_s$ and $s_s^\prime$ is described by the Field Access rule.
+\noindent\textbf{Inductive Step}. The machine takes $n$-steps:
+\[
+(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f}) \rightarrow_S (\cfgnt{L}_1\ \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f}) \rightarrow_S \ldots \rightarrow_S
+(\cfgnt{L}_n\ \cfgnt{R}_n\ \cfgnt{r}\ \cfgnt{f})
+\]
+By the induction hypothesis, $(\cfgnt{L}_n\ \cfgnt{R}_n)$ is location
+mutual exclusive. This matches the base case, in that the heap on the
+left side of the transition is location mutual exclusive, and by the
+same argument as in the base case,
+$(\cfgnt{L}_{n+1}\ \cfgnt{R}_{n+1})$ is thus location mutual exclusive.
+\begin{comment}
 The Field Access rule uses the Summarize rule to describe the relation between $\cfgnt{L}_{s}$ and $\cfgnt{L}_{s^\prime}$.
@@
 So, since the mutual exclusivity property holds for $s_s$, $s_s \rightarrow_S s_1$, and $s_{i} \rightarrow_S s_{i+1} $ for all $i$ such that $0 < i < n$, we are guaranteed that the mutually exclusive property holds for the final intermediate state $s_n$.
-This concludes the inductive argument about intermediate state.
+This concludes the inductive argument about
+\end{comment}
+\end{proof}
+
+%\begin{lemma}
+%\label{lem:lazyrefprops}
+%For any lazy state $s_\ell = ( \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta_\ell\ \cfgnt{e}_\ell\ \cfgnt{k}_\ell )$, for any reference $r \in \cfgnt{L}_\ell^\leftarrow$, 
+%$$ | \cfgnt{L}_\ell ( r) | = 1 $$
+%\end{lemma}
+%
+%\begin{proof}
+%In every rule in the Lazy machine that establishes a reference mapping, the value set contains exactly one location, constraint pair. 
+%\end{proof}
+
+\begin{theorem}[Mutual Exclusion]
+\label{thm:mutex}
+If we have a reachable summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$
+$$ 
+\begin{array}{l}
+\forall (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_s(\cfgnt{r})\ (\forall (\phi_\beta\ \cfgnt{l}_\beta) \in \cfgnt{L}_s(\cfgnt{r})\ ( \\
+\ \ \ \ (\cfgnt{l}_\alpha \neq \cfgnt{l}_\beta) \Rightarrow ((\phi_\alpha \wedge \phi_\beta) = \cfgt{false})))
+\end{array}
+$$
+\end{theorem}
+\begin{proof}
+The proof will proceed inductively.
+
+Base Case: Let $s_s$ be an initial state.
+By Definition~\ref{def:initstate}, for every reference $r_i \in \cfgnt{L}_s^\leftarrow$, the set $\cfgnt{L}_s(r_i)$ contains at most one element.
+Thus, the requirement that $l_\alpha \ne l_\beta$ is never met, and the Theorem is vacuously true.
+
+Inductive Step: Now we will show that if the exclusivity property holds for some state $s_s$, then it holds for any state $s_s^\prime$ where $s_s \rightarrow_s s_s^\prime$.
+In order to evaluate whether Theorem~\ref{thm:mutex} holds for state any $s_s\prime$, we must consider the rule that applied during the transition from $s_s$ to $s_s\prime$.
+There are two broad classes of rules: rules where $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$, and rules where $ \cfgnt{L}_s =  \cfgnt{L}_{s^\prime}$.
+Rules in the $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$ class modify the structure of the heap, and must be considered carefully to to consider the impact of those modifications.
+Only three rules belong to the class $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$: Field Access, Field Read, and New.
+
+We begin by considering the Field Access rule.
+Suppose $s_s$ has the form $\lp \cfgnt{L}_s\ \cfgnt{R}_{s}\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.
+In this case, the relationship between $s_s$ and $s_s^\prime$ is described by the Field Access rule.
+intermediate state.
 

### 2014-09-30 tex/abstract.tex
updating the figures in the motivation
a stab at a new abstract

@@
-One of the fundamental challenges of using symbolic execution
-to analyze software has been the treatment of dynamically
-allocated data.
-%, i.e., programs with complex data structures with
-%unbounded domains.
-State-of-the-art symbolic execution techniques 
-have addressed this challenge by constructing the heap \emph{lazily},
-materializing objects on the concrete heap ``as needed'' and
-using non-deterministic choice points to explore each feasible
-concrete heap configuration. Because analysis of the materialized
-heap locations relies on concrete program semantics, the lazy
-initialization approach exacerbates the state space explosion
-problem that limits the scalability of symbolic execution.
-In this work we present a novel approach for lazy symbolic execution
-of heap manipulating software which utilizes 
-a fully symbolic heap constructed on-the-fly during symbolic execution.
-Our approach is 1) \emph{scalable} -- it does not
-create the additional points of non-determinism
-introduced by existing lazy initialization techniques and it explores
-each execution path only once for any given set of isomorphic heaps,
-2) \emph{precise} -- at any given point during symbolic execution, 
-the symbolic heap represents the exact set of feasible
-concrete heap structures for the program under analysis, and
-3) \emph{expressive} -- the symbolic heap can represent recursive data structures 
-and heaps resulting from loops and recursive control structures in the code. 
-We report on a case-study of an implementation of our technique in the
-Symbolic PathFinder tool to illustrate its scalability, precision
-and expressiveness. We also discuss how test case generation -- a common
- use for symbolic execution results -- can benefit from symbolic
- execution which uses a fully symbolic heap.
+A fundamental challenge of using symbolic execution for software
+analysis has been the treatment of dynamically allocated data.
+State-of-the-art techniques have addressed this challenge
+through the use of heap summaries and by constructing the concrete
+heap ``lazily.'' In this work, we present a novel heap analysis technique
+which takes inspiration from both approaches and builds exact heap summaries
+lazily during symbolic execution. Our technique enables
+exact analysis of program properties and
+analysis of arbitrary recursive data structures. It also supports
+dynamic bounds for linked data structure inputs, and
+efficient sub-division of the underlying constraint problem.
+We demonstrate the precision and scalability of our approach
+in the Symbolic PathFinder framework for analyzing Java programs.
+
+%and by using 
+%materializing objects on the concrete heap ``as needed'' and
+%using non-deterministic choice points to explore each feasible
+%concrete heap configuration.
+
+%Because analysis of the materialized
+%heap locations relies on concrete program semantics, the lazy
+%initialization approach exacerbates the state space explosion
+%problem that limits the scalability of symbolic execution.
+%In this work we present a novel approach for lazy symbolic execution
+%of heap manipulating software which utilizes 
+%a fully symbolic heap constructed on-the-fly during symbolic execution.
+%Our approach is 1) \emph{scalable} -- it does not
+%create the additional points of non-determinism
+%introduced by existing lazy initialization techniques and it explores
+%each execution path only once for any given set of isomorphic heaps,
+%2) \emph{precise} -- at any given point during symbolic execution, 
+%the symbolic heap represents the exact set of feasible
+%concrete heap structures for the program under analysis, and
+%3) \emph{expressive} -- the symbolic heap can represent recursive data structures 
+%and heaps resulting from loops and recursive control structures in the code. 
+%We report on a case-study of an implementation of our technique in the
+%Symbolic PathFinder tool to illustrate its scalability, precision
+%and expressiveness. We also discuss how test case generation -- a common
+ %use for symbolic execution results -- can benefit from symbolic
+ %execution which uses a fully symbolic heap.

### 2014-10-01 tex/proofs.tex
Rewrote theorem 1

@@
 \subsection{Theorems}
-\begin{lemma}[Location Mutual Exclusion in $\rightarrow^*_S$]
+\begin{lemma}[$\rightarrow^*_S$ preserves location mutual exclusion]
 Given a location mutual exclusive heap, $(\cfgnt{L}_0\ \cfgnt{R}_0)$, from a
@@
 \rightarrow_S
-(\cfgnt{L}_1 \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f})$. Let $\Lambda = \mathbb{UN}(\cfgnt{L}_0, \cfgnt{R}_0, \cfgnt{r},
+(\cfgnt{L}_1\ \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f})$. Let $\Lambda = \mathbb{UN}(\cfgnt{L}_0, \cfgnt{R}_0, \cfgnt{r},
 \cfgnt{f})$ be the set of uninitialized locations. If $\Lambda = \emptyset$, then the \texttt{Summarize (end)}
-rule is active and $(\cfgnt{L}_1\ \cfgnt{R}_1) = (\cfgnt{L}_0\ \cfgnt{R}_0)$, which is location mutual exclusive by definition.
+rule is active and $(\cfgnt{L}_1\ \cfgnt{R}_1) = (\cfgnt{L}_0\ \cfgnt{R}_0)$, which is location mutual exclusive by the initial conditions in the lemma.
 
@@
   \cfgnt{L}_n(\cfgnt{R}_n(\cfgnt{l}_x,\cfgnt{f}))$ is location mutual exclusive
-  by definition, members of $\theta_\mathit{orig}$ are location
+  by the initial conditions on $(\cfgnt{L}_0\ \cfgnt{R}_0)$ in the lemma statement, members of $\theta_\mathit{orig}$ are location
   mutual exclusive with each other and with members in $\theta_\mathit{null}$,
@@
 \theta_\mathit{new} \cup \theta_\mathit{alias} \cup
-\theta_\mathit{orig}$ is thus location mutual exclusive making $(\cfgnt{L}_1 \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f})$ location mutual exclusive as well.
+\theta_\mathit{orig}$ is thus location mutual exclusive making $(\cfgnt{L}_1\ \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f})$ location mutual exclusive as well.
 
@@
 mutual exclusive. This matches the base case, in that the heap on the
-left side of the transition is location mutual exclusive, and by the
+left side of $\rightarrow_S$ is location mutual exclusive, and by the
 same argument as in the base case,
 $(\cfgnt{L}_{n+1}\ \cfgnt{R}_{n+1})$ is thus location mutual exclusive.
+
 \begin{comment}
+% Initial proof text taken from the theorem
 The Field Access rule uses the Summarize rule to describe the relation between $\cfgnt{L}_{s}$ and $\cfgnt{L}_{s^\prime}$.
@@
 
-\begin{theorem}[Mutual Exclusion]
+\begin{theorem}[$\rightarrow_\varsigma$ preserves location mutual exclusion]
 \label{thm:mutex}
+Given a summary state, $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, such that $s_s \rightarrow_\varsigma s_s^\prime$, where $s_s^\prime = ( \cfgnt{L}_s^\prime\ \cfgnt{R}_s^\prime\ \phi_s^\prime\ \eta_s^\prime\ \cfgnt{e}_s^\prime\ \cfgnt{k}_s^\prime )$, if the heap $(\cfgnt{L}_s\ \cfgnt{R}_s)$ is location mutual exclusive then the heap after the transition, $(\cfgnt{L}_s^\prime\ \cfgnt{R}_s^\prime)$ is also location mutual exclusive.
+\begin{comment}
 If we have a reachable summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$
@@
 $$
+\end{comment}
 \end{theorem}

### 2014-10-01 tex/proofs.tex
Added commentary

@@
 \subsection{Theorems}
-\begin{lemma}[$\rightarrow^*_S$ preserves location mutual exclusion]
-Given a location mutual exclusive heap, $(\cfgnt{L}_0\ \cfgnt{R}_0)$, from a
-summary state with a reference $\cfgnt{r}$ and field $\cfgnt{f}$, the
-new heap, $(\cfgnt{L}^\prime\ \cfgnt{R}^\prime)$, from the summary
-initialization machine, $(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f})
-\rightarrow^*_S
-(\cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \cfgnt{r}\ \cfgnt{f})$, after any number of machine steps, is also
-location mutual exclusive.
-\end{lemma}
-\begin{proof}
-Induction over the number of machine steps on the summary initialization machine in \figref{fig:symInit}.
 
-\noindent\textbf{Base Case}. The machine takes one step: $(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f})
-\rightarrow_S
-(\cfgnt{L}_1\ \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f})$. Let $\Lambda = \mathbb{UN}(\cfgnt{L}_0, \cfgnt{R}_0, \cfgnt{r},
-\cfgnt{f})$ be the set of uninitialized locations. If $\Lambda = \emptyset$, then the \texttt{Summarize (end)}
-rule is active and $(\cfgnt{L}_1\ \cfgnt{R}_1) = (\cfgnt{L}_0\ \cfgnt{R}_0)$, which is location mutual exclusive by the initial conditions in the lemma.
+The goal of this section is to prove that the representation relation,
+$\sqsubset$, is a bisimulation as defined in
+\eqref{eqn:BisimulationForwards} and
+\eqref{eqn:BisimulationBackwards}. This proof is accomplished by
+showing that the requisite homomorphism, $\rightharpoonup_h$, used in
+the representation relation exists. A bisimulation is a relation over
+pairs of states such that whenever two states, $s_\ell$ and
+$s_\varsigma$, are related in the bisimulation, $s_\ell \sqsubset
+s_\varsigma$, every successor, from either state, $s_\ell
+\rightarrow_\ell s_\ell^\prime$ or $s_\varsigma \rightarrow_\varsigma
+s_\varsigma^\prime$, has a corresponding mutual successor in the other
+state such that both of those successors are also related in the
+bisimulation: $s_\ell^\prime \sqsubset s_\varsigma^\prime$.
 
-If $\Lambda \neq \emptyset$, then the \texttt{Summarize} rule is
-active, and each new constraint location pair must be considered
-individually. These pairs are partitioned into the sets
-$\theta_\mathit{null}$, $\theta_\mathit{new}$,
-$\theta_\mathit{alias}$, and $\theta_\mathit{orig}$ by the rule. 
-\begin{itemize}
-\item Any member of $\theta_\mathit{null}$, $\theta_\mathit{new}$, and
-  $\theta_\mathit{alias}$ has a constraint of the form $\phi_x \wedge
-  \ldots$ while any member of $\theta_\mathrm{orig}$ has a constraint
-  of the form $\neg \phi_x \wedge \ldots$. As every
-  $(\phi_\mathit{orig}\ \cfgnt{l}_\mathit{orig}) \in
-  \cfgnt{L}_n(\cfgnt{R}_n(\cfgnt{l}_x,\cfgnt{f}))$ is location mutual exclusive
-  by the initial conditions on $(\cfgnt{L}_0\ \cfgnt{R}_0)$ in the lemma statement, members of $\theta_\mathit{orig}$ are location
-  mutual exclusive with each other and with members in $\theta_\mathit{null}$,
-  $\theta_\mathit{new}$, and $\theta_\mathit{alias}$.
-\item Any member of $\theta_\mathit{null}$ has the form $\ldots \wedge
-  \cfgnt{r}_f = \cfgnt{r}_\mathit{null}$ while any member of
-  $\theta_\mathit{new}$ and $\theta_\mathit{alias}$ has the form
-  $\ldots \wedge \cfgnt{r}_f \neq \cfgnt{r}_\mathit{null} \wedge
-  \ldots$. As $\theta_\mathit{null}$ is a singleton set, its location is
-  location mutual exclusive from those in $\theta_\mathit{new}$ and
-  $\theta_\mathit{alias}$.
-\item Any member of $\theta_\mathit{new}$ has a constraint of the form
-  $\ldots \wedge ( \wedge_{(
-  \cfgnt{r}_a,\ \phi_a,\ l_a) \in \rho}
-  \cfgnt{r}_f \ne \cfgnt{r}_a) )$ to assert it does not
-  alias anything while any member of $\theta_\mathit{alias}$ has
-  the form $\ldots \wedge \cfgnt{r}_f = \cfgnt{r}_a \wedge \ldots$ for
-  some alias $\cfgnt{r}_a$ with both partitions reasoning over the same set of aliases $\rho$.  As $\theta_\mathit{new}$ is a singleton set, its
-  location is location mutual exclusive from any member of
-  $\theta_\mathit{alias}$.
-\item Any member of $\theta_\mathit{alias}$ has the form
-\[\ldots \wedge \cfgnt{r}_f = \cfgnt{r}_a \wedge ( \wedge_{( \cfgnt{r}^{\prime}_a\ \phi^{\prime}_a\ l^{\prime}_a)  \in \rho\ ( \cfgnt{r}^\prime_a \neq \cfgnt{r}_a) } \cfgnt{r}_f \neq \cfgnt{r}^{\prime}_a)\]
-Each is mutually exclusive over the particular alias it asserts.
-\end{itemize}
-Every member in $\theta = \theta_\mathit{null} \cup
-\theta_\mathit{new} \cup \theta_\mathit{alias} \cup
-\theta_\mathit{orig}$ is thus location mutual exclusive making $(\cfgnt{L}_1\ \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f})$ location mutual exclusive as well.
+If the $\varsigma$-relation is considered to be a model of the
+$\ell-relation$ (i.e., a representation of that machine), then the
+representation relation, as a bisimulation, ensures that the
+$\varsigma$-relation is complete in that it any property that can be
+shown in the $\ell$-relation can also be shown in the
+$\varsigma$-relation; and further, the representation relation as a
+bisimulation ensures that the $\varsigma$-relation is also sound in
+that any property that can be shown to hold in the $\varsigma$-relation
+can also be shown to hold in the $\ell$-relation.
 
-\noindent\textbf{Inductive Step}. The machine takes $n$-steps:
-\[
-(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f}) \rightarrow_S (\cfgnt{L}_1\ \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f}) \rightarrow_S \ldots \rightarrow_S
-(\cfgnt{L}_n\ \cfgnt{R}_n\ \cfgnt{r}\ \cfgnt{f})
-\]
-By the induction hypothesis, $(\cfgnt{L}_n\ \cfgnt{R}_n)$ is location
-mutual exclusive. This matches the base case, in that the heap on the
-left side of $\rightarrow_S$ is location mutual exclusive, and by the
-same argument as in the base case,
-$(\cfgnt{L}_{n+1}\ \cfgnt{R}_{n+1})$ is thus location mutual exclusive.
+The proof of the representation relation as a bisimulation reasons
+over individual rules in the $\varsigma$-relation to show that each
+rule preserves exactness. That is to say that whenever the state on
+the left of the $\varsigma$-relation has a corresponding state that it
+represents in the $\ell$-relation, its successor set is both sound and
+complete relative the $\ell$-relation and subject to the
+representation relation. Intuitively, the $\varsigma$-relation, at a
+given state, has a successor to account for every successor from the
+$\ell$-relation at the corresponding state, and the $ell$-machine has
+a successor to account for every successor in the
+$\varsigma$-relation.
 
-\begin{comment}
-% Initial proof text taken from the theorem
-The Field Access rule uses the Summarize rule to describe the relation between $\cfgnt{L}_{s}$ and $\cfgnt{L}_{s^\prime}$.
-Because the summarize rule is essentially a fixed-point computation, we can reason about it as a machine that produces a sequence of intermediate states $s_1, s_2, ...
-, s_n$.
-We will use an inductive argument to show that the mutual exclusion property holds for any of those intermediate states.
-First, let state $s_\alpha$ be any state for which the property in Theorem~\ref{thm:mutex} holds, and let $s_\beta$ be the intermediate state where $s_\alpha \rightarrow_S s_\beta$.
-If all fields are initialized, then $s_\alpha$ and $s_\beta$ are identical, so the mutually exclusive property holds for $s_\beta$.
-Otherwise, there must be some location $\cfgnt{l}_{un} \in \cfgnt{L}_\alpha(r)$ for which field f contains a reference $r_a$ that could feasibly point to the uninitialized location.
-In this case, a new reference is created and a single entry is added to $\cfgnt{L}_\beta$.
-The elements of the set $\theta_{all} = \cfgnt{L}_\beta(\cfgnt{R}_\beta(\cfgnt{l}_{un},\cfgnt{f}))$ can be divided into four distinct subsets, $\theta_{cur}$, $\theta_{null}$, $\theta_{new}$, and $\theta_{alias}$.
-The set $\theta_{cur}$ contains the pairs containing locations from the reference $r_a$, $\theta_{null}$ contains the pair with the null location, $\theta_{new}$ contains a pair with a new location, and $\theta_{alias}$ contains pairs representing alias locations.
-Any two constraints in $\theta_{cur}$ are guaranteed to be pairwise mutually exclusive because of the inductive hypothesis, and any single constraint is guaranteed to be pairwise mutually exclusive with any constraint in $\theta_{null}$, $\theta_{new}$, or $\theta_{alias}$ because constraints in $\theta_{cur}$ contain the conjunct $\neg \phi$, while constraints in the other three sets are conjoined with $\phi$.
-The set $\theta_{null}$ contains only one element, which in turn contains the constraint $r_f = r_{null}$, which is guaranteed to be mutually exclusive with any constraint in $\theta_{new}$, or $\theta_{alias}$ because constraints in those sets contain the conjunct $r_f \neq r_{null}$.
-The set $\theta_{new}$ contains one element, which in turn contains the constraint containing the conjunct $ \wedge_{\lp \cfgnt{r}^\prime_a,\ \phi^\prime_a,\ l^\prime_a\rp  \in \rho} \cfgnt{r}_f \ne \cfgnt{r}^\prime_a$, which is guaranteed to be mutually exclusive with any constraint in $\theta_{alias}$, because each constraint in that set contains the conjunct $r_f = r_a$ for some $(r_a\ \phi_a\ l_a)\in \rho$.
-Any two elements of the set $\theta_{alias}$ are guaranteed to pairwise mutually exclusive because for each constraint that contains the conjunct $r_f = r_a$, every other constraint contains the conjunct $r_f \ne r_a$.
-Thus, all constraints from all pairs in $\theta{all}$ are guaranteed to be mutually exclusive, and the property from Theorem~\ref{thm:mutex} holds for intermediate state $s_\beta$.
+The proof of exactness of each rule relies on the ability to derive
+from the homomorphism in the representation relation in the current
+state, a new homomorphism that is sufficient to use in the
+representation relation that reasons over the successor states. The
+proof is constructive in that it shows how given a valid homomorphism
+for the current state, it is possible to derive a new homomorphism to
+reason about successor states.
 
-We have now shown that whether there are any uninitialized fields or not, the mutual exclusivity property holds for any intermediate state $s_\beta$, so long as $s_\alpha \rightarrow_S s_\beta$ and the property holds for $s_\alpha$.
-So, since the mutual exclusivity property holds for $s_s$, $s_s \rightarrow_S s_1$, and $s_{i} \rightarrow_S s_{i+1} $ for all $i$ such that $0 < i < n$, we are guaranteed that the mutually exclusive property holds for the final intermediate state $s_n$.
-This concludes the inductive argument about
-\end{comment}
-\end{proof}
+There are two slight complications in the proof: the field access rule
+relies on the $S$-relation that operates on a different state that
+then $\varsigma$-relation and constructing the new homomorphism in the
+equals-reference rule relies on the incoming heap being location
+mutual exclusive. The $S$-relation effectively produces an
+intermediary state that is the state where uninitialized references
+are initialized before the field access actually takes place. In
+essence, a state on the left of the $\varsigma$-relation that is a
+field access, undergoes a transition in which its heap is changed to
+initialize fields. Once the fields are initialized, then the actual
+field access takes place. The state with the heap that has the
+initialized fields is the intermediary state between the state on the
+left of the $\varsigma$-relation and the state on the right of the
+$\varsigma$-relation. The proof reasons separately about this
+intermediary state to prove that it too is exact.
 
-%\begin{lemma}
-%\label{lem:lazyrefprops}
-%For any lazy state $s_\ell = ( \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta_\ell\ \cfgnt{e}_\ell\ \cfgnt{k}_\ell )$, for any reference $r \in \cfgnt{L}_\ell^\leftarrow$, 
-%$$ | \cfgnt{L}_\ell ( r) | = 1 $$
-%\end{lemma}
-%
-%\begin{proof}
-%In every rule in the Lazy machine that establishes a reference mapping, the value set contains exactly one location, constraint pair. 
-%\end{proof}
+The equals-reference proof must show that any given reference in the
+heap is not able to point to two distinct locations at the same
+time. If the incoming heap is able to point to two valid locations at
+a given reference at the same time, then the help is
+non-deterministic, and it is not possible to construct a valid
+homomorphism from the existing homomorphism: which location should be
+used in the map? As such, the proof first establishes that
+$\varsigma$-relation preserves location mutual exclusive in the
+incoming heap. Once that is shown, the exactness of the equals
+reference rule is given.
 
-\begin{theorem}[$\rightarrow_\varsigma$ preserves location mutual exclusion]
-\label{thm:mutex}
-Given a summary state, $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, such that $s_s \rightarrow_\varsigma s_s^\prime$, where $s_s^\prime = ( \cfgnt{L}_s^\prime\ \cfgnt{R}_s^\prime\ \phi_s^\prime\ \eta_s^\prime\ \cfgnt{e}_s^\prime\ \cfgnt{k}_s^\prime )$, if the heap $(\cfgnt{L}_s\ \cfgnt{R}_s)$ is location mutual exclusive then the heap after the transition, $(\cfgnt{L}_s^\prime\ \cfgnt{R}_s^\prime)$ is also location mutual exclusive.
-\begin{comment}
-If we have a reachable summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$
-$$ 
-\begin{array}{l}
-\forall (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_s(\cfgnt{r})\ (\forall (\phi_\beta\ \cfgnt{l}_\beta) \in \cfgnt{L}_s(\cfgnt{r})\ ( \\
-\ \ \ \ (\cfgnt{l}_\alpha \neq \cfgnt{l}_\beta) \Rightarrow ((\phi_\alpha \wedge \phi_\beta) = \cfgt{false})))
-\end{array}
-$$
-\end{comment}
-\end{theorem}
-\begin{proof}
-The proof will proceed inductively.
-
-Base Case: Let $s_s$ be an initial state.
-By Definition~\ref{def:initstate}, for every reference $r_i \in \cfgnt{L}_s^\leftarrow$, the set $\cfgnt{L}_s(r_i)$ contains at most one element.
-Thus, the requirement that $l_\alpha \ne l_\beta$ is never met, and the Theorem is vacuously true.
-
-Inductive Step: Now we will show that if the exclusivity property holds for some state $s_s$, then it holds for any state $s_s^\prime$ where $s_s \rightarrow_s s_s^\prime$.
-In order to evaluate whether Theorem~\ref{thm:mutex} holds for state any $s_s\prime$, we must consider the rule that applied during the transition from $s_s$ to $s_s\prime$.
-There are two broad classes of rules: rules where $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$, and rules where $ \cfgnt{L}_s =  \cfgnt{L}_{s^\prime}$.
-Rules in the $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$ class modify the structure of the heap, and must be considered carefully to to consider the impact of those modifications.
-Only three rules belong to the class $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$: Field Access, Field Read, and New.
-
-We begin by considering the Field Access rule.
-Suppose $s_s$ has the form $\lp \cfgnt{L}_s\ \cfgnt{R}_{s}\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.
-In this case, the relationship between $s_s$ and $s_s^\prime$ is described by the Field Access rule.
-intermediate state.
-
-We now use this result to show that the mutual exclusion property holds for state $s_s^\prime$.
-The relation between the L-function from the final intermediate state $\cfgnt{L}^\prime$ and the L-function in $s_s^\prime$ is $ \cfgnt{L}_{s^\prime} = \cfgnt{L}^\prime[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}^\prime,\cfgnt{R}^\prime,\cfgnt{r},\cfgnt{f},\phi_g\rp ]$, where a new value set is created based on the $\mathbb{VS}$ function.
-The members of the value set have the form $(\phi\wedge \phi^\prime\ \ l)$.
-Choose any two distinct members of the value set, $(\phi_\alpha \wedge \phi_\alpha^\prime\ \ l_\alpha)$ and $(\phi_\beta \wedge \phi_\beta^\prime\ \ l_\beta)$.
-If $\phi_\alpha \ne \phi_\beta$, we know that exclusivity holds because $\phi_\alpha$ and $\phi_\beta$ came from the same value set in $s_s$, and are therefore exclusive.
-If $\phi_\alpha = \phi_\beta$, we know that exclusivity holds because $\phi_\alpha^\prime$ and $\phi_\beta^\prime$ came from the same value set in $s_s$ and are therefore exclusive.
-Thus, the exclusivity property holds for any pair of constraints in the value set.
-Since the only new value set in $L_{s^\prime}^\rightarrow$ is generated by the $\mathbb{VS}$ function, we are guaranteed that if exclusivity holds for $s_s$, then exclusivity holds for $s_s^\prime$.
-
-Suppose we have a field write instruction.
-This case is nearly identical as the field read.
-In this instruction, a new value set is created.
-The members of the value set have the form $(\phi\wedge \phi^\prime\ \ l)$.
-Choose any two distinct members of the value set, $(\phi_\alpha \wedge \phi_\alpha^\prime\ \ l_\alpha)$ and $(\phi_\beta \wedge \phi_\beta^\prime\ \ l_\beta)$.
-If $\phi_\alpha \ne \phi_\beta$, we know that exclusivity holds because $\phi_\alpha = \neg \phi_\beta$, so $\phi_\alpha$ and $\phi_\beta$ are therefore exclusive.
-If $\phi_\alpha = \phi_\beta$, we know that exclusivity holds because $\phi_\alpha^\prime$ and $\phi_\beta^\prime$ came from the same value set in $s_s$ and are therefore exclusive.
-Thus, the exclusivity property holds for any pair of constraints in the value set.
-Since exclusivity holds for the only new value set in $L_{s^\prime}^\rightarrow$, we are guaranteed that if exclusivity holds for $s_s$, then exclusivity holds for $s_s^\prime$.
-
-Suppose we have a "new" instruction. In this case, only one value set is added to $L_{s^\prime}^\rightarrow$, and that value set contains only one member, so exclusivity holds by default.
-
-Suppose we have any instruction other that a read, write, or new.
-No machine rule other than those three listed instructions modifies the $L$ function.
-Therefore, the exclusivity property must hold for $s_s^\prime$ in these cases.
-
-Since the exclusivity property holds for any initial state, and since it holds for any "next" state if the property holds for the previous state, we have proven the property for every symbolic state.
-\end{proof}
-
-\begin{corollary}
-Any state represented by any reachable summary state is a lazy state.
-\end{corollary}
-
-\begin{proof}
-By Theorem \ref{thm:mutex} since the constraints on every reference are mutually exclusive, the heap constraint for any heap with a reference pointing to more than one location will be unsatisfiable, and by Definition \ref{representation} will not be represented by the summary state.
-\end{proof}
-
-%\begin{comment}
-%%I'm wondering... do we use this theorem anywhere? I think the place we needed it got re-structured, am I right?
-%\begin{theorem}
-%\label{thm:colex}
-%If we have a summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, 
-%$$\bigvee \{ \phi \mid (\phi\ \cfgnt{l})\in \cfgnt{L}_s (\cfgnt{r})\} = \cfgt{true}$$
-%\end{theorem}
-%\begin{proof}
-%The proof will proceed inductively.
-%
-%Base Case: In the initial state $s_0$ there is only one location, and all of it's fields are initialized to contain the uninitiated reference $\cfgnt{r}_{un}$.
-Since the only reference is the uninitialized reference, for which the desired property holds by construction, the property is true for all references on the heap.
-%
-%Inductive Step: 
-%Suppose we have a summary state $s_s$ for which the property holds, and some state $s_s^\prime$ such that $s_s \rightarrow_S s_s^\prime$.
-If all relevant fields are initialized, then $s_s = s_s^\prime$, and the property holds trivially.
-If there is some uninitialized fields, then on of those fields will have a new reference $\cfgnt{r}_{new}$ added to it.
-The disjunction
-%$$ \bigvee \{ \phi \mid (\phi\ \cfgnt{l})\in \cfgnt{L}_s (\cfgnt{r}_{new})\}$$
-%Takes the form
-%\begin{align*}
-% (\phi_0) \vee (\neg \phi_0 \wedge \phi_1) \vee (\neg \phi_0 \wedge \neg \phi_1 \wedge \phi_2) \vee ...\\
-% ... \vee (\neg \phi_0 \wedge \neg \phi_1 \wedge ... \wedge \phi_n) \vee (\neg \phi_0 \wedge \neg \phi_1 \wedge ... \wedge \neg \phi_n)
-% \end{align*}
-% Which reduces to $\cfgt{true}$.
-Thus, the collective exhaustion property holds for intermediate states.
-Because the property holds for intermediate states, for summary machine rules we will assume without loss of generality that all relevant fields are initialized.
-% Suppose that the rule executed in the transition from $s_s$ to $s_s^\prime$ is the field read rule. 
-%Suppose we have a state $s_s$ for which the property holds, and some state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$. 
-% 
-%\end{proof}
-%\end{comment}
-%\begin{lemma}
-%\label{lem:ref}
-%For any symbolic state $s_s$, constraint $\phi$, and stack reference $\cfgnt{r}$ such that $(\phi\ \ell) \in \cfgnt{L}_s (\cfgnt{r})$, then 
-%\begin{equation}
-%\exists \Gamma_n^s\ ( \phi = \mathbb{PC} (\Gamma_n^s) )
-%\end{equation}
-%\end{lemma}
-%\begin{proof}
-%\end{proof}
-%
-%\begin{lemma}
-%\label{lem:path}
-%If there is some access path $\Gamma_n^s$ in state $s_s$ such that $\mathbb{S}(\phi_s \wedge \mathbb{PC}(\Gamma_n^s))$, then $\Gamma_n^\ell$ is an access path in some lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$
-%\end{lemma}
-%\begin{proof}
-%\end{proof}
+The final statement that $\sqsubset$ is a bisimulation is in \thref{th:bisim}.
 
@@
 
+\begin{lemma}[$\rightarrow^*_S$ preserves location mutual exclusion]
+Given a location mutual exclusive heap, $(\cfgnt{L}_0\ \cfgnt{R}_0)$, from a
+summary state with a reference $\cfgnt{r}$ and field $\cfgnt{f}$, the
+new heap, $(\cfgnt{L}^\prime\ \cfgnt{R}^\prime)$, from the summary
+initialization machine, $(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f})
+\rightarrow^*_S
+(\cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \cfgnt{r}\ \cfgnt{f})$, after any number of machine steps, is also
+location mutual exclusive.
+\end{lemma}
+\begin{proof}
+Induction over the number of machine steps on the summary initialization machine in \figref{fig:symInit}.
+
+\noindent\textbf{Base Case}. The machine takes one step: $(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f})
+\rightarrow_S
+(\cfgnt{L}_1\ \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f})$. Let $\Lambda = \mathbb{UN}(\cfgnt{L}_0, \cfgnt{R}_0, \cfgnt{r},
+\cfgnt{f})$ be the set of uninitialized locations. If $\Lambda = \emptyset$, then the \texttt{Summarize (end)}
+rule is active and $(\cfgnt{L}_1\ \cfgnt{R}_1) = (\cfgnt{L}_0\ \cfgnt{R}_0)$, which is location mutual exclusive by the initial conditions in the lemma.
+
+If $\Lambda \neq \emptyset$, then the \texttt{Summarize} rule is
+active, and each new constraint location pair must be considered
+individually. These pairs are partitioned into the sets
+$\theta_\mathit{null}$, $\theta_\mathit{new}$,
+$\theta_\mathit{alias}$, and $\theta_\mathit{orig}$ by the rule. 
+\begin{itemize}
+\item Any member of $\theta_\mathit{null}$, $\theta_\mathit{new}$, and
+  $\theta_\mathit{alias}$ has a constraint of the form $\phi_x \wedge
+  \ldots$ while any member of $\theta_\mathrm{orig}$ has a constraint
+  of the form $\neg \phi_x \wedge \ldots$. As every
+  $(\phi_\mathit{orig}\ \cfgnt{l}_\mathit{orig}) \in
+  \cfgnt{L}_n(\cfgnt{R}_n(\cfgnt{l}_x,\cfgnt{f}))$ is location mutual exclusive
+  by the initial conditions on $(\cfgnt{L}_0\ \cfgnt{R}_0)$ in the lemma statement, members of $\theta_\mathit{orig}$ are location
+  mutual exclusive with each other and with members in $\theta_\mathit{null}$,
+  $\theta_\mathit{new}$, and $\theta_\mathit{alias}$.
+\item Any member of $\theta_\mathit{null}$ has the form $\ldots \wedge
+  \cfgnt{r}_f = \cfgnt{r}_\mathit{null}$ while any member of
+  $\theta_\mathit{new}$ and $\theta_\mathit{alias}$ has the form
+  $\ldots \wedge \cfgnt{r}_f \neq \cfgnt{r}_\mathit{null} \wedge
+  \ldots$. As $\theta_\mathit{null}$ is a singleton set, its location is
+  location mutual exclusive from those in $\theta_\mathit{new}$ and
+  $\theta_\mathit{alias}$.
+\item Any member of $\theta_\mathit{new}$ has a constraint of the form
+  $\ldots \wedge ( \wedge_{(
+  \cfgnt{r}_a,\ \phi_a,\ l_a) \in \rho}
+  \cfgnt{r}_f \ne \cfgnt{r}_a) )$ to assert it does not
+  alias anything while any member of $\theta_\mathit{alias}$ has
+  the form $\ldots \wedge \cfgnt{r}_f = \cfgnt{r}_a \wedge \ldots$ for
+  some alias $\cfgnt{r}_a$ with both partitions reasoning over the same set of aliases $\rho$.  As $\theta_\mathit{new}$ is a singleton set, its
+  location is location mutual exclusive from any member of
+  $\theta_\mathit{alias}$.
+\item Any member of $\theta_\mathit{alias}$ has the form
+\[\ldots \wedge \cfgnt{r}_f = \cfgnt{r}_a \wedge ( \wedge_{( \cfgnt{r}^{\prime}_a\ \phi^{\prime}_a\ l^{\prime}_a)  \in \rho\ ( \cfgnt{r}^\prime_a \neq \cfgnt{r}_a) } \cfgnt{r}_f \neq \cfgnt{r}^{\prime}_a)\]
+Each is mutually exclusive over the particular alias it asserts.
+\end{itemize}
+Every member in $\theta = \theta_\mathit{null} \cup
+\theta_\mathit{new} \cup \theta_\mathit{alias} \cup
+\theta_\mathit{orig}$ is thus location mutual exclusive making $(\cfgnt{L}_1\ \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f})$ location mutual exclusive as well.
+
+\noindent\textbf{Inductive Step}. The machine takes $n$-steps:
+\[
+(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f}) \rightarrow_S (\cfgnt{L}_1\ \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f}) \rightarrow_S \ldots \rightarrow_S
+(\cfgnt{L}_n\ \cfgnt{R}_n\ \cfgnt{r}\ \cfgnt{f})
+\]
+By the induction hypothesis, $(\cfgnt{L}_n\ \cfgnt{R}_n)$ is location
+mutual exclusive. This matches the base case, in that the heap on the
+left side of $\rightarrow_S$ is location mutual exclusive, and by the
+same argument as in the base case,
+$(\cfgnt{L}_{n+1}\ \cfgnt{R}_{n+1})$ is thus location mutual exclusive.
+
+\begin{comment}
+% Initial proof text taken from the theorem
+The Field Access rule uses the Summarize rule to describe the relation between $\cfgnt{L}_{s}$ and $\cfgnt{L}_{s^\prime}$.
+Because the summarize rule is essentially a fixed-point computation, we can reason about it as a machine that produces a sequence of intermediate states $s_1, s_2, ...
+, s_n$.
+We will use an inductive argument to show that the mutual exclusion property holds for any of those intermediate states.
+First, let state $s_\alpha$ be any state for which the property in Theorem~\ref{thm:mutex} holds, and let $s_\beta$ be the intermediate state where $s_\alpha \rightarrow_S s_\beta$.
+If all fields are initialized, then $s_\alpha$ and $s_\beta$ are identical, so the mutually exclusive property holds for $s_\beta$.
+Otherwise, there must be some location $\cfgnt{l}_{un} \in \cfgnt{L}_\alpha(r)$ for which field f contains a reference $r_a$ that could feasibly point to the uninitialized location.
+In this case, a new reference is created and a single entry is added to $\cfgnt{L}_\beta$.
+The elements of the set $\theta_{all} = \cfgnt{L}_\beta(\cfgnt{R}_\beta(\cfgnt{l}_{un},\cfgnt{f}))$ can be divided into four distinct subsets, $\theta_{cur}$, $\theta_{null}$, $\theta_{new}$, and $\theta_{alias}$.
+The set $\theta_{cur}$ contains the pairs containing locations from the reference $r_a$, $\theta_{null}$ contains the pair with the null location, $\theta_{new}$ contains a pair with a new location, and $\theta_{alias}$ contains pairs representing alias locations.
+Any two constraints in $\theta_{cur}$ are guaranteed to be pairwise mutually exclusive because of the inductive hypothesis, and any single constraint is guaranteed to be pairwise mutually exclusive with any constraint in $\theta_{null}$, $\theta_{new}$, or $\theta_{alias}$ because constraints in $\theta_{cur}$ contain the conjunct $\neg \phi$, while constraints in the other three sets are conjoined with $\phi$.
+The set $\theta_{null}$ contains only one element, which in turn contains the constraint $r_f = r_{null}$, which is guaranteed to be mutually exclusive with any constraint in $\theta_{new}$, or $\theta_{alias}$ because constraints in those sets contain the conjunct $r_f \neq r_{null}$.
+The set $\theta_{new}$ contains one element, which in turn contains the constraint containing the conjunct $ \wedge_{\lp \cfgnt{r}^\prime_a,\ \phi^\prime_a,\ l^\prime_a\rp  \in \rho} \cfgnt{r}_f \ne \cfgnt{r}^\prime_a$, which is guaranteed to be mutually exclusive with any constraint in $\theta_{alias}$, because each constraint in that set contains the conjunct $r_f = r_a$ for some $(r_a\ \phi_a\ l_a)\in \rho$.
+Any two elements of the set $\theta_{alias}$ are guaranteed to pairwise mutually exclusive because for each constraint that contains the conjunct $r_f = r_a$, every other constraint contains the conjunct $r_f \ne r_a$.
+Thus, all constraints from all pairs in $\theta{all}$ are guaranteed to be mutually exclusive, and the property from Theorem~\ref{thm:mutex} holds for intermediate state $s_\beta$.
+
+We have now shown that whether there are any uninitialized fields or not, the mutual exclusivity property holds for any intermediate state $s_\beta$, so long as $s_\alpha \rightarrow_S s_\beta$ and the property holds for $s_\alpha$.
+So, since the mutual exclusivity property holds for $s_s$, $s_s \rightarrow_S s_1$, and $s_{i} \rightarrow_S s_{i+1} $ for all $i$ such that $0 < i < n$, we are guaranteed that the mutually exclusive property holds for the final intermediate state $s_n$.
+This concludes the inductive argument about
+\end{comment}
+\end{proof}
+
+%\begin{lemma}
+%\label{lem:lazyrefprops}
+%For any lazy state $s_\ell = ( \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta_\ell\ \cfgnt{e}_\ell\ \cfgnt{k}_\ell )$, for any reference $r \in \cfgnt{L}_\ell^\leftarrow$, 
+%$$ | \cfgnt{L}_\ell ( r) | = 1 $$
+%\end{lemma}
+%
+%\begin{proof}
+%In every rule in the Lazy machine that establishes a reference mapping, the value set contains exactly one location, constraint pair. 
+%\end{proof}
+
+\begin{theorem}[$\rightarrow_\varsigma$ preserves location mutual exclusion]
+\label{thm:mutex}
+Given a summary state, $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, such that $s_s \rightarrow_\varsigma s_s^\prime$, where $s_s^\prime = ( \cfgnt{L}_s^\prime\ \cfgnt{R}_s^\prime\ \phi_s^\prime\ \eta_s^\prime\ \cfgnt{e}_s^\prime\ \cfgnt{k}_s^\prime )$, if the heap $(\cfgnt{L}_s\ \cfgnt{R}_s)$ is location mutual exclusive then the heap after the transition, $(\cfgnt{L}_s^\prime\ \cfgnt{R}_s^\prime)$ is also location mutual exclusive.
+\begin{comment}
+If we have a reachable summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$
+$$ 
+\begin{array}{l}
+\forall (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_s(\cfgnt{r})\ (\forall (\phi_\beta\ \cfgnt{l}_\beta) \in \cfgnt{L}_s(\cfgnt{r})\ ( \\
+\ \ \ \ (\cfgnt{l}_\alpha \neq \cfgnt{l}_\beta) \Rightarrow ((\phi_\alpha \wedge \phi_\beta) = \cfgt{false})))
+\end{array}
+$$
+\end{comment}
+\end{theorem}
+\begin{proof}
+The proof will proceed inductively.
+
+Base Case: Let $s_s$ be an initial state.
+By Definition~\ref{def:initstate}, for every reference $r_i \in \cfgnt{L}_s^\leftarrow$, the set $\cfgnt{L}_s(r_i)$ contains at most one element.
+Thus, the requirement that $l_\alpha \ne l_\beta$ is never met, and the Theorem is vacuously true.
+
+Inductive Step: Now we will show that if the exclusivity property holds for some state $s_s$, then it holds for any state $s_s^\prime$ where $s_s \rightarrow_s s_s^\prime$.
+In order to evaluate whether Theorem~\ref{thm:mutex} holds for state any $s_s\prime$, we must consider the rule that applied during the transition from $s_s$ to $s_s\prime$.
+There are two broad classes of rules: rules where $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$, and rules where $ \cfgnt{L}_s =  \cfgnt{L}_{s^\prime}$.
+Rules in the $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$ class modify the structure of the heap, and must be considered carefully to to consider the impact of those modifications.
+Only three rules belong to the class $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$: Field Access, Field Read, and New.
+
+We begin by considering the Field Access rule.
+Suppose $s_s$ has the form $\lp \cfgnt{L}_s\ \cfgnt{R}_{s}\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.
+In this case, the relationship between $s_s$ and $s_s^\prime$ is described by the Field Access rule.
+intermediate state.
+
+We now use this result to show that the mutual exclusion property holds for state $s_s^\prime$.
+The relation between the L-function from the final intermediate state $\cfgnt{L}^\prime$ and the L-function in $s_s^\prime$ is $ \cfgnt{L}_{s^\prime} = \cfgnt{L}^\prime[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}^\prime,\cfgnt{R}^\prime,\cfgnt{r},\cfgnt{f},\phi_g\rp ]$, where a new value set is created based on the $\mathbb{VS}$ function.
+The members of the value set have the form $(\phi\wedge \phi^\prime\ \ l)$.
+Choose any two distinct members of the value set, $(\phi_\alpha \wedge \phi_\alpha^\prime\ \ l_\alpha)$ and $(\phi_\beta \wedge \phi_\beta^\prime\ \ l_\beta)$.
+If $\phi_\alpha \ne \phi_\beta$, we know that exclusivity holds because $\phi_\alpha$ and $\phi_\beta$ came from the same value set in $s_s$, and are therefore exclusive.
+If $\phi_\alpha = \phi_\beta$, we know that exclusivity holds because $\phi_\alpha^\prime$ and $\phi_\beta^\prime$ came from the same value set in $s_s$ and are therefore exclusive.
+Thus, the exclusivity property holds for any pair of constraints in the value set.
+Since the only new value set in $L_{s^\prime}^\rightarrow$ is generated by the $\mathbb{VS}$ function, we are guaranteed that if exclusivity holds for $s_s$, then exclusivity holds for $s_s^\prime$.
+
+Suppose we have a field write instruction.
+This case is nearly identical as the field read.
+In this instruction, a new value set is created.
+The members of the value set have the form $(\phi\wedge \phi^\prime\ \ l)$.
+Choose any two distinct members of the value set, $(\phi_\alpha \wedge \phi_\alpha^\prime\ \ l_\alpha)$ and $(\phi_\beta \wedge \phi_\beta^\prime\ \ l_\beta)$.
+If $\phi_\alpha \ne \phi_\beta$, we know that exclusivity holds because $\phi_\alpha = \neg \phi_\beta$, so $\phi_\alpha$ and $\phi_\beta$ are therefore exclusive.
+If $\phi_\alpha = \phi_\beta$, we know that exclusivity holds because $\phi_\alpha^\prime$ and $\phi_\beta^\prime$ came from the same value set in $s_s$ and are therefore exclusive.
+Thus, the exclusivity property holds for any pair of constraints in the value set.
+Since exclusivity holds for the only new value set in $L_{s^\prime}^\rightarrow$, we are guaranteed that if exclusivity holds for $s_s$, then exclusivity holds for $s_s^\prime$.
+
+Suppose we have a "new" instruction. In this case, only one value set is added to $L_{s^\prime}^\rightarrow$, and that value set contains only one member, so exclusivity holds by default.
+
+Suppose we have any instruction other that a read, write, or new.
+No machine rule other than those three listed instructions modifies the $L$ function.
+Therefore, the exclusivity property must hold for $s_s^\prime$ in these cases.
+
+Since the exclusivity property holds for any initial state, and since it holds for any "next" state if the property holds for the previous state, we have proven the property for every symbolic state.
+\end{proof}
+
+\begin{corollary}
+Any state represented by any reachable summary state is a lazy state.
+\end{corollary}
+
+\begin{proof}
+By Theorem \ref{thm:mutex} since the constraints on every reference are mutually exclusive, the heap constraint for any heap with a reference pointing to more than one location will be unsatisfiable, and by Definition \ref{representation} will not be represented by the summary state.
+\end{proof}
+
 %proof for reference compares. Here we will rely on the fact that since the L and R functions don't change, and since the phi function
@@
 \begin{theorem}
+\label{th:bisim}
 The representation relation $\sqsubset$ is a bisimulation.

### 2014-10-01 tex/proofs.tex
Added commentary

@@
 If the $\varsigma$-relation is considered to be a model of the
-$\ell-relation$ (i.e., a representation of that machine), then the
+$\ell$-relation (i.e., a representation of that machine), then the
 representation relation, as a bisimulation, ensures that the
-$\varsigma$-relation is complete in that it any property that can be
+$\varsigma$-relation is complete in that any property that can be
 shown in the $\ell$-relation can also be shown in the
@@
 given state, has a successor to account for every successor from the
-$\ell$-relation at the corresponding state, and the $ell$-machine has
+$\ell$-relation at the corresponding state, and the $\ell$-machine has
 a successor to account for every successor in the
@@
 state, a new homomorphism that is sufficient to use in the
-representation relation that reasons over the successor states. The
-proof is constructive in that it shows how given a valid homomorphism
-for the current state, it is possible to derive a new homomorphism to
-reason about successor states.
+representation relation that includes the successor states. The proof
+is constructive in that it shows how given a valid homomorphism for
+the current state, it is possible to derive a new homomorphism that
+includes successor states.
 
@@
 used in the map? As such, the proof first establishes that
-$\varsigma$-relation preserves location mutual exclusive in the
+the $\varsigma$-relation preserves location mutual exclusive in the
 incoming heap. Once that is shown, the exactness of the equals

### 2014-10-01 tex/proofs.tex
Slight retool to focus on deriving the representation relation.

@@
 \eqref{eqn:BisimulationForwards} and
-\eqref{eqn:BisimulationBackwards}. This proof is accomplished by
-showing that the requisite homomorphism, $\rightharpoonup_h$, used in
-the representation relation exists. A bisimulation is a relation over
-pairs of states such that whenever two states, $s_\ell$ and
+\eqref{eqn:BisimulationBackwards}.  A bisimulation is a relation over pairs of states such that whenever two states, $s_\ell$ and
 $s_\varsigma$, are related in the bisimulation, $s_\ell \sqsubset
@@
 The proof of the representation relation as a bisimulation reasons
-over individual rules in the $\varsigma$-relation to show that each
-rule preserves exactness. That is to say that whenever the state on
-the left of the $\varsigma$-relation has a corresponding state that it
+over individual rules in the $\varsigma$-relation to show that for
+each rule, the representation relation, $\sqsubset$, exists; thus, the
+representation relation is a bisimulation for the system consisting
+only of the rule in consideration. Whenever the state on the
+left of the $\varsigma$-relation has a corresponding state that it
 represents in the $\ell$-relation, its successor set is both sound and
-complete relative the $\ell$-relation and subject to the
-representation relation. Intuitively, the $\varsigma$-relation, at a
-given state, has a successor to account for every successor from the
-$\ell$-relation at the corresponding state, and the $\ell$-machine has
-a successor to account for every successor in the
-$\varsigma$-relation.
+complete relative the $\ell$-relation under the new
+representation relation that now includes the successors.
 
-The proof of exactness of each rule relies on the ability to derive
-from the homomorphism in the representation relation in the current
-state, a new homomorphism that is sufficient to use in the
-representation relation that includes the successor states. The proof
-is constructive in that it shows how given a valid homomorphism for
-the current state, it is possible to derive a new homomorphism that
-includes successor states.
+The heart of the representation relation is the homomorphism that maps
+locations in one heap to locations in the other heap. The proof
+reasons over of each rule and as mentioned previously, and derives
+from the current homomorphism in the representation relation for the
+current states, a new homomorphism that is sufficient to use in the a
+new representation relation that includes the successor states. The
+proof is constructive in that it shows how given a valid homomorphism
+for the current states, it is possible to derive a new homomorphism
+that includes successor states. With such a new homomorphism, it is
+possible to state that for the $\varsigma$-relation, when restricted
+to a specific rule (i.e., that is the only rule available in the
+relation), the representation relation is a bisimulation for that
+restricted $\varsigma$-relation. If such a bisimulation exists for all
+the individual rules, then it exists for the rules collectively.
 
-There are two slight complications in the proof: the field access rule
-relies on the $S$-relation that operates on a different state that
-then $\varsigma$-relation and constructing the new homomorphism in the
+There are two slight complications in the proof: first, the field access rule
+relies on the $S$-relation that operates on a different state 
+than then $\varsigma$-relation; and second, constructing the new homomorphism in the
 equals-reference rule relies on the incoming heap being location

### 2014-10-01 tex/precise.tex
Constraint mutual exclusion proof updated with details for summary machine
Rewrite some of mutual exclusion
Added location mutual exclusion on FA

@@
 
+\begin{definition}
+\label{def:VS}
 The function $\mathbb{VS}(L,R,\phi_g,r,f)$ constructs the value-set given a
@@
 \begin{array}{rcl}
-  \mathbb{VS}(L,R,\phi_g,r,f) & = & \{(\phi\wedge\phi^\prime\ l^\prime) \mid \\
-  & & \ \ \ \ \exists l\ ((l\ \phi) \in L(r)\ \wedge \\
-  & & \ \ \ \ \ \ \ \ \exists r^\prime \in R(l,f) ( \\
-  & & \ \ \ \ \ \ \ \ \ \ \ \ (l^\prime\ \phi^\prime) \in L(r^\prime)\ \wedge\\
+  \mathbb{VS}(\cfgnt{L},\cfgnt{R},\phi_g,\cfgnt{r},\cfgnt{f}) & = & \{(\phi\wedge\phi^\prime\ \cfgnt{l}^\prime) \mid \\
+  & & \ \ \ \ \exists \cfgnt{l}\ ((\phi\ l) \in L(r)\ \wedge \\
+  & & \ \ \ \ \ \ \ \ \exists \cfgnt{r}^\prime ( \cfgnt{r}^\prime = R(\cfgnt{l},\cfgnt{f})\ \wedge \\
+  & & \ \ \ \ \ \ \ \ \ \ \ \ (\phi^\prime\ l^\prime) \in \cfgnt{L}(\cfgnt{r}^\prime)\ \wedge\\
   & & \ \ \ \ \ \ \ \ \ \ \ \ \mathbb{S}(\phi\wedge\phi^\prime\wedge \phi_g)))\}
@@
 where $\mathbb{S}(\phi)$ returns true if $\phi$ is satisfiable.
+\end{definition}
 
+\begin{definition}
+\label{def:ST}
 The strengthen function $\mathbb{ST}(L,r,\phi^\prime)$ strengthens every
@@
 \begin{array}{rcl} 
-\mathbb{ST}(L,r,\phi) & = & \{ (\phi\wedge\phi^\prime\ l) \mid 
-(\phi^\prime\ l)\in L(r)\wedge\mathbb{S}(\phi\wedge\phi^\prime\wedge\phi_g) \}
+\mathbb{ST}(L,r,\phi,\phi_g) & = & \{ (\phi\wedge\phi^\prime\ l) \mid  \\
+& & \ \ \ \ (\phi^\prime\ l)\in L(r)\wedge\mathbb{S}(\phi\wedge\phi^\prime\wedge\phi_g) \}
 \end{array}
 \]
+\end{definition}
 

### 2014-10-01 tex/proofs.tex
Added location mutual exclusion on FA

@@
 over individual rules in the $\varsigma$-relation to show that for
-each rule, the representation relation, $\sqsubset$, exists; thus, the
-representation relation is a bisimulation for the system consisting
-only of the rule in consideration. Whenever the state on the
-left of the $\varsigma$-relation has a corresponding state that it
-represents in the $\ell$-relation, its successor set is both sound and
-complete relative the $\ell$-relation under the new
-representation relation that now includes the successors.
+each rule, the representation relation, $\sqsubset$, exists. The heart
+of the representation relation is the homomorphism that maps locations
+in one heap to locations in the other heap. The proof reasons over of
+each rule and as mentioned previously, and derives from the current
+homomorphism in the representation relation for the current states, a
+new homomorphism that is sufficient to use in the a new representation
+relation that includes the successor states. The proof is constructive
+in that it shows how given a valid homomorphism for the current
+states, it is possible to derive a new homomorphism that includes
+successor states. With such a new homomorphism, it is possible to
+state that for the $\varsigma$-relation, when restricted to a specific
+rule (i.e., that is the only rule available in the relation), the
+representation relation is a bisimulation for that restricted
+$\varsigma$-relation. If such a bisimulation exists for all the
+individual rules, then it exists for the rules collectively.
 
-The heart of the representation relation is the homomorphism that maps
-locations in one heap to locations in the other heap. The proof
-reasons over of each rule and as mentioned previously, and derives
-from the current homomorphism in the representation relation for the
-current states, a new homomorphism that is sufficient to use in the a
-new representation relation that includes the successor states. The
-proof is constructive in that it shows how given a valid homomorphism
-for the current states, it is possible to derive a new homomorphism
-that includes successor states. With such a new homomorphism, it is
-possible to state that for the $\varsigma$-relation, when restricted
-to a specific rule (i.e., that is the only rule available in the
-relation), the representation relation is a bisimulation for that
-restricted $\varsigma$-relation. If such a bisimulation exists for all
-the individual rules, then it exists for the rules collectively.
-
-There are two slight complications in the proof: first, the field access rule
-relies on the $S$-relation that operates on a different state 
-than then $\varsigma$-relation; and second, constructing the new homomorphism in the
-equals-reference rule relies on the incoming heap being location
-mutual exclusive. The $S$-relation effectively produces an
-intermediary state that is the state where uninitialized references
+There are two slight complications in the proof: first, the field
+access rule relies on the $S$-relation that operates on a different
+state than then $\varsigma$-relation; and second, constructing the new
+homomorphism in the equals-reference rule relies on the incoming heap
+being location mutual exclusive. The $S$-relation effectively produces
+an intermediary state that is the state where uninitialized references
 are initialized before the field access actually takes place. In
@@
 
-\begin{lemma}[Exactness of Summarize Rule]
+\begin{lemma}[Bisimulation for $S$-relation]
 \label{lem:init}
@@
 %we need to define how r' is arrived at for this one to work...
-\begin{lemma}[Exactness of Field Access Rule]
+\begin{lemma}[Bisumlation for $\rightarrow_{\varsigma|\mathit{FA}}$]
 \label{lem:access}
@@
 \begin{lemma}[$\rightarrow^*_S$ preserves location mutual exclusion]
+\label{lem:S-mutex}
 Given a location mutual exclusive heap, $(\cfgnt{L}_0\ \cfgnt{R}_0)$, from a
@@
 $(\cfgnt{L}_{n+1}\ \cfgnt{R}_{n+1})$ is thus location mutual exclusive.
-
-\begin{comment}
-% Initial proof text taken from the theorem
-The Field Access rule uses the Summarize rule to describe the relation between $\cfgnt{L}_{s}$ and $\cfgnt{L}_{s^\prime}$.
-Because the summarize rule is essentially a fixed-point computation, we can reason about it as a machine that produces a sequence of intermediate states $s_1, s_2, ...
-, s_n$.
-We will use an inductive argument to show that the mutual exclusion property holds for any of those intermediate states.
-First, let state $s_\alpha$ be any state for which the property in Theorem~\ref{thm:mutex} holds, and let $s_\beta$ be the intermediate state where $s_\alpha \rightarrow_S s_\beta$.
-If all fields are initialized, then $s_\alpha$ and $s_\beta$ are identical, so the mutually exclusive property holds for $s_\beta$.
-Otherwise, there must be some location $\cfgnt{l}_{un} \in \cfgnt{L}_\alpha(r)$ for which field f contains a reference $r_a$ that could feasibly point to the uninitialized location.
-In this case, a new reference is created and a single entry is added to $\cfgnt{L}_\beta$.
-The elements of the set $\theta_{all} = \cfgnt{L}_\beta(\cfgnt{R}_\beta(\cfgnt{l}_{un},\cfgnt{f}))$ can be divided into four distinct subsets, $\theta_{cur}$, $\theta_{null}$, $\theta_{new}$, and $\theta_{alias}$.
-The set $\theta_{cur}$ contains the pairs containing locations from the reference $r_a$, $\theta_{null}$ contains the pair with the null location, $\theta_{new}$ contains a pair with a new location, and $\theta_{alias}$ contains pairs representing alias locations.
-Any two constraints in $\theta_{cur}$ are guaranteed to be pairwise mutually exclusive because of the inductive hypothesis, and any single constraint is guaranteed to be pairwise mutually exclusive with any constraint in $\theta_{null}$, $\theta_{new}$, or $\theta_{alias}$ because constraints in $\theta_{cur}$ contain the conjunct $\neg \phi$, while constraints in the other three sets are conjoined with $\phi$.
-The set $\theta_{null}$ contains only one element, which in turn contains the constraint $r_f = r_{null}$, which is guaranteed to be mutually exclusive with any constraint in $\theta_{new}$, or $\theta_{alias}$ because constraints in those sets contain the conjunct $r_f \neq r_{null}$.
-The set $\theta_{new}$ contains one element, which in turn contains the constraint containing the conjunct $ \wedge_{\lp \cfgnt{r}^\prime_a,\ \phi^\prime_a,\ l^\prime_a\rp  \in \rho} \cfgnt{r}_f \ne \cfgnt{r}^\prime_a$, which is guaranteed to be mutually exclusive with any constraint in $\theta_{alias}$, because each constraint in that set contains the conjunct $r_f = r_a$ for some $(r_a\ \phi_a\ l_a)\in \rho$.
-Any two elements of the set $\theta_{alias}$ are guaranteed to pairwise mutually exclusive because for each constraint that contains the conjunct $r_f = r_a$, every other constraint contains the conjunct $r_f \ne r_a$.
-Thus, all constraints from all pairs in $\theta{all}$ are guaranteed to be mutually exclusive, and the property from Theorem~\ref{thm:mutex} holds for intermediate state $s_\beta$.
-
-We have now shown that whether there are any uninitialized fields or not, the mutual exclusivity property holds for any intermediate state $s_\beta$, so long as $s_\alpha \rightarrow_S s_\beta$ and the property holds for $s_\alpha$.
-So, since the mutual exclusivity property holds for $s_s$, $s_s \rightarrow_S s_1$, and $s_{i} \rightarrow_S s_{i+1} $ for all $i$ such that $0 < i < n$, we are guaranteed that the mutually exclusive property holds for the final intermediate state $s_n$.
-This concludes the inductive argument about
-\end{comment}
 \end{proof}
 
-%\begin{lemma}
-%\label{lem:lazyrefprops}
-%For any lazy state $s_\ell = ( \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta_\ell\ \cfgnt{e}_\ell\ \cfgnt{k}_\ell )$, for any reference $r \in \cfgnt{L}_\ell^\leftarrow$, 
-%$$ | \cfgnt{L}_\ell ( r) | = 1 $$
-%\end{lemma}
-%
-%\begin{proof}
-%In every rule in the Lazy machine that establishes a reference mapping, the value set contains exactly one location, constraint pair. 
-%\end{proof}
+\begin{lemma}[$\rightarrow_\mathit{FA}$ preserves location mutual exclusion]
+\label{lem:FA-mutex}
+Given a summary state, $s_\varsigma$, with a location mutual exclusive
+heap, $(\cfgnt{L}_\varsigma\ \cfgnt{R}_\varsigma) =
+\mathrm{heap}(s_\varsigma)$, the new heap,
+$(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
+\mathrm{heap}(s_\varsigma^\prime)$, in any related state on the field
+access rule, $s_\varsigma \rightarrow_\mathit{FA} s_\varsigma^\prime$, is also location mutual exclusive.
+\end{lemma}
+\begin{proof}
+Proof by definition of $\rightarrow_\mathit{FA}$ in \figref{fig:sym}.
+
+\lemref{lem:S-mutex} establishes that the heap coming out of the
+$S$-relation is location mutual exclusive, so it is only needed to
+show that location mutual exclusion is preserved by the call to the value function
+$\mathbb{VS}$ in the rule.
+
+\defref{def:VS} is the value function definition. From the definition,
+each constraint in each member of the value set has the form
+$(\phi\wedge \phi^\prime\ l)$ where $\phi$ and $\phi^\prime$ are the
+access constraints. The first constraint $\phi$ represents the
+condition under which the location is the location referenced by
+$r$. The second constraint, predicated on having resolved the actual
+location $\cfgnt{l}$ (expressed in $\phi$), is the condition under
+which the location $\cfgnt{l}^\prime$ is the actual object for the
+field as the reference for that field, $\cfgnt{r}^\prime =
+\cfgnt{R}(\cfgnt{l},\cfgnt{f})$, may point to several different
+locations.
+
+Choose any two distinct members of the value set, $(\phi_\alpha \wedge
+\phi_\alpha^\prime\ \ l_\alpha)$ and $(\phi_\beta \wedge
+\phi_\beta^\prime\ \ l_\beta)$. 
+\begin{itemize}
+\item If $\phi_\alpha = \phi_\beta$, then $\phi_\alpha^\prime \wedge
+  \phi_\beta^\prime = \cfgt{false}$ because $\cfgnt{l}_\alpha$ and
+  $\cfgnt{l}_\beta$ come from the same field reference, and since the
+  heap, $(\cfgnt{L}\ \cfgnt{R})$, is location mutual exclusive, locations
+  under a common reference must be mutual exclusive.
+\item If $\phi_\alpha \ne \phi_\beta$, then $\phi_\alpha \wedge \phi_\beta = \cfgt{false}$ because $\phi_\alpha$ comes from a location connected to $r$ that is different that the location connected to $r$ for $\phi_\beta$, and since the
+  heap, $(\cfgnt{L}\ \cfgnt{R})$, is location mutual exclusive, locations
+  under a common reference must be mutual exclusive.
+\end{itemize}
+The only change to the heap after the $S$-relation is applied is the addition of the new reference $\cfgnt{r}^\prime$ mapping to the value set from the value function.
+Since that set is location mutual exclusive and connect to $r^\prime$, the new heap $(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
+\mathrm{heap}(s_\varsigma^\prime)$ is also location mutual exclusive.
+\end{proof}
 
@@
 
-Base Case: Let $s_s$ be an initial state.
+(MUST SHOW IN THE FINAL THEOREM with statement that NO OTHER RULES MODIFY THE HEAP) Base Case: Let $s_s$ be an initial state.
 By Definition~\ref{def:initstate}, for every reference $r_i \in \cfgnt{L}_s^\leftarrow$, the set $\cfgnt{L}_s(r_i)$ contains at most one element.
@@
 
-Inductive Step: Now we will show that if the exclusivity property holds for some state $s_s$, then it holds for any state $s_s^\prime$ where $s_s \rightarrow_s s_s^\prime$.
-In order to evaluate whether Theorem~\ref{thm:mutex} holds for state any $s_s\prime$, we must consider the rule that applied during the transition from $s_s$ to $s_s\prime$.
-There are two broad classes of rules: rules where $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$, and rules where $ \cfgnt{L}_s =  \cfgnt{L}_{s^\prime}$.
-Rules in the $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$ class modify the structure of the heap, and must be considered carefully to to consider the impact of those modifications.
-Only three rules belong to the class $ \cfgnt{L}_s \neq  \cfgnt{L}_{s^\prime}$: Field Access, Field Read, and New.
-
-We begin by considering the Field Access rule.
-Suppose $s_s$ has the form $\lp \cfgnt{L}_s\ \cfgnt{R}_{s}\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.
-In this case, the relationship between $s_s$ and $s_s^\prime$ is described by the Field Access rule.
-intermediate state.
-
 We now use this result to show that the mutual exclusion property holds for state $s_s^\prime$.
 The relation between the L-function from the final intermediate state $\cfgnt{L}^\prime$ and the L-function in $s_s^\prime$ is $ \cfgnt{L}_{s^\prime} = \cfgnt{L}^\prime[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}^\prime,\cfgnt{R}^\prime,\cfgnt{r},\cfgnt{f},\phi_g\rp ]$, where a new value set is created based on the $\mathbb{VS}$ function.
-The members of the value set have the form $(\phi\wedge \phi^\prime\ \ l)$.
-Choose any two distinct members of the value set, $(\phi_\alpha \wedge \phi_\alpha^\prime\ \ l_\alpha)$ and $(\phi_\beta \wedge \phi_\beta^\prime\ \ l_\beta)$.
-If $\phi_\alpha \ne \phi_\beta$, we know that exclusivity holds because $\phi_\alpha$ and $\phi_\beta$ came from the same value set in $s_s$, and are therefore exclusive.
-If $\phi_\alpha = \phi_\beta$, we know that exclusivity holds because $\phi_\alpha^\prime$ and $\phi_\beta^\prime$ came from the same value set in $s_s$ and are therefore exclusive.
-Thus, the exclusivity property holds for any pair of constraints in the value set.
-Since the only new value set in $L_{s^\prime}^\rightarrow$ is generated by the $\mathbb{VS}$ function, we are guaranteed that if exclusivity holds for $s_s$, then exclusivity holds for $s_s^\prime$.
 

### 2014-10-01 tex/definitions.tex
Rewrote theorem 1
Added definition commentary

@@
 \subsection{Definitions}
+
+In Javalite, states are strings that match a certain pattern.
 
@@
 \label{def:state}
-The set of \textbf{states} $\mathcal{S}$ is defined as
+The set of \textbf{states} $\mathcal{S}$ is defined as the set of strings matching the pattern $s$ in \ref{fig:machine-syntax}.
 \end{definition}
@@
 
+You can think references as a pointers to sets of locations.
+More concretely, a reference is an integer that the $R$ function maps to a set of constraint, location pairs that define where it points to.
+Within a machine state, references are string encodings of integers.
+
 \begin{definition}
@@
 
-The total number of references in a summary state and a lazy state that it represents are generally not the same.
+In order to make the distinction between different types of references, we partition the set of references using modular arithmetic.
+Stack references are those references which are created as a result of a field read.
+The total number of references in a representing state and a represented state are generally not the same.
 However, the number of references on the stack in either state is always the same.
-In order to make the distinction between different types of references, we partition the set of natural numbers using modular arithmetic.
 
@@
 \end{definition}
+
+Input heap references are references that exist prior to program execution in the symbolic input heap.
+While this set of references may be infinite, they are discovered one at a time via lazy initialization.
 
@@
 \begin{definition}
-A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times \mathcal{S} $, which relat
-es machine states with successor states.
+A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times \mathcal{S} $, which relates machine states with successor states.
 Two important state transition relations are the \textbf{lazy state transition relation} $\rightarrow_\ell$ and the \textbf{summary state transition relation} $\rightarrow_\varsigma$.
@@
 
-\begin{definition}
-A state $s = (\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k})$ is a \textbf{lazy state} if and only if $\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (|\cfgnt{L}(\cfgnt{r})| = 1)$]
-\end{definition}
-
-\begin{definition}
-A state $s = (\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k})$ is a \textbf{summary state} if and only if 
-$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (|\cfgnt{L}(\cfgnt{r})| \ge 1)$.
-A lazy state is also a summary state by definition.
-\end{definition}
+%\begin{definition}
+%A state $s = (\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k})$ is a \textbf{lazy state} if and only if $\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (|\cfgnt{L}(\cfgnt{r})| = 1)$]
+%\end{definition}
+%
+%\begin{definition}
+%A state $s = (\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k})$ is a \textbf{summary state} if and only if 
+%$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (|\cfgnt{L}(\cfgnt{r})| \ge 1)$.
+%A lazy state is also a summary state by definition.
+%\end{definition}
 
@@
 \begin{array}{l}
-\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi_\alpha\ \cfgnt{l}_\alpha),(\phi_\beta\ \cfgnt{l}_\beta) \in \cfgnt{L}{r}\ (\\
+\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi_\alpha\ \cfgnt{l}_\alpha),(\phi_\beta\ \cfgnt{l}_\beta) \in \cfgnt{L}(r)\ (\\
 \ \ \ \ \cfgnt{l}_\alpha \neq \cfgnt{l}_\beta \Rightarrow \phi_\alpha \wedge \phi_\beta = \cfgt{false}))
@@
 \end{definition}
+
 %\begin{definition}
@@
 
+At times, it is useful to classify states in terms of patterns that the state strings match.
+In concrete terms, this is similar to asking what will be the next instruction to execute.
+For example, we know that left-hand states matching the pattern $ \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ only appear in the Field Access rule.
+
 \begin{definition}
@@
 
-\begin{definition}
-\label{def:interstate}
-\textbf{Intermediate states} are imaginary placeholder states used when reasoning about complex transition rules in terms of simpler sub-rules.
+%\begin{definition}
+%\label{def:interstate}
+%\textbf{Intermediate states} are imaginary placeholder states used when reasoning about complex transition rules in terms of simpler sub-rules.
 For example, the transition $s_x \rightarrow_\phi s_y$ may be equivalent to a sequence of simpler transitions $s_x \rightarrow_\alpha s_a \rightarrow_\beta s_b \rightarrow_\gamma s_y$.
@@
 However, it is important to remember that $s_a$ and $s_b$ are not technically involved in the transition $s_x \rightarrow_\phi s_y$, and indeed may not be part of any feasible state sequence under transition relation $\rightarrow_\phi$.
-\end{definition}
+%\end{definition}
 
@@
 
+We will later be concerned with establishing whether one state represents another state.
+We want to say that one state represents another state if equivalent paths lead out from each state.
+This path-centric notion of equivalence is known as functional equivalence.
+In establishing functional equivalence between states, it is important to determine whether the heaps within the states are themselves functionally equivalent.
+Two heaps are functionally equivalent if the same sequence of field accesses in each heap produces equivalent results.
+We define heap functional equivalence using a co-inductive definition of homomorphism over the access paths in the heaps.
+
 \begin{definition}
@@
 
+Since the access paths in any given heap are bound by certain constraints, to preserve control flow equivalence we must establish whether the collection of any constraints in a given heap are collectively feasible.
+The homomorphism constraint is the conjunction of all constraints in the image of the represented heap in the representer heap.
+
 \begin{definition}
@@
 \end{definition}
+
+The representation relation combines the previously established notions of heap homomorphism and feasibility with the added constraint that the variables, expressions, and continuation strings must match between the pairs of states.
 

### 2014-10-02 tex/proofs.tex
Renamed location mutual exclusion to detemrnism

@@
 homomorphism in the equals-reference rule relies on the incoming heap
-being location mutual exclusive. The $S$-relation effectively produces
+being deterministic. The $S$-relation effectively produces
 an intermediary state that is the state where uninitialized references
@@
 homomorphism from the existing homomorphism: which location should be
-used in the map? As such, the proof first establishes that
-the $\varsigma$-relation preserves location mutual exclusive in the
-incoming heap. Once that is shown, the exactness of the equals
+used in the map? As such, the proof first establishes that the
+$\varsigma$-relation preserves determinism when the incoming heap is
+deterministic. Once that is shown, the exactness of the equals
 reference rule is given.
@@
 
-\begin{lemma}[$\rightarrow^*_S$ preserves location mutual exclusion]
+\begin{lemma}[$\rightarrow^*_S$ preserves heap determinism]
 \label{lem:S-mutex}
-Given a location mutual exclusive heap, $(\cfgnt{L}_0\ \cfgnt{R}_0)$, from a
+Given a deterministic heap, $(\cfgnt{L}_0\ \cfgnt{R}_0)$, from a
 summary state with a reference $\cfgnt{r}$ and field $\cfgnt{f}$, the
@@
 \rightarrow^*_S
-(\cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \cfgnt{r}\ \cfgnt{f})$, after any number of machine steps, is also
-location mutual exclusive.
+(\cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \cfgnt{r}\ \cfgnt{f})$, after any number of machine steps, is also deterministic.
 \end{lemma}
@@
 \cfgnt{f})$ be the set of uninitialized locations. If $\Lambda = \emptyset$, then the \texttt{Summarize (end)}
-rule is active and $(\cfgnt{L}_1\ \cfgnt{R}_1) = (\cfgnt{L}_0\ \cfgnt{R}_0)$, which is location mutual exclusive by the initial conditions in the lemma.
+rule is active and $(\cfgnt{L}_1\ \cfgnt{R}_1) = (\cfgnt{L}_0\ \cfgnt{R}_0)$, which is deterministic by the initial conditions in the lemma.
 
@@
 \begin{itemize}
-\item Any member of $\theta_\mathit{null}$, $\theta_\mathit{new}$, and
-  $\theta_\mathit{alias}$ has a constraint of the form $\phi_x \wedge
-  \ldots$ while any member of $\theta_\mathrm{orig}$ has a constraint
-  of the form $\neg \phi_x \wedge \ldots$. As every
-  $(\phi_\mathit{orig}\ \cfgnt{l}_\mathit{orig}) \in
-  \cfgnt{L}_n(\cfgnt{R}_n(\cfgnt{l}_x,\cfgnt{f}))$ is location mutual exclusive
-  by the initial conditions on $(\cfgnt{L}_0\ \cfgnt{R}_0)$ in the lemma statement, members of $\theta_\mathit{orig}$ are location
-  mutual exclusive with each other and with members in $\theta_\mathit{null}$,
-  $\theta_\mathit{new}$, and $\theta_\mathit{alias}$.
-\item Any member of $\theta_\mathit{null}$ has the form $\ldots \wedge
+\item The original heap is
+  deterministic by definition, so any constraint in any member of the
+  set must have some term such that
+  \[\begin{array}{l}
+     \forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \theta_\mathit{orig}\ \\
+     \ \ \ \ ((\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
+     \end{array}
+  \]
+  Further, any member of $\theta_\mathrm{orig}$ has a constraint
+  of the form $\phi = \neg \phi_x \wedge \ldots$ while any member of $\theta_\mathit{null}$, $\theta_\mathit{new}$, and
+  $\theta_\mathit{alias}$ has a constraint of the form $\phi^\prime = \phi_x \wedge
+  \ldots$; thus
+  \[\begin{array}{l}
+     \forall (\phi\ \cfgnt{l}) \in \theta_\mathit{orig}\ (\forall (\phi^\prime\ \cfgnt{l}^\prime) \in \theta_\mathit{null} \cup \theta_\mathit{new} \cup \theta_\mathit{alias}\ (\\
+     \ \ \ \ \phi \wedge \phi^\prime = \cfgt{false}))
+    \end{array}
+  \]
+\item The only member of $\theta_\mathit{null}= \{(\phi\ \cfgnt{l}_\mathit{null})\}$ has the form $\phi = \ldots \wedge
   \cfgnt{r}_f = \cfgnt{r}_\mathit{null}$ while any member of
   $\theta_\mathit{new}$ and $\theta_\mathit{alias}$ has the form
-  $\ldots \wedge \cfgnt{r}_f \neq \cfgnt{r}_\mathit{null} \wedge
-  \ldots$. As $\theta_\mathit{null}$ is a singleton set, its location is
-  location mutual exclusive from those in $\theta_\mathit{new}$ and
-  $\theta_\mathit{alias}$.
-\item Any member of $\theta_\mathit{new}$ has a constraint of the form
-  $\ldots \wedge ( \wedge_{(
-  \cfgnt{r}_a,\ \phi_a,\ l_a) \in \rho}
-  \cfgnt{r}_f \ne \cfgnt{r}_a) )$ to assert it does not
-  alias anything while any member of $\theta_\mathit{alias}$ has
-  the form $\ldots \wedge \cfgnt{r}_f = \cfgnt{r}_a \wedge \ldots$ for
-  some alias $\cfgnt{r}_a$ with both partitions reasoning over the same set of aliases $\rho$.  As $\theta_\mathit{new}$ is a singleton set, its
-  location is location mutual exclusive from any member of
-  $\theta_\mathit{alias}$.
+  $\phi^\prime = \ldots \wedge \cfgnt{r}_f \neq \cfgnt{r}_\mathit{null} \wedge
+  \ldots$; thus
+  \[\begin{array}{l}
+     \forall (\phi^\prime\ \cfgnt{l}^\prime) \in \theta_\mathit{new} \cup \theta_\mathit{alias}\ (
+     \phi \wedge \phi^\prime = \cfgt{false})
+    \end{array}
+  \]
+\item The only member of $\theta_\mathit{new} =  \{(\phi\ \cfgnt{l}_f)\}$ has a constraint of the form
+  $\phi = \ldots \wedge ( \wedge_{( \cfgnt{r}_a,\ \phi_a,\ l_a) \in \rho}
+  \cfgnt{r}_f \ne \cfgnt{r}_a) )$ to assert it does not alias
+  anything, while any member of $\theta_\mathit{alias}$ has the form
+  $\phi^\prime = \ldots \wedge \cfgnt{r}_f = \cfgnt{r}_a \wedge \ldots$ to assert it aliases some
+  $\cfgnt{r}_a$ with both partitions reasoning over the same set
+  of aliases $\rho$; thus
+  \[\begin{array}{l}
+     \forall (\phi^\prime\ \cfgnt{l}^\prime) \in \theta_\mathit{alias}\ (
+     \phi \wedge \phi^\prime = \cfgt{false})
+    \end{array}
+  \]
 \item Any member of $\theta_\mathit{alias}$ has the form
 \[\ldots \wedge \cfgnt{r}_f = \cfgnt{r}_a \wedge ( \wedge_{( \cfgnt{r}^{\prime}_a\ \phi^{\prime}_a\ l^{\prime}_a)  \in \rho\ ( \cfgnt{r}^\prime_a \neq \cfgnt{r}_a) } \cfgnt{r}_f \neq \cfgnt{r}^{\prime}_a)\]
-Each is mutually exclusive over the particular alias it asserts.
+And thus, 
+  \[\begin{array}{l}
+     \forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \theta_\mathit{alias}\\
+     \ \ \ \ ((\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
+     \end{array}
+  \]
 \end{itemize}
-Every member in $\theta = \theta_\mathit{null} \cup
-\theta_\mathit{new} \cup \theta_\mathit{alias} \cup
-\theta_\mathit{orig}$ is thus location mutual exclusive making $(\cfgnt{L}_1\ \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f})$ location mutual exclusive as well.
+As $\theta$ is mapped to a single reference $r_f$ in an already deterministic heap, the
+resulting heap $(\cfgnt{L}_1\ \cfgnt{R}_1)$ is likewise deterministic.
 
@@
 
-\begin{lemma}[$\rightarrow_\mathit{FA}$ preserves location mutual exclusion]
+\begin{lemma}[$\rightarrow_\mathit{FA}$ preserves heap determinism]
 \label{lem:FA-mutex}
-Given a summary state, $s_\varsigma$, with a location mutual exclusive
-heap, $(\cfgnt{L}_\varsigma\ \cfgnt{R}_\varsigma) =
+Given a state, $s_\varsigma$, with a deterministic heap,
+$(\cfgnt{L}_\varsigma\ \cfgnt{R}_\varsigma) =
 \mathrm{heap}(s_\varsigma)$, the new heap,
 $(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
-\mathrm{heap}(s_\varsigma^\prime)$, in any related state on the field
-access rule, $s_\varsigma \rightarrow_\mathit{FA} s_\varsigma^\prime$, is also location mutual exclusive.
+\mathrm{heap}(s_\varsigma^\prime)$, in any state related by the field
+access rule, $s_\varsigma \rightarrow_\mathit{FA} s_\varsigma^\prime$,
+is also deterministic.
 \end{lemma}
@@
 \lemref{lem:S-mutex} establishes that the heap coming out of the
-$S$-relation is location mutual exclusive, so it is only needed to
-show that location mutual exclusion is preserved by the call to the value function
-$\mathbb{VS}$ in the rule.
+$S$-relation is deterministic, so it is only needed to show that
+determinism is preserved by the call to the value function,
+$\mathbb{VS}$, in the rule.
 
-\defref{def:VS} is the value function definition. From the definition,
-each constraint in each member of the value set has the form
-$(\phi\wedge \phi^\prime\ l)$ where $\phi$ and $\phi^\prime$ are the
-access constraints. The first constraint $\phi$ represents the
-condition under which the location is the location referenced by
-$r$. The second constraint, predicated on having resolved the actual
-location $\cfgnt{l}$ (expressed in $\phi$), is the condition under
-which the location $\cfgnt{l}^\prime$ is the actual object for the
-field as the reference for that field, $\cfgnt{r}^\prime =
-\cfgnt{R}(\cfgnt{l},\cfgnt{f})$, may point to several different
-locations.
-
-Choose any two distinct members of the value set, $(\phi_\alpha \wedge
-\phi_\alpha^\prime\ \ l_\alpha)$ and $(\phi_\beta \wedge
-\phi_\beta^\prime\ \ l_\beta)$. 
+Recall from \defref{def:VS} that each constraint in each member of the value set has the form
+$(\phi\wedge \phi^\prime\ l)$. Choose any two distinct members of the value set, $(\phi_\alpha \wedge
+\phi_\alpha^\prime\ l_\alpha^\prime)$ and $(\phi_\beta \wedge
+\phi_\beta^\prime\ l_\beta^\prime)$.
 \begin{itemize}
-\item If $\phi_\alpha = \phi_\beta$, then $\phi_\alpha^\prime \wedge
-  \phi_\beta^\prime = \cfgt{false}$ because $\cfgnt{l}_\alpha$ and
-  $\cfgnt{l}_\beta$ come from the same field reference, and since the
-  heap, $(\cfgnt{L}\ \cfgnt{R})$, is location mutual exclusive, locations
-  under a common reference must be mutual exclusive.
-\item If $\phi_\alpha \ne \phi_\beta$, then $\phi_\alpha \wedge \phi_\beta = \cfgt{false}$ because $\phi_\alpha$ comes from a location connected to $r$ that is different that the location connected to $r$ for $\phi_\beta$, and since the
-  heap, $(\cfgnt{L}\ \cfgnt{R})$, is location mutual exclusive, locations
-  under a common reference must be mutual exclusive.
+\item If $\phi_\alpha = \phi_\beta$, then by \defref{lem:S-mutex} 
+\[\begin{array}{l}
+\exists (\phi_\alpha\ \cfgnt{l}) \in \cfgnt{L}(\cfgnt{r})\ (\exists \cfgnt{r}^\prime \in \cfgnt{R}(\cfgnt{l},\cfgnt{f})\ (\\
+\ \ \ \ (\phi_\alpha^\prime\ l_\alpha^\prime) \in \cfgnt{L}(\cfgnt{r}^\prime) \wedge (\phi_\beta^\prime\ l_\beta^\prime) \in \cfgnt{L}(\cfgnt{r}^\prime)))
+\end{array}
+\]
+As $(\phi_\alpha^\prime\ \cfgnt{l}_\alpha^\prime)$ and $(\phi_\beta^\prime\ \cfgnt{l}_\beta^\prime)$ are distinct and connected to the same reference $\cfgnt{r}^\prime$ in a deterministic heap, $\phi_\alpha^\prime \wedge  \phi_\beta^\prime = \cfgt{false}$ by definition.
+\item If $\phi_\alpha \ne \phi_\beta$, then by \defref{lem:S-mutex} 
+\[\begin{array}{l}
+\exists \cfgnt{l}\ ((\phi_\alpha\ \cfgnt{l}) \in \cfgnt{L}(\cfgnt{r}) \wedge \exists \cfgnt{l}^\prime \neq \cfgnt{l} \ ((\phi_\beta\ \cfgnt{l}^\prime) \in \cfgnt{L}(\cfgnt{r})))
+\end{array}
+\]
+As $(\phi_\alpha\ \cfgnt{l})$ and $(\phi_\beta\ \cfgnt{l}^\prime)$ are distinct and connected to the same reference $\cfgnt{r}$ in a deterministic heap, $\phi_\alpha \wedge  \phi_\beta = \cfgt{false}$ by definition.
 \end{itemize}
-The only change to the heap after the $S$-relation is applied is the addition of the new reference $\cfgnt{r}^\prime$ mapping to the value set from the value function.
-Since that set is location mutual exclusive and connect to $r^\prime$, the new heap $(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
-\mathrm{heap}(s_\varsigma^\prime)$ is also location mutual exclusive.
+The only change to the heap after the $S$-relation is the
+addition of the new reference $\cfgnt{r}^\prime$ to point to the value
+set. As the value set meets the conditions for determinism, the new heap $(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
+\mathrm{heap}(s_\varsigma^\prime)$ is also deterministic.
 \end{proof}

### 2014-10-02 tex/precise.tex
Finished FW is deterministic

@@
 \label{def:ST}
-The strengthen function $\mathbb{ST}(L,r,\phi^\prime)$ strengthens every
-constraint from the reference $r$ with $\phi^\prime$ and keeps only location-constraint
-pairs that are satisfiable after this strengthening:
+The strengthen function $\mathbb{ST}(\cfgnt{L},\cfgnt{r},\phi,\phi_g)$ strengthens every
+constraint from the reference $\cfgnt{r}$ with $\phi$ and keeps only location-constraint
+pairs that are satisfiable after this strengthening with the inclusion of the global heap constraint $\phi_g$:
 \[
 \begin{array}{rcl} 
-\mathbb{ST}(L,r,\phi,\phi_g) & = & \{ (\phi\wedge\phi^\prime\ l) \mid  \\
-& & \ \ \ \ (\phi^\prime\ l)\in L(r)\wedge\mathbb{S}(\phi\wedge\phi^\prime\wedge\phi_g) \}
+\mathbb{ST}(\cfgnt{L},\cfgnt{r},\phi,\phi_g) & = & \{ (\phi\wedge\phi^\prime\ \cfgnt{l}^\prime) \mid  \\
+& & \ \ \ \ (\phi^\prime\ \cfgnt{l}^\prime)\in \cfgnt{L}(\cfgnt{r})\wedge\mathbb{S}(\phi\wedge\phi^\prime\wedge\phi_g) \}
 \end{array}

### 2014-10-02 tex/proofs.tex
Finished FW is deterministic

@@
 determinism is preserved by the call to the value function,
-$\mathbb{VS}$, in the rule.
+$\mathbb{VS}$, in the rule. Let $(\cfgnt{L}\ \cfgnt{R})$ be that new
+deterministic heap.
 
 Recall from \defref{def:VS} that each constraint in each member of the value set has the form
-$(\phi\wedge \phi^\prime\ l)$. Choose any two distinct members of the value set, $(\phi_\alpha \wedge
-\phi_\alpha^\prime\ l_\alpha^\prime)$ and $(\phi_\beta \wedge
-\phi_\beta^\prime\ l_\beta^\prime)$.
+$(\phi\wedge \phi^\prime\ \cfgnt{l})$. Choose any two distinct members of the value set, $(\phi_\alpha \wedge
+\phi_\alpha^\prime\ \cfgnt{l}_\alpha^\prime)$ and $(\phi_\beta \wedge
+\phi_\beta^\prime\ \cfgnt{l}_\beta^\prime)$.
 \begin{itemize}
-\item If $\phi_\alpha = \phi_\beta$, then by \defref{lem:S-mutex} 
+\item If $\phi_\alpha = \phi_\beta$, then by \defref{def:VS} 
 \[\begin{array}{l}
@@
 As $(\phi_\alpha^\prime\ \cfgnt{l}_\alpha^\prime)$ and $(\phi_\beta^\prime\ \cfgnt{l}_\beta^\prime)$ are distinct and connected to the same reference $\cfgnt{r}^\prime$ in a deterministic heap, $\phi_\alpha^\prime \wedge  \phi_\beta^\prime = \cfgt{false}$ by definition.
-\item If $\phi_\alpha \ne \phi_\beta$, then by \defref{lem:S-mutex} 
+\item If $\phi_\alpha \ne \phi_\beta$, then by \defref{def:VS} 
 \[\begin{array}{l}
@@
 addition of the new reference $\cfgnt{r}^\prime$ to point to the value
-set. As the value set meets the conditions for determinism, the new heap $(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
-\mathrm{heap}(s_\varsigma^\prime)$ is also deterministic.
+set. As the value set meets the conditions for determinism, the new heap, $(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
+\mathrm{heap}(s_\varsigma^\prime)$, is also deterministic.
+\end{proof}
+
+\begin{lemma}[$\rightarrow_\mathit{FW}$ preserves heap determinism]
+\label{lem:FW-mutex}
+Given a state, $s_\varsigma$, with a deterministic heap,
+$(\cfgnt{L}_\varsigma\ \cfgnt{R}_\varsigma) =
+\mathrm{heap}(s_\varsigma)$, the new heap,
+$(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
+\mathrm{heap}(s_\varsigma^\prime)$, in any state related by the field
+write rule, $s_\varsigma \rightarrow_\mathit{FW} s_\varsigma^\prime$,
+is also deterministic.
+\end{lemma}
+\begin{proof}
+Proof by definition of $\rightarrow_\mathit{FW}$ in \figref{fig:sym}.
+
+The $\rightarrow_\mathit{FW}$ rule relies on the $\mathbb{ST}$
+function. Recall from \defref{def:ST} that each constraint in each
+member of the strengthened set has the form $(\phi\wedge
+\phi^\prime\ \cfgnt{l}^\prime)$ where every member,
+$(\phi^\prime\ \cfgnt{l}^\prime)$, comes from
+$\cfgnt{L}_\varsigma(\cfgnt{r})$ on the same reference in a
+deterministic heap $(\cfgnt{L}_\varsigma\ \cfgnt{R}_\varsigma)$; thus,
+that set of meets the criteria for determinism by definition. So any
+application of $\mathbb{ST}$ preserves that criteria for determinism.
+
+The $\rightarrow_\mathit{FW}$ makes two uses of the $\mathbb{ST}$
+function, $\theta = \mathbb{ST}(\cfgnt{L},\cfgnt{r},\phi,\phi_g) \cup
+\mathbb{ST}(\cfgnt{L},\cfgnt{r}_\mathit{cur},\neg\phi,\phi_g)$, to
+build individual $\theta$ sets. Choose any two distinct members of $\theta$,
+$(\phi_\alpha \wedge \phi_\alpha^\prime\ \cfgnt{l}_\alpha^\prime)$ and
+$(\phi_\beta \wedge \phi_\beta^\prime\ \cfgnt{l}_\beta^\prime)$.
+\begin{itemize}
+\item If $\phi_\alpha = \phi_\beta$, then the constraints came from the
+  same call to $\mathbb{ST}$ so $\phi_\alpha^\prime \wedge
+  \phi_\beta^\prime = \cfgt{false}$ by definition.
+\item If $\phi_\alpha \ne \phi_\beta$, then the constraints came from
+  the different calls and are distinguished by the phase of $\phi$ in
+  the call so $\phi_\alpha \wedge \phi_\beta = \cfgt{false}$.
+\end{itemize}
+Each $\theta$ is mapped to a new reference from
+$\mathrm{fresh}_r()$. These are added to an already deterministic heap
+$(\cfgnt{L}_\varsigma\ \cfgnt{R}_\varsigma)$ and meet the criteria so
+that $(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime)$ is also
+deterministic.
 \end{proof}

### 2014-10-03 tex/proofs.tex
Finished heap determinism

@@
 \begin{lemma}[$\rightarrow^*_S$ preserves heap determinism]
-\label{lem:S-mutex}
+\label{lem:S-determ}
 Given a deterministic heap, $(\cfgnt{L}_0\ \cfgnt{R}_0)$, from a
@@
 \begin{lemma}[$\rightarrow_\mathit{FA}$ preserves heap determinism]
-\label{lem:FA-mutex}
+\label{lem:FA-determ}
 Given a state, $s_\varsigma$, with a deterministic heap,
@@
 
-\lemref{lem:S-mutex} establishes that the heap coming out of the
+\lemref{lem:S-determ} establishes that the heap coming out of the
 $S$-relation is deterministic, so it is only needed to show that
@@
 \end{itemize}
-The only change to the heap after the $S$-relation is the
-addition of the new reference $\cfgnt{r}^\prime$ to point to the value
-set. As the value set meets the conditions for determinism, the new heap, $(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
+The only change to the heap after the $S$-relation is the addition of
+the new reference $\cfgnt{r}^\prime = \mathrm{stack}_\cfgnt{r}()$ to
+point to the value set. As the value set meets the conditions for
+determinism, the new heap with $r^\prime$ and the value set,
+$(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
 \mathrm{heap}(s_\varsigma^\prime)$, is also deterministic.
@@
 \begin{lemma}[$\rightarrow_\mathit{FW}$ preserves heap determinism]
-\label{lem:FW-mutex}
+\label{lem:FW-determ}
 Given a state, $s_\varsigma$, with a deterministic heap,
@@
 
-\begin{theorem}[$\rightarrow_\varsigma$ preserves location mutual exclusion]
-\label{thm:mutex}
-Given a summary state, $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, such that $s_s \rightarrow_\varsigma s_s^\prime$, where $s_s^\prime = ( \cfgnt{L}_s^\prime\ \cfgnt{R}_s^\prime\ \phi_s^\prime\ \eta_s^\prime\ \cfgnt{e}_s^\prime\ \cfgnt{k}_s^\prime )$, if the heap $(\cfgnt{L}_s\ \cfgnt{R}_s)$ is location mutual exclusive then the heap after the transition, $(\cfgnt{L}_s^\prime\ \cfgnt{R}_s^\prime)$ is also location mutual exclusive.
-\begin{comment}
-If we have a reachable summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$
-$$ 
-\begin{array}{l}
-\forall (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_s(\cfgnt{r})\ (\forall (\phi_\beta\ \cfgnt{l}_\beta) \in \cfgnt{L}_s(\cfgnt{r})\ ( \\
-\ \ \ \ (\cfgnt{l}_\alpha \neq \cfgnt{l}_\beta) \Rightarrow ((\phi_\alpha \wedge \phi_\beta) = \cfgt{false})))
-\end{array}
-$$
-\end{comment}
+\begin{lemma}[$\rightarrow_J$ preserves heap determinism]
+\label{lem:J-determ}
+Given a state, $s_\varsigma$, with a deterministic heap,
+$(\cfgnt{L}_\varsigma\ \cfgnt{R}_\varsigma) =
+\mathrm{heap}(s_\varsigma)$, the new heap,
+$(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
+\mathrm{heap}(s_\varsigma^\prime)$, in any state related by the
+Javalite relation, $s_\varsigma \rightarrow_J s_\varsigma^\prime$, is
+also deterministic.
+\end{lemma}
+\begin{proof}
+Proof by definition of $\rightarrow_J$ in \figref{fig:javalite-common}.
+
+Every rule in $\rightarrow_J$ except \texttt{New} leaves the heap
+unmodified. The rule for \texttt{New} adds a single new location
+($\mathrm{fresh}_\cfgnt{l}(\cfgnt{C})$) to the heap on a single new
+reference ($\mathrm{stack}_r()$). The rule also points every field in
+the new location to $\cfgnt{r}_\mathit{null}$. As none of these
+mutations alter the determinism of the heap, the new heap
+$(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime)$ is also
+deterministic.
+\end{proof}
+
+\begin{theorem}[$\rightarrow_\varsigma$ preserves heap determinism]
+\label{thm:determ}
+Given a state, $s_\varsigma$, with a deterministic heap,
+$(\cfgnt{L}_\varsigma\ \cfgnt{R}_\varsigma) =
+\mathrm{heap}(s_\varsigma)$, the new heap,
+$(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
+\mathrm{heap}(s_\varsigma^\prime)$, in any state related by the
+symbolic relation, $s_\varsigma \rightarrow_\varsigma s_\varsigma^\prime$, is
+also deterministic.
 \end{theorem}
 \begin{proof}
-The proof will proceed inductively.
-
-(MUST SHOW IN THE FINAL THEOREM with statement that NO OTHER RULES MODIFY THE HEAP) Base Case: Let $s_s$ be an initial state.
-By Definition~\ref{def:initstate}, for every reference $r_i \in \cfgnt{L}_s^\leftarrow$, the set $\cfgnt{L}_s(r_i)$ contains at most one element.
-Thus, the requirement that $l_\alpha \ne l_\beta$ is never met, and the Theorem is vacuously true.
-
-We now use this result to show that the mutual exclusion property holds for state $s_s^\prime$.
-The relation between the L-function from the final intermediate state $\cfgnt{L}^\prime$ and the L-function in $s_s^\prime$ is $ \cfgnt{L}_{s^\prime} = \cfgnt{L}^\prime[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}^\prime,\cfgnt{R}^\prime,\cfgnt{r},\cfgnt{f},\phi_g\rp ]$, where a new value set is created based on the $\mathbb{VS}$ function.
-
-Suppose we have a field write instruction.
-This case is nearly identical as the field read.
-In this instruction, a new value set is created.
-The members of the value set have the form $(\phi\wedge \phi^\prime\ \ l)$.
-Choose any two distinct members of the value set, $(\phi_\alpha \wedge \phi_\alpha^\prime\ \ l_\alpha)$ and $(\phi_\beta \wedge \phi_\beta^\prime\ \ l_\beta)$.
-If $\phi_\alpha \ne \phi_\beta$, we know that exclusivity holds because $\phi_\alpha = \neg \phi_\beta$, so $\phi_\alpha$ and $\phi_\beta$ are therefore exclusive.
-If $\phi_\alpha = \phi_\beta$, we know that exclusivity holds because $\phi_\alpha^\prime$ and $\phi_\beta^\prime$ came from the same value set in $s_s$ and are therefore exclusive.
-Thus, the exclusivity property holds for any pair of constraints in the value set.
-Since exclusivity holds for the only new value set in $L_{s^\prime}^\rightarrow$, we are guaranteed that if exclusivity holds for $s_s$, then exclusivity holds for $s_s^\prime$.
-
-Suppose we have a "new" instruction. In this case, only one value set is added to $L_{s^\prime}^\rightarrow$, and that value set contains only one member, so exclusivity holds by default.
-
-Suppose we have any instruction other that a read, write, or new.
-No machine rule other than those three listed instructions modifies the $L$ function.
-Therefore, the exclusivity property must hold for $s_s^\prime$ in these cases.
-
-Since the exclusivity property holds for any initial state, and since it holds for any "next" state if the property holds for the previous state, we have proven the property for every symbolic state.
-\end{proof}
-
-\begin{corollary}
-Any state represented by any reachable summary state is a lazy state.
-\end{corollary}
-
-\begin{proof}
-By Theorem \ref{thm:mutex} since the constraints on every reference are mutually exclusive, the heap constraint for any heap with a reference pointing to more than one location will be unsatisfiable, and by Definition \ref{representation} will not be represented by the summary state.
+Proof by \lemref{FA-determ}, \lemref{FW-determ}, and \lemref{J-determ}
+which represent all the rules that relate states in
+$\rightarrow_\varsigma$.
 \end{proof}

### 2014-10-03 tex/definitions.tex
Renamed location mutual exclusion to detemrnism
Macro'd and renamed all the relations and state designations--first pass

@@
 A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times \mathcal{S} $, which relates machine states with successor states.
-Two important state transition relations are the \textbf{lazy state transition relation} $\rightarrow_\ell$ and the \textbf{summary state transition relation} $\rightarrow_\varsigma$.
-Each of these use a separate relation for initialization: $\rightarrow_I$ for initialization the lazy transition relation and $\rightarrow_S$ for initialization the summary transition relation.
+Two important state transition relations are \textbf{GSE} $\rgse$ and \textbf{symbolic} $\rsym$.
+Each of these use a separate relation for initialization: $\rinit$ for GSE and $\rsum$ for symbolic.
 All of these transition relations are defined in \figref{fig:lazy}, \figref{fig:lazyInit}, \figref{fig:sym}, and \figref{fig:symInit}.
@@
 \begin{definition}
-A heap, $(\cfgnt{L}\ \cfgnt{R})$, is \textbf{location mutual exclusive} if and only if 
+A heap, $(\cfgnt{L}\ \cfgnt{R})$, is \textbf{deterministic} if and only if 
 \[
 \begin{array}{l}
-\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi_\alpha\ \cfgnt{l}_\alpha),(\phi_\beta\ \cfgnt{l}_\beta) \in \cfgnt{L}(r)\ (\\
-\ \ \ \ \cfgnt{l}_\alpha \neq \cfgnt{l}_\beta \Rightarrow \phi_\alpha \wedge \phi_\beta = \cfgt{false}))
+\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
+\ \ \ \ (\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
 \end{array}

### 2014-10-03 tex/proofs.tex
Macro'd and renamed all the relations and state designations--first pass

@@
 \eqref{eqn:BisimulationForwards} and
-\eqref{eqn:BisimulationBackwards}.  A bisimulation is a relation over pairs of states such that whenever two states, $s_\ell$ and
-$s_\varsigma$, are related in the bisimulation, $s_\ell \sqsubset
-s_\varsigma$, every successor, from either state, $s_\ell
-\rightarrow_\ell s_\ell^\prime$ or $s_\varsigma \rightarrow_\varsigma
-s_\varsigma^\prime$, has a corresponding mutual successor in the other
+\eqref{eqn:BisimulationBackwards}.  A bisimulation is a relation over pairs of states such that whenever two states, $s_\gse$ and
+$s_\sym$, are related in the bisimulation, $s_\gse \sqsubset
+s_\sym$, every successor, from either state, $s_\gse
+\rgse s_\gse^\prime$ or $s_\sym \rsym
+s_\sym^\prime$, has a corresponding mutual successor in the other
 state such that both of those successors are also related in the
-bisimulation: $s_\ell^\prime \sqsubset s_\varsigma^\prime$.
+bisimulation: $s_\gse^\prime \sqsubset s_\sym^\prime$.
 
-If the $\varsigma$-relation is considered to be a model of the
-$\ell$-relation (i.e., a representation of that machine), then the
+If $\rsym$ is considered to be a model of the
+$\rgse$ (i.e., a representation of that machine), then the
 representation relation, as a bisimulation, ensures that the
-$\varsigma$-relation is complete in that any property that can be
-shown in the $\ell$-relation can also be shown in the
-$\varsigma$-relation; and further, the representation relation as a
-bisimulation ensures that the $\varsigma$-relation is also sound in
-that any property that can be shown to hold in the $\varsigma$-relation
-can also be shown to hold in the $\ell$-relation.
+$\rsym$ is complete in that any property that can be
+shown in states related on $\rgse$ can also be shown in the
+$\rsym$; and further, the representation relation as a
+bisimulation ensures that the $\rsym$ is also sound in
+that any property that can be shown to hold in states related by $\rsym$
+can also be shown to hold in the $\rgse$.
 
 The proof of the representation relation as a bisimulation reasons
-over individual rules in the $\varsigma$-relation to show that for
+over individual rules in $\rsym$ to show that for
 each rule, the representation relation, $\sqsubset$, exists. The heart
@@
 successor states. With such a new homomorphism, it is possible to
-state that for the $\varsigma$-relation, when restricted to a specific
+state that for $\rsym$, when restricted to a specific
 rule (i.e., that is the only rule available in the relation), the
-representation relation is a bisimulation for that restricted
-$\varsigma$-relation. If such a bisimulation exists for all the
+representation relation is a bisimulation for the restricted
+$\rsym$. If such a bisimulation exists for all the
 individual rules, then it exists for the rules collectively.
@@
 There are two slight complications in the proof: first, the field
-access rule relies on the $S$-relation that operates on a different
-state than then $\varsigma$-relation; and second, constructing the new
+access rule relies on $\rsum^*$ that operates on a different
+state than $\rsym$; and second, constructing the new
 homomorphism in the equals-reference rule relies on the incoming heap
-being deterministic. The $S$-relation effectively produces
+being deterministic. The relation $\rsum^*$ effectively produces
 an intermediary state that is the state where uninitialized references
 are initialized before the field access actually takes place. In
-essence, a state on the left of the $\varsigma$-relation that is a
+essence, a state on the left of $\rsym$ that is a
 field access, undergoes a transition in which its heap is changed to
@@
 initialized fields is the intermediary state between the state on the
-left of the $\varsigma$-relation and the state on the right of the
-$\varsigma$-relation. The proof reasons separately about this
+left of $\rsym$ and the state on the right of $\rsym$. The proof reasons separately about this
 intermediary state to prove that it too is exact.
@@
 homomorphism from the existing homomorphism: which location should be
-used in the map? As such, the proof first establishes that the
-$\varsigma$-relation preserves determinism when the incoming heap is
+used in the map? As such, the proof first establishes that
+$\rsym$ preserves determinism when the incoming heap is
 deterministic. Once that is shown, the exactness of the equals
@@
 \label{lem:init}
-If $s_s \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$ for symbolic state $s_s = \lp \cfgnt{L}_s\ \cfgnt{R}_{s}\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$, initial state $s_0$, and control flow path $\pi_n$, and if there exists some intermediate state state $s_s^\prime$ such that $(\cfgnt{L}_s\ \cfgnt{R}_{s}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C}) \rightarrow_S^* (\cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C})$, then:
- $$s_s^\prime \cong \{\forall s_\ell^\prime | \exists s_\ell (s_\ell \sqsubset s_s \wedge (s_\ell \rightarrow_I^* s_\ell^\prime) ) \}$$
+If $s_\sym \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$ for symbolic state $s_\sym = \lp \cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \phi_\sym\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$, initial state $s_0$, and control flow path $\pi_n$, and if there exists some intermediate state state $s_\sym^\prime$ such that $(\cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C}) \rsum^* (\cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C})$, then:
+ $$s_\sym^\prime \cong \{\forall s_\gse^\prime | \exists s_\gse (s_\gse \sqsubset s_\sym \wedge (s_\gse \rinit^* s_\gse^\prime) ) \}$$
 \end{lemma}
@@
 \begin{proof}
-In order for a state to be equivalent to a set of lazy states, it must be both sound and complete with respect to the set.
+In order for a state to be equivalent to a set of GSE states, it must be both sound and complete with respect to the set.
 We will begin the proof by showing completeness, and then finish by demonstrating soundness.
 
-To show completeness, we must show that any state in the set is represented by $s_s$.
+To show completeness, we must show that any state in the set is represented by $s_\sym$.
 The definition of representation requires the both the existence of a homomorphism, and proof that the homomorphism constraint is satisfiable.
-To show that a homomorphism exits, take any lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$.
-By Definition~\ref{representation}, we know $s_\ell = \lp \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.
-Take any state $s_\ell^\prime$ where $s_\ell \rightarrow_I^* s_\ell^\prime$, and state $s_s^\prime$ where $s_s \rightarrow_S^* s_s^\prime$.
-Note that  state $s_\ell^\prime$ has the form: $s_\ell^\prime = \lp \cfgnt{L}_{\ell^\prime}\ \cfgnt{R}_{\ell^\prime}\ \phi_{\ell^\prime}\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.Take any location, field pair $\lp l_\ell\  \cfgnt{f}\rp$ such that $\lp l_\ell\  \cfgnt{f}\rp \in \cfgnt{R}_{\ell}^\leftarrow$, and let $l_s = h(l_\ell)$.
-We may classify $l_\ell$ into one of three ways, based on the values of the $\cfgnt{R}$ function in each of the states $s_\ell$, $s_\ell^\prime$, $s_s$, and $s_s^\prime$, and we may define a function $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ based on that classification.
+To show that a homomorphism exits, take any GSE state $s_\gse$ such that $s_\gse \sqsubset s_\sym$.
+By Definition~\ref{representation}, we know $s_\gse = \lp \cfgnt{L}_\gse\ \cfgnt{R}_\gse\ \phi_\gse\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.
+Take any state $s_\gse^\prime$ where $s_\gse \rinit^* s_\gse^\prime$, and state $s_\sym^\prime$ where $s_\sym \rsum^* s_\sym^\prime$.
+Note that  state $s_\gse^\prime$ has the form: $s_\gse^\prime = \lp \cfgnt{L}_{\gse^\prime}\ \cfgnt{R}_{\gse^\prime}\ \phi_{\gse^\prime}\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.Take any location, field pair $\lp l_\gse\  \cfgnt{f}\rp$ such that $\lp l_\gse\  \cfgnt{f}\rp \in \cfgnt{R}_{\gse}^\leftarrow$, and let $l_\sym = h(l_\gse)$.
+We may classify $l_\gse$ into one of three ways, based on the values of the $\cfgnt{R}$ function in each of the states $s_\gse$, $s_\gse^\prime$, $s_\sym$, and $s_\sym^\prime$, and we may define a function $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ based on that classification.
 
-Class 1: $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f} ) = \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f} )$ and $\cfgnt{R}_{s} ( l_s,  \cfgnt{f} ) = \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$.
-Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{\ell}(\cfgnt{R}_{\ell} (\cfgnt{l}_\ell,f )) $.
+Class 1: $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f} ) = \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f} )$ and $\cfgnt{R}_{s} ( l_\sym,  \cfgnt{f} ) = \cfgnt{R}_{s^\prime} ( l_\sym,  \cfgnt{f})$.
+Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{\gse}(\cfgnt{R}_{\gse} (\cfgnt{l}_\gse,f )) $.
 In this case, let $h^\prime(l_\alpha) = h(l_\alpha)$.
-Since $s_\ell \rightharpoonup_h s_s$, we may surmise that:
-$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$$
+Since $s_\gse \rightharpoonup_h s_\sym$, we may surmise that:
+$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$$
 
-Class 2: $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f}) = \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_s,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$.
-Since $\cfgnt{R}_{s} ( l_s,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$, the Summarize rule must have altered this reference.
+Class 2: $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f}) = \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_\sym,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_\sym,  \cfgnt{f})$.
+Since $\cfgnt{R}_{s} ( l_\sym,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_\sym,  \cfgnt{f})$, the Summarize rule must have altered this reference.
 A reference created by the Summarize rule has a value set $\theta_{all}$ with four subsets: $\theta_{null}$, $\theta_{new}$, $\theta_{alias}$, and $\theta_{orig}$.
-Because $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f}) = \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f})$, we know that the location we want to map to lies in $\theta_{orig}$.
-Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{\ell}(\cfgnt{R}_{\ell} (\cfgnt{l}_\ell,f )) $, and let $l_{orig} = h(l_\alpha)$.
+Because $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f}) = \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$, we know that the location we want to map to lies in $\theta_{orig}$.
+Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{\gse}(\cfgnt{R}_{\gse} (\cfgnt{l}_\gse,f )) $, and let $l_{orig} = h(l_\alpha)$.
 In this case, we let $h^\prime(l_\alpha) = h(l_\alpha)$.
-Since $(\phi_a\ l_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f ))$.
+Since $(\phi_a\ l_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f ))$.
 Let $l_{orig} = h(l_\alpha)$.
-We can see that by the Summarize rule $ (\phi_b\ l_{orig})\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$, so therefore:
-$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$$
+We can see that by the Summarize rule $ (\phi_b\ l_{orig})\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$, so therefore:
+$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$$
 
-Class 3: $\cfgnt{R}_\ell ( l_\ell,  \cfgnt{f}) \neq \cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_s,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_s,  \cfgnt{f})$.
-In this case, there are two possibilities: either the new reference $\cfgnt{R}_{\ell^\prime} ( l_\ell,  \cfgnt{f})$ points to some location we've seen before $l_\alpha$, or it points to a previously unobserved location $l_\beta$.
+Class 3: $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f}) \neq \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_\sym,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_\sym,  \cfgnt{f})$.
+In this case, there are two possibilities: either the new reference $\cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$ points to some location we've seen before $l_\alpha$, or it points to a previously unobserved location $l_\beta$.
 By establishing which of these possibilities has happened, we can build $h^\prime$.
-To construct $h^\prime$, let $l_\alpha$ be any location such that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) $.
-If there exists $\phi_\alpha$ such that $\lp \phi_\alpha\ l_\alpha \rp \in \cfgnt{L}_{\ell}^\rightarrow $, let $h^\prime(l_\alpha) = h(l_\alpha)$.
-Otherwise, let $l_\beta$ be the location such that $(\phi_b\ \cfgnt{l}_\beta) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f )) $ and $(\phi_b\ \cfgnt{l}_\beta) \notin \cfgnt{L}_{s}(\cfgnt{R}_{s} (\cfgnt{l}_s,f )) $.
+To construct $h^\prime$, let $l_\alpha$ be any location such that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f )) $.
+If there exists $\phi_\alpha$ such that $\lp \phi_\alpha\ l_\alpha \rp \in \cfgnt{L}_{\gse}^\rightarrow $, let $h^\prime(l_\alpha) = h(l_\alpha)$.
+Otherwise, let $l_\beta$ be the location such that $(\phi_b\ \cfgnt{l}_\beta) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f )) $ and $(\phi_b\ \cfgnt{l}_\beta) \notin \cfgnt{L}_{s}(\cfgnt{R}_{s} (\cfgnt{l}_\sym,f )) $.
 Now, let $h^\prime(l_\alpha) = l_\beta$.
 Observe that either way,
-$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\ell,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_s,f ))$$
+$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$$
 
-Furthemore, since $l_\alpha$ and $l_\beta$ are new locations with uninitialized fields, we know that for any field $f^\prime$, $\{(\phi_p\ \bot)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\alpha,f^\prime ))$ and $ \{(\phi_p\ \bot)\} = \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\beta,f^\prime ))$ therefore, we know that:
-$$(\phi_p\ \cfgnt{l}_x) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_\alpha,f^\prime )) \Rightarrow (\phi_q\ h^\prime (\cfgnt{l}_x))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} ( h^\prime(\cfgnt{l}_\alpha),f ))$$
+Furthemore, since $l_\alpha$ and $l_\beta$ are new locations with uninitialized fields, we know that for any field $f^\prime$, $\{(\phi_p\ \bot)\} = \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\alpha,f^\prime ))$ and $ \{(\phi_p\ \bot)\} = \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\beta,f^\prime ))$ therefore, we know that:
+$$(\phi_p\ \cfgnt{l}_x) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\alpha,f^\prime )) \Rightarrow (\phi_q\ h^\prime (\cfgnt{l}_x))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} ( h^\prime(\cfgnt{l}_\alpha),f ))$$
 
-We have now shown that there exists a mapping $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ for all $\cfgnt{l}_{\ell^\prime} \in \cfgnt{L}_{\ell^\prime}^\rightarrow$ such that:
-$$ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime} (\cfgnt{l}_{\ell^\prime},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_{\ell^\prime},f )) $$
-By Definition~\ref{def:homomorphism} we know that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$.
+We have now shown that there exists a mapping $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ for all $\cfgnt{l}_{\gse^\prime} \in \cfgnt{L}_{\gse^\prime}^\rightarrow$ such that:
+$$ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_{\gse^\prime},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_{\gse^\prime},f )) $$
+By Definition~\ref{def:homomorphism} we know that $s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime$.
 
-It remains to show that $\mathbb{S}( \phi_s^\prime \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h} s_s^\prime) )$.
-For locations in Class 1, no new conjuncts are added to $\mathbb{HC}(s_\ell^\prime \rightharpoonup_{h} s_s^\prime)$, and therefore the satisfiability cannot be changed.
+It remains to show that $\mathbb{S}( \phi_\sym^\prime \wedge \mathbb{HC}(s_\gse^\prime \rightharpoonup_{h} s_\sym^\prime) )$.
+For locations in Class 1, no new conjuncts are added to $\mathbb{HC}(s_\gse^\prime \rightharpoonup_{h} s_\sym^\prime)$, and therefore the satisfiability cannot be changed.
 For locations in Class 2 or Class 3, the new constraints take either the form $\phi_x \wedge \phi_{orig}$, or $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$.
@@
 
-Since the heap constraint is satisfiable, we know that $s_\ell^\prime \sqsubset s_s^\prime $.
-We have therefore shown that for some summary state $s_s$ and an arbitrary lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$ :
+Since the heap constraint is satisfiable, we know that $s_\gse^\prime \sqsubset s_\sym^\prime $.
+We have therefore shown that for some symbolic state $s_\sym$ and an arbitrary GSE state $s_\gse$ such that $s_\gse \sqsubset s_\sym$ :
 \begin{equation} 
-(s_\ell \rightarrow_I^* s_\ell^\prime \wedge s_s \rightarrow_S^* s_s^\prime) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime 
+(s_\gse \rinit^* s_\gse^\prime \wedge s_\sym \rsum^* s_\sym^\prime) \Rightarrow s_\gse^\prime \sqsubset s_\sym^\prime 
 \end{equation}
@@
 %
-%We now show that the following four cases for $s_\ell^*$ are represented in $s_s^*$.
-For the following cases, let $\rightharpoonup_{h}$ be the homomorphism such that $s_\ell \rightharpoonup_{h} s_s$, let $\cfgnt{l}_\ell = \cfgnt{L}_\ell(\cfgnt{r})$, and let $\cfgnt{l}_s = h(\cfgnt{l}_\ell) $
+%We now show that the following four cases for $s_\gse^*$ are represented in $s_\sym^*$.
+For the following cases, let $\rightharpoonup_{h}$ be the homomorphism such that $s_\gse \rightharpoonup_{h} s_\sym$, let $\cfgnt{l}_\gse = \cfgnt{L}_\gse(\cfgnt{r})$, and let $\cfgnt{l}_\sym = h(\cfgnt{l}_\gse) $
 %
-%Case 1: Suppose $\cfgnt{R}_\ell(\cfgnt{l}_\ell) \neq \bot$.
-In this case, because $s_\ell \rightharpoonup_{h} s_s$, we know that $\cfgnt{R}_s(\cfgnt{l}_s) \neq \bot$.
-This means that in the Summarize rule, $\cfgnt{l}_s \notin \Lambda$, and therefore, $\cfgnt{R}_s(\cfgnt{l}_s) = \cfgnt{R}_{s^*}(\cfgnt{l}_s) $.
+%Case 1: Suppose $\cfgnt{R}_\gse(\cfgnt{l}_\gse) \neq \bot$.
+In this case, because $s_\gse \rightharpoonup_{h} s_\sym$, we know that $\cfgnt{R}_\sym(\cfgnt{l}_\sym) \neq \bot$.
+This means that in the Summarize rule, $\cfgnt{l}_\sym \notin \Lambda$, and therefore, $\cfgnt{R}_\sym(\cfgnt{l}_\sym) = \cfgnt{R}_{s^*}(\cfgnt{l}_\sym) $.
 By extension,
@@
 The key to this will be in showing that the constraints are mutually exclusive and collectively exhaustive.
-Mutually exclusive constraints are required because lazy heaps only point to one place at at time.
+Mutually exclusive constraints are required because GSE heaps only point to one place at at time.
 Collectively exhaustive constraints are required to eliminate any other possible heaps.
 We could start by explicitly enumerating the members of the product feasible set, and working from there to show that the symbolic heap is equivalent to that set.
-Or, we might do this on a case-by-case basis to show that for an arbitrary lazy state, any of it's three possible target states is in the feasible set.
+Or, we might do this on a case-by-case basis to show that for an arbitrary GSE state, any of it's three possible target states is in the feasible set.
 %
 %Having demonstrated each of these four cases, we now know that 
-%$$s_\ell^* \in \{\forall s_\ell^\prime | \exists s_\ell \sqsubset s_s (s_\ell \rightarrow_I^* s_\ell^\prime)  \} \Rightarrow  s_\ell^* \sqsubset s_s^*$$
+%$$s_\gse^* \in \{\forall s_\gse^\prime | \exists s_\gse \sqsubset s_\sym (s_\gse \rightarrow_I^* s_\gse^\prime)  \} \Rightarrow  s_\gse^* \sqsubset s_\sym^*$$
 
@@
 %Flawed argument:
-%We now prove the reverse case, that $s_s^*$ represents no infeasible states.
+%We now prove the reverse case, that $s_\sym^*$ represents no infeasible states.
 We modified no references from the previous heap, and did not alter the global invariant.
@@
 %okay, here is another crack at proving soundness
-We now prove the reverse case, that $s_s^*$ represents no infeasible states.
-Suppose that $s_s^\prime$ represents some infeasible state.
-This means that we represent some lazy state that has some reference r which points somewhere that no place in the feasible set points to.
+We now prove the reverse case, that $s_\sym^*$ represents no infeasible states.
+Suppose that $s_\sym^\prime$ represents some infeasible state.
+This means that we represent some GSE state that has some reference r which points somewhere that no place in the feasible set points to.
 Since we don't change the path condition, all the old references still point exactly to the same places they used to.
@@
 In the Summarize rule, the values and constraints for the new, null, uninitialized, and alias locations are contained in the sets $\theta_{new}$, $\theta_{null}$, $\theta{orig}$, and $\theta_{alias}$.
-Since the null, and uninitialized locations are already accounted for by the homomorphism $s_\ell \rightharpoonup_h s_s$, and since a new location was created symmetrically for both $s_\ell^\prime$ and $s_s^\prime$, the problem must be with some alias location that is part of $s_s$ but not $s_\ell$.
-This means that there must be a feasible path to a target location that does not exist for any lazy heap.
-So, pick an arbitrary lazy heap containing the location and field in question.
-If said target location does not exist, then there is no reference in the lazy heap pointing to that location.
-In the summary heap, the path constraint on the path leading to the undesired target contains an aliasing condition that states that the source reference only points to this target location on condition that the parent reference points there.
-However, since we already know that no other reference in the lazy heap points there, this condition must be infeasible.
+Since the null, and uninitialized locations are already accounted for by the homomorphism $s_\gse \rightharpoonup_h s_\sym$, and since a new location was created symmetrically for both $s_\gse^\prime$ and $s_\sym^\prime$, the problem must be with some alias location that is part of $s_\sym$ but not $s_\gse$.
+This means that there must be a feasible path to a target location that does not exist for any GSE heap.
+So, pick an arbitrary GSE heap containing the location and field in question.
+If said target location does not exist, then there is no reference in the GSE heap pointing to that location.
+In the symbolic heap, the path constraint on the path leading to the undesired target contains an aliasing condition that states that the source reference only points to this target location on condition that the parent reference points there.
+However, since we already know that no other reference in the GSE heap points there, this condition must be infeasible.
 Therefore, it is not part of the represented state.
@@
 We have now proven that 
-$$ s_\ell^* \sqsubset s_s^*  \Rightarrow  s_\ell^* \in \{\forall s_\ell^\prime | \exists s_\ell (s_\ell \sqsubset s_s \wedge (s_\ell \rightarrow_I^* s_\ell^\prime) ) \}$$
+$$ s_\gse^* \sqsubset s_\sym^*  \Rightarrow  s_\gse^* \in \{\forall s_\gse^\prime | \exists s_\gse (s_\gse \sqsubset s_\sym \wedge (s_\gse \rinit^* s_\gse^\prime) ) \}$$
 This fact, combined with our previous result, proves that
-$$s_s^*  \cong \{\forall s_\ell^\prime | \exists s_\ell (s_\ell \sqsubset s_s \wedge (s_\ell \rightarrow_I^* s_\ell^\prime) ) \}$$
+$$s_\sym^*  \cong \{\forall s_\gse^\prime | \exists s_\gse (s_\gse \sqsubset s_\sym \wedge (s_\gse \rinit^* s_\gse^\prime) ) \}$$
 
@@
 %we need to define how r' is arrived at for this one to work...
-\begin{lemma}[Bisumlation for $\rightarrow_{\varsigma|\mathit{FA}}$]
+\begin{lemma}[Bisumlation for $\rightarrow_{\sym|\mathit{FA}}$]
 \label{lem:access}
-%If there are symbolic states $s_s$ and $s_s^\prime$, control sequences $\pi_n$ and $\pi_{n+1}$, initial state $s_0$, and reference $\cfgnt{r}^\prime$ such that the following conditions hold:
+%If there are symbolic states $s_\sym$ and $s_\sym^\prime$, control sequences $\pi_n$ and $\pi_{n+1}$, initial state $s_0$, and reference $\cfgnt{r}^\prime$ such that the following conditions hold:
 %\begin{align}
-%s_s &= \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp \\
-%s_s &\cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp \\
+%s_\sym &= \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp \\
+%s_\sym &\cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp \\
 %\cfgnt{r}^\prime &= \mathrm{fresh}_r\lp \rp \\
 %\pi_{n+1} &=\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp \\
-%s_s &\rightarrow_s s_s^\prime
+%s_\sym &\rsym s_\sym^\prime
 %\end{align}
-%%$$s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$$ 
-%%$$s_s \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp$$ 
+%%$$s_\sym = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$$ 
+%%$$s_\sym \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp$$ 
 %%$$\pi_{n+1} =\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp$$ 
@@
 %then 
-%$$s_s^\prime \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_{n+1} \rp$$
-If there exists states $s_\ell$ and $s_s$ such that $s_s \in \mathcal{FA}$ and $s_\ell \sqsubset s_s$, then:
+%$$s_\sym^\prime \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_{n+1} \rp$$
+If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{FA}$ and $s_\gse \sqsubset s_\sym$, then:
 \begin{equation}
-\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
 \end{equation}
@@
 \begin{equation}
-\forall s_s^\prime ( s_s \rightarrow_s s_s^\prime\Rightarrow \exists s_\ell^\prime( (s_\ell \rightarrow_\ell s_\ell^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
 \end{equation}
@@
 Begin by assuming the conditions stated in Lemma~\ref{lem:access}.
-By Lemma~\ref{lem:init}, the summary intermediate state is equivalent to the set of lazy intermediate states, so we may assume without loss of generality that all of the pertinent fields in $s_s$ are initialized.
-Take an arbitrary lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$.
-Since $s_s$ is exact,  $s_\ell = \lp \cfgnt{L}_{\ell}\ \cfgnt{R}_{\ell}\ \phi_\ell\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k} \rp \rp$, and $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$.
-If we apply the state transition functions to achieve states $s_\ell^\prime$ and $s_s^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$ and  $s_s \rightarrow_s s_s^\prime$, we find that according to the Field Access rule:
-$$s_\ell^\prime = \lp \cfgnt{L}_{\ell} [\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}_{\ell}\ \phi_L\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
+By Lemma~\ref{lem:init}, the symbolic intermediate state is equivalent to the set of GSE intermediate states, so we may assume without loss of generality that all of the pertinent fields in $s_\sym$ are initialized.
+Take an arbitrary GSE state $s_\gse$ such that $s_\gse \sqsubset s_\sym$.
+Since $s_\sym$ is exact,  $s_\gse = \lp \cfgnt{L}_{\gse}\ \cfgnt{R}_{\gse}\ \phi_\gse\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k} \rp \rp$, and $s_\gse \in \mathbb{FS}(\rgse,s_0,\pi_n)$.
+If we apply the state transition functions to achieve states $s_\gse^\prime$ and $s_\sym^\prime$ such that $s_\gse \rgse s_\gse^\prime$ and  $s_\sym \rsym s_\sym^\prime$, we find that according to the Field Access rule:
+$$s_\gse^\prime = \lp \cfgnt{L}_{\gse} [\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}_{\gse}\ \phi_L\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
  and 
- $$ s_s^\prime = \lp \cfgnt{L}_{s}[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}_{s},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}_{s}\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
+ $$ s_\sym^\prime = \lp \cfgnt{L}_{s}[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}_{s},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}_{s}\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
 
-We now show that $s_\ell^\prime \sqsubset s_s^\prime$.
-Since $\eta$, $e$, and $k$ are identical between $s_s^\prime$ and $s_\ell^\prime $, the first condition is met by default.
+We now show that $s_\gse^\prime \sqsubset s_\sym^\prime$.
+Since $\eta$, $e$, and $k$ are identical between $s_\sym^\prime$ and $s_\gse^\prime $, the first condition is met by default.
 Now we construct the function $h^\prime$ such that $h^\prime = h$.
-Observe that since $s_\ell \rightharpoonup_{h} s_s$, and since $\cfgnt{R}_\ell$ and $\cfgnt{R}_s$ are unchanged from states $s_\ell$ to $s_\ell^\prime$ and $s_s$ to $s_s^\prime$ respectively, we are guaranteed that $ \cfgnt{r} = \cfgnt{R}_\ell(l,f) \Rightarrow \cfgnt{r} = \cfgnt{R}_s(h^\prime(l),f)$.
-Let $\{(\phi_\ell^\prime\ l^\prime)\} =  \cfgnt{L}_\ell(\cfgnt{R}_\ell(l,f))$.
-Since $\mathbb{S}(\phi_g \wedge \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s))$ is valid, we know that:
- $$(\phi_s \wedge \phi_s^\prime\ h(l^\prime)) \in \mathbb{VS}\lp \cfgnt{L}_{s},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp$$ 
+Observe that since $s_\gse \rightharpoonup_{h} s_\sym$, and since $\cfgnt{R}_\gse$ and $\cfgnt{R}_\sym$ are unchanged from states $s_\gse$ to $s_\gse^\prime$ and $s_\sym$ to $s_\sym^\prime$ respectively, we are guaranteed that $ \cfgnt{r} = \cfgnt{R}_\gse(l,f) \Rightarrow \cfgnt{r} = \cfgnt{R}_\sym(h^\prime(l),f)$.
+Let $\{(\phi_\gse^\prime\ l^\prime)\} =  \cfgnt{L}_\gse(\cfgnt{R}_\gse(l,f))$.
+Since $\mathbb{S}(\phi_g \wedge \mathbb{HC}(s_\gse \rightharpoonup_{h} s_\sym))$ is valid, we know that:
+ $$(\phi_\sym \wedge \phi_\sym^\prime\ h(l^\prime)) \in \mathbb{VS}\lp \cfgnt{L}_{s},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp$$ 
 From this, we may deduce that:
-$$ (\phi_\ell\ l) \in \cfgnt{L}_\ell^\prime(\cfgnt{r}^\prime) \Rightarrow (\phi_s \wedge \phi_s^\prime\ h^\prime(l))\in \cfgnt{L}_s^\prime(\cfgnt{r}^\prime)$$
-Since $\cfgnt{r}^\prime$ is the only new addition to $L_\ell^\prime$ and $L_s^\prime$, we now know that the assertion above holds for all $l \in \mathcal{L}$.
-Thus, we have shown that $s_\ell^\prime \rightharpoonup_{h} s_s^\prime$.
-Furthermore, since the constraints in $\mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime)$ are constructed using conjuncts already present in $ \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s)$, we are guaranteed that $\mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) \Leftrightarrow \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s)$, and therefore $\mathbb{S}(\phi_g \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime))$.
-This fact, and the fact that $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, means that by Definition~\ref{representation} we know $s_\ell^\prime \sqsubset s_s^\prime$.
+$$ (\phi_\gse\ l) \in \cfgnt{L}_\gse^\prime(\cfgnt{r}^\prime) \Rightarrow (\phi_\sym \wedge \phi_\sym^\prime\ h^\prime(l))\in \cfgnt{L}_\sym^\prime(\cfgnt{r}^\prime)$$
+Since $\cfgnt{r}^\prime$ is the only new addition to $L_\gse^\prime$ and $L_\sym^\prime$, we now know that the assertion above holds for all $l \in \mathcal{L}$.
+Thus, we have shown that $s_\gse^\prime \rightharpoonup_{h} s_\sym^\prime$.
+Furthermore, since the constraints in $\mathbb{HC}(s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime)$ are constructed using conjuncts already present in $ \mathbb{HC}(s_\gse \rightharpoonup_{h} s_\sym)$, we are guaranteed that $\mathbb{HC}(s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime) \Leftrightarrow \mathbb{HC}(s_\gse \rightharpoonup_{h} s_\sym)$, and therefore $\mathbb{S}(\phi_g \wedge \mathbb{HC}(s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime))$.
+This fact, and the fact that $\eta_{\gse} = \eta_{s} ,\ \cfgnt{e}_{\gse} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\gse} = \cfgnt{k}_{s}$, means that by Definition~\ref{representation} we know $s_\gse^\prime \sqsubset s_\sym^\prime$.
 We have now shown that:
 \begin{equation}
-\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
 \end{equation}
 
-%for any lazy state $s_\ell$: 
+%for any GSE state $s_\gse$: 
 %\begin{equation}
 %\label{eqn:slimpliesslprime}
-%s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime
+%s_\gse \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_n) \Rightarrow s_\gse^\prime \sqsubset s_\sym^\prime
 %\end{equation}
 
-%Since there is only one possible control flow sequence $\pi_{n+1}$, this means that if $s_\ell \rightarrow_\ell s_\ell^\prime$, then 
+%Since there is only one possible control flow sequence $\pi_{n+1}$, this means that if $s_\gse \rgse s_\gse^\prime$, then 
 %\begin{equation}
 %\label{eqn:slimpliesslprime2}
-%s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime\ \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})
+%s_\gse \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_n) \Leftrightarrow s_\gse^\prime\ \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1})
 %\end{equation}
 %
-%Combining Equations \ref{eqn:slimpliesslprime} and \ref{eqn:slimpliesslprime2}, we may finally conclude that $s_s^\prime$ is complete with respect to $\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$
+%Combining Equations \ref{eqn:slimpliesslprime} and \ref{eqn:slimpliesslprime2}, we may finally conclude that $s_\sym^\prime$ is complete with respect to $\mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1})$
 %\begin{equation}
 %\label{eqn:readforwards}
-%s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1}) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime
+%s_\gse^\prime \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1}) \Rightarrow s_\gse^\prime \sqsubset s_\sym^\prime
 %\end{equation}
 
-%Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$, but $s_i^\prime \notin \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
-Since $s_i^\prime \sqsubset s_s^\prime$, then by Lemma~\ref{lem:ref}, $\cfgnt{r}^\prime$ represents a valid path $\Gamma_{n+1}^{s\prime}$, in states $s_i^\prime$ and $s_s^\prime$.
-Furthermore, by Lemma~\ref{lem:path} we can surmise that $\mathbb{S}(\phi_s^\prime \wedge \mathbb{PC}(\Gamma_{n+1}^{s\prime}))$.
-By construction, $\Gamma_{n+1}^{s\prime}$ is an extension of the valid access path $\Gamma_{n}^{s}$ represented by reference $\cfgnt{r}$ in state $s_s$.
-Since $s_s$ is exact, there exists state $s_i$ such that $s_i \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n})$.
-and by our previous result, $s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
+%Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_\sym^\prime$, but $s_i^\prime \notin \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1})$.
+Since $s_i^\prime \sqsubset s_\sym^\prime$, then by Lemma~\ref{lem:ref}, $\cfgnt{r}^\prime$ represents a valid path $\Gamma_{n+1}^{s\prime}$, in states $s_i^\prime$ and $s_\sym^\prime$.
+Furthermore, by Lemma~\ref{lem:path} we can surmise that $\mathbb{S}(\phi_\sym^\prime \wedge \mathbb{PC}(\Gamma_{n+1}^{s\prime}))$.
+By construction, $\Gamma_{n+1}^{s\prime}$ is an extension of the valid access path $\Gamma_{n}^{s}$ represented by reference $\cfgnt{r}$ in state $s_\sym$.
+Since $s_\sym$ is exact, there exists state $s_i$ such that $s_i \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n})$.
+and by our previous result, $s_i^\prime \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1})$.
 We have a contradiction.
 
-Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$.
-Since $s_i^\prime \sqsubset s_s^\prime$, then by Definition~\ref{representation}, we know there exists a homomorphism $s_i^\prime \rightharpoonup_{h^\prime} s_s^\prime$, and that $\mathbb{S}( \phi_i^\prime \wedge \mathbb{HC}(s_i^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$.
+Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_\sym^\prime$.
+Since $s_i^\prime \sqsubset s_\sym^\prime$, then by Definition~\ref{representation}, we know there exists a homomorphism $s_i^\prime \rightharpoonup_{h^\prime} s_\sym^\prime$, and that $\mathbb{S}( \phi_i^\prime \wedge \mathbb{HC}(s_i^\prime \rightharpoonup_{h^\prime} s_\sym^\prime) )$.
 From state $s_i^\prime$, construct state $s_i$ such that
@@
 \end{align*}
-Observe that by virtue of the lazy Field Access rule, $s_i \rightarrow_\ell s_i^\prime$.
+Observe that by virtue of the GSE Field Access rule, $s_i \rgse s_i^\prime$.
 Now, construct function $h_i$ so that $h_i = h^\prime$.
-Observe that by Definition~\ref{def:homomorphism} $s_i \rightharpoonup_{h_i} s_s$,  and that $\mathbb{S}( \phi_i \wedge \mathbb{HC}(s_i \rightharpoonup_{h_i} s_s) )$, so $s_i \sqsubset s_s$.
+Observe that by Definition~\ref{def:homomorphism} $s_i \rightharpoonup_{h_i} s_\sym$,  and that $\mathbb{S}( \phi_i \wedge \mathbb{HC}(s_i \rightharpoonup_{h_i} s_\sym) )$, so $s_i \sqsubset s_\sym$.
 Therefore:
 \begin{equation}
-\forall s_s^\prime ( s_s \rightarrow_s s_s^\prime\Rightarrow \exists s_\ell^\prime( (s_\ell \rightarrow_\ell s_\ell^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
 \end{equation}
@@
 
-%Since $s_s$ is exact, $s_i \in\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$.
-Combining this with the fact that $s_i \rightarrow_\ell s_i^\prime$, we conclude that $s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$.
+%Since $s_\sym$ is exact, $s_i \in\mathbb{FS}(\rightarrow_{\gse},s_0,\pi_n)$.
+Combining this with the fact that $s_i \rgse s_i^\prime$, we conclude that $s_i^\prime \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1})$.
 We have a contradiction.
 %
-% Therefore, $s_s^\prime$ is sound with respect to $\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$:
+% Therefore, $s_\sym^\prime$ is sound with respect to $\mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1})$:
 % \begin{equation}
 % \label{eqn:readbackwards}
-% s_i^\prime \sqsubset s_s^\prime \Rightarrow s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})
+% s_i^\prime \sqsubset s_\sym^\prime \Rightarrow s_i^\prime \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1})
 % \end{equation}
-%Since $s_s$ is both sound and complete, we may combine Equations \ref{eqn:readforwards} and \ref{eqn:readbackwards} to find that 
-%$$s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1}) \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$
-%By Definition~\ref{equivalent}, $s_s^\prime \cong \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, and so by Definition~\ref{exact}, $s_s^\prime$ is exact.
+%Since $s_\sym$ is both sound and complete, we may combine Equations \ref{eqn:readforwards} and \ref{eqn:readbackwards} to find that 
+%$$s_\gse^\prime \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1}) \Leftrightarrow s_\gse^\prime \sqsubset s_\sym^\prime$$
+%By Definition~\ref{equivalent}, $s_\sym^\prime \cong \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_n)$, and so by Definition~\ref{exact}, $s_\sym^\prime$ is exact.
 
-%Case 2: If there are uninitialized fields, then the lazy initialization machine will make an intermediate state $s_t$.
-By Lemma~\ref{lem:init}, the summary intermediate state is equivalent to the set of lazy intermediate states.
-Since the summary intermediate state From the intermediate state, the proof is the same as for case 1.
+%Case 2: If there are uninitialized fields, then the GSE initialization machine will make an intermediate state $s_t$.
+By Lemma~\ref{lem:init}, the symbolic intermediate state is equivalent to the set of GSE intermediate states.
+Since the symbolic intermediate state From the intermediate state, the proof is the same as for case 1.
 \end{proof}
@@
 \label{lem:write}
-%If $s_s \cong \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n )$ for some symbolic state $s_s$, initial state $s_0$, and control flow path $\pi_n$, and if $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then:
-%$$s_\ell^\prime \sqsubset s_s^\prime \Leftrightarrow s_\ell^\prime \in \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) ) $$
-If there exists states $s_\ell$ and $s_s$ such that $s_s \in \mathcal{FW}$ and $s_\ell \sqsubset s_s$, then:
+%If $s_\sym \cong \mathbb{FS}(\rgse, s_0, \pi_n )$ for some symbolic state $s_\sym$, initial state $s_0$, and control flow path $\pi_n$, and if $s_\sym =  \lp \cfgnt{L}_\sym\ \cfgnt{R}_\sym\ \phi_\sym\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$, and if $s_\sym \rsym s_\sym^\prime$ for some state $s_\sym^\prime$, then:
+%$$s_\gse^\prime \sqsubset s_\sym^\prime \Leftrightarrow s_\gse^\prime \in \mathbb{FS}(\rgse, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) ) $$
+If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{FW}$ and $s_\gse \sqsubset s_\sym$, then:
 \begin{equation}
-\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
 \end{equation}
@@
 
-The first step is to show that there exists a state $s_s^\prime$ that is complete with respect to the feasible set.
-Take state $s_s$ and compute state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$.
-Take any lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$, and find state $s_\ell^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$.
-Let $l_\ell$ be the location such that $\{(\phi_a\ l_\ell )\} = \cfgnt{L}_\ell(\cfgnt{r}_x) $ for some $\phi_a$.
-To show that $s_\ell^\prime \sqsubset s_s^\prime$, we need to demonstrate that there exists a function $h^\prime$ such that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$, and that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$.
-Since $s_h \sqsubset s_s$, we know that there exists a function $h$ such that $s_\ell \rightharpoonup_{h} s_s$.
+The first step is to show that there exists a state $s_\sym^\prime$ that is complete with respect to the feasible set.
+Take state $s_\sym$ and compute state $s_\sym^\prime$ such that $s_\sym \rsym s_\sym^\prime$.
+Take any GSE state $s_\gse$ such that $s_\gse \sqsubset s_\sym$, and find state $s_\gse^\prime$ such that $s_\gse \rgse s_\gse^\prime$.
+Let $l_\gse$ be the location such that $\{(\phi_a\ l_\gse )\} = \cfgnt{L}_\gse(\cfgnt{r}_x) $ for some $\phi_a$.
+To show that $s_\gse^\prime \sqsubset s_\sym^\prime$, we need to demonstrate that there exists a function $h^\prime$ such that $s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime$, and that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime) )$.
+Since $s_h \sqsubset s_\sym$, we know that there exists a function $h$ such that $s_\gse \rightharpoonup_{h} s_\sym$.
 Let $h^\prime = h$.
 
-First, we consider how $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$.
-Let $l_\alpha$ and $l_\beta$ be arbitrary locations in $\cfgnt{L}_{\ell^\prime}^\rightarrow$ such that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\beta,f ))$, let $\theta = \cfgnt{L}_s(\cfgnt{R}_s(h(l_\ell),f))$, and let $\theta^\prime =   \cfgnt{L}_s^\prime(\cfgnt{R}_s^\prime(h(l_\ell),f))$.
+First, we consider how $s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime$.
+Let $l_\alpha$ and $l_\beta$ be arbitrary locations in $\cfgnt{L}_{\gse^\prime}^\rightarrow$ such that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime}(\cfgnt{l}_\beta,f ))$, let $\theta = \cfgnt{L}_\sym(\cfgnt{R}_\sym(h(l_\gse),f))$, and let $\theta^\prime =   \cfgnt{L}_\sym^\prime(\cfgnt{R}_\sym^\prime(h(l_\gse),f))$.
 
-Suppose $l_\beta \neq l_\ell$.
+Suppose $l_\beta \neq l_\gse$.
 In this case either $\theta = \theta^\prime$ or $\theta \neq \theta^\prime$ .
@@
 Otherwise, if $\theta \neq \theta^\prime$.
-We can see from the construction of the set $X$ in the summary Field Write rule that any feasible location in the set $\theta$ must also be in the set $\theta^\prime$.
-Since $s_\ell \sqsubset s_s$, we know that $h(l_\alpha)$ is in $\theta$, and is likewise in $\theta^\prime$.
-We have now established that in either case where $l_\beta \neq l_\ell$, $(\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (h(\cfgnt{l}_\beta),f ))$.
+We can see from the construction of the set $X$ in the symbolic Field Write rule that any feasible location in the set $\theta$ must also be in the set $\theta^\prime$.
+Since $s_\gse \sqsubset s_\sym$, we know that $h(l_\alpha)$ is in $\theta$, and is likewise in $\theta^\prime$.
+We have now established that in either case where $l_\beta \neq l_\gse$, $(\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (h(\cfgnt{l}_\beta),f ))$.
 
-On the other hand, suppose $l_\beta = l_\ell$.
-In this case we know that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\ell,f ))$.
-From the lazy field rule, we can surmise that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell}(\cfgnt{r} )$, and since $s_\ell \sqsubset s_s$, we know that $(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s}(\cfgnt{r})$ for some constraint $\phi_b$.
-Using this fact, we can apply the summary Field Write rule to infer that $l_\alpha$ must be one of the locations in $\theta^\prime$, and therefore $(\phi_c\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}^\prime(l_\ell,f))$
+On the other hand, suppose $l_\beta = l_\gse$.
+In this case we know that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime}(\cfgnt{l}_\gse,f ))$.
+From the GSE field rule, we can surmise that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse}(\cfgnt{r} )$, and since $s_\gse \sqsubset s_\sym$, we know that $(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s}(\cfgnt{r})$ for some constraint $\phi_b$.
+Using this fact, we can apply the symbolic Field Write rule to infer that $l_\alpha$ must be one of the locations in $\theta^\prime$, and therefore $(\phi_c\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}^\prime(l_\gse,f))$
 
 Thus, for arbitrary $l_\alpha$ and $l_\beta$:
-$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\beta,f )) \Rightarrow (\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (h(\cfgnt{l}_\beta),f ))$$
-Therefore, we have shown that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$.
+$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime}(\cfgnt{l}_\beta,f )) \Rightarrow (\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (h(\cfgnt{l}_\beta),f ))$$
+Therefore, we have shown that $s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime$.
 
-Establishing the fact that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$ is left as an exercise to the reader (waving hands in the air).
+Establishing the fact that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime) )$ is left as an exercise to the reader (waving hands in the air).
 
-By proving the existence of a valid homomorphism, we have shown that for any state $s_\ell^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$, then the state $s_s^\prime$ such that $s_s \rightarrow_s s_\ell^\prime$ represents $s_\ell^\prime$.
-Therefore, $\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )$.
+By proving the existence of a valid homomorphism, we have shown that for any state $s_\gse^\prime$ such that $s_\gse \rgse s_\gse^\prime$, then the state $s_\sym^\prime$ such that $s_\sym \rsym s_\gse^\prime$ represents $s_\gse^\prime$.
+Therefore, $\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )$.
 This concludes the proof of completeness.
 
-To show that $s_s^\prime$ is sound with respect to the feasible set, we use the same argument as in the field read proof: that any state $s_\ell^\prime$ represented by $s_s^\prime$ must have a counterpart state $s_\ell$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$ and $s_\ell \sqsubset s_s$.
-Because $s_s$ is exact, $s_\ell^\prime$ must be a part of the feasible set.
-Therefore, $\forall s_s^\prime ( s_s \rightarrow_s s_s^\prime\Rightarrow \exists s_\ell^\prime( (s_\ell \rightarrow_\ell s_\ell^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )$.
+To show that $s_\sym^\prime$ is sound with respect to the feasible set, we use the same argument as in the field read proof: that any state $s_\gse^\prime$ represented by $s_\sym^\prime$ must have a counterpart state $s_\gse$ such that $s_\gse \rgse s_\gse^\prime$ and $s_\gse \sqsubset s_\sym$.
+Because $s_\sym$ is exact, $s_\gse^\prime$ must be a part of the feasible set.
+Therefore, $\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )$.
 
@@
 
-\begin{lemma}[$\rightarrow^*_S$ preserves heap determinism]
+\begin{lemma}[$\rsum^*$ preserves heap determinism]
 \label{lem:S-determ}
 Given a deterministic heap, $(\cfgnt{L}_0\ \cfgnt{R}_0)$, from a
-summary state with a reference $\cfgnt{r}$ and field $\cfgnt{f}$, the
-new heap, $(\cfgnt{L}^\prime\ \cfgnt{R}^\prime)$, from the summary
-initialization machine, $(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f})
-\rightarrow^*_S
-(\cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \cfgnt{r}\ \cfgnt{f})$, after any number of machine steps, is also deterministic.
+state with a reference $\cfgnt{r}$ and field $\cfgnt{f}$, the
+new heap, $(\cfgnt{L}^\prime\ \cfgnt{R}^\prime)$, from the 
+summary machine, $(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f})
+\rsum^*
+(\cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \cfgnt{r}\ \cfgnt{f})$, is also deterministic.
 \end{lemma}
 \begin{proof}
-Induction over the number of machine steps on the summary initialization machine in \figref{fig:symInit}.
+Induction over the number of machine steps on the symbolic initialization machine in \figref{fig:symInit}.
 
 \noindent\textbf{Base Case}. The machine takes one step: $(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f})
-\rightarrow_S
+\rsum
 (\cfgnt{L}_1\ \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f})$. Let $\Lambda = \mathbb{UN}(\cfgnt{L}_0, \cfgnt{R}_0, \cfgnt{r},
@@
 \[
-(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f}) \rightarrow_S (\cfgnt{L}_1\ \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f}) \rightarrow_S \ldots \rightarrow_S
+(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f}) \rsum (\cfgnt{L}_1\ \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f}) \rsum \ldots \rsum
 (\cfgnt{L}_n\ \cfgnt{R}_n\ \cfgnt{r}\ \cfgnt{f})
@@
 mutual exclusive. This matches the base case, in that the heap on the
-left side of $\rightarrow_S$ is location mutual exclusive, and by the
+left side of $\rsum$ is location mutual exclusive, and by the
 same argument as in the base case,
@@
 \label{lem:FA-determ}
-Given a state, $s_\varsigma$, with a deterministic heap,
-$(\cfgnt{L}_\varsigma\ \cfgnt{R}_\varsigma) =
-\mathrm{heap}(s_\varsigma)$, the new heap,
-$(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
-\mathrm{heap}(s_\varsigma^\prime)$, in any state related by the field
-access rule, $s_\varsigma \rightarrow_\mathit{FA} s_\varsigma^\prime$,
+Given a state, $s_\sym$, with a deterministic heap,
+$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
+\mathrm{heap}(s_\sym)$, the new heap,
+$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
+\mathrm{heap}(s_\sym^\prime)$, in any state related by the field
+access rule, $s_\sym \rightarrow_\mathit{FA} s_\sym^\prime$,
 is also deterministic.
@@
 determinism, the new heap with $r^\prime$ and the value set,
-$(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
-\mathrm{heap}(s_\varsigma^\prime)$, is also deterministic.
+$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
+\mathrm{heap}(s_\sym^\prime)$, is also deterministic.
 \end{proof}
@@
 \label{lem:FW-determ}
-Given a state, $s_\varsigma$, with a deterministic heap,
-$(\cfgnt{L}_\varsigma\ \cfgnt{R}_\varsigma) =
-\mathrm{heap}(s_\varsigma)$, the new heap,
-$(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
-\mathrm{heap}(s_\varsigma^\prime)$, in any state related by the field
-write rule, $s_\varsigma \rightarrow_\mathit{FW} s_\varsigma^\prime$,
+Given a state, $s_\sym$, with a deterministic heap,
+$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
+\mathrm{heap}(s_\sym)$, the new heap,
+$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
+\mathrm{heap}(s_\sym^\prime)$, in any state related by the field
+write rule, $s_\sym \rightarrow_\mathit{FW} s_\sym^\prime$,
 is also deterministic.
@@
 $(\phi^\prime\ \cfgnt{l}^\prime)$, comes from
-$\cfgnt{L}_\varsigma(\cfgnt{r})$ on the same reference in a
-deterministic heap $(\cfgnt{L}_\varsigma\ \cfgnt{R}_\varsigma)$; thus,
+$\cfgnt{L}_\sym(\cfgnt{r})$ on the same reference in a
+deterministic heap $(\cfgnt{L}_\sym\ \cfgnt{R}_\sym)$; thus,
 that set of meets the criteria for determinism by definition. So any
@@
 $\mathrm{fresh}_r()$. These are added to an already deterministic heap
-$(\cfgnt{L}_\varsigma\ \cfgnt{R}_\varsigma)$ and meet the criteria so
-that $(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime)$ is also
+$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym)$ and meet the criteria so
+that $(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime)$ is also
 deterministic.
@@
 
-\begin{lemma}[$\rightarrow_J$ preserves heap determinism]
+\begin{lemma}[$\rcom$ preserves heap determinism]
 \label{lem:J-determ}
-Given a state, $s_\varsigma$, with a deterministic heap,
-$(\cfgnt{L}_\varsigma\ \cfgnt{R}_\varsigma) =
-\mathrm{heap}(s_\varsigma)$, the new heap,
-$(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
-\mathrm{heap}(s_\varsigma^\prime)$, in any state related by the
-Javalite relation, $s_\varsigma \rightarrow_J s_\varsigma^\prime$, is
+Given a state, $s_\sym$, with a deterministic heap,
+$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
+\mathrm{heap}(s_\sym)$, the new heap,
+$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
+\mathrm{heap}(s_\sym^\prime)$, in any state related by the
+Javalite relation, $s_\sym \rcom s_\sym^\prime$, is
 also deterministic.
@@
 \begin{proof}
-Proof by definition of $\rightarrow_J$ in \figref{fig:javalite-common}.
+Proof by definition of $\rcom$ in \figref{fig:javalite-common}.
 
-Every rule in $\rightarrow_J$ except \texttt{New} leaves the heap
+Every rule in $\rcom$ except \texttt{New} leaves the heap
 unmodified. The rule for \texttt{New} adds a single new location
@@
 mutations alter the determinism of the heap, the new heap
-$(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime)$ is also
+$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime)$ is also
 deterministic.
@@
 
-\begin{theorem}[$\rightarrow_\varsigma$ preserves heap determinism]
+\begin{theorem}[$\rsym$ preserves heap determinism]
 \label{thm:determ}
-Given a state, $s_\varsigma$, with a deterministic heap,
-$(\cfgnt{L}_\varsigma\ \cfgnt{R}_\varsigma) =
-\mathrm{heap}(s_\varsigma)$, the new heap,
-$(\cfgnt{L}_\varsigma^\prime\ \cfgnt{R}_\varsigma^\prime) =
-\mathrm{heap}(s_\varsigma^\prime)$, in any state related by the
-symbolic relation, $s_\varsigma \rightarrow_\varsigma s_\varsigma^\prime$, is
+Given a state, $s_\sym$, with a deterministic heap,
+$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
+\mathrm{heap}(s_\sym)$, the new heap,
+$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
+\mathrm{heap}(s_\sym^\prime)$, in any state related by the
+symbolic relation, $s_\sym \rsym s_\sym^\prime$, is
 also deterministic.
@@
 which represent all the rules that relate states in
-$\rightarrow_\varsigma$.
+$\rsym$.
 \end{proof}
@@
 \label{lem:compare}
-%If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then $s_s^\prime$ is equal to $ \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_{s^\prime}\ \eta\ \cfgnt{v}_{s^\prime}\ \cfgnt{k}\rp$ and is exact with respect to $s_0$ and $\pi_n \ (\eta\ \cfgnt{v}_{s^\prime}\ \cfgnt{k})$.
-If there exists states $s_\ell$ and $s_s$ such that $s_s \in \mathcal{RC}$ and $s_\ell \sqsubset s_s$, then:
+%If symbolic state $s_\sym =  \lp \cfgnt{L}_\sym\ \cfgnt{R}_\sym\ \phi_\sym\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, and if $s_\sym \rsym s_\sym^\prime$ for some state $s_\sym^\prime$, then $s_\sym^\prime$ is equal to $ \lp \cfgnt{L}_\sym\ \cfgnt{R}_\sym\ \phi_{s^\prime}\ \eta\ \cfgnt{v}_{s^\prime}\ \cfgnt{k}\rp$ and is exact with respect to $s_0$ and $\pi_n \ (\eta\ \cfgnt{v}_{s^\prime}\ \cfgnt{k})$.
+If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{RC}$ and $s_\gse \sqsubset s_\sym$, then:
 \begin{equation}
-\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
 \end{equation}
@@
 \begin{equation}
-\forall s_s^\prime ( s_s \rightarrow_s s_s^\prime\Rightarrow \exists s_\ell^\prime( (s_\ell \rightarrow_\ell s_\ell^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
 \end{equation}
 \end{lemma}
-There are two rules that apply to state $s_s$, one for the $\cfgt{true}$ branch and one for the $\cfgt{false}$ branch.
+There are two rules that apply to state $s_\sym$, one for the $\cfgt{true}$ branch and one for the $\cfgt{false}$ branch.
 Since the proofs for both rules are nearly identical, for brevity we will only show the proofs for the case for the $\cfgt{true}$ branch.
 \begin{proof}
-Assume there exists states $s_\ell$ and $s_s$ such that $s_s \in \mathcal{RC}$ and $s_\ell \sqsubset s_s$.
-Let $s_s^\prime$ be any state such that $s_s \rightarrow_s s_s$ and let $\zeta_T = \forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime )$.
-Since $s_\ell \sqsubset s_s$, we know that $s_\ell \in \mathcal{RC}$, and that there exists a homomorphism $s_\ell \rightharpoonup_{h} s_s$ such that $\mathbb{S}( \phi_s \wedge \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s) ) $.
-We partition $\zeta_T$ based on the values of $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$ as follows: Let
-$$\zeta_t = \zeta_T \setminus \{ s_f | (s_f= \lp \cfgnt{L}_f\ \cfgnt{R}_f\ \phi_\ell\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp) \wedge (\cfgnt{L}_f \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_f \lp \cfgnt{r}_1 \rp ) \}$$
+Assume there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{RC}$ and $s_\gse \sqsubset s_\sym$.
+Let $s_\sym^\prime$ be any state such that $s_\sym \rsym s_\sym$ and let $\zeta_T = \forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime )$.
+Since $s_\gse \sqsubset s_\sym$, we know that $s_\gse \in \mathcal{RC}$, and that there exists a homomorphism $s_\gse \rightharpoonup_{h} s_\sym$ such that $\mathbb{S}( \phi_\sym \wedge \mathbb{HC}(s_\gse \rightharpoonup_{h} s_\sym) ) $.
+We partition $\zeta_T$ based on the values of $\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp$ as follows: Let
+$$\zeta_t = \zeta_T \setminus \{ s_f | (s_f= \lp \cfgnt{L}_f\ \cfgnt{R}_f\ \phi_\gse\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp) \wedge (\cfgnt{L}_f \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_f \lp \cfgnt{r}_1 \rp ) \}$$
 and let
@@
 
-Furthermore, there are two possible configurations for $s_s^\prime$: $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp $ and $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp $.
-We now consider the partitions of $\zeta_T$ and configurations of $s_s^\prime$ in separate cases.
+Furthermore, there are two possible configurations for $s_\sym^\prime$: $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp $ and $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp $.
+We now consider the partitions of $\zeta_T$ and configurations of $s_\sym^\prime$ in separate cases.
 
-Case 1: Assume that $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp = \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$. 
-Compute state $s_\ell^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$.
-In this case, the lazy ``equals - references true" rule applied, therefore $s_\ell^\prime$ is in $\zeta_t$.
-Observe that by applying Theorem~\ref{thm:mutex}, $\phi_s^\prime \wedge \phi_0 \wedge \phi_1$ reduces to $\phi_s$.
-Therefore, $\mathbb{S}( \phi_s^\prime \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h} s_s^\prime) ) $ is true, and by extension, $s_\ell^\prime \sqsubset s_s^\prime$.
-Since this relation holds for arbitrary $s_\ell^\prime \in \zeta_t$, we now know that
+Case 1: Assume that $\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp = \cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp$. 
+Compute state $s_\gse^\prime$ such that $s_\gse \rgse s_\gse^\prime$.
+In this case, the GSE ``equals - references true" rule applied, therefore $s_\gse^\prime$ is in $\zeta_t$.
+Observe that by applying Theorem~\ref{thm:mutex}, $\phi_\sym^\prime \wedge \phi_0 \wedge \phi_1$ reduces to $\phi_\sym$.
+Therefore, $\mathbb{S}( \phi_\sym^\prime \wedge \mathbb{HC}(s_\gse^\prime \rightharpoonup_{h} s_\sym^\prime) ) $ is true, and by extension, $s_\gse^\prime \sqsubset s_\sym^\prime$.
+Since this relation holds for arbitrary $s_\gse^\prime \in \zeta_t$, we now know that
 \begin{equation}
 \label{eqn:RCForwardsTrue}
-((\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp = \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp) \wedge (s_\ell^\prime \in \zeta_t)) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime
+((\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp = \cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp) \wedge (s_\gse^\prime \in \zeta_t)) \Rightarrow s_\gse^\prime \sqsubset s_\sym^\prime
 \end{equation}
 
-Case 2:  Assume that $s_s^\prime$ has the form $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp $, and define $\theta_\alpha$, $\theta_0$ and $\theta_1$ as in the ``equals (references-true) rule''.
-Since $\cfgnt{L}_s$ and $\cfgnt{R}_s$ are unchanged from $s_s$, and $\phi_s^\prime$ is only a strengthened version of $\phi_s$,  we know that
+Case 2:  Assume that $s_\sym^\prime$ has the form $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp $, and define $\theta_\alpha$, $\theta_0$ and $\theta_1$ as in the ``equals (references-true) rule''.
+Since $\cfgnt{L}_\sym$ and $\cfgnt{R}_\sym$ are unchanged from $s_\sym$, and $\phi_\sym^\prime$ is only a strengthened version of $\phi_\sym$,  we know that
 \begin{equation}
 \label{eqn:RCSubset}
-\{s_\ell^\prime | s_\ell^\prime \sqsubset s_s^\prime \} \subseteq \{s_\ell^\prime | \exists s_\ell \lp s_\ell \sqsubset s_s \rp \wedge s_\ell \rightarrow_s s_\ell^\prime\}
+\{s_\gse^\prime | s_\gse^\prime \sqsubset s_\sym^\prime \} \subseteq \{s_\gse^\prime | \exists s_\gse \lp s_\gse \sqsubset s_\sym \rp \wedge s_\gse \rsym s_\gse^\prime\}
 \end{equation}
-Suppose that there exists state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$ and $s_i^\prime \notin \zeta_t$. Because of Equation \ref{eqn:RCSubset}, we know that 
-$$s_i^\prime \in \{s_\ell^\prime | \exists s_\ell \lp s_\ell \sqsubset s_s\rp \wedge s_\ell \rightarrow_s s_\ell^\prime\}$$ 
-Combining this with the assumption that $s_i^\prime \notin \zeta_t$, we must conclude that $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp \neq  \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$.
+Suppose that there exists state $s_i^\prime$ such that $s_i^\prime \sqsubset s_\sym^\prime$ and $s_i^\prime \notin \zeta_t$. Because of Equation \ref{eqn:RCSubset}, we know that 
+$$s_i^\prime \in \{s_\gse^\prime | \exists s_\gse \lp s_\gse \sqsubset s_\sym\rp \wedge s_\gse \rsym s_\gse^\prime\}$$ 
+Combining this with the assumption that $s_i^\prime \notin \zeta_t$, we must conclude that $\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp \neq  \cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp$.
 Because of this, and because of Theorem~\ref{thm:mutex}, we know that either all constraints in the set
@@
 $$\{\phi_i \mid \exists \phi_\alpha (\phi_\alpha \in \lp \theta_0 \cup \theta_1 \rp)\wedge \lp \phi_i = \phi_\alpha \wedge \phi_0 \wedge \phi_1 \rp\}$$ 
-is valid. Either way, $\mathbb{S}\lp\phi_i^\prime \wedge\phi_0\wedge \phi_1\rp$ is false and $s_s^\prime$ does not represent $s_i^\prime$. We have a contradiction. Therefore: 
+is valid. Either way, $\mathbb{S}\lp\phi_i^\prime \wedge\phi_0\wedge \phi_1\rp$ is false and $s_\sym^\prime$ does not represent $s_i^\prime$. We have a contradiction. Therefore: 
 \begin{equation}
 \label{eqn:RCBackwardsTrue}
-((s_s^\prime=\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp) \wedge (s_\ell^\prime \sqsubset s_s^\prime)) \Rightarrow s_\ell^\prime \in \zeta_t
+((s_\sym^\prime=\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp) \wedge (s_\gse^\prime \sqsubset s_\sym^\prime)) \Rightarrow s_\gse^\prime \in \zeta_t
 \end{equation}
 
-Case 3: Assume that $\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp$.
-This means that the lazy ``equals - references false" rule applies.
+Case 3: Assume that $\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp$.
+This means that the GSE ``equals - references false" rule applies.
 The proof for the ``equals - references false" rule is highly similar to the proof for Case 1, so we omit it for the sake of brevity.
@@
 \label{eqn:RCForwardsFalse}
-((\cfgnt{L}_\ell \lp \cfgnt{r}_0\rp = \cfgnt{L}_\ell \lp \cfgnt{r}_1 \rp) \wedge (s_\ell^\prime \in \zeta_t)) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime
+((\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp = \cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp) \wedge (s_\gse^\prime \in \zeta_t)) \Rightarrow s_\gse^\prime \sqsubset s_\sym^\prime
 \end{equation}
 
-Case 4: Assume that $s_s^\prime$ has the form $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp $.
+Case 4: Assume that $s_\sym^\prime$ has the form $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp $.
 The proof for this case is highly similar to the proof for Case 2, so we omit it for the sake of brevity. The result for this case is:
@@
 \label{eqn:RCBackwardsFalse}
-s_s^\prime=\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp \wedge s_\ell^\prime \sqsubset s_s^\prime \Rightarrow s_\ell^\prime \in \zeta_f
+s_\sym^\prime=\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp \wedge s_\gse^\prime \sqsubset s_\sym^\prime \Rightarrow s_\gse^\prime \in \zeta_f
 \end{equation}
@@
 \begin{equation}
-\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
 \end{equation}
@@
 \label{lem:new}
-If there exists states $s_\ell$ and $s_s$ such that $s_s \in \mathcal{NW}$ and $s_\ell \sqsubset s_s$, then:
+If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{NW}$ and $s_\gse \sqsubset s_\sym$, then:
 \begin{equation}
-\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
+\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
 \end{equation}
@@
 %\begin{theorem}[Exactness of Summary Machine States]
-%If $\Pi_n^s$ is a feasible summary state sequence, then the final state in $\Pi_n^s$ is equivalent to the feasible set of lazy states sharing the same control flow sequence:
+%If $\Pi_n^s$ is a feasible summary state sequence, then the final state in $\Pi_n^s$ is equivalent to the feasible set of GSE states sharing the same control flow sequence:
 %\begin{equation}
-%\mathit{last}(\Pi_n^s) \cong \mathbb{FS}(\rightarrow_\ell, \mathit{first}(\Pi_n^s), \mathbb{CF}(\Pi_n^s) )
+%\mathit{last}(\Pi_n^s) \cong \mathbb{FS}(\rgse, \mathit{first}(\Pi_n^s), \mathbb{CF}(\Pi_n^s) )
 %\end{equation}
@@
 %Base case: For any initial state $s_0$, the feasible state set contains a single element, $\{s_0\}$:
-%$$\mathbb{FS}(\rightarrow_\ell, (s_0), \mathbb{CF}(s_0)) = \{s_0\}$$
+%$$\mathbb{FS}(\rgse, (s_0), \mathbb{CF}(s_0)) = \{s_0\}$$
 %We can define a homomorphism from $s_0$ to $s_0$ using the identity function: 
@@
 Thus, any state in the feasible set must be represented by $s_0$: :
-%$$s_0 \in \mathbb{FS}(\rightarrow_\ell,s_0, (\eta_0\ e_0\ k_0) ) \Rightarrow s_0 \sqsubset s_0$$
+%$$s_0 \in \mathbb{FS}(\rgse,s_0, (\eta_0\ e_0\ k_0) ) \Rightarrow s_0 \sqsubset s_0$$
 %Furthermore, since every reference points to a single place, there is only one possible represented heap. Thus:
-%$$ \{s_0\} = \mathbb{FS}(\rightarrow_\ell,s_0, (\eta_0\ e_0\ k_0) )$$
+%$$ \{s_0\} = \mathbb{FS}(\rgse,s_0, (\eta_0\ e_0\ k_0) )$$
 %Since $s_0$ is the only represented heap, and since we know $s_0$ is in the feasible set, 
 %$$s_0 \sqsubset s_0 \Leftrightarrow s_0 \in \{s_0\}$$
-%We have now shown that $s_0 \cong \mathbb{FS}(\rightarrow_\ell, (s_0), \mathbb{CF}(s_0))$ for an arbitrary initial state $s_0$.
+%We have now shown that $s_0 \cong \mathbb{FS}(\rgse, (s_0), \mathbb{CF}(s_0))$ for an arbitrary initial state $s_0$.
 Since every feasible state sequence starts with an initial state, we now know that:
-% $$\mathit{last}(\Pi_1^s) \cong \mathbb{FS}(\rightarrow_\ell, \mathit{first}(\Pi_1^s), \mathbb{CF}(\Pi_1^s) ) $$
+% $$\mathit{last}(\Pi_1^s) \cong \mathbb{FS}(\rgse, \mathit{first}(\Pi_1^s), \mathbb{CF}(\Pi_1^s) ) $$
 %
-%Inductive step: If summary state $s_s$ is exact, then any state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$ is also exact.
-Suppose $s_s$ has the form for a field read, field write, or reference compare rule.
-By Lemmas \ref{lem:access}, \ref{lem:write}, and \ref{lem:compare}, $s_s^\prime$ will also be exact.
-%Suppose $s_s$ is accepted by the "new" rule.
-In this case, the new reference points to the new location on condition true, so it's obvious that $s_s$ represents all of the proper lazy states, and the existence of any infeasible lazy states represented by $s_s^\prime$ would imply that $s_s$ is not exact.
-%For all the other rules, the L and R functions and $\phi$ are unchanged, and the rules for  $\eta$, $e$, and $k$ are exactly the same between the lazy and summary machines, so there is a bijective mapping between the represented states in $s_s$ and $s_s^\prime$.
-%Thus, in all cases, if $s_s$ is exact, then $s_s^\prime$ is also exact.
+%Inductive step: If summary state $s_\sym$ is exact, then any state $s_\sym^\prime$ such that $s_\sym \rsym s_\sym^\prime$ is also exact.
+Suppose $s_\sym$ has the form for a field read, field write, or reference compare rule.
+By Lemmas \ref{lem:access}, \ref{lem:write}, and \ref{lem:compare}, $s_\sym^\prime$ will also be exact.
+%Suppose $s_\sym$ is accepted by the "new" rule.
+In this case, the new reference points to the new location on condition true, so it's obvious that $s_\sym$ represents all of the proper GSE states, and the existence of any infeasible GSE states represented by $s_\sym^\prime$ would imply that $s_\sym$ is not exact.
+%For all the other rules, the L and R functions and $\phi$ are unchanged, and the rules for  $\eta$, $e$, and $k$ are exactly the same between the GSE and summary machines, so there is a bijective mapping between the represented states in $s_\sym$ and $s_\sym^\prime$.
+%Thus, in all cases, if $s_\sym$ is exact, then $s_\sym^\prime$ is also exact.
 %
@@
 %
-%$$\mathit{last}(\Pi_n^s) \cong \mathbb{FS}(\rightarrow_\ell, \mathit{first}(\Pi_n^s), \mathbb{CF}(\Pi_n^s) ) $$
+%$$\mathit{last}(\Pi_n^s) \cong \mathbb{FS}(\rgse, \mathit{first}(\Pi_n^s), \mathbb{CF}(\Pi_n^s) ) $$
 %
@@
 \begin{proof}
-Take any two states $s_\ell$ and $s_s$ such that $s_\ell \sqsubset s_s$.
-If $s_s \in \mathcal{FA} \cup \mathcal{FW} \cup \mathcal{RC} \cup \mathcal{NW}$, then by Lemmas \ref{lem:access}, \ref{lem:write}, \ref{lem:compare}, and \ref{lem:new} we know Equations \ref{eqn:BisimulationForwards} and \ref{eqn:BisimulationBackwards} hold.
-If $s_s$ has any other form, the heap is not modified for $s_\ell^\prime$ or $s_s^\prime$, so then Equations \ref{eqn:BisimulationForwards} and \ref{eqn:BisimulationBackwards} hold by default.
-Thus, Equations \ref{eqn:BisimulationForwards} and \ref{eqn:BisimulationBackwards} hold for all  $s_\ell$ and $s_s$ such that $s_\ell \sqsubset s_s$.
+Take any two states $s_\gse$ and $s_\sym$ such that $s_\gse \sqsubset s_\sym$.
+If $s_\sym \in \mathcal{FA} \cup \mathcal{FW} \cup \mathcal{RC} \cup \mathcal{NW}$, then by Lemmas \ref{lem:access}, \ref{lem:write}, \ref{lem:compare}, and \ref{lem:new} we know Equations \ref{eqn:BisimulationForwards} and \ref{eqn:BisimulationBackwards} hold.
+If $s_\sym$ has any other form, the heap is not modified for $s_\gse^\prime$ or $s_\sym^\prime$, so then Equations \ref{eqn:BisimulationForwards} and \ref{eqn:BisimulationBackwards} hold by default.
+Thus, Equations \ref{eqn:BisimulationForwards} and \ref{eqn:BisimulationBackwards} hold for all  $s_\gse$ and $s_\sym$ such that $s_\gse \sqsubset s_\sym$.
 By Definition \ref{bisimulation}, $\sqsubset$ is a bisimulation.
@@
 \begin{corollary}
-For any given initial state, the set of possible control flow sequences under the lazy transition relation is exactly the set of possible control flow sequences under the summary transition relation.
+For any given initial state, the set of possible control flow sequences under the GSE transition relation is exactly the set of possible control flow sequences under the symbolic transition relation.
 \end{corollary}
@@
 \begin{corollary}
-For any given initial state, the number of final summary states is exactly the number of possible control flow sequences.
+For any given initial state, the number of final symbolic states is exactly the number of possible control flow sequences.
 \end{corollary}
@@
 %\begin{corollary}
-%For any given initial state, the set of solutions to the constraints in the final summary states provides an optimal set of concrete test inputs.
+%For any given initial state, the set of solutions to the constraints in the final symbolic states provides an optimal set of concrete test inputs.
 There is no smaller set that will exercise every possible control flow sequence.

### 2014-10-03 tex/proofs.tex
Minor revision on lem S-determ

@@
 \begin{proof}
-Induction over the number of machine steps on the symbolic initialization machine in \figref{fig:symInit}.
+Induction over the number of steps in $\rsum^*$ in \figref{fig:symInit}.
 
-\noindent\textbf{Base Case}. The machine takes one step: $(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f})
+\noindent\textbf{Base Case}. The relation makes one step: $(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f})
 \rsum
 (\cfgnt{L}_1\ \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f})$. Let $\Lambda = \mathbb{UN}(\cfgnt{L}_0, \cfgnt{R}_0, \cfgnt{r},
-\cfgnt{f})$ be the set of uninitialized locations. If $\Lambda = \emptyset$, then the \texttt{Summarize (end)}
+\cfgnt{f})$ be the set of uninitialized locations. If $\Lambda = \emptyset$, then the \textrm{S{\footnotesize UMMARIZE-END}}
 rule is active and $(\cfgnt{L}_1\ \cfgnt{R}_1) = (\cfgnt{L}_0\ \cfgnt{R}_0)$, which is deterministic by the initial conditions in the lemma.
 
-If $\Lambda \neq \emptyset$, then the \texttt{Summarize} rule is
+If $\Lambda \neq \emptyset$, then the \textrm{S{\footnotesize UMMARIZE}} rule is
 active, and each new constraint location pair must be considered
@@
 \end{itemize}
-As $\theta$ is mapped to a single reference $r_f$ in an already deterministic heap, the
+As $\theta$ is mapped to a single reference $r_f = \mathit{init}_r()$ in an already deterministic heap, the
 resulting heap $(\cfgnt{L}_1\ \cfgnt{R}_1)$ is likewise deterministic.
@@
 \]
-By the induction hypothesis, $(\cfgnt{L}_n\ \cfgnt{R}_n)$ is location
-mutual exclusive. This matches the base case, in that the heap on the
-left side of $\rsum$ is location mutual exclusive, and by the
+By the induction hypothesis, $(\cfgnt{L}_n\ \cfgnt{R}_n)$ is deterministic. This matches the base case, in that the heap on the
+left side of $\rsum$ is deterministic, and by the
 same argument as in the base case,
-$(\cfgnt{L}_{n+1}\ \cfgnt{R}_{n+1})$ is thus location mutual exclusive.
+$(\cfgnt{L}_{n+1}\ \cfgnt{R}_{n+1})$ is thus deterministic.
 \end{proof}
@@
 \label{lem:FA-determ}
-Given a state, $s_\sym$, with a deterministic heap,
-$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
-\mathrm{heap}(s_\sym)$, the new heap,
-$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
-\mathrm{heap}(s_\sym^\prime)$, in any state related by the field
-access rule, $s_\sym \rightarrow_\mathit{FA} s_\sym^\prime$,
+Given a state, $s$, with a deterministic heap,
+$(\cfgnt{L}\ \cfgnt{R}) =
+\mathrm{heap}(s)$, the new heap,
+$(\cfgnt{L}^\prime\ \cfgnt{R}^\prime) =
+\mathrm{heap}(s^\prime)$, in any state related by the field
+access rule, $s \rightarrow_\mathit{FA} s^\prime$,
 is also deterministic.
@@
 
-\lemref{lem:S-determ} establishes that the heap coming out of the
-$S$-relation is deterministic, so it is only needed to show that
-determinism is preserved by the call to the value function,
-$\mathbb{VS}$, in the rule. Let $(\cfgnt{L}\ \cfgnt{R})$ be that new
-deterministic heap.
+\lemref{lem:S-determ} establishes that the heap in the state on the right side of
+$\rsum^*$ is deterministic if the heap in the state on the left side
+is deterministic, so it is only needed to show that determinism is
+preserved by the call to the value function, $\mathbb{VS}$, in the
+rule. Let $(\cfgnt{L}\ \cfgnt{R})$ be the new deterministic heap related by $\rsum^*$.
 
@@
 determinism, the new heap with $r^\prime$ and the value set,
-$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
-\mathrm{heap}(s_\sym^\prime)$, is also deterministic.
+$(\cfgnt{L}^\prime\ \cfgnt{R}^\prime) =
+\mathrm{heap}(s^\prime)$, is also deterministic.
 \end{proof}

### 2014-10-06 tex/proofs.tex
Removed r_f

@@
 \begin{proof}
-Proof by \lemref{FA-determ}, \lemref{FW-determ}, and \lemref{J-determ}
+Proof by \lemref{lem:FA-determ}, \lemref{lem:FW-determ}, and \lemref{lem:J-determ}
 which represent all the rules that relate states in

### 2014-10-06 tex/proofs.tex
First try at restating lemma 1

@@
 
-\begin{lemma}[Bisimulation for $S$-relation]
+\begin{lemma}[$\sqsubset$ is a bisimulation for $\rinit$ and $\rsum$]
 \label{lem:init}
@@
 Since $\cfgnt{R}_{s} ( l_\sym,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_\sym,  \cfgnt{f})$, the Summarize rule must have altered this reference.
-A reference created by the Summarize rule has a value set $\theta_{all}$ with four subsets: $\theta_{null}$, $\theta_{new}$, $\theta_{alias}$, and $\theta_{orig}$.
-Because $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f}) = \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$, we know that the location we want to map to lies in $\theta_{orig}$.
+A reference created by the Summarize rule has a value set $\theta_{all}$ with four subsets: $\theta_{null}$, $\theta_{new}$, $\theta_{alias}$, and $\theta_\mathit{orig}$.
+Because $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f}) = \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$, we know that the location we want to map to lies in $\theta_\mathit{orig}$.
 Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{\gse}(\cfgnt{R}_{\gse} (\cfgnt{l}_\gse,f )) $, and let $l_{orig} = h(l_\alpha)$.
@@
 Let $l_{orig} = h(l_\alpha)$.
-We can see that by the Summarize rule $ (\phi_b\ l_{orig})\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$, so therefore:
+We can see that by the Summarize rule $ (\phi_b\ l_\mathit{orig})\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$, so therefore:
 $$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$$
@@
 For locations in Class 1, no new conjuncts are added to $\mathbb{HC}(s_\gse^\prime \rightharpoonup_{h} s_\sym^\prime)$, and therefore the satisfiability cannot be changed.
-For locations in Class 2 or Class 3, the new constraints take either the form $\phi_x \wedge \phi_{orig}$, or $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$.
-Constraints of the form  $\phi_x \wedge \phi_{orig}$ contain terms $\phi_x$ and $\phi_{orig}$ which were already conjoined to prior heap constraint, so satisfiability is not affected.
+For locations in Class 2 or Class 3, the new constraints take either the form $\phi_x \wedge \phi_\mathit{orig}$, or $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$.
+Constraints of the form  $\phi_x \wedge \phi_\mathit{orig}$ contain terms $\phi_x$ and $\phi_\mathit{orig}$ which were already conjoined to prior heap constraint, so satisfiability is not affected.
 In constraints of the form $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$, the term $\phi_x$ is conjoined to the prior heap constraint, and all the other terms involve the new variable $r_f$, so satisfiability is not affected.
@@
 All of the new references point to either a new location, the null location, the uninitialized location, or some alias.
-In the Summarize rule, the values and constraints for the new, null, uninitialized, and alias locations are contained in the sets $\theta_{new}$, $\theta_{null}$, $\theta{orig}$, and $\theta_{alias}$.
+In the Summarize rule, the values and constraints for the new, null, uninitialized, and alias locations are contained in the sets $\theta_{new}$, $\theta_{null}$, $\theta_\mathit{orig}$, and $\theta_{alias}$.
 Since the null, and uninitialized locations are already accounted for by the homomorphism $s_\gse \rightharpoonup_h s_\sym$, and since a new location was created symmetrically for both $s_\gse^\prime$ and $s_\sym^\prime$, the problem must be with some alias location that is part of $s_\sym$ but not $s_\gse$.

### 2014-10-09 tex/definitions.tex
re-orging

@@
-\subsection{Definitions}
-
-In Javalite, states are strings that match a certain pattern.
-
-\begin{definition}
-\label{def:state}
-The set of \textbf{states} $\mathcal{S}$ is defined as the set of strings matching the pattern $s$ in \ref{fig:machine-syntax}.
-\end{definition}
-
-\begin{definition}
-\label{def:initstate}
-$\mathcal{S}_0$ is defined as the set of \textbf{initial states}.
-An initial state is a state meeting the following conditions:  The range of L has exactly three locations: $l_{null}$, $l_{un}$, and $l_0$, the function R is defined only for location $l_0$, and for any field $f$, $R(l_0,f)$ returns $r_{un}$.
-\end{definition}
-
-You can think references as a pointers to sets of locations.
-More concretely, a reference is an integer that the $R$ function maps to a set of constraint, location pairs that define where it points to.
-Within a machine state, references are string encodings of integers.
-
-\begin{definition}
-The set of \textbf{references} $\mathcal{R}$ is defined as the set of natural numbers
- $$\mathcal{R} = \mathbb{N}$$
-\end{definition}
-
-In order to make the distinction between different types of references, we partition the set of references using modular arithmetic.
-Stack references are those references which are created as a result of a field read.
-The total number of references in a representing state and a represented state are generally not the same.
-However, the number of references on the stack in either state is always the same.
-
-\begin{definition}
-The set of \textbf{stack references} $\mathcal{R}_t$ is defined as
- $$\mathcal{R}_t =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 0\}$$. 
-\end{definition}
-
-Input heap references are references that exist prior to program execution in the symbolic input heap.
-While this set of references may be infinite, they are discovered one at a time via lazy initialization.
-
-\begin{definition}
-The set of \textbf{input heap references} $\mathcal{R}_h$ is defined as
- $$\mathcal{R}_h =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 1\}$$. 
-\end{definition}
-
-\begin{definition}
-The set of \textbf{new heap references} $\mathcal{R}_f$ is defined as
- $$\mathcal{R}_n =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$. 
-\end{definition}
-
-\begin{definition}
-For a given function $f:A \mapsto B$, the \textbf{image} $f^\rightarrow$ and \textbf{preimage} $f^\leftarrow$ are defined as
-\begin{align}
- f^\rightarrow &= \{ f(a) \mid a \in A\}\\
- f^\leftarrow &= \{ a \mid f(a) \in B \}
- \end{align}
- The bracket notation $ f^\rightarrow [C] $ is used to denote that the image is drawn from a specific subset:
- \begin{align}
- f^\rightarrow [C] &= \{ f(a) \mid a \in C\}\\
- f^\leftarrow [D] &= \{ a \mid f(a) \in D \}
- \end{align}
- Where $C \subset A$ and $D \subset B$
-\end{definition}
-
-\begin{definition}
-A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times \mathcal{S} $, which relates machine states with successor states.
-Two important state transition relations are \textbf{GSE} $\rgse$ and \textbf{symbolic} $\rsym$.
-Each of these use a separate relation for initialization: $\rinit$ for GSE and $\rsum$ for symbolic.
-All of these transition relations are defined in \figref{fig:lazy}, \figref{fig:lazyInit}, \figref{fig:sym}, and \figref{fig:symInit}.
-\end{definition}
+\subsection{Heap Properties}
 

### 2014-10-09 tex/javalite.tex
re-orging

--- 2014-08-22 tex/javalite.tex
@@
-\section{Javalite}
+\section{Preliminaries}
+
 \figref{fig:surface-syntax} defines the surface syntax for the
@@
 \input{surface-syntax}
-\input{machine-syntax}
 
+\subsection{Environment}
 The environment, $\eta$, associates a variable $\cfgnt{x}$ with a
@@
 $\cfgnt{v}$.
-
-The heap is a labeled bipartite graph consisting of references,
-$\cfgnt{r}$, and locations, $\cfgnt{l}$. The machine syntax in
-\figref{fig:machine-syntax} defines that graph in $\cfgnt{L}$, the
-location map, and $\cfgnt{R}$, the reference map. As done with the
-environment, $\cfgnt{L}$ and $\cfgnt{R}$ are treated as partial
-functions where $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the set
-of location-constraint pairs in the heap associated with the given
-reference, and$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the
-reference associated with the given location-field pair in the
-heap.
-
-As the updates to $\cfgnt{L}$ and $\cfgnt{R}$ are complex in the
-machine semantics, predicate calculus is used to describe updates to
-the functions. Consider the following example where $\cfgnt{l}$ is
-some location and$\rho$ is a set of references.
-\[
-\cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}][\forall \cfgnt{r}^\prime \in \rho\ \lp \cfgnt{r}^\prime \mapsto \lp \cfgt{true}\ l_\mathit{null}\rp \rp ]
-\]
-The new partial function $\cfgnt{L}^\prime$ is just like $\cfgnt{L}$ only it
-remaps $\cfgnt{r}$, and it remaps all the references in $\rho$.
-
-The location $\cfgnt{l}_\mathit{null}$ is a special location in the heap
-to represent null. It has a companion reference
-$\cfgnt{r}_\mathit{null}$. The initial heap for the machine is defined
-such that $\cfgnt{L}(\cfgnt{r}_\mathit{null}) = \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$
-
-The initial state of the machine needs to be defined.
-
-\input{javalite-common}
-
-The rewrite rules that define the Javalite semantics are in
-\figref{fig:javalite-common}.

### 2014-10-09 tex/lazy.tex
finished conditional initialization
re-orging

--- 2014-07-02 tex/lazy.tex
@@
-\begin{figure*}[t]
-\begin{center}
-\mprset{flushleft}
-\begin{mathpar}
-	\inferrule[Field Access]{
-      \{\lp\phi\ l\rp\} = \cfgnt{L}\lp\cfgnt{r}\rp\\
-      l \neq \cfgnt{l}_\mathit{null}\\\\
-      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \cfgnt{r}\ \cfgnt{f}\rp \rightarrow^*_I 
-      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi_g^\prime\ \cfgnt{r}\ \cfgnt{f} \rp \\\\ 
-      \{\lp\phi^\prime\ l^\prime\rp\} = \cfgnt{L}^\prime\lp\cfgnt{R}^\prime\lp l,\cfgnt{f}\rp\rp \\
-      \mathrm{fresh}_r\lp\rp  = \cfgnt{r}^\prime \\
-    }{
-      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp  \rightarrow \\\\
-      \lp \cfgnt{L}^\prime[\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}^\prime\ \phi_g^\prime\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp 
-	}
-\and
-	\inferrule[Field Write]{
-      \cfgnt{r}_x = \eta\lp \cfgnt{x}\rp\\ 
-      \{\lp\phi\ l\rp\} = \cfgnt{L}\lp\cfgnt{r}_x\rp \\
-      l \neq \cfgnt{l}_\mathit{null}\\\\
-      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \cfgnt{r}_x\ \cfgnt{f}\rp \rightarrow^*_I 
-      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi_g^\prime\ \cfgnt{r}_x\ \cfgnt{f} \rp \\\\ 
-      \mathrm{fresh}_r\lp\rp = \cfgnt{r}^\prime\\
-      \theta =  \cfgnt{L}^\prime\lp\cfgnt{r}\rp 
-    }{
-      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp  \rightarrow \\\\
-      \lp \cfgnt{L}^\prime[\cfgnt{r}^{\prime} \mapsto \theta]\ \cfgnt{R}^\prime[\lp l\ \cfgnt{f}\rp  \mapsto \cfgnt{r}^\prime]\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp 
-	}	
-\and
-    \inferrule[Equals (reference-true)]{
-    \cfgnt{L}\lp \cfgnt{r}_0\rp = \cfgnt{L}\lp \cfgnt{r}_1\rp\\
-    \phi_g^\prime = \lp\phi_g \wedge r_0 = r_1\rp
-    }{
-    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\ \cfgt{=}\ \cfgt{*} \rightarrow \cfgnt{k}\rp \rp  \rightarrow \\\\
-    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp 
-    }
-\and
-    \inferrule[Equals (reference-false)]{
-    \cfgnt{L}\lp \cfgnt{r}_0\rp \neq \cfgnt{L}\lp \cfgnt{r}_1\rp\\
-    \phi_g^\prime = \lp\phi_g \wedge r_0 \neq r_1\rp
-   }{
-    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\ \cfgt{=}\ \cfgt{*} \rightarrow \cfgnt{k}\rp \rp  \rightarrow \\\\
-    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp 
-    }
-\end{mathpar}
-\end{center}
-\caption{Generalized symbolic execution with lazy initialization.}
-\label{fig:lazy}
-\end{figure*}
+\section{Initialization of Symbolic References}
+
+In this section we present the Javalite rewrite rules for the concrete
+as well as summary initialization of symbolic references. The
+initialization rules are defined on the bi-partite graph consisting of
+references and locations. The lazy initialization of symbolic
+references consists of three key points of non-determinism where each
+symbolic reference can be initialized non-deterministically to null, a
+new instance of the symbolic reference, or aliases to symbolic
+references of the same type previously initialized. The initialization
+in GSE consists of creating branches in the execution tree for all the
+non-deterministic choices. On the other hand, the heap summarization
+approach creates a single branch that contains the summarization for
+all the initialization in a single bi-partitate graph.
+
+\input{initialize-lazy}
+\input{summarize-precise}
+
+The initialization rules are invoked when an uninitialized field in a
+symbolic reference is accessed. The function $\mathbb{UN}(\cfgnt{L},
+\cfgnt{R}, \cfgnt{r}, \cfgnt{f}) = \{\cfgnt{l}\ ...\}$ returns
+constraint-location pairs in which the field $\cfgnt{f}$ is
+uninitialized:
+\[
+\begin{array}{rcl}
+\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \\
+& & \ \ \ \ \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \\
+& & \ \ \ \ \ \ \ \ \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
+\end{array}
+\]
+where $\mathbb{S}(\phi)$ returns true if $\phi$ is
+satisfiable. Intutively, for the reference, $\cfgnt{r}$, it constructs
+the set, $\theta$, that contains all contraint-location pairs that
+point to the field $\cfgnt{f}$ and $\cfgnt{f}$ points to
+$\cfgnt{l}_\mathit{un}$. The cardinality of the set, $\theta$ is never
+greater than one in GSE and the constraint is always satisfiable
+because all constraints are constant. This property is relaxed in GSE
+with heap summaries.
+
+The rules in~\figref{fig:lazyInit} present the rewrite rules for the
+concrete initialization of symbolic heap objects.  These rules are
+invoked until a fix pointed is reached.
+
+The initialize (null) rewrite rule in~\figref{fig:lazyInit} first
+checks that the field, $\cfgnt{r}$ is uninitialized. The fresh method
+returns a new input heap reference from the partition
+
+\section{Accessing and Writing to Field References}
+
+\section{Equality and InEquality of References}
+
+\input{lazy-fig}

### 2014-10-09 tex/preliminaries.tex
adding prelim

\subsection{Heap: A Bi-partiate Graph}

\input{machine-syntax}

The heap in this work is a labeled bipartite graph consisting of
references, $\cfgnt{r}$, and locations, $\cfgnt{l}$. The machine
syntax in \figref{fig:machine-syntax} defines that graph in
$\cfgnt{L}$, the location map, and $\cfgnt{R}$, the reference map. As
done with the environment, $\cfgnt{L}$ and $\cfgnt{R}$ are treated as
partial functions where $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is
the set of location-constraint pairs in the heap associated with the
given reference, and $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is
the reference associated with the given location-field pair in the
heap.

As the updates to $\cfgnt{L}$ and $\cfgnt{R}$ are complex in the
machine semantics, predicate calculus is used to describe updates to
the functions. Consider the following example where $\cfgnt{l}$ is
some location and$\rho$ is a set of references.
\[
\cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}][\forall \cfgnt{r}^\prime \in \rho\ \lp \cfgnt{r}^\prime \mapsto \lp \cfgt{true}\ l_\mathit{null}\rp \rp ]
\]
The new partial function $\cfgnt{L}^\prime$ is just like $\cfgnt{L}$ only it
remaps $\cfgnt{r}$, and it remaps all the references in $\rho$.

The location $\cfgnt{l}_\mathit{null}$ is a special location in the heap
to represent null. It has a companion reference
$\cfgnt{r}_\mathit{null}$. The initial heap for the machine is defined
such that $\cfgnt{L}(\cfgnt{r}_\mathit{null}) = \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$

You can think references as a pointers to sets of locations. More concretely, a reference is an integer that the $R$ function maps to a set of constraint, location pairs that define where it points to. Within a machine state, references are string encodings of integers.

\begin{definition}
The set of \textbf{references} $\mathcal{R}$ is defined as the set of natural numbers
 $$\mathcal{R} = \mathbb{N}$$
\end{definition}

In order to make the distinction between different types of references, we partition the set of references using modular arithmetic. Stack references are those references which are created as a result of a field read. The total number of references in a representing state and a represented state are generally not the same. However, the number of references on the stack in either state is always the same.

\begin{definition}
The set of \textbf{stack references} $\mathcal{R}_t$ is defined as
 $$\mathcal{R}_t =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 0\}$$. 
\end{definition}

Input heap references are references that exist prior to program execution in the symbolic input heap. While this set of references may be infinite, they are discovered one at a time via lazy initialization.

\begin{definition}
The set of \textbf{input heap references} $\mathcal{R}_h$ is defined as
 $$\mathcal{R}_h =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 1\}$$. 
\end{definition}

\begin{definition}
The set of \textbf{new heap references} $\mathcal{R}_f$ is defined as
 $$\mathcal{R}_n =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$. 
\end{definition}

\begin{definition}
For a given function $f:A \mapsto B$, the \textbf{image} $f^\rightarrow$ and \textbf{preimage} $f^\leftarrow$ are defined as
\begin{align}
 f^\rightarrow &= \{ f(a) \mid a \in A\}\\
 f^\leftarrow &= \{ a \mid f(a) \in B \}
 \end{align}
 The bracket notation $ f^\rightarrow [C] $ is used to denote that the image is drawn from a specific subset:
 \begin{align}
 f^\rightarrow [C] &= \{ f(a) \mid a \in C\}\\
 f^\leftarrow [D] &= \{ a \mid f(a) \in D \}
 \end{align}
 Where $C \subset A$ and $D \subset B$
\end{definition}

A special reference, $\cfgnt{r}_\mathit{un}$, and location,
$\cfgnt{l}_\mathit{un}$, is introduced to support lazy
initialization. The '$\mathit{un}$' is to indicate the reference or
location is uninitialized at the point of execution.

\subsection{Common Execution Semantics}

In Javalite, states are strings that match a certain pattern.

\begin{definition}
\label{def:state}
The set of \textbf{states} $\mathcal{S}$ is defined as the set of strings matching the pattern $s$ in \ref{fig:machine-syntax}.
\end{definition}

\begin{definition}
\label{def:initstate}
$\mathcal{S}_0$ is defined as the set of \textbf{initial states}. An initial state is a state meeting the following conditions:  The range of L has exactly three locations: $l_{null}$, $l_{un}$, and $l_0$, the function R is defined only for location $l_0$, and for any field $f$, $R(l_0,f)$ returns $r_{un}$. 
\end{definition}

\input{javalite-common}

The rewrite rules that define the Javalite semantics are in
\figref{fig:javalite-common}.

### 2014-10-10 tex/motivation.tex
updates to section 2

--- 2014-06-24 tex/motivation.tex
@@
-\section{Background and Motivation}
-\label{motivations}
+\section{Overview}
+\label{sec:overview}
 
-Example
+In this section we present an overview of the methodology for
+computing heap summaries lazily for generalized symbolic execution
+and illustrate its application to a small example. We begin with
+a brief explanation of the two supporting technologies.
+
+\subsection{Generalized Symbolic Execution}
+
+The traditional notion of symbolic 
+execution~\cite{clarke76TSE,King:76} was developed in the
+context of sequential programs with a fixed number of program
+variables having primitive types, e.g., integer, Boolean.
+\emph{Generalized symbolic execution (GSE)}~\cite{GSE03} extends
+traditional symbolic execution to enable analysis of heap
+manipulating software written in commonly used imperative
+languages such as Java and C++. 
+GSE enables context and flow sensitive analysis of complex
+and potentially unbounded data structures by
+constructing the heap ``lazily'' during symbolic execution,
+generating potential heap structures based on program semantics.
+The original GSE algorithm uses lazy initialization in which
+symbolic execution explores different heap structures
+by materializing the heap at the first memory access (read) of
+an uninitialized symbolic object. At this point, a non-deterministic
+choice point of heap locations is created that includes three cases:
+(1) a null
+object, (2) a new instance of the object, and (3) aliases
+to other type-compatible symbolic objects that have been materialized
+along the same execution path~\cite{GSE03}.  
+Improvements to the original lazy initializtion algorithm include the 
+\emph{lazier} and \emph{lazier\#} algorithms, implemented as part of the 
+\emph{Bogor$/$Kiasan} framework~\cite{Kiasan06,Kiasan07}, which
+reduce the amount of nondeterminism in the lazy algorithm by
+delaying initialization, sometimes indefinitely. 
+Although the lazy initialization algorithms extend symbolic
+analysis to heap manipulating software through partially initialized
+structures created on-the-fly, the materialization process
+exacerbates the state space explosion problem and may generate
+heap structures which, because of size their, exceed the capabilities
+of the materialization technique.
+
+\subsection{Heap Summarization Techniques}
+
+\subsection{Our Approach}
+
+Our approach is inspired by two state-of-the-art techniques: Generalized 
+Symbolic Execution (GSE) and heap summarization techniques. Like GSE,
+our approach constructs the heap lazily, i.e., materializing the heap
+on-the-fly during symbolic execution. However, unlike GSE, we create
+a compact representation of the heap, i.e., a heap summary, which eliminates
+isomorphic heap shapes without losing precision. The heap summaries computed
+by our approach have two important advantages: 1) they are capable of 
+handling arbitrary data structures, including recursive data structures,
+and, 2) because of lazy initialization, dynamic bounding can be use to
+bound input data structures.
+
+\begin{figure}
+\begin{tabular}[c]{l}
+\begin{lstlisting}
+public class LinkedList {
+
+/** assume the linked list is valid with no cycles **/
+LLNode head;
+Data data0, data1, data2, data3, data4;
+
+private class Data { Integer val; }
+
+private class LLNode {
+  protected Data elem;
+  protected LLNode next; }
+
+public static boolean contains(LLNode root, Data val) {
+  LLNode node = root;
+  while (true) {
+    if(node.val == val)  return true;
+    if(node.next == null) return false;
+    node = node.next;
+}}
+
+public void run() {
+if(LinkedList.contains(head, data0) && LinkedList.contains(head,data1) &&
+   LinkedList.contains(head, data2) && LinkedList.contains(head, data3) &&
+   LinkedList.contains(head, data4)) return;
+\end{lstlisting}
+\end{tabular} 
+\caption{Linked list}
+\label{fig:example}
+\end{figure}
+
+\begin{figure}[htb]
+\scalebox{0.45}
+{\includegraphics[width=563px]{../figs/time_vs_complexity.pdf}}
+\caption{Time versus complexity for the linked list example}
+\label{fig:tvc}
+\end{figure}

### 2014-10-10 tex/motivation.tex

@@
 variables having primitive types, e.g., integer, Boolean.
-\emph{Generalized symbolic execution (GSE)}~\cite{GSE03} extends
+\emph{Generalized Symbolic Execution (GSE)}~\cite{GSE03} extends
 traditional symbolic execution to enable analysis of heap
@@
 Improvements to the original lazy initializtion algorithm include the 
-\emph{lazier} and \emph{lazier\#} algorithms, implemented as part of the 
-\emph{Bogor$/$Kiasan} framework~\cite{Kiasan06,Kiasan07}, which
+\emph{lazier} and \emph{lazier\#} algorithms~\cite{Kiasan06,Kiasan07}
+%implemented as part of the \emph{Bogor$/$Kiasan} framework, 
+which
 reduce the amount of nondeterminism in the lazy algorithm by
@@
 structures created on-the-fly, the materialization process
-exacerbates the state space explosion problem and may generate
-heap structures which, because of size their, exceed the capabilities
+exacerbates the state space explosion problem in symbolic
+execution and may generate
+heap structures which, because of their size, exceed the capabilities
 of the materialization technique.
@@
 
-Our approach is inspired by two state-of-the-art techniques: Generalized 
+Consider the code for a (partial) {\tt LinkedList} implementation
+shown in~\figref{fig:example}. 
+Generalized Symbolic Execution will materialize the heap by adding
+non-deterministic choice points representing the different potential heap
+configurations at each location in the program where a field is read.
+The number of choice points introduced by each field access is dependent
+on how many type compatible heap locations were materialized during 
+previous field reads on the current path
+and on the lazy initialization algorithm used by GSE. 
+The graph shown in~\figref{fig:tvc} illustrates the growth in the symbolic
+execution state space 
+in terms of time as the number of calls to the {\tt contains()} method which
+reads the {\tt head} field.
+The blue and green lines show growth for the lazy and lazier\# 
+initialization algorithms respectively.
+Notice that the runtime, i.e., non-determinism, increases rapidly with 
+only a small number of invocations of the {\tt contains()} method
+with the lazy and lazier\# approaches.
+
+Our technique, blah, builds on the lazy initialization algorithm for
+Generalized Symbolic Execution by materializing the heap on-the-fly, i.e.,
+``lazily'' during symbolic execution, but
+and heap summariesOur approach is inspired by two state-of-the-art techniques: Generalized 
 Symbolic Execution (GSE) and heap summarization techniques. Like GSE,
@@
    LinkedList.contains(head, data2) && LinkedList.contains(head, data3) &&
-   LinkedList.contains(head, data4)) return;
+   LinkedList.contains(head, data4)) return;}}
 \end{lstlisting}

### 2014-10-10 tex/preliminaries.tex

@@
 The set of \textbf{new heap references} $\mathcal{R}_f$ is defined as
- $$\mathcal{R}_n =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$. 
+ $$\mathcal{R}_f =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$. 
 \end{definition}
@@
 \figref{fig:javalite-common}.
+
+\begin{definition}
+A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times \mathcal{S} $, which relates machine states with successor states.
+Two important state transition relations are \textbf{GSE} $\rgse$ and \textbf{symbolic} $\rsym$.
+Each of these use a separate relation for initialization: $\rinit$ for GSE and $\rsum$ for symbolic.
+All of these transition relations are defined in \figref{fig:lazy}, \figref{fig:lazyInit}, \figref{fig:sym}, and \figref{fig:symInit}.
+\end{definition}

### 2014-10-13 tex/preliminaries.tex
shome imp files

@@
-\subsection{Heap: A Bi-partiate Graph}
+\subsection{Transition System}
+
+In Javalite, states are strings that match a certain pattern.
 
 \input{machine-syntax}
-
-The heap in this work is a labeled bipartite graph consisting of
-references, $\cfgnt{r}$, and locations, $\cfgnt{l}$. The machine
-syntax in \figref{fig:machine-syntax} defines that graph in
-$\cfgnt{L}$, the location map, and $\cfgnt{R}$, the reference map. As
-done with the environment, $\cfgnt{L}$ and $\cfgnt{R}$ are treated as
-partial functions where $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is
-the set of location-constraint pairs in the heap associated with the
-given reference, and $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is
-the reference associated with the given location-field pair in the
-heap.
-
-As the updates to $\cfgnt{L}$ and $\cfgnt{R}$ are complex in the
-machine semantics, predicate calculus is used to describe updates to
-the functions. Consider the following example where $\cfgnt{l}$ is
-some location and$\rho$ is a set of references.
-\[
-\cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}][\forall \cfgnt{r}^\prime \in \rho\ \lp \cfgnt{r}^\prime \mapsto \lp \cfgt{true}\ l_\mathit{null}\rp \rp ]
-\]
-The new partial function $\cfgnt{L}^\prime$ is just like $\cfgnt{L}$ only it
-remaps $\cfgnt{r}$, and it remaps all the references in $\rho$.
-
-The location $\cfgnt{l}_\mathit{null}$ is a special location in the heap
-to represent null. It has a companion reference
-$\cfgnt{r}_\mathit{null}$. The initial heap for the machine is defined
-such that $\cfgnt{L}(\cfgnt{r}_\mathit{null}) = \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$
-
-You can think references as a pointers to sets of locations.
-More concretely, a reference is an integer that the $R$ function maps to a set of constraint, location pairs that define where it points to.
-Within a machine state, references are string encodings of integers.
-
-\begin{definition}
-The set of \textbf{references} $\mathcal{R}$ is defined as the set of natural numbers
- $$\mathcal{R} = \mathbb{N}$$
-\end{definition}
-
-In order to make the distinction between different types of references, we partition the set of references using modular arithmetic.
-Stack references are those references which are created as a result of a field read.
-The total number of references in a representing state and a represented state are generally not the same.
-However, the number of references on the stack in either state is always the same.
-
-\begin{definition}
-The set of \textbf{stack references} $\mathcal{R}_t$ is defined as
- $$\mathcal{R}_t =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 0\}$$. 
-\end{definition}
-
-Input heap references are references that exist prior to program execution in the symbolic input heap.
-While this set of references may be infinite, they are discovered one at a time via lazy initialization.
-
-\begin{definition}
-The set of \textbf{input heap references} $\mathcal{R}_h$ is defined as
- $$\mathcal{R}_h =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 1\}$$. 
-\end{definition}
-
-\begin{definition}
-The set of \textbf{new heap references} $\mathcal{R}_f$ is defined as
- $$\mathcal{R}_f =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$. 
-\end{definition}
-
-\begin{definition}
-For a given function $f:A \mapsto B$, the \textbf{image} $f^\rightarrow$ and \textbf{preimage} $f^\leftarrow$ are defined as
-\begin{align}
- f^\rightarrow &= \{ f(a) \mid a \in A\}\\
- f^\leftarrow &= \{ a \mid f(a) \in B \}
- \end{align}
- The bracket notation $ f^\rightarrow [C] $ is used to denote that the image is drawn from a specific subset:
- \begin{align}
- f^\rightarrow [C] &= \{ f(a) \mid a \in C\}\\
- f^\leftarrow [D] &= \{ a \mid f(a) \in D \}
- \end{align}
- Where $C \subset A$ and $D \subset B$
-\end{definition}
-
-A special reference, $\cfgnt{r}_\mathit{un}$, and location,
-$\cfgnt{l}_\mathit{un}$, is introduced to support lazy
-initialization. The '$\mathit{un}$' is to indicate the reference or
-location is uninitialized at the point of execution.
-
-\subsection{Common Execution Semantics}
-
-In Javalite, states are strings that match a certain pattern.
 

### 2014-10-13 tex/heap.tex
heapy stuffy

\section{Heap: A Bi-partiate Graph}

The heap in this work is a labeled bipartite graph consisting of
references, $\cfgnt{r}$, and locations, $\cfgnt{l}$. The machine
syntax in \figref{fig:machine-syntax} defines that graph in
$\cfgnt{L}$, the location map, and $\cfgnt{R}$, the reference map. As
done with the environment, $\cfgnt{L}$ and $\cfgnt{R}$ are treated as
partial functions where $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is
the set of location-constraint pairs in the heap associated with the
given reference, and $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is
the reference associated with the given location-field pair in the
heap.

As the updates to $\cfgnt{L}$ and $\cfgnt{R}$ are complex in the
machine semantics, predicate calculus is used to describe updates to
the functions. Consider the following example where $\cfgnt{l}$ is
some location and$\rho$ is a set of references.
\[
\cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}][\forall \cfgnt{r}^\prime \in \rho\ \lp \cfgnt{r}^\prime \mapsto \lp \cfgt{true}\ l_\mathit{null}\rp \rp ]
\]
The new partial function $\cfgnt{L}^\prime$ is just like $\cfgnt{L}$
only it remaps $\cfgnt{r}$, and it remaps all the references in
$\rho$.

The location $\cfgnt{l}_\mathit{null}$ is a special location in the
heap to represent null. It has a companion reference
$\cfgnt{r}_\mathit{null}$. The initial heap for the machine is defined
such that $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
\{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$

You can think references as a pointers to sets of locations. More
concretely, a reference is an integer that the $R$ function maps to a
set of constraint, location pairs that define where it points
to. Within a machine state, references are string encodings of
integers.

\begin{definition}
The set of \textbf{references} $\mathcal{R}$ is defined as the set of natural numbers
 $$\mathcal{R} = \mathbb{N}$$
\end{definition}

In order to make the distinction between different types of references, we partition the set of references using modular arithmetic. Stack references are those references which are created as a result of a field read. The total number of references in a representing state and a represented state are generally not the same. However, the number of references on the stack in either state is always the same.

\begin{definition}
The set of \textbf{stack references} $\mathcal{R}_t$ is defined as
 $$\mathcal{R}_t =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 0\}$$. 
\end{definition}

Input heap references are references that exist prior to program execution in the symbolic input heap. While this set of references may be infinite, they are discovered one at a time via lazy initialization.

\begin{definition}
The set of \textbf{input heap references} $\mathcal{R}_h$ is defined as
 $$\mathcal{R}_h =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 1\}$$. 
\end{definition}

\begin{definition}
The set of \textbf{new heap references} $\mathcal{R}_f$ is defined as
 $$\mathcal{R}_f =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$. 
\end{definition}

\begin{definition}
For a given function $f:A \mapsto B$, the \textbf{image} $f^\rightarrow$ and \textbf{preimage} $f^\leftarrow$ are defined as
\begin{align}
 f^\rightarrow &= \{ f(a) \mid a \in A\}\\
 f^\leftarrow &= \{ a \mid f(a) \in B \}
 \end{align}
 The bracket notation $ f^\rightarrow [C] $ is used to denote that the image is drawn from a specific subset:
 \begin{align}
 f^\rightarrow [C] &= \{ f(a) \mid a \in C\}\\
 f^\leftarrow [D] &= \{ a \mid f(a) \in D \}
 \end{align}
 Where $C \subset A$ and $D \subset B$
\end{definition}

A special reference, $\cfgnt{r}_\mathit{un}$, and location,
$\cfgnt{l}_\mathit{un}$, is introduced to support lazy
initialization. The '$\mathit{un}$' is to indicate the reference or
location is uninitialized at the point of execution.

### 2014-10-16 tex/abstract.tex
Added Neha's changes to abstract

@@
 analysis has been the treatment of dynamically allocated data.
-State-of-the-art techniques have addressed this challenge
-through the use of heap summaries and by constructing the concrete
-heap ``lazily.'' In this work, we present a novel heap analysis technique
-which takes inspiration from both approaches and builds exact heap summaries
-lazily during symbolic execution. Our technique enables
-exact analysis of program properties and
-analysis of arbitrary recursive data structures. It also supports
-dynamic bounds for linked data structure inputs, and
-efficient sub-division of the underlying constraint problem.
-We demonstrate the precision and scalability of our approach
-in the Symbolic PathFinder framework for analyzing Java programs.
+State-of-the-art techniques have addressed this challenge through
+either (a) the use of summaries that over-approximate possible heaps, or
+(b) by materializing a concrete heap lazily during generalized
+symbolic execution. In this work, we present a novel heap
+initialization and analysis technique which takes inspiration from
+both approaches and constructs precise heap summaries lazily during
+symbolic execution.  Our approach is 1) \emph{scalable}: it reduces the
+points of non-determinism compared to generalized symbolic execution
+and explores each control-flow path only once for any given set of
+isomorphic heaps, 2) \emph{precise}: at any given point during symbolic
+execution, the symbolic heap represents the exact set of feasible
+concrete heap structures for the program under analysis, and 3)
+\emph{expressive}: the symbolic heap can represent recursive data
+structures. We demonstrate the precision and scalability of our
+approach by implementing it as an extension to the Symbolic PathFinder
+framework for analyzing Java programs.
 

### 2014-10-31 tex/results.tex
Added results section.

\section{Empirical Evaluation}
GSESH creates fewer execution paths than GSE, but it does so with increased path constraint complexity. Determining the impact of this tradeoff in real-world applications is an important research question.

Hypothesis

\subsection{Implementation}

\subsection{Bounding}
In order to perform a practical evaluation of programs involving recursive data structures, it is generally necessary to impose some sort of bounding to eliminate the number of lazy initializations to a manageable level. While these bounds may be asserted as invariants within the program in-situ, it is more practical to apply bounding via external means. There are several bounding techniques that may be applied to both GSE and GSESH, including execution path length bounding, k-bounding and n-bounding. k-bounding and n-bounding both operate by imposing limits on the size of the symbolic input heap, but differ in how such bounds are defined. n-bounding limits the number of objects created by lazy initialization, while k-bounding limits the length of initialized reference chains. k-bounding has the property of exhaustively exploring the full breadth of a given data structure, while n-bounding tends to explore deeper heap shapes while being somewhat less thorough in breadth. In addition, k-bounding and n-bounding may be combined to adjust the desired level of approximation between depth and breadth.

While k-bounding and n-bounding are applicable to both GSE and GSESH, they are not both equally suited for comparing the two methods. The main reason for this lies in how how each bounding technique impacts the functional equivalence of the respective methods.  k-bounding preserves the functional equivalence of GSE and GSESH, a fact which can be established by induction over the length of reference chains from a given initial state. In contrast, GSE and GSESH are not generally functionally equivalent under n-bounding. The reason is that since a GSESH state must represent all possible GSE states on an execution path, it generally includes more locations than any single GSE state it represents. This difference in state counts makes it difficult to externally assert n-bounding in a manner that preserves functional equivalence between GSE and GSESH. Functional equivalence may be preserved in the case where n-bounds are asserted via in-situ invariants, but the significant increase in constraint complexity makes this approach impractical. For this reason, n-bounding is was not selected for comparing GSE to GSESH in the tests performed in this paper.

In contrast to the heap-based bounds provided by k-bounding and n-bounding, execution path-length bounding works by limiting the number along any given execution path. As with other bounding techniques, the usefulness of path-length bounding hinges on whether it preserves functional equivalence. While path-length bounding preserves functional equivalence for GSE and GSESH as formulated in this paper, it does not preserve it for the algorithms as they are implemented in JPF. The reason for the discrepancy lies in how states are defined in JPF. In JPF, the notion of states is closely tied to the concept of nondeterminism. New states are created in JPF only when a nondeterministic choice is made, meaning the number of states on an execution path is tied to the number of nondeterministic choices. A discrepancy in the length of the respective execution paths may be caused by any difference in nondeterminism between the two methods. This is significant, since the nondeterminism in GSESH and GSE differs in both field reads and in reference compares. Field reads in GSESH are deterministic, whereas in GSE they may initiate a nondeterministic lazy initialization. Conversely, in GSE address compares are deterministic, but in GSESH address compares require a nondeterministic assertion over the truth of the branch condition. For this reason, path-length bounding was not used for this experimental evaluation. For future tests, we are considering inserting artificial points of nondeterminism in order to establish functional equivalence of path-length bounds between GSE and GSESH.

\subsection{Evaluation} 
Experimental set-up

Test Cases

In order to evaluate the performance of GSESH, the implementation was tested against three examples: LinkedList, BinarySearchTree, TreeMap.
The LinkedList example tests performance on linked list data structures. The test program begins by assuming an object invariant before initiating a sequence of contains() method calls. This is a challenging example for GSE because each call to the contains() method contains a new lazy initialization, which in turn creates an exponential path expansion throughout program execution. While the constraints for each path are easily solved, the sheer number of paths quickly becomes overwhelming.

The BinarySearchTree example test program consists simply of asserting the object invariant for a binary search tree. This example is interesting because it demonstrates nondeterminism from both aliasing constraints created during lazy initialization, and linear constraints from evaluating conditionals over numeric symbols.

Like the BinarySearchTree test, the TreeMap test is simply an assertion of an object invariant, in this case for a red/black tree. This example serves as a stress test for GSESH, since most of the nondeterminism comes from linear constraints over the shape of the tree, rather than aliasing constraints created during lazy initialization. In this case, the path advantage for GSESH is minimized.

For all tests, program complexity was adjusted via k-bounding. For the LinkedList test, the number of contains() method calls was added as an additional parameter. After the conclusion of each test, the test run-time, state count, and path counts were recorded.

Analysis

### 2014-10-31 tex/definitions.tex
First cut

@@
 \subsection{Heap Properties}
-
-%\begin{definition}
-%A state $s = (\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k})$ is a \textbf{lazy state} if and only if $\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (|\cfgnt{L}(\cfgnt{r})| = 1)$]
-%\end{definition}
-%
-%\begin{definition}
-%A state $s = (\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k})$ is a \textbf{summary state} if and only if 
-%$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (|\cfgnt{L}(\cfgnt{r})| \ge 1)$.
-%A lazy state is also a summary state by definition.
-%\end{definition}
 
@@
 
-%\begin{definition}
-%A \textbf{state sequence} is a sequence of states denoted as $\Pi_n = s_0,s_1,...,s_n$.
-A \textbf{feasible state sequence}, $\Pi_n^\phi = s_0,s_1,...,s_n$ is consistent with the transition: $\forall i\ (0 \leq i < n \Rightarrow s_i \rightarrow_{\Phi} s_{i+1})$, where $s_0\in \mathcal{S}_0$.
-%\end{definition}
-%
-%%For 
-%\begin{comment}
-%\begin{definition}
-%A \textbf{feasible state sequence} is defined as a sequence of states resulting from repeated application of the state transition relation to some initial state $s_0\in \mathcal{S}_0$: $$\Pi_n = s_0,s_1,...,s_n$$ where the relation $s_i \rightarrow_{\Phi} s_{i+1}$ holds for all $i \in \{ i | 0 \leq i < n \}$
-%\end{definition}
-%\end{comment}
-
-%For these definitions, we should bring in the notion of 
-%\begin{definition}
-%The set of \textbf{lazy states} $\mathcal{S}_\ell$ is defined as
-%\begin{align}
-%\mathcal{S}_\ell = \{s_n \mid \exists \Pi_n^\ell\ (\Pi_n^\ell = s_0, \ldots, s_n)\}
-%\end{align}
-%\end{definition}
-%
-%\begin{definition}
-%The set of \textbf{summary states} $\mathcal{S}_s$ is defined as
-%\begin{align}
-%\mathcal{S}_s = \{s_n \mid \exists \Pi_n^s\ (\Pi_n^s = s_0, \ldots, s_n)\}
-%\end{align}
-%\end{definition}
-
 At times, it is useful to classify states in terms of patterns that the state strings match.
@@
 \begin{definition}
-The sets $\mathcal{FA}$, $\mathcal{FW}$, $\mathcal{RC}$, and  $\mathcal{NW}$ are defined as the sets of states having the forms $ \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$,  $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$, $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$, and $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \lp \cfgt{new}\ \cfgnt{C}\rp \ \cfgnt{k}\rp$ respectively.
+The universe of reachable states is $S$. The universe is further partitioned into states that activate different rules.
+\begin{itemize}
+\item Field Access, $S_\mathit{FA} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}\ (\cfgnt{e} = \cfgnt{r}) \wedge \exists \cfgnt{f},\cfgnt{k}_0\ (\cfgnt{k} = \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}_0\rp) \}$
+\item Field Write,  $S_\mathit{FW} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}\ (\cfgnt{e} = \cfgnt{r}) \wedge \exists \cfgnt{x},\cfgnt{f},\cfgnt{k}_0\ (\cfgnt{k} = \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}_0\rp) \}$
+\item Equals, $S_\mathit{EQ} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}_0 (\cfgnt{e} = \cfgnt{r}_0) \wedge \exists r_1, k_1(\cfgnt{k} = \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}_1\rp \}$
+\item New, $S_\mathit{N} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{C}\ (\cfgnt{e} = \lp \cfgt{new}\ \cfgnt{C}\rp) \}$
+\end{itemize} 
 \end{definition}
-
-%\begin{definition}
-%\label{def:interstate}
-%\textbf{Intermediate states} are imaginary placeholder states used when reasoning about complex transition rules in terms of simpler sub-rules.
-For example, the transition $s_x \rightarrow_\phi s_y$ may be equivalent to a sequence of simpler transitions $s_x \rightarrow_\alpha s_a \rightarrow_\beta s_b \rightarrow_\gamma s_y$.
-When reasoning about this equivalent transition sequence, it can be useful to discuss the notional intermediate states $s_a$ and $s_b$.
-However, it is important to remember that $s_a$ and $s_b$ are not technically involved in the transition $s_x \rightarrow_\phi s_y$, and indeed may not be part of any feasible state sequence under transition relation $\rightarrow_\phi$.
-%\end{definition}
 
@@
 
-%\begin{definition}
-%A \textbf{field access descriptor} $\gamma_i$ is a tuple 
-%$$ \gamma_i = (\cfgnt{r}_i\ \phi_i\ \cfgnt{l}_i\ \cfgnt{f}_i)$$
-%\end{definition}
-%
-%\begin{definition}
-%An \textbf{access path} $\Gamma_n$ is a sequence of field access descriptors
-%$ \Gamma_n = \gamma_0,\gamma_1,...,\gamma_n $.
-%\end{definition}
-%
-%\begin{definition}
-%For a given access path $\Gamma_n$ the \textbf{access path constraint} $\mathbb{PC}(\Gamma_n)$ is defined as
-%$$\mathbb{PC}(\Gamma_n) =  \bigwedge \{\phi \mid \exists \gamma \in \Gamma_n \ (\gamma = (\cfgnt{r}\ \phi\ \cfgnt{e}\ \cfgnt{f}))\}$$  
-%\end{definition}
-%
-%\begin{definition}
-%For a given state $s= ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, a \textbf{valid access path} $\Gamma_n^s = \gamma_0,\gamma_1,...,\gamma_n$ satisfies the properties
-%\begin{align*}
-%\cfgnt{r}_0 &\in \mathit{refs}(\eta_s) \\
-%\mathbb{S}(&\phi_s \wedge \mathbb{PC}(\Gamma_n^s)) \\
-%\forall i & \in \mathbb{N}\ ( 0 \leq i < n \Leftrightarrow \gamma_i \in \Gamma_n^s\  \wedge\\
-%&\ \ \ \  \gamma_{i+1} \in \Gamma_n^s\  \wedge\\
-%&\ \ \ \  (\phi_i\ \cfgnt{l}_i)\in \cfgnt{L}_s(\cfgnt{r}_i)\ \wedge \\
-%&\ \ \ \  \cfgnt{r}_{i+1} = \cfgnt{R}_s(\cfgnt{l}_i,\cfgnt{f}_i)\ \wedge\\
-%&\ \ \ \ (\phi_{i+1}\ \cfgnt{l}_{i+1}) = \cfgnt{L}_s(\cfgnt{r}_{i+1}) )
-%\end{align*}
-%where $\gamma_i = (\cfgnt{r}_i\ \phi_i\ \cfgnt{l}_i\ \cfgnt{f}_i)$
-%\end{definition}
-
-We will later be concerned with establishing whether one state represents another state.
-We want to say that one state represents another state if equivalent paths lead out from each state.
-This path-centric notion of equivalence is known as functional equivalence.
-In establishing functional equivalence between states, it is important to determine whether the heaps within the states are themselves functionally equivalent.
-Two heaps are functionally equivalent if the same sequence of field accesses in each heap produces equivalent results.
-We define heap functional equivalence using a co-inductive definition of homomorphism over the access paths in the heaps.
+We will later be concerned with establishing whether one state
+represents another state. We want to say that one state represents
+another state if equivalent paths lead out from each state. This
+path-centric notion of equivalence is known as functional
+equivalence. In establishing functional equivalence between states, it
+is important to determine whether the heaps within the states are
+themselves functionally equivalent. Two heaps are functionally
+equivalent if the same sequence of field accesses in each heap
+produces equivalent results. We define heap functional equivalence
+using a co-inductive definition of homomorphism over the access paths
+in the heaps.
 
@@
 \label{def:homomorphism}
-A \textbf{homomorphism} $s_x \rightharpoonup_{h} s_y$, from state $s_x = ( \cfgnt{L}_x\ \cfgnt{R}_x\ \phi_x\ \eta_x\ \cfgnt{e}_x\ \cfgnt{k}_x )$ to state $s_y = ( \cfgnt{L}_y\ \cfgnt{R}_y\ \phi_y\ \eta_y\ \cfgnt{e}_y\ \cfgnt{k}_y )$, is defined as follows:
+A \textbf{homomorphism} $s_p \rightharpoonup_{h} s_q$, from state $s_p = ( \cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$ to state $s_q = ( \cfgnt{L}_q\ \cfgnt{R}_q\ \phi_q\ \eta_q\ \cfgnt{e}_q\ \cfgnt{k}_q )$, is defined as follows:
 $$
 \begin{array}{l}
- s_x \rightharpoonup_{h} s_y \Leftrightarrow \\
+ s_p \rightharpoonup_{h} s_q \Leftrightarrow \\
 \ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}( \exists \phi_\alpha\ (\exists \phi_\beta\ ( \\ 
-\ \ \ \ \ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_x(\cfgnt{R}_x (\cfgnt{l}_\beta,f )) \Rightarrow (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_y(\cfgnt{R}_y (h(\cfgnt{l}_\beta),f ))\ \\
+\ \ \ \ \ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ \\
 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  )) ) ) ) )
@@
 \begin{array}{l}
-s_x \rightharpoonup_{h} s_y \Leftrightarrow \\
+s_p \rightharpoonup_{h} s_q \Leftrightarrow \\
 \ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathit{fields}(\mathrm{type}(\cfgnt{l}_\beta))\ ( \\
-\ \ \ \ \ \ \ \ \ \ \ \ \forall (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_x(\cfgnt{R}_x (\cfgnt{l}_\beta,f ))\ ( \\
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \exists \phi_\beta\ ((\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_y(\cfgnt{R}_y (h(\cfgnt{l}_\beta),f )))))))\\
+\ \ \ \ \ \ \ \ \ \ \ \ \forall (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f ))\ ( \\
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \exists \phi_\beta\ ((\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f )))))))\\
 \end{array}
@@
 \label{def:hc}
-Given homomorphism $s_x \rightharpoonup_{h} s_y$, the \textbf{homomorphism constraint} $\mathbb{HC}(s_x \rightharpoonup_{h} s_y)$ is defined as:
+Given homomorphism $s_p \rightharpoonup_{h} s_q$, the \textbf{homomorphism constraint} $\mathbb{HC}(s_p \rightharpoonup_{h} s_q)$ is defined as:
 \begin{align*}
-\mathbb{HC}(s_x \rightharpoonup_{h} s_y) &= \\
- \bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_x^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_y^\rightarrow)\} 
+\mathbb{HC}(s_p \rightharpoonup_{h} s_q) &= \\
+ \bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_p^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_q^\rightarrow)\} 
 \end{align*}
@@
 \label{representation}
-The \textbf{representation relation} $\sqsubset$ is defined as follows: given state $s_y = ( \cfgnt{L}_y\ \cfgnt{R}_y\ \phi_y\ \eta_y\ \cfgnt{e}_y\ \cfgnt{k}_y )$ and state $s_x = ( \cfgnt{L}_x\ \cfgnt{R}_x\ \phi_x\ \eta_x\ \cfgnt{e}_x\ \cfgnt{k}_x )$, $s_y \sqsubset s_x $ if and only if $\eta_y = \eta_x ,\ \cfgnt{e}_y = \cfgnt{e}_x ,\ \cfgnt{k}_y = \cfgnt{k}_x$, and there exists a homomorphism $\ s_y \rightharpoonup_{h} s_x $ such that
+The \textbf{representation relation} $\sqsubset$ is defined as follows: given state $s_p = ( \cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$ and state $s_q = ( \cfgnt{L}_q\ \cfgnt{R}_q\ \phi_q\ \eta_q\ \cfgnt{e}_q\ \cfgnt{k}_q )$, $s_p \sqsubset s_q $ if and only if $\eta_p = \eta_q ,\ \cfgnt{e}_p = \cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, and there exists a homomorphism $\ s_p \rightharpoonup_{h} s_q $ such that
 \begin{equation}
 \label{eqn:valid}
- \mathbb{S}( \phi_x \wedge \mathbb{HC}(s_y \rightharpoonup_{h} s_x) ) 
+ \mathbb{S}( \phi_q \wedge \mathbb{HC}(s_p \rightharpoonup_{h} s_q) ) 
 \end{equation}
@@
 \label{bisimulation}
-A state relation $\mathcal{R}$ is a \textbf{bisimulation} if and only if for every state $s_x$ and $s_y$ such that $s_x\ \mathcal{R}\ s_y$, the following two properties hold: 
+The functional associated to bisimulation,  $F_\sim(\sqsubset)$, is the set of all pairs of states
+$(p\ q)$ such that
 \begin{equation}
 \label{eqn:BisimulationForwards}
-\forall s_x^\prime ( s_x \rightarrow_x s_x^\prime \Rightarrow \exists s_y^\prime( (s_y \rightarrow_y s_y^\prime )\wedge (s_x^\prime\ \mathcal{R}\ s_y^\prime ))  )
+\forall p^\prime ( p \rgse p^\prime \Rightarrow \exists q^\prime( (q \rsym q^\prime )\wedge (p^\prime\ \sqsubset\ q^\prime ))  )
 \end{equation}
@@
 \label{eqn:BisimulationBackwards}
-\forall s_y^\prime ( s_y \rightarrow_y s_y^\prime\Rightarrow \exists s_x^\prime( (s_x \rightarrow_x s_x^\prime )\wedge (s_x^\prime\ \mathcal{R}\ s_y^\prime ))  )
+\forall q^\prime ( q \rsym q^\prime\Rightarrow \exists p^\prime( (p \rgse p^\prime )\wedge (p^\prime\ \sqsubset\ q^\prime ))  )
 \end{equation}
+The bisimularity relation is the greatest fixed point of the functional.
 \end{definition}
 
-Note that in the literature it is customary to define bisimulation in terms of a single labeled transition system, whereas for the purposes of this paper the definition of bisimulation refers to a pair of transition relations $\rightarrow_x$ and $\rightarrow_y$ defined by reduction rules.
-Since it is possible to create a union of the two rule systems $\rightarrow_x \cup \rightarrow_y$, and since none of the transitions in the reduction rules in this paper are labeled, this definition is sufficient for all of the customary properties of bisimulation to apply.
-For a more detailed treatment on the application of bisimulation to reduction rule systems see \cite{GSE:barbedbisimulation}.
-
-%\begin{definition}
-%Given a state transition function $\rightarrow_{\Phi}$, an initial state $s_0$ and a control flow sequence $\pi_n$, the \textbf{feasible state set}, $\mathbb{FS}(\rightarrow_{\Phi},s_0,\pi_n)$, is defined as
-% $$
-%\begin{array}{l}
-%\mathbb{FS}(\rightarrow_{\Phi},s_0,\pi_n) = \\
-%\ \ \ \ \ \ \{s \mid \exists \Pi_n^\Phi\ (\pi_n = \mathbb{CF}(\Pi_n^\Phi) \wedge s \sqsubset \mathit{last}(\Pi_n^\Phi))\} 
-%\end{array}
-%$$
-%where $\mathit{last}(\Pi_n^\Phi)$ returns the last state on the feasible sequence.
-%\end{definition}
-%
-%\begin{definition}
-%\label{equivalent}
-%A summary state $s_s$ is \textbf{equivalent} to a set of lazy states $P$ if and only if $s_s$ represents every state in $P$ and represents no other state: 
-%$$s_s \cong P \Leftrightarrow (\forall s_i \in \mathcal{S}\ (s_i \in P \Leftrightarrow s_i \sqsubset s_s) )$$
-%\end{definition}
-%
-%\begin{definition}
-%\label{sound}
-%A state $s_s$ is \textbf{sound} with respect to a transition relation, $\rightarrow_\phi$, initial state, $s_0$, and control flow path, $\pi_n$, if and only if 
-%$$ \forall s_\ell \in \mathcal{S}_\ell\ (s_\ell \sqsubset s_s \Rightarrow s_\ell \in \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n) ) $$
-%\end{definition}
-%
-%\begin{definition}
-%\label{complete}
-%A state $s_s$ is \textbf{complete} with respect to a transition relation, $\rightarrow_\phi$, initial state, $s_0$, and control flow path, $\pi_n$, if and only if 
-%$$ \forall s_\ell \in \mathcal{S}_\ell\ ( s_\ell \in \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)\Rightarrow s_\ell \sqsubset s_s ) $$
-%\end{definition}
-%
-%\begin{definition}
-%\label{exact}
-%A state $s$ is \textbf{exact} with respect to a transition relation, $\rightarrow_\phi$, initial state, $s_0$, and control flow path, $\pi_n$, if and only if it is both sound and complete:
-%$$ s \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$$
-%\end{definition}
+Note that in the literature it is customary to define bisimulation in
+terms of a single labeled transition system, whereas for the purposes
+of this paper the definition of bisimulation refers to a pair of
+transition relations $\rightarrow_x$ and $\rightarrow_y$ defined by
+reduction rules. Since it is possible to create a union of the two
+rule systems $\rightarrow_x \cup \rightarrow_y$, and since none of the
+transitions in the reduction rules in this paper are labeled, this
+definition is sufficient for all of the customary properties of
+bisimulation to apply. For a more detailed treatment on the
+application of bisimulation to reduction rule systems see
+\cite{GSE:barbedbisimulation}.

### 2014-10-31 tex/proofs.tex
First cut

@@
 The goal of this section is to prove that the representation relation,
-$\sqsubset$, is a bisimulation as defined in
-\eqref{eqn:BisimulationForwards} and
-\eqref{eqn:BisimulationBackwards}.  A bisimulation is a relation over pairs of states such that whenever two states, $s_\gse$ and
+$\sqsubset$, is a bisimulation.  A bisimulation is a relation over pairs of states such that whenever two states, $s_\gse$ and
 $s_\sym$, are related in the bisimulation, $s_\gse \sqsubset
@@
 
-%may take one of four forms: either the field is already initialized, or the uninitialized field is initialized to a new reference, the null reference, or an alias.
-%
-%We now show that the following four cases for $s_\gse^*$ are represented in $s_\sym^*$.
-For the following cases, let $\rightharpoonup_{h}$ be the homomorphism such that $s_\gse \rightharpoonup_{h} s_\sym$, let $\cfgnt{l}_\gse = \cfgnt{L}_\gse(\cfgnt{r})$, and let $\cfgnt{l}_\sym = h(\cfgnt{l}_\gse) $
-%
-%Case 1: Suppose $\cfgnt{R}_\gse(\cfgnt{l}_\gse) \neq \bot$.
-In this case, because $s_\gse \rightharpoonup_{h} s_\sym$, we know that $\cfgnt{R}_\sym(\cfgnt{l}_\sym) \neq \bot$.
-This means that in the Summarize rule, $\cfgnt{l}_\sym \notin \Lambda$, and therefore, $\cfgnt{R}_\sym(\cfgnt{l}_\sym) = \cfgnt{R}_{s^*}(\cfgnt{l}_\sym) $.
-By extension,
-%
-%Case 2: Suppose the field is uninitialized, and the "new" rule gets executed. We add a new location, so this case is represented.
-%
-%Case 3: Suppose the field is uninitialized, and the "null" rule gets executed. We add a link to the null location, so this case is represented.
-%
-%Case 4: Suppose the field is uninitialized, and the "alias" rule gets executed.
-We add links to all possible aliases, so this case is also represented.
-In fact, we add more links than we really need, but the extra ones are infeasible for the case in question so it's not a problem.
-%
-%%for the next case, we need to show that the constraints in the symbolic heap don't allow any infeasible heaps.
-The key to this will be in showing that the constraints are mutually exclusive and collectively exhaustive.
-Mutually exclusive constraints are required because GSE heaps only point to one place at at time.
-Collectively exhaustive constraints are required to eliminate any other possible heaps.
-We could start by explicitly enumerating the members of the product feasible set, and working from there to show that the symbolic heap is equivalent to that set.
-Or, we might do this on a case-by-case basis to show that for an arbitrary GSE state, any of it's three possible target states is in the feasible set.
-%
-%Having demonstrated each of these four cases, we now know that 
-%$$s_\gse^* \in \{\forall s_\gse^\prime | \exists s_\gse \sqsubset s_\sym (s_\gse \rightarrow_I^* s_\gse^\prime)  \} \Rightarrow  s_\gse^* \sqsubset s_\sym^*$$
-
-%Comment:
-% there is a flaw in the following argument: we claim that "every reference points to the right place at the right time" However, this statement is misleading.
-The truth is that the way we've defined representation, we can only guarantee that every reference points to the right place at some right time, not every right time like we imply here.
-The rest of the argument falls apart unless we can first prove that every reference points to the right place at every right time.
-So, instead of saying A points to B some time when condition X is true, we need to say that A points to B every time condition X is true.
-In other words, that condition X implies A points to B.
-This is easy to prove if we don't introduce new variables into the Heap Condition.
-However, in this case we certainly do introduce a new variable: it's the new reference that we put into the empty field.
-%Flawed argument:
-%We now prove the reverse case, that $s_\sym^*$ represents no infeasible states.
-We modified no references from the previous heap, and did not alter the global invariant.
-This means that every old reference points to the right place at the right time, and that no old reference points to the wrong place at the wrong time.
-Thus, if there is a problem with a reference, it must be with one of the new references we created.
-Since we have already proved that every reference points to the right place at the right time (WARNING: though the preceding statement may be true, we haven't actually proved it yet.
-See the above comment), there must be some field that points to the wrong place at the wrong time.
-Since we know that every field points to the right place at the right time, and since we know that the constraints are mutually exclusive, we know that the "wrong time" can never be at the same time as the "right time".
-Since the right time is every time due to Theorem~\ref{thm:colex}, this implies that the wrong time is no time.
-
-%okay, here is another crack at proving soundness
 We now prove the reverse case, that $s_\sym^*$ represents no infeasible states.
@@
 %we need to define how r' is arrived at for this one to work...
-\begin{lemma}[Bisumlation for $\rightarrow_{\sym|\mathit{FA}}$]
+\begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
+If two field access states are related in the represented by relation,
+then they are also related in the functional associated to bisumlation.
 \label{lem:access}
-%If there are symbolic states $s_\sym$ and $s_\sym^\prime$, control sequences $\pi_n$ and $\pi_{n+1}$, initial state $s_0$, and reference $\cfgnt{r}^\prime$ such that the following conditions hold:
-%\begin{align}
-%s_\sym &= \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp \\
-%s_\sym &\cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp \\
-%\cfgnt{r}^\prime &= \mathrm{fresh}_r\lp \rp \\
-%\pi_{n+1} &=\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp \\
-%s_\sym &\rsym s_\sym^\prime
-%\end{align}
-%%$$s_\sym = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$$ 
-%%$$s_\sym \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp$$ 
-%%$$\pi_{n+1} =\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp$$ 
-%
-%then 
-%$$s_\sym^\prime \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_{n+1} \rp$$
-If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{FA}$ and $s_\gse \sqsubset s_\sym$, then:
-\begin{equation}
-\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
-\end{equation}
-and
-\begin{equation}
-\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
-\end{equation}
+$$
+\forall p \in S_\mathit{FA}\ (\forall q \in S_\mathit{FA}\ (p \sqsubset q \Rightarrow (p\ q) \in F_\sim(\sqsubset)))
+$$
 \end{lemma}
@@
 \begin{proof}
-Begin by assuming the conditions stated in Lemma~\ref{lem:access}.
-By Lemma~\ref{lem:init}, the symbolic intermediate state is equivalent to the set of GSE intermediate states, so we may assume without loss of generality that all of the pertinent fields in $s_\sym$ are initialized.
-Take an arbitrary GSE state $s_\gse$ such that $s_\gse \sqsubset s_\sym$.
-Since $s_\sym$ is exact,  $s_\gse = \lp \cfgnt{L}_{\gse}\ \cfgnt{R}_{\gse}\ \phi_\gse\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k} \rp \rp$, and $s_\gse \in \mathbb{FS}(\rgse,s_0,\pi_n)$.
-If we apply the state transition functions to achieve states $s_\gse^\prime$ and $s_\sym^\prime$ such that $s_\gse \rgse s_\gse^\prime$ and  $s_\sym \rsym s_\sym^\prime$, we find that according to the Field Access rule:
-$$s_\gse^\prime = \lp \cfgnt{L}_{\gse} [\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}_{\gse}\ \phi_L\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
- and 
- $$ s_\sym^\prime = \lp \cfgnt{L}_{s}[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}_{s},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}_{s}\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
+Proof by contradiction: assume $p \sqsubset q \wedge (p\ q) \not\in F_\sim(\sqsubset)$.
+
+The case where neither $p$ nor $q$ have successors is trivially satisfied by
+\defref{bisimulation} since the conditions for inclusion in
+$F_\sim(\sqsubset)$ are vacuously met. That is a contradiction.
+
+Consider now the case where $p$ and $q$ have successor states. The
+statement $p \sqsubset q$ (\defref{representation}) means that $p$ and
+$q$ are only differentiated by their heaps and global constraints
+since the environment ($\eta$), expression ($e$), and continuation
+($k$) are the same in both states.
+
+Ignoring the heaps, and given that $p$ and $q$ currently have
+the same environment, expression, and continuation, all successors
+of $p$ related by \textrm{F{\footnotesize IELD}}
+\textrm{A{\footnotesize CCESS}} in $\rgse$ (\figref{fig:lazy}) have
+the same unchanged environment from $p$, $\eta$, new expression
+$r^\prime = \mathrm{stack}_\cfgnt{r}()$, and continuation $\cfgnt{k}$
+from the old continuation in $p$ having completed the field
+access. Similarly, the one successor of $q$ related by $\rsym$
+(\figref{fig:symfield}), has that same $\eta$, $r^\prime =
+\mathrm{stack}_\cfgnt{r}()$, and $\cfgnt{k}$. As such, every successor
+of $p$/$q$ has a matching successor of $q$/$p$ that agrees on the
+environment, expression, and continuation meeting the first condition
+necessary to relate the successors in $\sqsubset$.
+
+Turning now to the heaps, \textrm{F{\footnotesize IELD}}
+\textrm{A{\footnotesize CCESS}}, in $\rgse$ and $\rsym$, initializes
+uninitialized locations in the heap on reference $\cfgnt{r}$ for field
+$\cfgnt{f}$. The heaps in $p$ and $q$ are still homomorphic after
+initialization, and the heap constraint in the homomorphism is still
+valid by \lemref{lem:init}. Let
+$(\cfgnt{L}^\prime_p\ \cfgnt{R}^\prime_p) \rightharpoonup_h
+(\cfgnt{L}^\prime_q\ \cfgnt{R}^\prime_q)$ be those new heaps and
+the homomorphism after initialization on the heap in $p$ with
+$\rightarrow_I^*$ (\figref{fig:lazyInit}) and the heap in $q$ with
+$\rightarrow_S^*$ (\figref{fig:symInit}).
+
+After initialization, \textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} for $\rgse$ creates a new heap
+$(\cfgnt{L}^\prime_p [\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}^\prime_p$
+
+and for $\rsym$ it relates the state 
+$$ 
+s_\sym^\prime = \lp \cfgnt{L}_{s}[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}_{s},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}_{s}\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp 
+$$
+
+The functional in \defref{} requires and forward
+\eqref{eqn:BisimulationForwards} and backward
+\eqref{eqn:BisimulationBackwards} relationship between successor
+heaps.
+
+\eqref{eqn:BisimulationForwards}
+\eqref{eqn:BisimulationBackwards}
 
@@
 
-%for any GSE state $s_\gse$: 
-%\begin{equation}
-%\label{eqn:slimpliesslprime}
-%s_\gse \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_n) \Rightarrow s_\gse^\prime \sqsubset s_\sym^\prime
-%\end{equation}
-
-%Since there is only one possible control flow sequence $\pi_{n+1}$, this means that if $s_\gse \rgse s_\gse^\prime$, then 
-%\begin{equation}
-%\label{eqn:slimpliesslprime2}
-%s_\gse \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_n) \Leftrightarrow s_\gse^\prime\ \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1})
-%\end{equation}
-%
-%Combining Equations \ref{eqn:slimpliesslprime} and \ref{eqn:slimpliesslprime2}, we may finally conclude that $s_\sym^\prime$ is complete with respect to $\mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1})$
-%\begin{equation}
-%\label{eqn:readforwards}
-%s_\gse^\prime \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1}) \Rightarrow s_\gse^\prime \sqsubset s_\sym^\prime
-%\end{equation}
-
-%Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_\sym^\prime$, but $s_i^\prime \notin \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1})$.
-Since $s_i^\prime \sqsubset s_\sym^\prime$, then by Lemma~\ref{lem:ref}, $\cfgnt{r}^\prime$ represents a valid path $\Gamma_{n+1}^{s\prime}$, in states $s_i^\prime$ and $s_\sym^\prime$.
-Furthermore, by Lemma~\ref{lem:path} we can surmise that $\mathbb{S}(\phi_\sym^\prime \wedge \mathbb{PC}(\Gamma_{n+1}^{s\prime}))$.
-By construction, $\Gamma_{n+1}^{s\prime}$ is an extension of the valid access path $\Gamma_{n}^{s}$ represented by reference $\cfgnt{r}$ in state $s_\sym$.
-Since $s_\sym$ is exact, there exists state $s_i$ such that $s_i \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n})$.
-and by our previous result, $s_i^\prime \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1})$.
-We have a contradiction.
-
 Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_\sym^\prime$.
@@
  This concludes the proof.
-
-%Since $s_\sym$ is exact, $s_i \in\mathbb{FS}(\rightarrow_{\gse},s_0,\pi_n)$.
-Combining this with the fact that $s_i \rgse s_i^\prime$, we conclude that $s_i^\prime \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1})$.
-We have a contradiction.
-%
-% Therefore, $s_\sym^\prime$ is sound with respect to $\mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1})$:
-% \begin{equation}
-% \label{eqn:readbackwards}
-% s_i^\prime \sqsubset s_\sym^\prime \Rightarrow s_i^\prime \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1})
-% \end{equation}
-%Since $s_\sym$ is both sound and complete, we may combine Equations \ref{eqn:readforwards} and \ref{eqn:readbackwards} to find that 
-%$$s_\gse^\prime \in \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_{n+1}) \Leftrightarrow s_\gse^\prime \sqsubset s_\sym^\prime$$
-%By Definition~\ref{equivalent}, $s_\sym^\prime \cong \mathbb{FS}(\rightarrow_{\gse},s_0,\pi_n)$, and so by Definition~\ref{exact}, $s_\sym^\prime$ is exact.
-
-%Case 2: If there are uninitialized fields, then the GSE initialization machine will make an intermediate state $s_t$.
-By Lemma~\ref{lem:init}, the symbolic intermediate state is equivalent to the set of GSE intermediate states.
-Since the symbolic intermediate state From the intermediate state, the proof is the same as for case 1.
 \end{proof}
@@
 \label{lem:write}
-%If $s_\sym \cong \mathbb{FS}(\rgse, s_0, \pi_n )$ for some symbolic state $s_\sym$, initial state $s_0$, and control flow path $\pi_n$, and if $s_\sym =  \lp \cfgnt{L}_\sym\ \cfgnt{R}_\sym\ \phi_\sym\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$, and if $s_\sym \rsym s_\sym^\prime$ for some state $s_\sym^\prime$, then:
-%$$s_\gse^\prime \sqsubset s_\sym^\prime \Leftrightarrow s_\gse^\prime \in \mathbb{FS}(\rgse, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) ) $$
 If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{FW}$ and $s_\gse \sqsubset s_\sym$, then:
@@
 
-%proof for reference compares. Here we will rely on the fact that since the L and R functions don't change, and since the phi function
 \begin{lemma}[Exactness of Reference Compare Rule]
 \label{lem:compare}
-%If symbolic state $s_\sym =  \lp \cfgnt{L}_\sym\ \cfgnt{R}_\sym\ \phi_\sym\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, and if $s_\sym \rsym s_\sym^\prime$ for some state $s_\sym^\prime$, then $s_\sym^\prime$ is equal to $ \lp \cfgnt{L}_\sym\ \cfgnt{R}_\sym\ \phi_{s^\prime}\ \eta\ \cfgnt{v}_{s^\prime}\ \cfgnt{k}\rp$ and is exact with respect to $s_0$ and $\pi_n \ (\eta\ \cfgnt{v}_{s^\prime}\ \cfgnt{k})$.
 If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{RC}$ and $s_\gse \sqsubset s_\sym$, then:
@@
 
-%\begin{theorem}[Exactness of Summary Machine States]
-%If $\Pi_n^s$ is a feasible summary state sequence, then the final state in $\Pi_n^s$ is equivalent to the feasible set of GSE states sharing the same control flow sequence:
-%\begin{equation}
-%\mathit{last}(\Pi_n^s) \cong \mathbb{FS}(\rgse, \mathit{first}(\Pi_n^s), \mathbb{CF}(\Pi_n^s) )
-%\end{equation}
-%\end{theorem}
-%\begin{proof}
-%The proof will proceed inductively.
-%
-%Base case: For any initial state $s_0$, the feasible state set contains a single element, $\{s_0\}$:
-%$$\mathbb{FS}(\rgse, (s_0), \mathbb{CF}(s_0)) = \{s_0\}$$
-%We can define a homomorphism from $s_0$ to $s_0$ using the identity function: 
-%$$\forall a \in \cfgnt{L}_0^\rightarrow ( h(a) = a )$$ 
-%Because the only constraints in the heap are $\mathit{true}$, the heap constraint evaluates to $\mathit{true}$.
-Since $phi_0$ also evaluates to $\mathit{true}$, the expression $\mathbb{S}(\phi_0 \wedge \mathbb{HC}(s_0 \rightarrow_h s_0 ) ) $ must evaluate to true.
-Thus, any state in the feasible set must be represented by $s_0$: :
-%$$s_0 \in \mathbb{FS}(\rgse,s_0, (\eta_0\ e_0\ k_0) ) \Rightarrow s_0 \sqsubset s_0$$
-%Furthermore, since every reference points to a single place, there is only one possible represented heap. Thus:
-%$$ \{s_0\} = \mathbb{FS}(\rgse,s_0, (\eta_0\ e_0\ k_0) )$$
-%Since $s_0$ is the only represented heap, and since we know $s_0$ is in the feasible set, 
-%$$s_0 \sqsubset s_0 \Leftrightarrow s_0 \in \{s_0\}$$
-%We have now shown that $s_0 \cong \mathbb{FS}(\rgse, (s_0), \mathbb{CF}(s_0))$ for an arbitrary initial state $s_0$.
-Since every feasible state sequence starts with an initial state, we now know that:
-% $$\mathit{last}(\Pi_1^s) \cong \mathbb{FS}(\rgse, \mathit{first}(\Pi_1^s), \mathbb{CF}(\Pi_1^s) ) $$
-%
-%Inductive step: If summary state $s_\sym$ is exact, then any state $s_\sym^\prime$ such that $s_\sym \rsym s_\sym^\prime$ is also exact.
-Suppose $s_\sym$ has the form for a field read, field write, or reference compare rule.
-By Lemmas \ref{lem:access}, \ref{lem:write}, and \ref{lem:compare}, $s_\sym^\prime$ will also be exact.
-%Suppose $s_\sym$ is accepted by the "new" rule.
-In this case, the new reference points to the new location on condition true, so it's obvious that $s_\sym$ represents all of the proper GSE states, and the existence of any infeasible GSE states represented by $s_\sym^\prime$ would imply that $s_\sym$ is not exact.
-%For all the other rules, the L and R functions and $\phi$ are unchanged, and the rules for  $\eta$, $e$, and $k$ are exactly the same between the GSE and summary machines, so there is a bijective mapping between the represented states in $s_\sym$ and $s_\sym^\prime$.
-%Thus, in all cases, if $s_\sym$ is exact, then $s_\sym^\prime$ is also exact.
-%
-%We have now shown that any feasible state sequence $\Pi_n^s$ is exact if the sub-sequence $\Pi_{n-1}^s$ is exact.
-%
-%Combining the result from the inductive step with the result from the base case, we can now say with certainty that for all $n$,
-%
-%$$\mathit{last}(\Pi_n^s) \cong \mathbb{FS}(\rgse, \mathit{first}(\Pi_n^s), \mathbb{CF}(\Pi_n^s) ) $$
-%
-%\end{proof}
-
 \begin{theorem}
@@
 \end{corollary}
-
-%\begin{corollary}
-%For any given initial state, the set of solutions to the constraints in the final symbolic states provides an optimal set of concrete test inputs.
-There is no smaller set that will exercise every possible control flow sequence.
-%\end{corollary}
-
-%proof: the global invariant is a constraint equation over the initial heap.
-That is to say, when you solve it, it assigns an integer to every variable.
-Those variables are references.
-Thus, solving the constraint equation gives you the location that each reference in the initial heap pointed to.
-%problem: Where the references pointed is only half of the problem.
-We also need to know which references were stored in which fields of which locations at the beginning of the program.
-This would not be hard to do - if we kept track of the initial heap as we created it, separate from the active heap, it should work - however, this is unimplemented

### 2014-11-06 tex/results.tex
Did some minor clean-up with the results section.
Added table with performance numbers.

@@
 
-Hypothesis
+Since the number of paths in GSE is exponential in the number of lazy initializations, it is expected that programs for which the number of lazy initializations is proportional to program complexity will evaluate more quickly using GSESH.
+On the other hand, since GSESH places a greater burden on the constraint solver, it is expected that programs where the lazy initialization count is constant or slowly increasing with respect to program complexity will evaluate more quickly using GSESH.
 
-\subsection{Implementation}
+\subsection{JPF Implementation}
+The Java Pathfinder (JPF) symbolic execution engine contains an implementation of GSE, which we extended with our own implementation of GSESH.
 
@@
 \subsection{Evaluation} 
-Experimental set-up
+Experimental set-up: TO BE ADDED
 
@@
 
-Analysis
+The results of the experiments are shown in table \ref{tab:results}.
+
+\begin{table} [h]
+  \centering
+  \begin{tabular}{| c | c | c | c | c | c | c | c |}
+  \hline
+   \multirow{2}{*}{Method }&\multirow{2}{*}{ $k$ }
+   &\multicolumn{2}{|c|}{Time} &\multicolumn{2}{|c|}{ Paths }\\
+								&	&GSE	&SH	&GSE & SH\\
+   \hline
+    \multirow{3}{*}{LinkedList }&3	& 1 & 1  &1656 & 25		 \\
+   		 				& 4	& 3 & 2	&17485  & 39 \\
+   						& 5	& 20 & 3	&232743 & 56\\
+						& 6	& 338 & 8		&3731094 & 76\\
+    \hline
+    \multirow{3}{*}{BinarySearchTree }&1	& 0 & 1	& 4	 & 4\\
+   		 				& 2	& 1 & 1 	& 26 & 17\\
+   						& 3	& 12 & 7	& 305 & 118\\
+    \hline
+      \multirow{3}{*}{TreeMap}&1	& 0 & 1 	&9 & 9 \\
+   		 				&2	& 1 & 3		& 100 & 46 \\
+   						&3	&21 & 206	& 3026 & 547 \\
+
+    \hline
+  \end{tabular}
+  \caption{test results}
+  \label{tab:results}
+\end{table}
+
+\subsection{Analysis}
+
+LinkedList
+As expected, the repeated use of lazy initialization throughout the program causes an exponential increase in the number of paths explored by GSE.
+By combining many of the GSE paths, SH avoids the exponential path explosion, demonstrating dramatically reduced, though still exponential, execution time growth.
+Remarkably, path growth in the k-bound appears to be sub-linear.
+
+BST
+The BinarySearchTree example is somewhat of a mixed bag.
+
+TreeMap

### 2014-11-06 tex/proofs.tex

@@
 
-After initialization, \textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} for $\rgse$ creates a new heap
-$(\cfgnt{L}^\prime_p [\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}^\prime_p$
+After initialization, \textrm{F{\footnotesize IELD}}
+\textrm{A{\footnotesize CCESS}} for $\rgse$ relates a new heap in any
+successor state as $(\cfgnt{L}^\prime_p [\cfgnt{r}^\prime \mapsto
+  \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}^\prime_p)$, and for $\rsym$ it
+relates the heap in the only successor state as $(\cfgnt{L}^\prime_q[\cfgnt{r}^\prime \mapsto
+  \mathbb{VS}\lp
+  \cfgnt{L}^\prime_q,\cfgnt{R}^\prime_q,\cfgnt{r},\cfgnt{f},\phi_g\rp
+]\ \cfgnt{R}^\prime_q)$; each version adding in the constraint-location pair or
+value set respectively on the same reference $\cfgnt{r}^\prime$.
 
-and for $\rsym$ it relates the state 
-$$ 
-s_\sym^\prime = \lp \cfgnt{L}_{s}[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}_{s},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}_{s}\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp 
-$$
-
-The functional in \defref{} requires and forward
+The functional in \defref{bisimulation} requires and forward
 \eqref{eqn:BisimulationForwards} and backward

### 2014-11-06 tex/definitions.tex
Fixed Field Access to only halt when NULL is the only choice

@@
 \label{def:hc}
-Given homomorphism $s_p \rightharpoonup_{h} s_q$, the \textbf{homomorphism constraint} $\mathbb{HC}(s_p \rightharpoonup_{h} s_q)$ is defined as:
+Given the homomorphism $(\cfgnt{L}_p\ \cfgnt{R}_p) \rightharpoonup_{h} (\cfgnt{L}_q\ \cfgnt{R}_q)$, the \textbf{homomorphism constraint} $\mathbb{HC}((\cfgnt{L}_p\ \cfgnt{R}_p) \rightharpoonup_{h} (\cfgnt{L}_q\ \cfgnt{R}_q))$ is defined as:
 \begin{align*}
-\mathbb{HC}(s_p \rightharpoonup_{h} s_q) &= \\
+\mathbb{HC}((\cfgnt{L}_p\ \cfgnt{R}_p) \rightharpoonup_{h} (\cfgnt{L}_q\ \cfgnt{R}_q)) &= \\
  \bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_p^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_q^\rightarrow)\} 
@@
 \label{representation}
-The \textbf{representation relation} $\sqsubset$ is defined as follows: given state $s_p = ( \cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$ and state $s_q = ( \cfgnt{L}_q\ \cfgnt{R}_q\ \phi_q\ \eta_q\ \cfgnt{e}_q\ \cfgnt{k}_q )$, $s_p \sqsubset s_q $ if and only if $\eta_p = \eta_q ,\ \cfgnt{e}_p = \cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, and there exists a homomorphism $\ s_p \rightharpoonup_{h} s_q $ such that
+The \textbf{representation relation} $\sqsubset$ is defined as
+follows: given state $s_p = (
+\cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$
+and state $s_q = (
+\cfgnt{L}_q\ \cfgnt{R}_q\ \phi_q\ \eta_q\ \cfgnt{e}_q\ \cfgnt{k}_q )$,
+$s_p \sqsubset s_q $ if and only if $\eta_p = \eta_q ,\ \cfgnt{e}_p =
+\cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, and there exists a
+homomorphism $(\cfgnt{L}_p\ \cfgnt{R}_p) \rightharpoonup_{h}
+(\cfgnt{L}_q\ \cfgnt{R}_q)$ such that
 \begin{equation}
@@
 \end{equation}
+The represented relation is extended to sets of states $P$ and $Q$ as
+$$
+P \sqsubset Q \Longleftrightarrow \forall q \in Q\ (\forall p \in S\ (p \sqsubset q \Rightarrow p \in P))
+$$
+\end{definition}
+
+\begin{definition}
+A state relation $p \rightarrow_x q$ is extended to sets of states $P \hookrightarrow_x Q$ as
+$$
+P \hookrightarrow_x Q \Longleftrightarrow \forall q \in S\ (p \rightarrow_x q \Rightarrow q \in Q)
+$$
+The $\rgse$ relations over sets of states is The $\rsym$ relation extended to sets of states
 \end{definition}
@@
 \label{bisimulation}
-The functional associated to bisimulation,  $F_\sim(\sqsubset)$, is the set of all pairs of states
-$(p\ q)$ such that
+The functional associated to bisimulation,  $F_\sim(\sqsubset)$, is the set of all pairs of sets of states
+$(P\ Q)$ such that
 \begin{equation}
 \label{eqn:BisimulationForwards}
-\forall p^\prime ( p \rgse p^\prime \Rightarrow \exists q^\prime( (q \rsym q^\prime )\wedge (p^\prime\ \sqsubset\ q^\prime ))  )
+\forall p \in P\ (\forall p^\prime\ ( p \rgse p^\prime \Rightarrow \exists q^\prime\ ( (q \rsym q^\prime )\wedge (p^\prime\ \sqsubset\ q^\prime ))))
 \end{equation}
@@
 \label{eqn:BisimulationBackwards}
-\forall q^\prime ( q \rsym q^\prime\Rightarrow \exists p^\prime( (p \rgse p^\prime )\wedge (p^\prime\ \sqsubset\ q^\prime ))  )
+\forall q \in Q\ (\forall q^\prime\ ( q \rsym q^\prime\Rightarrow \exists p^\prime\ ( (p \rgse p^\prime )\wedge (p^\prime\ \sqsubset\ q^\prime ))))
 \end{equation}

### 2014-11-06 tex/lazy.tex
adding some figures for the rules
remove noisy files and more info of sets on teh examples
adding figures for GSE
writing about the figures

@@
-\section{Initialization of Symbolic References}
+\section{Generating Heap Summaries}
 
-In this section we present the Javalite rewrite rules for the concrete
-as well as summary initialization of symbolic references. The
-initialization rules are defined on the bi-partite graph consisting of
-references and locations. The lazy initialization of symbolic
-references consists of three key points of non-determinism where each
-symbolic reference can be initialized non-deterministically to null, a
-new instance of the symbolic reference, or aliases to symbolic
-references of the same type previously initialized. The initialization
-in GSE consists of creating branches in the execution tree for all the
-non-deterministic choices. On the other hand, the heap summarization
-approach creates a single branch that contains the summarization for
-all the initialization in a single bi-partitate graph.
+\subsection{Initialization of Symbolic References}
 
-\input{initialize-lazy}
+In this section we present the Javalite rewrite rules for the summary
+initialization of symbolic references. The initialization rules are
+defined on the bi-partite graph consisting of references and
+locations. Recall that in generalized symbolic execution (GSE) for
+lazy initialization of symbolic references consists of three key
+points of non-determinism where each symbolic reference can be
+initialized non-deterministically to null, a new instance of the
+symbolic reference, or aliases to symbolic references of the same type
+previously initialized. The initialization in GSE consists of creating
+branches in the execution tree for all the non-deterministic
+choices. In contrast, the heap summarization approach creates a
+single branch that contains the summarization for all the
+initialization in a single bi-partitate graph.
+
 \input{summarize-precise}
@@
 point to the field $\cfgnt{f}$ and $\cfgnt{f}$ points to
-$\cfgnt{l}_\mathit{un}$. The cardinality of the set, $\theta$ is never
-greater than one in GSE and the constraint is always satisfiable
-because all constraints are constant. This property is relaxed in GSE
-with heap summaries.
+$\cfgnt{l}_\mathit{un}$.
 
-The rules in~\figref{fig:lazyInit} present the rewrite rules for the
-concrete initialization of symbolic heap objects.  These rules are
-invoked until a fix pointed is reached.
+% The cardinality of the set, $\theta$ is never
+%greater than one in GSE and the constraint is always satisfiable
+%because all constraints are constant. This property is relaxed in GSE
+%with heap summaries.
 
-The initialize (null) rewrite rule in~\figref{fig:lazyInit} first
-checks that the field, $\cfgnt{r}$ is uninitialized. The fresh method
-returns a new input heap reference from the partition
+The rewrite rule to initialize a heap in the symbolic summarization
+technique is shown in~\figref{fig:initHeap}. The set $\mathbb{UN}$
 
-\section{Accessing and Writing to Field References}
+ There are three
+constraint-location pair sets $\theta_\mathit{null}$,
+$\theta_\mathit{new}$, and $\theta_\mathit{alias}$ that correspond to
+the non-deterministic choices in GSE. The $\theta_\mathit{null}$ creates
+a constraint location pair where the constraint under which the field is read $\phi_x$ $l_\mathit{null}$
 
-\section{Equality and InEquality of References}
+\begin{figure*}[t]
+\begin{center}
+\begin{tabular}[c]{c|c|c|c}
+\begin{tabular}[c]{c}
+\scalebox{0.81}{\input{origHeap.pdf_t}} \\
+\end{tabular} &
+\begin{tabular}[c]{c}
+\scalebox{0.81}{\input{summarizeXHeap.pdf_t}} \\
+\end{tabular} &
+\begin{tabular}[c]{c}
+\scalebox{0.81}{\input{summarizeYHeap.pdf_t}} \\
+\end{tabular} &
+\begin{tabular}[c]{l}
+$\rho := \{ (r_1^i, r_1^i \neq r_\mathit{null}, l_1 \}$ \\
+$\theta_\mathit{null} := \{ ( r_2^i = r_\mathit{null}, l_\mathit{null}) \}$\\
+$\theta_\mathit{new} := \{ ( r_2^i \neq r_\mathit{null} \wedge r_2^i \neq r_1^i, l_2) \}$\\
+$\theta_\mathit{alias} := \{ ( r_1^i \neq r_\mathit{null} \wedge r_2^i \neq r_\mathit{null} \wedge r_2^i = r_1^i, l_1) \}$\\
+$\theta_\mathit{orig} := \{ \}$ \\
+$\phi_{\mathit{1a}} := r_1^i = r_\mathit{null} $ \\
+$\phi_{\mathit{1b}} := r_1^i \neq r_\mathit{null} $  \\
+$\phi_{\mathit{2a}} := r_2^i = r_\mathit{null}$ \\
+$\phi_{\mathit{2b}} := r_2^i \neq r_\mathit{null} \wedge r_2^i \neq r_1^i$ \\
+$\phi_{\mathit{2c}} :=  r_2^i \neq r_\mathit{null} \wedge r_2^i = r_1^i $ \\
+\end{tabular} \\
+(a) & (b) & (c) & (d) \\
+\end{tabular}
+\end{center}
+\caption{initialize this.x and this.y}
+\label{fig:initHeap}
+\end{figure*}
 
-\input{lazy-fig}
+We visualize the initialization process in the symbolic summarization
+technique in~\figref{fig:initHeap}. The heap
+in~\figref{fig:initHeap}(a) represents the initial heap. The
+references with the superscript $s$ indicates that it is a local
+reference. In~\figref{fig:initHeap} $r_0^s$ represents the reference
+for the $\mathit{this}$ instance which has two fields $x$ and $y$ of
+the same type. The reference $r_0^s$ points to the location
+$l_0$. Note that when no constraint is specified, then there is a
+implicit $\mathit{true}$ constraint. In~\figref{fig:initHeap} $r_0^s$
+points to $l_0$ on $\mathit{true}$. The fields $x$ and $y$ point to
+the uninitialized reference $r_\mathit{un}$. The reference
+$r_\mathit{un}$ points to the uninitialized location $l_\mathit{un}$
+on the $\mathit{true}$ constraint.
+
+The graph in~\figref{fig:initHeap}(b) represents the summary heap
+after the initialization of the $\mathit{this}.x$ field while the
+graph in~\figref{fig:initHeap}(c) represents the summary heap after
+the initialization of the $\mathit{this}.y$ field following the
+initialization of $\mathit{this}.x$. The list
+in~\figref{fig:initHeap}(d) represents the various sets constructed in
+the rewrite system when the initialization takes places. We also
+define the constraints of references to their corresponding labels in
+the graph.
+
+The access on $l_0.x$ creates a new input reference $r_1^i$ in the
+summary heap shown in~\figref{fig:initHeap}(b). The reference $r_1^1$
+points to the $l_\mathit{null}$ location under the constraint that
+$r_1^i$ is null: $\phi_{1a} := r_1^i = r_\mathit{null}$. The reference
+$r_1^i$ points to the location $l_1$ under the constraint that $r_1^i$
+is not null $\phi_{1b} :=r_1^i \neq r_\mathit{null}$. The location
+$l_1$ represents a fresh location of type $C$ is created on the heap
+such that $C$ is type of $\mathit{this}.x$.

### 2014-11-07 tex/lazy.tex
writing the initialization

@@
 The rewrite rule to initialize a heap in the symbolic summarization
-technique is shown in~\figref{fig:initHeap}. The set $\mathbb{UN}$
+technique is shown in~\figref{fig:symInit}. Given the unitialized set
+$\mathbb{UN}$ for field $f$, the $\mathit{min}_l$ function returns the
+constraint location pair based on a lexical ordering of locations. The
+init$_r$ method returns a new input reference $r_f$ while the
+fresh$_f$ returns a new location of type $C$. The set $\rho$ contains
+the set of reference location, $(r_a, l_a)$, pairs that the current
+field may alias. The pair $(r_a, l_a)$ is contained in the set $ \rho
+$ if $r_a$ is part of the input references initialized in the summary
+heap, $r_a$ is in the pre-image of $l_a$, and the type of $l_a$ is the
+same as the type of the field being initialized then the pair $(r_a,
+l_a)$ is added to the $\rho$ set.
 
- There are three
-constraint-location pair sets $\theta_\mathit{null}$,
-$\theta_\mathit{new}$, and $\theta_\mathit{alias}$ that correspond to
-the non-deterministic choices in GSE. The $\theta_\mathit{null}$ creates
-a constraint location pair where the constraint under which the field is read $\phi_x$ $l_\mathit{null}$
+There are three constraint-location pair sets that correspond to
+non-deterministic choices in GSE: (a) $\theta_\mathit{null}$ that
+creates a constraint that states $r_f$ is null under which it points
+to $l_\mathit{null}$, (b) $\theta_\mathit{new}$ the constraint that
+$r_f$ is not null and it does not alias another reference in set
+$\rho$ under which it points to the newly created location $l_f$, (c)
+and $\theta_\mathit{alias}$ where for each element in the set $(r_a,
+l_a) \in \rho$ it creates a constraints that $r_f$ is not null, points
+to $r_a$, and does not point to any reference contained in
+$(r_a^\prime, l_a^\prime) \in \rho$ such that $r_a \neq
+r_a^\prime$. Additionally $\theta_\mathit{orig}$ allows for the
+possibility that the field continues to remain uninitialized since the
+heap is symbolic. We refer to this initialization in the summary
+machine as conditional initialization. Finally, the fields of the
+reference $r_f$ are marked as uninitialized.
+
+In the post condition of the rule the reference $r_f$ points to
+$\theta$ which contains the union of all the constraint location pairs
+sets, and the field $f$ points to the new reference $r_f$ in the
+summary heap.  Note that the summarize rule invoked repeatedly until
+the set of unitialized constraint location pairs for field $f$ is
+empty. In other words the set $\lambda$ is empty. This consititutes
+the summarize end rule in~\figref{fig:symInit}.
 
@@
 $r_1^i$ points to the location $l_1$ under the constraint that $r_1^i$
-is not null $\phi_{1b} :=r_1^i \neq r_\mathit{null}$. The location
-$l_1$ represents a fresh location of type $C$ is created on the heap
-such that $C$ is type of $\mathit{this}.x$.
+is not $\mathit{null}$ $\phi_{1b} :=r_1^i \neq r_\mathit{null}$. The
+location $l_1$ represents a fresh location of type $C$ is created on
+the heap such that $C$ is type of $\mathit{this}.x$.
+
+Following the initialization to the $\mathit{this}.x$, when we
+initialize $\mathit{this}.y$ the resulting summary heap is shown
+in~\figref{fig:initHeap}(c). The set $\rho$ shown
+in~\figref{fig:initHeap}(d) contains the potential aliases for
+$\mathit{this}.y$ which is location $l_1$ ($\mathit{this}.x$). The
+constraint location $\theta$ sets represents the initialization
+choices for $\mathit{this}.y$. The new input reference $r_2^i$ for
+$this.y$ points to (a) location $l_\mathit{null}$ under the constraint
+$\phi_{2a} := r_2^i = r_\mathit{null}$, (b) location $l_2$ under the
+constraint $\phi_{2b} := r_2^i \neq r_\mathit{null} \wedge r_2^i \neq
+r_1^i$ that states that $r_2^i$ is not null and does not alias
+$r_1^i$, and (c) location $l_1$ under the constraint $\phi_{2c} :=
+r_2^i \neq r_\mathit{null} \wedge r_2^i = r_1^i$ that states $r_2^i$
+is not null and \emph{does} alias $r_1^i$.

### 2014-11-07 tex/definitions.tex

@@
 \begin{definition}
+\label{def:meta}
 A state relation $p \rightarrow_x q$ is extended to sets of states $P \hookrightarrow_x Q$ as
@@
 $$
-The $\rgse$ relations over sets of states is The $\rsym$ relation extended to sets of states
+The $\rgse$ relation over sets of states is $\rsgse = \hookrightarrow_\ell \wedge \hookrightarrow_\com$, and 
+the $\rsym$ relation extended to sets of states is 
+$$
+\rssym = \hookrightarrow_\mathit{FA} \cup \hookrightarrow_\mathit{FW} \cup \hookrightarrow_\mathit{EQ}^T \cup \hookrightarrow_\mathit{EQ}^F \cup \hookrightarrow_\com
+$$
 \end{definition}
@@
 \label{eqn:BisimulationForwards}
-\forall p \in P\ (\forall p^\prime\ ( p \rgse p^\prime \Rightarrow \exists q^\prime\ ( (q \rsym q^\prime )\wedge (p^\prime\ \sqsubset\ q^\prime ))))
+\forall P^\prime\ ( P \rsgse P^\prime \Rightarrow \exists Q^\prime\ ( (Q \rssym Q^\prime )\wedge (P^\prime\ \sqsubset\ Q^\prime )))
 \end{equation}
@@
 \label{eqn:BisimulationBackwards}
-\forall q \in Q\ (\forall q^\prime\ ( q \rsym q^\prime\Rightarrow \exists p^\prime\ ( (p \rgse p^\prime )\wedge (p^\prime\ \sqsubset\ q^\prime ))))
+\forall Q^\prime\ ( Q \rssym Q^\prime\Rightarrow \exists P^\prime\ ( (P \rsgse P^\prime )\wedge (P^\prime\ \sqsubset\ P^\prime )))
 \end{equation}

### 2014-11-07 tex/definitions.tex
Grouped Figure 8 and Figure 9

@@
 $$
-P \sqsubset Q \Longleftrightarrow \forall q \in Q\ (\forall p \in S\ (p \sqsubset q \Rightarrow p \in P))
+P \sqsubset Q \Longleftrightarrow |Q| = 1 \wedge \forall q \in Q\ (\forall p\ (p \sqsubset q \Rightarrow p \in P))
 $$
@@
 \label{def:meta}
-A state relation $p \rightarrow_x q$ is extended to sets of states $P \hookrightarrow_x Q$ as
+A state relation $p \rightarrow_x p^\prime$ is extended to sets of states $P \hookrightarrow_x P^\prime$ as
 $$
-P \hookrightarrow_x Q \Longleftrightarrow \forall q \in S\ (p \rightarrow_x q \Rightarrow q \in Q)
+P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime)
 $$
-The $\rgse$ relation over sets of states is $\rsgse = \hookrightarrow_\ell \wedge \hookrightarrow_\com$, and 
+The $\rgse$ relation over sets of states is $\rsgse = \hookrightarrow_\ell \cup \hookrightarrow_\com$, and 
 the $\rsym$ relation extended to sets of states is 
@@
 \label{eqn:BisimulationBackwards}
-\forall Q^\prime\ ( Q \rssym Q^\prime\Rightarrow \exists P^\prime\ ( (P \rsgse P^\prime )\wedge (P^\prime\ \sqsubset\ P^\prime )))
+\forall Q^\prime\ ( Q \rssym Q^\prime\Rightarrow \exists P^\prime\ ( (P \rsgse P^\prime )\wedge (P^\prime\ \sqsubset\ Q^\prime )))
 \end{equation}

### 2014-11-07 tex/proofs.tex
Grouped Figure 8 and Figure 9

@@
 \begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
-If two field access states are related in the represented by relation,
+If two sets of field access states are related in the represented by relation,
 then they are also related in the functional associated to bisumlation.

### 2014-11-08 tex/lazy.tex
adding the text for the field access

@@
 field may alias. The pair $(r_a, l_a)$ is contained in the set $ \rho
-$ if $r_a$ is part of the input references initialized in the summary
-heap, $r_a$ is in the pre-image of $l_a$, and the type of $l_a$ is the
-same as the type of the field being initialized then the pair $(r_a,
-l_a)$ is added to the $\rho$ set.
+$ if the following conditions hold: (i) $r_a$ is part of the input
+references initialized in the summary heap, (ii) $r_a$ is in the
+pre-image of $l_a$, (iii) and the type of $l_a$ is the same as the
+type of the field being initialized.
 

### 2014-11-08 tex/precise.tex
re-orging
remove noisy files and more info of sets on teh examples
reorging the figure
precise
Grouped Figure 8 and Figure 9
Grouped figures 10 and 12
adding the text for the field access

@@
-\section{GSE with Heap Summaries}
+\subsection{Accessing a Field Reference}
+
+\input{precise-fig}
+
+\begin{figure*}[t]
+\begin{center}
+\setlength{\tabcolsep}{50pt}
+\begin{tabular}[c]{cc}
+\usebox{\boxPFAFW} & 
+%\scalebox{0.91}{\input{faYHeap.pdf_t}} &
+\scalebox{0.91}{\input{fwXHeap.pdf_t}} \\ \\
+(a) & (b)
+\end{tabular}
+\end{center}
+\caption{field access for this.y and field write for this.x = this.y}
+\label{fig:fHeap}
+\end{figure*}
+
+There are two rewrite rules in~\figref{fig:fHeap}(a), one for field
+access and the other for field write. Let us consider the rewrite rule
+for field access. The first check we perform is whether there exists a
+constraint location pair for the $r$ being accessed such that the
+location is not null and the constraint when conjuncted with the
+global constraint is satisfiable. Next we extract all possible
+constraints under which $r$ points to a null location such that the
+constraint is satisfiable under the current global constraint,
+$\phi_g$. The negation of these constraints are added to the global
+constraint to create a new global constraint $\phi_g^\prime$. The
+update to the global constraint ensures that access of the field $f$
+happens only on non-null locations. The type $C$ of the field is
+extracted and passed to rewrite rule that performs the initialization
+of the symbolic heap. The initialization rules are described earlier
+in this section.
+
+Recall that during the initialization the rewrite rules
+in~\figref{fig:symHeap} add input references that map to fields being
+initialized.  Once the initialization is complete, however, we create
+a new local reference $r^\prime$. An important property of the
+references in the bi-partiate graph is that they are
+\emph{immutable}. Hence we de-reference the initialized input
+reference, assign its value to the the new local reference, and return
+the local reference. In order to de-reference a field $r.f$ we define
+a helper function which is called the value set.
 
@@
 
+In the post-condition of the rewrite rule we assign
+the value set of input reference $r$ to the local reference $r^\prime$
+and return the local reference $r^\prime$ in the next state.
+
+Consider the graph shown in~\figref{fig:fHeap}(b) the reference
+$r_2^i$ is created during the initialization of $\mathit{this}.y$. The
+reference that is returned during the access of the field, however, is
+$r_3^s$. The reference $r_3^s$ points to the value set of $r_2^i$
+which are: $(\phi_{2a}, l_\mathit{null})$, $(\phi_{2b}, l_2)$, and
+$(\phi_{2c}, l_1)$. The values of the constraints $\phi_{2a}$,
+$\phi{2b}$, and $\phi_{2c}$ are defined in~\figref{fig:initHeap}(d).
+
+\subsection{Writing to a Field}
+
 \begin{definition}
@@
 
-\input{summarize-precise}
-\input{precise-fig}
+\begin{comment}
+\begin{figure}[t]
+\begin{center}
+\begin{tabular}[c]{l}
+$\Psi_x = \{ (true, l_0, r_1^i) \}$\\
+$ST (L, r_3^s, \phi, \phi_g)$ \\
+$\theta = \{ (\phi_{2a}\; l_\mathit{null} ) (\phi_{2b}\; l_2) (\phi_{2c}\; l_1) \}$\\
+$ST(L, r_0, \phi, \phi_g)$\\
+$\theta = \{ \}$\\
+\end{tabular}
+\end{center}
+\caption{field write for this.x = this.y sets}
+\label{fig:faHeapSets}
+\end{figure}
+\end{comment}
+
+\subsection{Equality and InEquality of References}
+
+\input{precise-eq}
+
+\newsavebox{\boxPEX}
+\savebox{\boxPEX}{
+\begin{tabular}[c]{l}
+$L(r_1^i) = \{ (\phi_{1a}\; l_\mathit{null})\; (\phi_{1b}\; l_1) \}$ \\
+$L(r_2^i) = \{ (\phi_{2a}\; l_\mathit{null}),\; (\phi_{2b}\; l_2),\; (\phi_{2c}\; l_1) \} $\\
+  $\theta_0 = \{ \} $\\
+$\theta_1 = \{ \phi_{2b}\} $\\ \hline
+Equals true \\
+$\theta_\alpha = \{ (\phi_{1a}\; \wedge\; \phi_{2a} ) (\phi_{1b}\; \wedge\; \phi_{2c} ) \}$\\
+$\phi^\prime = \mathit{true} \wedge [ (\phi_{1a}\; \wedge\; \phi_{2a} )\vee (\phi_{1b}\; \wedge\; \phi_{2c} ) ] \wedge \neg\phi_{2b} $\\ \hline
+Equals false \\
+$\theta_\alpha = \{ (\phi_{1a}\; \implies\; \neg\phi_{2a} ) (\phi_{1b}\; \implies\; \neg\phi_{2c} ) \}$\\
+$\phi^\prime = \mathit{true} \wedge  (\phi_{1a}\; \implies\; \neg\phi_{2a} )\wedge (\phi_{1b}\; \implies\; \neg\phi_{2c} )  \wedge \phi_{2b} $\\ \hline
+\end{tabular}}
+
+\begin{figure*}
+\begin{tabular}[c]{cl}
+\usebox{\boxPEQ} & \usebox{\boxPEX} \\ \\
+(a) & (b) \\
+\end{tabular}
+\caption{equals true for this.x == this.y}
+\label{fig:eqs-true}
+\end{figure*}

### 2014-11-08 tex/precise.tex
adding moi changes

@@
 $(\phi_{2c}, l_1)$. The values of the constraints $\phi_{2a}$,
-$\phi{2b}$, and $\phi_{2c}$ are defined in~\figref{fig:initHeap}(d).
+$\phi_{2b}$, and $\phi_{2c}$ are defined in~\figref{fig:initHeap}(d).
 
 \subsection{Writing to a Field}
+
+The reference $r_x$ is the base pointer whose field is being written
+to while $r$ is the target reference. We look up the value of the base
+reference in the environment $\eta(x)$. The set $\Psi_x$ is the set of
+tuples of constraints, locations, and references which provide the
+reference chains leading from $r_x$ to the reference of the field,
+$r_\mathit{curr}$, being written to through $\phi$ and $l$.The goal is
+to overwrite the $r_\mathit{curr}$ references with the target
+references. Since the target of the write is $r$, we first check that the
+location constraint pairs of $L(r)$ are satisfiable when accessed
+through the $r_x$ chain. This is accomplished by the strengthing
+function.
 
@@
 \end{definition}
+
+Additionally, we also check for conditions where the write is not possible
 
@@
 \caption{equals true for this.x == this.y}
-\label{fig:eqs-true}
+\label{fig:eqs}
 \end{figure*}
+
+The rewrite rules for check the equals true and equals false when
+comparing two references in the symbolic summary heap is shown
+in~\figref{fig:eqs}(a). First the equals reference true rewrite rule
+returns true if two references $r_0$ and $r_1$ are equal. In GSE this
+is a simple comparision of object refrences. In the symbolic summary
+heap, however, there we campare sets of constraint location pairs for
+each reference. We construct three sets of constraints (i)
+$\Phi_\alpha$ constains combinations of constraints ($\phi_0 \wedge
+\phi_1$) from $r_0$ and $r_1$

### 2014-11-08 tex/precise.tex

@@
 heap, however, there we campare sets of constraint location pairs for
-each reference. We construct three sets of constraints (i)
+each reference. We construct three sets of constraints (i) In order to check whether 
+there are locations, $l$ in the heap such that under some constraints $\phi_0$ references $r_0$ and $r_1$
 $\Phi_\alpha$ constains combinations of constraints ($\phi_0 \wedge

### 2014-11-09 tex/definitions.tex
Locked math. Switch to paper

--- 2014-11-06 tex/definitions.tex
@@
 
+\begin{definition}
+A state is \textbf{well formed} if its heap is deterministic, type consistent across locations on a common reference, every reference points to a location, and only references from the stack partition are in the environment, expression, or continuation.
+\end{definition}
+
+\begin{lemma}[Successors of well-formed states]
+\label{lem:succ}
+Any well-formed state has at least one successor unless the expression is $\cfgnt{v}$ and the continuation is $\cfgt{end}$.
+\end{lemma}
+\begin{proof}
+Please write me!
+\end{proof}
+
 At times, it is useful to classify states in terms of patterns that the state strings match.
@@
 \begin{definition}
-The universe of reachable states is $S$. The universe is further partitioned into states that activate different rules.
+The universe of reachable states is $S$. The universe is further partitioned into states that activate different relations.
 \begin{itemize}
@@
 \label{def:hc}
-Given the homomorphism $(\cfgnt{L}_p\ \cfgnt{R}_p) \rightharpoonup_{h} (\cfgnt{L}_q\ \cfgnt{R}_q)$, the \textbf{homomorphism constraint} $\mathbb{HC}((\cfgnt{L}_p\ \cfgnt{R}_p) \rightharpoonup_{h} (\cfgnt{L}_q\ \cfgnt{R}_q))$ is defined as:
+Given the homomorphism $s_p \rightharpoonup_{h} s_q$, the \textbf{homomorphism constraint} $\mathbb{HC}(s_p \rightharpoonup_{h} s_q)$ is defined as:
 \begin{align*}
-\mathbb{HC}((\cfgnt{L}_p\ \cfgnt{R}_p) \rightharpoonup_{h} (\cfgnt{L}_q\ \cfgnt{R}_q)) &= \\
+\mathbb{HC}(s_p \rightharpoonup_{h} s_q) &= \\
  \bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_p^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_q^\rightarrow)\} 
 \end{align*}
+Where $\cfgnt{L}_p$ and $\cfgnt{L}_q$ are the locations maps from the heaps in $s_p$ and $s_q$.
 \end{definition}
 
-The representation relation combines the previously established notions of heap homomorphism and feasibility with the added constraint that the variables, expressions, and continuation strings must match between the pairs of states.
+The representation relation combines the previously established
+notions of heap homomorphism and feasibility with the added constraint
+that the variables, expressions, and continuation strings must match
+between the pairs of states.
 
@@
 $s_p \sqsubset s_q $ if and only if $\eta_p = \eta_q ,\ \cfgnt{e}_p =
-\cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, and there exists a
+\cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, the heaps are well-formed, and there exists a
 homomorphism $(\cfgnt{L}_p\ \cfgnt{R}_p) \rightharpoonup_{h}
@@
 $$
-P \sqsubset Q \Longleftrightarrow \forall q \in Q\ (\forall p \in S\ (p \sqsubset q \Rightarrow p \in P))
+P \sqsubset Q \Longleftrightarrow \forall q \in Q\ (\forall p\ (p \sqsubset q \Rightarrow p \in P))
 $$
@@
 
+\begin{lemma}[$Q$ is a singleton for $P \sqsubset Q$]
+\label{lem:unique}
+$$
+P \sqsubset Q \Rightarrow \forall q,q^\prime \in Q\ (\forall p\ (p \sqsubset q \Rightarrow p \sqsubset q^\prime)
+$$
+The notation $P \sqsubset q$ is used to indicate that single member of
+the set in the represented relation.
+\end{lemma}
+\begin{proof}
+Please write me?
+\end{proof}
 \begin{definition}
-A state relation $p \rightarrow_x q$ is extended to sets of states $P \hookrightarrow_x Q$ as
+\label{def:meta}
+A state relation $p \rightarrow_x p^\prime$ is extended to sets of states $P \hookrightarrow_x P^\prime$ as
 $$
-P \hookrightarrow_x Q \Longleftrightarrow \forall q \in S\ (p \rightarrow_x q \Rightarrow q \in Q)
+P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
 $$
-The $\rgse$ relations over sets of states is The $\rsym$ relation extended to sets of states
+The $\rgse$ relation over sets of states is $\rsgse = \hookrightarrow_\mathit{FA} \cup \hookrightarrow_\mathit{FA(N)} \cup \hookrightarrow_\mathit{FW} \cup \hookrightarrow_\mathit{FW(N)} \cup \hookrightarrow_\mathit{EQ(T)} \cup \hookrightarrow_\mathit{EQ(F)} \cup \hookrightarrow_\com$.%, and
+%the $\rsym$ relation extended to sets of states is 
+%$$
+%\rssym = \hookrightarrow_\mathit{FA} \cup \hookrightarrow_\mathit{FW} \cup \hookrightarrow_\mathit{EQ}^T \cup \hookrightarrow_\mathit{EQ}^F \cup \hookrightarrow_\com
+%$$
 \end{definition}
+
+\begin{lemma}[$P$ and $Q$ have same number of successors when $P \sqsubset q$]
+\label{lem:succCount}
+Let $X = \{P^\prime | P \leadsto P^\prime\}$ and $Y = \{q^\prime | q
+\rsym q^\prime\}$: $P \sqsubset q \Rightarrow |X| = |Y|$.
+\end{lemma}
+\begin{proof}
+Please write me?
+\end{proof}
 
@@
 \label{bisimulation}
-The functional associated to bisimulation,  $F_\sim(\sqsubset)$, is the set of all pairs of sets of states
-$(P\ Q)$ such that
+The functional associated to bisimulation,  $F_\sim$, is a function between binary relations. The functional applied to $\sqsubset$, denoted as $F_\sim(\sqsubset)$, is the set of all pairs
+$(P\ q)$ such that
 \begin{equation}
 \label{eqn:BisimulationForwards}
-\forall p \in P\ (\forall p^\prime\ ( p \rgse p^\prime \Rightarrow \exists q^\prime\ ( (q \rsym q^\prime )\wedge (p^\prime\ \sqsubset\ q^\prime ))))
+\forall P^\prime\ ( P \rsgse P^\prime \Rightarrow \exists q^\prime\ ( (q \rsym q^\prime )\wedge (P^\prime\ \sqsubset\ q^\prime )))
 \end{equation}
@@
 \label{eqn:BisimulationBackwards}
-\forall q \in Q\ (\forall q^\prime\ ( q \rsym q^\prime\Rightarrow \exists p^\prime\ ( (p \rgse p^\prime )\wedge (p^\prime\ \sqsubset\ q^\prime ))))
+\forall q^\prime\ ( q \rsym q^\prime\Rightarrow \exists P^\prime\ ( (P \rsgse P^\prime )\wedge (P^\prime\ \sqsubset\ q^\prime )))
 \end{equation}

### 2014-11-09 tex/proofs.tex
Locked math. Switch to paper

--- 2014-10-31 tex/proofs.tex
@@
 
-%we need to define how r' is arrived at for this one to work...
+\begin{comment}
+Choose any P and Q such that P is represented by Q on field access. Choose some P' that P transitions too.
+Pick some p' in P'. By definition, it is related to a p in P. Use that p. Show how that p is related to p'. Then relate to q'.
+
+Arbitrary P' such that P transitions to P'.
+Reason over each possible P' (how every many choices might exist--Only one for FA).
+Pick arbitrary p' in one of the sucessor.
+Do the forward proof.
+Show connection in q'.
+Connect to P' since it holds for arbitrary.
+
+Repeat process for each possible successor P'
+
+For backward, for each q', there must exists a p'. All we need is one p and then that implies there exists a P. Must do for all Q'. 
+\end{comment}
+
 \begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
-If two field access states are related in the represented by relation,
-then they are also related in the functional associated to bisumlation.
+If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisumlation.
 \label{lem:access}
 $$
-\forall p \in S_\mathit{FA}\ (\forall q \in S_\mathit{FA}\ (p \sqsubset q \Rightarrow (p\ q) \in F_\sim(\sqsubset)))
+\forall P \in 2^{S_\mathit{FA}}\ (P \sqsubset q \Rightarrow (P\ q) \in F_\sim(\sqsubset))
 $$
@@
 \begin{proof}
-Proof by contradiction: assume $p \sqsubset q \wedge (p\ q) \not\in F_\sim(\sqsubset)$.
+Proof by contradiction: assume $P \sqsubset q \wedge (P\ q) \not\in F_\sim(\sqsubset)$.
 
-The case where neither $p$ nor $q$ have successors is trivially satisfied by
-\defref{bisimulation} since the conditions for inclusion in
-$F_\sim(\sqsubset)$ are vacuously met. That is a contradiction.
+\lemref{lem:succ} ensures at least one successor of $P$ and $q$. Let $p^\prime \in P^\prime$ be any
+state in any successor set and $p \rgse p^\prime$ that state's
+predecessor. Let $q^\prime$ be similarly defined relative to $q$.  The states $p$ and $q$, by virtue of the
+representation relation, are only differentiated by their heaps and
+global constraints since the environment ($\eta$), expression ($r$),
+and continuation ($\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow
+\cfgnt{k}\rp$) are the same in all states 
+(\defref{representation}).
 
-Consider now the case where $p$ and $q$ have successor states. The
-statement $p \sqsubset q$ (\defref{representation}) means that $p$ and
-$q$ are only differentiated by their heaps and global constraints
-since the environment ($\eta$), expression ($e$), and continuation
-($k$) are the same in both states.
+There are two relations defined for field access in both $\rsgse$ and
+$\rsym$ for a null and non-null pointing reference (\figref{fig:lazy}
+and \figref{fig:fHeap}). In each relation, the environment is
+unchanged. For a null pointing reference, in both relations, the
+expression is $\cfgt{error}$ and the continuation is $\cfgt{end}$. For
+the non-null pointing reference, some care is needed. First each does
+use the same continuation $\cfgnt{k}$ (it is the same for $p$ and $q$
+by $\sqsubset$. As the environment and continuations are the same,
+$r^\prime = \mathrm{stack}_\cfgnt{r}()$, returns the same next largest
+number of current stake references from the partition. The first
+condition for inclusion in $\sqsubset$, equality between environments,
+expressions, and continuations, is met.
 
-Ignoring the heaps, and given that $p$ and $q$ currently have
-the same environment, expression, and continuation, all successors
-of $p$ related by \textrm{F{\footnotesize IELD}}
-\textrm{A{\footnotesize CCESS}} in $\rgse$ (\figref{fig:lazy}) have
-the same unchanged environment from $p$, $\eta$, new expression
-$r^\prime = \mathrm{stack}_\cfgnt{r}()$, and continuation $\cfgnt{k}$
-from the old continuation in $p$ having completed the field
-access. Similarly, the one successor of $q$ related by $\rsym$
-(\figref{fig:symfield}), has that same $\eta$, $r^\prime =
-\mathrm{stack}_\cfgnt{r}()$, and $\cfgnt{k}$. As such, every successor
-of $p$/$q$ has a matching successor of $q$/$p$ that agrees on the
-environment, expression, and continuation meeting the first condition
-necessary to relate the successors in $\sqsubset$.
+Now consider the heaps.  The functional in \defref{bisimulation} requires a forward
+\eqref{eqn:BisimulationForwards} and backward
+\eqref{eqn:BisimulationBackwards} relationship between successor
+heaps. First the forward direction.
 
-Turning now to the heaps, \textrm{F{\footnotesize IELD}}
-\textrm{A{\footnotesize CCESS}}, in $\rgse$ and $\rsym$, initializes
+\noindent{\textrm{F{\footnotesize IELD}}
+\textrm{A{\footnotesize CCESS (NULL)}}}: $p \rightarrow^\ell_\mathit{FA(N)}
+p^\prime$ because $l = l_\mathit{null}$ (\figref{fig:lazy}). As $p$
+is represented in $q$, $\exists q^\prime\ (q
+\rightarrow^\sym_\mathit{FA{N}} q^\prime$ since $l_{\mathit{null}}$
+must be feasible on the reference (\figref{fig:fHeap}).
+
+The successors $p^\prime$ and $q^\prime$ are only differentiated by
+their heap and global constraint as mentioned previously. Since each heap in each successor is unchanged
+from the predecessor state, the same homomorphism from $p \sqsubset q$
+establishes that $p^\prime \sqsubset q^\prime$ holds in the forward direction.
+
+\noindent\textrm{F{\footnotesize IELD}}
+\textrm{A{\footnotesize CCESS}}: $p \rightarrow^\ell_\mathit{FA}
+p^\prime $ because $\cfgnt{l} \neq \cfgnt{l}_\mathit{null}$. As $p$ is represented in $q$ there must be a feasible non-null location: $\exists q^\prime\ (q
+\rightarrow^\sym_\mathit{FA} q^\prime)$. The non-null pointing field access relations initialize
 uninitialized locations in the heap on reference $\cfgnt{r}$ for field
@@
 initialization, and the heap constraint in the homomorphism is still
-valid by \lemref{lem:init}. Let
-$(\cfgnt{L}^\prime_p\ \cfgnt{R}^\prime_p) \rightharpoonup_h
-(\cfgnt{L}^\prime_q\ \cfgnt{R}^\prime_q)$ be those new heaps and
+valid by \lemref{lem:init}. Let $(\cfgnt{L}^\prime_p\ \cfgnt{R}^\prime_p)$ and  
+$(\cfgnt{L}^\prime_q\ \cfgnt{R}^\prime_q)$ be those new heaps and $\rightharpoonup_h$
 the homomorphism after initialization on the heap in $p$ with
@@
 
-After initialization, \textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} for $\rgse$ creates a new heap
-$(\cfgnt{L}^\prime_p [\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}^\prime_p$
+The final heap in the successor state $p^\prime$ is
+$(\cfgnt{L}^\prime_p [\cfgnt{r}^\prime \mapsto
+  \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}^\prime_p)$, and for $q^\prime$
+the final heap in the successor state is
+$(\cfgnt{L}^\prime_q[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp
+  \cfgnt{L}^\prime_q,\cfgnt{R}^\prime_q,\cfgnt{r},\cfgnt{f},\phi^\prime_g\rp
+]\ \cfgnt{R}^\prime_q)$; each version adding in the
+constraint-location pair or value set respectively on the same
+reference $\cfgnt{r}^\prime$. As $r^\prime$ is a stack reference, and
+identical in both $p^\prime$ and $q^\prime$, and no new locations are
+added to either heap, the existing homomorphism after initialization
+still holds: $p^\prime \rightharpoonup_h q^\prime$.
 
-and for $\rsym$ it relates the state 
-$$ 
-s_\sym^\prime = \lp \cfgnt{L}_{s}[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}_{s},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}_{s}\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp 
-$$
+ To relate $p^\prime$ and $q^\prime$ on
+$\sqsubset$, it is necessary to create a new homomorphism:
+$(\cfgnt{L}^\prime_p\ \cfgnt{R}^\prime_p) \rightharpoonup_{h^\prime}
+(\cfgnt{L}^\prime_q\ \cfgnt{R}^\prime_q)$. To that end, construct the
+function $h^\prime$ such that $h^\prime = h$.
 
-The functional in \defref{} requires and forward
-\eqref{eqn:BisimulationForwards} and backward
-\eqref{eqn:BisimulationBackwards} relationship between successor
-heaps.
-
-\eqref{eqn:BisimulationForwards}
-\eqref{eqn:BisimulationBackwards}
-
-We now show that $s_\gse^\prime \sqsubset s_\sym^\prime$.
-Since $\eta$, $e$, and $k$ are identical between $s_\sym^\prime$ and $s_\gse^\prime $, the first condition is met by default.
-Now we construct the function $h^\prime$ such that $h^\prime = h$.
 Observe that since $s_\gse \rightharpoonup_{h} s_\sym$, and since $\cfgnt{R}_\gse$ and $\cfgnt{R}_\sym$ are unchanged from states $s_\gse$ to $s_\gse^\prime$ and $s_\sym$ to $s_\sym^\prime$ respectively, we are guaranteed that $ \cfgnt{r} = \cfgnt{R}_\gse(l,f) \Rightarrow \cfgnt{r} = \cfgnt{R}_\sym(h^\prime(l),f)$.
@@
 
-\begin{lemma}[$\rsum^*$ preserves heap determinism]
+\begin{lemma}[$\rsum^*$ produces well-formed heaps]
 \label{lem:S-determ}
@@
 
-\begin{lemma}[$\rightarrow_\mathit{FA}$ preserves heap determinism]
+\begin{lemma}[$\rightarrow_\mathit{FA}$ produces well-formed heaps]
 \label{lem:FA-determ}
@@
 
-\begin{lemma}[$\rightarrow_\mathit{FW}$ preserves heap determinism]
+\begin{lemma}[$\rightarrow_\mathit{FW}$ produces well-formed heaps]
 \label{lem:FW-determ}
@@
 
-\begin{lemma}[$\rcom$ preserves heap determinism]
+\begin{lemma}[$\rcom$ produces well-formed heaps]
 \label{lem:J-determ}
@@
 
-\begin{theorem}[$\rsym$ preserves heap determinism]
+\begin{theorem}[$\rsym$ preserves heap well-formedness]
 \label{thm:determ}

### 2014-11-09 tex/precise.tex
adding the correct style file

--- 2014-11-08 tex/precise.tex
@@
 heap, however, there we campare sets of constraint location pairs for
-each reference. We construct three sets of constraints (i)
-$\Phi_\alpha$ constains combinations of constraints ($\phi_0 \wedge
-\phi_1$) from $r_0$ and $r_1$
+each reference. We construct three sets of constraints. The first set,
+$\Phi_\alpha$, we check whether under some constraints $\phi_0$ and
+$\phi_1$ whether references $r_0$ and $r_1$ respectively point to the
+same location $l$.  For all such constraints we create conjunctions of
+the constraints $\phi_0 \wedge \phi_1$ and add them to set
+$\Phi_\alpha$. The next set of constraints si $\Phi_0$ which contains
+the set of constraints from $r_0$ that lead to $l$ such that there is
+no constraints under which $r_1$ can point to that $l$.

### 2014-11-09 tex/lazy.tex
Added error state for field access and regrouped the lazy machine.
added the new supplemenatal file

--- 2014-11-06 tex/lazy.tex
@@
-\section{Generating Heap Summaries}
+\section{Generalized Symbolic Execution}
 
-\subsection{Initialization of Symbolic References}
+Recall that in generalized symbolic execution (GSE) for lazy
+initialization of symbolic references consists of three key points of
+non-determinism where each symbolic reference can be initialized
+non-deterministically to null, a new instance of the symbolic
+reference, or aliases to symbolic references of the same type
+previously initialized. The initialization in GSE consists of creating
+branches in the execution tree for all the non-deterministic choices.
 
-In this section we present the Javalite rewrite rules for the summary
-initialization of symbolic references. The initialization rules are
-defined on the bi-partite graph consisting of references and
-locations. Recall that in generalized symbolic execution (GSE) for
-lazy initialization of symbolic references consists of three key
-points of non-determinism where each symbolic reference can be
-initialized non-deterministically to null, a new instance of the
-symbolic reference, or aliases to symbolic references of the same type
-previously initialized. The initialization in GSE consists of creating
-branches in the execution tree for all the non-deterministic
-choices. In contrast, the heap summarization approach creates a
-single branch that contains the summarization for all the
-initialization in a single bi-partitate graph.
+\input{initialize-lazy}
+\input{lazy-fig}
 
-\input{summarize-precise}
-
-The initialization rules are invoked when an uninitialized field in a
-symbolic reference is accessed. The function $\mathbb{UN}(\cfgnt{L},
-\cfgnt{R}, \cfgnt{r}, \cfgnt{f}) = \{\cfgnt{l}\ ...\}$ returns
-constraint-location pairs in which the field $\cfgnt{f}$ is
-uninitialized:
-\[
-\begin{array}{rcl}
-\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \\
-& & \ \ \ \ \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \\
-& & \ \ \ \ \ \ \ \ \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
-\end{array}
-\]
-where $\mathbb{S}(\phi)$ returns true if $\phi$ is
-satisfiable. Intutively, for the reference, $\cfgnt{r}$, it constructs
-the set, $\theta$, that contains all contraint-location pairs that
-point to the field $\cfgnt{f}$ and $\cfgnt{f}$ points to
-$\cfgnt{l}_\mathit{un}$.
-
-% The cardinality of the set, $\theta$ is never
-%greater than one in GSE and the constraint is always satisfiable
-%because all constraints are constant. This property is relaxed in GSE
-%with heap summaries.
-
-The rewrite rule to initialize a heap in the symbolic summarization
-technique is shown in~\figref{fig:initHeap}. The set $\mathbb{UN}$
-
- There are three
-constraint-location pair sets $\theta_\mathit{null}$,
-$\theta_\mathit{new}$, and $\theta_\mathit{alias}$ that correspond to
-the non-deterministic choices in GSE. The $\theta_\mathit{null}$ creates
-a constraint location pair where the constraint under which the field is read $\phi_x$ $l_\mathit{null}$
-
-\begin{figure*}[t]
-\begin{center}
-\begin{tabular}[c]{c|c|c|c}
-\begin{tabular}[c]{c}
-\scalebox{0.81}{\input{origHeap.pdf_t}} \\
-\end{tabular} &
-\begin{tabular}[c]{c}
-\scalebox{0.81}{\input{summarizeXHeap.pdf_t}} \\
-\end{tabular} &
-\begin{tabular}[c]{c}
-\scalebox{0.81}{\input{summarizeYHeap.pdf_t}} \\
-\end{tabular} &
-\begin{tabular}[c]{l}
-$\rho := \{ (r_1^i, r_1^i \neq r_\mathit{null}, l_1 \}$ \\
-$\theta_\mathit{null} := \{ ( r_2^i = r_\mathit{null}, l_\mathit{null}) \}$\\
-$\theta_\mathit{new} := \{ ( r_2^i \neq r_\mathit{null} \wedge r_2^i \neq r_1^i, l_2) \}$\\
-$\theta_\mathit{alias} := \{ ( r_1^i \neq r_\mathit{null} \wedge r_2^i \neq r_\mathit{null} \wedge r_2^i = r_1^i, l_1) \}$\\
-$\theta_\mathit{orig} := \{ \}$ \\
-$\phi_{\mathit{1a}} := r_1^i = r_\mathit{null} $ \\
-$\phi_{\mathit{1b}} := r_1^i \neq r_\mathit{null} $  \\
-$\phi_{\mathit{2a}} := r_2^i = r_\mathit{null}$ \\
-$\phi_{\mathit{2b}} := r_2^i \neq r_\mathit{null} \wedge r_2^i \neq r_1^i$ \\
-$\phi_{\mathit{2c}} :=  r_2^i \neq r_\mathit{null} \wedge r_2^i = r_1^i $ \\
-\end{tabular} \\
-(a) & (b) & (c) & (d) \\
-\end{tabular}
-\end{center}
-\caption{initialize this.x and this.y}
-\label{fig:initHeap}
-\end{figure*}
-
-We visualize the initialization process in the symbolic summarization
-technique in~\figref{fig:initHeap}. The heap
-in~\figref{fig:initHeap}(a) represents the initial heap. The
-references with the superscript $s$ indicates that it is a local
-reference. In~\figref{fig:initHeap} $r_0^s$ represents the reference
-for the $\mathit{this}$ instance which has two fields $x$ and $y$ of
-the same type. The reference $r_0^s$ points to the location
-$l_0$. Note that when no constraint is specified, then there is a
-implicit $\mathit{true}$ constraint. In~\figref{fig:initHeap} $r_0^s$
-points to $l_0$ on $\mathit{true}$. The fields $x$ and $y$ point to
-the uninitialized reference $r_\mathit{un}$. The reference
-$r_\mathit{un}$ points to the uninitialized location $l_\mathit{un}$
-on the $\mathit{true}$ constraint.
-
-The graph in~\figref{fig:initHeap}(b) represents the summary heap
-after the initialization of the $\mathit{this}.x$ field while the
-graph in~\figref{fig:initHeap}(c) represents the summary heap after
-the initialization of the $\mathit{this}.y$ field following the
-initialization of $\mathit{this}.x$. The list
-in~\figref{fig:initHeap}(d) represents the various sets constructed in
-the rewrite system when the initialization takes places. We also
-define the constraints of references to their corresponding labels in
-the graph.
-
-The access on $l_0.x$ creates a new input reference $r_1^i$ in the
-summary heap shown in~\figref{fig:initHeap}(b). The reference $r_1^1$
-points to the $l_\mathit{null}$ location under the constraint that
-$r_1^i$ is null: $\phi_{1a} := r_1^i = r_\mathit{null}$. The reference
-$r_1^i$ points to the location $l_1$ under the constraint that $r_1^i$
-is not null $\phi_{1b} :=r_1^i \neq r_\mathit{null}$. The location
-$l_1$ represents a fresh location of type $C$ is created on the heap
-such that $C$ is type of $\mathit{this}.x$.
+\input{lazy-eq}

### 2014-11-09 tex/precise.tex
added the new supplemenatal file

@@
+\section{Generating Symbolic Heap Summaries}
+
+\subsection{Initialization of Symbolic References}
+
+In this section we present the Javalite rewrite rules for the
+initialization of references in the symbolic heap summary. The
+initialization rules are defined on the bi-partite graph consisting of
+references and locations. In contrast, the heap summarization approach
+creates a single branch that contains the summarization for all the
+initialization in a single bi-partitate graph.
+
+\input{summarize-precise}
+
+The initialization rules are invoked when an uninitialized field in a
+symbolic reference is accessed. The function $\mathbb{UN}(\cfgnt{L},
+\cfgnt{R}, \cfgnt{r}, \cfgnt{f}) = \{\cfgnt{l}\ ...\}$ returns
+constraint-location pairs in which the field $\cfgnt{f}$ is
+uninitialized:
+\[
+\begin{array}{rcl}
+\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \\
+& & \ \ \ \ \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \\
+& & \ \ \ \ \ \ \ \ \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
+\end{array}
+\]
+where $\mathbb{S}(\phi)$ returns true if $\phi$ is
+satisfiable. Intutively, for the reference, $\cfgnt{r}$, it constructs
+the set, $\theta$, that contains all contraint-location pairs that
+point to the field $\cfgnt{f}$ and $\cfgnt{f}$ points to
+$\cfgnt{l}_\mathit{un}$.
+
+% The cardinality of the set, $\theta$ is never
+%greater than one in GSE and the constraint is always satisfiable
+%because all constraints are constant. This property is relaxed in GSE
+%with heap summaries.
+
+The rewrite rule to initialize a heap in the symbolic summarization
+technique is shown in~\figref{fig:symInit}. Given the unitialized set
+$\mathbb{UN}$ for field $f$, the $\mathit{min}_l$ function returns the
+constraint location pair based on a lexical ordering of locations. The
+init$_r$ method returns a new input reference $r_f$ while the
+fresh$_f$ returns a new location of type $C$. The set $\rho$ contains
+the set of reference location, $(r_a, l_a)$, pairs that the current
+field may alias. The pair $(r_a, l_a)$ is contained in the set $ \rho
+$ if the following conditions hold: (i) $r_a$ is part of the input
+references initialized in the summary heap, (ii) $r_a$ is in the
+pre-image of $l_a$, (iii) and the type of $l_a$ is the same as the
+type of the field being initialized.
+
+There are three constraint-location pair sets that correspond to
+non-deterministic choices in GSE: (a) $\theta_\mathit{null}$ that
+creates a constraint that states $r_f$ is null under which it points
+to $l_\mathit{null}$, (b) $\theta_\mathit{new}$ the constraint that
+$r_f$ is not null and it does not alias another reference in set
+$\rho$ under which it points to the newly created location $l_f$, (c)
+and $\theta_\mathit{alias}$ where for each element in the set $(r_a,
+l_a) \in \rho$ it creates a constraints that $r_f$ is not null, points
+to $r_a$, and does not point to any reference contained in
+$(r_a^\prime, l_a^\prime) \in \rho$ such that $r_a \neq
+r_a^\prime$. Additionally $\theta_\mathit{orig}$ allows for the
+possibility that the field continues to remain uninitialized since the
+heap is symbolic. We refer to this initialization in the summary
+machine as conditional initialization. Finally, the fields of the
+reference $r_f$ are marked as uninitialized.
+
+In the post condition of the rule the reference $r_f$ points to
+$\theta$ which contains the union of all the constraint location pairs
+sets, and the field $f$ points to the new reference $r_f$ in the
+summary heap.  Note that the summarize rule invoked repeatedly until
+the set of unitialized constraint location pairs for field $f$ is
+empty. In other words the set $\lambda$ is empty. This consititutes
+the summarize end rule in~\figref{fig:symInit}.
+
+\begin{figure*}[t]
+\begin{center}
+\begin{tabular}[c]{c|c|c|c}
+\begin{tabular}[c]{c}
+\scalebox{0.81}{\input{origHeap.pdf_t}} \\
+\end{tabular} &
+\begin{tabular}[c]{c}
+\scalebox{0.81}{\input{summarizeXHeap.pdf_t}} \\
+\end{tabular} &
+\begin{tabular}[c]{c}
+\scalebox{0.81}{\input{summarizeYHeap.pdf_t}} \\
+\end{tabular} &
+\begin{tabular}[c]{l}
+$\rho := \{ (r_1^i, r_1^i \neq r_\mathit{null}, l_1 \}$ \\
+$\theta_\mathit{null} := \{ ( r_2^i = r_\mathit{null}, l_\mathit{null}) \}$\\
+$\theta_\mathit{new} := \{ ( r_2^i \neq r_\mathit{null} \wedge r_2^i \neq r_1^i, l_2) \}$\\
+$\theta_\mathit{alias} := \{ ( r_1^i \neq r_\mathit{null} \wedge r_2^i \neq r_\mathit{null} \wedge r_2^i = r_1^i, l_1) \}$\\
+$\theta_\mathit{orig} := \{ \}$ \\
+$\phi_{\mathit{1a}} := r_1^i = r_\mathit{null} $ \\
+$\phi_{\mathit{1b}} := r_1^i \neq r_\mathit{null} $  \\
+$\phi_{\mathit{2a}} := r_2^i = r_\mathit{null}$ \\
+$\phi_{\mathit{2b}} := r_2^i \neq r_\mathit{null} \wedge r_2^i \neq r_1^i$ \\
+$\phi_{\mathit{2c}} :=  r_2^i \neq r_\mathit{null} \wedge r_2^i = r_1^i $ \\
+\end{tabular} \\
+(a) & (b) & (c) & (d) \\
+\end{tabular}
+\end{center}
+\caption{initialize this.x and this.y}
+\label{fig:initHeap}
+\end{figure*}
+
+We visualize the initialization process in the symbolic summarization
+technique in~\figref{fig:initHeap}. The heap
+in~\figref{fig:initHeap}(a) represents the initial heap. The
+references with the superscript $s$ indicates that it is a local
+reference. In~\figref{fig:initHeap} $r_0^s$ represents the reference
+for the $\mathit{this}$ instance which has two fields $x$ and $y$ of
+the same type. The reference $r_0^s$ points to the location
+$l_0$. Note that when no constraint is specified, then there is a
+implicit $\mathit{true}$ constraint. In~\figref{fig:initHeap} $r_0^s$
+points to $l_0$ on $\mathit{true}$. The fields $x$ and $y$ point to
+the uninitialized reference $r_\mathit{un}$. The reference
+$r_\mathit{un}$ points to the uninitialized location $l_\mathit{un}$
+on the $\mathit{true}$ constraint.
+
+The graph in~\figref{fig:initHeap}(b) represents the summary heap
+after the initialization of the $\mathit{this}.x$ field while the
+graph in~\figref{fig:initHeap}(c) represents the summary heap after
+the initialization of the $\mathit{this}.y$ field following the
+initialization of $\mathit{this}.x$. The list
+in~\figref{fig:initHeap}(d) represents the various sets constructed in
+the rewrite system when the initialization takes places. We also
+define the constraints of references to their corresponding labels in
+the graph.
+
+The access on $l_0.x$ creates a new input reference $r_1^i$ in the
+summary heap shown in~\figref{fig:initHeap}(b). The reference $r_1^1$
+points to the $l_\mathit{null}$ location under the constraint that
+$r_1^i$ is null: $\phi_{1a} := r_1^i = r_\mathit{null}$. The reference
+$r_1^i$ points to the location $l_1$ under the constraint that $r_1^i$
+is not $\mathit{null}$ $\phi_{1b} :=r_1^i \neq r_\mathit{null}$. The
+location $l_1$ represents a fresh location of type $C$ is created on
+the heap such that $C$ is type of $\mathit{this}.x$.
+
+Following the initialization to the $\mathit{this}.x$, when we
+initialize $\mathit{this}.y$ the resulting summary heap is shown
+in~\figref{fig:initHeap}(c). The set $\rho$ shown
+in~\figref{fig:initHeap}(d) contains the potential aliases for
+$\mathit{this}.y$ which is location $l_1$ ($\mathit{this}.x$). The
+constraint location $\theta$ sets represents the initialization
+choices for $\mathit{this}.y$. The new input reference $r_2^i$ for
+$this.y$ points to (a) location $l_\mathit{null}$ under the constraint
+$\phi_{2a} := r_2^i = r_\mathit{null}$, (b) location $l_2$ under the
+constraint $\phi_{2b} := r_2^i \neq r_\mathit{null} \wedge r_2^i \neq
+r_1^i$ that states that $r_2^i$ is not null and does not alias
+$r_1^i$, and (c) location $l_1$ under the constraint $\phi_{2c} :=
+r_2^i \neq r_\mathit{null} \wedge r_2^i = r_1^i$ that states $r_2^i$
+is not null and \emph{does} alias $r_1^i$.
+
 \subsection{Accessing a Field Reference}
-
 \input{precise-fig}
@@
 
-\begin{definition}
-\label{def:VS}
-The function $\mathbb{VS}(L,R,\phi_g,r,f)$ constructs the value-set given a
-heap, reference, and desired field:
-\[
-\begin{array}{rcl}
-  \mathbb{VS}(\cfgnt{L},\cfgnt{R},\phi_g,\cfgnt{r},\cfgnt{f}) & = & \{(\phi\wedge\phi^\prime\ \cfgnt{l}^\prime) \mid \\
-  & & \ \ \ \ \exists \cfgnt{l}\ ((\phi\ l) \in L(r)\ \wedge \\
-  & & \ \ \ \ \ \ \ \ \exists \cfgnt{r}^\prime ( \cfgnt{r}^\prime = R(\cfgnt{l},\cfgnt{f})\ \wedge \\
-  & & \ \ \ \ \ \ \ \ \ \ \ \ (\phi^\prime\ l^\prime) \in \cfgnt{L}(\cfgnt{r}^\prime)\ \wedge\\
-  & & \ \ \ \ \ \ \ \ \ \ \ \ \mathbb{S}(\phi\wedge\phi^\prime\wedge \phi_g)))\}
-\end{array}
-\]
-where $\mathbb{S}(\phi)$ returns true if $\phi$ is satisfiable.
-\end{definition}
+\input{value-set-def}
 
@@
 
-\begin{definition}
-\label{def:ST}
-The strengthen function $\mathbb{ST}(\cfgnt{L},\cfgnt{r},\phi,\phi_g)$ strengthens every
-constraint from the reference $\cfgnt{r}$ with $\phi$ and keeps only location-constraint
-pairs that are satisfiable after this strengthening with the inclusion of the global heap constraint $\phi_g$:
-\[
-\begin{array}{rcl} 
-\mathbb{ST}(\cfgnt{L},\cfgnt{r},\phi,\phi_g) & = & \{ (\phi\wedge\phi^\prime\ \cfgnt{l}^\prime) \mid  \\
-& & \ \ \ \ (\phi^\prime\ \cfgnt{l}^\prime)\in \cfgnt{L}(\cfgnt{r})\wedge\mathbb{S}(\phi\wedge\phi^\prime\wedge\phi_g) \}
-\end{array}
-\]
-\end{definition}
+\input{st-def}
 

### 2014-11-09 tex/intro.tex
starting to reorg the front matter

@@
 
-In recent years symbolic execution --
-a program analysis technique for systematic exploration of
-program execution paths using symbolic input values -- has provided
-the basis for various software testing and analysis techniques.
-For each execution path explored during symbolic execution, constraints
-on the symbolic inputs are collected to create a \emph{path
-condition}. The set of path conditions computed by symbolic execution
-characterize the observed program execution behaviours and can
-be used as an enabling technology for various applications, e.g., 
-regression 
+In recent years symbolic execution -- a program analysis technique for
+systematic exploration of program execution paths using symbolic input
+values -- has provided the basis for various software testing and
+analysis techniques.  For each execution path explored during symbolic
+execution, constraints on the symbolic inputs are collected to create
+a \emph{path condition}. The set of path conditions computed by
+symbolic execution characterize the observed program execution
+behaviours and can be used as an enabling technology for various
+applications, e.g., regression
 analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
-data structure repair~\cite{KhurshidETAL05RepairingStructurally}, dynamic
-discovery of invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, 
-and debugging\cite{Ma:2011}.
+data structure repair~\cite{KhurshidETAL05RepairingStructurally},
+dynamic discovery of
+invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, and
+debugging\cite{Ma:2011}.
 
@@
 
-With the advent of object-oriented
-languages that manipulate dynamically allocated data,
- .g., Java and C$++$, recent work has generalized the core ideas of 
-symbolic execution to enable analysis of programs containing
-complex data structures with unbounded domains, i.e., data stored
-on the heap~\cite{Kiasan06,Kiasan07,GSE03}.
-These techniques onstruct the heap in a lazy manner, 
-deferring materialization of objects on the concrete heap until
-they are needed for the analysis to proceed.
-%, i.e., until execution of a statement with a  dereference expression 
-%($x = r.f$).
-Treatment of
-heap allocated data then follows concrete program semantics 
-once a heap location is materialized, resulting in a large number
-of feasible concrete heap configurations, and as a result, a large
-number of points of 
-non-determinism to be analyzed, further exacerbating 
-the state space explosion problem.
+With the advent of object-oriented languages that manipulate
+dynamically allocated data, .g., Java and C$++$, recent work has
+generalized the core ideas of symbolic execution to enable analysis of
+programs containing complex data structures with unbounded domains,
+i.e., data stored on the heap~\cite{Kiasan06,Kiasan07,GSE03}.  These
+techniques construct the heap in a lazy manner, deferring
+materialization of objects on the concrete heap until they are needed
+for the analysis to proceed. The materilization accounts for various
+heap configurations and creates non-deterministic choices for the
+symbolic object to be initialized as (a) null, (b) instance of a new
+reference of a compatible class, and (c) alias an previously
+initialized symbolic reference. Treatment of heap allocated data then
+follows concrete program semantics once a heap location is
+materialized, resulting in a large number of feasible concrete heap
+configurations, and as a result, a large number of points of
+non-determinism to be analyzed, further exacerbating the state space
+explosion problem.
 
+\nsr{need a paragraph on heap summarization techniques}
+
+\begin{comment}
 THIS PARA IS NOT QUITE RIGHT BUT THE IDEA IS STARTING TO COME OUT.
@@
 e.g., regression analyses.
+\end{comment}
+
+In this work, we present a novel heap initialization and analysis
+technique which takes inspiration from both approaches and constructs
+precise heap summaries lazily during symbolic execution. \nsr{needs
+  some text on the fact we use java lite to formalize the heap
+  summary, some key characteristicss of the heap such as the fact it
+  is a bipartiate graph with locations and referneces, properties of
+  the heap such as the determinism and immutability}
+
+Our symbolic heap representation is expressive and can represent
+recursive data structures.  \nsr{Is any part of the formalism borrowed
+  from the dilligs? Which part are unique?}  \nsr{end on a couple
+  sentences about the various rules that will be talked about in the
+  paper}\nsr{The reader should be convinced about our expressiveness
+  claim here}
+
+We prove that our technique is precise, at any given point during
+symbolic execution, the symbolic heap represents the exact set of
+feasible concrete heap structures for the program under analysis, and
+\nsr{a paragraph that provides intution on how we are a bisumulation
+  with the GSE..reader should be convinced about the precision claim}
+
+Our demonstrate the scalability of our approach. Our technique reduces
+the points of non-determinism compared to generalized symbolic
+execution and explores each control-flow path only once for any given
+set of isomorphic heaps \nsr{a paragraph that provides a breif summary
+  of the results.. would be nice if we have numbers for lazier and
+  lazier Sharp as well.}
+
+\begin{comment}
 
@@
  \end{itemize}
+\end{comment}
 

### 2014-11-10 tex/bisimulation.tex
Almost done with bisimulation. Need only theorem and corolary.

\section{Bisimularity Relation}
Let $p \rgse p^\prime$ be the binary relation over the universe of states, $S$,
according to generalized symbolic execution with lazy initialization
(see the supplemental text for a precise definition of that
relation). Similarly, let $q \rsym q^\prime$ be the relation for the GSESH
algorithm in this paper. The principle theoretical result is the
existence of a bisimularity relation between states related on $p \rgse p^\prime$
and the states related on $q \rsym ^\prime$. A corollary is that $\rsym$ is
both sound and complete with respect to $\rgse$. Only a summary of the
proof is given due to space.

The inspiration for $\rsym$ came from a desire to create
a new way to initialize heap objects that avoided initializing heaps
that traverse redundant paths. The thought was to group together heaps
into equivalence classes: all the heaps that followed the same control
flow path to a given point of execution would be in the same
equivalence class at that point of execution. An equivalence class
splits at branches, where the program actually differentiates heaps.

The proof only reasons about well-formed states: heaps are
deterministic, type consistent, with no dangling references, and it
knows about any references in the environment, expression, or
continuation. Well-formed states always have a successor unless it is
the end of the program execution.

Let $p \rgse p^\prime$ be defined as a union over state relations:
$$
\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A\cdot} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W\cdot} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E\cdot} \cup \rgse^\com
$$
where \emph{A} is a field access $\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
\rightarrow \cfgnt{k}\rp$, \emph{W} is a field write $\lp
\cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
\cfgnt{k}\rp$, \emph{E} is a reference compare $\lp
\cfgnt{v}\ \cfgt{=}\ \cfgnt{*} \rightarrow \cfgnt{k}\rp$, $\cdot$
indicates a null reference in the operation or a false outcome, and
\emph{\com} is everything else in the language. A state relation is trivially extended to sets of states as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
$$
Let $\rgse$ be the extension of $\rgse$ to sets of states.
$$
\rsgse = \rgse^\mathit{A}
\cup \rgse^\mathit{A\cdot} \cup \rgse^\mathit{W} \cup
\rgse^\mathit{W\cdot} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E\cdot}
\cup \rgse^\com
$$
The definition embodies the notion of splitting equivalence classes at
certain operations. The set $P$ at a field access for example has two
potential successors: a non-null and null reference. Respectively, the
set $P \rgse^\com$ only has a single successor since those expressions
are not related to control flow.

The functional equivalence between heaps in states $p$
and $q$ requires both a mapping to relate the two heaps and a
constraint on the feasibility of that mapping in the presence of a
path constraint from symbolic execution. Subscripts indicates state
members as in $p = (
\cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$.
\begin{definition}
\label{def:homomorphism}
A \textbf{homomorphism} given the universe of field names $\mathcal{F}$ is 
$$
\begin{array}{l}
 s_p \rightharpoonup_{h} s_q \Leftrightarrow \\
\ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}\ ( \exists \phi_\alpha\ (\exists \phi_\beta\ ( \\ 
\ \ \ \ \ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow \\
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ \\
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  )) ) ) ) )
\end{array}
$$
\end{definition}

\begin{definition}
\label{def:hc}
The \textbf{homomorphism constraint} is
\begin{align*}
\mathbb{HC}(p \rightharpoonup_{h} q) &= \\
 \bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_p^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_q^\rightarrow)\} 
\end{align*}
\end{definition}
The functional equivalence between heaps on a homomorphism and
constraint asserts a common structures in the two heaps under certain
conditions. The equivalence is used to related states in $p \rgse
p^\prime$ to states in $q \rsym q^\prime$.
\begin{definition}
\label{representation}
States $(p\ q)$ are in the \textbf{representation relation}, $p \sqsubset q$, if and only if, $\eta_p = \eta_q ,\ \cfgnt{e}_p =
\cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, and there exists a
homomorphism $p \rightharpoonup_{h}
q$ such that
\begin{equation}
\label{eqn:valid}
 \mathbb{S}( \phi_q \wedge \mathbb{HC}(s_p \rightharpoonup_{h} s_q) ) 
\end{equation}
The represented relation is extended to sets of states $P$ and a single state $q$ as\footnote{The full proof argues $P \sqsubset Q$ but that $Q$ is
  always a singleton set containing $q$.}
$$
P \sqsubset q \Longleftrightarrow \forall p\ (p \sqsubset q \Rightarrow p \in P)
$$
\end{definition}
The statement $p \sqsubset q$ ensures that a functionally equivalent
heap to the one in $p$ is present, by the homomorphism, and valid, by
the heap constraint and path constraint, in $q$. As the states in $P$
are only differentiated by heaps and those states are only
differentiated from $q$ by both the heap and path constraint in $q$,
$P \sqsubset q$ implies that $q$ is representative of all the states
in $P$ up to the given point of execution expressed in $\phi_q$.
\begin{definition}
\label{bisimulation}
The \textbf{functional associated to bisimulation} applied to $\sqsubset$, denoted as $F_\sim(\sqsubset)$, is the set of all pairs
$(P\ q)$ such that
\begin{equation}
\label{eqn:BisimulationForwards}
\forall P^\prime\ ( P \rsgse P^\prime \Rightarrow \exists q^\prime\ ( (q \rsym q^\prime )\wedge (P^\prime\ \sqsubset\ q^\prime )))
\end{equation}
\begin{equation}
\label{eqn:BisimulationBackwards}
\forall q^\prime\ ( q \rsym q^\prime\Rightarrow \exists P^\prime\ ( (P \rsgse P^\prime )\wedge (P^\prime\ \sqsubset\ q^\prime )))
\end{equation}
\end{definition}
As is typical, the functional reasons over a forward and backward
simulation, while the application to dissimilar states using a
meta-relation, $\rsgse$ is somewhat non-standard; though

### 2014-11-10 tex/precise.tex
moving parts of the rules to the supp
unscaled the figures
Fixed field write
updates to equality

@@
 
-\input{summarize-precise}
+\input{summarize-precise-incomplete}
+
+\begin{figure*}
+\begin{tabular}[c]{l}
+\scalebox{1.0}{\usebox{\boxPI}} \\
+\end{tabular}
+\caption{The summary machine, $s ::= \lp\cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\ \cfgnt{C}\rp$, with $s\rsum^*s^\prime =  s \rsum \cdots \rsum s^\prime \rsum s^\prime$.}
+\label{fig:symInit}
+\end{figure*}
 
@@
 \subsection{Accessing a Field Reference}
-\input{precise-fig}
+\input{precise-fig-incomplete}
 
@@
 \begin{center}
-\setlength{\tabcolsep}{50pt}
+\setlength{\tabcolsep}{60pt}
+\hspace*{-35pt}
 \begin{tabular}[c]{cc}
-\usebox{\boxPFAFW} & 
+\scalebox{1.0}{\usebox{\boxPFAFW}} & 
 %\scalebox{0.91}{\input{faYHeap.pdf_t}} &
@@
 \subsection{Equality and InEquality of References}
+\input{precise-eq}
 
-\input{precise-eq}
+\begin{figure*}
+\begin{tabular}[c]{c}
+\scalebox{1.0}{\usebox{\boxPEQ}} \\
+% & \usebox{\boxPEX} \\ \\
+%(a) & (b) \\
+\end{tabular}
+\caption{FIXME: I desperately need a caption!}
+\label{fig:eqs}
+\end{figure*}
 
@@
 
-\begin{figure*}
-\begin{tabular}[c]{cl}
-\usebox{\boxPEQ} & \usebox{\boxPEX} \\ \\
-(a) & (b) \\
-\end{tabular}
-\caption{equals true for this.x == this.y}
-\label{fig:eqs}
-\end{figure*}
+The rewrite rules to compare two references in the symbolic summary
+heap are shown in~\figref{fig:eqs}. The equals references-true rewrite
+rule returns true when two references $r_0$ and $r_1$ are equal. In
+GSE this is a simple comparision of two concrete object references. In
+the symbolic summary heap, however, we compare sets of constraint
+location pairs pointed to by each reference. Let us consider the
+equals reference-true rewrite rule. Here, we construct three sets of
+constraints. To construct the first set, $\Phi_\alpha$, we check if
+there exist constraint location pairs $(\phi_0, l_0) \in L(r_0)$ and
+$(\phi_1, l_1) \in L(r_1)$ such that $l_0$ and $l_1$ are the same.
+For all such constraints we create conjunctions of the constraints
+$\phi_0 \wedge \phi_1$ and add them to set $\Phi_\alpha$. Intutively
+these represent the constraints under which $r_0$ and $r_1$ point to
+the same location in the heap. The next set of constraints is $\Phi_0$
+which contains a constraints under which $r_0$ points to a
+corresponding location $l_i$ such that $r_1$ \emph{does not} point to
+$l_i$ under any constraint. Inversely, the set of constraints $\Phi_1$
+contains the set of constraints under which $r_1$ points to a
+corresponding location $l_j$ and $r_0$ \emph{does not} point to $l_j$
+under any constraint.
 
-The rewrite rules for check the equals true and equals false when
-comparing two references in the symbolic summary heap is shown
-in~\figref{fig:eqs}(a). First the equals reference true rewrite rule
-returns true if two references $r_0$ and $r_1$ are equal. In GSE this
-is a simple comparision of object refrences. In the symbolic summary
-heap, however, there we campare sets of constraint location pairs for
-each reference. We construct three sets of constraints. The first set,
-$\Phi_\alpha$, we check whether under some constraints $\phi_0$ and
-$\phi_1$ whether references $r_0$ and $r_1$ respectively point to the
-same location $l$.  For all such constraints we create conjunctions of
-the constraints $\phi_0 \wedge \phi_1$ and add them to set
-$\Phi_\alpha$. The next set of constraints si $\Phi_0$ which contains
-the set of constraints from $r_0$ that lead to $l$ such that there is
-no constraints under which $r_1$ can point to that $l$.
+To the global constraint we add the disjunction of the constraints in
+$\Phi_\alpha$ to indicate that if any of the constraints are
+satisfiable, then references $r_0$ and $r_1$ can be true. Furthermore,
+we had to the global heap constraint, $\phi_g^\prime$, the
+conjunctions of negations to the constraints in $\Phi_0$ and
+$\Phi_1$. This indicates for locations that are not common to the
+references, the negations of their constraints are satisfiable. Before
+the rewrite rule returns true the satisfiability of the updated global
+heap constraint is checked.
+
+Consider the example in~\figref{fig:initHeap}(c), where we would like
+to check if $r_1^i$ and $r_2^i$ are equal. The set of constraint locations 
+pairs of the two references are:
+
+\[
+L(r_1^i) = \{ (\phi_{1a}\; l_\mathit{null})\; (\phi_{1b}\; l_1) \} 
+\]
+\[
+L(r_2^i) = \{ (\phi_{2a}\; l_\mathit{null}),\; (\phi_{2b}\; l_2),\; (\phi_{2c}\; l_1) \} \\
+\]
+
+\noindent{The three constraint sets are:}
+
+\[
+\Phi_\alpha = \{ (\phi_{1a}\; \wedge\; \phi_{2a} ) (\phi_{1b}\; \wedge\; \phi_{2c} ) \}\;
+\Phi_0 = \{ \}\; \Phi_1 = \{ \phi_{2b}\} \\
+\]
+
+\noindent{Finally the global constraint is} 
+\[
+\phi^\prime = \mathit{true} \wedge  (\phi_{1a}\; \implies\; \neg\phi_{2a} )\wedge (\phi_{1b}\; \implies\; \neg\phi_{2c} )  \wedge \phi_{2b}
+\]

### 2014-11-10 tex/bisimulation.tex
Finished first draft of bisimulation

@@
 \end{equation}
+If $\sqsubset$ is a bisimulation, then the greatest fixed point of $F_\sim(\sqsubset)$ is the bisimilarity relation.
 \end{definition}
@@
 simulation, while the application to dissimilar states using a
-meta-relation, $\rsgse$ is somewhat non-standard; though
+meta-relation, $\rsgse$, is somewhat non-standard; though convenient
+in this instance since it captures the notion of $q$ as a set of
+states \cite{GSE:barbedbisimulation}.
+
+\begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
+If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisumlation.
+\label{lem:access}
+$$
+\forall P \in 2^{S_\mathit{FA}}\ (P \sqsubset q \Rightarrow (P\ q) \in F_\sim(\sqsubset))
+$$
+\end{lemma}
+
+\begin{proof}
+Proof by contradiction: assume $P \sqsubset q \wedge (P\ q) \not\in F_\sim(\sqsubset)$.
+
+\noindent\textbf{Sketch}: Choose any $P$ and $q$ at the field access continuation such
+that $P \sqsubset q$. In the forward simulation
+\eqref{eqn:BisimulationForwards}, for each $P^\prime$ such that $P
+\rsgse P^\prime$, pick some $p^\prime \in P^\prime$. By definition $p \rgse
+p^\prime$, $p \in P$, and $p \sqsubset q$. The proof shows the
+existence of $q^\prime$ such that $q \rsym q^\prime$ and $p^\prime
+\sqsubset q^\prime$ using the existing homomorphism in $p \sqsubset q$.
+
+In the backward simulation \eqref{eqn:BisimulationBackwards}, for each
+$q^\prime$ such that $q \rsym q^\prime$, the proof posits the
+existences of some $p^\prime \sqsubset q^\prime$ and uses the
+homomorphism in $p^\prime \sqsubset q^\prime$ to derive a $p$ such
+that $p \rgse p^\prime$ and $p \in P$.
+
+As the forward and backward simulations hold for any $p \in P$, $P
+\sqsubset q$ must be in the functional, $F_\sim(\sqsubset)$, which is
+a contradiction.
+\end{proof}
+Similar lemmas are proved for field write and equals reference.
+
+\begin{theorem}
+\label{th:bisim}
+The relation $\sqsubset$ is a bisimulation.
+\end{theorem}
+\begin{proof}
+By definition of the bisimilarity relation. All of the common rules
+make no changes to the heap, so $P \subset q$ is included in the
+functional. The other transition relations are supported by lemmas
+such as \lemref{lem:access}.
+\end{proof}
+
+The notion $p \stackrel{n}{\rgse} p^\prime$ denotes that $p^\prime$ is
+the $n$-step successor of $p$, if it exists, and $q
+\stackrel{n}{\rsym} q^\prime$ is similarly defined. Completeness and
+soundness are readily established by \thref{th:bisim} and inducting
+over $n$.
+
+\begin{corollary}[$\rsym$ is complete]
+If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$ then
+$$
+\forall p^\prime\ (p \stackrel{n}{\rgse} p^\prime \Rightarrow \exists q^\prime\ (q \stackrel{n}{\rsym} q^\prime \wedge p^\prime \sqsubset q^\prime))
+$$
+\end{corollary}
+
+\begin{corollary}[$\rsym$ is sound]
+If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$ then
+$$
+\forall q^\prime\ (q \stackrel{n}{\rsym} q^\prime \Rightarrow \exists p^\prime\ (p \stackrel{n}{\rgse} p^\prime \wedge p^\prime \sqsubset q^\prime))
+$$
+\end{corollary}
+
+The relation, $P \sqsubset q$, is readily established in the initial
+state of a given program, as there is single initial state, $P_o =
+\{p_o\}$, in any valid Javalite program. The initial state $\rsym$ is
+then defined as $q_o = p_o$; $P_o \sqsubset q_o$ is trivially shown.

### 2014-11-10 tex/precise.tex
Fixed the centering
edits to the equality

@@
 \begin{figure*}
+\begin{center}
 \begin{tabular}[c]{c}
@@
 \end{tabular}
+\end{center}
 \caption{FIXME: I desperately need a caption!}
@@
 heap are shown in~\figref{fig:eqs}. The equals references-true rewrite
-rule returns true when two references $r_0$ and $r_1$ are equal. In
-GSE this is a simple comparision of two concrete object references. In
-the symbolic summary heap, however, we compare sets of constraint
-location pairs pointed to by each reference. Let us consider the
-equals reference-true rewrite rule. Here, we construct three sets of
-constraints. To construct the first set, $\Phi_\alpha$, we check if
-there exist constraint location pairs $(\phi_0, l_0) \in L(r_0)$ and
-$(\phi_1, l_1) \in L(r_1)$ such that $l_0$ and $l_1$ are the same.
-For all such constraints we create conjunctions of the constraints
-$\phi_0 \wedge \phi_1$ and add them to set $\Phi_\alpha$. Intutively
-these represent the constraints under which $r_0$ and $r_1$ point to
-the same location in the heap. The next set of constraints is $\Phi_0$
-which contains a constraints under which $r_0$ points to a
-corresponding location $l_i$ such that $r_1$ \emph{does not} point to
-$l_i$ under any constraint. Inversely, the set of constraints $\Phi_1$
-contains the set of constraints under which $r_1$ points to a
-corresponding location $l_j$ and $r_0$ \emph{does not} point to $l_j$
-under any constraint.
+rule returns true when two references $r_0$ and $r_1$ \emph{can} be
+equal. In GSE semantics checking equality of references is a simple
+comparision of two concrete object references. In the symbolic summary
+heap, however, we compare sets of constraint location pairs pointed to
+by each reference to determine if they could be equal.
 
-To the global constraint we add the disjunction of the constraints in
-$\Phi_\alpha$ to indicate that if any of the constraints are
-satisfiable, then references $r_0$ and $r_1$ can be true. Furthermore,
-we had to the global heap constraint, $\phi_g^\prime$, the
-conjunctions of negations to the constraints in $\Phi_0$ and
-$\Phi_1$. This indicates for locations that are not common to the
-references, the negations of their constraints are satisfiable. Before
-the rewrite rule returns true the satisfiability of the updated global
-heap constraint is checked.
+Consider the equals reference-true rewrite rule
+in~\figref{fig:eqs}. In order to check equality we construct three
+sets of constraints. For all constraint location pairs $(\phi_0, l_0)
+\in L(r_0)$ and $(\phi_1, l_1) \in L(r_1)$ such that $l_0$ and $l_1$
+are the same ($l_0 = l_1$) we create conjunctions of the constraints
+$\phi_0 \wedge \phi_1$ and add them to set $\Phi_\alpha$. Intutively,
+$\Phi_\alpha$ contains all constraints under which $r_0$ and $r_1$ may
+point to the same location in the symbolic summary heap. The second
+set, $\Phi_0$, contains constraints under which the reference $r_0$
+points corresponding locations such that the reference $r_1$
+\emph{does not} point to those locations under any
+constraint. Finally, the set, $\Phi_1$, contains constraints under
+which $r_1$ points to corresponding locations and $r_0$ \emph{does
+  not} point to those locations under any constraint.
 
-Consider the example in~\figref{fig:initHeap}(c), where we would like
-to check if $r_1^i$ and $r_2^i$ are equal. The set of constraint locations 
-pairs of the two references are:
+We use the three sets of constraints to update the current global heap
+constraint $\phi_g$ and create a new global heap constraint
+$\phi_g^\prime$. We add to $\phi_g$ the disjunction of the constraints
+in $\Phi_\alpha$ to indicate that if any of the constraints are
+satisfiable, then references $r_0$ and $r_1$ can be
+equal. Furthermore, we had to the global heap constraint,
+$\phi_g^\prime$, the conjunctions of negations to the constraints in
+$\Phi_0$ and $\Phi_1$. This indicates for locations that are not
+common to the references, the negations of their constraints are
+satisfiable. Before the rewrite rule returns true we check the
+satisfiability of the updated global heap constraint.
+
+Consider the example in~\figref{fig:initHeap}(c). In order to to check
+if $r_1^i$ and $r_2^i$ are equal we first get the constraint location
+pairs associated with each of the references:
 
@@
 \[
-\phi^\prime = \mathit{true} \wedge  (\phi_{1a}\; \implies\; \neg\phi_{2a} )\wedge (\phi_{1b}\; \implies\; \neg\phi_{2c} )  \wedge \phi_{2b}
+\phi^\prime = \mathit{true} \wedge [ (\phi_{1a}\; \wedge\; \phi_{2a} )\vee (\phi_{1b}\; \wedge\; \phi_{2c} ) ] \wedge \neg\phi_{2b} 
 \]
+
+\noindent{The equals references-false is the logical dual of the
+  reference-true rewrite rule. The references-false is shown
+  in~\figref{fig:eqs}.}

### 2014-11-11 tex/bisimulation.tex
Fixed some typoes

@@
 existence of a bisimularity relation between states related on $p \rgse p^\prime$
-and the states related on $q \rsym ^\prime$. A corollary is that $\rsym$ is
+and the states related on $q \rsym q^\prime$. A corollary is that $\rsym$ is
 both sound and complete with respect to $\rgse$. Only a summary of the
@@
 a new way to initialize heap objects that avoided initializing heaps
-that traverse redundant paths. The thought was to group together heaps
+that traverse the same control flow paths. The thought was to group together heaps
 into equivalence classes: all the heaps that followed the same control
@@
 indicates a null reference in the operation or a false outcome, and
-\emph{\com} is everything else in the language. A state relation is trivially extended to sets of states as
+\emph{\com} is everything else in the language. Any state relation, say $\rightarrow_x$, is trivially extended to sets of states as
 $$
@@
 $$
-\rsgse = \rgse^\mathit{A}
-\cup \rgse^\mathit{A\cdot} \cup \rgse^\mathit{W} \cup
-\rgse^\mathit{W\cdot} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E\cdot}
-\cup \rgse^\com
+\rsgse = \hookrightarrow_\gse^\mathit{A}
+\cup \hookrightarrow_\gse^\mathit{A\cdot} \cup \hookrightarrow_\gse^\mathit{W} \cup
+\hookrightarrow_\gse^\mathit{W\cdot} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E\cdot}
+\cup \hookrightarrow_\gse^\com
 $$

### 2014-11-11 tex/bisimulation.tex
Fixed a few typos

@@
 $$
-\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A\cdot} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W\cdot} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E\cdot} \cup \rgse^\com
+\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E\cdot} \cup \rgse^\com
 $$
@@
 $$
-Let $\rgse$ be the extension of $\rgse$ to sets of states.
+Let $\hookrightarrow_\gse$ be the extension of $\rgse$ to sets of states.
 $$
@@
 potential successors: a non-null and null reference. Respectively, the
-set $P \rgse^\com$ only has a single successor since those expressions
+set $P \rgse^\com P^\prime$ only has a single successor since those expressions
 are not related to control flow.
@@
 The functional equivalence between heaps on a homomorphism and
-constraint asserts a common structures in the two heaps under certain
+a homomorphism constraint asserts a common structures in the two heaps under certain
 conditions. The equivalence is used to related states in $p \rgse
@@
 \label{eqn:BisimulationForwards}
-\forall P^\prime\ ( P \rsgse P^\prime \Rightarrow \exists q^\prime\ ( (q \rsym q^\prime )\wedge (P^\prime\ \sqsubset\ q^\prime )))
+\forall P^\prime\ ( P \rsgse P^\prime \Rightarrow \exists q^\prime\ ( q \rsym q^\prime \wedge P^\prime\ \sqsubset\ q^\prime))
 \end{equation}
@@
 \label{eqn:BisimulationBackwards}
-\forall q^\prime\ ( q \rsym q^\prime\Rightarrow \exists P^\prime\ ( (P \rsgse P^\prime )\wedge (P^\prime\ \sqsubset\ q^\prime )))
+\forall q^\prime\ ( q \rsym q^\prime\Rightarrow \exists P^\prime\ ( P \rsgse P^\prime \wedge P^\prime\ \sqsubset\ q^\prime))
 \end{equation}
-If $\sqsubset$ is a bisimulation, then the greatest fixed point of $F_\sim(\sqsubset)$ is the bisimilarity relation.
+If $\sqsubset$ is a bisimulation, then the greatest fixed point of $F_\sim(\sqsubset)$ is the bisimilarity relation denoted by $\sim$.
 \end{definition}
@@
 \label{th:bisim}
-The relation $\sqsubset$ is a bisimulation.
+The relation $\sqsubset$ is a bisimulation: $\sqsubset\ \subseteq\ \sim$
 \end{theorem}

### 2014-11-11 tex/bisimulation.tex
Fixed corollaries

@@
 By definition of the bisimilarity relation. All of the common rules
-make no changes to the heap, so $P \subset q$ is included in the
+make no changes to the heap, so $P \sqsubset q$ is included in the
 functional. The other transition relations are supported by lemmas
@@
 
-The notion $p \stackrel{n}{\rgse} p^\prime$ denotes that $p^\prime$ is
+The notation $p \stackrel{n}{\rgse} p^\prime$ denotes that $p^\prime$ is
 the $n$-step successor of $p$, if it exists, and $q
@@
 \begin{corollary}[$\rsym$ is complete]
-If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$ then
+If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$ then for any $p \in P$
 $$
@@
 $$
-\forall q^\prime\ (q \stackrel{n}{\rsym} q^\prime \Rightarrow \exists p^\prime\ (p \stackrel{n}{\rgse} p^\prime \wedge p^\prime \sqsubset q^\prime))
+\forall q^\prime\ (q \stackrel{n}{\rsym} q^\prime \Rightarrow \exists p \in P\ (\exists p^\prime\ (p \stackrel{n}{\rgse} p^\prime \wedge p^\prime \sqsubset q^\prime)))
 $$

### 2014-11-11 tex/bisimulation.tex
Added stuff

@@
 algorithm in this paper. The principle theoretical result is the
-existence of a bisimularity relation between states related on $p \rgse p^\prime$
+existence of a bisimilarity relation between states related on $p \rgse p^\prime$
 and the states related on $q \rsym q^\prime$. A corollary is that $\rsym$ is
@@
 state of a given program, as there is single initial state, $P_o =
-\{p_o\}$, in any valid Javalite program. The initial state $\rsym$ is
+\{p_o\}$, in any valid Javalite program. The initial state for $\rsym$ is
 then defined as $q_o = p_o$; $P_o \sqsubset q_o$ is trivially shown.

### 2014-11-11 tex/related.tex
Started related work section. Added macro for GSE/GSESH to paper.tex. Updated bibliography

@@
 
-The related work goes here.
+\subsection{Symbolic Exection}
+Generalized symbolic execution \cite{GSE03} was the first symbolic execution method to handle linked data structures as inputs.
+Subsequent improvements to the method \cite{Deng:2006,Deng:2007} reduce path explosion by delaying path splitting over aliasing choices for as long as possible.
+However, since all of the above methods introduce nondeterminism during field reads and writes, they all worsen the path explosion problem to some extent or another.
+Since our heap representation does not introduce any nondeterminism beyond the level in standard symbolic execution, it will generally create fewer paths than these methods, sometimes by a wide margin.
+
+\subsection{Model Checking}
+Need to talk about Bounded Model Checking, etc.
+
+\subsection{Static Analysis}
+A number of static analysis techniques have been proposed that have some ability to reason about input heap structures.
+These techniques are usually over-approximations, often have difficulty reasoning about path-sensitive properties, or cannot reason about programs with recursive data structures.
+Moreover, static analysis methods are seldom useful for test-case generation.
+
+One notable static analysis method that is closely related to ours is the procedure summaries proposed by Isil and Tomas Dillig \cite{Dillig:2011}.
+Elements of their technique that are similar to ours include; references guarded by constraint expressions, conditional write semantics, and a general aversion to path splitting.
+However, their method is limited by most of the standard problems with static analysis techniques, including path sensitivity, imprecision, and recursive data structures.
+While their method has improved path sensitivity over standard static analysis methods, it remains limited by a statically-generated symbolic input heap, and cannot adapt to path-sensitive heap properties of the input heap.
+Thus, their method cannot determine a priori which nodes in the input heap are actually accessed by the program.
+It may potentially generate input heaps containing a significant number of nodes that have no impact on program execution.
+
+\subsection{Heap Representations}
+A number of other techniques model references using sets of guarded locations \cite{Xie:2005,Cherem:2007,Dillig:2011}.
+These sets, sometimes known as value sets or value summaries, allow multiple heaps to be represented simultaneously with a higher degree of precision than afforded by shape analysis.
+However, some of these previous attempts utilize non-local recursive definitions for objects.
+The impact of using recursive definitions for objects is two-fold.
+First, these techniques must use approximations to resolve reference inequalities, resulting in false positives in the results.
+Second, these techniques are incapable of reasoning about heaps with loops in the data structures due to infinite recursion during dereferencing.
+This means that either a large class of data structures must be avoided, or a large class of behaviors must be ignored.
+In our heap representation, object descriptions are entirely local, thus avoiding these pitfalls.

### 2014-11-11 tex/results.tex
Started related work section. Added macro for GSE/GSESH to paper.tex. Updated bibliography

--- 2014-10-31 tex/results.tex
@@
 \section{Empirical Evaluation}
-GSESH creates fewer execution paths than GSE, but it does so with increased path constraint complexity.
+\symtxt{} creates fewer execution paths than \gsetxt{}, but it does so with increased path constraint complexity.
 Determining the impact of this tradeoff in real-world applications is an important research question.
 
-Hypothesis
+Since the number of paths in \gsetxt{} is exponential in the number of lazy initializations, it is expected that programs for which the number of lazy initializations is proportional to program complexity will evaluate more quickly using \symtxt{}.
+On the other hand, since \symtxt{} places a greater burden on the constraint solver, it is expected that programs where the lazy initialization count is constant or slowly increasing with respect to program complexity will evaluate more quickly using \symtxt{}.
 
-\subsection{Implementation}
+\subsection{JPF Implementation}
+The Java Pathfinder (JPF) symbolic execution engine contains an implementation of \gsetxt{}, which we extended with our own implementation of \symtxt{}.
 
@@
 While these bounds may be asserted as invariants within the program in-situ, it is more practical to apply bounding via external means.
-There are several bounding techniques that may be applied to both GSE and GSESH, including execution path length bounding, k-bounding and n-bounding.
+There are several bounding techniques that may be applied to both \gsetxt{} and \symtxt{}, including execution path length bounding, k-bounding and n-bounding.
 k-bounding and n-bounding both operate by imposing limits on the size of the symbolic input heap, but differ in how such bounds are defined.
@@
 
-While k-bounding and n-bounding are applicable to both GSE and GSESH, they are not both equally suited for comparing the two methods.
+While k-bounding and n-bounding are applicable to both \gsetxt{} and \symtxt{}, they are not both equally suited for comparing the two methods.
 The main reason for this lies in how how each bounding technique impacts the functional equivalence of the respective methods.
-k-bounding preserves the functional equivalence of GSE and GSESH, a fact which can be established by induction over the length of reference chains from a given initial state.
-In contrast, GSE and GSESH are not generally functionally equivalent under n-bounding.
-The reason is that since a GSESH state must represent all possible GSE states on an execution path, it generally includes more locations than any single GSE state it represents.
-This difference in state counts makes it difficult to externally assert n-bounding in a manner that preserves functional equivalence between GSE and GSESH.
+k-bounding preserves the functional equivalence of \gsetxt{} and \symtxt{}, a fact which can be established by induction over the length of reference chains from a given initial state.
+In contrast, \gsetxt{} and \symtxt{} are not generally functionally equivalent under n-bounding.
+The reason is that since a \symtxt{} state must represent all possible \gsetxt{} states on an execution path, it generally includes more locations than any single \gsetxt{} state it represents.
+This difference in state counts makes it difficult to externally assert n-bounding in a manner that preserves functional equivalence between \gsetxt{} and \symtxt{}.
 Functional equivalence may be preserved in the case where n-bounds are asserted via in-situ invariants, but the significant increase in constraint complexity makes this approach impractical.
-For this reason, n-bounding is was not selected for comparing GSE to GSESH in the tests performed in this paper.
+For this reason, n-bounding is was not selected for comparing \gsetxt{} to \symtxt{} in the tests performed in this paper.
 
@@
 As with other bounding techniques, the usefulness of path-length bounding hinges on whether it preserves functional equivalence.
-While path-length bounding preserves functional equivalence for GSE and GSESH as formulated in this paper, it does not preserve it for the algorithms as they are implemented in JPF.
+While path-length bounding preserves functional equivalence for \gsetxt{} and \symtxt{} as formulated in this paper, it does not preserve it for the algorithms as they are implemented in JPF.
 The reason for the discrepancy lies in how states are defined in JPF.
@@
 A discrepancy in the length of the respective execution paths may be caused by any difference in nondeterminism between the two methods.
-This is significant, since the nondeterminism in GSESH and GSE differs in both field reads and in reference compares.
-Field reads in GSESH are deterministic, whereas in GSE they may initiate a nondeterministic lazy initialization.
-Conversely, in GSE address compares are deterministic, but in GSESH address compares require a nondeterministic assertion over the truth of the branch condition.
+This is significant, since the nondeterminism in \symtxt{} and \gsetxt{} differs in both field reads and in reference compares.
+Field reads in \symtxt{} are deterministic, whereas in \gsetxt{} they may initiate a nondeterministic lazy initialization.
+Conversely, in \gsetxt{} address compares are deterministic, but in \symtxt{} address compares require a nondeterministic assertion over the truth of the branch condition.
 For this reason, path-length bounding was not used for this experimental evaluation.
-For future tests, we are considering inserting artificial points of nondeterminism in order to establish functional equivalence of path-length bounds between GSE and GSESH.
+For future tests, we are considering inserting artificial points of nondeterminism in order to establish functional equivalence of path-length bounds between \gsetxt{} and \symtxt{}.
 
 \subsection{Evaluation} 
-Experimental set-up
+Experimental set-up: TO BE ADDED
 
@@
 
-In order to evaluate the performance of GSESH, the implementation was tested against three examples: LinkedList, BinarySearchTree, TreeMap.
+In order to evaluate the performance of \symtxt{}, the implementation was tested against three examples: LinkedList, BinarySearchTree, TreeMap.
 The LinkedList example tests performance on linked list data structures.
 The test program begins by assuming an object invariant before initiating a sequence of contains() method calls.
-This is a challenging example for GSE because each call to the contains() method contains a new lazy initialization, which in turn creates an exponential path expansion throughout program execution.
+This is a challenging example for \gsetxt{} because each call to the contains() method contains a new lazy initialization, which in turn creates an exponential path expansion throughout program execution.
 While the constraints for each path are easily solved, the sheer number of paths quickly becomes overwhelming.
@@
 Like the BinarySearchTree test, the TreeMap test is simply an assertion of an object invariant, in this case for a red/black tree.
-This example serves as a stress test for GSESH, since most of the nondeterminism comes from linear constraints over the shape of the tree, rather than aliasing constraints created during lazy initialization.
-In this case, the path advantage for GSESH is minimized.
+This example serves as a stress test for \symtxt{}, since most of the nondeterminism comes from linear constraints over the shape of the tree, rather than aliasing constraints created during lazy initialization.
+In this case, the path advantage for \symtxt{} is minimized.
 
@@
 
-Analysis
+The results of the experiments are shown in table \ref{tab:results}.
+
+\begin{table} [h]
+  \centering
+  \begin{tabular}{| c | c | c | c | c | c | c | c |}
+  \hline
+   \multirow{2}{*}{Method }&\multirow{2}{*}{ $k$ }
+   &\multicolumn{2}{|c|}{Time} &\multicolumn{2}{|c|}{ Paths }\\
+								&	&\gsetxt{}	&SH	&\gsetxt{} & SH\\
+   \hline
+    \multirow{3}{*}{LinkedList }&3	& 1 & 1  &1656 & 25		 \\
+   		 				& 4	& 3 & 2	&17485  & 39 \\
+   						& 5	& 20 & 3	&232743 & 56\\
+						& 6	& 338 & 8		&3731094 & 76\\
+    \hline
+    \multirow{3}{*}{BinarySearchTree }&1	& 0 & 1	& 4	 & 4\\
+   		 				& 2	& 1 & 1 	& 26 & 17\\
+   						& 3	& 12 & 7	& 305 & 118\\
+    \hline
+      \multirow{3}{*}{TreeMap}&1	& 0 & 1 	&9 & 9 \\
+   		 				&2	& 1 & 3		& 100 & 46 \\
+   						&3	&21 & 206	& 3026 & 547 \\
+
+    \hline
+  \end{tabular}
+  \caption{test results}
+  \label{tab:results}
+\end{table}
+
+\subsection{Analysis}
+
+LinkedList
+As expected, the repeated use of lazy initialization throughout the program causes an exponential increase in the number of paths explored by \gsetxt{}.
+By combining many of the \gsetxt{} paths, SH avoids the exponential path explosion, demonstrating dramatically reduced, though still exponential, execution time growth.
+Remarkably, path growth in the k-bound appears to be sub-linear.
+
+BST
+The BinarySearchTree example is somewhat of a mixed bag.
+
+TreeMap

### 2014-11-11 tex/related.tex
Added subsection on JPF implementation details

@@
 \subsection{Symbolic Exection}
-Generalized symbolic execution \cite{GSE03} was the first symbolic execution method to handle linked data structures as inputs.
+A number of adaptations to allow symbolic execution to cope with heap data structures have been proposed, beginning with Generalized symbolic execution \cite{GSE03}.
 Subsequent improvements to the method \cite{Deng:2006,Deng:2007} reduce path explosion by delaying path splitting over aliasing choices for as long as possible.
@@
 These sets, sometimes known as value sets or value summaries, allow multiple heaps to be represented simultaneously with a higher degree of precision than afforded by shape analysis.
-However, some of these previous attempts utilize non-local recursive definitions for objects.
+However, some of these previous attempts  \cite{Xie:2005,Cherem:2007} utilize non-local recursive definitions for objects.
 The impact of using recursive definitions for objects is two-fold.
@@
 In our heap representation, object descriptions are entirely local, thus avoiding these pitfalls.
+The other work \cite{Dillig:2011}, does not handle structures with loops despite having a local object representation, and has further drawbacks as previously enumerated.

### 2014-11-11 tex/results.tex
Added subsection on JPF implementation details

@@
 The Java Pathfinder (JPF) symbolic execution engine contains an implementation of \gsetxt{}, which we extended with our own implementation of \symtxt{}.
+Our heap representation lends itself to a number of simple performance optimizations, which have been included in the implementation.
+First, solutions to previous constraint problems are cached and re-used, to avoid sending a large number of queries to the SMT solver.
+Second, because only small portions of the path condition change from one state to the next, incremental solving is enabled to provide a substantial performance increase.
+Finally, by examining the location sets involved in a reference compare operation, a large number of reference compare instructions may be dispatched without consulting the solver to begin with.
+
+For practical purposes, the implementation also includes a number of features not shown in the simple language described in section 2.
+For example, integer operations are required in order to reason about ordered data structures such as binary search trees and red/black trees.
+The description of these operations is outside the scope of this paper.
 
 \subsection{Bounding}
-In order to perform a practical evaluation of programs involving recursive data structures, it is generally necessary to impose some sort of bounding to eliminate the number of lazy initializations to a manageable level.
+In order to perform a practical evaluation of programs involving recursive data structures, it is generally necessary to impose some sort of bounding to reduce the number of lazy initializations to a manageable level.
 While these bounds may be asserted as invariants within the program in-situ, it is more practical to apply bounding via external means.
@@
 
-BST
 The BinarySearchTree example is somewhat of a mixed bag.

### 2014-11-11 tex/conclusion.tex
Added conclusion section.

\section{Conclusion}

\subsection{Future Work}
While our representation reduces paths significantly compared to \gsetxt{}, there remains room for improvement. Another way to reduce path explosion is through state merging. We are investigating ways of merging states at join points in the program, perhaps involving a combination of heap merging and / or heap equivalence testing.

A key advantage of many symbolic execution techniques is the ability to generate test inputs to exercise every possible control flow path. Our technique could be adapted for test input generation by maintaining an explicit input heap in addition to the actual heap which is mutated as the program progresses.

We are also contemplating a variety of performance optimizations. Due to the structure of the constraints used in the heap representation, our representation is amenable to sophisticated results-caching schemes such as Green. Likewise, a considerable amount of solver time is spent calculating object invariants during program initialization. In order to improve responsiveness during debugging operations, it should be possible to cache object invariants between test runs in to obtain a substantial speed-up.

### 2014-11-11 tex/precise.tex

@@
 \section{Generating Symbolic Heap Summaries}
+
+In this section we present the rules for the $\rsym$ relation. The are
+three sets of rewrite rules: the initialization of symbolic
+references, the field access and write rules, and finally checking the
+equality and inequality of references. Here we describe each of the
+rules. They consist the core of the symbolic heap summary approach.
 
@@
 
-In this section we present the Javalite rewrite rules for the
-initialization of references in the symbolic heap summary. The
+In this section we present the rewrite rules for the initialization of
+references in the $\rsym$ relation for a symbolic heap summary. The
 initialization rules are defined on the bi-partite graph consisting of
-references and locations. In contrast, the heap summarization approach
-creates a single branch that contains the summarization for all the
-initialization in a single bi-partitate graph.
+references and locations. In the $\rgse$ relation during
+initialization of a symbolic references, it is non-deterministically
+assigned to null, new instance of the object, and alias any previously
+initialized symbolic reference. In contrast, the heap summarization
+approach creates a single branch that contains the summarization for
+all the initialization in a single bi-partitate graph.
 
@@
 technique is shown in~\figref{fig:symInit}. Given the unitialized set
-$\mathbb{UN}$ for field $f$, the $\mathit{min}_l$ function returns the
-constraint location pair based on a lexical ordering of locations. The
-init$_r$ method returns a new input reference $r_f$ while the
-fresh$_f$ returns a new location of type $C$. The set $\rho$ contains
-the set of reference location, $(r_a, l_a)$, pairs that the current
-field may alias. The pair $(r_a, l_a)$ is contained in the set $ \rho
-$ if the following conditions hold: (i) $r_a$ is part of the input
-references initialized in the summary heap, (ii) $r_a$ is in the
-pre-image of $l_a$, (iii) and the type of $l_a$ is the same as the
-type of the field being initialized.
+$\mathbb{UN}$ for field $f$, the $\mathit{min}_l$ function returns
+$(\phi_x, l_x)$ based on a lexical ordering of uninitialized locations
+in $\Lambda$. The init$_r$ method returns a new input reference $r_f$
+while the fresh$_f$ returns a new location of type $C$. The set $\rho$
+contains the set of reference location pairs, $(r_a, l_a)$, that the
+field being initialized may alias. The pair $(r_a, l_a)$ is contained
+in the set $ \rho $ if the following conditions hold: (i) $r_a$ is
+part of the input references initialized in the summary heap, (ii)
+$r_a$ is in the pre-image of $l_a$, (iii) and the type of $l_a$ is the
+same as the type of the field being initialized.
 
 There are three constraint-location pair sets that correspond to
-non-deterministic choices in GSE: (a) $\theta_\mathit{null}$ that
-creates a constraint that states $r_f$ is null under which it points
-to $l_\mathit{null}$, (b) $\theta_\mathit{new}$ the constraint that
-$r_f$ is not null and it does not alias another reference in set
-$\rho$ under which it points to the newly created location $l_f$, (c)
-and $\theta_\mathit{alias}$ where for each element in the set $(r_a,
-l_a) \in \rho$ it creates a constraints that $r_f$ is not null, points
-to $r_a$, and does not point to any reference contained in
-$(r_a^\prime, l_a^\prime) \in \rho$ such that $r_a \neq
-r_a^\prime$. Additionally $\theta_\mathit{orig}$ allows for the
-possibility that the field continues to remain uninitialized since the
-heap is symbolic. We refer to this initialization in the summary
-machine as conditional initialization. Finally, the fields of the
-reference $r_f$ are marked as uninitialized.
+non-deterministic choices in GSE: (a) $\theta_\mathit{null}$ contains
+a constraint $r_f = r_\mathit{null}$ paired with the location
+$l_\mathit{null}$, (b) $\theta_\mathit{new}$ creates a pair with the
+constraint $r_f$ is not null and it does not alias any reference in
+set $\rho$ under and a newly created location $l_f$, (c) and
+$\theta_\mathit{alias}$ where for each element in the set $(r_a, l_a)
+\in \rho$ it creates a constraints that $r_f$ is not null, points to
+$r_a$, and does not point to any reference contained in $(r_a^\prime,
+l_a^\prime) \in \rho$ such that $r_a < r_a^\prime$ based on a lexical
+ordering of initialized references. Additionally
+$\theta_\mathit{orig}$ allows for the possibility that the field
+continues to remain uninitialized since the heap is symbolic. We refer
+to this initialization in the summary machine as conditional
+initialization. Finally, the fields of the reference $r_f$ are marked
+as uninitialized. In the post condition of the rule the reference
+$r_f$ points to $\theta$ which contains the union of all the
+constraint location pairs sets, and the field $f$ points to the new
+reference $r_f$ in the summary heap.
 
-In the post condition of the rule the reference $r_f$ points to
-$\theta$ which contains the union of all the constraint location pairs
-sets, and the field $f$ points to the new reference $r_f$ in the
-summary heap.  Note that the summarize rule invoked repeatedly until
+\begin{comment}
+ Note that the summarize rule invoked repeatedly until
 the set of unitialized constraint location pairs for field $f$ is
-empty. In other words the set $\lambda$ is empty. This consititutes
+empty. In other words the set $\Lambda$ is empty. This consititutes
 the summarize end rule in~\figref{fig:symInit}.
+\end{comment}
 
@@
 \begin{tabular}[c]{l}
-$\rho := \{ (r_1^i, r_1^i \neq r_\mathit{null}, l_1 \}$ \\
+$\rho := \{ (r_1^i, l_1 \}$ \\
 $\theta_\mathit{null} := \{ ( r_2^i = r_\mathit{null}, l_\mathit{null}) \}$\\
@@
 
-We visualize the initialization process in the symbolic summarization
-technique in~\figref{fig:initHeap}. The heap
-in~\figref{fig:initHeap}(a) represents the initial heap. The
+We visualize the initialization process in~\figref{fig:initHeap}. The
+graph in~\figref{fig:initHeap}(a) represents the initial heap. The
 references with the superscript $s$ indicates that it is a local
-reference. In~\figref{fig:initHeap} $r_0^s$ represents the reference
-for the $\mathit{this}$ instance which has two fields $x$ and $y$ of
-the same type. The reference $r_0^s$ points to the location
-$l_0$. Note that when no constraint is specified, then there is a
-implicit $\mathit{true}$ constraint. In~\figref{fig:initHeap} $r_0^s$
-points to $l_0$ on $\mathit{true}$. The fields $x$ and $y$ point to
-the uninitialized reference $r_\mathit{un}$. The reference
-$r_\mathit{un}$ points to the uninitialized location $l_\mathit{un}$
-on the $\mathit{true}$ constraint.
+reference. In~\figref{fig:initHeap} $r_0^s$ represents a local
+reference for the $\mathit{this}$ reference which has two fields $x$
+and $y$ of the same type; reference $r_0^s$ points to location
+$l_0$. Note that when no constraint is specified in the graphs, then
+there is a implicit $\mathit{true}$ constraint, for example, $r_0^s$
+points to $l_0$ on the constraint $\mathit{true}$. The fields $x$ and
+$y$ point to the uninitialized reference $r_\mathit{un}$.
 
-The graph in~\figref{fig:initHeap}(b) represents the summary heap
-after the initialization of the $\mathit{this}.x$ field while the
-graph in~\figref{fig:initHeap}(c) represents the summary heap after
-the initialization of the $\mathit{this}.y$ field following the
-initialization of $\mathit{this}.x$. The list
+% The reference $r_\mathit{un}$ points to the uninitialized location
+%$l_\mathit{un}$ on the $\mathit{true}$ constraint.
+
+The graph in~\figref{fig:initHeap}(b) represents the symbolic heap
+summary after the initialization of the $\mathit{this}.x$ field while
+the graph in~\figref{fig:initHeap}(c) represents the symbolic heap
+summary after the initialization of the $\mathit{this}.y$ field
+following the initialization of $\mathit{this}.x$. The list
 in~\figref{fig:initHeap}(d) represents the various sets constructed in
-the rewrite system when the initialization takes places. We also
-define the constraints of references to their corresponding labels in
-the graph.
+the summarize rule during the initialization of $\mathit{this}.y$. We
+also define values of constraints used as labels in the graph.
 
@@
 
-\subsection{Accessing a Field Reference}
+\subsection{Reading and Writing References}
 \input{precise-fig-incomplete}
@@
 
-There are two rewrite rules in~\figref{fig:fHeap}(a), one for field
-access and the other for field write. Let us consider the rewrite rule
-for field access. The first check we perform is whether there exists a
-constraint location pair for the $r$ being accessed such that the
-location is not null and the constraint when conjuncted with the
-global constraint is satisfiable. Next we extract all possible
-constraints under which $r$ points to a null location such that the
-constraint is satisfiable under the current global constraint,
-$\phi_g$. The negation of these constraints are added to the global
-constraint to create a new global constraint $\phi_g^\prime$. The
-update to the global constraint ensures that access of the field $f$
-happens only on non-null locations. The type $C$ of the field is
-extracted and passed to rewrite rule that performs the initialization
-of the symbolic heap. The initialization rules are described earlier
-in this section.
+There are two rewrite rules in~\figref{fig:fHeap}(a), one for reading
+the value of a field (field-access) and the other when we write to a
+field (field-write). In both the field rewrite rules we first check we
+perform is whether there exists a constraint location pair for the $r$
+being accessed such that the location is not null and the constraint
+when conjuncted with the global constraint is satisfiable. Next we
+extract all possible constraints under which $r$ points to a null
+location such that the constraint is satisfiable under the current
+global constraint, $\phi_g$. The negation of these constraints are
+added to the global constraint to create a new global constraint
+$\phi_g^\prime$. The update to the global constraint ensures that
+access or write of the field $f$ happens only on non-null
+locations. There are rewrite rules for accessing and writing to fields
+on null locations where it leads the current program execution state
+to an error state. The rewrite rules for the accessing and writing to
+null locations are presented in the supplemental document.
 
-Recall that during the initialization the rewrite rules
-in~\figref{fig:symHeap} add input references that map to fields being
-initialized.  Once the initialization is complete, however, we create
-a new local reference $r^\prime$. An important property of the
-references in the bi-partiate graph is that they are
-\emph{immutable}. Hence we de-reference the initialized input
-reference, assign its value to the the new local reference, and return
-the local reference. In order to de-reference a field $r.f$ we define
-a helper function which is called the value set.
+In the field-access rewrite rule in~\figref{fig:fHeap}(a) after the
+non-nullness check we extract the The type $C$ of the field is
+extracted and invoke the summarize rewrite rule
+in~\figref{fig:symInit} that performs the initialization of the field
+if it points to uninitialized locations. Once the initialization is
+complete, we create a new local reference $r^\prime$. An important
+property of the references in the bi-partiate graph is that they are
+\emph{immutable}. Hence we create a new local reference and assign it
+to the initialized reference, and return the local reference. In order
+to de-reference a field $r.f$ we define a helper function which is
+called the value set.
 
@@
 
-\subsection{Writing to a Field}
-
-The reference $r_x$ is the base pointer whose field is being written
-to while $r$ is the target reference. We look up the value of the base
-reference in the environment $\eta(x)$. The set $\Psi_x$ is the set of
-tuples of constraints, locations, and references which provide the
-reference chains leading from $r_x$ to the reference of the field,
-$r_\mathit{curr}$, being written to through $\phi$ and $l$.The goal is
-to overwrite the $r_\mathit{curr}$ references with the target
-references. Since the target of the write is $r$, we first check that the
-location constraint pairs of $L(r)$ are satisfiable when accessed
-through the $r_x$ chain. This is accomplished by the strengthing
+The field-write rewrite rule in~\figref{fig:fHeap}(a) after the
+non-nullness check we We look up the value of the base reference in
+the environment $\eta(x)$.  The reference $r_x$ is the base pointer
+whose field, $r_\mathit{curr}$ is being written to to while the
+reference $r$ is the target reference. The set $\Psi_x$ contains
+tuples $(\phi l r_\mathit{curr})$ of constraints, locations, and
+references. These tuples represent access chains leading from $r_x$ to
+the reference of the field, $r_\mathit{curr}$. The goal is to
+overwrite the $r_\mathit{curr}$ references with the target
+references. Since the target of the write is $r$, we first check that
+the location constraint pairs of $L(r)$ are satisfiable when accessed
+through the $r_x$ chain. This is accomplished by the strengthening
 function.
@@
 
-Additionally, we also check for conditions where the write is not possible
+Note that the write is conditional. In the case that $\phi$ is true
+then $r_\mathit{curr}$ will point to the constraint location pairs of
+$L(r)$ while if $\phi$ is false then $r_\mathit{curr}$ will continue
+to point to the constraint location pair it is currently pointing to.
+Again since the references are immutable we create a new reference for
+each $r_\mathit{curr}$ and point them to the target constraint
+location pairs.
+
+Consider the example shown in~\figref{fig:fHeap}(b) where we assign
+$\mathit{this}.x := \mathit{this}.y$. Note that
+in~\figref{fig:initHeap}(c) $\mathit{this}.x$ is represented by
+$r_1^i$. After applying the field-write rule the reference $r_1^i$ is
+replaced by the fresh reference $r_4$ which now points to target
+$\mathit{this}.y$ represented by $L(r_2^i)$.
 
@@
 \end{center}
-\caption{field write for this.x = this.y sets}
+\caption{FIXME: When will I get a caption}
 \label{fig:faHeapSets}

### 2014-11-11 tex/heap.tex
Halfway through describing heaps. Fixed several small typos, spacing issues, and errors

@@
-\section{Heap: A Bi-partiate Graph}
+\subsection{Heaps as Bipartite Graphs}
+ADD REFERENCES ARE IMMUTABLE.
+DEFINE $\rsym$ and $\rgse$.
 
-The heap in this work is a labeled bipartite graph consisting of
-references, $\cfgnt{r}$, and locations, $\cfgnt{l}$. The machine
-syntax in \figref{fig:machine-syntax} defines that graph in
-$\cfgnt{L}$, the location map, and $\cfgnt{R}$, the reference map. As
-done with the environment, $\cfgnt{L}$ and $\cfgnt{R}$ are treated as
-partial functions where $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is
-the set of location-constraint pairs in the heap associated with the
-given reference, and $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is
-the reference associated with the given location-field pair in the
-heap.
+A novel contribution is the representation of the heap with a labeled
+bipartite graph consisting of references, $\cfgnt{r}$, and locations,
+$\cfgnt{l}$. The machine syntax in \figref{fig:machine-syntax} defines
+that graph in $\cfgnt{L}$, the location map, and $\cfgnt{R}$, the
+reference map. As done with the environment, $\cfgnt{L}$ and
+$\cfgnt{R}$ are treated as partial functions where $\cfgnt{L}(r) =
+\{(\phi\ \cfgnt{l})\ ...\}$ is the set of location-constraint pairs in
+the heap associated with the given reference, and
+$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the reference
+associated with the given location-field pair in the heap.
 
@@
 location is uninitialized at the point of execution.
+
+\begin{definition}
+\label{def:state}
+The set of \textbf{states} $\mathcal{S}$ is defined as the set of strings matching the pattern $s$ in \ref{fig:machine-syntax}.
+\end{definition}
+
+\begin{definition}
+\label{def:initstate}
+$\mathcal{S}_0$ is defined as the set of \textbf{initial states}.
+An initial state is a state meeting the following conditions:  The range of L has exactly three locations: $l_{null}$, $l_{un}$, and $l_0$, the function R is defined only for location $l_0$, and for any field $f$, $R(l_0,f)$ returns $r_{un}$.
+\end{definition}
+
+The rewrite rules that define the Javalite semantics are presented in
+the supplemental document accompanying the paper.
+
+\begin{definition}
+A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times \mathcal{S} $, which relates machine states with successor states.
+Two important state transition relations are \textbf{GSE} $\rgse$ and \textbf{symbolic} $\rsym$.
+Each of these use a separate relation for initialization: $\rinit$ for GSE and $\rsum$ for symbolic.
+All of these transition relations are defined in \figref{fig:lazy}, \figref{fig:lazyInit}, \figref{fig:sym}, and \figref{fig:symInit}.
+\end{definition}

### 2014-11-11 tex/javalite.tex
Halfway through describing heaps. Fixed several small typos, spacing issues, and errors

@@
-\section{Preliminaries}
+\section{Javalite}
+The algorithm for generalized symbolic execution with symbolic heaps
+is presented using Javalite. Javalite is a syntactic machine defined
+as rewrites on a string \cite{saints-MS}. The semantics are small-step
+using a CESK model with a (C)ontrol string representing the expression
+being evaluated, an (E)nvironment for local variables, a (S)tore for
+the heap, and a (K)ontinuation for what is to be executed next. The
+semantics of the original Javalite machine, and its machine syntax,
+are changed to reflect generalized symbolic execution and then
+generalized execution with symbolic heaps.
 
-\figref{fig:surface-syntax} defines the surface syntax for the
-Javalite language \cite{saints-MS}. \figref{fig:machine-syntax} is the
-machine syntax. Javalite is syntactic machine defined as rewrites on a
-string. The semantics use a CEKS model with a (C)ontrol string
-representing the expression being evaluated, an (E)nvironment for
-local variables, a (K)ontinuation for what is to be executed next, and
-a (S)tore for the heap.
+The surface syntax (input) for Javalite is in
+\figref{fig:surface-syntax} with the machine syntax (state) in
+\figref{fig:machine-syntax}. Terminals are in bold face while
+non-terminals are italicized. Ellipses indicate zero or more
+repetitions. Tuples omit the commas for compactness. The language
+itself uses s-expressions for convenience.
 
 \input{surface-syntax}
+\input{machine-syntax}
 
-\subsection{Environment}
-The environment, $\eta$, associates a variable $\cfgnt{x}$ with a
-value $\cfgnt{v}$. The value can be a reference, $\cfgnt{r}$ or one of
-the special values $\cfgt{null}$, $\cfgt{true}$, or
-$\cfgt{false}$. Although the Javalite machine is purely syntactic, for
-clarity and brevity in the presentation, the more complex structures
-such as the environment are treated as partial functions. As such,
-$\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference mapped to the variable
-in the environment. The notation $\eta^\prime = \eta[\cfgnt{x} \mapsto
-  \cfgnt{v}]$ defines a new partial function $\eta^\prime$ that is
-just like $\eta$ only the variable $\cfgnt{x}$ now maps to
-$\cfgnt{v}$.
+A Javalite program, $\cfgnt{P}$, is a registry of classes, $\mu$, with
+a tuple indicating a class, $\cfgnt{C}$, and a method, $\cfgnt{m}$,
+where execution starts. The only primitive type in Javalite is
+Boolean. Classes have fields, $([\cfgnt{T}\ \cfgnt{f}]\ ...)$, and
+methods, $(\cfgnt{M}\ ...)$. Methods only take a single
+parameter. Expressions, $\cfgnt{e}$, are somewhat typical with
+$\cfgt{:=}$ indicating assignment, $\cfgt{=}$ indicating comparison,
+$\cfgt{\$}$ as the dot-operator for field access, and $\cfgt{@}$ as
+the dot-operator for method invocation. There is no explicit return
+statement in Javalite; rather, the value of the last expression is
+used as a return value. A variable is always indicated by \cfgnt{x}
+and a value by \cfgnt{v}. A value can be a reference in the heap,
+$\cfgnt{r}$, or any of the special values. It is assumed that only
+type correct programs are given as input to the machine.
+
+The state of the Javalite machine (\figref{fig:machine-syntax}),
+$\cfgnt{s}$, includes the program registry, a pair of functions
+defining the heap $\lp\cfgnt{L}\ \cfgnt{R}\rp$, which is the store, a
+constraint, $\phi$, defined over references in the heap, the
+environment, $\eta$, for local variables, and the continuation
+$\cfgnt{k}$. The more complex structures such as the environment are
+defined as lists which start with empty, \cfgnt{mt}. The rewrite rules
+that define the semantics treat these lists as partial
+functions. As such, $\eta(\cfgnt{x}) = \cfgnt{r}$ is the
+reference mapped to the variable $\cfgnt{x}$. The notation
+$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
+partial function $\eta^\prime$ that is just like $\eta$ only the
+variable $\cfgnt{x}$ now maps to $\cfgnt{v}$.
+
+The continuation $\cfgnt{k}$ helps accomplish the small-step semantics
+by indicating where the hole, $\cfgt{*}$, is located, by storing
+temporary computations, and by keeping track of the next
+computation. For example, the continuation
+$\lp\cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp$ indicates
+that the machine is currently computing the expression for the object
+reference on which the field $\cfgnt{f}$ is going to be accessed. Once
+the field access is complete, the machine continues with $\cfgnt{k}$.
+
+\input{heap}

### 2014-11-11 tex/heap.tex
Minor checkpoint

--- 2014-10-13 tex/heap.tex
@@
-\section{Heap: A Bi-partiate Graph}
+\subsection{Heaps as Bipartite Graphs}
+An important aspect, and a novel contribution, of symbolic heaps its
+representation as a labeled bipartite graph consisting of
+references, $\cfgnt{r}$, and constraint location pairs,
+$\lp\phi\ \cfgnt{l}\rp$. The heap structure conveys that the actual
+location pointed to by a reference is conditional on aliasing
+relationships within the heap. In this way, the graph represents sets
+of heaps with the conditions under which those heaps exist.
 
-The heap in this work is a labeled bipartite graph consisting of
-references, $\cfgnt{r}$, and locations, $\cfgnt{l}$. The machine
-syntax in \figref{fig:machine-syntax} defines that graph in
-$\cfgnt{L}$, the location map, and $\cfgnt{R}$, the reference map. As
-done with the environment, $\cfgnt{L}$ and $\cfgnt{R}$ are treated as
-partial functions where $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is
-the set of location-constraint pairs in the heap associated with the
-given reference, and $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is
-the reference associated with the given location-field pair in the
-heap.
+The machine syntax in \figref{fig:machine-syntax} defines that graph
+in $\cfgnt{L}$, the location map, and $\cfgnt{R}$, the reference
+map. As done with the environment, $\cfgnt{L}$ and $\cfgnt{R}$ are
+treated as partial functions where $\cfgnt{L}(r) =
+\{(\phi\ \cfgnt{l})\ ...\}$ is the set of location-constraint pairs in
+the heap associated with the given reference, and
+$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the reference
+associated with the given location-field pair in the heap. Predicate
+calculus is used to describe the more complex updates to the heap in
+the semantics.
 
-As the updates to $\cfgnt{L}$ and $\cfgnt{R}$ are complex in the
-machine semantics, predicate calculus is used to describe updates to
-the functions. Consider the following example where $\cfgnt{l}$ is
-some location and$\rho$ is a set of references.
-\[
-\cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}][\forall \cfgnt{r}^\prime \in \rho\ \lp \cfgnt{r}^\prime \mapsto \lp \cfgt{true}\ l_\mathit{null}\rp \rp ]
-\]
-The new partial function $\cfgnt{L}^\prime$ is just like $\cfgnt{L}$
-only it remaps $\cfgnt{r}$, and it remaps all the references in
-$\rho$.
+There are several properties of the heap that are invariant and
+important to the correctness of the algorithm.
+\begin{compactitem}
+\item ADD REFERENCES ARE IMMUTABLE
+\end{compactitem}
 
@@
 
-You can think references as a pointers to sets of locations. More
-concretely, a reference is an integer that the $R$ function maps to a
-set of constraint, location pairs that define where it points
-to. Within a machine state, references are string encodings of
-integers.
-
-\begin{definition}
-The set of \textbf{references} $\mathcal{R}$ is defined as the set of natural numbers
- $$\mathcal{R} = \mathbb{N}$$
-\end{definition}
-
-In order to make the distinction between different types of references, we partition the set of references using modular arithmetic.
-Stack references are those references which are created as a result of a field read.
-The total number of references in a representing state and a represented state are generally not the same.
-However, the number of references on the stack in either state is always the same.
-
-\begin{definition}
-The set of \textbf{stack references} $\mathcal{R}_t$ is defined as
- $$\mathcal{R}_t =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 0\}$$. 
-\end{definition}
-
-Input heap references are references that exist prior to program execution in the symbolic input heap.
-While this set of references may be infinite, they are discovered one at a time via lazy initialization.
-
-\begin{definition}
-The set of \textbf{input heap references} $\mathcal{R}_h$ is defined as
- $$\mathcal{R}_h =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 1\}$$. 
-\end{definition}
-
-\begin{definition}
-The set of \textbf{new heap references} $\mathcal{R}_f$ is defined as
- $$\mathcal{R}_f =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$. 
-\end{definition}
-
-\begin{definition}
-For a given function $f:A \mapsto B$, the \textbf{image} $f^\rightarrow$ and \textbf{preimage} $f^\leftarrow$ are defined as
-\begin{align}
- f^\rightarrow &= \{ f(a) \mid a \in A\}\\
- f^\leftarrow &= \{ a \mid f(a) \in B \}
- \end{align}
- The bracket notation $ f^\rightarrow [C] $ is used to denote that the image is drawn from a specific subset:
- \begin{align}
- f^\rightarrow [C] &= \{ f(a) \mid a \in C\}\\
- f^\leftarrow [D] &= \{ a \mid f(a) \in D \}
- \end{align}
- Where $C \subset A$ and $D \subset B$
-\end{definition}
-
-A special reference, $\cfgnt{r}_\mathit{un}$, and location,
-$\cfgnt{l}_\mathit{un}$, is introduced to support lazy
-initialization. The '$\mathit{un}$' is to indicate the reference or
-location is uninitialized at the point of execution.
+DEFINE $\rsym$ and $\rgse$.

### 2014-11-11 tex/proofs.tex
Minor checkpoint

@@
 \section{Proofs}
+
+\begin{definition}
+The set of \textbf{references} $\mathcal{R}$ is defined as the set of natural numbers
+ $$\mathcal{R} = \mathbb{N}$$
+\end{definition}
+
+In order to make the distinction between different types of references, we partition the set of references using modular arithmetic.
+Stack references are those references which are created as a result of a field read.
+The total number of references in a representing state and a represented state are generally not the same.
+However, the number of references on the stack in either state is always the same.
+
+\begin{definition}
+The set of \textbf{stack references} $\mathcal{R}_t$ is defined as
+ $$\mathcal{R}_t =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 0\}$$. 
+\end{definition}
+
+Input heap references are references that exist prior to program execution in the symbolic input heap.
+While this set of references may be infinite, they are discovered one at a time via lazy initialization.
+
+\begin{definition}
+The set of \textbf{input heap references} $\mathcal{R}_h$ is defined as
+ $$\mathcal{R}_h =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 1\}$$. 
+\end{definition}
+
+\begin{definition}
+The set of \textbf{new heap references} $\mathcal{R}_f$ is defined as
+ $$\mathcal{R}_f =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$. 
+\end{definition}
+
+\begin{definition}
+For a given function $f:A \mapsto B$, the \textbf{image} $f^\rightarrow$ and \textbf{preimage} $f^\leftarrow$ are defined as
+\begin{align}
+ f^\rightarrow &= \{ f(a) \mid a \in A\}\\
+ f^\leftarrow &= \{ a \mid f(a) \in B \}
+ \end{align}
+ The bracket notation $ f^\rightarrow [C] $ is used to denote that the image is drawn from a specific subset:
+ \begin{align}
+ f^\rightarrow [C] &= \{ f(a) \mid a \in C\}\\
+ f^\leftarrow [D] &= \{ a \mid f(a) \in D \}
+ \end{align}
+ Where $C \subset A$ and $D \subset B$
+\end{definition}
+
+A special reference, $\cfgnt{r}_\mathit{un}$, and location,
+$\cfgnt{l}_\mathit{un}$, is introduced to support lazy
+initialization. The '$\mathit{un}$' is to indicate the reference or
+location is uninitialized at the point of execution.
+
+\begin{definition}
+\label{def:state}
+The set of \textbf{states} $\mathcal{S}$ is defined as the set of strings matching the pattern $s$ in \ref{fig:machine-syntax}.
+\end{definition}
+
+\begin{definition}
+\label{def:initstate}
+$\mathcal{S}_0$ is defined as the set of \textbf{initial states}. An
+initial state is a state meeting the following conditions: The range
+of L has exactly three locations: $l_{null}$, $l_{un}$, and $l_0$, the
+function R is defined only for location $l_0$, and for any field $f$,
+$R(l_0,f)$ returns $r_{un}$.
+\end{definition}
+
+The rewrite rules that define the Javalite semantics are presented in
+the supplemental document accompanying the paper.
+
+\begin{definition}
+A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary
+relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times
+\mathcal{S} $, which relates machine states with successor states. Two
+important state transition relations are \textbf{GSE} $\rgse$ and
+\textbf{symbolic} $\rsym$. Each of these use a separate relation for
+initialization: $\rinit$ for GSE and $\rsum$ for symbolic. All of
+these transition relations are defined in \figref{fig:lazy},
+\figref{fig:lazyInit}, \figref{fig:sym}, and \figref{fig:symInit}.
+\end{definition}
 

### 2014-11-11 tex/bisimulation.tex
Added heap properties

@@
 $$
-\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E\cdot} \cup \rgse^\com
+\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E^\prime} \cup \rgse^\com
 $$
@@
 \cfgnt{k}\rp$, \emph{E} is a reference compare $\lp
-\cfgnt{v}\ \cfgt{=}\ \cfgnt{*} \rightarrow \cfgnt{k}\rp$, $\cdot$
+\cfgnt{v}\ \cfgt{=}\ \cfgnt{*} \rightarrow \cfgnt{k}\rp$, the prime symbol
 indicates a null reference in the operation or a false outcome, and
@@
 \rsgse = \hookrightarrow_\gse^\mathit{A}
-\cup \hookrightarrow_\gse^\mathit{A\cdot} \cup \hookrightarrow_\gse^\mathit{W} \cup
-\hookrightarrow_\gse^\mathit{W\cdot} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E\cdot}
+\cup \hookrightarrow_\gse^\mathit{A^\prime} \cup \hookrightarrow_\gse^\mathit{W} \cup
+\hookrightarrow_\gse^\mathit{W^\prime} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E^\prime}
 \cup \hookrightarrow_\gse^\com
@@
 
+DEFINE $S$ and $S_{FA}$ and unify on the shorthand as $S_A$. 
 \begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]

### 2014-11-11 tex/heap.tex
Added heap properties

@@
 \subsection{Heaps as Bipartite Graphs}
-An important aspect, and a novel contribution, of symbolic heaps its
+An important aspect, and a novel contribution, of a symbolic heap is its
 representation as a labeled bipartite graph consisting of
 references, $\cfgnt{r}$, and constraint location pairs,
-$\lp\phi\ \cfgnt{l}\rp$. The heap structure conveys that the actual
+$\lp\phi\ \cfgnt{l}\rp$. The heap structure itself captures that the actual
 location pointed to by a reference is conditional on aliasing
@@
 
-The machine syntax in \figref{fig:machine-syntax} defines that graph
-in $\cfgnt{L}$, the location map, and $\cfgnt{R}$, the reference
-map. As done with the environment, $\cfgnt{L}$ and $\cfgnt{R}$ are
-treated as partial functions where $\cfgnt{L}(r) =
-\{(\phi\ \cfgnt{l})\ ...\}$ is the set of location-constraint pairs in
-the heap associated with the given reference, and
-$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the reference
-associated with the given location-field pair in the heap. Predicate
-calculus is used to describe the more complex updates to the heap in
-the semantics.
+The graph is expressed in in $\cfgnt{L}$, the location map, and
+$\cfgnt{R}$, the reference map. As done with the environment,
+$\cfgnt{L}$ and $\cfgnt{R}$ are treated as partial functions where
+$\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the set of
+location-constraint pairs in the heap associated with the given
+reference, and $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the
+reference associated with the given location-field pair in the
+heap. Predicate calculus is used to describe the more complex updates
+to the heap in the semantics.
 
 There are several properties of the heap that are invariant and
-important to the correctness of the algorithm.
+important to the correctness.
 \begin{compactitem}
-\item ADD REFERENCES ARE IMMUTABLE
-\end{compactitem}
-
-The location $\cfgnt{l}_\mathit{null}$ is a special location in the
+\item \textbf{Immutable references}: a reference does not change in
+  the location map; it always points to the same set of constraint
+  location pairs.
+\item \textbf{Reference partitions}: new references are drawn from
+  three distinct partitions $\mathrm{init}_r()$, $\mathrm{fresh}_r()$,
+  and $\mathrm{stack}_r()$. The references strictly increase in value
+  on each call, and modular arithmetic is used to determine the
+  partition to which a reference belongs.
+\item \textbf{Determinism}: a reference in  $(\cfgnt{L}\ \cfgnt{R})$ cannot point to two locations at the same time.
+\[
+\begin{array}{l}
+\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
+\ \ \ \ (\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
+\end{array}
+\]
+$\cfgnt{L}^\leftarrow$ is the pre-image of the location map.
+\item \textbf{Type consistent}: every location associated to a reference has the same type.
+\[
+\begin{array}{l}
+\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
+\ \ \ \ (\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))
+\end{array}
+\]
+\item \textbf{Null and Uninitialized}: The location $\cfgnt{l}_\mathit{null}$ is a special location in the
 heap to represent null. It has a companion reference
@@
 \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$
+\end{compactitem}
 

### 2014-11-11 tex/javalite.tex
Minor checkpoint
Added heap properties

@@
 The state of the Javalite machine (\figref{fig:machine-syntax}),
-$\cfgnt{s}$, includes the program registry, a pair of functions
-defining the heap $\lp\cfgnt{L}\ \cfgnt{R}\rp$, which is the store, a
-constraint, $\phi$, defined over references in the heap, the
-environment, $\eta$, for local variables, and the continuation
-$\cfgnt{k}$. The more complex structures such as the environment are
-defined as lists which start with empty, \cfgnt{mt}. The rewrite rules
-that define the semantics treat these lists as partial
-functions. As such, $\eta(\cfgnt{x}) = \cfgnt{r}$ is the
-reference mapped to the variable $\cfgnt{x}$. The notation
-$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
-partial function $\eta^\prime$ that is just like $\eta$ only the
-variable $\cfgnt{x}$ now maps to $\cfgnt{v}$.
+$\cfgnt{s}$, includes the program registry\footnote{The registry $\mu$
+  is implied in the rewrite rules rather that states for
+  compactness.}, a pair of functions defining the heap
+$\lp\cfgnt{L}\ \cfgnt{R}\rp$, which is the store, a constraint,
+$\phi$, defined over references in the heap, the environment, $\eta$,
+for local variables, and the continuation $\cfgnt{k}$. The more
+complex structures such as the environment are defined as lists which
+start with empty, \cfgnt{mt}. The rewrite rules that define the
+semantics treat these lists as partial functions. As such,
+$\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference mapped to the variable
+$\cfgnt{x}$. The notation $\eta^\prime = \eta[\cfgnt{x} \mapsto
+  \cfgnt{v}]$ defines a new partial function $\eta^\prime$ that is
+just like $\eta$ only the variable $\cfgnt{x}$ now maps to
+$\cfgnt{v}$.
 
@@
 the field access is complete, the machine continues with $\cfgnt{k}$.
-
-\input{heap}

### 2014-11-11 tex/intro.tex
made a pass on the intro; still needs work

--- 2014-06-24 tex/intro.tex
@@
 
-In recent years symbolic execution --
-a program analysis technique for systematic exploration of
-program execution paths using symbolic input values -- has provided
-the basis for many software testing and analysis techniques.
-For each execution path explored during symbolic execution, constraints
-on the symbolic inputs are collected to create a \emph{path
-condition}. The set of path conditions computed by symbolic execution
-characterize the observed program execution behaviours and can
-be used to perform various analyses of program behavior, e.g.,
-regression testing~\cite{} and differential program 
-analysis~\cite{}.
+In recent years symbolic execution has provided the basis for various 
+software testing and analysis techniques. Symbolic execution
+systematically explores the program execution space using
+symbolic input values, and for each explored path, computes
+constraints on the symbolic inputs to create a \emph{ path condition}.
+The set of path conditions computed by
+symbolic execution characterize the observed program execution
+behaviours and have been used as an enabling technology for various
+applications, e.g., regression
+analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
+data structure repair~\cite{KhurshidETAL05RepairingStructurally},
+dynamic discovery of
+invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, and
+debugging~\cite{Ma:2011}.
 
 Initial work on symbolic execution largely focused on checking 
-properties of programs with primitive types, such as integers and 
-booleans~\cite{clarke76TSE,King:76}. With the advent of object-oriented
-languages, such as Java and C$++$, one of the fundamental challenges 
-of using symbolic execution for program analysis
-has been how to analyze programs containing
-complex data structures with unbounded domains, i.e., data stored
-on the heap. State-of-the-art symbolic execution techniques have 
-addressed this challenge by constructing the heap in a lazy manner, 
-deferring materialization of objects on the concrete heap until
-they are needed, i.e., until execution of a statement with a 
-dereference expression ($x = r.f$)~\cite{Kiasan06,Kiasan07,GSE03}.
+properties of programs with primitive types~\cite{clarke76TSE,King:76}.
+%, e.g., integers and booleans 
+%Despite recent advances
+%in constraint solving technologies, improvements in
+%raw computing power, and advances in reduction
+%and abstraction techniques~\cite{AnandETAL2009AbsSymExe,Godefroid:POPL07}
+%symbolic execution of programs of modest size containing only
+%primitive types, remains challenging
+%because of the large number of execution paths generated
+%during symbolic analysis. 
+With the advent of object-oriented languages,
+% e.g., Java and C$++$, 
+recent work has generalized the core ideas of symbolic execution to enable 
+analysis of programs containing complex data structures with unbounded 
+domains, i.e., data stored on the heap~\cite{Kiasan06,Kiasan07,GSE03}.  
+These Generalized Symbolic Execution (GSE) techniques construct the 
+heap in a lazy manner, deferring
+materialization of objects on the concrete heap until they are needed
+for the analysis to proceed. The materilization 
+%accounts for various heap configurations, 
+creates additional non-deterministic 
+choice points in the symbolic execution tree representing 
+the feasible heap configurations.
+as (a) null, (b) instance of a new
+reference of a compatible class, and (c) alias an previously
+initialized symbolic reference. 
+Symbolic execution follows concrete program semantics for 
+materialized heap locations. Although this approach
+enables analysis of heap manipulating programs, a large number
+of feasible concrete heap configurations may be created 
+exacerbating
+the well known state space explosion problem
+associated with symbolic execution.
 
-Although the lazy symbolic execution techniques have been instrumental 
-in enabling analysis of heap manipulating software, treatment of
-heap data follows concrete program semantics once a heap location is
-materialized. The effect is to exacerbate 
-the state space explosion problem by creating additional points of 
-non-determinism during symbolic execution to account for the 
-different possible concrete heap configurations.
+%  resulting in a large number of feasible concrete heap
+%configurations, and as a result, a large number of points of
+%non-determinism to be analyzed.
+%, further exacerbating the state space
+%explosion problem.
 
-Need a transition here to talk about a symbolic heap
+Research in the abstract interpretation community has taken
+a very different approach to analyzing heap manipulating
+programs which computes a summary of possible heaps. 
+These techniques start with an initial heap configuration 
+and then using a static analysis, make updates to the
+heap following program semantics, ultimately creating a heap 
+summary which represents the potential heaps resulting from
+program execution~\cite{Dillig:2011}. Because these
+techniques are based on a static analysis, the heap summaries
+over-approximate the set of feasible heap configurations.
+%The primary challenge relative to heap
+%analysis for these techniques is to 
+%resolve potential dependencies of local results on the global
+%aliases in the heap. 
+%Recent work addresses these issues
+%through strong updates to heap locations 
+%at call sites~\cite{Dillig} and computation of dangerous 
+%aliases~\cite{Matosevic}. Because these techniques are based 
+%on a static analysis, the resulting summaries over-approximate
+%the actual potential heaps.
 
-In this paper we present a novel approach to lazy symbolic
-execution....
+In this work, we present a novel heap initialization and analysis 
+technique which takes inspiration from both GSE and existing
+heap summarization techniques. The intuition behind our analysis
+is to construct the heap lazily during symbolic execution
+but reduce the points of non-determinism in
+the symbolic execution tree by analyzing each control-flow
+path only once for any given set of isomorphic heaps. To 
+represent the exact set of feasible concrete heap structures 
+resulting from execution of the control-flow path, we use
+a heap summary.
+Our analysis improves on existing GSE approaches by 
+reducing the size of the symbolic execution state space explored,
+thereby improving scalability of symboic execution for heap
+manipulating software. It improves on existing heap summarization
+techniques by enabling analysis of arbitrary recursive data structures 
+(no initial heap configuration is required) while avoiding the imprecision
+introduced by these techniques.
 
-Our technique is 1) scalable -- it constructs the symbolic
-heap on-the-fly during symbolic execution but avoids introducing 
-additional points of non-determinism
-by maintaining only a (fully) symbolic heap,
-2) precise -- at any given point during symbolic execution, 
-the symbolic heap represents the exact set of feasible
-concrete heap structures for the program under analysis, and
-3) expressive -- the symbolic heap can represent recursive data structures 
-and heaps resulting from loops and recursive control structures in the code. 
-We report on a case-study of an implementation of our technique in the
-Symbolic PathFinder tool to illustrate
- its scalability and we discuss how test case generation -- a common
- use for the results of symbolic execution -- can benefit from symbolic
- execution using a fully symbolic heap.
+\nsr{a paragraph that provides a breif summary
+  of the results.. would be nice if we have numbers for lazier and
+  lazier Sharp as well.}
+  A preliminary evaluation of our technique
+shows that it can improve the scalability of symbolic execution
+of heap manipulating programs X fold over GSE-based analyses
+while maintaining precision and efficiency.
 
 This paper makes the following contributions:
+\begin{itemize}
+\item{We present a novel inter-procedural analysis technique for 
+symbolic execution of heap manipulating software which constructs 
+a precise heap summary.}
+\item{We use the JavaLite language~\cite{saints-MS} to formalize 
+the algorithm for constructing and manipulating the heap summary
+on-the-fly during symbolic execution.}
+\item{We implement our approach in the Symbolic PathFinder tool and
+empirically demonstrate that our technique improves
+the scalability of symbolic execution of heap maninpulating software
+over GSE, while maintaining efficiency and precision.}
+\item{We prove that at any given point during symbolic execution, the symbolic 
+heap represents the exact set of feasible concrete heap structures 
+for the program under analysis.}
+ \end{itemize}
 
-\begin{itemize}
-\item{We present a novel technique for analyzing heap manipulating
-programs that constructs a fully symbolic representatino of
-the heap on-the-fly durig symbolic execution.}
-\item{We prove the soundness and completeness of our algorithm...}
-\item{We implement our approach in the Symbolic PathFinder tool}
-\item{We demonstrate experimentally that our technique improves
-the scalability of symbolic execution of heap maninpulating software
-over state-of-the-art techniques.}
+%\nsr{needs
+%  some text on the fact we use java lite to formalize the heap
+%  summary, some key characteristicss of the heap such as the fact it
+%  is a bipartiate graph with locations and referneces, properties of
+%  the heap such as the determinism and immutability}
+\nsr{Is any part of the formalism borrowed
+from the dilligs? Which part are unique?}  \nsr{end on a couple
+sentences about the various rules that will be talked about in the
+paper}
 
- \end{itemize}
+\nsr{The reader should be convinced about our expressiveness
+  claim here}
+
+\nsr{a paragraph that provides intution on how we are a bisumulation
+  with the GSE..reader should be convinced about the precision claim}
 

### 2014-11-11 tex/evaluation.tex
adding a new file for data

--- 2014-11-11 tex/results.tex
@@
-\section{Empirical Evaluation}
-\symtxt{} creates fewer execution paths than \gsetxt{}, but it does so with increased path constraint complexity.
-Determining the impact of this tradeoff in real-world applications is an important research question.
-
-Since the number of paths in \gsetxt{} is exponential in the number of lazy initializations, it is expected that programs for which the number of lazy initializations is proportional to program complexity will evaluate more quickly using \symtxt{}.
-On the other hand, since \symtxt{} places a greater burden on the constraint solver, it is expected that programs where the lazy initialization count is constant or slowly increasing with respect to program complexity will evaluate more quickly using \symtxt{}.
-
-\subsection{JPF Implementation}
-The Java Pathfinder (JPF) symbolic execution engine contains an implementation of \gsetxt{}, which we extended with our own implementation of \symtxt{}.
-
-\subsection{Bounding}
-In order to perform a practical evaluation of programs involving recursive data structures, it is generally necessary to impose some sort of bounding to eliminate the number of lazy initializations to a manageable level.
-While these bounds may be asserted as invariants within the program in-situ, it is more practical to apply bounding via external means.
-There are several bounding techniques that may be applied to both \gsetxt{} and \symtxt{}, including execution path length bounding, k-bounding and n-bounding.
-k-bounding and n-bounding both operate by imposing limits on the size of the symbolic input heap, but differ in how such bounds are defined.
-n-bounding limits the number of objects created by lazy initialization, while k-bounding limits the length of initialized reference chains.
-k-bounding has the property of exhaustively exploring the full breadth of a given data structure, while n-bounding tends to explore deeper heap shapes while being somewhat less thorough in breadth.
-In addition, k-bounding and n-bounding may be combined to adjust the desired level of approximation between depth and breadth.
-
-While k-bounding and n-bounding are applicable to both \gsetxt{} and \symtxt{}, they are not both equally suited for comparing the two methods.
-The main reason for this lies in how how each bounding technique impacts the functional equivalence of the respective methods.
-k-bounding preserves the functional equivalence of \gsetxt{} and \symtxt{}, a fact which can be established by induction over the length of reference chains from a given initial state.
-In contrast, \gsetxt{} and \symtxt{} are not generally functionally equivalent under n-bounding.
-The reason is that since a \symtxt{} state must represent all possible \gsetxt{} states on an execution path, it generally includes more locations than any single \gsetxt{} state it represents.
-This difference in state counts makes it difficult to externally assert n-bounding in a manner that preserves functional equivalence between \gsetxt{} and \symtxt{}.
-Functional equivalence may be preserved in the case where n-bounds are asserted via in-situ invariants, but the significant increase in constraint complexity makes this approach impractical.
-For this reason, n-bounding is was not selected for comparing \gsetxt{} to \symtxt{} in the tests performed in this paper.
-
-In contrast to the heap-based bounds provided by k-bounding and n-bounding, execution path-length bounding works by limiting the number along any given execution path.
-As with other bounding techniques, the usefulness of path-length bounding hinges on whether it preserves functional equivalence.
-While path-length bounding preserves functional equivalence for \gsetxt{} and \symtxt{} as formulated in this paper, it does not preserve it for the algorithms as they are implemented in JPF.
-The reason for the discrepancy lies in how states are defined in JPF.
-In JPF, the notion of states is closely tied to the concept of nondeterminism.
-New states are created in JPF only when a nondeterministic choice is made, meaning the number of states on an execution path is tied to the number of nondeterministic choices.
-A discrepancy in the length of the respective execution paths may be caused by any difference in nondeterminism between the two methods.
-This is significant, since the nondeterminism in \symtxt{} and \gsetxt{} differs in both field reads and in reference compares.
-Field reads in \symtxt{} are deterministic, whereas in \gsetxt{} they may initiate a nondeterministic lazy initialization.
-Conversely, in \gsetxt{} address compares are deterministic, but in \symtxt{} address compares require a nondeterministic assertion over the truth of the branch condition.
-For this reason, path-length bounding was not used for this experimental evaluation.
-For future tests, we are considering inserting artificial points of nondeterminism in order to establish functional equivalence of path-length bounds between \gsetxt{} and \symtxt{}.
-
-\subsection{Evaluation} 
-Experimental set-up: TO BE ADDED
-
-Test Cases
-
-In order to evaluate the performance of \symtxt{}, the implementation was tested against three examples: LinkedList, BinarySearchTree, TreeMap.
-The LinkedList example tests performance on linked list data structures.
-The test program begins by assuming an object invariant before initiating a sequence of contains() method calls.
-This is a challenging example for \gsetxt{} because each call to the contains() method contains a new lazy initialization, which in turn creates an exponential path expansion throughout program execution.
-While the constraints for each path are easily solved, the sheer number of paths quickly becomes overwhelming.
-
-The BinarySearchTree example test program consists simply of asserting the object invariant for a binary search tree.
-This example is interesting because it demonstrates nondeterminism from both aliasing constraints created during lazy initialization, and linear constraints from evaluating conditionals over numeric symbols.
-
-Like the BinarySearchTree test, the TreeMap test is simply an assertion of an object invariant, in this case for a red/black tree.
-This example serves as a stress test for \symtxt{}, since most of the nondeterminism comes from linear constraints over the shape of the tree, rather than aliasing constraints created during lazy initialization.
-In this case, the path advantage for \symtxt{} is minimized.
-
-For all tests, program complexity was adjusted via k-bounding.
-For the LinkedList test, the number of contains() method calls was added as an additional parameter.
-After the conclusion of each test, the test run-time, state count, and path counts were recorded.
-
-The results of the experiments are shown in table \ref{tab:results}.
-
 \begin{table} [h]

### 2014-11-11 tex/bisimulation.tex
Minor tweak on last paragraph

@@
 The relation, $P \sqsubset q$, is readily established in the initial
-state of a given program, as there is single initial state, $P_o =
+state of a given program as there is single initial state, $P_o =
 \{p_o\}$, in any valid Javalite program. The initial state for $\rsym$ is
-then defined as $q_o = p_o$; $P_o \sqsubset q_o$ is trivially shown.
+then defined as $q_o = p_o$ so $P_o \sqsubset q_o$ trivially holds.

### 2014-11-11 tex/results.tex
setup for results

@@
-\section{Empirical Evaluation}
-\symtxt{} creates fewer execution paths than \gsetxt{}, but it does so with increased path constraint complexity.
-Determining the impact of this tradeoff in real-world applications is an important research question.
+\section{Evaluation}
 
-Since the number of paths in \gsetxt{} is exponential in the number of lazy initializations, it is expected that programs for which the number of lazy initializations is proportional to program complexity will evaluate more quickly using \symtxt{}.
-On the other hand, since \symtxt{} places a greater burden on the constraint solver, it is expected that programs where the lazy initialization count is constant or slowly increasing with respect to program complexity will evaluate more quickly using \symtxt{}.
+In this section we evaluate the effectiveness of \symtxt{} at
+analyzing programs with unbounded complex data input in the context of
+symbolic execution. In order to perform our evaluation we implement
+the \symtxt{} technique and evaluate its efficiacy on three Java data
+structure artifacts. We compare the results of \symtxt{} with other
+state of the art techniques that initialize complex data input
+symbolically. We first describe the tool infrastructure we use to
+implement our approach.
 
-\subsection{JPF Implementation}
-The Java Pathfinder (JPF) symbolic execution engine contains an implementation of \gsetxt{}, which we extended with our own implementation of \symtxt{}.
-Our heap representation lends itself to a number of simple performance optimizations, which have been included in the implementation.
-First, solutions to previous constraint problems are cached and re-used, to avoid sending a large number of queries to the SMT solver.
-Second, because only small portions of the path condition change from one state to the next, incremental solving is enabled to provide a substantial performance increase.
-Finally, by examining the location sets involved in a reference compare operation, a large number of reference compare instructions may be dispatched without consulting the solver to begin with.
+\subsection{Tool Support}
+We implement the \symtxt{} as an extension to the symbolic execution
+engine of Java PathFinder(JPF)---Symbolic Pathfinder
+(SPF)~\cite{visser:ase03,Pasareanu:ISSTA08,pasareanu:ase10}. SPF is an
+open source engine for performing symbolic execution on Java
+bytecode. The JPF framework provides mechanism for overwriting the
+execution semantics of the traditional concrete Java bytecode
+semantics. SPF leverages this to define symbolic execution semantics
+for Java bytecode. SPF performs a stateless search to generate the
+symbolic execution tree since state matching in general is
+undecidable.
 
-For practical purposes, the implementation also includes a number of features not shown in the simple language described in section 2.
-For example, integer operations are required in order to reason about ordered data structures such as binary search trees and red/black trees.
-The description of these operations is outside the scope of this paper.
+SPF contains the implementation for GSE with lazy initialization. At
+bytecodes that access uninitialized symbolic fields it creates custom
+non-deterministic choices for the field to be null, new instance of
+its type, and aliases to any previously initialized symbolic
+fields~\cite{DBLP:journals/ase/PasareanuVBGMR13}. Recent work also
+provides implementations of the lazier and lazier\# algorithms in the
+SPF framework~\cite{Hillery:2014}.
+
+We create a new extension to SPF in order to implement the~\symtxt{}
+approach. Even though our approach is presented using the Javalite
+semantics, the implementation contains support for the full Java
+semantics such as operations over integers and other data types
+supported in Java. We overwrite three main sets of Java bytecodes that
+map to the rewrite rules presented in~\secref{sec:precise}. We provide
+custom implementation of the following: (i) field access bytecodes,
+e.g., GETFIELD and ALOAD bytecodes, to implement the field-access and
+summarize rules in~\figref{fig:symInit} and~\figref{fig:fHeap}(a),
+(ii) the field write bytecodes, e.g., PUTFIELD and ASTORE bytecodes,
+to implement the field-write rules in~\figref{fig:fHeap}(a), and (iii)
+checking equality of references bytecode, IF\_ACMPEQ and IF\_ACMPNE,
+to implement the equals references-true and references-false rules
+in~\figref{fig:eqs}. \nsr{any custom implementation for integers? }
+
+The default constraints library in SPF handles constraints in the CNF
+form, these are unable to support constraints generated by \symtxt{}
+approach since they contain disjunctions. Transforming the constraints
+generated by \symtxt{} into a CNF form proved to be inefficient. We
+use the \texttt{jConstraints} library that provides support to handle
+arbitrary constraints~\cite{ase2014-ghilrr,jpf2014-dghirr}. It uses
+the z3 solver,~\cite{z3}, as the backend to solve the constraints. We
+leverage the incremental solving feature in z3 in our experiments. We
+also implement other optimizations that cache and re-use solutions to
+previous constraints. These optimizations are an important part of our
+implementation because only small portions of the heap constraint
+changes from one state to another.
+
+Loops and recursive methods over symbolic variables are bounded based
+on some user-provided limit. These bounds are based on some
+control-flow structure of the program and are often insufficient for
+analyzing programs with input of complex data types as demonstrated
+in~\cite{Kiasan07,Deng:2006}. In this work we use the $k$-bounding
+technique that bounds the length of a reference chain from the root of
+the heap~\cite{Deng:2006}.\nsr{check this!} Note we use $k$-bounding
+because it preserves the functional equivalence of \gsetxt{}, lazier,
+lazier\# and \symtxt{} techniques, a fact which can be established by
+induction over the length of reference chains from a given initial
+state. The $n$-bounding approach restricts the total number of
+references created along a certain path. There is no easy way to
+compare the number of references generated by \symtxt{} and other
+techniques since \symtxt{} can create many references at a single
+access point in its heap summary.
+
+\subsection{Case-Study}
+
+The goal of our technique to evaluate the efficiacy of our approach
+with respect to other state of the art algorithms for symbolic
+execution for dealing for unbounded complex data input. We empirically
+evaluate \symtxt{} by considering the following research questions:
+
+\begin{description}
+\item {\bf RQ1:} How does the cost of using \symtxt{} compare to that
+  of \gsetxt{}, lazier, and lazier\# algorithms?
+
+\item {\bf RQ2:} Does \symtxt{} technique enable other back-end
+  approaches that can leverage its output?
+\end{description}
+
+To evaluate we use three Java data structure artifacts (a) Linked List
+(b) Binary Search Tree, and (c) Tree Map. These data structures
+programs are often used to the evaluate symbolic execution algorithms
+with arbitrary heap inputs. The \emph{independent} variable in our
+study is the algorithm for initializing symbolic references and the
+$k$-bound. The initialization algorithms that we vary in our study
+are: \symtxt{}, \gsetxt{}, lazier, and lazier\#. We also vary the
+$k-bound$ for each the algorithms. We select three dependent variables
+and measures for our study: (i) time, (ii) states explored, and (iii)
+paths generated. The \emph{time} is the total time taken by each
+algorithm to explore the symbolic execution tree as well as total
+constraint solving time. The \emph{states explored} represents the
+number of nodes in the symbolic execution tree while the \emph{paths
+  generated} represent as the name suggests the number of unique paths
+in the symbolic execution tree.
+
+To perform our study we compile all our artifacts and run the analysis
+on \nsr{the machine}.
+
+\begin{comment}
+\symtxt{} creates fewer execution paths than \gsetxt{}, but it does so
+with increased path constraint complexity. Determining the impact of
+this tradeoff in real-world applications is an important research
+question.
+
+Since the number of paths in \gsetxt{} is exponential in the number of
+lazy initializations, it is expected that programs for which the
+number of lazy initializations is proportional to program complexity
+will evaluate more quickly using \symtxt{}. On the other hand, since
+\symtxt{} places a greater burden on the constraint solver, it is
+expected that programs where the lazy initialization count is constant
+or slowly increasing with respect to program complexity will evaluate
+more quickly using \symtxt{}.
+
+\subsection{Implementation}
+
+The Java Pathfinder (JPF) symbolic execution engine contains an
+implementation of \gsetxt{}, which we extended with our own
+implementation of \symtxt{}. Our heap representation lends itself to a
+number of simple performance optimizations, which have been included
+in the implementation. First, solutions to previous constraint
+problems are cached and re-used, to avoid sending a large number of
+queries to the SMT solver. Second, because only small portions of the
+path condition change from one state to the next, incremental solving
+is enabled to provide a substantial performance increase. Finally, by
+examining the location sets involved in a reference compare operation,
+a large number of reference compare instructions may be dispatched
+without consulting the solver to begin with.
+
+For practical purposes, the implementation also includes a number of
+features not shown in the simple language described in section 2. For
+example, integer operations are required in order to reason about
+ordered data structures such as binary search trees and red/black
+trees. The description of these operations is outside the scope of
+this paper.
 
 \subsection{Bounding}
-In order to perform a practical evaluation of programs involving recursive data structures, it is generally necessary to impose some sort of bounding to reduce the number of lazy initializations to a manageable level.
-While these bounds may be asserted as invariants within the program in-situ, it is more practical to apply bounding via external means.
-There are several bounding techniques that may be applied to both \gsetxt{} and \symtxt{}, including execution path length bounding, k-bounding and n-bounding.
-k-bounding and n-bounding both operate by imposing limits on the size of the symbolic input heap, but differ in how such bounds are defined.
-n-bounding limits the number of objects created by lazy initialization, while k-bounding limits the length of initialized reference chains.
-k-bounding has the property of exhaustively exploring the full breadth of a given data structure, while n-bounding tends to explore deeper heap shapes while being somewhat less thorough in breadth.
-In addition, k-bounding and n-bounding may be combined to adjust the desired level of approximation between depth and breadth.
+In order to perform a practical evaluation of programs involving
+recursive data structures, it is generally necessary to impose some
+sort of bounding to reduce the number of lazy initializations to a
+manageable level. While these bounds may be asserted as invariants
+within the program in-situ, it is more practical to apply bounding via
+external means. There are several bounding techniques that may be
+applied to both \gsetxt{} and \symtxt{}, including execution path
+length bounding, k-bounding and n-bounding. k-bounding and n-bounding
+both operate by imposing limits on the size of the symbolic input
+heap, but differ in how such bounds are defined. n-bounding limits the
+number of objects created by lazy initialization, while k-bounding
+limits the length of initialized reference chains. k-bounding has the
+property of exhaustively exploring the full breadth of a given data
+structure, while n-bounding tends to explore deeper heap shapes while
+being somewhat less thorough in breadth. In addition, k-bounding and
+n-bounding may be combined to adjust the desired level of
+approximation between depth and breadth.
 
-While k-bounding and n-bounding are applicable to both \gsetxt{} and \symtxt{}, they are not both equally suited for comparing the two methods.
-The main reason for this lies in how how each bounding technique impacts the functional equivalence of the respective methods.
-k-bounding preserves the functional equivalence of \gsetxt{} and \symtxt{}, a fact which can be established by induction over the length of reference chains from a given initial state.
-In contrast, \gsetxt{} and \symtxt{} are not generally functionally equivalent under n-bounding.
-The reason is that since a \symtxt{} state must represent all possible \gsetxt{} states on an execution path, it generally includes more locations than any single \gsetxt{} state it represents.
-This difference in state counts makes it difficult to externally assert n-bounding in a manner that preserves functional equivalence between \gsetxt{} and \symtxt{}.
-Functional equivalence may be preserved in the case where n-bounds are asserted via in-situ invariants, but the significant increase in constraint complexity makes this approach impractical.
-For this reason, n-bounding is was not selected for comparing \gsetxt{} to \symtxt{} in the tests performed in this paper.
+While k-bounding and n-bounding are applicable to both \gsetxt{} and
+\symtxt{}, they are not both equally suited for comparing the two
+methods. The main reason for this lies in how how each bounding
+technique impacts the functional equivalence of the respective
+methods.  k-bounding preserves the functional equivalence of \gsetxt{}
+and \symtxt{}, a fact which can be established by induction over the
+length of reference chains from a given initial state. In contrast,
+\gsetxt{} and \symtxt{} are not generally functionally equivalent
+under n-bounding. The reason is that since a \symtxt{} state must
+represent all possible \gsetxt{} states on an execution path, it
+generally includes more locations than any single \gsetxt{} state it
+represents. This difference in state counts makes it difficult to
+externally assert n-bounding in a manner that preserves functional
+equivalence between \gsetxt{} and \symtxt{}. Functional equivalence
+may be preserved in the case where n-bounds are asserted via in-situ
+invariants, but the significant increase in constraint complexity
+makes this approach impractical. For this reason, n-bounding is was
+not selected for comparing \gsetxt{} to \symtxt{} in the tests
+performed in this paper.
 
-In contrast to the heap-based bounds provided by k-bounding and n-bounding, execution path-length bounding works by limiting the number along any given execution path.
-As with other bounding techniques, the usefulness of path-length bounding hinges on whether it preserves functional equivalence.
-While path-length bounding preserves functional equivalence for \gsetxt{} and \symtxt{} as formulated in this paper, it does not preserve it for the algorithms as they are implemented in JPF.
-The reason for the discrepancy lies in how states are defined in JPF.
-In JPF, the notion of states is closely tied to the concept of nondeterminism.
-New states are created in JPF only when a nondeterministic choice is made, meaning the number of states on an execution path is tied to the number of nondeterministic choices.
-A discrepancy in the length of the respective execution paths may be caused by any difference in nondeterminism between the two methods.
-This is significant, since the nondeterminism in \symtxt{} and \gsetxt{} differs in both field reads and in reference compares.
-Field reads in \symtxt{} are deterministic, whereas in \gsetxt{} they may initiate a nondeterministic lazy initialization.
-Conversely, in \gsetxt{} address compares are deterministic, but in \symtxt{} address compares require a nondeterministic assertion over the truth of the branch condition.
-For this reason, path-length bounding was not used for this experimental evaluation.
-For future tests, we are considering inserting artificial points of nondeterminism in order to establish functional equivalence of path-length bounds between \gsetxt{} and \symtxt{}.
+In contrast to the heap-based bounds provided by k-bounding and
+n-bounding, execution path-length bounding works by limiting the
+number along any given execution path. As with other bounding
+techniques, the usefulness of path-length bounding hinges on whether
+it preserves functional equivalence. While path-length bounding
+preserves functional equivalence for \gsetxt{} and \symtxt{} as
+formulated in this paper, it does not preserve it for the algorithms
+as they are implemented in JPF. The reason for the discrepancy lies in
+how states are defined in JPF. In JPF, the notion of states is closely
+tied to the concept of nondeterminism. New states are created in JPF
+only when a nondeterministic choice is made, meaning the number of
+states on an execution path is tied to the number of nondeterministic
+choices. A discrepancy in the length of the respective execution paths
+may be caused by any difference in nondeterminism between the two
+methods. This is significant, since the nondeterminism in \symtxt{}
+and \gsetxt{} differs in both field reads and in reference
+compares. Field reads in \symtxt{} are deterministic, whereas in
+\gsetxt{} they may initiate a nondeterministic lazy
+initialization. Conversely, in \gsetxt{} address compares are
+deterministic, but in \symtxt{} address compares require a
+nondeterministic assertion over the truth of the branch condition. For
+this reason, path-length bounding was not used for this experimental
+evaluation. For future tests, we are considering inserting artificial
+points of nondeterminism in order to establish functional equivalence
+of path-length bounds between \gsetxt{} and \symtxt{}.
 
 \subsection{Evaluation}
+
 Experimental set-up: TO BE ADDED
@@
 
-In order to evaluate the performance of \symtxt{}, the implementation was tested against three examples: LinkedList, BinarySearchTree, TreeMap.
-The LinkedList example tests performance on linked list data structures.
-The test program begins by assuming an object invariant before initiating a sequence of contains() method calls.
-This is a challenging example for \gsetxt{} because each call to the contains() method contains a new lazy initialization, which in turn creates an exponential path expansion throughout program execution.
-While the constraints for each path are easily solved, the sheer number of paths quickly becomes overwhelming.
+In order to evaluate the performance of \symtxt{}, the implementation
+was tested against three examples: LinkedList, BinarySearchTree,
+TreeMap.  The LinkedList example tests performance on linked list data
+structures. The test program begins by assuming an object invariant
+before initiating a sequence of contains() method calls. This is a
+challenging example for \gsetxt{} because each call to the contains()
+method contains a new lazy initialization, which in turn creates an
+exponential path expansion throughout program execution. While the
+constraints for each path are easily solved, the sheer number of paths
+quickly becomes overwhelming.
 
-The BinarySearchTree example test program consists simply of asserting the object invariant for a binary search tree.
-This example is interesting because it demonstrates nondeterminism from both aliasing constraints created during lazy initialization, and linear constraints from evaluating conditionals over numeric symbols.
+The BinarySearchTree example test program consists simply of asserting
+the object invariant for a binary search tree. This example is
+interesting because it demonstrates nondeterminism from both aliasing
+constraints created during lazy initialization, and linear constraints
+from evaluating conditionals over numeric symbols.
 
-Like the BinarySearchTree test, the TreeMap test is simply an assertion of an object invariant, in this case for a red/black tree.
-This example serves as a stress test for \symtxt{}, since most of the nondeterminism comes from linear constraints over the shape of the tree, rather than aliasing constraints created during lazy initialization.
-In this case, the path advantage for \symtxt{} is minimized.
+Like the BinarySearchTree test, the TreeMap test is simply an
+assertion of an object invariant, in this case for a red/black
+tree. This example serves as a stress test for \symtxt{}, since most
+of the nondeterminism comes from linear constraints over the shape of
+the tree, rather than aliasing constraints created during lazy
+initialization. In this case, the path advantage for \symtxt{} is
+minimized.
 
-For all tests, program complexity was adjusted via k-bounding.
-For the LinkedList test, the number of contains() method calls was added as an additional parameter.
-After the conclusion of each test, the test run-time, state count, and path counts were recorded.
+For all tests, program complexity was adjusted via k-bounding. For the
+LinkedList test, the number of contains() method calls was added as an
+additional parameter. After the conclusion of each test, the test
+run-time, state count, and path counts were recorded.
 
@@
 
-\begin{table} [h]
-  \centering
-  \begin{tabular}{| c | c | c | c | c | c | c | c |}
-  \hline
-   \multirow{2}{*}{Method }&\multirow{2}{*}{ $k$ }
-   &\multicolumn{2}{|c|}{Time} &\multicolumn{2}{|c|}{ Paths }\\
-								&	&\gsetxt{}	&SH	&\gsetxt{} & SH\\
-   \hline
-    \multirow{3}{*}{LinkedList }&3	& 1 & 1  &1656 & 25		 \\
-   		 				& 4	& 3 & 2	&17485  & 39 \\
-   						& 5	& 20 & 3	&232743 & 56\\
-						& 6	& 338 & 8		&3731094 & 76\\
-    \hline
-    \multirow{3}{*}{BinarySearchTree }&1	& 0 & 1	& 4	 & 4\\
-   		 				& 2	& 1 & 1 	& 26 & 17\\
-   						& 3	& 12 & 7	& 305 & 118\\
-    \hline
-      \multirow{3}{*}{TreeMap}&1	& 0 & 1 	&9 & 9 \\
-   		 				&2	& 1 & 3		& 100 & 46 \\
-   						&3	&21 & 206	& 3026 & 547 \\
-
-    \hline
-  \end{tabular}
-  \caption{test results}
-  \label{tab:results}
-\end{table}
-
-\subsection{Analysis}
-
-LinkedList
-As expected, the repeated use of lazy initialization throughout the program causes an exponential increase in the number of paths explored by \gsetxt{}.
-By combining many of the \gsetxt{} paths, SH avoids the exponential path explosion, demonstrating dramatically reduced, though still exponential, execution time growth.
-Remarkably, path growth in the k-bound appears to be sub-linear.
-
-The BinarySearchTree example is somewhat of a mixed bag.
-
-TreeMap
+\end{comment}

### 2014-11-11 tex/bisimulation.tex
Defined S and S_A

@@
 continuation. Well-formed states always have a successor unless it is
-the end of the program execution.
+the end of the program execution. It is trivial to show that every
+rule in the transition relation preserves well-formedness.
 
@@
 \end{proof}
-Similar lemmas are proved for field write and equals reference.
+Similar lemmas are proved for field write and equals reference. These
+require additional lemmas on properties of the summary machine
+$\rightarrow_S$. Specifically, that it preserves determinism, and it
+preserves the homomorphism and the satisfiability of homomorphism constraint
 
@@
 
-The notation $p \stackrel{n}{\rgse} p^\prime$ denotes that $p^\prime$ is
-the $n$-step successor of $p$, if it exists, and $q
+The notation $p \stackrel{n}{\rgse} p^\prime$ denotes that $p^\prime$
+is the $n$-step successor of $p$, if it exists, and $q
 \stackrel{n}{\rsym} q^\prime$ is similarly defined. Completeness and
 soundness are readily established by \thref{th:bisim} and inducting
-over $n$.
+over $n$. The state $S$ is the universe of well-formed states, and the
+set $S_A \subseteq S$ is the set of states at a field access continuation.
 
 \begin{corollary}[$\rsym$ is complete]
-If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$ then for any $p \in P$
+If $P \in 2^{S_\mathit{A}}$ and $q \in S$ are such that $P \sqsubset q$ then for any $p \in P$
 $$
@@
 \begin{corollary}[$\rsym$ is sound]
-If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$ then
+If $P \in 2^{S_\mathit{A}}$ and $q \in S$ are such that $P \sqsubset q$ then
 $$

### 2014-11-12 tex/conclusion.tex
Added text to conclusion.

@@
 \section{Conclusion}
+We have presented a new heap representation for symbolic execution that maintains exactness, represents arbitrary heap structures without restrictions on aliasing relationships, and supports dynamic on-the-fly initialization of heap structures.
+Despite this unique combination of capabilities, performance is not sacrificed compared to previous methods, and in some cases is greatly enhanced.
 
 \subsection{Future Work}
+Planned future work includes extensions to reason about scalar types, support for test case generation, state merging, and solver performance enhancements.
+
+In this paper, we have restricted our presentation of symbolic heaps to constraints reasoning over heap morphology.
+However, in order to be useful for reasoning about real programs, we must consider the impact of scalar types.
+Our implementation includes limited support for linear operations over integer types, but we intent to extend support for all types of operations, as well as develop the theory for doing so.
+
+Another feature we would like to add is support for test case generation, which is traditionally a key advantage of symbolic execution techniques.
+Under the current rules, it is difficult to extract test cases because the heap may be destructively altered during field writes.
+A simple remedy would be to maintain an explicit input heap in addition to the actual heap which is mutated as the program progresses.
+
+Besides extending the capabilities of the algorithm, it should also be possible to increase performance through a variety of means.
 While our representation reduces paths significantly compared to \gsetxt{}, there remains room for improvement.
 Another way to reduce path explosion is through state merging.
-We are investigating ways of merging states at join points in the program, perhaps involving a combination of heap merging and / or heap equivalence testing.
+We are investigating ways of merging states at join points in the program, perhaps involving a combination of heap merging and / or heap equivalence testing as in \cite{Sen:2014}.
 
-A key advantage of many symbolic execution techniques is the ability to generate test inputs to exercise every possible control flow path.
-Our technique could be adapted for test input generation by maintaining an explicit input heap in addition to the actual heap which is mutated as the program progresses.
-
-We are also contemplating a variety of performance optimizations.
-Due to the structure of the constraints used in the heap representation, our representation is amenable to sophisticated results-caching schemes such as Green.
+We are also contemplating a variety of performance optimizations that deal with constraints.
+Due to the structure of the constraints used in the heap representation, our representation is amenable to sophisticated results-caching schemes such as Green \cite{Visser:2012}.
 Likewise, a considerable amount of solver time is spent calculating object invariants during program initialization.

### 2014-11-12 tex/evaluation.tex
Updated table with recent results
Added text to conclusion.

@@
    \hline
-    \multirow{3}{*}{LinkedList }&3	& 1 & 1  &1656 & 25		 \\
-   		 				& 4	& 3 & 2	&17485  & 39 \\
-   						& 5	& 20 & 3	&232743 & 56\\
-						& 6	& 338 & 8		&3731094 & 76\\
+    \multirow{3}{*}{LinkedList }&3	& 0.91 & 0.69  &1656 & 25		 \\
+   		 				& 4	& 2.92 & 0.91	&17485  & 39 \\
+   						& 5	& 20.8 & 1.59 &232743 & 56\\
+						& 6	& 283 & 2.36		&3731094 & 76\\
     \hline
-    \multirow{3}{*}{BinarySearchTree }&1	& 0 & 1	& 4	 & 4\\
-   		 				& 2	& 1 & 1 	& 26 & 17\\
-   						& 3	& 12 & 7	& 305 & 118\\
+    \multirow{3}{*}{BinarySearchTree } & 1	&0.26	& 0.36 & 6	 & 6\\
+   		 				& 2	& 0.83 & 0.93	& 143 & 33\\
+   						& 3	& 20.6 & 4.03 & 515 & 328\\
     \hline
-      \multirow{3}{*}{TreeMap}&1	& 0 & 1 	&9 & 9 \\
-   		 				&2	& 1 & 3		& 100 & 46 \\
-   						&3	&21 & 206	& 3026 & 547 \\
+      \multirow{3}{*}{TreeMap}&1	 & 0.47 & 0.77 &11 & 11 \\
+   		 				&2	& 8.99 & 4.72	& 127 & 73 \\
+   						& 3	& - & 146	& - & 887 \\
 
@@
 As expected, the repeated use of lazy initialization throughout the program causes an exponential increase in the number of paths explored by \gsetxt{}.
-By combining many of the \gsetxt{} paths, SH avoids the exponential path explosion, demonstrating dramatically reduced, though still exponential, execution time growth.
+By combining many of the \gsetxt{} paths, \shtxt{} avoids the exponential path explosion, demonstrating dramatically reduced, though still exponential, execution time growth.
 Remarkably, path growth in the k-bound appears to be sub-linear.
 
-The BinarySearchTree example is somewhat of a mixed bag.
+In the BinarySearchTree example, the
 
-TreeMap
+The TreeMap example has a large number of integer compare instructions, and so it should present the greatest challenge to the constraint solver. However, it still explores far fewer

### 2014-11-12 tex/evaluation.tex
Updated text.

@@
   \centering
-  \begin{tabular}{| c | c | c | c | c | c | c | c |}
+  \begin{tabular}{| c | c | r | r | r | r | }
   \hline
@@
 
-LinkedList
 As expected, the repeated use of lazy initialization throughout the program causes an exponential increase in the number of paths explored by \gsetxt{}.
-By combining many of the \gsetxt{} paths, \shtxt{} avoids the exponential path explosion, demonstrating dramatically reduced, though still exponential, execution time growth.
+By combining many of the \gsetxt{} paths, \symtxt{} avoids the exponential path explosion, demonstrating dramatically reduced, though still exponential, execution time growth.
 Remarkably, path growth in the k-bound appears to be sub-linear.
 
-In the BinarySearchTree example, the
+While the BinarySearchTree example introduces integer constraints, \symtxt{} performance does not appear to suffer due to the constraint burden.
+Indeed, at k=3, there appears to be a significant performance advantage in favor of \symtxt{}.
 
-The TreeMap example has a large number of integer compare instructions, and so it should present the greatest challenge to the constraint solver. However, it still explores far fewer
+The TreeMap example has a large number of integer compare instructions, and so it should present the greatest challenge to the constraint solver.
+Despite this, \symtxt{} still explores fewer paths than \gsetxt{}, and \gsetxt{} notably failed to terminate within the allotted time bounds for the $k=3$ test case.

### 2014-11-12 tex/related.tex
Updated text.

@@
 \subsection{Symbolic Exection}
-A number of adaptations to allow symbolic execution to cope with heap data structures have been proposed, beginning with Generalized symbolic execution \cite{GSE03}.
+As originally formulated, symbolic execution was incapable of reasoning beyond scalar input values.
+Since then, several adaptations to allow symbolic execution to cope with heap data structures have been proposed, beginning with Generalized symbolic execution \cite{GSE03}.
 Subsequent improvements to the method \cite{Deng:2006,Deng:2007} reduce path explosion by delaying path splitting over aliasing choices for as long as possible.
-However, since all of the above methods introduce nondeterminism during field reads and writes, they all worsen the path explosion problem to some extent or another.
+However, since all of the above methods introduce nondeterminism during field reads and writes, they all contribute to path explosion to some extent.
 Since our heap representation does not introduce any nondeterminism beyond the level in standard symbolic execution, it will generally create fewer paths than these methods, sometimes by a wide margin.
@@
 \subsection{Heap Representations}
-A number of other techniques model references using sets of guarded locations \cite{Xie:2005,Cherem:2007,Dillig:2011}.
+One significant line of work on representing heaps is shape analysis.
+Shape analysis attempts to reduce the complexity of the heap by combining multiple nodes with similar properties into summary nodes.
+The summary nodes typically establish may/must constraints over the heap structure, and typically represent an overapproximation of the represented heap.
+As such, program evaluations using shape analysis representations are prone to reporting large numbers of false positives.
+
+As in our representation, other methods have been proposed that model references using sets of guarded locations \cite{Xie:2005,Cherem:2007,Dillig:2011,Sen:2014}.
 These sets, sometimes known as value sets or value summaries, allow multiple heaps to be represented simultaneously with a higher degree of precision than afforded by shape analysis.
@@
 First, these techniques must use approximations to resolve reference inequalities, resulting in false positives in the results.
-Second, these techniques are incapable of reasoning about heaps with loops in the data structures due to infinite recursion during dereferencing.
+Second, these techniques are incapable of reasoning about heaps with recursive data structures due to the potential for infinite recursion during dereferencing.
 This means that either a large class of data structures must be avoided, or a large class of behaviors must be ignored.
 In our heap representation, object descriptions are entirely local, thus avoiding these pitfalls.
-The other work \cite{Dillig:2011}, does not handle structures with loops despite having a local object representation, and has further drawbacks as previously enumerated.
+Other methods  \cite{Dillig:2011,Sen:2014}, while having local morphological representations, do not provide for dynamic exploration of the initial heap state.
+
+Another line of work in heap representation lies in identifying isomorphic heap structures in order to avoid exploring redundant paths.
+Examples of such methods include Korat, XXX, and YYY.
+These methods are generally focused on the morphology of the heap alone, in isolation from the external constraint problems encountered during program execution.
+As such, these works are largely orthogonal to the methods presented here, though some of them may possibly be complimentary.

### 2014-11-12 tex/heap.tex

@@
 \subsection{Heaps as Bipartite Graphs}
-An important aspect, and a novel contribution, of a symbolic heap is its
-representation as a labeled bipartite graph consisting of
+An important aspect, and a novel contribution, of a symbolic heap is
+its representation as a labeled bipartite graph consisting of
 references, $\cfgnt{r}$, and constraint location pairs,
-$\lp\phi\ \cfgnt{l}\rp$. The heap structure itself captures that the actual
-location pointed to by a reference is conditional on aliasing
-relationships within the heap. In this way, the graph represents sets
-of heaps with the conditions under which those heaps exist.
+$\lp\phi\ \cfgnt{l}\rp$. The bipartite graph separates the constraint
+problem from the morphology problem, that is to say, the shape of the
+heap. Being bipartite also makes it so it is not needed to rewrite the
+path condition every time the heap is updated. Without these two
+properties, it would not be possible to lazily initialize heap
+locations along a program path. The heap structure itself captures
+that the actual location pointed to by a reference is conditional on
+aliasing relationships within the heap. In this way, the graph
+represents sets of heaps with the conditions under which those heaps
+exist.
 
-The graph is expressed in in $\cfgnt{L}$, the location map, and
+The graph is expressed in $\cfgnt{L}$, the location map, and
 $\cfgnt{R}$, the reference map. As done with the environment,
@@
 There are several properties of the heap that are invariant and
-important to the correctness.
+important to the correctness proofs on the algorithm.
 \begin{compactitem}
@@
   the location map; it always points to the same set of constraint
-  location pairs.
+  location pairs. The property ensures that constraints never need to
+  be rewritten as the program evolves its state.
 \item \textbf{Reference partitions}: new references are drawn from
-  three distinct partitions $\mathrm{init}_r()$, $\mathrm{fresh}_r()$,
-  and $\mathrm{stack}_r()$. The references strictly increase in value
-  on each call, and modular arithmetic is used to determine the
-  partition to which a reference belongs.
+  three distinct partitions $\mathrm{init}_r()$ for initialization,
+  $\mathrm{fresh}_r()$ for the input heap, and $\mathrm{stack}_r()$
+  for references in the expressions and continuations. The references
+  strictly increase in value on each call, and modular arithmetic is
+  used to determine the partition to which a reference belongs. The
+  partitions are a critical piece to the existence proof of a
+  bisimulation that relates states with a concrete heap to states with
+  heap summaries.
 \item \textbf{Determinism}: a reference in  $(\cfgnt{L}\ \cfgnt{R})$ cannot point to two locations at the same time.
@@
 $\cfgnt{L}^\leftarrow$ is the pre-image of the location map.
-\item \textbf{Type consistent}: every location associated to a reference has the same type.
+\item \textbf{Type consistency}: every location associated to a reference has the same type.
 \[
@@
 \]
-\item \textbf{Null and Uninitialized}: The location $\cfgnt{l}_\mathit{null}$ is a special location in the
-heap to represent null. It has a companion reference
-$\cfgnt{r}_\mathit{null}$. The initial heap for the machine is defined
-such that $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
-\{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$
+\item \textbf{Null and Uninitialized}: every heap contains special
+  locations for null ($\cfgnt{l}_\mathit{null}$) and uninitialized
+  ($\cfgnt{l}_\mathit{un}$) with corresponding references
+  $\cfgnt{r}_\mathit{null}$ and
+  $\cfgnt{r}_\mathit{un}$. $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
+  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
+  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
+  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$.
 \end{compactitem}
+The Javalite semantics are modified to operate on this new heap
+structure so that a heap summary represents an equivalence class of
+concrete heaps. All the concrete heaps that follow the same control
+flow to a point of execution are in the equivalence class represented
+by the summary. That equivalence class splits depending control flow
+branches, partitioning the heaps depending on the produced outcome.
 
-DEFINE $\rsym$ and $\rgse$.
+\subsection{State Transition Relation}
+
+The initial state of a Javalite program is constructed from its
+surface syntax on the $\cfgnt{P}$ production:
+$\lp\mu\ \lp\cfgnt{C}\ \cfgnt{m}\rp\rp$. Assuming that
+$\lp\cfgnt{L}\ \cfgnt{R}\rp$ is an empty heap with no references
+or locations and $\eta$ is an empty environment with no
+variables, the initial state is
+$$
+\begin{array}{l}
+\lp\mu 
+\ \cfgnt{L}[\cfgnt{r}_\mathit{null} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{null})\}\rp] 
+           [\cfgnt{r}_\mathit{un} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{un}\rp\}] \\
+\ \cfgnt{R}
+\ \cfgt{true}\ \eta\  \lp\lp\cfgt{new}\ \cfgnt{C}\rp\ \cfgt{@}\ \cfgnt{m}\ \cfgt{true}\rp\rp\ \cfgt{end}\rp
+\end{array}
+$$
+The first expression in the initial state is a call to a constructor
+to create an instance of the class $\cfgnt{C}$. Once an instance of
+$\cfgnt{C}$ is exists, the methods $\cfgnt{m}$ of the class is
+invoked.
+
+The common portion of Javalite for the new heap summary is defined
+elsewhere, but in general, the semantics of Javalite are expressed as
+rewrites on strings using pattern matching. Consider the rewrite rule
+for the beginning of a field access instruction:
+$$
+\mprset{flushleft}
+	\inferrule[Field Access(eval)]{}{
+      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgnt{e}\ \cfgt{\$}\ \cfgnt{f}\rp \ \cfgnt{k}\rp  \rcom 
+      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp 
+	}
+$$
+If the string representing the state matches the left side, then it
+creates the new string on the right. In this example, the new string
+on the right is now evaluating the expression $\cfgnt{e}$ in the field
+access, and it includes the continuation indicating that it still
+needs to complete the actual field access once the expression is
+evaluated.
+
+Other more complex rules such as the one to create a new instance of a
+class define constraints on the rewrites and more complex
+transformations on the heap.
+$$
+\mprset{flushleft}
+	\inferrule[New]{
+      \cfgnt{r} = \mathrm{stack}_r\lp \rp\\
+      l = \mathrm{fresh}_l\lp \cfgnt{C}\rp\\\\
+      \cfgnt{R}^\prime = \cfgnt{R}[\forall \cfgnt{f} \in \mathit{fields}\lp \mathrm{C}\rp \ \lp \lp l\ \cfgnt{f}\rp  \mapsto \cfgnt{r}_\mathit{null} \rp ] \\\\
+      \cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}]
+    }{
+      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgt{new}\ \cfgnt{C}\rp \ \cfgnt{k}\rp  \rcom
+      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi\ \eta\ \cfgnt{r}\ \cfgnt{k}\rp 
+	}
+$$
+Here when the string matches the new-expression, it is written to use
+a new heap where all the fields for the new object point to null and
+the location map points a new stack reference to that new object.
+
+The full operational semantics for generalized symbolic execution with
+lazy initialization for Javalite are in the supplemental
+document. From here forward, that machine is referred to by the
+relation $\rgse$ or $p \rgse p^\prime$. The new algorithm for symbolic
+execution with summary heaps is indicated by $\rsym$ or $q \rsym
+q^\prime$, and it is defined in the next section.

### 2014-11-12 tex/javalite.tex

@@
 The algorithm for generalized symbolic execution with symbolic heaps
-is presented using Javalite. Javalite is a syntactic machine defined
-as rewrites on a string \cite{saints-MS}. The semantics are small-step
-using a CESK model with a (C)ontrol string representing the expression
-being evaluated, an (E)nvironment for local variables, a (S)tore for
-the heap, and a (K)ontinuation for what is to be executed next. The
-semantics of the original Javalite machine, and its machine syntax,
-are changed to reflect generalized symbolic execution and then
-generalized execution with symbolic heaps.
+is presented using Javalite. Javalite retains the essence of Java and
+other object oriented languages with formalization in both PLT
+Redex and Coq so the outcome of any program has a precise
+deterministic meaning \cite{saints-MS}.
+
+Javalite, is a syntactic machine defined as rewrites on a string.  The
+semantics are small-step using the CESK model with a (C)ontrol string
+representing the expression being evaluated, an (E)nvironment for
+local variables, a (S)tore for the heap, and a (K)ontinuation for what
+is to be executed next.  The semantics of the original Javalite
+machine, and its machine syntax, are changed to reflect generalized
+symbolic execution and then generalized execution with symbolic heaps.
 
@@
 $\cfgnt{s}$, includes the program registry\footnote{The registry $\mu$
-  is implied in the rewrite rules rather that states for
-  compactness.}, a pair of functions defining the heap
+  is implied in the rewrite rules and note included in the state tuples.}, a pair of functions defining the heap
 $\lp\cfgnt{L}\ \cfgnt{R}\rp$, which is the store, a constraint,

### 2014-11-12 tex/precise.tex
adding a new file for data
Unified notationin the figures and added captions.

@@
 \section{Generating Symbolic Heap Summaries}
+\label{sec:precise}
 
@@
 $\mathbb{UN}$ for field $f$, the $\mathit{min}_l$ function returns
-$(\phi_x, l_x)$ based on a lexical ordering of uninitialized locations
-in $\Lambda$. The init$_r$ method returns a new input reference $r_f$
+$(\phi_x, \cfgnt{l}_x)$ based on a lexical ordering of uninitialized locations
+in $\Lambda$. The init$_r$ method returns a new input reference $\cfgnt{r}_f$
 while the fresh$_f$ returns a new location of type $C$. The set $\rho$
-contains the set of reference location pairs, $(r_a, l_a)$, that the
-field being initialized may alias. The pair $(r_a, l_a)$ is contained
-in the set $ \rho $ if the following conditions hold: (i) $r_a$ is
+contains the set of reference location pairs, $(\cfgnt{r}_a, \cfgnt{l}_a)$, that the
+field being initialized may alias. The pair $(\cfgnt{r}_a, \cfgnt{l}_a)$ is contained
+in the set $ \rho $ if the following conditions hold: (i) $\cfgnt{r}_a$ is
 part of the input references initialized in the summary heap, (ii)
-$r_a$ is in the pre-image of $l_a$, (iii) and the type of $l_a$ is the
+$\cfgnt{r}_a$ is in the pre-image of $\cfgnt{l}_a$, (iii) and the type of $\cfgnt{l}_a$ is the
 same as the type of the field being initialized.
@@
 non-deterministic choices in GSE: (a) $\theta_\mathit{null}$ contains
-a constraint $r_f = r_\mathit{null}$ paired with the location
-$l_\mathit{null}$, (b) $\theta_\mathit{new}$ creates a pair with the
-constraint $r_f$ is not null and it does not alias any reference in
-set $\rho$ under and a newly created location $l_f$, (c) and
-$\theta_\mathit{alias}$ where for each element in the set $(r_a, l_a)
-\in \rho$ it creates a constraints that $r_f$ is not null, points to
-$r_a$, and does not point to any reference contained in $(r_a^\prime,
-l_a^\prime) \in \rho$ such that $r_a < r_a^\prime$ based on a lexical
+a constraint $\cfgnt{r}_f = \cfgnt{r}_\mathit{null}$ paired with the location
+$\cfgnt{l}_\mathit{null}$, (b) $\theta_\mathit{new}$ creates a pair with the
+constraint $\cfgnt{r}_f$ is not null and it does not alias any reference in
+set $\rho$ under and a newly created location $\cfgnt{l}_f$, (c) and
+$\theta_\mathit{alias}$ where for each element in the set $(\cfgnt{r}_a, \cfgnt{l}_a)
+\in \rho$ it creates a constraints that $\cfgnt{r}_f$ is not null, points to
+$\cfgnt{r}_a$, and does not point to any reference contained in $(\cfgnt{r}_a^\prime,
+\cfgnt{l}_a^\prime) \in \rho$ such that $\cfgnt{r}_a < \cfgnt{r}_a^\prime$ based on a lexical
 ordering of initialized references. Additionally
@@
 to this initialization in the summary machine as conditional
-initialization. Finally, the fields of the reference $r_f$ are marked
+initialization. Finally, the fields of the reference $\cfgnt{r}_f$ are marked
 as uninitialized. In the post condition of the rule the reference
-$r_f$ points to $\theta$ which contains the union of all the
+$\cfgnt{r}_f$ points to $\theta$ which contains the union of all the
 constraint location pairs sets, and the field $f$ points to the new
-reference $r_f$ in the summary heap.
+reference $\cfgnt{r}_f$ in the summary heap.
 
@@
 \begin{tabular}[c]{l}
-$\rho := \{ (r_1^i, l_1 \}$ \\
-$\theta_\mathit{null} := \{ ( r_2^i = r_\mathit{null}, l_\mathit{null}) \}$\\
-$\theta_\mathit{new} := \{ ( r_2^i \neq r_\mathit{null} \wedge r_2^i \neq r_1^i, l_2) \}$\\
-$\theta_\mathit{alias} := \{ ( r_1^i \neq r_\mathit{null} \wedge r_2^i \neq r_\mathit{null} \wedge r_2^i = r_1^i, l_1) \}$\\
+$\rho := \{ (\cfgnt{r}_1^i, \cfgnt{l}_1 \}$ \\
+$\theta_\mathit{null} := \{ ( \cfgnt{r}_2^i = \cfgnt{r}_\mathit{null}, \cfgnt{l}_\mathit{null}) \}$\\
+$\theta_\mathit{new} := \{ ( \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_1^i, \cfgnt{l}_2) \}$\\
+$\theta_\mathit{alias} := \{ ( \cfgnt{r}_1^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i = \cfgnt{r}_1^i, \cfgnt{l}_1) \}$\\
 $\theta_\mathit{orig} := \{ \}$ \\
-$\phi_{\mathit{1a}} := r_1^i = r_\mathit{null} $ \\
-$\phi_{\mathit{1b}} := r_1^i \neq r_\mathit{null} $  \\
-$\phi_{\mathit{2a}} := r_2^i = r_\mathit{null}$ \\
-$\phi_{\mathit{2b}} := r_2^i \neq r_\mathit{null} \wedge r_2^i \neq r_1^i$ \\
-$\phi_{\mathit{2c}} :=  r_2^i \neq r_\mathit{null} \wedge r_2^i = r_1^i $ \\
+$\phi_{\mathit{1a}} := \cfgnt{r}_1^i = \cfgnt{r}_\mathit{null} $ \\
+$\phi_{\mathit{1b}} := \cfgnt{r}_1^i \neq \cfgnt{r}_\mathit{null} $  \\
+$\phi_{\mathit{2a}} := \cfgnt{r}_2^i = \cfgnt{r}_\mathit{null}$ \\
+$\phi_{\mathit{2b}} := \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_1^i$ \\
+$\phi_{\mathit{2c}} :=  \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i = \cfgnt{r}_1^i $ \\
 \end{tabular} \\
@@
 \end{center}
-\caption{initialize this.x and this.y}
+\caption{An example that initializes $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ and $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$.
+(a) Initial heap structure.
+(b) After $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ is initialized.
+(c) After $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ is initialized.
+(d) Constraint sets from the summary rule and constraints on the edges.}
 \label{fig:initHeap}
@@
 references with the superscript $s$ indicates that it is a local
-reference. In~\figref{fig:initHeap} $r_0^s$ represents a local
-reference for the $\mathit{this}$ reference which has two fields $x$
-and $y$ of the same type; reference $r_0^s$ points to location
-$l_0$. Note that when no constraint is specified in the graphs, then
-there is a implicit $\mathit{true}$ constraint, for example, $r_0^s$
-points to $l_0$ on the constraint $\mathit{true}$. The fields $x$ and
-$y$ point to the uninitialized reference $r_\mathit{un}$.
+reference. In~\figref{fig:initHeap} $\cfgnt{r}_0^s$ represents a local
+reference for the $\cfgt{this}$ reference which has two fields $x$
+and $y$ of the same type; reference $\cfgnt{r}_0^s$ points to location
+$\cfgnt{l}_0$. Note that when no constraint is specified in the graphs, then
+there is a implicit $\mathit{true}$ constraint, for example, $\cfgnt{r}_0^s$
+points to $\cfgnt{l}_0$ on the constraint $\mathit{true}$. The fields $x$ and
+$y$ point to the uninitialized reference $\cfgnt{r}_\mathit{un}$.
 
-% The reference $r_\mathit{un}$ points to the uninitialized location
-%$l_\mathit{un}$ on the $\mathit{true}$ constraint.
+% The reference $\cfgnt{r}_\mathit{un}$ points to the uninitialized location
+%$\cfgnt{l}_\mathit{un}$ on the $\mathit{true}$ constraint.
 
 The graph in~\figref{fig:initHeap}(b) represents the symbolic heap
-summary after the initialization of the $\mathit{this}.x$ field while
+summary after the initialization of the $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ field while
 the graph in~\figref{fig:initHeap}(c) represents the symbolic heap
-summary after the initialization of the $\mathit{this}.y$ field
-following the initialization of $\mathit{this}.x$. The list
+summary after the initialization of the $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ field
+following the initialization of $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$. The list
 in~\figref{fig:initHeap}(d) represents the various sets constructed in
-the summarize rule during the initialization of $\mathit{this}.y$. We
+the summarize rule during the initialization of $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$. We
 also define values of constraints used as labels in the graph.
 
-The access on $l_0.x$ creates a new input reference $r_1^i$ in the
-summary heap shown in~\figref{fig:initHeap}(b). The reference $r_1^1$
-points to the $l_\mathit{null}$ location under the constraint that
-$r_1^i$ is null: $\phi_{1a} := r_1^i = r_\mathit{null}$. The reference
-$r_1^i$ points to the location $l_1$ under the constraint that $r_1^i$
-is not $\mathit{null}$ $\phi_{1b} :=r_1^i \neq r_\mathit{null}$. The
-location $l_1$ represents a fresh location of type $C$ is created on
-the heap such that $C$ is type of $\mathit{this}.x$.
+The access on $\cfgnt{l}_0.x$ creates a new input reference $\cfgnt{r}_1^i$ in the
+summary heap shown in~\figref{fig:initHeap}(b). The reference $\cfgnt{r}_1^1$
+points to the $\cfgnt{l}_\mathit{null}$ location under the constraint that
+$\cfgnt{r}_1^i$ is null: $\phi_{1a} := \cfgnt{r}_1^i = \cfgnt{r}_\mathit{null}$. The reference
+$\cfgnt{r}_1^i$ points to the location $\cfgnt{l}_1$ under the constraint that $\cfgnt{r}_1^i$
+is not $\mathit{null}$ $\phi_{1b} :=\cfgnt{r}_1^i \neq \cfgnt{r}_\mathit{null}$. The
+location $\cfgnt{l}_1$ represents a fresh location of type $C$ is created on
+the heap such that $C$ is type of $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$.
 
-Following the initialization to the $\mathit{this}.x$, when we
-initialize $\mathit{this}.y$ the resulting summary heap is shown
+Following the initialization to the $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$, when we
+initialize $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ the resulting summary heap is shown
 in~\figref{fig:initHeap}(c). The set $\rho$ shown
 in~\figref{fig:initHeap}(d) contains the potential aliases for
-$\mathit{this}.y$ which is location $l_1$ ($\mathit{this}.x$). The
+ $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ which is location $\cfgnt{l}_1$ ($\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$). The
 constraint location $\theta$ sets represents the initialization
-choices for $\mathit{this}.y$. The new input reference $r_2^i$ for
-$this.y$ points to (a) location $l_\mathit{null}$ under the constraint
-$\phi_{2a} := r_2^i = r_\mathit{null}$, (b) location $l_2$ under the
-constraint $\phi_{2b} := r_2^i \neq r_\mathit{null} \wedge r_2^i \neq
-r_1^i$ that states that $r_2^i$ is not null and does not alias
-$r_1^i$, and (c) location $l_1$ under the constraint $\phi_{2c} :=
-r_2^i \neq r_\mathit{null} \wedge r_2^i = r_1^i$ that states $r_2^i$
-is not null and \emph{does} alias $r_1^i$.
+choices for $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$. The new input reference $\cfgnt{r}_2^i$ for
+$\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ points to (a) location $\cfgnt{l}_\mathit{null}$ under the constraint
+$\phi_{2a} := \cfgnt{r}_2^i = \cfgnt{r}_\mathit{null}$, (b) location $\cfgnt{l}_2$ under the
+constraint $\phi_{2b} := \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq
+\cfgnt{r}_1^i$ that states that $\cfgnt{r}_2^i$ is not null and does not alias
+$\cfgnt{r}_1^i$, and (c) location $\cfgnt{l}_1$ under the constraint $\phi_{2c} :=
+\cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i = \cfgnt{r}_1^i$ that states $\cfgnt{r}_2^i$
+is not null and \emph{does} alias $\cfgnt{r}_1^i$.
 
@@
 \end{center}
-\caption{field access for this.y and field write for this.x = this.y}
+\caption{Field read and write relations with an example heap.
+(a) Field-access, $\rsym^\mathit{A}$, and field-write, $\rsym^\mathit{W}$, rewrite rules for the $\rsym$ relation.
+(b) The final heap after $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\ \cfgt{:=}\ \lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp\rp$.}
 \label{fig:fHeap}
@@
 Consider the graph shown in~\figref{fig:fHeap}(b) the reference
-$r_2^i$ is created during the initialization of $\mathit{this}.y$. The
+$\cfgnt{r}_2^i$ is created during the initialization of $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$. The
 reference that is returned during the access of the field, however, is
-$r_3^s$. The reference $r_3^s$ points to the value set of $r_2^i$
-which are: $(\phi_{2a}, l_\mathit{null})$, $(\phi_{2b}, l_2)$, and
-$(\phi_{2c}, l_1)$. The values of the constraints $\phi_{2a}$,
+$\cfgnt{r}_3^s$. The reference $\cfgnt{r}_3^s$ points to the value set of $\cfgnt{r}_2^i$
+which are: $(\phi_{2a}, \cfgnt{l}_\mathit{null})$, $(\phi_{2b}, \cfgnt{l}_2)$, and
+$(\phi_{2c}, \cfgnt{l}_1)$. The values of the constraints $\phi_{2a}$,
 $\phi_{2b}$, and $\phi_{2c}$ are defined in~\figref{fig:initHeap}(d).
@@
 non-nullness check we We look up the value of the base reference in
-the environment $\eta(x)$.  The reference $r_x$ is the base pointer
-whose field, $r_\mathit{curr}$ is being written to to while the
+the environment $\eta(x)$.  The reference $\cfgnt{r}_x$ is the base pointer
+whose field, $\cfgnt{r}_\mathit{curr}$ is being written to to while the
 reference $r$ is the target reference. The set $\Psi_x$ contains
-tuples $(\phi l r_\mathit{curr})$ of constraints, locations, and
-references. These tuples represent access chains leading from $r_x$ to
-the reference of the field, $r_\mathit{curr}$. The goal is to
-overwrite the $r_\mathit{curr}$ references with the target
+tuples $(\phi l \cfgnt{r}_\mathit{curr})$ of constraints, locations, and
+references. These tuples represent access chains leading from $\cfgnt{r}_x$ to
+the reference of the field, $\cfgnt{r}_\mathit{curr}$. The goal is to
+overwrite the $\cfgnt{r}_\mathit{curr}$ references with the target
 references. Since the target of the write is $r$, we first check that
 the location constraint pairs of $L(r)$ are satisfiable when accessed
-through the $r_x$ chain. This is accomplished by the strengthening
+through the $\cfgnt{r}_x$ chain. This is accomplished by the strengthening
 function.
@@
 Note that the write is conditional. In the case that $\phi$ is true
-then $r_\mathit{curr}$ will point to the constraint location pairs of
-$L(r)$ while if $\phi$ is false then $r_\mathit{curr}$ will continue
+then $\cfgnt{r}_\mathit{curr}$ will point to the constraint location pairs of
+$L(r)$ while if $\phi$ is false then $\cfgnt{r}_\mathit{curr}$ will continue
 to point to the constraint location pair it is currently pointing to.
 Again since the references are immutable we create a new reference for
-each $r_\mathit{curr}$ and point them to the target constraint
+each $\cfgnt{r}_\mathit{curr}$ and point them to the target constraint
 location pairs.
@@
 Consider the example shown in~\figref{fig:fHeap}(b) where we assign
-$\mathit{this}.x := \mathit{this}.y$. Note that
-in~\figref{fig:initHeap}(c) $\mathit{this}.x$ is represented by
-$r_1^i$. After applying the field-write rule the reference $r_1^i$ is
-replaced by the fresh reference $r_4$ which now points to target
-$\mathit{this}.y$ represented by $L(r_2^i)$.
+$\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\ \cfgt{:=}\ \lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp\rp$. Note that
+in~\figref{fig:initHeap}(c) $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ is represented by
+$\cfgnt{r}_1^i$. After applying the field-write rule the reference $\cfgnt{r}_1^i$ is
+replaced by the fresh reference $\cfgnt{r}_4$ which now points to target
+ $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ represented by $L(\cfgnt{r}_2^i)$.
 
@@
 \begin{tabular}[c]{l}
-$\Psi_x = \{ (true, l_0, r_1^i) \}$\\
-$ST (L, r_3^s, \phi, \phi_g)$ \\
-$\theta = \{ (\phi_{2a}\; l_\mathit{null} ) (\phi_{2b}\; l_2) (\phi_{2c}\; l_1) \}$\\
-$ST(L, r_0, \phi, \phi_g)$\\
+$\Psi_x = \{ (true, \cfgnt{l}_0, \cfgnt{r}_1^i) \}$\\
+$ST (L, \cfgnt{r}_3^s, \phi, \phi_g)$ \\
+$\theta = \{ (\phi_{2a}\; \cfgnt{l}_\mathit{null} ) (\phi_{2b}\; \cfgnt{l}_2) (\phi_{2c}\; \cfgnt{l}_1) \}$\\
+$ST(L, \cfgnt{r}_0, \phi, \phi_g)$\\
 $\theta = \{ \}$\\
@@
 \end{center}
-\caption{FIXME: I desperately need a caption!}
+\caption{The reference compare rewrite rule for both the true, $\rsym^\mathit{E}$, and false, $\rsym^\mathit{E^\prime}$ outcomes.}
 \label{fig:eqs}
@@
 \begin{tabular}[c]{l}
-$L(r_1^i) = \{ (\phi_{1a}\; l_\mathit{null})\; (\phi_{1b}\; l_1) \}$ \\
-$L(r_2^i) = \{ (\phi_{2a}\; l_\mathit{null}),\; (\phi_{2b}\; l_2),\; (\phi_{2c}\; l_1) \} $\\
+$L(\cfgnt{r}_1^i) = \{ (\phi_{1a}\; \cfgnt{l}_\mathit{null})\; (\phi_{1b}\; \cfgnt{l}_1) \}$ \\
+$L(\cfgnt{r}_2^i) = \{ (\phi_{2a}\; \cfgnt{l}_\mathit{null}),\; (\phi_{2b}\; \cfgnt{l}_2),\; (\phi_{2c}\; \cfgnt{l}_1) \} $\\
   $\theta_0 = \{ \} $\\
@@
 heap are shown in~\figref{fig:eqs}. The equals references-true rewrite
-rule returns true when two references $r_0$ and $r_1$ \emph{can} be
+rule returns true when two references $\cfgnt{r}_0$ and $\cfgnt{r}_1$ \emph{can} be
 equal. In GSE semantics checking equality of references is a simple
@@
 in~\figref{fig:eqs}. In order to check equality we construct three
-sets of constraints. For all constraint location pairs $(\phi_0, l_0)
-\in L(r_0)$ and $(\phi_1, l_1) \in L(r_1)$ such that $l_0$ and $l_1$
-are the same ($l_0 = l_1$) we create conjunctions of the constraints
+sets of constraints. For all constraint location pairs $(\phi_0, \cfgnt{l}_0)
+\in L(\cfgnt{r}_0)$ and $(\phi_1, \cfgnt{l}_1) \in L(\cfgnt{r}_1)$ such that $\cfgnt{l}_0$ and $\cfgnt{l}_1$
+are the same ($\cfgnt{l}_0 = \cfgnt{l}_1$) we create conjunctions of the constraints
 $\phi_0 \wedge \phi_1$ and add them to set $\Phi_\alpha$. Intutively,
-$\Phi_\alpha$ contains all constraints under which $r_0$ and $r_1$ may
+$\Phi_\alpha$ contains all constraints under which $\cfgnt{r}_0$ and $\cfgnt{r}_1$ may
 point to the same location in the symbolic summary heap. The second
-set, $\Phi_0$, contains constraints under which the reference $r_0$
-points corresponding locations such that the reference $r_1$
+set, $\Phi_0$, contains constraints under which the reference $\cfgnt{r}_0$
+points corresponding locations such that the reference $\cfgnt{r}_1$
 \emph{does not} point to those locations under any
 constraint. Finally, the set, $\Phi_1$, contains constraints under
-which $r_1$ points to corresponding locations and $r_0$ \emph{does
+which $\cfgnt{r}_1$ points to corresponding locations and $\cfgnt{r}_0$ \emph{does
   not} point to those locations under any constraint.
@@
 in $\Phi_\alpha$ to indicate that if any of the constraints are
-satisfiable, then references $r_0$ and $r_1$ can be
+satisfiable, then references $\cfgnt{r}_0$ and $\cfgnt{r}_1$ can be
 equal. Furthermore, we had to the global heap constraint,
@@
 Consider the example in~\figref{fig:initHeap}(c). In order to to check
-if $r_1^i$ and $r_2^i$ are equal we first get the constraint location
+if $\cfgnt{r}_1^i$ and $\cfgnt{r}_2^i$ are equal we first get the constraint location
 pairs associated with each of the references:
@@
 \[
-L(r_1^i) = \{ (\phi_{1a}\; l_\mathit{null})\; (\phi_{1b}\; l_1) \} 
+L(\cfgnt{r}_1^i) = \{ (\phi_{1a}\; \cfgnt{l}_\mathit{null})\; (\phi_{1b}\; \cfgnt{l}_1) \} 
 \]
 \[
-L(r_2^i) = \{ (\phi_{2a}\; l_\mathit{null}),\; (\phi_{2b}\; l_2),\; (\phi_{2c}\; l_1) \} \\
+L(\cfgnt{r}_2^i) = \{ (\phi_{2a}\; \cfgnt{l}_\mathit{null}),\; (\phi_{2b}\; \cfgnt{l}_2),\; (\phi_{2c}\; \cfgnt{l}_1) \} \\
 \]

### 2014-11-12 tex/precise.tex
Removed commas in tuples

@@
 $\mathbb{UN}$ for field $f$, the $\mathit{min}_l$ function returns
-$(\phi_x, \cfgnt{l}_x)$ based on a lexical ordering of uninitialized locations
+$(\phi_x\ \cfgnt{l}_x)$ based on a lexical ordering of uninitialized locations
 in $\Lambda$. The init$_r$ method returns a new input reference $\cfgnt{r}_f$
 while the fresh$_f$ returns a new location of type $C$. The set $\rho$
-contains the set of reference location pairs, $(\cfgnt{r}_a, \cfgnt{l}_a)$, that the
-field being initialized may alias. The pair $(\cfgnt{r}_a, \cfgnt{l}_a)$ is contained
+contains the set of reference location pairs, $(\cfgnt{r}_a\ \cfgnt{l}_a)$, that the
+field being initialized may alias. The pair $(\cfgnt{r}_a\ \cfgnt{l}_a)$ is contained
 in the set $ \rho $ if the following conditions hold: (i) $\cfgnt{r}_a$ is
@@
 set $\rho$ under and a newly created location $\cfgnt{l}_f$, (c) and
-$\theta_\mathit{alias}$ where for each element in the set $(\cfgnt{r}_a, \cfgnt{l}_a)
+$\theta_\mathit{alias}$ where for each element in the set $(\cfgnt{r}_a\ \cfgnt{l}_a)
 \in \rho$ it creates a constraints that $\cfgnt{r}_f$ is not null, points to
-$\cfgnt{r}_a$, and does not point to any reference contained in $(\cfgnt{r}_a^\prime,
+$\cfgnt{r}_a$, and does not point to any reference contained in $(\cfgnt{r}_a^\prime\ 
 \cfgnt{l}_a^\prime) \in \rho$ such that $\cfgnt{r}_a < \cfgnt{r}_a^\prime$ based on a lexical
@@
 \begin{tabular}[c]{l}
-$\rho := \{ (\cfgnt{r}_1^i, \cfgnt{l}_1 \}$ \\
-$\theta_\mathit{null} := \{ ( \cfgnt{r}_2^i = \cfgnt{r}_\mathit{null}, \cfgnt{l}_\mathit{null}) \}$\\
-$\theta_\mathit{new} := \{ ( \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_1^i, \cfgnt{l}_2) \}$\\
-$\theta_\mathit{alias} := \{ ( \cfgnt{r}_1^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i = \cfgnt{r}_1^i, \cfgnt{l}_1) \}$\\
+$\rho := \{ (\cfgnt{r}_1^i\ \cfgnt{l}_1 \}$ \\
+$\theta_\mathit{null} := \{ ( \cfgnt{r}_2^i = \cfgnt{r}_\mathit{null}\ \cfgnt{l}_\mathit{null}) \}$\\
+$\theta_\mathit{new} := \{ ( \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_1^i\ \cfgnt{l}_2) \}$\\
+$\theta_\mathit{alias} := \{ ( \cfgnt{r}_1^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i = \cfgnt{r}_1^i\ \cfgnt{l}_1) \}$\\
 $\theta_\mathit{orig} := \{ \}$ \\
@@
 $\cfgnt{r}_3^s$. The reference $\cfgnt{r}_3^s$ points to the value set of $\cfgnt{r}_2^i$
-which are: $(\phi_{2a}, \cfgnt{l}_\mathit{null})$, $(\phi_{2b}, \cfgnt{l}_2)$, and
-$(\phi_{2c}, \cfgnt{l}_1)$. The values of the constraints $\phi_{2a}$,
+which are: $(\phi_{2a}\ \cfgnt{l}_\mathit{null})$, $(\phi_{2b}\ \cfgnt{l}_2)$, and
+$(\phi_{2c}\ \cfgnt{l}_1)$. The values of the constraints $\phi_{2a}$,
 $\phi_{2b}$, and $\phi_{2c}$ are defined in~\figref{fig:initHeap}(d).
@@
 reference $r$ is the target reference. The set $\Psi_x$ contains
-tuples $(\phi l \cfgnt{r}_\mathit{curr})$ of constraints, locations, and
+tuples $(\phi\ l\ \cfgnt{r}_\mathit{curr})$ of constraints, locations, and
 references. These tuples represent access chains leading from $\cfgnt{r}_x$ to
@@
 references. Since the target of the write is $r$, we first check that
-the location constraint pairs of $L(r)$ are satisfiable when accessed
+the location constraint pairs of $\cfgnt{L}(r)$ are satisfiable when accessed
 through the $\cfgnt{r}_x$ chain. This is accomplished by the strengthening
@@
 then $\cfgnt{r}_\mathit{curr}$ will point to the constraint location pairs of
-$L(r)$ while if $\phi$ is false then $\cfgnt{r}_\mathit{curr}$ will continue
+$\cfgnt{L}(\cfgnt{r})$ while if $\phi$ is false then $\cfgnt{r}_\mathit{curr}$ will continue
 to point to the constraint location pair it is currently pointing to.
@@
 replaced by the fresh reference $\cfgnt{r}_4$ which now points to target
- $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ represented by $L(\cfgnt{r}_2^i)$.
+ $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ represented by $\cfgnt{L}(\cfgnt{r}_2^i)$.
 
@@
 \begin{tabular}[c]{l}
-$\Psi_x = \{ (true, \cfgnt{l}_0, \cfgnt{r}_1^i) \}$\\
-$ST (L, \cfgnt{r}_3^s, \phi, \phi_g)$ \\
+$\Psi_x = \{ (true\ \cfgnt{l}_0\ \cfgnt{r}_1^i) \}$\\
+$ST (\cfgnt{L}, \cfgnt{r}_3^s, \phi, \phi_g)$ \\
 $\theta = \{ (\phi_{2a}\; \cfgnt{l}_\mathit{null} ) (\phi_{2b}\; \cfgnt{l}_2) (\phi_{2c}\; \cfgnt{l}_1) \}$\\
-$ST(L, \cfgnt{r}_0, \phi, \phi_g)$\\
+$ST(\cfgnt{L}, \cfgnt{r}_0, \phi, \phi_g)$\\
 $\theta = \{ \}$\\
@@
 \begin{tabular}[c]{l}
-$L(\cfgnt{r}_1^i) = \{ (\phi_{1a}\; \cfgnt{l}_\mathit{null})\; (\phi_{1b}\; \cfgnt{l}_1) \}$ \\
-$L(\cfgnt{r}_2^i) = \{ (\phi_{2a}\; \cfgnt{l}_\mathit{null}),\; (\phi_{2b}\; \cfgnt{l}_2),\; (\phi_{2c}\; \cfgnt{l}_1) \} $\\
+$\cfgnt{L}(\cfgnt{r}_1^i) = \{ (\phi_{1a}\; \cfgnt{l}_\mathit{null})\; (\phi_{1b}\; \cfgnt{l}_1) \}$ \\
+$\cfgnt{L}(\cfgnt{r}_2^i) = \{ (\phi_{2a}\; \cfgnt{l}_\mathit{null}),\; (\phi_{2b}\; \cfgnt{l}_2),\; (\phi_{2c}\; \cfgnt{l}_1) \} $\\
   $\theta_0 = \{ \} $\\
@@
 in~\figref{fig:eqs}. In order to check equality we construct three
-sets of constraints. For all constraint location pairs $(\phi_0, \cfgnt{l}_0)
-\in L(\cfgnt{r}_0)$ and $(\phi_1, \cfgnt{l}_1) \in L(\cfgnt{r}_1)$ such that $\cfgnt{l}_0$ and $\cfgnt{l}_1$
+sets of constraints. For all constraint location pairs $(\phi_0\ \cfgnt{l}_0)
+\in \cfgnt{L}(\cfgnt{r}_0)$ and $(\phi_1\ \cfgnt{l}_1) \in \cfgnt{L}(\cfgnt{r}_1)$ such that $\cfgnt{l}_0$ and $\cfgnt{l}_1$
 are the same ($\cfgnt{l}_0 = \cfgnt{l}_1$) we create conjunctions of the constraints
@@
 pairs associated with each of the references:
-
 \[
-L(\cfgnt{r}_1^i) = \{ (\phi_{1a}\; \cfgnt{l}_\mathit{null})\; (\phi_{1b}\; \cfgnt{l}_1) \} 
+\cfgnt{L}(\cfgnt{r}_1^i) = \{ (\phi_{1a}\; \cfgnt{l}_\mathit{null})\; (\phi_{1b}\; \cfgnt{l}_1) \} 
 \]
 \[
-L(\cfgnt{r}_2^i) = \{ (\phi_{2a}\; \cfgnt{l}_\mathit{null}),\; (\phi_{2b}\; \cfgnt{l}_2),\; (\phi_{2c}\; \cfgnt{l}_1) \} \\
+\cfgnt{L}(\cfgnt{r}_2^i) = \{ (\phi_{2a}\; \cfgnt{l}_\mathit{null})\; (\phi_{2b}\; \cfgnt{l}_2)\; (\phi_{2c}\; \cfgnt{l}_1) \} \\
 \]
-
 \noindent{The three constraint sets are:} 
-
 \[
@@
 \]
-
 \noindent{Finally the global constraint is} 
@@
 \]
-
 \noindent{The equals references-false is the logical dual of the

### 2014-11-12 tex/javalite.tex
updates to javalite and fixed missing paren in CL definition in surface syntax

--- 2014-11-11 tex/javalite.tex
@@
-\section{Javalite}
-The algorithm for generalized symbolic execution with symbolic heaps
-is presented using Javalite. Javalite is a syntactic machine defined
-as rewrites on a string \cite{saints-MS}. The semantics are small-step
-using a CESK model with a (C)ontrol string representing the expression
-being evaluated, an (E)nvironment for local variables, a (S)tore for
-the heap, and a (K)ontinuation for what is to be executed next. The
-semantics of the original Javalite machine, and its machine syntax,
-are changed to reflect generalized symbolic execution and then
-generalized execution with symbolic heaps.
+\section{Background}
+\subsection{Javalite}
+We present our summary heap algorithm using Javalite, an
+executable formalization of a Java-like language~\cite{saints-MS}. Javalite retains 
+the essence of Java and other object-oriented languages with formalizations 
+in both PLT Redex and Coq so that the outcome of any program has a precise
+and deterministic meaning.
 
-The surface syntax (input) for Javalite is in
-\figref{fig:surface-syntax} with the machine syntax (state) in
-\figref{fig:machine-syntax}. Terminals are in bold face while
+Javalite is a syntactic machine defined as rewrites on a string.  The
+semantics are small-step using the CEKS model with a (C)ontrol string
+representing the expression being evaluated, an (E)nvironment for
+local variables, a (S)tore for the heap, and a (K)ontinuation for what
+is to be executed next.  In this work we change the semantics of the original
+ Javalite machine and its machine syntax to represent (i) generalized
+symbolic execution~\cite{GSE03}, and (ii) the summary heap algorithm
+presented in this work.
+
+The surface syntax (input) for Javalite is shown 
+in~\figref{fig:surface-syntax}, and the machine syntax (state)
+in~\figref{fig:machine-syntax}. Terminals are in bold face while
 non-terminals are italicized. Ellipses indicate zero or more
@@
 Boolean. Classes have fields, $([\cfgnt{T}\ \cfgnt{f}]\ ...)$, and
-methods, $(\cfgnt{M}\ ...)$. Methods only take a single
-parameter. Expressions, $\cfgnt{e}$, are somewhat typical with
-$\cfgt{:=}$ indicating assignment, $\cfgt{=}$ indicating comparison,
-$\cfgt{\$}$ as the dot-operator for field access, and $\cfgt{@}$ as
-the dot-operator for method invocation. There is no explicit return
+methods, $(\cfgnt{M}\ ...)$. Methods are limited to a single
+parameter in our Javalite machine. Expressions, $\cfgnt{e}$, are 
+equivalent to a CEKS machine's control string, 
+%somewhat typical
+where $\cfgt{:=}$ indicates assignment, $\cfgt{=}$ indicates comparison,
+and $\cfgt{\$}$ represents the dot-operator for field access. The dot-operator
+for method invocation is represented by $\cfgt{@}$. There is no explicit return
 statement in Javalite; rather, the value of the last expression is
-used as a return value. A variable is always indicated by \cfgnt{x}
+used as the return value. A variable is always indicated by \cfgnt{x}
 and a value by \cfgnt{v}. A value can be a reference in the heap,
-$\cfgnt{r}$, or any of the special values. It is assumed that only
+$\cfgnt{r}$, or any of the special values shown in~\figref{fig:surface-syntax}. 
+We assume that only
 type correct programs are given as input to the machine.
@@
 The state of the Javalite machine (\figref{fig:machine-syntax}),
-$\cfgnt{s}$, includes the program registry\footnote{The registry $\mu$
-  is implied in the rewrite rules rather that states for
-  compactness.}, a pair of functions defining the heap
-$\lp\cfgnt{L}\ \cfgnt{R}\rp$, which is the store, a constraint,
+$\cfgnt{s}$, includes the program registry, $\mu$\footnote{The registry $\mu$
+  is implied in the rewrite rules and not included in the state tuples.},
+  and a pair of functions defining the heap
+$\lp\cfgnt{L}\ \cfgnt{R}\rp$, which is the store. The state also
+includes a constraint,
 $\phi$, defined over references in the heap, the environment, $\eta$,
 for local variables, and the continuation $\cfgnt{k}$. The more
-complex structures such as the environment are defined as lists which
+complex structures, such as the environment, are defined as lists which
 start with empty, \cfgnt{mt}. The rewrite rules that define the
 semantics treat these lists as partial functions. As such,
-$\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference mapped to the variable
+$\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference $\cfgnt{r}$ mapped to the variable
 $\cfgnt{x}$. The notation $\eta^\prime = \eta[\cfgnt{x} \mapsto
   \cfgnt{v}]$ defines a new partial function $\eta^\prime$ that is
-just like $\eta$ only the variable $\cfgnt{x}$ now maps to
+the same as $\eta$ except that the variable $\cfgnt{x}$ now maps to
 $\cfgnt{v}$.

### 2014-11-12 tex/intro.tex
changes to intro

@@
 %accounts for various heap configurations, 
-creates additional non-deterministic 
-choice points in the symbolic execution tree representing 
-the feasible heap configurations.
-as (a) null, (b) instance of a new
-reference of a compatible class, and (c) alias an previously
-initialized symbolic reference. 
-Symbolic execution follows concrete program semantics for 
-materialized heap locations. Although this approach
-enables analysis of heap manipulating programs, a large number
-of feasible concrete heap configurations may be created 
-exacerbating
-the well known state space explosion problem
-associated with symbolic execution.
+creates additional non-deterministic choice points in the symbolic
+execution tree representing the feasible heap configurations.  as (a)
+null, (b) instance of a new reference of a compatible class, and (c)
+alias an previously initialized symbolic reference.  Symbolic
+execution follows concrete program semantics for materialized heap
+locations. Although this approach enables analysis of heap
+manipulating programs, a large number of feasible concrete heap
+configurations may be created exacerbating the well known state space
+explosion problem associated with symbolic execution.
 
@@
 
-Research in the abstract interpretation community has taken
-a very different approach to analyzing heap manipulating
-programs which computes a summary of possible heaps. 
-These techniques start with an initial heap configuration 
-and then using a static analysis, make updates to the
-heap following program semantics, ultimately creating a heap 
-summary which represents the potential heaps resulting from
-program execution~\cite{Dillig:2011}. Because these
-techniques are based on a static analysis, the heap summaries
-over-approximate the set of feasible heap configurations.
-%The primary challenge relative to heap
-%analysis for these techniques is to 
-%resolve potential dependencies of local results on the global
-%aliases in the heap. 
-%Recent work addresses these issues
-%through strong updates to heap locations 
-%at call sites~\cite{Dillig} and computation of dangerous 
-%aliases~\cite{Matosevic}. Because these techniques are based 
-%on a static analysis, the resulting summaries over-approximate
-%the actual potential heaps.
+The goal of this work is to mitigate the state space explosion problem
+in GSE by grouping multiple heaps together and only partitioning the
+heaps at points of divergence in the control flow graph. To achieve
+this goal, we found inspiration from recent work in the domain of
+static analysis that uses sets of constraints over heap locations to
+encode multiple heaps in a single representation. These sets,
+sometimes known as value sets or value summaries, allow multiple heaps
+to be represented simultaneously with a higher degree of precision
+than afforded by traditional shape analysis techniques. Some of these
+previous attempts, however, are unable to handle aliasing in heaps due
+to a recursive definition of objects~\cite{..}, while others require a
+set of heaps as input and are unable to initialize heaps
+on-the-fly~\cite{..}. For these reasons the techniques use
+over-approximations to reason about heaps and may report false
+positives. Also, an update to the heap required a rewrite of the
+constraint system making it prohitive for use in the context of
+symbolic execution.
+
+%The goal of this work is find a more compact representation of the heaps
+%and be better able to leverage constraint solvers.
+%The  But any update of the heap required a rewrite on the constraint system
+%or simply was not opssible to initialize and handle the aliasing possiblities.
+
+%The goal is to leverage that
+
+%Research in the abstract interpretation community has taken a very
+%different approach to analyzing heap manipulating programs which
+%computes a summary of possible heaps.  These techniques start with an
+%initial heap configuration and then using a static analysis, make
+%updates to the heap following program semantics, ultimately creating
+%a heap summary which represents the potential heaps resulting from
+%program execution~\cite{Dillig:2011}. Because these techniques are
+%based on a static analysis, the heap summaries over-approximate the
+%set of feasible heap configurations.
+
+%The primary challenge relative to heap analysis for these techniques
+%is to resolve potential dependencies of local results on the global
+%aliases in the heap.  Recent work addresses these issues through
+%strong updates to heap locations at call sites~\cite{Dillig} and
+%computation of dangerous aliases~\cite{Matosevic}. Because these
+%techniques are based on a static analysis, the resulting summaries
+%over-approximate the actual potential heaps.
 
 In this work, we present a novel heap initialization and analysis
-technique which takes inspiration from both GSE and existing
-heap summarization techniques. The intuition behind our analysis
-is to construct the heap lazily during symbolic execution
-but reduce the points of non-determinism in
-the symbolic execution tree by analyzing each control-flow
-path only once for any given set of isomorphic heaps. To 
-represent the exact set of feasible concrete heap structures 
-resulting from execution of the control-flow path, we use
-a heap summary.
-Our analysis improves on existing GSE approaches by 
-reducing the size of the symbolic execution state space explored,
-thereby improving scalability of symboic execution for heap
-manipulating software. It improves on existing heap summarization
-techniques by enabling analysis of arbitrary recursive data structures 
-(no initial heap configuration is required) while avoiding the imprecision
+technique which takes inspiration from both GSE and existing heap
+summarization techniques. The intuition behind our analysis is to
+construct the heap lazily during symbolic execution but reduce the
+points of non-determinism in the symbolic execution tree by analyzing
+each control-flow path only once for any given set of isomorphic
+heaps. To represent the exact set of feasible concrete heap structures
+resulting from execution of the control-flow path, we use a heap
+summary.  Our analysis improves on existing GSE approaches by reducing
+the size of the symbolic execution state space explored, thereby
+improving scalability of symboic execution for heap manipulating
+software. It improves on existing heap summarization techniques by
+enabling analysis of arbitrary recursive data structures (no initial
+heap configuration is required) while avoiding the imprecision
 introduced by these techniques.

### 2014-11-12 tex/results.tex
adding a todo about the evaluation set up
Added label on results section

@@
 \section{Evaluation}
-
+\label{sec:eval}
 In this section we evaluate the effectiveness of \symtxt{} at
@@
 To perform our study we compile all our artifacts and run the analysis
-on \nsr{the machine}.
+on \nsr{the machine.. sthuff about the time bound etc.}.
 

### 2014-11-12 tex/javalite.tex
Restricted fields to non-primitive types

@@
 where execution starts. The only primitive type in Javalite is
-Boolean. Classes have fields, $([\cfgnt{T}\ \cfgnt{f}]\ ...)$, and
-methods, $(\cfgnt{M}\ ...)$. Methods are limited to a single
+Boolean. Classes have fields non-primitive, $([\cfgnt{C}\ \cfgnt{f}]\ ...)$, and
+methods, $(\cfgnt{M}\ ...)$.\footnote{Summary heaps are able to support non-primitive fields (see \secref{sec:eval}).
+They are omitted to focus and simplify the presentation.} Methods are limited to a single
 parameter in our Javalite machine. Expressions, $\cfgnt{e}$, are 

### 2014-11-12 tex/definitions.tex
Reworked supplemental upto definitions and proofs.

@@
-\subsection{Heap Properties}
+\section{Definitions}
+
+\begin{definition}
+The set of \textbf{references} $\mathcal{R}$ is defined as the set of natural numbers
+ $$\mathcal{R} = \mathbb{N}$$
+\end{definition}
+
+In order to make the distinction between different types of references, we partition the set of references using modular arithmetic.
+Stack references are those references which are created as a result of a field read.
+The total number of references in a representing state and a represented state are generally not the same.
+However, the number of references on the stack in either state is always the same.
+
+\begin{definition}
+The set of \textbf{stack references} $\mathcal{R}_t$ is defined as
+ $$\mathcal{R}_t =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 0\}$$. 
+\end{definition}
+
+Input heap references are references that exist prior to program execution in the symbolic input heap.
+While this set of references may be infinite, they are discovered one at a time via lazy initialization.
+
+\begin{definition}
+The set of \textbf{input heap references} $\mathcal{R}_h$ is defined as
+ $$\mathcal{R}_h =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 1\}$$. 
+\end{definition}
+
+\begin{definition}
+The set of \textbf{new heap references} $\mathcal{R}_f$ is defined as
+ $$\mathcal{R}_f =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$. 
+\end{definition}
+
+\begin{definition}
+For a given function $f:A \mapsto B$, the \textbf{image} $f^\rightarrow$ and \textbf{preimage} $f^\leftarrow$ are defined as
+\begin{align}
+ f^\rightarrow &= \{ f(a) \mid a \in A\}\\
+ f^\leftarrow &= \{ a \mid f(a) \in B \}
+ \end{align}
+ The bracket notation $ f^\rightarrow [C] $ is used to denote that the image is drawn from a specific subset:
+ \begin{align}
+ f^\rightarrow [C] &= \{ f(a) \mid a \in C\}\\
+ f^\leftarrow [D] &= \{ a \mid f(a) \in D \}
+ \end{align}
+ Where $C \subset A$ and $D \subset B$
+\end{definition}
+
+A special reference, $\cfgnt{r}_\mathit{un}$, and location,
+$\cfgnt{l}_\mathit{un}$, is introduced to support lazy
+initialization. The '$\mathit{un}$' is to indicate the reference or
+location is uninitialized at the point of execution.
+
+\begin{definition}
+\label{def:state}
+The set of \textbf{states} $\mathcal{S}$ is defined as the set of strings matching the pattern $s$ in \ref{fig:machine-syntax}.
+\end{definition}
+
+\begin{definition}
+\label{def:initstate}
+$\mathcal{S}_0$ is defined as the set of \textbf{initial states}. An
+initial state is a state meeting the following conditions: The range
+of L has exactly three locations: $l_{null}$, $l_{un}$, and $l_0$, the
+function R is defined only for location $l_0$, and for any field $f$,
+$R(l_0,f)$ returns $r_{un}$.
+\end{definition}
+
+The rewrite rules that define the Javalite semantics are presented in
+the supplemental document accompanying the paper.
+
+\begin{definition}
+A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary
+relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times
+\mathcal{S} $, which relates machine states with successor states. Two
+important state transition relations are \textbf{GSE} $\rgse$ and
+\textbf{symbolic} $\rsym$. Each of these use a separate relation for
+initialization: $\rinit$ for GSE and $\rsum$ for symbolic. All of
+these transition relations are defined in \figref{fig:lazy},
+\figref{fig:lazyInit}, \figref{fig:sym}, and \figref{fig:symInit}.
+\end{definition}
 

### 2014-11-12 tex/lazy.tex
Reworked supplemental upto definitions and proofs.

@@
 
-Recall that in generalized symbolic execution (GSE) for lazy
-initialization of symbolic references consists of three key points of
-non-determinism where each symbolic reference can be initialized
-non-deterministically to null, a new instance of the symbolic
-reference, or aliases to symbolic references of the same type
-previously initialized. The initialization in GSE consists of creating
-branches in the execution tree for all the non-deterministic choices.
+The specialization of Javalite to generalized symbolic execution with
+lazy initialization using the summary heap is in \figref{fig:lazyInit}
+for the initialization and \figref{fig:lazy} for how the
+initialization is used. Specifically, the field-access rule in
+\figref{fig:lazy} uses initialization, $\rightarrow_I^*$, to be sure
+the accessed field is instantiated. Initialization in generalized
+symbolic execution never happens for more than one object on any use
+of $\rightarrow_I^*$: $\Lambda$ is either empty or contains exactly one
+location.
+
+An uninitialized object may be lazily initialized
+non-deterministically to null, a new instance of the object, or an to
+an object of the same type also initialized lazily. The
+non-deterministic initialization creates branches in the execution
+tree during state space exploration.
+
+The $\rgse$ relation is a union over branching points on control flow
+to support the final proof of the existence of a
+bisimulation. Although it is apparent that there is non-determinism in
+initialization, it is not the initialization where control flow
+diverges in program execution. Rather, that occurs at branches and
+exceptions, and that is reflected in the composition of $\rgse$.
 
@@
 \input{lazy-fig}
-
-\input{lazy-eq}

### 2014-11-12 tex/intro.tex
fixed a sentence
still working on the intro

@@
 over-approximations to reason about heaps and may report false
-positives. Also, an update to the heap required a rewrite of the
-constraint system making it prohitive for use in the context of
-symbolic execution.
+positives. Also, update to heaps require a rewrite of the constraint
+system making it prohitive for use in the context of symbolic
+execution.
 
@@
 
-In this work, we present a novel heap initialization and analysis
-technique which takes inspiration from both GSE and existing heap
-summarization techniques. The intuition behind our analysis is to
-construct the heap lazily during symbolic execution but reduce the
-points of non-determinism in the symbolic execution tree by analyzing
-each control-flow path only once for any given set of isomorphic
-heaps. To represent the exact set of feasible concrete heap structures
-resulting from execution of the control-flow path, we use a heap
-summary.  Our analysis improves on existing GSE approaches by reducing
+In this work, we present a technique for heap summarization,
+initialization, and analysis in the context of symbolic execution. We
+represent the heap as a bipartiate graph of references and sets of
+constraints over locations. The use of a bipartiate graph affords two
+key advantages: (i) it allows for a non-recursive definition of
+objects, allowing us to handle aliasing and (ii) it does not require
+rewrite of the constraints during updates to the heap. We lazily
+initialize, summarize, and update the bipartiate graph during symbolic
+execution. Unlike GSE, however, we only partition the heaps at points
+of divergence in the control flow graph. These points of
+non-determinism at field accesses that lead to null-pointer exception
+and checking equality of references. The former represents a
+divergence due to exceptional control flow while the later due to
+program structure.
+
+%In this work, we present a novel heap initialization and analysis
+%technique which takes inspiration from both GSE and existing heap
+%summarization techniques. The intuition behind our analysis is to
+%construct the heap lazily during symbolic execution but reduce the
+%points of non-determinism in the symbolic execution tree by analyzing
+%each control-flow path only once for any given set of isomorphic
+%heaps. To represent the exact set of feasible concrete heap
+%structures resulting from execution of the control-flow path, we use
+%a heap summary.
+
+ Our analysis improves on existing GSE approaches by reducing
 the size of the symbolic execution state space explored, thereby

### 2014-11-12 tex/intro.tex
still working on the intro
intro moving along

@@
 objects, allowing us to handle aliasing and (ii) it does not require
-rewrite of the constraints during updates to the heap. We lazily
-initialize, summarize, and update the bipartiate graph during symbolic
-execution. Unlike GSE, however, we only partition the heaps at points
+rewrite of the constraints during updates to the heap nor does it
+introduce any auxillary variables in the constraints. During symbolic
+execution, we initialize, summarize, and update the bipartiate
+graph. Unlike GSE, however, the heaps are partitioned only at points
 of divergence in the control flow graph. These points of
-non-determinism at field accesses that lead to null-pointer exception
-and checking equality of references. The former represents a
+non-determinism are at field accesses that lead to null-pointer
+exceptions and at comparisons of references. The former represents a
 divergence due to exceptional control flow while the later due to

### 2014-11-12 tex/intro.tex
precision

@@
 of divergence in the control flow graph. These points of
-non-determinism are at field accesses that lead to null-pointer
-exceptions and at comparisons of references. The former represents a
-divergence due to exceptional control flow while the later due to
-program structure.
+non-determinism are at field accesses or writes that lead to
+null-pointer exceptions and at comparisons of references. The former
+represents a divergence due to exceptional control flow while the
+later due to program structure.
 
@@
 %a heap summary.
+
+The heap summary approach for symbolic execution is sound and complete
+with respect to anything you can prove using a GSE machine. We should
+the existence of a bi-simulation relation. In other words, any
+property that can be proved using GSE can also be proved using heap
+summaries, furthermore, any property proved by heap summaries can also
+be proved by GSE---given the same bounds on heap reference chains and
+loops.
+
+%preserves the heap
+%configurations and program behaviors
+
+%complete --> anything prove with GSE you can with heap sound -->
+%preserves the same behaviors in the GSE machine.
 

### 2014-11-12 tex/intro.tex
precision

@@
 The heap summary approach for symbolic execution is sound and complete
-with respect to anything you can prove using a GSE machine. We should
-the existence of a bi-simulation relation. In other words, any
-property that can be proved using GSE can also be proved using heap
-summaries, furthermore, any property proved by heap summaries can also
-be proved by GSE---given the same bounds on heap reference chains and
-loops.
+with respect to a GSE machine. We show the existence of a
+bi-simulation relation. In other words, any property that can be
+proved using GSE can also be proved using heap summaries, furthermore,
+any property proved by heap summaries can also be proved by
+GSE---given the same bounds on heap reference chains and loops.
 

### 2014-11-12 tex/heap.tex
updates to heap.tex

--- 2014-11-11 tex/heap.tex
@@
 \subsection{Heaps as Bipartite Graphs}
-An important aspect, and a novel contribution, of a symbolic heap is its
-representation as a labeled bipartite graph consisting of
-references, $\cfgnt{r}$, and constraint location pairs,
-$\lp\phi\ \cfgnt{l}\rp$. The heap structure itself captures that the actual
-location pointed to by a reference is conditional on aliasing
-relationships within the heap. In this way, the graph represents sets
-of heaps with the conditions under which those heaps exist.
+\sjp{General comment: we are missing motivation for why we discuss both
+the gse and the summary heap machines - perhaps this goes in the intro?
+And the fact that the GSE machine implements lazy versus lazier, etc. and
+why this decision}
+An important part and novel contribution of summary heaps for
+symbolic execution is the labeled bipartite graph representation
+of the heap which enables a summary heap to represent an equivalence class of
+concrete heaps--all of the concrete heaps that follow the same control
+flow to a given point of execution. The equivalence class splits depending 
+on control flow branches, partitioning the heaps depending on the 
+produced outcome. \sjp{Last sentence should be clarified.}
 
-The graph is expressed in in $\cfgnt{L}$, the location map, and
-$\cfgnt{R}$, the reference map. As done with the environment,
+The bipartite graph consists of 
+references, $\cfgnt{r}$, and constraint-location pairs,
+$\lp\phi\ \cfgnt{l}\rp$, capturing the fact that the
+actual location pointed to by a reference is conditional on
+aliasing relationships within the heap. In this way, the graph
+represents sets of heaps with the conditions under which those heaps
+exist. This representation separates the constraint
+problem from the morphology problem, i.e, separates the \sjp{??}
+from the shape of the heap, and also makes 
+it unnecessary to rewrite the
+path condition every time the heap is updated. Without these two
+features,
+%properties, 
+it would not be possible to lazily initialize heap
+locations along a program path.
+
+The graph is expressed in the location map, $\cfgnt{L}$, and
+the reference map, $\cfgnt{R}$. As done with the environment,
 $\cfgnt{L}$ and $\cfgnt{R}$ are treated as partial functions where
 $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the set of
-location-constraint pairs in the heap associated with the given
+constraint-location pairs in the heap associated with the given
 reference, and $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the
@@
 
-There are several properties of the heap that are invariant and
-important to the correctness.
+There are several properties of the summary heap 
+enforced by the rewrite rules that are invariant and
+important to the correctness proofs
+presented in \sjp{need sec ref}.
 \begin{compactitem}
@@
   the location map; it always points to the same set of constraint
-  location pairs.
+  location pairs. This property ensures that constraints never need to
+  be rewritten as the program evolves its state.
 \item \textbf{Reference partitions}: new references are drawn from
-  three distinct partitions $\mathrm{init}_r()$, $\mathrm{fresh}_r()$,
-  and $\mathrm{stack}_r()$. The references strictly increase in value
-  on each call, and modular arithmetic is used to determine the
-  partition to which a reference belongs.
-\item \textbf{Determinism}: a reference in  $(\cfgnt{L}\ \cfgnt{R})$ cannot point to two locations at the same time.
+  three distinct partitions (i) $\mathrm{init}_r()$ for initialization, (ii)
+  $\mathrm{fresh}_r()$ for the input heap, and (iii) $\mathrm{stack}_r()$
+  for references in the expressions and continuations. The references
+  strictly increase in value on each call, and modular arithmetic is
+  used to determine the partition to which a reference belongs. Reference
+  partitions are a critical piece to the existence proof of a
+  bisimulation that relates states with a concrete heap to states with
+  a summary heap (see \sjp{add secref}).
+\item \textbf{Determinism}: a reference in  $(\cfgnt{L}\ \cfgnt{R})$ cannot point to two  locations at the same time \sjp{multiple locations simultaneously?}.
 \[
@@
 \]
-$\cfgnt{L}^\leftarrow$ is the pre-image of the location map.
-\item \textbf{Type consistent}: every location associated to a reference has the same type.
+$\cfgnt{L}^\leftarrow$ is the pre-image of the location map. \sjp{need more of a description here}
+\item \textbf{Type consistency}: all locations associated with a reference have the same type.
 \[
@@
 \]
-\item \textbf{Null and Uninitialized}: The location $\cfgnt{l}_\mathit{null}$ is a special location in the
-heap to represent null. It has a companion reference
-$\cfgnt{r}_\mathit{null}$. The initial heap for the machine is defined
-such that $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
-\{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$
+\item \textbf{Null and Uninitialized}: every summary heap contains 
+a special location for null ($\cfgnt{l}_\mathit{null}$), and a special
+location for uninitialized
+  ($\cfgnt{l}_\mathit{un}$), with corresponding references
+  $\cfgnt{r}_\mathit{null}$ and
+  $\cfgnt{r}_\mathit{un}$, respectively. $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
+  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
+  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
+  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$.
 \end{compactitem}
 
-DEFINE $\rsym$ and $\rgse$.
+\subsection{State Transition Relation}
+
+The initial state of a Javalite program is constructed from its
+surface syntax on the $\cfgnt{P}$ production:
+$\lp\mu\ \lp\cfgnt{C}\ \cfgnt{m}\rp\rp$. Assuming that
+$\lp\cfgnt{L}\ \cfgnt{R}\rp$ is an empty heap with no references
+or locations and $\eta$ is an empty environment with no
+variables, the initial state is
+$$
+\begin{array}{l}
+\lp\mu 
+\ \cfgnt{L}[\cfgnt{r}_\mathit{null} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{null})\}\rp] 
+           [\cfgnt{r}_\mathit{un} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{un}\rp\}] \\
+\ \cfgnt{R}
+\ \cfgt{true}\ \eta\  \lp\lp\cfgt{new}\ \cfgnt{C}\rp\ \cfgt{@}\ \cfgnt{m}\ \cfgt{true}\rp\rp\ \cfgt{end}\rp
+\end{array}
+$$
+The first expression in the initial state is a call to a constructor
+to create an instance of the class $\cfgnt{C}$. \sjp{I was under the
+impression that Javalite does not have constructors -- that
+It only initializes the new object's locations on the heap with their default
+values.} Once an instance of
+$\cfgnt{C}$ exists, the method $\cfgnt{m}$ of the class is
+invoked.
+
+In general, the semantics of Javalite are expressed as
+rewrites on strings using pattern matching. Consider the rewrite rule
+for the beginning of a  field access instruction \sjp{in the Javalite
+machine?}:
+$$
+\mprset{flushleft}
+	\inferrule[Field Access(eval)]{}{
+      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgnt{e}\ \cfgt{\$}\ \cfgnt{f}\rp \ \cfgnt{k}\rp  \rcom 
+      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp 
+	}
+$$
+If the string representing the current state matches the left side, then it
+creates the new string on the right. In this example, the new string
+on the right is now evaluating the expression $\cfgnt{e}$ in the field
+access, and it includes the continuation indicating that it still
+needs to complete the actual field access once the expression is
+evaluated.
+
+Other more complex rules such as the one to create a new instance of a
+class define constraints on the rewrites and more complex
+transformations on the heap.
+$$
+\mprset{flushleft}
+	\inferrule[New]{
+      \cfgnt{r} = \mathrm{stack}_r\lp \rp\\
+      l = \mathrm{fresh}_l\lp \cfgnt{C}\rp\\\\
+      \cfgnt{R}^\prime = \cfgnt{R}[\forall \cfgnt{f} \in \mathit{fields}\lp \mathrm{C}\rp \ \lp \lp l\ \cfgnt{f}\rp  \mapsto \cfgnt{r}_\mathit{null} \rp ] \\\\
+      \cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}]
+    }{
+      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgt{new}\ \cfgnt{C}\rp \ \cfgnt{k}\rp  \rcom
+      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi\ \eta\ \cfgnt{r}\ \cfgnt{k}\rp 
+	}
+$$
+In this rule, when the string matches the new-expression, it is rewritten to use
+a new heap location where all of the fields for the new object point to
+$\cfgnt{r}_\mathit{null}$
+and the location map points a new stack reference to that new object.
+
+In the remainder of the paper, we refer to the the generalized
+symbolic execution with lazy initialization machine by the relation
+$\rgse$ or $p \rgse p^\prime$, and to the new summary heap 
+machine by $\rsym$ or $q \rsym q^\prime$.
+Due to space restrictions, the full operational semantics for generalized 
+symbolic execution with
+lazy initialization for Javalite are presented in the supplemental
+document. We also  present the portion of the Javalite 
+rewrite rules which are common to both machines in 
+the supplementary document. In the next section, we present
+the rewrite rules specific to the new summary heap algorithm for symbolic
+execution.

### 2014-11-12 tex/intro.tex

@@
 The heap summary approach for symbolic execution is sound and complete
-with respect to a GSE machine. We show the existence of a
-bi-simulation relation. In other words, any property that can be
-proved using GSE can also be proved using heap summaries, furthermore,
-any property proved by heap summaries can also be proved by
-GSE---given the same bounds on heap reference chains and loops.
+with respect to properties that are provable using GSE. This is
+accomplished by showing the existence of a bisimulation relation. In
+other words, any property that can be proved using GSE can also be
+proved using heap summaries, furthermore, any property proved by heap
+summaries can also be proved by GSE---given the same bounds on heap
+reference chains and loops.
+
+In a preliminary evaluation comparing the efficiacy of the heap
+summary technique with respect to the other GSE approaches, we observe
+a two-order of magnitude reduction in the total time taken to explore
+the same state space. We implement the heap summary approach as an
+extension to the Symbolic PathFinder symbolic execution engine and
+analyze three Java data structure artifacts. For these examples, we
+show that where other GSE approaches are unable to complete
+exploration within the provided time bound, the summary heap finishes
+exploration in a few seconds.
+
+%shows that it can improve the scalability of symbolic execution of
+%heap manipulating programs X fold over GSE-based analyses while
+%maintaining precision and efficiency.
 
@@
 
- Our analysis improves on existing GSE approaches by reducing
-the size of the symbolic execution state space explored, thereby
-improving scalability of symboic execution for heap manipulating
-software. It improves on existing heap summarization techniques by
-enabling analysis of arbitrary recursive data structures (no initial
-heap configuration is required) while avoiding the imprecision
-introduced by these techniques.
+%Our analysis improves on existing GSE approaches by reducing
+%the size of the symbolic execution state space explored, thereby
+%improving scalability of symboic execution for heap manipulating
+%software. It improves on existing heap summarization techniques by
+%enabling analysis of arbitrary recursive data structures (no initial
+%heap configuration is required) while avoiding the imprecision
+%introduced by these techniques.
 
-\nsr{a paragraph that provides a breif summary
-  of the results.. would be nice if we have numbers for lazier and
-  lazier Sharp as well.}
-  A preliminary evaluation of our technique
-shows that it can improve the scalability of symbolic execution
-of heap manipulating programs X fold over GSE-based analyses
-while maintaining precision and efficiency.
+%\nsr{a paragraph that provides a breif summary of the results.. would
+%  be nice if we have numbers for lazier and lazier Sharp as well.}
 
-This paper makes the following contributions:
-\begin{itemize}
-\item{We present a novel inter-procedural analysis technique for 
-symbolic execution of heap manipulating software which constructs 
-a precise heap summary.}
-\item{We use the JavaLite language~\cite{saints-MS} to formalize 
-the algorithm for constructing and manipulating the heap summary
-on-the-fly during symbolic execution.}
-\item{We implement our approach in the Symbolic PathFinder tool and
-empirically demonstrate that our technique improves
-the scalability of symbolic execution of heap maninpulating software
-over GSE, while maintaining efficiency and precision.}
-\item{We prove that at any given point during symbolic execution, the symbolic 
-heap represents the exact set of feasible concrete heap structures 
-for the program under analysis.}
- \end{itemize}
+\noindent{This paper makes the following contributions:}
+
+\begin{description}
+
+\item\textbf{-} Define a heap encoding as a bipartiate graph of
+  references and sets of constraints over locations.
+
+% to handle alias and efficient updates of constraints.
+
+\item\textbf{-} Present an algorithm to initialize, summarize, and
+  update the bipartiate graphs during symbolic execution.
+
+\item\textbf{-} Show the existence of a bisimulation relation prove
+  that the heap summary approach is sound and complete with respect to
+  properties provable by GSE.
+
+\item\textbf{-} Demonstrate the scability of the heap summary approach
+  compared to GSE approaches.
+
+\end{description}
+
+\noindent{In this paper, we present a brief over of the a Java-like
+  language and the encoding of heaps as a bipartiate graph. We use the
+  Java-like language to define the formal semantics of the heap
+  summary machine and then prove the existence of a bisumulation
+  relation. Finally we present an evaluation of the heap summary
+  approach. }
+
+%\item{We present a novel inter-procedural analysis technique for 
+%symbolic execution of heap manipulating software which constructs 
+%a precise heap summary.}
+%\item{We use the JavaLite language~\cite{saints-MS} to formalize 
+%the algorithm for constructing and manipulating the heap summary
+%on-the-fly during symbolic execution.}
+%\item{We implement our approach in the Symbolic PathFinder tool and
+%empirically demonstrate that our technique improves
+%the scalability of symbolic execution of heap maninpulating software
+%over GSE, while maintaining efficiency and precision.}
+%\item{We prove that at any given point during symbolic execution, the symbolic 
+%heap represents the exact set of feasible concrete heap structures 
+%for the program under analysis.}
+% \end{description}
 
@@
 %  the heap such as the determinism and immutability}
-\nsr{Is any part of the formalism borrowed
-from the dilligs? Which part are unique?}  \nsr{end on a couple
-sentences about the various rules that will be talked about in the
-paper}
 
-\nsr{The reader should be convinced about our expressiveness
-  claim here}
+%\nsr{Is any part of the formalism borrowed
+%from the dilligs? Which part are unique?}  \nsr{end on a couple
+%sentences about the various rules that will be talked about in the
+%paper}
 
-\nsr{a paragraph that provides intution on how we are a bisumulation
-  with the GSE..reader should be convinced about the precision claim}
+%\nsr{The reader should be convinced about our expressiveness
+%  claim here}
+
+%\nsr{a paragraph that provides intution on how we are a bisumulation
+%  with the GSE..reader should be convinced about the precision claim}
 

### 2014-11-12 tex/intro.tex
finished the intro

@@
 
-\item\textbf{-} Show the existence of a bisimulation relation prove
+\item\textbf{-} Show the existence of a bisimulation relation to prove
   that the heap summary approach is sound and complete with respect to
@@
 
-\noindent{In this paper, we present a brief over of the a Java-like
+\noindent{In this paper, we present a brief overview of a Java-like
   language and the encoding of heaps as a bipartiate graph. We use the

### 2014-11-12 tex/precise.tex
updates to sec 3.1

@@
-\section{Generating Symbolic Heap Summaries}
+\section{Generating Summary Heaps}
 \label{sec:precise}
 
-In this section we present the rules for the $\rsym$ relation. The are
-three sets of rewrite rules: the initialization of symbolic
-references, the field access and write rules, and finally checking the
-equality and inequality of references. Here we describe each of the
-rules. They consist the core of the symbolic heap summary approach.
+In this section we present the rewrite rules for the $\rsym$ relation. 
+There are three sets of rewrite rules specific to the summary
+heap algorithm: (i) rules to initialize symbolic
+references, (ii) field access and write rules, and (iii) rules
+to check equality and inequality of references. These rules
+form the core of the summary heap algorithm.
 
@@
 
-In this section we present the rewrite rules for the initialization of
-references in the $\rsym$ relation for a symbolic heap summary. The
-initialization rules are defined on the bi-partite graph consisting of
-references and locations. In the $\rgse$ relation during
-initialization of a symbolic references, it is non-deterministically
-assigned to null, new instance of the object, and alias any previously
-initialized symbolic reference. In contrast, the heap summarization
-approach creates a single branch that contains the summarization for
-all the initialization in a single bi-partitate graph.
+During initialization of symbolic references in the $\rgse$ relation,
+non-determinitic choices are introduced into the search to
+account for initiaization of the reference to $\mathit{null}$, a new instance of the 
+object, and to any type compatible object previously
+initialized. In contrast, initialization rules for the $\rsym$ relation are 
+defined on the bipartite graph consisting of references and locations,
+and create a single branch containing a summarization of
+all the initializations in a single graph.
 
@@
 
-The initialization rules are invoked when an uninitialized field in a
+The initialization rules are invoked whenever an uninitialized field in a
 symbolic reference is accessed. The function $\mathbb{UN}(\cfgnt{L},
 \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) = \{\cfgnt{l}\ ...\}$ returns
-constraint-location pairs in which the field $\cfgnt{f}$ is
+constraint-location pairs in which field $\cfgnt{f}$ is
 uninitialized:
@@
 where $\mathbb{S}(\phi)$ returns true if $\phi$ is
-satisfiable. Intutively, for the reference, $\cfgnt{r}$, it constructs
-the set, $\theta$, that contains all contraint-location pairs that
-point to the field $\cfgnt{f}$ and $\cfgnt{f}$ points to
+satisfiable. Intutively, for reference $\cfgnt{r}$, this function constructs
+the set, $\theta$ containing all contraint-location pairs that
+point to field $\cfgnt{f}$ and $\cfgnt{f}$ points to
 $\cfgnt{l}_\mathit{un}$.
@@
 
-The rewrite rule to initialize a heap in the symbolic summarization
-technique is shown in~\figref{fig:symInit}. Given the unitialized set
+The rewrite rule to initialize a heap in the summary heap algorithm
+is shown in~\figref{fig:symInit}. Given the unitialized set
 $\mathbb{UN}$ for field $f$, the $\mathit{min}_l$ function returns
 $(\phi_x\ \cfgnt{l}_x)$ based on a lexical ordering of uninitialized locations
-in $\Lambda$. The init$_r$ method returns a new input reference $\cfgnt{r}_f$
+in $\Lambda$. The init$_r$ method returns a new input reference $\cfgnt{r}_f$,
 while the fresh$_f$ returns a new location of type $C$. The set $\rho$
-contains the set of reference location pairs, $(\cfgnt{r}_a\ \cfgnt{l}_a)$, that the
-field being initialized may alias. The pair $(\cfgnt{r}_a\ \cfgnt{l}_a)$ is contained
+contains the set of reference-location pairs, $(\cfgnt{r}_a\ \cfgnt{l}_a)$, the
+field being initialized may alias. A pair $(\cfgnt{r}_a\ \cfgnt{l}_a)$ is contained
 in the set $ \rho $ if the following conditions hold: (i) $\cfgnt{r}_a$ is
 part of the input references initialized in the summary heap, (ii)
-$\cfgnt{r}_a$ is in the pre-image of $\cfgnt{l}_a$, (iii) and the type of $\cfgnt{l}_a$ is the
-same as the type of the field being initialized.
+$\cfgnt{r}_a$ is in the pre-image of $\cfgnt{l}_a$, and (iii) the type 
+of $\cfgnt{l}_a$ is the same as the type of the field being initialized.
 
-There are three constraint-location pair sets that correspond to
+There are three constraint-location pair sets that correspond to the
 non-deterministic choices in GSE: (a) $\theta_\mathit{null}$ contains
 a constraint $\cfgnt{r}_f = \cfgnt{r}_\mathit{null}$ paired with the location
-$\cfgnt{l}_\mathit{null}$, (b) $\theta_\mathit{new}$ creates a pair with the
-constraint $\cfgnt{r}_f$ is not null and it does not alias any reference in
-set $\rho$ under and a newly created location $\cfgnt{l}_f$, (c) and
+$\cfgnt{l}_\mathit{null}$, (b) \sjp{something is not right in this choice}
+$\theta_\mathit{new}$ creates a pair with a
+constraint representing the fact that $\cfgnt{r}_f$ is not null and it does 
+not alias any reference in set $\rho$ under and a newly created location 
+$\cfgnt{l}_f$, and (c) 
 $\theta_\mathit{alias}$ where for each element in the set $(\cfgnt{r}_a\ \cfgnt{l}_a)
-\in \rho$ it creates a constraints that $\cfgnt{r}_f$ is not null, points to
+\in \rho$ it creates a constraint stating that $\cfgnt{r}_f$ is not null, points to
 $\cfgnt{r}_a$, and does not point to any reference contained in $(\cfgnt{r}_a^\prime\ 
 \cfgnt{l}_a^\prime) \in \rho$ such that $\cfgnt{r}_a < \cfgnt{r}_a^\prime$ based on a lexical
-ordering of initialized references. Additionally
+ordering of initialized references. Additionally,
 $\theta_\mathit{orig}$ allows for the possibility that the field
-continues to remain uninitialized since the heap is symbolic. We refer
-to this initialization in the summary machine as conditional
-initialization. Finally, the fields of the reference $\cfgnt{r}_f$ are marked
-as uninitialized. In the post condition of the rule the reference
+continues to remain uninitialized since the heap is symbolic.
+\sjp{The last statement seems to jump out since we have not been
+talking about the heap being symbolic (have we?)} We refer
+to initialization in the summary machine as conditional
+initialization \sjp{Not sure why we say this - what does it mean
+to the reader?}. Finally, the fields of the reference $\cfgnt{r}_f$ are marked
+as uninitialized. In the post condition of the rule, the reference
 $\cfgnt{r}_f$ points to $\theta$ which contains the union of all the
@@
 $\cfgnt{l}_0$. Note that when no constraint is specified in the graphs, then
-there is a implicit $\mathit{true}$ constraint, for example, $\cfgnt{r}_0^s$
+there is an implicit $\mathit{true}$ constraint, for example, $\cfgnt{r}_0^s$
 points to $\cfgnt{l}_0$ on the constraint $\mathit{true}$. The fields $x$ and
@@
 
-The graph in~\figref{fig:initHeap}(b) represents the symbolic heap
-summary after the initialization of the $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ field while
+The graph in~\figref{fig:initHeap}(b) represents the summary heap
+after the initialization of the $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ field while
 the graph in~\figref{fig:initHeap}(c) represents the symbolic heap
@@
 
-Following the initialization to the $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$, when we
-initialize $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ the resulting summary heap is shown
+Following initialization to $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$, when
+$\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ is initialized, the resulting summary heap is shown
 in~\figref{fig:initHeap}(c). The set $\rho$ shown

### 2014-11-12 tex/evaluation.tex
Updated results table.
Updated results table with state counts.

@@
-\begin{table} [h]
+\begin{figure*}[t]
+%\begin{table} [t]
   \centering
-  \begin{tabular}{| c | c | r | r | r | r | }
+  \begin{tabular}{| c | c | r | r | r | r | r | r | r | r | r |}
   \hline
    \multirow{2}{*}{Method }&\multirow{2}{*}{ $k$ }
-   &\multicolumn{2}{|c|}{Time} &\multicolumn{2}{|c|}{ Paths }\\
-								&	&\gsetxt{}	&SH	&\gsetxt{} & SH\\
+   &\multicolumn{3}{|c|}{Time} &\multicolumn{3}{|c|}{States} &\multicolumn{3}{|c|}{ Paths }\\
+								&	&\gsetxt{} & LS		&SH		&\gsetxt{}	& LS & SH&\gsetxt{}	& LS & SH\\
    \hline
-    \multirow{3}{*}{LinkedList }&3	& 0.91 & 0.69  &1656 & 25		 \\
-   		 				& 4	& 2.92 & 0.91	&17485  & 39 \\
-   						& 5	& 20.8 & 1.59 &232743 & 56\\
-						& 6	& 283 & 2.36		&3731094 & 76\\
+    \multirow{3}{*}{LinkedList }			&3	& 0.91	& 1.21	& 0.69	& 2465	& 2844	& 99		&1656	& 1269	& 25\\
+   		 						& 4	& 2.92	& 3.35	& 0.91	& 25774	& 29977	& 155	&17485	& 13550	& 39\\
+   								& 5	& 20.78	& 19.47	& 1.59	& 341164	& 400296	& 223	&232743	& 181849	& 56\\
+								& 6	& 280.56	& 299.19	& 2.36	&5447980	&6437201	& 303	&3731094	&2933027	& 76\\
     \hline
-    \multirow{3}{*}{BinarySearchTree } & 1	&0.26	& 0.36 & 6	 & 6\\
-   		 				& 2	& 0.83 & 0.93	& 143 & 33\\
-   						& 3	& 20.6 & 4.03 & 515 & 328\\
+    \multirow{3}{*}{BinarySearchTree }	& 1	& 0.26	& 0.28	& 0.36	& 19		& 23		& 29		& 6		& 6		& 6\\
+   		 						& 2	& 0.83	& 1.28	& 0.93	& 143	& 143	& 145	& 43		& 42		& 33\\
+   								& 3	& 20.63	& 25.55	& 4.03	& 1953	& 1703	& 1485	& 515	& 515	& 328\\
     \hline
-      \multirow{3}{*}{TreeMap}&1	 & 0.47 & 0.77 &11 & 11 \\
-   		 				&2	& 8.99 & 4.72	& 127 & 73 \\
-   						& 3	& - & 146	& - & 887 \\
+      \multirow{3}{*}{TreeMap}			& 1	& 0.47	& 0.52	& 0.77	& 65		& 70		& 215	& 11		& 11		& 11\\
+   		 						& 2	& 8.99	& 9.73	& 4.72	& 1009	& 942	& 3219	& 127	& 122	& 73\\
+   								& 3	& -		& -		& 145.56	& -		& -		& 78695	& -		& -		& 887\\
 
@@
   \label{tab:results}
-\end{table}
+%\end{table}
+\end{figure*}
 
@@
 
-As expected, the repeated use of lazy initialization throughout the program causes an exponential increase in the number of paths explored by \gsetxt{}.
+The results ofAs expected, the repeated use of lazy initialization throughout the program causes an exponential increase in the number of paths explored by \gsetxt{}.
 By combining many of the \gsetxt{} paths, \symtxt{} avoids the exponential path explosion, demonstrating dramatically reduced, though still exponential, execution time growth.

### 2014-11-12 tex/bisimulation.tex
Moved a definition.
Addressed contributions and concerns in heap.tex

@@
-\section{Bisimularity Relation}
+\section{Bisimilarity Relation}
+\label{sec:bisim}
 Let $p \rgse p^\prime$ be the binary relation over the universe of states, $S$,
@@
 
-DEFINE $S$ and $S_{FA}$ and unify on the shorthand as $S_A$. 
+The state $S$ is the universe of well-formed states, and the
+set $S_A \subseteq S$ is the set of states at a field access continuation.
 \begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
@@
 soundness are readily established by \thref{th:bisim} and inducting
-over $n$. The state $S$ is the universe of well-formed states, and the
-set $S_A \subseteq S$ is the set of states at a field access continuation.
+over $n$.
 

### 2014-11-12 tex/heap.tex
Addressed contributions and concerns in heap.tex

@@
-\subsection{Heaps as Bipartite Graphs}
-\sjp{General comment: we are missing motivation for why we discuss both
-the gse and the summary heap machines - perhaps this goes in the intro?
-And the fact that the GSE machine implements lazy versus lazier, etc. and
-why this decision}
-An important part and novel contribution of summary heaps for
-symbolic execution is the labeled bipartite graph representation
-of the heap which enables a summary heap to represent an equivalence class of
-concrete heaps--all of the concrete heaps that follow the same control
-flow to a given point of execution. The equivalence class splits depending 
-on control flow branches, partitioning the heaps depending on the 
-produced outcome. \sjp{Last sentence should be clarified.}
+\subsection{Summary Heaps as Bipartite Graphs}
+An important part and novel contribution of summary heaps for symbolic
+execution is the labeled bipartite graph representation of the heap
+which enables a summary heap to group heaps together that follow the
+same control flow to a given point of execution. The group of heaps
+split depending on control flow branches: heaps in the original group
+that follow a true outcome form a new group while heaps from that same
+original group that follow a false outcome form a different
+group. State explosion in symbolic execution is thus mitigated by
+storing a group of heaps in the state and only branching when that
+group splits.
 
-The bipartite graph consists of 
-references, $\cfgnt{r}$, and constraint-location pairs,
-$\lp\phi\ \cfgnt{l}\rp$, capturing the fact that the
-actual location pointed to by a reference is conditional on
-aliasing relationships within the heap. In this way, the graph
-represents sets of heaps with the conditions under which those heaps
-exist. This representation separates the constraint
-problem from the morphology problem, i.e, separates the \sjp{??}
-from the shape of the heap, and also makes 
-it unnecessary to rewrite the
-path condition every time the heap is updated. Without these two
-features,
-%properties, 
-it would not be possible to lazily initialize heap
-locations along a program path.
-
-The graph is expressed in the location map, $\cfgnt{L}$, and
-the reference map, $\cfgnt{R}$. As done with the environment,
-$\cfgnt{L}$ and $\cfgnt{R}$ are treated as partial functions where
-$\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the set of
-constraint-location pairs in the heap associated with the given
-reference, and $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the
-reference associated with the given location-field pair in the
-heap. Predicate calculus is used to describe the more complex updates
-to the heap in the semantics.
+The bipartite graph itself consists of references, $\cfgnt{r}$, and
+constraint-location pairs, $\lp\phi\ \cfgnt{l}\rp$. The graph is
+expressed in the location map, $\cfgnt{L}$, and the reference map,
+$\cfgnt{R}$. As done with the environment, $\cfgnt{L}$ and $\cfgnt{R}$
+are treated as partial functions where $\cfgnt{L}(r) =
+\{(\phi\ \cfgnt{l})\ ...\}$ is the set of constraint-location pairs in
+the heap associated with the given reference, and
+$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the reference
+associated with the given location-field pair in the heap. Predicate
+calculus is used to describe the more complex updates to the heap in
+the semantics.
 
@@
 important to the correctness proofs
-presented in \sjp{need sec ref}.
+presented in \secref{sec:bisim}.
+
+\textbf{Reference partitions}: new references are drawn from
+  three distinct partitions (i) $\mathrm{init}_\cfgnt{r}()$ for references for the \emph{input heap}, (ii) $\mathrm{fresh}_\cfgnt{r}()$ for references for \emph{auxiliary literals}, and
+  (iii) $\mathrm{stack}_\cfgnt{r}()$ for references for the \emph{stack literals} in the expressions and
+  continuations. The references strictly increase in value on each
+  call, and modular arithmetic is used to determine the partition to
+  which a reference belongs. Reference partitions are a critical piece
+  to the existence proof of a bisimulation between the summary heap
+  algorithm and generalized symbolic execution (see \secref{sec:bisim}).
 \begin{compactitem}
-\item \textbf{Immutable references}: a reference does not change in
-  the location map; it always points to the same set of constraint
-  location pairs. This property ensures that constraints never need to
-  be rewritten as the program evolves its state.
-\item \textbf{Reference partitions}: new references are drawn from
-  three distinct partitions (i) $\mathrm{init}_r()$ for initialization, (ii)
-  $\mathrm{fresh}_r()$ for the input heap, and (iii) $\mathrm{stack}_r()$
-  for references in the expressions and continuations. The references
-  strictly increase in value on each call, and modular arithmetic is
-  used to determine the partition to which a reference belongs. Reference
-  partitions are a critical piece to the existence proof of a
-  bisimulation that relates states with a concrete heap to states with
-  a summary heap (see \sjp{add secref}).
-\item \textbf{Determinism}: a reference in  $(\cfgnt{L}\ \cfgnt{R})$ cannot point to two  locations at the same time \sjp{multiple locations simultaneously?}.
+\item \textbf{Input heap}: these references have two
+  interpretations: one as a literal and another as a variable. First,
+  an input heap reference is a literal, and that literal is a node in
+  the summary heap. Second, an input heap reference is a variable, and
+  that variable is a term in any number of constraints that label
+  edges in the summary heap. Only input heap references and the
+  special reference $\cfgnt{r}_\mathit{null}$ appear in constraints
+\item \textbf{Auxiliary literals}: these references are only used to define additional structure in
+  the bipartite graph and are not part of any constraint and do not appear
+  in any environment, expression, or continuation.
+\item \textbf{Stack references}: these references are also used to define additional structure in the bipartite graph but may also appear in the environment, expression, or continuation.
+These are not part of any constraint.
+\end{compactitem}
+
+\textbf{Immutable references}: a reference does not change in the
+location map. It always points to the same set of constraint location
+pairs. This property ensures that constraints never need to be
+rewritten as the program evolves its state.
+
+\textbf{Determinism}: a reference in  $(\cfgnt{L}\ \cfgnt{R})$ cannot point multiple locations simultaneously.
 \[
@@
 \]
-$\cfgnt{L}^\leftarrow$ is the pre-image of the location map. \sjp{need more of a description here}
-\item \textbf{Type consistency}: all locations associated with a reference have the same type.
+$\cfgnt{L}^\leftarrow$ is the pre-image of the location
+map. Informally, any two constraint location pairs connected to a
+common reference form a contradiction: only one can be true in any
+satisfying assignment. The property means that a satisfying assignment
+resolving aliasing relationships results in a deterministic heap: a
+field access returns a single location.
+
+\noindent\textbf{Type consistency}: all locations associated with a reference have the same type.
 \[
@@
 \]
-\item \textbf{Null and Uninitialized}: every summary heap contains 
+
+\textbf{Null and Uninitialized}: every summary heap contains 
 a special location for null ($\cfgnt{l}_\mathit{null}$), and a special
@@
   $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
-  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$.
+  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. These special references can be used in constraints.
+
+The reference partitions merit further discussion as they are a
+central contribution of this work. The heap summary algorithm creates
+many references that are auxiliary literals or stack literals to
+define the structure of the bipartite graph.  It reserves input heap
+reference for constraints expressing potential aliasing. A solver
+reasons over the aliasing relationships, and a satisfying assignment
+uniquely identifies active edges in the graph. Those active edges
+describe a concrete heap and its shape.
+
+For example, if the solver assigns input heap variables $\cfgnt{r}$ and $\cfgnt{r}^\prime$
+such that $\cfgnt{r} = \cfgnt{r}^\prime$ is true, then there exists
+some location $\cfgnt{l}$ and constraints $\phi$ and $\phi^\prime$ such
+that
+\begin{compactitem}
+\item $\lp\phi\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r})$; and
+\item $\lp\phi^\prime\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r}^\prime)$; and
+\item $\phi$ and $\phi^\prime$ are true under aliasing assignments from the solver.
 \end{compactitem}
+In this way, the graph groups heaps with the conditions under which
+those heaps exist. This representation, by virtue of the reference
+partitions, separates the constraint problem from the morphology
+problem: it is possible to update the heap without having to rewrite
+constraints. Without this separation, it would not be possible to
+lazily initialize heap locations along a program path.
 
@@
 $$
-The first expression in the initial state is a call to a constructor
-to create an instance of the class $\cfgnt{C}$. \sjp{I was under the
-impression that Javalite does not have constructors -- that
-It only initializes the new object's locations on the heap with their default
-values.} Once an instance of
-$\cfgnt{C}$ exists, the method $\cfgnt{m}$ of the class is
-invoked.
+The first expression in the initial state is to construct a new object
+in the summary heap of type $\cfgnt{C}$. Note that the resulting object is not referenced
+by the input heap since it comes from the new-expression.  Once an
+instance of $\cfgnt{C}$ exists in the summary heap, the method
+$\cfgnt{m}$ of the class is invoked.
 
@@
 rewrites on strings using pattern matching. Consider the rewrite rule
-for the beginning of a  field access instruction \sjp{in the Javalite
-machine?}:
+for the beginning of a field access instruction in the Javalite
+machine:
 $$
@@
 
-In the remainder of the paper, we refer to the the generalized
-symbolic execution with lazy initialization machine by the relation
-$\rgse$ or $p \rgse p^\prime$, and to the new summary heap 
-machine by $\rsym$ or $q \rsym q^\prime$.
-Due to space restrictions, the full operational semantics for generalized 
-symbolic execution with
-lazy initialization for Javalite are presented in the supplemental
-document. We also  present the portion of the Javalite 
-rewrite rules which are common to both machines in 
-the supplementary document. In the next section, we present
-the rewrite rules specific to the new summary heap algorithm for symbolic
-execution.
+To show the heap summary algorithm is sound and complete with respect
+to properties proved by generalized symbolic execution, we refer to
+the generalized symbolic execution with lazy initialization machine by
+the relation $\rgse$ or $p \rgse p^\prime$, and to the new summary
+heap algorithm machine by $\rsym$ or $q \rsym q^\prime$. Both machines
+use the summary heap structure, and for simplicity,
+both use lazy initialization as opposed to lazier or lazier\#.
+
+Due to space restrictions, the full operational semantics for
+generalized symbolic execution with lazy initialization for Javalite
+are presented in the supplemental document. We also present the
+portion of the Javalite rewrite rules which are common to both
+machines in the supplementary document. In the next section, we
+present the rewrite rules specific to the new summary heap algorithm
+for symbolic execution.

### 2014-11-12 tex/javalite.tex
Addressed contributions and concerns in heap.tex

@@
-\section{Background}
-\subsection{Javalite}
-We present our summary heap algorithm using Javalite, an
+\section{Summary Heap Framework}
+\subsection{Syntax}
+The summary heap algorithm is presented using Javalite, an
 executable formalization of a Java-like language~\cite{saints-MS}. Javalite retains 
-the essence of Java and other object-oriented languages with formalizations 
+the essence of Java and other object-oriented languages but with formalizations 
 in both PLT Redex and Coq so that the outcome of any program has a precise
@@
 Javalite is a syntactic machine defined as rewrites on a string.  The
-semantics are small-step using the CEKS model with a (C)ontrol string
+semantics are small-step using the CESK architecture with a (C)ontrol string
 representing the expression being evaluated, an (E)nvironment for
@@
 where execution starts. The only primitive type in Javalite is
-Boolean. Classes have fields non-primitive, $([\cfgnt{C}\ \cfgnt{f}]\ ...)$, and
+Boolean. Classes have non-primitive fields , $([\cfgnt{C}\ \cfgnt{f}]\ ...)$, and
 methods, $(\cfgnt{M}\ ...)$.\footnote{Summary heaps are able to support non-primitive fields (see \secref{sec:eval}).
 They are omitted to focus and simplify the presentation.} Methods are limited to a single
-parameter in our Javalite machine. Expressions, $\cfgnt{e}$, are 
-equivalent to a CEKS machine's control string, 
-%somewhat typical
-where $\cfgt{:=}$ indicates assignment, $\cfgt{=}$ indicates comparison,
-and $\cfgt{\$}$ represents the dot-operator for field access. The dot-operator
-for method invocation is represented by $\cfgt{@}$. There is no explicit return
+parameter in our Javalite machine. Expressions, $\cfgnt{e}$,  
+include statements, and they
+ use '$\cfgt{:=}$' to indicate assignment and '$\cfgt{=}$' to indicate comparison.
+The dot-operator for field access is replaced by '$\cfgt{\$}$', and the dot-operator
+for method invocation is replaced by '$\cfgt{@}$' since '.' is reserved in PLT Redex. There is no explicit return
 statement in Javalite; rather, the value of the last expression is
 used as the return value. A variable is always indicated by \cfgnt{x}
-and a value by \cfgnt{v}. A value can be a reference in the heap,
-$\cfgnt{r}$, or any of the special values shown in~\figref{fig:surface-syntax}. 
+and a value by \cfgnt{v}. A value can be a reference in the heap, $\cfgnt{r}$, or any of the special values shown in~\figref{fig:surface-syntax}. 
 We assume that only
@@
 The state of the Javalite machine (\figref{fig:machine-syntax}),
-$\cfgnt{s}$, includes the program registry, $\mu$\footnote{The registry $\mu$
-  is implied in the rewrite rules and not included in the state tuples.},
-  and a pair of functions defining the heap
-$\lp\cfgnt{L}\ \cfgnt{R}\rp$, which is the store. The state also
-includes a constraint,
+$\cfgnt{s}$, includes the program registry, $\mu$, a pair of functions defining the heap
+$\lp\cfgnt{L}\ \cfgnt{R}\rp$, a constraint,
 $\phi$, defined over references in the heap, the environment, $\eta$,
-for local variables, and the continuation $\cfgnt{k}$. The more
-complex structures, such as the environment, are defined as lists which
+for local variables, and the continuation $\cfgnt{k}$.\footnote{The registry $\mu$ never changes so it is omitted from the state tuple in the rest of the presentation for compactness.}  The more
+complex structures, such as the environment and heap, are defined as lists that
 start with empty, \cfgnt{mt}. The rewrite rules that define the
 semantics treat these lists as partial functions. As such,
-$\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference $\cfgnt{r}$ mapped to the variable
+$\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference $\cfgnt{r}$ associated with variable
 $\cfgnt{x}$. The notation $\eta^\prime = \eta[\cfgnt{x} \mapsto

### 2014-11-12 tex/heap.tex
Minor word changes

@@
 \textbf{Determinism}: a reference in  $(\cfgnt{L}\ \cfgnt{R})$ cannot point multiple locations simultaneously.
-\[
+$$
 \begin{array}{l}
@@
 \end{array}
-\]
+$$
 $\cfgnt{L}^\leftarrow$ is the pre-image of the location
@@
 
-\noindent\textbf{Type consistency}: all locations associated with a reference have the same type.
+\textbf{Type consistency}: all locations associated with a reference have the same type.
 \[
@@
 The reference partitions merit further discussion as they are a
-central contribution of this work. The heap summary algorithm creates
+central to the proofs. The heap summary algorithm creates
 many references that are auxiliary literals or stack literals to
-define the structure of the bipartite graph.  It reserves input heap
-reference for constraints expressing potential aliasing. A solver
+define the structure of the bipartite graph.  It only uses input heap
+references for constraints expressing potential aliasing. A solver
 reasons over the aliasing relationships, and a satisfying assignment

### 2014-11-12 tex/heap.tex
Reworked section 2.2. opening paragraph

@@
 \subsection{Summary Heaps as Bipartite Graphs}
-An important part and novel contribution of summary heaps for symbolic
-execution is the labeled bipartite graph representation of the heap
-which enables a summary heap to group heaps together that follow the
-same control flow to a given point of execution. The group of heaps
-split depending on control flow branches: heaps in the original group
-that follow a true outcome form a new group while heaps from that same
-original group that follow a false outcome form a different
-group. State explosion in symbolic execution is thus mitigated by
-storing a group of heaps in the state and only branching when that
-group splits.
+A novel contribution of summary heaps for symbolic execution is the
+labeled bipartite graph representation of the heap which enables a
+summary heap to group heaps together that follow the same control flow
+to a given point of execution. The graph structure is able to capture
+group membership and compute value sets using entirely non-recursive
+local look up. Additionally, updates on the heap do not require
+rewriting the path condition or any constraints in the heap.
 

### 2014-11-12 tex/heap.tex
Fixed the formatting

@@
 local look up. Additionally, updates on the heap do not require
-rewriting the path condition or any constraints in the heap.
+rewriting the path condition or any constraints in summary heap.
 
@@
 
-There are several properties of the summary heap 
-enforced by the rewrite rules that are invariant and
-important to the correctness proofs
-presented in \secref{sec:bisim}.
+There are several properties of the summary heap enforced by the
+rewrite rules that are invariant and important to the correctness
+proofs presented in \secref{sec:bisim}: \emph{reference partitions},
+\emph{immutable references}, \emph{determinism}, and \emph{type
+  consistency}.
 
-\textbf{Reference partitions}: new references are drawn from
+Reference partitions: new references are drawn from
   three distinct partitions (i) $\mathrm{init}_\cfgnt{r}()$ for references for the \emph{input heap}, (ii) $\mathrm{fresh}_\cfgnt{r}()$ for references for \emph{auxiliary literals}, and
@@
   call, and modular arithmetic is used to determine the partition to
-  which a reference belongs. Reference partitions are a critical piece
-  to the existence proof of a bisimulation between the summary heap
-  algorithm and generalized symbolic execution (see \secref{sec:bisim}).
-\begin{compactitem}
-\item \textbf{Input heap}: these references have two
+  which a reference belongs.
+\begin{compactdesc}
+\item[Input heap] these references have two
   interpretations: one as a literal and another as a variable. First,
@@
   special reference $\cfgnt{r}_\mathit{null}$ appear in constraints
-\item \textbf{Auxiliary literals}: these references are only used to define additional structure in
+\item[Auxiliary literals] these references are only used to define additional structure in
   the bipartite graph and are not part of any constraint and do not appear
   in any environment, expression, or continuation.
-\item \textbf{Stack references}: these references are also used to define additional structure in the bipartite graph but may also appear in the environment, expression, or continuation.
+\item[Stack references] these references are also used to define additional structure in the bipartite graph but may also appear in the environment, expression, or continuation.
 These are not part of any constraint.
-\end{compactitem}
+\end{compactdesc}
+Reference partitions are a critical piece to the existence proof of a
+bisimilation between the summary heap algorithm and generalized
+symbolic execution (see \secref{sec:bisim}).
 
-\textbf{Immutable references}: a reference does not change in the
+Immutable references: a reference does not change in the
 location map. It always points to the same set of constraint location
@@
 
-\textbf{Determinism}: a reference in  $(\cfgnt{L}\ \cfgnt{R})$ cannot point multiple locations simultaneously.
+Determinism: a reference in  $(\cfgnt{L}\ \cfgnt{R})$ cannot point multiple locations simultaneously.
 $$
@@
 
-\textbf{Type consistency}: all locations associated with a reference have the same type.
+Type consistency: all locations associated with a reference have the same type.
 \[
@@
 
-\textbf{Null and Uninitialized}: every summary heap contains 
+Null and Uninitialized: every summary heap contains 
 a special location for null ($\cfgnt{l}_\mathit{null}$), and a special

### 2014-11-12 tex/heap.tex
Unified formating on section 2

@@
 proofs presented in \secref{sec:bisim}: \emph{reference partitions},
-\emph{immutable references}, \emph{determinism}, and \emph{type
-  consistency}.
+\emph{immutable references}, \emph{determinism}, \emph{type
+  consistency}, and \emph{null and uninitialized}.
 
-Reference partitions: new references are drawn from
+\emph{Reference partitions} are new references drawn from
   three distinct partitions (i) $\mathrm{init}_\cfgnt{r}()$ for references for the \emph{input heap}, (ii) $\mathrm{fresh}_\cfgnt{r}()$ for references for \emph{auxiliary literals}, and
@@
 
-Immutable references: a reference does not change in the
+\emph{Immutable references} means that a reference does not change in the
 location map. It always points to the same set of constraint location
@@
 
-Determinism: a reference in  $(\cfgnt{L}\ \cfgnt{R})$ cannot point multiple locations simultaneously.
+\emph{Determinism} means that a reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point multiple locations simultaneously.
 $$
@@
 
-Type consistency: all locations associated with a reference have the same type.
+\emph{Type consistency} implies that all locations associated with a reference have the same type.
 \[
@@
 
-Null and Uninitialized: every summary heap contains 
+\emph{Null and Uninitialized} means that every summary heap contains 
 a special location for null ($\cfgnt{l}_\mathit{null}$), and a special
@@
 
-The reference partitions merit further discussion as they are a
-central to the proofs. The heap summary algorithm creates
+To summarize, the heap summary algorithm creates
 many references that are auxiliary literals or stack literals to

### 2014-11-13 tex/evaluation.tex
Completed text for the evaluation section

@@
-\begin{figure*}[t]
-%\begin{table} [t]
+%\begin{figure*}[t]
+\begin{table*} [t]
   \centering
@@
    &\multicolumn{3}{|c|}{Time} &\multicolumn{3}{|c|}{States} &\multicolumn{3}{|c|}{ Paths }\\
-								&	&\gsetxt{} & LS		&SH		&\gsetxt{}	& LS & SH&\gsetxt{}	& LS & SH\\
+								&	&\gsetxt{} & L\#		&SL		&\gsetxt{}	& L\# & SL&\gsetxt{}	& L\# 	& SL\\
    \hline
@@
   \label{tab:results}
-%\end{table}
-\end{figure*}
+\end{table*}
+%\end{figure*}
 
 \subsection{Analysis}
+The results of the experiments are presented in Table \ref{tab:results}.
+The rows contain to individual $k$-bounded test runs for each of the evaluated programs.
+The columns show the run time, state count and path count for each of the three algorithms tested.
+The headings \gsetxt{}, L\#, and SL correspond to the Generalized Symblic Execution, lazier\#, and \symtxt{} algorithms, respectively.
+Table entries containing - correspond to test runs that exceeded the allotted time bounds.
 
-The results ofAs expected, the repeated use of lazy initialization throughout the program causes an exponential increase in the number of paths explored by \gsetxt{}.
-By combining many of the \gsetxt{} paths, \symtxt{} avoids the exponential path explosion, demonstrating dramatically reduced, though still exponential, execution time growth.
-Remarkably, path growth in the k-bound appears to be sub-linear.
+In agreement with the theoretical results, the number of paths explored by \symtxt{} is strictly less than or equal the number of paths explored by \gsetxt{} for any given test run.
+Curiously, the same relationship does not hold true for states.
+State counts can vary between algorithms, because states in JPF represent points of nondeterminism, and each algorithm differs in this regard.
+For example, \gsetxt{} has additional points of nondeterminism during field reads, but in contrast address compares are completely deterministic.
+Thus, in example programs with large numbers address compares, such as TreeMap, state counts for lazier\# and \symtxt{} may exceed those for \gsetxt{}.
+Despite this, in practice this is often mitigated by the fact that symtxt{} can dispatch address compares without consulting the constraint solver.
 
-While the BinarySearchTree example introduces integer constraints, \symtxt{} performance does not appear to suffer due to the constraint burden.
-Indeed, at k=3, there appears to be a significant performance advantage in favor of \symtxt{}.
-
-The TreeMap example has a large number of integer compare instructions, and so it should present the greatest challenge to the constraint solver.
-Despite this, \symtxt{} still explores fewer paths than \gsetxt{}, and \gsetxt{} notably failed to terminate within the allotted time bounds for the $k=3$ test case.
+Run times for most tests strongly favor \symtxt{}, especially LinkedList example.
+In fact, a number of test cases can be efficiently completed using \symtxt{} for k-bounds that are not practical to be attempted with \gsetxt{} or lazier\#, including the BinarySearchTree for $k=4$ and LinkedList for $k=8$.
+Some of this discrepancy may be accounted for by the fact that \symtxt{} is equipped for incremental solving, however, in informal testing with the incremental solver turned off, \symtxt{} usually performed better than \gsetxt and lazier\#, especially in test runs with high k-bounds.

### 2014-11-13 tex/results.tex

@@
 \label{sec:eval}
-In this section we evaluate the effectiveness of \symtxt{} at
-analyzing programs with unbounded complex data input in the context of
-symbolic execution. In order to perform our evaluation we implement
-the \symtxt{} technique and evaluate its efficiacy on three Java data
-structure artifacts. We compare the results of \symtxt{} with other
-state of the art techniques that initialize complex data input
-symbolically. We first describe the tool infrastructure we use to
-implement our approach.
+In this section we evaluate the effectiveness of the \symtxt{}
+approach at analyzing programs with unbounded complex data input in
+the context of symbolic execution. In order to perform our evaluation
+we implement the \symtxt{} technique and evaluate its efficiacy on
+three Java data structure artifacts. We compare the results of the
+\symtxt{} approach with other state of the art techniques that
+initialize complex data input symbolically. We first describe the tool
+infrastructure we use to implement our approach.
 
@@
 engine of Java PathFinder(JPF)---Symbolic Pathfinder
-(SPF)~\cite{visser:ase03,Pasareanu:ISSTA08,pasareanu:ase10}. SPF is an
-open source engine for performing symbolic execution on Java
-bytecode. The JPF framework provides mechanism for overwriting the
-execution semantics of the traditional concrete Java bytecode
-semantics. SPF leverages this to define symbolic execution semantics
-for Java bytecode. SPF performs a stateless search to generate the
-symbolic execution tree since state matching in general is
-undecidable.
-
-SPF contains the implementation for GSE with lazy initialization. At
-bytecodes that access uninitialized symbolic fields it creates custom
-non-deterministic choices for the field to be null, new instance of
-its type, and aliases to any previously initialized symbolic
-fields~\cite{DBLP:journals/ase/PasareanuVBGMR13}. Recent work also
+(SPF)~\cite{visser:ase03,Pasareanu:ISSTA08,pasareanu:ase10,DBLP:journals/ase/PasareanuVBGMR13}. SPF
+is an open source engine for performing symbolic execution on Java
+bytecode. SPF overwrites the concrete execution semantics of Java
+bytecode to generate a symbolic execution tree. SPF contains an
+implementation for GSE with lazy initialization. Recent work also
 provides implementations of the lazier and lazier\# algorithms in the
@@
 
+%since state matching in general is undecidable.  SPF leverages this
+%to define symbolic execution semantics for Java bytecode.  At
+%bytecodes that access uninitialized symbolic fields it creates custom
+%non-deterministic choices for the field to be null, new instance of
+%its type, and aliases to any previously initialized symbolic
+%fields~\cite{} SPF performs a stateless search to generate the
+%symbolic execution tree.
+
 We create a new extension to SPF in order to implement the~\symtxt{}
-approach. Even though our approach is presented using the Javalite
-semantics, the implementation contains support for the full Java
-semantics such as operations over integers and other data types
-supported in Java. We overwrite three main sets of Java bytecodes that
-map to the rewrite rules presented in~\secref{sec:precise}. We provide
-custom implementation of the following: (i) field access bytecodes,
-e.g., GETFIELD and ALOAD bytecodes, to implement the field-access and
-summarize rules in~\figref{fig:symInit} and~\figref{fig:fHeap}(a),
-(ii) the field write bytecodes, e.g., PUTFIELD and ASTORE bytecodes,
-to implement the field-write rules in~\figref{fig:fHeap}(a), and (iii)
-checking equality of references bytecode, IF\_ACMPEQ and IF\_ACMPNE,
-to implement the equals references-true and references-false rules
-in~\figref{fig:eqs}. \nsr{any custom implementation for integers? }
+approach. In addition to the operations presented in the Javalite
+semantics, the implementation contains support for operations over
+integers. Examples of bytecode that we overwrite in the SPF engine are
+as follows: (i) field access bytecodes, e.g., GETFIELD and ALOAD
+bytecodes, to implement the field-access and summarize rules
+in~\figref{fig:symInit} and~\figref{fig:fHeap}(a), (ii) the field
+write bytecodes, e.g., PUTFIELD and ASTORE bytecodes, to implement the
+field-write rules in~\figref{fig:fHeap}(a), (iii) checking equality of
+references bytecode, IF\_ACMPEQ and IF\_ACMPNE, to implement the
+equals references-true and references-false rules in~\figref{fig:eqs}
+(iv) linear arithmetic operations on integers and (v) comparison
+operations on integers. We are currently working on adding support for
+floating point operations, arrays, and bit-operations.
 
-The default constraints library in SPF handles constraints in the CNF
-form, these are unable to support constraints generated by \symtxt{}
-approach since they contain disjunctions. Transforming the constraints
-generated by \symtxt{} into a CNF form proved to be inefficient. We
-use the \texttt{jConstraints} library that provides support to handle
-arbitrary constraints~\cite{ase2014-ghilrr,jpf2014-dghirr}. It uses
-the z3 solver,~\cite{z3}, as the backend to solve the constraints. We
+The default constraints library in SPF requires constraints to be in
+the CNF form, and is unable to support constraints generated by the
+\symtxt{} approach since they contain disjunctions. Transforming the
+constraints generated by the \symtxt{} approach into a CNF form proved
+to be inefficient. We use the \texttt{jConstraints} library that
+provides support to handle arbitrary
+constraints~\cite{ase2014-ghilrr,jpf2014-dghirr}. It uses the z3
+solver,~\cite{z3}, as the backend to solve the constraints. We
 leverage the incremental solving feature in z3 in our experiments. We
@@
 
+\begin{comment}
 Loops and recursive methods over symbolic variables are bounded based
@@
 access point in its heap summary.
+\end{comment}
 
@@
 are: \symtxt{}, \gsetxt{}, lazier, and lazier\#. We also vary the
-$k-bound$ for each the algorithms. We select three dependent variables
-and measures for our study: (i) time, (ii) states explored, and (iii)
-paths generated. The \emph{time} is the total time taken by each
-algorithm to explore the symbolic execution tree as well as total
-constraint solving time. The \emph{states explored} represents the
-number of nodes in the symbolic execution tree while the \emph{paths
-  generated} represent as the name suggests the number of unique paths
-in the symbolic execution tree.
+$k$-bound for each the algorithms. Note that $k$-bounding bounds the
+length of a reference chain from the root of the heap~\cite{Deng:2006}
+We select three dependent variables and measures for our study: (i)
+time, (ii) states explored, and (iii) paths generated. The \emph{time}
+is the total time taken by each algorithm to explore the symbolic
+execution tree as well as total constraint solving time. The
+\emph{states explored} represents the number of nodes in the symbolic
+execution tree while the \emph{paths generated} represent as the name
+suggests the number of unique paths in the symbolic execution tree.
 

### 2014-11-13 tex/evaluation.tex
Fixed caption on results table
fixed a typo in the evaluation
Refactored evaluation section to emphasize performance benefits

@@
   \end{tabular}
-  \caption{test results}
+  \caption{Test results.}
   \label{tab:results}
@@
 
-In agreement with the theoretical results, the number of paths explored by \symtxt{} is strictly less than or equal the number of paths explored by \gsetxt{} for any given test run.
-Curiously, the same relationship does not hold true for states.
+In most tests, run times strongly favor \symtxt{}, especially for nontrivial k-values.
+Performance improvement ranges from 4.8x for BinarySearchTree at $k$=3, to 118x for LinkedList at $k$=6.
+In fact, a number of test cases can be efficiently completed using \symtxt{} for k-bounds that are not practical to be attempted with \gsetxt{} or lazier\#, including the BinarySearchTree for $k$=4 and LinkedList for $k$=8.
+Some of this discrepancy may be accounted for by the fact that \symtxt{} is equipped for incremental solving, however, during informal testing with the incremental solver turned off, \symtxt{} usually performed better than \gsetxt and lazier\#, especially in test runs with high k-bounds.
+
+Path counts likewise substantially favor \symtxt{}.
+In agreement with the theoretical results, the number of paths explored by \symtxt{} is strictly less than or equal the number of paths explored by \gsetxt{} for all test cases.
+More surprisingly, \symtxt{} path growth appears to be sub-exponential in $k$ for the LinkedList program.
+
+Curiously, the pattern established with run-times and path counts does not hold true for state counts.
 State counts can vary between algorithms, because states in JPF represent points of nondeterminism, and each algorithm differs in this regard.
@@
 Thus, in example programs with large numbers address compares, such as TreeMap, state counts for lazier\# and \symtxt{} may exceed those for \gsetxt{}.
-Despite this, in practice this is often mitigated by the fact that symtxt{} can dispatch address compares without consulting the constraint solver.
-
-Run times for most tests strongly favor \symtxt{}, especially LinkedList example.
-In fact, a number of test cases can be efficiently completed using \symtxt{} for k-bounds that are not practical to be attempted with \gsetxt{} or lazier\#, including the BinarySearchTree for $k=4$ and LinkedList for $k=8$.
-Some of this discrepancy may be accounted for by the fact that \symtxt{} is equipped for incremental solving, however, in informal testing with the incremental solver turned off, \symtxt{} usually performed better than \gsetxt and lazier\#, especially in test runs with high k-bounds.
+Despite this, in practice this is often mitigated by the fact that \symtxt{} can dispatch address compares without consulting the constraint solver.

### 2014-11-13 tex/related.tex

@@
 
-\subsection{Symbolic Exection}
-As originally formulated, symbolic execution was incapable of reasoning beyond scalar input values.
-Since then, several adaptations to allow symbolic execution to cope with heap data structures have been proposed, beginning with Generalized symbolic execution \cite{GSE03}.
-Subsequent improvements to the method \cite{Deng:2006,Deng:2007} reduce path explosion by delaying path splitting over aliasing choices for as long as possible.
-However, since all of the above methods introduce nondeterminism during field reads and writes, they all contribute to path explosion to some extent.
-Since our heap representation does not introduce any nondeterminism beyond the level in standard symbolic execution, it will generally create fewer paths than these methods, sometimes by a wide margin.
+%\subsection{Symbolic Exection}
 
-\subsection{Model Checking}
-Need to talk about Bounded Model Checking, etc.
+Recent years have seen a significant growth in research projects based
+on symbolic execution, first introduced in the 1970's by
+Clarke~\cite{Clarke:76} and King~\cite{King:76}.  These projects have
+pursued three primary research directions to enhance traditional
+symbolic execution: (1)~to improve its
+effectiveness~\cite{Godefroid:PLDI05,Sen:FSE05,CadarEngler05EXE,KiasanKunit,Pasareanu:2011};
+(2)~to improve its
+efficiency~\cite{AnandETAL2009AbsSymExe,KhurshidSuen2005AbsSymExe,Godefroid:POPL07,Inkumsah:2008,ChangPhD10DataFlowSymbolicExecution,Santelices:ISSTA10,Visser:2012};
+and (3)~to improve its
+applicability~\cite{Person:FSE08,KhurshidETAL05RepairingStructurally,CsallnerETAL08DySy,SeoETAL06EnergyConsumptionFrameworkDistributedJava,Geldenhuys:2012,Ma:2011}. Handling
+unbounded data input of complex type has continued to be a challenge
+for symbolic execution.  Generalized symbolic execution \cite{GSE03}
+with lazy initialization set the path to materializing fields
+concretely. Subsequent improvements to the method
+\cite{Deng:2006,Deng:2007} to reduce path explosion by delaying path
+splitting over aliasing choices for as long as possible. However,
+since all of the above methods introduce nondeterminism during field
+reads and writes, they all contribute to path explosion to some
+extent.
 
-\subsection{Static Analysis}
-A number of static analysis techniques have been proposed that have some ability to reason about input heap structures.
-These techniques are usually over-approximations, often have difficulty reasoning about path-sensitive properties, or cannot reason about programs with recursive data structures.
-Moreover, static analysis methods are seldom useful for test-case generation.
+% Since our heap representation does not introduce any nondeterminism
+%beyond the level in standard symbolic execution, it will generally
+%create fewer paths than these methods, sometimes by a wide margin.
 
-One notable static analysis method that is closely related to ours is the procedure summaries proposed by Isil and Tomas Dillig \cite{Dillig:2011}.
-Elements of their technique that are similar to ours include; references guarded by constraint expressions, conditional write semantics, and a general aversion to path splitting.
-However, their method is limited by most of the standard problems with static analysis techniques, including path sensitivity, imprecision, and recursive data structures.
-While their method has improved path sensitivity over standard static analysis methods, it remains limited by a statically-generated symbolic input heap, and cannot adapt to path-sensitive heap properties of the input heap.
-Thus, their method cannot determine a priori which nodes in the input heap are actually accessed by the program.
-It may potentially generate input heaps containing a significant number of nodes that have no impact on program execution.
+%\subsection{Model Checking} Need to talk about Bounded Model
+%Checking, etc.
 
-\subsection{Heap Representations}
-One significant line of work on representing heaps is shape analysis.
-Shape analysis attempts to reduce the complexity of the heap by combining multiple nodes with similar properties into summary nodes.
-The summary nodes typically establish may/must constraints over the heap structure, and typically represent an overapproximation of the represented heap.
-As such, program evaluations using shape analysis representations are prone to reporting large numbers of false positives.
+%\subsection{Static Analysis}
 
-As in our representation, other methods have been proposed that model references using sets of guarded locations \cite{Xie:2005,Cherem:2007,Dillig:2011,Sen:2014}.
-These sets, sometimes known as value sets or value summaries, allow multiple heaps to be represented simultaneously with a higher degree of precision than afforded by shape analysis.
-However, some of these previous attempts  \cite{Xie:2005,Cherem:2007} utilize non-local recursive definitions for objects.
-The impact of using recursive definitions for objects is two-fold.
-First, these techniques must use approximations to resolve reference inequalities, resulting in false positives in the results.
-Second, these techniques are incapable of reasoning about heaps with recursive data structures due to the potential for infinite recursion during dereferencing.
-This means that either a large class of data structures must be avoided, or a large class of behaviors must be ignored.
-In our heap representation, object descriptions are entirely local, thus avoiding these pitfalls.
-Other methods  \cite{Dillig:2011,Sen:2014}, while having local morphological representations, do not provide for dynamic exploration of the initial heap state.
+A number of static analysis techniques have been proposed that have
+some ability to reason about input heap structures. One notable static
+analysis method that is closely related to ours is the procedure
+summaries proposed by Isil and Tomas Dillig \cite{Dillig:2011}.  While
+their method has improved path sensitivity over standard static
+analysis methods, it remains limited by a statically-generated
+symbolic input heap, and cannot adapt to path-sensitive heap
+properties of the input heap.
 
-Another line of work in heap representation lies in identifying isomorphic heap structures in order to avoid exploring redundant paths.
-Examples of such methods include Korat, XXX, and YYY.
-These methods are generally focused on the morphology of the heap alone, in isolation from the external constraint problems encountered during program execution.
-As such, these works are largely orthogonal to the methods presented here, though some of them may possibly be complimentary.
+% These techniques are usually over-approximations, often have
+% difficulty reasoning about path-sensitive properties, or cannot
+% reason about programs with recursive data structures. Moreover,
+% static analysis methods are seldom useful for test-case generation.
+
+%. Elements of their technique that are similar to ours include;
+%references guarded by constraint expressions, conditional write
+%semantics, and a general aversion to path splitting. However, their
+%method is limited by most of the standard problems with static
+%analysis techniques, including path sensitivity, imprecision, and
+%recursive data structures.
+
+% Thus, their method cannot determine a priori which nodes in the
+%input heap are actually accessed by the program. It may potentially
+%generate input heaps containing a significant number of nodes that
+%have no impact on program execution.
+
+%\subsection{Heap Representations}
+
+%One significant line of work on representing heaps is shape
+%analysis. Shape analysis attempts to reduce the complexity of the
+%heap by combining multiple nodes with similar properties into summary
+%nodes. The summary nodes typically establish may/must constraints
+%over the heap structure, and typically represent an overapproximation
+%of the represented heap. As such, program evaluations using shape
+%analysis representations are prone to reporting large numbers of
+%false positives.
+
+As in our representation, other methods have been proposed that model
+references using sets of guarded locations
+\cite{Xie:2005,Cherem:2007,Dillig:2011,Sen:2014}. These sets,
+sometimes known as value sets or value summaries, allow multiple heaps
+to be represented simultaneously with a higher degree of precision
+than afforded by shape analysis. However, some of these previous
+attempts \cite{Xie:2005,Cherem:2007} utilize non-local recursive
+definitions for objects. The impact of using recursive definitions for
+objects is two-fold. First, these techniques must use approximations
+to resolve reference inequalities, resulting in false positives in the
+results. Second, these techniques are incapable of reasoning about
+heaps with recursive data structures due to the potential for infinite
+recursion during dereferencing. This means that either a large class
+of data structures must be avoided, or a large class of behaviors must
+be ignored. In our heap representation, object descriptions are
+entirely local, thus avoiding these pitfalls. Other methods
+\cite{Dillig:2011,Sen:2014}, while having local morphological
+representations, do not provide for dynamic exploration of the initial
+heap state.
+
+Another line of work in heap representation lies in identifying
+isomorphic heap structures in order to avoid exploring redundant
+paths. Examples of such methods include Korat, XXX, and YYY. These
+methods are generally focused on the morphology of the heap alone, in
+isolation from the external constraint problems encountered during
+program execution. As such, these works are largely orthogonal to the
+methods presented here, though some of them may possibly be
+complimentary.

### 2014-11-13 tex/evaluation.tex
Added a short summary to the evaluation.

@@
 Despite this, in practice this is often mitigated by the fact that \symtxt{} can dispatch address compares without consulting the constraint solver.
+
+In summary, it appears that the benefits of avoiding initialization-based nondeterminism more than outweigh the increased complexity in the constraints.
+In fact, \symtxt{} can analyze certain types of programs with orders of magnitude greater efficiency than with \gsetxt{} or lazier#, while covering exactly the same test cases with zero loss of precision.

### 2014-11-13 tex/evaluation.tex
fixing the hash problem

--- 2014-11-13 tex/evaluation.tex
@@
 Despite this, in practice this is often mitigated by the fact that \symtxt{} can dispatch address compares without consulting the constraint solver.
+
+In summary, it appears that the benefits of avoiding
+initialization-based nondeterminism more than outweigh the increased
+complexity in the constraints. In fact, \symtxt{} can analyze certain
+types of programs with orders of magnitude greater efficiency than
+with \gsetxt{} or lazier\#, while covering exactly the same test cases
+with zero loss of precision.

### 2014-11-13 tex/evaluation.tex
Fixed some typos with the evaluation.

@@
 In fact, a number of test cases can be efficiently completed using \symtxt{} for k-bounds that are not practical to be attempted with \gsetxt{} or lazier\#, including the BinarySearchTree for $k$=4 and LinkedList for $k$=8.
-Some of this discrepancy may be accounted for by the fact that \symtxt{} is equipped for incremental solving, however, during informal testing with the incremental solver turned off, \symtxt{} usually performed better than \gsetxt and lazier\#, especially in test runs with high k-bounds.
+Some of this discrepancy may be accounted for by the fact that \symtxt{} is equipped for incremental solving, however, during informal testing with the incremental solver turned off, \symtxt{} usually performed better than \gsetxt{} and lazier\#, especially in test runs with high k-bounds.
 
@@
 
-In summary, it appears that the benefits of avoiding
-initialization-based nondeterminism more than outweigh the increased
-complexity in the constraints. In fact, \symtxt{} can analyze certain
-types of programs with orders of magnitude greater efficiency than
-with \gsetxt{} or lazier\#, while covering exactly the same test cases
-with zero loss of precision.
+In summary, it appears that the benefits of avoiding initialization-based nondeterminism more than outweigh the increased complexity in the constraints.
+In fact, \symtxt{} can analyze certain types of programs with orders of magnitude greater efficiency than with \gsetxt{} or lazier\#, while covering exactly the same test cases with zero loss of precision.

### 2014-11-13 tex/intro.tex
Rewrote some portions on the introducation based on Jay's feedback

--- 2014-11-12 tex/intro.tex
@@
 domains, i.e., data stored on the heap~\cite{Kiasan06,Kiasan07,GSE03}.  
-These Generalized Symbolic Execution (GSE) techniques construct the 
+These \emph{Generalized Symbolic Execution} (GSE) techniques construct the 
 heap in a lazy manner, deferring
@@
 creates additional non-deterministic choice points in the symbolic
-execution tree representing the feasible heap configurations.  as (a)
-null, (b) instance of a new reference of a compatible class, and (c)
-alias an previously initialized symbolic reference.  Symbolic
-execution follows concrete program semantics for materialized heap
-locations. Although this approach enables analysis of heap
+execution tree by representing the feasible heap configurations as (i)
+null, (ii) an instance of a new reference of a compatible class, and (iii)
+an alias to a previously initialized symbolic reference.  Symbolic
+execution then follows concrete program semantics for materialized heap
+locations. Although this approach enables the analysis of heap
 manipulating programs, a large number of feasible concrete heap
-configurations may be created exacerbating the well known state space
-explosion problem associated with symbolic execution.
+configurations are created leading to state space explosion.
 
@@
 in GSE by grouping multiple heaps together and only partitioning the
-heaps at points of divergence in the control flow graph. To achieve
-this goal, we found inspiration from recent work in the domain of
-static analysis that uses sets of constraints over heap locations to
-encode multiple heaps in a single representation. These sets,
-sometimes known as value sets or value summaries, allow multiple heaps
-to be represented simultaneously with a higher degree of precision
-than afforded by traditional shape analysis techniques. Some of these
-previous attempts, however, are unable to handle aliasing in heaps due
-to a recursive definition of objects~\cite{..}, while others require a
-set of heaps as input and are unable to initialize heaps
-on-the-fly~\cite{..}. For these reasons the techniques use
-over-approximations to reason about heaps and may report false
-positives. Also, update to heaps require a rewrite of the constraint
-system making it prohitive for use in the context of symbolic
-execution.
+heaps at points of divergence in the control flow graph. Our
+inspiration is found in the domain of static analysis that uses sets
+of constraints over heap locations to encode multiple heaps in a
+single representation. These sets, sometimes known as value sets or
+value summaries, allow multiple heaps to be represented simultaneously
+with a higher degree of precision than afforded by traditional
+techniques for shape analysis.
+
+Unfortunately, value sets often do not support aliasing and require a
+recursive definition of objects~\cite{..}. Also, it is not obvious how
+to support heap updates in value sets, and in particular, on-the-fly
+lazy initialization as is common in GSE, so it is not unusual to
+require a fully initialized set of input heaps in the analysis. As is
+typical in static analysis, over approximation of the value sets
+alleviates some of the limitations but also leads to false positives,
+and when heap updates are supported, with or without over
+approximation, the path constraint must be rewritten to reflect the
+update, and the constraints in the value set must also be rewritten.
 
@@
 
-In this work, we present a technique for heap summarization,
-initialization, and analysis in the context of symbolic execution. We
-represent the heap as a bipartiate graph of references and sets of
-constraints over locations. The use of a bipartiate graph affords two
-key advantages: (i) it allows for a non-recursive definition of
-objects, allowing us to handle aliasing and (ii) it does not require
-rewrite of the constraints during updates to the heap nor does it
-introduce any auxillary variables in the constraints. During symbolic
-execution, we initialize, summarize, and update the bipartiate
-graph. Unlike GSE, however, the heaps are partitioned only at points
-of divergence in the control flow graph. These points of
-non-determinism are at field accesses or writes that lead to
-null-pointer exceptions and at comparisons of references. The former
-represents a divergence due to exceptional control flow while the
-later due to program structure.
+The solution presented in this paper to enabling value sets in symbolic execution
+with lazy initialization is to represent the heap as a bipartite graph
+consisting of references and locations. A reference is able to point
+to several different locations; each edge is predicated on constraints
+over aliasing between references. Locations point back to references
+on different fields. The bipartite graph enables (i) the use of
+aliasing to define objects rather than recursive definitions; (ii)
+value set computation using only local information; and (iii) heap
+updates that only impact affected locations, require no constraint
+rewriting, and require no auxiliary variables in the constraints.  We
+call this new heap a summary heap.
+
+To mitigate state space explosion in GSE, the solution described in
+paper uses a summary heap in the symbolic execution. This summary heap
+algorithm defines how the bipartite graph updates in lazy
+initialization. Unlike GSE, however, the summary heap algorithm
+partitions only at points of divergence in the control flow
+graph. These points of non-determinism are at field accesses or writes
+that lead to null-pointer exceptions and at comparisons of
+references. The former represents a divergence due to exceptional
+control flow while the later due to program structure.
 
@@
 
-The heap summary approach for symbolic execution is sound and complete
-with respect to properties that are provable using GSE. This is
-accomplished by showing the existence of a bisimulation relation. In
-other words, any property that can be proved using GSE can also be
-proved using heap summaries, furthermore, any property proved by heap
-summaries can also be proved by GSE---given the same bounds on heap
+Importantly, the summary heap algorithm is sound and complete with
+respect to properties that are provable using GSE. This proof is
+accomplished by showing the existence of a bisimulation relation
+between states in GSE and states in the summary heap algorithm. In
+practical terms, any property that can be proved using GSE can also be
+proved using summary heaps, furthermore, any property proved by
+summary heaps can also be proved by GSE. Of course, Both require a bound on heap
 reference chains and loops.
 
-In a preliminary evaluation comparing the efficiacy of the heap
-summary technique with respect to the other GSE approaches, we observe
-a two-order of magnitude reduction in the total time taken to explore
-the same state space. We implement the heap summary approach as an
-extension to the Symbolic PathFinder symbolic execution engine and
-analyze three Java data structure artifacts. For these examples, we
-show that where other GSE approaches are unable to complete
-exploration within the provided time bound, the summary heap finishes
-exploration in a few seconds.
+Aside from the novelty of the heap summary and it application to
+symbolic execution, the new data structure appears to ameliorate state
+explosion in symbolic execution. A preliminary implementation in Java
+Pathfinder (JPF), described in this paper, compares the heap summary
+algorithm on a handful of benchmarks, each representing different
+degrees of initialization and branching, to GSE with lazy
+initialization in Symbolic Pathfinder (SPF) and implementation
+lazier\# also in SPF. The results show that in general, that the heap
+summary algorithm improves over other techniques, and in some
+instances, the improvement is remarkable: two-orders of magnitude
+reduction in running time. More critically though, the heap summary
+enables the initialization of larger more complex heaps than
+heretofore possible as shown in our results.
+
+\begin{comment}
+We implement the summary heap algorithm as an extension to \emph{Java
+  PathFinder} (JPF) and compare it to GSE with lazy initialization in
+\emph{Symbolic Pathfinder (SPF)} and an implementation of lazier\#
+initialization in SPF.  The comparison shows on some examples up to a two-order of magnitude
+reduction in the total time taken to explore the same state space
+defined by the bound on the longest heap reference chain.  For these
+examples, we show that where other GSE approaches are unable to
+complete exploration within the provided time bound, the summary heap
+finishes exploration in a few seconds.
+\end{comment}
 
@@
 
-\item\textbf{-} Define a heap encoding as a bipartiate graph of
-  references and sets of constraints over locations.
+\item\textbf{-} A summary heap as a bipartite graph that supports aliasing, local value set computation, and heap updates.
 
@@
 
-\item\textbf{-} Present an algorithm to initialize, summarize, and
+\item\textbf{-} A summary heap algorithm to initialize, summarize, and
   update the bipartiate graphs during symbolic execution.
 
-\item\textbf{-} Show the existence of a bisimulation relation prove
+\item\textbf{-} A proof of the existence of a bisimulation relation to establish
   that the heap summary approach is sound and complete with respect to
@@
 
-\item\textbf{-} Demonstrate the scability of the heap summary approach
-  compared to GSE approaches.
+\item\textbf{-} A proof of concept implementation and small empirical study to demonstrate the scability of the heap summary approach
+  compared to other GSE approaches.
 
@@
 
-\noindent{In this paper, we present a brief over of the a Java-like
-  language and the encoding of heaps as a bipartiate graph. We use the
-  Java-like language to define the formal semantics of the heap
-  summary machine and then prove the existence of a bisumulation
-  relation. Finally we present an evaluation of the heap summary
-  approach. }
+\noindent{The rest of this paper discusses a formal language semantics
+  for the summary heap algorithm definition with the definition of the
+  summary heap. The paper then presents the application of summary
+  heaps to symbolic execution. Following the algorithm definition, the
+  existence proof of bisimulation is given with the accompanying
+  corollaries for soundness and completeness. This is followed by the
+  implementation in JPF and the evaluation. The paper ends with the
+  conclusion and future work.}
 

### 2014-11-13 tex/precise.tex
Rewrote some portions on the introducation based on Jay's feedback

@@
 $\mathbb{UN}$ for field $f$, the $\mathit{min}_l$ function returns
-$(\phi_x\ \cfgnt{l}_x)$ based on a lexical ordering of uninitialized locations
+$(\phi_x\ \cfgnt{l}_x)$ based on a lexicographical ordering of uninitialized locations
 in $\Lambda$. The init$_r$ method returns a new input reference $\cfgnt{r}_f$,

### 2014-11-13 tex/intro.tex
Focused language

@@
 of constraints over heap locations to encode multiple heaps in a
-single representation. These sets, sometimes known as value sets or
-value summaries, allow multiple heaps to be represented simultaneously
+single representation. These sets, sometimes known as \emph{value sets} or
+\emph{value summaries}, allow multiple heaps to be represented simultaneously
 with a higher degree of precision than afforded by traditional
@@
 Unfortunately, value sets often do not support aliasing and require a
-recursive definition of objects~\cite{..}. Also, it is not obvious how
-to support heap updates in value sets, and in particular, on-the-fly
-lazy initialization as is common in GSE, so it is not unusual to
-require a fully initialized set of input heaps in the analysis. As is
+recursive definition of objects~\cite{..}. Also, heap updates often
+require that the path constraint be rewritten to reflect the update,
+and the constraints in the value set may also need to be rewritten with the
+addition of auxiliary variables. These non-local operations make it
+difficult to use value sets in symbolic execution. As is
 typical in static analysis, over approximation of the value sets
-alleviates some of the limitations but also leads to false positives,
-and when heap updates are supported, with or without over
-approximation, the path constraint must be rewritten to reflect the
-update, and the constraints in the value set must also be rewritten.
+alleviates some of the limitations but also leads to false positives.
 
@@
 consisting of references and locations. A reference is able to point
-to several different locations; each edge is predicated on constraints
+to several different locations: each edge predicated on constraints
 over aliasing between references. Locations point back to references
@@
 
-Aside from the novelty of the heap summary and it application to
+Aside from the novelty of the heap summary and its application to
 symbolic execution, the new data structure appears to ameliorate state
-explosion in symbolic execution. A preliminary implementation in Java
+explosion in symbolic execution as hoped. A preliminary implementation in Java
 Pathfinder (JPF), described in this paper, compares the heap summary
@@
 
-\begin{description}
+\begin{compactdesc}
 
@@
 
-\end{description}
-
-\noindent{The rest of this paper discusses a formal language semantics
-  for the summary heap algorithm definition with the definition of the
-  summary heap. The paper then presents the application of summary
-  heaps to symbolic execution. Following the algorithm definition, the
-  existence proof of bisimulation is given with the accompanying
-  corollaries for soundness and completeness. This is followed by the
-  implementation in JPF and the evaluation. The paper ends with the
-  conclusion and future work.}
+\end{compactdesc}
+The rest of this paper defines summary heap and its to symbolic
+execution. Following the algorithm definition, the existence proof of
+bisimulation is given with the accompanying corollaries for soundness
+and completeness. This is followed by the implementation in JPF and
+the evaluation. The paper ends with the conclusion and future work.
 

### 2014-11-13 tex/intro.tex
Restored paragraph

@@
 
+Some of these
+previous attempts, however, are unable to handle aliasing in heaps due
+to a recursive definition of objects~\cite{..}, while others require a
+set of heaps as input and are unable to initialize heaps
+on-the-fly~\cite{..}. For these reasons the techniques use
+over-approximations to reason about heaps and may report false
+positives. Also, update to heaps require a rewrite of the constraint
+system making it prohitive for use in the context of symbolic
+execution.
+
+\begin{comment}
 Unfortunately, value sets often do not support aliasing and require a
@@
 alleviates some of the limitations but also leads to false positives.
+\end{comment}
 

### 2014-11-13 tex/intro.tex
tweak to the intro

@@
 of constraints over heap locations to encode multiple heaps in a
-single representation. These sets, sometimes known as \emph{value sets} or
-\emph{value summaries}, allow multiple heaps to be represented simultaneously
-with a higher degree of precision than afforded by traditional
-techniques for shape analysis.
-
-Some of these
+single representation. These sets, sometimes known as \emph{value
+  sets} or \emph{value summaries}, allow multiple heaps to be
+represented simultaneously with a higher degree of precision than
+afforded by traditional techniques for shape analysis. Some of these
 previous attempts, however, are unable to handle aliasing in heaps due
@@
 set of heaps as input and are unable to initialize heaps
-on-the-fly~\cite{..}. For these reasons the techniques use
-over-approximations to reason about heaps and may report false
-positives. Also, update to heaps require a rewrite of the constraint
-system making it prohitive for use in the context of symbolic
-execution.
+on-the-fly~\cite{..}.  As is typical in static analysis, over
+approximation of the heap representations alleviates some of the
+limitations but also leads to false positives. Also, update to heaps
+require a rewrite of the constraint system making it prohitive for use
+in the context of symbolic execution.
 
@@
 
-The solution presented in this paper to enabling value sets in symbolic execution
-with lazy initialization is to represent the heap as a bipartite graph
-consisting of references and locations. A reference is able to point
-to several different locations: each edge predicated on constraints
-over aliasing between references. Locations point back to references
-on different fields. The bipartite graph enables (i) the use of
-aliasing to define objects rather than recursive definitions; (ii)
-value set computation using only local information; and (iii) heap
-updates that only impact affected locations, require no constraint
-rewriting, and require no auxiliary variables in the constraints.  We
-call this new heap a summary heap.
+The solution presented in this paper to enabling value sets in
+symbolic execution with lazy initialization is to represent the heap
+as a bipartite graph consisting of references and locations. A
+reference is able to point to several different locations: each edge
+predicated on constraints over aliasing between references. Locations
+point back to references on different fields. The bipartite graph
+enables (i) the use of aliasing to define objects rather than
+recursive definitions; (ii) value set computation using only local
+information; and (iii) heap updates that only impact affected
+locations, require no constraint rewriting, and require no auxiliary
+variables in the constraints.  We call this new heap a summary heap.
 

### 2014-11-13 tex/heap.tex
Minor edits

@@
 local look up. Additionally, updates on the heap do not require
-rewriting the path condition or any constraints in summary heap.
+rewriting the path condition or any constraints in the summary heap.
 
@@
 $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the reference
-associated with the given location-field pair in the heap. Predicate
-calculus is used to describe the more complex updates to the heap in
-the semantics.
+associated with the given location-field pair in the heap.
 
@@
 proofs presented in \secref{sec:bisim}: \emph{reference partitions},
-\emph{immutable references}, \emph{determinism}, \emph{type
+\emph{immutability}, \emph{determinism}, \emph{type
   consistency}, and \emph{null and uninitialized}.
@@
 \begin{compactdesc}
-\item[Input heap] these references have two
+\item[Input heap:] these references have two
   interpretations: one as a literal and another as a variable. First,
@@
   special reference $\cfgnt{r}_\mathit{null}$ appear in constraints
-\item[Auxiliary literals] these references are only used to define additional structure in
+\item[Auxiliary literals:] these references are only used to define additional structure in
   the bipartite graph and are not part of any constraint and do not appear
   in any environment, expression, or continuation.
-\item[Stack references] these references are also used to define additional structure in the bipartite graph but may also appear in the environment, expression, or continuation.
+\item[Stack references:] these references are also used to define additional structure in the bipartite graph but may also appear in the environment, expression, or continuation.
 These are not part of any constraint.
@@
 
-\emph{Immutable references} means that a reference does not change in the
+\emph{Immutability} means that a reference does not change in the
 location map. It always points to the same set of constraint location
@@
 \item $\lp\phi^\prime\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r}^\prime)$; and
-\item $\phi$ and $\phi^\prime$ are true under aliasing assignments from the solver.
+\item $\phi$ and $\phi^\prime$ hold in aliasing assignments from the solver.
 \end{compactitem}
 In this way, the graph groups heaps with the conditions under which
-those heaps exist. This representation, by virtue of the reference
-partitions, separates the constraint problem from the morphology
-problem: it is possible to update the heap without having to rewrite
-constraints. Without this separation, it would not be possible to
-lazily initialize heap locations along a program path.
+those heaps exist. This representation separates the constraint
+problem from the morphology problem: it is possible to update the heap
+without having to rewrite constraints. Without this separation, it
+would not be possible to lazily initialize heap locations along a
+program path.
 
@@
 To show the heap summary algorithm is sound and complete with respect
-to properties proved by generalized symbolic execution, we refer to
-the generalized symbolic execution with lazy initialization machine by
-the relation $\rgse$ or $p \rgse p^\prime$, and to the new summary
-heap algorithm machine by $\rsym$ or $q \rsym q^\prime$. Both machines
-use the summary heap structure, and for simplicity,
-both use lazy initialization as opposed to lazier or lazier\#.
+to properties proved by GSE, we define a transition relation that
+relates states according GSE and refer to it as $\rgse$ or $p \rgse
+p^\prime$. Similarly we define for the new summary heap algorithm
+$\rsym$ or $q \rsym q^\prime$. For simplicity, both use lazy
+initialization as opposed to lazier or lazier\#.
 
-Due to space restrictions, the full operational semantics for
-generalized symbolic execution with lazy initialization for Javalite
-are presented in the supplemental document. We also present the
-portion of the Javalite rewrite rules which are common to both
-machines in the supplementary document. In the next section, we
-present the rewrite rules specific to the new summary heap algorithm
-for symbolic execution.
+The full operational semantics for $\rgse$ are in the supplemental
+document. In the next section, we present the rewrite rules specific
+to $\rsym$.

### 2014-11-13 tex/javalite.tex
Minor edits

@@
 is to be executed next.  In this work we change the semantics of the original
- Javalite machine and its machine syntax to represent (i) generalized
-symbolic execution~\cite{GSE03}, and (ii) the summary heap algorithm
+ Javalite machine and its machine syntax to represent (i) GSE~\cite{GSE03}, and (ii) the summary heap algorithm
 presented in this work.

### 2014-11-13 tex/intro.tex
reworked

@@
 
+In order to represent multiple heaps simultaneously in the context of
+symbolic execution we define a novel heap representation and an
+algorithm to initialize and update the heap on-the-fly. Our summary
+heap approach supports aliasing, it does not require constraint
+rewriting on heap updates, and it reduces the non-determinism in the
+search space during symbolic execution.
+
+\begin{comment}
+
 The solution presented in this paper to enabling value sets in
@@
 
-Importantly, the summary heap algorithm is sound and complete with
-respect to properties that are provable using GSE. This proof is
-accomplished by showing the existence of a bisimulation relation
-between states in GSE and states in the summary heap algorithm. In
-practical terms, any property that can be proved using GSE can also be
-proved using summary heaps, furthermore, any property proved by
-summary heaps can also be proved by GSE. Of course, Both require a bound on heap
-reference chains and loops.
+\end{comment}
+We represent the heap as a bipartite graph consisting of references and locations.
+Each reference is able to point to multiple locations, where each edge is predicated on constraints over aliasing between references.
+Each location points to a single reference for a given field.
+The use of a bipartiate graph affords two
+key advantages: (i) it allows for a non-recursive definition of objects which enables us to support aliasing, and (ii) it does not require rewriting of the constraints during updates to the heap nor does it introduce auxillary variables into the constraints.
+
+This summary heap algorithm defines how the bipartite graph is updated during lazy initialization.
+Unlike GSE, however, the summary heap algorithm introduces non-determinism in the search only at points of divergence in the control flow graph.
+These points of non-determinism are at field accesses or writes that lead to null-pointer exceptions and at comparisons of references.
+The former represents a divergence due to exceptional control flow while the latter is due to program structure.
+The precise heap representation based on a bipartiate graph coupled with this algorithm to perform updates to the heap enable us to successfully mitigate the state space explosion problem in GSE.
+
+The summary heap algorithm is sound and complete with respect to
+properties that are provable using GSE. This proof is accomplished by
+showing the existence of a bisimulation relation between states in GSE
+and states in the summary heap algorithm. In practical terms, any
+property that can be proved using GSE can also be proved using summary
+heaps, furthermore, any property proved by summary heaps can also be
+proved by GSE. Of course, both require a bound on heap reference
+chains and loops.
 

### 2014-11-13 tex/intro.tex
reworked

@@
 
-In order to represent multiple heaps simultaneously in the context of
-symbolic execution we define a novel heap representation and an
-algorithm to initialize and update the heap on-the-fly. Our summary
-heap approach supports aliasing, it does not require constraint
-rewriting on heap updates, and it reduces the non-determinism in the
-search space during symbolic execution.
+In this work, in order to effectively represent multiple heaps
+simultaneously in the context of symbolic execution we define a novel
+heap representation and an algorithm to initialize and update the heap
+on-the-fly. Our summary heap approach supports aliasing, it does not
+require constraint rewriting on heap updates, and it reduces the
+non-determinism in the search space during symbolic execution.
 
-\begin{comment}
+We represent the heap as a bipartite graph consisting of references
+and locations. Each reference is able to point to multiple locations,
+where each edge is predicated on constraints over aliasing between
+references. Each location points to a single reference for a given
+field. The use of a bipartiate graph affords two key advantages: (i)
+it allows for a non-recursive definition of objects which enables us
+to support aliasing, and (ii) it does not require rewriting of the
+constraints during updates to the heap nor does it introduce auxillary
+variables into the constraints.
 
-The solution presented in this paper to enabling value sets in
-symbolic execution with lazy initialization is to represent the heap
-as a bipartite graph consisting of references and locations. A
-reference is able to point to several different locations: each edge
-predicated on constraints over aliasing between references. Locations
-point back to references on different fields. The bipartite graph
-enables (i) the use of aliasing to define objects rather than
-recursive definitions; (ii) value set computation using only local
-information; and (iii) heap updates that only impact affected
-locations, require no constraint rewriting, and require no auxiliary
-variables in the constraints.  We call this new heap a summary heap.
+This summary heap algorithm defines how the bipartite graph is updated
+during lazy initialization. Unlike GSE, however, the summary heap
+algorithm introduces non-determinism in the search only at points of
+divergence in the control flow graph. These points of non-determinism
+are at field accesses or writes that lead to null-pointer exceptions
+and at comparisons of references. The former represents a divergence
+due to exceptional control flow while the latter is due to program
+structure. The precise heap representation based on a bipartiate graph
+coupled with this algorithm to perform updates to the heap enable us
+to successfully mitigate the state space explosion problem in GSE.
 
-To mitigate state space explosion in GSE, the solution described in
-paper uses a summary heap in the symbolic execution. This summary heap
-algorithm defines how the bipartite graph updates in lazy
-initialization. Unlike GSE, however, the summary heap algorithm
-partitions only at points of divergence in the control flow
-graph. These points of non-determinism are at field accesses or writes
-that lead to null-pointer exceptions and at comparisons of
-references. The former represents a divergence due to exceptional
-control flow while the later due to program structure.
-
-%In this work, we present a novel heap initialization and analysis
-%technique which takes inspiration from both GSE and existing heap
-%summarization techniques. The intuition behind our analysis is to
-%construct the heap lazily during symbolic execution but reduce the
-%points of non-determinism in the symbolic execution tree by analyzing
-%each control-flow path only once for any given set of isomorphic
-%heaps. To represent the exact set of feasible concrete heap
-%structures resulting from execution of the control-flow path, we use
-%a heap summary.
-
-\end{comment}
-We represent the heap as a bipartite graph consisting of references and locations.
-Each reference is able to point to multiple locations, where each edge is predicated on constraints over aliasing between references.
-Each location points to a single reference for a given field.
-The use of a bipartiate graph affords two
-key advantages: (i) it allows for a non-recursive definition of objects which enables us to support aliasing, and (ii) it does not require rewriting of the constraints during updates to the heap nor does it introduce auxillary variables into the constraints.
-
-This summary heap algorithm defines how the bipartite graph is updated during lazy initialization.
-Unlike GSE, however, the summary heap algorithm introduces non-determinism in the search only at points of divergence in the control flow graph.
-These points of non-determinism are at field accesses or writes that lead to null-pointer exceptions and at comparisons of references.
-The former represents a divergence due to exceptional control flow while the latter is due to program structure.
-The precise heap representation based on a bipartiate graph coupled with this algorithm to perform updates to the heap enable us to successfully mitigate the state space explosion problem in GSE.
-
-The summary heap algorithm is sound and complete with respect to
-properties that are provable using GSE. This proof is accomplished by
-showing the existence of a bisimulation relation between states in GSE
-and states in the summary heap algorithm. In practical terms, any
-property that can be proved using GSE can also be proved using summary
-heaps, furthermore, any property proved by summary heaps can also be
-proved by GSE. Of course, both require a bound on heap reference
-chains and loops.
+The summary heap algorithm is sound and complete with
+respect to properties that are provable using GSE. This proof is
+accomplished by showing the existence of a bisimulation relation
+between states in GSE and states in the summary heap algorithm. In
+practical terms, any property that can be proved using GSE can also be
+proved using summary heaps, furthermore, any property proved by
+summary heaps can also be proved by GSE. Of course, both require a
+bound on heap reference chains and loops.
 

### 2014-11-13 tex/intro.tex
boo

@@
 
-In this work, in order to effectively represent multiple heaps
-simultaneously in the context of symbolic execution we define a novel
-heap representation and an algorithm to initialize and update the heap
+In this work, to effectively represent multiple heaps simultaneously
+in the context of symbolic execution we define a novel heap
+representation and an algorithm to initialize and update the heap
 on-the-fly. Our summary heap approach supports aliasing, it does not

### 2014-11-13 tex/intro.tex
boo

@@
 due to exceptional control flow while the latter is due to program
-structure. The precise heap representation based on a bipartiate graph
-coupled with this algorithm to perform updates to the heap enable us
-to successfully mitigate the state space explosion problem in GSE.
+structure.
+
+% The precise heap representation based on a bipartiate graph coupled
+%with this algorithm to perform updates to the heap enable us to
+%successfully mitigate the state space explosion problem in GSE.
 
@@
 symbolic execution, the new data structure appears to ameliorate state
-explosion in symbolic execution as hoped. A preliminary implementation in Java
-Pathfinder (JPF), described in this paper, compares the heap summary
-algorithm on a handful of benchmarks, each representing different
-degrees of initialization and branching, to GSE with lazy
-initialization in Symbolic Pathfinder (SPF) and implementation
-lazier\# also in SPF. The results show that in general, that the heap
-summary algorithm improves over other techniques, and in some
+explosion in symbolic execution as hoped. A preliminary implementation
+in Java Pathfinder (JPF) shows that in general, that the heap summary
+algorithm improves over other state-of-the-art techniques, and in some
 instances, the improvement is remarkable: two-orders of magnitude
@@
 heretofore possible as shown in our results.
+
+%, described in this paper, compares the heap summary algorithm on a
+%handful of benchmarks, each representing different degrees of
+%initialization and branching, to GSE with lazy initialization in
+%Symbolic Pathfinder (SPF) and implementation lazier\# also in
+%SPF. The results
 
@@
 
-\item\textbf{-} A summary heap as a bipartite graph that supports aliasing, local value set computation, and heap updates.
+\item\textbf{-} A summary heap as a bipartite graph that supports
+  aliasing and does not require rewriting of constraints.
 
@@
 \end{compactdesc}
-The rest of this paper defines summary heap and its to symbolic
-execution. Following the algorithm definition, the existence proof of
-bisimulation is given with the accompanying corollaries for soundness
-and completeness. This is followed by the implementation in JPF and
-the evaluation. The paper ends with the conclusion and future work.
+
+%The rest of this paper defines summary heap and its to symbolic
+%execution. Following the algorithm definition, the existence proof of
+%bisimulation is given with the accompanying corollaries for soundness
+%and completeness. This is followed by the implementation in JPF and
+%the evaluation. The paper ends with the conclusion and future work.
 

### 2014-11-13 tex/abstract.tex
abstract

@@
+A fundamental challenge of using symbolic execution for software
+analysis has been the treatment of dynamically allocated
+data. Generalized symbolic execution (GSE) techniques have addressed
+this challenge by materializing a concrete heap lazily during field
+accesses.  This approach however, exacerbates the state space
+explosion problem.  In this work, we present a novel symbolic
+execution technique which takes inspiration from the static analysis
+domain and defines a novel bipartite graph representation of the heap
+and a lazy initialization algorithm that, unlike state-of-the-art
+techniques, (a) supports aliasing, (b) does not require rewrite of
+constraints on heap updates, (c) can initialize the heap-on-the-fly,
+and (d) reduces the number of points of non-determinism during the
+search. Our approach is sound and complete with respect to the
+properties provable by GSE. A preliminary evaluation of our
+implementation in Java Pathfinder shows the summary heap enables the
+initialization of larger more complex heaps than previously possible.
+
+\begin{comment}
 A fundamental challenge of using symbolic execution for software
@@
 framework for analyzing Java programs.
+\end{comment}
 

### 2014-11-13 tex/results.tex
tigthening results

@@
 \symtxt{} approach with other state of the art techniques that
-initialize complex data input symbolically. We first describe the tool
-infrastructure we use to implement our approach.
+initialize complex data input symbolically.
 
-\subsection{Tool Support}
-We implement the \symtxt{} as an extension to the symbolic execution
-engine of Java PathFinder(JPF)---Symbolic Pathfinder
+Symbolic Pathfinder
 (SPF)~\cite{visser:ase03,Pasareanu:ISSTA08,pasareanu:ase10,DBLP:journals/ase/PasareanuVBGMR13}. SPF
@@
 equals references-true and references-false rules in~\figref{fig:eqs}
-(iv) linear arithmetic operations on integers and (v) comparison
+(iv) linear arithmetic operations on integers, and (v) comparison
 operations on integers. We are currently working on adding support for
-floating point operations, arrays, and bit-operations.
-
-The default constraints library in SPF requires constraints to be in
-the CNF form, and is unable to support constraints generated by the
-\symtxt{} approach since they contain disjunctions. Transforming the
-constraints generated by the \symtxt{} approach into a CNF form proved
-to be inefficient. We use the \texttt{jConstraints} library that
-provides support to handle arbitrary
+floating point operations, arrays, and bit-operations.  We use the
+\texttt{jConstraints} library that provides support to handle the heap
 constraints~\cite{ase2014-ghilrr,jpf2014-dghirr}. It uses the z3
@@
 changes from one state to another.
+
+%The default constraints library in SPF requires constraints to be in
+%the CNF form, and is unable to support constraints generated by the
+%\symtxt{} approach since they contain disjunctions. Transforming the
+%constraints generated by the \symtxt{} approach into a CNF form
+%proved to be inefficient.
 
@@
 execution for dealing for unbounded complex data input. We empirically
-evaluate \symtxt{} by considering the following research questions:
+evaluate \symtxt{} by considering the following research question:
 
@@
 
-\item {\bf RQ2:} Does \symtxt{} technique enable other back-end
-  approaches that can leverage its output?
+%\item {\bf RQ2:} Does \symtxt{} technique enable other back-end
+%  approaches that can leverage its output?
 \end{description}
@@
 suggests the number of unique paths in the symbolic execution tree.
-
-To perform our study we compile all our artifacts and run the analysis
-on \nsr{the machine.. sthuff about the time bound etc.}.
 

### 2014-11-13 tex/precise.tex
Finished section 3.1

--- 2014-11-12 tex/precise.tex
@@
 \label{sec:precise}
-
-In this section we present the rewrite rules for the $\rsym$ relation. 
-There are three sets of rewrite rules specific to the summary
-heap algorithm: (i) rules to initialize symbolic
-references, (ii) field access and write rules, and (iii) rules
-to check equality and inequality of references. These rules
-form the core of the summary heap algorithm.
+There are three sets of rewrite rules specific to the summary heap
+algorithm: (i) rules to initialize symbolic references, (ii) rules to complete field
+access and field write, and (iii) rules to check equality and
+inequality of references. The other rules are common to both $\rsym$
+and $\rgse$.
 
@@
 
-During initialization of symbolic references in the $\rgse$ relation,
-non-determinitic choices are introduced into the search to
-account for initiaization of the reference to $\mathit{null}$, a new instance of the 
-object, and to any type compatible object previously
-initialized. In contrast, initialization rules for the $\rsym$ relation are 
-defined on the bipartite graph consisting of references and locations,
-and create a single branch containing a summarization of
-all the initializations in a single graph.
+Initialization of uninitialized references in the $\rgse$ relation is
+a non-deterministic choice that creates a heap either for
+the initialization of the reference to $\mathit{null}$, a new instance of
+the object, or to any type compatible object in the input heap (e.g.,
+previously initialized by $\rgse$). In contrast, initialization in the
+$\rsym$ relation creates a single summary heap containing all of the
+possible initialization choices.
 
@@
 
-The initialization rules are invoked whenever an uninitialized field in a
-symbolic reference is accessed. The function $\mathbb{UN}(\cfgnt{L},
-\cfgnt{R}, \cfgnt{r}, \cfgnt{f}) = \{\cfgnt{l}\ ...\}$ returns
-constraint-location pairs in which field $\cfgnt{f}$ is
-uninitialized:
+The initialization rules, \figref{fig:symInit}, are invoked whenever
+an uninitialized field in a symbolic reference is accessed. The
+interaction with the solver in the definition of the rules is denoted
+by $\mathbb{S}(\phi)$ where it returns true if $\phi$ is
+satisfiable. The end rule is active when there is nothing to
+initialize. This condition is determined by the function
+$\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) =
+\{\lp\phi\ \cfgnt{l}\rp\ ...\}$ which returns constraint-location pairs
+where the field $\cfgnt{f}$ is uninitialized.
 \[
@@
 \]
-where $\mathbb{S}(\phi)$ returns true if $\phi$ is
-satisfiable. Intutively, for reference $\cfgnt{r}$, this function constructs
-the set, $\theta$ containing all contraint-location pairs that
-point to field $\cfgnt{f}$ and $\cfgnt{f}$ points to
-$\cfgnt{l}_\mathit{un}$.
+For reference $\cfgnt{r}$, this function constructs the set, $\theta$,
+of constraint location pairs reachable from $\cfgnt{r}$ on the field
+$\cfgnt{f}$ that are valid under the access path from $\cfgnt{r}$.
 
@@
 
-The rewrite rule to initialize a heap in the summary heap algorithm
-is shown in~\figref{fig:symInit}. Given the unitialized set
-$\mathbb{UN}$ for field $f$, the $\mathit{min}_l$ function returns
-$(\phi_x\ \cfgnt{l}_x)$ based on a lexical ordering of uninitialized locations
-in $\Lambda$. The init$_r$ method returns a new input reference $\cfgnt{r}_f$,
-while the fresh$_f$ returns a new location of type $C$. The set $\rho$
-contains the set of reference-location pairs, $(\cfgnt{r}_a\ \cfgnt{l}_a)$, the
-field being initialized may alias. A pair $(\cfgnt{r}_a\ \cfgnt{l}_a)$ is contained
-in the set $ \rho $ if the following conditions hold: (i) $\cfgnt{r}_a$ is
-part of the input references initialized in the summary heap, (ii)
-$\cfgnt{r}_a$ is in the pre-image of $\cfgnt{l}_a$, and (iii) the type 
-of $\cfgnt{l}_a$ is the same as the type of the field being initialized.
+In~\figref{fig:symInit}, given the unitialized set $\mathbb{UN}$ for
+field $f$, the $\mathit{min}_l$ function returns
+$(\phi_x\ \cfgnt{l}_x)$ based on a lexicographical ordering of
+uninitialized locations in $\Lambda$ to make initialization
+deterministic (the same heap is always initialized in the same
+way). 
+%The $\mathrm{fresh}_\cfgnt{l}(\cfgnt{C})$ call returns a new location of type $C$. 
+The set $\rho$ contains the set of
+reference-location pairs from the input heap that are potential
+alias. Minimizing over the set of references in the pre-image ensures
+that any pair in $\rho$ is the reference $\cfgnt{r}_a$ that birthed
+the location $\cfgnt{l}_a$ in some prior initialization (i.e., it was
+$\cfgnt{r}_f$ and $\cfgnt{l}_f$ at one time). Aliasing constraint
+in the new summary heap reason over these original creators; otherwise aliasing and local value set
+computation breaks down.  The reference partitions with their
+monotonicity make this determination possible.
 
-There are three constraint-location pair sets that correspond to the
-non-deterministic choices in GSE: (a) $\theta_\mathit{null}$ contains
-a constraint $\cfgnt{r}_f = \cfgnt{r}_\mathit{null}$ paired with the location
-$\cfgnt{l}_\mathit{null}$, (b) \sjp{something is not right in this choice}
-$\theta_\mathit{new}$ creates a pair with a
-constraint representing the fact that $\cfgnt{r}_f$ is not null and it does 
-not alias any reference in set $\rho$ under and a newly created location 
-$\cfgnt{l}_f$, and (c) 
-$\theta_\mathit{alias}$ where for each element in the set $(\cfgnt{r}_a\ \cfgnt{l}_a)
+There are three sets correspond to the non-deterministic choices in
+GSE with a fourth that preserves the pre-initialized heap structure
+(the constraints in each preserve the access path to the location):
+(i) $\theta_\mathit{null}$ asserts the condition under which
+$\cfgnt{l}_\mathit{null}$ is possible (any time the solver assigns
+values to reference variables in such a way that $\cfgnt{r}_f =
+\cfgnt{r}_\mathit{null}$ holds as does access path $\phi_x$). (ii)
+$\theta_\mathit{new}$, meaning $\cfgnt{r}_f$ refers to the fresh
+location, occurs when $\cfgnt{r}_f$ is not new or any other alias. (iii) any member of $\theta_\mathit{alias}$ restricts $\cfgnt{r}_f$ to
+only alias one member of $\rho$ and not alias any member of $\rho$
+that was initialized earlier than the current choice (a later
+initialization may indeed alias the current alias choice in a valid
+heap but the current choice cannot alias both the choice and a
+previous initialization). And (iv) $\theta_\mathit{orig}$  implements conditional initialization to preserve the
+original heap structure. This property is needed for the bisumulation. 
+These sets are added into the heap on the field after initializing the fields in the new location to $\cfgnt{l}_\mathit{un}$.
+
+\begin{comment} where for each element in the set $(\cfgnt{r}_a\ \cfgnt{l}_a)
 \in \rho$ it creates a constraint stating that $\cfgnt{r}_f$ is not null, points to
@@
 reference $\cfgnt{r}_f$ in the summary heap.
+\end{comment}
 
@@
 graph in~\figref{fig:initHeap}(a) represents the initial heap. The
-references with the superscript $s$ indicates that it is a local
-reference. In~\figref{fig:initHeap} $\cfgnt{r}_0^s$ represents a local
-reference for the $\cfgt{this}$ reference which has two fields $x$
+references with the superscript $s$ indicates that it is a reference from the stack partition.
+ In~\figref{fig:initHeap} $\cfgnt{r}_0^s$ represents a stack
+reference for the $\cfgt{this}$ variable which has two fields $x$
 and $y$ of the same type; reference $\cfgnt{r}_0^s$ points to location
@@
 
-The access on $\cfgnt{l}_0.x$ creates a new input reference $\cfgnt{r}_1^i$ in the
+The access on $\cfgnt{l}_0.x$ creates a new input heap reference $\cfgnt{r}_1^i$ in the
 summary heap shown in~\figref{fig:initHeap}(b). The reference $\cfgnt{r}_1^1$

### 2014-11-13 tex/conclusion.tex
useless commit message

@@
 
-Another feature we would like to add is support for test case generation, which is traditionally a key advantage of symbolic execution techniques.
-Under the current rules, it is difficult to extract test cases because the heap may be destructively altered during field writes.
-A simple remedy would be to maintain an explicit input heap in addition to the actual heap which is mutated as the program progresses.
+\begin{comment}
+Another feature we would like to add is support for test case
+generation, which is traditionally a key advantage of symbolic
+execution techniques. Under the current rules, it is difficult to
+extract test cases because the heap may be destructively altered
+during field writes. A simple remedy would be to maintain an explicit
+input heap in addition to the actual heap which is mutated as the
+program progresses.
+\end{comment}
 

### 2014-11-13 tex/evaluation.tex
useless commit message

--- 2014-11-13 tex/evaluation.tex
@@
   \centering
-  \begin{tabular}{| c | c | r | r | r | r | r | r | r | r | r |}
+  \scalebox{0.88}{\begin{tabular}{| c | c | r | r | r | r | r | r | r | r | r |}
   \hline
@@
     \hline
-  \end{tabular}
-  \caption{Test results.}
+  \end{tabular}}
+  \caption{Comparing the efficiency of the summary heap appraoch to GSE and Lazier\# algorithms.}
   \label{tab:results}
@@
 
-\subsection{Analysis}
-The results of the experiments are presented in Table \ref{tab:results}.
-The rows contain to individual $k$-bounded test runs for each of the evaluated programs.
-The columns show the run time, state count and path count for each of the three algorithms tested.
-The headings \gsetxt{}, L\#, and SL correspond to the Generalized Symblic Execution, lazier\#, and \symtxt{} algorithms, respectively.
-Table entries containing - correspond to test runs that exceeded the allotted time bounds.
+%\subsection{Analysis}
 
-In most tests, run times strongly favor \symtxt{}, especially for nontrivial k-values.
-Performance improvement ranges from 4.8x for BinarySearchTree at $k$=3, to 118x for LinkedList at $k$=6.
-In fact, a number of test cases can be efficiently completed using \symtxt{} for k-bounds that are not practical to be attempted with \gsetxt{} or lazier\#, including the BinarySearchTree for $k$=4 and LinkedList for $k$=8.
-Some of this discrepancy may be accounted for by the fact that \symtxt{} is equipped for incremental solving, however, during informal testing with the incremental solver turned off, \symtxt{} usually performed better than \gsetxt and lazier\#, especially in test runs with high k-bounds.
+The results of the experiments are presented in Table
+\ref{tab:results}. The rows contain to individual $k$-bounded test
+runs for each of the evaluated programs. The columns show the total
+walk clock time in seconds, states explored, and paths generated for
+each of the algorithms. The headings \gsetxt{}, L\#, and SL correspond
+to the Generalized Symblic Execution, lazier\#, and \symtxt{}
+algorithms, respectively. Note that we do no present the results for
+lazier algorithm since they are almost identical to that of lazier\#
+for our examples. Table entries containing - correspond to test runs
+that exceeded the allotted time bounds. Each trial is time bounded to
+10 mins.
 
-Path counts likewise substantially favor \symtxt{}.
-In agreement with the theoretical results, the number of paths explored by \symtxt{} is strictly less than or equal the number of paths explored by \gsetxt{} for all test cases.
-More surprisingly, \symtxt{} path growth appears to be sub-exponential in $k$ for the LinkedList program.
+In most tests, run times strongly favor \symtxt{}, especially for
+large $k$-values. Performance improvement ranges from $4.8x$ for
+BinarySearchTree at $k$=3, to $118x$ for LinkedList at $k$=6. In fact,
+for certain $k$-bounds a number of experiments completed exploration
+using \symtxt{} in a few seconds whereas \gsetxt{} or lazier\# were
+unable to do, e.g., BinarySearchTree for $k$=4 and LinkedList for
+$k$=8. These results demonstrate the potential of using \symtxt{} as
+an approach to handle data input of complex types. The lower runtimes
+show that we can prove properties using \symtxt{} faster compared to
+\gsetxt{}.
 
-Curiously, the pattern established with run-times and path counts does not hold true for state counts.
-State counts can vary between algorithms, because states in JPF represent points of nondeterminism, and each algorithm differs in this regard.
-For example, \gsetxt{} has additional points of nondeterminism during field reads, but in contrast address compares are completely deterministic.
-Thus, in example programs with large numbers address compares, such as TreeMap, state counts for lazier\# and \symtxt{} may exceed those for \gsetxt{}.
-Despite this, in practice this is often mitigated by the fact that \symtxt{} can dispatch address compares without consulting the constraint solver.
+% Some of this discrepancy may be accounted for by the fact that
+%\symtxt{} is equipped for incremental solving, however, during
+%informal testing with the incremental solver turned off, \symtxt{}
+%usually performed better than \gsetxt{} and lazier\#, especially in
+%test runs with high k-bounds.
 
-In summary, it appears that the benefits of avoiding initialization-based nondeterminism more than outweigh the increased complexity in the constraints.
-In fact, \symtxt{} can analyze certain types of programs with orders of magnitude greater efficiency than with \gsetxt{} or lazier#, while covering exactly the same test cases with zero loss of precision.
+Path counts likewise substantially favor \symtxt{}. The number of
+paths explored by \symtxt{} is strictly less than or equal the number
+of paths explored by \gsetxt{} for all test cases. We can use this
+result to do more efficient test case generation. From a path
+generated we can use the solutions provided by the constraint solver
+to instantiate a set of concrete heaps to provide as test input. These
+can provide a smaller test suite to achieve control-flow path coverage
+compared to GSE and Lazier\#.
+
+%Interestingly, \symtxt{} path growth appears
+%to be sub-exponential in $k$ for the LinkedList program.
+
+Curiously, the pattern established with run-times and path counts does
+not hold true for state counts. State counts can vary between
+algorithms, because states in JPF represent points of nondeterminism,
+and each algorithm differs in this regard. For example, \gsetxt{} has
+additional points of nondeterminism during field reads, but in
+contrast references compares are completely deterministic. Thus, in
+example programs with large numbers reference compares, such as
+TreeMap, state counts for lazier\# and \symtxt{} may exceed those for
+\gsetxt{}. The larger state count, however, does not contribute to the
+runtime of the technique.
+
+% Despite this, in practice this is often mitigated by the
+%fact that \symtxt{} can dispatch address compares without consulting
+%the constraint solver.
+
+In summary, it appears that the benefits of avoiding
+initialization-based nondeterminism more than outweigh the increased
+complexity in the constraints due to the advances made in SMT
+solvers. In fact, \symtxt{} can analyze certain types of programs with
+orders of magnitude greater efficiency than with \gsetxt{} or
+lazier\#, while covering exactly the same control flow paths.

### 2014-11-13 tex/abstract.tex
Proofreading, fixing typos.

@@
 implementation in Java Pathfinder shows the summary heap enables the
-initialization of larger more complex heaps than previously possible.
+initialization of larger, more complex heaps than previously possible.
 

### 2014-11-13 tex/intro.tex
boo
Proofreading, fixing typos.

@@
 previous attempts, however, are unable to handle aliasing in heaps due
-to a recursive definition of objects~\cite{..}, while others require a
+to a recursive definition of objects~\cite{Xie:2005}, while others require a
 set of heaps as input and are unable to initialize heaps
-on-the-fly~\cite{..}.  As is typical in static analysis, over
-approximation of the heap representations alleviates some of the
-limitations but also leads to false positives. Also, update to heaps
-require a rewrite of the constraint system making it prohitive for use
+on-the-fly~\cite{Dillig:2011,Tillmann:2008}.  As is typical in static analysis, over
+approximation of the heap representations alleviates some of these
+limitations but also leads to false positives. Also, updates to heaps
+require a rewrite of the constraint system making it prohibtive for use
 in the context of symbolic execution.
@@
 representation and an algorithm to initialize and update the heap
-on-the-fly. Our summary heap approach supports aliasing, it does not
-require constraint rewriting on heap updates, and it reduces the
+on-the-fly. Our summary heap approach supports aliasing, does not
+require constraint rewriting on heap updates, and reduces
 non-determinism in the search space during symbolic execution.
@@
 references. Each location points to a single reference for a given
-field. The use of a bipartiate graph affords two key advantages: (i)
+field. The use of a bipartite graph affords two key advantages: (i)
 it allows for a non-recursive definition of objects which enables us
-to support aliasing, and (ii) it does not require rewriting of the
-constraints during updates to the heap nor does it introduce auxillary
-variables into the constraints.
+to support aliasing, and (ii) it does not introduce auxiliary variables or 
+require rewriting non-local constraints during updates to the heap.
 
-This summary heap algorithm defines how the bipartite graph is updated
+The summary heap algorithm defines how the bipartite graph is updated
 during lazy initialization. Unlike GSE, however, the summary heap
@@
 divergence in the control flow graph. These points of non-determinism
-are at field accesses or writes that lead to null-pointer exceptions
+are at field accesses that lead to null-pointer exceptions
 and at comparisons of references. The former represents a divergence
@@
 
-Aside from the novelty of the heap summary and its application to
-symbolic execution, the new data structure appears to ameliorate state
-explosion in symbolic execution as hoped. A preliminary implementation
-in Java Pathfinder (JPF) shows that in general, that the heap summary
-algorithm improves over other state-of-the-art techniques, and in some
-instances, the improvement is remarkable: two-orders of magnitude
-reduction in running time. More critically though, the heap summary
-enables the initialization of larger more complex heaps than
-heretofore possible as shown in our results.
+%Aside from the novelty of the heap summary and its application to
+%symbolic execution, the new data structure appears to ameliorate
+%state explosion in symbolic execution as hoped.
+
+A preliminary implementation in Java Pathfinder (JPF) shows that in
+general, that the heap summary algorithm improves over other
+state-of-the-art techniques, and in some instances, the improvement is
+remarkable: two-orders of magnitude reduction in running time. More
+critically though, the heap summary enables the initialization of
+larger more complex heaps than heretofore possible as shown in our
+results.
 
@@
 
-\item\textbf{-} A summary heap as a bipartite graph that supports
-  aliasing and does not require rewriting of constraints.
+\item\textbf{-} A symbolic summary heap representing
+sets of concrete heaps without overapproximation or restricting aliasing.
+% supports aliasing, and and allows strong updates without auxiliary variables 
+% or constraint rewriting.
 
@@
 
-\item\textbf{-} A summary heap algorithm to initialize, summarize, and
-  update the bipartiate graphs during symbolic execution.
+\item\textbf{-} A algorithm to initialize, summarize, and
+  update summary heaps during symbolic execution, without mutating 
+  constraints or introducing auxiliary variables.
 
@@
 
-\item\textbf{-} A proof of concept implementation and small empirical study to demonstrate the scability of the heap summary approach
+\item\textbf{-} A proof-of-concept implementation and small empirical study 
+demonstrating the scalability of the heap summary approach
   compared to other GSE approaches.

### 2014-11-13 tex/intro.tex
Adjusted the contributions section to better highlight the strengths of our approach.

@@
 
-\item\textbf{-} A symbolic summary heap representing
-sets of concrete heaps without overapproximation or restricting aliasing.
-% supports aliasing, and and allows strong updates without auxiliary variables 
-% or constraint rewriting.
+%\item\textbf{-} A summary heap that represents sets of concrete heaps
+% without approximation or morphological restrictions.
 
-% to handle alias and efficient updates of constraints.
+\item\textbf{-} A non-approximate, morphologically arbitrary, and efficient 
+summary heap representation.
 
-\item\textbf{-} A algorithm to initialize, summarize, and
-  update summary heaps during symbolic execution, without mutating 
-  constraints or introducing auxiliary variables.
+\item\textbf{-} An algorithm to dynamically initialize, summarize, and
+  update the summary heap during symbolic execution.
 
-\item\textbf{-} A proof of the existence of a bisimulation relation to establish
-  that the heap summary approach is sound and complete with respect to
+\item\textbf{-} A bisimulation proof establishing the soundness and 
+completeness of the heap summary approach with respect to
 properties provable by GSE.
@@
 \end{compactdesc}
+
+%\begin{compactdesc}
+%
+%\item\textbf{-} A summary heap as a bipartite graph that supports
+%  aliasing and does not require rewriting of constraints.
+%
+%% to handle alias and efficient updates of constraints.
+%
+%\item\textbf{-} A summary heap algorithm to initialize, summarize, and
+%  update the bipartiate graphs during symbolic execution.
+%
+%\item\textbf{-} A proof of the existence of a bisimulation relation to establish
+%  that the heap summary approach is sound and complete with respect to
+%  properties provable by GSE.
+%
+%\item\textbf{-} A proof of concept implementation and small empirical study to demonstrate the scability of the heap summary approach
+%  compared to other GSE approaches.
+%
+%\end{compactdesc}
 

### 2014-11-13 tex/intro.tex
minor changes to intro

@@
 constraints on the symbolic inputs to create a \emph{ path condition}.
-The set of path conditions computed by
+The path conditions computed by
 symbolic execution characterize the observed program execution
@@
 approximation of the heap representations alleviates some of these
-limitations but also leads to false positives. Also, updates to heaps
+limitations but also leads to infeasible heaps. Also, heap updates
 require a rewrite of the constraint system making it prohibtive for use
@@
 In this work, to effectively represent multiple heaps simultaneously
-in the context of symbolic execution we define a novel heap
+in the context of symbolic execution, we define a novel heap
 representation and an algorithm to initialize and update the heap
@@
 to support aliasing, and (ii) it does not introduce auxiliary variables or 
-require rewriting non-local constraints during updates to the heap.
+require rewriting of non-local constraints during updates to the heap.
 
@@
 
-The summary heap algorithm is sound and complete with
+This combination of summary heap and lazy initialization
+enable us to improve the efficiency of symbolic execution of heap
+manipulating programs over state-of-the-art techniques.
+Furthermore, the summary heap algorithm is sound and complete with
 respect to properties that are provable using GSE. This proof is
@@
 practical terms, any property that can be proved using GSE can also be
-proved using summary heaps, furthermore, any property proved by
+proved using summary heaps, and, any property proved by
 summary heaps can also be proved by GSE. Of course, both require a
@@
 critically though, the heap summary enables the initialization of
-larger more complex heaps than heretofore possible as shown in our
+larger more complex heaps than previously possible as shown in our
 results.
@@
 
-\item\textbf{-} A proof-of-concept implementation and small empirical study 
-demonstrating the scalability of the heap summary approach
+\item\textbf{-} A proof-of-concept implementation and empirical study 
+demonstrating the scalability of the summary heap approach
 compared to other GSE approaches.

### 2014-11-13 tex/abstract.tex
Changed one letter

@@
 and a lazy initialization algorithm that, unlike state-of-the-art
-techniques, (a) supports aliasing, (b) does not require rewrite of
-constraints on heap updates, (c) can initialize the heap-on-the-fly,
-and (d) reduces the number of points of non-determinism during the
+techniques, (i) supports aliasing, (ii) does not require rewrite of
+constraints on heap updates, (iii) can initialize the heap-on-the-fly,
+and (iv) reduce the number of points of non-determinism during the
 search. Our approach is sound and complete with respect to the

### 2014-11-13 tex/intro.tex
Commented out explanation of sound and complete--not needed for this audience

@@
 respect to properties that are provable using GSE. This proof is
-accomplished by showing the existence of a bisimulation relation
-between states in GSE and states in the summary heap algorithm. In
+accomplished by showing the existence of a bisimulation
+between states in GSE and states in the summary heap algorithm. 
+\begin{comment}
+In
 practical terms, any property that can be proved using GSE can also be
@@
 bound on heap reference chains and loops.
+\end{comment}
 
@@
 A preliminary implementation in Java Pathfinder (JPF) shows that in
-general, that the heap summary algorithm improves over other
+general, the heap summary algorithm improves over other
 state-of-the-art techniques, and in some instances, the improvement is

### 2014-11-13 tex/heap.tex
Proofreading, fixing typos.
Minor edits and redundant text removal

@@
 group membership and compute value sets using entirely non-recursive
-local look up. Additionally, updates on the heap do not require
-rewriting the path condition or any constraints in the summary heap.
+local lookup. Additionally, updates on the heap do not require
+rewriting the path condition.
 
@@
 rewrite rules that are invariant and important to the correctness
-proofs presented in \secref{sec:bisim}: \emph{reference partitions},
+proofs in \secref{sec:bisim}: \emph{reference partitions},
 \emph{immutability}, \emph{determinism}, \emph{type
@@
 
-\emph{Reference partitions} are new references drawn from
+\emph{Reference partitions}: new references drawn from
   three distinct partitions (i) $\mathrm{init}_\cfgnt{r}()$ for references for the \emph{input heap}, (ii) $\mathrm{fresh}_\cfgnt{r}()$ for references for \emph{auxiliary literals}, and
-  (iii) $\mathrm{stack}_\cfgnt{r}()$ for references for the \emph{stack literals} in the expressions and
+  (iii) $\mathrm{stack}_\cfgnt{r}()$ for references for \emph{stack literals} in the expressions and
   continuations. The references strictly increase in value on each
@@
 \item[Input heap:] these references have two
-  interpretations: one as a literal and another as a variable. First,
-  an input heap reference is a literal, and that literal is a node in
-  the summary heap. Second, an input heap reference is a variable, and
-  that variable is a term in any number of constraints that label
+  interpretations: one as a literal and another as a variable. As a literal it is a node in
+  the summary heap. As a variable it is a term in any number of constraints that label
   edges in the summary heap. Only input heap references and the
@@
 
-\emph{Determinism} means that a reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point multiple locations simultaneously.
+\emph{Determinism} means that a reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously. In the definition $\cfgnt{L}^\leftarrow$ is the pre-image of the location map.
 $$
@@
 $$
-$\cfgnt{L}^\leftarrow$ is the pre-image of the location
-map. Informally, any two constraint location pairs connected to a
+Informally, any two constraint location pairs connected to a
 common reference form a contradiction: only one can be true in any
-satisfying assignment. The property means that a satisfying assignment
+satisfying assignment. The property ensures that any satisfying assignment
 resolving aliasing relationships results in a deterministic heap: a
-field access returns a single location.
+field access returns a single location under that assignment.
 
@@
 \item $\lp\phi^\prime\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r}^\prime)$; and
-\item $\phi$ and $\phi^\prime$ hold in aliasing assignments from the solver.
+\item $\phi$ and $\phi^\prime$ hold in the aliasing assignments from the solver.
 \end{compactitem}
@@
 
-Other more complex rules such as the one to create a new instance of a
-class define constraints on the rewrites and more complex
+Other more complex rules, such as one to create a new instance of a
+class, define constraints on the rewrites and more complex
 transformations on the heap.

### 2014-11-13 tex/related.tex
updates to related work

@@
 on symbolic execution, first introduced in the 1970's by
-Clarke~\cite{Clarke:76} and King~\cite{King:76}.  These projects have
-pursued three primary research directions to enhance traditional
-symbolic execution: (1)~to improve its
-effectiveness~\cite{Godefroid:PLDI05,Sen:FSE05,CadarEngler05EXE,KiasanKunit,Pasareanu:2011};
-(2)~to improve its
-efficiency~\cite{AnandETAL2009AbsSymExe,KhurshidSuen2005AbsSymExe,Godefroid:POPL07,Inkumsah:2008,ChangPhD10DataFlowSymbolicExecution,Santelices:ISSTA10,Visser:2012};
-and (3)~to improve its
-applicability~\cite{Person:FSE08,KhurshidETAL05RepairingStructurally,CsallnerETAL08DySy,SeoETAL06EnergyConsumptionFrameworkDistributedJava,Geldenhuys:2012,Ma:2011}. Handling
-unbounded data input of complex type has continued to be a challenge
-for symbolic execution.  Generalized symbolic execution \cite{GSE03}
-with lazy initialization set the path to materializing fields
-concretely. Subsequent improvements to the method
-\cite{Deng:2006,Deng:2007} to reduce path explosion by delaying path
-splitting over aliasing choices for as long as possible. However,
-since all of the above methods introduce nondeterminism during field
-reads and writes, they all contribute to path explosion to some
-extent.
+Clarke~\cite{Clarke:76} and King~\cite{King:76}. Initial work on symbolic
+execution largely focused on checking properties of program with
+primitive types. Several recent projects generalized the core
+idea of symbolic execution which enabled it to be applied to
+programs with more general types, including references and 
+arrays~\cite{GSE03,Godefroid:PLDI05,Sen:FSE05,CadarEngler05EXE,KiasanKunit}.
+Our work leverages the core idea in generalized symbolic execution
+with lazy initialization to construct the heap on-the-fly during symbolic
+execution, but avoids the nondeterminism introduced by GSE by
+constructing a summary heap and will generally create fewer paths
+than GSE techniques.
+
+%These projects have
+%pursued three primary research directions to enhance traditional
+%symbolic execution: (1)~to improve its
+%effectiveness~\cite{Godefroid:PLDI05,Sen:FSE05,CadarEngler05EXE,KiasanKunit,Pasareanu:2011};
+%(2)~to improve its
+%efficiency~\cite{AnandETAL2009AbsSymExe,KhurshidSuen2005AbsSymExe,Godefroid:POPL07,Inkumsah:2008,ChangPhD10DataFlowSymbolicExecution,Santelices:ISSTA10,Visser:2012};
+%and (3)~to improve its
+%applicability~\cite{Person:FSE08,KhurshidETAL05RepairingStructurally,CsallnerETAL08DySy,SeoETAL06EnergyConsumptionFrameworkDistributedJava,Geldenhuys:2012,Ma:2011}.
+%analyzing programs containing complex data structure with unbounded
+%domains continues to be challenging
+%for symbolic execution techniques.  Generalized symbolic execution \cite{GSE03}
+%with lazy initialization set the path to materializing fields
+%concretely. Subsequent improvements to the method
+%\cite{Deng:2006,Deng:2007} to reduce path explosion by delaying path
+%splitting over aliasing choices for as long as possible. However,
+%since all of the above methods introduce nondeterminism during field
+%reads and writes, they all contribute to path explosion to some
+%extent.
 
@@
 
-A number of static analysis techniques have been proposed that have
-some ability to reason about input heap structures. One notable static
-analysis method that is closely related to ours is the procedure
-summaries proposed by Isil and Tomas Dillig \cite{Dillig:2011}.  While
-their method has improved path sensitivity over standard static
+A number of static analysis techniques have been proposed
+to support reasoning about input heap structures~\cite{}. The technique
+most closely related to (and which served as inspiration for) our approach
+is the procedure summary proposed by Dillig et al. to support modular
+reasoning~\cite{Dillig:2011}.  While
+their method improves path sensitivity over standard static
 analysis methods, it remains limited by a statically-generated
-symbolic input heap, and cannot adapt to path-sensitive heap
+symbolic input heap and it cannot adapt to path-sensitive heap
 properties of the input heap.
@@
 
-As in our representation, other methods have been proposed that model
-references using sets of guarded locations
-\cite{Xie:2005,Cherem:2007,Dillig:2011,Sen:2014}. These sets,
+Other techniques have been proposed to model
+references using sets of guarded
+locations~\cite{Xie:2005,Cherem:2007,Dillig:2011,Sen:2014}. These sets,
 sometimes known as value sets or value summaries, allow multiple heaps
@@
 than afforded by shape analysis. However, some of these previous
-attempts \cite{Xie:2005,Cherem:2007} utilize non-local recursive
-definitions for objects. The impact of using recursive definitions for
-objects is two-fold. First, these techniques must use approximations
+attempts~\cite{Xie:2005,Cherem:2007} utilize non-local recursive
+definitions for objects. The impact of such an approach is two-fold. 
+First, these techniques must use approximations
 to resolve reference inequalities, resulting in false positives in the
@@
 isomorphic heap structures in order to avoid exploring redundant
-paths. Examples of such methods include Korat, XXX, and YYY. These
-methods are generally focused on the morphology of the heap alone, in
-isolation from the external constraint problems encountered during
-program execution. As such, these works are largely orthogonal to the
-methods presented here, though some of them may possibly be
-complimentary.
+paths. Examples of such methods include Korat~\cite{Milicevic:2007},
+XXX, and YYY. These
+methods are generally focused on the morphology of the heap apart
+from the external constraint problems encountered during
+program execution, and as such, are largely orthogonal to this work.

### 2014-11-13 tex/abstract.tex
some minor tweaks to the abstract

--- 2014-11-13 tex/abstract.tex
@@
 this challenge by materializing a concrete heap lazily during field
-accesses.  This approach however, exacerbates the state space
-explosion problem.  In this work, we present a novel symbolic
-execution technique which takes inspiration from the static analysis
-domain and defines a novel bipartite graph representation of the heap
-and a lazy initialization algorithm that, unlike state-of-the-art
-techniques, (a) supports aliasing, (b) does not require rewrite of
-constraints on heap updates, (c) can initialize the heap-on-the-fly,
-and (d) reduces the number of points of non-determinism during the
-search. Our approach is sound and complete with respect to the
+accesses.  These techniques however, exacerbate the path explosion
+problem.  In this work, we present a heap summary approach which takes
+inspiration from the static analysis domain and defines a bipartiate
+graph to encode multiple heaps in single representation, which, unlike
+state-of-the-art static analysis approaches, (i) supports aliasing,
+(ii) does not require rewrite of constraints on heap updates, and
+(iii) can initialize the heap-on-the-fly. We also define a heap
+summary algorithm to perform heap updates during symbolic execution on
+this representation in order to mitigate the path explosion problem in
+GSE techniques. Our approach is sound and complete with respect to the
 properties provable by GSE. A preliminary evaluation of our
-implementation in Java Pathfinder shows the summary heap enables the
-initialization of larger more complex heaps than previously possible.
+implementation in Java Pathfinder framework shows the summary heap
+enables the initialization of larger, more complex heaps than
+previously possible.
 

### 2014-11-13 tex/abstract.tex
some minor tweaks to the abstract

@@
 accesses.  These techniques however, exacerbate the path explosion
-problem.  In this work, we present a heap summary approach which takes
+problem.  In this work, we present a summary heap approach which takes
 inspiration from the static analysis domain and defines a bipartiate
@@
 (ii) does not require rewrite of constraints on heap updates, and
-(iii) can initialize the heap-on-the-fly. We also define a heap
-summary algorithm to perform heap updates during symbolic execution on
+(iii) can initialize the heap-on-the-fly. We also define a summary
+heap algorithm to perform heap updates during symbolic execution on
 this representation in order to mitigate the path explosion problem in

### 2014-11-13 tex/intro.tex
blah blah

@@
 software testing and analysis techniques. Symbolic execution
-systematically explores the program execution space using
-symbolic input values, and for each explored path, computes
-constraints on the symbolic inputs to create a \emph{ path condition}.
-The path conditions computed by
-symbolic execution characterize the observed program execution
-behaviours and have been used as an enabling technology for various
-applications, e.g., regression
+systematically explores the program execution space using symbolic
+input values, and for each explored path, computes constraints on the
+symbolic inputs to create a \emph{ path condition}.  The path
+conditions computed by symbolic execution characterize the observed
+program execution behaviours and have been used as an enabling
+technology for various applications, e.g., regression
 analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
@@
 Initial work on symbolic execution largely focused on checking
-properties of programs with primitive types~\cite{clarke76TSE,King:76}.
-%, e.g., integers and booleans 
-%Despite recent advances
-%in constraint solving technologies, improvements in
-%raw computing power, and advances in reduction
-%and abstraction techniques~\cite{AnandETAL2009AbsSymExe,Godefroid:POPL07}
-%symbolic execution of programs of modest size containing only
-%primitive types, remains challenging
-%because of the large number of execution paths generated
-%during symbolic analysis. 
-With the advent of object-oriented languages,
-% e.g., Java and C$++$, 
-recent work has generalized the core ideas of symbolic execution to enable 
-analysis of programs containing complex data structures with unbounded 
-domains, i.e., data stored on the heap~\cite{Kiasan06,Kiasan07,GSE03}.  
-These \emph{Generalized Symbolic Execution} (GSE) techniques construct the 
-heap in a lazy manner, deferring
-materialization of objects on the concrete heap until they are needed
-for the analysis to proceed. The materilization 
-%accounts for various heap configurations, 
-creates additional non-deterministic choice points in the symbolic
-execution tree by representing the feasible heap configurations as (i)
-null, (ii) an instance of a new reference of a compatible class, and (iii)
+properties of programs with primitive
+types~\cite{clarke76TSE,King:76}.  With the advent of object-oriented
+languages, recent work has generalized the core ideas of symbolic
+execution to enable analysis of programs containing complex data
+structures with unbounded domains, i.e., data stored on the
+heap~\cite{Kiasan06,Kiasan07,GSE03}.  These \emph{Generalized Symbolic
+  Execution} (GSE) techniques construct the heap in a lazy manner,
+deferring materialization of objects on the concrete heap until they
+are needed for the analysis to proceed. The materilization creates
+additional non-deterministic choice points in the symbolic execution
+tree by representing the feasible heap configurations as (i) null,
+(ii) an instance of a new reference of a compatible class, and (iii)
 an alias to a previously initialized symbolic reference.  Symbolic
-execution then follows concrete program semantics for materialized heap
-locations. Although this approach enables the analysis of heap
+execution then follows concrete program semantics for materialized
+heap locations. Although this approach enables the analysis of heap
 manipulating programs, a large number of feasible concrete heap
-configurations are created leading to state space explosion.
+configurations are created leading to a path explosion.
 
-%  resulting in a large number of feasible concrete heap
-%configurations, and as a result, a large number of points of
-%non-determinism to be analyzed.
-%, further exacerbating the state space
-%explosion problem.
-
-The goal of this work is to mitigate the state space explosion problem
-in GSE by grouping multiple heaps together and only partitioning the
-heaps at points of divergence in the control flow graph. Our
-inspiration is found in the domain of static analysis that uses sets
-of constraints over heap locations to encode multiple heaps in a
-single representation. These sets, sometimes known as \emph{value
-  sets} or \emph{value summaries}, allow multiple heaps to be
-represented simultaneously with a higher degree of precision than
-afforded by traditional techniques for shape analysis. Some of these
-previous attempts, however, are unable to handle aliasing in heaps due
-to a recursive definition of objects~\cite{Xie:2005}, while others require a
-set of heaps as input and are unable to initialize heaps
-on-the-fly~\cite{Dillig:2011,Tillmann:2008}.  As is typical in static analysis, over
-approximation of the heap representations alleviates some of these
-limitations but also leads to infeasible heaps. Also, heap updates
-require a rewrite of the constraint system making it prohibtive for use
-in the context of symbolic execution.
+The goal of this work is to mitigate the path explosion problem in GSE
+by grouping multiple heaps together and only partitioning the heaps at
+points of divergence in the control flow graph. Our inspiration is
+found in the domain of static analysis that uses sets of constraints
+over heap locations to encode multiple heaps in a single
+representation. These sets, sometimes known as \emph{value sets} or
+\emph{value summaries}, allow multiple heaps to be represented
+simultaneously with a higher degree of precision than afforded by
+traditional techniques for shape analysis. Some of these previous
+attempts, however, are unable to handle aliasing in heaps due to a
+recursive definition of objects~\cite{Xie:2005}, while others require
+a set of heaps as input and are unable to initialize heaps
+on-the-fly~\cite{Dillig:2011,Tillmann:2008}.  As is typical in static
+analysis, over approximation of the heap representations alleviates
+some of these limitations but often leads to infeasible heaps. Also,
+heap updates require a rewrite of the constraint system making it
+prohibtive for use in the context of symbolic execution.
 

### 2014-11-13 tex/precise.tex
At VS in my edits

@@
 a non-deterministic choice that creates a heap either for
-the initialization of the reference to $\mathit{null}$, a new instance of
+the initialization of the reference to null, a new instance of
 the object, or to any type compatible object in the input heap (e.g.,
@@
 \]
-For reference $\cfgnt{r}$, this function constructs the set, $\theta$,
-of constraint location pairs reachable from $\cfgnt{r}$ on the field
-$\cfgnt{f}$ that are valid under the access path from $\cfgnt{r}$.
+A pair in the set means the field in the location maps to a reference
+that then points to $\cfgnt{l}_\mathit{un}$, and that the path to that
+location is feasible on some aliasing assignment.
 
@@
 
-In~\figref{fig:symInit}, given the unitialized set $\mathbb{UN}$ for
+In~\figref{fig:symInit}, given the unitialized set $\Lambda$ for
 field $f$, the $\mathit{min}_l$ function returns
@@
 uninitialized locations in $\Lambda$ to make initialization
-deterministic (the same heap is always initialized in the same
-way). 
+deterministic (i.e., the same heap is always initialized in the same
+way as order determines how many aliases are available in the input heap at any given point in initialization). 
 %The $\mathrm{fresh}_\cfgnt{l}(\cfgnt{C})$ call returns a new location of type $C$. 
@@
 reference-location pairs from the input heap that are potential
-alias. Minimizing over the set of references in the pre-image ensures
-that any pair in $\rho$ is the reference $\cfgnt{r}_a$ that birthed
-the location $\cfgnt{l}_a$ in some prior initialization (i.e., it was
-$\cfgnt{r}_f$ and $\cfgnt{l}_f$ at one time). Aliasing constraint
+aliases. Minimizing over the set of references in the pre-image ensures
+that any pair in $\rho$ is the reference $\cfgnt{r}_a$ and the location $\cfgnt{l}_a$ materialized at the same time in some prior initialization (i.e., they were once
+$\cfgnt{r}_f$ and $\cfgnt{l}_f$). Aliasing constraints
 in the new summary heap reason over these original creators; otherwise aliasing and local value set
@@
 
-There are three sets correspond to the non-deterministic choices in
-GSE with a fourth that preserves the pre-initialized heap structure
-(the constraints in each preserve the access path to the location):
+There are three sets corresponding to the non-deterministic choices in
+GSE with a fourth that preserves the pre-initialized heap structure.
+Note that the constraints always preserve the access path to the location which is $\phi_x$.
 (i) $\theta_\mathit{null}$ asserts the condition under which
 $\cfgnt{l}_\mathit{null}$ is possible (any time the solver assigns
-values to reference variables in such a way that $\cfgnt{r}_f =
-\cfgnt{r}_\mathit{null}$ holds as does access path $\phi_x$). (ii)
-$\theta_\mathit{new}$, meaning $\cfgnt{r}_f$ refers to the fresh
-location, occurs when $\cfgnt{r}_f$ is not new or any other alias. (iii) any member of $\theta_\mathit{alias}$ restricts $\cfgnt{r}_f$ to
-only alias one member of $\rho$ and not alias any member of $\rho$
+values to reference variables in such a way that both $\phi_x$ and $\cfgnt{r}_f =
+\cfgnt{r}_\mathit{null}$ hold). (ii)
+$\theta_\mathit{new}$ is active when $\cfgnt{r}_f$ points to the
+fresh location. This occurs when $\cfgnt{r}_f$ is not new or any other alias. (iii) a member of $\theta_\mathit{alias}$ restricts $\cfgnt{r}_f$ to
+a particular alias in $\rho$, and at the same time, not alias any member of $\rho$
 that was initialized earlier than the current choice (a later
-initialization may indeed alias the current alias choice in a valid
-heap but the current choice cannot alias both the choice and a
-previous initialization). And (iv) $\theta_\mathit{orig}$  implements conditional initialization to preserve the
+initialization may indeed also alias the current choice in a valid
+heap as order determines the number of aliasing choices available). And (iv) $\theta_\mathit{orig}$  implements conditional initialization to preserve the
 original heap structure. This property is needed for the bisumulation. 
-These sets are added into the heap on the field after initializing the fields in the new location to $\cfgnt{l}_\mathit{un}$.
+These sets are added into the heap on $\cfgnt{r}_f$ after the fields for $\cfgnt{l}_f$ are initialized to $\cfgnt{r}_\mathit{un}$.
 
@@
 (c) After $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ is initialized.
-(d) Constraint sets from the summary rule and constraints on the edges.}
+(d) Sets in the summarize rule and constraints on the edges.}
 \label{fig:initHeap}
@@
 references with the superscript $s$ indicates that it is a reference from the stack partition.
- In~\figref{fig:initHeap} $\cfgnt{r}_0^s$ represents a stack
+ In~\figref{fig:initHeap}, $\cfgnt{r}_0^s$ represents a stack
 reference for the $\cfgt{this}$ variable which has two fields $x$
-and $y$ of the same type; reference $\cfgnt{r}_0^s$ points to location
-$\cfgnt{l}_0$. Note that when no constraint is specified in the graphs, then
+and $y$ of the same type. Note that when no constraint is specified in the graphs, then
 there is an implicit $\mathit{true}$ constraint, for example, $\cfgnt{r}_0^s$
@@
 
-The access on $\cfgnt{l}_0.x$ creates a new input heap reference $\cfgnt{r}_1^i$ in the
-summary heap shown in~\figref{fig:initHeap}(b). The reference $\cfgnt{r}_1^1$
+The access of $x$ from $\cfgnt{l}_0$ creates a new input heap reference $\cfgnt{r}_1^i$ in the
+summary heap shown in~\figref{fig:initHeap}(b). The reference $\cfgnt{r}_1^i$
 points to the $\cfgnt{l}_\mathit{null}$ location under the constraint that
-$\cfgnt{r}_1^i$ is null: $\phi_{1a} := \cfgnt{r}_1^i = \cfgnt{r}_\mathit{null}$. The reference
+$\cfgnt{r}_1^i$ is null (\figref{fig:inintHeap}(d)): $\phi_{1a} := \cfgnt{r}_1^i = \cfgnt{r}_\mathit{null}$. The reference
 $\cfgnt{r}_1^i$ points to the location $\cfgnt{l}_1$ under the constraint that $\cfgnt{r}_1^i$
-is not $\mathit{null}$ $\phi_{1b} :=\cfgnt{r}_1^i \neq \cfgnt{r}_\mathit{null}$. The
-location $\cfgnt{l}_1$ represents a fresh location of type $C$ is created on
-the heap such that $C$ is type of $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$.
+is not $\mathit{null}$ ($\phi_{1b}$). The
+location $\cfgnt{l}_1$, a fresh location of type $C$ (the type of field $\cfgnt{x}\rp$), is added to the heap. There are no aliases because the input heap was empty.
 
-Following initialization to $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$, when
-$\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ is initialized, the resulting summary heap is shown
-in~\figref{fig:initHeap}(c). The set $\rho$ shown
-in~\figref{fig:initHeap}(d) contains the potential aliases for
- $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ which is location $\cfgnt{l}_1$ ($\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$). The
+Following $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$, 
+$\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ is initialized leading to the summary heap
+in~\figref{fig:initHeap}(c). The set $\rho$ 
+in~\figref{fig:initHeap}(d) contains the one potential aliases $\cfgnt{l}_1$ from the previous initialization for $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$.
+It also shows the $\theta$-sets for this initialization and the resulting edge labels.
+Note that the ordering between aliases in $\theta_\mathit{alias}$ does not matter until a third field is initialized and there are two potential choices.
+
+\begin{comment}
+The
 constraint location $\theta$ sets represents the initialization
@@
 is not null and \emph{does} alias $\cfgnt{r}_1^i$.
+\end{comment}
 
@@
 the value of a field (field-access) and the other when we write to a
-field (field-write). In both the field rewrite rules we first check we
-perform is whether there exists a constraint location pair for the $r$
-being accessed such that the location is not null and the constraint
-when conjuncted with the global constraint is satisfiable. Next we
-extract all possible constraints under which $r$ points to a null
-location such that the constraint is satisfiable under the current
-global constraint, $\phi_g$. The negation of these constraints are
-added to the global constraint to create a new global constraint
-$\phi_g^\prime$. The update to the global constraint ensures that
-access or write of the field $f$ happens only on non-null
-locations. There are rewrite rules for accessing and writing to fields
-on null locations where it leads the current program execution state
-to an error state. The rewrite rules for the accessing and writing to
-null locations are presented in the supplemental document.
+field (field-write). Both rules first check that the operations can be
+performed on a non-null location. If such is the case, then the global
+constraint $\phi_g$ is updated to disallow any viable null locations
+from this point forward: future accesses are non-null.
+%perform is whether there exists a constraint location pair for the $r$
+%being accessed such that the location is not null and the constraint
+%when conjuncted with the global constraint is satisfiable. Next we
+%extract all possible constraints under which $r$ points to a null
+%location such that the constraint is satisfiable under the current
+%global constraint, $\phi_g$. The negation of these constraints are
+%added to the global constraint to create a new global constraint
+%$\phi_g^\prime$.
+%The update to the global constraint ensures that
+%access or write of the field $f$ happens only on non-null
+%locations. 
+When there is a feasible null location in the summary heap on the
+field access operations, the machine moves to an error state. The
+rewrite rules for null locations are in the supplemental document.
 
-In the field-access rewrite rule in~\figref{fig:fHeap}(a) after the
+In the field-access rewrite rule in~\figref{fig:fHeap}(a), after the
 non-nullness check we extract the The type $C$ of the field is

### 2014-11-13 tex/operations.tex
Split precise.tex into multiple sections.

--- 2014-11-13 tex/precise.tex
@@
-\section{Generating Summary Heaps}
-\label{sec:precise}
-
-In this section we present the rewrite rules for the $\rsym$ relation. 
-There are three sets of rewrite rules specific to the summary
-heap algorithm: (i) rules to initialize symbolic
-references, (ii) field access and write rules, and (iii) rules
-to check equality and inequality of references. These rules
-form the core of the summary heap algorithm.
-
-\subsection{Initialization of Symbolic References}
-
-During initialization of symbolic references in the $\rgse$ relation,
-non-determinitic choices are introduced into the search to
-account for initiaization of the reference to $\mathit{null}$, a new instance of the 
-object, and to any type compatible object previously
-initialized. In contrast, initialization rules for the $\rsym$ relation are 
-defined on the bipartite graph consisting of references and locations,
-and create a single branch containing a summarization of
-all the initializations in a single graph.
-
-\input{summarize-precise-incomplete}
-
-\begin{figure*}
-\begin{tabular}[c]{l}
-\scalebox{1.0}{\usebox{\boxPI}} \\
-\end{tabular}
-\caption{The summary machine, $s ::= \lp\cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\ \cfgnt{C}\rp$, with $s\rsum^*s^\prime =  s \rsum \cdots \rsum s^\prime \rsum s^\prime$.}
-\label{fig:symInit}
-\end{figure*}
-
-The initialization rules are invoked whenever an uninitialized field in a
-symbolic reference is accessed. The function $\mathbb{UN}(\cfgnt{L},
-\cfgnt{R}, \cfgnt{r}, \cfgnt{f}) = \{\cfgnt{l}\ ...\}$ returns
-constraint-location pairs in which field $\cfgnt{f}$ is
-uninitialized:
-\[
-\begin{array}{rcl}
-\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \\
-& & \ \ \ \ \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \\
-& & \ \ \ \ \ \ \ \ \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
-\end{array}
-\]
-where $\mathbb{S}(\phi)$ returns true if $\phi$ is
-satisfiable. Intutively, for reference $\cfgnt{r}$, this function constructs
-the set, $\theta$ containing all contraint-location pairs that
-point to field $\cfgnt{f}$ and $\cfgnt{f}$ points to
-$\cfgnt{l}_\mathit{un}$.
-
-% The cardinality of the set, $\theta$ is never
-%greater than one in GSE and the constraint is always satisfiable
-%because all constraints are constant. This property is relaxed in GSE
-%with heap summaries.
-
-The rewrite rule to initialize a heap in the summary heap algorithm
-is shown in~\figref{fig:symInit}. Given the unitialized set
-$\mathbb{UN}$ for field $f$, the $\mathit{min}_l$ function returns
-$(\phi_x\ \cfgnt{l}_x)$ based on a lexicographical ordering of uninitialized locations
-in $\Lambda$. The init$_r$ method returns a new input reference $\cfgnt{r}_f$,
-while the fresh$_f$ returns a new location of type $C$. The set $\rho$
-contains the set of reference-location pairs, $(\cfgnt{r}_a\ \cfgnt{l}_a)$, the
-field being initialized may alias. A pair $(\cfgnt{r}_a\ \cfgnt{l}_a)$ is contained
-in the set $ \rho $ if the following conditions hold: (i) $\cfgnt{r}_a$ is
-part of the input references initialized in the summary heap, (ii)
-$\cfgnt{r}_a$ is in the pre-image of $\cfgnt{l}_a$, and (iii) the type 
-of $\cfgnt{l}_a$ is the same as the type of the field being initialized.
-
-There are three constraint-location pair sets that correspond to the
-non-deterministic choices in GSE: (a) $\theta_\mathit{null}$ contains
-a constraint $\cfgnt{r}_f = \cfgnt{r}_\mathit{null}$ paired with the location
-$\cfgnt{l}_\mathit{null}$, (b) \sjp{something is not right in this choice}
-$\theta_\mathit{new}$ creates a pair with a
-constraint representing the fact that $\cfgnt{r}_f$ is not null and it does 
-not alias any reference in set $\rho$ under and a newly created location 
-$\cfgnt{l}_f$, and (c) 
-$\theta_\mathit{alias}$ where for each element in the set $(\cfgnt{r}_a\ \cfgnt{l}_a)
-\in \rho$ it creates a constraint stating that $\cfgnt{r}_f$ is not null, points to
-$\cfgnt{r}_a$, and does not point to any reference contained in $(\cfgnt{r}_a^\prime\ 
-\cfgnt{l}_a^\prime) \in \rho$ such that $\cfgnt{r}_a < \cfgnt{r}_a^\prime$ based on a lexical
-ordering of initialized references. Additionally,
-$\theta_\mathit{orig}$ allows for the possibility that the field
-continues to remain uninitialized since the heap is symbolic.
-\sjp{The last statement seems to jump out since we have not been
-talking about the heap being symbolic (have we?)} We refer
-to initialization in the summary machine as conditional
-initialization \sjp{Not sure why we say this - what does it mean
-to the reader?}. Finally, the fields of the reference $\cfgnt{r}_f$ are marked
-as uninitialized. In the post condition of the rule, the reference
-$\cfgnt{r}_f$ points to $\theta$ which contains the union of all the
-constraint location pairs sets, and the field $f$ points to the new
-reference $\cfgnt{r}_f$ in the summary heap.
-
-\begin{comment}
- Note that the summarize rule invoked repeatedly until
-the set of unitialized constraint location pairs for field $f$ is
-empty. In other words the set $\Lambda$ is empty. This consititutes
-the summarize end rule in~\figref{fig:symInit}.
-\end{comment}
-
-\begin{figure*}[t]
-\begin{center}
-\begin{tabular}[c]{c|c|c|c}
-\begin{tabular}[c]{c}
-\scalebox{0.81}{\input{origHeap.pdf_t}} \\
-\end{tabular} &
-\begin{tabular}[c]{c}
-\scalebox{0.81}{\input{summarizeXHeap.pdf_t}} \\
-\end{tabular} &
-\begin{tabular}[c]{c}
-\scalebox{0.81}{\input{summarizeYHeap.pdf_t}} \\
-\end{tabular} &
-\begin{tabular}[c]{l}
-$\rho := \{ (\cfgnt{r}_1^i\ \cfgnt{l}_1 \}$ \\
-$\theta_\mathit{null} := \{ ( \cfgnt{r}_2^i = \cfgnt{r}_\mathit{null}\ \cfgnt{l}_\mathit{null}) \}$\\
-$\theta_\mathit{new} := \{ ( \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_1^i\ \cfgnt{l}_2) \}$\\
-$\theta_\mathit{alias} := \{ ( \cfgnt{r}_1^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i = \cfgnt{r}_1^i\ \cfgnt{l}_1) \}$\\
-$\theta_\mathit{orig} := \{ \}$ \\
-$\phi_{\mathit{1a}} := \cfgnt{r}_1^i = \cfgnt{r}_\mathit{null} $ \\
-$\phi_{\mathit{1b}} := \cfgnt{r}_1^i \neq \cfgnt{r}_\mathit{null} $  \\
-$\phi_{\mathit{2a}} := \cfgnt{r}_2^i = \cfgnt{r}_\mathit{null}$ \\
-$\phi_{\mathit{2b}} := \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_1^i$ \\
-$\phi_{\mathit{2c}} :=  \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i = \cfgnt{r}_1^i $ \\
-\end{tabular} \\
-(a) & (b) & (c) & (d) \\
-\end{tabular}
-\end{center}
-\caption{An example that initializes $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ and $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$.
-(a) Initial heap structure.
-(b) After $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ is initialized.
-(c) After $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ is initialized.
-(d) Constraint sets from the summary rule and constraints on the edges.}
-\label{fig:initHeap}
-\end{figure*}
-
-We visualize the initialization process in~\figref{fig:initHeap}. The
-graph in~\figref{fig:initHeap}(a) represents the initial heap. The
-references with the superscript $s$ indicates that it is a local
-reference. In~\figref{fig:initHeap} $\cfgnt{r}_0^s$ represents a local
-reference for the $\cfgt{this}$ reference which has two fields $x$
-and $y$ of the same type; reference $\cfgnt{r}_0^s$ points to location
-$\cfgnt{l}_0$. Note that when no constraint is specified in the graphs, then
-there is an implicit $\mathit{true}$ constraint, for example, $\cfgnt{r}_0^s$
-points to $\cfgnt{l}_0$ on the constraint $\mathit{true}$. The fields $x$ and
-$y$ point to the uninitialized reference $\cfgnt{r}_\mathit{un}$.
-
-% The reference $\cfgnt{r}_\mathit{un}$ points to the uninitialized location
-%$\cfgnt{l}_\mathit{un}$ on the $\mathit{true}$ constraint.
-
-The graph in~\figref{fig:initHeap}(b) represents the summary heap
-after the initialization of the $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ field while
-the graph in~\figref{fig:initHeap}(c) represents the symbolic heap
-summary after the initialization of the $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ field
-following the initialization of $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$. The list
-in~\figref{fig:initHeap}(d) represents the various sets constructed in
-the summarize rule during the initialization of $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$. We
-also define values of constraints used as labels in the graph.
-
-The access on $\cfgnt{l}_0.x$ creates a new input reference $\cfgnt{r}_1^i$ in the
-summary heap shown in~\figref{fig:initHeap}(b). The reference $\cfgnt{r}_1^1$
-points to the $\cfgnt{l}_\mathit{null}$ location under the constraint that
-$\cfgnt{r}_1^i$ is null: $\phi_{1a} := \cfgnt{r}_1^i = \cfgnt{r}_\mathit{null}$. The reference
-$\cfgnt{r}_1^i$ points to the location $\cfgnt{l}_1$ under the constraint that $\cfgnt{r}_1^i$
-is not $\mathit{null}$ $\phi_{1b} :=\cfgnt{r}_1^i \neq \cfgnt{r}_\mathit{null}$. The
-location $\cfgnt{l}_1$ represents a fresh location of type $C$ is created on
-the heap such that $C$ is type of $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$.
-
-Following initialization to $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$, when
-$\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ is initialized, the resulting summary heap is shown
-in~\figref{fig:initHeap}(c). The set $\rho$ shown
-in~\figref{fig:initHeap}(d) contains the potential aliases for
- $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ which is location $\cfgnt{l}_1$ ($\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$). The
-constraint location $\theta$ sets represents the initialization
-choices for $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$. The new input reference $\cfgnt{r}_2^i$ for
-$\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ points to (a) location $\cfgnt{l}_\mathit{null}$ under the constraint
-$\phi_{2a} := \cfgnt{r}_2^i = \cfgnt{r}_\mathit{null}$, (b) location $\cfgnt{l}_2$ under the
-constraint $\phi_{2b} := \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq
-\cfgnt{r}_1^i$ that states that $\cfgnt{r}_2^i$ is not null and does not alias
-$\cfgnt{r}_1^i$, and (c) location $\cfgnt{l}_1$ under the constraint $\phi_{2c} :=
-\cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i = \cfgnt{r}_1^i$ that states $\cfgnt{r}_2^i$
-is not null and \emph{does} alias $\cfgnt{r}_1^i$.
-
 \subsection{Reading and Writing References}

### 2014-11-13 tex/precise.tex
Split precise.tex into multiple sections.

--- 2014-11-13 tex/precise.tex
@@
 is not null and \emph{does} alias $\cfgnt{r}_1^i$.
-
-\subsection{Reading and Writing References}
-\input{precise-fig-incomplete}
-
-\begin{figure*}[t]
-\begin{center}
-\setlength{\tabcolsep}{60pt}
-\hspace*{-35pt}
-\begin{tabular}[c]{cc}
-\scalebox{1.0}{\usebox{\boxPFAFW}} & 
-%\scalebox{0.91}{\input{faYHeap.pdf_t}} &
-\scalebox{0.91}{\input{fwXHeap.pdf_t}} \\ \\
-(a) & (b)
-\end{tabular}
-\end{center}
-\caption{Field read and write relations with an example heap.
-(a) Field-access, $\rsym^\mathit{A}$, and field-write, $\rsym^\mathit{W}$, rewrite rules for the $\rsym$ relation.
-(b) The final heap after $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\ \cfgt{:=}\ \lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp\rp$.}
-\label{fig:fHeap}
-\end{figure*}
-
-There are two rewrite rules in~\figref{fig:fHeap}(a), one for reading
-the value of a field (field-access) and the other when we write to a
-field (field-write). In both the field rewrite rules we first check we
-perform is whether there exists a constraint location pair for the $r$
-being accessed such that the location is not null and the constraint
-when conjuncted with the global constraint is satisfiable. Next we
-extract all possible constraints under which $r$ points to a null
-location such that the constraint is satisfiable under the current
-global constraint, $\phi_g$. The negation of these constraints are
-added to the global constraint to create a new global constraint
-$\phi_g^\prime$. The update to the global constraint ensures that
-access or write of the field $f$ happens only on non-null
-locations. There are rewrite rules for accessing and writing to fields
-on null locations where it leads the current program execution state
-to an error state. The rewrite rules for the accessing and writing to
-null locations are presented in the supplemental document.
-
-In the field-access rewrite rule in~\figref{fig:fHeap}(a) after the
-non-nullness check we extract the The type $C$ of the field is
-extracted and invoke the summarize rewrite rule
-in~\figref{fig:symInit} that performs the initialization of the field
-if it points to uninitialized locations. Once the initialization is
-complete, we create a new local reference $r^\prime$. An important
-property of the references in the bi-partiate graph is that they are
-\emph{immutable}. Hence we create a new local reference and assign it
-to the initialized reference, and return the local reference. In order
-to de-reference a field $r.f$ we define a helper function which is
-called the value set.
-
-\input{value-set-def}
-
-In the post-condition of the rewrite rule we assign
-the value set of input reference $r$ to the local reference $r^\prime$
-and return the local reference $r^\prime$ in the next state.
-
-Consider the graph shown in~\figref{fig:fHeap}(b) the reference
-$\cfgnt{r}_2^i$ is created during the initialization of $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$. The
-reference that is returned during the access of the field, however, is
-$\cfgnt{r}_3^s$. The reference $\cfgnt{r}_3^s$ points to the value set of $\cfgnt{r}_2^i$
-which are: $(\phi_{2a}\ \cfgnt{l}_\mathit{null})$, $(\phi_{2b}\ \cfgnt{l}_2)$, and
-$(\phi_{2c}\ \cfgnt{l}_1)$. The values of the constraints $\phi_{2a}$,
-$\phi_{2b}$, and $\phi_{2c}$ are defined in~\figref{fig:initHeap}(d).
-
-The field-write rewrite rule in~\figref{fig:fHeap}(a) after the
-non-nullness check we We look up the value of the base reference in
-the environment $\eta(x)$.  The reference $\cfgnt{r}_x$ is the base pointer
-whose field, $\cfgnt{r}_\mathit{curr}$ is being written to to while the
-reference $r$ is the target reference. The set $\Psi_x$ contains
-tuples $(\phi\ l\ \cfgnt{r}_\mathit{curr})$ of constraints, locations, and
-references. These tuples represent access chains leading from $\cfgnt{r}_x$ to
-the reference of the field, $\cfgnt{r}_\mathit{curr}$. The goal is to
-overwrite the $\cfgnt{r}_\mathit{curr}$ references with the target
-references. Since the target of the write is $r$, we first check that
-the location constraint pairs of $\cfgnt{L}(r)$ are satisfiable when accessed
-through the $\cfgnt{r}_x$ chain. This is accomplished by the strengthening
-function.
-
-\input{st-def}
-
-Note that the write is conditional. In the case that $\phi$ is true
-then $\cfgnt{r}_\mathit{curr}$ will point to the constraint location pairs of
-$\cfgnt{L}(\cfgnt{r})$ while if $\phi$ is false then $\cfgnt{r}_\mathit{curr}$ will continue
-to point to the constraint location pair it is currently pointing to.
-Again since the references are immutable we create a new reference for
-each $\cfgnt{r}_\mathit{curr}$ and point them to the target constraint
-location pairs.
-
-Consider the example shown in~\figref{fig:fHeap}(b) where we assign
-$\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\ \cfgt{:=}\ \lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp\rp$. Note that
-in~\figref{fig:initHeap}(c) $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ is represented by
-$\cfgnt{r}_1^i$. After applying the field-write rule the reference $\cfgnt{r}_1^i$ is
-replaced by the fresh reference $\cfgnt{r}_4$ which now points to target
- $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ represented by $\cfgnt{L}(\cfgnt{r}_2^i)$.
-
-\begin{comment}
-\begin{figure}[t]
-\begin{center}
-\begin{tabular}[c]{l}
-$\Psi_x = \{ (true\ \cfgnt{l}_0\ \cfgnt{r}_1^i) \}$\\
-$ST (\cfgnt{L}, \cfgnt{r}_3^s, \phi, \phi_g)$ \\
-$\theta = \{ (\phi_{2a}\; \cfgnt{l}_\mathit{null} ) (\phi_{2b}\; \cfgnt{l}_2) (\phi_{2c}\; \cfgnt{l}_1) \}$\\
-$ST(\cfgnt{L}, \cfgnt{r}_0, \phi, \phi_g)$\\
-$\theta = \{ \}$\\
-\end{tabular}
-\end{center}
-\caption{FIXME: When will I get a caption}
-\label{fig:faHeapSets}
-\end{figure}
-\end{comment}
-
-\subsection{Equality and InEquality of References}
-\input{precise-eq}
-
-\begin{figure*}
-\begin{center}
-\begin{tabular}[c]{c}
-\scalebox{1.0}{\usebox{\boxPEQ}} \\
-% & \usebox{\boxPEX} \\ \\
-%(a) & (b) \\
-\end{tabular}
-\end{center}
-\caption{The reference compare rewrite rule for both the true, $\rsym^\mathit{E}$, and false, $\rsym^\mathit{E^\prime}$ outcomes.}
-\label{fig:eqs}
-\end{figure*}
-
-\newsavebox{\boxPEX}
-\savebox{\boxPEX}{
-\begin{tabular}[c]{l}
-$\cfgnt{L}(\cfgnt{r}_1^i) = \{ (\phi_{1a}\; \cfgnt{l}_\mathit{null})\; (\phi_{1b}\; \cfgnt{l}_1) \}$ \\
-$\cfgnt{L}(\cfgnt{r}_2^i) = \{ (\phi_{2a}\; \cfgnt{l}_\mathit{null}),\; (\phi_{2b}\; \cfgnt{l}_2),\; (\phi_{2c}\; \cfgnt{l}_1) \} $\\
-  $\theta_0 = \{ \} $\\
-$\theta_1 = \{ \phi_{2b}\} $\\ \hline
-Equals true \\
-$\theta_\alpha = \{ (\phi_{1a}\; \wedge\; \phi_{2a} ) (\phi_{1b}\; \wedge\; \phi_{2c} ) \}$\\
-$\phi^\prime = \mathit{true} \wedge [ (\phi_{1a}\; \wedge\; \phi_{2a} )\vee (\phi_{1b}\; \wedge\; \phi_{2c} ) ] \wedge \neg\phi_{2b} $\\ \hline
-Equals false \\
-$\theta_\alpha = \{ (\phi_{1a}\; \implies\; \neg\phi_{2a} ) (\phi_{1b}\; \implies\; \neg\phi_{2c} ) \}$\\
-$\phi^\prime = \mathit{true} \wedge  (\phi_{1a}\; \implies\; \neg\phi_{2a} )\wedge (\phi_{1b}\; \implies\; \neg\phi_{2c} )  \wedge \phi_{2b} $\\ \hline
-\end{tabular}}
-
-The rewrite rules to compare two references in the symbolic summary
-heap are shown in~\figref{fig:eqs}. The equals references-true rewrite
-rule returns true when two references $\cfgnt{r}_0$ and $\cfgnt{r}_1$ \emph{can} be
-equal. In GSE semantics checking equality of references is a simple
-comparision of two concrete object references. In the symbolic summary
-heap, however, we compare sets of constraint location pairs pointed to
-by each reference to determine if they could be equal.
-
-Consider the equals reference-true rewrite rule
-in~\figref{fig:eqs}. In order to check equality we construct three
-sets of constraints. For all constraint location pairs $(\phi_0\ \cfgnt{l}_0)
-\in \cfgnt{L}(\cfgnt{r}_0)$ and $(\phi_1\ \cfgnt{l}_1) \in \cfgnt{L}(\cfgnt{r}_1)$ such that $\cfgnt{l}_0$ and $\cfgnt{l}_1$
-are the same ($\cfgnt{l}_0 = \cfgnt{l}_1$) we create conjunctions of the constraints
-$\phi_0 \wedge \phi_1$ and add them to set $\Phi_\alpha$. Intutively,
-$\Phi_\alpha$ contains all constraints under which $\cfgnt{r}_0$ and $\cfgnt{r}_1$ may
-point to the same location in the symbolic summary heap. The second
-set, $\Phi_0$, contains constraints under which the reference $\cfgnt{r}_0$
-points corresponding locations such that the reference $\cfgnt{r}_1$
-\emph{does not} point to those locations under any
-constraint. Finally, the set, $\Phi_1$, contains constraints under
-which $\cfgnt{r}_1$ points to corresponding locations and $\cfgnt{r}_0$ \emph{does
-  not} point to those locations under any constraint.
-
-We use the three sets of constraints to update the current global heap
-constraint $\phi_g$ and create a new global heap constraint
-$\phi_g^\prime$. We add to $\phi_g$ the disjunction of the constraints
-in $\Phi_\alpha$ to indicate that if any of the constraints are
-satisfiable, then references $\cfgnt{r}_0$ and $\cfgnt{r}_1$ can be
-equal. Furthermore, we had to the global heap constraint,
-$\phi_g^\prime$, the conjunctions of negations to the constraints in
-$\Phi_0$ and $\Phi_1$. This indicates for locations that are not
-common to the references, the negations of their constraints are
-satisfiable. Before the rewrite rule returns true we check the
-satisfiability of the updated global heap constraint.
-
-Consider the example in~\figref{fig:initHeap}(c). In order to to check
-if $\cfgnt{r}_1^i$ and $\cfgnt{r}_2^i$ are equal we first get the constraint location
-pairs associated with each of the references:
-\[
-\cfgnt{L}(\cfgnt{r}_1^i) = \{ (\phi_{1a}\; \cfgnt{l}_\mathit{null})\; (\phi_{1b}\; \cfgnt{l}_1) \} 
-\]
-\[
-\cfgnt{L}(\cfgnt{r}_2^i) = \{ (\phi_{2a}\; \cfgnt{l}_\mathit{null})\; (\phi_{2b}\; \cfgnt{l}_2)\; (\phi_{2c}\; \cfgnt{l}_1) \} \\
-\]
-\noindent{The three constraint sets are:} 
-\[
-\Phi_\alpha = \{ (\phi_{1a}\; \wedge\; \phi_{2a} ) (\phi_{1b}\; \wedge\; \phi_{2c} ) \}\;
-\Phi_0 = \{ \}\; \Phi_1 = \{ \phi_{2b}\} \\
-\]
-\noindent{Finally the global constraint is} 
-\[
-\phi^\prime = \mathit{true} \wedge [ (\phi_{1a}\; \wedge\; \phi_{2a} )\vee (\phi_{1b}\; \wedge\; \phi_{2c} ) ] \wedge \neg\phi_{2b} 
-\]
-\noindent{The equals references-false is the logical dual of the
-  reference-true rewrite rule. The references-false is shown
-  in~\figref{fig:eqs}.}

### 2014-11-13 tex/intro.tex

@@
 some of these limitations but often leads to infeasible heaps. Also,
-heap updates require a rewrite of the constraint system making it
-prohibtive for use in the context of symbolic execution.
-
-\begin{comment}
-Unfortunately, value sets often do not support aliasing and require a
-recursive definition of objects~\cite{..}. Also, heap updates often
-require that the path constraint be rewritten to reflect the update,
-and the constraints in the value set may also need to be rewritten with the
-addition of auxiliary variables. These non-local operations make it
-difficult to use value sets in symbolic execution. As is
-typical in static analysis, over approximation of the value sets
-alleviates some of the limitations but also leads to false positives.
-\end{comment}
-
-%The goal of this work is find a more compact representation of the heaps
-%and be better able to leverage constraint solvers.
-%The  But any update of the heap required a rewrite on the constraint system
-%or simply was not opssible to initialize and handle the aliasing possiblities.
-
-%The goal is to leverage that
-
-%Research in the abstract interpretation community has taken a very
-%different approach to analyzing heap manipulating programs which
-%computes a summary of possible heaps.  These techniques start with an
-%initial heap configuration and then using a static analysis, make
-%updates to the heap following program semantics, ultimately creating
-%a heap summary which represents the potential heaps resulting from
-%program execution~\cite{Dillig:2011}. Because these techniques are
-%based on a static analysis, the heap summaries over-approximate the
-%set of feasible heap configurations.
-
-%The primary challenge relative to heap analysis for these techniques
-%is to resolve potential dependencies of local results on the global
-%aliases in the heap.  Recent work addresses these issues through
-%strong updates to heap locations at call sites~\cite{Dillig} and
-%computation of dangerous aliases~\cite{Matosevic}. Because these
-%techniques are based on a static analysis, the resulting summaries
-%over-approximate the actual potential heaps.
+most static analysis techniques for heap updates require a rewrite of
+the constraint system making it prohibitive for use in the context of
+symbolic execution.
 
@@
 representation and an algorithm to initialize and update the heap
-on-the-fly. Our summary heap approach supports aliasing, does not
-require constraint rewriting on heap updates, and reduces
+on-the-fly. In essence, our summary heap approach supports aliasing,
+does not require constraint rewriting on heap updates, and reduces
 non-determinism in the search space during symbolic execution.
@@
 references. Each location points to a single reference for a given
-field. The use of a bipartite graph affords two key advantages: (i)
-it allows for a non-recursive definition of objects which enables us
-to support aliasing, and (ii) it does not introduce auxiliary variables or 
-require rewriting of non-local constraints during updates to the heap.
+field. The use of a bipartite graph affords two key advantages: (i) it
+allows for a non-recursive definition of objects which enables us to
+support aliasing, and (ii) it does not introduce auxiliary variables
+or require rewriting of non-local constraints during updates to the
+heap.
 
@@
 divergence in the control flow graph. These points of non-determinism
-are at field accesses that lead to null-pointer exceptions
-and at comparisons of references. The former represents a divergence
-due to exceptional control flow while the latter is due to program
-structure.
+are at field accesses that lead to null-pointer exceptions and at
+comparisons of references. The former represents a divergence due to
+exceptional control flow while the latter is due to program structure.
+The combination of the heap representation and the summary heap
+algorithm enables us to improve the efficiency of symbolic execution
+of heap manipulating programs over state-of-the-art techniques.
 
@@
 
-This combination of summary heap and lazy initialization
-enable us to improve the efficiency of symbolic execution of heap
-manipulating programs over state-of-the-art techniques.
-Furthermore, the summary heap algorithm is sound and complete with
-respect to properties that are provable using GSE. This proof is
-accomplished by showing the existence of a bisimulation
-between states in GSE and states in the summary heap algorithm. 
 \begin{comment}
@@
 
-A preliminary implementation in Java Pathfinder (JPF) shows that in
-general, the heap summary algorithm improves over other
-state-of-the-art techniques, and in some instances, the improvement is
-remarkable: two-orders of magnitude reduction in running time. More
-critically though, the heap summary enables the initialization of
-larger more complex heaps than previously possible as shown in our
-results.
+The summary heap algorithm is sound and complete with respect to
+properties that are provable using GSE. This proof is accomplished by
+showing the existence of a bisimulation between states in GSE and
+states in the summary heap algorithm.  A preliminary implementation in
+Java Pathfinder (JPF) shows that in general, the heap summary
+algorithm improves over other state-of-the-art techniques, and in some
+instances, the improvement is remarkable: two-orders of magnitude
+reduction in running time. More importantly though, the heap summary
+enables the initialization of larger more complex heaps than
+previously possible as shown in our results.
 

### 2014-11-13 tex/precise.tex

@@
 is not null and \emph{does} alias $\cfgnt{r}_1^i$.
+\end{comment}

### 2014-11-13 tex/related.tex

@@
 
-%\subsection{Symbolic Exection}
+While there exists a large body of work related to summary heaps,
+we discuss work most closely related, including techniques for
+scaling symbolic execution of programs with complex data types,
+heap summary techniques, ...
 
-Recent years have seen a significant growth in research projects based
-on symbolic execution, first introduced in the 1970's by
-Clarke~\cite{Clarke:76} and King~\cite{King:76}. Initial work on symbolic
-execution largely focused on checking properties of program with
-primitive types. Several recent projects generalized the core
+%Recent years have seen a significant growth in research projects based
+%on symbolic execution, first introduced in the 1970's by
+%Clarke~\cite{Clarke:76} and King~\cite{King:76}.
+
+Initial work on symbolic execution largely focused on checking 
+properties of imperative programs with primitive
+primitive types~\cite{Clarke:76,King:76}. Several recent projects 
+generalized the core
 idea of symbolic execution which enabled it to be applied to

### 2014-11-13 tex/conclusion.tex
updates to conclusion

--- 2014-11-12 tex/conclusion.tex
@@
 \section{Conclusion}
+
+Although our approach is inspired by the work in the static analysis domain, the heap representations used by those techniques do not lend themselves for use in symbolic execution since they rely on approximations, they are inflexible in what types of relations can be expressed, and they rely on rewriting of constraints.
+In this work, we present a heap summary technique for symbolic execution that maintains exactness, represents arbitrary heap structures without restrictions on aliasing relationships, and supports dynamic on-the-fly initialization of heap structures.
+Despite this unique combination of capabilities, the summary heap technique outperforms  state-of-the-art symbolic execution techniques, and in some cases the performance gains are considerable.
+We believe that performance gains in symbolic execution can naturally benefit a variety of analyses based on symbolic execution, for example, verification of properties, especially those related to the heap, test case generation, program evolution techniques such as directed incremental symbolic execution~\cite{person:pldi2011}, and other back-end analyses.
+
+In this work, we restricted our presentation of symbolic heaps to constraints reasoning over heap morphology.
+However, in order to be useful for reasoning about real programs, we must also consider the impact of scalar types.
+Our implementation includes limited support for linear operations over integer types, however, we plan to add support for all types of operations such as floating point operations, arrays, and bitvectors.
+
+\begin{comment}
+
 We have presented a new heap representation for symbolic execution that maintains exactness, represents arbitrary heap structures without restrictions on aliasing relationships, and supports dynamic on-the-fly initialization of heap structures.
@@
 
-Another feature we would like to add is support for test case generation, which is traditionally a key advantage of symbolic execution techniques.
-Under the current rules, it is difficult to extract test cases because the heap may be destructively altered during field writes.
-A simple remedy would be to maintain an explicit input heap in addition to the actual heap which is mutated as the program progresses.
+Another feature we would like to add is support for test case
+generation, which is traditionally a key advantage of symbolic
+execution techniques. Under the current rules, it is difficult to
+extract test cases because the heap may be destructively altered
+during field writes. A simple remedy would be to maintain an explicit
+input heap in addition to the actual heap which is mutated as the
+program progresses.
 
@@
 In order to improve responsiveness during debugging operations, it should be possible to cache object invariants between test runs in to obtain a substantial speed-up.
+\end{comment}

### 2014-11-13 tex/precise.tex

@@
 The initialization rules, \figref{fig:symInit}, are invoked whenever
-an uninitialized field in a symbolic reference is accessed. The
+a field containing an uninitialized reference is accessed. The
 interaction with the solver in the definition of the rules is denoted
@@
 $\theta_\mathit{new}$ is active when $\cfgnt{r}_f$ points to the
-fresh location. This occurs when $\cfgnt{r}_f$ is not new or any other alias. (iii) a member of $\theta_\mathit{alias}$ restricts $\cfgnt{r}_f$ to
+fresh location. This occurs when $\cfgnt{r}_f$ is not new or any other alias. (iii) each member of $\theta_\mathit{alias}$ restricts $\cfgnt{r}_f$ to
 a particular alias in $\rho$, and at the same time, not alias any member of $\rho$
@@
 graph in~\figref{fig:initHeap}(a) represents the initial heap. The
-references with the superscript $s$ indicates that it is a reference from the stack partition.
+reference superscripts $s$ and $i$ indicate the partition containing the reference.
  In~\figref{fig:initHeap}, $\cfgnt{r}_0^s$ represents a stack
 reference for the $\cfgt{this}$ variable which has two fields $x$
-and $y$ of the same type. Note that when no constraint is specified in the graphs, then
-there is an implicit $\mathit{true}$ constraint, for example, $\cfgnt{r}_0^s$
+and $y$ of the same type. Note that when no constraint is specified for a location,
+there is an implicit $\mathit{true}$ constraint. For example, $\cfgnt{r}_0^s$
 points to $\cfgnt{l}_0$ on the constraint $\mathit{true}$. The fields $x$ and
@@
 
-The access of $x$ from $\cfgnt{l}_0$ creates a new input heap reference $\cfgnt{r}_1^i$ in the
-summary heap shown in~\figref{fig:initHeap}(b). The reference $\cfgnt{r}_1^i$
+Accessing field $x$ from $\cfgnt{l}_0$ creates a new input heap reference $\cfgnt{r}_1^i$ in the
+summary heap shown in~\figref{fig:initHeap}(b). Reference $\cfgnt{r}_1^i$
 points to the $\cfgnt{l}_\mathit{null}$ location under the constraint that
-$\cfgnt{r}_1^i$ is null (\figref{fig:inintHeap}(d)): $\phi_{1a} := \cfgnt{r}_1^i = \cfgnt{r}_\mathit{null}$. The reference
-$\cfgnt{r}_1^i$ points to the location $\cfgnt{l}_1$ under the constraint that $\cfgnt{r}_1^i$
-is not $\mathit{null}$ ($\phi_{1b}$). The
-location $\cfgnt{l}_1$, a fresh location of type $C$ (the type of field $\cfgnt{x}\rp$), is added to the heap. There are no aliases because the input heap was empty.
+$\cfgnt{r}_1^i$ is null (constraint $\phi_{1a}$ in  \figref{fig:initHeap}(d)), reference
+$\cfgnt{r}_1^i$ points to location $\cfgnt{l}_1$ under the constraint that $\cfgnt{r}_1^i$
+is not $\mathit{null}$ (constraint $\phi_{1b}$), and fresh location $\cfgnt{l}_1$ of type $C$ 
+(the type of field $\cfgnt{x}$), is added to the heap. There are no aliases because $\cfgnt{l}_1$ 
+is the first location of type $C$ to be initialized.
 
@@
 It also shows the $\theta$-sets for this initialization and the resulting edge labels.
-Note that the ordering between aliases in $\theta_\mathit{alias}$ does not matter until a third field is initialized and there are two potential choices.
+Note that the ordering between aliases in $\theta_\mathit{alias}$ is insignificant until a third field is initialized and there are two potential choices.
 

### 2014-11-13 tex/operations.tex

@@
 In the field-access rewrite rule in~\figref{fig:fHeap}(a), after the
-non-nullness check we extract the The type $C$ of the field is
-extracted and invoke the summarize rewrite rule
+non-nullness check, the rules gets the field type $\cfgnt{C}$ and uses
+the summarize machine,\figref{fig:symInit}, to get a new summary heap
+that is initialized on the field $\cfgnt{f}$. The summary heap after
+initialization is further modified in the final state of the field
+access to include a new stack reference pointing to the value set from
+the read. The new stack reference is the return value from the operation.
+\input{value-set-def}
+The value set computation is local: it only considers
+constraint locations on the reference $\cfgnt{r}$. Further, it only
+includes things that are feasible under the current path condition
+$\phi_g$. It also ensures that the access path valid.
+
+There is a constraint from the base reference and a given
+location. Once a location is selected, the field is accessed to get
+another reference, and from that reference there is a set of locations
+each with a constraint. The first constraint from the base reference
+plus this second constraint to the actual location of the field
+comprise the access path. For each member of the value set, these
+constraints together with the global path constraint must be satisfied
+on some aliasing assignment.
+
+\begin{comment}invoke the summarize rewrite rule
 in~\figref{fig:symInit} that performs the initialization of the field
@@
 
-\input{value-set-def}
-
 In the post-condition of the rewrite rule we assign
@@
 and return the local reference $r^\prime$ in the next state.
+\end{comment}
 
-Consider the graph shown in~\figref{fig:fHeap}(b) the reference
-$\cfgnt{r}_2^i$ is created during the initialization of $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$. The
-reference that is returned during the access of the field, however, is
-$\cfgnt{r}_3^s$. The reference $\cfgnt{r}_3^s$ points to the value set of $\cfgnt{r}_2^i$
-which are: $(\phi_{2a}\ \cfgnt{l}_\mathit{null})$, $(\phi_{2b}\ \cfgnt{l}_2)$, and
-$(\phi_{2c}\ \cfgnt{l}_1)$. The values of the constraints $\phi_{2a}$,
-$\phi_{2b}$, and $\phi_{2c}$ are defined in~\figref{fig:initHeap}(d).
+Consider the graph shown in~\figref{fig:fHeap}(b). The goal is to
+complete the operation $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$. The
+machine first evaluates the local variable look up to get the base
+reference: $\eta(\cfgt{this}) = \cfgnt{r}^s_0$. From the base
+reference, field access is able to complete returning the stack
+reference $\cfgnt{r}_3^s$ in the figure. The reference $\cfgnt{r}_3^s$
+points to the value set of $\cfgnt{r}_2^i$:
+$(\phi_{2a}\ \cfgnt{l}_\mathit{null})$, $(\phi_{2b}\ \cfgnt{l}_2)$,
+and $(\phi_{2c}\ \cfgnt{l}_1)$.
 
-The field-write rewrite rule in~\figref{fig:fHeap}(a) after the
-non-nullness check we We look up the value of the base reference in
-the environment $\eta(x)$.  The reference $\cfgnt{r}_x$ is the base pointer
-whose field, $\cfgnt{r}_\mathit{curr}$ is being written to to while the
+For field-write in~\figref{fig:fHeap}(a), after the
+non-null check and strengthening of the global heap constraint, it computes the current references associated with the field in every location in $\Psi_\cfgnt{x}$.
+Please note that the reference $\cfgnt{r}_x$ is the base reference
+whose field, $\cfgnt{r}_\mathit{cur}$ is being written to while the
 reference $r$ is the target reference. The set $\Psi_x$ contains
-tuples $(\phi\ l\ \cfgnt{r}_\mathit{curr})$ of constraints, locations, and
+tuples $(\phi\ l\ \cfgnt{r}_\mathit{cur})$ of constraints, locations, and
 references. These tuples represent access chains leading from $\cfgnt{r}_x$ to
-the reference of the field, $\cfgnt{r}_\mathit{curr}$. The goal is to
-overwrite the $\cfgnt{r}_\mathit{curr}$ references with the target
-references. Since the target of the write is $r$, we first check that
-the location constraint pairs of $\cfgnt{L}(r)$ are satisfiable when accessed
-through the $\cfgnt{r}_x$ chain. This is accomplished by the strengthening
-function.
+the reference of the field, $\cfgnt{r}_\mathit{cur}$.
+The goal is to change the fields to no longer point to $\cfgnt{r}_\mathit{cur}$, but rather fresh references that have both the original locations before the write and the locations from the write in the value sets (i.e., conditional write).
+Since the target of the write is $r$, the rule checks that
+the location constraint pairs of $\cfgnt{L}(\cfgnt{r})$ are satisfiable when accessed
+through the $\cfgnt{r}_x$ chain in the strengthening function.
+\input{st-def}
+Constraints on locations are strengthened with new aliasing conditions
+and those that are feasible with the current path constraint are
+retained.
 
-\input{st-def}
+Strengthening in the field write creates a value set the
+contains feasible locations if the write happens on that location (the
+first call) and feasible locations if the write does not happen on
+that location (the second call). This is the conditional in the write. In the case that $\phi$ is true
+then $\cfgnt{r}_\mathit{cur}$ will point to the constraint location pairs of
+$\cfgnt{L}(\cfgnt{r})$ while if $\phi$ is false then $\cfgnt{r}_\mathit{cur}$ will continue
+to point to the constraint location pair it is currently referenced.
+As the references are immutable, the rule creates fresh reference for
+each $\cfgnt{r}_\mathit{cur}$ and points them to the appropriate value sets.
 
-Note that the write is conditional. In the case that $\phi$ is true
-then $\cfgnt{r}_\mathit{curr}$ will point to the constraint location pairs of
-$\cfgnt{L}(\cfgnt{r})$ while if $\phi$ is false then $\cfgnt{r}_\mathit{curr}$ will continue
-to point to the constraint location pair it is currently pointing to.
-Again since the references are immutable we create a new reference for
-each $\cfgnt{r}_\mathit{curr}$ and point them to the target constraint
-location pairs.
-
-Consider the example shown in~\figref{fig:fHeap}(b) where we assign
+Consider again the example shown in~\figref{fig:fHeap}(b) where we assign
 $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\ \cfgt{:=}\ \lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp\rp$. Note that
@@
 rule returns true when two references $\cfgnt{r}_0$ and $\cfgnt{r}_1$ \emph{can} be
-equal. In GSE semantics checking equality of references is a simple
+equal. In GSE semantics, checking equality of references is a simple
 comparision of two concrete object references. In the symbolic summary
 heap, however, we compare sets of constraint location pairs pointed to
-by each reference to determine if they could be equal.
+by each reference to determine if equality is possible.
 
 Consider the equals reference-true rewrite rule
-in~\figref{fig:eqs}. In order to check equality we construct three
-sets of constraints. For all constraint location pairs $(\phi_0\ \cfgnt{l}_0)
+in~\figref{fig:eqs}. In order to check equality, three
+sets of constraints are used. For all constraint location pairs $(\phi_0\ \cfgnt{l}_0)
 \in \cfgnt{L}(\cfgnt{r}_0)$ and $(\phi_1\ \cfgnt{l}_1) \in \cfgnt{L}(\cfgnt{r}_1)$ such that $\cfgnt{l}_0$ and $\cfgnt{l}_1$
-are the same ($\cfgnt{l}_0 = \cfgnt{l}_1$) we create conjunctions of the constraints
+are the same ($\cfgnt{l}_0 = \cfgnt{l}_1$), the rule creates conjunctions of the constraints
 $\phi_0 \wedge \phi_1$ and add them to set $\Phi_\alpha$. Intutively,
@@
 set, $\Phi_0$, contains constraints under which the reference $\cfgnt{r}_0$
-points corresponding locations such that the reference $\cfgnt{r}_1$
+points to corresponding locations such that the reference $\cfgnt{r}_1$
 \emph{does not} point to those locations under any
@@
 common to the references, the negations of their constraints are
-satisfiable. Before the rewrite rule returns true we check the
+satisfiable.
+The rule does not complete (i.e., is not feasible) if the new global constraint is not satisfied on any aliasing assignment.
+In such a case, the true outcome is not possible on any heap in the summary.
+
+Before the rewrite rule returns true we check the
 satisfiability of the updated global heap constraint.
@@
 \noindent{The equals references-false is the logical dual of the
-  reference-true rewrite rule. The references-false is shown
+  reference-true rewrite rule. The references-false is also shown
   in~\figref{fig:eqs}.}

### 2014-11-13 tex/evaluation.tex
Proofreading, fixing typos.
polishing of evaluation section

@@
 The results of the experiments are presented in Table
-\ref{tab:results}. The rows contain to individual $k$-bounded test
-runs for each of the evaluated programs. The columns show the total
-walk clock time in seconds, states explored, and paths generated for
+\ref{tab:results}. Each row contains the results for the specified $k$-bound 
+for each artifact evaluated. The columns show the total
+wall clock time in seconds, states explored, and paths generated for
 each of the algorithms. The headings \gsetxt{}, L\#, and SL correspond

### 2014-11-13 tex/bisimulation.tex
Finished pass on bisimulation.

@@
 \label{sec:bisim}
-Let $p \rgse p^\prime$ be the binary relation over the universe of states, $S$,
-according to generalized symbolic execution with lazy initialization
-(see the supplemental text for a precise definition of that
-relation). Similarly, let $q \rsym q^\prime$ be the relation for the GSESH
-algorithm in this paper. The principle theoretical result is the
-existence of a bisimilarity relation between states related on $p \rgse p^\prime$
+Recall that $p \rgse p^\prime$ is the binary relation over the universe of states, $S$,
+according to GSE with lazy initialization. Similarly, $q \rsym q^\prime$ is the relation for the summary heap algorithm
+presented in this paper. The principle theoretical result is the
+existence of a bisimulation between states related on $p \rgse p^\prime$
 and the states related on $q \rsym q^\prime$.  A corollary is that $\rsym$ is
-both sound and complete with respect to $\rgse$. Only a summary of the
-proof is given due to space.
+both sound and complete with respect to properties provable in $\rgse$. Only a summary of the
+proofs is given due to space.
 
@@
 $$
-\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E^\prime} \cup \rgse^\com
+\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E^\prime} \cup \rcom
 $$
-where \emph{A} is a field access $\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
-\rightarrow \cfgnt{k}\rp$, \emph{W} is a field write $\lp
+where \emph{A} is a field access after evaluating the expression for the base reference $\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
+\rightarrow \cfgnt{k}\rp$, \emph{W} is a field write after evaluating the expression for the right operand$\lp
 \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
-\cfgnt{k}\rp$, \emph{E} is a reference compare $\lp
+\cfgnt{k}\rp$, \emph{E} is a reference compare after evaluating the left and right operand expressions $\lp
 \cfgnt{v}\ \cfgt{=}\ \cfgnt{*} \rightarrow \cfgnt{k}\rp$, the prime symbol
@@
 $$
-Let $\hookrightarrow_\gse$ be the extension of $\rgse$ to sets of states.
+Let $\hookrightarrow_\gse$ be the extension of $\rgse$ to sets of
+states. From this extension, a new meta transition relation is defined
+over sets of states as
 $$
@@
 \hookrightarrow_\gse^\mathit{W^\prime} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E^\prime}
-\cup \hookrightarrow_\gse^\com
+\cup \hookrightarrow_\com
 $$
-The definition embodies the notion of splitting equivalence classes at
-certain operations. The set $P$ at a field access for example has two
-potential successors: a non-null and null reference. Respectively, the
-set $P \rgse^\com P^\prime$ only has a single successor since those expressions
-are not related to control flow.
+The definition embodies the notion of splitting groups of heaps at
+certain operations. The set $P$ at a field access after base reference is known, for example, has two
+potential successors: a non-null and null reference. The $\rsgse$ relation has two successors at that point to divide $P$ into the two outcomes. In contrast, the
+set $P \rgse^\com P^\prime$ only has a single successor since anything in $\rightarrow_\com$ is not related to control flow (e.g., variable look up, creating continuations, etc.).
 
@@
 constraint on the feasibility of that mapping in the presence of a
-path constraint from symbolic execution. Subscripts indicates state
+path constraint from symbolic execution. Subscripts indicates state tuple
 members as in $p = (
@@
 The functional equivalence between heaps on a homomorphism and
-a homomorphism constraint asserts a common structures in the two heaps under certain
+a homomorphism constraint asserts a common structure in the two heaps under certain
 conditions. The equivalence is used to related states in $p \rgse
@@
 \end{equation}
-The represented relation is extended to sets of states $P$ and a single state $q$ as\footnote{The full proof argues $P \sqsubset Q$ but that $Q$ is
-  always a singleton set containing $q$.}
+The represented relation is extended to sets of states $P$ and a single state $q$ as\footnote{The full proof argues $P \sqsubset Q$ but that any member $Q$ represents that same set of heaps as any other member of $q$ so it is sufficient to a member of $q$ in the relation.}
 $$
@@
 simulation, while the application to dissimilar states using a
-meta-relation, $\rsgse$, is somewhat non-standard; though convenient
+meta-relation, $\rsgse$, is somewhat non-standard; though it is convenient
 in this instance since it captures the notion of $q$ as a set of
@@
 
-The state $S$ is the universe of well-formed states, and the
-set $S_A \subseteq S$ is the set of states at a field access continuation.
+In the following lemma, recall that $S$ is the universe of well-formed states, and the
+set $S_A \subseteq S$ is the set of states at a field access continuation having computed the base reference.
 \begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
@@
 In the backward simulation \eqref{eqn:BisimulationBackwards}, for each
-$q^\prime$ such that $q \rsym q^\prime$, the proof posits the
-existences of some $p^\prime \sqsubset q^\prime$ and uses the
+$q^\prime$ such that $q \rsym q^\prime$, the proof posits that with any 
+$p^\prime$ such that $p^\prime \sqsubset q^\prime$, it is possible to use the
 homomorphism in $p^\prime \sqsubset q^\prime$ to derive a $p$ such
@@
 Similar lemmas are proved for field write and equals reference. These
-require additional lemmas on properties of the summary machine
-$\rightarrow_S$. Specifically, that it preserves determinism, and it
-preserves the homomorphism and the satisfiability of homomorphism constraint
+require additional lemmas on properties of the summarize machine
+$\rightarrow_S$. Specifically, that it preserves determinism, it
+preserves the homomorphism, and it preserves the satisfiability of the homomorphism constraint
 
@@
 \begin{proof}
-By definition of the bisimilarity relation. All of the common rules
+By definition of bisimilarity. All of the common rules in $\rcom$
 make no changes to the heap, so $P \sqsubset q$ is included in the
-functional. The other transition relations are supported by lemmas
+functional. The other rules that affect the heap are supported by lemmas
 such as \lemref{lem:access}.
@@
 The notation $p \stackrel{n}{\rgse} p^\prime$ denotes that $p^\prime$
-is the $n$-step successor of $p$, if it exists, and $q
+is the $n$-step successor of $p$, when it exists, and $q
 \stackrel{n}{\rsym} q^\prime$ is similarly defined. Completeness and

### 2014-11-13 tex/operations.tex
Proofread opearations.tex

@@
 In the field-access rewrite rule in~\figref{fig:fHeap}(a), after the
-non-nullness check, the rules gets the field type $\cfgnt{C}$ and uses
-the summarize machine,\figref{fig:symInit}, to get a new summary heap
-that is initialized on the field $\cfgnt{f}$. The summary heap after
-initialization is further modified in the final state of the field
-access to include a new stack reference pointing to the value set from
+null check, the rule gets the field type $\cfgnt{C}$ and uses
+the summarize machine, \figref{fig:symInit}, to get a new summary heap
+that is initialized on the field $\cfgnt{f}$. After
+initialization, the summary heap is further modified to include 
+a new stack reference pointing to the value set from
 the read. The new stack reference is the return value from the operation.
@@
 
-There is a constraint from the base reference and a given
-location. Once a location is selected, the field is accessed to get
-another reference, and from that reference there is a set of locations
-each with a constraint. The first constraint from the base reference
-plus this second constraint to the actual location of the field
+There is a constraint $\phi$ from the base reference $r$ and a given
+location. Once a location $l$ is selected, the field $\cfgnt{f}$ is accessed to get
+another reference $r^\prime$, and from that reference there is a set of locations
+each with a constraint. The first constraint $\phi$ from the base reference
+plus this second constraint to the actual location of the field $\phi^\prime$
 comprise the access path. For each member of the value set, these
@@
 
-Strengthening in the field write creates a value set the
-contains feasible locations if the write happens on that location (the
-first call) and feasible locations if the write does not happen on
-that location (the second call). This is the conditional in the write. In the case that $\phi$ is true
+Strengthening in the field write creates a value set that
+contains two types of locations:  those for the case where the write is feasible (the
+first call), and those for the case where it is not (the second call). 
+This is the conditional in the write. In the case that $\phi$ is true
 then $\cfgnt{r}_\mathit{cur}$ will point to the constraint location pairs of
@@
 to point to the constraint location pair it is currently referenced.
-As the references are immutable, the rule creates fresh reference for
+As the references are immutable, the rule creates fresh references for
 each $\cfgnt{r}_\mathit{cur}$ and points them to the appropriate value sets.
@@
 satisfiable, then references $\cfgnt{r}_0$ and $\cfgnt{r}_1$ can be
-equal. Furthermore, we had to the global heap constraint,
+equal. Furthermore, we conjoin to the global heap constraint 
 $\phi_g^\prime$, the conjunctions of negations to the constraints in
@@
 common to the references, the negations of their constraints are
-satisfiable.
-The rule does not complete (i.e., is not feasible) if the new global constraint is not satisfied on any aliasing assignment.
-In such a case, the true outcome is not possible on any heap in the summary.
+satisfiable. The rule does not complete (i.e., is not feasible) if the new
+ global constraint is not satisfied on any aliasing assignment. In such a case, 
+ the $\cfgt{true}$ outcome is not possible on any heap in the summary.
 
-Before the rewrite rule returns true we check the
+Before the rewrite rule returns $\cfgt{true}$ we check the
 satisfiability of the updated global heap constraint.
@@
 \]
-\noindent{The equals references-false is the logical dual of the
-  reference-true rewrite rule. The references-false is also shown
+\noindent{The equals references-false rule is the logical dual of the
+  reference-true rewrite rule. The references-false rule is also shown
   in~\figref{fig:eqs}.}

### 2014-11-13 tex/bisimulation.tex

@@
 In the backward simulation \eqref{eqn:BisimulationBackwards}, for each
-$q^\prime$ such that $q \rsym q^\prime$, the proof posits that with any 
-$p^\prime$ such that $p^\prime \sqsubset q^\prime$, it is possible to use the
+$q^\prime$ such that $q \rsym q^\prime$, the proof posits the existence of some 
+$p^\prime$ such that $p^\prime \sqsubset q^\prime$. It then uses the
 homomorphism in $p^\prime \sqsubset q^\prime$ to derive a $p$ such
-that $p \rgse p^\prime$ and $p \in P$.
+that $p \rgse p^\prime$ and $p \in P$. The existence of $P^\prime$ is established by the existence of $p^\prime$, and $P \sqsubset q$ makes $P^\prime$ the actual successor of $P$.
 

### 2014-11-13 tex/results.tex
useless commit message

@@
 In this section we evaluate the effectiveness of the \symtxt{}
-approach at analyzing programs with unbounded complex data input in
-the context of symbolic execution. In order to perform our evaluation
-we implement the \symtxt{} technique and evaluate its efficiacy on
+approach at analyzing programs with unbounded complex input data in
+the context of symbolic execution. To perform our evaluation
+we implement a prototype of the \symtxt{} technique and evaluate its efficiacy on
 three Java data structure artifacts. We compare the results of the
-\symtxt{} approach with other state of the art techniques that
-initialize complex data input symbolically.
+\symtxt{} approach with other state-of-the-art symbolic execution techniques 
+that support analysis of program with complex input data types.
 
-Symbolic Pathfinder
-(SPF)~\cite{visser:ase03,Pasareanu:ISSTA08,pasareanu:ase10,DBLP:journals/ase/PasareanuVBGMR13}. SPF
-is an open source engine for performing symbolic execution on Java
-bytecode. SPF overwrites the concrete execution semantics of Java
+Symbolic Pathfinder (SPF) is an open source engine for performing symbolic 
+execution on Java 
+bytecode~\cite{visser:ase03,Pasareanu:ISSTA08,pasareanu:ase10,DBLP:journals/ase/PasareanuVBGMR13}.
+SPF overwrites the concrete execution semantics of Java
 bytecode to generate a symbolic execution tree. SPF contains an
@@
 
-We create a new extension to SPF in order to implement the~\symtxt{}
-approach. In addition to the operations presented in the Javalite
-semantics, the implementation contains support for operations over
-integers. Examples of bytecode that we overwrite in the SPF engine are
-as follows: (i) field access bytecodes, e.g., GETFIELD and ALOAD
-bytecodes, to implement the field-access and summarize rules
-in~\figref{fig:symInit} and~\figref{fig:fHeap}(a), (ii) the field
-write bytecodes, e.g., PUTFIELD and ASTORE bytecodes, to implement the
-field-write rules in~\figref{fig:fHeap}(a), (iii) checking equality of
-references bytecode, IF\_ACMPEQ and IF\_ACMPNE, to implement the
-equals references-true and references-false rules in~\figref{fig:eqs}
-(iv) linear arithmetic operations on integers, and (v) comparison
-operations on integers. We are currently working on adding support for
+The prototype of  our~\symtxt{} approach is implemented as a new extension to SPF.
+In addition to the operations presented in the Javalite
+semantics (see \secref{sec:precise}), the implementation contains 
+support for operations over
+integers. Examples of bytecode implemented in SPF to support \symtxt{} 
+algorithm include:
+(i) field access bytecodes, e.g., GETFIELD and ALOAD, to implement the 
+field-access and summarize rules
+in~\figref{fig:symInit} and~\figref{fig:fHeap}(a) respectively, (ii) the field
+write bytecodes, e.g., PUTFIELD and ASTORE, to implement the
+field-write rules in~\figref{fig:fHeap}(a), and (iii) equality checking of
+references bytecodes, IF\_ACMPEQ and IF\_ACMPNE, to implement the
+equals references-true and references-false rules in~\figref{fig:eqs}.
+We also implement linear arithmetic operations on integers, and integer
+comparison operations. We are currently working on adding support for
 floating point operations, arrays, and bit-operations.  We use the
-\texttt{jConstraints} library that provides support to handle the heap
+\texttt{jConstraints} library which provides support for handling heap
 constraints~\cite{ase2014-ghilrr,jpf2014-dghirr}. It uses the z3
-solver,~\cite{z3}, as the backend to solve the constraints. We
+solver~\cite{deMouraBjorner08Z3} as the underlying constraint solver. We
 leverage the incremental solving feature in z3 in our experiments. We
@@
 
-\subsection{Case-Study}
-
-The goal of our technique to evaluate the efficiacy of our approach
-with respect to other state of the art algorithms for symbolic
-execution for dealing for unbounded complex data input. We empirically
-evaluate \symtxt{} by considering the following research question:
+The goal of our experiment is to evaluate the efficiacy of our approach
+with respect to other state-of-the-art techniques for symbolic
+execution of programs with unbounded complex data input. We empirically
+evaluate the \symtxt{} algorithm by considering the following research question:
 
 \begin{description}
-\item {\bf RQ1:} How does the cost of using \symtxt{} compare to that
-  of \gsetxt{}, lazier, and lazier\# algorithms?
+\item {\bf RQ1:} How does the cost of the \symtxt{} algorithm compare with
+the \gsetxt{} (lazy), lazier, and lazier\# algorithms?
 
@@
 
-To evaluate we use three Java data structure artifacts (a) Linked List
-(b) Binary Search Tree, and (c) Tree Map. These data structures
-programs are often used to the evaluate symbolic execution algorithms
-with arbitrary heap inputs. The \emph{independent} variable in our
+The evaluation is performed using three Java data structure artifacts 
+(a) Linked List,
+(b) Binary Search Tree, and (c) Tree Map. 
+\sjp{next sentence is bumpy}
+These data structure
+programs are often used to evaluate symbolic execution algorithms
+that analyze software using arbitrary heap inputs. The \emph{independent} variable in our
 study is the algorithm for initializing symbolic references and the
@@
 are: \symtxt{}, \gsetxt{}, lazier, and lazier\#. We also vary the
-$k$-bound for each the algorithms. Note that $k$-bounding bounds the
-length of a reference chain from the root of the heap~\cite{Deng:2006}
+$k$-bound for each of the algorithms. Note that $k$-bounding bounds the
+length of a reference chain from the root of the heap~\cite{Deng:2006}.
 We select three dependent variables and measures for our study: (i)
@@
 \emph{states explored} represents the number of nodes in the symbolic
-execution tree while the \emph{paths generated} represent as the name
-suggests the number of unique paths in the symbolic execution tree.
+execution tree, and the \emph{paths generated} represents 
+the number of unique paths in the symbolic execution tree.
 

### 2014-11-13 tex/precise.tex
committing changes

@@
 \label{sec:precise}
-There are three sets of rewrite rules specific to the summary heap
-algorithm: (i) rules to initialize symbolic references, (ii) rules to complete field
-access and field write, and (iii) rules to check equality and
-inequality of references. The other rules are common to both $\rsym$
-and $\rgse$.
+In this section we present the summary heap algorithm that operates on
+the bipartiate graph described in the previous section.  The summary
+heap algorithm initializes, updates, and partitions the heap. It only
+partitions the heap at points of divergence in the control flow graph
+such as field accesses or writes (exeception control flow due to null
+pointers) or comparisons of references (program control flow). There
+are three sets of rewrite rules specific to the summary heap
+algorithm: (i) rules to initialize symbolic references, (ii) rules to
+complete field access and field write, and (iii) rules to check
+equality and inequality of references. The other rules are common to
+both $\rsym$ and $\rgse$. The complete set of rules are shown in the
+supplemental attached with the paper.
 
@@
 
-Initialization of uninitialized references in the $\rgse$ relation is
-a non-deterministic choice that creates a heap either for
-the initialization of the reference to null, a new instance of
-the object, or to any type compatible object in the input heap (e.g.,
-previously initialized by $\rgse$). In contrast, initialization in the
-$\rsym$ relation creates a single summary heap containing all of the
-possible initialization choices.
+Initialization of references in GSE ($\rgse$ relation) is a
+non-deterministic choice where the reference in the heap is
+initialized to null, a new instance of the object, or to any type
+compatible object in the input heap (e.g., previously initialized by
+$\rgse$). In contrast, initialization in the $\rsym$ relation creates
+a single summary heap containing all of the possible initialization
+choices.
 
@@
 
-The initialization rules, \figref{fig:symInit}, are invoked whenever
-a field containing an uninitialized reference is accessed. The
+The initialization rules, \figref{fig:symInit}, are invoked whenever a
+field pointing to an uninitialized reference is accessed. The
 interaction with the solver in the definition of the rules is denoted
-by $\mathbb{S}(\phi)$ where it returns true if $\phi$ is
-satisfiable. The end rule is active when there is nothing to
+by $\mathbb{S}(\phi)$ which returns true if $\phi$ is satisfiable. The
+summarize-end rule becomes active when there is nothing to
 initialize. This condition is determined by the function
 $\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) =
-\{\lp\phi\ \cfgnt{l}\rp\ ...\}$ which returns constraint-location pairs
-where the field $\cfgnt{f}$ is uninitialized.
+\{\lp\phi\ \cfgnt{l}\rp\ ...\}$ which returns constraint-location
+pairs where the field $\cfgnt{f}$ is uninitialized.
 \[

### 2014-11-13 tex/evaluation.tex
Finished Eval

@@
    \multirow{2}{*}{Method }&\multirow{2}{*}{ $k$ }
-   &\multicolumn{3}{|c|}{Time} &\multicolumn{3}{|c|}{States} &\multicolumn{3}{|c|}{ Paths }\\
+   &\multicolumn{3}{|c|}{Time (seconds)} &\multicolumn{3}{|c|}{States} &\multicolumn{3}{|c|}{ Paths }\\
 								&	&\gsetxt{} & L\#		&SL		&\gsetxt{}	& L\# & SL&\gsetxt{}	& L\# 	& SL\\
@@
 algorithms, respectively. Note that we do no present the results for
-lazier algorithm since they are almost identical to that of lazier\#
-for our examples. Table entries containing - correspond to test runs
-that exceeded the allotted time bounds. Each trial is time bounded to
-10 mins.
+the lazier algorithm since they are almost identical to that of lazier\#
+for our examples. Table entries containing '-' correspond to test runs
+that exceeded the allotted time bound of 10 minutes.
 
-In most tests, run times strongly favor \symtxt{}, especially for
+In most tests, run times strongly favor the \symtxt{} algorithm, especially for
 large $k$-values. Performance improvement ranges from $4.8x$ for
@@
 for certain $k$-bounds a number of experiments completed exploration
-using \symtxt{} in a few seconds whereas \gsetxt{} or lazier\# were
-unable to do, e.g., BinarySearchTree for $k$=4 and LinkedList for
-$k$=8. These results demonstrate the potential of using \symtxt{} as
-an approach to handle data input of complex types. The lower runtimes
-show that we can prove properties using \symtxt{} faster compared to
+using the \symtxt{} algorithm in a few seconds whereas \gsetxt{} or lazier\# were
+unable to finish, e.g., BinarySearchTree for $k$=4 and LinkedList for
+$k$=8. These results demonstrate the potential of using the \symtxt{} algorithm 
+to handle data input for complex types. The lower running times
+show that we can prove properties using the \symtxt{} algorithm faster than
 \gsetxt{}.
@@
 
-Path counts likewise substantially favor \symtxt{}. The number of
-paths explored by \symtxt{} is strictly less than or equal the number
+Path counts likewise substantially favor the \symtxt{} algorithm. The number of
+paths explored by the algorithm is strictly less than or equal to the number
 of paths explored by \gsetxt{} for all test cases. We can use this
@@
 to instantiate a set of concrete heaps to provide as test input. These
-can provide a smaller test suite to achieve control-flow path coverage
+can provide a smaller test suite to achieve control-flow path coverage when
 compared to GSE and Lazier\#.
@@
 not hold true for state counts. State counts can vary between
-algorithms, because states in JPF represent points of nondeterminism,
+algorithms because states in JPF represent points of nondeterminism,
 and each algorithm differs in this regard. For example, \gsetxt{} has
 additional points of nondeterminism during field reads, but in
-contrast references compares are completely deterministic. Thus, in
-example programs with large numbers reference compares, such as
-TreeMap, state counts for lazier\# and \symtxt{} may exceed those for
+contrast reference compares are completely deterministic. Thus, in
+example programs with large numbers of reference compares, such as
+TreeMap, state counts for lazier\# and the \symtxt{} algorithm may exceed those for
 \gsetxt{}. The larger state count, however, does not contribute to the
@@
 
-In summary, it appears that the benefits of avoiding
-initialization-based nondeterminism more than outweigh the increased
+In summary, the benefits of avoiding
+initialization-based non-determinism outweigh the increased
 complexity in the constraints due to the advances made in SMT
-solvers. In fact, \symtxt{} can analyze certain types of programs with
+solvers in these examples. In fact, the \symtxt{} algorithm can analyze certain types of programs with
 orders of magnitude greater efficiency than with \gsetxt{} or

### 2014-11-13 tex/results.tex
Finished Eval

@@
 In this section we evaluate the effectiveness of the \symtxt{}
-approach at analyzing programs with unbounded complex input data in
+algorithm at analyzing programs with unbounded complex input data in
 the context of symbolic execution. To perform our evaluation
-we implement a prototype of the \symtxt{} technique and evaluate its efficiacy on
+we implement a prototype of the algorithm and evaluate its efficiacy on
 three Java data structure artifacts. We compare the results of the
 \symtxt{} approach with other state-of-the-art symbolic execution techniques 
-that support analysis of program with complex input data types.
+that support analysis of programs with complex input data types.
 
@@
 
-The prototype of  our~\symtxt{} approach is implemented as a new extension to SPF.
+The prototype of  our~\symtxt{} algorithm is implemented as a new extension to SPF.
 In addition to the operations presented in the Javalite
@@
 support for operations over
-integers. Examples of bytecode implemented in SPF to support \symtxt{} 
-algorithm include:
+integers including symbolic representations. Examples of bytecode implemented in SPF to support the \symtxt{} algorithm
+include:
 (i) field access bytecodes, e.g., GETFIELD and ALOAD, to implement the 
@@
 The evaluation is performed using three Java data structure artifacts 
-(a) Linked List,
-(b) Binary Search Tree, and (c) Tree Map. 
-\sjp{next sentence is bumpy}
-These data structure
-programs are often used to evaluate symbolic execution algorithms
-that analyze software using arbitrary heap inputs. The \emph{independent} variable in our
+(i) Linked List,
+(ii) Binary Search Tree, and (iii) Tree Map. 
+These are the typical data structures for evaluating symbolic execution algorithms with heap initialization. The \emph{independent} variable in our
 study is the algorithm for initializing symbolic references and the

### 2014-11-13 tex/conclusion.tex
Minor fixes

@@
 
-Although our approach is inspired by the work in the static analysis domain, the heap representations used by those techniques do not lend themselves for use in symbolic execution since they rely on approximations, they are inflexible in what types of relations can be expressed, and they rely on rewriting of constraints.
-In this work, we present a heap summary technique for symbolic execution that maintains exactness, represents arbitrary heap structures without restrictions on aliasing relationships, and supports dynamic on-the-fly initialization of heap structures.
-Despite this unique combination of capabilities, the summary heap technique outperforms  state-of-the-art symbolic execution techniques, and in some cases the performance gains are considerable.
-We believe that performance gains in symbolic execution can naturally benefit a variety of analyses based on symbolic execution, for example, verification of properties, especially those related to the heap, test case generation, program evolution techniques such as directed incremental symbolic execution~\cite{person:pldi2011}, and other back-end analyses.
+Although our approach is inspired by the work in the static analysis
+domain, the heap representations used by those techniques do not lend
+themselves to symbolic execution since they rely on
+approximations, they are inflexible in what types of relations can be
+expressed, and they rely on rewriting of constraints.  In this work,
+we present a heap summary technique for symbolic execution that
+maintains exactness, represents arbitrary heap structures without
+restrictions on aliasing relationships, and supports dynamic
+on-the-fly initialization of heap structures. This unique
+combination of capabilities enables the summary heap to outperform
+state-of-the-art symbolic execution techniques, and in some cases, the
+performance gains are considerable. We believe that performance gains
+in symbolic execution can naturally benefit a variety of analyses
+based on symbolic execution, for example, verification of properties,
+especially those related to the heap, test case generation, program
+evolution techniques such as directed incremental symbolic
+execution~\cite{person:pldi2011}, and other back-end analyses.
 
-In this work, we restricted our presentation of symbolic heaps to constraints reasoning over heap morphology.
-However, in order to be useful for reasoning about real programs, we must also consider the impact of scalar types.
-Our implementation includes limited support for linear operations over integer types, however, we plan to add support for all types of operations such as floating point operations, arrays, and bitvectors.
+In this work, we restricted our presentation of symbolic heaps to
+constraints reasoning over heap morphology. However, in order to be
+useful for reasoning about real programs, we must also consider the
+impact of scalar types. Our implementation includes limited support
+for linear operations over integer types, however, we plan to add
+support for all types of operations such as floating point operations,
+arrays, and bitvectors.
 

### 2014-11-13 tex/results.tex
fixing a duplicate entry in the bibg

@@
 analyzing programs with input of complex data types as demonstrated
-in~\cite{Kiasan07,Deng:2006}. In this work we use the $k$-bounding
+in~\cite{Kiasan07,Kiasan06}. In this work we use the $k$-bounding
 technique that bounds the length of a reference chain from the root of
@@
 The evaluation is performed using three Java data structure artifacts
-(i) Linked List,
-(ii) Binary Search Tree, and (iii) Tree Map. 
-These are the typical data structures for evaluating symbolic execution algorithms with heap initialization. The \emph{independent} variable in our
-study is the algorithm for initializing symbolic references and the
-$k$-bound. The initialization algorithms that we vary in our study
+(i) Linked List, (ii) Binary Search Tree, and (iii) Tree Map.  These
+are the typical data structures for evaluating symbolic execution
+algorithms with heap initialization. The \emph{independent} variable
+in our study is the algorithm for initializing symbolic references and
+the $k$-bound. The initialization algorithms that we vary in our study
 are: \symtxt{}, \gsetxt{}, lazier, and lazier\#. We also vary the
-$k$-bound for each of the algorithms. Note that $k$-bounding bounds the
-length of a reference chain from the root of the heap~\cite{Deng:2006}.
-We select three dependent variables and measures for our study: (i)
-time, (ii) states explored, and (iii) paths generated. The \emph{time}
-is the total time taken by each algorithm to explore the symbolic
-execution tree as well as total constraint solving time. The
-\emph{states explored} represents the number of nodes in the symbolic
-execution tree, and the \emph{paths generated} represents 
-the number of unique paths in the symbolic execution tree.
+$k$-bound for each of the algorithms. Note that $k$-bounding bounds
+the length of a reference chain from the root of the
+heap~\cite{Kiasan06}.  We select three dependent variables and
+measures for our study: (i) time, (ii) states explored, and (iii)
+paths generated. The \emph{time} is the total time taken by each
+algorithm to explore the symbolic execution tree as well as total
+constraint solving time. The \emph{states explored} represents the
+number of nodes in the symbolic execution tree, and the \emph{paths
+  generated} represents the number of unique paths in the symbolic
+execution tree.
 

### 2014-11-13 tex/bisimulation.tex
updated the proofs

@@
-\section{Bisimilarity Relation}
+\section{Bisimilarity Proof}
 \label{sec:bisim}
@@
 
-The proof only reasons about well-formed states: heaps are
-deterministic, type consistent, with no dangling references, and it
-knows about any references in the environment, expression, or
-continuation. Well-formed states always have a successor unless it is
-the end of the program execution. It is trivial to show that every
-rule in the transition relation preserves well-formedness.
+The proof only reasons about well-formed states, which have
+deterministic, type-consistent heaps, and feasible environments, expressions, and
+continuations. Well-formed states always have successors unless at the end of a 
+program execution. It is trivial to show that the set of well-formed states is closed
+under the transition relation.
 
@@
 $$
-The definition embodies the notion of splitting groups of heaps at
-certain operations. The set $P$ at a field access after base reference is known, for example, has two
-potential successors: a non-null and null reference. The $\rsgse$ relation has two successors at that point to divide $P$ into the two outcomes. In contrast, the
+This definition embodies the notion of splitting groups of heaps at
+certain operations. For example, suppose we have a set $P$ containing a single state $p$
+with all references uninitialized. If $p$ is a field access state, it has two
+potential successors: one with a non-null reference, and one with a null reference. 
+The $\rsgse$ relation has two successors at that point to divide $P$ into the two outcomes. In contrast, the
 set $P \rgse^\com P^\prime$ only has a single successor since anything in $\rightarrow_\com$ is not related to control flow (e.g., variable look up, creating continuations, etc.).

### 2014-11-13 tex/proofs.tex
Reworked supplemental upto definitions and proofs.
updated the proofs

--- 2014-11-09 tex/proofs.tex
@@
 \section{Proofs}
-
-\input{definitions}
-
-\subsection{Theorems}
+\subsection{Lemmas}
 
@@
 
+\begin{theorem}
+If $R \subseteq F\sim(R)$, then $R$ is a bisimulation.
+\label{lem:bisim}
+\end{theorem}
+The proof can be found in any good text on bisimulation.
+%For the proof, we refer the reader to \cite{Sangiorgi:2011}
+
+\begin{theorem}
+
+\end{theorem}
+
+%\begin{lemma}[$\sqsubset$ is a bisimulation for $\rinit$ and $\rsum$]
+%\label{lem:init}
+%If $s_\sym \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$ for symbolic state $s_\sym = \lp \cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \phi_\sym\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$, initial state $s_0$, and control flow path $\pi_n$, and if there exists some intermediate state state $s_\sym^\prime$ such that $(\cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C}) \rsum^* (\cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C})$, then:
+% $$s_\sym^\prime \cong \{\forall s_\gse^\prime | \exists s_\gse (s_\gse \sqsubset s_\sym \wedge (s_\gse \rinit^* s_\gse^\prime) ) \}$$
+%\end{lemma}
+
 \begin{lemma}[$\sqsubset$ is a bisimulation for $\rinit$ and $\rsum$]
 \label{lem:init}
-If $s_\sym \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$ for symbolic state $s_\sym = \lp \cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \phi_\sym\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$, initial state $s_0$, and control flow path $\pi_n$, and if there exists some intermediate state state $s_\sym^\prime$ such that $(\cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C}) \rsum^* (\cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C})$, then:
- $$s_\sym^\prime \cong \{\forall s_\gse^\prime | \exists s_\gse (s_\gse \sqsubset s_\sym \wedge (s_\gse \rinit^* s_\gse^\prime) ) \}$$
+If $P \sqsubset q$ and if $\exists q^\prime (q \rsym q^\prime )$ , then $\exists 
 \end{lemma}
@@
 %proof for field write
-\begin{lemma}[Exactness of Field Write Rule]
-\label{lem:write}
-If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{FW}$ and $s_\gse \sqsubset s_\sym$, then:
-\begin{equation}
-\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
-\end{equation}
-and
-\begin{equation}
-\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
-\end{equation}
+%\begin{lemma}[Exactness of Field Write Rule]
+%\label{lem:write}
+%If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{FW}$ and $s_\gse \sqsubset s_\sym$, then:
+%\begin{equation}
+%\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
+%\end{equation}
+%and
+%\begin{equation}
+%\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
+%\end{equation}
+%\end{lemma}
+
+\begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{W{\footnotesize RITE}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
+If $P \in 2^{S_\mathit{FW}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisumlation.
+\label{lem:access}
+$$
+\forall P \in 2^{S_\mathit{FW}}\ (P \sqsubset q \Rightarrow (P\ q) \in F_\sim(\sqsubset))
+$$
 \end{lemma}
+
 \begin{proof}
@@
 
-\begin{lemma}[$\rsum^*$ produces well-formed heaps]
+\begin{lemma}[$\rsum^*$ preserves heap determinism]
 \label{lem:S-determ}
@@
 
-\begin{lemma}[$\rightarrow_\mathit{FA}$ produces well-formed heaps]
+\begin{lemma}[$\rightarrow_\mathit{FA}$ preserves heap determinism]
 \label{lem:FA-determ}
@@
 
-\begin{lemma}[$\rightarrow_\mathit{FW}$ produces well-formed heaps]
+\begin{lemma}[$\rightarrow_\mathit{FW}$ preserves heap determinism]
 \label{lem:FW-determ}
@@
 
-\begin{lemma}[$\rcom$ produces well-formed heaps]
+\begin{lemma}[$\rcom$ preserves heap determinism]
 \label{lem:J-determ}
@@
 
-\begin{lemma}[Exactness of Reference Compare Rule]
-\label{lem:compare}
-If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{RC}$ and $s_\gse \sqsubset s_\sym$, then:
-\begin{equation}
-\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
-\end{equation}
-and
-\begin{equation}
-\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
-\end{equation}
+%\begin{lemma}[Exactness of Reference Compare Rule]
+%\label{lem:compare}
+%If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{RC}$ and $s_\gse \sqsubset s_\sym$, then:
+%\begin{equation}
+%\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
+%\end{equation}
+%and
+%\begin{equation}
+%\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
+%\end{equation}
+%\end{lemma}
+
+\begin{lemma}[\textrm{E{\footnotesize QUALS}} } preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
+If $P \in 2^{S_\mathit{E}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisumlation.
+\label{lem:access}
+$$
+\forall P \in 2^{S_\mathit{E}}\ (P \sqsubset q \Rightarrow (P\ q) \in F_\sim(\sqsubset))
+$$
 \end{lemma}
-There are two rules that apply to state $s_\sym$, one for the $\cfgt{true}$ branch and one for the $\cfgt{false}$ branch.
+
+There are two rules that apply to state $s_\sym \in 2^{E}$, one for the $\cfgt{true}$ branch and one for the $\cfgt{false}$ branch.
 Since the proofs for both rules are nearly identical, for brevity we will only show the proofs for the case for the $\cfgt{true}$ branch.
@@
 
-\begin{lemma}[Exactness of New Rule]
-\label{lem:new}
-If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{NW}$ and $s_\gse \sqsubset s_\sym$, then:
-\begin{equation}
-\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
-\end{equation}
-and
-\begin{equation}
-\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
-\end{equation}
+%\begin{lemma}[Exactness of New Rule]
+%\label{lem:new}
+%If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{NW}$ and $s_\gse \sqsubset s_\sym$, then:
+%\begin{equation}
+%\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
+%\end{equation}
+%and
+%\begin{equation}
+%\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
+%\end{equation}
 
-\begin{proof}
-The proof is left as an exercise to the reader.
-\end{proof}
+%\end{lemma}
 
-\end{lemma}
+%
+%\begin{proof}
+%The proof follows immediately from the rule.
+%\end{proof}
 

### 2014-11-13 tex/abstract.tex

@@
 problem.  In this work, we present a summary heap approach which takes
-inspiration from the static analysis domain and defines a bipartiate
+inspiration from the static analysis domain and defines a bipartite
 graph to encode multiple heaps in single representation, which, unlike

### 2014-11-13 tex/precise.tex

@@
 In this section we present the summary heap algorithm that operates on
-the bipartiate graph described in the previous section.  The summary
+the bipartite graph described in the previous section.  The summary
 heap algorithm initializes, updates, and partitions the heap. It only
 partitions the heap at points of divergence in the control flow graph
-such as field accesses or writes (exeception control flow due to null
+such as field accesses or writes (execeptional control flow due to null
 pointers) or comparisons of references (program control flow). There
@@
 
-In~\figref{fig:symInit}, given the unitialized set $\Lambda$ for
+In~\figref{fig:symInit}, given the uninitialized set $\Lambda$ for
 field $f$, the $\mathit{min}_l$ function returns
@@
 heap as order determines the number of aliasing choices available). And (iv) $\theta_\mathit{orig}$  implements conditional initialization to preserve the
-original heap structure. This property is needed for the bisumulation. 
+original heap structure. This property is needed for the bisimulation. 
 These sets are added into the heap on $\cfgnt{r}_f$ after the fields for $\cfgnt{l}_f$ are initialized to $\cfgnt{r}_\mathit{un}$.

### 2014-11-13 tex/related.tex
changes so far

@@
 
-While there exists a large body of work related to summary heaps,
-we discuss work most closely related, including techniques for
-scaling symbolic execution of programs with complex data types,
-heap summary techniques, ...
-
-%Recent years have seen a significant growth in research projects based
-%on symbolic execution, first introduced in the 1970's by
-%Clarke~\cite{Clarke:76} and King~\cite{King:76}.
+In this section we discuss some closely related works, including
+techniques for scaling symbolic execution of programs with complex
+data types and heap summary techniques. Note that there is a huge body
+of work on analyzing programs with heaps in the domain of static
+analysis, testing, and verification.
 
 Initial work on symbolic execution largely focused on checking
-properties of imperative programs with primitive
-primitive types~\cite{Clarke:76,King:76}. Several recent projects 
-generalized the core
-idea of symbolic execution which enabled it to be applied to
+properties of imperative programs with primitive primitive
+types~\cite{Clarke:76,King:76}. Several recent projects generalized
+the core idea of symbolic execution which enabled it to be applied to
 programs with more general types, including references and
@@
 Our work leverages the core idea in generalized symbolic execution
-with lazy initialization to construct the heap on-the-fly during symbolic
-execution, but avoids the nondeterminism introduced by GSE by
-constructing a summary heap and will generally create fewer paths
-than GSE techniques.
+with lazy initialization to construct the heap on-the-fly during
+symbolic execution, but avoids the nondeterminism introduced by GSE by
+constructing a summary heap and will generally create fewer paths than
+GSE techniques.
 
-%These projects have
-%pursued three primary research directions to enhance traditional
-%symbolic execution: (1)~to improve its
-%effectiveness~\cite{Godefroid:PLDI05,Sen:FSE05,CadarEngler05EXE,KiasanKunit,Pasareanu:2011};
-%(2)~to improve its
-%efficiency~\cite{AnandETAL2009AbsSymExe,KhurshidSuen2005AbsSymExe,Godefroid:POPL07,Inkumsah:2008,ChangPhD10DataFlowSymbolicExecution,Santelices:ISSTA10,Visser:2012};
-%and (3)~to improve its
-%applicability~\cite{Person:FSE08,KhurshidETAL05RepairingStructurally,CsallnerETAL08DySy,SeoETAL06EnergyConsumptionFrameworkDistributedJava,Geldenhuys:2012,Ma:2011}.
-%analyzing programs containing complex data structure with unbounded
-%domains continues to be challenging
-%for symbolic execution techniques.  Generalized symbolic execution \cite{GSE03}
-%with lazy initialization set the path to materializing fields
-%concretely. Subsequent improvements to the method
-%\cite{Deng:2006,Deng:2007} to reduce path explosion by delaying path
-%splitting over aliasing choices for as long as possible. However,
-%since all of the above methods introduce nondeterminism during field
-%reads and writes, they all contribute to path explosion to some
-%extent.
+Pex is a tool for dynamic symbolic execution for .NET programs. In
+order to handle data structures Pex uses a theory of arrays and does
+not initialization~\cite{export:81193}.  It is required to have a
+constraint solver that handles the theory for unbounded arrays for
+this approach to be tractable. It would be an interesting comparision
+to perform in future work.
 
-% Since our heap representation does not introduce any nondeterminism
-%beyond the level in standard symbolic execution, it will generally
-%create fewer paths than these methods, sometimes by a wide margin.
+A number of static analysis techniques have been proposed to support
+reasoning about input heap structures. The technique most closely
+related to (and which served as inspiration for) our approach is the
+procedure summary proposed by Dillig et al. to support modular
+reasoning~\cite{Dillig:2011}.  While their method improves path
+sensitivity over standard static analysis methods, it remains limited
+by a statically-generated symbolic input heap and it cannot adapt to
+path-sensitive heap properties of the input heap.
 
-%\subsection{Model Checking} Need to talk about Bounded Model
-%Checking, etc.
-
-%\subsection{Static Analysis}
-
-A number of static analysis techniques have been proposed
-to support reasoning about input heap structures~\cite{}. The technique
-most closely related to (and which served as inspiration for) our approach
-is the procedure summary proposed by Dillig et al. to support modular
-reasoning~\cite{Dillig:2011}.  While
-their method improves path sensitivity over standard static
-analysis methods, it remains limited by a statically-generated
-symbolic input heap and it cannot adapt to path-sensitive heap
-properties of the input heap.
-
-% These techniques are usually over-approximations, often have
-% difficulty reasoning about path-sensitive properties, or cannot
-% reason about programs with recursive data structures. Moreover,
-% static analysis methods are seldom useful for test-case generation.
-
-%. Elements of their technique that are similar to ours include;
-%references guarded by constraint expressions, conditional write
-%semantics, and a general aversion to path splitting. However, their
-%method is limited by most of the standard problems with static
-%analysis techniques, including path sensitivity, imprecision, and
-%recursive data structures.
-
-% Thus, their method cannot determine a priori which nodes in the
-%input heap are actually accessed by the program. It may potentially
-%generate input heaps containing a significant number of nodes that
-%have no impact on program execution.
-
-%\subsection{Heap Representations}
-
-%One significant line of work on representing heaps is shape
-%analysis. Shape analysis attempts to reduce the complexity of the
-%heap by combining multiple nodes with similar properties into summary
-%nodes. The summary nodes typically establish may/must constraints
-%over the heap structure, and typically represent an overapproximation
-%of the represented heap. As such, program evaluations using shape
-%analysis representations are prone to reporting large numbers of
-%false positives.
-
-Other techniques have been proposed to model
-references using sets of guarded
-locations~\cite{Xie:2005,Cherem:2007,Dillig:2011,Sen:2014}. These sets,
-sometimes known as value sets or value summaries, allow multiple heaps
-to be represented simultaneously with a higher degree of precision
-than afforded by shape analysis. However, some of these previous
-attempts~\cite{Xie:2005,Cherem:2007} utilize non-local recursive
-definitions for objects. The impact of such an approach is two-fold. 
-First, these techniques must use approximations
-to resolve reference inequalities, resulting in false positives in the
-results. Second, these techniques are incapable of reasoning about
-heaps with recursive data structures due to the potential for infinite
-recursion during dereferencing. This means that either a large class
-of data structures must be avoided, or a large class of behaviors must
-be ignored. In our heap representation, object descriptions are
+Other techniques have been proposed to model references using sets of
+guarded
+locations~\cite{Xie:2005,Cherem:2007,Dillig:2011,Sen:2014}. These
+sets, sometimes known as value sets or value summaries, allow multiple
+heaps to be represented simultaneously with a higher degree of
+precision than afforded by shape analysis. However, some of these
+previous attempts~\cite{Xie:2005,Cherem:2007} utilize non-local
+recursive definitions for objects.  In our heap representation, object descriptions are
 entirely local, thus avoiding these pitfalls. Other methods
@@
 
+There is also a large body of work on generating tests for
+object-oriented programs that use a variety of techniques to generate
+heap structures to test object-oriented
+programs~\cite{xie2005symstra,xie2004rostra,boyapati2002korat,artzi2006finding}.
 Another line of work in heap representation lies in identifying
 isomorphic heap structures in order to avoid exploring redundant
-paths. Examples of such methods include Korat~\cite{Milicevic:2007},
-XXX, and YYY. These
-methods are generally focused on the morphology of the heap apart
-from the external constraint problems encountered during
-program execution, and as such, are largely orthogonal to this work.
+paths~\cite{milicevic2007korat}.  These methods are generally focused
+on the morphology of the heap apart from the external constraint
+problems encountered during program execution, and as such, are
+largely orthogonal to this work. Recent work shows that the need for
+reasoning about heap structures is an important
+problem~\cite{barr2013collecting}. Delta execution is another work
+that combines states for object-oriented programs~\cite{d2008delta}.
+
+%The impact of such an approach is two-fold.  First, these techniques
+%must use approximations to resolve reference inequalities, resulting
+%in false positives in the results. Second, these techniques are
+%incapable of reasoning about heaps with recursive data structures due
+%to the potential for infinite recursion during dereferencing. This
+%means that either a large class of data structures must be avoided,
+%or a large class of behaviors must be ignored.

### 2014-11-13 tex/results.tex
changes so far

@@
 
-The goal of our experiment is to evaluate the efficiacy of our approach
-with respect to other state-of-the-art techniques for symbolic
-execution of programs with unbounded complex data input. We empirically
-evaluate the \symtxt{} algorithm by considering the following research question:
-
-\begin{description}
-\item {\bf RQ1:} How does the cost of the \symtxt{} algorithm compare with
-the \gsetxt{} (lazy), lazier, and lazier\# algorithms?
+The goal of our experiment is to evaluate the efficiacy of our
+approach with respect to other state-of-the-art techniques for
+symbolic execution of programs with unbounded complex data input. We
+empirically evaluate the \symtxt{} algorithm by considering the
+following research question: How does the cost of the \symtxt{}
+algorithm compare with the \gsetxt{} (lazy), lazier, and lazier\#
+algorithms?
 
@@
 %  approaches that can leverage its output?
-\end{description}
+%\end{description}
 

### 2014-11-13 tex/evaluation.tex
adding the evaluation

@@
   \end{tabular}}
-  \caption{Comparing the efficiency of the summary heap appraoch to GSE and Lazier\# algorithms.}
+  \caption{Comparing the efficiency of the summary heap approach to GSE and Lazier\# algorithms.}
   \label{tab:results}
@@
 each of the algorithms. The headings \gsetxt{}, L\#, and SL correspond
-to the Generalized Symblic Execution, lazier\#, and \symtxt{}
+to the Generalized Symbolic Execution, lazier\#, and \symtxt{}
 algorithms, respectively. Note that we do no present the results for
@@
 
-Curiously, the pattern established with run-times and path counts does
-not hold true for state counts. State counts can vary between
-algorithms because states in JPF represent points of nondeterminism,
-and each algorithm differs in this regard. For example, \gsetxt{} has
-additional points of nondeterminism during field reads, but in
+The number of states varies between algorithms, for example, \gsetxt{}
+has additional points of nondeterminism during field reads, but in
 contrast reference compares are completely deterministic. Thus, in
 example programs with large numbers of reference compares, such as
-TreeMap, state counts for lazier\# and the \symtxt{} algorithm may exceed those for
-\gsetxt{}. The larger state count, however, does not contribute to the
-runtime of the technique.
+TreeMap, state counts for lazier\# and the \symtxt{} algorithm may
+exceed those for \gsetxt{}. We observed that the additional states
+generated by the summary heap algorithm are unsatisfiable at the point
+of reference compares; this is why they do not contribute any
+additional branches in the final symbolic execution tree. Furthermore,
+the larger state count does not impact the overall runtime of the
+technique.
+
+%The additional states generated by summary heap are unsatisfiable
+%which is why they do not add nodes in the final symbolic execution
+%tree. Furthermore, the larger state count does not impact the overall
+%runtime of the technique.
 

### 2014-11-13 tex/intro.tex

@@
 conditions computed by symbolic execution characterize the observed
-program execution behaviours and have been used as an enabling
+program execution behaviors and have been used as an enabling
 technology for various applications, e.g., regression
@@
 deferring materialization of objects on the concrete heap until they
-are needed for the analysis to proceed. The materilization creates
+are needed for the analysis to proceed. The materialization creates
 additional non-deterministic choice points in the symbolic execution

### 2014-11-13 tex/bisimulation.tex
Minor cuts

@@
 a new way to initialize heap objects that avoided initializing heaps
-that traverse the same control flow paths. The thought was to group together heaps
-into equivalence classes: all the heaps that followed the same control
-flow path to a given point of execution would be in the same
-equivalence class at that point of execution. An equivalence class
-splits at branches, where the program actually differentiates heaps.
-
-The proof only reasons about well-formed states, which have
+that traverse the same control flow paths. The proof only reasons about well-formed states, which have
 deterministic, type-consistent heaps, and feasible environments, expressions, and

### 2014-11-13 tex/precise.tex
Minor cuts

@@
 \label{sec:precise}
-In this section we present the summary heap algorithm that operates on
-the bipartite graph described in the previous section.  The summary
-heap algorithm initializes, updates, and partitions the heap. It only
+The summary
+heap algorithm only
 partitions the heap at points of divergence in the control flow graph

### 2014-11-13 tex/results.tex
argh

@@
 
-The prototype of  our~\symtxt{} algorithm is implemented as a new extension to SPF.
-In addition to the operations presented in the Javalite
-semantics (see \secref{sec:precise}), the implementation contains 
-support for operations over
-integers including symbolic representations. Examples of bytecode implemented in SPF to support the \symtxt{} algorithm
-include:
-(i) field access bytecodes, e.g., GETFIELD and ALOAD, to implement the 
-field-access and summarize rules
-in~\figref{fig:symInit} and~\figref{fig:fHeap}(a) respectively, (ii) the field
-write bytecodes, e.g., PUTFIELD and ASTORE, to implement the
-field-write rules in~\figref{fig:fHeap}(a), and (iii) equality checking of
-references bytecodes, IF\_ACMPEQ and IF\_ACMPNE, to implement the
-equals references-true and references-false rules in~\figref{fig:eqs}.
-We also implement linear arithmetic operations on integers, and integer
-comparison operations. We are currently working on adding support for
-floating point operations, arrays, and bit-operations.  We use the
+The prototype of our~\symtxt{} algorithm is implemented as a new
+extension to SPF.  In addition to the operations presented in the
+Javalite semantics (see \secref{sec:precise}), the implementation
+contains support for operations over integers.
+% including symbolic
+%representations.
+% Examples of bytecode implemented in SPF to support the \symtxt{} algorithm
+%include:
+%(i) field access bytecodes, e.g., GETFIELD and ALOAD, to implement the 
+%field-access and summarize rules
+%in~\figref{fig:symInit} and~\figref{fig:fHeap}(a) respectively, (ii) the field
+%write bytecodes, e.g., PUTFIELD and ASTORE, to implement the
+%field-write rules in~\figref{fig:fHeap}(a), and (iii) equality checking of
+%references bytecodes, IF\_ACMPEQ and IF\_ACMPNE, to implement the
+%equals references-true and references-false rules in~\figref{fig:eqs}.
+%We also implement linear arithmetic operations on integers, and integer
+%comparison operations.
+We are currently working on adding support for floating point
+operations, arrays, and bit-operations.  We use the
 \texttt{jConstraints} library which provides support for handling heap
 constraints~\cite{ase2014-ghilrr,jpf2014-dghirr}. It uses the z3
-solver~\cite{deMouraBjorner08Z3} as the underlying constraint solver. We
-leverage the incremental solving feature in z3 in our experiments. We
-also implement other optimizations that cache and re-use solutions to
-previous constraints. These optimizations are an important part of our
-implementation because only small portions of the heap constraint
-changes from one state to another.
+solver~\cite{deMouraBjorner08Z3} as the underlying constraint
+solver. We leverage the incremental solving feature in z3 in our
+experiments. We also implement other optimizations that cache and
+re-use solutions to previous constraints. These optimizations are an
+important part of our implementation because only small portions of
+the heap constraint changes from one state to another.
 

### 2014-11-13 tex/results.tex
results

@@
 the context of symbolic execution. To perform our evaluation
-we implement a prototype of the algorithm and evaluate its efficiacy on
+we implement a prototype of the algorithm and evaluate its efficacy on
 three Java data structure artifacts. We compare the results of the
@@
 
-The goal of our experiment is to evaluate the efficiacy of our
+The goal of our experiment is to evaluate the efficacy of our
 approach with respect to other state-of-the-art techniques for

### 2014-11-13 tex/bisimulation.tex
Fixed

@@
 in this instance since it captures the notion of $q$ as a set of
-states \cite{GSE:barbedbisimulation}.
+states \cite{Sangiorgi:2011}.
 

### 2014-11-13 tex/javalite.tex
Removed extra space on comma

@@
 where execution starts. The only primitive type in Javalite is
-Boolean. Classes have non-primitive fields , $([\cfgnt{C}\ \cfgnt{f}]\ ...)$, and
+Boolean. Classes have non-primitive fields, $([\cfgnt{C}\ \cfgnt{f}]\ ...)$, and
 methods, $(\cfgnt{M}\ ...)$.\footnote{Summary heaps are able to support non-primitive fields (see \secref{sec:eval}).

### 2015-01-15 cav-2015-tex/abstract.tex
Added cav

--- 2014-11-13 tex/abstract.tex
@@
 previously possible.
-
-\begin{comment}
-A fundamental challenge of using symbolic execution for software
-analysis has been the treatment of dynamically allocated data.
-State-of-the-art techniques have addressed this challenge through
-either (a) the use of summaries that over-approximate possible heaps, or
-(b) by materializing a concrete heap lazily during generalized
-symbolic execution. In this work, we present a novel heap
-initialization and analysis technique which takes inspiration from
-both approaches and constructs precise heap summaries lazily during
-symbolic execution.  Our approach is 1) \emph{scalable}: it reduces the
-points of non-determinism compared to generalized symbolic execution
-and explores each control-flow path only once for any given set of
-isomorphic heaps, 2) \emph{precise}: at any given point during symbolic
-execution, the symbolic heap represents the exact set of feasible
-concrete heap structures for the program under analysis, and 3)
-\emph{expressive}: the symbolic heap can represent recursive data
-structures. We demonstrate the precision and scalability of our
-approach by implementing it as an extension to the Symbolic PathFinder
-framework for analyzing Java programs.
-\end{comment}
-
-%and by using 
-%materializing objects on the concrete heap ``as needed'' and
-%using non-deterministic choice points to explore each feasible
-%concrete heap configuration.
-
-%Because analysis of the materialized
-%heap locations relies on concrete program semantics, the lazy
-%initialization approach exacerbates the state space explosion
-%problem that limits the scalability of symbolic execution.
-%In this work we present a novel approach for lazy symbolic execution
-%of heap manipulating software which utilizes 
-%a fully symbolic heap constructed on-the-fly during symbolic execution.
-%Our approach is 1) \emph{scalable} -- it does not
-%create the additional points of non-determinism
-%introduced by existing lazy initialization techniques and it explores
-%each execution path only once for any given set of isomorphic heaps,
-%2) \emph{precise} -- at any given point during symbolic execution, 
-%the symbolic heap represents the exact set of feasible
-%concrete heap structures for the program under analysis, and
-%3) \emph{expressive} -- the symbolic heap can represent recursive data structures 
-%and heaps resulting from loops and recursive control structures in the code. 
-%We report on a case-study of an implementation of our technique in the
-%Symbolic PathFinder tool to illustrate its scalability, precision
-%and expressiveness. We also discuss how test case generation -- a common
- %use for symbolic execution results -- can benefit from symbolic
- %execution which uses a fully symbolic heap.

### 2015-01-15 cav-2015-tex/motivation.tex
Added cav

\paragraph{Why would you want to do lazy initialization, instead of using pre-generated input heaps?}
\begin{compactdesc}
\item[Generate a minimal set of independent test inputs:] 
If you generate a fixed set of 1000 data structures at the beginning,
you don’t know which of those 1000 data structures will actually
result in different execution paths. Since many inputs may result in
identical execution paths, the “path-independence” of those inputs is
uncertain. Consider the case of a linked list, where each node
contains two references, one for a data object, and one for the next
node in the list. Suppose you want to test a function that makes
structural transformations on linked lists. Perhaps your function
removes loops, counts the number of nodes, or pops the first node off
the list. If you tried every possible linked list as an input to your
function, you would find that many of your lists led to identical
execution paths, simply because the “data” reference was never
accessed. Without lazy initialization, you would have to know
beforehand which parts of your data structure will get accessed, and
which will not. With lazy initialization, we test only independent
sets of inputs, without any prior knowledge of the data structure. In
fact, we generate a minimal set of independent test inputs within the
given bounds.

\item[Make per-path search decisions:] 
With lazy initialization, we can make search decisions dynamically
based on the machine state. For example, suppose you want to limit the
number of nodes that any given execution path might attempt to
access. Note that this is very different than bounding the input heap
to a set size. Without lazy initialization, you would have to know
exactly which reference chains any given execution path will follow
beforehand. However, with lazy initialization, it is simple to keep
track of the number of nodes that have been accessed at run-time, and
limit the size of the lazy-initialized input heap dynamically. Some
examples of types of per-path bounding metrics which are possible
using lazy initialization include: length of reference chains, number
of cycles in the graph, number of nodes accessed by the program, the
amount of memory available to the test machine, total number of memory
reads/writes. (Note that some of these things may be difficult to
relate exactly back to the concrete heaps)

\item[Generate test inputs based on per-path execution properties:] 
Per-path search bounds can be combined with the test-input generation
capability to answer questions like “Which test inputs will generate
fewer than 20 memory read operations?”.

\item[Cope with certain types of unbounded inputs:] 
In some cases, lazy initialization can exactly model program behavior
even when the size of the input heap is unbounded. For example,
suppose we have a function that pushes a node on to the front of a
linked list. In this case, lazy initialization will correctly model
all program behaviors for linked lists of arbitrary size.

\item[Less work for the programmer:] 
You don’t need to generate any special data invariants specific to the
analysis. They are generated on-the-fly from invariants written in
normal program code.

\item[Delay choices about data structures:] 
If you are exploring a program with 1000 possible input structures, an
execution tree with 1000 leaves will have fewer states that a set of
1000 separate paths. Even in the case where all paths are merged into
a single path, the constraints on the earlier states will be simpler
if you don’t have to distinguish all 1000 possible inputs.
\end{compactdesc}

\paragraph{There are lots of symbolic heap representations. Why hasn’t anyone done lazy initialization before?}
\begin{compactitem}
\item[Inductively Defined Symbolic Locations:] 
Earlier techniques using similar representations (SATURN, the Dilligs)
have been limited by inductively defined symbolic locations. Suppose
you were to define symbolic locations as being either a method
parameter or a dereferenced symbolic location. This works well in
heaps without loops, because dereferenced symbolic location are
guaranteed to be “smaller” (closer to the root of the heap) than their
targets. However, this inductive definition breaks down in the case of
loops. Some recent work uses with non-recursive data structures,
(e.g. Koushik’s stuff), but they don’t do lazy initialization.

\item[Flat memory models:] 
Many prior techniques make no special treatment for object-oriented
memory models (Boogie, PEX, etc.). Typically the memory is modeled as
a flat address space instead of a more high-level heap. There are many
types of interactions that are possible in this memory model, such as
pointer arithmetic and array indexing, which are not possible in an
object-oriented system. Accounting for these interactions make lazy
initialization challenging to implement.

\item[Path splitting during memory access:] 
Several existing methods for doing lazy initialization during symbolic
execution introduce nondeterminism during memory access operations
(GSE, Lazier\#, etc.). These new points of nondeterminism contribute
to path explosion, rendering these methods infeasible for all but the
smallest heap fragments.
\end{compactitem}

\paragraph{What’s special about using a graph representation? Why not represent the heap as an equation?}
\begin{compactdesc}
\item[Fewer Solver Calls:] 
With a graph-based representation, we can answer structural questions
about the heap without consulting the solver. For example, when
comparing two references, if the intersection of their value sets is
empty, we can surmise that they are in all cases unequal. Some heap
properties that may be resolvable from structural properties alone
are: equivalence of references, connectivity of heap fragments, upper
bounds on pointer chain length, upper bounds on number of objects in
the heap, and the absence of loops / aliasing.

\item[Non-inductive definition of references:] 
A graph-based representation can provide a non-inductive definition of
the heap. Equation-based systems for modeling memories tend to
introduce lots of auxiliary variables, which can complicate
dereferencing and may place restrictions on heap morphology.  
\end{compactdesc}

\paragraph{What’s special about the “bipartite graph” representation?}
\begin{compactdesc}
\item[Object-oriented heap:] 
Our bipartite graph is a non-recursive model more suited to OO
programming than one based on pointers. In many OO programming
environments, you don’t have to worry about nasty things like pointer
arithmetic, so a cleaner model reduces wasted effort. You might say
the bipartite graph is how we’ve modeled a “theory of objects” for
heap constraint problems.
\end{compactdesc}

### 2015-01-15 cav-2015-tex/rw.tex
Added cav

\section{Related Work}
\noindent\textbf{A Lightweight Symbolic Virtual Machine for Solver-Aided Host Languages Emina Torlak and Ras Bodik. Programming Language Design and Implementation} (PLDI'14)

\noindent{\textbf{What the reviewers said:} \emph{"the paper [Torlak et al. 2014] definitely shows how to apply the same compact representation to symbolic execution."}

\noindent\textbf{What I think:} They aren’t really breaking any ground with the heap representation here. It’s pretty much the same thing as what was in SATURN. The main focus of the paper is on a VM for mixed symbolic-concrete programming languages. It’s probably worth citing, if only as part of a list of similar techniques.

\noindent\textbf{How this is similar to SymHeap:}

\noindent\textbf{How this is different from SymHeap:}
\begin{compactenum}
\item They don’t do lazy initialization. \emph{"The shape of all data structures remains concrete during SVM evaluation."}
\item There are no real bounding mechanisms, and they assume that programs are self-finitizing.
\begin{compactitem}
\item They don’t really handle recursion or loops.
\item They can’t make any sort of heap-specific bounds
\item They try to sell this as a feature, by the way, by claiming that they don’t “artificially finitize executions by explicitly bounding the depth of recursion.” That’s the nicest cover-up for a program that fails to terminate I’ve ever heard.
\end{compactitem}
\item Their representation is different. Although, they have value
  sets, I don’t see a bipartite graph, locations, fields, etc. This is
  worrisome since the reviewer was certain this is the same
  representation as ours.
\item They do weird domain-specific programming languages instead of our java-like language.
\end{compactenum}

Generating precise and concise procedure summaries, POPL’2008

What the reviewer said: This was in a general list of “missing” related work

What I think: This paper is about procedure summaries. It looks like they are concerned with a more general type of problem than we are with the heap, and that the heap-related stuff is a specialization of their framework. It’s worth citing, as an example of a global access-path style representation.

How this is similar to SymHeap:
1) Uses sets of guarded values, which they call micr-transformers. Their “micro-transformers” can be made to look lot like our references. A dereferencing operation may be performed using a “composition of micro-transformers”.

How this is different from SymHeap: 
1) The heap is stored as global access paths, related directly to variables. Thus, they don’t have any explicit local representation of the heap, and determining reachability is impossible without consulting the solver.

2) Potential aliasing relationships are determined in a path-insensitive manner, prior to program execution, by means of power sets.

3) It doesn’t look like they do lazy initialization. The size of parameter sets is fixed at the beginning of the program

Boogie: A Modular Reusable Verifier for Object-Oriented Programs FMCO'2005

What the reviewer said: This was in a list of “missing” related work, categorized as “work on precise memory models for verification-condition generation”.

What I think: Boogie doesn’t have a built-in heap encoding. It uses a 2d array to model the heap, and compiles the entire program-correctness problem into a single constraint equation, which it ships off to a constraint solver. It’s a very different sort of analysis. Worth mentioning as part of a list of verification-condition generators, but not for anything else.

Structural Abstractions of Software Verification Conditions, CAV'2007

What the reviewer said: This was in a list of “missing” related work, categorized as “work on precise memory models for verification-condition generation”.

What I think: As far as heap representation goes, this doesn’t look very interesting. Like most VC generators, they assume that input pointers don’t alias. This is a little interesting from a solving standpoint, because they turn the VC into a tree that they then perform structural operations on without consulting a solver. This is reminiscent of how we can do some heap operations without consulting the solver.

A Tool for Checking ANSI-C programs, TACAS'04

What the reviewer said: This was in a general list of “missing” related work.

What I think: This is one of Clarke’s papers on bounded model checking. It couldn’t hurt to cite it, but it’s not super-related.

Precise Pointer reasoning for Dynamic test Generation, ISSTA'2009

What the reviewer said: This was in a general list of “missing” related work.

What I think: This paper is about how to handle pointers during dynamic symbolic execution. It handles pointer dereferences much like GSE, by resolving possible aliases at the time of the dereferencing, but does not seem to include the possibility of a “new” choice. One difference is that this method is adapted to allow pointer arithmetic. The memory model is basically a flat address space, without any explicit notion of a heap.

How this is like SymHeap: It’s a symbolic execution technique that has some facility for linked data structures. Their pointers can be nondeterministic, much like the references in symHeap, and they do conditional writes in a similar fashion as symHeap.

Why this is different from SymHeap:

1 )The memory model is completely different. It’s an addressable array instead of an object-oriented heap. There are no facilities for heap-specific operations like k- or n-bounding.

2) They have a fixed set of memory locations from the onset. There is no concept of lazy initialization to some “new” reference.

Compositional dynamic test generation. Patrice Godefroid. 2007.

What the Reviewer Said: There is an alternative way to represent a summary using logical
formulas and extra variables [Godefroid 2007]. I wonder how such a
representation would work for GSE and heap summarization. Such a
representation would not require the complex update algorithm
described in the paper. It would be useful if the authors could
comment on this and experimentally compare with the technique.

What I think: The SMART approach in Godefroid’s paper is sound but not complete. That is to say, every bug it finds is a real bug, but it is not guaranteed to account for all possible program paths. Given the incomplete of their method, the fact that their representation is simpler is unsurprising.

MultiSE: Multi-Path Symbolic Execution using Value Summaries [Sen et al. 2014]

What the reviewer said: The reviewer claimed that the technique presented in this paper uses the same heap representation as us.

What I think: This paper uses essentially the same representation as the Dilligs. In fact, I think in many ways the Dillig’s work is more sophisticated than the treatment presented here.

How It’s similar to SymHeap: It’s symbolic execution, with a heap. Their heap has value sets like ours does, and their write operation looks like ours.

How it’s different from SymHeap: They don’t do lazy initialization. They use BDDs to represent expressions. Their graph isn’t bipartite.

### 2015-01-16 cav-2015-tex/evaluation.tex
Added the technnical stuff

--- 2014-11-13 tex/evaluation.tex
@@
 each of the algorithms. The headings \gsetxt{}, L\#, and SL correspond
-to the Generalized Symbolic Execution, lazier\#, and \symtxt{}
+to the Generalized Symbolic Execution, Lazier\#, and \symtxt{}
 algorithms, respectively. Note that we do no present the results for
-the lazier algorithm since they are almost identical to that of lazier\#
+the Lazier algorithm since they are almost identical to that of Lazier\#
 for our examples. Table entries containing '-' correspond to test runs
@@
 for certain $k$-bounds a number of experiments completed exploration
-using the \symtxt{} algorithm in a few seconds whereas \gsetxt{} or lazier\# were
+using the \symtxt{} algorithm in a few seconds whereas \gsetxt{} or Lazier\# were
 unable to finish, e.g., BinarySearchTree for $k$=4 and LinkedList for
@@
 %informal testing with the incremental solver turned off, \symtxt{}
-%usually performed better than \gsetxt{} and lazier\#, especially in
+%usually performed better than \gsetxt{} and Lazier\#, especially in
 %test runs with high k-bounds.
@@
 example programs with large numbers of reference compares, such as
-TreeMap, state counts for lazier\# and the \symtxt{} algorithm may
+TreeMap, state counts for Lazier\# and the \symtxt{} algorithm may
 exceed those for \gsetxt{}. We observed that the additional states
@@
 orders of magnitude greater efficiency than with \gsetxt{} or
-lazier\#, while covering exactly the same control flow paths.
+Lazier\#, while covering exactly the same control flow paths.

### 2015-01-16 cav-2015-tex/summary-heap.tex
Added the technnical stuff

--- 2014-11-13 tex/heap.tex
@@
+\section{Summary Heap Framework}
+The summary heap algorithm is presented using Javalite, an
+executable formalization of a Java-like language~\cite{saints-MS}. Javalite retains 
+the essence of Java and other object-oriented languages but with formalizations 
+in both PLT Redex and Coq so that the outcome of any program has a precise
+and deterministic meaning.
+
+Javalite is a syntactic machine defined as rewrites on a string.  The
+semantics are small-step using the CESK architecture with a (C)ontrol string
+representing the expression being evaluated, an (E)nvironment for
+local variables, a (S)tore for the heap, and a (K)ontinuation for what
+is to be executed next.  In this work we change the semantics of the original
+ Javalite machine and its machine syntax to represent (i) GSE~\cite{GSE03}, and (ii) the summary heap algorithm
+presented in this work.
+
+The surface syntax (input) for Javalite is shown 
+in~\figref{fig:surface-syntax}, and the machine syntax (state)
+in~\figref{fig:machine-syntax}. Terminals are in bold face while
+non-terminals are italicized. Ellipses indicate zero or more
+repetitions. Tuples omit the commas for compactness. The language
+itself uses s-expressions for convenience.
+
+\input{surface-syntax}
+\input{machine-syntax}
+
+A Javalite program, $\cfgnt{P}$, is a registry of classes, $\mu$, with
+a tuple indicating a class, $\cfgnt{C}$, and a method, $\cfgnt{m}$,
+where execution starts. The only primitive type in Javalite is
+Boolean. Classes have non-primitive fields, $([\cfgnt{C}\ \cfgnt{f}]\ ...)$, and
+methods, $(\cfgnt{M}\ ...)$.\footnote{Summary heaps are able to support non-primitive fields (see \secref{sec:eval}).
+They are omitted to focus and simplify the presentation.} Methods are limited to a single
+parameter in our Javalite machine. Expressions, $\cfgnt{e}$,  
+include statements, and they
+ use '$\cfgt{:=}$' to indicate assignment and '$\cfgt{=}$' to indicate comparison.
+The dot-operator for field access is replaced by '$\cfgt{\$}$', and the dot-operator
+for method invocation is replaced by '$\cfgt{@}$' since '.' is reserved in PLT Redex. There is no explicit return
+statement in Javalite; rather, the value of the last expression is
+used as the return value. A variable is always indicated by \cfgnt{x}
+and a value by \cfgnt{v}. A value can be a reference in the heap, $\cfgnt{r}$, or any of the special values shown in~\figref{fig:surface-syntax}. 
+We assume that only
+type correct programs are given as input to the machine.
+
+The state of the Javalite machine (\figref{fig:machine-syntax}),
+$\cfgnt{s}$, includes the program registry, $\mu$, a pair of functions defining the heap
+$\lp\cfgnt{L}\ \cfgnt{R}\rp$, a constraint,
+$\phi$, defined over references in the heap, the environment, $\eta$,
+for local variables, and the continuation $\cfgnt{k}$.\footnote{The registry $\mu$ never changes so it is omitted from the state tuple in the rest of the presentation for compactness.}  The more
+complex structures, such as the environment and heap, are defined as lists that
+start with empty, \cfgnt{mt}. The rewrite rules that define the
+semantics treat these lists as partial functions. As such,
+$\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference $\cfgnt{r}$ associated with variable
+$\cfgnt{x}$. The notation $\eta^\prime = \eta[\cfgnt{x} \mapsto
+  \cfgnt{v}]$ defines a new partial function $\eta^\prime$ that is
+the same as $\eta$ except that the variable $\cfgnt{x}$ now maps to
+$\cfgnt{v}$.
+
+The continuation $\cfgnt{k}$ helps accomplish the small-step semantics
+by indicating where the hole, $\cfgt{*}$, is located, by storing
+temporary computations, and by keeping track of the next
+computation. For example, the continuation
+$\lp\cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp$ indicates
+that the machine is currently computing the expression for the object
+reference on which the field $\cfgnt{f}$ is going to be accessed. Once
+the field access is complete, the machine continues with $\cfgnt{k}$.
+
 \subsection{Summary Heaps as Bipartite Graphs}
@@
 The bipartite graph itself consists of references, $\cfgnt{r}$, and
-constraint-location pairs, $\lp\phi\ \cfgnt{l}\rp$. The graph is
+constraint-location pairs, $\lp\phi\ \cfgnt{l}\rp$. Locations may be 
+altered to perform updates, whereas references are immutable
+once they are added to the graph. The graph is
 expressed in the location map, $\cfgnt{L}$, and the reference map,
@@
 \begin{compactitem}
-\item $\lp\phi\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r})$; and
-\item $\lp\phi^\prime\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r}^\prime)$; and
-\item $\phi$ and $\phi^\prime$ hold in the aliasing assignments from the solver.
+\item[-] $\lp\phi\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r})$; and
+\item[-] $\lp\phi^\prime\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r}^\prime)$; and
+\item[-] $\phi$ and $\phi^\prime$ hold in the aliasing assignments from the solver.
 \end{compactitem}
@@
 to $\rsym$.
+
+\subsection{Generating Summary Heaps}
+\label{sec:precise}
+The summary
+heap algorithm only
+partitions the heap at points of divergence in the control flow graph
+such as field accesses or writes (execeptional control flow due to null
+pointers) or comparisons of references (program control flow). There
+are three sets of rewrite rules specific to the summary heap
+algorithm: (i) rules to initialize symbolic references, (ii) rules to
+complete field access and field write, and (iii) rules to check
+equality and inequality of references. The other rules are common to
+both $\rsym$ and $\rgse$. The complete set of rules are shown in the
+supplemental attached with the paper.
+
+Initialization of references in GSE ($\rgse$ relation) is a
+non-deterministic choice where the reference in the heap is
+initialized to null, a new instance of the object, or to any type
+compatible object in the input heap (e.g., previously initialized by
+$\rgse$). In contrast, initialization in the $\rsym$ relation creates
+a single summary heap containing all of the possible initialization
+choices.
+
+\input{summarize-precise-incomplete}
+
+\begin{figure*}
+\begin{tabular}[c]{l}
+\scalebox{1.0}{\usebox{\boxPI}} \\
+\end{tabular}
+\caption{The summary machine, $s ::= \lp\cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\ \cfgnt{C}\rp$, with $s\rsum^*s^\prime =  s \rsum \cdots \rsum s^\prime \rsum s^\prime$.}
+\label{fig:symInit}
+\end{figure*}
+
+The initialization rules, \figref{fig:symInit}, are invoked whenever a
+field pointing to an uninitialized reference is accessed. The
+interaction with the solver in the definition of the rules is denoted
+by $\mathbb{S}(\phi)$ which returns true if $\phi$ is satisfiable. The
+summarize-end rule becomes active when there is nothing to
+initialize. This condition is determined by the function
+$\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) =
+\{\lp\phi\ \cfgnt{l}\rp\ ...\}$ which returns constraint-location
+pairs where the field $\cfgnt{f}$ is uninitialized.
+\[
+\begin{array}{rcl}
+\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \\
+& & \ \ \ \ \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \\
+& & \ \ \ \ \ \ \ \ \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
+\end{array}
+\]
+A pair in the set means the field in the location maps to a reference
+that then points to $\cfgnt{l}_\mathit{un}$, and that the path to that
+location is feasible on some aliasing assignment.
+
+% The cardinality of the set, $\theta$ is never
+%greater than one in GSE and the constraint is always satisfiable
+%because all constraints are constant. This property is relaxed in GSE
+%with heap summaries.
+
+In~\figref{fig:symInit}, given the uninitialized set $\Lambda$ for
+field $f$, the $\mathit{min}_l$ function returns
+$(\phi_x\ \cfgnt{l}_x)$ based on a lexicographical ordering of
+uninitialized locations in $\Lambda$ to make initialization
+deterministic (i.e., the same heap is always initialized in the same
+way as order determines how many aliases are available in the input heap at any given point in initialization). 
+%The $\mathrm{fresh}_\cfgnt{l}(\cfgnt{C})$ call returns a new location of type $C$. 
+The set $\rho$ contains the set of
+reference-location pairs from the input heap that are potential
+aliases. Minimizing over the set of references in the pre-image ensures
+that any pair in $\rho$ is the reference $\cfgnt{r}_a$ and the location $\cfgnt{l}_a$ materialized at the same time in some prior initialization (i.e., they were once
+$\cfgnt{r}_f$ and $\cfgnt{l}_f$). Aliasing constraints
+in the new summary heap reason over these original creators; otherwise aliasing and local value set
+computation breaks down.  The reference partitions with their
+monotonicity make this determination possible.
+
+There are three sets corresponding to the non-deterministic choices in
+GSE with a fourth that preserves the pre-initialized heap structure.
+Note that the constraints always preserve the access path to the location which is $\phi_x$.
+(i) $\theta_\mathit{null}$ asserts the condition under which
+$\cfgnt{l}_\mathit{null}$ is possible (any time the solver assigns
+values to reference variables in such a way that both $\phi_x$ and $\cfgnt{r}_f =
+\cfgnt{r}_\mathit{null}$ hold). (ii)
+$\theta_\mathit{new}$ is active when $\cfgnt{r}_f$ points to the
+fresh location. This occurs when $\cfgnt{r}_f$ is not new or any other alias. (iii) each member of $\theta_\mathit{alias}$ restricts $\cfgnt{r}_f$ to
+a particular alias in $\rho$, and at the same time, not alias any member of $\rho$
+that was initialized earlier than the current choice (a later
+initialization may indeed also alias the current choice in a valid
+heap as order determines the number of aliasing choices available). And (iv) $\theta_\mathit{orig}$  implements conditional initialization to preserve the
+original heap structure. This property is needed for the bisimulation. 
+These sets are added into the heap on $\cfgnt{r}_f$ after the fields for $\cfgnt{l}_f$ are initialized to $\cfgnt{r}_\mathit{un}$.
+
+\begin{figure*}[t]
+\begin{center}
+\begin{tabular}[c]{c|c|c|c}
+\begin{tabular}[c]{c}
+\scalebox{0.81}{\input{origHeap.pdf_t}} \\
+\end{tabular} &
+\begin{tabular}[c]{c}
+\scalebox{0.81}{\input{summarizeXHeap.pdf_t}} \\
+\end{tabular} &
+\begin{tabular}[c]{c}
+\scalebox{0.81}{\input{summarizeYHeap.pdf_t}} \\
+\end{tabular} &
+\begin{tabular}[c]{l}
+$\rho := \{ (\cfgnt{r}_1^i\ \cfgnt{l}_1 \}$ \\
+$\theta_\mathit{null} := \{ ( \cfgnt{r}_2^i = \cfgnt{r}_\mathit{null}\ \cfgnt{l}_\mathit{null}) \}$\\
+$\theta_\mathit{new} := \{ ( \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_1^i\ \cfgnt{l}_2) \}$\\
+$\theta_\mathit{alias} := \{ ( \cfgnt{r}_1^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i = \cfgnt{r}_1^i\ \cfgnt{l}_1) \}$\\
+$\theta_\mathit{orig} := \{ \}$ \\
+$\phi_{\mathit{1a}} := \cfgnt{r}_1^i = \cfgnt{r}_\mathit{null} $ \\
+$\phi_{\mathit{1b}} := \cfgnt{r}_1^i \neq \cfgnt{r}_\mathit{null} $  \\
+$\phi_{\mathit{2a}} := \cfgnt{r}_2^i = \cfgnt{r}_\mathit{null}$ \\
+$\phi_{\mathit{2b}} := \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_1^i$ \\
+$\phi_{\mathit{2c}} :=  \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i = \cfgnt{r}_1^i $ \\
+\end{tabular} \\
+(a) & (b) & (c) & (d) \\
+\end{tabular}
+\end{center}
+\caption{An example that initializes $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ and $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$.
+(a) Initial heap structure.
+(b) After $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ is initialized.
+(c) After $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ is initialized.
+(d) Sets in the summarize rule and constraints on the edges.}
+\label{fig:initHeap}
+\end{figure*}
+
+We visualize the initialization process in~\figref{fig:initHeap}. The
+graph in~\figref{fig:initHeap}(a) represents the initial heap. The
+reference superscripts $s$ and $i$ indicate the partition containing the reference.
+ In~\figref{fig:initHeap}, $\cfgnt{r}_0^s$ represents a stack
+reference for the $\cfgt{this}$ variable which has two fields $x$
+and $y$ of the same type. Note that when no constraint is specified for a location,
+there is an implicit $\mathit{true}$ constraint. For example, $\cfgnt{r}_0^s$
+points to $\cfgnt{l}_0$ on the constraint $\mathit{true}$. The fields $x$ and
+$y$ point to the uninitialized reference $\cfgnt{r}_\mathit{un}$.
+
+The graph in~\figref{fig:initHeap}(b) represents the summary heap
+after the initialization of the $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ field while
+the graph in~\figref{fig:initHeap}(c) represents the symbolic heap
+summary after the initialization of the $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ field
+following the initialization of $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$. The list
+in~\figref{fig:initHeap}(d) represents the various sets constructed in
+the summarize rule during the initialization of $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$. We
+also define values of constraints used as labels in the graph.
+
+Accessing field $x$ from $\cfgnt{l}_0$ creates a new input heap reference $\cfgnt{r}_1^i$ in the
+summary heap shown in~\figref{fig:initHeap}(b). Reference $\cfgnt{r}_1^i$
+points to the $\cfgnt{l}_\mathit{null}$ location under the constraint that
+$\cfgnt{r}_1^i$ is null (constraint $\phi_{1a}$ in  \figref{fig:initHeap}(d)), reference
+$\cfgnt{r}_1^i$ points to location $\cfgnt{l}_1$ under the constraint that $\cfgnt{r}_1^i$
+is not $\mathit{null}$ (constraint $\phi_{1b}$), and fresh location $\cfgnt{l}_1$ of type $C$ 
+(the type of field $\cfgnt{x}$), is added to the heap. There are no aliases because $\cfgnt{l}_1$ 
+is the first location of type $C$ to be initialized.
+
+Following $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{x}\rp$,
+$\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$ is initialized leading to
+the summary heap in~\figref{fig:initHeap}(c). The set $\rho$
+in~\figref{fig:initHeap}(d) contains the one potential aliases
+$\cfgnt{l}_1$ from the previous initialization for
+$\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{x}\rp$. It also shows the
+$\theta$-sets for this initialization and the resulting edge
+labels. Note that the ordering between aliases in
+$\theta_\mathit{alias}$ is insignificant until a third field is
+initialized and there are two potential choices.

### 2015-01-22 cav-2015-tex/rw.tex
Added more related work to the bibliography, started the motivation and related work subsections.

@@
 \section{Related Work}
-\noindent\textbf{A Lightweight Symbolic Virtual Machine for Solver-Aided Host Languages Emina Torlak and Ras Bodik. Programming Language Design and Implementation} (PLDI'14)
 
-\noindent{\textbf{What the reviewers said:} \emph{"the paper [Torlak et al. 2014] definitely shows how to apply the same compact representation to symbolic execution."}
+\noindent\textbf{Symbolic Execution} 
+Initial work on symbolic execution largely focused on checking
+properties of imperative programs with primitive primitive
+types~\cite{Clarke:76,King:76}. Several recent projects generalized
+the core idea of symbolic execution which enabled it to be applied to
+programs with more general types, including references and
+arrays~\cite{GSE03,Godefroid:PLDI05,Sen:FSE05,CadarEngler05EXE,KiasanKunit}.
+Our work leverages the core idea in generalized symbolic execution
+with lazy initialization to construct the heap on-the-fly during
+symbolic execution, but avoids the nondeterminism introduced by GSE by
+constructing a summary heap and will generally create fewer paths than
+GSE techniques.
 
-\noindent\textbf{What I think:} They aren’t really breaking any ground with the heap representation here.
+Key limitations of symbolic execution include path explosion and non-symbolic operations.
+Mitigation of the path explosion problem has focused on composition, modular analysis, and state merging.
+Dynamic Symbolic Execution is the primary technique to circumvent the limitations of constraint solvers.
+
+More recently, dynamic symbolic execution (\dsetxt{}, sometimes referred to as concolic execution) has emerged as a way to enable symbolic execution to continue on programs that contain elements that cannot be reasoned about symbolically.
+~\dsetxt{} works by executing a program using concrete and symbolic engines simultaneously.
+When the program reaches a statement that cannot be reasoned about symbolically, it substitutes in values from the concrete execution and continues.
+When reaching the end of a program path, DSE inverts the branch conditions and uses the solver to generate concrete inputs for another execution path.
+Initial DSE attempts
+
+In the absence of an effective theory of references, DSE has been a natural choice for reasoning about programs that contain them.
+A number of DSE techniques use concretization when reasoning about references ~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}.
+However, as demonstrated in \ref{fig:DSEtest}, DSE underapproximates when it concretizes symbolic values, resulting in an incomplete analysis.
+The SAGE DSE engine includes more sophisticated methods for reasoning about references, and can successfully reason about the example in \ref{fig:DSEtest}.
+However, SAGE only accepts programs where memory allocation is independent of the of program inputs, and as such does not support a complete theory of computation.
+
+\noindent\textbf{Bounded Model Checking}
+
+\noindent\textbf{Static Analysis}
+
+\noindent\textbf{Test Input Generation}
+
+\noindent\textbf{Symbolic Value Sets}
+A number of techniques use value sets.
+Some of them are general techniques where all program values are represented using value sets.
+While symbolic referencing operations could be supported in principle with these methods, it is not clear from the published material exactly how that might be accomplished.
+Others use value sets specifically in the context of referencing operations, however, these methods suffer from other limitations.
+
+%\noindent\textbf{A Lightweight Symbolic Virtual Machine for Solver-Aided Host Languages Emina Torlak and Ras Bodik. Programming Language Design and Implementation} (PLDI'14)
+%
+%\noindent{\textbf{What the reviewers said:} \emph{"the paper [Torlak et al. 2014] definitely shows how to apply the same compact representation to symbolic execution."}
+%
+%\noindent\textbf{What I think:} They aren’t really breaking any ground with the heap representation here.
 It’s pretty much the same thing as what was in SATURN.
@@
 It’s probably worth citing, if only as part of a list of similar techniques.
-
-\noindent\textbf{How this is similar to SymHeap:}
-
-\noindent\textbf{How this is different from SymHeap:}
-\begin{compactenum}
-\item They don’t do lazy initialization. \emph{"The shape of all data structures remains concrete during SVM evaluation."}
-\item There are no real bounding mechanisms, and they assume that programs are self-finitizing.
-\begin{compactitem}
-\item They don’t really handle recursion or loops.
-\item They can’t make any sort of heap-specific bounds
-\item They try to sell this as a feature, by the way, by claiming that they don’t “artificially finitize executions by explicitly bounding the depth of recursion.” That’s the nicest cover-up for a program that fails to terminate I’ve ever heard.
-\end{compactitem}
-\item Their representation is different. Although, they have value
-  sets, I don’t see a bipartite graph, locations, fields, etc. This is
-  worrisome since the reviewer was certain this is the same
-  representation as ours.
-\item They do weird domain-specific programming languages instead of our java-like language.
-\end{compactenum}
-
-Generating precise and concise procedure summaries, POPL’2008
-
-What the reviewer said: This was in a general list of “missing” related work
-
-What I think: This paper is about procedure summaries.
+%
+%\noindent\textbf{How this is similar to SymHeap:}
+%
+%\noindent\textbf{How this is different from SymHeap:}
+%\begin{compactenum}
+%\item They don’t do lazy initialization. \emph{"The shape of all data structures remains concrete during SVM evaluation."}
+%\item There are no real bounding mechanisms, and they assume that programs are self-finitizing.
+%\begin{compactitem}
+%\item They don’t really handle recursion or loops.
+%\item They can’t make any sort of heap-specific bounds
+%\item They try to sell this as a feature, by the way, by claiming that they don’t “artificially finitize executions by explicitly bounding the depth of recursion.” That’s the nicest cover-up for a program that fails to terminate I’ve ever heard.
+%\end{compactitem}
+%\item Their representation is different. Although, they have value
+%  sets, I don’t see a bipartite graph, locations, fields, etc. This is
+%  worrisome since the reviewer was certain this is the same
+%  representation as ours.
+%\item They do weird domain-specific programming languages instead of our java-like language.
+%\end{compactenum}
+%
+%Generating precise and concise procedure summaries, POPL’2008
+%
+%What the reviewer said: This was in a general list of “missing” related work
+%
+%What I think: This paper is about procedure summaries.
 It looks like they are concerned with a more general type of problem than we are with the heap, and that the heap-related stuff is a specialization of their framework.
 It’s worth citing, as an example of a global access-path style representation.
-
-How this is similar to SymHeap:
-1) Uses sets of guarded values, which they call micr-transformers.
+%
+%How this is similar to SymHeap:
+%1) Uses sets of guarded values, which they call micr-transformers.
 Their “micro-transformers” can be made to look lot like our references.
 A dereferencing operation may be performed using a “composition of micro-transformers”.
-
-How this is different from SymHeap: 
-1) The heap is stored as global access paths, related directly to variables.
+%
+%How this is different from SymHeap: 
+%1) The heap is stored as global access paths, related directly to variables.
 Thus, they don’t have any explicit local representation of the heap, and determining reachability is impossible without consulting the solver.
-
-2) Potential aliasing relationships are determined in a path-insensitive manner, prior to program execution, by means of power sets.
-
-3) It doesn’t look like they do lazy initialization. The size of parameter sets is fixed at the beginning of the program
-
-Boogie: A Modular Reusable Verifier for Object-Oriented Programs FMCO'2005
-
-What the reviewer said: This was in a list of “missing” related work, categorized as “work on precise memory models for verification-condition generation”.
-
-What I think: Boogie doesn’t have a built-in heap encoding.
+%
+%2) Potential aliasing relationships are determined in a path-insensitive manner, prior to program execution, by means of power sets.
+%
+%3) It doesn’t look like they do lazy initialization. The size of parameter sets is fixed at the beginning of the program
+%
+%Boogie: A Modular Reusable Verifier for Object-Oriented Programs FMCO'2005
+%
+%What the reviewer said: This was in a list of “missing” related work, categorized as “work on precise memory models for verification-condition generation”.
+%
+%What I think: Boogie doesn’t have a built-in heap encoding.
 It uses a 2d array to model the heap, and compiles the entire program-correctness problem into a single constraint equation, which it ships off to a constraint solver.
@@
 Worth mentioning as part of a list of verification-condition generators, but not for anything else.
-
-Structural Abstractions of Software Verification Conditions, CAV'2007
-
-What the reviewer said: This was in a list of “missing” related work, categorized as “work on precise memory models for verification-condition generation”.
-
-What I think: As far as heap representation goes, this doesn’t look very interesting.
+%
+%Structural Abstractions of Software Verification Conditions, CAV'2007
+%
+%What the reviewer said: This was in a list of “missing” related work, categorized as “work on precise memory models for verification-condition generation”.
+%
+%What I think: As far as heap representation goes, this doesn’t look very interesting.
 Like most VC generators, they assume that input pointers don’t alias.
@@
 This is reminiscent of how we can do some heap operations without consulting the solver.
-
-A Tool for Checking ANSI-C programs, TACAS'04
-
-What the reviewer said: This was in a general list of “missing” related work.
-
-What I think: This is one of Clarke’s papers on bounded model checking. It couldn’t hurt to cite it, but it’s not super-related.
-
-Precise Pointer reasoning for Dynamic test Generation, ISSTA'2009
-
-What the reviewer said: This was in a general list of “missing” related work.
-
-What I think: This paper is about how to handle pointers during dynamic symbolic execution.
+%
+%A Tool for Checking ANSI-C programs, TACAS'04
+%
+%What the reviewer said: This was in a general list of “missing” related work.
+%
+%What I think: This is one of Clarke’s papers on bounded model checking. It couldn’t hurt to cite it, but it’s not super-related.
+%
+%Precise Pointer reasoning for Dynamic test Generation, ISSTA'2009
+%
+%What the reviewer said: This was in a general list of “missing” related work.
+%
+%What I think: This paper is about how to handle pointers during dynamic symbolic execution.
 It handles pointer dereferences much like GSE, by resolving possible aliases at the time of the dereferencing, but does not seem to include the possibility of a “new” choice.
@@
 The memory model is basically a flat address space, without any explicit notion of a heap.
-
-How this is like SymHeap: It’s a symbolic execution technique that has some facility for linked data structures.
+%
+%How this is like SymHeap: It’s a symbolic execution technique that has some facility for linked data structures.
 Their pointers can be nondeterministic, much like the references in symHeap, and they do conditional writes in a similar fashion as symHeap.
-
-Why this is different from SymHeap:
-
-1 )The memory model is completely different. It’s an addressable array instead of an object-oriented heap. There are no facilities for heap-specific operations like k- or n-bounding.
-
-2) They have a fixed set of memory locations from the onset. There is no concept of lazy initialization to some “new” reference.
-
-Compositional dynamic test generation. Patrice Godefroid. 2007.
-
-What the Reviewer Said: There is an alternative way to represent a summary using logical
-formulas and extra variables [Godefroid 2007]. I wonder how such a
-representation would work for GSE and heap summarization. Such a
-representation would not require the complex update algorithm
-described in the paper. It would be useful if the authors could
-comment on this and experimentally compare with the technique.
-
-What I think: The SMART approach in Godefroid’s paper is sound but not complete.
+%
+%Why this is different from SymHeap:
+%
+%1 )The memory model is completely different. It’s an addressable array instead of an object-oriented heap. There are no facilities for heap-specific operations like k- or n-bounding. 
+%
+%2) They have a fixed set of memory locations from the onset. There is no concept of lazy initialization to some “new” reference.
+%
+%Compositional dynamic test generation. Patrice Godefroid. 2007.
+%
+%What the Reviewer Said: There is an alternative way to represent a summary using logical
+%formulas and extra variables [Godefroid 2007]. I wonder how such a
+%representation would work for GSE and heap summarization. Such a
+%representation would not require the complex update algorithm
+%described in the paper. It would be useful if the authors could
+%comment on this and experimentally compare with the technique.
+%
+%What I think: The SMART approach in Godefroid’s paper is sound but not complete.
 That is to say, every bug it finds is a real bug, but it is not guaranteed to account for all possible program paths.
 Given the incomplete of their method, the fact that their representation is simpler is unsurprising.
-
-MultiSE: Multi-Path Symbolic Execution using Value Summaries [Sen et al. 2014]
-
-What the reviewer said: The reviewer claimed that the technique presented in this paper uses the same heap representation as us.
-
-What I think: This paper uses essentially the same representation as the Dilligs. In fact, I think in many ways the Dillig’s work is more sophisticated than the treatment presented here.
-
-How It’s similar to SymHeap: It’s symbolic execution, with a heap. Their heap has value sets like ours does, and their write operation looks like ours.
-
-How it’s different from SymHeap: They don’t do lazy initialization. They use BDDs to represent expressions. Their graph isn’t bipartite.
+%
+%MultiSE: Multi-Path Symbolic Execution using Value Summaries [Sen et al. 2014]
+%
+%What the reviewer said: The reviewer claimed that the technique presented in this paper uses the same heap representation as us.
+%
+%What I think: This paper uses essentially the same representation as the Dilligs. In fact, I think in many ways the Dillig’s work is more sophisticated than the treatment presented here.
+%
+%How It’s similar to SymHeap: It’s symbolic execution, with a heap. Their heap has value sets like ours does, and their write operation looks like ours.
+%
+%How it’s different from SymHeap: They don’t do lazy initialization. They use BDDs to represent expressions. Their graph isn’t bipartite.

### 2015-01-24 cav-2015-tex/rw.tex
Updated related work, bibliography.

@@
 properties of imperative programs with primitive primitive
-types~\cite{Clarke:76,King:76}. Several recent projects generalized
-the core idea of symbolic execution which enabled it to be applied to
+types~\cite{Clarke:76,King:76}.
+Limitations of early symbolic execution techniques includes non-primitive data types, path explosion and non-symbolic operations.
+Subsequent adaptations of symbolic execution have sought to overcome these limitations.
+
+To address the issue of references, several projects have generalized
+the core idea of symbolic execution, enabling it to be applied to
 programs with more general types, including references and
-arrays~\cite{GSE03,Godefroid:PLDI05,Sen:FSE05,CadarEngler05EXE,KiasanKunit}.
+arrays~\cite{GSE03,KiasanKunit,Rosner:2015}.
+However, these generalized symbolic execution (GSE) techniques universally require nondeterministic case-splitting during dereferencing operations, thus exacerbating the path explosion problem.
 Our work leverages the core idea in generalized symbolic execution
@@
 
-Key limitations of symbolic execution include path explosion and non-symbolic operations.
-Mitigation of the path explosion problem has focused on composition, modular analysis, and state merging.
-Dynamic Symbolic Execution is the primary technique to circumvent the limitations of constraint solvers.
+Recent progress has been made towards mitigating path explosion via state merging~\cite{Kuznetsov:2012,Sen:2014,Torlak:2014}.
+While the independently developed techniques in~\cite{Sen:2014,Torlak:2014} use representations similar to the one presented here, none of these techniques address the fundamental issue concerning symbolic heaps, namely dereferencing symbolic input references.
+For these reasons, we believe these works to be both orthogonal and complimentary to our own.
 
-More recently, dynamic symbolic execution (\dsetxt{}, sometimes referred to as concolic execution) has emerged as a way to enable symbolic execution to continue on programs that contain elements that cannot be reasoned about symbolically.
+Dynamic symbolic execution (\dsetxt{}, sometimes referred to as concolic execution) has emerged as a way to enable symbolic execution to continue on programs that contain elements that cannot be reasoned about symbolically.
 ~\dsetxt{} works by executing a program using concrete and symbolic engines simultaneously.
@@
 When reaching the end of a program path, DSE inverts the branch conditions and uses the solver to generate concrete inputs for another execution path.
-Initial DSE attempts
+While concretization allows DSE to explore a much wider selection of programs, this freedom comes at the price of completeness.
+The process of concretization introduces approximation such that
 
@@
 However, as demonstrated in \ref{fig:DSEtest}, DSE underapproximates when it concretizes symbolic values, resulting in an incomplete analysis.
-The SAGE DSE engine includes more sophisticated methods for reasoning about references, and can successfully reason about the example in \ref{fig:DSEtest}.
-However, SAGE only accepts programs where memory allocation is independent of the of program inputs, and as such does not support a complete theory of computation.
+The SAGE DSE engine~\cite{Elkarablieh:2009} includes more sophisticated methods for reasoning about references, and can successfully reason about the example in \ref{fig:DSEtest}.
+However, the heap model in SAGE requires fixing the size of the memory prior to starting the analysis, and is therefore not complete.
 
 \noindent\textbf{Bounded Model Checking}
+Bounded model checking (BMC) techniques seek to avoid the path explosion problem by converting an entire program execution, along with its specifications, into a constraint problem called a verification condition.
+The advantage in creating a single constraint is that SMT solvers can often reason more efficiently about all paths simultaneously rather than on a case-by-case basis.
+Many BMC methods include a model for reasoning about references, including those described in ~\cite{Clarke:2004,Barnett:2006,Xie:2005,Babic:2007,Dillig:2011}.
+However, BMC techniques are not complete for general programs, due to the need to set an execution path-length bound prior to conducting the analysis.
+By extension, the reference models used in BMC methods are generally not complete.
+Other limitations include assuming that symbolic references do not alias~\cite{Xie:2005,Babic:2007}, that data structures are not recursive~\cite{Dillig:2011}, or requiring that symbolic references are never dereferenced~\cite{Clarke:2004}.
 
@@
 
-\noindent\textbf{Test Input Generation}
-
-\noindent\textbf{Symbolic Value Sets}
-A number of techniques use value sets.
-Some of them are general techniques where all program values are represented using value sets.
-While symbolic referencing operations could be supported in principle with these methods, it is not clear from the published material exactly how that might be accomplished.
-Others use value sets specifically in the context of referencing operations, however, these methods suffer from other limitations.
+\noindent\textbf{Symbolic Heap Representations}
+% a good place to mention procedure summaries, like Yorsh and the Dilligs.
+Our work builds upon a number of prior techniques that use sets of guarded values to represent program state~\cite{Sen:2014,Torlak:2014,Yorsh:2008,Xie:2005,Dillig:2011,Elkarablieh:2009}.
+The methods presented in~\cite{Sen:2014,Torlak:2014,Yorsh:2008} use value sets to represent all symbolic program state, including references.
+While symbolic referencing operations could be supported in principle with these methods, it is not clear from the published material exactly how that might be accomplished, especially in the case of dereferencing.
+All of the methods presenting solutions to the dereferencing problem~\cite{Xie:2005,Dillig:2011,Elkarablieh:2009} do not perform a complete analysis.
 

### 2015-01-27 cav-2015-tex/rw.tex
Re-worked the introduciton, added section for a high-level description of the method, added more to related work section.

@@
 programs with more general types, including references and
-arrays~\cite{GSE03,KiasanKunit,Rosner:2015}.
-However, these generalized symbolic execution (GSE) techniques universally require nondeterministic case-splitting during dereferencing operations, thus exacerbating the path explosion problem.
+arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}.
+However, these generalized symbolic execution (GSE) techniques work by branching over multiple copies of the system state during dereferencing operations, thus exacerbating the path explosion problem.
 Our work leverages the core idea in generalized symbolic execution
@@
 While concretization allows DSE to explore a much wider selection of programs, this freedom comes at the price of completeness.
-The process of concretization introduces approximation such that
+The process of concretization introduces approximation such that all possible execution paths may not be explored.
 
@@
 The SAGE DSE engine~\cite{Elkarablieh:2009} includes more sophisticated methods for reasoning about references, and can successfully reason about the example in \ref{fig:DSEtest}.
-However, the heap model in SAGE requires fixing the size of the memory prior to starting the analysis, and is therefore not complete.
+However, the heap model in SAGE requires fixing the size of memory prior to starting the analysis, and is therefore not complete.
 
@@
 However, BMC techniques are not complete for general programs, due to the need to set an execution path-length bound prior to conducting the analysis.
-By extension, the reference models used in BMC methods are generally not complete.
+By extension, the bounded reference models used in BMC methods are generally not complete.
 Other limitations include assuming that symbolic references do not alias~\cite{Xie:2005,Babic:2007}, that data structures are not recursive~\cite{Dillig:2011}, or requiring that symbolic references are never dereferenced~\cite{Clarke:2004}.
 
-\noindent\textbf{Static Analysis}
-
 \noindent\textbf{Symbolic Heap Representations}
+A number of techniques use summary heap representations that are not sound. These models can greatly reduce the complexity of dereferencing queries, but do not allow.
 % a good place to mention procedure summaries, like Yorsh and the Dilligs.
@@
 The methods presented in~\cite{Sen:2014,Torlak:2014,Yorsh:2008} use value sets to represent all symbolic program state, including references.
-While symbolic referencing operations could be supported in principle with these methods, it is not clear from the published material exactly how that might be accomplished, especially in the case of dereferencing.
-All of the methods presenting solutions to the dereferencing problem~\cite{Xie:2005,Dillig:2011,Elkarablieh:2009} do not perform a complete analysis.
+While symbolic referencing operations could, in principle, be supported with these methods, it is not clear from the published material exactly how that might be accomplished, especially in the case of dereferencing.
+All of the methods presenting solutions to the dereferencing problem~\cite{Xie:2005,Dillig:2011,Elkarablieh:2009} are not complete, because they require setting a bound on the size of the input heap prior to conducting the analysis.
 

### 2015-01-28 cav-2015-tex/rw.tex
Cleaned up the introduction, added some conted to related work.

@@
 Initial work on symbolic execution largely focused on checking
-properties of imperative programs with primitive primitive
+properties of imperative programs with primitive
 types~\cite{Clarke:76,King:76}.
-Limitations of early symbolic execution techniques includes non-primitive data types, path explosion and non-symbolic operations.
-Subsequent adaptations of symbolic execution have sought to overcome these limitations.
+Limitations of early symbolic execution techniques included non-primitive data types, path explosion and non-symbolic operations.
+Subsequent adaptations have sought to overcome these limitations.
 
@@
 \noindent\textbf{Symbolic Heap Representations}
-A number of techniques use summary heap representations that are not sound. These models can greatly reduce the complexity of dereferencing queries, but do not allow.
+Due to technological limitations, many early symbolic heap representations focused on reducing the computational complexity of dereferencing queries.
+By introducing certain heuristics and approximations, the computational burden can be greatly reduced, at the cost of precision.
+Since the problem of weeding out false positives can be at least as difficult as the program analysis itself, there has been a renewed interest in more precise heap representations.
+However, these newer methods generally err on the side of under-approximation, producing an analysis that is not complete.
+
+Several GSE techniques~\cite{GSE03,KiasanKunit} form an exception to this rule, presenting an input heap model that is unconstrained and unbounded.
+However, GSE does not offer a mechanism for representing the set of heaps along an execution path as a unified symbolic value.
+As a result GSE does not produce a path condition representing the complete set of inputs for a given execution path, negating a significant advantage of symbolic execution.
+The work presented here overcomes this limitation by using symbolic values to represent the heap.
+
 % a good place to mention procedure summaries, like Yorsh and the Dilligs.
-Our work builds upon a number of prior techniques that use sets of guarded values to represent program state~\cite{Sen:2014,Torlak:2014,Yorsh:2008,Xie:2005,Dillig:2011,Elkarablieh:2009}.
+The symbolic heap value sets presented in this work build upon a number of prior techniques that use sets of guarded values to represent program state~\cite{Sen:2014,Torlak:2014,Yorsh:2008,Xie:2005,Dillig:2011,Elkarablieh:2009}.
 The methods presented in~\cite{Sen:2014,Torlak:2014,Yorsh:2008} use value sets to represent all symbolic program state, including references.
 While symbolic referencing operations could, in principle, be supported with these methods, it is not clear from the published material exactly how that might be accomplished, especially in the case of dereferencing.
-All of the methods presenting solutions to the dereferencing problem~\cite{Xie:2005,Dillig:2011,Elkarablieh:2009} are not complete, because they require setting a bound on the size of the input heap prior to conducting the analysis.
+All of the methods presenting solutions to the dereferencing problem~\cite{Xie:2005,Dillig:2011,Elkarablieh:2009} are not complete, for a variety of reasons which have been enumerated previously.
 

### 2015-01-28 cav-2015-tex/approach.tex
adding text and rules for the main body

--- 2014-11-13 tex/heap.tex
@@
-\subsection{Summary Heaps as Bipartite Graphs}
-A novel contribution of summary heaps for symbolic execution is the
-labeled bipartite graph representation of the heap which enables a
-summary heap to group heaps together that follow the same control flow
-to a given point of execution. The graph structure is able to capture
-group membership and compute value sets using entirely non-recursive
-local lookup. Additionally, updates on the heap do not require
-rewriting the path condition.
+\subsection{Generating Summary Heaps}
+\label{sec:precise}
+The summary
+heap algorithm only
+partitions the heap at points of divergence in the control flow graph
+such as field accesses or writes (execeptional control flow due to null
+pointers) or comparisons of references (program control flow). There
+are three sets of rewrite rules specific to the summary heap
+algorithm: (i) rules to initialize symbolic references, (ii) rules to
+complete field access and field write, and (iii) rules to check
+equality and inequality of references.
 
-The bipartite graph itself consists of references, $\cfgnt{r}$, and
-constraint-location pairs, $\lp\phi\ \cfgnt{l}\rp$. The graph is
-expressed in the location map, $\cfgnt{L}$, and the reference map,
-$\cfgnt{R}$. As done with the environment, $\cfgnt{L}$ and $\cfgnt{R}$
-are treated as partial functions where $\cfgnt{L}(r) =
-\{(\phi\ \cfgnt{l})\ ...\}$ is the set of constraint-location pairs in
-the heap associated with the given reference, and
-$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the reference
-associated with the given location-field pair in the heap.
+\input{summarize-precise-incomplete}
 
-There are several properties of the summary heap enforced by the
-rewrite rules that are invariant and important to the correctness
-proofs in \secref{sec:bisim}: \emph{reference partitions},
-\emph{immutability}, \emph{determinism}, \emph{type
-  consistency}, and \emph{null and uninitialized}.
+\begin{figure*}
+\begin{tabular}[c]{l}
+\scalebox{1.0}{\usebox{\boxPI}} \\
+\end{tabular}
+\caption{Summary machine, $s ::= \lp\cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\ \cfgnt{C}\rp$, with $s\rsum^*s^\prime =  s \rsum \cdots \rsum s^\prime \rsum s^\prime$.}
+\label{fig:symInit}
+\end{figure*}
 
-\emph{Reference partitions}: new references drawn from
-  three distinct partitions (i) $\mathrm{init}_\cfgnt{r}()$ for references for the \emph{input heap}, (ii) $\mathrm{fresh}_\cfgnt{r}()$ for references for \emph{auxiliary literals}, and
-  (iii) $\mathrm{stack}_\cfgnt{r}()$ for references for \emph{stack literals} in the expressions and
-  continuations. The references strictly increase in value on each
-  call, and modular arithmetic is used to determine the partition to
-  which a reference belongs.
-\begin{compactdesc}
-\item[Input heap:] these references have two
-  interpretations: one as a literal and another as a variable. As a literal it is a node in
-  the summary heap. As a variable it is a term in any number of constraints that label
-  edges in the summary heap. Only input heap references and the
-  special reference $\cfgnt{r}_\mathit{null}$ appear in constraints
-\item[Auxiliary literals:] these references are only used to define additional structure in
-  the bipartite graph and are not part of any constraint and do not appear
-  in any environment, expression, or continuation.
-\item[Stack references:] these references are also used to define additional structure in the bipartite graph but may also appear in the environment, expression, or continuation.
-These are not part of any constraint.
-\end{compactdesc}
-Reference partitions are a critical piece to the existence proof of a
-bisimilation between the summary heap algorithm and generalized
-symbolic execution (see \secref{sec:bisim}).
-
-\emph{Immutability} means that a reference does not change in the
-location map. It always points to the same set of constraint location
-pairs. This property ensures that constraints never need to be
-rewritten as the program evolves its state.
-
-\emph{Determinism} means that a reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously. In the definition $\cfgnt{L}^\leftarrow$ is the pre-image of the location map.
-$$
-\begin{array}{l}
-\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
-\ \ \ \ (\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
-\end{array}
-$$
-Informally, any two constraint location pairs connected to a
-common reference form a contradiction: only one can be true in any
-satisfying assignment. The property ensures that any satisfying assignment
-resolving aliasing relationships results in a deterministic heap: a
-field access returns a single location under that assignment.
-
-\emph{Type consistency} implies that all locations associated with a reference have the same type.
+The initialization rule in \figref{fig:symInit} is invoked whenever a
+field pointing to an uninitialized reference is accessed. The
+interaction with the solver in the definition of the rules is denoted
+by $\mathbb{S}(\phi)$ which returns true if $\phi$ is satisfiable.
+%The summarize-end rule becomes active when there is nothing to
+%initialize.
+ The check for uninitialized references is determined by the function
+ $\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) =
+ \{\lp\phi\ \cfgnt{l}\rp\ ...\}$ which returns constraint-location
+ pairs where the field $\cfgnt{f}$ is uninitialized.
 \[
-\begin{array}{l}
-\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
-\ \ \ \ (\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))
+\begin{array}{rcl}
+\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \\
+& & \ \ \ \ \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \\
+& & \ \ \ \ \ \ \ \ \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
 \end{array}
@@
 
-\emph{Null and Uninitialized} means that every summary heap contains 
-a special location for null ($\cfgnt{l}_\mathit{null}$), and a special
-location for uninitialized
-  ($\cfgnt{l}_\mathit{un}$), with corresponding references
-  $\cfgnt{r}_\mathit{null}$ and
-  $\cfgnt{r}_\mathit{un}$, respectively. $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
-  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
-  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
-  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. These special references can be used in constraints.
+In~\figref{fig:symInit}, given the uninitialized set $\Lambda$ for
+field $f$, the $\mathit{min}_l$ function returns
+$(\phi_x\ \cfgnt{l}_x)$ based on a lexicographical ordering of
+uninitialized locations in $\Lambda$ to make initialization
+deterministic.  The set $\rho$ contains the set of reference-location
+pairs from the input heap that are potential aliases.  There are four
+choices: (i) $\theta_\mathit{null}$ asserts the condition under which
+$\cfgnt{l}_\mathit{null}$ is possible, (ii) $\theta_\mathit{new}$ is
+active when $\cfgnt{r}_f$ points to the fresh location, (iii) each
+member of $\theta_\mathit{alias}$ restricts $\cfgnt{r}_f$ to a
+particular alias in $\rho$, and at the same time, not alias any member
+of $\rho$ that was initialized earlier than the current choice, and
+(iv) $\theta_\mathit{orig}$ implements conditional initialization to
+preserve the original heap structure.  These sets are added into the
+heap on $\cfgnt{r}_f$ after the fields for $\cfgnt{l}_f$ are
+initialized to $\cfgnt{r}_\mathit{un}$.
 
-To summarize, the heap summary algorithm creates
-many references that are auxiliary literals or stack literals to
-define the structure of the bipartite graph.  It only uses input heap
-references for constraints expressing potential aliasing. A solver
-reasons over the aliasing relationships, and a satisfying assignment
-uniquely identifies active edges in the graph. Those active edges
-describe a concrete heap and its shape.
+\begin{figure*}[t]
+\begin{center}
+\begin{tabular}[c]{c|c|c|c}
+\begin{tabular}[c]{c}
+\scalebox{0.81}{\input{origHeap.pdf_t}} \\
+\end{tabular} &
+\begin{tabular}[c]{c}
+\scalebox{0.81}{\input{summarizeXHeap.pdf_t}} \\
+\end{tabular} &
+\begin{tabular}[c]{c}
+\scalebox{0.81}{\input{summarizeYHeap.pdf_t}} \\
+\end{tabular} &
+\begin{tabular}[c]{l}
+$\rho := \{ (\cfgnt{r}_1^i\ \cfgnt{l}_1 \}$ \\
+$\theta_\mathit{null} := \{ ( \cfgnt{r}_2^i = \cfgnt{r}_\mathit{null}\ \cfgnt{l}_\mathit{null}) \}$\\
+$\theta_\mathit{new} := \{ ( \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_1^i\ \cfgnt{l}_2) \}$\\
+$\theta_\mathit{alias} := \{ ( \cfgnt{r}_1^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i = \cfgnt{r}_1^i\ \cfgnt{l}_1) \}$\\
+$\theta_\mathit{orig} := \{ \}$ \\
+$\phi_{\mathit{1a}} := \cfgnt{r}_1^i = \cfgnt{r}_\mathit{null} $ \\
+$\phi_{\mathit{1b}} := \cfgnt{r}_1^i \neq \cfgnt{r}_\mathit{null} $  \\
+$\phi_{\mathit{2a}} := \cfgnt{r}_2^i = \cfgnt{r}_\mathit{null}$ \\
+$\phi_{\mathit{2b}} := \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_1^i$ \\
+$\phi_{\mathit{2c}} :=  \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i = \cfgnt{r}_1^i $ \\
+\end{tabular} \\
+(a) & (b) & (c) & (d) \\
+\end{tabular}
+\end{center}
+\caption{An example that initializes $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ and $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$.
+(a) Initial heap structure.
+(b) After $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ is initialized.
+(c) After $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ is initialized.
+(d) Sets in the summarize rule and constraints on the edges.}
+\label{fig:initHeap}
+\end{figure*}
 
-For example, if the solver assigns input heap variables $\cfgnt{r}$ and $\cfgnt{r}^\prime$
-such that $\cfgnt{r} = \cfgnt{r}^\prime$ is true, then there exists
-some location $\cfgnt{l}$ and constraints $\phi$ and $\phi^\prime$ such
-that
-\begin{compactitem}
-\item $\lp\phi\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r})$; and
-\item $\lp\phi^\prime\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r}^\prime)$; and
-\item $\phi$ and $\phi^\prime$ hold in the aliasing assignments from the solver.
-\end{compactitem}
-In this way, the graph groups heaps with the conditions under which
-those heaps exist. This representation separates the constraint
-problem from the morphology problem: it is possible to update the heap
-without having to rewrite constraints. Without this separation, it
-would not be possible to lazily initialize heap locations along a
-program path.
+We visualize the initialization process in~\figref{fig:initHeap}. The
+graph in~\figref{fig:initHeap}(a) represents the initial heap. The
+reference superscripts $s$ and $i$ indicate the partition containing
+the reference.  In~\figref{fig:initHeap}, $\cfgnt{r}_0^s$ represents a
+stack reference for the $\cfgt{this}$ variable which has two fields
+$x$ and $y$ of the same type. Note that when no constraint is
+specified for a location, there is an implicit $\mathit{true}$
+constraint. For example, $\cfgnt{r}_0^s$ points to $\cfgnt{l}_0$ on
+the constraint $\mathit{true}$. The fields $x$ and $y$ point to the
+uninitialized reference $\cfgnt{r}_\mathit{un}$. The graph
+in~\figref{fig:initHeap}(b) represents the summary heap after the
+initialization of the $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{x}\rp$ field
+while the graph in~\figref{fig:initHeap}(c) represents the symbolic
+heap summary after the initialization of the
+$\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$ field following the
+initialization of $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{x}\rp$. The list
+in~\figref{fig:initHeap}(d) represents the various sets constructed in
+the summarize rule during the initialization of
+$\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$. We also define values of
+constraints used as labels in the graph.
 
-\subsection{State Transition Relation}
+\input{precise-fig-incomplete}
 
-The initial state of a Javalite program is constructed from its
-surface syntax on the $\cfgnt{P}$ production:
-$\lp\mu\ \lp\cfgnt{C}\ \cfgnt{m}\rp\rp$. Assuming that
-$\lp\cfgnt{L}\ \cfgnt{R}\rp$ is an empty heap with no references
-or locations and $\eta$ is an empty environment with no
-variables, the initial state is
-$$
-\begin{array}{l}
-\lp\mu 
-\ \cfgnt{L}[\cfgnt{r}_\mathit{null} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{null})\}\rp] 
-           [\cfgnt{r}_\mathit{un} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{un}\rp\}] \\
-\ \cfgnt{R}
-\ \cfgt{true}\ \eta\  \lp\lp\cfgt{new}\ \cfgnt{C}\rp\ \cfgt{@}\ \cfgnt{m}\ \cfgt{true}\rp\rp\ \cfgt{end}\rp
-\end{array}
-$$
-The first expression in the initial state is to construct a new object
-in the summary heap of type $\cfgnt{C}$. Note that the resulting object is not referenced
-by the input heap since it comes from the new-expression.  Once an
-instance of $\cfgnt{C}$ exists in the summary heap, the method
-$\cfgnt{m}$ of the class is invoked.
+There are two rewrite rules in~\figref{fig:fHeap}(a), one for reading
+the value of a field (field-access) and the other when we write to a
+field (field-write). Both rules first check that the operations can be
+performed on a non-null location.  In the field-access rewrite rule
+in~\figref{fig:fHeap} gets the field type $\cfgnt{C}$ and uses the
+summarize machine, \figref{fig:symInit}, to get a new summary heap
+that is initialized on the field $\cfgnt{f}$. After initialization,
+the summary heap is further modified to include a new stack reference
+pointing to the value set from the read. The new stack reference is
+the return value from the operation.
 
-In general, the semantics of Javalite are expressed as
-rewrites on strings using pattern matching. Consider the rewrite rule
-for the beginning of a field access instruction in the Javalite
-machine:
-$$
-\mprset{flushleft}
-	\inferrule[Field Access(eval)]{}{
-      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgnt{e}\ \cfgt{\$}\ \cfgnt{f}\rp \ \cfgnt{k}\rp  \rcom 
-      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp 
-	}
-$$
-If the string representing the current state matches the left side, then it
-creates the new string on the right. In this example, the new string
-on the right is now evaluating the expression $\cfgnt{e}$ in the field
-access, and it includes the continuation indicating that it still
-needs to complete the actual field access once the expression is
-evaluated.
+ \input{value-set-def}
 
-Other more complex rules, such as one to create a new instance of a
-class, define constraints on the rewrites and more complex
-transformations on the heap.
-$$
-\mprset{flushleft}
-	\inferrule[New]{
-      \cfgnt{r} = \mathrm{stack}_r\lp \rp\\
-      l = \mathrm{fresh}_l\lp \cfgnt{C}\rp\\\\
-      \cfgnt{R}^\prime = \cfgnt{R}[\forall \cfgnt{f} \in \mathit{fields}\lp \mathrm{C}\rp \ \lp \lp l\ \cfgnt{f}\rp  \mapsto \cfgnt{r}_\mathit{null} \rp ] \\\\
-      \cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}]
-    }{
-      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgt{new}\ \cfgnt{C}\rp \ \cfgnt{k}\rp  \rcom
-      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi\ \eta\ \cfgnt{r}\ \cfgnt{k}\rp 
-	}
-$$
-In this rule, when the string matches the new-expression, it is rewritten to use
-a new heap location where all of the fields for the new object point to
-$\cfgnt{r}_\mathit{null}$
-and the location map points a new stack reference to that new object.
+The value set computation is local: it only considers constraint
+locations on the reference $\cfgnt{r}$. Further, it only includes
+things that are feasible under the current path condition $\phi_g$. It
+also ensures that the access path is valid. There is a constraint
+$\phi$ from the base reference $r$ and a given location. Once a
+location $l$ is selected, the field $\cfgnt{f}$ is accessed to get
+another reference $r^\prime$, and from that reference there is a set
+of locations each with a constraint. The first constraint $\phi$ from
+the base reference plus this second constraint to the actual location
+of the field $\phi^\prime$ comprise the access path. For each member
+of the value set, these constraints together with the global path
+constraint must be satisfied on some aliasing assignment.
 
-To show the heap summary algorithm is sound and complete with respect
-to properties proved by GSE, we define a transition relation that
-relates states according GSE and refer to it as $\rgse$ or $p \rgse
-p^\prime$. Similarly we define for the new summary heap algorithm
-$\rsym$ or $q \rsym q^\prime$. For simplicity, both use lazy
-initialization as opposed to lazier or lazier\#.
+For field-write in~\figref{fig:fHeap}, after the non-null check and
+strengthening of the global heap constraint, it computes the current
+references associated with the field in every location in
+$\Psi_\cfgnt{x}$. Please note that the reference $\cfgnt{r}_x$ is the
+base reference whose field, $\cfgnt{r}_\mathit{cur}$ is being written
+to while the reference $r$ is the target reference. The set $\Psi_x$
+contains tuples $(\phi\ l\ \cfgnt{r}_\mathit{cur})$ of constraints,
+locations, and references. These tuples represent access chains
+leading from $\cfgnt{r}_x$ to the reference of the field,
+$\cfgnt{r}_\mathit{cur}$. The goal is to change the fields to no
+longer point to $\cfgnt{r}_\mathit{cur}$, but rather fresh references
+that have both the original locations before the write and the
+locations from the write in the value sets (i.e., conditional
+write). Since the target of the write is $r$, the rule checks that the
+location constraint pairs of $\cfgnt{L}(\cfgnt{r})$ are satisfiable
+when accessed through the $\cfgnt{r}_x$ chain in the strengthening
+function.  \input{st-def} Constraints on locations are strengthened
+with new aliasing conditions and those that are feasible with the
+current path constraint are retained.
 
-The full operational semantics for $\rgse$ are in the supplemental
-document. In the next section, we present the rewrite rules specific
-to $\rsym$.
+Strengthening in the field write creates a value set that contains two
+types of locations: those for the case where the write is feasible
+(the first call), and those for the case where it is not (the second
+call).  This is the conditional in the write. In the case that $\phi$
+is true then $\cfgnt{r}_\mathit{cur}$ will point to the constraint
+location pairs of $\cfgnt{L}(\cfgnt{r})$ while if $\phi$ is false then
+$\cfgnt{r}_\mathit{cur}$ will continue to point to the constraint
+location pair it is currently referenced.  As the references are
+immutable, the rule creates fresh references for each
+$\cfgnt{r}_\mathit{cur}$ and points them to the appropriate value
+sets.
+
+\input{precise-eq}
+
+\begin{figure*}
+\begin{center}
+\begin{tabular}[c]{c}
+\scalebox{1.0}{\usebox{\boxPEQ}} \\
+% & \usebox{\boxPEX} \\ \\
+%(a) & (b) \\
+\end{tabular}
+\end{center}
+\caption{The reference compare rewrite rule for true, $\rsym^\mathit{E}$ outcomes.}
+\label{fig:eqs}
+\end{figure*}
+
+The rewrite rules to compare two references in the symbolic summary
+heap are shown in~\figref{fig:eqs}. The equals references-true rewrite
+rule returns true when two references $\cfgnt{r}_0$ and $\cfgnt{r}_1$
+\emph{can} be equal. Intutively, $\Phi_\alpha$ contains all
+constraints under which $\cfgnt{r}_0$ and $\cfgnt{r}_1$ may point to
+the same location in the symbolic summary heap. The second set,
+$\Phi_0$, contains constraints under which the reference $\cfgnt{r}_0$
+points to corresponding locations such that the reference
+$\cfgnt{r}_1$ \emph{does not} point to those locations under any
+constraint. Finally, the set, $\Phi_1$, contains constraints under
+which $\cfgnt{r}_1$ points to corresponding locations and
+$\cfgnt{r}_0$ \emph{does not} point to those locations under any
+constraint. We use the three sets of constraints to update the current
+global heap constraint $\phi_g$ and create a new global heap
+constraint $\phi_g^\prime$. We add to $\phi_g$ the disjunction of the
+constraints in $\Phi_\alpha$ to indicate that if any of the
+constraints are satisfiable, then references $\cfgnt{r}_0$ and
+$\cfgnt{r}_1$ can be equal. Furthermore, we conjoin to the global heap
+constraint $\phi_g^\prime$, the conjunctions of negations to the
+constraints in $\Phi_0$ and $\Phi_1$. This indicates for locations
+that are not common to the references, the negations of their
+constraints are satisfiable. The rule does not complete (i.e., is not
+feasible) if the new global constraint is not satisfied on any
+aliasing assignment. In such a case, the $\cfgt{true}$ outcome is not
+possible on any heap in the summary. Before the rewrite rule returns
+$\cfgt{true}$ we check the satisfiability of the updated global heap
+constraint. The reference-false is the logical dual of the rule.

### 2015-01-28 cav-2015-tex/st-def.tex
adding text and rules for the main body

\begin{definition}
\label{def:ST}
The strengthen function $\mathbb{ST}(\cfgnt{L},\cfgnt{r},\phi,\phi_g)$ strengthens every
constraint from the reference $\cfgnt{r}$ with $\phi$ and keeps only location-constraint
pairs that are satisfiable after this strengthening with the inclusion of the global heap constraint $\phi_g$:
\[
\begin{array}{rcl} 
\mathbb{ST}(\cfgnt{L},\cfgnt{r},\phi,\phi_g) & = & \{ (\phi\wedge\phi^\prime\ \cfgnt{l}^\prime) \mid  \\
& & \ \ \ \ (\phi^\prime\ \cfgnt{l}^\prime)\in \cfgnt{L}(\cfgnt{r})\wedge\mathbb{S}(\phi\wedge\phi^\prime\wedge\phi_g) \}
\end{array}
\]
\end{definition}

### 2015-01-30 cav-2015-tex/abstract.tex
Re-wrote the abstract to reflect the new approach.

@@
-A fundamental challenge of using symbolic execution for software
-analysis has been the treatment of dynamically allocated
-data. Generalized symbolic execution (GSE) techniques have addressed
-this challenge by materializing a concrete heap lazily during field
-accesses.  These techniques however, exacerbate the path explosion
-problem.  In this work, we present a summary heap approach which takes
-inspiration from the static analysis domain and defines a bipartite
-graph to encode multiple heaps in single representation, which, unlike
-state-of-the-art static analysis approaches, (i) supports aliasing,
-(ii) does not require rewrite of constraints on heap updates, and
-(iii) can initialize the heap-on-the-fly. We also define a summary
-heap algorithm to perform heap updates during symbolic execution on
-this representation in order to mitigate the path explosion problem in
-GSE techniques. Our approach is sound and complete with respect to the
-properties provable by GSE. A preliminary evaluation of our
-implementation in Java Pathfinder framework shows the summary heap
-enables the initialization of larger, more complex heaps than
-previously possible.
+A fundamental challenge of using symbolic execution for software analysis 
+has been the treatment of dynamically allocated data. The main problems 
+center on dereferencing symbolic data. When dereferencing symbolic values 
+from an unconstrained symbolic input heap, existing methods resort to either 
+approximation or case splitting. Since both options negate significant 
+advantages of symbolic execution techniques, finding a definitive symbolic 
+heap representation has been an open problem. This paper introduces a 
+new technique for representing and manipulating symbolic heaps that (i) 
+reasons over arbitrary, unbounded, and otherwise unconstrained symbolic 
+input values, and (ii) produces a path condition that exactly represents all 
+possible program values for a given execution path. The symbolic heap 
+representation is the first to produce path conditions that are provably sound 
+and complete with respect to all program properties verifiable through 
+symbolic execution, without any restrictions or simplifying assumptions. An 
+evaluation of a proof-of-concept implementation in the Java Pathfinder 
+framework is presented, demonstrating the computational feasibility of the 
+approach.
+
+%A fundamental challenge of using symbolic execution for software
+%analysis has been the treatment of dynamically allocated
+%data. Generalized symbolic execution (GSE) techniques have addressed
+%this challenge by materializing a concrete heap lazily during field
+%accesses.  These techniques however, exacerbate the path explosion
+%problem.  In this work, we present a summary heap approach which takes
+%inspiration from the static analysis domain and defines a bipartite
+%graph to encode multiple heaps in single representation, which, unlike
+%state-of-the-art static analysis approaches, (i) supports aliasing,
+%(ii) does not require rewrite of constraints on heap updates, and
+%(iii) can initialize the heap-on-the-fly. We also define a summary
+%heap algorithm to perform heap updates during symbolic execution on
+%this representation in order to mitigate the path explosion problem in
+%GSE techniques. Our approach is sound and complete with respect to the
+%properties provable by GSE. A preliminary evaluation of our
+%implementation in Java Pathfinder framework shows the summary heap
+%enables the initialization of larger, more complex heaps than
+%previously possible.

### 2015-01-30 cav-2015-tex/abstract.tex
New abstract

--- 2015-01-15 cav-2015-tex/abstract.tex
@@
 A fundamental challenge of using symbolic execution for software
-analysis has been the treatment of dynamically allocated
-data. Generalized symbolic execution (GSE) techniques have addressed
-this challenge by materializing a concrete heap lazily during field
-accesses.  These techniques however, exacerbate the path explosion
-problem.  In this work, we present a summary heap approach which takes
-inspiration from the static analysis domain and defines a bipartite
-graph to encode multiple heaps in single representation, which, unlike
-state-of-the-art static analysis approaches, (i) supports aliasing,
-(ii) does not require rewrite of constraints on heap updates, and
-(iii) can initialize the heap-on-the-fly. We also define a summary
-heap algorithm to perform heap updates during symbolic execution on
-this representation in order to mitigate the path explosion problem in
-GSE techniques. Our approach is sound and complete with respect to the
-properties provable by GSE. A preliminary evaluation of our
-implementation in Java Pathfinder framework shows the summary heap
-enables the initialization of larger, more complex heaps than
-previously possible.
+analysis is the treatment of dynamically allocated data. Existing
+static analysis techniques over-approximate the potential heaps,
+dynamic symbolic execution techniques often under-approximate the
+heaps, while generalized symbolic execution leads to excessive
+case-splitting. This paper introduces a compact heap representation
+along with heap update rules that (i) allow reads and writes of
+symbolic references, (ii) does not require constraint rewriting, and
+(iii) supports arbitrary recursive data structures. As such, the
+representation and update rules capture all possible heaps that follow
+a common execution path. More importantly, in contrast to
+state-of-the-art techniques, the definition and update rules are
+unconstrained and not subject to bounds such as the number of heap
+locations, aliasing, or memory partitions. An evaluation of a
+proof-of-concept implementation in the Java Pathfinder framework is
+presented to demonstrate the computational feasibility of the approach
+over several classical symbolic execution benchmarks.

### 2015-02-02 cav-2015-tex/summary-heap.tex

--- 2014-11-13 tex/heap.tex
@@
-\subsection{Summary Heaps as Bipartite Graphs}
-A novel contribution of summary heaps for symbolic execution is the
-labeled bipartite graph representation of the heap which enables a
-summary heap to group heaps together that follow the same control flow
-to a given point of execution. The graph structure is able to capture
-group membership and compute value sets using entirely non-recursive
-local lookup. Additionally, updates on the heap do not require
-rewriting the path condition.
+\section{Summary Heap Framework}
+The summary heap algorithm is defined using
+Javalite~\cite{saints-MS}. The small-step semantics of Javalite,
+defined as a syntactic machine using a CESK architecture, are modified
+to perform symbolic execution on a summary heap. The surface (input)
+and machine (state) syntax is shown
+in~\figref{fig:syntax}. Terminals are in bold face while non-terminals
+are italicized. Ellipses indicate zero or more repetitions. Tuples
+omit the commas for compactness.
 
-The bipartite graph itself consists of references, $\cfgnt{r}$, and
-constraint-location pairs, $\lp\phi\ \cfgnt{l}\rp$. The graph is
+\input{surface-syntax}
+\input{machine-syntax}
+\begin{figure}[t]
+\begin{center}
+\begin{tabular}{c}
+\scalebox{0.9}{\usebox{\boxSurface}} \\
+(a) \\\\
+\scalebox{0.9}{\usebox{\boxMachine}} \\
+(b)
+\end{tabular}
+\end{center}
+\caption{Syntax for Javalite. (a) The Javalite surface syntax. (b) The machine syntax with $\bowtie\ \in \{\wedge,\vee,\Rightarrow\}$.}
+\label{fig:syntax}
+\end{figure}
+
+A Javalite program, $\cfgnt{P}$, is a registry of classes, $\mu$, with
+a tuple indicating a class, $\cfgnt{C}$, and a method, $\cfgnt{m}$,
+where execution starts. The only primitive type in Javalite is
+Boolean. For simplicity in presentation, classes have only non-primitive fields, and methods have a single
+parameter. Expressions, $\cfgnt{e}$,  
+include statements, and they
+ use '$\cfgt{:=}$' to indicate assignment and '$\cfgt{=}$' to indicate comparison.
+The dot-operator for field access is replaced by '$\cfgt{\$}$', and the dot-operator
+for method invocation is replaced by '$\cfgt{@}$' since '.' is reserved in PLT Redex. There is no explicit return
+statement; rather, the value of the last expression is
+used as the return value. A variable is always indicated by \cfgnt{x}
+and a value by \cfgnt{v}. A value can be a reference in the heap, $\cfgnt{r}$, or any of the special values shown in~\figref{fig:syntax}(a). 
+Only type correct programs are given as input to the machine.
+
+The state of the Javalite machine,
+$\cfgnt{s}$, includes the program registry, $\mu$, a pair of functions defining the heap
+$\lp\cfgnt{L}\ \cfgnt{R}\rp$, a constraint,
+$\phi$, defined over references in the heap, the environment, $\eta$,
+for local variables, and the continuation $\cfgnt{k}$. The registry never changes so it is omitted from the state tuple in the rest of the presentation.  The more
+complex structures, such as the environment and heap, are defined as lists that
+start with empty, \cfgnt{mt}. These lists are treated as partial functions so
+$\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference $\cfgnt{r}$ associated with variable
+$\cfgnt{x}$. The notation $\eta^\prime = \eta[\cfgnt{x} \mapsto
+  \cfgnt{v}]$ defines a new partial function $\eta^\prime$ that is
+the same as $\eta$ except that the variable $\cfgnt{x}$ now maps to
+$\cfgnt{v}$. The continuation $\cfgnt{k}$ indicates where the hole, $\cfgt{*}$, is located, stores temporary computation, and keeps track of the next 
+computation. For example, the continuation
+$\lp\cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp$ indicates
+that the machine is evaluating the expression for the object
+reference on which the field $\cfgnt{f}$ is going to be accessed. Once
+the field access is complete, the machine continues with $\cfgnt{k}$.
+
+A summary heap is a bipartite graph on references, $\cfgnt{r}$, and
+constraint location pairs, $\lp\phi\ \cfgnt{l}\rp$. The graph is
 expressed in the location map, $\cfgnt{L}$, and the reference map,
@@
 $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the reference
-associated with the given location-field pair in the heap.
+associated with the given location-field pair in the heap. References
+in the graph are immutable. Locations, however, are mutated on
+updates. The structure with the immutability of references mean that
+look-ups in the heap are non-recursive and updates do not modify the
+current path condition.
 
-There are several properties of the summary heap enforced by the
-rewrite rules that are invariant and important to the correctness
-proofs in \secref{sec:bisim}: \emph{reference partitions},
-\emph{immutability}, \emph{determinism}, \emph{type
-  consistency}, and \emph{null and uninitialized}.
-
-\emph{Reference partitions}: new references drawn from
-  three distinct partitions (i) $\mathrm{init}_\cfgnt{r}()$ for references for the \emph{input heap}, (ii) $\mathrm{fresh}_\cfgnt{r}()$ for references for \emph{auxiliary literals}, and
-  (iii) $\mathrm{stack}_\cfgnt{r}()$ for references for \emph{stack literals} in the expressions and
-  continuations. The references strictly increase in value on each
-  call, and modular arithmetic is used to determine the partition to
-  which a reference belongs.
+The soundness and completeness proofs rely on a set of invariants that
+are preserved by the small-step semantics during symbolic execution:
+\emph{reference partitions}, \emph{null and uninitialized}, \emph{immutability}, \emph{determinism}, and
+\emph{type consistency}.
 \begin{compactdesc}
-\item[Input heap:] these references have two
-  interpretations: one as a literal and another as a variable. As a literal it is a node in
-  the summary heap. As a variable it is a term in any number of constraints that label
-  edges in the summary heap. Only input heap references and the
-  special reference $\cfgnt{r}_\mathit{null}$ appear in constraints
-\item[Auxiliary literals:] these references are only used to define additional structure in
-  the bipartite graph and are not part of any constraint and do not appear
-  in any environment, expression, or continuation.
-\item[Stack references:] these references are also used to define additional structure in the bipartite graph but may also appear in the environment, expression, or continuation.
-These are not part of any constraint.
-\end{compactdesc}
-Reference partitions are a critical piece to the existence proof of a
-bisimilation between the summary heap algorithm and generalized
-symbolic execution (see \secref{sec:bisim}).
-
-\emph{Immutability} means that a reference does not change in the
-location map. It always points to the same set of constraint location
-pairs. This property ensures that constraints never need to be
-rewritten as the program evolves its state.
-
-\emph{Determinism} means that a reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously. In the definition $\cfgnt{L}^\leftarrow$ is the pre-image of the location map.
-$$
-\begin{array}{l}
-\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
-\ \ \ \ (\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
-\end{array}
-$$
-Informally, any two constraint location pairs connected to a
-common reference form a contradiction: only one can be true in any
-satisfying assignment. The property ensures that any satisfying assignment
-resolving aliasing relationships results in a deterministic heap: a
-field access returns a single location under that assignment.
-
-\emph{Type consistency} implies that all locations associated with a reference have the same type.
-\[
-\begin{array}{l}
-\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
-\ \ \ \ (\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))
-\end{array}
-\]
-
-\emph{Null and Uninitialized} means that every summary heap contains 
+\item[Reference partitions] means that a reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
+  heap} that includes $\cfgnt{r}_\mathit{null}$ (these are created by lazy initialization and are the only references that appear as variables in
+  constraints); $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
+  literals} that includes $\cfgnt{r}_\mathit{un}$ (these add structure but do not appear elsewhere); and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
+  literals} (these appear in environments, expressions, and continuations).
+\item[Null and Uninitialized] means that every summary heap contains 
 a special location for null ($\cfgnt{l}_\mathit{null}$), and a special
 location for uninitialized
-  ($\cfgnt{l}_\mathit{un}$), with corresponding references
-  $\cfgnt{r}_\mathit{null}$ and
-  $\cfgnt{r}_\mathit{un}$, respectively. $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
+  ($\cfgnt{l}_\mathit{un}$) with $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
   \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
   $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
-  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. These special references can be used in constraints.
+  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. 
+\item[Immutability] means that a reference does not change in the
+location map, and as a consequence, constraints never need to be
+rewritten as the program evolves its state.
+\item[Determinism] means that a reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
+$
+\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
+(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
+$
+where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. 
+\item[Type consistency] means that all locations associated with a reference have the same type:
+$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
+(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$
 
-To summarize, the heap summary algorithm creates
-many references that are auxiliary literals or stack literals to
-define the structure of the bipartite graph.  It only uses input heap
-references for constraints expressing potential aliasing. A solver
-reasons over the aliasing relationships, and a satisfying assignment
-uniquely identifies active edges in the graph. Those active edges
-describe a concrete heap and its shape.
+\end{compactdesc}
 
-For example, if the solver assigns input heap variables $\cfgnt{r}$ and $\cfgnt{r}^\prime$
-such that $\cfgnt{r} = \cfgnt{r}^\prime$ is true, then there exists
-some location $\cfgnt{l}$ and constraints $\phi$ and $\phi^\prime$ such
-that
-\begin{compactitem}
-\item $\lp\phi\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r})$; and
-\item $\lp\phi^\prime\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r}^\prime)$; and
-\item $\phi$ and $\phi^\prime$ hold in the aliasing assignments from the solver.
-\end{compactitem}
-In this way, the graph groups heaps with the conditions under which
-those heaps exist. This representation separates the constraint
-problem from the morphology problem: it is possible to update the heap
-without having to rewrite constraints. Without this separation, it
-would not be possible to lazily initialize heap locations along a
-program path.
+A key insight to the summary heap is that although many auxiliary or
+stack literals are created in symbolic execution with lazy
+initialization, only input heap references appear in constraints
+expressing potential aliasing relationships. A solver reasons over the
+aliasing relationships, and a satisfying assignment uniquely
+identifies active edges in the graph. Those active edges describe a
+representative concrete heap and its shape. For example, if the solver
+assigns input heap variables $\cfgnt{r}$ and $\cfgnt{r}^\prime$ such
+that $\cfgnt{r} = \cfgnt{r}^\prime$ is true, then there exists some
+location $\cfgnt{l}$ and constraints $\phi$ and $\phi^\prime$ such
+that (i) $\lp\phi\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r})$; (ii)
+$\lp\phi^\prime\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r}^\prime)$; and
+(iii) $\phi$ and $\phi^\prime$ hold in the aliasing assignments from
+the solver.  In this way, the graph groups heaps with the conditions
+under which those heaps exist so look-ups are non-recursive and
+updates do not modify the path condition or require rewrites on
+constraints.
 
-\subsection{State Transition Relation}
+\subsection{Semantics}
 
-The initial state of a Javalite program is constructed from its
-surface syntax on the $\cfgnt{P}$ production:
-$\lp\mu\ \lp\cfgnt{C}\ \cfgnt{m}\rp\rp$. Assuming that
-$\lp\cfgnt{L}\ \cfgnt{R}\rp$ is an empty heap with no references
-or locations and $\eta$ is an empty environment with no
-variables, the initial state is
+Given an input program $\lp\mu\ \lp\cfgnt{C}\ \cfgnt{m}\rp\rp$, the initial machine state is
 $$
@@
 $$
-The first expression in the initial state is to construct a new object
-in the summary heap of type $\cfgnt{C}$. Note that the resulting object is not referenced
-by the input heap since it comes from the new-expression.  Once an
-instance of $\cfgnt{C}$ exists in the summary heap, the method
-$\cfgnt{m}$ of the class is invoked.
+The expression in the initial state constructs a new object of type
+$\cfgnt{C}$ and then invokes the method $\cfgnt{m}$ in that
+object.
 
-In general, the semantics of Javalite are expressed as
+The semantics are expressed as
 rewrites on strings using pattern matching. Consider the rewrite rule
-for the beginning of a field access instruction in the Javalite
-machine:
+for the beginning of a field access instruction:
 $$
@@
 and the location map points a new stack reference to that new object.
+Notice that references for objects from the new-expression are auxiliary literals
+so they do not appear in any constraint in the summary heap as an aliasing option.
 
+\begin{comment}
+MOVE TO THE PROOF SECTION
 To show the heap summary algorithm is sound and complete with respect
-to properties proved by GSE, we define a transition relation that
-relates states according GSE and refer to it as $\rgse$ or $p \rgse
-p^\prime$. Similarly we define for the new summary heap algorithm
-$\rsym$ or $q \rsym q^\prime$. For simplicity, both use lazy
-initialization as opposed to lazier or lazier\#.
-
-The full operational semantics for $\rgse$ are in the supplemental
-document. In the next section, we present the rewrite rules specific
-to $\rsym$.
+to properties proved by GSE, a transition relation that
+relates states according GSE is defined as $\rgse$ or $p \rgse
+p^\prime$. Similarly the transition relation for the new summary heap algorithm is given as
+$\rsym$ or $q \rsym q^\prime$ (defined in the next section). For simplicity, both use lazy
+initialization as opposed to lazier or lazier\#. The full operational semantics for $\rgse$ are in the appendix. 
+\end{comment}

### 2015-02-02 cav-2015-tex/summary-heap.tex
Finished crunch on math

@@
 \section{Summary Heap Framework}
+\label{sec:sh}
 The summary heap algorithm is defined using
@@
 so they do not appear in any constraint in the summary heap as an aliasing option.
-
-\begin{comment}
-MOVE TO THE PROOF SECTION
-To show the heap summary algorithm is sound and complete with respect
-to properties proved by GSE, a transition relation that
-relates states according GSE is defined as $\rgse$ or $p \rgse
-p^\prime$. Similarly the transition relation for the new summary heap algorithm is given as
-$\rsym$ or $q \rsym q^\prime$ (defined in the next section). For simplicity, both use lazy
-initialization as opposed to lazier or lazier\#. The full operational semantics for $\rgse$ are in the appendix. 
-\end{comment}

### 2015-02-02 cav-2015-tex/bisimulation.tex
Somebody forgot to add a file...

--- 2014-11-13 tex/bisimulation.tex
@@
 \label{sec:bisim}
-Recall that $p \rgse p^\prime$ is the binary relation over the universe of states, $S$,
-according to GSE with lazy initialization. Similarly, $q \rsym q^\prime$ is the relation for the summary heap algorithm
-presented in this paper. The principle theoretical result is the
-existence of a bisimulation between states related on $p \rgse p^\prime$
-and the states related on $q \rsym q^\prime$.  A corollary is that $\rsym$ is
-both sound and complete with respect to properties provable in $\rgse$. Only a summary of the
-proofs is given due to space.
-
-The inspiration for $\rsym$ came from a desire to create
-a new way to initialize heap objects that avoided initializing heaps
-that traverse the same control flow paths. The proof only reasons about well-formed states, which have
-deterministic, type-consistent heaps, and feasible environments, expressions, and
-continuations. Well-formed states always have successors unless at the end of a 
-program execution. It is trivial to show that the set of well-formed states is closed
-under the transition relation.
-
-Let $p \rgse p^\prime$ be defined as a union over state relations:
-$$
-\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E^\prime} \cup \rcom
-$$
-where \emph{A} is a field access after evaluating the expression for the base reference $\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
-\rightarrow \cfgnt{k}\rp$, \emph{W} is a field write after evaluating the expression for the right operand$\lp
-\cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
-\cfgnt{k}\rp$, \emph{E} is a reference compare after evaluating the left and right operand expressions $\lp
-\cfgnt{v}\ \cfgt{=}\ \cfgnt{*} \rightarrow \cfgnt{k}\rp$, the prime symbol
-indicates a null reference in the operation or a false outcome, and
-\emph{\com} is everything else in the language. Any state relation, say $\rightarrow_x$, is trivially extended to sets of states as
+The theoretical result is the existence of a bisimulation between
+states related by GSE with lazy initialization ($p \rgse p^\prime$)
+and states related by the algorithm in this paper ($q \rsym q^\prime$). The relations are on the universe of \emph{well-formed} states $S$, which have the
+properties in \secref{sec:sh} with the constraint that
+the states are \emph{feasible}: successors exist unless at
+\cfgt{end}. Let $p \rgse p^\prime$ be a union over relations for GSE (see appendix):
+$\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E^\prime} \cup \rcom$, where \emph{A} is a field access after evaluating the expression for
+the base reference $\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow
+\cfgnt{k}\rp$, \emph{W} is a field write after evaluating the
+expression for the right operand $\lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
+\cfgnt{k}\rp$, \emph{E} is a reference compare after evaluating the
+left and right operands $\lp \cfgnt{v}\ \cfgt{=}\ \cfgnt{*}
+\rightarrow \cfgnt{k}\rp$, the prime symbol indicates a null reference
+in the operation or a false outcome, and \emph{\com} is everything
+else in the language. Any state relation, say $\rightarrow_x$, is
+trivially extended to sets of states as
 $$
@@
 $$
-This definition embodies the notion of splitting groups of heaps at
+The relation captures the notion of splitting groups of heaps at
 certain operations. For example, suppose we have a set $P$ containing a single state $p$
 with all references uninitialized. If $p$ is a field access state, it has two
-potential successors: one with a non-null reference, and one with a null reference. 
-The $\rsgse$ relation has two successors at that point to divide $P$ into the two outcomes. In contrast, the
-set $P \rgse^\com P^\prime$ only has a single successor since anything in $\rightarrow_\com$ is not related to control flow (e.g., variable look up, creating continuations, etc.).
+potential successors in GSE: a non-null reference and a null reference. 
+Thus, the $\rsgse$ relation has two successors and divides $P$ into the two outcomes.
 
@@
 constraint on the feasibility of that mapping in the presence of a
-path constraint from symbolic execution. Subscripts indicates state tuple
+path constraint from symbolic execution. Subscripts indicate state tuple
 members as in $p = (
@@
 \begin{array}{l}
- s_p \rightharpoonup_{h} s_q \Leftrightarrow \\
-\ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}\ ( \exists \phi_\alpha\ (\exists \phi_\beta\ ( \\ 
-\ \ \ \ \ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow \\
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ \\
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  )) ) ) ) )
+ s_p \rightharpoonup_{h} s_q \Leftrightarrow 
+\exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}\ ( \exists \phi_\alpha\ (\exists \phi_\beta\ ( \\ 
+\ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow 
+(\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ 
+ )) ) ) ) )
 \end{array}
@@
 \end{definition}
-
 \begin{definition}
@@
 The \textbf{homomorphism constraint} is
-\begin{align*}
-\mathbb{HC}(p \rightharpoonup_{h} q) &= \\
+%\begin{align*}
+\[
+\mathbb{HC}(p \rightharpoonup_{h} q) = 
 \bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_p^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_q^\rightarrow)\}
-\end{align*}
+\]
+%\end{align*}
 \end{definition}
-The functional equivalence between heaps on a homomorphism and
-a homomorphism constraint asserts a common structure in the two heaps under certain
-conditions. The equivalence is used to related states in $p \rgse
+Functional equivalence asserts a common structure in the two heaps under certain
+conditions. It is used to relate states in $p \rgse
 p^\prime$ to states in $q \rsym q^\prime$.
@@
 \cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, and there exists a
-homomorphism $p \rightharpoonup_{h}
-q$ such that
-\begin{equation}
-\label{eqn:valid}
- \mathbb{S}( \phi_q \wedge \mathbb{HC}(s_p \rightharpoonup_{h} s_q) ) 
-\end{equation}
-The represented relation is extended to sets of states $P$ and a single state $q$ as\footnote{The full proof argues $P \sqsubset Q$ but that any member $Q$ represents that same set of heaps as any other member of $q$ so it is sufficient to a member of $q$ in the relation.}
-$$
-P \sqsubset q \Longleftrightarrow \forall p\ (p \sqsubset q \Rightarrow p \in P)
-$$
+homomorphism $p \rightharpoonup_{h} q$
+such that $\mathbb{S}( \phi_q \wedge \mathbb{HC}(s_p \rightharpoonup_{h} s_q) )$.
+The represented relation is extended to sets of states $P$ and a single state $q$ as
+$P \sqsubset q \Longleftrightarrow \forall p\ (p \sqsubset q \Rightarrow p \in P)$.
 \end{definition}
@@
 \end{definition}
-As is typical, the functional reasons over a forward and backward
-simulation, while the application to dissimilar states using a
-meta-relation, $\rsgse$, is somewhat non-standard; though it is convenient
-in this instance since it captures the notion of $q$ as a set of
-states \cite{Sangiorgi:2011}.
+Although the functional reasons over a forward and backward
+simulation as typical~ \cite{Sangiorgi:2011}, its use of a meta-relation, $\rsgse$, is unique.
 
-In the following lemma, recall that $S$ is the universe of well-formed states, and the
-set $S_A \subseteq S$ is the set of states at a field access continuation having computed the base reference.
+In the lemma, $S$ is the universe of well-formed states, and the
+set $S_A \subseteq S$ is states at a field access continuation having computed the base reference.
 \begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
@@
 \end{proof}
+
 Similar lemmas are proved for field write and equals reference. These
-require additional lemmas on properties of the summarize machine
-$\rightarrow_S$. Specifically, that it preserves determinism, it
-preserves the homomorphism, and it preserves the satisfiability of the homomorphism constraint
+require additional lemmas on the summarize machine
+$\rightarrow_S$: that it preserves determinism, the
+homomorphism, and the satisfiability of the homomorphism constraint
 
@@
 \stackrel{n}{\rsym} q^\prime$ is similarly defined. Completeness and
-soundness are readily established by \thref{th:bisim} and inducting
+soundness fall out of \thref{th:bisim} by inducting
 over $n$.

### 2015-02-02 cav-2015-tex/bisimulation.tex
Removed math mode on corollaries

@@
 If $P \in 2^{S_\mathit{A}}$ and $q \in S$ are such that $P \sqsubset q$ then for any $p \in P$
-$$
-\forall p^\prime\ (p \stackrel{n}{\rgse} p^\prime \Rightarrow \exists q^\prime\ (q \stackrel{n}{\rsym} q^\prime \wedge p^\prime \sqsubset q^\prime))
-$$
+$\forall p^\prime\ (p \stackrel{n}{\rgse} p^\prime \Rightarrow \exists q^\prime\ (q \stackrel{n}{\rsym} q^\prime \wedge p^\prime \sqsubset q^\prime))$
 \end{corollary}
@@
 If $P \in 2^{S_\mathit{A}}$ and $q \in S$ are such that $P \sqsubset q$ then
-$$
-\forall q^\prime\ (q \stackrel{n}{\rsym} q^\prime \Rightarrow \exists p \in P\ (\exists p^\prime\ (p \stackrel{n}{\rgse} p^\prime \wedge p^\prime \sqsubset q^\prime)))
-$$
+$\forall q^\prime\ (q \stackrel{n}{\rsym} q^\prime \Rightarrow \exists p \in P\ (\exists p^\prime\ (p \stackrel{n}{\rgse} p^\prime \wedge p^\prime \sqsubset q^\prime)))$
 \end{corollary}

### 2015-02-03 cav-2015-tex/evaluation.tex
updates to eval section

@@
+\section{Evaluation}
+
 %\begin{figure*}[t]
@@
    &\multicolumn{3}{|c|}{Time (seconds)} &\multicolumn{3}{|c|}{States} &\multicolumn{3}{|c|}{ Paths }\\
-								&	&\gsetxt{} & L\#		&SL		&\gsetxt{}	& L\# & SL&\gsetxt{}	& L\# 	& SL\\
+								&	&\gsetxt{} & L\#		&SH		&\gsetxt{}	& L\# & SH&\gsetxt{}	& L\# 	& SH\\
    \hline
@@
   \end{tabular}}
-  \caption{Comparing the efficiency of the summary heap approach to GSE and Lazier\# algorithms.}
+  \caption{Comparing the efficiency of the summary heap with the GSE and Lazier\# algorithms.}
   \label{tab:results}
@@
 %\subsection{Analysis}
+We empirically evaluate the \symtxt{}
+algorithm for analyzing programs with unbounded heap allocated
+data in the context of symbolic execution.
+To perform our evaluation we implemented a prototype of the \symtxt{} 
+algorithm in Symbolic PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13} 
+and evaluate its efficacy on three Java data structure artifacts.
+SPF includes an implementation of GSE with lazy initialization.
+In recent work, we implemented the  Lazier and Lazier\#
+algorithms in SPF~\cite{Hillery:2014}.
 
-The results of the experiments are presented in Table
-\ref{tab:results}. Each row contains the results for the specified $k$-bound 
+The results of the experiments are presented in Table~\ref{tab:results}. 
+Each row reports the results for the specified $k$-bound 
 for each artifact evaluated. The columns show the total
 wall clock time in seconds, states explored, and paths generated for
-each of the algorithms. The headings \gsetxt{}, L\#, and SL correspond
+each algorithm. The headings \gsetxt{}, L\#, and SH correspond
 to the Generalized Symbolic Execution, Lazier\#, and \symtxt{}
-algorithms, respectively. Note that we do no present the results for
-the Lazier algorithm since they are almost identical to that of Lazier\#
-for our examples. Table entries containing '-' correspond to test runs
-that exceeded the allotted time bound of 10 minutes.
+algorithms, respectively. Note that we omit the results for
+the Lazier algorithm because they are nearly identical to the Lazier\#
+results for these artifacts. A table entry of  '-' indicates the analysis
+exceeded the allotted time bound of 10 minutes.
 
-In most tests, run times strongly favor the \symtxt{} algorithm, especially for
+The results in Table~\ref{tab:results} demonstrate the efficiency of the 
+\symtxt{} algorithm, especially for
 large $k$-values. Performance improvement ranges from $4.8x$ for
 BinarySearchTree at $k$=3, to $118x$ for LinkedList at $k$=6. In fact,
-for certain $k$-bounds a number of experiments completed exploration
+for some $k$-bounds a number of experiments completed exploration
 using the \symtxt{} algorithm in a few seconds whereas \gsetxt{} or Lazier\# were
@@
 $k$=8. These results demonstrate the potential of using the \symtxt{} algorithm 
-to handle data input for complex types. The lower running times
-show that we can prove properties using the \symtxt{} algorithm faster than
-\gsetxt{}.
+to analyze programs with complex types. The lower running times
+show that we can prove properties using the \symtxt{} algorithm 
+faster than \gsetxt{}.
+
+The number of states explored varies between algorithms. For example,
+\gsetxt{} creates additional points of nondeterminism during field reads, 
+while reference compares are completely deterministic. Thus, in
+example programs with large numbers of reference compares, e.g.,
+TreeMap, state counts for Lazier\# and the \symtxt{} algorithm may
+exceed those for \gsetxt{}. We observed that the additional states
+generated by the summary heap algorithm are unsatisfiable at the point
+of reference compares; this is why they do not contribute any
+additional branches in the final symbolic execution tree. Furthermore,
+the larger state count does not impact the overall runtime of the
+technique.
 
@@
 
-Path counts likewise substantially favor the \symtxt{} algorithm. The number of
-paths explored by the algorithm is strictly less than or equal to the number
-of paths explored by \gsetxt{} for all test cases. We can use this
-result to do more efficient test case generation. From a path
-generated we can use the solutions provided by the constraint solver
-to instantiate a set of concrete heaps to provide as test input. These
-can provide a smaller test suite to achieve control-flow path coverage when
-compared to GSE and Lazier\#.
+The path counts shown in Table~\ref{tab:results} also show the advantage
+of the \symtxt{} algorithm over the \gsetxt{} and L\# algorithms, each of
+which performs case-splitting during the analysis.
+The number of paths explored by the \symtxt{} algorithm is strictly 
+less than or equal to the number
+of paths explored by \gsetxt{} for all artifacts. As a result,
+fewer test cases will be generated to achieve the same control-flow 
+path coverage when compared to GSE and Lazier\#.
+
+%In summary, the benefits of avoiding
+%initialization-based non-determinism outweigh the increased
+%complexity in the constraints due to the advances made in SMT
+%solvers in these examples. In fact, the \symtxt{} algorithm can analyze certain types of programs with
+%orders of magnitude greater efficiency than with \gsetxt{} or
+%Lazier\#, while covering exactly the same control flow paths.
+
+%We can use this
+%result to do more efficient test case generation. From a path
+%generated we can use the solutions provided by the constraint solver
+%to instantiate a set of concrete heaps to provide as test input.
 
@@
 %to be sub-exponential in $k$ for the LinkedList program.
-
-The number of states varies between algorithms, for example, \gsetxt{}
-has additional points of nondeterminism during field reads, but in
-contrast reference compares are completely deterministic. Thus, in
-example programs with large numbers of reference compares, such as
-TreeMap, state counts for Lazier\# and the \symtxt{} algorithm may
-exceed those for \gsetxt{}. We observed that the additional states
-generated by the summary heap algorithm are unsatisfiable at the point
-of reference compares; this is why they do not contribute any
-additional branches in the final symbolic execution tree. Furthermore,
-the larger state count does not impact the overall runtime of the
-technique.
 
@@
 %the constraint solver.
-
-In summary, the benefits of avoiding
-initialization-based non-determinism outweigh the increased
-complexity in the constraints due to the advances made in SMT
-solvers in these examples. In fact, the \symtxt{} algorithm can analyze certain types of programs with
-orders of magnitude greater efficiency than with \gsetxt{} or
-Lazier\#, while covering exactly the same control flow paths.

### 2015-02-04 cav-2015-tex/approach.tex
pass through section 2.2

@@
-\subsection{Generating Summary Heaps}
+\subsection{Generating Symbolic Heaps}
 \label{sec:precise}
-The summary
-heap algorithm only
-partitions the heap at points of divergence in the control flow graph
-such as field accesses or writes (execeptional control flow due to null
-pointers) or comparisons of references (program control flow). There
-are three sets of rewrite rules specific to the summary heap
-algorithm: (i) rules to initialize symbolic references, (ii) rules to
-complete field access and field write, and (iii) rules to check
-equality and inequality of references.
+
+The symbolic heap algorithm only partitions the heap at points of
+divergence in the control flow graph such as comparisons of references
+(program control flow) and field dereferences or writes (execeptional
+control flow due to null pointers). There are three sets of rewrite
+rules specific to the symbolic heap algorithm: (i) rules to initialize
+symbolic references, (ii) rules to perform field dereferences and
+writes, and (iii) rules to check equality and inequality of
+references.
 
@@
 \end{tabular}
-\caption{Summary machine, $s ::= \lp\cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\ \cfgnt{C}\rp$, with $s\rsum^*s^\prime =  s \rsum \cdots \rsum s^\prime \rsum s^\prime$.}
+\caption{Initializing fields, $s ::= \lp\cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\ \cfgnt{C}\rp$, with $s\rsum^*s^\prime =  s \rsum \cdots \rsum s^\prime \rsum s^\prime$.}
 \label{fig:symInit}
@@
 The initialization rule in \figref{fig:symInit} is invoked whenever a
-field pointing to an uninitialized reference is accessed. The
-interaction with the solver in the definition of the rules is denoted
-by $\mathbb{S}(\phi)$ which returns true if $\phi$ is satisfiable.
-%The summarize-end rule becomes active when there is nothing to
-%initialize.
- The check for uninitialized references is determined by the function
+field within an uninitialized reference is accessed. The interaction
+with the solver in the definition of the rules is denoted by
+$\mathbb{S}(\phi)$ which returns true if $\phi$ is satisfiable.  The
+check for uninitialized references is determined by the function
 $\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) =
@@
 \begin{array}{rcl}
-\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \\
-& & \ \ \ \ \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \\
-& & \ \ \ \ \ \ \ \ \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
+\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
 \end{array}
@@
 uninitialized locations in $\Lambda$ to make initialization
-deterministic.  The set $\rho$ contains the set of reference-location
-pairs from the input heap that are potential aliases.  There are four
-choices: (i) $\theta_\mathit{null}$ asserts the condition under which
-$\cfgnt{l}_\mathit{null}$ is possible, (ii) $\theta_\mathit{new}$ is
-active when $\cfgnt{r}_f$ points to the fresh location, (iii) each
-member of $\theta_\mathit{alias}$ restricts $\cfgnt{r}_f$ to a
-particular alias in $\rho$, and at the same time, not alias any member
-of $\rho$ that was initialized earlier than the current choice, and
-(iv) $\theta_\mathit{orig}$ implements conditional initialization to
-preserve the original heap structure.  These sets are added into the
-heap on $\cfgnt{r}_f$ after the fields for $\cfgnt{l}_f$ are
-initialized to $\cfgnt{r}_\mathit{un}$.
+deterministic.  The set $\rho$ contains reference-location pairs that
+represent potential aliases. There are four cases encoded in the
+symbolic heap: (i) $\theta_\mathit{null}$ represents the condition
+where $\cfgnt{l}_\mathit{null}$ is possible, (ii)
+$\theta_\mathit{new}$ represents the case where $\cfgnt{r}_f$ points
+to a fresh location, (iii) each member of $\theta_\mathit{alias}$
+restricts $\cfgnt{r}_f$ to a particular alias in $\rho$, and at the
+same time, not alias any member of $\rho$ that was initialized earlier
+than the current choice, and (iv) $\theta_\mathit{orig}$ implements
+conditional initialization to preserve the original heap structure.
+These sets are added into the heap on $\cfgnt{r}_f$ after the fields
+for $\cfgnt{l}_f$ are initialized to $\cfgnt{r}_\mathit{un}$.
 
@@
 uninitialized reference $\cfgnt{r}_\mathit{un}$. The graph
-in~\figref{fig:initHeap}(b) represents the summary heap after the
+in~\figref{fig:initHeap}(b) represents the symbolic heap after the
 initialization of the $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{x}\rp$ field
 while the graph in~\figref{fig:initHeap}(c) represents the symbolic
-heap summary after the initialization of the
+heap after the initialization of the
 $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$ field following the
@@
 in~\figref{fig:initHeap}(d) represents the various sets constructed in
-the summarize rule during the initialization of
-$\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$. We also define values of
-constraints used as labels in the graph.
+initialization rule for $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$. We
+also define values of constraints used as labels in the graph.
 
@@
 performed on a non-null location.  In the field-access rewrite rule
-in~\figref{fig:fHeap} gets the field type $\cfgnt{C}$ and uses the
-summarize machine, \figref{fig:symInit}, to get a new summary heap
-that is initialized on the field $\cfgnt{f}$. After initialization,
-the summary heap is further modified to include a new stack reference
-pointing to the value set from the read. The new stack reference is
-the return value from the operation.
+in~\figref{fig:fHeap} gets the field type $\cfgnt{C}$ and uses
+\figref{fig:symInit}, to get a new symbolic heap that is initialized
+on the field $\cfgnt{f}$. The symbolic heap is further modified to
+include a new stack reference pointing to the value set from the read;
+the new stack reference is the return value from the operation.
 
@@
 locations on the reference $\cfgnt{r}$. Further, it only includes
-things that are feasible under the current path condition $\phi_g$. It
-also ensures that the access path is valid. There is a constraint
-$\phi$ from the base reference $r$ and a given location. Once a
-location $l$ is selected, the field $\cfgnt{f}$ is accessed to get
-another reference $r^\prime$, and from that reference there is a set
-of locations each with a constraint. The first constraint $\phi$ from
-the base reference plus this second constraint to the actual location
-of the field $\phi^\prime$ comprise the access path. For each member
-of the value set, these constraints together with the global path
-constraint must be satisfied on some aliasing assignment.
+constraints that are feasible under the current path condition
+$\phi_g$. It also ensures that the access path is valid. There is a
+constraint $\phi$ from the base reference $r$ and a given
+location. Once a location $l$ is selected its field $\cfgnt{f}$ is
+accessed to get another reference $r^\prime$, and from that reference
+there is a set of locations each with a constraint. The first
+constraint $\phi$ from the base reference plus this second constraint
+to the actual location of the field $\phi^\prime$ comprise the access
+path. For each member of the value set, these constraints together
+with the global path constraint must be satisfied on some aliasing
+assignment. \nsr{neha: this para needs work -- flow and content}
 
@@
 
-The rewrite rules to compare two references in the symbolic summary
-heap are shown in~\figref{fig:eqs}. The equals references-true rewrite
-rule returns true when two references $\cfgnt{r}_0$ and $\cfgnt{r}_1$
+The rewrite rules to compare two references in the symbolic heap are
+shown in~\figref{fig:eqs}. The equals references-true rewrite rule
+returns true when two references $\cfgnt{r}_0$ and $\cfgnt{r}_1$
 \emph{can} be equal. Intutively, $\Phi_\alpha$ contains all
 constraints under which $\cfgnt{r}_0$ and $\cfgnt{r}_1$ may point to
-the same location in the symbolic summary heap. The second set,
-$\Phi_0$, contains constraints under which the reference $\cfgnt{r}_0$
-points to corresponding locations such that the reference
-$\cfgnt{r}_1$ \emph{does not} point to those locations under any
+the same location in the symbolic heap. The second set, $\Phi_0$,
+contains constraints under which the reference $\cfgnt{r}_0$ points to
+corresponding locations such that the reference $\cfgnt{r}_1$
+\emph{does not} point to those locations under any
 constraint. Finally, the set, $\Phi_1$, contains constraints under
@@
 aliasing assignment. In such a case, the $\cfgt{true}$ outcome is not
-possible on any heap in the summary. Before the rewrite rule returns
+possible on any symbolic heap. Before the rewrite rule returns
 $\cfgt{true}$ we check the satisfiability of the updated global heap

### 2015-02-04 cav-2015-tex/approach.tex
Simplified definitions and corrected a few minor errors.

@@
 
-The symbolic heap algorithm only partitions the heap at points of
-divergence in the control flow graph such as comparisons of references
-(program control flow) and field dereferences or writes (execeptional
-control flow due to null pointers). There are three sets of rewrite
+The symbolic heap algorithm only partitions the heap at comparison
+operations or for exception handling. 
+There are three sets of rewrite
 rules specific to the symbolic heap algorithm: (i) rules to initialize

### 2015-02-04 cav-2015-tex/bisimulation.tex
Simplified definitions and corrected a few minor errors.

@@
 \label{sec:bisim}
-The theoretical result is the existence of a bisimulation between
-states related by GSE with lazy initialization ($p \rgse p^\prime$)
+The theoretical result is the existence of a bisimulation between sets of states
+states related by GSE ($p \rgse p^\prime$)
 and states related by the algorithm in this paper ($q \rsym q^\prime$). The relations are on the universe of \emph{well-formed} states $S$, which have the

### 2015-02-05 cav-2015-tex/rw.tex
Updated the related work to talk about CLP based heap reasoning schemes.

@@
 The work presented here overcomes this limitation by using symbolic values to represent the heap.
+
+A number of constraint-based programming techniques are capable of reasoning about heaps~\cite{Degrave:2010,Charreteur:2009,Albert:2013}.
+Most notably, the technique in~\cite{Albert:2013} is capable of reasoning about dereferencing operations in a per-path set of unknown input heaps.
+However, none of these methods provide guarantees about the precision of the analysis performed, nor is it obvious that such guarantees are possible.
 

### 2015-02-05 cav-2015-tex/summary-heap.tex
minor wording changes and comments

@@
 \label{sec:sh}
+
+\sjp{summary heap or symbolic heap?}
 The summary heap algorithm is defined using
@@
 to perform symbolic execution on a summary heap. The surface (input)
-and machine (state) syntax is shown
+syntax and machine (state) syntax are shown
 in~\figref{fig:syntax}. Terminals are in bold face while non-terminals
@@
 in the graph are immutable. Locations, however, are mutated on
-updates. The structure with the immutability of references mean that
+updates. 
+%The structure with the 
+Immutability of references means that
 look-ups in the heap are non-recursive and updates do not modify the
@@
 
-The soundness and completeness proofs rely on a set of invariants that
+The soundness and completeness proofs \sjp{in Section...} rely on a set of 
+invariants \sjp{properties of the summary heap?} that
 are preserved by the small-step semantics during symbolic execution:
-\emph{reference partitions}, \emph{null and uninitialized}, \emph{immutability}, \emph{determinism}, and
-\emph{type consistency}.
+%\emph{reference partitions}, \emph{null and uninitialized}, \emph{immutability}, \emph{determinism}, and
+%\emph{type consistency}.
 \begin{compactdesc}
@@
 
+\sjp{Up to now, no discussion of lazy initialization - what it is or how it is being used.}
 A key insight to the summary heap is that although many auxiliary or
-stack literals are created in symbolic execution with lazy
-initialization, only input heap references appear in constraints
-expressing potential aliasing relationships. A solver reasons over the
+stack literals are created during symbolic execution with lazy
+initialization, only input heap references appear in the constraints
+expressing potential aliasing relationships. A solver is used to reason over the
 aliasing relationships, and a satisfying assignment uniquely
-identifies active edges in the graph. Those active edges describe a
+identifies \emph{active edges} in the graph -- the set of edges describing a
 representative concrete heap and its shape. For example, if the solver

### 2015-02-05 cav-2015-tex/summary-heap.tex
edits to the approach section

@@
-\section{Summary Heap Framework}
+\section{Our Approach}
 \label{sec:sh}
 
-\sjp{summary heap or symbolic heap?}
-The summary heap algorithm is defined using
-Javalite~\cite{saints-MS}. The small-step semantics of Javalite,
-defined as a syntactic machine using a CESK architecture, are modified
-to perform symbolic execution on a summary heap. The surface (input)
-syntax and machine (state) syntax are shown
+The symbolic heap algorithm is defined using
+Javalite~\cite{saints-MS}. Note that the approach is not restricted to
+this language or even Java in general; we use Javalite simply as
+mechanism to describe our approach. The small-step semantics of
+Javalite, defined as a syntactic machine using a CESK architecture,
+are modified to perform symbolic execution on a symbolic heap. The
+surface (input) syntax and machine (state) syntax are shown
 in~\figref{fig:syntax}. Terminals are in bold face while non-terminals
@@
 
-A summary heap is a bipartite graph on references, $\cfgnt{r}$, and
-constraint location pairs, $\lp\phi\ \cfgnt{l}\rp$. The graph is
-expressed in the location map, $\cfgnt{L}$, and the reference map,
-$\cfgnt{R}$. As done with the environment, $\cfgnt{L}$ and $\cfgnt{R}$
-are treated as partial functions where $\cfgnt{L}(r) =
-\{(\phi\ \cfgnt{l})\ ...\}$ is the set of constraint-location pairs in
-the heap associated with the given reference, and
-$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the reference
-associated with the given location-field pair in the heap. References
-in the graph are immutable. Locations, however, are mutated on
-updates. 
-%The structure with the 
-Immutability of references means that
-look-ups in the heap are non-recursive and updates do not modify the
-current path condition.
+\subsection{Symbolic Heap}
+
+Our symbolic heap is a field sensitive points-to graph with edges
+annotated with disjunctive formulas describing aliasing
+relationships. We represent the symbolic heap is a bipartite graph on
+references, $\cfgnt{r}$, and constraint location pairs,
+$\lp\phi\ \cfgnt{l}\rp$. The graph is expressed in the location map,
+$\cfgnt{L}$, and the reference map, $\cfgnt{R}$. As done with the
+environment, $\cfgnt{L}$ and $\cfgnt{R}$ are treated as partial
+functions where $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the set
+of constraint-location pairs in the heap associated with the given
+reference, and $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the
+reference associated with the given location-field pair in the
+heap. References in the graph are immutable. Locations, however, are
+mutated on updates.  Immutability of references means that look-ups in
+the heap are non-recursive and updates do not modify the current path
+condition.
 
 The soundness and completeness proofs \sjp{in Section...} rely on a set of 
-invariants \sjp{properties of the summary heap?} that
+invariants \sjp{properties of the symbolic heap?} that
 are preserved by the small-step semantics during symbolic execution:
@@
   literals} (these appear in environments, expressions, and continuations).
-\item[Null and Uninitialized] means that every summary heap contains 
+\item[Null and Uninitialized] means that every symbolic heap contains 
 a special location for null ($\cfgnt{l}_\mathit{null}$), and a special
@@
 
-\sjp{Up to now, no discussion of lazy initialization - what it is or how it is being used.}
-A key insight to the summary heap is that although many auxiliary or
-stack literals are created during symbolic execution with lazy
-initialization, only input heap references appear in the constraints
-expressing potential aliasing relationships. A solver is used to reason over the
-aliasing relationships, and a satisfying assignment uniquely
-identifies \emph{active edges} in the graph -- the set of edges describing a
-representative concrete heap and its shape. For example, if the solver
-assigns input heap variables $\cfgnt{r}$ and $\cfgnt{r}^\prime$ such
-that $\cfgnt{r} = \cfgnt{r}^\prime$ is true, then there exists some
-location $\cfgnt{l}$ and constraints $\phi$ and $\phi^\prime$ such
-that (i) $\lp\phi\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r})$; (ii)
+%\sjp{Up to now, no discussion of lazy initialization - what it is or
+%  how it is being used.}  \nsr{A key insight to the summary heap is
+%  that although many auxiliary or stack literals are created during
+%  symbolic execution with lazy initialization, only input heap
+%  references appear in the constraints expressing potential aliasing
+%  relationships.}
+A solver is used to reason over the aliasing relationships, and a
+satisfying assignment uniquely identifies the set of aliasing
+relationships that are representative of a concrete heap and its
+shape. For example, if the solver assigns input heap variables
+$\cfgnt{r}$ and $\cfgnt{r}^\prime$ such that $\cfgnt{r} =
+\cfgnt{r}^\prime$ is true, then there exists some location $\cfgnt{l}$
+and constraints $\phi$ and $\phi^\prime$ such that (i)
+$\lp\phi\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r})$; (ii)
 $\lp\phi^\prime\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r}^\prime)$; and
@@
 
-\subsection{Semantics}
+\subsection{Semantics of Javalite}
 
@@
 	}
-$$
-In this rule, when the string matches the new-expression, it is rewritten to use
-a new heap location where all of the fields for the new object point to
-$\cfgnt{r}_\mathit{null}$
-and the location map points a new stack reference to that new object.
-Notice that references for objects from the new-expression are auxiliary literals
-so they do not appear in any constraint in the summary heap as an aliasing option.
+$$ In this rule, when the string matches the new-expression, it is
+        rewritten to use a new heap location where all of the fields
+        for the new object point to $\cfgnt{r}_\mathit{null}$ and the
+        location map points a new stack reference to that new object.
+        Note that references for objects from the new-expression are
+        auxiliary literals, so they do not appear in any constraint in
+        the symbolic heap as an aliasing option.

### 2015-02-05 cav-2015-tex/summary-heap.tex
more changes
Cleaned up the definitions

--- 2015-02-02 cav-2015-tex/summary-heap.tex
@@
 \begin{compactdesc}
-\item[Reference partitions] means that a reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
-  heap} that includes $\cfgnt{r}_\mathit{null}$ (these are created by lazy initialization and are the only references that appear as variables in
-  constraints); $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
-  literals} that includes $\cfgnt{r}_\mathit{un}$ (these add structure but do not appear elsewhere); and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
-  literals} (these appear in environments, expressions, and continuations).
-\item[Null and Uninitialized] means that every summary heap contains 
-a special location for null ($\cfgnt{l}_\mathit{null}$), and a special
-location for uninitialized
+\item[Reference partitions:] Each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
+  heap}% that includes $\cfgnt{r}_\mathit{null}$ (these are created by lazy initialization and are the only references that appear as variables in constraints)
+  ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
+  literals}% that includes $\cfgnt{r}_\mathit{un}$ (these add structure but do not appear elsewhere)
+  ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
+  literals} %(these appear in environments, expressions, and continuations).
+\item[Null and Uninitialized:] Every summary heap contains 
+two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized,
   ($\cfgnt{l}_\mathit{un}$) with $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
@@
   \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. 
-\item[Immutability] means that a reference does not change in the
-location map, and as a consequence, constraints never need to be
-rewritten as the program evolves its state.
-\item[Determinism] means that a reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
+\item[Immutability:] References do not change once added to the
+location map, eliminating any need for constraint rewriting as the program state evolves.
+\item[Determinism:] A reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
 $
@@
 where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. 
-\item[Type consistency] means that all locations associated with a reference have the same type:
+\item[Type consistency:] All locations associated with a reference have the same type:
 $\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
@@
 
-A key insight to the summary heap is that although many auxiliary or
+A key property of the summary heap is that although many auxiliary or
 stack literals are created in symbolic execution with lazy
-initialization, only input heap references appear in constraints
-expressing potential aliasing relationships. A solver reasons over the
+initialization, only input heap references appear in constraints. A solver reasons over the
 aliasing relationships, and a satisfying assignment uniquely

### 2015-02-06 cav-2015-tex/abstract.tex

@@
 heaps, while generalized symbolic execution leads to excessive
-case-splitting. This paper introduces a compact heap representation
+case-splitting. This paper introduces a compact heap representation,
 along with heap update rules that (i) allow reads and writes of
-symbolic references, (ii) does not require constraint rewriting, and
-(iii) supports arbitrary recursive data structures. As such, the
+symbolic references, (ii) do not require constraint rewriting, and
+(iii) support arbitrary recursive data structures. As such, the
 representation and update rules capture all possible heaps that follow
-a common execution path. More importantly, in contrast to
+a common execution path. More importantly, in contrast to existing
 state-of-the-art techniques, the definition and update rules are
-unconstrained and not subject to bounds such as the number of heap
+unconstrained and not subject to bounds, such as the number of heap
 locations, aliasing, or memory partitions. An evaluation of a

### 2015-02-06 cav-2015-tex/approach.tex
edits to the approach section

@@
-\subsection{Generating Symbolic Heaps}
+\subsection{Generating and Updating Symbolic Heaps}
 \label{sec:precise}
@@
 The symbolic heap algorithm only partitions the heap at comparison
-operations or for exception handling. 
-There are three sets of rewrite
+operations or for exception handling.  There are three sets of rewrite
 rules specific to the symbolic heap algorithm: (i) rules to initialize
@@
 field (field-write). Both rules first check that the operations can be
-performed on a non-null location.  In the field-access rewrite rule
-in~\figref{fig:fHeap} gets the field type $\cfgnt{C}$ and uses
-\figref{fig:symInit}, to get a new symbolic heap that is initialized
-on the field $\cfgnt{f}$. The symbolic heap is further modified to
-include a new stack reference pointing to the value set from the read;
-the new stack reference is the return value from the operation.
+performed on a non-null location. The field-access rewrite rule
+in~\figref{fig:fHeap} dereferences a field of type $\cfgnt{C}$ and
+uses \figref{fig:symInit}, to get a new symbolic heap that is
+initialized on the field $\cfgnt{f}$. The symbolic heap is further
+modified to include a new stack reference pointing to the value set
+(possible values of the field) returned during the dereferencing; the
+new stack reference is the return value from the operation.
 
@@
 with the global path constraint must be satisfied on some aliasing
-assignment. \nsr{neha: this para needs work -- flow and content}
+assignment. % \nsr{neha: this para needs work -- flow and content}
 
@@
 references associated with the field in every location in
-$\Psi_\cfgnt{x}$. Please note that the reference $\cfgnt{r}_x$ is the
-base reference whose field, $\cfgnt{r}_\mathit{cur}$ is being written
-to while the reference $r$ is the target reference. The set $\Psi_x$
+$\Psi_\cfgnt{x}$. Note that the reference $\cfgnt{r}_x$ is the base
+reference whose field, $\cfgnt{r}_\mathit{cur}$ is being written to,
+while the reference $r$ is the target reference. The set $\Psi_x$
 contains tuples $(\phi\ l\ \cfgnt{r}_\mathit{cur})$ of constraints,
@@
 (the first call), and those for the case where it is not (the second
-call).  This is the conditional in the write. In the case that $\phi$
-is true then $\cfgnt{r}_\mathit{cur}$ will point to the constraint
-location pairs of $\cfgnt{L}(\cfgnt{r})$ while if $\phi$ is false then
-$\cfgnt{r}_\mathit{cur}$ will continue to point to the constraint
-location pair it is currently referenced.  As the references are
-immutable, the rule creates fresh references for each
-$\cfgnt{r}_\mathit{cur}$ and points them to the appropriate value
-sets.
+call). In the case that $\phi$ is true then $\cfgnt{r}_\mathit{cur}$
+will point to the constraint location pairs of $\cfgnt{L}(\cfgnt{r})$.
+Whereas, if $\phi$ is false then $\cfgnt{r}_\mathit{cur}$ will
+continue to point to the constraint location pair it currently
+references.  As the references are immutable, the rule creates fresh
+references for each $\cfgnt{r}_\mathit{cur}$ and points them to the
+appropriate value sets.
 
@@
 
-The rewrite rules to compare two references in the symbolic heap are
+The rewrite rule to compare two references in the symbolic heap is
 shown in~\figref{fig:eqs}. The equals references-true rewrite rule

### 2015-02-06 cav-2015-tex/summary-heap.tex

--- 2015-02-05 cav-2015-tex/summary-heap.tex
@@
 annotated with disjunctive formulas describing aliasing
-relationships. We represent the symbolic heap is a bipartite graph on
+relationships. We represent the symbolic heap as a bipartite graph on
 references, $\cfgnt{r}$, and constraint location pairs,
@@
 \begin{compactdesc}
-\item[Reference partitions] means that a reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
-  heap} that includes $\cfgnt{r}_\mathit{null}$ (these are created by lazy initialization and are the only references that appear as variables in
-  constraints); $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
-  literals} that includes $\cfgnt{r}_\mathit{un}$ (these add structure but do not appear elsewhere); and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
-  literals} (these appear in environments, expressions, and continuations).
-\item[Null and Uninitialized] means that every symbolic heap contains 
-a special location for null ($\cfgnt{l}_\mathit{null}$), and a special
-location for uninitialized
+%<<<<<<< HEAD
+\item[Reference partitions:] Each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
+  heap}% that includes $\cfgnt{r}_\mathit{null}$ (these are created by lazy initialization and are the only references that appear as variables in constraints)
+  ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
+  literals}% that includes $\cfgnt{r}_\mathit{un}$ (these add structure but do not appear elsewhere)
+  ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
+  literals} %(these appear in environments, expressions, and continuations).
+\item[Null and Uninitialized:] Every summary heap contains 
+two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized,
+%=======
+%\item[Reference partitions] means that a reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
+%  heap} that includes $\cfgnt{r}_\mathit{null}$ (these are created by lazy initialization and are the only references that appear as variables in
+%  constraints); $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
+%  literals} that includes $\cfgnt{r}_\mathit{un}$ (these add structure but do not appear elsewhere); and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
+%  literals} (these appear in environments, expressions, and continuations).
+%\item[Null and Uninitialized] means that every symbolic heap contains 
+%a special location for null ($\cfgnt{l}_\mathit{null}$), and a special
+%location for uninitialized
+%>>>>>>> 49c83f34a0b5afd58adc4b6649b15e2cbc93437c
   ($\cfgnt{l}_\mathit{un}$) with $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
@@
 $\lp\phi\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r})$; (ii)
+>>>>>>> 49c83f34a0b5afd58adc4b6649b15e2cbc93437c
 $\lp\phi^\prime\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r}^\prime)$; and

### 2015-02-06 cav-2015-tex/appendix.tex
Added appendix

\section*{Appendix: Common Rules for Javalite}
\input{javalite-common}

The surface syntax and the machine syntax for the Javalite syntactic
machine are in the main paper. \figref{fig:javalite-common} defines
the rewrite relations for the portion of the Javalite language
semantics that are common to both generalized symbolic execution and
the summary heap algorithm. The relation $\rcom$ includes all of these
rules. Excepting \textrm{N{\footnotesize EW}}, the rules do not update
the heap, and are largely concerned with argument evaluation in an
expected way. It is assumed that only type safe programs are input to
the machine so there is no type checking or error conditions. The
machine simply halts if no rewrite is enabled.

%% Includes its section definition
\input{lazy}

\input{precise-fig}

\input{summarize-precise}

\section{Summary Heap Algorithm}

\begin{figure*}[t]
\begin{center}
\setlength{\tabcolsep}{60pt}
\hspace*{-35pt}
\begin{tabular}[c]{cc}
\scalebox{1.0}{\usebox{\boxPFAFW}} & 
%\scalebox{0.91}{\input{faYHeap.pdf_t}} &
\scalebox{0.91}{\input{fwXHeap.pdf_t}} \\ \\
(a) & (b)
\end{tabular}
\end{center}
\caption{Field read and write relations with an example heap. (a) Field-access, $\rsym^\mathit{A}$, and field-write, $\rsym^\mathit{W}$, rewrite rules for the $\rsym$ relation. (b) The final heap after $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\ \cfgt{:=}\ \lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp\rp$.}
\label{fig:fHeap}
\end{figure*}

\begin{figure*}
\begin{tabular}[c]{l}
\scalebox{1.0}{\usebox{\boxPI}} \\
\end{tabular}
\caption{The summary machine, $s ::= \lp\cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\ \cfgnt{C}\rp$, with $s\rsum^*s^\prime =  s \rsum \cdots \rsum s^\prime \rsum s^\prime$.}
\label{fig:symInit}
\end{figure*}

The rewrite rules for field access or field write when a null reference is possible leads to an error state.
$$
\begin{array}{c}
	\inferrule[Field Access (NULL)]{
      \exists \lp \phi\ l\rp \in \cfgnt{L}\lp \cfgnt{r}\rp\ \lp l = l_{\mathit{null}} \wedge \mathbb{S}\lp \phi \wedge \phi_g\rp \rp
    }{
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp  \rsym^\mathit{A^\prime}
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgt{error}\ \cfgt{end} \rp
	} \\
\\
	\inferrule[Field Write (NULL)]{
      \cfgnt{r}_x = \eta\lp \cfgnt{x}\rp \\
      \exists \lp \phi\ l\rp \in \cfgnt{L}\lp \cfgnt{r}_x\rp\ \lp l \neq l_{\mathit{null}} \wedge \mathbb{S}\lp \phi \wedge \phi_g\rp \rp
    }{
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp  \rsym^\mathit{F^\prime}
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgt{error}\ \cfgt{end}\rp
	}	
\end{array}
$$
The rules reflect a branch in the control flow for the summary heap
algorithm: one branch being the feasible null outcome (shown here), and the
other branch being the potential non-null
outcome (shown in the main paper). In the non-null case, the path constraint is updated to
restrict out all possible null instances.

\input{definitions}

### 2015-02-06 cav-2015-tex/rw.tex
Did some cleanup in the related works section.

@@
 In the absence of an effective theory of references, DSE has been a natural choice for reasoning about programs that contain them.
-A number of DSE techniques use concretization when reasoning about references ~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}.
-However, as demonstrated in \ref{fig:DSEtest}, DSE underapproximates when it concretizes symbolic values, resulting in an incomplete analysis.
-The SAGE DSE engine~\cite{Elkarablieh:2009} includes more sophisticated methods for reasoning about references, and can successfully reason about the example in \ref{fig:DSEtest}.
+A number of DSE techniques use concretization when reasoning about references~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}.
+However, as demonstrated in~\cite{Elkarablieh:2009}, DSE underapproximates when it concretizes symbolic values, resulting in an incomplete analysis.
+The SAGE DSE engine~\cite{Elkarablieh:2009} includes more sophisticated methods for reasoning about references, and can successfully reason about more complicated examples.
 However, the heap model in SAGE requires fixing the size of memory prior to starting the analysis, and is therefore not complete.
@@
 The advantage in creating a single constraint is that SMT solvers can often reason more efficiently about all paths simultaneously rather than on a case-by-case basis.
-Many BMC methods include a model for reasoning about references, including those described in ~\cite{Clarke:2004,Barnett:2006,Xie:2005,Babic:2007,Dillig:2011}.
+Many BMC methods include a model for reasoning about references, including those described in~\cite{Clarke:2004,Barnett:2006,Xie:2005,Babic:2007,Dillig:2011}.
 However, BMC techniques are not complete for general programs, due to the need to set an execution path-length bound prior to conducting the analysis.
@@
 
-\noindent\textbf{Symbolic Heap Representations}
-Due to technological limitations, many early symbolic heap representations focused on reducing the computational complexity of dereferencing queries.
+\noindent\textbf{Other Symbolic Heap Representations}
+%Due to technological limitations, many early symbolic heap representations focused on reducing the computational complexity of dereferencing queries.
 By introducing certain heuristics and approximations, the computational burden can be greatly reduced, at the cost of precision.
@@
 However, these newer methods generally err on the side of under-approximation, producing an analysis that is not complete.
-
-Several GSE techniques~\cite{GSE03,KiasanKunit} form an exception to this rule, presenting an input heap model that is unconstrained and unbounded.
+%
+%Several GSE techniques~\cite{GSE03,KiasanKunit} form an exception to this rule, presenting an input heap model that is unconstrained and unbounded.
 However, GSE does not offer a mechanism for representing the set of heaps along an execution path as a unified symbolic value.
@@
 The work presented here overcomes this limitation by using symbolic values to represent the heap.
-
 A number of constraint-based programming techniques are capable of reasoning about heaps~\cite{Degrave:2010,Charreteur:2009,Albert:2013}.
 Most notably, the technique in~\cite{Albert:2013} is capable of reasoning about dereferencing operations in a per-path set of unknown input heaps.
-However, none of these methods provide guarantees about the precision of the analysis performed, nor is it obvious that such guarantees are possible.
+However, none of these methods provide guarantees about the precision of the analysis performed, nor is it clear whether such guarantees are possible.
 

### 2015-02-06 cav-2015-tex/summary-heap.tex
Added reference to proofs section.

@@
 
-The soundness and completeness proofs \sjp{in Section...} rely on a set of 
-invariants \sjp{properties of the symbolic heap?} that
+The soundness and completeness proofs in Section~\ref{sec:bisim} rely on a set of 
+properties of the symbolic heap that
 are preserved by the small-step semantics during symbolic execution:

### 2015-02-06 cav-2015-tex/summary-heap.tex
Fixed a bug left over from a previous merge.

@@
 $\lp\phi\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r})$; (ii)
->>>>>>> 49c83f34a0b5afd58adc4b6649b15e2cbc93437c
 $\lp\phi^\prime\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r}^\prime)$; and

### 2015-02-06 cav-2015-tex/bisimulation.tex
Added introductory paragraph to the proof section

@@
 \label{sec:bisim}
-The theoretical result is the existence of a bisimulation between sets of states
+This section establishes the correctness of the~\symtxt{}.
+Demonstrating correctness is important because many summary heap techniques are correct only when certain, often unstated, assumptions are made.
+To show the absence of such assumptions, it is necessary to demonstrate soundness and completess with respect to all properties provable by symbolic execution.
+The proof relies on the observation that a state in symbolic execution can be thought of as representing a set of possible concrete states.
+Similarly, a state in the~\symtxt{} machine represents a set of possible~\gsetxt{} states.
+The goal is to show that states in the~\symtxt{} machine behave exactly like the sets of~\gsetxt{} states that they represent.
+
+The main theoretical result establishes the existence of a bisimulation between sets of states
 states related by GSE ($p \rgse p^\prime$)

### 2015-02-06 cav-2015-tex/rw.tex
Did another pass on the related work.

@@
 arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}.
-However, these generalized symbolic execution (GSE) techniques work by branching over multiple copies of the system state during dereferencing operations, thus exacerbating the path explosion problem.
-Our work leverages the core idea in generalized symbolic execution
-with lazy initialization to construct the heap on-the-fly during
+However, these generalized symbolic execution (GSE) techniques work by branching over multiple copies of the system state during dereferencing operations, exacerbating path explosion and fragmenting the path condition.
+Producing a complete path condition for a single given control flow path would require merging an exponential number of states.
+Our work leverages the core idea in generalized symbolic execution with lazy initialization using on-the-fly reasoning to model a black-box input heap during
 symbolic execution, but avoids the nondeterminism introduced by GSE by
-constructing a summary heap and will generally create fewer paths than
-GSE techniques.
+constructing a single summary heap and polynomially-sized path condition for each control flow path.
 
@@
 
-Dynamic symbolic execution (\dsetxt{}, sometimes referred to as concolic execution) has emerged as a way to enable symbolic execution to continue on programs that contain elements that cannot be reasoned about symbolically.
+Dynamic symbolic execution (\dsetxt{}) has emerged as a way to enable symbolic execution to continue on programs that contain elements that cannot be reasoned about symbolically.
 ~\dsetxt{} works by executing a program using concrete and symbolic engines simultaneously.
 When the program reaches a statement that cannot be reasoned about symbolically, it substitutes in values from the concrete execution and continues.
-When reaching the end of a program path, DSE inverts the branch conditions and uses the solver to generate concrete inputs for another execution path.
-While concretization allows DSE to explore a much wider selection of programs, this freedom comes at the price of completeness.
-The process of concretization introduces approximation such that all possible execution paths may not be explored.
-
 In the absence of an effective theory of references, DSE has been a natural choice for reasoning about programs that contain them.
 A number of DSE techniques use concretization when reasoning about references~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}.
-However, as demonstrated in~\cite{Elkarablieh:2009}, DSE underapproximates when it concretizes symbolic values, resulting in an incomplete analysis.
-The SAGE DSE engine~\cite{Elkarablieh:2009} includes more sophisticated methods for reasoning about references, and can successfully reason about more complicated examples.
-However, the heap model in SAGE requires fixing the size of memory prior to starting the analysis, and is therefore not complete.
+However, as demonstrated in~\cite{Elkarablieh:2009},~\dsetxt{} underapproximates when it concretizes symbolic values, resulting in an incomplete analysis.
+The SAGE~\dsetxt{} engine~\cite{Elkarablieh:2009} includes more sophisticated methods for reasoning about references, and can successfully reason about more complicated examples.
+However, the heap model in SAGE prohibits input-dependent memory allocation.
+The fixed-memory requirement means that analyses of programs accepting indefinite input heaps may terminate prematurely, even for the class of self-limiting solver-compatible programs.
+Since symbolic execution is otherwise sound and complete for this class, bounded heap models are, in general, incomplete with respect to symbolic execution.
+In contrast, the~\symtxt{} model presented in this paper represents a truly unbounded black box.
+While practical considerations may require that some sort of bounds be placed on the symbolic execution itself, the nature of those bounds need not be dictated by the~\symtxt{}.
 
@@
 However, BMC techniques are not complete for general programs, due to the need to set an execution path-length bound prior to conducting the analysis.
-By extension, the bounded reference models used in BMC methods are generally not complete.
-Other limitations include assuming that symbolic references do not alias~\cite{Xie:2005,Babic:2007}, that data structures are not recursive~\cite{Dillig:2011}, or requiring that symbolic references are never dereferenced~\cite{Clarke:2004}.
+By extension, the reference models used in BMC methods generally require a predetermined size bound, and and are thus incomplete with respect to symbolic execution.
+Other limitations include assuming that symbolic references do not alias~\cite{Xie:2005,Babic:2007}, that data structures are not recursive~\cite{Dillig:2011}, or prohibiting dereferencing of black-box input references~\cite{Clarke:2004}.
 
@@
 Most notably, the technique in~\cite{Albert:2013} is capable of reasoning about dereferencing operations in a per-path set of unknown input heaps.
-However, none of these methods provide guarantees about the precision of the analysis performed, nor is it clear whether such guarantees are possible.
+However, no guarantee is made about the precision of the analysis performed, nor is it obvious that such a guarantee is possible for the proposed method.
 
@@
 The methods presented in~\cite{Sen:2014,Torlak:2014,Yorsh:2008} use value sets to represent all symbolic program state, including references.
-While symbolic referencing operations could, in principle, be supported with these methods, it is not clear from the published material exactly how that might be accomplished, especially in the case of dereferencing.
-All of the methods presenting solutions to the dereferencing problem~\cite{Xie:2005,Dillig:2011,Elkarablieh:2009} are not complete, for a variety of reasons which have been enumerated previously.
+While symbolic referencing operations could, in principle, be supported with these methods, it is not clear from the published material exactly how that might be accomplished, especially when reasoning about dereferencing in a black-box input heap.
+All of the methods presenting solutions to the dereferencing problem~\cite{Xie:2005,Dillig:2011,Elkarablieh:2009} are not complete, for a variety of reasons which have been previously enumerated.
 

### 2015-02-06 cav-2015-tex/bisimulation.tex

--- 2015-02-04 cav-2015-tex/bisimulation.tex
@@
 \label{sec:bisim}
-The theoretical result is the existence of a bisimulation between sets of states
-states related by GSE ($p \rgse p^\prime$)
-and states related by the algorithm in this paper ($q \rsym q^\prime$). The relations are on the universe of \emph{well-formed} states $S$, which have the
-properties in \secref{sec:sh} with the constraint that
-the states are \emph{feasible}: successors exist unless at
-\cfgt{end}. Let $p \rgse p^\prime$ be a union over relations for GSE (see appendix):
-$\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E^\prime} \cup \rcom$, where \emph{A} is a field access after evaluating the expression for
-the base reference $\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow
-\cfgnt{k}\rp$, \emph{W} is a field write after evaluating the
-expression for the right operand $\lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
+
+%This section establishes the correctness of
+%the~\symtxt{}. Demonstrating correctness is important because many
+%summary heap techniques are correct only when certain, often
+%unstated, assumptions are made. To show the absence of such
+%assumptions, it is necessary to demonstrate soundness and completess
+%with respect to all properties provable by symbolic execution. The
+%proof relies on the observation that a state in symbolic execution
+%can be thought of as representing a set of possible concrete
+%states. Similarly, a state in the~\symtxt{} machine represents a set
+%of possible~\gsetxt{} states. The goal is to show that states in
+%the~\symtxt{} machine behave exactly like the sets of~\gsetxt{}
+%states that they represent.
+
+The bisimulation proof in this section establishes the soundness and
+completeness of the symbolic heap approach with respect to Generalized
+Symbolic Execution (GSE). Intuitively, any properties proven with GSE
+can also be proved using the symbolic heap algorithm.  GSE concretizes
+the possible heap configurations along with various aliasing
+relationships when an uninitialized field is dereferenced. The rules
+for initializing and updating the fields in the Javalite semantics for
+GSE are shown in the~\appref{app:gse}. The proof demonstrates a bisimulation
+relation between the states generated by GSE and the states generated
+by the symbolic heap algorithm. The proof only reasons about
+well-formed states, which have deterministic, type-consistent heaps,
+and feasible environments, expressions, and continuations. Well-formed
+states always have successors unless at the end of a program
+execution. It is trivial to show that the set of well-formed states is
+closed under the transition relation.
+
+The main theoretical result establishes the existence of a
+bisimulation between sets of states states related by GSE ($p \rgse
+p^\prime$) and states related by the algorithm in this paper ($q \rsym
+q^\prime$). The relations are on the universe of \emph{well-formed}
+states $S$, which have the properties in \secref{sec:sh} with the
+constraint that the states are \emph{feasible}: successors exist
+unless at \cfgt{end}. Let $p \rgse p^\prime$ be a union over relations
+for GSE (see appendix): $\rgse = \rgse^\mathit{A} \cup
+\rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup
+\rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup
+\rgse^\mathit{E^\prime} \cup \rcom$, where \emph{A} is a field access
+after evaluating the expression for the base reference $\lp
+\cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp$, \emph{W} is
+a field write after evaluating the expression for the right operand
+$\lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
 \cfgnt{k}\rp$, \emph{E} is a reference compare after evaluating the

### 2015-02-06 cav-2015-tex/lazy.tex

--- 2014-11-12 tex/lazy.tex
@@
 \section{Generalized Symbolic Execution}
-
+\label{app:gse}
 The specialization of Javalite to generalized symbolic execution with

### 2015-02-07 cav-2015-tex/rw.tex
pass over related work

@@
 
-\noindent\textbf{Symbolic Execution} 
 Initial work on symbolic execution largely focused on checking
@@
 types~\cite{Clarke:76,King:76}.
-Limitations of early symbolic execution techniques included non-primitive data types, path explosion and non-symbolic operations.
-Subsequent adaptations have sought to overcome these limitations.
-
-To address the issue of references, several projects have generalized
-the core idea of symbolic execution, enabling it to be applied to
-programs with more general types, including references and
-arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}.
-However, these generalized symbolic execution (GSE) techniques work by branching over multiple copies of the system state during dereferencing operations, exacerbating path explosion and fragmenting the path condition.
-Producing a complete path condition for a single given control flow path would require merging an exponential number of states.
-Our work leverages the core idea in generalized symbolic execution with lazy initialization using on-the-fly reasoning to model a black-box input heap during
-symbolic execution, but avoids the nondeterminism introduced by GSE by
-constructing a single summary heap and polynomially-sized path condition for each control flow path.
+% Limitations of early symbolic execution techniques included non-primitive data types, path explosion and non-symbolic operations. Subsequent adaptations have sought to overcome these limitations.
+Several projects have generalized the core idea of symbolic execution,
+enabling it to be applied to programs with more general types,
+including references and
+arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. However, these
+generalized symbolic execution (GSE) techniques work by branching over
+multiple copies of the system state during dereferencing operations,
+exacerbating path explosion
+% and fragmenting the path condition. Producing a complete path
+%condition for a single given control flow path would require merging
+%an exponential number of states.
+Our work leverages the core idea in generalized symbolic
+execution with lazy initialization using on-the-fly reasoning to model
+a black-box input heap during symbolic execution, but avoids the
+nondeterminism introduced by GSE by constructing a single summary heap
+and polynomially-sized path condition for each control flow path.
 
@@
 
-Dynamic symbolic execution (\dsetxt{}) has emerged as a way to enable symbolic execution to continue on programs that contain elements that cannot be reasoned about symbolically.
-~\dsetxt{} works by executing a program using concrete and symbolic engines simultaneously.
-When the program reaches a statement that cannot be reasoned about symbolically, it substitutes in values from the concrete execution and continues.
-In the absence of an effective theory of references, DSE has been a natural choice for reasoning about programs that contain them.
-A number of DSE techniques use concretization when reasoning about references~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}.
-However, as demonstrated in~\cite{Elkarablieh:2009},~\dsetxt{} underapproximates when it concretizes symbolic values, resulting in an incomplete analysis.
-The SAGE~\dsetxt{} engine~\cite{Elkarablieh:2009} includes more sophisticated methods for reasoning about references, and can successfully reason about more complicated examples.
-However, the heap model in SAGE prohibits input-dependent memory allocation.
-The fixed-memory requirement means that analyses of programs accepting indefinite input heaps may terminate prematurely, even for the class of self-limiting solver-compatible programs.
-Since symbolic execution is otherwise sound and complete for this class, bounded heap models are, in general, incomplete with respect to symbolic execution.
-In contrast, the~\symtxt{} model presented in this paper represents a truly unbounded black box.
-While practical considerations may require that some sort of bounds be placed on the symbolic execution itself, the nature of those bounds need not be dictated by the~\symtxt{}.
+%Dynamic symbolic execution (\dsetxt{}) has emerged as a way to enable
+%symbolic execution to continue on programs that contain elements that
+%cannot be reasoned about symbolically. ~\dsetxt{} works by executing
+%a program using concrete and symbolic engines simultaneously. When
+%the program reaches a statement that cannot be reasoned about
+%symbolically, it substitutes in values from the concrete execution
+%and continues. In the absence of an effective theory of references,
+%DSE has been a natural choice for reasoning about programs that
+%contain them.
 
-\noindent\textbf{Bounded Model Checking}
-Bounded model checking (BMC) techniques seek to avoid the path explosion problem by converting an entire program execution, along with its specifications, into a constraint problem called a verification condition.
-The advantage in creating a single constraint is that SMT solvers can often reason more efficiently about all paths simultaneously rather than on a case-by-case basis.
-Many BMC methods include a model for reasoning about references, including those described in~\cite{Clarke:2004,Barnett:2006,Xie:2005,Babic:2007,Dillig:2011}.
-However, BMC techniques are not complete for general programs, due to the need to set an execution path-length bound prior to conducting the analysis.
-By extension, the reference models used in BMC methods generally require a predetermined size bound, and and are thus incomplete with respect to symbolic execution.
-Other limitations include assuming that symbolic references do not alias~\cite{Xie:2005,Babic:2007}, that data structures are not recursive~\cite{Dillig:2011}, or prohibiting dereferencing of black-box input references~\cite{Clarke:2004}.
+A number of dynamic symbolic execution (DSE) techniques either use
+concretization when reasoning about references or require solvers that
+support theories of
+arrays~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}. Sometimes,
+however, as demonstrated in~\cite{Elkarablieh:2009},~\dsetxt{}
+underapproximates the possible heaps configurations when it
+concretizes symbolic values. The SAGE~\dsetxt{}
+engine~\cite{Elkarablieh:2009} includes more sophisticated methods for
+reasoning about references, and can successfully reason about more
+complicated examples. However, the heap model in SAGE prohibits
+input-dependent memory allocation. The fixed-memory requirement means
+that analyses of programs accepting indefinite input heaps may
+terminate prematurely, even for the class of self-limiting
+solver-compatible programs.
 
-\noindent\textbf{Other Symbolic Heap Representations}
-%Due to technological limitations, many early symbolic heap representations focused on reducing the computational complexity of dereferencing queries.
-By introducing certain heuristics and approximations, the computational burden can be greatly reduced, at the cost of precision.
-Since the problem of weeding out false positives can be at least as difficult as the program analysis itself, there has been a renewed interest in more precise heap representations.
-However, these newer methods generally err on the side of under-approximation, producing an analysis that is not complete.
-%
-%Several GSE techniques~\cite{GSE03,KiasanKunit} form an exception to this rule, presenting an input heap model that is unconstrained and unbounded.
-However, GSE does not offer a mechanism for representing the set of heaps along an execution path as a unified symbolic value.
-As a result GSE does not produce a path condition representing the complete set of inputs for a given execution path, negating a significant advantage of symbolic execution.
-The work presented here overcomes this limitation by using symbolic values to represent the heap.
-A number of constraint-based programming techniques are capable of reasoning about heaps~\cite{Degrave:2010,Charreteur:2009,Albert:2013}.
-Most notably, the technique in~\cite{Albert:2013} is capable of reasoning about dereferencing operations in a per-path set of unknown input heaps.
-However, no guarantee is made about the precision of the analysis performed, nor is it obvious that such a guarantee is possible for the proposed method.
+Many bounded model checking (BMC) methods include a model for
+reasoning about references, including those described
+in~\cite{Clarke:2004,Barnett:2006,Xie:2005,Babic:2007,Dillig:2011}. However,
+BMC techniques generally need to predetermine bounds of a heap. Other
+limitations include assuming that symbolic references do not
+alias~\cite{Xie:2005,Babic:2007}, that data structures are not
+recursive~\cite{Dillig:2011}, or prohibiting dereferencing of
+black-box input references~\cite{Clarke:2004}.
 
-% a good place to mention procedure summaries, like Yorsh and the Dilligs.
-The symbolic heap value sets presented in this work build upon a number of prior techniques that use sets of guarded values to represent program state~\cite{Sen:2014,Torlak:2014,Yorsh:2008,Xie:2005,Dillig:2011,Elkarablieh:2009}.
-The methods presented in~\cite{Sen:2014,Torlak:2014,Yorsh:2008} use value sets to represent all symbolic program state, including references.
-While symbolic referencing operations could, in principle, be supported with these methods, it is not clear from the published material exactly how that might be accomplished, especially when reasoning about dereferencing in a black-box input heap.
-All of the methods presenting solutions to the dereferencing problem~\cite{Xie:2005,Dillig:2011,Elkarablieh:2009} are not complete, for a variety of reasons which have been previously enumerated.
+A number of constraint-based programming techniques are capable of
+reasoning about
+heaps~\cite{Degrave:2010,Charreteur:2009,Albert:2013}. Most notably,
+the technique in~\cite{Albert:2013} is capable of reasoning about
+dereferencing operations in a per-path set of unknown input
+heaps. However, no guarantees are made about the precision of the
+analysis performed.
+
+The symbolic heap value sets presented in this work build upon a
+number of prior techniques that use sets of guarded values to
+represent program
+state~\cite{Sen:2014,Torlak:2014,Yorsh:2008,Xie:2005,Dillig:2011,Elkarablieh:2009}. The
+methods presented in~\cite{Sen:2014,Torlak:2014,Yorsh:2008} use value
+sets to represent all symbolic program state, including
+references. While symbolic referencing operations could, in principle,
+be supported with these methods, it is not clear from the published
+material exactly how that might be accomplished, especially when
+reasoning about dereferencing in a black-box input heap. All of the
+methods presenting solutions to the dereferencing
+problem~\cite{Xie:2005,Dillig:2011,Elkarablieh:2009} are not complete,
+for a variety of reasons which have been previously enumerated.
 

### 2015-02-07 cav-2015-tex/bisimulation.tex
Slight tweak on bisimulation

@@
 for initializing and updating the fields in the Javalite semantics for
-GSE are shown in the~\appref{app:gse}. The proof demonstrates a bisimulation
-relation between the states generated by GSE and the states generated
-by the symbolic heap algorithm. The proof only reasons about
-well-formed states, which have deterministic, type-consistent heaps,
-and feasible environments, expressions, and continuations. Well-formed
-states always have successors unless at the end of a program
-execution. It is trivial to show that the set of well-formed states is
-closed under the transition relation.
+GSE are shown in the~\appref{app:gse}.
 
-The main theoretical result establishes the existence of a
-bisimulation between sets of states states related by GSE ($p \rgse
-p^\prime$) and states related by the algorithm in this paper ($q \rsym
+The proof shows the existence of a
+bisimulation between sets of states related by GSE ($p \rgse
+p^\prime$) and states related by the symbolic heap and update rules in this paper ($q \rsym
 q^\prime$). The relations are on the universe of \emph{well-formed}

### 2015-02-07 cav-2015-tex/rw.tex
Fixed typos.

@@
 multiple copies of the system state during dereferencing operations,
-exacerbating path explosion
+exacerbating path explosion.
 % and fragmenting the path condition. Producing a complete path

### 2015-02-07 cav-2015-tex/bisimulation.tex
Ran spell check.

@@
 completeness of the symbolic heap approach with respect to Generalized
-Symbolic Execution (GSE). Intuitively, any properties proven with GSE
-can also be proved using the symbolic heap algorithm.  GSE concretizes
+Symbolic Execution (\gsetxt{}). Intuitively, any properties proven with~\gsetxt{}
+can also be proved using the symbolic heap algorithm.~\gsetxt{} concretizes
 the possible heap configurations along with various aliasing
@@
 for initializing and updating the fields in the Javalite semantics for
-GSE are shown in the~\appref{app:gse}.
+\gsetxt{} are shown in the~\appref{app:gse}.
 
 The proof shows the existence of a
-bisimulation between sets of states related by GSE ($p \rgse
+bisimulation between sets of states related by~\gsetxt{} ($p \rgse
 p^\prime$) and states related by the symbolic heap and update rules in this paper ($q \rsym
@@
 unless at \cfgt{end}. Let $p \rgse p^\prime$ be a union over relations
-for GSE (see appendix): $\rgse = \rgse^\mathit{A} \cup
+for~\gsetxt{} (see appendix): $\rgse = \rgse^\mathit{A} \cup
 \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup
@@
 with all references uninitialized. If $p$ is a field access state, it has two
-potential successors in GSE: a non-null reference and a null reference. 
+potential successors in~\gsetxt{}: a non-null reference and a null reference. 
 Thus, the $\rsgse$ relation has two successors and divides $P$ into the two outcomes.

### 2015-02-07 cav-2015-tex/evaluation.tex
Ran spell check.

@@
   \end{tabular}}
-  \caption{Comparing the efficiency of the summary heap with the GSE and Lazier\# algorithms.}
+  \caption{Comparing the efficiency of the summary heap with the~\gsetxt{} and Lazier\# algorithms.}
   \label{tab:results}
@@
 and evaluate its efficacy on three Java data structure artifacts.
-SPF includes an implementation of GSE with lazy initialization.
+SPF includes an implementation of~\gsetxt{} with lazy initialization.
 In recent work, we implemented the  Lazier and Lazier\#
@@
 fewer test cases will be generated to achieve the same control-flow 
-path coverage when compared to GSE and Lazier\#.
+path coverage when compared to~\gsetxt{} and Lazier\#.
 

### 2015-02-07 cav-2015-tex/rw.tex
Ran spell check.

--- 2015-02-07 cav-2015-tex/rw.tex
@@
 arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. However, these
-generalized symbolic execution (GSE) techniques work by branching over
+generalized symbolic execution (\gsetxt{}) techniques work by branching over
 multiple copies of the system state during dereferencing operations,
-exacerbating path explosion
+exacerbating path explosion.
 % and fragmenting the path condition. Producing a complete path
@@
 a black-box input heap during symbolic execution, but avoids the
-nondeterminism introduced by GSE by constructing a single summary heap
+nondeterminism introduced by~\gsetxt{} by constructing a single summary heap
 and polynomially-sized path condition for each control flow path.
@@
 
-A number of dynamic symbolic execution (DSE) techniques either use
+A number of dynamic symbolic execution (\dsetxt{}) techniques either use
 concretization when reasoning about references or require solvers that
@@
 however, as demonstrated in~\cite{Elkarablieh:2009},~\dsetxt{}
-underapproximates the possible heaps configurations when it
+under-approximates the possible heaps configurations when it
 concretizes symbolic values. The SAGE~\dsetxt{}
@@
 %What I think: This paper is about how to handle pointers during dynamic symbolic execution.
-It handles pointer dereferences much like GSE, by resolving possible aliases at the time of the dereferencing, but does not seem to include the possibility of a “new” choice.
+It handles pointer dereferences much like~\gsetxt{}, by resolving possible aliases at the time of the dereferencing, but does not seem to include the possibility of a “new” choice.
 One difference is that this method is adapted to allow pointer arithmetic.
@@
 %formulas and extra variables [Godefroid 2007]. I wonder how such a
-%representation would work for GSE and heap summarization. Such a
+%representation would work for~\gsetxt{} and heap summarization. Such a
 %representation would not require the complex update algorithm

### 2015-02-07 cav-2015-tex/appendix.tex
Fixed some multiply-defined references
edits

@@
-\section*{Appendix: Common Rules for Javalite}
+\section{Rules for Javalite}\label{app:javalite}
+
 \input{javalite-common}
@@
 semantics that are common to both generalized symbolic execution and
-the summary heap algorithm. The relation $\rcom$ includes all of these
+the symbolic heap algorithm. The relation $\rcom$ includes all of these
 rules. Excepting \textrm{N{\footnotesize EW}}, the rules do not update
@@
 
-\section{Summary Heap Algorithm}
+\section{Symbolic Heap Algorithm}
 
-\begin{figure*}[t]
-\begin{center}
-\setlength{\tabcolsep}{60pt}
-\hspace*{-35pt}
-\begin{tabular}[c]{cc}
-\scalebox{1.0}{\usebox{\boxPFAFW}} & 
-%\scalebox{0.91}{\input{faYHeap.pdf_t}} &
-\scalebox{0.91}{\input{fwXHeap.pdf_t}} \\ \\
-(a) & (b)
-\end{tabular}
-\end{center}
-\caption{Field read and write relations with an example heap.
+%\begin{figure*}[t]
+%\begin{center}
+%\setlength{\tabcolsep}{60pt}
+%\hspace*{-35pt}
+%\begin{tabular}[c]{cc}
+%\scalebox{1.0}{\usebox{\boxPFAFW}} & 
+%%\scalebox{0.91}{\input{faYHeap.pdf_t}} &
+%\scalebox{0.91}{\input{fwXHeap.pdf_t}} \\ \\
+%(a) & (b)
+%\end{tabular}
+%\end{center}
+%\caption{Field read and write relations with an example heap.
 (a) Field-access, $\rsym^\mathit{A}$, and field-write, $\rsym^\mathit{W}$, rewrite rules for the $\rsym$ relation.
 (b) The final heap after $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\ \cfgt{:=}\ \lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp\rp$.}
-\label{fig:fHeap}
-\end{figure*}
+%\label{fig:fHeap}
+%\end{figure*}
 
-\begin{figure*}
-\begin{tabular}[c]{l}
-\scalebox{1.0}{\usebox{\boxPI}} \\
-\end{tabular}
-\caption{The summary machine, $s ::= \lp\cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\ \cfgnt{C}\rp$, with $s\rsum^*s^\prime =  s \rsum \cdots \rsum s^\prime \rsum s^\prime$.}
-\label{fig:symInit}
-\end{figure*}
+%\begin{figure*}
+%\begin{tabular}[c]{l}
+%\scalebox{1.0}{\usebox{\boxPI}} \\
+%\end{tabular}
+%\caption{The summary machine, $s ::= \lp\cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\ \cfgnt{C}\rp$, with $s\rsum^*s^\prime =  s \rsum \cdots \rsum s^\prime \rsum s^\prime$.}
+%\label{fig:symInit}
+%\end{figure*}
 
@@
 \end{array}
-$$
-The rules reflect a branch in the control flow for the summary heap
-algorithm: one branch being the feasible null outcome (shown here), and the
-other branch being the potential non-null
-outcome (shown in the main paper). In the non-null case, the path constraint is updated to
-restrict out all possible null instances.
+$$ The rules reflect a branch in the control flow for the symbolic
+heap algorithm: one branch being the feasible null outcome (shown
+here), and the other branch being the potential non-null outcome
+(shown in the main paper). In the non-null case, the path constraint
+is updated to restrict out all possible null instances.
 
-\input{definitions}
+%\input{definitions}

### 2015-02-07 cav-2015-tex/conclusion.tex
Added the technnical stuff
edits

--- 2014-11-13 tex/conclusion.tex
@@
 domain, the heap representations used by those techniques do not lend
-themselves to symbolic execution since they rely on
-approximations, they are inflexible in what types of relations can be
-expressed, and they rely on rewriting of constraints.  In this work,
-we present a heap summary technique for symbolic execution that
-maintains exactness, represents arbitrary heap structures without
-restrictions on aliasing relationships, and supports dynamic
-on-the-fly initialization of heap structures. This unique
-combination of capabilities enables the summary heap to outperform
-state-of-the-art symbolic execution techniques, and in some cases, the
-performance gains are considerable. We believe that performance gains
-in symbolic execution can naturally benefit a variety of analyses
-based on symbolic execution, for example, verification of properties,
-especially those related to the heap, test case generation, program
-evolution techniques such as directed incremental symbolic
-execution~\cite{person:pldi2011}, and other back-end analyses.
+themselves to symbolic execution since they rely on approximations,
+they are inflexible in what types of relations can be expressed, and
+they rely on rewriting of constraints.  In this work, we present a
+heap representation for symbolic execution that maintains exactness,
+represents arbitrary heap structures without restrictions on aliasing
+relationships, and supports dynamic on-the-fly initialization of heap
+structures. This unique combination of capabilities enables the
+symbolic heap algorithm to outperform state-of-the-art symbolic
+execution techniques, and in some cases, the performance gains are
+considerable. We believe that performance gains in symbolic execution
+can naturally benefit a variety of analyses based on symbolic
+execution, for example, verification of properties, especially those
+related to the heap, test case generation, program evolution
+techniques such as directed incremental symbolic
+execution~\cite{person:pldi2011}, and other back-end analyses. In
+future work we plan to evaluate the impact of analyses that rely on
+symbolic execution.
+
+\begin{comment}
 
@@
 arrays, and bitvectors.
-
-\begin{comment}
 

### 2015-02-07 cav-2015-tex/evaluation.tex
edits

@@
 algorithms in SPF~\cite{Hillery:2014}.
+
+The prototype of our~\symtxt{} algorithm is implemented as a new
+extension to SPF.  In addition to the operations presented in the in
+this paper, the implementation contains support for operations over
+integers.  We are currently working on adding support for floating
+point operations, arrays, and bit-operations.  We use the
+\texttt{jConstraints} library which provides support for handling heap
+constraints~\cite{ase2014-ghilrr,jpf2014-dghirr}. It uses the z3
+solver~\cite{deMouraBjorner08Z3} as the underlying constraint
+solver. We leverage the incremental solving feature in z3 in our
+experiments. We also implement other optimizations that cache and
+re-use solutions to previous constraints. These optimizations are an
+important part of our implementation because only small portions of
+the heap constraint changes from one state to another.
 

### 2015-02-07 cav-2015-tex/summary-heap.tex
edits

@@
 where execution starts. The only primitive type in Javalite is
-Boolean. For simplicity in presentation, classes have only non-primitive fields, and methods have a single
-parameter. Expressions, $\cfgnt{e}$,  
-include statements, and they
- use '$\cfgt{:=}$' to indicate assignment and '$\cfgt{=}$' to indicate comparison.
-The dot-operator for field access is replaced by '$\cfgt{\$}$', and the dot-operator
-for method invocation is replaced by '$\cfgt{@}$' since '.' is reserved in PLT Redex. There is no explicit return
-statement; rather, the value of the last expression is
+Boolean. For simplicity in presentation, classes have only
+non-primitive fields, and methods have a single
+parameter. Expressions, $\cfgnt{e}$, include statements, and they use
+'$\cfgt{:=}$' to indicate assignment and '$\cfgt{=}$' to indicate
+comparison.  The dot-operator for field access is replaced by
+'$\cfgt{\$}$', and the dot-operator for method invocation is replaced
+by '$\cfgt{@}$' since '.' is reserved in PLT Redex. There is no
+explicit return statement; rather, the value of the last expression is
 used as the return value. A variable is always indicated by \cfgnt{x}
-and a value by \cfgnt{v}. A value can be a reference in the heap, $\cfgnt{r}$, or any of the special values shown in~\figref{fig:syntax}(a). 
-Only type correct programs are given as input to the machine.
+and a value by \cfgnt{v}. A value can be a reference in the heap,
+$\cfgnt{r}$, or any of the special values shown
+in~\figref{fig:syntax}(a).  Only type correct programs are given as
+input to the machine.
 
-The state of the Javalite machine,
-$\cfgnt{s}$, includes the program registry, $\mu$, a pair of functions defining the heap
-$\lp\cfgnt{L}\ \cfgnt{R}\rp$, a constraint,
-$\phi$, defined over references in the heap, the environment, $\eta$,
-for local variables, and the continuation $\cfgnt{k}$. The registry never changes so it is omitted from the state tuple in the rest of the presentation.  The more
-complex structures, such as the environment and heap, are defined as lists that
-start with empty, \cfgnt{mt}. These lists are treated as partial functions so
-$\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference $\cfgnt{r}$ associated with variable
-$\cfgnt{x}$. The notation $\eta^\prime = \eta[\cfgnt{x} \mapsto
-  \cfgnt{v}]$ defines a new partial function $\eta^\prime$ that is
-the same as $\eta$ except that the variable $\cfgnt{x}$ now maps to
-$\cfgnt{v}$. The continuation $\cfgnt{k}$ indicates where the hole, $\cfgt{*}$, is located, stores temporary computation, and keeps track of the next 
-computation. For example, the continuation
-$\lp\cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp$ indicates
-that the machine is evaluating the expression for the object
-reference on which the field $\cfgnt{f}$ is going to be accessed. Once
-the field access is complete, the machine continues with $\cfgnt{k}$.
+The state of the Javalite machine, $\cfgnt{s}$, includes the program
+registry, $\mu$, a pair of functions defining the heap
+$\lp\cfgnt{L}\ \cfgnt{R}\rp$, a constraint, $\phi$, defined over
+references in the heap, the environment, $\eta$, for local variables,
+and the continuation $\cfgnt{k}$. The registry never changes so it is
+omitted from the state tuple in the rest of the presentation.  The
+more complex structures, such as the environment and heap, are defined
+as lists that start with empty, \cfgnt{mt}. These lists are treated as
+partial functions so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
+$\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation
+$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
+partial function $\eta^\prime$ that is the same as $\eta$ except that
+the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. The continuation
+$\cfgnt{k}$ indicates where the hole, $\cfgt{*}$, is located, stores
+temporary computation, and keeps track of the next computation. For
+example, the continuation $\lp\cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
+\rightarrow \cfgnt{k}\rp$ indicates that the machine is evaluating the
+expression for the object reference on which the field $\cfgnt{f}$ is
+going to be accessed. Once the field access is complete, the machine
+continues with $\cfgnt{k}$.
 
@@
 
-The soundness and completeness proofs in Section~\ref{sec:bisim} rely on a set of 
-properties of the symbolic heap that
-are preserved by the small-step semantics during symbolic execution:
+The soundness and completeness proofs in Section~\ref{sec:bisim} rely
+on certain characteristics of the symbolic heap that are preserved by
+the small-step semantics during symbolic execution:
 %\emph{reference partitions}, \emph{null and uninitialized}, \emph{immutability}, \emph{determinism}, and
@@
         auxiliary literals, so they do not appear in any constraint in
-        the symbolic heap as an aliasing option.
+        the symbolic heap as an aliasing option. The complete set of
+        semantic rules for Javalite are presented
+        in Appendix A.

### 2015-02-07 cav-2015-tex/evaluation.tex
changing summary to symbolic

@@
   \end{tabular}}
-  \caption{Comparing the efficiency of the summary heap with the~\gsetxt{} and Lazier\# algorithms.}
+  \caption{Comparing the efficiency of the symbolic heap with the~\gsetxt{} and Lazier\# algorithms.}
   \label{tab:results}
@@
 exceed those for \gsetxt{}. We observed that the additional states
-generated by the summary heap algorithm are unsatisfiable at the point
+generated by the symbolic heap algorithm are unsatisfiable at the point
 of reference compares; this is why they do not contribute any

### 2015-02-07 cav-2015-tex/rw.tex
changing summary to symbolic

@@
 %an exponential number of states.
-Our work leverages the core idea in generalized symbolic
-execution with lazy initialization using on-the-fly reasoning to model
-a black-box input heap during symbolic execution, but avoids the
-nondeterminism introduced by~\gsetxt{} by constructing a single summary heap
-and polynomially-sized path condition for each control flow path.
+Our work leverages the core idea in generalized symbolic execution
+with lazy initialization using on-the-fly reasoning to model a
+black-box input heap during symbolic execution, but avoids the
+nondeterminism introduced by~\gsetxt{} by constructing a single
+symbolic heap and polynomially-sized path condition for each control
+flow path.
 

### 2015-03-26 tex/definitions.tex
Added proofs and definitions to ./tex/paper.tex to create an extended version of the paper. Numerous corrections to proofs.tex

@@
 \end{equation}
-The bisimularity relation is the greatest fixed point of the functional.
+The bisimilarity relation is the greatest fixed point of the functional.
 \end{definition}
@@
 \cite{GSE:barbedbisimulation}.
+
+\paragraph{Relationship between bisimulation and fix points}
+
+If you have a lattice $L$, and you have some 
+function $F$ which transforms one point on the lattice into another, then
+$F$ is an endofunction on $L$. For any endofunction $F$, a 
+a post-fixed point of $F$ is any point $x$ where $x < F(x)$, and a pre-fixed 
+point is any point $x$ where $F(x) < x$. The inductively defined set $F_\mathit{ind}$
+is equal to the meet of all the pre-fixed points, and the conductively 
+defined set $F_\mathit{coind}$ is equal to the join of all post-fixed points. 
+$x \leq F_\mathit{coins}$. If $F$ is monotone, then the greatest fixed point $\mathit{gfp}(F)$ 
+is equal to the coinductive set, and the least fixed point $\mathit{lfp}(F)$ is equal to the 
+inductive set.
+
+For some monotone endofunction $F$, the inductive proof principle states that 
+if $F(x) \leq x$, then $\mathit{lfp}(F) \leq x$. Similarly, the coinductive proof 
+principle states that if $x \leq F(x)$, then $x \leq \mathit{gfp}(F)$.
+
+Because the functional associated to bisimulation $F_\sim$ is monotone over 
+the lattice formed by sets of pairs of states, we may invoke the coinductive proof principle
+to identify post-fixed points of $\mathit{gfp}(F_\sim)$. It can be proved that
+the greatest fixed point of the functional associated to 
+bisimulation is equal to the bisimilarity relation $\sim = \mathit{gfp}(F_\sim)$, that 
+all bisimulations are 
+post-fixed points of $F_\sim$, and all post-fixed points of $F_\sim$ are 
+bisimulations. Thus, we may invoke the coinductive proof principle to show that some relation $R$ is a bisimulation, by proving that $R$ is a pre-fixed point of $F_\sim$: $R \leq F_\sim(R)$.

### 2015-03-26 tex/proofs.tex
Added proofs and definitions to ./tex/paper.tex to create an extended version of the paper. Numerous corrections to proofs.tex

@@
 \begin{theorem}
-If $R \subseteq F\sim(R)$, then $R$ is a bisimulation.
+If $R \subseteq F_\sim(R)$, then $R$ is a bisimulation.
 \label{lem:bisim}
@@
 
-\begin{lemma}[$\sqsubset$ is a bisimulation for $\rinit$ and $\rsum$]
+\begin{lemma}[Existence of Equivalent Initialized States]
 \label{lem:init}
-If $P \sqsubset q$ and if $\exists q^\prime (q \rsym q^\prime )$ , then $\exists 
+If we have state $q$, and set of states $P$ such that $q \in 2^{S_\mathit{FA}}$ and $P \sqsubset q$, then there exists state $q^+$ and set of states $P^+$ such that $P \sim P^+$, $q \sim q^+$, $P^+ \sqsubset q^+$, and all the relevant fields are initialized.
 \end{lemma}
@@
 \begin{proof}
-In order for a state to be equivalent to a set of GSE states, it must be both sound and complete with respect to the set.
-We will begin the proof by showing completeness, and then finish by demonstrating soundness.
+Our proof strategy is to take arbitrary $q$ and $P$, and then construct $q^+$ and $P^+$ such that $P \sim P^+$, $q \sim q^+$, and all the relevant fields are initialized.
+We then prove that $P^+ \sqsubset q^+$.
 
-To show completeness, we must show that any state in the set is represented by $s_\sym$.
-The definition of representation requires the both the existence of a homomorphism, and proof that the homomorphism constraint is satisfiable.
-To show that a homomorphism exits, take any GSE state $s_\gse$ such that $s_\gse \sqsubset s_\sym$.
-By Definition~\ref{representation}, we know $s_\gse = \lp \cfgnt{L}_\gse\ \cfgnt{R}_\gse\ \phi_\gse\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.
-Take any state $s_\gse^\prime$ where $s_\gse \rinit^* s_\gse^\prime$, and state $s_\sym^\prime$ where $s_\sym \rsum^* s_\sym^\prime$.
-Note that  state $s_\gse^\prime$ has the form: $s_\gse^\prime = \lp \cfgnt{L}_{\gse^\prime}\ \cfgnt{R}_{\gse^\prime}\ \phi_{\gse^\prime}\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.Take any location, field pair $\lp l_\gse\  \cfgnt{f}\rp$ such that $\lp l_\gse\  \cfgnt{f}\rp \in \cfgnt{R}_{\gse}^\leftarrow$, and let $l_\sym = h(l_\gse)$.
-We may classify $l_\gse$ into one of three ways, based on the values of the $\cfgnt{R}$ function in each of the states $s_\gse$, $s_\gse^\prime$, $s_\sym$, and $s_\sym^\prime$, and we may define a function $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ based on that classification.
+Let $q$ be any state such that $q \in 2^{S_\mathit{FA}}$, and let $P$ be a set of states such that $P \sqsubset q$.
+By Definition~\ref{representation}, $q = \lp \cfgnt{L}_q\ \cfgnt{R}_q\ \phi_q\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.
+Let $q^+$ be the state such that $q^+ = \lp \cfgnt{L}_{q}^\prime\ \cfgnt{R}_{q}^\prime\ \phi_{q}\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ where $\cfgnt{L}_{q}^\prime$ and  $\cfgnt{R}_{q}^\prime$ are as defined in the $\rsym$ field access rule.
+Although the $\rsum$ relation does not relate states, we use the notation ${q} \rsum^* q^+$ to show this type of relationship between pairs of states.
+Let $p$ be any state such that $p \in P$.
+Define state $p^+$ in a similar fashion as $q^+$, except using the $\rgse$ field access rule.
+Define $P^+$ to be the set of all possible states like $p^+$: $P^+ = \{\forall {p}^+ | \exists {p} ({p} \sqsubset {q} \wedge ({p} \rinit^* {p}^+) ) \}$, and define $P^{q}$ to be the set of all states represented by $q^+$: $P^{q} = \{\forall {p}^\prime | {p}^\prime \sqsubset {q}^\prime \}$.
+Since $P^+$ and $q^+$ are simply pre-initialized versions of $P$ and $q$, it follows immediately that $P \sim P^+$ and $q \sim q^+$, and that all the relevant fields are initialized.
 
-Class 1: $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f} ) = \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f} )$ and $\cfgnt{R}_{s} ( l_\sym,  \cfgnt{f} ) = \cfgnt{R}_{s^\prime} ( l_\sym,  \cfgnt{f})$.
-Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{\gse}(\cfgnt{R}_{\gse} (\cfgnt{l}_\gse,f )) $.
+It remains to show that $P^+ \sqsubset q^+$.
+We will do so by proving that both $P^+ \subset P^q$ and $P^q \subset P^+$.
+From $p$, take any location, field pair $\lp l_p\  \cfgnt{f}\rp$ such that $\lp l_p\  \cfgnt{f}\rp \in \cfgnt{R}_{p}^\leftarrow$, and let $l_q = h(l_p)$.
+We may classify $l_p$ into one of three ways, based on the values of the $\cfgnt{R}$ function in each of the states $p$, $p^+$, $q$, and $q^+$, and we may define a function $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ based on that classification.
+
+Class 1: $\cfgnt{R}_{p} ( l_{p},  \cfgnt{f} ) = \cfgnt{R}_{p}^\prime ( l_{p},  \cfgnt{f} )$ and $\cfgnt{R}_{s} ( l_{q},  \cfgnt{f} ) = \cfgnt{R}_{q}^\prime ( l_{q},  \cfgnt{f})$.
+Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{p}(\cfgnt{R}_{p} (\cfgnt{l}_{p},f )) $.
 In this case, let $h^\prime(l_\alpha) = h(l_\alpha)$.
-Since $s_\gse \rightharpoonup_h s_\sym$, we may surmise that:
-$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$$
+Since $p \rightharpoonup_h {q}$, we may surmise that:
+$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_{p},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{q}^\prime (\cfgnt{l}_{q},f ))$$
 
-Class 2: $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f}) = \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_\sym,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_\sym,  \cfgnt{f})$.
-Since $\cfgnt{R}_{s} ( l_\sym,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_\sym,  \cfgnt{f})$, the Summarize rule must have altered this reference.
+Class 2: $\cfgnt{R}_{p} ( l_{p},  \cfgnt{f}) = \cfgnt{R}_{p}^\prime ( l_{p},  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_{q},  \cfgnt{f}) \neq \cfgnt{R}_{q}^\prime ( l_{q},  \cfgnt{f})$.
+Since $\cfgnt{R}_{s} ( l_{q},  \cfgnt{f}) \neq \cfgnt{R}_{q}^\prime ( l_{q},  \cfgnt{f})$, the Summarize rule must have altered this reference.
 A reference created by the Summarize rule has a value set $\theta_{all}$ with four subsets: $\theta_{null}$, $\theta_{new}$, $\theta_{alias}$, and $\theta_\mathit{orig}$.
-Because $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f}) = \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$, we know that the location we want to map to lies in $\theta_\mathit{orig}$.
-Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{\gse}(\cfgnt{R}_{\gse} (\cfgnt{l}_\gse,f )) $, and let $l_{orig} = h(l_\alpha)$.
+Because $\cfgnt{R}_{p} ( l_{p},  \cfgnt{f}) = \cfgnt{R}_{p}^\prime ( l_{p},  \cfgnt{f})$, we know that the location we want to map to lies in $\theta_\mathit{orig}$.
+Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{p}(\cfgnt{R}_{p} (\cfgnt{l}_{p},f )) $, and let $l_{orig} = h(l_\alpha)$.
 In this case, we let $h^\prime(l_\alpha) = h(l_\alpha)$.
-Since $(\phi_a\ l_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f ))$.
+Since $(\phi_a\ l_\alpha) \in \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_{p},f ))$.
 Let $l_{orig} = h(l_\alpha)$.
-We can see that by the Summarize rule $ (\phi_b\ l_\mathit{orig})\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$, so therefore:
-$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$$
+We can see that by the Summarize rule $ (\phi_b\ l_\mathit{orig})\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{q}^\prime (\cfgnt{l}_{q},f ))$, so therefore:
+$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_{p},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{q}^\prime (\cfgnt{l}_{q},f ))$$
 
-Class 3: $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f}) \neq \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_\sym,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_\sym,  \cfgnt{f})$.
-In this case, there are two possibilities: either the new reference $\cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$ points to some location we've seen before $l_\alpha$, or it points to a previously unobserved location $l_\beta$.
+Class 3: $\cfgnt{R}_{p} ( l_{p},  \cfgnt{f}) \neq \cfgnt{R}_{p}^\prime ( l_{p},  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_{q},  \cfgnt{f}) \neq \cfgnt{R}_{q}^\prime ( l_{q},  \cfgnt{f})$.
+In this case, there are two possibilities: either the new reference $\cfgnt{R}_{p}^\prime ( l_{p},  \cfgnt{f})$ points to some location we've seen before $l_\alpha$, or it points to a previously unobserved location $l_\beta$.
 By establishing which of these possibilities has happened, we can build $h^\prime$.
-To construct $h^\prime$, let $l_\alpha$ be any location such that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f )) $.
-If there exists $\phi_\alpha$ such that $\lp \phi_\alpha\ l_\alpha \rp \in \cfgnt{L}_{\gse}^\rightarrow $, let $h^\prime(l_\alpha) = h(l_\alpha)$.
-Otherwise, let $l_\beta$ be the location such that $(\phi_b\ \cfgnt{l}_\beta) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f )) $ and $(\phi_b\ \cfgnt{l}_\beta) \notin \cfgnt{L}_{s}(\cfgnt{R}_{s} (\cfgnt{l}_\sym,f )) $.
+To construct $h^\prime$, let $l_\alpha$ be any location such that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_{p},f )) $.
+If there exists $\phi_\alpha$ such that $\lp \phi_\alpha\ l_\alpha \rp \in \cfgnt{L}_{p}^\rightarrow $, let $h^\prime(l_\alpha) = h(l_\alpha)$.
+Otherwise, let $l_\beta$ be the location such that $(\phi_b\ \cfgnt{l}_\beta) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{q}^\prime (\cfgnt{l}_{q},f )) $ and $(\phi_b\ \cfgnt{l}_\beta) \notin \cfgnt{L}_{s}(\cfgnt{R}_{s} (\cfgnt{l}_{q},f )) $.
 Now, let $h^\prime(l_\alpha) = l_\beta$.
 Observe that either way,
-$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$$
+$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_{p},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{q}^\prime (\cfgnt{l}_{q},f ))$$
 
-Furthemore, since $l_\alpha$ and $l_\beta$ are new locations with uninitialized fields, we know that for any field $f^\prime$, $\{(\phi_p\ \bot)\} = \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\alpha,f^\prime ))$ and $ \{(\phi_p\ \bot)\} = \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\beta,f^\prime ))$ therefore, we know that:
-$$(\phi_p\ \cfgnt{l}_x) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\alpha,f^\prime )) \Rightarrow (\phi_q\ h^\prime (\cfgnt{l}_x))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} ( h^\prime(\cfgnt{l}_\alpha),f ))$$
+Furthemore, since $l_\alpha$ and $l_\beta$ are new locations with uninitialized fields, we know that for any field $f^\prime$, $\{(\phi_p\ \bot)\} = \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_\alpha,f^\prime ))$ and $ \{(\phi_p\ \bot)\} = \cfgnt{L}_{s^\prime}(\cfgnt{R}_{q}^\prime (\cfgnt{l}_\beta,f^\prime ))$ therefore, we know that:
+$$(\phi_p\ \cfgnt{l}_x) \in \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_\alpha,f^\prime )) \Rightarrow (\phi_q\ h^\prime (\cfgnt{l}_x))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{q}^\prime ( h^\prime(\cfgnt{l}_\alpha),f ))$$
 
-We have now shown that there exists a mapping $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ for all $\cfgnt{l}_{\gse^\prime} \in \cfgnt{L}_{\gse^\prime}^\rightarrow$ such that:
-$$ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_{\gse^\prime},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_{\gse^\prime},f )) $$
-By Definition~\ref{def:homomorphism} we know that $s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime$.
+We have now shown that there exists a mapping $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ for all $\cfgnt{l}_{\gse^\prime} \in \cfgnt{L}_{p}^\prime^\rightarrow$ such that:
+$$ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_{\gse^\prime},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_{\gse^\prime},f )) $$
+By Definition~\ref{def:homomorphism} we know that $p^+ \rightharpoonup_{h^\prime} q^+$.
 
-It remains to show that $\mathbb{S}( \phi_\sym^\prime \wedge \mathbb{HC}(s_\gse^\prime \rightharpoonup_{h} s_\sym^\prime) )$.
-For locations in Class 1, no new conjuncts are added to $\mathbb{HC}(s_\gse^\prime \rightharpoonup_{h} s_\sym^\prime)$, and therefore the satisfiability cannot be changed.
+It remains to show that $\mathbb{S}( \phi_\sym^\prime \wedge \mathbb{HC}(p^+ \rightharpoonup_{h} q^+) )$.
+For locations in Class 1, no new conjuncts are added to $\mathbb{HC}(p^+ \rightharpoonup_{h} q^+)$, and therefore the satisfiability cannot be changed.
 For locations in Class 2 or Class 3, the new constraints take either the form $\phi_x \wedge \phi_\mathit{orig}$, or $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$.
@@
 
-Since the heap constraint is satisfiable, we know that $s_\gse^\prime \sqsubset s_\sym^\prime $.
-We have therefore shown that for some symbolic state $s_\sym$ and an arbitrary GSE state $s_\gse$ such that $s_\gse \sqsubset s_\sym$ :
+Since the heap constraint is satisfiable, we know that $p^+ \sqsubset q^+ $. We have therefore shown that for some symbolic state ${q}$ and an arbitrary GSE state $p$ such that $p \sqsubset {q}$ :
 \begin{equation} 
-(s_\gse \rinit^* s_\gse^\prime \wedge s_\sym \rsum^* s_\sym^\prime) \Rightarrow s_\gse^\prime \sqsubset s_\sym^\prime 
+(p \rinit^* p^+ \wedge {q} \rsum^* q^+) \Rightarrow p^+ \sqsubset q^+ 
 \end{equation}
 
-We now prove the reverse case, that $s_\sym^*$ represents no infeasible states.
-Suppose that $s_\sym^\prime$ represents some infeasible state.
-This means that we represent some GSE state that has some reference r which points somewhere that no place in the feasible set points to.
-Since we don't change the path condition, all the old references still point exactly to the same places they used to.
+It follows immediately that $P^+ \subset P^q$.
+We now prove the reverse case, that $P^q \subset P^+$.
+Suppose that $q^+$ represents some infeasible state.
+This means that $q$ represents some GSE state that has some reference r which points somewhere that no place in the feasible set points to.
+Since the path condition is identical between $q$ and $q^+$, all references common to the two states point exactly to the same places under the same initial conditions.
 
-So, the problem must be with one of the new references.
-All of the new references point to either a new location, the null location, the uninitialized location, or some alias.
+So, the problem must be with one of the references which is present in $q^+$, but not $q$.
+All of these references point to either a new location, the null location, the uninitialized location, or some alias.
 In the Summarize rule, the values and constraints for the new, null, uninitialized, and alias locations are contained in the sets $\theta_{new}$, $\theta_{null}$, $\theta_\mathit{orig}$, and $\theta_{alias}$.
-Since the null, and uninitialized locations are already accounted for by the homomorphism $s_\gse \rightharpoonup_h s_\sym$, and since a new location was created symmetrically for both $s_\gse^\prime$ and $s_\sym^\prime$, the problem must be with some alias location that is part of $s_\sym$ but not $s_\gse$.
+Since the null, and uninitialized locations are already accounted for by the homomorphism $p \rightharpoonup_h {q}$, and since a new location was created symmetrically for both $p^+$ and $q^+$, the problem must be with some alias location that is part of ${q}$ but not $p$.
 This means that there must be a feasible path to a target location that does not exist for any GSE heap.
@@
 We have now proven that 
-$$ s_\gse^* \sqsubset s_\sym^*  \Rightarrow  s_\gse^* \in \{\forall s_\gse^\prime | \exists s_\gse (s_\gse \sqsubset s_\sym \wedge (s_\gse \rinit^* s_\gse^\prime) ) \}$$
-This fact, combined with our previous result, proves that
-$$s_\sym^*  \cong \{\forall s_\gse^\prime | \exists s_\gse (s_\gse \sqsubset s_\sym \wedge (s_\gse \rinit^* s_\gse^\prime) ) \}$$
+$$ {p}^* \sqsubset {q}^*  \Rightarrow  {p}^* \in \{\forall {p}^\prime | \exists {p} ({p} \sqsubset {q} \wedge ({p} \rinit^* {p}^\prime) ) \}$$
+From this result, it is certain that $P^q \subset P^+$.
+This fact, combined with our previous result, proves that $P^q \cong P^+$.
+This, with our previous assumption that $P^{q} = \{\forall {p}^\prime | {p}^\prime \sqsubset {q}^\prime \}$, leads us to our final conclusion:
+$$ P^+ \sqsubset q^+$$.
 
@@
 Reason over each possible P' (how every many choices might exist--Only one for FA).
-Pick arbitrary p' in one of the sucessor.
+Pick arbitrary p' in one of the successor.
 Do the forward proof.
@@
 \begin{proof}
-Proof by contradiction: assume $P \sqsubset q \wedge (P\ q) \not\in F_\sim(\sqsubset)$.
+%Proof by contradiction: assume $P \sqsubset q \wedge (P\ q) \not\in F_\sim(\sqsubset)$.
 
-\lemref{lem:succ} ensures at least one successor of $P$ and $q$. Let $p^\prime \in P^\prime$ be any
+By \lemref{lem:init}, we may assume without loss of generality that \cfgnt{r} points to no locations where field \cfgnt{f} is uninitialized.
+Furthermore, \lemref{lem:succ} ensures at least one successor of $P$ and $q$.
+Let $p^\prime \in P^\prime$ be any
 state in any successor set and $p \rgse p^\prime$ that state's
@@
 representation relation, are only differentiated by their heaps and
-global constraints since the environment ($\eta$), expression ($r$),
+global constraints since the environment ($\eta$), expression ($\cfgnt{r}$),
 and continuation ($\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow
@@
 by $\sqsubset$. As the environment and continuations are the same,
-$r^\prime = \mathrm{stack}_\cfgnt{r}()$, returns the same next largest
+$\cfgnt{r}^\prime = \mathrm{stack}_\cfgnt{r}()$, returns the same next largest
 number of current stake references from the partition. The first
@@
 is represented in $q$, $\exists q^\prime\ (q
-\rightarrow^\sym_\mathit{FA{N}} q^\prime$ since $l_{\mathit{null}}$
+\rightarrow^\sym_\mathit{FA(N)} q^\prime$ since $l_{\mathit{null}}$
 must be feasible on the reference (\figref{fig:fHeap}).
@@
 constraint-location pair or value set respectively on the same
-reference $\cfgnt{r}^\prime$. As $r^\prime$ is a stack reference, and
+reference $\cfgnt{r}^\prime$. As $\cfgnt{r}^\prime$ is a stack reference, and
 identical in both $p^\prime$ and $q^\prime$, and no new locations are
@@
 $\sqsubset$, it is necessary to create a new homomorphism:
-$(\cfgnt{L}^\prime_p\ \cfgnt{R}^\prime_p) \rightharpoonup_{h^\prime}
-(\cfgnt{L}^\prime_q\ \cfgnt{R}^\prime_q)$. To that end, construct the
+$\gsest^\prime \rightharpoonup_{h^\prime}
+\symst^\prime$. To that end, construct the
 function $h^\prime$ such that $h^\prime = h$.
 
-Observe that since $s_\gse \rightharpoonup_{h} s_\sym$, and since $\cfgnt{R}_\gse$ and $\cfgnt{R}_\sym$ are unchanged from states $s_\gse$ to $s_\gse^\prime$ and $s_\sym$ to $s_\sym^\prime$ respectively, we are guaranteed that $ \cfgnt{r} = \cfgnt{R}_\gse(l,f) \Rightarrow \cfgnt{r} = \cfgnt{R}_\sym(h^\prime(l),f)$.
-Let $\{(\phi_\gse^\prime\ l^\prime)\} =  \cfgnt{L}_\gse(\cfgnt{R}_\gse(l,f))$.
-Since $\mathbb{S}(\phi_g \wedge \mathbb{HC}(s_\gse \rightharpoonup_{h} s_\sym))$ is valid, we know that:
- $$(\phi_\sym \wedge \phi_\sym^\prime\ h(l^\prime)) \in \mathbb{VS}\lp \cfgnt{L}_{s},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp$$ 
+Observe that since $p \rightharpoonup_{h} q$, and since $\cfgnt{R}_\gsest$ and $\cfgnt{R}_q$ are unchanged from states $p$ to $p^\prime$ and $q$ to $q^\prime$ respectively, we are guaranteed that $ \cfgnt{r} = \cfgnt{R}_\gsest(l,f) \Rightarrow \cfgnt{r} = \cfgnt{R}_q(h^\prime(l),f)$.
+Let $\{(\phi_\gsest^\prime\ l^\prime)\} =  \cfgnt{L}_\gsest(\cfgnt{R}_\gsest(l,f))$.
+Since $\mathbb{S}(\phi_g \wedge \mathbb{HC}(p \rightharpoonup_{h} q))$ is valid, we know that:
+ $$(\phi_q \wedge \phi_q^\prime\ h(l^\prime)) \in \mathbb{VS}\lp \cfgnt{L}_{s},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp$$ 
 From this, we may deduce that:
-$$ (\phi_\gse\ l) \in \cfgnt{L}_\gse^\prime(\cfgnt{r}^\prime) \Rightarrow (\phi_\sym \wedge \phi_\sym^\prime\ h^\prime(l))\in \cfgnt{L}_\sym^\prime(\cfgnt{r}^\prime)$$
-Since $\cfgnt{r}^\prime$ is the only new addition to $L_\gse^\prime$ and $L_\sym^\prime$, we now know that the assertion above holds for all $l \in \mathcal{L}$.
-Thus, we have shown that $s_\gse^\prime \rightharpoonup_{h} s_\sym^\prime$.
-Furthermore, since the constraints in $\mathbb{HC}(s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime)$ are constructed using conjuncts already present in $ \mathbb{HC}(s_\gse \rightharpoonup_{h} s_\sym)$, we are guaranteed that $\mathbb{HC}(s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime) \Leftrightarrow \mathbb{HC}(s_\gse \rightharpoonup_{h} s_\sym)$, and therefore $\mathbb{S}(\phi_g \wedge \mathbb{HC}(s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime))$.
-This fact, and the fact that $\eta_{\gse} = \eta_{s} ,\ \cfgnt{e}_{\gse} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\gse} = \cfgnt{k}_{s}$, means that by Definition~\ref{representation} we know $s_\gse^\prime \sqsubset s_\sym^\prime$.
+$$ (\phi_\gsest\ l) \in \cfgnt{L}_\gsest^\prime(\cfgnt{r}^\prime) \Rightarrow (\phi_q \wedge \phi_q^\prime\ h^\prime(l))\in \cfgnt{L}_q^\prime(\cfgnt{r}^\prime)$$
+Since $\cfgnt{r}^\prime$ is the only new addition to $L_\gsest^\prime$ and $L_q^\prime$, we now know that the assertion above holds for all $l \in \mathcal{L}$.
+Thus, we have shown that $p^\prime \rightharpoonup_{h} q^\prime$.
+Furthermore, since the constraints in $\mathbb{HC}(p^\prime \rightharpoonup_{h^\prime} q^\prime)$ are constructed using conjuncts already present in $ \mathbb{HC}(p \rightharpoonup_{h} q)$, we are guaranteed that $\mathbb{HC}(p^\prime \rightharpoonup_{h^\prime} q^\prime) \Leftrightarrow \mathbb{HC}(p \rightharpoonup_{h} q)$, and therefore $\mathbb{S}(\phi_g \wedge \mathbb{HC}(p^\prime \rightharpoonup_{h^\prime} q^\prime))$.
+This fact, and the fact that $\eta_\gsest = \eta_{s} ,\ \cfgnt{e}_\gsest = \cfgnt{e}_{s} ,\ \cfgnt{k}_\gsest = \cfgnt{k}_{s}$, means that by Definition~\ref{representation} we know $p^\prime \sqsubset q^\prime$.
 We have now shown that:
 \begin{equation}
-\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
+\forall \Gsest^\prime ( \Gsest \rsgse \Gsest^\prime \Rightarrow \exists q^\prime( (q \rsym q^\prime )\wedge (\Gsest^\prime\ \sqsubset\ q^\prime ))  )
 \end{equation}
 
-Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_\sym^\prime$.
-Since $s_i^\prime \sqsubset s_\sym^\prime$, then by Definition~\ref{representation}, we know there exists a homomorphism $s_i^\prime \rightharpoonup_{h^\prime} s_\sym^\prime$, and that $\mathbb{S}( \phi_i^\prime \wedge \mathbb{HC}(s_i^\prime \rightharpoonup_{h^\prime} s_\sym^\prime) )$.
-From state $s_i^\prime$, construct state $s_i$ such that
+Now, to prove the reverse direction, choose any state $\gsest^\prime$ such that $\gsest^\prime \sqsubset q^\prime$.
+Since $\gsest^\prime \sqsubset q^\prime$, then by Definition~\ref{representation}, we know there exists a homomorphism $\gsest^\prime \rightharpoonup_{h^\prime} q^\prime$, and that $\mathbb{S}( \phi_\gsest^\prime \wedge \mathbb{HC}(\gsest^\prime \rightharpoonup_{h^\prime} q^\prime) )$.
+From state $\gsest^\prime$, construct state $\gsest$ such that
 \begin{align*}
-s_i &= \lp \cfgnt{L}_{i}\ \cfgnt{R}_{i}\ \phi_i\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp\\
-L_i &= L_{i^\prime} \setminus \{\cfgnt{r}^\prime \}\\
-R_i &= R_{i^\prime}\\
-\phi_i &= \phi_i^\prime
+\gsest &= \lp \cfgnt{L}_\gsest\ \cfgnt{R}_\gsest\ \phi_\gsest\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp\\
+L_\gsest &= L_{\gsest^\prime} \setminus \{\cfgnt{r}^\prime \}\\
+R_\gsest &= R_{\gsest^\prime}\\
+\phi_\gsest &= \phi_\gsest^\prime
 \end{align*}
-Observe that by virtue of the GSE Field Access rule, $s_i \rgse s_i^\prime$.
-Now, construct function $h_i$ so that $h_i = h^\prime$.
-Observe that by Definition~\ref{def:homomorphism} $s_i \rightharpoonup_{h_i} s_\sym$,  and that $\mathbb{S}( \phi_i \wedge \mathbb{HC}(s_i \rightharpoonup_{h_i} s_\sym) )$, so $s_i \sqsubset s_\sym$.
+Observe that by virtue of the GSE Field Access rule, $\gsest \rgse \gsest^\prime$.
+Now, construct function $h_\gsest$ so that $h_\gsest = h^\prime$.
+Observe that by Definition~\ref{def:homomorphism} $\gsest \rightharpoonup_{h_\gsest} q$,  and that $\mathbb{S}( \phi_\gsest \wedge \mathbb{HC}(\gsest \rightharpoonup_{h_\gsest} q) )$, so $\gsest \sqsubset q$.
 Therefore:
 \begin{equation}
-\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
+\forall q^\prime ( q \rsym q^\prime\Rightarrow \exists \Gsest^\prime( (\Gsest \rsgse \Gsest^\prime )\wedge (\Gsest^\prime\ \sqsubset\ q^\prime ))  )
 \end{equation}
@@
 If $P \in 2^{S_\mathit{FW}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisumlation.
-\label{lem:access}
+\label{lem:write}
 $$
@@
 \begin{proof}
-Begin by assuming the conditions from Lemma~\ref{lem:write}.
+Begin by assuming the conditions from Lemma~\ref{lem:write}: Take arbitrary state $q \in S$ and set of states $P \in 2^{S_\mathit{FW}}$ such that $P \sqsubset q$.
 
-The first step is to show that there exists a state $s_\sym^\prime$ that is complete with respect to the feasible set.
-Take state $s_\sym$ and compute state $s_\sym^\prime$ such that $s_\sym \rsym s_\sym^\prime$.
-Take any GSE state $s_\gse$ such that $s_\gse \sqsubset s_\sym$, and find state $s_\gse^\prime$ such that $s_\gse \rgse s_\gse^\prime$.
-Let $l_\gse$ be the location such that $\{(\phi_a\ l_\gse )\} = \cfgnt{L}_\gse(\cfgnt{r}_x) $ for some $\phi_a$.
-To show that $s_\gse^\prime \sqsubset s_\sym^\prime$, we need to demonstrate that there exists a function $h^\prime$ such that $s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime$, and that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime) )$.
-Since $s_h \sqsubset s_\sym$, we know that there exists a function $h$ such that $s_\gse \rightharpoonup_{h} s_\sym$.
+The first step is to prove that the conditions in \eqnref{eqn:BisimulationForwards} hold.
+Take state $\symst$ and compute state $\symst^\prime$ such that $\symst \rsym \symst^\prime$.
+Take any GSE state $\gsest$ such that $\gsest \sqsubset \symst$, and find state $\gsest^\prime$ such that $\gsest \rgse \gsest^\prime$.
+Let $l_\gsest$ be the location such that $\{(\phi_a\ l_\gsest )\} = \cfgnt{L}_\gsest(\cfgnt{r}_x) $ for some $\phi_a$.
+To show that $\gsest^\prime \sqsubset \symst^\prime$, we need to demonstrate that there exists a function $h^\prime$ such that $\gsest^\prime \rightharpoonup_{h^\prime} \symst^\prime$, and that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(\gsest^\prime \rightharpoonup_{h^\prime} \symst^\prime) )$.
+Since $s_h \sqsubset \symst$, we know that there exists a function $h$ such that $\gsest \rightharpoonup_{h} \symst$.
 Let $h^\prime = h$.
 
-First, we consider how $s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime$.
-Let $l_\alpha$ and $l_\beta$ be arbitrary locations in $\cfgnt{L}_{\gse^\prime}^\rightarrow$ such that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime}(\cfgnt{l}_\beta,f ))$, let $\theta = \cfgnt{L}_\sym(\cfgnt{R}_\sym(h(l_\gse),f))$, and let $\theta^\prime =   \cfgnt{L}_\sym^\prime(\cfgnt{R}_\sym^\prime(h(l_\gse),f))$.
+First, we consider how $\gsest^\prime \rightharpoonup_{h^\prime} \symst^\prime$.
+Let $l_\alpha$ and $l_\beta$ be arbitrary locations in $\cfgnt{L}_{\gsest^\prime}^\rightarrow$ such that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\gsest^\prime}(\cfgnt{R}_{\gsest^\prime}(\cfgnt{l}_\beta,f ))$, let $\theta = \cfgnt{L}_\symst(\cfgnt{R}_\symst(h(l_\gsest),f))$, and let $\theta^\prime =   \cfgnt{L}_\symst^\prime(\cfgnt{R}_\symst^\prime(h(l_\gsest),f))$.
 
-Suppose $l_\beta \neq l_\gse$.
+Suppose $l_\beta \neq l_\gsest$.
 In this case either $\theta = \theta^\prime$ or $\theta \neq \theta^\prime$ .
@@
 We can see from the construction of the set $X$ in the symbolic Field Write rule that any feasible location in the set $\theta$ must also be in the set $\theta^\prime$.
-Since $s_\gse \sqsubset s_\sym$, we know that $h(l_\alpha)$ is in $\theta$, and is likewise in $\theta^\prime$.
-We have now established that in either case where $l_\beta \neq l_\gse$, $(\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (h(\cfgnt{l}_\beta),f ))$.
+Since $\gsest \sqsubset \symst$, we know that $h(l_\alpha)$ is in $\theta$, and is likewise in $\theta^\prime$.
+We have now established that in either case where $l_\beta \neq l_\gsest$, $(\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (h(\cfgnt{l}_\beta),f ))$.
 
-On the other hand, suppose $l_\beta = l_\gse$.
-In this case we know that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime}(\cfgnt{l}_\gse,f ))$.
-From the GSE field rule, we can surmise that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse}(\cfgnt{r} )$, and since $s_\gse \sqsubset s_\sym$, we know that $(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s}(\cfgnt{r})$ for some constraint $\phi_b$.
-Using this fact, we can apply the symbolic Field Write rule to infer that $l_\alpha$ must be one of the locations in $\theta^\prime$, and therefore $(\phi_c\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}^\prime(l_\gse,f))$
+On the other hand, suppose $l_\beta = l_\gsest$.
+In this case we know that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\gsest^\prime}(\cfgnt{R}_{\gsest^\prime}(\cfgnt{l}_\gsest,f ))$.
+From the GSE field rule, we can surmise that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gsest}(\cfgnt{r} )$, and since $\gsest \sqsubset \symst$, we know that $(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s}(\cfgnt{r})$ for some constraint $\phi_b$.
+Using this fact, we can apply the symbolic Field Write rule to infer that $l_\alpha$ must be one of the locations in $\theta^\prime$, and therefore $(\phi_c\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}^\prime(l_\gsest,f))$
 
 Thus, for arbitrary $l_\alpha$ and $l_\beta$:
-$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime}(\cfgnt{l}_\beta,f )) \Rightarrow (\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (h(\cfgnt{l}_\beta),f ))$$
-Therefore, we have shown that $s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime$.
+$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gsest^\prime}(\cfgnt{R}_{\gsest^\prime}(\cfgnt{l}_\beta,f )) \Rightarrow (\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (h(\cfgnt{l}_\beta),f ))$$
+Therefore, we have shown that $\gsest^\prime \rightharpoonup_{h^\prime} \symst^\prime$.
 
-Establishing the fact that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime) )$ is left as an exercise to the reader (waving hands in the air).
+Since the path condition is unchanged, and since no new constraints are added to the represented heaps, we are guaranteed that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(\gsest^\prime \rightharpoonup_{h^\prime} \symst^\prime) )$.
 
-By proving the existence of a valid homomorphism, we have shown that for any state $s_\gse^\prime$ such that $s_\gse \rgse s_\gse^\prime$, then the state $s_\sym^\prime$ such that $s_\sym \rsym s_\gse^\prime$ represents $s_\gse^\prime$.
-Therefore, $\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )$.
-This concludes the proof of completeness.
+By proving the existence of a valid homomorphism, we have shown that for any state $\gsest^\prime$ such that $\gsest \rgse \gsest^\prime$, then the state $\symst^\prime$ such that $\symst \rsym \gsest^\prime$ represents $\gsest^\prime$.
+Therefore, $\forall \Gsest^\prime ( \Gsest \rsgse \Gsest^\prime \Rightarrow \exists \symst^\prime( (\symst \rsym \symst^\prime )\wedge (\Gsest^\prime\ \sqsubset\ \symst^\prime ))  )$.
 
-To show that $s_\sym^\prime$ is sound with respect to the feasible set, we use the same argument as in the field read proof: that any state $s_\gse^\prime$ represented by $s_\sym^\prime$ must have a counterpart state $s_\gse$ such that $s_\gse \rgse s_\gse^\prime$ and $s_\gse \sqsubset s_\sym$.
-Because $s_\sym$ is exact, $s_\gse^\prime$ must be a part of the feasible set.
-Therefore, $\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )$.
+To prove the reverse direction, we use the same argument as in the field read proof: that any state $\gsest^\prime$ represented by $\symst^\prime$ must have a counterpart state $\gsest$ such that $\gsest \rgse \gsest^\prime$ and $\gsest \sqsubset \symst$.
+Because $\gsest \sqsubset \symst$ , $\gsest$ must be a member of the set $\Gsest$.
+Therefore, $\forall \symst^\prime ( \symst \rsym \symst^\prime\Rightarrow \exists \Gsest^\prime( (\Gsest \rsgse \Gsest^\prime )\wedge (\Gsest^\prime\ \sqsubset\ \symst^\prime ))  )$.
 
@@
 
-\begin{lemma}[\textrm{E{\footnotesize QUALS}} } preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
+\begin{lemma}[\textrm{E{\footnotesize QUALS}} ] preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
 If $P \in 2^{S_\mathit{E}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisumlation.

### 2015-03-26 tex/definitions.tex
Cleaned up the reference-equals proof, as well as miscellaneous other problems in proofs.tex. Commented out problems in Definitions.tex

@@
 \ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}( \exists \phi_\alpha\ (\exists \phi_\beta\ ( \\ 
-\ \ \ \ \ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ \\
+\ \ \ \ \ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow \\
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ \\
 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  )) ) ) ) )
@@
 
-\begin{lemma}[$Q$ is a singleton for $P \sqsubset Q$]
-\label{lem:unique}
-$$
-P \sqsubset Q \Rightarrow \forall q,q^\prime \in Q\ (\forall p\ (p \sqsubset q \Rightarrow p \sqsubset q^\prime)
-$$
-The notation $P \sqsubset q$ is used to indicate that single member of
-the set in the represented relation.
-\end{lemma}
-\begin{proof}
-Please write me?
-\end{proof}
+%\begin{lemma}[$Q$ is a singleton for $P \sqsubset Q$]
+%\label{lem:unique}
+%$$
+%P \sqsubset Q \Rightarrow \forall q,q^\prime \in Q\ (\forall p\ (p \sqsubset q \Rightarrow p \sqsubset q^\prime)
+%$$
+%The notation $P \sqsubset q$ is used to indicate that single member of
+%the set in the represented relation.
+%\end{lemma}
+%\begin{proof}
+%Please write me?
+%\end{proof}
+
 \begin{definition}
@@
 
-\begin{lemma}[$P$ and $Q$ have same number of successors when $P \sqsubset q$]
-\label{lem:succCount}
-Let $X = \{P^\prime | P \leadsto P^\prime\}$ and $Y = \{q^\prime | q
-\rsym q^\prime\}$: $P \sqsubset q \Rightarrow |X| = |Y|$.
-\end{lemma}
-\begin{proof}
-Please write me?
-\end{proof}
+%\begin{lemma}[$P$ and $Q$ have same number of successors when $P \sqsubset q$]
+%\label{lem:succCount}
+%Let $X = \{P^\prime | P \leadsto P^\prime\}$ and $Y = \{q^\prime | q
+%\rsym q^\prime\}$: $P \sqsubset q \Rightarrow |X| = |Y|$.
+%\end{lemma}
+%\begin{proof}
+%Please write me?
+%\end{proof}
 
@@
 definition is sufficient for all of the customary properties of
-bisimulation to apply. For a more detailed treatment on the
-application of bisimulation to reduction rule systems see
-\cite{GSE:barbedbisimulation}.
+bisimulation to apply. 
+%For a more detailed treatment on the
+%application of bisimulation to reduction rule systems see
+%\cite{GSE:barbedbisimulation}.
 

### 2015-03-26 tex/proofs.tex
Cleaned up the reference-equals proof, as well as miscellaneous other problems in proofs.tex. Commented out problems in Definitions.tex

@@
 The goal of this section is to prove that the representation relation,
-$\sqsubset$, is a bisimulation.  A bisimulation is a relation over pairs of states such that whenever two states, $s_\gse$ and
-$s_\sym$, are related in the bisimulation, $s_\gse \sqsubset
-s_\sym$, every successor, from either state, $s_\gse
-\rgse s_\gse^\prime$ or $s_\sym \rsym
-s_\sym^\prime$, has a corresponding mutual successor in the other
+$\sqsubset$, is a bisimulation.  A bisimulation is a relation over pairs of states such that whenever two states, $\gsest$ and
+$\symst$, are related in the bisimulation, $\gsest \sqsubset
+\symst$, every successor, from either state, $\gsest
+\rgse \gsest^\prime$ or $\symst \rsym
+\symst^\prime$, has a corresponding mutual successor in the other
 state such that both of those successors are also related in the
-bisimulation: $s_\gse^\prime \sqsubset s_\sym^\prime$.
+bisimulation: $\gsest^\prime \sqsubset \symst^\prime$.
 
@@
 
-\begin{theorem}
-
-\end{theorem}
+%\begin{theorem}
+%If exists state $\symst$ and set of states $\Gsest$ such that \eqnref{eqn:BisimulationForwards} and \eqnref{eqn:BisimulationBackwards} are satisfied, then:
+%$$(\Gsest \ \symst) \in F_\sim(\sqsubset)$$
+%\label{}
+%\end{theorem}
 
@@
 %\label{lem:init}
-%If $s_\sym \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$ for symbolic state $s_\sym = \lp \cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \phi_\sym\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$, initial state $s_0$, and control flow path $\pi_n$, and if there exists some intermediate state state $s_\sym^\prime$ such that $(\cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C}) \rsum^* (\cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C})$, then:
-% $$s_\sym^\prime \cong \{\forall s_\gse^\prime | \exists s_\gse (s_\gse \sqsubset s_\sym \wedge (s_\gse \rinit^* s_\gse^\prime) ) \}$$
+%If $\symst \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$ for symbolic state $\symst = \lp \cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \phi_\sym\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$, initial state $s_0$, and control flow path $\pi_n$, and if there exists some intermediate state state $\symst^\prime$ such that $(\cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C}) \rsum^* (\cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C})$, then:
+% $$\symst^\prime \cong \{\forall \gsest^\prime | \exists \gsest (\gsest \sqsubset \symst \wedge (\gsest \rinit^* \gsest^\prime) ) \}$$
 %\end{lemma}
@@
 \end{equation}
- This concludes the proof.
+By \defref{bisimulation}, we conclude:
+$$(\Gsest \ \symst) \in F_\sim(\sqsubset)$$
 \end{proof}
@@
 %\label{lem:write}
-%If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{FW}$ and $s_\gse \sqsubset s_\sym$, then:
+%If there exists states $\gsest$ and $\symst$ such that $\symst \in \mathcal{FW}$ and $\gsest \sqsubset \symst$, then:
 %\begin{equation}
-%\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
+%\forall \gsest^\prime ( \gsest \rgse \gsest^\prime \Rightarrow \exists \symst^\prime( (\symst \rsym \symst^\prime )\wedge (\gsest^\prime\ \sqsubset\ \symst^\prime ))  )
 %\end{equation}
@@
 %\begin{equation}
-%\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
+%\forall \symst^\prime ( \symst \rsym \symst^\prime\Rightarrow \exists \gsest^\prime( (\gsest \rgse \gsest^\prime )\wedge (\gsest^\prime\ \sqsubset\ \symst^\prime ))  )
 %\end{equation}
@@
 Therefore, $\forall \symst^\prime ( \symst \rsym \symst^\prime\Rightarrow \exists \Gsest^\prime( (\Gsest \rsgse \Gsest^\prime )\wedge (\Gsest^\prime\ \sqsubset\ \symst^\prime ))  )$.
+
+By \defref{bisimulation}, we conclude:
+$$(\Gsest \ \symst) \in F_\sim(\sqsubset)$$
 
@@
 \begin{proof}
-Proof by definition of $\rightarrow_\mathit{FA}$ in \figref{fig:sym}.
+Proof by definition of $\rightarrow_\mathit{FA}$ in \figref{fig:fHeap}.
 
@@
 \label{lem:FW-determ}
-Given a state, $s_\sym$, with a deterministic heap,
+Given a state, $\symst$, with a deterministic heap,
 $(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
-\mathrm{heap}(s_\sym)$, the new heap,
+\mathrm{heap}(\symst)$, the new heap,
 $(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
-\mathrm{heap}(s_\sym^\prime)$, in any state related by the field
-write rule, $s_\sym \rightarrow_\mathit{FW} s_\sym^\prime$,
+\mathrm{heap}(\symst^\prime)$, in any state related by the field
+write rule, $\symst \rightarrow_\mathit{FW} \symst^\prime$,
 is also deterministic.
@@
 \begin{proof}
-Proof by definition of $\rightarrow_\mathit{FW}$ in \figref{fig:sym}.
+Proof by definition of $\rightarrow_\mathit{FW}$ in \figref{fig:fHeap}.
 
@@
 \label{lem:J-determ}
-Given a state, $s_\sym$, with a deterministic heap,
+Given a state, $\symst$, with a deterministic heap,
 $(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
-\mathrm{heap}(s_\sym)$, the new heap,
+\mathrm{heap}(\symst)$, the new heap,
 $(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
-\mathrm{heap}(s_\sym^\prime)$, in any state related by the
-Javalite relation, $s_\sym \rcom s_\sym^\prime$, is
+\mathrm{heap}(\symst^\prime)$, in any state related by the
+Javalite relation, $\symst \rcom \symst^\prime$, is
 also deterministic.
@@
 \label{thm:determ}
-Given a state, $s_\sym$, with a deterministic heap,
+Given a state, $\symst$, with a deterministic heap,
 $(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
-\mathrm{heap}(s_\sym)$, the new heap,
+\mathrm{heap}(\symst)$, the new heap,
 $(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
-\mathrm{heap}(s_\sym^\prime)$, in any state related by the
-symbolic relation, $s_\sym \rsym s_\sym^\prime$, is
+\mathrm{heap}(\symst^\prime)$, in any state related by the
+symbolic relation, $\symst \rsym \symst^\prime$, is
 also deterministic.
@@
 %\label{lem:compare}
-%If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{RC}$ and $s_\gse \sqsubset s_\sym$, then:
+%If there exists states $\gsest$ and $\symst$ such that $\symst \in \mathcal{RC}$ and $\gsest \sqsubset \symst$, then:
 %\begin{equation}
-%\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
+%\forall \gsest^\prime ( \gsest \rgse \gsest^\prime \Rightarrow \exists \symst^\prime( (\symst \rsym \symst^\prime )\wedge (\gsest^\prime\ \sqsubset\ \symst^\prime ))  )
 %\end{equation}
@@
 If $P \in 2^{S_\mathit{E}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisumlation.
-\label{lem:access}
+\label{lem:compare}
 $$
@@
 
-There are two rules that apply to state $s_\sym \in 2^{E}$, one for the $\cfgt{true}$ branch and one for the $\cfgt{false}$ branch.
+There are two rules that apply to states in $2^{E}$, one for the $\cfgt{true}$ branch and one for the $\cfgt{false}$ branch.
 Since the proofs for both rules are nearly identical, for brevity we will only show the proofs for the case for the $\cfgt{true}$ branch.
 \begin{proof}
-Assume there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{RC}$ and $s_\gse \sqsubset s_\sym$.
-Let $s_\sym^\prime$ be any state such that $s_\sym \rsym s_\sym$ and let $\zeta_T = \forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime )$.
-Since $s_\gse \sqsubset s_\sym$, we know that $s_\gse \in \mathcal{RC}$, and that there exists a homomorphism $s_\gse \rightharpoonup_{h} s_\sym$ such that $\mathbb{S}( \phi_\sym \wedge \mathbb{HC}(s_\gse \rightharpoonup_{h} s_\sym) ) $.
-We partition $\zeta_T$ based on the values of $\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp$ as follows: Let
-$$\zeta_t = \zeta_T \setminus \{ s_f | (s_f= \lp \cfgnt{L}_f\ \cfgnt{R}_f\ \phi_\gse\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp) \wedge (\cfgnt{L}_f \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_f \lp \cfgnt{r}_1 \rp ) \}$$
+Assume there exists states $\gsest$ and $\symst$ such that $\symst \in \mathcal{RC}$ and $\gsest \sqsubset \symst$.
+Let $\symst^\prime$ be any state such that $\symst \rsym \symst$ and let $\zeta_T = \forall \gsest^\prime ( \gsest \rgse \gsest^\prime )$.
+Since $\gsest \sqsubset \symst$, we know that $\gsest \in \mathcal{RC}$, and that there exists a homomorphism $\gsest \rightharpoonup_{h} \symst$ such that $\mathbb{S}( \phi_\sym \wedge \mathbb{HC}(\gsest \rightharpoonup_{h} \symst) ) $.
+We partition $\zeta_T$ based on the values of $\cfgnt{L}_\gsest \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\gsest \lp \cfgnt{r}_1 \rp$ as follows: Let
+$$\zeta_t = \zeta_T \setminus \{ s_f | (s_f= \lp \cfgnt{L}_f\ \cfgnt{R}_f\ \phi_\gsest\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp) \wedge (\cfgnt{L}_f \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_f \lp \cfgnt{r}_1 \rp ) \}$$
 and let
@@
 
-Furthermore, there are two possible configurations for $s_\sym^\prime$: $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp $ and $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp $.
-We now consider the partitions of $\zeta_T$ and configurations of $s_\sym^\prime$ in separate cases.
+Furthermore, there are two possible configurations for $\symst^\prime$: $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp $ and $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp $.
+We now consider the partitions of $\zeta_T$ and configurations of $\symst^\prime$ in separate cases.
 
-Case 1: Assume that $\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp = \cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp$. 
-Compute state $s_\gse^\prime$ such that $s_\gse \rgse s_\gse^\prime$.
-In this case, the GSE ``equals - references true" rule applied, therefore $s_\gse^\prime$ is in $\zeta_t$.
-Observe that by applying Theorem~\ref{thm:mutex}, $\phi_\sym^\prime \wedge \phi_0 \wedge \phi_1$ reduces to $\phi_\sym$.
-Therefore, $\mathbb{S}( \phi_\sym^\prime \wedge \mathbb{HC}(s_\gse^\prime \rightharpoonup_{h} s_\sym^\prime) ) $ is true, and by extension, $s_\gse^\prime \sqsubset s_\sym^\prime$.
-Since this relation holds for arbitrary $s_\gse^\prime \in \zeta_t$, we now know that
+Case 1: Assume that $\cfgnt{L}_\gsest \lp \cfgnt{r}_0\rp = \cfgnt{L}_\gsest \lp \cfgnt{r}_1 \rp$. 
+Compute state $\gsest^\prime$ such that $\gsest \rgse \gsest^\prime$.
+In this case, the GSE ``equals - references true" rule applied, therefore $\gsest^\prime$ is in $\zeta_t$.
+Observe that by applying Theorem~\ref{thm:determ}, $\phi_\sym^\prime \wedge \phi_0 \wedge \phi_1$ reduces to $\phi_\sym$.
+Therefore, $\mathbb{S}( \phi_\sym^\prime \wedge \mathbb{HC}(\gsest^\prime \rightharpoonup_{h} \symst^\prime) ) $ is true, and by extension, $\gsest^\prime \sqsubset \symst^\prime$.
+Since this relation holds for arbitrary $\gsest^\prime \in \zeta_t$, we now know that
 \begin{equation}
 \label{eqn:RCForwardsTrue}
-((\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp = \cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp) \wedge (s_\gse^\prime \in \zeta_t)) \Rightarrow s_\gse^\prime \sqsubset s_\sym^\prime
+((\cfgnt{L}_\gsest \lp \cfgnt{r}_0\rp = \cfgnt{L}_\gsest \lp \cfgnt{r}_1 \rp) \wedge (\gsest^\prime \in \zeta_t)) \Rightarrow \gsest^\prime \sqsubset \symst^\prime
 \end{equation}
 
-Case 2:  Assume that $s_\sym^\prime$ has the form $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp $, and define $\theta_\alpha$, $\theta_0$ and $\theta_1$ as in the ``equals (references-true) rule''.
-Since $\cfgnt{L}_\sym$ and $\cfgnt{R}_\sym$ are unchanged from $s_\sym$, and $\phi_\sym^\prime$ is only a strengthened version of $\phi_\sym$,  we know that
+Case 2:  Assume that $\symst^\prime$ has the form $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp $, and define $\theta_\alpha$, $\theta_0$ and $\theta_1$ as in the ``equals (references-true) rule''.
+Since $\cfgnt{L}_\sym$ and $\cfgnt{R}_\sym$ are unchanged from $\symst$, and $\phi_\sym^\prime$ is only a strengthened version of $\phi_\sym$,  we know that
 \begin{equation}
 \label{eqn:RCSubset}
-\{s_\gse^\prime | s_\gse^\prime \sqsubset s_\sym^\prime \} \subseteq \{s_\gse^\prime | \exists s_\gse \lp s_\gse \sqsubset s_\sym \rp \wedge s_\gse \rsym s_\gse^\prime\}
+\{\gsest^\prime | \gsest^\prime \sqsubset \symst^\prime \} \subseteq \{\gsest^\prime | \exists \gsest \lp \gsest \sqsubset \symst \rp \wedge \gsest \rsym \gsest^\prime\}
 \end{equation}
-Suppose that there exists state $s_i^\prime$ such that $s_i^\prime \sqsubset s_\sym^\prime$ and $s_i^\prime \notin \zeta_t$. Because of Equation \ref{eqn:RCSubset}, we know that 
-$$s_i^\prime \in \{s_\gse^\prime | \exists s_\gse \lp s_\gse \sqsubset s_\sym\rp \wedge s_\gse \rsym s_\gse^\prime\}$$ 
-Combining this with the assumption that $s_i^\prime \notin \zeta_t$, we must conclude that $\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp \neq  \cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp$.
-Because of this, and because of Theorem~\ref{thm:mutex}, we know that either all constraints in the set
+Suppose that there exists state $s_i^\prime$ such that $s_i^\prime \sqsubset \symst^\prime$ and $s_i^\prime \notin \zeta_t$. Because of Equation \ref{eqn:RCSubset}, we know that 
+$$s_i^\prime \in \{\gsest^\prime | \exists \gsest \lp \gsest \sqsubset \symst\rp \wedge \gsest \rsym \gsest^\prime\}$$ 
+Combining this with the assumption that $s_i^\prime \notin \zeta_t$, we must conclude that $\cfgnt{L}_\gsest \lp \cfgnt{r}_0\rp \neq  \cfgnt{L}_\gsest \lp \cfgnt{r}_1 \rp$.
+Because of this, and because of Theorem~\ref{thm:determ}, we know that either all constraints in the set
 $$\{\phi_i \mid \exists \phi_\alpha (\phi_\alpha \in \theta_\alpha)\wedge \phi_i = \lp\phi_\alpha \wedge \phi_0 \wedge \phi_1\rp\}$$ are unsatisfiable, or that at least one constraint in the set
 $$\{\phi_i \mid \exists \phi_\alpha (\phi_\alpha \in \lp \theta_0 \cup \theta_1 \rp)\wedge \lp \phi_i = \phi_\alpha \wedge \phi_0 \wedge \phi_1 \rp\}$$ 
-is valid. Either way, $\mathbb{S}\lp\phi_i^\prime \wedge\phi_0\wedge \phi_1\rp$ is false and $s_\sym^\prime$ does not represent $s_i^\prime$. We have a contradiction. Therefore: 
+is valid. Either way, $\mathbb{S}\lp\phi_i^\prime \wedge\phi_0\wedge \phi_1\rp$ is false and $\symst^\prime$ does not represent $s_i^\prime$. We have a contradiction. Therefore: 
 \begin{equation}
 \label{eqn:RCBackwardsTrue}
-((s_\sym^\prime=\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp) \wedge (s_\gse^\prime \sqsubset s_\sym^\prime)) \Rightarrow s_\gse^\prime \in \zeta_t
+((\symst^\prime=\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp) \wedge (\gsest^\prime \sqsubset \symst^\prime)) \Rightarrow \gsest^\prime \in \zeta_t
 \end{equation}
 
-Case 3: Assume that $\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp$.
+Case 3: Assume that $\cfgnt{L}_\gsest \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_\gsest \lp \cfgnt{r}_1 \rp$.
 This means that the GSE ``equals - references false" rule applies.
@@
 \label{eqn:RCForwardsFalse}
-((\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp = \cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp) \wedge (s_\gse^\prime \in \zeta_t)) \Rightarrow s_\gse^\prime \sqsubset s_\sym^\prime
+((\cfgnt{L}_\gsest \lp \cfgnt{r}_0\rp = \cfgnt{L}_\gsest \lp \cfgnt{r}_1 \rp) \wedge (\gsest^\prime \in \zeta_t)) \Rightarrow \gsest^\prime \sqsubset \symst^\prime
 \end{equation}
 
-Case 4: Assume that $s_\sym^\prime$ has the form $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp $.
+Case 4: Assume that $\symst^\prime$ has the form $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp $.
 The proof for this case is highly similar to the proof for Case 2, so we omit it for the sake of brevity. The result for this case is:
@@
 \label{eqn:RCBackwardsFalse}
-s_\sym^\prime=\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp \wedge s_\gse^\prime \sqsubset s_\sym^\prime \Rightarrow s_\gse^\prime \in \zeta_f
+\symst^\prime=\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp \wedge \gsest^\prime \sqsubset \symst^\prime \Rightarrow \gsest^\prime \in \zeta_f
 \end{equation}
@@
 \begin{equation}
-\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
+\forall \gsest^\prime ( \gsest \rgse \gsest^\prime \Rightarrow \exists \symst^\prime( (\symst \rsym \symst^\prime )\wedge (\gsest^\prime\ \sqsubset\ \symst^\prime ))  )
 \end{equation}
@@
 \begin{equation}
-\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
+\forall \symst^\prime ( \symst \rsym \symst^\prime\Rightarrow \exists \gsest^\prime( (\gsest \rgse \gsest^\prime )\wedge (\gsest^\prime\ \sqsubset\ \symst^\prime ))  )
 \end{equation}
+By \defref{bisimulation}, we conclude:
+$$(\Gsest \ \symst) \in F_\sim(\sqsubset)$$
 \end{proof}
@@
 %\label{lem:new}
-%If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{NW}$ and $s_\gse \sqsubset s_\sym$, then:
+%If there exists states $\gsest$ and $\symst$ such that $\symst \in \mathcal{NW}$ and $\gsest \sqsubset \symst$, then:
 %\begin{equation}
-%\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
+%\forall \gsest^\prime ( \gsest \rgse \gsest^\prime \Rightarrow \exists \symst^\prime( (\symst \rsym \symst^\prime )\wedge (\gsest^\prime\ \sqsubset\ \symst^\prime ))  )
 %\end{equation}
@@
 \begin{proof}
-Take any two states $s_\gse$ and $s_\sym$ such that $s_\gse \sqsubset s_\sym$.
-If $s_\sym \in \mathcal{FA} \cup \mathcal{FW} \cup \mathcal{RC} \cup \mathcal{NW}$, then by Lemmas \ref{lem:access}, \ref{lem:write}, \ref{lem:compare}, and \ref{lem:new} we know Equations \ref{eqn:BisimulationForwards} and \ref{eqn:BisimulationBackwards} hold.
-If $s_\sym$ has any other form, the heap is not modified for $s_\gse^\prime$ or $s_\sym^\prime$, so then Equations \ref{eqn:BisimulationForwards} and \ref{eqn:BisimulationBackwards} hold by default.
-Thus, Equations \ref{eqn:BisimulationForwards} and \ref{eqn:BisimulationBackwards} hold for all  $s_\gse$ and $s_\sym$ such that $s_\gse \sqsubset s_\sym$.
+Take any two states $\gsest$ and $\symst$ such that $\gsest \sqsubset \symst$.
+If $\symst \in \mathcal{FA} \cup \mathcal{FW} \cup \mathcal{RC}$, then by Lemmas \ref{lem:access}, \ref{lem:write}, and \ref{lem:compare} we know Equations \ref{eqn:BisimulationForwards} and \ref{eqn:BisimulationBackwards} hold.
+If $\symst$ has any other form, the heap is not modified for $\gsest^\prime$ or $\symst^\prime$, so then Equations \ref{eqn:BisimulationForwards} and \ref{eqn:BisimulationBackwards} hold by default.
+Thus, Equations \ref{eqn:BisimulationForwards} and \ref{eqn:BisimulationBackwards} hold for all  $\gsest$ and $\symst$ such that $\gsest \sqsubset \symst$.
 By Definition \ref{bisimulation}, $\sqsubset$ is a bisimulation.
+\end{proof}
 
-\end{proof}
+Note that in the above proof we omit consideration of states in $\mathcal{NW}$, as this case is trivial.
 

### 2015-03-27 tex/abstract.tex
Brought in abstract, intro, and related work from CAV paper.

@@
 A fundamental challenge of using symbolic execution for software
-analysis has been the treatment of dynamically allocated
-data. Generalized symbolic execution (GSE) techniques have addressed
-this challenge by materializing a concrete heap lazily during field
-accesses.  These techniques however, exacerbate the path explosion
-problem.  In this work, we present a summary heap approach which takes
-inspiration from the static analysis domain and defines a bipartite
-graph to encode multiple heaps in single representation, which, unlike
-state-of-the-art static analysis approaches, (i) supports aliasing,
-(ii) does not require rewrite of constraints on heap updates, and
-(iii) can initialize the heap-on-the-fly. We also define a summary
-heap algorithm to perform heap updates during symbolic execution on
-this representation in order to mitigate the path explosion problem in
-GSE techniques. Our approach is sound and complete with respect to the
-properties provable by GSE. A preliminary evaluation of our
-implementation in Java Pathfinder framework shows the summary heap
-enables the initialization of larger, more complex heaps than
-previously possible.
+analysis is the treatment of dynamically allocated data. This paper
+introduces a compact symbolic heap representation based on a field
+sensitive points-to graph with edges annotated with disjunctive
+formulas describing aliasing relationships, along with a set of
+rewrite rules that describe the initialization, dereferencing, and
+update to fields in the symbolic heaps. The symbolic heap supports
+arbitrary recursive data structures and captures all possible heaps
+that follow a common control flow path up to the point of
+execution. An evaluation of a proof-of-concept implementation in the
+Java Pathfinder framework is presented to demonstrate the
+computational feasibility of the approach over several classical
+symbolic execution benchmarks.
 
-\begin{comment}
-A fundamental challenge of using symbolic execution for software
-analysis has been the treatment of dynamically allocated data.
-State-of-the-art techniques have addressed this challenge through
-either (a) the use of summaries that over-approximate possible heaps, or
-(b) by materializing a concrete heap lazily during generalized
-symbolic execution. In this work, we present a novel heap
-initialization and analysis technique which takes inspiration from
-both approaches and constructs precise heap summaries lazily during
-symbolic execution.  Our approach is 1) \emph{scalable}: it reduces the
-points of non-determinism compared to generalized symbolic execution
-and explores each control-flow path only once for any given set of
-isomorphic heaps, 2) \emph{precise}: at any given point during symbolic
-execution, the symbolic heap represents the exact set of feasible
-concrete heap structures for the program under analysis, and 3)
-\emph{expressive}: the symbolic heap can represent recursive data
-structures. We demonstrate the precision and scalability of our
-approach by implementing it as an extension to the Symbolic PathFinder
-framework for analyzing Java programs.
-\end{comment}
-
-%and by using 
-%materializing objects on the concrete heap ``as needed'' and
-%using non-deterministic choice points to explore each feasible
-%concrete heap configuration.
-
-%Because analysis of the materialized
-%heap locations relies on concrete program semantics, the lazy
-%initialization approach exacerbates the state space explosion
-%problem that limits the scalability of symbolic execution.
-%In this work we present a novel approach for lazy symbolic execution
-%of heap manipulating software which utilizes 
-%a fully symbolic heap constructed on-the-fly during symbolic execution.
-%Our approach is 1) \emph{scalable} -- it does not
-%create the additional points of non-determinism
-%introduced by existing lazy initialization techniques and it explores
-%each execution path only once for any given set of isomorphic heaps,
-%2) \emph{precise} -- at any given point during symbolic execution, 
-%the symbolic heap represents the exact set of feasible
-%concrete heap structures for the program under analysis, and
-%3) \emph{expressive} -- the symbolic heap can represent recursive data structures 
-%and heaps resulting from loops and recursive control structures in the code. 
-%We report on a case-study of an implementation of our technique in the
-%Symbolic PathFinder tool to illustrate its scalability, precision
-%and expressiveness. We also discuss how test case generation -- a common
- %use for symbolic execution results -- can benefit from symbolic
- %execution which uses a fully symbolic heap.
+%A fundamental challenge of using symbolic execution for software
+%analysis is the treatment of dynamically allocated data. Existing
+%static analysis techniques over-approximate the potential heaps,
+%dynamic symbolic execution techniques often under-approximate the
+%heaps, while generalized symbolic execution leads to excessive
+%case-splitting. This paper introduces a compact heap representation,
+%along with heap update rules that (i) allow reads and writes of
+%symbolic references, (ii) do not require constraint rewriting, and
+%(iii) support arbitrary recursive data structures. As such, the
+%representation and update rules capture all possible heaps that
+%follow a common execution path. More importantly, in contrast to
+%existing state-of-the-art techniques, the definition and update rules
+%are unconstrained and not subject to bounds, such as the number of
+%heap locations, aliasing, or memory partitions. An evaluation of a
+%proof-of-concept implementation in the Java Pathfinder framework is
+%presented to demonstrate the computational feasibility of the
+%approach over several classical symbolic execution benchmarks.

### 2015-03-27 tex/definitions.tex
Brought in abstract, intro, and related work from CAV paper.

@@
 \section{Definitions}
-
+\label{sec:defs}
 \begin{definition}
@@
 these transition relations are defined in \figref{fig:lazy},
-\figref{fig:lazyInit}, \figref{fig:sym}, and \figref{fig:symInit}.
+\figref{fig:lazyInit}, \figref{fig:javalite-common}, \figref{fig:eqs}, \figref{fig:fHeap} and \figref{fig:symInit}.
 \end{definition}
@@
 \begin{proof}
-Please write me!
+Proof of this lemma can be obtained by simple inspection of the rules.
 \end{proof}
@@
 bisimulation to apply. 
-%For a more detailed treatment on the
-%application of bisimulation to reduction rule systems see
-%\cite{GSE:barbedbisimulation}.
+For a more detailed treatment on the
+application of bisimulation to reduction rule systems see
+\cite{Sangiorgi:2011}.
 
@@
 
-If you have a lattice $L$, and you have some 
-function $F$ which transforms one point on the lattice into another, then
-$F$ is an endofunction on $L$. For any endofunction $F$, a 
+Given a lattice $L$, for any endofunction $F$ over points in $L$, 
 a post-fixed point of $F$ is any point $x$ where $x < F(x)$, and a pre-fixed 
 point is any point $x$ where $F(x) < x$. The inductively defined set $F_\mathit{ind}$
-is equal to the meet of all the pre-fixed points, and the conductively 
+is equal to the meet of all the pre-fixed points, and the coinductively 
 defined set $F_\mathit{coind}$ is equal to the join of all post-fixed points. 
-$x \leq F_\mathit{coins}$. If $F$ is monotone, then the greatest fixed point $\mathit{gfp}(F)$ 
+If $F$ is monotone, then the greatest fixed point $\mathit{gfp}(F)$ 
 is equal to the coinductive set, and the least fixed point $\mathit{lfp}(F)$ is equal to the 
@@
 post-fixed points of $F_\sim$, and all post-fixed points of $F_\sim$ are 
-bisimulations. Thus, we may invoke the coinductive proof principle to show that some relation $R$ is a bisimulation, by proving that $R$ is a pre-fixed point of $F_\sim$: $R \leq F_\sim(R)$.
+bisimulations. Thus, we may invoke the coinductive proof principle to show that some
+ relation $R$ is a bisimulation, by proving that $R$ is a pre-fixed point of $F_\sim$: $R \leq F_\sim(R)$.

### 2015-03-27 tex/heap.tex
Added a sentence about the immutability of references.
Changed bullets on list to be dashes as in the introduction.
Brought in abstract, intro, and related work from CAV paper.

@@
 rewrite rules that are invariant and important to the correctness
-proofs in \secref{sec:bisim}: \emph{reference partitions},
+proofs in \secref{sec:proofs}: \emph{reference partitions},
 \emph{immutability}, \emph{determinism}, \emph{type
@@
 bisimilation between the summary heap algorithm and generalized
-symbolic execution (see \secref{sec:bisim}).
+symbolic execution (see \secref{sec:defs}).
 

### 2015-03-27 tex/intro.tex
Made lazier Lazier everywhere
Brought in abstract, intro, and related work from CAV paper.

@@
 In recent years symbolic execution has provided the basis for various
+software testing and analysis techniques. Symbolic execution explores
+the program by treating input values as symbolic, and for each
+explored path, it computes a set of feasible constraints on the
+symbolic inputs to create a \emph{path condition}. Path conditions
+computed by symbolic execution characterize the observed program
+execution behaviors and have been used as an enabling technology for
+various applications, e.g., regression
+analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
+data structure repair~\cite{KhurshidETAL05RepairingStructurally},
+dynamic discovery of
+invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, and
+debugging~\cite{Ma:2011}.
+
+The path conditions computed by symbolic execution have two important
+features: 1) they characterize the set of feasible execution paths,
+i.e., infeasible paths are omitted, and 2) each path condition encodes
+the set of concrete program inputs that would cause execution to
+follow the same control flow path. Because path conditions are encoded
+as constraints over program inputs, the reasoning capabilities of
+symbolic execution are limited by the underlying constraint
+solver. Recent work has explored the strengths and limitations of
+tools which leverage constraint solvers, e.g., concolic execution,
+identifying symbolic dereferencing and updating operations as areas
+for potential improvement~\cite{Chen:2013,Qu:2011}.  Precisely
+modeling these operations, however, is challenging because it requires
+formulating logical predicates over an input domain that contains a
+potentially unbounded number of references.
+
+The most direct approach to address these challenges is to approximate
+the results of a symbolic deference by substituting in a valid
+concrete value, as is done in dynamic symbolic execution
+(\dsetxt{})~\cite{Godefroid:POPL07,Godefroid:2005,Sen:2005,Tillmann:2008}. These
+approaches partition the universe of heaps in the symbolic
+representation but often under-approximate the partitions or require
+array theories in the constraint
+solver~\cite{Chen:2013,Elkarablieh:2009}. A more effective approach is
+to partition the reachable heaps by using value summary
+representations, where multiple values for a reference may be
+represented along a single execution
+path~\cite{Dillig:2011,Elkarablieh:2009,Sen:2014,Torlak:2014,Xie:2005,Yorsh:2008}. Systems
+using these representations perform analyses that are more complete
+than standard~\dsetxt{} methods, but their associated dereferencing
+operations require placing further restrictions on the input heap,
+such as limiting the number of nodes~\cite{Elkarablieh:2009}, the
+nature of aliasing relationships~\cite{Babic:2007,Xie:2005}, or the
+the use of recursive data structures~\cite{Dillig:2011}.
+
+An alternative approach which does not under-approximate the heap is
+Generalized Symbolic Execution
+(\gsetxt{})~\cite{Cadar:2008,KiasanKunit,GSE03,Rosner:2015}.  On symbolic
+dereferencing operations,~\gsetxt{} partitions the input space between the
+various possible aliasing configurations on-the-fly and also creates
+non-deterministic choice points on the current path in order to
+explore each heap configuration. This approach, however, is
+inefficient because it does not treat heap allocated data as symbolic,
+but instead concretizes all possible heap configurations.
+
+The contribution of this work is a non-trivial adaptation of concepts
+in abstract interpretation to the domain of symbolic execution. The
+result of which, unlike~\gsetxt{}, is the ability to efficiently generate
+and update \emph{symbolic heaps} to produce a single path constraint
+that is sound and complete up to the point of execution. This is
+accomplished by representing the symbolic heap with a field sensitive
+points-to graph with edges annotated with disjunctive formulas
+describing aliasing relationships. Where~\gsetxt{} branches the heap at every
+de-reference, the symbolic heap in this work splits only at reference
+comparison operations or field operations that may throw exceptions.
+
+The correctness of the symbolic heap and its on-the-fly update rules
+for symbolic execution is shown by proving the existence of a
+bisimulation between symbolic heap states and~\gsetxt{} states. From that
+result comes the soundness and completeness of the path constraint up
+to the point of execution.  The efficiency of the representation is
+established with an exploratory empirical evaluation within the Java
+PathFinder framework over a classical set of symbolic execution
+benchmarks. The evaluation demonstrates how the symbolic heap scales
+compared to state-of-art~\gsetxt{} algorithms.
+
+This new symbolic heap and update rules for symbolic execution is a
+novel approach for de-referencing and updating heap allocated data
+that brings together the best features of previous work while removing
+the limitations of that same work. Although it draws inspiration from
+abstract interpretation by defining a symbolic heap,
+\begin{compactitem}
+  \item it is an exact representation, without over- or under-approximation;
+  \item it imposes no restrictions on the set of heaps that can be defined;
+  \item it does not require the creation of an initial set of input heaps;
+  \item it is not tied to specific constraint solver theories, e.g., arrays; and
+  \item it does not require global constraint rewriting for on-the-fly updates.
+\end{compactitem}
+These several properties set this work apart from other related works.
+
+\begin{comment}
+\section{Introduction}
+
+% SymExe is cool because for reasons x,y, and z
+
+In recent years symbolic execution has provided the basis for various
 software testing and analysis techniques. Symbolic execution
-systematically explores the program execution space using symbolic
-input values, and for each explored path, computes constraints on the
-symbolic inputs to create a \emph{ path condition}.  The path
-conditions computed by symbolic execution characterize the observed
-program execution behaviors and have been used as an enabling
+systematically explores the program execution space representing input
+values symbolically, and for each explored path, it computes
+constraints on the symbolic inputs to create a \emph{ path condition}.
+Path conditions computed by symbolic execution characterize the
+observed program execution behaviors and have been used as an enabling
 technology for various applications, e.g., regression
@@
 
-Initial work on symbolic execution largely focused on checking
-properties of programs with primitive
-types~\cite{clarke76TSE,King:76}.  With the advent of object-oriented
-languages, recent work has generalized the core ideas of symbolic
-execution to enable analysis of programs containing complex data
-structures with unbounded domains, i.e., data stored on the
-heap~\cite{Kiasan06,Kiasan07,GSE03}.  These \emph{Generalized Symbolic
-  Execution} (GSE) techniques construct the heap in a lazy manner,
-deferring materialization of objects on the concrete heap until they
-are needed for the analysis to proceed. The materialization creates
-additional non-deterministic choice points in the symbolic execution
-tree by representing the feasible heap configurations as (i) null,
-(ii) an instance of a new reference of a compatible class, and (iii)
-an alias to a previously initialized symbolic reference.  Symbolic
-execution then follows concrete program semantics for materialized
-heap locations. Although this approach enables the analysis of heap
-manipulating programs, a large number of feasible concrete heap
-configurations are created leading to a path explosion.
+The path conditions computed by symbolic execution have two important
+characteristics: 1) they characterize the set of feasible execution
+paths, i.e., infeasible paths are omitted, and 2) each path condition
+represents the set of concrete program inputs that would cause
+execution to follow that program path. Because path conditions are
+encoded as constraints over program inputs, the reasoning capabilities
+of symbolic execution are limited by the underlying constraint solver.
+Thus, extending the capabilities of symbolic execution to reason about
+new theories is an area of active research. Of particular interest are
+symbolic dereferencing and updating
+operations~\cite{Chen:2013,Qu:2011}. Precisely modeling these
+operations is challenging, because it requires formulating logical
+predicates over an input domain containing a potentially unbounded
+number of references.
 
-The goal of this work is to mitigate the path explosion problem in GSE
-by grouping multiple heaps together and only partitioning the heaps at
-points of divergence in the control flow graph. Our inspiration is
-found in the domain of static analysis that uses sets of constraints
-over heap locations to encode multiple heaps in a single
-representation. These sets, sometimes known as \emph{value sets} or
-\emph{value summaries}, allow multiple heaps to be represented
-simultaneously with a higher degree of precision than afforded by
-traditional techniques for shape analysis. Some of these previous
-attempts, however, are unable to handle aliasing in heaps due to a
-recursive definition of objects~\cite{Xie:2005}, while others require
-a set of heaps as input and are unable to initialize heaps
-on-the-fly~\cite{Dillig:2011,Tillmann:2008}.  As is typical in static
-analysis, over approximation of the heap representations alleviates
-some of these limitations but often leads to infeasible heaps. Also,
-most static analysis techniques for heap updates require a rewrite of
-the constraint system making it prohibitive for use in the context of
-symbolic execution.
+Current strategies for symbolic dereferencing require making tradeoffs
+between the completeness of the analysis and the completeness of the
+path condition. For example, one simple approach is to terminate
+execution upon attempting to dereference any symbolic
+value~\cite{Clarke:2004}. While this preserves the integrity of the
+path condition, it comes at the cost of an incomplete analysis. To
+enable a more complete analysis, dynamic symbolic execution (\dsetxt{}),
+approximates the results of a symbolic dereferencing by substituting
+in a valid concrete
+value~\cite{Godefroid:POPL07,Godefroid:2005,Sen:2005,Tillmann:2008}. This
+allows execution to continue, but the approximation renders the path
+condition incomplete~\cite{Chen:2013,Elkarablieh:2009}, by effectively
+partitioning the space of input heaps into those where the result of
+the dereferencing matches the concrete execution. Larger partitions
+can be achieved by using value summary representations, where multiple
+values for a reference may be represented along a single execution
+path~\cite{Dillig:2011,Elkarablieh:2009,Sen:2014,Torlak:2014,Xie:2005,Yorsh:2008}. Systems
+using these representations perform analyses that are more complete
+than standard~\dsetxt{} methods, but their associated dereferencing
+operations require placing further restrictions on the input heap,
+such as limiting the number of nodes~\cite{Elkarablieh:2009}, the
+nature of aliasing relationships~\cite{Babic:2007,Xie:2005}, or the
+shape of the heap itself~\cite{Dillig:2011}. Finally, at the opposite
+end of the spectrum lies generalized symbolic execution
+(\gsetxt{})~\cite{Cadar:2008,KiasanKunit,GSE03,Rosner:2015}, which
+accomplishes a fully complete analysis at the cost of an incomplete
+path condition \sjp{not clear what an incomplete path condition
+  is}. On symbolic dereferencing operations,~\gsetxt{} partitions the input
+space between the various possible aliasing configurations
+\sjp{so?}. Thus, none of the current techniques provide the option of
+maintaining both a complete analysis and a complete path
+condition. This is in stark contrast to symbolic execution over
+primitive types, which enjoys both properties simultaneously.
 
-In this work, to effectively represent multiple heaps simultaneously
-in the context of symbolic execution, we define a novel heap
-representation and an algorithm to initialize and update the heap
-on-the-fly. In essence, our summary heap approach supports aliasing,
-does not require constraint rewriting on heap updates, and reduces
-non-determinism in the search space during symbolic execution.
+\sjp{Need to explain that the techniques still operate within some bound for loops, etc.}
 
-We represent the heap as a bipartite graph consisting of references
-and locations. Each reference is able to point to multiple locations,
-where each edge is predicated on constraints over aliasing between
-references. Each location points to a single reference for a given
-field. The use of a bipartite graph affords two key advantages: (i) it
-allows for a non-recursive definition of objects which enables us to
-support aliasing, and (ii) it does not introduce auxiliary variables
-or require rewriting of non-local constraints during updates to the
-heap.
+\sjp{Notion of on-the-fly updates is not here}
 
-The summary heap algorithm defines how the bipartite graph is updated
-during lazy initialization. Unlike GSE, however, the summary heap
-algorithm introduces non-determinism in the search only at points of
-divergence in the control flow graph. These points of non-determinism
-are at field accesses that lead to null-pointer exceptions and at
-comparisons of references. The former represents a divergence due to
-exceptional control flow while the latter is due to program structure.
-The combination of the heap representation and the summary heap
-algorithm enables us to improve the efficiency of symbolic execution
-of heap manipulating programs over state-of-the-art techniques.
+\sjp{Nowhere do we refer to the technique as a summary heap framework or algorithm,
+so the next section with its heading just jumps out of nowhere.}
 
-% The precise heap representation based on a bipartiate graph coupled
-%with this algorithm to perform updates to the heap enable us to
-%successfully mitigate the state space explosion problem in GSE.
-
-\begin{comment}
-In
-practical terms, any property that can be proved using GSE can also be
-proved using summary heaps, and, any property proved by
-summary heaps can also be proved by GSE. Of course, both require a
-bound on heap reference chains and loops.
-\end{comment}
-
-%Aside from the novelty of the heap summary and its application to
-%symbolic execution, the new data structure appears to ameliorate
-%state explosion in symbolic execution as hoped.
-
-The summary heap algorithm is sound and complete with respect to
-properties that are provable using GSE. This proof is accomplished by
-showing the existence of a bisimulation between states in GSE and
-states in the summary heap algorithm.  A preliminary implementation in
-Java Pathfinder (JPF) shows that in general, the heap summary
-algorithm improves over other state-of-the-art techniques, and in some
-instances, the improvement is remarkable: two-orders of magnitude
-reduction in running time. More importantly though, the heap summary
-enables the initialization of larger more complex heaps than
-previously possible as shown in our results.
-
-%, described in this paper, compares the heap summary algorithm on a
-%handful of benchmarks, each representing different degrees of
-%initialization and branching, to GSE with lazy initialization in
-%Symbolic Pathfinder (SPF) and implementation lazier\# also in
-%SPF. The results
-
-\begin{comment}
-We implement the summary heap algorithm as an extension to \emph{Java
-  PathFinder} (JPF) and compare it to GSE with lazy initialization in
-\emph{Symbolic Pathfinder (SPF)} and an implementation of lazier\#
-initialization in SPF.  The comparison shows on some examples up to a two-order of magnitude
-reduction in the total time taken to explore the same state space
-defined by the bound on the longest heap reference chain.  For these
-examples, we show that where other GSE approaches are unable to
-complete exploration within the provided time bound, the summary heap
-finishes exploration in a few seconds.
-\end{comment}
-
-%shows that it can improve the scalability of symbolic execution of
-%heap manipulating programs X fold over GSE-based analyses while
-%maintaining precision and efficiency.
-
-%preserves the heap
-%configurations and program behaviors
-
-%complete --> anything prove with GSE you can with heap sound -->
-%preserves the same behaviors in the GSE machine.
-
-%Our analysis improves on existing GSE approaches by reducing
-%the size of the symbolic execution state space explored, thereby
-%improving scalability of symboic execution for heap manipulating
-%software. It improves on existing heap summarization techniques by
-%enabling analysis of arbitrary recursive data structures (no initial
-%heap configuration is required) while avoiding the imprecision
-%introduced by these techniques.
-
-%\nsr{a paragraph that provides a breif summary of the results.. would
-%  be nice if we have numbers for lazier and lazier Sharp as well.}
+This paper introduces a technique that avoids these problems by
+preserving the following properties of classical symbolic execution:
+(i) Inputs are represented by unbounded and unconstrained input
+symbols. This lack of predetermined constraints is key to avoiding
+under-approximation, which in turn is required for performing a
+complete analysis. (ii) Points of nondeterminism are only introduced
+at control flow instructions, which is critical for maintaining a
+complete path condition for a given control flow path.
 
@@
 
-%\item\textbf{-} A summary heap that represents sets of concrete heaps
-% without approximation or morphological restrictions.
-
-\item\textbf{-} A non-approximate, morphologically arbitrary, and efficient 
-summary heap representation.
-
-\item\textbf{-} An algorithm to dynamically initialize, summarize, and
-  update the summary heap during symbolic execution.
+\item\textbf{-} The first sound and complete system for reasoning symbolically about the 
+set of input heaps along any valid program path.
 
@@
 completeness of the heap summary approach with respect to
-properties provable by GSE.
+properties provable by~\gsetxt{}.
 
@@
 demonstrating the scalability of the summary heap approach
-compared to other GSE approaches.
+compared to other~\gsetxt{} approaches.
 
 \end{compactdesc}
-
-%\begin{compactdesc}
-%
-%\item\textbf{-} A summary heap as a bipartite graph that supports
-%  aliasing and does not require rewriting of constraints.
-%
-%% to handle alias and efficient updates of constraints.
-%
-%\item\textbf{-} A summary heap algorithm to initialize, summarize, and
-%  update the bipartiate graphs during symbolic execution.
-%
-%\item\textbf{-} A proof of the existence of a bisimulation relation to establish
-%  that the heap summary approach is sound and complete with respect to
-%  properties provable by GSE.
-%
-%\item\textbf{-} A proof of concept implementation and small empirical study to demonstrate the scability of the heap summary approach
-%  compared to other GSE approaches.
-%
-%\end{compactdesc}
-
-%The rest of this paper defines summary heap and its to symbolic
-%execution. Following the algorithm definition, the existence proof of
-%bisimulation is given with the accompanying corollaries for soundness
-%and completeness. This is followed by the implementation in JPF and
-%the evaluation. The paper ends with the conclusion and future work.
-
-%\item{We present a novel inter-procedural analysis technique for 
-%symbolic execution of heap manipulating software which constructs 
-%a precise heap summary.}
-%\item{We use the JavaLite language~\cite{saints-MS} to formalize 
-%the algorithm for constructing and manipulating the heap summary
-%on-the-fly during symbolic execution.}
-%\item{We implement our approach in the Symbolic PathFinder tool and
-%empirically demonstrate that our technique improves
-%the scalability of symbolic execution of heap maninpulating software
-%over GSE, while maintaining efficiency and precision.}
-%\item{We prove that at any given point during symbolic execution, the symbolic 
-%heap represents the exact set of feasible concrete heap structures 
-%for the program under analysis.}
-% \end{description}
-
-%\nsr{needs
-%  some text on the fact we use java lite to formalize the heap
-%  summary, some key characteristicss of the heap such as the fact it
-%  is a bipartiate graph with locations and referneces, properties of
-%  the heap such as the determinism and immutability}
-
-%\nsr{Is any part of the formalism borrowed
-%from the dilligs? Which part are unique?}  \nsr{end on a couple
-%sentences about the various rules that will be talked about in the
-%paper}
-
-%\nsr{The reader should be convinced about our expressiveness
-%  claim here}
-
-%\nsr{a paragraph that provides intution on how we are a bisumulation
-%  with the GSE..reader should be convinced about the precision claim}
-
-\begin{comment}
-\newcommand{\Indstate}[1][1]{\State\hspace{#1\algorithmicindent}}
-
-\begin{figure}
-\begin{center}
-\begin{algorithmic}[1]
-\Procedure{load}{$r,f$}
-\If{$r$ is initialized and $f$ is uninitialized}
-\If{ $f$ has a reference type}
-\State nondeterministically assign to $f$:
-\State  \ \ null  %hacky way to indent.
-\State \ \ non-null
-\EndIf
-\If{$f$ has a primitive type}
-\State assign $f$ a new symbol
-\EndIf
-\EndIf
-\If{$r$ is uninitialized}
-\State nondeterministically assign to $f$:
-\State  \ \ a new symbolic location  %hacky way to indent.
-\State \ \ an existing symbolic location
-\EndIf
-\State\Return $r.f$
-\EndProcedure
-\end{algorithmic}
-\end{center}
-\caption{Lazier\# Initialization}
-\end{figure}
-
-Lazy initialization is a symbolic execution technique where memory structures are created on-demand, as they are required.
 \end{comment}

### 2015-03-27 tex/related.tex
removing duplicate
Brought in abstract, intro, and related work from CAV paper.

@@
 
-In this section we discuss some closely related works, including
-techniques for scaling symbolic execution of programs with complex
-data types and heap summary techniques. Note that there is a huge body
-of work on analyzing programs with heaps in the domain of static
-analysis, testing, and verification.
+Initial work on symbolic execution largely focused on checking
+properties of imperative programs with primitive
+types~\cite{Clarke:76,King:76}.
+Several projects have generalized the core idea of symbolic execution,
+enabling it to be applied to programs with more general types,
+including references and
+arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. However, these
+generalized symbolic execution (\gsetxt{}) techniques work by branching over
+multiple copies of the system state during dereferencing operations,
+exacerbating path explosion.
+Our work leverages the core idea in generalized symbolic execution
+with lazy initialization using on-the-fly reasoning to model a
+black-box input heap during symbolic execution, but avoids the
+nondeterminism introduced by~\gsetxt{} by constructing a single
+symbolic heap and polynomially-sized path condition for each control
+flow path.
 
-Initial work on symbolic execution largely focused on checking
-properties of imperative programs with primitive primitive
-types~\cite{Clarke:76,King:76}. Several recent projects generalized
-the core idea of symbolic execution which enabled it to be applied to
-programs with more general types, including references and
-arrays~\cite{GSE03,Godefroid:PLDI05,Sen:FSE05,CadarEngler05EXE,KiasanKunit}.
-Our work leverages the core idea in generalized symbolic execution
-with lazy initialization to construct the heap on-the-fly during
-symbolic execution, but avoids the nondeterminism introduced by GSE by
-constructing a summary heap and will generally create fewer paths than
-GSE techniques.
+Recent progress has been made towards mitigating path explosion via state merging~\cite{Kuznetsov:2012,Sen:2014,Torlak:2014}.
+While the independently developed techniques in~\cite{Sen:2014,Torlak:2014} use representations similar to the one presented here, none of these techniques address the fundamental issue concerning symbolic heaps, namely dereferencing symbolic input references.
+For these reasons, we believe these works to be both orthogonal and complimentary to our own.
 
-Pex is a tool for dynamic symbolic execution for .NET programs. In
-order to handle data structures Pex uses a theory of arrays and does
-not initialization~\cite{export:81193}.  It is required to have a
-constraint solver that handles the theory for unbounded arrays for
-this approach to be tractable. It would be an interesting comparision
-to perform in future work.
+A number of dynamic symbolic execution (\dsetxt{}) techniques either use
+concretization when reasoning about references or require solvers that
+support theories of
+arrays~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}. Sometimes,
+however, as demonstrated in~\cite{Elkarablieh:2009},~\dsetxt{}
+under-approximates the possible heaps configurations when it
+concretizes symbolic values. The SAGE~\dsetxt{}
+engine~\cite{Elkarablieh:2009} includes more sophisticated methods for
+reasoning about references, and can successfully reason about more
+complicated examples. However, the heap model in SAGE prohibits
+input-dependent memory allocation. The fixed-memory requirement means
+that analyses of programs accepting indefinite input heaps may
+terminate prematurely, even for the class of self-limiting
+solver-compatible programs.
 
-A number of static analysis techniques have been proposed to support
-reasoning about input heap structures. The technique most closely
-related to (and which served as inspiration for) our approach is the
-procedure summary proposed by Dillig et al. to support modular
-reasoning~\cite{Dillig:2011}.  While their method improves path
-sensitivity over standard static analysis methods, it remains limited
-by a statically-generated symbolic input heap and it cannot adapt to
-path-sensitive heap properties of the input heap.
+Many bounded model checking (BMC) methods include a model for
+reasoning about references, including those described
+in~\cite{Clarke:2004,Barnett:2006,Xie:2005,Babic:2007,Dillig:2011}. However,
+BMC techniques generally need to predetermine bounds of a heap. Other
+limitations include assuming that symbolic references do not
+alias~\cite{Xie:2005,Babic:2007}, that data structures are not
+recursive~\cite{Dillig:2011}, or prohibiting dereferencing of
+black-box input references~\cite{Clarke:2004}.
 
-Other techniques have been proposed to model references using sets of
-guarded
-locations~\cite{Xie:2005,Cherem:2007,Dillig:2011,Sen:2014}. These
-sets, sometimes known as value sets or value summaries, allow multiple
-heaps to be represented simultaneously with a higher degree of
-precision than afforded by shape analysis. However, some of these
-previous attempts~\cite{Xie:2005,Cherem:2007} utilize non-local
-recursive definitions for objects.  In our heap representation, object descriptions are
-entirely local, thus avoiding these pitfalls. Other methods
-\cite{Dillig:2011,Sen:2014}, while having local morphological
-representations, do not provide for dynamic exploration of the initial
-heap state.
+A number of constraint-based programming techniques are capable of
+reasoning about
+heaps~\cite{Degrave:2010,Charreteur:2009,Albert:2013}. Most notably,
+the technique in~\cite{Albert:2013} is capable of reasoning about
+dereferencing operations in a per-path set of unknown input
+heaps. However, no guarantees are made about the precision of the
+analysis performed.
 
-There is also a large body of work on generating tests for
-object-oriented programs that use a variety of techniques to generate
-heap structures to test object-oriented
-programs~\cite{xie2005symstra,xie2004rostra,boyapati2002korat,artzi2006finding}.
-Another line of work in heap representation lies in identifying
-isomorphic heap structures in order to avoid exploring redundant
-paths~\cite{milicevic2007korat}.  These methods are generally focused
-on the morphology of the heap apart from the external constraint
-problems encountered during program execution, and as such, are
-largely orthogonal to this work. Recent work shows that the need for
-reasoning about heap structures is an important
-problem~\cite{barr2013collecting}. Delta execution is another work
-that combines states for object-oriented programs~\cite{d2008delta}.
-
-%The impact of such an approach is two-fold.  First, these techniques
-%must use approximations to resolve reference inequalities, resulting
-%in false positives in the results. Second, these techniques are
-%incapable of reasoning about heaps with recursive data structures due
-%to the potential for infinite recursion during dereferencing. This
-%means that either a large class of data structures must be avoided,
-%or a large class of behaviors must be ignored.
+The symbolic heap value sets presented in this work build upon a
+number of prior techniques that use sets of guarded values to
+represent program
+state~\cite{Sen:2014,Torlak:2014,Yorsh:2008,Xie:2005,Dillig:2011,Elkarablieh:2009}. The
+methods presented in~\cite{Sen:2014,Torlak:2014,Yorsh:2008} use value
+sets to represent all symbolic program state, including
+references. While symbolic referencing operations could, in principle,
+be supported with these methods, it is not clear from the published
+material exactly how that might be accomplished, especially when
+reasoning about dereferencing in a black-box input heap. All of the
+methods presenting solutions to the dereferencing
+problem~\cite{Xie:2005,Dillig:2011,Elkarablieh:2009} are not complete,
+for a variety of reasons which have been previously enumerated.

### 2015-03-27 tex/evaluation.tex
Added additional linkedList test results to table 1.

@@
 								& 6	& 280.56	& 299.19	& 2.36	&5447980	&6437201	& 303	&3731094	&2933027	& 76\\
+								& 7	& -		& -		& 5.07	& -		&-		& 395	&-		&-		& 99\\
+								& 8	& -		& -		& 17.49	& -		&-		& 499	&-		&-		& 125\\
+								& 9	& -		& -		& 63.96	& -		&-		& 615	&-		&-		& 154\\
+								& 10	& -		& -		& 206.93	& -		&-		& 743	&-		&-		& 186\\
     \hline

### 2015-03-27 tex/related.tex
Fixed a typo in related.tex that was causing a column overflow.

@@
 arrays~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}. Sometimes,
-however, as demonstrated in~\cite{Elkarablieh:2009},~\dsetxt{}
+however, as demonstrated in~\cite{Elkarablieh:2009}, ~\dsetxt{} 
 under-approximates the possible heaps configurations when it

### 2015-04-20 ase-2015-tex/bisimulation.tex
Created ase-2015-tex folder, ported CAV paper to ASE format.

--- 2015-02-07 cav-2015-tex/bisimulation.tex
@@
 completeness of the symbolic heap approach with respect to Generalized
-Symbolic Execution (\gsetxt{}). Intuitively, any properties proven with~\gsetxt{}
-can also be proved using the symbolic heap algorithm.~\gsetxt{} concretizes
-the possible heap configurations along with various aliasing
-relationships when an uninitialized field is dereferenced. The rules
-for initializing and updating the fields in the Javalite semantics for
-\gsetxt{} are shown in the~\appref{app:gse}.
+Symbolic Execution (\gsetxt{}). Intuitively, any properties proven
+with~\gsetxt{} can also be proved using the symbolic heap
+algorithm.~\gsetxt{} concretizes the possible heap configurations
+along with various aliasing relationships when an uninitialized field
+is dereferenced. The rules for initializing and updating the fields in
+the Javalite semantics for \gsetxt{} are shown in Appendix B where as
+the the complete set of rules for the symbolic heap algorithm are
+shown in Appendix C.
 

### 2015-04-20 ase-2015-tex/lazy.tex
Created ase-2015-tex folder, ported CAV paper to ASE format.

--- 2014-11-12 tex/lazy.tex
@@
 \section{Generalized Symbolic Execution}
-
+\label{app:gse}
 The specialization of Javalite to generalized symbolic execution with
-lazy initialization using the summary heap is in \figref{fig:lazyInit}
-for the initialization and \figref{fig:lazy} for how the
-initialization is used. Specifically, the field-access rule in
+lazy initialization using the symbolic heap is in
+\figref{fig:lazyInit} for the initialization and \figref{fig:lazy} for
+how the initialization is used. Specifically, the field-access rule in
 \figref{fig:lazy} uses initialization, $\rightarrow_I^*$, to be sure
@@
 symbolic execution never happens for more than one object on any use
-of $\rightarrow_I^*$: $\Lambda$ is either empty or contains exactly one
-location.
+of $\rightarrow_I^*$: $\Lambda$ is either empty or contains exactly
+one location.
 

### 2015-04-20 ase-2015-tex/overview.tex
Created ase-2015-tex folder, ported CAV paper to ASE format.

\section{Overview}
In this section, the general concepts behind symbolic execution are first introduced in the context of primitive value types. The initial framework is then extended to include symbolic references and the symbolic input heap.

\subsection{Symbolic Execution}
At it’s foundation, symbolic execution is about finding relationships between program variables by means of constraints in the form of predicates over symbolic program inputs.

%here, we'll give a simple example for how symbolic execution works.

The path condition represents a set of valid concrete program inputs. Concrete executions with program inputs satisfying the path condition will result in a trace identical to that followed by the symbolic execution. Conversely, any concrete execution with an initial state not satisfying the path condition will follow a different path. In this manner, the path condition is an exact representation of all program inputs along a given execution path.

\subsection{Symbolic Input Heap}
Directly in this vein, our references, and indeed our heap as a whole are essentially predicates describing relationships between program variables and the symbolic input heap. These predicates are formed by compositions of heap operations that occur over the course of program execution. As with any symbolic execution technique, equality conditions between heap predicates form constraints, which accumulate along a program execution path in the form of a path condition.

The symbolic input heap represents the unconstrained, unbounded set of possible input heap configurations. Input references represent handles to arbitrary locations within the input heap. The heap at any moment in program execution is represented as a compositional expression over the initial input heap and input references.

%At this point, we’d introduce the symbolic heap and associated operations at a purely symbolic level. We’d have a few heap operations, such as a field read, field write, and reference comparison, along with the symbolic heap and references represented by single-letter symbols. The set-up would look something like this:

Let A and B be symbolic heaps, p and q be symbolic references, and i be a field index. Note that A,B,x, and y are predicates, while f is a literal. A field read operation is a function mapping a heap, reference, and a field index to a reference: 
$$ \mathit{read}: (H \times R \times F) \rightarrow R$$
(Where H R and F are the domains of heaps, references, and fields, respectively)

A field write operation is a function mapping a heap, a reference, a field index, and another reference to a heap:
$$\mathit{write}: (H \times R \times F \times R) \rightarrow H$$

We would then show a very simple program example, along with the classical symbolic execution tree to illustrate how the symbolic heap works. The example might look something like this:

suppose we have a program that looks like this:

\begin{figure}
void getData( container v )\{

container x = v.data;

this.data = x;

\}
\caption{}
\end{figure}

The initial program state looks like this:
 $$\{heap = A, this = a, v = b, x = null , PC = phi\}$$

After the line “container x = v.data;", the system state will be:
$$\{heap = A , this = a, v = b, x = read(A,b,data), PC = phi\}$$

After the line “this.data = x;”, the system state is:
$$\{heap = write(A,a,data,read(A,b,data)), v = b, x = read(A,b,data), PC = phi\}$$

It is important to note that the symbolic input heap itself is static and unchanging from the start of program execution. This is true whether or not the program is single or multi-threaded. In this context, the term "lazy initialization" is somewhat of a misnomer. The process of lazy initialization does in no way alter the symbolic input heap, but instead establishes a partition over the space of possible input heaps without changing or constraining that input heap in any way.

### 2015-04-20 ase-2015-tex/st-def.tex
Created ase-2015-tex folder, ported CAV paper to ASE format.

\begin{definition}
\label{def:ST}
The function $\mathbb{ST}(\cfgnt{L},\cfgnt{r},\phi,\phi_g)$
strengthens every constraint from the reference $\cfgnt{r}$ with
$\phi$ and retaining location-constraint pairs that are satisfiable
after this strengthening with the inclusion of the global heap
constraint $\phi_g$:
\[
\begin{array}{rcl} 
\mathbb{ST}(\cfgnt{L},\cfgnt{r},\phi,\phi_g) & = & \{ (\phi\wedge\phi^\prime\ \cfgnt{l}^\prime) \mid (\phi^\prime\ \cfgnt{l}^\prime)\in \cfgnt{L}(\cfgnt{r})\wedge\mathbb{S}(\phi\wedge\phi^\prime\wedge\phi_g) \}
\end{array}
\]
\end{definition}

### 2015-04-21 ase-2015-tex/approach.tex
Reformatted figures to not be stuck in columns.

--- 2015-02-06 cav-2015-tex/approach.tex
@@
 
-\begin{figure*}
+\begin{figure*}[t]
+\begin{center}
 \begin{tabular}[c]{l}
@@
 \end{tabular}
+\end{center}
 \caption{Initializing fields, $s ::= \lp\cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\ \cfgnt{C}\rp$, with $s\rsum^*s^\prime =  s \rsum \cdots \rsum s^\prime \rsum s^\prime$.}
@@
 \begin{array}{rcl}
-\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
+\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \\ & &
+ \ \ \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \\ & &
+ \ \ \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
 \end{array}
@@
 \begin{center}
-\begin{tabular}[c]{c|c|c|c}
-\begin{tabular}[c]{c}
-\scalebox{0.81}{\input{origHeap.pdf_t}} \\
+\begin{tabular}[c]{c|c|c}
+\begin{tabular}[c]{c c}
+\scalebox{0.81}{\input{origHeap.pdf_t}}&  \\
 \end{tabular} &
@@
 \scalebox{0.81}{\input{summarizeYHeap.pdf_t}} \\
-\end{tabular} &
+\end{tabular}\\
+(a) & (b) & (c)\\
+\end{tabular}
+\begin{tabular}[c]{c}
+\begin{tabular}[c]{c c}
+\hline
 \begin{tabular}[c]{l}
-$\rho := \{ (\cfgnt{r}_1^i\ \cfgnt{l}_1 \}$ \\
+$\rho := \{ (\cfgnt{r}_1^i\ \cfgnt{l}_1) \}$ \\
 $\theta_\mathit{null} := \{ ( \cfgnt{r}_2^i = \cfgnt{r}_\mathit{null}\ \cfgnt{l}_\mathit{null}) \}$\\
@@
 $\theta_\mathit{orig} := \{ \}$ \\
+\end{tabular} &
+\begin{tabular}[c]{l}
 $\phi_{\mathit{1a}} := \cfgnt{r}_1^i = \cfgnt{r}_\mathit{null} $ \\
@@
 $\phi_{\mathit{2c}} :=  \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i = \cfgnt{r}_1^i $ \\
+\end{tabular}\\
 \end{tabular} \\
-(a) & (b) & (c) & (d) \\
+(d)
 \end{tabular}
@@
 \input{precise-fig-incomplete}
+
+\begin{figure*}[t]
+\begin{center}
+\begin{tabular}[c]{l}
+\scalebox{1.0}{\usebox{\boxPFAFW}} \\
+\end{tabular}
+\end{center}
+\caption{Field read and write relations: Field-access, $\rsym^\mathit{A}$, and field-write, $\rsym^\mathit{W}$, rewrite rules for the $\rsym$ relation.}
+\label{fig:fHeap}
+\end{figure*}
 
@@
 constraint. The reference-false is the logical dual of the rule.
+
+Consider the example in~\figref{fig:initHeap}(c). In order to to check
+if $\cfgnt{r}_1^i$ and $\cfgnt{r}_2^i$ are equal we first get the constraint location
+pairs associated with each of the references:
+\[
+\cfgnt{L}(\cfgnt{r}_1^i) = \{ (\phi_{1a}\; \cfgnt{l}_\mathit{null})\; (\phi_{1b}\; \cfgnt{l}_1) \} 
+\]
+\[
+\cfgnt{L}(\cfgnt{r}_2^i) = \{ (\phi_{2a}\; \cfgnt{l}_\mathit{null})\; (\phi_{2b}\; \cfgnt{l}_2)\; (\phi_{2c}\; \cfgnt{l}_1) \} \\
+\]
+\noindent{The three constraint sets are:} 
+\[
+\Phi_\alpha = \{ (\phi_{1a}\; \wedge\; \phi_{2a} ) (\phi_{1b}\; \wedge\; \phi_{2c} ) \}\;
+\Phi_0 = \{ \}\; \Phi_1 = \{ \phi_{2b}\} \\
+\]
+\noindent{Finally the global constraint is} 
+\[
+\phi^\prime = \mathit{true} \wedge [ (\phi_{1a}\; \wedge\; \phi_{2a} )\vee (\phi_{1b}\; \wedge\; \phi_{2c} ) ] \wedge \neg\phi_{2b} 
+\]

### 2015-04-22 ase-2015-tex/evaluation.tex
Added additional explanation to the evaluation section.

--- 2015-02-07 cav-2015-tex/evaluation.tex
@@
    \multirow{2}{*}{Method }&\multirow{2}{*}{ $k$ }
-   &\multicolumn{3}{|c|}{Time (seconds)} &\multicolumn{3}{|c|}{States} &\multicolumn{3}{|c|}{ Paths }\\
-								&	&\gsetxt{} & L\#		&SH		&\gsetxt{}	& L\# & SH&\gsetxt{}	& L\# 	& SH\\
+   &\multicolumn{3}{c|}{Time (seconds)} &\multicolumn{3}{c|}{States} &\multicolumn{3}{c|}{ Paths }\\
+								&	&\gsetxt{} & L\#		&SL		&\gsetxt{}	& L\# & SL&\gsetxt{}	& L\# 	& SL\\
    \hline
@@
    								& 3	& 20.63	& 25.55	& 4.03	& 1953	& 1703	& 1485	& 515	& 515	& 328\\
+								& 4	& -		& -		& 410.89	& -		&-		& 73635	&-		&-		& 15563\\
     \hline
@@
 \end{table*}
+
 %\end{figure*}
@@
 the heap constraint changes from one state to another. 
+\bah{The solver optimizations used in the \symtxt{} are not applicable to \gsetxt{}-style techniques, as they do not generate or solve any heap-related constraints.
+Even with the solver optimizations these techniques would have the same performance characteristics.
+The overhead in \gsetxt{} arises from case-splitting (generating states) rather than solver time.
+}
+
+\bah{The benchmarks all include invariants and traversals of data structures.
+The chosen benchmarks have a high proportion of heap-related operations, putting maximum focus on the heap analysis methods under investigation.
+They are included to provide evidence of the general computational efficiency of the SH approach.
+In future work we plan to evaluate it on a more diverse set of benchmarks.
+The BinarySearchTree test uses the class of the same name from Alan Weiss' book titled ``Data Structures and Algorithm Analysis in Java''.
+The test method first asserts a repOk() invariant, before conducting a traversal to find an arbitrary integer key in the tree.
+The TreeMap method comes from the standard java.util library, and is an implementation of a balanced red/black tree.
+This method asserts a repOk() invariant, before traversing the tree.
+The LinkedList test starts by asserting a repOk() invariant, which checks for loops in the linked list using Floyd’s cycle-finding algorithm.
+The linked list is then traversed using a contains() method that attempts to locate an arbitrary reference key in the list.}
+
+\bah{All benchmarks were performed with respect to a given k-bounds.
+k-bounding limits the length of reference chains to some user-defined integer k.
+k-bounding was chosen because it provides a fair means of comparison of all the techniques under investigation.
+More details on k-bounding can be found in~\cite{Deng:2007}.}
 

### 2015-04-23 ase-2015-tex/approach.tex
Added javalite details to main paper.

--- 2015-02-06 cav-2015-tex/approach.tex
@@
 
-The symbolic heap algorithm only partitions the heap at comparison
+Unlike~\gsetxt{}, the symbolic heap algorithm only partitions the heap at comparison
 operations or for exception handling.  There are three sets of rewrite
@@
 
-\begin{figure*}
+\begin{figure*}[t]
+\centering
+%\begin{center}
 \begin{tabular}[c]{l}
 \scalebox{1.0}{\usebox{\boxPI}} \\
+
 \end{tabular}
+%\end{center}
+
 \caption{Initializing fields, $s ::= \lp\cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\ \cfgnt{C}\rp$, with $s\rsum^*s^\prime =  s \rsum \cdots \rsum s^\prime \rsum s^\prime$.}
@@
 for $\cfgnt{l}_f$ are initialized to $\cfgnt{r}_\mathit{un}$.
+
+%\begin{figure*}[t]
+%\begin{center}
+%\begin{tabular}[c]{c|c|c}
+%\begin{tabular}[c]{c c}
+%\scalebox{0.81}{\input{origHeap.pdf_t}}&  \\
+%\end{tabular} &
+%\begin{tabular}[c]{c}
+%\scalebox{0.81}{\input{summarizeXHeap.pdf_t}} \\
+%\end{tabular} &
+%\begin{tabular}[c]{c}
+%\scalebox{0.81}{\input{summarizeYHeap.pdf_t}} \\
+%\end{tabular}\\
+%(a) & (b) & (c)\\
+%\end{tabular}
+%\begin{tabular}[c]{c}
+%\begin{tabular}[c]{c c}
+%\hline
+%\begin{tabular}[c]{l}
+%$\rho := \{ (\cfgnt{r}_1^i\ \cfgnt{l}_1) \}$ \\
+%$\theta_\mathit{null} := \{ ( \cfgnt{r}_2^i = \cfgnt{r}_\mathit{null}\ \cfgnt{l}_\mathit{null}) \}$\\
+%$\theta_\mathit{new} := \{ ( \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_1^i\ \cfgnt{l}_2) \}$\\
+%$\theta_\mathit{alias} := \{ ( \cfgnt{r}_1^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i = \cfgnt{r}_1^i\ \cfgnt{l}_1) \}$\\
+%$\theta_\mathit{orig} := \{ \}$ \\
+%\end{tabular} &
+%\begin{tabular}[c]{l}
+%$\phi_{\mathit{1a}} := \cfgnt{r}_1^i = \cfgnt{r}_\mathit{null} $ \\
+%$\phi_{\mathit{1b}} := \cfgnt{r}_1^i \neq \cfgnt{r}_\mathit{null} $  \\
+%$\phi_{\mathit{2a}} := \cfgnt{r}_2^i = \cfgnt{r}_\mathit{null}$ \\
+%$\phi_{\mathit{2b}} := \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_1^i$ \\
+%$\phi_{\mathit{2c}} :=  \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i = \cfgnt{r}_1^i $ \\
+%\end{tabular}\\
+%\end{tabular} \\
+%(d)
+%\end{tabular}
+%\end{center}
+%\caption{An example that initializes $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ and $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$.
+(a) Initial heap structure.
+(b) After $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ is initialized.
+(c) After $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ is initialized.
+(d) Sets in the summarize rule and constraints on the edges.}
+%\label{fig:initHeap}
+%\end{figure*}
 

### 2015-04-23 ase-2015-tex/summary-heap.tex
Created ase-2015-tex folder, ported CAV paper to ASE format.
Added javalite details to main paper.

--- 2015-02-07 cav-2015-tex/summary-heap.tex
@@
   literals} %(these appear in environments, expressions, and continuations).
-\item[Null and Uninitialized:] Every summary heap contains 
+\item[Null and Uninitialized:] Every symbolic heap contains 
 two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized,
@@
         auxiliary literals, so they do not appear in any constraint in
-        the symbolic heap as an aliasing option. The complete set of
-        semantic rules for Javalite are presented
-        in Appendix A.
+        the symbolic heap as an aliasing option.
+
+ \input{javalite-common}
+
+\figref{fig:javalite-common} defines
+the rewrite relations for the portion of the Javalite language
+semantics that are common to both generalized symbolic execution and
+the symbolic heap algorithm. The relation $\rcom$ includes all of these
+rules. Excepting \textrm{N{\footnotesize EW}}, the rules do not update
+the heap, and are largely concerned with argument evaluation in an
+expected way. It is assumed that only type safe programs are input to
+the machine so there is no type checking or error conditions. The
+machine simply halts if no rewrite is enabled.
+\bah{
+\input{lazy}	
+}
+\input{precise-fig}
+
+\input{summarize-precise}

### 2015-05-04 ase-2015-tex/abstract.tex
Added separate section for preliminaries, a new figure and explanation for the basic concepts of the symbolic heap, and a new subsection for limitations of the symbolic heap.

--- 2015-03-27 tex/abstract.tex
@@
 A fundamental challenge of using symbolic execution for software
-analysis is the treatment of dynamically allocated data. This paper
+analysis is the treatment of dynamically allocated data. \bah{Existing 
+techniques either underapproximate the space of possible inputs, 
+or are computationally infeasible.} This paper
 introduces a compact symbolic heap representation based on a field

### 2015-05-04 ase-2015-tex/conclusion.tex
Added separate section for preliminaries, a new figure and explanation for the basic concepts of the symbolic heap, and a new subsection for limitations of the symbolic heap.

--- 2015-02-07 cav-2015-tex/conclusion.tex
@@
-\section{Conclusion}
+\section{Discussion}
 
-Although our approach is inspired by the work in the static analysis
-domain, the heap representations used by those techniques do not lend
-themselves to symbolic execution since they rely on approximations,
-they are inflexible in what types of relations can be expressed, and
-they rely on rewriting of constraints.  In this work, we present a
+\subsection{Limitations}
+\bah{This paper presents a symbolic heap that is both sound and complete with respect to the properties verifiable through symbolic execution.
+However, when the symbolic heap is used in conjunction with any analysis method, it is subject the limitations inherent to the underlying technique.
+For example, for programs that do not exhibit self-limiting behavior, as a practical matter symbolic execution generally requires some sort of bounds to limit infinite loops and recursion.
+This means that some sort of constraint will invariably be imposed by the symbolic execution engine, impacting the heap as it would any other symbolic value.
+In this case, the advantage of our method is that these constraints may be freely chosen to suit the purposes of the analysis at hand, rather than being imposed by a limitation of the heap representation.}
+
+\subsection{Conclusion}
+
+In this work, we present a
 heap representation for symbolic execution that maintains exactness,

### 2015-05-04 ase-2015-tex/evaluation.tex
Added separate section for preliminaries, a new figure and explanation for the basic concepts of the symbolic heap, and a new subsection for limitations of the symbolic heap.

@@
 the heap constraint changes from one state to another. 
-\bah{The solver optimizations used in the \symtxt{} are not applicable to \gsetxt{}-style techniques, as they do not generate or solve any heap-related constraints.
+The solver optimizations used in the \symtxt{} are not applicable to \gsetxt{}-style techniques, as they do not generate or solve any heap-related constraints.
 Even with the solver optimizations these techniques would have the same performance characteristics.
 The overhead in \gsetxt{} arises from case-splitting (generating states) rather than solver time.
-}
 
-\bah{The benchmarks all include invariants and traversals of data structures.
+The benchmarks all include invariants and traversals of data structures.
 The chosen benchmarks have a high proportion of heap-related operations, putting maximum focus on the heap analysis methods under investigation.
@@
 The LinkedList test starts by asserting a repOk() invariant, which checks for loops in the linked list using Floyd’s cycle-finding algorithm.
-The linked list is then traversed using a contains() method that attempts to locate an arbitrary reference key in the list.}
+The linked list is then traversed using a contains() method that attempts to locate an arbitrary reference key in the list.
 
-\bah{All benchmarks were performed with respect to a given k-bounds.
+All benchmarks were performed with respect to a given k-bounds.
 k-bounding limits the length of reference chains to some user-defined integer k.
 k-bounding was chosen because it provides a fair means of comparison of all the techniques under investigation.
-More details on k-bounding can be found in~\cite{Deng:2007}.}
+More details on k-bounding can be found in~\cite{Deng:2007}.
 

### 2015-05-04 ase-2015-tex/intro.tex
Added separate section for preliminaries, a new figure and explanation for the basic concepts of the symbolic heap, and a new subsection for limitations of the symbolic heap.

--- 2015-03-27 tex/intro.tex
@@
 
-The contribution of this work is a non-trivial adaptation of concepts
-in abstract interpretation to the domain of symbolic execution. The
+\bah{The contribution of this work is a method for modeling and solving systems 
+of constraints over a symbolic input heap.} The
 result of which, unlike~\gsetxt{}, is the ability to efficiently generate
@@
 
-\item\textbf{-} The first sound and complete system for reasoning symbolically about the 
-set of input heaps along any valid program path.
+\item\textbf{-} A system for reasoning symbolically about the 
+set of input heaps along any valid program path that is sound
+and complete with respect to symbolic execution.
 

### 2015-05-04 ase-2015-tex/lazy.tex
Added javalite details to main paper.
Added separate section for preliminaries, a new figure and explanation for the basic concepts of the symbolic heap, and a new subsection for limitations of the symbolic heap.

@@
-\section{Generalized Symbolic Execution}
+\subsection{Generalized Symbolic Execution}
 \label{app:gse}
-The specialization of Javalite to generalized symbolic execution with
-lazy initialization using the symbolic heap is in
+The rules to generalized symbolic execution with
+lazy initialization using the symbolic heap are in
 \figref{fig:lazyInit} for the initialization and \figref{fig:lazy} for
 how the initialization is used. Specifically, the field-access rule in
-\figref{fig:lazy} uses initialization, $\rightarrow_I^*$, to be sure
+\figref{fig:lazy} uses initialization, $\rightarrow_I^*$, to ensure
 the accessed field is instantiated. Initialization in generalized

### 2015-05-04 ase-2015-tex/summary-heap.tex
Added separate section for preliminaries, a new figure and explanation for the basic concepts of the symbolic heap, and a new subsection for limitations of the symbolic heap.

@@
-\section{Our Approach}
+\section{Prelimiaries}
 \label{sec:sh}
-
-The symbolic heap algorithm is defined using
-Javalite~\cite{saints-MS}. Note that the approach is not restricted to
-this language or even Java in general; we use Javalite simply as
-mechanism to describe our approach. The small-step semantics of
-Javalite, defined as a syntactic machine using a CESK architecture,
-are modified to perform symbolic execution on a symbolic heap. The
-surface (input) syntax and machine (state) syntax are shown
-in~\figref{fig:syntax}. Terminals are in bold face while non-terminals
-are italicized. Ellipses indicate zero or more repetitions. Tuples
-omit the commas for compactness.
-
-\input{surface-syntax}
-\input{machine-syntax}
-\begin{figure}[t]
-\begin{center}
-\begin{tabular}{c}
-\scalebox{0.9}{\usebox{\boxSurface}} \\
-(a) \\\\
-\scalebox{0.9}{\usebox{\boxMachine}} \\
-(b)
-\end{tabular}
-\end{center}
-\caption{Syntax for Javalite. (a) The Javalite surface syntax. (b) The machine syntax with $\bowtie\ \in \{\wedge,\vee,\Rightarrow\}$.}
-\label{fig:syntax}
-\end{figure}
-
-A Javalite program, $\cfgnt{P}$, is a registry of classes, $\mu$, with
-a tuple indicating a class, $\cfgnt{C}$, and a method, $\cfgnt{m}$,
-where execution starts. The only primitive type in Javalite is
-Boolean. For simplicity in presentation, classes have only
-non-primitive fields, and methods have a single
-parameter. Expressions, $\cfgnt{e}$, include statements, and they use
-'$\cfgt{:=}$' to indicate assignment and '$\cfgt{=}$' to indicate
-comparison.  The dot-operator for field access is replaced by
-'$\cfgt{\$}$', and the dot-operator for method invocation is replaced
-by '$\cfgt{@}$' since '.' is reserved in PLT Redex. There is no
-explicit return statement; rather, the value of the last expression is
-used as the return value. A variable is always indicated by \cfgnt{x}
-and a value by \cfgnt{v}. A value can be a reference in the heap,
-$\cfgnt{r}$, or any of the special values shown
-in~\figref{fig:syntax}(a).  Only type correct programs are given as
-input to the machine.
-
-The state of the Javalite machine, $\cfgnt{s}$, includes the program
-registry, $\mu$, a pair of functions defining the heap
-$\lp\cfgnt{L}\ \cfgnt{R}\rp$, a constraint, $\phi$, defined over
-references in the heap, the environment, $\eta$, for local variables,
-and the continuation $\cfgnt{k}$. The registry never changes so it is
-omitted from the state tuple in the rest of the presentation.  The
-more complex structures, such as the environment and heap, are defined
-as lists that start with empty, \cfgnt{mt}. These lists are treated as
-partial functions so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
-$\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation
-$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
-partial function $\eta^\prime$ that is the same as $\eta$ except that
-the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. The continuation
-$\cfgnt{k}$ indicates where the hole, $\cfgt{*}$, is located, stores
-temporary computation, and keeps track of the next computation. For
-example, the continuation $\lp\cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
-\rightarrow \cfgnt{k}\rp$ indicates that the machine is evaluating the
-expression for the object reference on which the field $\cfgnt{f}$ is
-going to be accessed. Once the field access is complete, the machine
-continues with $\cfgnt{k}$.
 
@@
 heap. References in the graph are immutable. Locations, however, are
-mutated on updates.  Immutability of references means that look-ups in
-the heap are non-recursive and updates do not modify the current path
-condition.
+mutated on updates.
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[scale=0.2]{../figs/simple_heap_scratch.png}
+\end{center}
+\caption{Example Heap (scratch image, not for publication!)}
+\label{fig:exampleHeap}
+\end{figure}
+
+\bah{\figref{fig:exampleHeap} shows an example symbolic heap. References are 
+represented by circles and locations are represented by squares. Arrows leaving
+references correspond to the value sets returned by the $\cfgnt{L}$ function, and 
+arrows leaving the squares correspond to the $\cfgnt{R}$ function.}
 
@@
 the small-step semantics during symbolic execution:
-%\emph{reference partitions}, \emph{null and uninitialized}, \emph{immutability}, \emph{determinism}, and
-%\emph{type consistency}.
+
 \begin{compactdesc}
-%<<<<<<< HEAD
 \item[Reference partitions:] Each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
@@
 two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized,
-%=======
-%\item[Reference partitions] means that a reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
-%  heap} that includes $\cfgnt{r}_\mathit{null}$ (these are created by lazy initialization and are the only references that appear as variables in
-%  constraints); $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
-%  literals} that includes $\cfgnt{r}_\mathit{un}$ (these add structure but do not appear elsewhere); and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
-%  literals} (these appear in environments, expressions, and continuations).
-%\item[Null and Uninitialized] means that every symbolic heap contains 
-%a special location for null ($\cfgnt{l}_\mathit{null}$), and a special
-%location for uninitialized
-%>>>>>>> 49c83f34a0b5afd58adc4b6649b15e2cbc93437c
   ($\cfgnt{l}_\mathit{un}$) with $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
@@
 
-\subsection{Semantics of Javalite}
+\subsection{Semantics}
+
+In this work, symbolic execution semantics are is defined using
+a small-step operational semantics similar to the one presented 
+in~\cite{saints-MS}. The small-step semantics,
+defined as a syntactic machine using a CESK architecture~\cite{Felleisen:1992},
+are modified to perform symbolic execution on a symbolic heap. The
+surface (input) syntax and machine (state) syntax are shown
+in~\figref{fig:syntax}. Terminals are in bold face while non-terminals
+are italicized. Ellipses indicate zero or more repetitions. Tuples
+omit the commas for compactness.
+
+\input{surface-syntax}
+\input{machine-syntax}
+\begin{figure}[t]
+\begin{center}
+\begin{tabular}{c}
+\scalebox{0.9}{\usebox{\boxSurface}} \\
+(a) \\\\
+\scalebox{0.9}{\usebox{\boxMachine}} \\
+(b)
+\end{tabular}
+\end{center}
+\caption{Syntax for Javalite. (a) The Javalite surface syntax. (b) The machine syntax with $\bowtie\ \in \{\wedge,\vee,\Rightarrow\}$.}
+\label{fig:syntax}
+\end{figure}
+
+A program, $\cfgnt{P}$, is a registry of classes, $\mu$, with
+a tuple indicating a class, $\cfgnt{C}$, and a method, $\cfgnt{m}$,
+where execution starts. The only primitive type in Javalite is
+Boolean. For simplicity in presentation, classes have only
+non-primitive fields, and methods have a single
+parameter. Expressions, $\cfgnt{e}$, include statements, and they use
+'$\cfgt{:=}$' to indicate assignment and '$\cfgt{=}$' to indicate
+comparison.  The dot-operator for field access is replaced by
+'$\cfgt{\$}$', and the dot-operator for method invocation is replaced
+by '$\cfgt{@}$' since '.' is reserved in PLT Redex. There is no
+explicit return statement; rather, the value of the last expression is
+used as the return value. A variable is always indicated by \cfgnt{x}
+and a value by \cfgnt{v}. A value can be a reference in the heap,
+$\cfgnt{r}$, or any of the special values shown
+in~\figref{fig:syntax}(a).  Only type correct programs are given as
+input to the machine.
+
+The state of the machine, $\cfgnt{s}$, includes the program
+registry, $\mu$, a pair of functions defining the heap
+$\lp\cfgnt{L}\ \cfgnt{R}\rp$, a constraint, $\phi$, defined over
+references in the heap, the environment, $\eta$, for local variables,
+and the continuation $\cfgnt{k}$. The registry never changes so it is
+omitted from the state tuple in the rest of the presentation.  The
+more complex structures, such as the environment and heap, are defined
+as lists that start with empty, \cfgnt{mt}. These lists are treated as
+partial functions so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
+$\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation
+$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
+partial function $\eta^\prime$ that is the same as $\eta$ except that
+the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. The continuation
+$\cfgnt{k}$ indicates where the hole, $\cfgt{*}$, is located, stores
+temporary computation, and keeps track of the next computation. For
+example, the continuation $\lp\cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
+\rightarrow \cfgnt{k}\rp$ indicates that the machine is evaluating the
+expression for the object reference on which the field $\cfgnt{f}$ is
+going to be accessed. Once the field access is complete, the machine
+continues with $\cfgnt{k}$.
 
@@
 \figref{fig:javalite-common} defines
-the rewrite relations for the portion of the Javalite language
+the rewrite relations for the portion of the language
 semantics that are common to both generalized symbolic execution and
@@
 machine simply halts if no rewrite is enabled.
-\bah{
+
 \input{lazy}
-}
+
 \input{precise-fig}

### 2015-05-08 ase-2015-tex/intro.tex
Some minor rewrites to the introduction, renamed Semantics subsection.

@@
 non-deterministic choice points on the current path in order to
-explore each heap configuration. This approach, however, is
-inefficient because it does not treat heap allocated data as symbolic,
-but instead concretizes all possible heap configurations.
+explore each heap configuration. \bah{This approach, however, is
+inefficient because it initiates a new search path for every possible heap configuration.
+The resulting path growth is exponential in the number of dereferencing operations.}
 
-\bah{The contribution of this work is a method for modeling and solving systems 
-of constraints over a symbolic input heap.} The
+The contribution of this work is a method for modeling and solving systems 
+of constraints over a symbolic input heap.The
 result of which, unlike~\gsetxt{}, is the ability to efficiently generate

### 2015-05-08 ase-2015-tex/summary-heap.tex
Some minor rewrites to the introduction, renamed Semantics subsection.

@@
 
-\bah{\figref{fig:exampleHeap} shows an example symbolic heap. References are 
+\figref{fig:exampleHeap} shows an example symbolic heap. References are 
 represented by circles and locations are represented by squares. Arrows leaving
 references correspond to the value sets returned by the $\cfgnt{L}$ function, and 
-arrows leaving the squares correspond to the $\cfgnt{R}$ function.}
+arrows leaving the squares correspond to the $\cfgnt{R}$ function.
 
@@
 
-\subsection{Semantics}
+\subsection{Symbolic Execution Semantics}
 

### 2015-05-15 ase-2015-tex/approach.tex
Added separate section for preliminaries, a new figure and explanation for the basic concepts of the symbolic heap, and a new subsection for limitations of the symbolic heap.
Added information about test case generation.

@@
-\subsection{Generating and Updating Symbolic Heaps}
+\section{Generating and Updating Symbolic Heaps}
 \label{sec:precise}
@@
 \]
+
+\subsection{Applying Method Invariants}
+Assume-type invariants are achievable by using a simple ITE structure: if(precondition) then testmethod() else failAssume().
+Any paths which which reach the failAssume() method call are ignored.
+Assert-type postconditions are accomplished using the standard Java assert() keyword.
+Failed assertions will cause an uncaught exception which may cause the search to optionally terminate or backtrack.
+
+Application of complex method invariants is facilitated by repOk-style methods as described in~\cite{boyapati2002korat}.
+
+\subsection{Symbolic Input Heap}
+The methods described above are useful for determining the current symbolic heap along an execution path, but they are also easily generalized for to tracking the symbolic input heap.
+For a given execution path, the symbolic input heap represents the constraints defining set of all heaps that would result in that path.
+At the start of program execution the symbolic input heap is unconstrained, admitting the set of all possible heaps.
+As symbolic execution proceeds and the path condition grows, the symbolic input heap becomes more constrained, representing a subset of the space of possible inputs.
+The symbolic input heap can be determined by maintaining a record of all lazy initializations separately from the main symbolic heap.
+Each lazy initialization produces a new reference $r^\prime$ and location $l_x$ which are added to special initial reference and location maps $R_i$ and $L_i$.
+These input heap mappings are updated only by lazy initializations and changes to the path condition, but are not affected by other forms of heap updates, such as new allocations or writes.
+
+\subsection{Heap Preconditions and Postconditions}
+For many types of analysis, such as modular analysis and change impact analysis, it is desirable to determine method preconditions and postconditions.
+Determination of both preconditions and postconditions is facilitated by the symbolic heap.
+The symbolic heap at the final state on an execution path is equivalent to a per-path postcondition, a constraint describing the complete set of output heaps that are possible for that execution path.
+Likewise, the symbolic input heap at a terminal state is the precondition for that path.
+For a self-limiting program, the set of feasible path-terminal symbolic heaps forms the strongest postcondition, and the set of input heaps forms the weakest precondition.
+
+\subsection{Heap Concretization}
+%-what is concretization
+%-Valuations
+%-Each valuation causes exactly one constraint per reference to evaluate to Òtrue"
+While a symbolic heap represents a set of possible heap configurations, it is often useful to be able to extract a single heap instance from that set of possible heaps.
+The process of extracting concrete values from symbolic values is commonly known as concretization.
+The symbolic heap may be concretized by utilizing the solution provided by the SMT solver when it decides the satisfiability of the path condition.
+The SMT solver provides the solution in the form of a valuation, which is an assignment of numerical values to each of the variables in the path condition.
+In the case of the symbolic heap, the numeric values assigned to reference variables can be thought of as the physical memory addresses to which each of the references is pointing.
+
+The symbolic heap is concretized by applying the solution valuation to each of the constraints in every value set in $\cfgnt{L}$.
+The assignments from the solution valuation will cause the constraint equations to evaluate to either true or false.
+By the determinism property of the symbolic heap, for each reference in $L$, exactly one constraint will evaluate to true, while all others will evaluate to false.
+The location associated with that constraint is then selected for the reference to point to in the resulting concrete heap.
+
+\subsection{Test input generation}
+%What is test-case generation?
+%How we use the symbolic input heap to generate test cases.
+%-concretize the symbolic input heap
+A common application for symbolic execution is test-input generation.
+By concretizing the symbolic input heap at any point during program execution, a concrete test input may be generated for the current execution path.
+Since each unique execution path is explored exactly once, it is possible to generate a set of test inputs that covers every unique execution path by concretizing the symbolic input heap at the end of each path.
+For the class of self-limiting programs, this set of test inputs is optimal with regards to the number of cases required to achieve total feasible path coverage.

### 2015-05-15 ase-2015-tex/summary-heap.tex
Added information about test case generation.

@@
 
- \input{javalite-common}
-
-\figref{fig:javalite-common} defines
-the rewrite relations for the portion of the language
+% \input{javalite-common}
+%
+The rewrite relations for the portion of the language
 semantics that are common to both generalized symbolic execution and
-the symbolic heap algorithm. The relation $\rcom$ includes all of these
+the symbolic heap algorithm may be found in \cite{Hillery:2015}. The relation $\rcom$ includes all of these
 rules. Excepting \textrm{N{\footnotesize EW}}, the rules do not update
@@
 
-\input{precise-fig}
+%\input{precise-fig}
 

### 2015-05-15 ase-2015-tex/abstract.tex
Added information about test case generation.
Updated the abstract to mention new features. Moved limitations from conclusion to Symbolic Heaps section.:

--- 2015-03-27 tex/abstract.tex
@@
-A fundamental challenge of using symbolic execution for software
-analysis is the treatment of dynamically allocated data. This paper
-introduces a compact symbolic heap representation based on a field
-sensitive points-to graph with edges annotated with disjunctive
-formulas describing aliasing relationships, along with a set of
-rewrite rules that describe the initialization, dereferencing, and
-update to fields in the symbolic heaps. The symbolic heap supports
-arbitrary recursive data structures and captures all possible heaps
-that follow a common control flow path up to the point of
-execution. An evaluation of a proof-of-concept implementation in the
-Java Pathfinder framework is presented to demonstrate the
-computational feasibility of the approach over several classical
-symbolic execution benchmarks.
+A fundamental challenge of using symbolic execution for software analysis is the treatment of dynamically allocated data.
+Existing techniques either underapproximate the space of possible inputs or are computationally infeasible.
+For example, dynamic symbolic execution (DSE) handles symbolic dereferencing by substituting in a value from a valid concrete execution.
+Generalized symbolic execution (GSE) initiates a new search path for every possible aliasing configuration.
+This paper introduces a method for de-referencing and manipulating values in a true block-box symbolic input heap that overcomes the limitations of previous methods.
+The symbolic heap supports arbitrary recursive data structures and captures all possible heaps that follow a common control flow path up to the point of execution.
+Computation of complex preconditions and postconditions is supported, as well as automatic generation of test inputs.
+An evaluation of a proof-of-concept implementation in the Java Pathfinder framework is presented to demonstrate the computational feasibility of the approach over several classical symbolic execution benchmarks.
 

### 2015-05-15 ase-2015-tex/approach.tex
Updated the abstract to mention new features. Moved limitations from conclusion to Symbolic Heaps section.:

@@
 
-Application of complex method invariants is facilitated by repOk-style methods as described in~\cite{boyapati2002korat}.
+Application of complex method invariants is facilitated by $\mathtt{repOk}$-style methods as described in~\cite{boyapati2002korat}.
 
@@
 For the class of self-limiting programs, this set of test inputs is optimal with regards to the number of cases required to achieve total feasible path coverage.
+
+\subsection{Limitations}
+This paper presents a symbolic heap that is both sound and complete with respect to the properties verifiable through symbolic execution.
+However, when the symbolic heap is used in conjunction with any analysis method, it is subject the limitations inherent to the underlying technique.
+For example, for programs that do not exhibit self-limiting behavior, as a practical matter symbolic execution generally requires some sort of bounds to limit infinite loops and recursion.
+This means that some sort of constraint will invariably be imposed by the symbolic execution engine, impacting the heap as it would any other symbolic value.
+In this case, the advantage of our method is that these constraints may be freely chosen to suit the purposes of the analysis at hand, rather than being imposed by a limitation of the heap representation.

### 2015-05-15 ase-2015-tex/conclusion.tex
Updated the abstract to mention new features. Moved limitations from conclusion to Symbolic Heaps section.:

--- 2015-02-07 cav-2015-tex/conclusion.tex
@@
 
-Although our approach is inspired by the work in the static analysis
-domain, the heap representations used by those techniques do not lend
-themselves to symbolic execution since they rely on approximations,
-they are inflexible in what types of relations can be expressed, and
-they rely on rewriting of constraints.  In this work, we present a
+In this work, we present a
 heap representation for symbolic execution that maintains exactness,

### 2015-05-15 ase-2015-tex/intro.tex
Updated the abstract to mention new features. Moved limitations from conclusion to Symbolic Heaps section.:

@@
 non-deterministic choice points on the current path in order to
-explore each heap configuration. \bah{This approach, however, is
+explore each heap configuration. This approach, however, is
 inefficient because it initiates a new search path for every possible heap configuration.
-The resulting path growth is exponential in the number of dereferencing operations.}
+The resulting path growth is exponential in the number of dereferencing operations.
 
@@
 that brings together the best features of previous work while removing
-the limitations of that same work. Although it draws inspiration from
-abstract interpretation by defining a symbolic heap,
+the limitations of that same work. The symbolic heap has the following 
+properties:
 \begin{compactitem}
-  \item it is an exact representation, without over- or under-approximation;
-  \item it imposes no restrictions on the set of heaps that can be defined;
-  \item it does not require the creation of an initial set of input heaps;
-  \item it is not tied to specific constraint solver theories, e.g., arrays; and
-  \item it does not require global constraint rewriting for on-the-fly updates.
+  \item constraints are neither over- or under-approximated;
+  \item it does not restrict the set of heaps that can be defined;
+  \item it does not require explicit construction of heap inputs;
+  \item automatically computes path pre- and postconditions;
+  \item generates path-coverage-optimal sets of test input heaps;
+  \item it supports complex user-defined heap structure invariants 
 \end{compactitem}
-These several properties set this work apart from other related works.
 

### 2015-05-16 ase-2015-tex/approach.tex
Improved the section on applying assertions.

@@
 
-\subsection{Applying Method Invariants}
-Assume-type invariants are achievable by using a simple ITE structure: if(precondition) then testmethod() else failAssume().
-Any paths which which reach the failAssume() method call are ignored.
-Assert-type postconditions are accomplished using the standard Java assert() keyword.
-Failed assertions will cause an uncaught exception which may cause the search to optionally terminate or backtrack.
+\subsection{Applying Assertions}
+In symbolic execution, a typical program-verification test setup follows a three-step sequence: 1) assume a precondition, 2) analyze the method under test, and 3) assert a postcondition.
+The black-box nature of the symbolic input heap enables complex assertions to be applied to heap-manipulating programs directly in the native programming environment, without special annotations or instrumentastion predicates to guide the solver.
+The Java benchmark methods in~\secref{sec:evaluation} all follow the same basic structure, shown in \figref{fig:testcode}.
+Assume-type preconditions are implemented by using a simple if-then-else structure.
+Paths that pass the precondition check go on to execute the test method, while paths fail will reach the preconditionFalse() method, and may be discarded in a post processing step.
+Assert-type postconditions are accomplished using the standard Java $\cfgt{assert}$ keyword.
+Failed assertions trigger an exception which causes the analysis to optionally terminate or backtrack.
+Application of complex assertions is facilitated by $\mathtt{repOk}$-style methods as described in~\cite{boyapati2002korat}.
 
-Application of complex method invariants is facilitated by $\mathtt{repOk}$-style methods as described in~\cite{boyapati2002korat}.
+\lstset{
+language=Java,
+%float,
+%caption= {Standard Test Setup}
+morekeywords=[1]{assert}
+}
+\begin{figure}
+\begin{lstlisting}[]
+if( precondition() ){
+	testMethod();
+	assert postcondition();
+}else{
+	preconditionFalse();
+}
+\end{lstlisting}
+\caption{Standard Benchmark Framework}
+\label{fig:testcode}
+\end{figure}
 
 \subsection{Symbolic Input Heap}
-The methods described above are useful for determining the current symbolic heap along an execution path, but they are also easily generalized for to tracking the symbolic input heap.
+The symbolic heap semantics described in this paper are useful for determining the current symbolic heap along an execution path, but they are also easily generalized to the symbolic input heap.
 For a given execution path, the symbolic input heap represents the constraints defining set of all heaps that would result in that path.
@@
 %-Each valuation causes exactly one constraint per reference to evaluate to Òtrue"
-While a symbolic heap represents a set of possible heap configurations, it is often useful to be able to extract a single heap instance from that set of possible heaps.
-The process of extracting concrete values from symbolic values is commonly known as concretization.
-The symbolic heap may be concretized by utilizing the solution provided by the SMT solver when it decides the satisfiability of the path condition.
-The SMT solver provides the solution in the form of a valuation, which is an assignment of numerical values to each of the variables in the path condition.
-In the case of the symbolic heap, the numeric values assigned to reference variables can be thought of as the physical memory addresses to which each of the references is pointing.
+When an SMT solver decides that a path condition is satisfiable, it provides a solution in the form of a valuation, which is an assignment of numerical values to each of the variables in the path condition.
+In the case of the symbolic heap, the reference variable valuations can be thought of as the physical memory addresses to which each of the references is pointing.
+This information can be used to perform a concretization of the symbolic heap, reducing it to a single concrete member of the set of heaps it represents.
 
-The symbolic heap is concretized by applying the solution valuation to each of the constraints in every value set in $\cfgnt{L}$.
+The symbolic heap is concretized by using the valuation to assign values to the variables of the constraints in the value sets in $\cfgnt{L}$.
 The assignments from the solution valuation will cause the constraint equations to evaluate to either true or false.

### 2015-05-16 ase-2015-tex/approach.tex
started replacing other wordings with path condition, reworked value set function explanation paragraph

--- 2015-05-15 ase-2015-tex/approach.tex
@@
 
-The value set computation is local: it only considers constraint
-locations on the reference $\cfgnt{r}$. Further, it only includes
-constraints that are feasible under the current path condition
-$\phi_g$. It also ensures that the access path is valid. There is a
-constraint $\phi$ from the base reference $r$ and a given
-location. Once a location $l$ is selected its field $\cfgnt{f}$ is
-accessed to get another reference $r^\prime$, and from that reference
-there is a set of locations each with a constraint. The first
-constraint $\phi$ from the base reference plus this second constraint
-to the actual location of the field $\phi^\prime$ comprise the access
-path. For each member of the value set, these constraints together
-with the global path constraint must be satisfied on some aliasing
-assignment. % \nsr{neha: this para needs work -- flow and content}
+For a reference $\cfgnt{r}$ and field $\cfgnt{f}$, the value set function computes 
+the set of locations that the field could dereference to, paired with a local and valid access path constraint
+that is feasible under the current path condition $\phi_g$.
+The access path constraint is the union of two local constraints: 
+the constraint $\phi$ from dereferencing $\cfgnt{r}$ to location $\cfgnt{l}$, 
+and the constraint $\phi^\prime$ from dereferencing the field $\cfgnt{f}$ of the location $\cfgnt{l}$ to the actual location of the field, $\cfgnt{l}^\prime$. 
+This access path constraint, paired with location $\cfgnt{l}^\prime$, is a member of the value set only if its union with the path condition is satisfiable, ensuring that the access path is valid and feasible under the path condition.
+ % \nsr{neha: this para needs work -- flow and content tao: worked on the flow}
 

### 2015-05-16 ase-2015-tex/summary-heap.tex
Added new intro figure.
started replacing other wordings with path condition, reworked value set function explanation paragraph

@@
 \begin{center}
-\includegraphics[scale=0.2]{../figs/simple_heap_scratch.png}
+\includegraphics[scale=0.5]{../figs/simple_heap_scratch.pdf}
 \end{center}
-\caption{Example Heap (scratch image, not for publication!)}
+\caption{Example Symbolic Heap}
 \label{fig:exampleHeap}
@@
 registry, $\mu$, a pair of functions defining the heap
-$\lp\cfgnt{L}\ \cfgnt{R}\rp$, a constraint, $\phi$, defined over
+$\lp\cfgnt{L}\ \cfgnt{R}\rp$, the path condition, $\phi$, a constraint defined over
 references in the heap, the environment, $\eta$, for local variables,

### 2015-05-16 ase-2015-tex/approach.tex
more global path constraint -> path condition

@@
 with new aliasing conditions and those that are feasible with the
-current path constraint are retained.
+current path condition are retained.
 
@@
 $\cfgnt{r}_0$ \emph{does not} point to those locations under any
-constraint. We use the three sets of constraints to update the current
-global heap constraint $\phi_g$ and create a new global heap
-constraint $\phi_g^\prime$. We add to $\phi_g$ the disjunction of the
+constraint. We use the three sets of constraints to create a new path condition \phi_g^\prime$
+as an update of the current path condition $\phi_g$. We add to $\phi_g$ the disjunction of the
 constraints in $\Phi_\alpha$ to indicate that if any of the

### 2015-05-16 ase-2015-tex/summary-heap.tex
defined r_null, r_un, fresh_l, isInit(), and mathcal{L}

@@
   ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
-  literals} %(these appear in environments, expressions, and continuations).
+  literals}. %(these appear in environments, expressions, and continuations).
+  Only input heap references appear in constraints to express potential aliasing.
+  Auxiliary literals and stack references are used to define additional structure in the bipartite graph but only stack references can appear in environments, expressions, or continuations.
 \item[Null and Uninitialized:] Every symbolic heap contains 
 two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized,
-  ($\cfgnt{l}_\mathit{un}$) with $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
+  ($\cfgnt{l}_\mathit{un}$)  with corresponding references 
+  $\cfgnt{r}_\mathit{null}$ and $\cfgnt{r}_\mathit{un} 
+  where $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
   \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
@@
         location map points a new stack reference to that new object.
-        Note that references for objects from the new-expression are
+        New heap locations returned from \mathrm{fresh}_l are monotonically
+        increasing.
+        Also note that references for objects from the new-expression are
         auxiliary literals, so they do not appear in any constraint in

### 2015-05-16 ase-2015-tex/summary-heap.tex
Miscellaneous improvements.

--- 2015-05-16 ase-2015-tex/summary-heap.tex
@@
 environment, $\cfgnt{L}$ and $\cfgnt{R}$ are treated as partial
-functions where $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the set
-of constraint-location pairs in the heap associated with the given
-reference, and $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the
+functions. $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the set
+of constraint-location pairs (value set) in the heap associated with the given
+reference. The constraint associated with each location is a guard
+representing the conditions under which the associated reference
+maps to the given location. By definition, any location appears 
+at most once in any given value set. Unions of value sets containing
+the same location are resolved by forming a disjunction of the constraints
+from each set. $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the
 reference associated with the given location-field pair in the

### 2015-05-16 ase-2015-tex/approach.tex

@@
 In~\figref{fig:symInit}, given the uninitialized set $\Lambda$ for
-field $f$, the $\mathit{min}_l$ function returns
+field $f$, the $\mathrm{min}_l$ function returns
 $(\phi_x\ \cfgnt{l}_x)$ based on a lexicographical ordering of
@@
 deterministic.  The set $\rho$ contains reference-location pairs that
-represent potential aliases. There are four cases encoded in the
+represent potential aliases, where $\mathrm{isInit}\lp\rp$ ensures that the references are initialized. 
+There are four cases encoded in the
 symbolic heap: (i) $\theta_\mathit{null}$ represents the condition

### 2015-05-16 ase-2015-tex/st-def.tex
Reformatted figures to not be stuck in columns.

@@
 $\phi$ and retaining location-constraint pairs that are satisfiable
-after this strengthening with the inclusion of the global heap
-constraint $\phi_g$:
+after this strengthening with the inclusion of the path condition $\phi_g$:
 \[
 \begin{array}{rcl} 
-\mathbb{ST}(\cfgnt{L},\cfgnt{r},\phi,\phi_g) & = & \{ (\phi\wedge\phi^\prime\ \cfgnt{l}^\prime) \mid (\phi^\prime\ \cfgnt{l}^\prime)\in \cfgnt{L}(\cfgnt{r})\wedge\mathbb{S}(\phi\wedge\phi^\prime\wedge\phi_g) \}
+\mathbb{ST}(\cfgnt{L},\cfgnt{r},\phi,\phi_g) & = & \{ (\phi\wedge\phi^\prime\ \cfgnt{l}^\prime) \mid (\phi^\prime\ \cfgnt{l}^\prime)\in \cfgnt{L}(\cfgnt{r})\wedge \\ & & 
+\ \ \mathbb{S}(\phi\wedge\phi^\prime\wedge\phi_g) \}
 \end{array}

### 2015-05-16 ase-2015-tex/bisimulation.tex
Added additional explanation to the evaluation section.
defined r_null, r_un, fresh_l, isInit(), and mathcal{L}
elaboration on reference partitions, wording tweaks, removing Javalite

--- 2015-02-07 cav-2015-tex/bisimulation.tex
@@
 completeness of the symbolic heap approach with respect to Generalized
-Symbolic Execution (\gsetxt{}). Intuitively, any properties proven with~\gsetxt{}
-can also be proved using the symbolic heap algorithm.~\gsetxt{} concretizes
-the possible heap configurations along with various aliasing
-relationships when an uninitialized field is dereferenced. The rules
-for initializing and updating the fields in the Javalite semantics for
-\gsetxt{} are shown in the~\appref{app:gse}.
+Symbolic Execution (\gsetxt{}). Intuitively, any properties proven
+with~\gsetxt{} can also be proved using the symbolic heap
+algorithm.~\gsetxt{} concretizes the possible heap configurations
+along with various aliasing relationships when an uninitialized field
+is dereferenced. The rules for initializing and updating the fields in
+the machine's semantics for \gsetxt{} as well as
+the the complete set of rules for the symbolic heap algorithm can
+be found in ~\cite{Hillery:2015}.
 
@@
 \label{def:homomorphism}
-A \textbf{homomorphism} given the universe of field names $\mathcal{F}$ is 
+A \textbf{homomorphism}, given the universe of field indices $\mathcal{F}$ and the universe of locations $\mathcal{L}$, is 
 $$
@@
 \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}\ ( \exists \phi_\alpha\ (\exists \phi_\beta\ ( \\ 
-\ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow 
-(\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ 
+\ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow \\
+\ \ \ \ \ \ \ \ (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ 
  )) ) ) ) )
@@
 state of a given program as there is single initial state, $P_o =
-\{p_o\}$, in any valid Javalite program. The initial state for $\rsym$ is
+\{p_o\}$, in any valid program. The initial state for $\rsym$ is
 then defined as $q_o = p_o$ so $P_o \sqsubset q_o$ trivially holds.

### 2015-05-16 ase-2015-tex/summary-heap.tex
elaboration on reference partitions, wording tweaks, removing Javalite

--- 2015-05-16 ase-2015-tex/summary-heap.tex
@@
 \end{center}
-\caption{Syntax for Javalite. (a) The Javalite surface syntax. (b) The machine syntax with $\bowtie\ \in \{\wedge,\vee,\Rightarrow\}$.}
+\caption{ (a) The surface syntax. (b) The machine syntax with $\bowtie\ \in \{\wedge,\vee,\Rightarrow\}$.}
 \label{fig:syntax}
@@
 a tuple indicating a class, $\cfgnt{C}$, and a method, $\cfgnt{m}$,
-where execution starts. The only primitive type in Javalite is
-Boolean. For simplicity in presentation, classes have only
-non-primitive fields, and methods have a single
+where execution starts. For simplicity in presentation, booleans are the only primitive type, 
+classes have only non-primitive fields, and methods have a single
 parameter. Expressions, $\cfgnt{e}$, include statements, and they use

### 2015-05-16 ase-2015-tex/summary-heap.tex
explained how e relates to continuation hole *

@@
 registry, $\mu$, a pair of functions defining the heap
-$\lp\cfgnt{L}\ \cfgnt{R}\rp$, the path condition, $\phi$, a constraint defined over
+$\lp\cfgnt{L}\ \cfgnt{R}\rp$, represented in the syntactic machine as singly linked lists of mappings, 
+the path condition, $\phi$, a constraint defined over
 references in the heap, the environment, $\eta$, for local variables,
@@
 the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. The continuation
-$\cfgnt{k}$ indicates where the hole, $\cfgt{*}$, is located, stores
-temporary computation, and keeps track of the next computation. For
+$\cfgnt{k}$ indicates with $\cfgnt{*} where the expression $\cfgnt{e}$ came from, stores
+temporary computation, and keeps track of the next continuation. For
 example, the continuation $\lp\cfgt{*}\ \cfgt{\$}\ \cfgnt{f}

### 2015-05-16 ase-2015-tex/summary-heap.tex
Updated the prelimiaries section.

--- 2015-05-16 ase-2015-tex/summary-heap.tex
@@
 
+In symbolic execution, the program state is represented symbolically, as a function of the program’s inputs.
+That is to say, the values stored in the memory locations accessed by the program are represented as expressions where the only free variables are the program input parameters.
+Determining the symbolic state is relatively simple for programs that perform linear manipulations of numeric input parameters.
+However, the task becomes more challenging for programs that accept references as inputs, in part because it is not obvious exactly how many program input parameters there are.
+For example, consider the case of dereferencing an input reference that points to an object that itself contains multiple fields.
+Should each of those field values be included as program input parameters?
+What if some of the fields contain references?
+It would seem as if dereferencing symbolic input references opens the door to a potentially unbounded number of parameters.
+
+%Our solution treats the heap as a hidden input parameter to every program.
+%expressed completely in terms of a black-box symbolic input heap
+%and the input reference parameters.
 Our symbolic heap is a field sensitive points-to graph with edges

### 2015-05-16 ase-2015-tex/summary-heap.tex
Fixed unmatching math mode scopes ($)

@@
   ($\cfgnt{l}_\mathit{un}$)  with corresponding references 
-  $\cfgnt{r}_\mathit{null}$ and $\cfgnt{r}_\mathit{un} 
+  $\cfgnt{r}_\mathit{null}$ and $\cfgnt{r}_\mathit{un}$ 
   where $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
@@
 the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. The continuation
-$\cfgnt{k}$ indicates with $\cfgnt{*} where the expression $\cfgnt{e}$ came from, stores
+$\cfgnt{k}$ indicates with $\cfgnt{*}$ where the expression $\cfgnt{e}$ came from, stores
 temporary computation, and keeps track of the next continuation. For
@@
         location map points a new stack reference to that new object.
-        New heap locations returned from \mathrm{fresh}_l are monotonically
+        New heap locations returned from $\mathrm{fresh}_l$ are monotonically
         increasing.

### 2015-05-16 ase-2015-tex/summary-heap.tex
Some more tweaking to the prelimiaries, and intro.

--- 2015-05-16 ase-2015-tex/summary-heap.tex
@@
 That is to say, the values stored in the memory locations accessed by the program are represented as expressions where the only free variables are the program input parameters.
-Determining the symbolic state is relatively simple for programs that perform linear manipulations of numeric input parameters.
+For programs accepting references as input parameters, the symbolic input heap exists as an additional, implicit input parameter.
+Symbolic reference values are expressions formed entirely in terms of the input reference parameters and the symbolic input heap.
+
+%Determining the symbolic state is relatively simple for programs that perform linear manipulations of numeric input parameters.
 However, the task becomes more challenging for programs that accept references as inputs, in part because it is not obvious exactly how many program input parameters there are.
@@
 %and the input reference parameters.
-Our symbolic heap is a field sensitive points-to graph with edges
+The collective state of all symbolic program reference values
+is known as the \emph{symbolic heap}. Our symbolic heap 
+is a field sensitive points-to graph with edges
 annotated with disjunctive formulas describing aliasing

### 2015-05-16 ase-2015-tex/summary-heap.tex
removed duplicate discussion of L and R as lists of mappings

--- 2015-05-16 ase-2015-tex/summary-heap.tex
@@
 the same location are resolved by forming a disjunction of the constraints
-from each set. $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the
+from each set. $\cfgnt{R}(\cfgnt{l}, \cfgnt{f}) = \cfgnt{r}$ is the
 reference associated with the given location-field pair in the
@@
 registry, $\mu$, a pair of functions defining the heap
-$\lp\cfgnt{L}\ \cfgnt{R}\rp$, represented in the syntactic machine as singly linked lists of mappings, 
+$\lp\cfgnt{L}\ \cfgnt{R}\rp$, 
 the path condition, $\phi$, a constraint defined over
@@
 more complex structures, such as the environment and heap, are defined
-as lists that start with empty, \cfgnt{mt}. These lists are treated as
+as singly linked lists of mappings that start with empty, \cfgnt{mt}. These lists are treated as
 partial functions so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference

### 2015-08-29 vmcai-2016-tex/approach.tex
Started new folder for VMCAI submission.

--- 2015-05-16 ase-2015-tex/approach.tex
@@
 for $\cfgnt{l}_f$ are initialized to $\cfgnt{r}_\mathit{un}$.
-
-%\begin{figure*}[t]
-%\begin{center}
-%\begin{tabular}[c]{c|c|c}
-%\begin{tabular}[c]{c c}
-%\scalebox{0.81}{\input{origHeap.pdf_t}}&  \\
-%\end{tabular} &
-%\begin{tabular}[c]{c}
-%\scalebox{0.81}{\input{summarizeXHeap.pdf_t}} \\
-%\end{tabular} &
-%\begin{tabular}[c]{c}
-%\scalebox{0.81}{\input{summarizeYHeap.pdf_t}} \\
-%\end{tabular}\\
-%(a) & (b) & (c)\\
-%\end{tabular}
-%\begin{tabular}[c]{c}
-%\begin{tabular}[c]{c c}
-%\hline
-%\begin{tabular}[c]{l}
-%$\rho := \{ (\cfgnt{r}_1^i\ \cfgnt{l}_1) \}$ \\
-%$\theta_\mathit{null} := \{ ( \cfgnt{r}_2^i = \cfgnt{r}_\mathit{null}\ \cfgnt{l}_\mathit{null}) \}$\\
-%$\theta_\mathit{new} := \{ ( \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_1^i\ \cfgnt{l}_2) \}$\\
-%$\theta_\mathit{alias} := \{ ( \cfgnt{r}_1^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i = \cfgnt{r}_1^i\ \cfgnt{l}_1) \}$\\
-%$\theta_\mathit{orig} := \{ \}$ \\
-%\end{tabular} &
-%\begin{tabular}[c]{l}
-%$\phi_{\mathit{1a}} := \cfgnt{r}_1^i = \cfgnt{r}_\mathit{null} $ \\
-%$\phi_{\mathit{1b}} := \cfgnt{r}_1^i \neq \cfgnt{r}_\mathit{null} $  \\
-%$\phi_{\mathit{2a}} := \cfgnt{r}_2^i = \cfgnt{r}_\mathit{null}$ \\
-%$\phi_{\mathit{2b}} := \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i \neq \cfgnt{r}_1^i$ \\
-%$\phi_{\mathit{2c}} :=  \cfgnt{r}_2^i \neq \cfgnt{r}_\mathit{null} \wedge \cfgnt{r}_2^i = \cfgnt{r}_1^i $ \\
-%\end{tabular}\\
-%\end{tabular} \\
-%(d)
-%\end{tabular}
-%\end{center}
-%\caption{An example that initializes $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ and $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$.
-(a) Initial heap structure.
-(b) After $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{x}\rp$ is initialized.
-(c) After $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ is initialized.
-(d) Sets in the summarize rule and constraints on the edges.}
-%\label{fig:initHeap}
-%\end{figure*}
 
@@
 $\cfgnt{r}_0$ \emph{does not} point to those locations under any
-constraint. We use the three sets of constraints to create a new path condition \phi_g^\prime$
+constraint. We use the three sets of constraints to create a new path condition $\phi_g^\prime$
 as an update of the current path condition $\phi_g$. We add to $\phi_g$ the disjunction of the
@@
 \]
-
-\subsection{Applying Assertions}
-In symbolic execution, a typical program-verification test setup follows a three-step sequence: 1) assume a precondition, 2) analyze the method under test, and 3) assert a postcondition.
-The black-box nature of the symbolic input heap enables complex assertions to be applied to heap-manipulating programs directly in the native programming environment, without special annotations or instrumentastion predicates to guide the solver.
-The Java benchmark methods in~\secref{sec:evaluation} all follow the same basic structure, shown in \figref{fig:testcode}.
-Assume-type preconditions are implemented by using a simple if-then-else structure.
-Paths that pass the precondition check go on to execute the test method, while paths fail will reach the preconditionFalse() method, and may be discarded in a post processing step.
-Assert-type postconditions are accomplished using the standard Java $\cfgt{assert}$ keyword.
-Failed assertions trigger an exception which causes the analysis to optionally terminate or backtrack.
-Application of complex assertions is facilitated by $\mathtt{repOk}$-style methods as described in~\cite{boyapati2002korat}.
-
-\lstset{
-language=Java,
-%float,
-%caption= {Standard Test Setup}
-morekeywords=[1]{assert}
-}
-\begin{figure}
-\begin{lstlisting}[]
-if( precondition() ){
-	testMethod();
-	assert postcondition();
-}else{
-	preconditionFalse();
-}
-\end{lstlisting}
-\caption{Standard Benchmark Framework}
-\label{fig:testcode}
-\end{figure}
-
-\subsection{Symbolic Input Heap}
-The symbolic heap semantics described in this paper are useful for determining the current symbolic heap along an execution path, but they are also easily generalized to the symbolic input heap.
-For a given execution path, the symbolic input heap represents the constraints defining set of all heaps that would result in that path.
-At the start of program execution the symbolic input heap is unconstrained, admitting the set of all possible heaps.
-As symbolic execution proceeds and the path condition grows, the symbolic input heap becomes more constrained, representing a subset of the space of possible inputs.
-The symbolic input heap can be determined by maintaining a record of all lazy initializations separately from the main symbolic heap.
-Each lazy initialization produces a new reference $r^\prime$ and location $l_x$ which are added to special initial reference and location maps $R_i$ and $L_i$.
-These input heap mappings are updated only by lazy initializations and changes to the path condition, but are not affected by other forms of heap updates, such as new allocations or writes.
-
-\subsection{Heap Preconditions and Postconditions}
-For many types of analysis, such as modular analysis and change impact analysis, it is desirable to determine method preconditions and postconditions.
-Determination of both preconditions and postconditions is facilitated by the symbolic heap.
-The symbolic heap at the final state on an execution path is equivalent to a per-path postcondition, a constraint describing the complete set of output heaps that are possible for that execution path.
-Likewise, the symbolic input heap at a terminal state is the precondition for that path.
-For a self-limiting program, the set of feasible path-terminal symbolic heaps forms the strongest postcondition, and the set of input heaps forms the weakest precondition.
-
-\subsection{Heap Concretization}
-%-what is concretization
-%-Valuations
-%-Each valuation causes exactly one constraint per reference to evaluate to Òtrue"
-When an SMT solver decides that a path condition is satisfiable, it provides a solution in the form of a valuation, which is an assignment of numerical values to each of the variables in the path condition.
-In the case of the symbolic heap, the reference variable valuations can be thought of as the physical memory addresses to which each of the references is pointing.
-This information can be used to perform a concretization of the symbolic heap, reducing it to a single concrete member of the set of heaps it represents.
-
-The symbolic heap is concretized by using the valuation to assign values to the variables of the constraints in the value sets in $\cfgnt{L}$.
-The assignments from the solution valuation will cause the constraint equations to evaluate to either true or false.
-By the determinism property of the symbolic heap, for each reference in $L$, exactly one constraint will evaluate to true, while all others will evaluate to false.
-The location associated with that constraint is then selected for the reference to point to in the resulting concrete heap.
-
-\subsection{Test input generation}
-%What is test-case generation?
-%How we use the symbolic input heap to generate test cases.
-%-concretize the symbolic input heap
-A common application for symbolic execution is test-input generation.
-By concretizing the symbolic input heap at any point during program execution, a concrete test input may be generated for the current execution path.
-Since each unique execution path is explored exactly once, it is possible to generate a set of test inputs that covers every unique execution path by concretizing the symbolic input heap at the end of each path.
-For the class of self-limiting programs, this set of test inputs is optimal with regards to the number of cases required to achieve total feasible path coverage.
-
-\subsection{Limitations}
-This paper presents a symbolic heap that is both sound and complete with respect to the properties verifiable through symbolic execution.
-However, when the symbolic heap is used in conjunction with any analysis method, it is subject the limitations inherent to the underlying technique.
-For example, for programs that do not exhibit self-limiting behavior, as a practical matter symbolic execution generally requires some sort of bounds to limit infinite loops and recursion.
-This means that some sort of constraint will invariably be imposed by the symbolic execution engine, impacting the heap as it would any other symbolic value.
-In this case, the advantage of our method is that these constraints may be freely chosen to suit the purposes of the analysis at hand, rather than being imposed by a limitation of the heap representation.

### 2015-08-29 vmcai-2016-tex/intro.tex
Started new folder for VMCAI submission.

--- 2015-05-15 ase-2015-tex/intro.tex
@@
 In recent years symbolic execution has provided the basis for various
-software testing and analysis techniques. Symbolic execution explores
-the program by treating input values as symbolic, and for each
-explored path, it computes a set of feasible constraints on the
-symbolic inputs to create a \emph{path condition}. Path conditions
-computed by symbolic execution characterize the observed program
-execution behaviors and have been used as an enabling technology for
-various applications, e.g., regression
+software testing and analysis techniques, e.g., regression
 analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
@@
 
-The path conditions computed by symbolic execution have two important
-features: 1) they characterize the set of feasible execution paths,
-i.e., infeasible paths are omitted, and 2) each path condition encodes
-the set of concrete program inputs that would cause execution to
-follow the same control flow path. Because path conditions are encoded
-as constraints over program inputs, the reasoning capabilities of
-symbolic execution are limited by the underlying constraint
-solver. Recent work has explored the strengths and limitations of
+Recent work has explored the strengths and limitations of
 tools which leverage constraint solvers, e.g., concolic execution,
@@
 
-The most direct approach to address these challenges is to approximate
-the results of a symbolic deference by substituting in a valid
-concrete value, as is done in dynamic symbolic execution
-(\dsetxt{})~\cite{Godefroid:POPL07,Godefroid:2005,Sen:2005,Tillmann:2008}. These
-approaches partition the universe of heaps in the symbolic
-representation but often under-approximate the partitions or require
-array theories in the constraint
-solver~\cite{Chen:2013,Elkarablieh:2009}. A more effective approach is
-to partition the reachable heaps by using value summary
+A promising approach to this problem has been to
+to partition the reachable heaps by using \emph{symbolic heap}
 representations, where multiple values for a reference may be
 represented along a single execution
-path~\cite{Dillig:2011,Elkarablieh:2009,Sen:2014,Torlak:2014,Xie:2005,Yorsh:2008}. Systems
-using these representations perform analyses that are more complete
-than standard~\dsetxt{} methods, but their associated dereferencing
-operations require placing further restrictions on the input heap,
-such as limiting the number of nodes~\cite{Elkarablieh:2009}, the
-nature of aliasing relationships~\cite{Babic:2007,Xie:2005}, or the
-the use of recursive data structures~\cite{Dillig:2011}.
+path~\cite{Dillig:2011,Elkarablieh:2009,Sen:2014,Torlak:2014,Xie:2005,Yorsh:2008}.
+However, it remains an open question whether or not these methods can be used to exactly model all possible program behaviors in the case of an arbitrary input.
 
-An alternative approach which does not under-approximate the heap is
-Generalized Symbolic Execution
-(\gsetxt{})~\cite{Cadar:2008,KiasanKunit,GSE03,Rosner:2015}.  On symbolic
-dereferencing operations,~\gsetxt{} partitions the input space between the
-various possible aliasing configurations on-the-fly and also creates
-non-deterministic choice points on the current path in order to
-explore each heap configuration. This approach, however, is
-inefficient because it initiates a new search path for every possible heap configuration.
-The resulting path growth is exponential in the number of dereferencing operations.
-
-The contribution of this work is a method for modeling and solving systems 
-of constraints over a symbolic input heap.The
-result of which, unlike~\gsetxt{}, is the ability to efficiently generate
-and update \emph{symbolic heaps} to produce a single path constraint
-that is sound and complete up to the point of execution. This is
-accomplished by representing the symbolic heap with a field sensitive
-points-to graph with edges annotated with disjunctive formulas
-describing aliasing relationships. Where~\gsetxt{} branches the heap at every
-de-reference, the symbolic heap in this work splits only at reference
-comparison operations or field operations that may throw exceptions.
-
-The correctness of the symbolic heap and its on-the-fly update rules
-for symbolic execution is shown by proving the existence of a
-bisimulation between symbolic heap states and~\gsetxt{} states. From that
-result comes the soundness and completeness of the path constraint up
-to the point of execution.  The efficiency of the representation is
-established with an exploratory empirical evaluation within the Java
-PathFinder framework over a classical set of symbolic execution
-benchmarks. The evaluation demonstrates how the symbolic heap scales
-compared to state-of-art~\gsetxt{} algorithms.
-
-This new symbolic heap and update rules for symbolic execution is a
-novel approach for de-referencing and updating heap allocated data
-that brings together the best features of previous work while removing
-the limitations of that same work. The symbolic heap has the following 
-properties:
-\begin{compactitem}
-  \item constraints are neither over- or under-approximated;
-  \item it does not restrict the set of heaps that can be defined;
-  \item it does not require explicit construction of heap inputs;
-  \item automatically computes path pre- and postconditions;
-  \item generates path-coverage-optimal sets of test input heaps;
-  \item it supports complex user-defined heap structure invariants 
-\end{compactitem}
+The contribution of this work is to build on these previous efforts, by demonstrating how to dereference pointers in an unknown symbolic input heap, thereby proving that value-summary representations are sound and complete with respect to properties provable by symbolic execution.
+A proof-of-concept implementation also demonstrates the efficiency of value-summary representations, as compared to the previous best-known exact analysis method.
 

### 2015-08-29 vmcai-2016-tex/summary-heap.tex
Started new folder for VMCAI submission.

--- 2015-05-16 ase-2015-tex/summary-heap.tex
@@
 \subsection{Symbolic Heap}
-
-In symbolic execution, the program state is represented symbolically, as a function of the program’s inputs.
-That is to say, the values stored in the memory locations accessed by the program are represented as expressions where the only free variables are the program input parameters.
-For programs accepting references as input parameters, the symbolic input heap exists as an additional, implicit input parameter.
-Symbolic reference values are expressions formed entirely in terms of the input reference parameters and the symbolic input heap.
 
@@
 
-%\sjp{Up to now, no discussion of lazy initialization - what it is or
-%  how it is being used.}  \nsr{A key insight to the summary heap is
-%  that although many auxiliary or stack literals are created during
-%  symbolic execution with lazy initialization, only input heap
-%  references appear in the constraints expressing potential aliasing
-%  relationships.}
-A solver is used to reason over the aliasing relationships, and a
-satisfying assignment uniquely identifies the set of aliasing
-relationships that are representative of a concrete heap and its
-shape. For example, if the solver assigns input heap variables
-$\cfgnt{r}$ and $\cfgnt{r}^\prime$ such that $\cfgnt{r} =
-\cfgnt{r}^\prime$ is true, then there exists some location $\cfgnt{l}$
-and constraints $\phi$ and $\phi^\prime$ such that (i)
-$\lp\phi\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r})$; (ii)
-$\lp\phi^\prime\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r}^\prime)$; and
-(iii) $\phi$ and $\phi^\prime$ hold in the aliasing assignments from
-the solver.  In this way, the graph groups heaps with the conditions
-under which those heaps exist so look-ups are non-recursive and
-updates do not modify the path condition or require rewrites on
-constraints.
-
 \subsection{Symbolic Execution Semantics}
 
-In this work, symbolic execution semantics are is defined using
+Symbolic execution semantics are is defined using
 a small-step operational semantics similar to the one presented 

### 2015-08-29 vmcai-2016-tex/bisimulation.tex
Started new folder for VMCAI submission.
Fixed a typo in the proofs section.

--- 2015-05-16 ase-2015-tex/bisimulation.tex
@@
 \label{sec:bisim}
-
-%This section establishes the correctness of
-%the~\symtxt{}. Demonstrating correctness is important because many
-%summary heap techniques are correct only when certain, often
-%unstated, assumptions are made. To show the absence of such
-%assumptions, it is necessary to demonstrate soundness and completess
-%with respect to all properties provable by symbolic execution. The
-%proof relies on the observation that a state in symbolic execution
-%can be thought of as representing a set of possible concrete
-%states. Similarly, a state in the~\symtxt{} machine represents a set
-%of possible~\gsetxt{} states. The goal is to show that states in
-%the~\symtxt{} machine behave exactly like the sets of~\gsetxt{}
-%states that they represent.
 
@@
 unless at \cfgt{end}. Let $p \rgse p^\prime$ be a union over relations
-for~\gsetxt{} (see appendix): $\rgse = \rgse^\mathit{A} \cup
+for~\gsetxt{} (see~\cite{Hillery:2015}): $\rgse = \rgse^\mathit{A} \cup
 \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup
@@
 $$
-P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
+P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Leftrightarrow p^\prime \in P^\prime))
 $$

### 2015-08-31 vmcai-2016-tex/approach.tex
Fixed the initialization example figure to fit.
Implemented many fixes recommended by ASE reviewers.

@@
 
-The initialization rule in \figref{fig:symInit} is invoked whenever a
-field within an uninitialized reference is accessed. The interaction
+The initialization rule in \figref{fig:symInit} is invoked whenever 
+an uninitialized field is accessed. The interaction
 with the solver in the definition of the rules is denoted by
@@
 (c) After $\lp\cfgt{this}\  \cfgt{\$}\ \cfgnt{y}\rp$ is initialized.
-(d) Sets in the summarize rule and constraints on the edges.}
+(d) Sets in the initialization rule and constraints on the edges.}
 \label{fig:initHeap}

### 2015-08-31 vmcai-2016-tex/bisimulation.tex
Implemented many fixes recommended by ASE reviewers.

@@
  s_p \rightharpoonup_{h} s_q \Leftrightarrow 
-\exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}\ ( \exists \phi_\alpha\ (\exists \phi_\beta\ ( \\ 
+\exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}\ ( \forall \phi_\alpha\ (\\ 
 \ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow \\
-\ \ \ \ \ \ \ \ (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ 
+\ \ \ \ \ \ \ \ \exists \phi_\beta\ ( (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ 
  )) ) ) ) )
@@
 The represented relation is extended to sets of states $P$ and a single state $q$ as
-$P \sqsubset q \Longleftrightarrow \forall p\ (p \sqsubset q \Rightarrow p \in P)$.
+$P \sqsubset q \Longleftrightarrow \forall p\ (p \sqsubset q \Leftrightarrow p \in P)$.
 \end{definition}
@@
 \begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
-If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisumlation.
+If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisimulation.
 \label{lem:access}

### 2015-08-31 vmcai-2016-tex/summary-heap.tex
Implemented many fixes recommended by ASE reviewers.

@@
 
-The state of the machine, $\cfgnt{s}$, includes the program
-registry, $\mu$, a pair of functions defining the heap
-$\lp\cfgnt{L}\ \cfgnt{R}\rp$, 
-the path condition, $\phi$, a constraint defined over
-references in the heap, the environment, $\eta$, for local variables,
+The machine state $\cfgnt{s}$ includes the program
+registry $\mu$, a pair of functions $\lp\cfgnt{L}\ \cfgnt{R}\rp$ which defines the heap, 
+the path condition $\phi$ which is a constraint defined over
+references in the heap, the environment  $\eta$ which maps local variables to references,
 and the continuation $\cfgnt{k}$. The registry never changes so it is

### 2015-08-31 vmcai-2016-tex/value-set-def.tex
Implemented many fixes recommended by ASE reviewers.

\begin{definition}
\label{def:VS}
The $\mathbb{VS}$ function constructs the value set given a
heap, reference, and desired field where $\mathbb{S}(\phi)$ returns true if $\phi$ is satisfiable.
\[
\begin{array}{rcl}
  \mathbb{VS}(L,R,\phi_g,\cfgnt{r},\cfgnt{f}) & = &
  \{(\phi\wedge\phi^\prime\ l^\prime) \mid \exists
  l\ ((\phi\ l) \in L(\cfgnt{r})\ \wedge \\ & &
  \ \ (\phi^\prime\ l^\prime) \in L(R(l,\cfgnt{f}))\ \wedge \\ & &
  \ \ \mathbb{S}(\phi\wedge\phi^\prime\wedge \phi_g))\}
\end{array}
\]
\end{definition}

### 2015-09-03 vmcai-2016-tex/evaluation.tex
Updated the evaluation to address concerns raised by ASE reviewers.

--- 2015-05-04 ase-2015-tex/evaluation.tex
@@
 \section{Evaluation}
-
+\label{sec:evaluation}
 %\begin{figure*}[t]
@@
 %\subsection{Analysis}
-We empirically evaluate the \symtxt{}
-algorithm for analyzing programs with unbounded heap allocated
-data in the context of symbolic execution.
-To perform our evaluation we implemented a prototype of the \symtxt{} 
+Although the utility of value-set representations has been demonstrated
+in previous works,
+it remains an open question whether the dereferencing scheme
+presented here represents a practical alternative to the
+case-splitting methods currently in use. It is possible 
+that the benefits of path-reduction are offset by the increased
+complexity of the underlying constraints problem.
+
+To resolve this question, we implemented a prototype of the \symtxt{} 
 algorithm in Symbolic PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13} 
@@
 this paper, the implementation contains support for operations over
-integers.  We are currently working on adding support for floating
-point operations, arrays, and bit-operations.  We use the
-\texttt{jConstraints} library which provides support for handling heap
-constraints~\cite{ase2014-ghilrr,jpf2014-dghirr}. It uses the z3
-solver~\cite{deMouraBjorner08Z3} as the underlying constraint
-solver. We leverage the incremental solving feature in z3 in our
-experiments. We also implement other optimizations that cache and
-re-use solutions to previous constraints. These optimizations are an
-important part of our implementation because only small portions of
-the heap constraint changes from one state to another. 
-The solver optimizations used in the \symtxt{} are not applicable to \gsetxt{}-style techniques, as they do not generate or solve any heap-related constraints.
-Even with the solver optimizations these techniques would have the same performance characteristics.
-The overhead in \gsetxt{} arises from case-splitting (generating states) rather than solver time.
+integers, calculating per-path preconditions 
+and postconditions, as well as path-coverage-optimal sets of 
+test input heaps. A standalone version of the system, independent
+from JPF is also under development~\cite{heapsolver2015}.
 
@@
 The linked list is then traversed using a contains() method that attempts to locate an arbitrary reference key in the list.
-
-All benchmarks were performed with respect to a given k-bounds.
-k-bounding limits the length of reference chains to some user-defined integer k.
-k-bounding was chosen because it provides a fair means of comparison of all the techniques under investigation.
-More details on k-bounding can be found in~\cite{Deng:2007}.
+For all benchmarks, the length of reference chain initializations was limited to some integer $k$.
+More details on $k$-bounding can be found in~\cite{Deng:2007}.
 
@@
 for each artifact evaluated. The columns show the total
-wall clock time in seconds, states explored, and paths generated for
+time in seconds, states explored, and paths generated for
 each algorithm. The headings \gsetxt{}, L\#, and SH correspond
@@
 
-The results in Table~\ref{tab:results} demonstrate the efficiency of the 
-\symtxt{} algorithm, especially for
-large $k$-values. Performance improvement ranges from $4.8x$ for
+The results show that \symtst{} dramatically reduces 
+the number of paths that are explored, without producing a commensurate
+increase in constraint solver time. Performance improvement ranges from $4.8x$ for
 BinarySearchTree at $k$=3, to $118x$ for LinkedList at $k$=6. In fact,
@@
 unable to finish, e.g., BinarySearchTree for $k$=4 and LinkedList for
-$k$=8. These results demonstrate the potential of using the \symtxt{} algorithm 
-to analyze programs with complex types. The lower running times
-show that we can prove properties using the \symtxt{} algorithm 
-faster than \gsetxt{}.
+$k$=8.
 
@@
 additional branches in the final symbolic execution tree. Furthermore,
-the larger state count does not impact the overall runtime of the
+the since larger state count is essentially a result of bookkeeping, it
+does not impact the overall runtime of the
 technique.

### 2015-09-03 vmcai-2016-tex/intro.tex
Updated the evaluation to address concerns raised by ASE reviewers.

@@
 A promising approach to this problem has been to
-to partition the reachable heaps by using \emph{symbolic heap}
-representations, where multiple values for a reference may be
-represented along a single execution
+to partition the reachable heaps by using sets of guarded values.
+These \emph{symbolic heap}
+representations represent multiple values for a reference along a single execution
 path~\cite{Dillig:2011,Elkarablieh:2009,Sen:2014,Torlak:2014,Xie:2005,Yorsh:2008}.

### 2015-09-03 vmcai-2016-tex/rw.tex
Started new folder for VMCAI submission.
Updated the evaluation to address concerns raised by ASE reviewers.

--- 2015-02-07 cav-2015-tex/rw.tex
@@
 \section{Related Work}
+\label{sec:related}
 
-Initial work on symbolic execution largely focused on checking
-properties of imperative programs with primitive
-types~\cite{Clarke:76,King:76}.
-% Limitations of early symbolic execution techniques included non-primitive data types, path explosion and non-symbolic operations. Subsequent adaptations have sought to overcome these limitations.
+\subsection{Program Analysis using Symbolic Heaps}
+The symbolic heap methods in this work build upon a
+number of prior program analysis techniques that use sets of guarded values to
+represent program
+state~\cite{Sen:2014,Torlak:2014,Yorsh:2008,Xie:2005,Dillig:2011,Elkarablieh:2009}. 
+The method was pioneered in Verification-Condition Generator (VCG) style techniques such as ~\cite{Xie:2005,Yorsh:2008}, where value sets were used to 
+represent aliasing-free tree-like heaps. The work in~\cite{Dillig:2011} relaxed the aliasing restrictions by using a pre-computed set of symbolic input heaps.
+
+Recently, value sets have been adapted for use in symbolic execution, for the purposes of state merging ~\cite{Sen:2014,Torlak:2014} and invariant detection~\cite{Ferrara:2014}.
+While these methods demonstrate the utility of value sets in combination with symbolic execution, none of these techniques address dereferencing of symbolic input references.
+Since dereferencing is a fundamental problem treated in this paper, we believe these other works to be both orthogonal and complimentary to our own.
+
+\subsection{Other Heap Representations in Symbolic Execution}
+%Need to talk about GSE, DSE, SAGE, PEX
+%GSE
 Several projects have generalized the core idea of symbolic execution,
@@
 exacerbating path explosion.
-% and fragmenting the path condition. Producing a complete path
-%condition for a single given control flow path would require merging
-%an exponential number of states.
-Our work leverages the core idea in generalized symbolic
-execution with lazy initialization using on-the-fly reasoning to model
-a black-box input heap during symbolic execution, but avoids the
-nondeterminism introduced by~\gsetxt{} by constructing a single summary heap
-and polynomially-sized path condition for each control flow path.
 
-Recent progress has been made towards mitigating path explosion via state merging~\cite{Kuznetsov:2012,Sen:2014,Torlak:2014}.
-While the independently developed techniques in~\cite{Sen:2014,Torlak:2014} use representations similar to the one presented here, none of these techniques address the fundamental issue concerning symbolic heaps, namely dereferencing symbolic input references.
-For these reasons, we believe these works to be both orthogonal and complimentary to our own.
-
-%Dynamic symbolic execution (\dsetxt{}) has emerged as a way to enable
-%symbolic execution to continue on programs that contain elements that
-%cannot be reasoned about symbolically. ~\dsetxt{} works by executing
-%a program using concrete and symbolic engines simultaneously. When
-%the program reaches a statement that cannot be reasoned about
-%symbolically, it substitutes in values from the concrete execution
-%and continues. In the absence of an effective theory of references,
-%DSE has been a natural choice for reasoning about programs that
-%contain them.
-
-A number of dynamic symbolic execution (\dsetxt{}) techniques either use
-concretization when reasoning about references or require solvers that
-support theories of
-arrays~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}. Sometimes,
+%DSE
+Dynamic symbolic execution (\dsetxt{}) techniques may use
+concretization when reasoning about references~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}, enabling much greater program
+coverage than classical symbolic execution alone. In particular, PEX~\cite{Tillmann:2008}
+has demonstrated a high degree of utility in a wide variety of 
+practical verification scenarios. Sometimes,
 however, as demonstrated in~\cite{Elkarablieh:2009},~\dsetxt{}
@@
 engine~\cite{Elkarablieh:2009} includes more sophisticated methods for
-reasoning about references, and can successfully reason about more
-complicated examples. However, the heap model in SAGE prohibits
-input-dependent memory allocation. The fixed-memory requirement means
-that analyses of programs accepting indefinite input heaps may
-terminate prematurely, even for the class of self-limiting
-solver-compatible programs.
+reasoning symbolically about references, and can successfully handle
+complicated examples. However, SAGE uses a
+theory of fixed-length arrays to model the heap, and is thus incomplete
+for programs with input-dependent memory allocation. We believe that the 
+techniques presented in this work can be used to extend practical tools 
+like PEX for applications requiring formal correctness guarantees.
 
-Many bounded model checking (BMC) methods include a model for
-reasoning about references, including those described
-in~\cite{Clarke:2004,Barnett:2006,Xie:2005,Babic:2007,Dillig:2011}. However,
-BMC techniques generally need to predetermine bounds of a heap. Other
-limitations include assuming that symbolic references do not
-alias~\cite{Xie:2005,Babic:2007}, that data structures are not
-recursive~\cite{Dillig:2011}, or prohibiting dereferencing of
-black-box input references~\cite{Clarke:2004}.
+\subsection{Formal Results on Symbolic Heaps}
+The symbolic heap used by SAGE~\cite{Elkarablieh:2009} was shown to be sound and complete for programs with input-independent memory allocation.
+Our method is sound and complete for all states reached by symbolic execution.
 
-A number of constraint-based programming techniques are capable of
-reasoning about
-heaps~\cite{Degrave:2010,Charreteur:2009,Albert:2013}. Most notably,
-the technique in~\cite{Albert:2013} is capable of reasoning about
-dereferencing operations in a per-path set of unknown input
-heaps. However, no guarantees are made about the precision of the
-analysis performed.
+Recently, several separation logic solvers have been proven to be sound and complete for heaps with linked lists, trees~\cite{Piskac:2014}, or data structures satisfying user-supplied invariants~\cite{Brotherston:2014}.
+In contrast, our method is sound and complete without restriction on data structures, and requires no explicit invariants, but our result is restricted to the properties provable by symbolic execution.
 
-The symbolic heap value sets presented in this work build upon a
-number of prior techniques that use sets of guarded values to
-represent program
-state~\cite{Sen:2014,Torlak:2014,Yorsh:2008,Xie:2005,Dillig:2011,Elkarablieh:2009}. The
-methods presented in~\cite{Sen:2014,Torlak:2014,Yorsh:2008} use value
-sets to represent all symbolic program state, including
-references. While symbolic referencing operations could, in principle,
-be supported with these methods, it is not clear from the published
-material exactly how that might be accomplished, especially when
-reasoning about dereferencing in a black-box input heap. All of the
-methods presenting solutions to the dereferencing
-problem~\cite{Xie:2005,Dillig:2011,Elkarablieh:2009} are not complete,
-for a variety of reasons which have been previously enumerated.
+The heap in~\cite{Dillig:2011} was proven to be monotonic with respect to the number of valid solutions.
 
-%\noindent\textbf{A Lightweight Symbolic Virtual Machine for Solver-Aided Host Languages Emina Torlak and Ras Bodik. Programming Language Design and Implementation} (PLDI'14)
+Some heap methods, such as those used by VC generators, may be sound and complete if the correct bounds are chosen. However, choosing the bounds is at least as hard as analyzing the program.
+
+%Odds and ends leftover from last time:
+
+%Our work leverages the core idea in generalized symbolic execution
+%with lazy initialization using on-the-fly reasoning to model a
+%black-box input heap during symbolic execution, but avoids the
+%nondeterminism introduced by~\gsetxt{} by constructing a single
+%symbolic heap and polynomially-sized path condition for each control
+%flow path.
 %
-%\noindent{\textbf{What the reviewers said:} \emph{"the paper [Torlak et al. 2014] definitely shows how to apply the same compact representation to symbolic execution."}
+%Recent progress has been made towards mitigating path explosion via state merging~\cite{Kuznetsov:2012,Sen:2014,Torlak:2014}. 
 %
-%\noindent\textbf{What I think:} They aren’t really breaking any ground with the heap representation here.
-It’s pretty much the same thing as what was in SATURN.
-The main focus of the paper is on a VM for mixed symbolic-concrete programming languages.
-It’s probably worth citing, if only as part of a list of similar techniques.
 %
-%\noindent\textbf{How this is similar to SymHeap:}
+
 %
-%\noindent\textbf{How this is different from SymHeap:}
-%\begin{compactenum}
-%\item They don’t do lazy initialization. \emph{"The shape of all data structures remains concrete during SVM evaluation."}
-%\item There are no real bounding mechanisms, and they assume that programs are self-finitizing.
-%\begin{compactitem}
-%\item They don’t really handle recursion or loops.
-%\item They can’t make any sort of heap-specific bounds
-%\item They try to sell this as a feature, by the way, by claiming that they don’t “artificially finitize executions by explicitly bounding the depth of recursion.” That’s the nicest cover-up for a program that fails to terminate I’ve ever heard.
-%\end{compactitem}
-%\item Their representation is different. Although, they have value
-%  sets, I don’t see a bipartite graph, locations, fields, etc. This is
-%  worrisome since the reviewer was certain this is the same
-%  representation as ours.
-%\item They do weird domain-specific programming languages instead of our java-like language.
-%\end{compactenum}
+%Many bounded model checking (BMC) methods include a model for
+%reasoning about references, including those described
+%in~\cite{Clarke:2004,Barnett:2006,Xie:2005,Babic:2007,Dillig:2011}. However,
+%BMC techniques generally need to predetermine bounds of a heap. Other
+%limitations include assuming that symbolic references do not
+%alias~\cite{Xie:2005,Babic:2007}, that data structures are not
+%recursive~\cite{Dillig:2011}, or prohibiting dereferencing of
+%black-box input references~\cite{Clarke:2004}.
 %
-%Generating precise and concise procedure summaries, POPL’2008
+%A number of constraint-based programming techniques are capable of
+%reasoning about
+%heaps~\cite{Degrave:2010,Charreteur:2009,Albert:2013}. Most notably,
+%the technique in~\cite{Albert:2013} is capable of reasoning about
+%dereferencing operations in a per-path set of unknown input
+%heaps. However, no guarantees are made about the precision of the
+%analysis performed.
 %
-%What the reviewer said: This was in a general list of “missing” related work
 %
-%What I think: This paper is about procedure summaries.
-It looks like they are concerned with a more general type of problem than we are with the heap, and that the heap-related stuff is a specialization of their framework.
-It’s worth citing, as an example of a global access-path style representation.
 %
-%How this is similar to SymHeap:
-%1) Uses sets of guarded values, which they call micr-transformers.
-Their “micro-transformers” can be made to look lot like our references.
-A dereferencing operation may be performed using a “composition of micro-transformers”.
-%
-%How this is different from SymHeap: 
-%1) The heap is stored as global access paths, related directly to variables.
-Thus, they don’t have any explicit local representation of the heap, and determining reachability is impossible without consulting the solver.
-%
-%2) Potential aliasing relationships are determined in a path-insensitive manner, prior to program execution, by means of power sets.
-%
-%3) It doesn’t look like they do lazy initialization. The size of parameter sets is fixed at the beginning of the program
-%
-%Boogie: A Modular Reusable Verifier for Object-Oriented Programs FMCO'2005
-%
-%What the reviewer said: This was in a list of “missing” related work, categorized as “work on precise memory models for verification-condition generation”.
-%
-%What I think: Boogie doesn’t have a built-in heap encoding.
-It uses a 2d array to model the heap, and compiles the entire program-correctness problem into a single constraint equation, which it ships off to a constraint solver.
-It’s a very different sort of analysis.
-Worth mentioning as part of a list of verification-condition generators, but not for anything else.
-%
-%Structural Abstractions of Software Verification Conditions, CAV'2007
-%
-%What the reviewer said: This was in a list of “missing” related work, categorized as “work on precise memory models for verification-condition generation”.
-%
-%What I think: As far as heap representation goes, this doesn’t look very interesting.
-Like most VC generators, they assume that input pointers don’t alias.
-This is a little interesting from a solving standpoint, because they turn the VC into a tree that they then perform structural operations on without consulting a solver.
-This is reminiscent of how we can do some heap operations without consulting the solver.
-%
-%A Tool for Checking ANSI-C programs, TACAS'04
-%
-%What the reviewer said: This was in a general list of “missing” related work.
-%
-%What I think: This is one of Clarke’s papers on bounded model checking. It couldn’t hurt to cite it, but it’s not super-related.
-%
-%Precise Pointer reasoning for Dynamic test Generation, ISSTA'2009
-%
-%What the reviewer said: This was in a general list of “missing” related work.
-%
-%What I think: This paper is about how to handle pointers during dynamic symbolic execution.
-It handles pointer dereferences much like~\gsetxt{}, by resolving possible aliases at the time of the dereferencing, but does not seem to include the possibility of a “new” choice.
-One difference is that this method is adapted to allow pointer arithmetic.
-The memory model is basically a flat address space, without any explicit notion of a heap.
-%
-%How this is like SymHeap: It’s a symbolic execution technique that has some facility for linked data structures.
-Their pointers can be nondeterministic, much like the references in symHeap, and they do conditional writes in a similar fashion as symHeap.
-%
-%Why this is different from SymHeap:
-%
-%1 )The memory model is completely different. It’s an addressable array instead of an object-oriented heap. There are no facilities for heap-specific operations like k- or n-bounding. 
-%
-%2) They have a fixed set of memory locations from the onset. There is no concept of lazy initialization to some “new” reference.
-%
-%Compositional dynamic test generation. Patrice Godefroid. 2007.
-%
-%What the Reviewer Said: There is an alternative way to represent a summary using logical
-%formulas and extra variables [Godefroid 2007]. I wonder how such a
-%representation would work for~\gsetxt{} and heap summarization. Such a
-%representation would not require the complex update algorithm
-%described in the paper. It would be useful if the authors could
-%comment on this and experimentally compare with the technique.
-%
-%What I think: The SMART approach in Godefroid’s paper is sound but not complete.
-That is to say, every bug it finds is a real bug, but it is not guaranteed to account for all possible program paths.
-Given the incomplete of their method, the fact that their representation is simpler is unsurprising.
-%
-%MultiSE: Multi-Path Symbolic Execution using Value Summaries [Sen et al. 2014]
-%
-%What the reviewer said: The reviewer claimed that the technique presented in this paper uses the same heap representation as us.
-%
-%What I think: This paper uses essentially the same representation as the Dilligs. In fact, I think in many ways the Dillig’s work is more sophisticated than the treatment presented here.
-%
-%How It’s similar to SymHeap: It’s symbolic execution, with a heap. Their heap has value sets like ours does, and their write operation looks like ours.
-%
-%How it’s different from SymHeap: They don’t do lazy initialization. They use BDDs to represent expressions. Their graph isn’t bipartite.

### 2015-09-09 vmcai-2016-tex/abstract.tex
Started new folder for VMCAI submission.
Re-did the introduction, and tried to harmonize the rest of the paper somewhat.

--- 2015-03-27 tex/abstract.tex
@@
-A fundamental challenge of using symbolic execution for software
-analysis is the treatment of dynamically allocated data. This paper
-introduces a compact symbolic heap representation based on a field
-sensitive points-to graph with edges annotated with disjunctive
-formulas describing aliasing relationships, along with a set of
-rewrite rules that describe the initialization, dereferencing, and
-update to fields in the symbolic heaps. The symbolic heap supports
-arbitrary recursive data structures and captures all possible heaps
-that follow a common control flow path up to the point of
-execution. An evaluation of a proof-of-concept implementation in the
-Java Pathfinder framework is presented to demonstrate the
-computational feasibility of the approach over several classical
-symbolic execution benchmarks.
+A recent trend in symbolic execution of object-oriented programs is the modeling of references as sets of guarded values, enabling multiple heap shapes to be represented in a single state.
+A fundamental problem with using these guarded value sets is the creation of test inputs for programs accepting symbolic reference input parameters.
+Although several solutions have been proposed, none have been proven to be sound and complete with respect to the properties provable by generalized symbolic execution (GSE).
+This work presents a method for initializing reference inputs in a black-box symbolic input heap that exactly preserves GSE semantics.
+A correctness proof for the initialization scheme is provided, as well as the results of an empirical evaluation of a proof-of-concept implementation.
+The initialization technique can be used to ensure that guarded value set based symbolic execution engines operate in a provably correct manner with regards to symbolic references.
 
-%A fundamental challenge of using symbolic execution for software
-%analysis is the treatment of dynamically allocated data. Existing
-%static analysis techniques over-approximate the potential heaps,
-%dynamic symbolic execution techniques often under-approximate the
-%heaps, while generalized symbolic execution leads to excessive
-%case-splitting. This paper introduces a compact heap representation,
-%along with heap update rules that (i) allow reads and writes of
-%symbolic references, (ii) do not require constraint rewriting, and
-%(iii) support arbitrary recursive data structures. As such, the
-%representation and update rules capture all possible heaps that
-%follow a common execution path. More importantly, in contrast to
-%existing state-of-the-art techniques, the definition and update rules
-%are unconstrained and not subject to bounds, such as the number of
-%heap locations, aliasing, or memory partitions. An evaluation of a
-%proof-of-concept implementation in the Java Pathfinder framework is
-%presented to demonstrate the computational feasibility of the
-%approach over several classical symbolic execution benchmarks.
+%A fundamental challenge of using symbolic execution for software analysis is the treatment of dynamically allocated data.
+Existing techniques either underapproximate the space of possible inputs or are computationally infeasible.
+For example, dynamic symbolic execution (DSE) handles symbolic dereferencing by substituting in a value from a valid concrete execution.
+Generalized symbolic execution (GSE) initiates a new search path for every possible aliasing configuration.
+This paper introduces a method for de-referencing and manipulating values in a true block-box symbolic input heap that overcomes the limitations of previous methods.
+The symbolic heap supports arbitrary recursive data structures and captures all possible heaps that follow a common control flow path.
+Computation of complex preconditions and postconditions is supported, as well as automatic generation of test inputs.
+An evaluation of a proof-of-concept implementation in the Java Pathfinder framework is presented to demonstrate the computational feasibility of the approach over several classical symbolic execution benchmarks.

### 2015-09-09 vmcai-2016-tex/bisimulation.tex
Re-did the introduction, and tried to harmonize the rest of the paper somewhat.

@@
-\section{Bisimilarity Proof}
+\section{Correctness}
 \label{sec:bisim}
+A major drawback of previous methods for creating test inputs for
+symbolic heaps has been a lack of completeness. Incomplete heap
+representations may not create a set of inputs that represents
+the entire space of possible inputs. By missing some possible
+inputs, the subsequent analysis may fail to recognize 
+possible program behaviors.
 
-The bisimulation proof in this section establishes the soundness and
+The theorems in this section establish the soundness and
 completeness of the symbolic heap approach with respect to Generalized
-Symbolic Execution (\gsetxt{}). Intuitively, any properties proven
+Symbolic Execution (\gsetxt{}). Intuitively, the theorems imply that any properties proven
 with~\gsetxt{} can also be proved using the symbolic heap
-algorithm.~\gsetxt{} concretizes the possible heap configurations
-along with various aliasing relationships when an uninitialized field
-is dereferenced. The rules for initializing and updating the fields in
-the machine's semantics for \gsetxt{} as well as
-the the complete set of rules for the symbolic heap algorithm can
+algorithm. The proofs for the theorems, as well as
+the complete set of semantic rules for~\gsetxt{} and~\symtxt{} can
 be found in ~\cite{Hillery:2015}.
@@
 
-\begin{proof}
-Proof by contradiction: assume $P \sqsubset q \wedge (P\ q) \not\in F_\sim(\sqsubset)$.
-
-\noindent\textbf{Sketch}: Choose any $P$ and $q$ at the field access continuation such
-that $P \sqsubset q$. In the forward simulation
-\eqref{eqn:BisimulationForwards}, for each $P^\prime$ such that $P
-\rsgse P^\prime$, pick some $p^\prime \in P^\prime$. By definition $p \rgse
-p^\prime$, $p \in P$, and $p \sqsubset q$. The proof shows the
-existence of $q^\prime$ such that $q \rsym q^\prime$ and $p^\prime
-\sqsubset q^\prime$ using the existing homomorphism in $p \sqsubset q$.
-
-In the backward simulation \eqref{eqn:BisimulationBackwards}, for each
-$q^\prime$ such that $q \rsym q^\prime$, the proof posits the existence of some 
-$p^\prime$ such that $p^\prime \sqsubset q^\prime$. It then uses the
-homomorphism in $p^\prime \sqsubset q^\prime$ to derive a $p$ such
-that $p \rgse p^\prime$ and $p \in P$. The existence of $P^\prime$ is established by the existence of $p^\prime$, and $P \sqsubset q$ makes $P^\prime$ the actual successor of $P$.
-
-As the forward and backward simulations hold for any $p \in P$, $P
-\sqsubset q$ must be in the functional, $F_\sim(\sqsubset)$, which is
-a contradiction.
-\end{proof}
+%\begin{proof}
+%Proof by contradiction: assume $P \sqsubset q \wedge (P\ q) \not\in F_\sim(\sqsubset)$.
+%
+%\noindent\textbf{Sketch}: Choose any $P$ and $q$ at the field access continuation such
+%that $P \sqsubset q$. In the forward simulation
+%\eqref{eqn:BisimulationForwards}, for each $P^\prime$ such that $P
+%\rsgse P^\prime$, pick some $p^\prime \in P^\prime$. By definition $p \rgse
+%p^\prime$, $p \in P$, and $p \sqsubset q$. The proof shows the
+%existence of $q^\prime$ such that $q \rsym q^\prime$ and $p^\prime
+%\sqsubset q^\prime$ using the existing homomorphism in $p \sqsubset q$.
+%
+%In the backward simulation \eqref{eqn:BisimulationBackwards}, for each
+%$q^\prime$ such that $q \rsym q^\prime$, the proof posits the existence of some 
+%$p^\prime$ such that $p^\prime \sqsubset q^\prime$. It then uses the
+%homomorphism in $p^\prime \sqsubset q^\prime$ to derive a $p$ such
+%that $p \rgse p^\prime$ and $p \in P$. The existence of $P^\prime$ is established by the existence of $p^\prime$, and $P \sqsubset q$ makes $P^\prime$ the actual successor of $P$.
+%
+%As the forward and backward simulations hold for any $p \in P$, $P
+%\sqsubset q$ must be in the functional, $F_\sim(\sqsubset)$, which is
+%a contradiction.
+%\end{proof}
 
@@
 \end{theorem}
-\begin{proof}
-By definition of bisimilarity. All of the common rules in $\rcom$
-make no changes to the heap, so $P \sqsubset q$ is included in the
-functional. The other rules that affect the heap are supported by lemmas
-such as \lemref{lem:access}.
-\end{proof}
+%\begin{proof}
+%By definition of bisimilarity. All of the common rules in $\rcom$
+%make no changes to the heap, so $P \sqsubset q$ is included in the
+%functional. The other rules that affect the heap are supported by lemmas
+%such as \lemref{lem:access}.
+%\end{proof}
 
-The notation $p \stackrel{n}{\rgse} p^\prime$ denotes that $p^\prime$
-is the $n$-step successor of $p$, when it exists, and $q
-\stackrel{n}{\rsym} q^\prime$ is similarly defined. Completeness and
-soundness fall out of \thref{th:bisim} by inducting
-over $n$.
+%The notation $p \stackrel{n}{\rgse} p^\prime$ denotes that $p^\prime$
+%is the $n$-step successor of $p$, when it exists, and $q
+%\stackrel{n}{\rsym} q^\prime$ is similarly defined. Completeness and
+%soundness fall out of \thref{th:bisim} by inducting
+%over $n$.
 
@@
 
-The relation, $P \sqsubset q$, is readily established in the initial
-state of a given program as there is single initial state, $P_o =
-\{p_o\}$, in any valid program. The initial state for $\rsym$ is
-then defined as $q_o = p_o$ so $P_o \sqsubset q_o$ trivially holds.
+%The relation, $P \sqsubset q$, is readily established in the initial
+%state of a given program as there is single initial state, $P_o =
+%\{p_o\}$, in any valid program. The initial state for $\rsym$ is
+%then defined as $q_o = p_o$ so $P_o \sqsubset q_o$ trivially holds.

### 2015-09-09 vmcai-2016-tex/evaluation.tex
Re-did the introduction, and tried to harmonize the rest of the paper somewhat.

@@
 %\subsection{Analysis}
-Although the utility of value-set representations has been demonstrated
-in previous works,
-it remains an open question whether the dereferencing scheme
-presented here represents a practical alternative to the
+Although the correctness of~\symtxt{} has been demonstrated,
+it remains an open question whether it represents a practical alternative to the
 case-splitting methods currently in use. It is possible 
-that the benefits of path-reduction are offset by the increased
-complexity of the underlying constraints problem.
+that the benefit of decreasing the number of paths explored is
+offset by the increased complexity of the underlying constraints problem.
 
@@
 and evaluate its efficacy on three Java data structure artifacts.
-SPF includes an implementation of~\gsetxt{} with lazy initialization.
-In recent work, we implemented the  Lazier and Lazier\#
-algorithms in SPF~\cite{Hillery:2014}.
-
-The prototype of our~\symtxt{} algorithm is implemented as a new
-extension to SPF.  In addition to the operations presented in the in
+%SPF includes an implementation of~\gsetxt{} with lazy initialization.
+%In recent work, we implemented the  Lazier and Lazier\#
+%algorithms in SPF~\cite{Hillery:2014}.
+%
+%The prototype of our~\symtxt{} algorithm is implemented as an
+%extension to SPF.  
+In addition to the operations presented in
 this paper, the implementation contains support for operations over
@@
 and postconditions, as well as path-coverage-optimal sets of 
-test input heaps. A standalone version of the system, independent
-from JPF is also under development~\cite{heapsolver2015}.
+test input heaps. 
+%A standalone version of the system, independent
+%from JPF is also under development~\cite{heapsolver2015}.
 
-The benchmarks all include invariants and traversals of data structures.
-The chosen benchmarks have a high proportion of heap-related operations, putting maximum focus on the heap analysis methods under investigation.
-They are included to provide evidence of the general computational efficiency of the SH approach.
-In future work we plan to evaluate it on a more diverse set of benchmarks.
+The benchmarks focus on a number of common data structures, including a linked list, binary search tree, and red/black tree.
 The BinarySearchTree test uses the class of the same name from Alan Weiss' book titled ``Data Structures and Algorithm Analysis in Java''.
@@
 The linked list is then traversed using a contains() method that attempts to locate an arbitrary reference key in the list.
-For all benchmarks, the length of reference chain initializations was limited to some integer $k$.
+For benchmarking purposes, the length of reference chain initializations was limited to some integer $k$.
 More details on $k$-bounding can be found in~\cite{Deng:2007}.
@@
 
-The results show that \symtst{} dramatically reduces 
-the number of paths that are explored, without producing a commensurate
-increase in constraint solver time. Performance improvement ranges from $4.8x$ for
+The results demonstrate that for these common data structures,
+the complexity of the constraints generated by~\symtxt{} is more 
+than offset by the reduction in paths explored. Performance improvement ranges from $4.8x$ for
 BinarySearchTree at $k$=3, to $118x$ for LinkedList at $k$=6. In fact,
@@
 unable to finish, e.g., BinarySearchTree for $k$=4 and LinkedList for
-$k$=8.
+$k$=8. However, these numbers should 
+not be taken as an indication of performance gains that could be 
+expected in more general analysis situations. Real-world performance
+gain will most likely depend on the proportion of paths avoided that
+would otherwise have been explored via case-splitting.
 
-The number of states explored varies between algorithms. For example,
-\gsetxt{} creates additional points of nondeterminism during field reads, 
-while reference compares are completely deterministic. Thus, in
-example programs with large numbers of reference compares, e.g.,
-TreeMap, state counts for Lazier\# and the \symtxt{} algorithm may
-exceed those for \gsetxt{}. We observed that the additional states
-generated by the symbolic heap algorithm are unsatisfiable at the point
-of reference compares; this is why they do not contribute any
-additional branches in the final symbolic execution tree. Furthermore,
-the since larger state count is essentially a result of bookkeeping, it
-does not impact the overall runtime of the
-technique.
+%how does the per-path cost look for our method
+
+%The number of states explored varies between algorithms. For example,
+%\gsetxt{} creates additional points of nondeterminism during field reads, 
+%while reference compares are completely deterministic. Thus, in
+%example programs with large numbers of reference compares, e.g.,
+%TreeMap, state counts for Lazier\# and the \symtxt{} algorithm may
+%exceed those for \gsetxt{}. We observed that the additional states
+%generated by the symbolic heap algorithm are unsatisfiable at the point
+%of reference compares; this is why they do not contribute any
+%additional branches in the final symbolic execution tree. Furthermore,
+%the since larger state count is essentially a result of bookkeeping, it
+%does not impact the overall runtime of the
+%technique.
 
@@
 
-The path counts shown in Table~\ref{tab:results} also show the advantage
-of the \symtxt{} algorithm over the \gsetxt{} and L\# algorithms, each of
-which performs case-splitting during the analysis.
-The number of paths explored by the \symtxt{} algorithm is strictly 
-less than or equal to the number
-of paths explored by \gsetxt{} for all artifacts. As a result,
-fewer test cases will be generated to achieve the same control-flow 
-path coverage when compared to~\gsetxt{} and Lazier\#.
+%The path counts shown in Table~\ref{tab:results} also show the advantage
+%of the \symtxt{} algorithm over the \gsetxt{} and L\# algorithms, each of
+%which performs case-splitting during the analysis.
+%The number of paths explored by the \symtxt{} algorithm is strictly 
+%less than or equal to the number
+%of paths explored by \gsetxt{} for all artifacts. As a result,
+%fewer test cases will be generated to achieve the same control-flow 
+%path coverage when compared to~\gsetxt{} and Lazier\#.
 

### 2015-09-09 vmcai-2016-tex/intro.tex
Re-did the introduction, and tried to harmonize the rest of the paper somewhat.

--- 2015-08-29 vmcai-2016-tex/intro.tex
@@
 
-In recent years symbolic execution has provided the basis for various
-software testing and analysis techniques, e.g., regression
-analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
-data structure repair~\cite{KhurshidETAL05RepairingStructurally},
-dynamic discovery of
-invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, and
-debugging~\cite{Ma:2011}.
+%In recent years symbolic execution has provided the basis for various
+%software testing and analysis techniques, e.g., regression
+%analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
+%data structure repair~\cite{KhurshidETAL05RepairingStructurally},
+%dynamic discovery of
+%invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, and
+%debugging~\cite{Ma:2011}.
+%
+%Recent work has explored the strengths and limitations of
+%tools which leverage constraint solvers, e.g., concolic execution,
+%identifying symbolic dereferencing and updating operations as areas
+%for potential improvement~\cite{Chen:2013,Qu:2011}.
 
-Recent work has explored the strengths and limitations of
-tools which leverage constraint solvers, e.g., concolic execution,
-identifying symbolic dereferencing and updating operations as areas
-for potential improvement~\cite{Chen:2013,Qu:2011}.  Precisely
-modeling these operations, however, is challenging because it requires
-formulating logical predicates over an input domain that contains a
-potentially unbounded number of references.
+In symbolic execution, the values of program variables are represented as constraints over the program’s inputs.
+During the course of an execution, a program variable may assume a number of possible values under a variety of different conditions.
+One way to represent this behavior is by pairing each possible value with the with the constraints under which it is assumed.
+A set of such value-constraint pairs, called a \emph{guarded value set}, represents the state of a program variable.
 
-A promising approach to this problem has been to
-to partition the reachable heaps by using \emph{symbolic heap}
-representations, where multiple values for a reference may be
-represented along a single execution
-path~\cite{Dillig:2011,Elkarablieh:2009,Sen:2014,Torlak:2014,Xie:2005,Yorsh:2008}.
-However, it remains an open question whether or not these methods can be used to exactly model all possible program behaviors in the case of an arbitrary input.
+Guarded value sets are rising in importance in the representation of reference values.
+First appearing in Verification-Condition Generator (VCG) style techniques~\cite{Xie:2005,Dillig:2011}, guarded value sets are a convenient way to represent sets of heap shapes.
+More recently, guarded value sets are being used in symbolic execution for the purposes of modularization~\cite{Yorsh:2008}, state merging~\cite{Sen:2014}, and for determining invariants~\cite{Ferrara:2014,Torlak:2014}.
 
-The contribution of this work is to build on these previous efforts, by demonstrating how to dereference pointers in an unknown symbolic input heap, thereby proving that value-summary representations are sound and complete with respect to properties provable by symbolic execution.
-A proof-of-concept implementation also demonstrates the efficiency of value-summary representations, as compared to the previous best-known exact analysis method.
+A common hurdle to using guarded value sets is the treatment of symbolic heap inputs.
+Precisely modeling operations on heap inputs is challenging because it requires formulating logical predicates over an input domain that contains a potentially unbounded number of references~\cite{Chen:2013,Qu:2011}.
+Manually creating test inputs can be a time consuming and error-prone process, automatic case-splitting methods~\cite{GSE03,Deng:2007} quickly produce an overwhelming number of execution paths, and user-supplied logical invariants require a high degree of skill to create.
+Thus, despite the advantages of using guarded value sets, it remains an open question how they can be used in symbolic execution to automatically model all possible program behaviors in the case of an arbitrary input heap.
 
-\begin{comment}
-\section{Introduction}
-
-% SymExe is cool because for reasons x,y, and z
-
-In recent years symbolic execution has provided the basis for various
-software testing and analysis techniques. Symbolic execution
-systematically explores the program execution space representing input
-values symbolically, and for each explored path, it computes
-constraints on the symbolic inputs to create a \emph{ path condition}.
-Path conditions computed by symbolic execution characterize the
-observed program execution behaviors and have been used as an enabling
-technology for various applications, e.g., regression
-analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
-data structure repair~\cite{KhurshidETAL05RepairingStructurally},
-dynamic discovery of
-invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, and
-debugging~\cite{Ma:2011}.
-
-The path conditions computed by symbolic execution have two important
-characteristics: 1) they characterize the set of feasible execution
-paths, i.e., infeasible paths are omitted, and 2) each path condition
-represents the set of concrete program inputs that would cause
-execution to follow that program path. Because path conditions are
-encoded as constraints over program inputs, the reasoning capabilities
-of symbolic execution are limited by the underlying constraint solver.
-Thus, extending the capabilities of symbolic execution to reason about
-new theories is an area of active research. Of particular interest are
-symbolic dereferencing and updating
-operations~\cite{Chen:2013,Qu:2011}. Precisely modeling these
-operations is challenging, because it requires formulating logical
-predicates over an input domain containing a potentially unbounded
-number of references.
-
-Current strategies for symbolic dereferencing require making tradeoffs
-between the completeness of the analysis and the completeness of the
-path condition. For example, one simple approach is to terminate
-execution upon attempting to dereference any symbolic
-value~\cite{Clarke:2004}. While this preserves the integrity of the
-path condition, it comes at the cost of an incomplete analysis. To
-enable a more complete analysis, dynamic symbolic execution (\dsetxt{}),
-approximates the results of a symbolic dereferencing by substituting
-in a valid concrete
-value~\cite{Godefroid:POPL07,Godefroid:2005,Sen:2005,Tillmann:2008}. This
-allows execution to continue, but the approximation renders the path
-condition incomplete~\cite{Chen:2013,Elkarablieh:2009}, by effectively
-partitioning the space of input heaps into those where the result of
-the dereferencing matches the concrete execution. Larger partitions
-can be achieved by using value summary representations, where multiple
-values for a reference may be represented along a single execution
-path~\cite{Dillig:2011,Elkarablieh:2009,Sen:2014,Torlak:2014,Xie:2005,Yorsh:2008}. Systems
-using these representations perform analyses that are more complete
-than standard~\dsetxt{} methods, but their associated dereferencing
-operations require placing further restrictions on the input heap,
-such as limiting the number of nodes~\cite{Elkarablieh:2009}, the
-nature of aliasing relationships~\cite{Babic:2007,Xie:2005}, or the
-shape of the heap itself~\cite{Dillig:2011}. Finally, at the opposite
-end of the spectrum lies generalized symbolic execution
-(\gsetxt{})~\cite{Cadar:2008,KiasanKunit,GSE03,Rosner:2015}, which
-accomplishes a fully complete analysis at the cost of an incomplete
-path condition \sjp{not clear what an incomplete path condition
-  is}. On symbolic dereferencing operations,~\gsetxt{} partitions the input
-space between the various possible aliasing configurations
-\sjp{so?}. Thus, none of the current techniques provide the option of
-maintaining both a complete analysis and a complete path
-condition. This is in stark contrast to symbolic execution over
-primitive types, which enjoys both properties simultaneously.
-
-\sjp{Need to explain that the techniques still operate within some bound for loops, etc.}
-
-\sjp{Notion of on-the-fly updates is not here}
-
-\sjp{Nowhere do we refer to the technique as a summary heap framework or algorithm,
-so the next section with its heading just jumps out of nowhere.}
-
-This paper introduces a technique that avoids these problems by
-preserving the following properties of classical symbolic execution:
-(i) Inputs are represented by unbounded and unconstrained input
-symbols. This lack of predetermined constraints is key to avoiding
-under-approximation, which in turn is required for performing a
-complete analysis. (ii) Points of nondeterminism are only introduced
-at control flow instructions, which is critical for maintaining a
-complete path condition for a given control flow path.
-
-\noindent{This paper makes the following contributions:}
-
-\begin{compactdesc}
-
-\item\textbf{-} A system for reasoning symbolically about the 
-set of input heaps along any valid program path that is sound
-and complete with respect to symbolic execution.
-
-\item\textbf{-} A bisimulation proof establishing the soundness and 
-completeness of the heap summary approach with respect to
-properties provable by~\gsetxt{}.
-
-\item\textbf{-} A proof-of-concept implementation and empirical study 
-demonstrating the scalability of the summary heap approach
-compared to other~\gsetxt{} approaches.
-
-\end{compactdesc}
-\end{comment}
+The contribution of this work is to build on previous efforts, by demonstrating how to dereference pointers in an unknown symbolic input heap, and by proving that the dereferencing scheme is sound and complete with respect to properties provable by symbolic execution.
+A proof-of-concept implementation also demonstrates the efficiency of value-summary representations, as compared to existing case-splitting methods.

### 2015-09-09 vmcai-2016-tex/summary-heap.tex
Re-did the introduction, and tried to harmonize the rest of the paper somewhat.

--- 2015-08-29 vmcai-2016-tex/summary-heap.tex
@@
 
-\subsection{Symbolic Heap}
-
-%Determining the symbolic state is relatively simple for programs that perform linear manipulations of numeric input parameters.
-However, the task becomes more challenging for programs that accept references as inputs, in part because it is not obvious exactly how many program input parameters there are.
-For example, consider the case of dereferencing an input reference that points to an object that itself contains multiple fields.
-Should each of those field values be included as program input parameters?
-What if some of the fields contain references?
-It would seem as if dereferencing symbolic input references opens the door to a potentially unbounded number of parameters.
-
-%Our solution treats the heap as a hidden input parameter to every program.
-%expressed completely in terms of a black-box symbolic input heap
-%and the input reference parameters.
-The collective state of all symbolic program reference values
-is known as the \emph{symbolic heap}. Our symbolic heap 
-is a field sensitive points-to graph with edges
-annotated with disjunctive formulas describing aliasing
-relationships. We represent the symbolic heap as a bipartite graph on
-references, $\cfgnt{r}$, and constraint location pairs,
-$\lp\phi\ \cfgnt{l}\rp$. The graph is expressed in the location map,
-$\cfgnt{L}$, and the reference map, $\cfgnt{R}$. As done with the
-environment, $\cfgnt{L}$ and $\cfgnt{R}$ are treated as partial
-functions. $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the set
-of constraint-location pairs (value set) in the heap associated with the given
-reference. The constraint associated with each location is a guard
-representing the conditions under which the associated reference
-maps to the given location. By definition, any location appears 
-at most once in any given value set. Unions of value sets containing
-the same location are resolved by forming a disjunction of the constraints
-from each set. $\cfgnt{R}(\cfgnt{l}, \cfgnt{f}) = \cfgnt{r}$ is the
-reference associated with the given location-field pair in the
-heap. References in the graph are immutable. Locations, however, are
-mutated on updates.
-
-\begin{figure}[t]
-\begin{center}
-\includegraphics[scale=0.5]{../figs/simple_heap_scratch.pdf}
-\end{center}
-\caption{Example Symbolic Heap}
-\label{fig:exampleHeap}
-\end{figure}
-
-\figref{fig:exampleHeap} shows an example symbolic heap. References are 
-represented by circles and locations are represented by squares. Arrows leaving
-references correspond to the value sets returned by the $\cfgnt{L}$ function, and 
-arrows leaving the squares correspond to the $\cfgnt{R}$ function.
-
-The soundness and completeness proofs in Section~\ref{sec:bisim} rely
-on certain characteristics of the symbolic heap that are preserved by
-the small-step semantics during symbolic execution:
-
-\begin{compactdesc}
-\item[Reference partitions:] Each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
-  heap}% that includes $\cfgnt{r}_\mathit{null}$ (these are created by lazy initialization and are the only references that appear as variables in constraints)
-  ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
-  literals}% that includes $\cfgnt{r}_\mathit{un}$ (these add structure but do not appear elsewhere)
-  ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
-  literals}. %(these appear in environments, expressions, and continuations).
-  Only input heap references appear in constraints to express potential aliasing.
-  Auxiliary literals and stack references are used to define additional structure in the bipartite graph but only stack references can appear in environments, expressions, or continuations.
-\item[Null and Uninitialized:] Every symbolic heap contains 
-two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized,
-  ($\cfgnt{l}_\mathit{un}$)  with corresponding references 
-  $\cfgnt{r}_\mathit{null}$ and $\cfgnt{r}_\mathit{un}$ 
-  where $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
-  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
-  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
-  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. 
-\item[Immutability:] References do not change once added to the
-location map, eliminating any need for constraint rewriting as the program state evolves.
-\item[Determinism:] A reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
-$
-\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
-(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
-$
-where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. 
-\item[Type consistency:] All locations associated with a reference have the same type:
-$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
-(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$
-
-\end{compactdesc}
-
-\subsection{Symbolic Execution Semantics}
+\subsection{Symbolic Execution}
 
@@
 '$\cfgt{\$}$', and the dot-operator for method invocation is replaced
-by '$\cfgt{@}$' since '.' is reserved in PLT Redex. There is no
+by '$\cfgt{@}$'. There is no
 explicit return statement; rather, the value of the last expression is
@@
 
-The state of the machine, $\cfgnt{s}$, includes the program
-registry, $\mu$, a pair of functions defining the heap
-$\lp\cfgnt{L}\ \cfgnt{R}\rp$, 
-the path condition, $\phi$, a constraint defined over
-references in the heap, the environment, $\eta$, for local variables,
+A \emph{symbolic heap} is a tuple $(\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta)$, where the~\emph{location map} $\cfgnt{L}$,~\emph{reference map} $\cfgnt{R}$, and~\emph{environment} $\eta$ are partial functions, and the~\emph{path condition} $\phi$ is a predicate over the program variables.
+Given reference $r$, $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the set of constraint-location pairs (guarded value set) in the heap associated with $r$.
+The constraint  associated with each location is a guard
+representing the conditions under which the associated reference
+maps to the given location. By definition, any location appears 
+at most once in any given value set. Unions of value sets containing
+the same location are resolved by forming a disjunction of the constraints
+from each set. $\cfgnt{R}(\cfgnt{l}, \cfgnt{f}) = \cfgnt{r}$ is the
+reference associated with the given location-field pair in the
+heap. The environment  $\eta$ maps local variables to references.
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[scale=0.5]{../figs/simple_heap_scratch.pdf}
+\end{center}
+\caption{Example Symbolic Heap}
+\label{fig:exampleHeap}
+\end{figure}
+
+Conceptually, the symbolic heap may be thought of as a bipartite graph. \figref{fig:exampleHeap} shows an example symbolic heap graph. References are 
+represented by circles and locations are represented by squares. Arrows leaving
+references correspond to the value sets returned by the $\cfgnt{L}$ function, and 
+arrows leaving the squares correspond to the $\cfgnt{R}$ function.
+
+The machine state $\cfgnt{s}$ includes the program
+registry $\mu$, the symbolic heap,
 and the continuation $\cfgnt{k}$. The registry never changes so it is
@@
 The semantics are expressed as
-rewrites on strings using pattern matching. Consider the rewrite rule
-for the beginning of a field access instruction:
-$$
-\mprset{flushleft}
-	\inferrule[Field Access(eval)]{}{
-      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgnt{e}\ \cfgt{\$}\ \cfgnt{f}\rp \ \cfgnt{k}\rp  \rcom 
-      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp 
-	}
-$$
-If the string representing the current state matches the left side, then it
-creates the new string on the right. In this example, the new string
-on the right is now evaluating the expression $\cfgnt{e}$ in the field
-access, and it includes the continuation indicating that it still
-needs to complete the actual field access once the expression is
-evaluated.
-
-Other more complex rules, such as one to create a new instance of a
-class, define constraints on the rewrites and more complex
-transformations on the heap.
-$$
-\mprset{flushleft}
-	\inferrule[New]{
-      \cfgnt{r} = \mathrm{stack}_r\lp \rp\\
-      l = \mathrm{fresh}_l\lp \cfgnt{C}\rp\\\\
-      \cfgnt{R}^\prime = \cfgnt{R}[\forall \cfgnt{f} \in \mathit{fields}\lp \mathrm{C}\rp \ \lp \lp l\ \cfgnt{f}\rp  \mapsto \cfgnt{r}_\mathit{null} \rp ] \\\\
-      \cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}]
-    }{
-      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgt{new}\ \cfgnt{C}\rp \ \cfgnt{k}\rp  \rcom
-      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi\ \eta\ \cfgnt{r}\ \cfgnt{k}\rp 
-	}
-$$ In this rule, when the string matches the new-expression, it is
-        rewritten to use a new heap location where all of the fields
-        for the new object point to $\cfgnt{r}_\mathit{null}$ and the
-        location map points a new stack reference to that new object.
-        New heap locations returned from $\mathrm{fresh}_l$ are monotonically
-        increasing.
-        Also note that references for objects from the new-expression are
-        auxiliary literals, so they do not appear in any constraint in
-        the symbolic heap as an aliasing option.
-
+rewrites on strings using pattern matching. 
+%Consider the rewrite rule
+%for the beginning of a field access instruction:
+%$$
+%\mprset{flushleft}
+%	\inferrule[Field Access(eval)]{}{
+%      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgnt{e}\ \cfgt{\$}\ \cfgnt{f}\rp \ \cfgnt{k}\rp  \rcom 
+%      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp 
+%	}
+%$$
+%If the string representing the current state matches the left side, then it
+%creates the new string on the right. In this example, the new string
+%on the right is now evaluating the expression $\cfgnt{e}$ in the field
+%access, and it includes the continuation indicating that it still
+%needs to complete the actual field access once the expression is
+%evaluated.
+%
+%Other more complex rules, such as one to create a new instance of a
+%class, define constraints on the rewrites and more complex
+%transformations on the heap.
+%$$
+%\mprset{flushleft}
+%	\inferrule[New]{
+%      \cfgnt{r} = \mathrm{stack}_r\lp \rp\\
+%      l = \mathrm{fresh}_l\lp \cfgnt{C}\rp\\\\
+%      \cfgnt{R}^\prime = \cfgnt{R}[\forall \cfgnt{f} \in \mathit{fields}\lp \mathrm{C}\rp \ \lp \lp l\ \cfgnt{f}\rp  \mapsto \cfgnt{r}_\mathit{null} \rp ] \\\\
+%      \cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}]
+%    }{
+%      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgt{new}\ \cfgnt{C}\rp \ \cfgnt{k}\rp  \rcom
+%      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi\ \eta\ \cfgnt{r}\ \cfgnt{k}\rp 
+%	}
+%$$ In this rule, when the string matches the new-expression, it is
+%        rewritten to use a new heap location where all of the fields
+%        for the new object point to $\cfgnt{r}_\mathit{null}$ and the
+%        location map points a new stack reference to that new object.
+%        New heap locations returned from $\mathrm{fresh}_l$ are monotonically
+%        increasing.
+%        Also note that references for objects from the new-expression are
+%        auxiliary literals, so they do not appear in any constraint in
+%        the symbolic heap as an aliasing option. 
+%        
 % \input{javalite-common}
@@
 \input{summarize-precise}
+
+\subsection{Symbolic Heap}
+
+%Determining the symbolic state is relatively simple for programs that perform linear manipulations of numeric input parameters.
+However, the task becomes more challenging for programs that accept references as inputs, in part because it is not obvious exactly how many program input parameters there are.
+For example, consider the case of dereferencing an input reference that points to an object that itself contains multiple fields.
+Should each of those field values be included as program input parameters?
+What if some of the fields contain references?
+It would seem as if dereferencing symbolic input references opens the door to a potentially unbounded number of parameters.
+
+%Our solution treats the heap as a hidden input parameter to every program.
+%expressed completely in terms of a black-box symbolic input heap
+%and the input reference parameters.
+
+Certain characteristics of the symbolic heap are preserved by
+the small-step semantics during symbolic execution:
+
+\begin{compactdesc}
+\item[Reference partitions:] Each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
+  heap}% that includes $\cfgnt{r}_\mathit{null}$ (these are created by lazy initialization and are the only references that appear as variables in constraints)
+  ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
+  literals}% that includes $\cfgnt{r}_\mathit{un}$ (these add structure but do not appear elsewhere)
+  ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
+  literals}. %(these appear in environments, expressions, and continuations).
+  Only input heap references appear in constraints to express potential aliasing.
+  Auxiliary literals and stack references are used to define additional structure in the bipartite graph but only stack references can appear in environments, expressions, or continuations.
+\item[Null and Uninitialized:] Every symbolic heap contains 
+two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized,
+  ($\cfgnt{l}_\mathit{un}$)  with corresponding references 
+  $\cfgnt{r}_\mathit{null}$ and $\cfgnt{r}_\mathit{un}$ 
+  where $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
+  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
+  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
+  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. 
+\item[Immutability:] References do not change once added to the
+location map, eliminating any need for constraint rewriting as the program state evolves.
+\item[Determinism:] A reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
+$
+\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
+(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
+$
+where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. 
+\item[Type consistency:] All locations associated with a reference have the same type:
+$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
+(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$
+
+\end{compactdesc}

### 2015-09-10 vmcai-2016-tex/approach.tex
Divided content from section 2.3 into the rest of the text. Changed constraint-location pairs to guarded value sets. Brought back the explanation for the Field Access Eval rewrite rule. Added citiations for other papers using similar benchmarks. Added citation for exponential growth of the binarysearch tree path space. Refactored the evaluation to end with the main conclusion.

@@
 $\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) =
-\{\lp\phi\ \cfgnt{l}\rp\ ...\}$ which returns constraint-location
-pairs where the field $\cfgnt{f}$ is uninitialized.
+\{\lp\phi\ \cfgnt{l}\rp\ ...\}$ which a returns guarded value set 
+containing those locations where the field $\cfgnt{f}$ is uninitialized.
 \[
@@
 For a reference $\cfgnt{r}$ and field $\cfgnt{f}$, the value set function computes 
-the set of locations that the field could dereference to, paired with a local and valid access path constraint
-that is feasible under the current path condition $\phi_g$.
+the guarded value set of locations and access path constraints
+that are feasible under the current path condition $\phi_g$.
 The access path constraint is the union of two local constraints: 
@@
 write). Since the target of the write is $r$, the rule checks that the
-location constraint pairs of $\cfgnt{L}(\cfgnt{r})$ are satisfiable
+constraints of the guarded value set $\cfgnt{L}(\cfgnt{r})$ are satisfiable
 when accessed through the $\cfgnt{r}_x$ chain in the strengthening
@@
 call). In the case that $\phi$ is true then $\cfgnt{r}_\mathit{cur}$
-will point to the constraint location pairs of $\cfgnt{L}(\cfgnt{r})$.
+will point to the guarded value set $\cfgnt{L}(\cfgnt{r})$.
 Whereas, if $\phi$ is false then $\cfgnt{r}_\mathit{cur}$ will
@@
 Consider the example in~\figref{fig:initHeap}(c). In order to to check
-if $\cfgnt{r}_1^i$ and $\cfgnt{r}_2^i$ are equal we first get the constraint location
-pairs associated with each of the references:
+if $\cfgnt{r}_1^i$ and $\cfgnt{r}_2^i$ are equal we first get the 
+guarded value set associated with each of the references:
 \[

### 2015-09-10 vmcai-2016-tex/evaluation.tex
Divided content from section 2.3 into the rest of the text. Changed constraint-location pairs to guarded value sets. Brought back the explanation for the Field Access Eval rewrite rule. Added citiations for other papers using similar benchmarks. Added citation for exponential growth of the binarysearch tree path space. Refactored the evaluation to end with the main conclusion.

@@
 algorithm in Symbolic PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13} 
-and evaluate its efficacy on three Java data structure artifacts.
+and evaluate its efficacy on Java data structure artifacts.
 %SPF includes an implementation of~\gsetxt{} with lazy initialization.
@@
 
-The benchmarks focus on a number of common data structures, including a linked list, binary search tree, and red/black tree.
-The BinarySearchTree test uses the class of the same name from Alan Weiss' book titled ``Data Structures and Algorithm Analysis in Java''.
+The data structures used in the benchmarks are a standard set commonly used in analyses involving heap-manipulating programs~\cite{Deng:2006,Deng:2007,boyapati2002korat,Ferrara:2014,Rosner:2015}, including a linked list, binary search tree, and red/black tree.
+The BinarySearchTree test uses the class of the same name from Alan Weiss' book~\cite{Weiss:1998}.
 The test method first asserts a repOk() invariant, before conducting a traversal to find an arbitrary integer key in the tree.
@@
 For benchmarking purposes, the length of reference chain initializations was limited to some integer $k$.
-More details on $k$-bounding can be found in~\cite{Deng:2007}.
+For both the tree examples, the number of possible non-isomorphic tree structures grows exponentially in k~\cite{Deng:2007}, resulting a corresponding exponential growth in analysis times for case-splitting techniques.
 
@@
 
-The results demonstrate that for these common data structures,
-the complexity of the constraints generated by~\symtxt{} is more 
-than offset by the reduction in paths explored. Performance improvement ranges from $4.8x$ for
+Performance improvement ranges from $4.8x$ for
 BinarySearchTree at $k$=3, to $118x$ for LinkedList at $k$=6. In fact,
@@
 unable to finish, e.g., BinarySearchTree for $k$=4 and LinkedList for
-$k$=8. However, these numbers should 
-not be taken as an indication of performance gains that could be 
-expected in more general analysis situations. Real-world performance
-gain will most likely depend on the proportion of paths avoided that
-would otherwise have been explored via case-splitting.
+$k$=8. The results demonstrate that for these common data structures,
+the complexity of the constraints generated by~\symtxt{} is more 
+than offset by the reduction in paths explored.
 

### 2015-09-10 vmcai-2016-tex/intro.tex
Divided content from section 2.3 into the rest of the text. Changed constraint-location pairs to guarded value sets. Brought back the explanation for the Field Access Eval rewrite rule. Added citiations for other papers using similar benchmarks. Added citation for exponential growth of the binarysearch tree path space. Refactored the evaluation to end with the main conclusion.

@@
 
-The contribution of this work is to build on previous efforts, by demonstrating how to dereference pointers in an unknown symbolic input heap, and by proving that the dereferencing scheme is sound and complete with respect to properties provable by symbolic execution.
+The contribution of this work is to build on previous efforts, by demonstrating an initialization scheme that enables pointer dereferencing in an unknown symbolic input heap, and by proving that the initialization scheme is sound and complete with respect to properties provable by symbolic execution.
 A proof-of-concept implementation also demonstrates the efficiency of value-summary representations, as compared to existing case-splitting methods.

### 2015-09-10 vmcai-2016-tex/lazy.tex
Divided content from section 2.3 into the rest of the text. Changed constraint-location pairs to guarded value sets. Brought back the explanation for the Field Access Eval rewrite rule. Added citiations for other papers using similar benchmarks. Added citation for exponential growth of the binarysearch tree path space. Refactored the evaluation to end with the main conclusion.

--- 2015-05-04 ase-2015-tex/lazy.tex
@@
 one location.
+
+The~\gsetxt{} initialization rules preserve several important properties of the symbolic heap.
+In the heap generated by~\gsetst{}, each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
+  heap}
+  ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
+  literals}
+  ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
+  literals}.
+  Only input heap references appear in constraints to express potential aliasing.
+  Auxiliary literals and stack references are used to define additional structure in the bipartite graph but only stack references can appear in environments, expressions, or continuations.
+Changes to $R$ are monotonically increasing, eliminating any need for constraint rewriting as the program state evolves.
+A reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
+$
+\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
+(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
+$
+where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. 
+All locations associated with a reference have the same type:
+$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
+(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$
 

### 2015-09-10 vmcai-2016-tex/summary-heap.tex
Divided content from section 2.3 into the rest of the text. Changed constraint-location pairs to guarded value sets. Brought back the explanation for the Field Access Eval rewrite rule. Added citiations for other papers using similar benchmarks. Added citation for exponential growth of the binarysearch tree path space. Refactored the evaluation to end with the main conclusion.

@@
 A \emph{symbolic heap} is a tuple $(\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta)$, where the~\emph{location map} $\cfgnt{L}$,~\emph{reference map} $\cfgnt{R}$, and~\emph{environment} $\eta$ are partial functions, and the~\emph{path condition} $\phi$ is a predicate over the program variables.
-Given reference $r$, $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the set of constraint-location pairs (guarded value set) in the heap associated with $r$.
+Given reference $r$, $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the guarded value set in the heap associated with $r$.
 The constraint  associated with each location is a guard
@@
 
-Given an input program $\lp\mu\ \lp\cfgnt{C}\ \cfgnt{m}\rp\rp$, the initial machine state is
+Execution begins with the initial machine state. The expression for the initial state constructs a new object of type
+$\cfgnt{C}$ and then invokes the method $\cfgnt{m}$ in that
+object. The initial symbolic heap contains 
+two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized,
+  ($\cfgnt{l}_\mathit{un}$)  with corresponding references 
+  $\cfgnt{r}_\mathit{null}$ and $\cfgnt{r}_\mathit{un}$ 
+  where $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
+  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
+  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
+  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. 
+Given an input program $\lp\mu\ \lp\cfgnt{C}\ \cfgnt{m}\rp\rp$, the expression for the initial machine state is
 $$
@@
 $$
-The expression in the initial state constructs a new object of type
-$\cfgnt{C}$ and then invokes the method $\cfgnt{m}$ in that
-object.
 
@@
 rewrites on strings using pattern matching. 
-%Consider the rewrite rule
-%for the beginning of a field access instruction:
-%$$
-%\mprset{flushleft}
-%	\inferrule[Field Access(eval)]{}{
-%      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgnt{e}\ \cfgt{\$}\ \cfgnt{f}\rp \ \cfgnt{k}\rp  \rcom 
-%      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp 
-%	}
-%$$
-%If the string representing the current state matches the left side, then it
-%creates the new string on the right. In this example, the new string
-%on the right is now evaluating the expression $\cfgnt{e}$ in the field
-%access, and it includes the continuation indicating that it still
-%needs to complete the actual field access once the expression is
-%evaluated.
+Consider the rewrite rule
+for the beginning of a field access instruction:
+$$
+\mprset{flushleft}
+	\inferrule[Field Access(eval)]{}{
+      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgnt{e}\ \cfgt{\$}\ \cfgnt{f}\rp \ \cfgnt{k}\rp  \rcom 
+      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp 
+	}
+$$
+If the string representing the current state matches the left side, then it
+creates the new string on the right. In this example, the new string
+on the right is now evaluating the expression $\cfgnt{e}$ in the field
+access, and it includes the continuation indicating that it still
+needs to complete the actual field access once the expression is
+evaluated.
 %
@@
 %
+
 The rewrite relations for the portion of the language
@@
 
-\subsection{Symbolic Heap}
-
 %Determining the symbolic state is relatively simple for programs that perform linear manipulations of numeric input parameters.
@@
 %and the input reference parameters.
-
-Certain characteristics of the symbolic heap are preserved by
-the small-step semantics during symbolic execution:
-
-\begin{compactdesc}
-\item[Reference partitions:] Each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
-  heap}% that includes $\cfgnt{r}_\mathit{null}$ (these are created by lazy initialization and are the only references that appear as variables in constraints)
-  ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
-  literals}% that includes $\cfgnt{r}_\mathit{un}$ (these add structure but do not appear elsewhere)
-  ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
-  literals}. %(these appear in environments, expressions, and continuations).
-  Only input heap references appear in constraints to express potential aliasing.
-  Auxiliary literals and stack references are used to define additional structure in the bipartite graph but only stack references can appear in environments, expressions, or continuations.
-\item[Null and Uninitialized:] Every symbolic heap contains 
-two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized,
-  ($\cfgnt{l}_\mathit{un}$)  with corresponding references 
-  $\cfgnt{r}_\mathit{null}$ and $\cfgnt{r}_\mathit{un}$ 
-  where $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
-  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
-  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
-  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. 
-\item[Immutability:] References do not change once added to the
-location map, eliminating any need for constraint rewriting as the program state evolves.
-\item[Determinism:] A reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
-$
-\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
-(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
-$
-where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. 
-\item[Type consistency:] All locations associated with a reference have the same type:
-$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
-(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$
-
-\end{compactdesc}

### 2015-09-10 vmcai-2016-tex/approach.tex
Corrected numerous typos throughout the paper.

@@
 in~\figref{fig:initHeap}(d) represents the various sets constructed in
-initialization rule for $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$. We
-also define values of constraints used as labels in the graph.
+the initialization $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$.
 
@@
 initialized on the field $\cfgnt{f}$. The symbolic heap is further
-modified to include a new stack reference pointing to the value set
+modified to include a new stack reference pointing to the guarded value set
 (possible values of the field) returned during the dereferencing; the

### 2015-09-10 vmcai-2016-tex/bisimulation.tex
Corrected numerous typos throughout the paper.

@@
 
-In the lemma, $S$ is the universe of well-formed states, and the
-set $S_A \subseteq S$ is states at a field access continuation having computed the base reference.
+In the following lemma, $S$ is the universe of well-formed states, and $S_{FA} \subseteq S$ is the set of states at a field access continuation having computed the base reference.
 \begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]

### 2015-09-10 vmcai-2016-tex/evaluation.tex
Corrected numerous typos throughout the paper.

@@
 that the benefit of decreasing the number of paths explored is
-offset by the increased complexity of the underlying constraints problem.
+offset by the increased complexity of the resulting path condition.
 
@@
 results for these artifacts. A table entry of  '-' indicates the analysis
-exceeded the allotted time bound of 10 minutes.
+exceeded the allotted time bound of 1 hour.
 
@@
 BinarySearchTree at $k$=3, to $118x$ for LinkedList at $k$=6. In fact,
-for some $k$-bounds a number of experiments completed exploration
-using the \symtxt{} algorithm in a few seconds whereas \gsetxt{} or Lazier\# were
+for some $k$-bounds a number of experiments complete exploration
+using the \symtxt{} algorithm in a few seconds whereas \gsetxt{} or Lazier\# are
 unable to finish, e.g., BinarySearchTree for $k$=4 and LinkedList for

### 2015-09-10 vmcai-2016-tex/intro.tex
Corrected numerous typos throughout the paper.

@@
 
-In symbolic execution, the values of program variables are represented as constraints over the program’s inputs.
+In symbolic execution, the values of program variables are represented as constraints over the program's inputs.
 During the course of an execution, a program variable may assume a number of possible values under a variety of different conditions.
-One way to represent this behavior is by pairing each possible value with the with the constraints under which it is assumed.
-A set of such value-constraint pairs, called a \emph{guarded value set}, represents the state of a program variable.
+One way to represent this behavior is by pairing each possible value with the constraints under which it is assumed.
+A set of such value-constraint pairs, called a \emph{guarded value set}\footnote{Guarded value sets are variously referred to in the literature as \emph{guarded location sets}, \emph{symbolic value sets}, or \emph{value summaries}.
+The term guarded value set is sometimes abbreviated in this text as~\emph{value set}.}, represents the state of a program variable.
 

### 2015-09-10 vmcai-2016-tex/lazy.tex
Corrected numerous typos throughout the paper.

@@
   Only input heap references appear in constraints to express potential aliasing.
-  Auxiliary literals and stack references are used to define additional structure in the bipartite graph but only stack references can appear in environments, expressions, or continuations.
+  Auxiliary literals and stack references are used to define additional structure in the heap but only stack references can appear in environments, expressions, or continuations.
 Changes to $R$ are monotonically increasing, eliminating any need for constraint rewriting as the program state evolves.

### 2015-09-10 vmcai-2016-tex/rw.tex
Corrected numerous typos throughout the paper.

@@
 \label{sec:related}
-
-\subsection{Program Analysis using Symbolic Heaps}
+%
+%\subsection{Program Analysis using Symbolic Heaps}
 The symbolic heap methods in this work build upon a
-number of prior program analysis techniques that use sets of guarded values to
+number of prior program analysis techniques that use guarded value sets to
 represent program
@@
 Since dereferencing is a fundamental problem treated in this paper, we believe these other works to be both orthogonal and complimentary to our own.
-
-\subsection{Other Heap Representations in Symbolic Execution}
+%
+%\subsection{Other Heap Representations in Symbolic Execution}
 %Need to talk about GSE, DSE, SAGE, PEX
@@
 
-\subsection{Formal Results on Symbolic Heaps}
+%
+%\subsection{Formal Results on Symbolic Heaps}
 The symbolic heap used by SAGE~\cite{Elkarablieh:2009} was shown to be sound and complete for programs with input-independent memory allocation.

### 2015-09-10 vmcai-2016-tex/summary-heap.tex
Corrected numerous typos throughout the paper.

@@
 
-Symbolic execution semantics are is defined using
+Symbolic execution semantics are defined using
 a small-step operational semantics similar to the one presented 
@@
 represented by circles and locations are represented by squares. Arrows leaving
-references correspond to the value sets returned by the $\cfgnt{L}$ function, and 
+references correspond to the guarded value sets returned by the $\cfgnt{L}$ function, and 
 arrows leaving the squares correspond to the $\cfgnt{R}$ function.
@@
 the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. The continuation
-$\cfgnt{k}$ indicates with $\cfgnt{*}$ where the expression $\cfgnt{e}$ came from, stores
+$\cfgnt{k}$ indicates with the symbol $\cfgnt{*}$ where the expression $\cfgnt{e}$ came from, stores
 temporary computation, and keeps track of the next continuation. For
@@
 object. The initial symbolic heap contains 
-two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized,
-  ($\cfgnt{l}_\mathit{un}$)  with corresponding references 
+two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized
+  ($\cfgnt{l}_\mathit{un}$),  with corresponding references 
   $\cfgnt{r}_\mathit{null}$ and $\cfgnt{r}_\mathit{un}$ 
@@
 expected way. It is assumed that only type safe programs are input to
-the machine so there is no type checking or error conditions. The
-machine simply halts if no rewrite is enabled.
+the machine so there is no type checking. The
+machine halts if no rewrite is enabled.
 

### 2015-09-10 vmcai-2016-tex/approach.tex
Re-worked parts of the introduction for clarity. Added transition material to sections on GSE and symbolic initialization.

@@
-\section{Generating and Updating Symbolic Heaps}
+\section{Symbolic Initialization}
 \label{sec:precise}
+Although the case-splitting methods used in~\gsetxt{} can be applied
+to guarded value sets, a direct implementation would run into the same
+path explosion problems. This work presents a new initialization scheme which avoids the
+nondeterminism introduced by~\gsetxt{}. Called \emph{\symtxt{}}, this scheme leverages the core idea in generalized symbolic execution
+with lazy initialization, using on-the-fly reasoning to model a
+black-box input heap during symbolic execution. Unlike~\gsetxt{}, \symtxt{} constructs a single
+symbolic heap and polynomially-sized path condition for each control
+flow path.
 
-Unlike~\gsetxt{}, the symbolic heap algorithm only partitions the heap at comparison
-operations or for exception handling.  There are three sets of rewrite
-rules specific to the symbolic heap algorithm: (i) rules to initialize
+There are three sets of rewrite
+rules specific to the~\symtxt{} algorithm: (i) rules to initialize
 symbolic references, (ii) rules to perform field dereferences and

### 2015-09-10 vmcai-2016-tex/intro.tex
Re-worked parts of the introduction for clarity. Added transition material to sections on GSE and symbolic initialization.

@@
 A common hurdle to using guarded value sets is the treatment of symbolic heap inputs.
-Precisely modeling operations on heap inputs is challenging because it requires formulating logical predicates over an input domain that contains a potentially unbounded number of references~\cite{Chen:2013,Qu:2011}.
-Manually creating test inputs can be a time consuming and error-prone process, automatic case-splitting methods~\cite{GSE03,Deng:2007} quickly produce an overwhelming number of execution paths, and user-supplied logical invariants require a high degree of skill to create.
+For many applications, it is desirable to model the input heap as a black box, with operations over the input references providing the only means of divining its structure.
+Precisely modeling operations on black-box heap inputs is challenging because it requires formulating logical predicates over an input domain that contains a potentially unbounded number of hidden references~\cite{Chen:2013,Qu:2011}.
+Generalized symbolic execution (\gsetxt{}) methods~\cite{GSE03,Deng:2007} provide an accurate solution, but they quickly produce an overwhelming number of execution paths for all but the simplest heap shapes.
+Efforts to extend~\gsetxt{} principles to guarded value sets have failed to produce provably equivalent results.
 Thus, despite the advantages of using guarded value sets, it remains an open question how they can be used in symbolic execution to automatically model all possible program behaviors in the case of an arbitrary input heap.

### 2015-09-10 vmcai-2016-tex/lazy.tex
Re-worked parts of the introduction for clarity. Added transition material to sections on GSE and symbolic initialization.

@@
 \label{app:gse}
+Several projects have generalized the core idea of symbolic execution,
+enabling it to be applied to programs with more general types,
+including references and
+arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. These
+generalized symbolic execution (\gsetxt{}) techniques work by branching over
+multiple copies of the system state during dereferencing operations, creating
+new location symbols on an as-needed basis in a process called~\emph{lazy initialization}.
+
 The rules to generalized symbolic execution with

### 2015-09-11 vmcai-2016-tex/approach.tex
All sections were edited to remove first-person voice, e.g. we, our, etc.

@@
 
-We visualize the initialization process in~\figref{fig:initHeap}. The
+\figref{fig:initHeap} illustrates the initialization process. The
 graph in~\figref{fig:initHeap}(a) represents the initial heap. The
@@
 There are two rewrite rules in~\figref{fig:fHeap}(a), one for reading
-the value of a field (field-access) and the other when we write to a
+the value of a field (field-access) and the other for writing to a
 field (field-write). Both rules first check that the operations can be
@@
 $\cfgnt{r}_0$ \emph{does not} point to those locations under any
-constraint. We use the three sets of constraints to create a new path condition $\phi_g^\prime$
-as an update of the current path condition $\phi_g$. We add to $\phi_g$ the disjunction of the
+constraint. The three sets of constraints are used to create a new path condition $\phi_g^\prime$
+as an update of the current path condition $\phi_g$.  The update is accomplished by first taking the disjunction of the
 constraints in $\Phi_\alpha$ to indicate that if any of the
 constraints are satisfiable, then references $\cfgnt{r}_0$ and
-$\cfgnt{r}_1$ can be equal. Furthermore, we conjoin to the global heap
-constraint $\phi_g^\prime$, the conjunctions of negations to the
-constraints in $\Phi_0$ and $\Phi_1$. This indicates for locations
+$\cfgnt{r}_1$ can be equal. This disjunction is then conjoined with $\phi_g$ to form $\phi_g^\prime$. Furthermore, the conjunctions of negations to the
+constraints in $\Phi_0$ and $\Phi_1$ is conjoined with $\phi_g^\prime$. This indicates for locations
 that are not common to the references, the negations of their
@@
 possible on any symbolic heap. Before the rewrite rule returns
-$\cfgt{true}$ we check the satisfiability of the updated global heap
+$\cfgt{true}$, it verifies the satisfiability of the updated global heap
 constraint. The reference-false is the logical dual of the rule.
 
-Consider the example in~\figref{fig:initHeap}(c). In order to to check
-if $\cfgnt{r}_1^i$ and $\cfgnt{r}_2^i$ are equal we first get the 
+Consider the example in~\figref{fig:initHeap}(c). In order to compare
+$\cfgnt{r}_1^i$ and $\cfgnt{r}_2^i$, the Equals rule gets the 
 guarded value set associated with each of the references:

### 2015-09-11 vmcai-2016-tex/conclusion.tex
All sections were edited to remove first-person voice, e.g. we, our, etc.

--- 2015-05-15 ase-2015-tex/conclusion.tex
@@
 
-In this work, we present a
+This work presents a
 heap representation for symbolic execution that maintains exactness,
@@
 execution techniques, and in some cases, the performance gains are
-considerable. We believe that performance gains in symbolic execution
-can naturally benefit a variety of analyses based on symbolic
+considerable. The performance gains in symbolic execution
+may naturally benefit a variety of analyses based on symbolic
 execution, for example, verification of properties, especially those
@@
 techniques such as directed incremental symbolic
-execution~\cite{person:pldi2011}, and other back-end analyses. In
-future work we plan to evaluate the impact of analyses that rely on
+execution~\cite{person:pldi2011}, and other back-end analyses. Potential future work includes evaluating the impact of analyses that rely on
 symbolic execution.

### 2015-09-11 vmcai-2016-tex/evaluation.tex
All sections were edited to remove first-person voice, e.g. we, our, etc.

@@
 
-To resolve this question, we implemented a prototype of the \symtxt{} 
-algorithm in Symbolic PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13} 
-and evaluate its efficacy on Java data structure artifacts.
+To resolve this question, a prototype of the \symtxt{} 
+algorithm was developed in the Symbolic PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13} framework
+to evaluate its efficacy on Java data structure artifacts.
 %SPF includes an implementation of~\gsetxt{} with lazy initialization.
@@
 to the Generalized Symbolic Execution, Lazier\#, and \symtxt{}
-algorithms, respectively. Note that we omit the results for
-the Lazier algorithm because they are nearly identical to the Lazier\#
+algorithms, respectively. The results for
+the Lazier algorithm are omitted because they are nearly identical to the Lazier\#
 results for these artifacts. A table entry of  '-' indicates the analysis

### 2015-09-11 vmcai-2016-tex/lazy.tex
All sections were edited to remove first-person voice, e.g. we, our, etc.

@@
 The~\gsetxt{} initialization rules preserve several important properties of the symbolic heap.
-In the heap generated by~\gsetst{}, each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
+In the heap generated by~\gsetxt{}, each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
   heap}

### 2015-09-11 vmcai-2016-tex/rw.tex
All sections were edited to remove first-person voice, e.g. we, our, etc.

@@
 While these methods demonstrate the utility of value sets in combination with symbolic execution, none of these techniques address dereferencing of symbolic input references.
-Since dereferencing is a fundamental problem treated in this paper, we believe these other works to be both orthogonal and complimentary to our own.
+Since dereferencing is a fundamental problem treated in this paper, these other works may be considered both orthogonal and complimentary to~\symtxt{}.
 %
@@
 theory of fixed-length arrays to model the heap, and is thus incomplete
-for programs with input-dependent memory allocation. We believe that the 
+for programs with input-dependent memory allocation. It is hoped that the 
 techniques presented in this work can be used to extend practical tools 
@@
 %\subsection{Formal Results on Symbolic Heaps}
-The symbolic heap used by SAGE~\cite{Elkarablieh:2009} was shown to be sound and complete for programs with input-independent memory allocation.
-Our method is sound and complete for all states reached by symbolic execution.
+The symbolic heap used by SAGE~\cite{Elkarablieh:2009} was shown to be sound and complete for programs with input-independent memory allocation.~\symtxt{} is sound and complete for all states reached by symbolic execution.
 
 Recently, several separation logic solvers have been proven to be sound and complete for heaps with linked lists, trees~\cite{Piskac:2014}, or data structures satisfying user-supplied invariants~\cite{Brotherston:2014}.
-In contrast, our method is sound and complete without restriction on data structures, and requires no explicit invariants, but our result is restricted to the properties provable by symbolic execution.
+In contrast,~\symtxt{} is sound and complete without restriction on data structures, and requires no explicit invariants, but this result is restricted to the properties provable by symbolic execution.
 

### 2015-09-12 vmcai-2016-tex/bisimulation.tex
All sections were edited to remove first-person voice, e.g. we, our, etc.
Revision and refactor

@@
 \label{sec:bisim}
-A major drawback of previous methods for creating test inputs for
-symbolic heaps has been a lack of completeness. Incomplete heap
-representations may not create a set of inputs that represents
+
+Incomplete heap representations may not create a set of inputs that represents
 the entire space of possible inputs. By missing some possible
 inputs, the subsequent analysis may fail to recognize 
-possible program behaviors.
-
-The theorems in this section establish the soundness and
-completeness of the symbolic heap approach with respect to Generalized
-Symbolic Execution (\gsetxt{}). Intuitively, the theorems imply that any properties proven
-with~\gsetxt{} can also be proved using the symbolic heap
-algorithm. The proofs for the theorems, as well as
+possible program behaviors. The theorems in this section establish the soundness and
+completeness of symbolic initialization with respect to classical GSE with lazy initialization. Intuitively, the theorems imply that any properties proven
+with~\gsetxt{} can also be proved using symbolic initialization. The proofs for the theorems, as well as
 the complete set of semantic rules for~\gsetxt{} and~\symtxt{} can
@@
 The relation captures the notion of splitting groups of heaps at
-certain operations. For example, suppose we have a set $P$ containing a single state $p$
+certain operations. For example, suppose a set $P$ contains a single state $p$
 with all references uninitialized. If $p$ is a field access state, it has two

### 2015-09-12 vmcai-2016-tex/intro.tex
Minor tweak to the intro.
Revision and refactor

@@
 A common hurdle to using guarded value sets is the treatment of symbolic heap inputs.
-For many applications, it is desirable to model the input heap as a black box, with operations over the input references providing the only means of divining its structure.
-Precisely modeling operations on black-box heap inputs is challenging because it requires formulating logical predicates over an input domain that contains a potentially unbounded number of hidden references~\cite{Chen:2013,Qu:2011}.
+For many applications, it is desirable to model the input heap as unconstrained, with operations over the input references providing the only means of divining its structure.
+Precisely modeling operations on unconstrained heap inputs is challenging because it requires formulating logical predicates over an input domain that contains a potentially unbounded number of hidden references~\cite{Chen:2013,Qu:2011}.
 Generalized symbolic execution (\gsetxt{}) methods~\cite{GSE03,Deng:2007} provide an accurate solution, but they quickly produce an overwhelming number of execution paths for all but the simplest heap shapes.
-Efforts to extend~\gsetxt{} principles to guarded value sets have failed to produce provably equivalent results.
+Efforts to extend~\gsetxt{} principles to guarded value sets have failed to produce provably equivalent results \cite{LISTEFFORTS}.
 Thus, despite the advantages of using guarded value sets, it remains an open question how they can be used in symbolic execution to automatically model all possible program behaviors in the case of an arbitrary input heap.
 
-The contribution of this work is to build on previous efforts, by demonstrating an initialization scheme that enables pointer dereferencing in an unknown symbolic input heap, and by proving that the initialization scheme is sound and complete with respect to properties provable by symbolic execution.
-A proof-of-concept implementation also demonstrates the efficiency of value-summary representations, as compared to existing case-splitting methods.
+The contribution of this work is a symbolic initialization scheme for uninitialized pointers in a fully symbolic heap.
+Where GSE lazily instantiates uninitialized pointers to either reference NULL, a new instance of the correct type, or an alias to a previously initialized object, the symbolic initialization in this work creates a guarded value set expressing all of these eventualities in the same symbolic heap.
+Where GSE branches the search space on each choice, symbolic initialization does not.
+Symbolic initialization only branches on reference compares, partitioning the symbolic to indicate heaps where the references alias and heaps where the references do not.
+
+This paper includes a proof that symbolic initialization is sound and complete with respect to properties provable by GSE.
+Such a results is important because it means that symbolic initialization can be used to create input heaps for other analyses in a way that is provably correct with regards to GSE: there are no missing heaps and there are no extra heaps.
+
+A proof-of-concept implementation of symbolic initialization is reported in this paper.
+It demonstrates the efficiency of~\symtxt{}, as compared to existing~\gsetxt{} methods.
+The use of the guarded value sets does require extra interaction with an SMT solver, but the savings in representing multiple heap shapes in a single representation overcomes the cost of the solver calls.
+In fact, the comparison shows an exponential increase in the number of heaps that can be analyzed in a set of benchmark examples meaning that other approaches based on~\gsetxt\ fail to complete.

### 2015-09-12 vmcai-2016-tex/lazy.tex
Revision and refactor

--- 2015-09-10 vmcai-2016-tex/lazy.tex
@@
-\subsection{Generalized Symbolic Execution}
+\section{GSE}
 \label{app:gse}
-The rules to generalized symbolic execution with
-lazy initialization using the symbolic heap are in
-\figref{fig:lazyInit} for the initialization and \figref{fig:lazy} for
-how the initialization is used. Specifically, the field-access rule in
-\figref{fig:lazy} uses initialization, $\rightarrow_I^*$, to ensure
-the accessed field is instantiated. Initialization in generalized
-symbolic execution never happens for more than one object on any use
-of $\rightarrow_I^*$: $\Lambda$ is either empty or contains exactly
-one location.
+Classical GSE and its variants all subscribe to the same ideal: an uninitialized object may be lazily initialized
+in a non-deterministic way to null, a new instance of the object, or an to
+an object of the same type also initialized lazily (i.e., the \emph{input heap}) \cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. The
+non-determinism creates branches in the execution
+tree during state space exploration. GSE semantics are defined here to give insight to symbolic initialization and support the proof that it preserves GSE behaviors.
 
-The~\gsetxt{} initialization rules preserve several important properties of the symbolic heap.
-In the heap generated by~\gsetst{}, each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
-  heap}
+The rules for classical GSE using the symbolic heap are in
+\figref{fig:lazyInit} for lazy initialization: NULL, new, and alias.
+Fresh references and locations strictly increase so it is possible to minimize over a set to find the first created.
+References are partitioned to support latter proofs: $\mathrm{init}_\cfgnt{r}()$ for the input
+  heap
   ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
@@
     literals}.
-  Only input heap references appear in constraints to express potential aliasing.
-  Auxiliary literals and stack references are used to define additional structure in the heap but only stack references can appear in environments, expressions, or continuations.
-Changes to $R$ are monotonically increasing, eliminating any need for constraint rewriting as the program state evolves.
-A reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
-$
-\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
-(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
-$
-where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. 
-All locations associated with a reference have the same type:
-$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
-(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$
+  In general, as shown in the next section,
+  only input heap references appear in constraints to express potential aliasing, and only stack references can appear in environments, expressions, or continuations.
+Finally, the \emph{isInit} is true for initialized references from the input heap (i.e., potential aliases).
 
-An uninitialized object may be lazily initialized
-non-deterministically to null, a new instance of the object, or an to
-an object of the same type also initialized lazily. The
-non-deterministic initialization creates branches in the execution
-tree during state space exploration.
+How the lazy
+initialization is used is defined in \figref{fig:lazy}. Specifically,
+the field-access rule in \figref{fig:lazy} uses initialization,
+$\rightarrow_I^*$, to ensure the accessed field is
+instantiated. Initialization in generalized symbolic execution never
+happens for more than one object on any use of $\rightarrow_I^*$:
+$\Lambda$ is either empty or contains exactly one location.
+The rest of the rules in \figref{fig:lazy} do not initialize, but they are included to elucidate how symbolic initialization differs from GSE with lazy initialization.
 
-The $\rgse$ relation is a union over branching points on control flow
+The $\rgse$ relation defined in \figref{fig:lazy} is a union over branching points on control flow
 to support the final proof of the existence of a
@@
 initialization, it is not the initialization where control flow
-diverges in program execution. Rather, that occurs at branches and
-exceptions, and that is reflected in the composition of $\rgse$.
+diverges in program execution. Rather, that occurs at branches and NULL-exceptions, and that is reflected in the composition of $\rgse$.
 

### 2015-09-12 vmcai-2016-tex/summary-heap.tex
Revision and refactor

@@
-\section{Prelimiaries}
-\label{sec:sh}
+\section{A Symbolic Heap}
+A \emph{symbolic heap} is a tuple
+$(\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta)$, where the~\emph{location map}
+$\cfgnt{L}$,~\emph{reference map} $\cfgnt{R}$, and~\emph{environment}
+$\eta$ are partial functions, and the~\emph{path condition} $\phi$ is
+a predicate over the program variables. Given reference $r$,
+$\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the guarded value set
+in the heap associated with $r$. The constraint associated with each
+location is a guard representing the conditions under which the
+associated reference maps to the given location. By definition, any
+location appears at most once in any given value set. Unions of value
+sets containing the same location are resolved by forming a
+disjunction of the constraints from each set. $\cfgnt{R}(\cfgnt{l},
+\cfgnt{f}) = \cfgnt{r}$ is the reference associated with the given
+location-field pair in the heap.
 
-\subsection{Symbolic Execution}
+\begin{figure}[t]
+\begin{center}
+\includegraphics[scale=0.5]{../figs/simple_heap_scratch.pdf}
+\end{center}
+\caption{Example Symbolic Heap}
+\label{fig:exampleHeap}
+\end{figure}
 
-Symbolic execution semantics are defined using
-a small-step operational semantics similar to the one presented 
-in~\cite{saints-MS}. The small-step semantics,
-defined as a syntactic machine using a CESK architecture~\cite{Felleisen:1992},
-are modified to perform symbolic execution on a symbolic heap. The
-surface (input) syntax and machine (state) syntax are shown
+Conceptually, the symbolic heap may be thought of as a bipartite
+graph. \figref{fig:exampleHeap} shows an example symbolic heap
+graph. References are represented by circles and locations are
+represented by squares. Arrows leaving references correspond to the
+guarded value sets returned by the $\cfgnt{L}$ function, and arrows
+leaving the squares correspond to the $\cfgnt{R}$ function. The
+reference $\cfgnt{r}_1$ has has two members in it guarded value set,
+so the location pointed to by $\cfgnt{r}_1$ depends on its aliasing
+relationship to $\cfgnt{r}_0$.
+
+The reference $\cfgnt{r}_\mathit{un}$ is a special reference to
+indicate something that has yet to be initialized. In general,every
+symbolic heap contains two special locations, null
+($\cfgnt{l}_\mathit{null}$), and uninitialized
+($\cfgnt{l}_\mathit{un}$), with corresponding references
+$\cfgnt{r}_\mathit{null}$ and $\cfgnt{r}_\mathit{un}$ where
+$\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
+\{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
+$\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
+\{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$.
+
+For well-formed symbolic heaps, a reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
+$
+\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
+(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
+$
+where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. Also, for a well-formed heap, all locations associated with a reference have the same type:
+$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
+(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$
+
+\section{Operational Semantics}
+This paper defines symbolic initialization using
+a small-step operational semantics in the context of a syntactic machine with a CESK architecture~\cite{Felleisen:1992, saints-MS}. The
+surface (input) syntax and machine (state) syntax (which omits the symbolic heap definition previously given and the environment) are shown
 in~\figref{fig:syntax}. Terminals are in bold face while non-terminals
@@
 
-A \emph{symbolic heap} is a tuple $(\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta)$, where the~\emph{location map} $\cfgnt{L}$,~\emph{reference map} $\cfgnt{R}$, and~\emph{environment} $\eta$ are partial functions, and the~\emph{path condition} $\phi$ is a predicate over the program variables.
-Given reference $r$, $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the guarded value set in the heap associated with $r$.
-The constraint  associated with each location is a guard
-representing the conditions under which the associated reference
-maps to the given location. By definition, any location appears 
-at most once in any given value set. Unions of value sets containing
-the same location are resolved by forming a disjunction of the constraints
-from each set. $\cfgnt{R}(\cfgnt{l}, \cfgnt{f}) = \cfgnt{r}$ is the
-reference associated with the given location-field pair in the
-heap. The environment  $\eta$ maps local variables to references.
-
-\begin{figure}[t]
-\begin{center}
-\includegraphics[scale=0.5]{../figs/simple_heap_scratch.pdf}
-\end{center}
-\caption{Example Symbolic Heap}
-\label{fig:exampleHeap}
-\end{figure}
-
-Conceptually, the symbolic heap may be thought of as a bipartite graph. \figref{fig:exampleHeap} shows an example symbolic heap graph. References are 
-represented by circles and locations are represented by squares. Arrows leaving
-references correspond to the guarded value sets returned by the $\cfgnt{L}$ function, and 
-arrows leaving the squares correspond to the $\cfgnt{R}$ function.
-
 The machine state $\cfgnt{s}$ includes the program
-registry $\mu$, the symbolic heap,
-and the continuation $\cfgnt{k}$. The registry never changes so it is
-omitted from the state tuple in the rest of the presentation.  The
-more complex structures, such as the environment and heap, are defined
-as singly linked lists of mappings that start with empty, \cfgnt{mt}. These lists are treated as
-partial functions so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
+registry $\mu$, the symbolic heap, the global path constraint, the environment $\eta$, the current expression (i.e., program), and the continuation $\cfgnt{k}$. The registry never changes so it is
+omitted from the state tuple in the rest of the presentation. The environment is a partial function so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
 $\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation
@@
 partial function $\eta^\prime$ that is the same as $\eta$ except that
-the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. The continuation
+the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. This notation is used with symbolic heaps as well.
+
+The continuation
 $\cfgnt{k}$ indicates with the symbol $\cfgnt{*}$ where the expression $\cfgnt{e}$ came from, stores
@@
 
-Execution begins with the initial machine state. The expression for the initial state constructs a new object of type
-$\cfgnt{C}$ and then invokes the method $\cfgnt{m}$ in that
-object. The initial symbolic heap contains 
-two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized
-  ($\cfgnt{l}_\mathit{un}$),  with corresponding references 
-  $\cfgnt{r}_\mathit{null}$ and $\cfgnt{r}_\mathit{un}$ 
-  where $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
-  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
-  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
-  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. 
 Given an input program $\lp\mu\ \lp\cfgnt{C}\ \cfgnt{m}\rp\rp$, the expression for the initial machine state is
@@
 $$
-
 The semantics are expressed as
@@
 
-The rewrite relations for the portion of the language
-semantics that are common to both generalized symbolic execution and
-the symbolic heap algorithm may be found in \cite{Hillery:2015}. The relation $\rcom$ includes all of these
-rules. Excepting \textrm{N{\footnotesize EW}}, the rules do not update
+The rewrite relations for the more mundane portions of the language
+that do not update the symbolic heap are in the appendix with more details in 
+\cite{Hillery:2015}. Excepting \textrm{N{\footnotesize EW}}, the rules do not update
 the heap, and are largely concerned with argument evaluation in an
@@
 the machine so there is no type checking. The
-machine halts if no rewrite is enabled.
+machine halts if no rewrite is enabled. In the rest of this paper the relation $s \rcom
+s^\prime$ indicates that two states are related by these more
+mundane rules.
 

### 2015-09-12 vmcai-2016-tex/intro.tex
Fixed some obvious dumbness

@@
 Where GSE branches the search space on each choice, symbolic initialization does not.
-Symbolic initialization only branches on reference compares, partitioning the symbolic to indicate heaps where the references alias and heaps where the references do not.
+Symbolic initialization only branches on reference compares, partitioning the symbolic heap to indicate heaps where the references alias and heaps where the references do not.
 
 This paper includes a proof that symbolic initialization is sound and complete with respect to properties provable by GSE.
-Such a results is important because it means that symbolic initialization can be used to create input heaps for other analyses in a way that is provably correct with regards to GSE: there are no missing heaps and there are no extra heaps.
+Such a result is important because it means that symbolic initialization can be used to create input heaps for other analyses in a way that is provably correct with regards to GSE: there are no missing heaps and there are no extra heaps.
 

### 2015-09-12 vmcai-2016-tex/summary-heap.tex
Fixed some obvious dumbness

@@
 The reference $\cfgnt{r}_\mathit{un}$ is a special reference to
-indicate something that has yet to be initialized. In general,every
+indicate something that has yet to be initialized. In general, every
 symbolic heap contains two special locations, null
@@
 \end{center}
-\caption{ (a) The surface syntax. (b) The machine syntax with $\bowtie\ \in \{\wedge,\vee,\Rightarrow\}$.}
+\caption{ (a) The surface syntax. (b) The machine syntax.}
 \label{fig:syntax}
@@
 
+\begin{comment}
 Given an input program $\lp\mu\ \lp\cfgnt{C}\ \cfgnt{m}\rp\rp$, the expression for the initial machine state is
@@
 $$
+\end{comment}
+
 The semantics are expressed as

### 2015-09-12 vmcai-2016-tex/lazy.tex
Some more changes

@@
 $\Lambda$ is either empty or contains exactly one location.
+This property is an artifact of how GSE case spits when it instantiates: each choice is a new unique heap.
 The rest of the rules in \figref{fig:lazy} do not initialize, but they are included to elucidate how symbolic initialization differs from GSE with lazy initialization.
@@
 bisimulation. Although it is apparent that there is non-determinism in
-initialization, it is not the initialization where control flow
-diverges in program execution. Rather, that occurs at branches and NULL-exceptions, and that is reflected in the composition of $\rgse$.
+initialization at the first reference access partitioning the search space, control flow branches at comparisons and NULL-exceptions. This property is reflected in the composition of $\rgse$.
 

### 2015-09-12 vmcai-2016-tex/summary-heap.tex
Some more changes

@@
 \section{A Symbolic Heap}
-A \emph{symbolic heap} is a tuple
+A \emph{symbolic heap}, as defined in this work, is a tuple
 $(\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta)$, where the~\emph{location map}

### 2015-09-12 vmcai-2016-tex/abstract.tex
Revision and refactor
edits to evaluation and conclusion

@@
-A recent trend in symbolic execution of object-oriented programs is the modeling of references as sets of guarded values, enabling multiple heap shapes to be represented in a single state.
-A fundamental problem with using these guarded value sets is the creation of test inputs for programs accepting symbolic reference input parameters.
-Although several solutions have been proposed, none have been proven to be sound and complete with respect to the properties provable by generalized symbolic execution (GSE).
-This work presents a method for initializing reference inputs in a black-box symbolic input heap that exactly preserves GSE semantics.
-A correctness proof for the initialization scheme is provided, as well as the results of an empirical evaluation of a proof-of-concept implementation.
-The initialization technique can be used to ensure that guarded value set based symbolic execution engines operate in a provably correct manner with regards to symbolic references.
+A recent trend in the analysis of object-oriented programs is the
+modeling of references as sets of guarded values, enabling multiple
+heap shapes to be represented in a single state. A fundamental problem
+with using these guarded value sets is the creation of test inputs for
+programs accepting symbolic reference input parameters. Although
+several solutions have been proposed, none have been proven to be
+sound and complete with respect to the properties provable by
+generalized symbolic execution (GSE). This work presents a method for
+initializing reference inputs in a symbolic input heap using guarded
+value sets that exactly preserves GSE semantics. A correctness proof
+for the initialization scheme is provided, as well as the results of
+an empirical evaluation of a proof-of-concept implementation. The
+initialization technique can be used to ensure that guarded value set
+based symbolic execution engines operate in a provably correct manner
+with regards to symbolic references.
 

### 2015-09-12 vmcai-2016-tex/evaluation.tex
edits to evaluation and conclusion

@@
   \centering
+  \caption{Comparing \symtxt{} with the~\gsetxt{} and Lazier\# algorithms.}
   \scalebox{0.88}{\begin{tabular}{| c | c | r | r | r | r | r | r | r | r | r |}
@@
   \end{tabular}}
-  \caption{Comparing the efficiency of the symbolic heap with the~\gsetxt{} and Lazier\# algorithms.}
+
   \label{tab:results}
@@
 %\subsection{Analysis}
-Although the correctness of~\symtxt{} has been demonstrated,
-it remains an open question whether it represents a practical alternative to the
-case-splitting methods currently in use. It is possible 
-that the benefit of decreasing the number of paths explored is
-offset by the increased complexity of the resulting path condition.
+The \symtxt{} algorithm is implemented as an extension to the Symbolic
+PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13}
+framework. In addition to the operations presented in this paper, the
+implementation contains support for operations over integers,
+calculating per-path preconditions and postconditions, as well as
+generating test input heaps that exercise all feasible control flow
+paths. We are currently working on adding support for floating point
+operations, arrays, and bit-operations. The \symtxt{} implementation
+uses the \texttt{jConstraints}
+library~\cite{ase2014-ghilrr,jpf2014-dghirr} to encode the heap
+constraints and the z3 solver~\cite{deMouraBjorner08Z3} as the
+underlying constraint solver. We leverage the incremental solving
+feature in z3 in our experiments. We also implement other
+optimizations that cache and re-use solutions to previous
+constraints. These optimizations are an important part of our
+implementation because only small portions of the heap constraint
+change during execution.
 
-To resolve this question, a prototype of the \symtxt{} 
-algorithm was developed in the Symbolic PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13} framework
-to evaluate its efficacy on Java data structure artifacts.
-%SPF includes an implementation of~\gsetxt{} with lazy initialization.
-%In recent work, we implemented the  Lazier and Lazier\#
-%algorithms in SPF~\cite{Hillery:2014}.
-%
-%The prototype of our~\symtxt{} algorithm is implemented as an
-%extension to SPF.  
-In addition to the operations presented in
-this paper, the implementation contains support for operations over
-integers, calculating per-path preconditions 
-and postconditions, as well as path-coverage-optimal sets of 
-test input heaps. 
-%A standalone version of the system, independent
-%from JPF is also under development~\cite{heapsolver2015}.
+SPF includes an implementation of~\gsetxt{} with lazy initialization.
+In recent work, we implemented the Lazier and Lazier\# algorithms in
+SPF~\cite{Hillery:2014}; these constitute the state of art approaches
+case-splitting based lazy initialization techniques. The goal of our
+experiment is to evaluate the efficacy of our approach with respect to
+other state-of-the-art techniques for symbolic execution of programs
+with unbounded complex data input. We empirically evaluate the
+\symtxt{} algorithm by considering the following research question:
+How does the cost of the \symtxt{} algorithm (SL) compare with that of
+\gsetxt{} (GSE), Lazier, Lazier\#(L\#) algorithms?
 
-The data structures used in the benchmarks are a standard set commonly used in analyses involving heap-manipulating programs~\cite{Deng:2006,Deng:2007,boyapati2002korat,Ferrara:2014,Rosner:2015}, including a linked list, binary search tree, and red/black tree.
-The BinarySearchTree test uses the class of the same name from Alan Weiss' book~\cite{Weiss:1998}.
-The test method first asserts a repOk() invariant, before conducting a traversal to find an arbitrary integer key in the tree.
-The TreeMap method comes from the standard java.util library, and is an implementation of a balanced red/black tree.
-This method asserts a repOk() invariant, before traversing the tree.
-The LinkedList test starts by asserting a repOk() invariant, which checks for loops in the linked list using Floyd’s cycle-finding algorithm.
-The linked list is then traversed using a contains() method that attempts to locate an arbitrary reference key in the list.
-For benchmarking purposes, the length of reference chain initializations was limited to some integer $k$.
-For both the tree examples, the number of possible non-isomorphic tree structures grows exponentially in k~\cite{Deng:2007}, resulting a corresponding exponential growth in analysis times for case-splitting techniques.
+The \emph{independent} variable in our study is the $k$-bound;
+$k$-bounding bounds the length of a reference chain from the root of
+the heap~\cite{Kiasan06}.  We select three dependent variables and
+measures for our study: (i) time, (ii) states explored, and (iii)
+paths generated. The \emph{time} is the total time taken by each
+algorithm to explore the symbolic execution tree as well as total
+constraint solving time. The \emph{states explored} represents the
+number of nodes in the symbolic execution tree, and the \emph{paths
+  generated} represents the number of unique paths in the symbolic
+execution tree.
 
-The results of the experiments are presented in Table~\ref{tab:results}. 
-Each row reports the results for the specified $k$-bound 
-for each artifact evaluated. The columns show the total
-time in seconds, states explored, and paths generated for
-each algorithm. The headings \gsetxt{}, L\#, and SH correspond
-to the Generalized Symbolic Execution, Lazier\#, and \symtxt{}
-algorithms, respectively. The results for
-the Lazier algorithm are omitted because they are nearly identical to the Lazier\#
-results for these artifacts. A table entry of  '-' indicates the analysis
-exceeded the allotted time bound of 1 hour.
+The data structures evaluated are a standard set commonly used in
+analyses involving heap-manipulating
+programs~\cite{Deng:2006,Deng:2007,boyapati2002korat,Ferrara:2014,Rosner:2015},
+including a linked list, binary search tree, and red/black tree. We
+use a repOk() method (a class invariant) for data structures in
+object-oriented code~\cite{boyapati2002korat}. The repOk() methods
+provide a mechanism to generate valid inputs for the methods under
+test; symbolic execution has been used to generate test inputs using
+repOk() methods in~\cite{visser2004test}. In this work, we define and
+use repOk() methods to generate valid heaps with the appropriate
+$k$-bounds before executing the methods under test. Note that this
+allows us to have precision in checking properties of the heap that is
+not possible in static analysis based techniques~\cite{Dillig:2011}.
 
-Performance improvement ranges from $4.8x$ for
-BinarySearchTree at $k$=3, to $118x$ for LinkedList at $k$=6. In fact,
-for some $k$-bounds a number of experiments complete exploration
-using the \symtxt{} algorithm in a few seconds whereas \gsetxt{} or Lazier\# are
-unable to finish, e.g., BinarySearchTree for $k$=4 and LinkedList for
-$k$=8. The results demonstrate that for these common data structures,
-the complexity of the constraints generated by~\symtxt{} is more 
-than offset by the reduction in paths explored.
+The results of the experiments are presented in
+Table~\ref{tab:results}.  Each row reports the results for the
+specified $k$-bound for each artifact evaluated. The columns show the
+total time in seconds, states explored, and paths generated for each
+algorithm. The headings \gsetxt{}, L\#, and SL correspond to the GSE,
+Lazier\#, and \symtxt{} algorithms, respectively. The results for the
+Lazier algorithm are omitted because they are nearly identical to the
+Lazier\# results for these artifacts. A table entry of '-' indicates
+the analysis exceeded the allotted time bound of 1 hour.
 
-%how does the per-path cost look for our method
+The number of possible non-isomorphic heap configurations grows
+exponentially for case-splitting techniques with a monotonic increase
+in $k$, resulting a corresponding exponential increase in analysis
+times . This is event in all the examples in
+Table~\ref{tab:results}. The GSE and L\# algorithms are unable to
+finish exploration in a time bound of one hour for $k\geq 7$ for the
+LinkedList, $k\geq 4$ for the BinarySearchTree, and $k\geq 3$ for the
+TreeMap examples. The improvement in analysis time for the \symtxt{}
+over the state of the art case splitting techniques range from $4.8x$
+for BinarySearchTree at $k$=3, to $118x$ for LinkedList at $k$=6. In
+fact, for some $k$-bounds a number of experiments complete exploration
+using the \symtxt{} algorithm in a few seconds whereas \gsetxt{} or
+Lazier\# are unable to finish, e.g., BinarySearchTree for $k$=4 and
+LinkedList for $k$=8.
 
-%The number of states explored varies between algorithms. For example,
-%\gsetxt{} creates additional points of nondeterminism during field reads, 
-%while reference compares are completely deterministic. Thus, in
-%example programs with large numbers of reference compares, e.g.,
-%TreeMap, state counts for Lazier\# and the \symtxt{} algorithm may
-%exceed those for \gsetxt{}. We observed that the additional states
-%generated by the symbolic heap algorithm are unsatisfiable at the point
-%of reference compares; this is why they do not contribute any
-%additional branches in the final symbolic execution tree. Furthermore,
-%the since larger state count is essentially a result of bookkeeping, it
-%does not impact the overall runtime of the
-%technique.
+The number of path explored by \symtxt{} algorithm are strictly less
+than or equal to the number of paths explored by \gsetxt{} for all the
+evaluated artifacts. We can use this result to do more efficient test
+case generation. From a generated path and corresponding symbolic heap
+we can use the solutions provided by the constraint solver to
+instantiate a set of concrete heaps to provide as test input. These
+provide a smaller test suite to achieve control-flow path coverage as
+compared to GSE and Lazier\#. Note that the ability to perform test
+input generation is another advantage of \symtxt{} technique over
+static analysis approaches.
 
-% Some of this discrepancy may be accounted for by the fact that
-%\symtxt{} is equipped for incremental solving, however, during
-%informal testing with the incremental solver turned off, \symtxt{}
-%usually performed better than \gsetxt{} and Lazier\#, especially in
-%test runs with high k-bounds.
+The number of states varies between algorithms, for example, \gsetxt{}
+has additional points of nondeterminism during field reads, but in
+contrast reference compares are completely deterministic. Thus, in
+example programs with large numbers of reference compares, such as
+TreeMap, state counts for Lazier\# and the \symtxt{} algorithm may
+exceed those for \gsetxt{}. We observed that the additional states
+generated by the summary heap algorithm are unsatisfiable at the point
+of reference compares; this is why they do not contribute any
+additional branches in the final symbolic execution tree. Furthermore,
+the larger state count and the corresponding satisfiability checks on
+the constraint solver does not increase the overall runtime of the
+technique.
 
-%The path counts shown in Table~\ref{tab:results} also show the advantage
-%of the \symtxt{} algorithm over the \gsetxt{} and L\# algorithms, each of
-%which performs case-splitting during the analysis.
-%The number of paths explored by the \symtxt{} algorithm is strictly 
-%less than or equal to the number
-%of paths explored by \gsetxt{} for all artifacts. As a result,
-%fewer test cases will be generated to achieve the same control-flow 
-%path coverage when compared to~\gsetxt{} and Lazier\#.
-
-%In summary, the benefits of avoiding
-%initialization-based non-determinism outweigh the increased
-%complexity in the constraints due to the advances made in SMT
-%solvers in these examples. In fact, the \symtxt{} algorithm can analyze certain types of programs with
-%orders of magnitude greater efficiency than with \gsetxt{} or
-%Lazier\#, while covering exactly the same control flow paths.
-
-%We can use this
-%result to do more efficient test case generation. From a path
-%generated we can use the solutions provided by the constraint solver
-%to instantiate a set of concrete heaps to provide as test input.
-
-%Interestingly, \symtxt{} path growth appears
-%to be sub-exponential in $k$ for the LinkedList program.
-
-%The additional states generated by summary heap are unsatisfiable
-%which is why they do not add nodes in the final symbolic execution
-%tree. Furthermore, the larger state count does not impact the overall
-%runtime of the technique.
-
-% Despite this, in practice this is often mitigated by the
-%fact that \symtxt{} can dispatch address compares without consulting
-%the constraint solver.
+In summary, the benefits of avoiding case-splitting based
+non-determinism outweigh the increased complexity in the constraints
+over heaps due to the advances made in SMT solvers in these
+examples. In fact, the \symtxt{} algorithm can analyze certain types
+of programs with orders of magnitude greater efficiency than with
+\gsetxt{} or Lazier\#, while covering exactly the same feasible
+control flow paths in the program.

### 2015-09-12 vmcai-2016-tex/intro.tex
Some more changes
edits to evaluation and conclusion

@@
 
-In symbolic execution, the values of program variables are represented as constraints over the program's inputs.
-During the course of an execution, a program variable may assume a number of possible values under a variety of different conditions.
-One way to represent this behavior is by pairing each possible value with the constraints under which it is assumed.
-A set of such value-constraint pairs, called a \emph{guarded value set}\footnote{Guarded value sets are variously referred to in the literature as \emph{guarded location sets}, \emph{symbolic value sets}, or \emph{value summaries}.
-The term guarded value set is sometimes abbreviated in this text as~\emph{value set}.}, represents the state of a program variable.
+In symbolic execution, the values of program variables are represented
+as constraints over the program's inputs. During the course of an
+execution, a program variable may assume a number of possible values
+under a variety of different conditions. One way to represent this
+behavior is by pairing each possible value with the constraints under
+which it is assumed. A set of such value-constraint pairs, called a
+\emph{guarded value set}\footnote{Guarded value sets are variously
+  referred to in the literature as \emph{guarded location sets},
+  \emph{symbolic value sets}, or \emph{value summaries}. The term
+  guarded value set is sometimes abbreviated in this text
+  as~\emph{value set}.}, represents the state of a program variable.
 
-Guarded value sets are rising in importance in the representation of reference values.
-First appearing in Verification-Condition Generator (VCG) style techniques~\cite{Xie:2005,Dillig:2011}, guarded value sets are a convenient way to represent sets of heap shapes.
-More recently, guarded value sets are being used in symbolic execution for the purposes of modularization~\cite{Yorsh:2008}, state merging~\cite{Sen:2014}, and for determining invariants~\cite{Ferrara:2014,Torlak:2014}.
+Guarded value sets are rising in importance in the representation of
+reference values. First appearing in Verification-Condition Generator
+(VCG) style techniques~\cite{Xie:2005,Dillig:2011}, guarded value sets
+are a convenient way to represent sets of heap shapes. More recently,
+guarded value sets are being used in symbolic execution for the
+purposes of modularization~\cite{Yorsh:2008}, state
+merging~\cite{Sen:2014}, and for determining
+invariants~\cite{Ferrara:2014,Torlak:2014}.
 
-A common hurdle to using guarded value sets is the treatment of symbolic heap inputs.
-For many applications, it is desirable to model the input heap as unconstrained, with operations over the input references providing the only means of divining its structure.
-Precisely modeling operations on unconstrained heap inputs is challenging because it requires formulating logical predicates over an input domain that contains a potentially unbounded number of hidden references~\cite{Chen:2013,Qu:2011}.
-Generalized symbolic execution (\gsetxt{}) methods~\cite{GSE03,Deng:2007} provide an accurate solution, but they quickly produce an overwhelming number of execution paths for all but the simplest heap shapes.
-Efforts to extend~\gsetxt{} principles to guarded value sets have failed to produce provably equivalent results \cite{LISTEFFORTS}.
-Thus, despite the advantages of using guarded value sets, it remains an open question how they can be used in symbolic execution to automatically model all possible program behaviors in the case of an arbitrary input heap.
+A common hurdle to using guarded value sets is the treatment of
+symbolic heap inputs. For many applications, it is desirable to model
+the input heap as unconstrained, with operations over the input
+references providing the only means of divining its
+structure. Precisely modeling operations on unconstrained heap inputs
+is challenging because it requires formulating logical predicates over
+an input domain that contains a potentially unbounded number of hidden
+references~\cite{Chen:2013,Qu:2011}. Generalized symbolic execution
+(\gsetxt{}) methods~\cite{GSE03,Deng:2007} provide an accurate
+solution, but they quickly produce an overwhelming number of execution
+paths for all but the simplest heap shapes. Efforts to
+extend~\gsetxt{} principles to guarded value sets have failed to
+produce provably equivalent results \cite{LISTEFFORTS}. Thus, despite
+the advantages of using guarded value sets, it remains an open
+question how they can be used in symbolic execution to automatically
+model all possible program behaviors in the case of an arbitrary input
+heap.
 
-The contribution of this work is a symbolic initialization scheme for uninitialized pointers in a fully symbolic heap.
-Where GSE lazily instantiates uninitialized pointers to either reference NULL, a new instance of the correct type, or an alias to a previously initialized object, the symbolic initialization in this work creates a guarded value set expressing all of these eventualities in the same symbolic heap.
-Where GSE branches the search space on each choice, symbolic initialization does not.
-Symbolic initialization only branches on reference compares, partitioning the symbolic heap to indicate heaps where the references alias and heaps where the references do not.
+The contribution of this work is a symbolic initialization scheme for
+uninitialized references in a fully symbolic heap. Where GSE lazily
+instantiates uninitialized references to either NULL, a new instance
+of the correct type, or an alias to a previously initialized object,
+the symbolic initialization in this work creates a guarded value set
+expressing all of these eventualities in the same symbolic heap. Where
+GSE branches the search space on each choice, symbolic initialization
+does not. Symbolic initialization only branches on reference compares,
+partitioning the symbolic heap to indicate heaps where the references
+alias and heaps where the references do not.
 
-This paper includes a proof that symbolic initialization is sound and complete with respect to properties provable by GSE.
-Such a result is important because it means that symbolic initialization can be used to create input heaps for other analyses in a way that is provably correct with regards to GSE: there are no missing heaps and there are no extra heaps.
+This paper includes a proof that symbolic initialization is sound and
+complete with respect to properties provable by GSE. Such a result is
+important because it means that symbolic initialization can be used to
+create input heaps for other analyses in a way that is provably
+correct with regards to GSE: there are no missing heaps and there are
+no extra heaps.
 
-A proof-of-concept implementation of symbolic initialization is reported in this paper.
-It demonstrates the efficiency of~\symtxt{}, as compared to existing~\gsetxt{} methods.
-The use of the guarded value sets does require extra interaction with an SMT solver, but the savings in representing multiple heap shapes in a single representation overcomes the cost of the solver calls.
-In fact, the comparison shows an exponential increase in the number of heaps that can be analyzed in a set of benchmark examples meaning that other approaches based on~\gsetxt\ fail to complete.
+A proof-of-concept implementation of symbolic initialization is
+reported in this paper. The implementation is for Java in the Java
+Pathfinder tool. It demonstrates the efficiency of~\symtxt{}, as
+compared to existing~\gsetxt{} methods. The use of the guarded value
+sets does require extra interaction with an SMT solver, but the
+savings in representing multiple heap shapes in a single
+representation overcomes the cost of the solver calls. In fact, the
+comparison shows an exponential increase in the number of heaps that
+can be analyzed in a set of benchmark examples meaning that other
+approaches based on~\gsetxt\ fail to complete.

### 2015-09-14 vmcai-2016-tex/abstract.tex
First 3 sections...

@@
 for the initialization scheme is provided, as well as the results of
-an empirical evaluation of a proof-of-concept implementation. The
+an empirical evaluation of a proof-of-concept implementation showing a real increase in the size and number of analyzed heaps compared to existing GSE representations. The
 initialization technique can be used to ensure that guarded value set

### 2015-09-14 vmcai-2016-tex/intro.tex
First 3 sections...

@@
 important because it means that symbolic initialization can be used to
-create input heaps for other analyses in a way that is provably
+create test inputs for other analyses in a way that is provably
 correct with regards to GSE: there are no missing heaps and there are

### 2015-09-14 vmcai-2016-tex/lazy.tex
First 3 sections...

@@
 \label{app:gse}
-Classical GSE and its variants all subscribe to the same ideal: an uninitialized object may be lazily initialized
-in a non-deterministic way to null, a new instance of the object, or an to
-an object of the same type also initialized lazily (i.e., the \emph{input heap}) \cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. The
-non-determinism creates branches in the execution
-tree during state space exploration. GSE semantics are defined here to give insight to symbolic initialization and support the proof that it preserves GSE behaviors.
+GSE semantics are defined here to give insight to the new symbolic initialization approach and support the proof that the new approach preserves GSE behaviors.
+GSE and its variants have the same non-deterministic choice given a reference to an uninitialized object; that reference can point to null, a new instance of an object with the correct type, or to an object of the same type that has been instantiated previously by GSE \cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}.
+The objects instantiated for new instances are referred to as the \emph{input heap}.
+Only these objects comprise the potential alias set when GSE encounters references to uninitialized objects.
+In general, the GSE search space branches at uninitialized objects, and the number of branches depends on the size of the input heap.
 
-The rules for classical GSE using the symbolic heap are in
-\figref{fig:lazyInit} for lazy initialization: NULL, new, and alias.
-Fresh references and locations strictly increase so it is possible to minimize over a set to find the first created.
-References are partitioned to support latter proofs: $\mathrm{init}_\cfgnt{r}()$ for the input
+The lazy initialization rules for GSE on the symbolic heap are in
+\figref{fig:lazyInit}: NULL, new, and alias.
+The rules rely on fresh references and locations that strictly increase so it is possible to minimize over a set to find the first created.
+Further, references are partitioned to support latter proofs: $\mathrm{init}_\cfgnt{r}()$ for the input
   heap
@@
   In general, as shown in the next section,
-  only input heap references appear in constraints to express potential aliasing, and only stack references can appear in environments, expressions, or continuations.
-Finally, the \emph{isInit} is true for initialized references from the input heap (i.e., potential aliases).
+  only input heap references appear in constraints to express potential aliasing, and only stack references appear in environments, expressions, or continuations.
+Finally, the \emph{isInit} function is true for initialized references from the input heap (i.e., potential aliases).
 
@@
 The rest of the rules in \figref{fig:lazy} do not initialize, but they are included to elucidate how symbolic initialization differs from GSE with lazy initialization.
+In particular, there is no branching in the search space on reference compare for GSE because references point to a single location.
+The new symbolic initialization using guarded value sets in the next section changes this behavior.
 
@@
 bisimulation. Although it is apparent that there is non-determinism in
-initialization at the first reference access partitioning the search space, control flow branches at comparisons and NULL-exceptions. This property is reflected in the composition of $\rgse$.
+initialization at the first access to an uninitialized reference, control flow branches at comparisons and NULL-exceptions. This property is reflected in the composition of $\rgse$.
 

### 2015-09-14 vmcai-2016-tex/summary-heap.tex
First 3 sections...

@@
 $\eta$ are partial functions, and the~\emph{path condition} $\phi$ is
-a predicate over the program variables. Given reference $r$,
+a predicate over the program variables. Given reference $r$ in the heap,
 $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the guarded value set
-in the heap associated with $r$. The constraint associated with each
+associated with $r$. The constraint associated with each
 location is a guard representing the conditions under which the
@@
 leaving the squares correspond to the $\cfgnt{R}$ function. The
-reference $\cfgnt{r}_1$ has has two members in it guarded value set,
+reference $\cfgnt{r}_1$ in the figure has two members in its guarded value set,
 so the location pointed to by $\cfgnt{r}_1$ depends on its aliasing
@@
 $\cfgnt{r}$, or any of the special values shown
-in~\figref{fig:syntax}(a).  Only type correct programs are given as
-input to the machine.
+in~\figref{fig:syntax}(a).
 

### 2015-09-14 vmcai-2016-tex/lazy.tex
More changes

@@
 How the lazy
-initialization is used is defined in \figref{fig:lazy}. Specifically,
-the field-access rule in \figref{fig:lazy} uses initialization,
-$\rightarrow_I^*$, to ensure the accessed field is
-instantiated. Initialization in generalized symbolic execution never
+initialization is used is defined in \figref{fig:lazy} with the $\rgse$ relation collecting all the rules into a single relation on states.
+This relation is used later by the proof.
+GSE initialization takes place on the field-access rule in \figref{fig:lazy},
+using the $\rightarrow_I^*$ relation from \figref{fig:lazyInit}, to ensure the accessed field is
+instantiated. Initialization in GSE never
 happens for more than one object on any use of $\rightarrow_I^*$:
-$\Lambda$ is either empty or contains exactly one location.
+the set $\Lambda$ is either empty or contains exactly one location.
 This property is an artifact of how GSE case spits when it instantiates: each choice is a new unique heap.
+This changes in the next section with the new symbolic initialization that collects all the choices into a single heap using guarded value sets.
+
 The rest of the rules in \figref{fig:lazy} do not initialize, but they are included to elucidate how symbolic initialization differs from GSE with lazy initialization.
-In particular, there is no branching in the search space on reference compare for GSE because references point to a single location.
-The new symbolic initialization using guarded value sets in the next section changes this behavior.
-
-The $\rgse$ relation defined in \figref{fig:lazy} is a union over branching points on control flow
-to support the final proof of the existence of a
-bisimulation. Although it is apparent that there is non-determinism in
-initialization at the first access to an uninitialized reference, control flow branches at comparisons and NULL-exceptions. This property is reflected in the composition of $\rgse$.
+In particular, there is no branching in the search space on reference compare for GSE because references point to a single location after initialization.
+The new symbolic initialization using guarded value sets in this papers changes this behavior.
 

### 2015-09-14 vmcai-2016-tex/abstract.tex
Another pass on abstract and intro

@@
 with using these guarded value sets is the creation of test inputs for
-programs accepting symbolic reference input parameters. Although
+program analyses that accept symbolic reference input parameters. Although
 several solutions have been proposed, none have been proven to be

### 2015-09-14 vmcai-2016-tex/intro.tex
Another pass on abstract and intro

@@
 A common hurdle to using guarded value sets is the treatment of
-symbolic heap inputs. For many applications, it is desirable to model
-the input heap as unconstrained, with operations over the input
-references providing the only means of divining its
-structure. Precisely modeling operations on unconstrained heap inputs
+\emph{symbolic} heap inputs.
+A symbolic heap input refers to a portion of the heap that is yet unconstrained, meaning that it is able to take on any shape.
+For many applications, such a symbolic heap input is desirable for modeling sets of heaps in the analysis: the operations on the heap discovered in the analysis further constrain the symbolic heap input
+structure.
+
+Precisely modeling operations on unconstrained heaps
 is challenging because it requires formulating logical predicates over
@@
 references~\cite{Chen:2013,Qu:2011}. Generalized symbolic execution
-(\gsetxt{}) methods~\cite{GSE03,Deng:2007} provide an accurate
+(\gsetxt{}), and its variants, provide an accurate
 solution, but they quickly produce an overwhelming number of execution
-paths for all but the simplest heap shapes. Efforts to
+paths for all but the simplest heap shapes \cite{GSE03,Deng:2007}. Efforts to
 extend~\gsetxt{} principles to guarded value sets have failed to
@@
 the advantages of using guarded value sets, it remains an open
-question how they can be used in symbolic execution to automatically
+question to how they can be used in symbolic execution to automatically
 model all possible program behaviors in the case of an arbitrary input
@@
 
-The contribution of this work is a symbolic initialization scheme for
-uninitialized references in a fully symbolic heap. Where GSE lazily
+The contribution of this work is \emph{symbolic initialization} for 
+uninitialized references in a fully symbolic heap. Where \gsetxt\ lazily
 instantiates uninitialized references to either NULL, a new instance
-of the correct type, or an alias to a previously initialized object,
-the symbolic initialization in this work creates a guarded value set
-expressing all of these eventualities in the same symbolic heap. Where
-GSE branches the search space on each choice, symbolic initialization
-does not. Symbolic initialization only branches on reference compares,
-partitioning the symbolic heap to indicate heaps where the references
+of the correct type, or an alias to a previously initialized object, \symtxt\ creates a guarded value set
+expressing all of these eventualities in a single symbolic heap. Where
+\gsetxt\ branches the search space on each choice, \symtxt{} does not.
+Symbolic initialization only branches on reference compares; thus it creates equivalence classes over heaps and only partitions those classes at compares to indicate heaps where the references
 alias and heaps where the references do not.
 
-This paper includes a proof that symbolic initialization is sound and
-complete with respect to properties provable by GSE. Such a result is
-important because it means that symbolic initialization can be used to
+This paper includes a proof that \symtxt\ is sound and
+complete with respect to properties provable by \gsetxt. Such a result is
+important because it means that \symtxt\ can be used to
 create test inputs for other analyses in a way that is provably
-correct with regards to GSE: there are no missing heaps and there are
-no extra heaps.
+correct with regards to \gsetxt: there are no missing \gsetxt\ heaps and there are
+no extra GSE heaps.
 
@@
 Pathfinder tool. It demonstrates the efficiency of~\symtxt{}, as
-compared to existing~\gsetxt{} methods. The use of the guarded value
-sets does require extra interaction with an SMT solver, but the
+compared to existing~\gsetxt{} methods. Although guarded value
+sets require extra interaction with an SMT solver, the
 savings in representing multiple heap shapes in a single
-representation overcomes the cost of the solver calls. In fact, the
+structure overcomes the cost of the solver calls. In fact, the
 comparison shows an exponential increase in the number of heaps that
-can be analyzed in a set of benchmark examples meaning that other
-approaches based on~\gsetxt\ fail to complete.
+can be analyzed in a set of benchmark examples, meaning that other
+approaches based on~\gsetxt\ fail to complete in the allotted time.

### 2015-09-14 vmcai-2016-tex/approach.tex
Changes from Ben's non-pushed work

@@
 \label{sec:precise}
-Although the case-splitting methods used in~\gsetxt{} can be applied
-to guarded value sets, a direct implementation would run into the same
-path explosion problems. This work presents a new initialization scheme which avoids the
+%Although the lazy initialization method used in~\gsetxt{} can be applied
+%to guarded value sets, a direct case-splitting implementation would run into the same
+%path explosion problems as~\gstetxt{}.
+A more desirable approach would be to create a new~\symtxt{} scheme that uses the state merging properties inherent to guarded value sets in order to avoid creating new paths during dereferencing operations.
+To accomplish this in a manner equivalent to~\gsetxt{}, uninitialized reference values must be initialized to guarded value sets that exactly reproduce the behavior of the individual~\gsetxt{} paths.
+Since~\gsetxt{} either chooses a new reference, a null reference, or an alias to an existing reference during lazy initialization, it seems obvious that these should be the locations represented in the guarded value set produced by~\symtxt{}.
+Although choosing the appropriate locations is straightforward, choosing the guards is more complicated.
+Since lazy initialization does not alter the path condition, it provides few clues as to what guards might be used.
+Thus, choosing the appropriate guards is the key obstacle in creating the desired~\symtxt{} scheme.
+%
+%If the exact nature of the guards is opaque, a few of the requirements may be divined by observing the properties of references.
+Since in a concrete heap, no reference points to two locations at the same time, the guards in any value set must be mutually exclusive.
+Also, since every reference points somewhere~\footnote{Even so-called dangling pointers can be thought of as pointing to unallocated memory.}, the set of guards must be collectively exhaustive.
+Furthermore, the fact that the input heap may contain a practically unbounded number of distinct references indicates that the value domain of the variables used in the guards should be similarly unbounded.
+
+%We don't really care about the locations where the references are stored, only whether references alias or not.
+
+This work presents a new initialization scheme which avoids the
 nondeterminism introduced by~\gsetxt{}. Called \emph{\symtxt{}}, this scheme leverages the core idea in generalized symbolic execution
@@
 
-The initialization rule in \figref{fig:symInit} is invoked whenever 
-an uninitialized field is accessed. The interaction
-with the solver in the definition of the rules is denoted by
-$\mathbb{S}(\phi)$ which returns true if $\phi$ is satisfiable.  The
-check for uninitialized references is determined by the function
-$\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) =
-\{\lp\phi\ \cfgnt{l}\rp\ ...\}$ which a returns guarded value set 
-containing those locations where the field $\cfgnt{f}$ is uninitialized.
-\[
-\begin{array}{rcl}
-\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \\ & &
- \ \ \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \\ & &
- \ \ \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
-\end{array}
-\]
-
 In~\figref{fig:symInit}, given the uninitialized set $\Lambda$ for
@@
 There are four cases encoded in the
-symbolic heap: (i) $\theta_\mathit{null}$ represents the condition
+symbolic heap. The first three correspond to the three types of choices made during lazy initialization: (i) $\theta_\mathit{null}$ represents the condition
 where $\cfgnt{l}_\mathit{null}$ is possible, (ii)
@@
 same time, not alias any member of $\rho$ that was initialized earlier
-than the current choice, and (iv) $\theta_\mathit{orig}$ implements
-conditional initialization to preserve the original heap structure.
-These sets are added into the heap on $\cfgnt{r}_f$ after the fields
+than the current choice.
+
+Unlike the first three cases, which correspond directly to~\gsetxt{} initialization rules, case (iv) is unique to~\symtxt{}.
+In this case, $\theta_\mathit{orig}$ implements conditional initialization to preserve the original heap structure.
+This step is necessary in order to maintain homomorphism\footnote{Homomorphism is an important property relied on by the correctness proof.} between symbolic heaps created using~\symtxt{} and the~\gsetxt{} heaps they are intended to represent.
+The sets from each of the four cases are added into the heap on $\cfgnt{r}_f$ after the fields
 for $\cfgnt{l}_f$ are initialized to $\cfgnt{r}_\mathit{un}$.
@@
 
-There are two rewrite rules in~\figref{fig:fHeap}(a), one for reading
+There are two rewrite rules in~\figref{fig:fHeap}, one for reading
 the value of a field (field-access) and the other for writing to a
@@
 (possible values of the field) returned during the dereferencing; the
-new stack reference is the return value from the operation.
+new stack reference is the return value from the $\mathbb{VS}$ operation.
 

### 2015-09-14 vmcai-2016-tex/bisimulation.tex
Changes from Ben's non-pushed work

--- 2015-09-10 vmcai-2016-tex/bisimulation.tex
@@
 \label{sec:bisim}
-A major drawback of previous methods for creating test inputs for
-symbolic heaps has been a lack of completeness. Incomplete heap
-representations may not create a set of inputs that represents
-the entire space of possible inputs. By missing some possible
-inputs, the subsequent analysis may fail to recognize 
-possible program behaviors.
+%A major drawback of previous methods for creating test inputs for
+%symbolic heaps has been a lack of completeness. Incomplete heap
+%representations may not create a set of inputs that represents
+%the entire space of possible inputs. By missing some possible
+%inputs, the subsequent analysis may fail to recognize 
+%possible program behaviors.
 
@@
 with~\gsetxt{} can also be proved using the symbolic heap
-algorithm. The proofs for the theorems, as well as
+algorithm. What follows is a brief description of the requisite terminology,
+followed by the theorem statements. The proofs for the theorems, as well as
 the complete set of semantic rules for~\gsetxt{} and~\symtxt{} can
@@
 
-The proof shows the existence of a
+The theorems assert the existence of a
 bisimulation between sets of states related by~\gsetxt{} ($p \rgse

### 2015-09-14 vmcai-2016-tex/summary-heap.tex
Fixed a few things to be consistent

@@
 \section{A Symbolic Heap}
-A \emph{symbolic heap}, as defined in this work, is a tuple
-$(\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta)$, where the~\emph{location map}
-$\cfgnt{L}$,~\emph{reference map} $\cfgnt{R}$, and~\emph{environment}
-$\eta$ are partial functions, and the~\emph{path condition} $\phi$ is
-a predicate over the program variables. Given reference $r$ in the heap,
+A \emph{symbolic heap}, as defined in this work, is a pair
+$(\cfgnt{L}\ \cfgnt{R})$, indicating a \emph{location map}
+$\cfgnt{L}$ and a \emph{reference map} $\cfgnt{R}$.  Given a reference $r$ in the heap,
 $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the guarded value set
@@
 
-For well-formed symbolic heaps, a reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
+A \emph{well-formed} symbolic heap is \emph{deterministic} and \emph{type consistent}. Determinism means a reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
 $
@@
 $
-where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. Also, for a well-formed heap, all locations associated with a reference have the same type:
+where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$.
+Type consistent means that all locations in a guarded value set from a reference have the same type\footnote{Although not treated in this presentation, the concept naturally extends to polymorphic languages}:
 $\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
@@
 a small-step operational semantics in the context of a syntactic machine with a CESK architecture~\cite{Felleisen:1992, saints-MS}. The
-surface (input) syntax and machine (state) syntax (which omits the symbolic heap definition previously given and the environment) are shown
-in~\figref{fig:syntax}. Terminals are in bold face while non-terminals
+surface  syntax  (input) and machine  syntax (state) are shown
+in~\figref{fig:syntax}. The machine syntax omits the list based syntactic structures for the partial functions in the heap etc.  Terminals are in bold face while non-terminals
 are italicized. Ellipses indicate zero or more repetitions. Tuples
@@
 The machine state $\cfgnt{s}$ includes the program
-registry $\mu$, the symbolic heap, the global path constraint, the environment $\eta$, the current expression (i.e., program), and the continuation $\cfgnt{k}$. The registry never changes so it is
-omitted from the state tuple in the rest of the presentation. The environment is a partial function so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
+registry $\mu$, the symbolic heap, the~\emph{path condition} $\phi$, the \emph{environment} $\eta$, the current expression (i.e., program), and the continuation $\cfgnt{k}$.
+The registry never changes so it is
+omitted from the state tuple in the rest of the presentation. The path condition is a predicate of the program variables. 
+The environment is a partial function so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
 $\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation

### 2015-09-14 vmcai-2016-tex/abstract.tex
edits to the abstract

--- 2015-09-14 vmcai-2016-tex/abstract.tex
@@
 modeling of references as sets of guarded values, enabling multiple
-heap shapes to be represented in a single state. A fundamental problem
-with using these guarded value sets is the creation of test inputs for
-programs accepting symbolic reference input parameters. Although
-several solutions have been proposed, none have been proven to be
-sound and complete with respect to the properties provable by
-generalized symbolic execution (GSE). This work presents a method for
-initializing reference inputs in a symbolic input heap using guarded
-value sets that exactly preserves GSE semantics. A correctness proof
-for the initialization scheme is provided, as well as the results of
-an empirical evaluation of a proof-of-concept implementation showing a real increase in the size and number of analyzed heaps compared to existing GSE representations. The
-initialization technique can be used to ensure that guarded value set
-based symbolic execution engines operate in a provably correct manner
-with regards to symbolic references.
+heap shapes to be represented in a single state.  A fundamental
+problem with using these guarded value sets is the inability to
+generate test inputs in a manner similar to symbolic execution based
+analyses.
+%is the creation of test inputs for
+%program analyses that accept symbolic reference input
+%parameters.
+Although several solutions have been proposed, none have been proven
+to be sound and complete with respect to the heap properties provable
+by generalized symbolic execution (GSE) given certain user-defined
+bounds. This work presents a method for initializing input references
+in a symbolic input heap using guarded value sets that exactly
+preserves GSE semantics. A correctness proof for the initialization
+scheme is provided, as well as the results of an empirical evaluation
+of a proof-of-concept implementation showing a real increase in the
+size and number of analyzed heaps compared to existing GSE
+representations. The initialization technique can be used to ensure
+that guarded value set based symbolic execution engines operate in a
+provably correct manner with regards to symbolic references as well as
+provide the ability to generate concrete heaps that serve as test
+inputs to the program.
 

### 2015-09-14 vmcai-2016-tex/abstract.tex
Toned down empirical study

@@
 to be sound and complete with respect to the heap properties provable
-by generalized symbolic execution (GSE) given certain user-defined
-bounds. This work presents a method for initializing input references
+by generalized symbolic execution (GSE). This work presents a method for initializing input references
 in a symbolic input heap using guarded value sets that exactly
 preserves GSE semantics. A correctness proof for the initialization
-scheme is provided, as well as the results of an empirical evaluation
-of a proof-of-concept implementation showing a real increase in the
-size and number of analyzed heaps compared to existing GSE
+scheme is provided with a proof-of-concept implementation. Results from an empirical evaluation on a standard set of \gsetxt{} benchmarks show an increase in the
+size and number of analyzed heaps over existing GSE
 representations. The initialization technique can be used to ensure

### 2015-09-14 vmcai-2016-tex/intro.tex
Toned down empirical study

@@
 \section{Introduction}
-
-%In recent years symbolic execution has provided the basis for various
-%software testing and analysis techniques, e.g., regression
-%analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
-%data structure repair~\cite{KhurshidETAL05RepairingStructurally},
-%dynamic discovery of
-%invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, and
-%debugging~\cite{Ma:2011}.
-%
-%Recent work has explored the strengths and limitations of
-%tools which leverage constraint solvers, e.g., concolic execution,
-%identifying symbolic dereferencing and updating operations as areas
-%for potential improvement~\cite{Chen:2013,Qu:2011}.
 
@@
 reported in this paper. The implementation is for Java in the Java
-Pathfinder tool. It demonstrates the efficiency of~\symtxt{}, as
-compared to existing~\gsetxt{} methods. Although guarded value
+Pathfinder tool.
+It demonstrates on a standard set of benchmarks for GSE evaluation (\cite{PAPERSESTABLISHINGBENCHMARKSET}) an increase in the number of heaps that can be analyzed when compared to existing ~\gsetxt{} methods.
+Although guarded value
 sets require extra interaction with an SMT solver, the
 savings in representing multiple heap shapes in a single
-structure overcomes the cost of the solver calls. In fact, the
+structure can overcome the cost of the solver calls. For the tree structures in the standard benchmarks, the
 comparison shows an exponential increase in the number of heaps that
-can be analyzed in a set of benchmark examples, meaning that other
+can be analyzed, meaning that other
 approaches based on~\gsetxt\ fail to complete in the allotted time.
+
+In summary, this paper presents a new initialization technique that
+enables the use of guarded value sets in heap representations in a
+sound and complete manner. Such a result means that any analysis using
+this initialization technique can be assured of precision with regard
+to \gsetxt{} semantics \cite{THINGSTHATBENEFIT}. This includes generating concrete heaps for test input generation.

### 2015-09-14 vmcai-2016-tex/abstract.tex
Changes with Ben

@@
 preserves GSE semantics. A correctness proof for the initialization
-scheme is provided with a proof-of-concept implementation. Results from an empirical evaluation on a standard set of \gsetxt{} benchmarks show an increase in the
+scheme is provided with a proof-of-concept implementation. Results from an empirical evaluation on a command set of \gsetxt{} data structure benchmarks show an increase in the
 size and number of analyzed heaps over existing GSE

### 2015-09-14 vmcai-2016-tex/bisimulation.tex
Changes with Ben

@@
 in the operation or a false outcome, and \emph{\com} is everything
-else in the language. Any state relation, say $\rightarrow_x$, is
+else in the language. Any state relation, say $\rightarrow_x^Y$, is
 trivially extended to sets of states as
 $$
-P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Leftrightarrow p^\prime \in P^\prime))
+P \hookrightarrow_x^Y P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x^Y p^\prime \Leftrightarrow p^\prime \in P^\prime))
 $$
@@
 \end{definition}
-Functional equivalence asserts a common structure in the two heaps under certain
+The notation $\cfgnt{L}_p^\rightarrow$ denotes the image of $\cfgnt{L}_p$. Functional equivalence asserts a common structure in the two heaps under certain
 conditions. It is used to relate states in $p \rgse
@@
 \end{definition}
-Although the functional reasons over a forward and backward
-simulation as typical~ \cite{Sangiorgi:2011}, its use of a meta-relation, $\rsgse$, is unique.
+Other than the use of a meta-relation, $\rsgse$, \defref{bisimulation} reasons over the typical forward and backward
+simulation~\cite{Sangiorgi:2011}.
 

### 2015-09-14 vmcai-2016-tex/evaluation.tex
Changes with Ben

@@
 generating test input heaps that exercise all feasible control flow
-paths. We are currently working on adding support for floating point
-operations, arrays, and bit-operations. The \symtxt{} implementation
-uses the \texttt{jConstraints}
-library~\cite{ase2014-ghilrr,jpf2014-dghirr} to encode the heap
-constraints and the z3 solver~\cite{deMouraBjorner08Z3} as the
-underlying constraint solver. We leverage the incremental solving
-feature in z3 in our experiments. We also implement other
-optimizations that cache and re-use solutions to previous
-constraints. These optimizations are an important part of our
-implementation because only small portions of the heap constraint
-change during execution.
+paths. Future work is adding support for floating point
+operations, arrays, and bit-operations.
+
+The \symtxt{} implementation uses \texttt{jConstraints} with the z3 solver \cite{ase2014-ghilrr,jpf2014-dghirr,deMouraBjorner08Z3}.
+The implementation takes advantage of incremental solving and employs caching for performance since only small portions of the heap constraint changes during the search.
 

### 2015-09-14 vmcai-2016-tex/intro.tex
Changes with Ben

@@
 paths for all but the simplest heap shapes \cite{GSE03,Deng:2007}. Efforts to
-extend~\gsetxt{} principles to guarded value sets have failed to
-produce provably equivalent results \cite{LISTEFFORTS}. Thus, despite
+extend~\gsetxt{} principles to guarded value sets have yet to
+produce provably equivalent results \cite{LISTOFEFFORTS}. Thus, despite
 the advantages of using guarded value sets, it remains an open
@@
 Pathfinder tool.
-It demonstrates on a standard set of benchmarks for GSE evaluation (\cite{PAPERSESTABLISHINGBENCHMARKSET}) an increase in the number of heaps that can be analyzed when compared to existing ~\gsetxt{} methods.
+It demonstrates on a command set of data structure benchmarks for GSE evaluation (\cite{PAPERSESTABLISHINGBENCHMARKSET}) an increase in the number of heaps that can be analyzed when compared to existing ~\gsetxt{} methods.
 Although guarded value

### 2015-09-14 vmcai-2016-tex/summary-heap.tex
Changes with Ben

@@
 \section{A Symbolic Heap}
-A \emph{symbolic heap}, as defined in this work, is a pair
-$(\cfgnt{L}\ \cfgnt{R})$, indicating a \emph{location map}
-$\cfgnt{L}$ and a \emph{reference map} $\cfgnt{R}$.  Given a reference $r$ in the heap,
+A \emph{symbolic heap}, as defined in this work, is a tuple
+$(\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta)$, indicating a \emph{location map}
+$\cfgnt{L}$, a \emph{reference map} $\cfgnt{R}$, a \emph{path condition} $\phi$, and an \emph{environment} $\eta$.  Given a reference $r$ in the heap,
 $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the guarded value set
@@
 \end{figure}
+
+The path condition is a predicate of the program variables. The environment is a partial function so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
+$\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation
+$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
+partial function $\eta^\prime$ that is the same as $\eta$ except that
+the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. This notation for update is used with $\cfgnt{L}$ and $\cfgnt{R}$ as well.
 
@@
 
-A \emph{well-formed} symbolic heap is \emph{deterministic} and \emph{type consistent}. Determinism means a reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
+A \emph{well-formed} symbolic heap is \emph{deterministic} and \emph{type consistent}.
+Determinism means a reference in $(\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta)$ cannot point to multiple locations simultaneously:
 $
@@
 The machine state $\cfgnt{s}$ includes the program
-registry $\mu$, the symbolic heap, the~\emph{path condition} $\phi$, the \emph{environment} $\eta$, the current expression (i.e., program), and the continuation $\cfgnt{k}$.
-The registry never changes so it is
-omitted from the state tuple in the rest of the presentation. The path condition is a predicate of the program variables. 
-The environment is a partial function so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
-$\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation
-$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
-partial function $\eta^\prime$ that is the same as $\eta$ except that
-the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. This notation is used with symbolic heaps as well.
-
-The continuation
+registry $\mu$, the symbolic heap, the current expression (i.e., program), and the continuation $\cfgnt{k}$. The registry never changes so it is
+omitted from the state tuple in the rest of the presentation. The continuation
 $\cfgnt{k}$ indicates with the symbol $\cfgnt{*}$ where the expression $\cfgnt{e}$ came from, stores

### 2015-09-15 vmcai-2016-tex/intro.tex
Fixed references in intro.tex

--- 2015-09-14 vmcai-2016-tex/intro.tex
@@
 solution, but they quickly produce an overwhelming number of execution
-paths for all but the simplest heap shapes \cite{GSE03,Deng:2007}. Efforts to
-extend~\gsetxt{} principles to guarded value sets have failed to
-produce provably equivalent results \cite{LISTEFFORTS}. Thus, despite
+paths for all but the simplest heap shapes \cite{GSE03,Deng:2007}. Other efforts to 
+create heap inputs for guarded value set-based analysis 
+techniques \cite{Dillig:2011,Xie:2005} have yet to
+produce results provably equivalent to~\gsetxt{}. Thus, despite
 the advantages of using guarded value sets, it remains an open
@@
 Pathfinder tool.
-It demonstrates on a standard set of benchmarks for GSE evaluation (\cite{PAPERSESTABLISHINGBENCHMARKSET}) an increase in the number of heaps that can be analyzed when compared to existing ~\gsetxt{} methods.
+It demonstrates on a common set of data structure benchmarks for GSE evaluation~\cite{Deng:2006,Deng:2007,boyapati2002korat,Ferrara:2014,Rosner:2015} an increase in the number of heaps that can be analyzed when compared to existing ~\gsetxt{} methods.
 Although guarded value

### 2015-09-15 vmcai-2016-tex/intro.tex
Fixed another reference in the intro.

@@
 Pathfinder tool.
-It demonstrates on a common set of data structure benchmarks for GSE evaluation~\cite{Deng:2006,Deng:2007,boyapati2002korat,Ferrara:2014,Rosner:2015} an increase in the number of heaps that can be analyzed when compared to existing ~\gsetxt{} methods.
+It demonstrates on a common set of data structure benchmarks for GSE evaluation~\cite{Deng:2006,Deng:2007,boyapati2002korat,Ferrara:2014,Rosner:2015} an increase in the number of heaps that can be analyzed when compared to existing~\gsetxt{} methods.
 Although guarded value
@@
 
-In summary, this paper presents a new initialization technique that
+In summary, this paper presents a new initialization technique called symbolic initialization that
 enables the use of guarded value sets in heap representations in a
-sound and complete manner. Such a result means that any analysis using
-this initialization technique can be assured of precision with regard
-to \gsetxt{} semantics \cite{THINGSTHATBENEFIT}. This includes generating concrete heaps for test input generation.
+sound and complete manner. Such a result means that guarded 
+value set-based analysis methods~\cite{Ferrara:2014,Torlak:2014,Sen:2014,Xie:2005,Dillig:2011,Yorsh:2008} can use symbolic initialization to be assured of precision with regard
+to~\gsetxt{} semantics. This includes generating concrete heaps for test input generation.

### 2015-09-15 vmcai-2016-tex/rw.tex
Changes from Ben's non-pushed work
Changes with Ben
Updated related work, bibliography.

@@
 represent program
-state~\cite{Sen:2014,Torlak:2014,Yorsh:2008,Xie:2005,Dillig:2011,Elkarablieh:2009}. 
-The method was pioneered in Verification-Condition Generator (VCG) style techniques such as ~\cite{Xie:2005,Yorsh:2008}, where value sets were used to 
-represent aliasing-free tree-like heaps. The work in~\cite{Dillig:2011} relaxed the aliasing restrictions by using a pre-computed set of symbolic input heaps.
+state~\cite{Sen:2014,Torlak:2014,Xie:2005,Dillig:2011,Elkarablieh:2009}. 
+The method was pioneered in Verification-Condition Generator (VCG) style techniques such as ~\cite{Xie:2005}, where value sets were used to 
+initialize aliasing-free tree-like heaps.
+The work in~\cite{Dillig:2011} relaxed the aliasing restrictions by using a pre-computed set of symbolic input heaps, but was instead limited to heaps without recursive data structures.
 
 Recently, value sets have been adapted for use in symbolic execution, for the purposes of state merging ~\cite{Sen:2014,Torlak:2014} and invariant detection~\cite{Ferrara:2014}.
-While these methods demonstrate the utility of value sets in combination with symbolic execution, none of these techniques address dereferencing of symbolic input references.
+These methods demonstrate the utility of value sets in combination with symbolic execution.
+However, none of these techniques address the dereferencing of symbolic input references.
 Since dereferencing is a fundamental problem treated in this paper, these other works may be considered both orthogonal and complimentary to~\symtxt{}.
-%
+
 %\subsection{Other Heap Representations in Symbolic Execution}
@@
 %GSE
-Several projects have generalized the core idea of symbolic execution,
-enabling it to be applied to programs with more general types,
+Symbolic initialization also draws inspiration from lazy initialization, the core idea of generalized symbolic execution (\gsetxt{})\cite{GSE03}.
+Several projects have used lazy initialization to conduct symbolic execution on programs with more general types,
 including references and
-arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. However, these
-generalized symbolic execution (\gsetxt{}) techniques work by branching over
+arrays~\cite{KiasanKunit,Cadar:2008,Deng:2007,Rosner:2015,Blackshear:2013,Filieri:2015}. However, \gsetxt{} techniques branch over
 multiple copies of the system state during dereferencing operations,
@@
 
+%Other projects have used non value-set based symbolic heap representations, including dynamic symbolic execution engines, and separation logic based solvers.
+
 %DSE
-Dynamic symbolic execution (\dsetxt{}) techniques may use
-concretization when reasoning about references~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}, enabling much greater program
-coverage than classical symbolic execution alone. In particular, PEX~\cite{Tillmann:2008}
-has demonstrated a high degree of utility in a wide variety of 
-practical verification scenarios. Sometimes,
-however, as demonstrated in~\cite{Elkarablieh:2009},~\dsetxt{}
-under-approximates the possible heaps configurations when it
-concretizes symbolic values. The SAGE~\dsetxt{}
-engine~\cite{Elkarablieh:2009} includes more sophisticated methods for
-reasoning symbolically about references, and can successfully handle
-complicated examples. However, SAGE uses a
-theory of fixed-length arrays to model the heap, and is thus incomplete
-for programs with input-dependent memory allocation. It is hoped that the 
-techniques presented in this work can be used to extend practical tools 
-like PEX for applications requiring formal correctness guarantees.
+A number of dynamic symbolic execution (\dsetxt{}) methods use some form 
+of symbolic heap representation, including PEX~\cite{Tillmann:2008} and SAGE~\cite{Elkarablieh:2009}.
+These~\dsetxt{} methods have shown a high degree of utility in practical applications with a wide variety of real-world programs.
+However, PEX and SAGE use array theories to represent program state instead of guarded value sets.
+The use of array theories impacts the completeness of SAGE, which was proven complete only for programs whose memory allocations are independent of their inputs.
+We are unaware of any completeness results regarding PEX, but we suspect that a proof would require the same qualifications as SAGE.
 
-%
-%\subsection{Formal Results on Symbolic Heaps}
-The symbolic heap used by SAGE~\cite{Elkarablieh:2009} was shown to be sound and complete for programs with input-independent memory allocation.~\symtxt{} is sound and complete for all states reached by symbolic execution.
-
-Recently, several separation logic solvers have been proven to be sound and complete for heaps with linked lists, trees~\cite{Piskac:2014}, or data structures satisfying user-supplied invariants~\cite{Brotherston:2014}.
-In contrast,~\symtxt{} is sound and complete without restriction on data structures, and requires no explicit invariants, but this result is restricted to the properties provable by symbolic execution.
-
-The heap in~\cite{Dillig:2011} was proven to be monotonic with respect to the number of valid solutions.
-
-Some heap methods, such as those used by VC generators, may be sound and complete if the correct bounds are chosen. However, choosing the bounds is at least as hard as analyzing the program.
+Several separation logic solvers have been proven to be sound and complete for heaps with linked lists~\cite{Navarro:2011,Cook:2011,Berdine:2005}, trees~\cite{Piskac:2014}, or data structures satisfying user-supplied invariants~\cite{Brotherston:2014}.
+Separation logic solvers can also reason about entailment, which is presently beyond the scope of~\symtxt{}.
+However,~\symtxt{} is sound and complete without restriction on data structures, and requires no explicit invariants.
 

### 2015-09-15 vmcai-2016-tex/rw.tex
Added a phrase accidentally deleted from rw.tex

@@
 state~\cite{Sen:2014,Torlak:2014,Xie:2005,Dillig:2011,Elkarablieh:2009}.
-The method was pioneered in Verification-Condition Generator (VCG) style techniques such as ~\cite{Xie:2005}, where value sets were used to 
+In particular, the field write and equals reference compare rules are similar to methods appearing in these works.
+The real contribution of \symtxt\ is the initialization part of the field access rules which preserves the \gsetxt\ semantics.
+Guarded value set heap initialization was pioneered in Verification-Condition Generator (VCG) style techniques such as ~\cite{Xie:2005}, where value sets were used to 
 initialize aliasing-free tree-like heaps.

### 2015-09-15 vmcai-2016-tex/bisimulation.tex
Added new define equals macro.

@@
 Symbolic Execution (\gsetxt{}). Intuitively, the theorems imply that any properties proven
-with~\gsetxt{} can also be proved using the symbolic heap
+with~\gsetxt{} can also be proved using the~\symtxt{}
 algorithm. What follows is a brief description of the requisite terminology,
@@
 q^\prime$). The relations are on the universe of \emph{well-formed}
-states $S$, which have the properties in \secref{sec:sh} with the
+states $S$, which have the properties in \secref{sec:symheap} with the
 constraint that the states are \emph{feasible}: successors exist
@@
 $$
-P \hookrightarrow_x^Y P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x^Y p^\prime \Leftrightarrow p^\prime \in P^\prime))
+P \hookrightarrow_x^Y P^\prime \defeq \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x^Y p^\prime \Leftrightarrow p^\prime \in P^\prime))
 $$
@@
 \begin{array}{l}
- s_p \rightharpoonup_{h} s_q \Leftrightarrow 
+ s_p \rightharpoonup_{h} s_q \defeq
 \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}\ ( \forall \phi_\alpha\ (\\ 
@@
 \[
-\mathbb{HC}(p \rightharpoonup_{h} q) = 
+\mathbb{HC}(p \rightharpoonup_{h} q) \defeq
 \bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_p^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_q^\rightarrow)\}
@@
 The represented relation is extended to sets of states $P$ and a single state $q$ as
-$P \sqsubset q \Longleftrightarrow \forall p\ (p \sqsubset q \Leftrightarrow p \in P)$.
+$P \sqsubset q \defeq \forall p\ (p \sqsubset q \Leftrightarrow p \in P)$.
 \end{definition}

### 2015-09-15 vmcai-2016-tex/intro.tex

@@
 create heap inputs for guarded value set-based analysis 
-techniques \cite{Dillig:2011,Xie:2005} have yet to
-produce results provably equivalent to~\gsetxt{}. Thus, despite
+techniques  have yet to
+produce results provably equivalent to~\gsetxt{} \cite{Dillig:2011,Xie:2005}. Thus, despite
 the advantages of using guarded value sets, it remains an open

### 2015-09-15 vmcai-2016-tex/rw.tex

@@
 These~\dsetxt{} methods have shown a high degree of utility in practical applications with a wide variety of real-world programs.
-However, PEX and SAGE use array theories to represent program state instead of guarded value sets.
-The use of array theories impacts the completeness of SAGE, which was proven complete only for programs whose memory allocations are independent of their inputs.
-We are unaware of any completeness results regarding PEX, but we suspect that a proof would require the same qualifications as SAGE.
+PEX and SAGE use array theories to represent program state instead of guarded value sets.
+SAGE has been proven complete for programs whose memory allocations are independent of their inputs.
+This work is complementary to PEX and SAGE, and we believe could be leveraged to further improve those tools.
 
 Several separation logic solvers have been proven to be sound and complete for heaps with linked lists~\cite{Navarro:2011,Cook:2011,Berdine:2005}, trees~\cite{Piskac:2014}, or data structures satisfying user-supplied invariants~\cite{Brotherston:2014}.
-Separation logic solvers can also reason about entailment, which is presently beyond the scope of~\symtxt{}.
-However,~\symtxt{} is sound and complete without restriction on data structures, and requires no explicit invariants.
+Separation logic solvers can also reason about entailment which is a subject of future work for symbolic initialization.
+Solutions in separation logic do not lend themselves to test case generation is  goal in this work.
 

### 2015-09-16 tex/conclusion.tex
Updated exended paper to reflect VMCAI updates.

@@
 
-Although our approach is inspired by the work in the static analysis
-domain, the heap representations used by those techniques do not lend
-themselves to symbolic execution since they rely on
-approximations, they are inflexible in what types of relations can be
-expressed, and they rely on rewriting of constraints.  In this work,
-we present a heap summary technique for symbolic execution that
-maintains exactness, represents arbitrary heap structures without
-restrictions on aliasing relationships, and supports dynamic
-on-the-fly initialization of heap structures. This unique
-combination of capabilities enables the summary heap to outperform
-state-of-the-art symbolic execution techniques, and in some cases, the
-performance gains are considerable. We believe that performance gains
-in symbolic execution can naturally benefit a variety of analyses
-based on symbolic execution, for example, verification of properties,
+In this work we present a \symtxt{} algorithm for uninitialized
+references in a fully symbolic heap. Where GSE lazily instantiates
+uninitialized references to either NULL, a new instance of the correct
+type, or an alias to a previously initialized object, the symbolic
+initialization in this work creates a guarded value set expressing all
+of these eventualities in the same symbolic heap. We prove that the
+\symtxt{} algorithm is sound and complete with respect to properties
+provable by GSE.
+
+An initial implementation of the technique has been done within the
+Java PathFinder framework. The \symtxt{} algorithm outperforms
+state-of-the-art case-splitting based symbolic execution techniques,
+and in some cases, the performance gains are considerable in a set of
+Java data structure artifacts. The performance gains in symbolic
+execution may naturally benefit a variety of analyses based on
+symbolic execution, for example, verification of properties,
 especially those related to the heap, test case generation, program
 evolution techniques such as directed incremental symbolic
-execution~\cite{person:pldi2011}, and other back-end analyses.
+execution~\cite{person:pldi2011}, and other back-end
+analyses. Potential future work includes evaluating the impact of
+analyses that rely on symbolic execution.
+
+\begin{comment}
 

### 2015-09-16 tex/evaluation.tex
Added additional BinarySearchTree test results to table 1.
Updated exended paper to reflect VMCAI updates.

@@
+\section{Evaluation}
+\label{sec:evaluation}
 %\begin{figure*}[t]
@@
    \multirow{2}{*}{Method }&\multirow{2}{*}{ $k$ }
-   &\multicolumn{3}{|c|}{Time (seconds)} &\multicolumn{3}{|c|}{States} &\multicolumn{3}{|c|}{ Paths }\\
+   &\multicolumn{3}{c|}{Time (seconds)} &\multicolumn{3}{c|}{States} &\multicolumn{3}{c|}{ Paths }\\
 								&	&\gsetxt{} & L\#		&SL		&\gsetxt{}	& L\# & SL&\gsetxt{}	& L\# 	& SL\\
@@
   \end{tabular}}
-  \caption{Comparing the efficiency of the summary heap approach to GSE and Lazier\# algorithms.}
+
   \label{tab:results}
 \end{table*}
+
 %\end{figure*}
@@
 %\subsection{Analysis}
+The \symtxt{} algorithm is implemented as an extension to the Symbolic
+PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13}
+framework. In addition to the operations presented in this paper, the
+implementation contains support for operations over integers,
+calculating per-path preconditions and postconditions, as well as
+generating test input heaps that exercise all feasible control flow
+paths. Future work is adding support for floating point
+operations, arrays, and bit-operations.
 
-The results of the experiments are presented in Table
-\ref{tab:results}. Each row contains the results for the specified $k$-bound 
-for each artifact evaluated. The columns show the total
-wall clock time in seconds, states explored, and paths generated for
-each of the algorithms. The headings \gsetxt{}, L\#, and SL correspond
-to the Generalized Symbolic Execution, Lazier\#, and \symtxt{}
-algorithms, respectively. Note that we do no present the results for
-the Lazier algorithm since they are almost identical to that of Lazier\#
-for our examples. Table entries containing '-' correspond to test runs
-that exceeded the allotted time bound of 10 minutes.
+The \symtxt{} implementation uses \texttt{jConstraints} with the z3 solver \cite{ase2014-ghilrr,jpf2014-dghirr,deMouraBjorner08Z3}.
+The implementation takes advantage of incremental solving and employs caching for performance since only small portions of the heap constraint changes during the search.
 
-In most tests, run times strongly favor the \symtxt{} algorithm, especially for
-large $k$-values. Performance improvement ranges from $4.8x$ for
-BinarySearchTree at $k$=3, to $118x$ for LinkedList at $k$=6. In fact,
-for certain $k$-bounds a number of experiments completed exploration
-using the \symtxt{} algorithm in a few seconds whereas \gsetxt{} or Lazier\# were
-unable to finish, e.g., BinarySearchTree for $k$=4 and LinkedList for
-$k$=8. These results demonstrate the potential of using the \symtxt{} algorithm 
-to handle data input for complex types. The lower running times
-show that we can prove properties using the \symtxt{} algorithm faster than
-\gsetxt{}.
+SPF includes an implementation of~\gsetxt{} with lazy initialization.
+In recent work, we implemented the Lazier and Lazier\# algorithms in
+SPF~\cite{Hillery:2014}; these constitute the state of art approaches
+case-splitting based lazy initialization techniques. The goal of our
+experiment is to evaluate the efficacy of our approach with respect to
+other state-of-the-art techniques for symbolic execution of programs
+with unbounded complex data input. We empirically evaluate the
+\symtxt{} algorithm by considering the following research question:
+How does the cost of the \symtxt{} algorithm (SL) compare with that of
+\gsetxt{} (GSE), Lazier, Lazier\# (L\#) algorithms?
 
-% Some of this discrepancy may be accounted for by the fact that
-%\symtxt{} is equipped for incremental solving, however, during
-%informal testing with the incremental solver turned off, \symtxt{}
-%usually performed better than \gsetxt{} and Lazier\#, especially in
-%test runs with high k-bounds.
+The \emph{independent} variable in our study is the $k$-bound;
+$k$-bounding bounds the length of a reference chain from the root of
+the heap~\cite{Kiasan06}.  We select three dependent variables and
+measures for our study: (i) time, (ii) states explored, and (iii)
+paths generated. The \emph{time} is the total time taken by each
+algorithm to explore the symbolic execution tree as well as total
+constraint solving time. The \emph{states explored} represents the
+number of nodes in the symbolic execution tree, and the \emph{paths
+  generated} represents the number of unique paths in the symbolic
+execution tree.
 
-Path counts likewise substantially favor the \symtxt{} algorithm. The number of
-paths explored by the algorithm is strictly less than or equal to the number
-of paths explored by \gsetxt{} for all test cases. We can use this
-result to do more efficient test case generation. From a path
-generated we can use the solutions provided by the constraint solver
-to instantiate a set of concrete heaps to provide as test input. These
-can provide a smaller test suite to achieve control-flow path coverage when
-compared to GSE and Lazier\#.
+The data structures evaluated are a standard set commonly used in
+analyses involving heap-manipulating
+programs~\cite{Deng:2006,Deng:2007,boyapati2002korat,Ferrara:2014,Rosner:2015},
+including a linked list, binary search tree, and red/black tree. We
+use a repOk() method (a class invariant) for data structures in
+object-oriented code~\cite{boyapati2002korat}. The repOk() methods
+provide a mechanism to generate valid inputs for the methods under
+test; symbolic execution has been used to generate test inputs using
+repOk() methods in~\cite{visser2004test}. In this work, we define and
+use repOk() methods to generate valid heaps with the appropriate
+$k$-bounds before executing the methods under test. Note that this
+allows us to have precision in checking properties of the heap that is
+not possible in static analysis based techniques~\cite{Dillig:2011}.
 
-%Interestingly, \symtxt{} path growth appears
-%to be sub-exponential in $k$ for the LinkedList program.
+The results of the experiments are presented in
+Table~\ref{tab:results}.  Each row reports the results for the
+specified $k$-bound for each artifact evaluated. The columns show the
+total time in seconds, states explored, and paths generated for each
+algorithm. The headings \gsetxt{}, L\#, and SL correspond to the GSE,
+Lazier\#, and \symtxt{} algorithms, respectively. The results for the
+Lazier algorithm are omitted because they are nearly identical to the
+Lazier\# results for these artifacts. A table entry of '-' indicates
+the analysis exceeded the allotted time bound of 1 hour.
+
+The number of possible non-isomorphic heap configurations grows
+exponentially for case-splitting techniques with a monotonic increase
+in $k$, resulting a corresponding exponential increase in analysis
+times . This is evident in all the examples in
+Table~\ref{tab:results}. The GSE and L\# algorithms are unable to
+finish exploration in a time bound of one hour for $k\geq 7$ for the
+LinkedList, $k\geq 4$ for the BinarySearchTree, and $k\geq 3$ for the
+TreeMap examples. The improvement in analysis time for the \symtxt{}
+over the state of the art case splitting techniques range from $4.8x$
+for BinarySearchTree at $k$=3, to $118x$ for LinkedList at $k$=6. In
+fact, for some $k$-bounds a number of experiments complete exploration
+using the \symtxt{} algorithm in a few seconds whereas \gsetxt{} or
+Lazier\# are unable to finish, e.g., BinarySearchTree for $k$=4 and
+LinkedList for $k$=8.
+
+The number of path explored by \symtxt{} algorithm are strictly less
+than or equal to the number of paths explored by \gsetxt{} for all the
+evaluated artifacts. We can use this result to do more efficient test
+case generation. From a generated path and corresponding symbolic heap
+we can use the solutions provided by the constraint solver to
+instantiate a set of concrete heaps to provide as test input. These
+provide a smaller test suite to achieve control-flow path coverage as
+compared to GSE and Lazier\#. Note that the ability to perform test
+input generation is another advantage of \symtxt{} technique over
+static analysis approaches.
 
@@
 additional branches in the final symbolic execution tree. Furthermore,
-the larger state count does not impact the overall runtime of the
+the larger state count and the corresponding satisfiability checks on
+the constraint solver does not increase the overall runtime of the
 technique.
 
-%The additional states generated by summary heap are unsatisfiable
-%which is why they do not add nodes in the final symbolic execution
-%tree. Furthermore, the larger state count does not impact the overall
-%runtime of the technique.
-
-% Despite this, in practice this is often mitigated by the
-%fact that \symtxt{} can dispatch address compares without consulting
-%the constraint solver.
-
-In summary, the benefits of avoiding
-initialization-based non-determinism outweigh the increased
-complexity in the constraints due to the advances made in SMT
-solvers in these examples. In fact, the \symtxt{} algorithm can analyze certain types of programs with
-orders of magnitude greater efficiency than with \gsetxt{} or
-Lazier\#, while covering exactly the same control flow paths.
+In summary, the benefits of avoiding case-splitting based
+non-determinism outweigh the increased complexity in the constraints
+over heaps due to the advances made in SMT solvers in these
+examples. In fact, the \symtxt{} algorithm can analyze certain types
+of programs with orders of magnitude greater efficiency than with
+\gsetxt{} or Lazier\#, while covering exactly the same feasible
+control flow paths in the program.

### 2015-09-16 tex/lazy.tex
Updated exended paper to reflect VMCAI updates.

--- 2014-11-09 tex/lazy.tex
@@
-\section{Generalized Symbolic Execution}
+\section{GSE}
+\label{app:gse}
+This section introduces \gsetxt\ semantics on which \symtxt\ builds.
+GSE and its variants have the same non-deterministic choice given a reference to an uninitialized object; that reference can point to null, a new instance of an object with the correct type, or to an object of the same type that has been instantiated previously by GSE \cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}.
+The objects instantiated for new instances are referred to as the \emph{input heap}.
+Only these objects comprise the potential alias set when GSE encounters references to uninitialized objects.
+In general, the GSE search space branches at uninitialized objects, and the number of branches depends on the size of the input heap.
 
-Recall that in generalized symbolic execution (GSE) for lazy
-initialization of symbolic references consists of three key points of
-non-determinism where each symbolic reference can be initialized
-non-deterministically to null, a new instance of the symbolic
-reference, or aliases to symbolic references of the same type
-previously initialized. The initialization in GSE consists of creating
-branches in the execution tree for all the non-deterministic choices.
+The lazy initialization rules for GSE on the symbolic heap are in
+\figref{fig:lazyInit}: NULL, new, and alias.
+The rules rely on fresh references and locations that strictly increase so it is possible to minimize over a set to find the first created.
+Further, references are partitioned to support latter proofs: $\mathrm{init}_\cfgnt{r}()$ for the input
+  heap
+  ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
+  literals}
+  ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
+    literals}.
+  In general, as shown in the next section,
+  only input heap references appear in constraints to express potential aliasing, and only stack references appear in environments, expressions, or continuations.
+Finally, the \emph{isInit} function is true for initialized references from the input heap (i.e., potential aliases).
+
+How the lazy
+initialization is used is defined in \figref{fig:lazy} with the $\rgse$ relation collecting all the rules into a single relation on states.
+This relation is used later by the proof.
+GSE initialization takes place on the field-access rule in \figref{fig:lazy},
+using the $\rightarrow_I^*$ relation from \figref{fig:lazyInit}, to ensure the accessed field is
+instantiated. Initialization in GSE never
+happens for more than one object on any use of $\rightarrow_I^*$:
+the set $\Lambda$ is either empty or contains exactly one location.
+This property is an artifact of how GSE case splits when it instantiates: each choice is a new unique heap.
+This changes in the next section with the new symbolic initialization that collects all the choices into a single heap using guarded value sets.
+
+The rest of the rules in \figref{fig:lazy} do not initialize, but they are included to elucidate how symbolic initialization differs from GSE with lazy initialization.
+In particular, there is no branching in the search space on reference compare for GSE because references point to a single location after initialization.
+The new symbolic initialization using guarded value sets in this papers changes this behavior.
 

### 2015-09-16 tex/rw.tex
Updated exended paper to reflect VMCAI updates.

--- 2015-09-15 vmcai-2016-tex/rw.tex
@@
 including references and
-arrays~\cite{KiasanKunit,Cadar:2008,Deng:2007,Rosner:2015,Blackshear:2013,Filieri:2015}. However, \gsetxt{} techniques branch over
+arrays~\cite{KiasanKunit,Cadar:2008,Blackshear:2013,Filieri:2015}.
+Improvements to the basic lazy initialization algorithm have been proposed, including delaying aliasing choices~\cite{Deng:2007}, or checking initializations against invariants as they occur~\cite{Braione:2015,Rosner:2015}.
+However, these \gsetxt{} techniques branch over
 multiple copies of the system state during dereferencing operations,
@@
 Separation logic solvers can also reason about entailment which is a subject of future work for symbolic initialization.
-Solutions in separation logic do not lend themselves to test case generation is  goal in this work.
+Solutions in separation logic do not lend themselves to test case generation,  a goal of this work.
 

### 2015-09-16 tex/summary-heap.tex
Updated exended paper to reflect VMCAI updates.

--- 2015-09-14 vmcai-2016-tex/summary-heap.tex
@@
 \section{A Symbolic Heap}
+\label{sec:symheap}
 A \emph{symbolic heap}, as defined in this work, is a tuple

### 2015-09-17 tex/definitions.tex
Added defeq macro for definitions. Updated VS and ST function definitions, as well as summarize-precise figures. Changed bibliography style to get it to compile.

@@
 The set of \textbf{references} $\mathcal{R}$ is defined as the set of natural numbers
- $$\mathcal{R} = \mathbb{N}$$
+ $$\mathcal{R} \defeq{} \mathbb{N}$$
 \end{definition}
@@
 The set of \textbf{stack references} $\mathcal{R}_t$ is defined as
- $$\mathcal{R}_t =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 0\}$$. 
+ $$\mathcal{R}_t \defeq{}\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 0\}$$
 \end{definition}
@@
 The set of \textbf{input heap references} $\mathcal{R}_h$ is defined as
- $$\mathcal{R}_h =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 1\}$$. 
+ $$\mathcal{R}_h \defeq{}\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 1\}$$
 \end{definition}
@@
 The set of \textbf{new heap references} $\mathcal{R}_f$ is defined as
- $$\mathcal{R}_f =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$. 
+ $$\mathcal{R}_f \defeq{}\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$ 
 \end{definition}
@@
 \begin{align}
- f^\rightarrow &= \{ f(a) \mid a \in A\}\\
- f^\leftarrow &= \{ a \mid f(a) \in B \}
+ f^\rightarrow &\defeq{} \{ f(a) \mid a \in A\}\\
+ f^\leftarrow &\defeq{} \{ a \mid f(a) \in B \}
  \end{align}
@@
  \begin{align}
- f^\rightarrow [C] &= \{ f(a) \mid a \in C\}\\
- f^\leftarrow [D] &= \{ a \mid f(a) \in D \}
+ f^\rightarrow [C] &\defeq{} \{ f(a) \mid a \in C\}\\
+ f^\leftarrow [D] &\defeq{} \{ a \mid f(a) \in D \}
  \end{align}
@@
 \label{def:state}
-The set of \textbf{states} $\mathcal{S}$ is defined as the set of strings matching the pattern $s$ in \ref{fig:machine-syntax}.
+The set of \textbf{states} $\mathcal{S}$ is defined as the set of strings matching the pattern $s$ in \figref{fig:syntax}(b).
 \end{definition}
@@
 \begin{itemize}
-\item Field Access, $S_\mathit{FA} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}\ (\cfgnt{e} = \cfgnt{r}) \wedge \exists \cfgnt{f},\cfgnt{k}_0\ (\cfgnt{k} = \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}_0\rp) \}$
-\item Field Write,  $S_\mathit{FW} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}\ (\cfgnt{e} = \cfgnt{r}) \wedge \exists \cfgnt{x},\cfgnt{f},\cfgnt{k}_0\ (\cfgnt{k} = \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}_0\rp) \}$
-\item Equals, $S_\mathit{EQ} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}_0 (\cfgnt{e} = \cfgnt{r}_0) \wedge \exists r_1, k_1(\cfgnt{k} = \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}_1\rp \}$
-\item New, $S_\mathit{N} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{C}\ (\cfgnt{e} = \lp \cfgt{new}\ \cfgnt{C}\rp) \}$
+\item Field Access, $S_\mathit{FA} \defeq{} \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}\ (\cfgnt{e} = \cfgnt{r}) \wedge \exists \cfgnt{f},\cfgnt{k}_0\ (\cfgnt{k} = \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}_0\rp) \}$
+\item Field Write,  $S_\mathit{FW} \defeq{} \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}\ (\cfgnt{e} = \cfgnt{r}) \wedge \exists \cfgnt{x},\cfgnt{f},\cfgnt{k}_0\ (\cfgnt{k} = \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}_0\rp) \}$
+\item Equals, $S_\mathit{EQ} \defeq{} \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}_0 (\cfgnt{e} = \cfgnt{r}_0) \wedge \exists r_1, k_1(\cfgnt{k} = \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}_1\rp \}$
+\item New, $S_\mathit{N} \defeq{} \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{C}\ (\cfgnt{e} = \lp \cfgt{new}\ \cfgnt{C}\rp) \}$
 \end{itemize} 
@@
 \begin{definition}
-Given a sequence of states $$\Pi_n = s_0,s_1,...,s_n$$ where $$s_i = (\cfgnt{L}_i\ \cfgnt{R}_i\ \phi_i\ \eta_i\ \cfgnt{e}_i\ \cfgnt{k}_i )$$ the \textbf{control flow sequence} of $\Pi_n$ is the defined as the sequence of tuples $$ \pi_n = \mathbb{CF}(\Pi_n) = (\eta_0\ \cfgnt{e}_0\ \cfgnt{k}_0),(\eta_1\ \cfgnt{e}_1\ \cfgnt{k}_1),...,(\eta_n\ \cfgnt{e}_n\ \cfgnt{k}_n)$$
+Given a sequence of states $$\Pi_n = s_0,s_1,...,s_n$$ where $$s_i = (\cfgnt{L}_i\ \cfgnt{R}_i\ \phi_i\ \eta_i\ \cfgnt{e}_i\ \cfgnt{k}_i )$$ the \textbf{control flow sequence} of $\Pi_n$ is the defined as the sequence of tuples $$ \mathbb{CF}(\Pi_n) \defeq{} (\eta_0\ \cfgnt{e}_0\ \cfgnt{k}_0),(\eta_1\ \cfgnt{e}_1\ \cfgnt{k}_1),...,(\eta_n\ \cfgnt{e}_n\ \cfgnt{k}_n)$$
 \end{definition}
@@
 \label{def:homomorphism}
-A \textbf{homomorphism} $s_p \rightharpoonup_{h} s_q$, from state $s_p = ( \cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$ to state $s_q = ( \cfgnt{L}_q\ \cfgnt{R}_q\ \phi_q\ \eta_q\ \cfgnt{e}_q\ \cfgnt{k}_q )$, is defined as follows:
+A \textbf{homomorphism}, given the universe of field indices $\mathcal{F}$ and the universe of locations $\mathcal{L}$, is 
 $$
 \begin{array}{l}
- s_p \rightharpoonup_{h} s_q \Leftrightarrow \\
-\ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}( \exists \phi_\alpha\ (\exists \phi_\beta\ ( \\ 
-\ \ \ \ \ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow \\
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ \\
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  )) ) ) ) )
+ s_p \rightharpoonup_{h} s_q\ \defeq \ 
+\exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}\ ( \forall \phi_\alpha\ (\\ 
+\ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow \\
+\ \ \ \ \ \ \ \ \exists \phi_\beta\ ( (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ 
+ )) ) ) ) )
 \end{array}
 $$
-\begin{comment}
-$$
-\begin{array}{l}
-s_p \rightharpoonup_{h} s_q \Leftrightarrow \\
-\ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathit{fields}(\mathrm{type}(\cfgnt{l}_\beta))\ ( \\
-\ \ \ \ \ \ \ \ \ \ \ \ \forall (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f ))\ ( \\
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \exists \phi_\beta\ ((\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f )))))))\\
-\end{array}
-$$
-\end{comment}
 \end{definition}
@@
 \label{def:hc}
-Given the homomorphism $s_p \rightharpoonup_{h} s_q$, the \textbf{homomorphism constraint} $\mathbb{HC}(s_p \rightharpoonup_{h} s_q)$ is defined as:
-\begin{align*}
-\mathbb{HC}(s_p \rightharpoonup_{h} s_q) &= \\
+The \textbf{homomorphism constraint} is
+%\begin{align*}
+\[
+\mathbb{HC}(p \rightharpoonup_{h} q) \defeq
 \bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_p^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_q^\rightarrow)\}
-\end{align*}
-Where $\cfgnt{L}_p$ and $\cfgnt{L}_q$ are the locations maps from the heaps in $s_p$ and $s_q$.
+\]
+%\end{align*}
 \end{definition}
@@
 \label{representation}
-The \textbf{representation relation} $\sqsubset$ is defined as
-follows: given state $s_p = (
-\cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$
-and state $s_q = (
-\cfgnt{L}_q\ \cfgnt{R}_q\ \phi_q\ \eta_q\ \cfgnt{e}_q\ \cfgnt{k}_q )$,
-$s_p \sqsubset s_q $ if and only if $\eta_p = \eta_q ,\ \cfgnt{e}_p =
-\cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, the heaps are well-formed, and there exists a
-homomorphism $(\cfgnt{L}_p\ \cfgnt{R}_p) \rightharpoonup_{h}
-(\cfgnt{L}_q\ \cfgnt{R}_q)$ such that
-\begin{equation}
-\label{eqn:valid}
- \mathbb{S}( \phi_q \wedge \mathbb{HC}(s_p \rightharpoonup_{h} s_q) ) 
-\end{equation}
-The represented relation is extended to sets of states $P$ and $Q$ as
-$$
-P \sqsubset Q \Longleftrightarrow \forall q \in Q\ (\forall p\ (p \sqsubset q \Rightarrow p \in P))
-$$
+States $(p\ q)$ are in the \textbf{representation relation}, $p \sqsubset q$, if and only if, $\eta_p = \eta_q ,\ \cfgnt{e}_p =
+\cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, and there exists a
+homomorphism $p \rightharpoonup_{h} q$
+such that $\mathbb{S}( \phi_q \wedge \mathbb{HC}(s_p \rightharpoonup_{h} s_q) )$.
+The represented relation is extended to sets of states $P$ and a single state $q$ as
+$P \sqsubset q \defeq \forall p\ (p \sqsubset q \Leftrightarrow p \in P)$.
 \end{definition}
@@
 \label{def:meta}
-A state relation $p \rightarrow_x p^\prime$ is extended to sets of states $P \hookrightarrow_x P^\prime$ as
+Any state relation, say $\rightarrow_x^Y$, is extended to sets of states as
 $$
-P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
+P \hookrightarrow_x^Y P^\prime \defeq \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x^Y p^\prime \Leftrightarrow p^\prime \in P^\prime))
 $$

### 2015-09-17 tex/evaluation.tex
Added defeq macro for definitions. Updated VS and ST function definitions, as well as summarize-precise figures. Changed bibliography style to get it to compile.

@@
 %\subsection{Analysis}
-The \symtxt{} algorithm is implemented as an extension to the Symbolic
+The~\symtxt{} algorithm is implemented as an extension to the Symbolic
 PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13}
@@
 
-The \symtxt{} implementation uses \texttt{jConstraints} with the z3 solver \cite{ase2014-ghilrr,jpf2014-dghirr,deMouraBjorner08Z3}.
+The~\symtxt{} implementation uses the z3 solver with ~\texttt{jConstraints}~\cite{ase2014-ghilrr,jpf2014-dghirr,deMouraBjorner08Z3}.
 The implementation takes advantage of incremental solving and employs caching for performance since only small portions of the heap constraint changes during the search.

### 2015-10-26 vmcai-2016-tex/abstract.tex
Added in some of the changes suggested by VMCAI reviewers.

--- 2015-09-14 vmcai-2016-tex/abstract.tex
@@
 preserves GSE semantics. A correctness proof for the initialization
-scheme is provided with a proof-of-concept implementation. Results from an empirical evaluation on a standard set of \gsetxt{} benchmarks show an increase in the
+scheme is provided with a proof-of-concept implementation. Results from an empirical evaluation on a common set of \gsetxt{} data structure benchmarks show an increase in the
 size and number of analyzed heaps over existing GSE

### 2015-10-26 vmcai-2016-tex/lazy.tex
Added in some of the changes suggested by VMCAI reviewers.

@@
 \label{app:gse}
-GSE semantics are defined here to give insight to the new symbolic initialization approach and support the proof that the new approach preserves GSE behaviors.
+This section introduces \gsetxt\ semantics on which \symtxt\ builds.
 GSE and its variants have the same non-deterministic choice given a reference to an uninitialized object; that reference can point to null, a new instance of an object with the correct type, or to an object of the same type that has been instantiated previously by GSE \cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}.
@@
 In general, the GSE search space branches at uninitialized objects, and the number of branches depends on the size of the input heap.
+The function
+$\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) =
+\{\lp\phi\ \cfgnt{l}\rp\ ...\}$ returns constraint-location
+pairs where the field $\cfgnt{f}$ is uninitialized.
+
+\[
+\begin{array}{rcl}
+\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
+\end{array}
+\]
 
@@
 the set $\Lambda$ is either empty or contains exactly one location.
-This property is an artifact of how GSE case spits when it instantiates: each choice is a new unique heap.
+This property is an artifact of how GSE case splits when it instantiates: each choice is a new unique heap.
 This changes in the next section with the new symbolic initialization that collects all the choices into a single heap using guarded value sets.

### 2015-10-26 vmcai-2016-tex/summary-heap.tex
Added in some of the changes suggested by VMCAI reviewers.

@@
 a tuple indicating a class, $\cfgnt{C}$, and a method, $\cfgnt{m}$,
-where execution starts. For simplicity in presentation, booleans are the only primitive type, 
+where execution starts. For simplicity in presentation, Booleans are the only primitive type, 
 classes have only non-primitive fields, and methods have a single

### 2015-10-26 vmcai-2016-tex/approach.tex
Changes with Ben
Added forward references to VS and ST functions.

@@
 references.
+Rules relating to (ii) and (iii) are similar to previously proposed methods utilizing guarded value sets \cite{Sen:2014,Dillig:2011}.
+The rules for (i) are novel in how they  preserve \gsetxt\ semantics.
 
@@
 
+Certain rewrite rules depend on auxiliary on the relations in \defref{def:VS} and \defref{def:ST}, such as those in~\figref{fig:fHeap}.
 There are two rewrite rules in~\figref{fig:fHeap}, one for reading

### 2015-10-28 vmcai-2016-tex/approach.tex
Addressed reviewer concerns

@@
 
-\caption{Initializing fields, $s ::= \lp\cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\ \cfgnt{C}\rp$, with $s\rsum^*s^\prime =  s \rsum \cdots \rsum s^\prime \rsum s^\prime$.}
+\caption{Initializing fields, $s ::= \lp\cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\ \cfgnt{C}\rp$, with $s\rsum^*s^\prime =  s \rsum \cdots \rsum s^\prime$.}
 \label{fig:symInit}
@@
 
-In~\figref{fig:symInit}, given the uninitialized set $\Lambda$ for
+In~\figref{fig:symInit}, similar to before, given the uninitialized set $\Lambda$ for
 field $f$, the $\mathrm{min}_l$ function returns
-$(\phi_x\ \cfgnt{l}_x)$ based on a lexicographical ordering of
-uninitialized locations in $\Lambda$ to make initialization
-deterministic.  The set $\rho$ contains reference-location pairs that
+$(\phi_x\ \cfgnt{l}_x)$ which represents the earliest created uninitialized location in that set.  The set $\rho$ contains reference-location pairs that
 represent potential aliases, where $\mathrm{isInit}\lp\rp$ ensures that the references are initialized. 
@@
 
-Unlike the first three cases, which correspond directly to~\gsetxt{} initialization rules, case (iv) is unique to~\symtxt{}.
+Unlike the first three cases, which correspond directly to~\gsetxt{} initialization rules, $\theta_\mathit{orig}$, case (iv), is unique to~\symtxt{}.
 In this case, $\theta_\mathit{orig}$ implements conditional initialization to preserve the original heap structure.
-This step is necessary in order to maintain homomorphism\footnote{Homomorphism is an important property relied on by the correctness proof.} between symbolic heaps created using~\symtxt{} and the~\gsetxt{} heaps they are intended to represent.
+This step is necessary in order to maintain \emph{homomorphism} (i.e., equivalent shapes) between symbolic heaps created using~\symtxt{} and the~\gsetxt{} heaps they are intended to represent.
 The sets from each of the four cases are added into the heap on $\cfgnt{r}_f$ after the fields
@@
 reference superscripts $s$ and $i$ indicate the partition containing
-the reference.  In~\figref{fig:initHeap}, $\cfgnt{r}_0^s$ represents a
+the reference: input, auxiliary, or stack.  In~\figref{fig:initHeap}, $\cfgnt{r}_0^s$ represents a
 stack reference for the $\cfgt{this}$ variable which has two fields
@@
 in~\figref{fig:initHeap}(d) represents the various sets constructed in
-the initialization $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$.
+the initialization for $\lp\cfgt{this}\ \cfgt{\$}\ \cfgnt{y}\rp$.
 
@@
 
-Certain rewrite rules depend on auxiliary on the relations in \defref{def:VS} and \defref{def:ST}, such as those in~\figref{fig:fHeap}.
 There are two rewrite rules in~\figref{fig:fHeap}, one for reading
@@
 performed on a non-null location. The field-access rewrite rule
-in~\figref{fig:fHeap} dereferences a field of type $\cfgnt{C}$ and
-uses \figref{fig:symInit}, to get a new symbolic heap that is
+in~\figref{fig:fHeap} dereferences a field of type $\cfgnt{C}$, recall that the heaps are type consistent and programs are type safe, and
+uses the $\rsum^*$ relation from \figref{fig:symInit}, to get a new symbolic heap that is
 initialized on the field $\cfgnt{f}$. The symbolic heap is further
@@
 
-Strengthening in the field write creates a value set that contains two
+Strengthening in the field write creates a value set, \cfgnt{X},  that contains two
 types of locations: those for the case where the write is feasible
-(the first call), and those for the case where it is not (the second
-call). In the case that $\phi$ is true then $\cfgnt{r}_\mathit{cur}$
+(the first call in \cfgnt{X}), and those for the case where it is not (the second
+call in \cfgnt{X}). In the case that $\phi$ is true then $\cfgnt{r}_\mathit{cur}$
 will point to the guarded value set $\cfgnt{L}(\cfgnt{r})$.
@@
 returns true when two references $\cfgnt{r}_0$ and $\cfgnt{r}_1$
-\emph{can} be equal. Intutively, $\Phi_\alpha$ contains all
+\emph{can be equal}. Intuitively, $\Phi_\alpha$ contains all
 constraints under which $\cfgnt{r}_0$ and $\cfgnt{r}_1$ may point to

### 2015-10-28 vmcai-2016-tex/bisimulation.tex
Redefined some equals instances.
Addressed reviewer concerns

@@
 The theorems in this section establish the soundness and
-completeness of the symbolic heap approach with respect to Generalized
-Symbolic Execution (\gsetxt{}). Intuitively, the theorems imply that any properties proven
-with~\gsetxt{} can also be proved using the~\symtxt{}
+completeness of the symbolic heap approach with respect to \gsetxt{}. Intuitively, the theorems imply that any properties proven
+with~\gsetxt{} can also be proven using the~\symtxt{}
 algorithm. What follows is a brief description of the requisite terminology,
 followed by the theorem statements. The proofs for the theorems, as well as
-the complete set of semantic rules for~\gsetxt{} and~\symtxt{} can
-be found in ~\cite{Hillery:2015}.
+the complete set of semantic rules for~\gsetxt{} and~\symtxt{} are in ~\cite{Hillery:2015}.
 
@@
 unless at \cfgt{end}. Let $p \rgse p^\prime$ be a union over relations
-for~\gsetxt{} (see~\cite{Hillery:2015}): $\rgse = \rgse^\mathit{A} \cup
+for~\gsetxt{}: $\rgse = \rgse^\mathit{A} \cup
 \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup
@@
 else in the language. Any state relation, say $\rightarrow_x^Y$, is
-trivially extended to sets of states as
+extended to sets of states as
 $$
@@
 $$
-\rsgse = \hookrightarrow_\gse^\mathit{A}
+\rsgse \defeq \hookrightarrow_\gse^\mathit{A}
 \cup \hookrightarrow_\gse^\mathit{A^\prime} \cup \hookrightarrow_\gse^\mathit{W} \cup
@@
 \begin{array}{l}
- s_p \rightharpoonup_{h} s_q \defeq
+ s_p \rightharpoonup_{h} s_q\ \defeq \ 
 \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}\ ( \forall \phi_\alpha\ (\\ 
@@
 
-In the following lemma, $S$ is the universe of well-formed states, and $S_{FA} \subseteq S$ is the set of states at a field access continuation having computed the base reference.
+In the following lemma, $S$ is the universe of well-formed states, and $S_{\mathit{FA}} \subseteq S$ is the set of states at a field access continuation having computed the base reference.
 \begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
@@
 
-Similar lemmas are proved for field write and equals reference. These
-require additional lemmas on the summarize machine
+Similar lemmas are proven for field write and equals reference. These
+require additional lemmas on the initialization relation
 $\rightarrow_S$: that it preserves determinism, the
-homomorphism, and the satisfiability of the homomorphism constraint
+homomorphism, and the satisfiability of the homomorphism constraint.
 

### 2015-10-28 vmcai-2016-tex/conclusion.tex
Addressed reviewer concerns

@@
 
-This work presents a
-heap representation for symbolic execution that maintains exactness,
-represents arbitrary heap structures without restrictions on aliasing
-relationships, and supports dynamic on-the-fly initialization of heap
-structures. This unique combination of capabilities enables the
-symbolic heap algorithm to outperform state-of-the-art symbolic
-execution techniques, and in some cases, the performance gains are
-considerable. The performance gains in symbolic execution
-may naturally benefit a variety of analyses based on symbolic
-execution, for example, verification of properties, especially those
-related to the heap, test case generation, program evolution
-techniques such as directed incremental symbolic
-execution~\cite{person:pldi2011}, and other back-end analyses. Potential future work includes evaluating the impact of analyses that rely on
-symbolic execution.
+This paper presents a \symtxt{} algorithm for uninitialized
+references in a fully symbolic heap. Where GSE lazily instantiates
+uninitialized references to either NULL, a new instance of the correct
+type, or an alias to a previously initialized object, the symbolic
+initialization in this work creates a guarded value set expressing all
+of these eventualities in the same symbolic heap. The paper includes a proof that the
+\symtxt{} algorithm is sound and complete with respect to properties
+provable by GSE.
+
+An initial implementation of the technique has been done within the
+Java PathFinder framework. The \symtxt{} algorithm outperforms
+state-of-the-art case-splitting based symbolic execution techniques,
+and in some cases, the performance gains are considerable in a set of
+common Java data structure artifacts used to benchmark symbolic representations. The performance gains in symbolic
+execution may naturally benefit a variety of analyses based on
+symbolic execution, for example, verification of properties,
+especially those related to the heap, test case generation, program
+evolution techniques such as directed incremental symbolic
+execution~\cite{person:pldi2011}, and other back-end
+analyses. Potential future work includes evaluating the impact of
+analyses that rely on symbolic execution and solving the problem of detecting heap entailment.
 

### 2015-10-28 vmcai-2016-tex/evaluation.tex
Addressed reviewer concerns

@@
 %\begin{figure*}[t]
+%\end{figure*}
+
+%\subsection{Analysis}
+The \symtxt{} algorithm is implemented as an extension to the Symbolic
+PathFinder (SPF)
+framework~\cite{DBLP:journals/ase/PasareanuVBGMR13}. In addition to the operations presented in this paper, the
+implementation contains support for operations over integers,
+calculating per-path preconditions and postconditions, as well as
+generating test input heaps that exercise all feasible control flow
+paths. Future work is adding support for floating point
+operations, arrays, and bit-operations.
+
+The \symtxt{} implementation uses \texttt{jConstraints} with the z3 solver \cite{ase2014-ghilrr,jpf2014-dghirr,deMouraBjorner08Z3}.
+The implementation takes advantage of incremental solving and employs caching for performance since only small portions of the heap constraint change during the search.
+
+SPF includes an implementation of~\gsetxt{} with lazy initialization.
+In recent work, we implemented the Lazier and Lazier\# algorithms in
+SPF~\cite{Hillery:2014}; these constitute the state of art approaches
+to case-splitting based lazy initialization techniques. The goal of our
+experiment is to evaluate the efficacy of our approach with respect to these
+other techniques for symbolic execution of programs
+with unbounded complex data input. The empirical study tries to answer the following research question:
+How does the cost of the \symtxt{} algorithm compare with that of the \gsetxt{} and Lazier\# algorithms?
+
+The \emph{independent} variable in the study is the $k$-bound;
+$k$-bounding bounds the length of a reference chain from the root of
+the heap~\cite{Deng:2006}.  The study selects three dependent variables and
+measures: (i) time, (ii) states explored, and (iii)
+paths generated. The \emph{time} is the total time taken by each
+algorithm to explore the symbolic execution tree as well as total
+constraint solving time. The \emph{states explored} represents the
+number of nodes in the symbolic execution tree, and the \emph{paths
+  generated} represents the number of unique paths in the symbolic
+execution tree.
+
+The data structures evaluated are a standard set that is commonly used in
+analyses involving heap-manipulating
+programs~\cite{Deng:2006,Deng:2007,boyapati2002korat,Ferrara:2014,Rosner:2015},
+including a linked list, binary search tree, and red/black tree. The actual tests
+use a repOk() method (a class invariant) for data structures in
+object-oriented code to generate valid inputs for the methods under
+test via symbolic execution~\cite{boyapati2002korat,visser2004test}. Note that this
+allows us to have precision in checking properties of the heap that is
+not possible in static analysis based techniques (i.e., the symbolic execution generated heaps satisfy the repOK() invariant)~\cite{Dillig:2011}.
+
 \begin{table*} [t]
@@
 
-%\end{figure*}
-
-%\subsection{Analysis}
-The \symtxt{} algorithm is implemented as an extension to the Symbolic
-PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13}
-framework. In addition to the operations presented in this paper, the
-implementation contains support for operations over integers,
-calculating per-path preconditions and postconditions, as well as
-generating test input heaps that exercise all feasible control flow
-paths. Future work is adding support for floating point
-operations, arrays, and bit-operations.
-
-The \symtxt{} implementation uses \texttt{jConstraints} with the z3 solver \cite{ase2014-ghilrr,jpf2014-dghirr,deMouraBjorner08Z3}.
-The implementation takes advantage of incremental solving and employs caching for performance since only small portions of the heap constraint changes during the search.
-
-SPF includes an implementation of~\gsetxt{} with lazy initialization.
-In recent work, we implemented the Lazier and Lazier\# algorithms in
-SPF~\cite{Hillery:2014}; these constitute the state of art approaches
-case-splitting based lazy initialization techniques. The goal of our
-experiment is to evaluate the efficacy of our approach with respect to
-other state-of-the-art techniques for symbolic execution of programs
-with unbounded complex data input. We empirically evaluate the
-\symtxt{} algorithm by considering the following research question:
-How does the cost of the \symtxt{} algorithm (SL) compare with that of
-\gsetxt{} (GSE), Lazier, Lazier\#(L\#) algorithms?
-
-The \emph{independent} variable in our study is the $k$-bound;
-$k$-bounding bounds the length of a reference chain from the root of
-the heap~\cite{Kiasan06}.  We select three dependent variables and
-measures for our study: (i) time, (ii) states explored, and (iii)
-paths generated. The \emph{time} is the total time taken by each
-algorithm to explore the symbolic execution tree as well as total
-constraint solving time. The \emph{states explored} represents the
-number of nodes in the symbolic execution tree, and the \emph{paths
-  generated} represents the number of unique paths in the symbolic
-execution tree.
-
-The data structures evaluated are a standard set commonly used in
-analyses involving heap-manipulating
-programs~\cite{Deng:2006,Deng:2007,boyapati2002korat,Ferrara:2014,Rosner:2015},
-including a linked list, binary search tree, and red/black tree. We
-use a repOk() method (a class invariant) for data structures in
-object-oriented code~\cite{boyapati2002korat}. The repOk() methods
-provide a mechanism to generate valid inputs for the methods under
-test; symbolic execution has been used to generate test inputs using
-repOk() methods in~\cite{visser2004test}. In this work, we define and
-use repOk() methods to generate valid heaps with the appropriate
-$k$-bounds before executing the methods under test. Note that this
-allows us to have precision in checking properties of the heap that is
-not possible in static analysis based techniques~\cite{Dillig:2011}.
-
 The results of the experiments are presented in
@@
 algorithm. The headings \gsetxt{}, L\#, and SL correspond to the GSE,
-Lazier\#, and \symtxt{} algorithms, respectively. The results for the
-Lazier algorithm are omitted because they are nearly identical to the
-Lazier\# results for these artifacts. A table entry of '-' indicates
+Lazier\#, and \symtxt{} algorithms, respectively. A table entry of '-' indicates
 the analysis exceeded the allotted time bound of 1 hour.
@@
 exponentially for case-splitting techniques with a monotonic increase
-in $k$, resulting a corresponding exponential increase in analysis
-times . This is event in all the examples in
+in $k$, resulting in a corresponding exponential increase in analysis
+times. This is evident in all the examples in
 Table~\ref{tab:results}. The GSE and L\# algorithms are unable to
@@
 for BinarySearchTree at $k$=3, to $118x$ for LinkedList at $k$=6. In
-fact, for some $k$-bounds a number of experiments complete exploration
+fact, for some $k$-bounds, a number of experiments complete exploration
 using the \symtxt{} algorithm in a few seconds whereas \gsetxt{} or
@@
 
-The number of path explored by \symtxt{} algorithm are strictly less
+The number of path explored by the \symtxt{} algorithm are strictly less
 than or equal to the number of paths explored by \gsetxt{} for all the
-evaluated artifacts. We can use this result to do more efficient test
-case generation. From a generated path and corresponding symbolic heap
-we can use the solutions provided by the constraint solver to
-instantiate a set of concrete heaps to provide as test input. These
+evaluated artifacts. This result means it is possible to do more efficient test
+case generation by using the generated path and corresponding symbolic heap
+solutions provided by the constraint solver to
+instantiate a set of concrete heaps. These heaps
 provide a smaller test suite to achieve control-flow path coverage as
 compared to GSE and Lazier\#. Note that the ability to perform test
-input generation is another advantage of \symtxt{} technique over
+input generation is another advantage of the \symtxt{} technique over
 static analysis approaches.
@@
 TreeMap, state counts for Lazier\# and the \symtxt{} algorithm may
-exceed those for \gsetxt{}. We observed that the additional states
+exceed those for \gsetxt{}. Observe that the additional states
 generated by the summary heap algorithm are unsatisfiable at the point
 of reference compares; this is why they do not contribute any
-additional branches in the final symbolic execution tree. Furthermore,
+additional branches in the final symbolic execution tree. More critically,
 the larger state count and the corresponding satisfiability checks on
@@
 examples. In fact, the \symtxt{} algorithm can analyze certain types
-of programs with orders of magnitude greater efficiency than with
+of programs with orders of magnitude greater efficiency than that of
 \gsetxt{} or Lazier\#, while covering exactly the same feasible

### 2015-10-28 vmcai-2016-tex/lazy.tex
Addressed reviewer concerns

@@
 The function
-$\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) =
+
+The lazy initialization rules for GSE on the symbolic heap are in
+\figref{fig:lazyInit}: NULL, new, and alias.
+The symbol $\cfgnt{C}$ represents a type (or class) while $\mathit{fields}\lp \mathrm{C}\rp$ returns the fields in the type.
+The function $\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) =
 \{\lp\phi\ \cfgnt{l}\rp\ ...\}$ returns constraint-location
 pairs where the field $\cfgnt{f}$ is uninitialized.
-
   \[
@@
 \]
+The function $\mathbb{S}\lp \phi \wedge \phi^\prime \rp$ returns true
+if there is a satisfying assignment of references for $\phi \wedge
+\phi^\prime$; otherwise it returns false.
 
-The lazy initialization rules for GSE on the symbolic heap are in
-\figref{fig:lazyInit}: NULL, new, and alias.
-The rules rely on fresh references and locations that strictly increase so it is possible to minimize over a set to find the first created.
+The rules rely on fresh references and locations that strictly increase so it is possible to minimize over a set to find the first created (i.e., references and locations are ordered).
+As such, the $\mathrm{min}_l$ function is able to return $(\phi_x\ \cfgnt{l}_x)$ the earliest created uninitialized location in a set, and similarly, $\mathrm{min}_r$ is able to return the earliest created reference in a set.
 Further, references are partitioned to support latter proofs: $\mathrm{init}_\cfgnt{r}()$ for the input
@@
 initialization is used is defined in \figref{fig:lazy} with the $\rgse$ relation collecting all the rules into a single relation on states.
-This relation is used later by the proof.
 GSE initialization takes place on the field-access rule in \figref{fig:lazy},
@@
 the set $\Lambda$ is either empty or contains exactly one location.
-This property is an artifact of how GSE case splits when it instantiates: each choice is a new unique heap.
+This property is an artifact of how GSE case splits when it instantiates: each choice, NULL, new, or an alias, is a new unique heap.
 This changes in the next section with the new symbolic initialization that collects all the choices into a single heap using guarded value sets.
+The field-write rule also uses $\theta$ to represent a set of constraint-location pairs, which in GSE, again should always be a singleton set for the same reason as previously mentioned.
 

### 2015-10-28 vmcai-2016-tex/rw.tex
Addressed reviewer concerns

@@
 %GSE
-Symbolic initialization also draws inspiration from lazy initialization, the core idea of generalized symbolic execution (\gsetxt{})\cite{GSE03}.
+Symbolic initialization also draws inspiration from lazy initialization, the core idea of \gsetxt{}\cite{GSE03}.
 Several projects have used lazy initialization to conduct symbolic execution on programs with more general types,
 including references and
-arrays~\cite{KiasanKunit,Cadar:2008,Deng:2007,Rosner:2015,Blackshear:2013,Filieri:2015}. However, \gsetxt{} techniques branch over
+arrays~\cite{KiasanKunit,Cadar:2008,Blackshear:2013,Filieri:2015}.
+Improvements to the basic lazy initialization algorithm have been proposed, including delaying aliasing choices~\cite{Deng:2007}, or checking initializations against invariants as they occur~\cite{Braione:2015,Rosner:2015}.
+However, these \gsetxt{} techniques branch over
 multiple copies of the system state during dereferencing operations,
@@
 PEX and SAGE use array theories to represent program state instead of guarded value sets.
-SAGE has been proven complete for programs whose memory allocations are independent of their inputs.
-This work is complementary to PEX and SAGE, and we believe could be leveraged to further improve those tools.
+SAGE has been proven complete for programs whose memory allocations are independent of their inputs. This work is complementary to PEX and SAGE and could be leveraged to further improve those tools.
 
@@
 Separation logic solvers can also reason about entailment which is a subject of future work for symbolic initialization.
-Solutions in separation logic do not lend themselves to test case generation is  goal in this work.
+Solutions in separation logic do not lend themselves to test case generation which is a contribution of the new approach in this paper.
 

### 2015-10-30 tex/proofs.tex
Brought in abstract, intro, and related work from CAV paper.
Removed apppendix and references. Fixed bib.

@@
 \section{Proofs}
+\label{sec:proofs}
 \subsection{Lemmas}
@@
 
-We have now shown that there exists a mapping $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ for all $\cfgnt{l}_{\gse^\prime} \in \cfgnt{L}_{p}^\prime^\rightarrow$ such that:
+We have now shown that there exists a mapping $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ for all $\cfgnt{l}_{\gse^\prime} \in \cfgnt{L}_{p}^{\prime^\rightarrow}$ such that:
 $$ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_{\gse^\prime},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_{\gse^\prime},f )) $$

### 2015-10-30 vmcai-2016-tex/summary-heap.tex
Addressed reviewer concerns
Removed apppendix and references. Fixed bib.

@@
 
-The path condition is a predicate of the program variables. The environment is a partial function so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
+The path condition is a predicate of references in the heap. The environment is a partial function so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
 $\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation
@@
 are italicized. Ellipses indicate zero or more repetitions. Tuples
-omit the commas for compactness.
+omit the commas for compactness. The language only considers objects as values and does not support looping structures to focus the discussion on the symbolic heap representation.
 
@@
 The rewrite relations for the more mundane portions of the language
-that do not update the symbolic heap are in the appendix with more details in 
+that do not update the symbolic heap are in 
 \cite{Hillery:2015}. Excepting \textrm{N{\footnotesize EW}}, the rules do not update
